### 2016-06-27 2nd_round_comments/DVCS-CAN-Meeting-Comments.tex
Added a folder for the second round comments

\section*{\centering{Summary of April 13, 2016 phone conference and requests from the NP-PWG review committee
M. Garcon, S. Kuhn and Zein-Eddine Meziani\\ 
to M. Hattawi and co-authors}}

\begin{enumerate}
\item RTPC calibration: all previous questions are considered answered 
satisfactorily. Remains a significant effort to rewrite the corresponding 
section(s) more clearly.

\item Event selection cuts: the committee acknowledges the numerous studies 
(variation of cuts) that have been performed. It is not fully convinced, 
however, that there is no remaining background (other than $\pi^{0}$s only) in 
either channel, and about the argument on the statistics (for cutting tails).  
Consequently, it is requested:
\begin{enumerate}
\item To show plots of correlations between exclusivity cuts:
\begin{enumerate}
  \item 2D missing $ep\gamma X$ M2 vs $\Delta \phi$: is there a gain to be 
     expected by a contour cut? If yes, implement. Shown in figure 
     \ref{fig:2d_delta_phi_MM2_InCoh}
    \begin{figure}[!h]
    \includegraphics[height=5.6cm]{fig/delta_phi_epgamma_M2_Mis.png}
    \includegraphics[height=5.6cm]{fig/delta_phi_epgamma_M2_Mis_with.png}
    \caption{ $\Delta \phi$ vs. $MM^{2}_{ep\gamma X}$ before (left) and 
    after (right) the exclusivity cuts.}
    \label{fig:2d_delta_phi_MM2_InCoh}
    \end{figure}

  \item Produce all 9 plots in right figure of slides 5 and 9 of \url{ 
     https://clasweb.jlab.org/rungroups/lowq/wiki/images/a/a0/ExcluCuts-CANeg6.pdf}   
     for a 2$\sigma$ and 1$\sigma$ cuts on missing $ep\gamma X$ M2.
    \begin{figure}[tbp]
    \includegraphics[height=14.6cm]{fig/all_sigmas_coh_exc_cuts.pdf}
    \caption{Coherent exclusivity distributions for the different cut 
    width on $e^{4}He\gamma X$ missing mass squared. }
    \label{fig:2d_delta_phi_MM2_InCoh}
    \end{figure}                                                                  
    \begin{figure}[tbp]
    \includegraphics[height=14.6cm]{fig/all_sigmas_incoh_exc_cuts.pdf}
    \caption{ Incoherent exclusivity distributions for the different cut  
    width on $ep\gamma X$ missing mass squared.}
    \label{fig:2d_delta_phi_MM2_InCoh}
    \end{figure}

    \end{enumerate}
\item (optionally) In the incoherent case, extract ALU with 2 variations of the 
   ep missing M2 right cut, moving it tighter to the left (e.g.  1 and 0.75 
   GeV2).  (also see the evolution of the other distributions when doing so).
\end{enumerate}

\item Free proton asymmetries from FX's publication: implement a (possibly 3D/9 
points) interpolation to smooth out both statistical fluctuations and 
kinematical dependences. Reintroduce a corresponding section in the CAN. Take 
into account both stat. and syst. errors of both experiments in the ratio. The 
committee recommends though to be cautious about the statements on the 
asymmetry ratios in the future publication.

\item CFF: the committee acknowledges that the new procedure (2-parameter fit 
with complete formula at leading-twist) is more satisfying. It recommends 
though to be cautious about the statements on CFF in the future publication.

\item CAN: a number of answers to previous questions have to appear in the CAN.  
This includes (but may not be limited to)

Figs 1-4 of \url{https://clasweb.jlab.org/rungroups/lowq/wiki/images/a/a3/Final_1st_round_comments.pdf} 
Tighter $edist$ cut [-2,+3 mm].
Otherwise, even if you do not show it in the CAN, mention in one line that a 
specific study was done.
\item Miscellaneous:
   \begin{enumerate}
      \item 4-D dependences of the ratio R: the statement that the integrated R's 
    are flat is disputable (see Figs 4.16 and 4.17), but we are ready to accept 
    that the effect discussed is small and taken care of in the systematic 
    errors.
 \item not convinced that comparing 9 phi-bins to 11 is a definitive answer, 
    when not applying any finite bin size correction. But again, in view of the 
    size of statistical and systematic errors, would accept that.
 \item Your Eq.(4) of "answer" is probably wrong. For our own understanding, 
   look into this argument again.
\item ...
   \end{enumerate}

\item Please keep a record of the changes in the CAN, as we will probably not 
re-read the whole text.

\item Request to see the very first draft of the publication.
\end{enumerate}

### 2016-06-27 analysis-note-v2/Appendix.tex
added the second version of the analysis note

\appendix
\chead[]{\let\uppercase\relax\leftmark}

%\chapter{Appendix}
\chapter{$e ~^4He \rightarrow e ~^4He ~\gamma$ cross section} \label{app:Helium_cross_section}
The differential cross section for a longitudinally-polarized electron beam ($\lambda$) and an unpolarized $^4$He target can written as:
\small
\begin{equation}
\frac{d^{5}\sigma_{\lambda}}{dx_{A} dQ^{2} dt d\phi_{e} d\phi} = 
\frac{\alpha^{3}}{16 \pi^{2}} \frac{x_{A} \, y^{2}}{Q^{4} \sqrt{1 + \epsilon ^{2}}} 
\frac{
|\mathcal{T}_{BH}|^{2} + |{\mathcal{T}}_{DVCS}^{\lambda}|^{2} + {\mathcal{I}}_{BH*DVCS}^{\lambda}}{e^{6}}
\label{eq:sigdiff}
\end{equation}
\normalsize
where $y = \frac{p \cdot q}{p \cdot k}$, $\epsilon  =  \frac{2 x_{A} M_{A}}{Q}$ 
and $x_A  =  \frac{Q^2}{2 p \cdot q}$. The different amplitudes can be written 
as \cite{BM_2009}:
\small
\begin{equation}
|\mathcal{T}_{BH}|^{2} =  
\frac{e^{6} (1 + \epsilon^{2})^{-2}}{x^{2}_{A} y^{2} t \mathcal{P}_{1}(\phi) \mathcal{P}_{2}(\phi)} \left[ c_{0}^{BH} + c_{1}^{BH} \cos(\phi) + c_{2}^{BH} \cos(2\phi)\right] 
\label{TTBH}
\end{equation}

\begin{equation}
|\mathcal{T}_{DVCS}|^{2} =  \frac{e^{6}}{y^{2} Q^{2}} \left[ c_{0}^{DVCS} + \sum_{n=1}^{2} \Bigg( c_{n}^{DVCS} \cos(n \phi) + \lambda s_{n}^{DVCS} \sin(n \phi)\Bigg) \right] 
\label{TTDVCS}
\end{equation}

\begin{equation}
\mathcal{I}_{BH*DVCS} =  \frac{\pm e^{6}}{x_A y^{3} t \, \mathcal{P}_{1}(\phi) 
\mathcal{P}_{2}(\phi)} \left[ c_{0}^{I} + \sum_{n=0}^{3} \Bigg( c_{n}^{I} \cos(n \phi) + \lambda s_{n}^{I} \sin(n \phi) \Bigg) \right] 
\label{TTinter} 
\end{equation}
\\
\normalsize
where $\mathcal{P}_{1}(\phi)$ and $\mathcal{P}_{2}(\phi)$ are BH propagators and defined as:
\small
\begin{align}
&\mathcal{P}_{1}(\phi) = \frac{(k - q')^{2}}{Q^{2}} = - \frac{1}{y (1 + \epsilon^{2})} 
\big[ J + 2 K \cos(\phi) \big] \\
&\mathcal{P}_{2}(\phi) = \frac{(k - \Delta)^{2}}{Q^{2}} = 1 + \frac{t}{Q^{2}} + 
\frac{1}{y (1 + \epsilon^{2})} \big[ J + 2 K \cos(\phi) \big]
\end{align}
~~~~~~~~~~~with,
\begin{align}
& J = \bigg( 1 - y - \frac{y \epsilon^{2}}{2} \bigg) \bigg(1 + \frac{t}{Q^{2}} \bigg) - 
(1 - x_{A})(2 - y) \frac{t}{Q^{2}} \\
& K^{2} = - \delta t \, (1 - x_{A}) \bigg( 1 - y - \frac{y^{2} \epsilon^{2}}{4} \bigg) 
\bigg\{ \sqrt{1 + \epsilon^{2}} + \frac{4 x_{A} (1-x_{A}) + \epsilon^{2}}{4 (1 - x_{A})}
\delta t \bigg\} \\
& \delta t = \frac{t - t_{min}}{Q^{2}} = \frac{t}{Q^{2}} + \frac{2(1-x_{A}) \left(1- \sqrt{1 + 
\epsilon^{2}} \right) + \epsilon^{2}}{4 x_{A} (1- x_{A}) + \epsilon^{2}}
\end{align}
\normalsize
where $t_{min}$ represents the kinematic boundary of the process and defined as:
\small
\begin{equation}
t_{min} = Q^2 \frac{2(1-x_A)(1 - \sqrt{1+\epsilon^2}) + \epsilon^2}{4 x_A(1-x_A) + \epsilon^2}
\end{equation}
\normalsize
The Fourier coefficients, in equations \ref{TTBH}, \ref{TTDVCS} and \ref{TTinter}, of a spin-0 target are defined as:
\small
\begin{eqnarray}
c_0^{BH} = & \bigg[ & \left\{ {(2-y)}^2 + y^2{(1+\epsilon^2)}^2 \right\} 
\left\{ \frac{\epsilon^2 Q^2}{t} + 4 (1-x_A) + (4x_A+\epsilon^2) \frac{t}{Q^2} 
\right\} \nonumber \\
& \phantom{\bigg[} & + 2 \epsilon^2 \left\{ 4(1-y)(3+2\epsilon^2) + y^2(2-\epsilon^4) 
\right\} - 4 x_A^2{(2-y)}^2 (2+\epsilon^2) \frac{t}{Q^2} \nonumber \\
& \phantom{\bigg[} & + 8 K^2 \frac{\epsilon^2 Q^2}{t} \,\,\,\,\,\,\, \bigg] F_A^2(t)  \\
c_1^{BH} = & \phantom{\bigg[} & -8 (2-y) K \left\{ 2 x_A + \epsilon^2 - 
\frac{\epsilon^2 Q^2}{t} \right\} F_A^2(t)  \\
c_2^{BH} = & \phantom{\bigg[} & 8 K^2 \frac{\epsilon^2 Q^2}{t} F_A^2(t) 
\end{eqnarray} 
\normalsize
where $F_A(t)$ is the electromagnetic form factor of the $^4$He. At leading twist, the $|\mathcal{T}_{DVCS}|^{2}$ writes as a function of only one CFF according to
\small
\begin{equation}
%c_0^{DVCS} = 2 (2-2y+y^2) \, {\mathcal H}_A {\mathcal H}^{\star}_A 
   c_0^{DVCS}= 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + \epsilon^2} \, 
   {\mathcal H}_A {\mathcal H}^{\star}_A 
   \label{eq:c0DVCS}
\end{equation}
\normalsize
and the interference amplitude coefficients are written as:
\small
\begin{equation}
s_{1}^{INT} = F_{A}(t) \Im m(\mathcal{H}_{A}) S_{++}(1),
\end{equation}
with
\begin{eqnarray}
   S_{++}(1) &=& \frac{-8K(2-y)y}{1+\epsilon^2} \left( 1 + 
\frac{1-xA+\frac{\sqrt{1+\epsilon^2}-1}{2}}{1+\epsilon^2} 
\frac{t-t_{min}}{Q^{2}} \right) \cdot F_{A}(t) \label{eq:s1I}
\end{eqnarray}

%c_0^{INT} & = & - 8 (2 - y) \frac{t}{Q^2} F_A \, \Re e \{{\mathcal H}_A\} 
%\label{eq:c0I} \\
% & \times & \left\{ (2-x_A)(1-y) - (1-x_A){(2-y)}^2 \left( 1 - 
% \frac{t_{min}}{Q^2} \right) \right\} \nonumber \\

%c_1^{INT} & = & 8 K (2y-y^2-2) F_A \, \Re e \{{\mathcal H}_A\} \label{eq:c1I}

\begin{eqnarray}
\small
c_0^{INT} &=& F_A(t) \Re e(\mathcal{H}_{A}) C_{++}(0),
\end{eqnarray}
with \begin{eqnarray}  C_{++}(0) &=&
\frac{-4(2-y)(1+\sqrt{1+\epsilon^{2}})}{(1+\epsilon^{2})^2}  \bigg\{ 
   \frac{\widetilde{K}^2}{Q^2}  \frac{(2-y)^2}{\sqrt{1+\epsilon^{2}}} \, \\
   &+& \frac{t}{Q^2}  \left( 1 - y - \frac{\epsilon^2}{4} y^2 \right)  
(2-x_{A}) \left(  1 + \frac{2x_A(2-x_A + \frac{\sqrt{1+\epsilon^{2}}-1}{2} + 
\frac{\epsilon^{2}}{2x_A})\frac{t}{Q^2} + \epsilon^{2}}{(2-x_A) 
(1+\sqrt{1+\epsilon^{2}})}  \right)  \bigg\} \nonumber
 \label{eq:c0I} 
 \end{eqnarray}

\begin{eqnarray}
   c_1^{INT} &=&  F_A(t) \Re e(\mathcal{H}_{A}) C_{++}(1),
\end{eqnarray}
with

   \begin{eqnarray}
   C_{++}(1) &=&
   \frac{-16K(1-y+\frac{\epsilon^{2}}{4}y^2)}{(1+\epsilon^{2})^{5/2}}\bigg\{\left(1+(1-x_A)\frac{\sqrt{1+\epsilon^{2}}-1}{2x_A} 
   + \frac{\epsilon^{2}}{4x_A}\right) 
\frac{x_At}{Q^2}-\frac{3\epsilon^{2}}{4.0} \bigg\} \nonumber \\&-& 4K \left( 
2-2y+y^2+\frac{\epsilon^{2}}{2}y^2\right)\frac{1+\sqrt{1+\epsilon^{2}}-\epsilon^{2}}{(1+e2)^{5/2}}\bigg\{1-(1-3x_A)\frac{t}{Q^2}\nonumber\\&\,\,\,\,&\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,+\frac{1-\sqrt{1+\epsilon^{2}}+3\epsilon^{2}}{1+\sqrt{1+\epsilon^{2}}-\epsilon^{2}} 
\frac{x_A*t}{Q^2}\bigg\} \label{eq:c1I}
\end{eqnarray}

\normalsize

\chapter{The parametrizations for the RTPC} \label{app:RTPC_appendix}
\begin{itemize}

\item The parametrizations of the mean ($\mu$) and the width ($\sigma$) of 
   $\Delta z$ distributions shown in figure \ref{fig:rrtpc_delta_z}, with L and 
   R stand for the left and the right modules of the RTPC, and $z$ in mm:
\small
\begin{eqnarray}
\hspace{-0.3in} \mu_{\Delta z}^{L}(z) &=& 2.80051 -0.0624556*z +0.00035567*z^{2} +5.25789e-06*z^{3}\\
\hspace{-0.3in} \sigma_{\Delta z}^{L}(z) &=& 7.48614 -0.00776678*z -3.66892e-05*z^{2}\\
\hspace{-0.3in} \mu_{\Delta z}^{R}(z) &=& -3.85725 -0.061265*z +0.000324528*z^{2} +4.28801e-06*z^{3}\\
\hspace{-0.3in} \sigma_{\Delta z}^{R}(z) &=& 8.67335 -0.00975138*z +8.01378e-05*z^{2}
\end{eqnarray}  
\normalsize
\item  The parametrizations of the mean ($\mu$) and the width ($\sigma$) of $\Delta \phi$ distributions shown in figure \ref{fig:delta_phi_elastic} are:
\small
\begin{eqnarray}
\hspace{-0.2in} \mu_{\Delta \phi}^{L}(z) &=& 178.053 +0.0298072*z -0.000362634*z^{2} -2.32442e-07*z^{3}\\
\hspace{-0.2in} \sigma_{\Delta \phi}^{L}(z) &=& 2.00365 +0.0011081*z +4.1589e-05*z^{2} -2.95347e-07*z^{3}\\
\hspace{-0.2in} \mu_{\Delta \phi}^{R}(z) &=& 181.3 +0.00749361*z -0.000338728*z^{2} +6.37882e-06*z^{3}\\
\hspace{-0.2in} \sigma_{\Delta \phi}^{R}(z) &=& 2.0939 +9.59331e-05*z +2.16727e-05*z^{2} -5.69296e-08*z^{3}
\end{eqnarray} 
\normalsize

\item The parametrizations of the mean ($\mu$) and the width ($\sigma$) of $\Delta \theta$ distribution shown in figure \ref{fig:delta_theta_elastic} are: 
\small
\begin{eqnarray}
\hspace{-0.2in} \mu_{\Delta \theta}(z) &=& -1.02349 -0.0487393*z +0.000219641*z^{2} +3.84156e-06*z^{3}\\
\hspace{-0.2in} \sigma_{\Delta \theta}(z) &=& 3.57854 +0.00639663*z
\end{eqnarray}
\normalsize

~\newpage
\item The drift speed parametrization:
\begin{figure}[!h]
\centering
\includegraphics[scale=0.28]{fig_rtpc/p0_RunNumber.png}
\includegraphics[scale=0.28]{fig_rtpc/p1_RunNumber.png}
\includegraphics[scale=0.28]{fig_rtpc/p2_RunNumber.png}
\includegraphics[scale=0.28]{fig_rtpc/p3_RunNumber.png}
\caption{ The fit parameters: $p_{0}$, $p_{1}$, $p_{2}$, and $p_{3}$ for the individual runs. The red lines represent their piece-wise fits. }
\label{fig:Drift_speed_fit_par}
\end{figure}

\begin{equation}
TDC_{max/2} (z)= p_{0} +  p_{1} * e^{p_{2}*(z-p_{3})^{2}}
\end{equation}

\begin {table}[!h]
\begin{center}
\begin{tabular}{|l|l|l|l|l|}
\hline
run range &  $p_{0}$ &  $p_{1}$ \\&  $p_{2}$ &  $p_{3}$ \\
\hline
61448 - 61481 & 
\small{ 1.14312e+03 - 1.75217e-02 *$r_{N}$} & 
\small{ 3.27339e+00 + 5.32577e-05 *$r_{N}$} \\&
\small{-7.55131e-02 + 1.22429e-06 *$r_{N}$} &  
\small{ 3.76627e+03 - 6.14148e-02 *$r_{N}$}\\
\hline
61483 - 61611 &  
\small{ 1.21405e+02 - 9.40705e-04 *$r_{N}$} & 
\small{ 3.89644e+00 + 6.33813e-05 *$r_{N}$}  \\& 
\small{ 4.09308e-03 - 6.97839e-08 *$r_{N}$} & 
\small{-9.04583e+02 + 1.45062e-02 *$r_{N}$}\\
\hline
61612 - 61646 & 
\small{ 1.39733e+03 - 2.16496e-02 *$r_{N}$} & 
\small{-3.07845e+02 + 5.10814e-03 *$r_{N}$}  \\&
\small{-8.23774e-02 + 1.33384e-06 *$r_{N}$} & 
\small{-9.05752e+02 + 1.44872e-02 *$r_{N}$}\\
\hline
61655 - 61779 &
\small{ 1.45093e+02 - 1.33438e-03 *$r_{N}$} &
\small{ 1.63746e+02 - 2.54273e-03 *$r_{N}$} \\&
\small{-5.10501e-04 + 5.64359e-09 *$r_{N}$} &
\small{ 4.26282e+02 - 7.12408e-03 *$r_{N}$}\\
\hline
61791 - 61930&
\small{ 2.18243e+02 - 2.51495e-03 *$r_{N}$} &
\small{ 4.92691e+01 - 6.90443e-04 *$r_{N}$} \\&
\small{-1.11909e-02 + 1.78407e-07 *$r_{N}$} &
\small{ 4.26297e+02 - 7.12383e-03 *$r_{N}$}\\
\hline
61931 - 61961)&
\small{ 2.18152e+02 - 2.51641e-03 *$r_{N}$} &
\small{ 4.92921e+01 - 6.90070e-04 *$r_{N}$} \\&
\small{-1.11766e-02 + 1.78639e-07 *$r_{N}$} &
\small{ 4.23668e+02 - 7.16628e-03 *$r_{N}$} \\
\hline
\end{tabular}
\caption[]{The parameters of $TDC_{max/2}$ used in EG6 experiment reconstruction codes.}
\label{Table:TDCmax}
\end{center}
\end{table}

~\newpage
\item Drift paths' parametrization:
\begin{equation}
  \Delta \phi (TDC, z)=  \sum\limits_{i=0}^{4} p_{i}(z)*TDC^{i}
\end{equation}
\begin{table}[!h]
\begin{center}
\begin{tabular}{|l|l|l|l|}
\hline
Parameter & ~~~~~constant & ~~~~~~~*z & ~~~~~~~*$z^{2}$\\
\hline
~~~~$p_{0}$   & 0.14222     &-6.52562e-05 & 4.06768e-06\\
\hline
~~~~$p_{1}$   &-0.00147368  & 5.64924e-06 &-7.31944e-07\\
\hline
~~~~$p_{2}$   & 0.000216222 & 6.25749e-09 & 1.8923e-08 \\
\hline
~~~~$p_{3}$   &-3.82450e-06 &-6.29825e-09 &-1.89627e-10\\
\hline
~~~~$p_{4}$   & 3.22973e-08 & 7.52017e-11 & 1.08564e-12\\
\hline
\end{tabular}
\caption{The drift paths extracted in the EG6 experiment.}
\label{table:drift_paths}
\end{center}
\end{table}

\end{itemize}

%\part{SIDIS generalized cross section}
%\begin{align}
%\lefteqn{\frac{d\sigma}{dx \, dy\, d\phi_{S} \,dz\, d\phi_h\, d P_{h\perp}^2}
%=}
%\nonumber \\ & \quad 
%\frac{\alpha^2}{x y Q^2}\,
%\frac{y^2}{2\,(1-\varepsilon)}\,  \biggl( 1+\frac{\gamma^2}{2x} \biggr)\, \Biggl\{ F_{UU ,T} +  %\varepsilon F_{UU ,L} + \sqrt{2\,\varepsilon (1+\varepsilon)}\,\cos\phi_h\,
%F_{UU}^{\cos\phi_h} \nonumber \\  & \quad \qquad + \varepsilon \cos(2\phi_h)\, 
%F_{UU}^{\cos 2\phi_h} + \lambda_e\, \sqrt{2\,\varepsilon (1-\varepsilon)}\,  \sin\phi_h\, 
%F_{LU}^{\sin\phi_h} \phantom{\Bigg[ \Bigg] }
%\nonumber \\  & \quad \qquad + S_\parallel\, \Bigg[ \sqrt{2\, \varepsilon (1+\varepsilon)}\,
%  \sin\phi_h\, F_{UL}^{\sin\phi_h} +  \varepsilon \sin(2\phi_h)\,  F_{UL}^{\sin 2\phi_h} \Bigg]
%\nonumber \\  & \quad \qquad
%+ S_\parallel \lambda_e\, \Bigg[ \, \sqrt{1-\varepsilon^2}\; 
%F_{LL} +\sqrt{2\,\varepsilon (1-\varepsilon)}\,
%  \cos\phi_h\,  F_{LL}^{\cos \phi_h} \Bigg] \nonumber \\  & \quad \qquad
%+ |{S}_\perp|\, \Bigg[ \sin(\phi_h-\phi_S)\, \Bigl(F_{UT ,T}^{\sin(\phi_h -\phi_S)}
%+ \varepsilon\, F_{UT ,L}^{\sin(\phi_h -\phi_S)}\Bigr) \nonumber \\  & \quad  \qquad \qquad
%+ \varepsilon\, \sin(\phi_h+\phi_S)\,  F_{UT}^{\sin(\phi_h +\phi_S)}
%+ \varepsilon\, \sin(3\phi_h-\phi_S)\, F_{UT}^{\sin(3\phi_h -\phi_S)}
%\phantom{\Bigg[ \Bigg] } \nonumber \\  & \quad \qquad \qquad + \sqrt{2\,\varepsilon (1+\varepsilon)}\, 
%  \sin\phi_S\,  F_{UT}^{\sin \phi_S }
%+ \sqrt{2\,\varepsilon (1+\varepsilon)}\,  \sin(2\phi_h-\phi_S)\,  
%F_{UT}^{\sin(2\phi_h -\phi_S)} \Bigg] \nonumber \\  & \quad \qquad 
%+ |{S}_\perp| \lambda_e\, \Bigg[  \sqrt{1-\varepsilon^2}\, \cos(\phi_h-\phi_S)\, 
%F_{LT}^{\cos(\phi_h -\phi_S)}
%+\sqrt{2\,\varepsilon (1-\varepsilon)}\,   \cos\phi_S\,  F_{LT}^{\cos \phi_S}
%\nonumber \\  & \quad \qquad \qquad +\sqrt{2\,\varepsilon (1-\varepsilon)}\,  \cos(2\phi_h-\phi_S)\,  %F_{LT}^{\cos(2\phi_h - \phi_S)} \Bigg] \Biggr\}
%\label{crossmaster}
%\end{align}

%\begin{align}
%\varepsilon &= \frac{1-y -\frac{1}{4} \gamma^2 y^2}{1-y
%  +\frac{1}{2} y^2 +\frac{1}{4} \gamma^2 y^2} ,
%\end{align}

\chapter{The parametrization of the IC-photons energy corrections} \label{App:AppendixA}
\begin{itemize}
\item $\alpha$ parametrization
\vspace{-0.2in}
\begin{equation}
\alpha (x) = c_{0} + c_{2} \left[ e^{-c_{3}(x - c_{1})} - e^{-c_{4}(x - c_{1})} \right],
\end{equation}

\vspace{-0.2in}
\begin {table}[!h]
\begin{center}
\begin{tabular}{|l|l|l|l|l|l|l|l|}
\hline
$Fun_{N}$ & xmin  &   xmax    &  $c_{0}$     &   $c_{1}$    &  $c_{2}$      &   $c_{3}$  &   $c_{4}$\\
\hline
1  &  61510    & 61514   &  -0.00671929   &  61493     & -0.00868856    &   -0.114874  &  -0.117953\\
\hline
2   &  61519   &  61525  &    -0.00160398   &  61585.7  &  -2.1e-09    &   0.38362    &  0.38362\\
\hline
3   &  61531   &  61545  &    -0.00956513   &  61876.8  & -0.0295579   &    1.23958e-06 &  0.000704112\\
\hline
4   &  61546   &  61556  &    -0.000414459  &   61521.8  &-0.0179471   &    -0.0316302  &  -0.030899\\
\hline
5   &  61558   &  61580  &    -0.00731749  &   61532.4 &  -0.465254   &    0.0200131   &   0.0193213\\
\hline
6   &  61581   & 61590   &   0.0604759    & 61561.7  & -19.3314    & 0.0407449   & 0.0411026\\
\hline
7   &  61604   & 61608    &  -0.00320342  &   61521.1  &  -0.00074357   &    -0.018373  &    -0.0243743\\
\hline
8   &  61609   & 61622     & -0.00205987  &   61649.1  &   5.94004e-05   &    0.0760846  &    -2.64412\\
\hline
9   &  61623   & 61637    &  -0.00153458  &   61640.7  &   -1.02541e-10 &   0.965545   &   0.959411\\
\hline
10  &   61638   &  61646  &    -0.000735223  &   61763.1  & -0.00476067   & 0.0423013  &    0.0422956\\
\hline
11  &   61655  &  61675   &   -0.00123166   &  61561.1  &  -2.63733e-06  &  -0.159566  &    -0.159566\\
\hline
12  &  61678    & 61711   &   -0.00294886   &  61670.6   & -0.0079126   &    0.052612  &    0.0252883\\
\hline
13   &  61712   &  61713   &   -0.00102705   &  61711.9 &   -0.0034062 &  -3.1972   &   -3.19763\\
\hline
14   &  61714   &  61724   &   -0.00109184   &  61731.2&    -1.14221e-06  &     0.308061   &-4.24803\\
\hline
15   &  61725   &  61729   &   -0.00915958   &  61716.6 &     -0.0240355 &      0.137179  & 0.0524492\\
\hline
16   &  61731   &  61779   &   -0.00295947   &  61669.4 &  0.0130552    & 0.00768358   &   0.0117274\\
\hline
17   &  61791   &  61796   &   -0.00117275   &  61791.9  &  -0.00210188  &  5.63266   &   5.63003\\
\hline
18   &  61797   &  61826   &   0.00155106   &  61787.7 &  -0.980189  &     0.0514066 &     0.0518518\\
\hline
19   &  61829   &  61843   &   -0.0015276  &   61826 &  -0.00204473 &      2.72258   &   0.275824\\
\hline
20   &  61848  &   61874   &   0.0265578   &  61973.2 &  -0.0249309&    0.0010753   &   -0.186452\\
\hline
21   &  61876 &  61895    &  -0.00205642   &  61715.7  & -3.3277e-05 &   -0.065808   &   -0.0658091\\
\hline
22   &  61904  & 61915    &  -0.00274984   &  62178.9  &   -0.107207&     0.00976882  &    0.00977186\\
\hline
23   &  61925   &61930    &  0.0064528    & 61924.8   & -0.00849265  & 0.0278942  &   9.3268 \\
\hline
\end{tabular}
\caption{$\alpha$ parametrization shown in figure \ref{fig:ic_alpha_beta_fitting}.}
\label{Table:ic_alpha_corrections}
\end{center}
\end{table}

~\newpage
\item $\beta$ parametrization

\begin{equation}
\beta (x) = p_{0} + p_{2} \left[ e^{-p_{3}(x - p_{1})} - e^{-p_{4}(x - p_{1})} \right],
\end{equation}

\begin {table}[!h]
\begin{center}
\begin{tabular}{|l|l|l|l|l|l|l|l|}
\hline
$Fun_{N}$ & xmin  &   xmax    &  $p_{0}$     &   $p_{1}$    &  $p_{2}$      &   $p_{3}$  &   $p_{4}$\\
\hline
1   &  61510   &61514   &   0.139127   &  61508.7   &   -0.00705827      & -0.127   &   -0.163719\\
\hline
2   &  61519   &  61525  &    0.144057  &   61553.1  &    6.44528e-05   &    0.384066 &     0.384069\\
\hline
3   &  61531   &  61545   &   -0.238301    & 61487    &  -1.28623      & 0.0260483   &   0.011476\\
\hline
4   &  61546    & 61556    &  0.0904474   &  61545.1   &   -0.0367149 &      2.10481  &    -0.0186192\\
\hline
5   &  61558  &   61580     & 0.095243   &  61543.5  &    -0.197639  &     0.0280817  &    0.015222\\
\hline
6   &  61581   &  61590 & 0.0643454     &61557.1    &  -0.394422    &   0.0358816   &   0.0212999\\
\hline
7   &  61604    & 61608  &    0.138436 &    61605.4  &    -0.0142253    &   -0.0323464  &    -0.0103419\\
\hline
8  &   61609    & 61622   &   0.135047    & 61605.8   &   -0.00856825    &   0.157423    &  0.0474859\\
\hline
9   &  61623    & 61637    &  0.137445   &  61646.8    &  -1.46307e-05  &     0.273975  &    -0.0770047\\
\hline
10 &    61638    & 61646    &  0.141909 &    61651.9 &     -0.103873    &   0.00713496   &  0.000949948\\
\hline
11&   61655  & 61675  & 0.127712   &  61652.8   &  -0.00969769     &  0.220956  &    0.00215349\\
\hline
12 &  61678   &  61711 &     0.137774     &61697.7  &    -9.15967e-05    &   0.237965 &     -0.158587\\
\hline
13  & 61712   & 61713   &   0.124706     &61655.1    &  -3.72443e-05    &   -0.0443564 &     -0.100321\\
\hline
14    & 61714  &   61724 &     0.138057 &    61726.8  &    -0.000274029   &    0.234    &  -4.45937\\
\hline
15   &  61725  &   61729  &    0.108381    & 61721.3   &   -0.0289603    &   0.77633  &    -0.00285553\\
\hline
16  &   61731  &   61779   &   0.113727   &  61726   &   -0.0236114     &  0.243927    &  -0.00196355\\
\hline
17 &    61791  &   61791    &  0.136619  &   0.0   &   0.0   &    0.0  &    0.0\\
\hline
18&   61792   &  61796 & 0.138708   &  61914.5   &   1.07991e-09     &  0.181595    &  0.181612\\
\hline
19 &  61797  &   61825  &    0.137559   &  61839.6 &     -0.000312349  &     0.160791&      0.159434\\
\hline
20  &61826   & 61843     & 0.0359758   &  61810.5   &   -0.10032      & 0.215911     & -0.000529924\\
\hline
21 & 61848  &  61874      &0.116396   &  61891.7   &   -0.385562     &  -0.0563216    &  -0.0479573\\
\hline
22&   61876  &   61915  &  0.105816  &   61872.2    &  -0.0312028     &  0.384691    &  -0.00145868\\
\hline
23 & 61925   &  61930    &  0.137809   &  61927.5    &  -0.00071665  &     0.620419   &   0.222406\\

\hline
\end{tabular}
\caption{$\beta$ parametrization shown in figure \ref{fig:ic_alpha_beta_fitting}.}
\label{Table:ic_beta_corrections}
\end{center}
\end{table}
\end{itemize}

~\newpage

\chapter{Exclusive $\pi^{0}$ events selection}\label{app:Exclusive_pi0_selection}

~~~~~The exclusive selection of the experimental $e^{4}He\pi^{0}$ and $ep\pi^{0}$ events require the detection of only one good electron, one good $\pi^{0}$ in the topology ICIC or ICEC, and one good $^{4}He$ track in the coherent channel or one good proton in the incoherent channel case. Furthermore, in order to ensure that this is a deep process we apply a set of initial requirements. The exclusivity of the reaction is ensured by a set of exclusivity cuts like for the DVCS channels. These requirements and exclusivity cuts are presented for the case of the coherent $e^{4}He\pi^{0}$ events are:

\paragraph{Initial criteria}
~\\
~\\
These requirements are made to ensure that the selected events occurre at the partonic level:
\begin{itemize}
\item High virtuality of the exchanged photon ($Q^{2}$>1 $GeV^{2}$).
\item High energy of the emitted $\pi^{0}$ ($E_{\pi^{0}}$ > 2 GeV).
\item The invariant mass of the virtual photon and the target proton is greater than 2 GeV$^{2}$/c$^{2}$ in order to avoid the baryons resonances region.
\item The transfer momentum squared ($-t$) between the initial target and the recoil one is greater than the minimum allowed one ($t_{min}$) defined by the kinematics of the incoming and the scattered electrons. The definition of $t_{min}$ for each channel can be found in the corresponding DVCS channel selection presented previously.
\end{itemize}

\paragraph{Exclusivity requirements}
~\\
~\\The exclusivity of the selected $e^{4}He\pi^{0}$ events is done with the following cuts:
\begin{itemize}
\item The coplanarity cut ($\Delta \phi$) between the recoil $^{4}He$ and the produced $\pi^{0}$.
\item The missing energy, mass and transverse momentum cuts in the configuration $e^{4}He\pi^{0}X$.
\item The missing mass cut in the configuration $e^{4}HeX$.
\item The missing mass cut in the configuration $e\pi^{0}X$.
\item The cone angle cut between $e^{4}HeX$ and the reconstructed $\pi^{0}$.
\end{itemize}
  The same procedure holds for the case of the incoherent $ep\pi^{0}$ events. In the following two subsections, the results of the two channels selection are presented.
~\newpage
\section{$e^{4}He\pi^{0}$ exclusivity cuts}
~~~~The events which pass the following exclusivity cuts are assumed to be good $e^{4}He\pi^{0}$ events.

\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{fig_dvcs/all_coh_pi0_exc_cuts.png}
\caption{The blue distributions represent all the  $e^{4}He\pi^{0}$ events before the exclusivity cuts. The shaded distributions show the events which passed all the exclusivity cuts except for the quantity plotted. The red lines are $3\sigma$ cuts. The mean and sigma values of each distribution are listed in table \ref{Table:cohpi0_exclusivity_cuts}.} 
\label{fig:cohpi0_exclusivty_cuts}
\end{figure}

\paragraph{Comparison with simulation}
~\\
~\\As for the selection of the experimental $e^{4}He\pi^{0}$ events, the simulated events have to pass an equivalent set of exclusivity cuts in addition to the $\pi^{0}$ electroproduction criteria, presented at the beginning of this section. In this section, we show the comparison between the experimental and the simulated selected  $e^{4}He\pi^{0}$ events as a function of the kinematic variables ($Q^{2}$, $x_{B}$, $-t$), figure \ref{fig:coh_pi0_comparison_with_simulation}, and as a function of the variables used for the exclusivity cuts, figure \ref{fig:coh_pi0_comparison_with_simulation_2}.\\

\begin{figure}[h!]
\hspace{-0.1in}\includegraphics[scale=0.37]{fig_dvcs/comp/Q2_Coh_pi0.png}
\hspace{-0.4in}\includegraphics[scale=0.37]{fig_dvcs/comp/xB_Coh_pi0.png}
\hspace*{-0.1in}\includegraphics[scale=0.37]{fig_dvcs/comp/t_Coh_pi0.png}
\hspace{-0.4in}\includegraphics[scale=0.37]{fig_dvcs/comp/phi_h_Coh_pi0.png}
\caption{Comparison between the simulated $e^{4}He\pi^{0}$ events (red lines) and the experimental events (blue shaded distributions) as a function of the kinematic variables: $Q^{2}$, $x_{B}$, $-t$ and $\phi_{h}$ respectively from top to right to right and from top to bottom.}
\label{fig:coh_pi0_comparison_with_simulation}
\end{figure}

\begin{figure}[h!]
\includegraphics[scale=0.35]{fig_dvcs/comp/Coh_pi0_delta_phi.png}
\includegraphics[scale=0.35]{fig_dvcs/comp/Coh_pi0_e4Hepi0_E_Mis.png}
\includegraphics[scale=0.35]{fig_dvcs/comp/Coh_pi0_e4Hepi0_M2_Mis.png}
\includegraphics[scale=0.35]{fig_dvcs/comp/Coh_pi0_e4Hepi0_PT_Mis.png}
\includegraphics[scale=0.35]{fig_dvcs/comp/Coh_pi0_e4He_M2_Mis.png}
\includegraphics[scale=0.35]{fig_dvcs/comp/Coh_pi0_epi0_M2_Mis.png}
\caption{Comparison between the simulated and experimental $e^{4}He\gamma$ events in terms of the exclusivity variables. The vertical black line indicates the theoretically expected value for each exclusive variable.} 
\label{fig:coh_pi0_comparison_with_simulation_2}
\end{figure}

Even with low experimental statistics, figures \ref{fig:coh_pi0_comparison_with_simulation} and \ref{fig:coh_pi0_comparison_with_simulation_2} show a good match between the simulation and the experimental   $e^{4}He\gamma$ events for the different kinematic variables, which is satisfying  for our background subtraction goal.

~\newpage
~\newpage
\section{$ep\pi^{0}$ exclusivity cuts}
The $ep\pi^{0}$ events which pass the initial deepness criteria and the exclusivity cuts, marked by the red vertical lines in the figure below, are considered as clean events.

\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{fig_dvcs/all_incoh_pi0_exc_cuts.png}
\caption{The blue distributions represent all the $ep\pi^{0}$ events before any exclusive requirement. The shaded brown distributions show the events which passed all the exclusivity cuts except the quantity plotted. The vertical red lines represent $3\sigma$ cuts on the shaded distribution. The mean and sigma values of each distribution are listed in table \ref{Table:incohpi0_exclusivity_cuts}.} 
\label{fig:incohpi0_exclusivty_cuts}
\end{figure}

\paragraph{Comparison with simulation}
~\\
~\\
In this section, the experimental selected $ep\pi^{0}$ events are compared to the Monte Carlo simulated events. Figure \ref{fig:incoh_pi0_comparison_with_simulation} shows the comparison as a function of the kinematic variables. Figure \ref{fig:incoh_comparison_with_simulation_exclusive} shows the comparison in terms of the different exclusivity variables. One can see an agreement within some degrees of differences, which might come from the fact that our protons are bound ones and the physics of the nuclear process is not fully understood. 
\begin{figure}[h!]
\includegraphics[scale=0.35]{fig_dvcs/comp/Q2_InCoh_pi0.png}
\includegraphics[scale=0.35]{fig_dvcs/comp/xB_InCoh_pi0.png}
\includegraphics[scale=0.35]{fig_dvcs/comp/t_InCoh_pi0.png}
\includegraphics[scale=0.35]{fig_dvcs/comp/phi_h_InCoh_pi0.png}
\caption{Comparison between the Monte Carlo simulated $ep\pi^{0}$ events (red lines) and the experimental ones (blue shaded distributions) as a function of the kinematic variables: $Q^{2}$, $x_{B}$, $-t$, and $\phi$, respectively from top to right to right and from top to bottom.}
\label{fig:incoh_pi0_comparison_with_simulation}
\end{figure}

\begin{figure}[h!]
\includegraphics[scale=0.35]{fig_dvcs/comp/InCoh_pi0_delta_phi_InCoh.png}
\includegraphics[scale=0.35]{fig_dvcs/comp/InCoh_pi0_eppi0_E_Mis.png}
\includegraphics[scale=0.35]{fig_dvcs/comp/InCoh_pi0_eppi0_M2_Mis.png}
\includegraphics[scale=0.35]{fig_dvcs/comp/InCoh_pi0_eppi0_PT_Mis.png}
\includegraphics[scale=0.35]{fig_dvcs/comp/InCoh_pi0_epi0_M2_Mis_InCoh.png}
\includegraphics[scale=0.35]{fig_dvcs/comp/InCoh_pi0_Theta_pi0X_InCoh.png}
\caption{Comparison between the simulated and experimental $ep\pi^{0}$ DVCS events as a function of the variables used for the exclusivity cuts. The simulated distributions are normalized with respect to the experimental ones. The vertical black lines indicate the theoretically expected values.} 
\label{fig:incoh_comparison_with_simulation_exclusive}
\end{figure}

\chapter{Tables list of the exclusive distributions}\label{exclusivity_cuts}
\begin{itemize}

\item Exclusive $e^{4}He\gamma$ distributions
\begin {table}[!h]
\begin{center}
\begin{tabular}{|l|l|l|}
\hline
The quantity &  ~~~mean & ~~~~~$\sigma$ \\
\hline
$\Delta \phi$ &  1.79405e-01 & 4.53791e-01 \\
\hline
$E_{X}$ ($e^{4}He\gamma X$) &  1.56814e-02 & 2.51492e-01 \\ 
\hline
$M^{2}_{X}$ ($e^{4}He\gamma X$) &  -2.96869e-03 & 9.10158e-03 \\ 
\hline
$pt_{X}$ ($e^{4}He\gamma X$) & 4.14664e-02 & 4.24914e-02 \\ 
\hline
$M^{2}_{X}$ ($e^{4}HeX$) &  -1.72013e-02 & 2.33988e-01 \\
\hline
 $M^{2}_{X}$ ($e\gamma X$) &  1.40066e+01 & 1.85929 \\
\hline
$\theta$ ($\gamma$,$e^{4}HeX$) &  5.08070e-01 & 4.74883e-01\\
\hline
$px_{X}$ ($e^{4}He\gamma X$) & -2.32102e-03  & 4.52945e-02\\
\hline
$py_{X}$ ($e^{4}He\gamma X$) &  -8.97351e-04 & 3.89937e-02\\ 
\hline
\end{tabular}
\caption{ The mean and sigma values of the exclusive coherent quantities drawn in figure \ref{fig:coh_exclusivty_cuts}.}
\label{Table:coh_exclusivity_cuts}
\end{center}
\end{table}

\item Exclusive $e^{4}He\pi^{0}$ distributions
\begin {table}[!h]
\begin{center}
\begin{tabular}{|l|l|l|}
\hline
The quantity &  ~~~mean & ~~~~~$\sigma$  \\
\hline
$\Delta \phi$ & 1.41750e-01  & 3.84202e-01 \\
\hline
$E_{X}$ ($e^{4}He\pi^{0} X$)     &  7.80328e-03 & 1.85770e-01 \\
\hline
$M^{2}_{X}$ ($e^{4}He\pi^{0} X$) &  -2.31650e-03 & 8.65851e-03 \\
\hline
$pt_{X}$ ($e^{4}He\pi^{0} X$)    & 4.36619e-02  & 3.25254e-02 \\
\hline
$M^{2}_{X}$ ($e^{4}HeX$) &  -1.30346e-02 & 2.07791e-01 \\
\hline
$M^{2}_{X}$ ($e\pi^{0} X$)  & 1.39835e+01 & 1.33781\\
\hline
$\theta$ ($\pi^{0}$,$e^{4}HeX$) & 5.30001e-01  & 3.44745e-01\\
\hline
$px_{X}$ ($e^{4}He\pi^{0} X$)    &   -3.79596e-03  &  4.20732e-02\\
\hline
 $py_{X}$ ($e^{4}He\pi^{0} X$)    &   9.41010e-04  & 3.50393e-02 \\
\hline
\end{tabular}
\caption{ The mean and sigma values of the exclusive coherent quantities drawn in figure \ref{fig:cohpi0_exclusivty_cuts}.}
\label{Table:cohpi0_exclusivity_cuts}
\end{center}
\end{table}

~\newpage
\item Exclusive $ep\gamma$ distributions

\begin {table}[!h]
\begin{center}
\begin{tabular}{|l|l|l|}
\hline
The quantity &  ~~~mean & ~~~~~$\sigma$ \\
\hline
$\Delta \phi$ &  4.22584e-02 & 1.39413 \\
\hline
$E_{X}$ ($ep\gamma X$) &  6.27739e-02 & 1.34499e-01 \\
\hline
$M^{2}_{X}$ ($ep\gamma X$) &  -1.00889e-02 & 1.58503e-02 \\ 
\hline
$pt_{X}$ ($ep\gamma X$) & 8.03008e-02 & 4.28511e-02 \\  
\hline
$M^{2}_{X}$ ($epX$) &  2.40257e-01 & 3.66321e-01 \\
\hline
$M^{2}_{X}$ ($e\gamma X$) &  1.01266 & 2.03835e-01 \\
\hline
$\theta$ ($\gamma$, $epX$) &  1.06788 & 6.76469e-01 \\
\hline
$px_{X}$ ($ep\gamma X$) & 3.48024e-03  &  8.19527e-02\\
\hline
$py_{X}$ ($ep\gamma X$) & -1.50911e-03 & 8.16219e-02\\
\hline
\end{tabular}
\caption{ The mean and sigma values of the exclusive incoherent quantities drawn in figure \ref{fig:incoh_exclusivty_cuts}.}
\label{Table:incoh_exclusivity_cuts}
\end{center}
\end{table}

\item Exclusive $ep\pi^{0}$ distributions
\begin {table}[!h]
\begin{center}
\begin{tabular}{|l|l|l|}
\hline
The quantity &  ~~~mean & ~~~~~$\sigma$  \\
\hline
$\Delta \phi$ & -3.25864e-02  & 2.11499 \\

\hline
$E_{X}$ ($ep\pi^{0} X$) &  9.23934e-02 & 1.50977e-01 \\

\hline
$M^{2}_{X}$ ($ep\pi^{0} X$) &  -1.11900e-02 & 2.31963e-02 \\

\hline
$pt_{X}$ ($ep\pi^{0} X$) & 1.02247e-01 & 5.31387e-02 \\

\hline
$M^{2}_{X}$ ($epX$) & 2.27334e-01  & 2.98775e-01\\
\hline
$M^{2}_{X}$ ($e\pi^{0} X$) & 1.07125  & 2.79845e-01\\
\hline
$\theta$ ($\pi^{0}$, $epX$) &  1.42739 & 8.89072e-01 \\
\hline
$px_{X}$ ($ep\pi^{0} X$) &  2.19686e-03  & 9.01343e-02 \\
\hline
$py_{X}$ ($ep\pi^{0} X$) &  -1.30580e-03 & 9.05090e-02  \\ 
\hline
\end{tabular}
\caption{ The mean and sigma values of the exclusive $ep\pi^{0}$ quantities drawn in shaded brown in figure \ref{fig:incohpi0_exclusivty_cuts}.}
\label{Table:incohpi0_exclusivity_cuts}
\end{center}
\end{table}
\end{itemize}

\section*{ALU tables}
\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
         \hline
         1.143 & 0.136 & 0.096 &  23.32563   &    0.1370716  $\pm$   0.08373948  $\pm$   0.02571563 \\
         1.143 & 0.136 & 0.096 &  59.81847   &    0.3758095  $\pm$   0.07101178  $\pm$   0.01885969 \\
         1.143 & 0.136 & 0.096 &  97.78493   &    0.4125528  $\pm$   0.08798407  $\pm$   0.04038886 \\
         1.143 & 0.136 & 0.096 &  140.0018   &    0.159693   $\pm$   0.1366452   $\pm$   0.02678967 \\
         1.143 & 0.136 & 0.096 &  179.0882   &    0.1714253  $\pm$   0.1398893   $\pm$   0.02789155 \\
         1.143 & 0.136 & 0.096 &  219.1279   &   -0.1240822  $\pm$   0.1156237   $\pm$   0.02484531 \\
         1.143 & 0.136 & 0.096 &  263.7259   &   -0.3608519  $\pm$   0.09411095  $\pm$   0.03891253 \\
         1.143 & 0.136 & 0.096 &  302.9283   &   -0.1683747  $\pm$   0.07604881  $\pm$   0.02632836 \\
         1.143 & 0.136 & 0.096 &  337.3336   &   -0.3508557  $\pm$   0.07680001  $\pm$   0.03431105 \\
         \hline                                                                          
         1.423 & 0.172 & 0.099 &  19.94307   &    0.1650792  $\pm$   0.067211    $\pm$   0.02673700 \\
         1.423 & 0.172 & 0.099 &  57.17185   &    0.3028724  $\pm$   0.068908    $\pm$   0.02503328 \\
         1.423 & 0.172 & 0.099 &  95.77216   &    0.4372785  $\pm$   0.099537    $\pm$   0.04267748 \\
         1.423 & 0.172 & 0.099 &  137.9543   &    0.1147926  $\pm$   0.142932    $\pm$   0.02500644 \\
         1.423 & 0.172 & 0.099 &  180.9498   &    0.1924395  $\pm$   0.1806951   $\pm$   0.03026008 \\
         1.423 & 0.172 & 0.099 &  220.1671   &   -0.2589808  $\pm$   0.1611112   $\pm$   0.03447198 \\
         1.423 & 0.172 & 0.099 &  263.1496   &   -0.3065283  $\pm$   0.1158366   $\pm$   0.03663218 \\
         1.423 & 0.172 & 0.099 &  302.3187   &   -0.3646641  $\pm$   0.069707    $\pm$   0.03835156 \\
         1.423 & 0.172 & 0.099 &  338.0674   &   -0.1660148  $\pm$   0.069482    $\pm$   0.02613428 \\
         \hline

         1.902 & 0.224 & 0.107 &  20.96588   &    0.0841330  $\pm$   0.06370723  $\pm$   0.02345626 \\
         1.902 & 0.224 & 0.107 &  56.59966   &    0.3739804  $\pm$   0.06574343  $\pm$   0.01851792 \\
         1.902 & 0.224 & 0.107 &  95.79632   &    0.1779531  $\pm$   0.1058264   $\pm$   0.0173685  \\
         1.902 & 0.224 & 0.107 &  139.5123   &    0.1574064  $\pm$   0.1713567   $\pm$   0.01702304 \\
         1.902 & 0.224 & 0.107 &  179.5613   &   -0.0837227  $\pm$   0.2119008   $\pm$   0.01265815 \\
         1.902 & 0.224 & 0.107 &  221.6768   &   -0.1251566  $\pm$   0.1783256   $\pm$   0.01528429 \\
         1.902 & 0.224 & 0.107 &  263.0872   &   -0.3069055  $\pm$   0.1173135   $\pm$   0.02602474 \\
         1.902 & 0.224 & 0.107 &  303.6431   &   -0.2404473  $\pm$   0.07568278  $\pm$   0.02071202 \\
         1.902 & 0.224 & 0.107 &  339.2973   &   -0.184311   $\pm$   0.06150122  $\pm$   0.01635832 \\
      \hline 
      \hline
      \end{tabular}
      \caption{ The coherent $A_{LU}$ in $Q^2$ bins}
      \label{table:Coh_Q2_BSA}
   \end{center}
\end{table}

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
         \hline
        1.164 & 0.132 & 0.095 &   24.70837  &    -0.0009864  $\pm$   0.1023417     $\pm$   0.02214862    \\
        1.164 & 0.132 & 0.095 &   60.38457  &     0.394491   $\pm$   0.06742577    $\pm$   0.01984295    \\
        1.164 & 0.132 & 0.095 &   98.05482  &     0.4169974  $\pm$   0.0822727     $\pm$   0.04084068    \\
        1.164 & 0.132 & 0.095 &   140.4849  &     0.2629772  $\pm$   0.1287244     $\pm$   0.03336946    \\
        1.164 & 0.132 & 0.095 &   178.7877  &     0.1917519  $\pm$   0.133959      $\pm$   0.02937379    \\
        1.164 & 0.132 & 0.095 &   218.4067  &    -0.1139352  $\pm$   0.1099316     $\pm$   0.02438166    \\
        1.164 & 0.132 & 0.095 &   263.7104  &    -0.3303477  $\pm$   0.08687361    $\pm$   0.0372357     \\
        1.164 & 0.132 & 0.095 &   302.0021  &    -0.158615   $\pm$   0.06873616    $\pm$   0.02598807    \\
        1.164 & 0.132 & 0.095 &   335.3734  &    -0.2978278  $\pm$   0.09144179    $\pm$   0.03198552    \\
         \hline

        1.439 & 0.17 & 0.099 &    21.20114   &    0.1944966  $\pm$   0.06481715    $\pm$   0.023002136   \\
        1.439 & 0.17 & 0.099 &    57.05011   &    0.2135007  $\pm$   0.0688628     $\pm$   0.01959182    \\
        1.439 & 0.17 & 0.099 &    95.32827   &    0.3033697  $\pm$   0.1028014     $\pm$   0.0295878     \\
        1.439 & 0.17 & 0.099 &    137.6747   &    0.1027237  $\pm$   0.134283      $\pm$   0.01876947    \\
        1.439 & 0.17 & 0.099 &    180.8816   &   -0.0055032  $\pm$   0.1730991     $\pm$   0.0197908     \\
        1.439 & 0.17 & 0.099 &    220.8371   &   -0.2294214  $\pm$   0.1615644     $\pm$   0.0270881     \\
        1.439 & 0.17 & 0.099 &    264.4366   &   -0.2758285  $\pm$   0.1156173     $\pm$   0.02923329    \\
        1.439 & 0.17 & 0.099 &    302.6414   &   -0.3697083  $\pm$   0.07362371    $\pm$   0.03312501    \\
        1.439 & 0.17 & 0.099 &    337.925    &   -0.2626907  $\pm$   0.06672689    $\pm$   0.02543044    \\              
         \hline

        1.844 & 0.225 & 0.107 &   19.94412   &    0.1199148  $\pm$   0.0610976     $\pm$   0.024893846   \\
        1.844 & 0.225 & 0.107 &   56.1033    &    0.4535308  $\pm$   0.07056983    $\pm$   0.02240954    \\
        1.844 & 0.225 & 0.107 &   95.56723   &    0.2782661  $\pm$   0.1178502     $\pm$   0.02714954    \\
        1.844 & 0.225 & 0.107 &   139.3193   &   -0.0854730  $\pm$   0.2144445     $\pm$   0.01668931    \\
        1.844 & 0.225 & 0.107 &   180.6025   &    0.1409771  $\pm$   0.2599303     $\pm$   0.02044162    \\
        1.844 & 0.225 & 0.107 &   223.7917   &   -0.2456453  $\pm$   0.2105987     $\pm$   0.02706752    \\
        1.844 & 0.225 & 0.107 &   260.904    &   -0.3907139  $\pm$   0.1417117     $\pm$   0.03533464    \\
        1.844 & 0.225 & 0.107 &   304.3742   &   -0.2674945  $\pm$   0.08101173    $\pm$   0.02630272    \\
        1.844 & 0.225 & 0.107 &   340.0658   &   -0.125335   $\pm$   0.06016415    $\pm$   0.01755089    \\
         \hline  
         \hline
      \end{tabular}
      \caption{The coherent ALU in $x_B$ bins}
      \label{table:Coh_xB_BSA}
   \end{center}
\end{table}

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\

         \hline
           1.36 & 0.160 & 0.080 &   21.30242  &  0.1531553   $\pm$  0.07225752   $\pm$  0.026305318    \\
           1.36 & 0.160 & 0.080 &   57.11194  &  0.2900274   $\pm$  0.06585235   $\pm$  0.02439207     \\
           1.36 & 0.160 & 0.080 &   96.15277  &  0.4041914   $\pm$  0.09641501   $\pm$  0.03947151     \\
           1.36 & 0.160 & 0.080 &   137.9588  &  0.1402594   $\pm$  0.1434757    $\pm$  0.02522018     \\
           1.36 & 0.160 & 0.080 &   179.2052  &  0.3218006   $\pm$  0.1641379    $\pm$  0.03717874     \\
           1.36 & 0.160 & 0.080 &   221.4243  &  -0.3213178  $\pm$  0.1356342    $\pm$  0.03708316     \\
           1.36 & 0.160 & 0.080 &   265.92    &  -0.392002   $\pm$  0.1066914    $\pm$  0.04038161     \\
           1.36 & 0.160 & 0.080 &   301.3226  &  -0.2284983  $\pm$  0.07726413   $\pm$  0.02940459     \\
           1.36 & 0.160 & 0.080 &   339.661   &  -0.2348847  $\pm$  0.06494273   $\pm$  0.02810254     \\
         \hline                                                                         
           1.507 & 0.179 & 0.094 &  21.17746   & 0.1631617   $\pm$  0.07120653   $\pm$  0.026711914     \\
           1.507 & 0.179 & 0.094 &  56.92214   & 0.3715996   $\pm$  0.06870001   $\pm$  0.02842517      \\
           1.507 & 0.179 & 0.094 &  97.24788   & 0.3145243   $\pm$  0.09659388   $\pm$  0.03076673      \\
           1.507 & 0.179 & 0.094 &  141.6889   & 0.1388844   $\pm$  0.1607593    $\pm$  0.02150343      \\
           1.507 & 0.179 & 0.094 &  179.6762   & -0.3612444  $\pm$  0.1723714    $\pm$  0.03603272      \\
           1.507 & 0.179 & 0.094 &  220.3783   & -0.029479   $\pm$  0.1576259    $\pm$  0.01477838      \\
           1.507 & 0.179 & 0.094 &  262.64     & -0.2524102  $\pm$  0.1096333    $\pm$  0.02830972      \\
           1.507 & 0.179 & 0.094 &  303.6787   & -0.282367   $\pm$  0.07599572   $\pm$  0.02864878      \\
           1.507 & 0.179 & 0.094 &  338.2113   & -0.1464348  $\pm$  0.07113145   $\pm$  0.02012911      \\
         \hline

           1.610 & 0.193 & 0.127 &  21.08428   & 0.0341355   $\pm$  0.07013161   $\pm$   0.021403381     \\
           1.610 & 0.193 & 0.127 &  59.38832   & 0.4083206   $\pm$  0.07247885   $\pm$   0.02045513      \\
           1.610 & 0.193 & 0.127 &  96.08225   & 0.3209038   $\pm$  0.1013991    $\pm$   0.0313346       \\
           1.610 & 0.193 & 0.127 &  138.5581   & 0.1170443   $\pm$  0.146122     $\pm$   0.02038013      \\
           1.610 & 0.193 & 0.127 &  180.2608   & 0.3477719   $\pm$  0.1581127    $\pm$   0.0354366       \\
           1.610 & 0.193 & 0.127 &  218.4883   & -0.091217   $\pm$  0.142311     $\pm$   0.01898904      \\
           1.610 & 0.193 & 0.127 &  261.3985   & -0.320382   $\pm$  0.1108918    $\pm$   0.0327608       \\
           1.610 & 0.193 & 0.127 &  303.3648   & -0.266328   $\pm$  0.07080153   $\pm$   0.02802882      \\
           1.610 & 0.193 & 0.127 &  337.2208   & -0.261976   $\pm$  0.07224138   $\pm$   0.02615273      \\
         \hline
         \hline
      \end{tabular}
      \caption{The coherent $A_{LU}$ in -t bins}
      \label{table:Coh_t_BSA}
   \end{center}
\end{table}

% incoherent channel

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
 \hline  
  1.395 & 0.166 & 0.407  &   21.10406  &  0.04811468 $\pm$  0.04658231  $\pm$  0.012062557     \\
  1.395 & 0.166 & 0.407  &   61.33965  &  0.0836005  $\pm$  0.0531715   $\pm$  0.015623204     \\
  1.395 & 0.166 & 0.407  &   95.84617  &  0.1792438  $\pm$  0.05315892  $\pm$  0.02637904      \\
  1.395 & 0.166 & 0.407  &   140.0124  &  0.04524659 $\pm$  0.07010027  $\pm$  0.0158652       \\
  1.395 & 0.166 & 0.407  &   181.9726  &  0.1242038  $\pm$  0.08510458  $\pm$  0.02346724      \\
  1.395 & 0.166 & 0.407  &   219.0216  &  0.03828423 $\pm$  0.07649991  $\pm$  0.01509915      \\
  1.395 & 0.166 & 0.407  &   259.0493  &  -0.1422473 $\pm$  0.0495869   $\pm$  0.02266091      \\
  1.395 & 0.166 & 0.407  &   303.8597  &  -0.1478417 $\pm$  0.03942399  $\pm$  0.01968592      \\
  1.395 & 0.166 & 0.407  &   337.5399  &  -0.0844819 $\pm$  0.04879445  $\pm$  0.01425768      \\
 \hline

  1.886 & 0.233 & 0.499 &    20.62881  &  -0.0058365 $\pm$  0.03877985  $\pm$  0.012482536     \\
  1.886 & 0.233 & 0.499 &    58.90961  &  0.1058029  $\pm$  0.05262749  $\pm$  0.016983385     \\
  1.886 & 0.233 & 0.499 &    95.93819  &  0.1373368  $\pm$  0.06176916  $\pm$  0.02021609      \\
  1.886 & 0.233 & 0.499 &    141.0758  &  0.2106814  $\pm$  0.09877572  $\pm$  0.02858216      \\
  1.886 & 0.233 & 0.499 &    179.8328  &  0.06009099 $\pm$  0.1188988   $\pm$  0.01464961      \\
  1.886 & 0.233 & 0.499 &    220.9095  &  -0.03806458 $\pm$  0.1066278   $\pm$  
 0.04304848      \\
  1.886 & 0.233 & 0.499 &    260.608   &  -0.1192977 $\pm$  0.07428519  $\pm$  0.01808374      \\
  1.886 & 0.233 & 0.499 &    304.2599  &  -0.2011292 $\pm$  0.05552498  $\pm$  0.0198082       \\
  1.886 & 0.233 & 0.499 &    338.4649  &  -0.0815212 $\pm$  0.0567802   $\pm$  0.01138369      \\
 \hline

  2.338 & 0.29 & 0.521  &    20.72956  &  0.08229175 $\pm$  0.03744839  $\pm$  0.013506039    \\ 
  2.338 & 0.29 & 0.521  &    56.90895  &  0.155593   $\pm$  0.05379751  $\pm$  0.01010521     \\ 
  2.338 & 0.29 & 0.521  &    94.91647  &  0.05217237 $\pm$  0.0715696   $\pm$  0.017660975    \\ 
  2.338 & 0.29 & 0.521  &    141.1955  &  0.1371172  $\pm$  0.1260972   $\pm$  0.01618568     \\ 
  2.338 & 0.29 & 0.521  &    181.6533  &  -0.2127209 $\pm$  0.1556657   $\pm$  0.02363223     \\ 
  2.338 & 0.29 & 0.521  &    224.0629  &  0.2006703  $\pm$  0.1501709   $\pm$  0.02122811     \\ 
  2.338 & 0.29 & 0.521  &    261.0354  &  -0.2716077 $\pm$  0.09343596  $\pm$  0.02419026     \\ 
  2.338 & 0.29 & 0.521  &    303.8146  &  -0.2199163 $\pm$  0.06880397  $\pm$  0.01534961     \\ 
  2.338 & 0.29 & 0.521  &    339.3798  &  -0.0379564 $\pm$  0.06803362  $\pm$  0.014507918    \\ 
 \hline

  3.098 &0.379 & 0.65  &     20.11158  &  0.1124871  $\pm$  0.03615842  $\pm$  0.014743619    \\ 
  3.098 &0.379 & 0.65  &     56.98647  &  0.0725830  $\pm$  0.0555646   $\pm$  0.014717011    \\ 
  3.098 &0.379 & 0.65  &     95.74599  &  0.1911079  $\pm$  0.07990027  $\pm$  0.02811833     \\ 
  3.098 &0.379 & 0.65  &     137.8186  &  -0.005798  $\pm$  0.1509773   $\pm$  0.01296021     \\ 
  3.098 &0.379 & 0.65  &     179.3002  &  -0.605363  $\pm$  0.2490573   $\pm$  0.027008585    \\ 
  3.098 &0.379 & 0.65  &     227.8571  &  0.1695245  $\pm$  0.1915087   $\pm$  0.02732611     \\ 
  3.098 &0.379 & 0.65  &     263.4649  &  -0.120036  $\pm$  0.09407594  $\pm$  0.02149023     \\ 
  3.098 &0.379 & 0.65  &     303.8994  &  -0.178453  $\pm$  0.04217566  $\pm$  0.02211641     \\ 
  3.098 &0.379 & 0.65  &     340.4588  &  -0.059749  $\pm$  0.03455414  $\pm$  0.01412915     \\ 
 \hline
 \hline
      \end{tabular}
      \caption{The incoherent $A_{LU}$ in $Q^2$ bins}
      \label{table:InCoh_Q2_BSA}
   \end{center}
\end{table}

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
         \hline 
  1.425 & 0.162 & 0.397 &   21.03589  &  0.08658236   $\pm$  0.04970597   $\pm$  0.013707438    \\
  1.425 & 0.162 & 0.397 &   62.13969  &  0.09617981   $\pm$  0.0520029    $\pm$  0.016508612    \\
  1.425 & 0.162 & 0.397 &   95.88097  &  0.1468384    $\pm$  0.05007717   $\pm$  0.02161179     \\
  1.425 & 0.162 & 0.397 &   140.2158  &  0.05840751   $\pm$  0.06522249   $\pm$  0.0149864      \\
  1.425 & 0.162 & 0.397 &   181.147   &  0.1472116    $\pm$  0.07694323   $\pm$  0.02355567     \\
  1.425 & 0.162 & 0.397 &   218.8907  &  -0.0045843   $\pm$  0.07180578   $\pm$  0.01995755     \\
  1.425 & 0.162 & 0.397 &   259.1392  &  -0.1140192   $\pm$  0.04807579   $\pm$  0.01836548     \\
  1.425 & 0.162 & 0.397 &   303.893   &  -0.1078614   $\pm$  0.04183492   $\pm$  0.01540446     \\
  1.425 & 0.162 & 0.397 &   337.0219  &  -0.0313563   $\pm$  0.05506042   $\pm$  0.01052464     \\
  \hline

  1.922 & 0.227 & 0.418 &   22.06063  &  -0.0071624   $\pm$  0.04158333   $\pm$  0.013118195    \\
  1.922 & 0.227 & 0.418 &   58.5659   &  0.09277118   $\pm$  0.05070619   $\pm$  0.016106517    \\
  1.922 & 0.227 & 0.418 &   96.23033  &  0.1248119    $\pm$  0.05973952   $\pm$  0.01838518     \\
  1.922 & 0.227 & 0.418 &   141.4482  &  0.1767175    $\pm$  0.09500723   $\pm$  0.0246086      \\
  1.922 & 0.227 & 0.418 &   181.8282  &  -0.0887164   $\pm$  0.1180524    $\pm$  0.01655364     \\
  1.922 & 0.227 & 0.418 &   221.2517  &  -0.2925814   $\pm$  0.102211     $\pm$  0.03431685     \\
  1.922 & 0.227 & 0.418 &   260.3485  &  -0.1909171   $\pm$  0.06539497   $\pm$  0.02278749     \\
  1.922 & 0.227 & 0.418 &   303.5284  &  -0.2302893   $\pm$  0.05094602   $\pm$  0.02067598     \\
  1.922 & 0.227 & 0.418 &   337.3474  &  -0.0637682   $\pm$  0.05413252   $\pm$  0.01008997     \\
  \hline

  2.354 & 0.287 & 0.492 &   20.85891  &  0.04657884   $\pm$  0.036766     $\pm$  0.01988718     \\
  2.354 & 0.287 & 0.492 &   57.91331  &  0.1459641    $\pm$  0.0526584    $\pm$  0.019557668    \\
  2.354 & 0.287 & 0.492 &   94.69206  &  0.128379     $\pm$  0.07104001   $\pm$  0.01884086     \\
  2.354 & 0.287 & 0.492 &   139.8528  &  0.1707919    $\pm$  0.1258279    $\pm$  0.02424851     \\
  2.354 & 0.287 & 0.492 &   179.8321  &  -0.3851509   $\pm$  0.1628791    $\pm$  0.014502416    \\
  2.354 & 0.287 & 0.492 &   225.9931  &  0.359824     $\pm$  0.1375561    $\pm$  0.014015373    \\
  2.354 & 0.287 & 0.492 &   261.519   &  -0.2473872   $\pm$  0.08518201   $\pm$  0.02723866     \\
  2.354 & 0.287 & 0.492 &   304.2744  &  -0.1756475   $\pm$  0.04527543   $\pm$  0.01784578     \\
  2.354 & 0.287 & 0.492 &   338.8707  &  -0.0591266   $\pm$  0.04527858   $\pm$  0.01010778     \\
 \hline

  2.987 & 0.390 & 0.714 &   19.433    &  0.1032664    $\pm$  0.03435814   $\pm$  0.014305278    \\
  2.987 & 0.390 & 0.714 &   55.24427  &  0.07535726   $\pm$  0.06348906   $\pm$  0.014826822    \\
  2.987 & 0.390 & 0.714 &   95.27441  &  0.21340720   $\pm$  0.1066241    $\pm$  0.03136377     \\
  2.987 & 0.390 & 0.714 &   134.3823  &  -0.2684007   $\pm$  0.2723481    $\pm$  0.03863117     \\
  2.987 & 0.390 & 0.714 &   182.475   &  3.6842530    $\pm$  5.592241     $\pm$  0.03642855     \\
  2.987 & 0.390 & 0.714 &   232.2045  &  -0.3810377   $\pm$  0.426418     $\pm$  0.04691644     \\
  2.987 & 0.390 & 0.714 &   264.8367  &  -0.0853021   $\pm$  0.1126019    $\pm$  0.02026491     \\
  2.987 & 0.390 & 0.714 &   304.1341  &  -0.1678875   $\pm$  0.04062397   $\pm$  0.02296748     \\
  2.987 & 0.390 & 0.714 &   341.2705  &  -0.0649467   $\pm$  0.03014188   $\pm$  0.01568537     \\
 \hline
 \hline
 \end{tabular}
 \caption{The incoherent $A_{LU}$ in $x_B$ bins}
 \label{table:InCoh_xB_BSA}
 \end{center}
\end{table}

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
  \hline
   1.823 & 0.213 & 0.145 &   22.36456  &   0.08044984  $\pm$  0.044171     $\pm$  0.013519389    \\
   1.823 & 0.213 & 0.145 &   57.76681  &   0.139094    $\pm$  0.05252524   $\pm$  0.019097037    \\
   1.823 & 0.213 & 0.145 &   97.34826  &   0.1215345   $\pm$  0.05070444   $\pm$  0.01794958     \\
   1.823 & 0.213 & 0.145 &   141.6077  &   0.1973951   $\pm$  0.07158507   $\pm$  0.0263301      \\
   1.823 & 0.213 & 0.145 &   180.9132  &   0.03301465  $\pm$  0.087735     $\pm$  0.01504234     \\
   1.823 & 0.213 & 0.145 &   219.6382  &   0.00344467  $\pm$  0.07526837   $\pm$  0.018209534    \\
   1.823 & 0.213 & 0.145 &   261.1274  &  -0.1527359   $\pm$  0.05030086   $\pm$  0.01958999     \\
   1.823 & 0.213 & 0.145 &   303.674   &  -0.1071745   $\pm$  0.04406731   $\pm$  0.0137369      \\
   1.823 & 0.213 & 0.145 &   337.0581  &  -0.06869941  $\pm$  0.04715184   $\pm$  0.01004524     \\
 \hline

  2.127 & 0.255 & 0.282  &   21.36259  &  0.07262895   $\pm$ 0.04230211    $\pm$  0.013126559   \\
  2.127 & 0.255 & 0.282  &   59.22203  &  0.03806518   $\pm$ 0.04905662    $\pm$  0.012518665   \\
  2.127 & 0.255 & 0.282  &   95.55563  &  0.22988040   $\pm$ 0.05867932    $\pm$  0.03380763    \\
  2.127 & 0.255 & 0.282  &   140.5704  &  -0.03154477  $\pm$ 0.08162287    $\pm$  0.0178829     \\
  2.127 & 0.255 & 0.282  &   181.2953  &  -0.1565047   $\pm$ 0.10092       $\pm$  0.0298368     \\
  2.127 & 0.255 & 0.282  &   219.844   &  -0.03787627  $\pm$ 0.09359193    $\pm$  0.01834677    \\
  2.127 & 0.255 & 0.282  &   259.6599  &  -0.1349929   $\pm$ 0.05604338    $\pm$  0.02535689    \\
  2.127 & 0.255 & 0.282  &   304.1345  &  -0.1822338   $\pm$ 0.03916768    $\pm$  0.02481545    \\
  2.127 & 0.255 & 0.282  &   338.5113  &  -0.07208852  $\pm$ 0.04495988    $\pm$  0.01711214    \\
 \hline                                                                          
  2.308 & 0.284 & 0.490 &    20.67062  &  0.129165     $\pm$ 0.0415758     $\pm$  0.015497728  \\
  2.308 & 0.284 & 0.490 &    59.71279  &  0.113594     $\pm$ 0.05196332    $\pm$  0.017545246  \\
  2.308 & 0.284 & 0.490 &    94.41645  &  0.1003674    $\pm$ 0.06511375    $\pm$  0.01472001   \\
  2.308 & 0.284 & 0.490 &    137.7611  &  0.1088956    $\pm$ 0.1159367     $\pm$  0.01662967   \\
  2.308 & 0.284 & 0.490 &    181.8561  &  0.3436873    $\pm$ 0.1353462     $\pm$  0.03922332   \\
  2.308 & 0.284 & 0.490 &    225.1743  &  -0.06749131  $\pm$ 0.1106012     $\pm$  0.01250426   \\
  2.308 & 0.284 & 0.490 &    259.4171  &  -0.2186645   $\pm$ 0.06202168    $\pm$  0.02341567   \\
  2.308 & 0.284 & 0.490 &    302.9163  &  -0.1778958   $\pm$ 0.03422616    $\pm$  0.01629588   \\
  2.308 & 0.284 & 0.490 &    338.8539  &  -0.04591294  $\pm$ 0.03922611    $\pm$  0.017893601  \\
 \hline                         
   2.406 & 0.308 & 0.90 &    20.16669  &  0.01851554   $\pm$ 0.03466921    $\pm$ 0.017815254  \\
   2.406 & 0.308 & 0.90 &    57.08842  &  0.167122     $\pm$ 0.06853916    $\pm$ 0.01086996   \\
   2.406 & 0.308 & 0.90 &    93.11341  &  0.07585309   $\pm$ 0.140148      $\pm$ 0.01108901   \\
   2.406 & 0.308 & 0.90 &    132.8371  &  -0.1390574   $\pm$ 0.4839775     $\pm$ 0.01772069   \\
   2.406 & 0.308 & 0.90 &    177.344   &  1.854154     $\pm$ 0.5453675     $\pm$ 0.01816686   \\ 
   2.406 & 0.308 & 0.90 &    228.2105  &  5.778605     $\pm$ 10.58589      $\pm$ 0.01512427   \\
   2.406 & 0.308 & 0.90 &    263.1194  &  0.02895751   $\pm$ 0.1390042     $\pm$ 0.017122356  \\
   2.406 & 0.308 & 0.90 &    305.0914  &  -0.1501369   $\pm$ 0.04840413    $\pm$ 0.01297528   \\
   2.406 & 0.308 & 0.90 &    340.095   &  -0.05253375  $\pm$ 0.03990596    $\pm$ 0.016446498  \\
 \hline
 \hline
 \end{tabular}
 \caption{The incoherent $A_{LU}$ in -t bins}
 \label{table:InCoh_t_BSA}
 \end{center}
\end{table}

### 2016-06-27 analysis-note-v2/Hadron_structure.tex
added the second version of the analysis note

\chapter{Introduction} \label{Nuclear_DVCS}
\section{DVCS off Helium-4} \label{Nuclear_DVCS}
~~~~Nuclear targets provide access to the measurement of two DVCS channels: the coherent and the incoherent. In the coherent channel, the target nucleus remains intact and recoils as a whole while emitting a real photon ($eA \rightarrow e' A' \gamma$). This process allows to measure the nuclear GPDs of the target, which contain information on the partons correlations and the nuclear forces in the target \cite{M_Polyakov,EMC_simonetta}. In the incoherent channel, the nucleus breaks up and the DVCS takes place on a bound nucleon that emits the final photon ($eA \rightarrow e' N' \gamma$ X). The latter allows to measure the GPDs of the bound nucleons and study the medium modifications of the nucleons in the nuclear medium. Figure \ref{fig:nuclear_DVCS} shows the diagrams of the two DVCS channels. \\
\begin{figure}[tbp]
\centering
\includegraphics[scale=0.3]{fig/nuclear_DVCS.png}
\caption{The leading twist handbag diagrams of the two DVCS channels from a nuclear target, coherent channel (on the left) and incoherent channel (on the right). } 
\label{fig:nuclear_DVCS}
\end{figure}

The GPDs depend on three variables: $x$, $\xi$ and $t$. $x+\xi$ is the 
nucleon's longitudinal momentum fraction carried by the struck quark, 2$\xi$ is 
the longitudinal momentum fraction of the momentum transfer $\Delta$ ($= p' - 
p$), and $t$ (=$\Delta^{2}$) is the squared momentum transfer between the 
initial and the final states of the hadron target. Experimentally, only $\xi$ 
and $t$ are measurable in the DVCS reaction. At twist-2 order, $\xi$ can be 
calculated as $x_B/(2-x_B)$, where $x_B$ is the Bjorken variable $(= 
Q^{2}/(2M_{N}(E-E')$ with $Q^2$ is the vertuality of the exchanged photon, 
$M_{N}$ is the mass of the nucleon and $E(E')$ is the energy of the incident 
(scattered) electron.\\

The number of GPDs needed to parametrize the partonic structure of a nucleus 
depends on the different configurations between the spin of the nucleus and the 
helicity direction of the struck quark.  In principle, for a target of spin 
$s$, the number of the chiral-even GPDs is equal to ($2s+1$)$^2$ for each quark 
flavor.  For instance, at leading twist level, nine chiral-even GPDs are 
required to parametrize the partonic structure of the deuteron, because it has 
a spin one \cite{Kir, Van}.  This makes studying this nucleus a non-trivial 
task.  The DVCS off spinless nuclear targets, such as $^4He$, $^{12}C$ and 
$^{16}O$, is simpler to study as only one GPD ($H_{A}(x,\xi,t)$) arises at 
leading twist to parametrize their partonic structure.\\

 Nuclear DVCS provides a quantitative information on the nuclear medium 
 effects, the quark confinement size of the bound nucleons, see figure 
 \ref{fig:quarks_nucleus}. The Fourier transform of the nucleon GPDs over the 
 momentum transfer $\Delta$ gives the transverse separation ($b'$) between 
 quarks in the nucleon, while the transform of the nuclear GPD 
 ($H_{A}(x,\xi,t)$) gives the transverse separation ($b$) between the quarks in 
 the nucleus. Knowing these two separations, one can access the transverse 
 separation ($\beta = b - b'$) between the nucleons in a nucleus 
 \cite{EMC_simonetta}.\\
%\begin{eqnarray}
%q_{N}(x,b') &=& \int \frac{d^{2}\Delta}{2\pi^{2}} e^{ib'.\Delta} H_{N}(x,0,t) \Rrightarrow q_{N}(x) = \int d^{2}b' q_{N}(x,b')\\
%q_{A}(x,b') &=& \int \frac{d^{2}\Delta}{2\pi^{2}} e^{ib.\Delta} H_{A}(x,0,t) \Rrightarrow q_{A}(x) = \int d^{2}b q_{A}(x,b)\\
%\rho_{A}(y,\beta) &=& \int \frac{d^{2}\Delta}{2\pi^{2}} e^{i\beta.\Delta} \rho_{A}(y,0,t) \Rrightarrow \rho_{A}(y) = \int d^{2}\beta \rho_{N}(y,\beta)
%\end{eqnarray}
\begin{figure}[tbp]
\centering
\includegraphics[scale=0.6]{fig/quarks_nucleus.png}
\vspace{-0.7in}
\caption{The spatial coordinates of quarks in a nucleus. See main text for definition of the variables. The figure is from \cite{simonetta_pre}. } 
\label{fig:quarks_nucleus}
\end{figure}

The $^4$He nucleus shows a clear EMC effect. This nucleus is characterized by its spin-zero, a high density and it is a well-known few-body system. These aspects make the $^4$He nucleus an ideal target to be considered for the understanding of the nuclear effects at the partonic level. \\

  In principle, the $^4$He GPD $H_{A}(x,\xi,t)$ characterized by:
 \begin{itemize}
 \item The universality of $H_{A}$: the $H_{A}$ describes the partonic structure of the $^4$He in a DVCS reaction the same way as in a DVMP reaction. 
 \item In the forward limit ($t\rightarrow 0$), $H_{A}$ is reduced to the usual PDF of $^4$He that is accessible via DIS.
 \item $H_{A}$ can be decomposed into a polynomial in $\xi$.
 \item The first moment of $H_{A}$ is the $^4$He elastic electromagnetic form factor $F_{A}(t)$, such as:
 \begin{equation}
   \sum_{q} \int_{-1}^{1} dx ~H_{A}^{q}(x, \xi, t) =  F_{A}(t),
\end{equation}
  where the sum runs over all the quark flavors.
  \item The second moment of $H_{A}^{q}(x, \xi, t)$ reads
  \begin{equation}
  \int_{-1}^{1} dx ~x H_{A}^{q}(x, \xi, t) = M ^{q/A}_{2}(t) + \frac{4}{5} \xi^{2} d^{q/A}_{2}(t)
  \end{equation}
    where the first term of the right-hand side represents the momentum fraction carried by each quark flavor q, and the second term is encoding information about the forces experienced by partons inside the nuclei \cite{M_Polyakov}. 
  \item $H_{A}$ is not directly measured from experiment, but we measure its corresponding Compton form factor $\mathcal{H}_{A}$. 
\end{itemize}  
~~~~The $^4$He DVCS amplitude can be expressed as \cite{Kir}:
 \begin{equation}
 \mathcal{T}_{DVCS} \propto \sum_{q} e^{2}_{q} \mathcal{P} \int_{-1}^{1} dx \left(\frac{1}{x-\xi} + \frac{1}{x+\xi} \right) H^{q}_{A}(x,\xi,t) \\- i\pi \sum_{q} \left( e^{2}_{q} \left[ H^{q}_{A}(\xi,\xi,t) - H^{q}_{A}(-\xi,\xi,t) \right] \right),
\end{equation}
 where the first term on the right-hand side stands for the real part of the CFF $\mathcal{H}_{A}$, while the second term for the imaginary part of $\mathcal{H}_{A}$. \\

The coherent DVCS amplitude is enhanced through the interference with the BH process, that is calculable from the well-known elastic FF. Figure \ref{fig:He-4_FFs} shows the world measurements of the $^4$He $F_{A}(t)$ along with theoretical calculations. Following the $F_{A}(t)$ parametrization by R. Frosch and his collaborators \cite{He_4_FF_Frosch} (valid at the small values of $-t$ which are of interest in this work), figure \ref{fig:BH_cross_section_4He} shows the calculated BH as a function of the azimuthal angle between the leptonic and the hadronic planes ($\phi$), using a 6~GeV electron beam on a $^4$He target.\\

  The experimentally measured $e ^4He \rightarrow e ^4He \gamma$ cross section can be decomposed into BH, DVCS, and interference terms. The differential cross section can be written like in Appendix \ref{app:Helium_cross_section}, equation \ref{eq:sigdiff}. By generalizing the BMK model \cite{Kir}, the nuclear BH, DVCS and interference scattering amplitudes can be decomposed into a finite series of Fourier harmonics as can be found in Appendix \ref{app:Helium_cross_section}, equations \ref{TTBH}, \ref{TTDVCS} and \ref{TTinter}.\\

\begin{figure}[tp]
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.2in}\includegraphics[height=6.1cm]{fig/He-4_FF.png}
\caption{$^4$He charge form factor measurements at Stanford, SLAC, Orsay, Mainz and JLab Hall A compared with theoretical calculations. The figure is from \cite{He_4_FF}. } 
\label{fig:He-4_FFs}
\end{minipage} \hfill
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.3in}\includegraphics[height=6.3cm]{fig/BH_He-4.png}
\caption{The calculated BH cross section as a function of $\phi$ on a $^4He$ target at three values of $x_{B}$ and fixed values of $Q^{2}$ and $t$. ($t$~=~-~0.1~GeV$^2$/c$^2$ corresponds to $Q^2$~$\approx$~2.57~fm$^{-2}$ on figure \ref{fig:He-4_FFs}).}
\vspace{+0.3in}
\label{fig:BH_cross_section_4He}
\end{minipage}
\end{figure}

\subsection{Beam-spin asymmetry}
~~~~It is convenient to use the beam-spin asymmetry as DVCS observable because most of the experimental normalization and acceptance issues cancel out in an asymmetry ratio. The beam-spin asymmetry is measured using a polarized lepton beam on an unpolarized target (U). JLab provides a longitudinally (L) polarized electron beam, $P_{B}~\approx$~85~$\%$. It is defined as:
  \begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
  where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the DVCS differential cross section for a positive (negative) beam helicity.\\

 At leading twist, the beam-spin asymmetry ($A_{LU}$) with the  two opposite helicities of a  longitudinally-polarized electron beam (L) on a spin-zero target (U) can be written as:        
\begin{eqnarray}
A_{LU}& =& \frac{x_A(1+\epsilon^2)^2}{y} \, s_1^{INT} \sin(\phi) \, 
\bigg/ \, \bigg[ \, \sum_{n=0}^{n=2}c_n^{BH}\cos{(n\phi)} +  \\
& & \frac{x_A^2 t {(1+\epsilon^2)}^2}{Q^2} P_1(\phi) P_2(\phi) \, c_0^{DVCS} + 
\frac{x_A (1+\epsilon^2)^2}{y} \sum_{n=0}^{n=1} c_n^{INT} \cos{(n\phi)} \bigg].  \nonumber 
\label{eq:coh_BSA}
\end{eqnarray}

where $\mathcal{P}_1(\phi)$ and $\mathcal {P}_2(\phi)$ are the Bethe-Heitler 
propagators. The factors: $c_{0,1,2}^{BH}$, $c_0^{DVCS}$, $c_{0,1}^{INT}$ and 
$s_1^{INT}$ are the Fourier coefficients of the BH, the DVCS and the 
interference amplitudes for a spin-zero target \cite{Kir}. The explicit 
expressions of these coefficients can be found in Appendix 
\ref{app:Helium_cross_section}.\\

\subsection{Theoretical predictions} \label{Theoretical_hypotheses}
\paragraph{On-shell calculations}
~\\
~\\  
~~~~The nuclear GPD $H_{A}$ can be described as the sum of the individual nucleons' GPDs. In the model based on the impulse approximation of V. Guzey {\it et al.} \cite{EMC_vadim_1, EMC_vadim_3}, a nucleus  is assumed to consist of non-relativistic non-interacting nucleons, and these nucleons interact independently with the probe. Assuming that the nucleon GPDs $H$ and $E$ are the dominant GPDs in the unpolarized target scattering case, the nuclear GPD $H_{A}$ for each quark flavor $q$ can be written as:
\begin{align}
H_{A}^{q}(x_A, \xi_{A}, t) &= \frac{dx_{N}}{dx_{A}} \Bigg[ Z \bigg( H^q_p(x_{N}, 
\xi_{N}, t) + \frac{t}{4 M^2} E^q_p(x_{N}, \xi_{N}, t) \bigg)\\ \nonumber
& + (A-Z) \bigg( H^q_n(x_{N}, \xi_{N}, t) + \frac{t}{4 M^2} E^q_n(x_{N}, \xi_{N}, t) 
\bigg) \Bigg] F_{A}(t),
\label{eq:guzey}
\end{align}
where the factor $dx_{N}/dx_{A}$ is the Jacobian for the transformation of $x$ 
from the nucleonic $x_N$ to the nuclear $x_{A}$. It is equal to $ 
A(2-x_{A})/(2-x_{B})$ with $x_A = x_B/A$. $\xi_{A}$ is defined as 
$x_{A}/(2-x_{A})$ and $\xi_{N}$ is equal to $x_B/(2-x_B)$. For free nucleons, the 
GPDs are constructed using the double distributions ansatz 
\cite{free_proton_GPDs}.  In this approximation, the GPD $H$ with its evolution 
in $Q^2$, can be written as:
\begin{equation}
H^{q}(x,\xi,t, Q^2) = \int_{0}^{1}d\beta \int_{-1+|\beta|}^{1+|\beta|} d\alpha \delta(\beta +\alpha \xi -x) \pi(\beta, \alpha) \beta^{-\alpha'(1-\beta)t} q_{\nu}(\beta, Q^2),
\end{equation} 
where the parameters $\alpha$ and $\beta$ are new variables that link $x$ and $\xi$ linearly as $x = \beta + \alpha \xi$, $q_{\nu}$ is the valence unpolarized PDF and the profile function $\pi(\beta, \alpha)$ takes the form
\begin{equation}
\pi(\beta, \alpha) = \frac{3}{4} \frac{(1-\beta)^2 - \alpha^2}{(1-\beta)^3}.
\end{equation}
The t-dependence of the GPD is introduced through Regge ansatz \cite{guidal_2}, with the slope $\alpha'$ equal to 1.105 GeV$^{-2}$ that allows to recover the ordinary form factors of the nucleons.\\

This model enables to link the nuclear CFFs to the ones of the nucleons. However, it neglects the medium modifications and the binding effects between the nucleons in a nucleus. To take into account the nuclear modifications, the bound nucleons can be assumed to be modified in proportion to the corresponding bound nucleon elastic form factors \cite{EMC_vadim_2}. That is, the GPD $H$ of the bound proton ($H^{q/p*}$) can be written as:
\begin{equation}
H^{q/p*}(x,\xi,t, Q^2) = \frac{F^{p*}_{1}}{F^{p}_{1}} H^{q/p}(x,\xi,t, Q^2),
\end{equation}
where $F^{p}_{1}$ ($F^{p*}_{1}$) is the Dirac form factor of the free (bound) proton.
The bound nucleon form factor is calculated using the Quark-Meson Coupling (QMC) model \cite{QMC}, that predicts a suppression as the nuclear density increases. As a result of these calculations, figure~\ref{fig:EMC_vadim} shows the ratio of the bound (incoherent DVCS channel off $^4$He) to free proton beam-spin asymmetry ($A_{LU}$), at $\phi$ = 90$^{\circ}$, as a function of $x_B$, using a 6-GeV longitudinally-polarized electron beam at $Q^2$=~2~GeV$^2$/c$^2$ and two values of the transfer momentum $t$. This ratio represents a generalization of the EMC effect, for $t$ greater than zero. This model predicts an enhancement of the bound-proton beam-spin asymmetry, which increases with $t$. \\
\begin{figure}[tbp]
\centering
\includegraphics[scale=0.35]{fig/EMC_ALU_vadim.png}
\caption{The theoretical predictions by V.~Guzey \cite{EMC_vadim_2} for the 
"generalized" EMC effect in terms of the beam-spin asymmetry ratio between the 
bound proton in $^4$He and the free proton as a function of Bj\"orken variable 
$x_B$. The calculations are performed at two values of $-t$, 0.2 and 0.4 
GeV$^2$/c$^2$, with a 6 GeV electron beam and $Q^2$ = 2 GeV$^2$/c$^2$. } 
\label{fig:EMC_vadim}
\end{figure}

\paragraph{Off-shell calculations}
~\\
~\\ 
Another model for nuclear GPDs in the impulse approximation uses the nuclear spectral function. For a spin-zero nucleus, the GPD $H^{A}$ can be written as \cite{EMC_simonetta}:
\begin{align}
H^{A}(x, \zeta, t) &= \sum_{N} \int \frac{d^{2}P_{\perp} dY}{2(2\pi)^3} \, 
   \frac{1}{A-Y}\,  \, \rho^{A}(P^2, P'^2) \mathcal{A}\\ \nonumber
& ~~~~~~~~ \times \sqrt{\frac{Y-\zeta}{Y}} \left[H^{N}_{OFF}(\frac{x}{Y}, 
\frac{\zeta}{Y},P^2, t) - \frac{1}{4} \frac{(\zeta/Y)^2}{1-\zeta/Y } 
E^{N}_{OFF}(\frac{x}{Y}, \frac{\zeta}{Y},P^2, t) \right]
\label{eq:simonetta}
\end{align}
where $P$ and $P'$ are the incoming and outgoing nucleons three-momenta, $Y$ is 
a dynamical variable defined as $\frac{y+A\zeta}{1+\zeta}$, $\mathcal{A} = 
(Y-\zeta/2)(\sqrt{Y(Y-\zeta)})$ is a normalization factor with $\zeta = 
\frac{2\xi}{1+\xi/A}$, $\rho^{A}(P^2, P'^2)$ is the off-forward nuclear 
spectral function accounting for all configurations of the final nuclear system 
and the binding effects between the nucleons. In a non-relativistic 
approximation, $\rho^{A}$ is defined as \cite{simonetta_2}:
\begin{equation}
\rho^{A}(P^2, P'^2) = 2\pi M_A \int dP\,P\,\Phi(P)\,\Phi(P') 
\end{equation}
with $\Phi$ the nuclear wave function in momentum space. The off-forward nucleon GPDs, $H^{N}_{OFF}$ and $E^{N}_{OFF}$, are characterized by the off-shellness which is linked to $P^2$. One recovers the free nucleon GPDs by disregarding this off-shellness.\\

The nuclear effects can be expressed with the ratio between the nuclear and the nucleon GPDs. This ratio becomes equal to the ordinary EMC ratio in the forward limit ($t = 0$). As the nuclear form factor of the $^4$He has a steeper drop in $t$ than the nucleonic one, it is more convenient to define the ratio between normalized GPDs as:
\begin{equation}
R_{A}(x, \xi,t) = \frac{H^{A}(x, \xi, t)/F^{A}(t)}{H^{p}(x, \xi, t)/F^{1}_{p}(t)}
\end{equation}
where $F^{1}_{p}(t)$ is the Dirac form factor of the proton. Figure \ref{fig:4HeEMC_RA} shows the EMC ratios measured via DIS on $^4$He compared to theoretical calculations. One can see that the latter calculations by S.~Liuti and K.~Taneja describe the EMC effect differently than the first scenario due to the off-shell effects of the nucleons associated in their calculation.\\

The nuclear effects can be also viewed as the beam-spin asymmetry ratio ($\frac{A^{Incoh}_{LU}}{A^{p}_{LU}}$) between the incoherent proton and the free proton. Figure \ref{fig:EMC_Simonetta} shows the predicted EMC effect in $^4$He in terms of $\frac{A^{Incoh}_{LU}}{A^{p}_{LU}}$ as a function of $x_B$. The calculated ratio appears to be very sensitive on $t$, which encodes the information on the transverse degrees of freedom of the partons in the nucleon.\\

\begin{figure}[tbp]
\begin{minipage}[c]{.46\linewidth}
%\hspace{-0.4in}
\includegraphics[height=7.8cm]{fig/4HeEMC_RA.png}
\caption{The EMC effect in $^4$He. The data points are the $^4$He EMC ratios \cite{He4_DIS_data}. The black dotted and solid curves are theoretical calculations based on a binding and a diquark model respectively, at $-t$= 0.1 GeV$^2$/c$^2$. The blue curve shows the theoretical calculation at the forward limit by Liuti and Taneja \cite{EMC_simonetta}.} 
\label{fig:4HeEMC_RA}
\end{minipage} \hfill
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.3in}
\includegraphics[height=7.8cm]{fig/EMC_ALU_simonetta.png}
\caption{The theoretical calculations by S. Liuti and K. Taneja \cite{EMC_simonetta} of the beam-spin asymmetry ratio between the bound proton, in $^4$He, and the free proton. The ratio is plotted as a function of $x$ at three different values of $-t$: 0, 0.095, and 0.329 GeV$^2$/c$^2$.}
\label{fig:EMC_Simonetta}
\vspace{+0.2in}
\end{minipage}
\end{figure}

We conclude that nuclear DVCS is a promising field that can give more details about the nature of the nuclear forces through the study of the nuclear GPDs, and through the study of the modifications of the nucleons' GPDs in nuclei.

\subsection{Nuclear DVCS measurements}
~~~~~The first nuclear DVCS experiments were carried out by the HERMES 
collaboration \cite{HERMES_BSA}. In these measurements, 
longitudinally-polarized electron and positron beams at energies equal to 27.6 
GeV were scattered onto fixed nuclear targets (hydrogen, helium-4, nitrogen, 
neon, krypton and xenon) to study the DVCS reaction. The HERMES spectrometer 
did not detect the nuclear recoils. However, the exclusivity of the selected 
DVCS events was approximately ensured by a cut on the missing mass of the final 
state configuration $e\gamma X$. The separation between the coherent and the 
incoherent DVCS channels was made with a cut on $t$: the coherent channel is 
assumed to dominate the low $t$-region, while the higher $t$-region is assumed 
to be dominated by the incoherent channel on the protons and the neutrons.  
Figure \ref{fig:HERMES_BSA} shows the $\sin(\phi)$ amplitude of the beam-spin 
asymmetries off the different targets in $t$-bins measured by HERMES.  These 
asymmetries are further separated into coherent and incoherent asymmetries.  
Figure \ref{fig:HERMES_BSA_1} shows the mass dependence of the $\sin(\phi)$ 
amplitude of the coherent and the incoherent beam-spin asymmetries integrated 
over all the data sample for each target type.\\

\begin{figure}[tbp]
\centering
\includegraphics[height=9.7cm]{fig/HERMES_BSA.png}
\caption{The $t$-dependence of the $\sin(\phi)$ amplitude of the beam-spin asymmetries measured by HERMES on different nuclear targets. The error bars show only the statistical uncertainties, while the systematic uncertainties are indicated by the bands on each plot. \cite{HERMES_BSA}.} 
\label{fig:HERMES_BSA}
\end{figure}
\begin{figure}[tbp]
\centering
\includegraphics[height=8.0cm]{fig/HERMES_BSA_2.png}
\caption{The nuclear-mass dependence of the $\sin(\phi)$ amplitude of the beam-spin asymmetries for the coherent (upper panel) and the incoherent (lower panel) data samples. The values of $t_{coh}$ and $t_{incoh}$ for each nuclear target were determined from Monte-Carlo simulations \cite{HERMES_BSA}.}
\label{fig:HERMES_BSA_1}
\end{figure}

The HERMES inclusive measurements of the nuclear beam-spin asymmetries clearly suffer from a lack of statistics for a precise investigation of their physics content. Within the given uncertainties, their nuclear beam-spin asymmetries have shown neither enhancement, nor a nuclear-mass dependence.

### 2016-06-27 analysis-note-v2/RTPC.tex
added the second version of the analysis note

\chapter{Radial time projection chamber}

\section{The EG6 RTPC}

~~~~At 6 GeV incident electron beam energy, the recoil $^{4}He$ nuclei from the coherent DVCS channel, have an average momentum around 200 MeV/c. CLAS cannot detect such low energy particles, for exemple protons are detected with a threshold of about 250 MeV/c, which will be even worse for helium. In order to detect such low-energy recoils a Radial TPC (RTPC), similar to the one used during the BoNuS run \cite{BONUS}, was added to CLAS. In 2009, the CLAS-EG6 group \cite{proposal} has built this RTPC, figure \ref{fig:RTPC2} shows a close photo of the RTPC, while figure \ref{fig:RTPC_xscetion} shows a schematic drawing of its internal structure. It is a 200 mm-long and 150 mm-diameter TPC, composed of two electronically separated modules, each covering about 150$^{\circ}$ of the azimuthal angle. The RTPC tracks the charged particles through the ionization centers they leave in the gas-filled detection volume. Then, the ionized electrons drift under the effect of an electric field and are amplified by a gas electron multiplier system before to be detected on collection pads.

\begin{figure}[tp]
\begin{minipage}[c]{.46\linewidth}
\vspace{0.3in}
\includegraphics[height=6.2cm]{fig_rtpc/RTPC_exp_cut.jpg}
\vspace{0.1in}
\caption{A view of the RTPC before insertion into the solenoid. The incident electron beam comes from the left.} 
\label{fig:RTPC2}
\end{minipage} \hfill
\begin{minipage}[c]{.46\linewidth}
\hspace*{-0.3in}\includegraphics[height=8.0cm]{fig_rtpc/RTPC_1_all.png}
\caption{A cross section of the RTPC taken on a plane perpendicular to the beam line, with a typical $^4He$ track crossing the drift volume.}
\label{fig:RTPC_xscetion}
\end{minipage}
\end{figure}

\subsection{Design}

The RTPC has the following substructure, from the beam axis to the exterior:

\begin{itemize}
\item The target extends along the RTPC's central z-axis, with a diameter of 6 mm. It is enclosed in a 27-$\mu$m-thick Kapton wall.

\item The first gas gap extends from 3 mm to 20 mm radial distances. It is filled with $^{4}He$ gas at one atmospheric pressure. This region is swarmed with M\o ller electrons induced by the beam, but filling this region with a light gas like $^{4}He$ at low pressure minimizes their secondary interactions, while the magnetic field of the solenoid keeps them away from the sensitive drift region. This gap is surrounded by a grounded window made of 4-$\mu$m-thick aluminized mylar.

\item The second gas gap extends from 20 mm to 30 mm radial distances and is filled with a gas mixture of 80$\%$ Neon (Ne) and 20$\%$ Dimethyl Ether (DME: $C_{2}H_{6}O$). This drift gas fills all the following gaps up to the external shell.

\item The cathode foil, which is made of 4-$\mu$m-thick aluminized mylar, surrounds the second gas gap. It is connected to a voltage of 4.3 kV to generate an electric field in the drift region.

\item The drift region is filled with the Ne-DME gas mixture. It extends from the cathode, 30 mm from the beam line, to the first gas electron multiplier layer, 60 mm from the beam line.

\item The amplification system is composed of three Gas Electron Multiplier (GEM) layers located at radii of 60 mm, 63 mm, and 66 mm.

\item The electron collection system has an internal radius of 69 mm and collects the charges. The data are then pre-amplified and transmitted to the data acquisition system.  
\end{itemize}

The Ne-DME gas mixture has been chosen as the drift gas because of its low-diffusion characteristics and small Lorentz angles (the angles between the drift direction of electrons under the influence of magnetic field and the direction of the electric field). These characteristics minimize the changes in the drift velocity of the ionization electrons \cite{DME}.\\

The GEMs amplify the ionized electrons to produce measurable signals. Figure \ref{fig:GEMs} shows a microscopic photo of a GEM. It is made from an insulator (Kapton) sandwiched between two copper layers. The mesh of each GEM layer is chemically etched with 50-$\mu$m-diameter holes in double-conical cross section shapes, as can be seen from the schematic plot on the right.\\

\begin{figure}[tbp]
\centering
\includegraphics[height=5.5cm]{fig_rtpc/GEM_photo.jpg}
\hspace{0.4in}
\includegraphics[height=6.0cm]{fig_rtpc/gem_holes.png}
\caption{On the left: A microscopic image of a GEM shows the amplification holes, and the two copper layers, separated by a Kapton insulator. This figure is from \cite{BONUS_2}. On the right: Schematic of the hole structure in the GEMs with the electric field lines (solid red) and the equipotentials (dashed blue). This figure is from
 \cite{GEM_holes}. } 
\label{fig:GEMs}
\end{figure}

 The electrons amplification is achieved through the holes via the strong electric field, that is generated by a 400-V potential difference between the two copper layers. Such a strong field leads to high ionization of the initial electrons and therefore amplification of the signals. Furthermore, an additional potential difference of 150 V is set between each two successive GEM layers to push the amplified electrons towards the readout board. In this configuration, the gain of each GEM layer is of the order of 100.\\

 The RTPC electron collection system has 3200 readout pads. Each module of the 
 RTPC has 40 rows and 40 columns of readout pads, each is 5 mm long and 4.45 mm 
 wide. Each group of 16 pads is connected to a pre-amplifier before the 
 recorded signals are carried to the acquisition electronics. There are 20 
 rows and 5 columns of pre-amplifiers per module. This readout system records 
 the charge information in time bins, in which the charge is measured in 
 Analog-to-Digital-Converter (ADC) units, while the time is 
 recorded in Time-to-Digital-Converter (TDC) units, in which each TDC is equal 
 to 114 ns. This measurement indicating the time taken by the electrons to drift from the 
 ionization point to the readout board.

\subsection{Working principle}
~~~~When a charged particle traverses a gas, it ionizes the gas-atoms along its trajectory. In a TPC, the electrons released in the ionization drift towards the readout board under the effect of an applied electric field. The drift velocity depends on the gas mixture, and on the electric ($\vec{E}$) and magnetic ($\vec{B}$) fields. The recorded time of the electrons provides information on how far the initial ionizations happened in the drift region, leading to reconstruct the original points of ionization, while the recorded ADCs give the deposited energy.\\

In our TPC the cathode and the anode are two cylinders. Thus, the generated $\vec{E}$ field in the drift region has a purely radial components, perpendicular to the beam line, with a magnitude around 500 V/cm. However, the two-cylinders configuration produces small gradient components at the sides of the RTPC. This issue was solved by installing field cages at the ends of the RTPC to keep a regular $\vec{E}$ field. These caused some high voltage issues and were disconnected during the experiment, partly justifying the time dependent calibration described below. \\

 The $\vec{B}$ field is generated by the solenoid. Figure \ref{fig:B_MAP} shows the magnetic field vectors in the different regions of the RTPC. The presence of the magnetic field enables us to deduce the momentum of a charged particle from the curvature of its track and the known magnetic field.
% from:
%\begin{equation}
%p = R q |\overrightarrow{B}| sin(\theta)
%\end{equation}
%where R is the radius of the track's curvature, q and $\theta$ are the charge and the polar angle of the %particle.

\begin{figure}[tp]
\centering
\includegraphics[scale=0.40]{fig_rtpc/B_MAP.png}
\caption[]{The solenoid magnetic field vectors in the RTPC, shown in the $r-z$ plane, where $r$ is the radial distance from the central axis and $z$ represents the longitudinal distance along the RTPC.} 
\label{fig:B_MAP}
\end{figure}

\subsection{Track reconstruction}
~~~~In order to reconstruct tracks we must first select the good hits. The 
first step is the rejection of out-of-time hits and the noise reduction, as 
will be explained in section \ref{sec:noise_rejection}. The second step is the 
spatial reconstruction of the hits, using the extracted drift speed and drift 
paths. For each registered hit, the position of the initial ionization is 
obtained from the recorded time (TDC) and from the position of its pad.  In the 
third step, the reconstructed nearby hits are linked together in  chains.  The 
maximum distance between two adjacent hits must be less than 10.5 mm to chain 
them. Then, the number of hits per chain is required to be greater than 10 hits 
in order to proceed to the fitting step. \\

A fit to a chain of hits is performed in two iterations. In the first iteration, the hits of the chain are fitted with a helix. The helix fit is based on a circle fit in the $x-y$ plane followed by a linear fit in the $s-z$ plane for the hits of the chain, where $s=\sqrt{x^2+y^2}$.  In the second iteration, the residual between the fit and each hit is calculated. If the hit's residual is greater than 5 mm, the hit is excluded from the chain. Then the hits are re-fitted with the same previous helix fit giving five final parameters for each track's chain. From these five parameters, one can reconstruct all the parameters of a track. For example, one can calculate the momentum from the known longitudinal magnetic field ($\vec{B_{z}}$), the radius of curvature of the track ($r_{0}$) and the polar angle ($\theta$), like:
\begin{eqnarray}
p_{tot} = \sqrt{p_{\|}^2 + p_{\perp}^2}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \\
\text{with } p_{\perp} = 0.3\cdot q \cdot B_{z} \cdot |r_{0}|\text{and } p_{\|} = p_{\perp}/tan(\theta),\nonumber
\end{eqnarray}
where $p$ is in GeV/c unit, $q$ is the elementary charge, $B_{z}$ is in Tesla (T) and $r_{0}$ is in meters (m). For example, In a magnetic field of 4.5 T, the recoil $^4$He nuclei from DVCS (elastic) reaction have kinetic energies in the range [10, 25] ([17, 35]) MeV, from momenta of [260, 450] ([360, 550]) MeV and $r_{0}$ [70, 150] ([130,180]) mm.

\section{RTPC calibration}
~~~~Reconstructing a trajectory from the recorded time information of the electrons requires a good knowledge of their drift speed and drift paths. Also, the gains of the readout pads are required to calculate $\frac{dE}{dx}$ from the recorded ADCs. The drift paths and the gain calibration of the RTPC require well identified events, so we decided to use elastic scattering ($e^{4}He \rightarrow e^{4}He$). We had specific calibration runs with 1-pass beam energies of 1.024 and 1.269 GeV in order to enhance the cross section of the elastic process at large angles, which is highly suppressed at higher beam energy.\\

A GEANT4 simulation for the RTPC has been developed to help reproduce these events in order to properly extract the drift paths and the gains. Their extractions are based on comparing the experimentally identified $^4He$ elastic tracks to the GEANT4 simulated ones. Indeed, the kinematics of each elastic $^4He$ can be calculated from the electron measured in CLAS and then simulated in GEANT4. The output of the simulation is then compared with the measured signals to determine the drift paths. \\

This process is iterative since good tracks need to be identified at the beginning of the process. For this analysis, we started from a MAGBOLTZ calibration, which was then improved with the method described above with several iterations. In particular, changes in the alignment of the RTPC with respect to the beamline, detailed in CLAS-NOTE~\cite{eg6beamoffset}. In the following subsections, we present here only the selection of the RTPC tracks and elastic events for the last iteration of our calibration process. It is then followed by details on the techniques of calibration.

\subsection{Event selection}
~~~~Figure \ref{fig:RTPC_track} shows a drawing of a segment of the RTPC, where a $^4He$ track (in 
green) crosses the volume of the RTPC, producing a chain of ionization points 
within the drift gas. The released electrons follow the drift paths (in black) 
towards the readout board under the effect of the  electromagnetic field 
between the anode and the cathode. The electrons released close to the cathode 
take the maximum drift time ($TDC_{max}$) to reach the readout pads, while the 
electrons released close to the anode take the minimum time ($TDC_{min} = 15$ the 
trigger time), also called time offset, which is identical 
for all readout channels. In our convention, the distance between the 
first ionization point in the chain and the cathode is labelled as $sdist$, 
while the distance between the last point and the anode is labelled as 
$edist$.\\

\begin{figure}[tbp]
\centering
\vspace{-0.1in}
\includegraphics[scale=0.38]{fig_rtpc/RTPC_track.png}
\vspace{-0.1in}
\caption{Schematic of a segment of the RTPC in a plane perpendicular to the beam line, with a $^4He$ track (in green) crossing the volume. See the text for description of the various elements and notations.} 
\label{fig:RTPC_track}
\end{figure}

Because the two modules of the RTPC are electronically separated, we will sometimes show their distributions separately. In our angular convention, the right module of the RTPC covers the azimuthal angles between 90$^{\circ}$ and 270$^{\circ}$, while the left-side module covers the rest of the azimuthal angles.

\subsubsection{RTPC good track requirements}

~~~~A good RTPC track passes the following requirements:
\begin{itemize}
\item The number of active pads in the track is greater than 3.

\item We apply a cut on the vertex position in $z$ of the reconstructed tracks to insure it is in the RTPC volume, i.e. $z$ $\in$ [-80,80] mm, as illustrated in figure \ref{fig:rtpc_zz}.

\item We request a positive radius of curvature ($r_{0}>0$): the $^4He$ is a positively 
   charged nucleus and the reconstructed track in the RTPC must have positive 
   radius of curvature. In other words, it travels in a clockwise direction if 
   one looks into the electron beam. The curvature distribution of the 
   collected RTPC tracks is shown in figure \ref{fig:rtpc_ro}.

\item We check the quality of the helix fit with a $\chi^{2}$ cut (< 3.5). The quality of the fit ($\chi^{2}$) is defined as:

\begin{equation}
   \chi^{2} = \frac{\displaystyle \left(\frac{DOCA}{\sigma_r}\right)^2 
       + \sum_{i = 1}^{ N_{pts}} \left(\frac{r^{pt}_{i} 
      - r^{helix}_{i} }{\sigma_{r}}\right)^{2}  + \left( \frac{\phi^{pt}_{i} - 
      \phi^{helix}_{i} }{\sigma_{\phi}}\right)^{2} + \left( \frac{z^{pt}_{i} - 
   z^{helix}_{i} }{\sigma_{z} } \right)^{2}}{N_{pts} - 4}
\end{equation}
where $\frac{DOCA}{\sigma_r}$ is the beam-spot constraint, $r^{pt}_{i}$, 
$\phi^{pt}_{i}$, $z^{pt}_{i}$ are the radial, azimuthal, longitudinal 
coordinates of each reconstructed hit "$i$". ($r^{helix}_{i}$,
$\phi^{helix}_{i}$, $z^{helix}_{i}$) is the point on the helix fit that is 
closest to the reconstructed hit $i$. The resolutions are defined as ($\sigma_{r}$, 
$\sigma_{\phi}$, $\sigma_{z}$) = (0.53 mm, 2$^{\circ}$, 1.2 mm) based on the size
of the readout pads were kept identical for all calibration iterations. 
$N_{pts}$ is the total number of the hits in the chain.  Figure 
\ref{fig:rrtpc_X2} shows the $\chi^{2}$ distributions for the positive tracks 
which originate within the RTPC.

\begin{figure}[tbp]
\centering
\includegraphics[scale=0.38]{fig_rtpc/rtpc_z.png}
\caption{The z-vertex distributions for the reconstructed tracks in the RTPC.} 
\label{fig:rtpc_zz}
\end{figure}

\item $sdist$ ($\in$ [-2.0,2.0] mm) and $edist$ ($\in$ [-1,5] mm ) cuts: the cuts are applied to ensure that a track is on time, i.e. that the first ionization point is close to the cathode and the last point is close to the anode. The $sdist$ and $edist$ distributions are shown in figures \ref{fig:rrtpc_sdist} and \ref{fig:rrtpc_edist} respectively\footnote{The long tail on the positive side of the $edist$ distribution is mostly due to electronic noise. Note that after applying all the elastic He-4 selection cuts, we observe that most of the tails for both $edist$ and $sdist$ are removed.}.

\item Vertex correspondence: the track reconstructed in the RTPC has to originate from the same place as the electron that triggered the event. We define $\Delta z$ as the difference between the electron z-vertex and the z-vertex of the RTPC track. Due to variations in the electric and the magnetic fields along the 200 cm of length of the RTPC, $\Delta z$ shows a dependence on the longitudinal position along the RTPC ($z_{RTPC}$). This can be seen in figure \ref{fig:rrtpc_delta_z}. These distributions are fitted to extract the mean and the width of $\Delta z$ as a function of $z_{RTPC}$. We then apply a 2$\sigma$ cut around the mean to select the RTPC good tracks. The parametrizations of the mean ($\mu$) and the width ($\sigma$) of $\Delta z$ can be found in Appendix \ref{app:RTPC_appendix}.

\begin{figure}[tbp]
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.3in}
\includegraphics[height=6.5cm]{fig_rtpc/rtpc_r0.png}
\caption{The radius of curvature of the reconstructed tracks in the RTPC.} 
\vspace{0.4in}
\label{fig:rtpc_ro}
\end{minipage} \hfill
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.3in}
\includegraphics[height=6.5cm]{fig_rtpc/rtpc_X2.png}
\caption{The $\chi^{2}$ distribution for the positive tracks in the RTPC. The red line represents the cut we apply to select good tracks.}
\vspace{+0.1in}
\label{fig:rrtpc_X2}
\end{minipage}
\end{figure}

\begin{figure}[tbp]
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.3in}
\includegraphics[height=6.5cm]{fig_rtpc/rtpc_sdist.png}
\caption{$sdist$ distribution for the positive tracks in the RTPC. We set $|sdist|$ < 2.0 mm to select good tracks.} 
\vspace{0.3in}
\label{fig:rrtpc_sdist}
\end{minipage} \hfill
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.3in}
\includegraphics[height=6.5cm]{fig_rtpc/rtpc_edist.png}
\caption{$edist$ distribution for the positive tracks in the RTPC. We require -1.0 mm < $edist$ < 5.0 mm to select the good tracks.}
\vspace{+0.2in}
\label{fig:rrtpc_edist}
\end{minipage}
\end{figure}

\begin{figure}[tbp]
\includegraphics[scale=0.34]{fig_rtpc/delta_z_z_l.png}
\includegraphics[scale=0.34]{fig_rtpc/delta_z_z_r.png}
\caption{The $\Delta z$ distribution versus the RTPC longitudinal position ($z_{RTPC}$) for the left and the right modules of the RTPC, respectively. The black lines represent the mean value of $\Delta z$ as a function of $z_{RTPC}$, while the red lines are 2$\sigma$ cuts around the mean.} 
\label{fig:rrtpc_delta_z}
\end{figure}  
\end{itemize}

\subsubsection{Elastic selection}
   The elastic process on $^{4}He$ is defined as:
\begin{equation}
\centering
e(k) + ^{4}He(p) \rightarrow e(k') + ^{4}He(p')
\end{equation}
with the symbols in parenthesis representing the four-momenta of the particles. \\

 In addition to the previously good-track requirements, in order to select the elastic events we impose further constraints. The co-planarity between the scattered electron and the recoil $^4He$ is ensured using a $\Delta \phi$ (=$\phi_{e}-\phi_{^{4}He}$) cut as shown in Figure \ref{fig:delta_phi_elastic}. Like for $\Delta z$, the $\Delta \phi$ 2$\sigma$ cut is dependent on $z$ to account for variations. Our final parametrizations can be found in Appendix \ref{app:RTPC_appendix} as well.\\

An additional elastic cut is performed by comparing the measured $^4He$ polar angle to the calculated one, based on the measured electron in CLAS. Indeed, from momentum conservation the $^4He$ polar angle can be calculated as:
\begin{eqnarray}
\theta^{^4He}_{cal} &=&  sin^{-1}\left(\frac{p_{e'}}{p^{^4He}_{cal}} \cdot \sqrt{1-cos^{2}\theta_{e'}}\right) \\
\text{ with~~} p^{^4He}_{cal} &=& \sqrt{(E_{b} + M_{^4He} - p_{e'})^{2} - M^{2}_{^4He}}
\label{equ:theta_helium}
\end{eqnarray}
where $p_{e'}$ and $\theta_{e'}$ are the electron's measured momentum and polar angle, $E_{b}$ is the beam energy and $M_{^4He}$ is the helium mass (3.727 GeV/c$^{2}$). Figure \ref{fig:delta_theta_elastic} shows the $\Delta \theta$ ($\theta^{^4He}_{cal}$ - $\theta^{^4He}_{meas}$) distribution versus the $^4He$ z-vertex. No significant difference was observed between the two modules regarding this quantity. The obtained parametrization of the mean and the width of the $\Delta \theta$  distribution can be found in Appendix \ref{app:RTPC_appendix}.\\

\begin{figure}[tp]
\includegraphics[scale=0.34]{fig_rtpc/delta_phi_z_l.png}
\includegraphics[scale=0.34]{fig_rtpc/delta_phi_z_r.png}
\caption[]{The distributions of $\Delta \phi$ as a function of $z$ along the RTPC for the selected good tracks in the RTPC, for the two halves of the RTPC respectively. In each plot, the black line is the mean of $\Delta \phi$ and the red lines are 2$\sigma$ cuts to select the elastic events.} 
\label{fig:delta_phi_elastic}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[scale=0.370]{fig_rtpc/delta_theta_z.png}
\caption[]{The $\Delta \theta$ distribution, for the selected events after the $\Delta \phi$ cut, as a function of $z$ along the RTPC. The black line represents the mean, while the red lines are 2$\sigma$ cuts around the mean to select the elastic $^4He$ events. } 
\label{fig:delta_theta_elastic}
\end{figure}

Constructing the invariant mass is one way to verify the efficiency of the previously described selection procedures. For a helium target, the invariant mass (W) is:\\
\begin{equation}
 W = \sqrt{-2E_{b}p_{e^{'}}(1-cos(\theta_{e^{'}})) + M_{^{4}He}^2 + 2(E_{b}-p_{e^{'}}) M_{^{4}He}}.
\end{equation}
with the conventions for the variables as in equation \ref{equ:theta_helium}. Figure \ref{fig:W_elastic} shows the W distribution of the events that have a good track in the RTPC and the identified elastic events. One can see the good agreement between the helium-4 real mass and the mean value of the identified elastic events. The difference in width is related to the different resolutions of the corresponding CLAS sectors. The reaction products are emitted back to back resulting in only small regions of overlapping acceptances between the RTPC and CLAS enhancing this effect. The reason for this is that local variations of the resolution can be much more important than ones averaged over the full detector.
\\

\begin{figure}[tbp]
\includegraphics[scale=0.32]{fig_rtpc/fit_W_distribution_l.png}
\includegraphics[scale=0.32]{fig_rtpc/fit_W_distribution_r.png}
\caption[]{The invariant mass distributions for events with one good RTPC track (in blue) and the events passing the elastic cuts (in shaded) for each of the two modules of the RTPC, respectively.}
\label{fig:W_elastic}
\end{figure}

The figures presented for $\Delta z$ and $\Delta\phi$ distributions in this section are shown after all the
calibration and detector alignments (RTPC alignment is described in 
CLAS-NOTE-2013-008). The observed remaining dependences are not fully 
understood and probably arise from field misalignement and variations in the 
electric and magnetic fields within the chamber.

\subsection{drift paths and drift speed calibration}

\subsubsection{Drift speed parametrization}
~~~~The electrons follow their drift paths with a certain speed, named drift speed. This speed is affected by the experimental conditions, such as the variations in the magnetic field or in the gas composition. We can measure this speed using the tracks detected in the RTPC, as it is explained in this section.\\

In our TPC, the electrons released close to the cathode take the maximum drift time ($TDC_{max}$) to reach the readout pads while the geometrical symmetry along the RTPC ensures that these electrons always travel the same distance. Therefore, by identifying the $TDC_{max}$, the drift speed can be deduced. Figure \ref{fig:TDC_profile} shows the time profile of the collected hits for the detected good tracks. The experimental drift time ranges between the trigger time (TDC$_{min}$ = 15 TDCs) to 75 TDCs. The time profile shows an expected dropping edge at high TDCs due to the geometrical constraints. In order to avoid the statistical effects in determining the  $TDC_{max}$, we define a value named as $TDC_{max/2}$ at which the dropping edge passes to half of the maximum number of hits in each hits-time profile. $TDC_{max/2}$ is inversely proportional to the drift speed.\\

We measure the $TDC_{max/2}$ along the length of the RTPC to take into account the variations in the electric and magnetic fields. The results can be seen in figure \ref{fig:RunNumber_61551_TDCmax_Zslice}, where a clear variation of the drift speed along the RTPC was observed. \\ 
\begin{figure}[tbp]
\centering
\vspace{-0.1in}
\includegraphics[scale=0.35]{fig_rtpc/TDC_profile.png}
\caption{Time profile of the collected hits for the RTPC good tracks in one experimental run, run 61511. The $TDC_{max/2}$ is the time at which the dropping edge passes half the maximum number of hits. }
\label{fig:TDC_profile}
\end{figure}

We also monitor the $TDC_{max/2}$ evolution during the time of the experiment, to take into account variations. The EG6 experiment has recorded data with different electron-beam energies: 1.204, 5.7, 6.064 and 1.269 GeV. The 5.7 and 6.064 data sets have low elastic cross sections compared to the 1.206 and 1.269 data sets. For this reason, we use all the RTPC good tracks and not only the elastic ones for these. Before checking the stability of $TDC_{max/2}$ over the experimental running period, we want to check the feasibility of using all good tracks for the purpose of parametrizing the drift speed. In this check, the $TDC_{max/2}$ identified using the good tracks of the 1.206-GeV data set is compared to the one identified from the elastic events of the same data sets. The result is shown in figure \ref{fig:TDCmax_ratio}, in which the ratio between the two $TDC_{max/2}$ is plotted as a function of the longitudinal position along the RTPC. This ratio is consistent with 1, within 1$\%$. Thus we can conclude that using the hits of the collected good tracks is a good approximation. \\

\begin{figure}[tp]
\begin{minipage}[c]{.46\linewidth}
\hspace*{-0.3in}
\includegraphics[height=9.5cm]{fig_rtpc/RunNumber_61551_TDCmax_Zslice.png}
\caption{$TDC_{max/2}$ variation as a function of the longitudinal position along the RTPC in one experimental run, 61510.} 
\label{fig:RunNumber_61551_TDCmax_Zslice}
\end{minipage} \hfill
\begin{minipage}[c]{.46\linewidth}
\hspace*{-0.3in}
\includegraphics[height=9.0cm]{fig_rtpc/TDCmax_ratio_final.png}
\caption{Ratio between $TDC_{max/2}$ extracted using the RTPC good tracks and the one extracted using the clean elastic events, both from the 1.204-GeV dataset.}
\label{fig:TDCmax_ratio}
\end{minipage}
\end{figure}

The variations with time of $TDC_{max/2}$ are shown in figure \ref{fig:Drift_run_number}, in which each point is a run of about two hours of data taking. One can see a non-negligible variation over the three months of data taking due to the changes in the experimental conditions. The main cause of these variations is probably the variation of proportions in the drift gas mixture which was not perfectly under control due to leaks in the thin parts of the detector.\\

As $TDC_{max/2} -15 $ ($= 
\frac{Drift~path~length}{Drift~speed}$) varies with both run number (time) and 
the geometry of the RTPC ($z$ along the RTPC). We
parametrize the dependence on $z$ for each run in the form:\\
\begin{equation}
TDC_{max/2} (z)= p_{0} +  p_{1} * e^{p_{2}*(z-p_{3})^{2}}.
\label{equ:drift_speed_fit}
\end{equation}
Then fits are performed for these parameters as functions of the run number, such that the drift speed parametrization depends on the run and $z$ along the RTPC. The numeric parametrizations of $p_{0}$, $p_{1}$, $p_{2}$, and $p_{3}$ can be found in Appendix \ref{app:RTPC_appendix}, table \ref{Table:TDCmax}. \\

These functions are implemented in our reconstruction codes, and, as a result 
of adapting the drift speed with these functions, more good tracks and elastic 
events were identified comparing to the previous calibration set. Figure 
\ref{fig:Drift_run_number} also shows the gain percentages of the good tracks 
(GT) and the elastic events (El) in few runs. One can see a gradual improvement 
with time because of giving the right drift speed, which together with the 
drift paths gives more precise reconstructed hits chain. Therefore, the 
parameters of the reconstructed tracks ($sdist$, $edist$ ... etc) are more likely to pass the 
selection requirements and so more tracks are found to be good. \\

\begin{figure}[tp]
\hspace{-0.3in}
\includegraphics[scale=0.45]{fig_rtpc/Drift_run_number.png}
\caption{ The integrated $TDC_{max/2}$ over the full z-RTPC as a function of 
run number.  The gain after calibration in the collected good tracks (GT) and 
elastic events (El) are shown for a sample of runs.}
\label{fig:Drift_run_number}
\end{figure}

\subsubsection{Drift paths parametrization}
~~~~A drift path is the trajectory that an electron follows after being released in the drift region. The standard software to calculate these paths is the MAGBOLTZ program \cite{MAGBOLTZ}. This program requires precise knowledge of the experimental conditions, such as the detector's geometry, the exact composition of the drift gas and the applied electric and magnetic fields. Thus any variation in these conditions would give inaccurate calculated drift paths. In the EG6 experiment, MAGBOLTZ has been used to calculate a first set of drift paths, but it was observed for the drift speed that we do not have a perfect knowledge of the RTPC's conditions. Therefore, the first set of the drift paths is not accurate. For this reason, we chose to calculate the drift paths in a way that does not require an exact knowledge of the conditions in the chamber and is instead based on our experimental data. \\

In our alternative method, we use the identified elastic ($e ~ ^{4}He \rightarrow e ~ ^{4}He$) events to extract the drift paths. For these events, the kinematics of the recoil $^{4}He$ are calculated from the scattered electron. Then the electrons' drift paths can be extracted from comparing the experimentally measured hits in the RTPC to the trajectory of a similar simulated $^{4}He$. In this technique, the drift paths are obtained independently of our knowledge of the exact conditions in the RTPC, in particular the electric field and the gas mixture have no impact. \\

Due to the magnetic field, the drift paths are not linear. This is handled by 
the following procedure, in which we perform the drift paths' extraction in 
two passes. In the first pass, we assume a linear correlation between the 
radius of emission $R$ (we work here in radial coordinates: $R$ and $\phi$) and the 
drift time, to link the GEANT4 hits to the measured hits. Through this association, we obtain an 
initial set of drift paths in the form of a $\Delta \phi$ distribution as function of time. We define $\Delta \phi$ the 
difference between the $\phi$ of the simulated hits and the $\phi$ of the pad 
which measured a hit. In the second pass, we refine the initial 
correlation between the radius and the time using the initial drift paths, and 
we extract final drift paths. To take into account the variations of the magnetic 
field and therefore the varying Lorentz angle, the extraction 
is made in $z$ bins along the RTPC. \\

The procedure steps are:\\
\begin{itemize}
\item We first select a sample of well identified elastic events in our experimental data. Using the
   kinematics of the scattered electrons in these events, we generate in GEANT4
   a sample of events identical to the measured ones. 
\item  For each couple of events (the experimental one and its simulated equivalent)
   we make a linear correlation between $R$, from simulation, and TDC from 
   real data, to link the GEANT4 hits to the measured ones. In our TPC, the 
   maximum $R$ equals 60 mm (close to the anode) at the trigger time, 
   (TDC$_{min}$ = 15 TDCs), and the minimum R equals 30 mm (close to the 
   cathode) at maximum TDC ($TDC_{max}$). Thus, the linear correlations can be 
   written as:
\begin{equation}
   R(TDC) = \frac{60-30}{15-TDC_{max}} (TDC-15) + 60.
\label{equ:R_TDC}
\end{equation}
We apply 3 TDCs-wide windows around the linear R-TDC correlation to associate the 
GEANT4 simulated hits to measured hits.

\item From these selected hits, we construct the drift paths $\Delta \phi$ (= 
   $\phi_{sim.}$ - $\phi_{hit\_pad}$) versus TDC. The results can be seen in 
   figure \ref{fig:1st_pass_delta_phi}. $\Delta \phi$ at the anode (TDC = 15) 
   is not equal to zero because there is a drift in $\phi$ between the anode 
   (the first GEM layer at radial distance equal to 60 mm) and the readout pads 
   (at radial distance equal to 69mm).

\begin{figure}[tp]
\centering
\includegraphics[scale=0.45]{fig_rtpc/TdcPhi_p1_10.png}
\caption{(First pass). Distribution of $\Delta \phi$ as a function of TDC for 
   in one $z$ bin. The width of the bin is 10 mm, 
with the center at $z$ = 5 mm. The black line represents a fit for 
$\Delta\phi$.  }
\label{fig:1st_pass_delta_phi}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[scale=0.45]{fig_rtpc/TdcR_p2_10.png}
\caption{(Second pass). The calculated R as a function of TDC is corrected by the $\Delta \phi$ relation extracted from the first pass.}
\label{fig:R_TDC}
\end{figure}

\item The correlation between R and TDC is refined using the extracted initial 
   $\Delta \phi$ as a function of TDC as:
\begin{equation}
   R (TDC) = R_{min} + \bigg[\sum\limits_{i=TDC_{Max}}^{TDC} \sqrt{DS^{2} - 
      R^{2}(i) \cdot \left(\frac{\partial \Delta \phi}{\partial TDC}(i) 
\right)^{2}}~~~~\bigg] \cdot TDC,
 \end{equation}
where DS is the average drift speed, equal to 0.7 mm/TDC ( 6.14 $\mu$m/ns), 
$R_{min}$ equals to 30 mm, $R(i)$ is the linear correlation defined in equation 
\ref{equ:R_TDC} and $\Delta \phi (i)$ is the fit in figure 
\ref{fig:1st_pass_delta_phi}. The sum is multiplied by a TDC (=114 ns) unit.  
The calculated R, figure \ref{fig:R_TDC}, is very close to a straight line, 
indicating that only two itterations are probably enough.

\item In the second pass, we use the newly found R(TDC) relation to construct new $\Delta \phi$ distributions, see figure \ref{fig:final_drift_paths}.

\begin{figure}[tp]
\centering
\includegraphics[scale=0.45]{fig_rtpc/FitResult_p2_10.png}
\caption{(Second pass). Distribution of $\Delta \phi$ as a function of TDC 
located in the same $z$ bin shown in figure \ref{fig:1st_pass_delta_phi}. The 
black line represents the final drift paths.}
\label{fig:final_drift_paths}
\end{figure}
\end{itemize}

We performed a third pass in which the R(TDC) correlation is refined using the drift paths from the second pass and new drift paths were extracted. As a result, we observed no difference between the drift paths of the second and the third passes. In other words, extracting the drift paths from two iterations gives us stable drift paths. \\

The first drift paths were extracted using the elastic events from the early 1.204 GeV dataset. In order to ensure the consistency of these drift paths over the experimental running period, we extracted another set of drift paths using the elastic events of the 1.269 GeV runs. We observed no difference between the two sets of the drift paths, ensuring their stability over the experimental period and leaving the dependence on the TDC and $z$. The final drift paths are extracted using both datasets, 1.204 and 1.269 GeV. They take the form:
\vspace{-0.1in}
\begin{equation}
\Delta \phi (TDC, z)=  \sum\limits_{i=0}^{4} p_{i}(z)*TDC^{i},
\end{equation}
where the parameters, $p_{0}$, $p_{1}$, $p_{2}$, $p_{3}$ and $p_{4}$ are functions of $z$, as can be seen in Appendix \ref{app:RTPC_appendix}, table \ref{table:drift_paths}. The final drift paths are implemented in our reconstruction codes such that the reconstructed position of each hit becomes:
\begin{equation}
\phi_{exp}(z, TDC) = \phi _{hit\_pad} - \Delta \phi (z, TDC).
\end{equation}

~~~~It is important to note that the drift paths have shown strong sensitivity to the other RTPC calibrations. Therefore, we performed iterative extractions of the drift paths and, as a results, obtained more good tracks with a signal to background ratio largely improved. Figure \ref{fig:sdist_comp_pass1v1_v6} shows an illustration of the improvements in terms of the $sdist$ parameter using the same initial collected data with an old drift paths and a newer set.

\begin{figure}[tp]
\centering
\includegraphics[scale=0.38]{fig_rtpc/sdist_comp_pass1_v1_v6.png}
\caption{The $sdist$ distribution for the collected tracks in the RTPC using the same initial collected data with an old set of drift paths, on the left, and a newer set, on the right.}
\label{fig:sdist_comp_pass1v1_v6}
\end{figure}

\subsubsection{summary}
The drift paths and drift speed were first extracted using the
MAGBOLTZ Monte Carlo simulation. One can find the detailed procedure of
a similar extraction in the BoNuS analysis note \cite{GEM_holes}.
Then, we improved this first result with many iterations after
each change that would affect the drift paths, such as the beam-offset
 and gain calibrations of the RTPC. Moreover after each pass, the number of
 elastic events used for calibration increased, justifying by itself a new calibration. Overall, this was a long
 process that evolved and improved over the years and we concentrated in the
 note on the description of the final iteration of this calibration.

\subsection{Gain calibration}
The second important calibration is the amplitude of the signal provided in ADC units. Since each charged particle deposits a certain amount of energy ($\small{\frac{dE}{dX}}$) when crossing a material, we can identify particles based on this variable. The ($\small{\frac{dE}{dX}}$) depends on the characteristics of the particle, such as its energy, mass and charge, and the nature of the medium as well. \\

$\small{\frac{dE}{dX}}$ can be calculated using the Bethe-Bloch formula \cite{bethe_block}:
\begin{eqnarray}
 \left\langle \frac{dE}{dX} \right\rangle &=& \rho K z^{2} \frac{Z}{A} \frac{1}{\beta^{2}} \left[ \frac{1}{2} ln \left(\frac{2m_{e}c^{2}\beta^{2}\gamma^{2}T_{max}}{I_{max}} \right) - \beta^{2} -\frac{\delta\beta\gamma}{2}\right]\\
\text{with }
T_{max} &=& \frac{2m_{e}c^{2}\beta^{2}\gamma^{2}}{1+2\gamma m_{e}/M + (m_{e}/M)^{2}} 
\end{eqnarray}
where $T_{max}$ is the maximum kinetic energy of a free electron in a single collision, and $z$, $M$, $\beta$ are the charge, mass and speed (=$p/ \sqrt{M^2 + p^2}$, where $p$ is the momentum) of the particle, respectively. $m_{e}$ is the electron mass and the constant $K$ is equal to $4 \pi N_{A} r^{2}_{e}m_{e}c^{2}$ = 0.307075 MeV mol$^{-1}$ cm$^{2}$. $Z$, $A$, $I$, $\rho$ are the effective charge, atomic number, mean excitation energy and mass density of the medium. In the RTPC, these constants are equal to 66, 126.79 mg mol$^{-1}$, 99.79 eV and 1.03 mg/cm$^3$, respectively. \\

Experimentally, $\small{\frac{dE}{dX}}$ can be calculated from the collected ADCs as: 
\begin{equation}
 \left\langle \frac{dE}{dX} \right\rangle= \frac{\sum\limits_{i} \frac{ADC_{i}}{Gi}}{vtl},
\end{equation}
where the sum runs over all the pads contributing to a track. $ADC_{i}$ is the recorded amplitude in each pad $i$, and $G_{i}$ is its gain. The $vtl$ is the total visible length of the track in the active drift volume. This is of course assuming the energy loss in the drift region is small in regard to the total energy of the particle, which is true except close to our detection threshold.\\

The electron collection system of the RTPC has 3200 readout pads. The gain of each pad is the ratio between the deposited energy and the output recorded value. We extracted the gains using two techniques. The first one is by comparing the experimental recorded $\small{\frac{dE}{dX}}$ to the expected values calculated from the Bethe-Bloch formula. The second technique is based on comparing the experimental ADCs to the GEANT4 simulated ones, track by track. We latter refined this second method by comparing the ADCs of each pad to the average ADCs of the other pads in the same track.\\

The two techniques were investigated for the EG6 experiment using the elastic 
events from the 1.206 GeV data set. The first method involves a series of 
equations to be solved to obtain the gains.

~~~~The second method requires improvements in the simulation, in order to match the real experiment. In summary, these improvements are:
\begin{itemize}
\item Implementation in the simulation of the previously extracted parametrizations of the drift speed and the drift paths.
\item Global ADC normalization to give reasonable simulated values. In the left module, 1 ADC is equal to 
17 eV, while it is equal to 21 eV in the right module. These normalizations were extracted from the comparison of the data to the GEANT4 simulation.
\item Rejection of the signals from bad pads. During the experiment, the readout system of the RTPC suffered from 555 dead or noisy pads. These pads are marked by the dotted squares in figure \ref{fig:pad_row_col}.
\item Smearing the position of the simulated hits. Experimentally, the average number of hits per track is around 80 while the initially reconstructed mean value from the simulation is around 50. We apply a Gaussian smearing on the position of the simulated hits to make the simulation more realistic, see figure \ref{fig:NNb_hits}.

\item Application of the TPC's DAQ cut on the simulated data. Experimentally, each pad must have at least 3 consecutive time bins, with ADC values above the threshold, 35 ADCs, in order to be recorded. Then, the hits of three neighboring bins on each side of the above threshold bins are also recorded, while the other hits are not.
\end{itemize}

\begin{figure}[tp]
\centering
\includegraphics[scale=0.40]{fig_rtpc/NNb_hits.png}
\caption{The distributions of the number of hits per track. The black, the blue and the red distributions are the number of hits per track  for respectively, the experimental data, simulation before smearing and the simulation with smearing.}
\label{fig:NNb_hits}
\end{figure}

To illustrate the procedure of comparing simulated tracks with real tracks,
we show in Figure \ref{fig:EVENT_adc_tdc} the simulated ADCs and the 
experimental ones as a function of the TDCs for the same track. 
Then, the gain of each pad can be obtained as the ratio of the mean experimental 
ADCs to the one of the simulated track. For each pad, these gain 
ratios were collected from all the identified elastic events and fitted by a 
Landau function to obtain their gains.

As mentionned earlier, we refine this calibration after 
the extracted gains are applied to the experimental data. We compare the ratio between the 
mean ADCs of each pad to the mean ADCs of the whole track. This ratio is 
collected from all the elastic events and a gain correction factor is extracted 
for each pad. The final gains of the second method are obtained with the application of 
this extra correction.\\

\begin{figure}[tp]
\centering
\vspace{-0.1in}
\includegraphics[scale=0.350]{fig_rtpc/EVENT_adc_tdc.png}
\caption{The simulated (top) and the experimental (bottom) ADCs versus TDC distributions for the same track. The same colors indicate hits that were registered in the same channel for the simulation and the experiment.}
\label{fig:EVENT_adc_tdc}
\end{figure}

As the two modules of the RTPC are electronically separated, we look at their calibrations separately. Figure \ref{fig:dedx_p_exp_2nd} shows the ratio between the calculated $\small{\frac{dE}{dX}}$, using the gains of both methods, and the GEANT4 simulated $\small{\frac{dE}{dX}}$ for the elastic events in the two modules of the RTPC. We conclude that extracting the gains from comparing data to simulation in terms of the ADCs of the individual tracks gives more precise gains than solving the series of equations. Figure \ref{fig:pad_row_col} shows the gains from the second method, where the dotted squares refer to the dead or noisy pads. These are the ones that are implemented in the EG6 reconstruction codes.\\

\begin{figure}[tbp]
\centering
\includegraphics[scale=0.400]{fig_rtpc/dedx_p_sim_exp_2nd.png}
\caption{The ratio between the experimental $dE/dx$, using the gains obtained with the two methods (1$^{st}$ in blue, and 2$^{nd}$ in black), to the GEANT4 simulated $dE/dx$, plotted for the two modules of the RTPC, respectively left and right. }
\label{fig:dedx_p_exp_2nd}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[scale=0.300]{fig_rtpc/pad_row_col.png}
\caption{The extracted gains from the second method. The dotted squares refer to the position of the excluded pads.}
\label{fig:pad_row_col}
\end{figure}

In the left module of the RTPC, figure \ref{fig:dedx_p_exp_2nd}, one notices an 
additional unexpected lower peak (dEdx$_{exp}$/dEdx$_{sim} \sim$ 0.3). These 
events pass all the elastic requirements but for some reasons they have lower 
ADC values. They represent around $7\%$ of all the elastic events. After 
extended studies, the nature of these particles is not identified yet. We note 
that this is a global phenomenon in the left module as 94$\%$ of the left 
module's pads are involved in both some low and high dEdx events. For instance, 
figure \ref{fig:Chann_706} shows the average ADC versus TDC distributions for 
the recorded hits in one of these pads in the left module. For the calibration 
procedures, the events with low dEdx were excluded as we do not fully 
understand their nature, see figure \ref{fig:dedx_cal_left}.\\
\begin{figure}[tbp]
\centering
\includegraphics[scale=0.4]{fig_rtpc/Chan_706_1.png}
\includegraphics[scale=0.4]{fig_rtpc/Chan_706_2.png}
\caption{The average ADC vs. TDC distributions of the experimental hits recorded for the elastic events in one pad of the left module, pad number 706. On the top: the distribution for the elastic tracks in the region where dEdx$_{exp}$/dEdx$_{sim} $ $\sim$ 1. On the bottom: the distribution for the elastic tracks that exhibit dEdx$_{exp}$/dEdx$_{sim} $ $\sim$ 0.3.}
\label{fig:Chann_706}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[scale=0.4]{fig_rtpc/dedx_l_cal_cut.png}
\caption{DEdx as a function of the measured momentum inside the left module of 
the RTPC for a sample of the identified elastic $^{4}He$ tracks. The red dashed 
line represents the cut we applied to exclude the low dEdX events from usage 
for the calibration purposes explained earlier in this chapter.}
\label{fig:dedx_cal_left}
\end{figure}

To check the validity of the extracted gains, we show $\small{\frac{dE}{dX}}$ versus the momentum (per charge unit) measured in the RTPC for all the collected tracks of the 1.206 GeV data set. In the plots, we add the theoretical lines derived from the Bethe-Bloch formula for possible detected particles: $^4He$, $^3He$, $^3H$, Deuterium (d) and the protons.
\begin{figure}[tbp]
\includegraphics[scale=0.35]{fig_rtpc/dedx_p_l.png}
\includegraphics[scale=0.35]{fig_rtpc/dedx_p_r.png}
\caption{The experimental $\small{\frac{dE}{dX}}$ calculated using the second method gains versus $p/q$ of all the collected good tracks in the RTPC in the early 1.204 GeV dataset.}
\label{fig:dedx_all}
\end{figure}
One can see the different bands corresponding to the different detected particles.  
Even though the bands are very wide, the $\small{\frac{dE}{dX}}$ can be used to 
perform particles identification for large data set and different physics 
processes. In this analysis, the $\small{\frac{dE}{dX}}$ is not used to 
identified the recoil $^{4}He$ in the coherent DVCS event selection, as the 
 set of exclusivity cuts that will be 
presented in chapter 4 appears to be strict enough.

\subsection{Noise rejection}
\label{sec:noise_rejection}
~~~~The RTPC was designed to reduce noise and contribution from M\o ller 
electrons via the first and second 1 atm gas gaps. During data taking, the 
readout thresholds of the RTPC were set low to avoid efficiency problems, with 
the effect of recording more electronic noise. The latter effect is illustrated 
by the large occupancies in the top panel of 
figure~\ref{fig:occ_noiserej}.

Two independent noise signatures were found, and event-based algorithms were implemented to significantly reduce them offline. This resulted in improved track quality, increased track efficiency, and the opportunity to reintroduce channels otherwise determined to be too noisy.  This also resulted in more uniform occupancy, shown in the bottom panel of figure~\ref{fig:occ_noiserej}.

Here we describe the methods and their specific effects. These are implemented 
in EG6's pass2 reconstruction in \texttt{\$CLAS\_PACK/gem/noisypads.c}.

\subsubsection{Oscillatory Noise}
An oscillatory noise signature was found for many RTPC readout pads, and is 
attributed largely to the electronics. The signature is a series of hits 
falling on a fixed ADC vs TDC curve for TDC less than 30.  About 18\% of the 
active pads have very strong contributions from this type of noise, which 
previously resulted in many of them being marked as ``bad'' due to high 
occupancies.

An algorithm was developed to remove hits corresponding to this noise without suppressing good hits.  First, the ADC vs TDC noise curve was parameterized.  Next, for every event and channel independently, the number of hits falling on this curve is counted.  If a significant number of hits lie far above or below the noise curve, no rejection is performed.  If most of the hits below TDC=30 fall on the noise curve, all hits below TDC=30 are rejected for that channel.  Figure \ref{fig:Adcvstdcnoise} shows the effect of this noise reduction for one very noisy pad.

The result of this algorithm is 5$\%$ more good tracks reconstructed, with improved signal to background ratio, as can be seen in figure \ref{fig:noise_edist_}. 
Further, this allowed to recover 40 channels that had previously been ignored due to high occupancies before this noise rejection.

\begin{figure}[tbp]
%\hspace{-0.4in}
\includegraphics[scale=0.3]{fig_rtpc/noisy_pad_before_rejection.png}
\includegraphics[scale=0.3]{fig_rtpc/noisy_pad_after_rejection.png}
%\vspace{-0.3in}
\caption{The integrated ADC vs. TDC of the hits for good tracks before (left) and after (right) the oscillatory noise reduction, for a particular pad with strong noise. The event sample and color scales are identical in both plots.}
\label{fig:Adcvstdcnoise}
\end{figure}

\begin{figure}[tbp]
%\hspace{-0.4in}
\includegraphics[scale=0.55]{fig_rtpc/400px-Edist_noiserej.png}
\includegraphics[scale=0.55]{fig_rtpc/400px-X2_noiserej.png}
%\vspace{-0.1in}
\caption{The $edist$ (left) and the $\chi^{2}$ (right) distributions for all the tracks collected in the RTPC before (blue) and after (red) the oscillatory noise rejection. The event sample and color scales are identical in both plots.}
\label{fig:noise_edist_}
\end{figure}

\subsubsection{Readout Group Noise}
Another noise signature is isolated to particular readout boards, corresponding 
to 8x2 channel groups. Initially many of these 8x2 groups were ignored in 
reconstruction due to very high occupancy (see figure \ref{fig:occ_noiserej}).  
Upon further analysis, we found many events where these groups behaved normally 
and measured good tracks, while in other events the whole 8x2 channel group 
fired. In other words, the noise level of channels within the groups is 
correlated in time.

An event-based method was implemented to treat this noise by computing an event pedestal for the entire group for cases when there exist neighboring hits.
Hits in the 8x2 with no neighboring hits outside the group were used to calculated an event pedestal for the group. That pedestal is subtracted off all hits in the board in that event. If there are no neighboring hits outside the 8x2 group, the whole group is rejected in that event.

The effect of this algorithm on a couple reconstructed tracks is shown in figure~\ref{fig:HotBoardSubtract}.  The overall result was another 5\% increase in good tracks, and this noise subtraction also allowed to recover 32 more channels previously ignored due to high occupancy.

\begin{figure}[htbp]\centering
  \includegraphics[width=13cm]{fig_rtpc/HotBoardSubtract.png}
  \caption{Example effects of readout board noise subtraction for tracks in two events (corresponding to the two rows in the figure).  The known hot 8x2 readout groups are shown in the orange rectange in the leftmost column.  Color scale is ADC.\label{fig:HotBoardSubtract}}
\end{figure}

\begin{figure}[htbp]\centering
  \includegraphics[width=12cm]{fig_rtpc/Occ2d_norej2.png}
  \includegraphics[width=12cm,trim={2.5cm 0 0 0},clip]{fig_rtpc/Occ2d_rej.png}
  \caption{Occupancies before (top) and after (bottom) the two noise reduction algorithms.  The event sample and occupancy color scales are identical in the two plots.\label{fig:occ_noiserej}}
\end{figure}

\clearpage
\section{Tracking resolution}
~~~~The RTPC tracking resolution is defined as the spread of the reconstructed 
track vertex, angles and momentum with respect to their true values. In the EG6 
experiment, we use the cleanly identified elastic events to estimate the RTPC 
resolutions. The CLAS detector nominally provides electron detection with an 
angular resolution around 1 and 4 mrad in $\theta$ and $\phi$, and a momentum 
resolution ($\frac{\Delta p}{p}$) around 0.5$\%$ \cite{CLASref}. The z-vertex 
resolution of about 3 mm for an extended target in the presence of the 
solenoid, as can be observed experimentally from the target window, figure 
\ref{fig:electron_z_vertex_res}. \\
\begin{figure}[tbp]
   \centering
   \includegraphics[height=6.2cm]{fig_rtpc/clas_z_resolution.png}
   \caption{ z-vertex of scattered electrons from the downstream window of the 
   target. The z-vetex resolution of CLAS here is about 3 mm.}
   \label{fig:electron_z_vertex_res}
\end{figure}

With such electron resolutions, one can extract the RTPC resolutions by 
comparing the calculated kinematics of the recoil elastic $^4He$ nuclei  with 
the measured experimental values, as shown in figures 
\ref{fig:rtpc_resolution_z}, \ref{fig:rtpc_resolution_phi}, 
\ref{fig:rtpc_resolution_theta}, \ref{fig:rtpc_resolution_p} for the two halves 
of the RTPC separately. The distributions are fitted with a Gaussian and the 
extracted widths are listed in table \ref{table:rtpc_resolutions}.  One can see 
that for the resolution, the two modules of the RTPC show almost the same 
performance. These resolutions will be used to match the simulated data to the 
experimental ones, as will be shown in the following chapter.\\

One notices slight shifts in $\Delta z$, $\Delta \phi$, and $\Delta \theta$ distributions. The reason of the shifts may rise from our non-perfect knowledge of the exact conditions in the chamber, such as the magnetic field, that affect the reconstructed parameters of the tracks. The reconstructed momenta show 10-15$\%$ systematic shifts compared to the calculated values.

\begin{figure}[tbp]
\includegraphics[scale=0.31]{fig_rtpc/fit_delta_z_l.png}
\includegraphics[scale=0.31]{fig_rtpc/fit_delta_z_r.png}
\caption{The z-vertex resolution of the two modules of the RTPC, respectively.}
\label{fig:rtpc_resolution_z}
\end{figure}

\begin{figure}[tbp]
\includegraphics[scale=0.31]{fig_rtpc/fit_delta_phi_l.png}
\includegraphics[scale=0.31]{fig_rtpc/fit_delta_phi_r.png}
\caption{The azimuthal angle resolution of the two modules of the RTPC, 
respectively.}
\label{fig:rtpc_resolution_phi}
\end{figure}

\begin{figure}[tbp]
\includegraphics[scale=0.31]{fig_rtpc/fit_delta_theta_l.png}
\includegraphics[scale=0.31]{fig_rtpc/fit_delta_theta_r.png}
\caption{The polar angle resolution of the two modules of the RTPC, 
respectively.}
\label{fig:rtpc_resolution_theta}
\end{figure}

\begin{figure}[tbp]
\includegraphics[scale=0.31]{fig_rtpc/fit_delta_p_l.png}
\includegraphics[scale=0.31]{fig_rtpc/fit_delta_p_r.png}
\caption{The momentum resolution of the two modules of the RTPC, respectively.}
\label{fig:rtpc_resolution_p}
\end{figure}

\begin{table}[tbp]
\begin{center}
\begin{tabular}{|l|l|l|l|l|}
\hline
RTPC's module & ~~~~~~$\sigma_{z}$ ~~~~~~&  ~~~~~~$\sigma_{\phi}$~~~~~~ & ~~~~~~$\sigma_{\theta}$~~~~~~ & ~~~~~~$\sigma_{p}$~~~~~~\\
\hline
Left module &  ~~~~6.03 mm & ~~~~1.93$^{\circ}$ & ~~~~3.78$^{\circ}$ & ~~~~~~9$\%$ \\
\hline
Right module & ~~~~7.40 mm & ~~~~1.94$^{\circ}$ & ~~~~4.02$^{\circ}$  & ~~~~~~8 $\%$\\
\hline
\end{tabular}
\caption{The resolutions of the two modules of the RTPC.}
\label{table:rtpc_resolutions}
\end{center}
\end{table}

\section{RTPC tracking offsets}
TBC

\section{RTPC efficiency}
The previous distributions have shown that the two modules of the RTPC have 
slightly different yield, however this yield should not be linked to a different 
performance of the RTPC. The differences are mainly due to complicated 
convolution of CLAS and the RTPC acceptance. We measured the efficiency of the 
RTPC using the elastic scattering, and a result found that the left and the 
right modules have similar efficiencies except near the target windows, as 
shown in figure \ref{fig:rtpc_eff}.

\begin{figure}[tbp]
\centering
\hspace{+0.3in}\includegraphics[width=10.5cm]{fig_rtpc/tpceffyields.png}
\includegraphics[width=10cm]{fig_rtpc/tpceff.png}
\caption{On top is the inclusive and exclusive elastic yields separated into
 the two RTPC halves (LEFT/RIGHT).  Here the inclusive yields are the
 number of electrons in the elastic W-peak
 whose corresponding elastically scattered $^4$He would have been in the
 acceptance of the RTPC, and the exclusive yields require the additional
 detection of the $^4$He. On
 bottom is the RTPC $^4$He efficiency calculated from the ratio of exclusive
 and inclusive elastic yields.
 \label{fig:rtpc_eff}}
 \end{figure}

### 2016-06-27 analysis-note-v2/analysis-2.tex
added the second version of the analysis note

\chapter{DVCS beam-spin asymmetry extraction}

~~~~In the previous chapter, the events were filtered to select the ones which have one and only one good electron, and other good particles in coincidence with the electron. This chapter explains the procedure we used to extract the beam-spin asymmetry observable following this order: clean the DVCS data sample by choosing good run list, ensure the exclusivity of the selected events by imposing the conservation laws, subtract the background by combining data with simulation, and binning the identified DVCS events. This chapter contains also an estimation of the systematic uncertainty contribution from each source on the measured beam-spin asymmetry.\\

In the following, the selection procedures of the coherent DVCS events is detailed and generalized to the cases of incoherent DVCS, the coherent $\pi^{0}$, and the incoherent $\pi^{0}$ channels.

\section{Coherent channel}
\subsection{Good run list}
~~~~In principle, with constant beam luminosity, target density and pressure, the event rate has to be constant over the experimental time. Due to the changes in the experimental conditions, such as changing a trigger in a detector, a slight shift in the beam position or a system failure somewhere, this rate changes. We minimize the effects of these changes on the reconstructed events by selecting the good runs. To this aim, we monitor the ratio of the number of the good tracks reconstructed in the RTPC to number of the detected good electrons in CLAS (<tpc/e>) as a function of run number. Furthermore, we also look at this ratio in the six sectors of CLAS, as they are independent of each other and their performances might be different. \\

In this work, after the PID procedures, a run is considered good if:
\begin{itemize}
\item The integrated $<tpc/e>$ rate over the six sectors of CLAS is consistent with the neighboring runs.
\item The six sectors show small fluctuations for each run. 
\end{itemize}

~~~~Figure \ref{fig:tpc_over_e_Run_sec.png} shows the integrated and the 
sector-dependence of <tpc/e> for the individual runs. One notices a universal 
variation of this ratio over the three months of data taking. This can be 
attributed to changes in the RTPC. In particular, we had leaks in our gas 
system that appeared during the run. This probably caused gas contamination, 
changing the properties of the detector.

\begin{figure}[h!]
\hspace*{-0.3in}\includegraphics[scale=0.45]{fig_dvcs/tpc_over_e_Run.png}
\hspace*{-0.3in}\includegraphics[scale=0.45]{fig_dvcs/tpc_over_e_Run_sec.png}
\caption{On the top: The integrated $<tpc/e>$ ratio (over the six sectors of CLAS) for the individual runs. The blue points refer to the good runs, while the black ones are the rejected ones. On the bottom: the $<tpc/e>$ ratio is shown for each sector of CLAS. The colored points indicate the different sectors for each good run, while the black ones are the rejected runs without color difference between the sectors. In both plots, the experimental setting changes that might cause a change in the event rate are indicated with vertical colored lines.} 
\label{fig:tpc_over_e_Run_sec.png}
\end{figure}

\subsection{Coherent DVCS event selection}
~~~~Events with one and only one good electron, one and only one good RTPC track and at least one good photon are considered good coherent DVCS candidates. Even though the DVCS reaction has only one real photon in the final state, events with more than one good photon are not discarded at this stage. This is motivated by the fact that some photons correspond to random coincidences and discarding these events results in losing good events. Then, events with one or more $\pi^{0}$ are removed from the coherent DVCS sample. After that, the most energetic photon in each remaining event is chosen as the DVCS photon. Next, to consider an event as a clean $^{4}He$ DVCS, it has to pass respectively two sets of requirements: DVCS characteristic cuts and exclusivity cuts.

~\newpage
\paragraph{DVCS characteristics}
\begin{itemize}
\item $Q^{2}$ > 1 GeV$^{2}$: to ensure that the interaction occurs at the partonic level and the applicability of the factorization in the DVCS  handbag diagram.
%\item The invariant mass of the system of the virtual photon and the target 
   %proton is greater than $2~GeV/c{^2}$. This cut avoids the region of 
   %excitation of the proton to resonances.
\item $ -t > -t_{min}$: the transferred momentum squared to the recoil $^{4}He$ has to be greater than a minimum value defined by the kinematics of the beam and the scattered electron as:
\begin{equation}
   t_{min} = - Q^{2} \frac{2(1- x_{A})(1 - \sqrt{1 + \epsilon ^{2}}) + \epsilon 
   ^{2}}{4 x_{A}(1-x_{A})+ \epsilon ^{2}},\\
\end{equation}
where $\epsilon ^{2} = \frac{4M^{2}_{^4He}x^{2}_{A}}{Q^{2}}$, $x_{A} = \frac{M_{p}\cdot x_{B}}{M_{^4He}}$ and $M_{p}$ ($M_{^4He}$) is the proton ($^{4}He$) mass.\\

In the case of the proton DVCS, the variable $x_{A}$ is replaced by the Bjorken $x_{B}$ in the formula for $t_{min}$.

\item $E_{\gamma}>$ 2 GeV. This is a cleaning cut applied to reduce the 
   background in the DVCS sample as the simulation indicates that no DVCS 
   events are expected with photon energy less than 2 GeV. Figure 
   \ref{fig:energy_dvcs_photons} shows the energy distributions of the 
   simulated coherent and incoherent DVCS events.

\begin{figure}[tbp]
      \includegraphics[height=5.0cm]{fig_dvcs/photon_energy_coh_sim.png}
      \includegraphics[height=5.5cm]{fig_dvcs/photon_energy_incoh_sim.png}
          \caption{The energy distribution of the simulated coherent, on top, 
          and incoherent, on bottom, DVCS photons.}
          \label{fig:energy_dvcs_photons}
\end{figure}

\end{itemize}

\paragraph{Exclusivity cuts}

~\\
The coherent DVCS reaction is:
\begin{equation}
e(\mathbf{P}_{e}) + ~~^{4}He(\mathbf{P}_{^{4}He}) \rightarrow e'(\mathbf{P_{e'}}) +  ~~^{4}He'(\mathbf{P}_{^{4}He'}) + \gamma(\mathbf{P}_{\gamma})
\label{coh_dvcs_equ}
\end{equation}
where the symbols in the parentheses are the energy-momentum four-vectors. We define the additional four-vectors:
\begin{eqnarray}
\text{virtual photon vector } (\mathbf{P}_{\gamma^{*}}) &=&  \mathbf{P}_{e} -  \mathbf{P}_{e'} \\
\hspace{0.4in}  \mathbf{P}^{e^{4}He\gamma}_{X} &=& \mathbf{P}_{\gamma^{*}} + \mathbf{P}_{^{4}He} - (\mathbf{P}_{\gamma} + \mathbf{P}_{^{4}He'})\\
~~~~~~~~~~\mathbf{P}^{e^{4}He}_{X} &=& \mathbf{P}_{\gamma^{*}} + \mathbf{P}_{^{4}He} -  \mathbf{P}_{^{4}He'} \\
\hspace{0.2in} \mathbf{P}^{e\gamma}_{X} &=& \mathbf{P}_{\gamma^{*}} + \mathbf{P}_{^{4}He} - ~~\mathbf{P}_{\gamma}
\end{eqnarray}

~~~~The exclusivity of the coherent DVCS reaction is ensured by imposing the following conservation laws:
\begin{itemize}
\item The co-planarity cut ($\Delta \phi$). In principle, the virtual photon, the emitted real photon and the recoil helium lie in the same plane, which is called the hadronic plane. Thus the DVCS events must have $\Delta \phi$ values around zero. The hadronic plane can be defined in three ways:
\begin{eqnarray}
\overrightarrow{HP}_{1} &=& \overrightarrow{\mathbf{P}}_{^{4}He'} \times \overrightarrow{\mathbf{P}}_{\gamma^{*}}\\
\overrightarrow{HP}_{2} &=& \overrightarrow{\mathbf{P}}_{^{4}He'}  \times \overrightarrow{\mathbf{P}}_{\gamma}\\
\overrightarrow{HP}_{3} &=& \overrightarrow{\mathbf{P}}_{\gamma^{*}} \times \overrightarrow{\mathbf{P}}_{\gamma}
\end{eqnarray}
$\Delta \phi$ is defined to be the $\phi$ difference between these planes and is calculable from three combinations: ($\overrightarrow{HP}_{1}$, $\overrightarrow{HP}_{2}$), ($\overrightarrow{HP}_{1}$, $\overrightarrow{HP}_{3}$) and ($\overrightarrow{HP}_{2}$, $\overrightarrow{HP}_{3}$). We investigated the three combinations and we decided to use the second one as it gives better resolution.

\item Missing energy, mass and transverse momentum ($p^{T}_{X} = \sqrt{(p^{x}_{X})^2 + (p^{y}_{X}})^2$) cuts on $\mathbf{P}^{e^{4}He\gamma}_{X}$.

\item Missing mass cuts on the $e^{4}HeX$ and $e\gamma X$ systems, which are defined as $(P^{e^{4}He}_{X})^{2}$ and $(P^{e\gamma}_{X})^{2}$ respectively.

\item Cone angle cut between the measured real photon and the missing particle in the $e^{4}HeX$ configuration. It is defined as:
\begin{equation}
\theta(\gamma, e^{4}HeX) = cos^{-1} \left( \frac{\overrightarrow{\mathbf{P}}_{\gamma} \cdot \overrightarrow{\mathbf{P}}^{e^{4}He}_{X}}{|\overrightarrow{\mathbf{P}}_{\gamma^{}}| |\overrightarrow{\mathbf{P}}^{e^{4}He}_{X}|}   \right).
\end{equation}
\end{itemize}
~~~~~Figure \ref{fig:coh_exclusivty_cuts} summarizes all the exclusivity cuts. In these plots, the blue distributions represent the coherent events after the DVCS characteristic cuts and before all the exclusivity cuts. The shaded distributions stand for the events which passed all the exclusivity cuts except the one on the quantity plotted. We fitted each shaded distribution by a Gaussian and then we applied  3$\sigma$ cuts around the mean value of each distribution. The events which pass these cuts are assumed to be good $^{4}He$ DVCS events. 
~\\
~\\

\begin{figure}[!h]
\centering
\includegraphics[scale=0.4]{fig_dvcs/all_coh_exc_cuts.png}
\caption{The coherent DVCS exclusivity cuts. The blue distributions represent the coherent DVCS events candidate. The shaded distributions represent the events which passed all the exclusivity cuts except the quantity plotted. The vertical red lines represent $3\sigma$ cuts. The missing momentum in $x$ and $y$ directions in the configuration $e^{4}He\gamma X$, are shown for information. The mean and the sigma values of each quantity can be found in Appendix \ref{exclusivity_cuts}, table \ref{Table:coh_exclusivity_cuts}.} 
\label{fig:coh_exclusivty_cuts}
\end{figure}

\subsection{Coherent channel checking}

\subsubsection{Checking $^{4}He$ PID}

\begin{figure}[tbp]
      \hspace{-0.5cm}
      \includegraphics[height=14.2cm]{fig_dvcs/all_coh_pid.png}
      \caption{Distributions of the exclusive variable for the identified DVCS 
      events with only one track in the RTPC (blue), one track and PID1 is 
      equal to 47 (red), and processing all the tracks in each event with the 
      exclusivity variables (black).}
      \label{fig:dedx_check}
\end{figure}

In this analysis We claim that kinematic exclusivity cuts are sufficient to
cleanly select coherent $^4$He DVCS events without the need for $\frac{dE}{dx}$
cuts. We performed few checks regarding applying a PID cut, where the full data
was analyzed in the following three sets:\\
\begin{itemize}
\item Processing all the reconstructed tracks in each event with the exclusivity
cuts.\\
\item Processing events with only one good track in the RTPC being
reconstructed.\\
\item Processing events with only one track that passes a dedx cut.\\
\end{itemize}

The results are shown in figure \ref{fig:dedx_check} in terms of the
exclusive variables for the identified coherent DVCS events. One can see that
applying a PID cut would only change the statistics and not the width of
distributions. On the other hand, figure \ref{fig:coh_alu_PID} shows a 
comparison between the reconstructed beam-spin asymmetries with and without 
applying a PID cut. The two sets of asymmetries are compatible within the given 
statistical error bars. From these two observations, we deduce that a PID cut 
on the Helium would not reduce any background contribution.
   \begin{figure}[tbp]
         \centering
         \includegraphics[height=8.2cm]{fig_dvcs/Coh_ALU_W_out_PID.pdf}
         \caption{The integrated coherent beam-spin asymmetries as a function 
         of $\phi$ with (red) and without (blue) applying a PID cut on Helium 
      tracks.}
         \label{fig:coh_alu_PID}
      \end{figure}

\subsubsection{Left/Right modules of the RTPC}
The two modules of the RTPC have shown different yields in terms of the 
identified good track, see Section 3.1.4. This different yields should not 
affect the DVCS distributions neither the reconstructed beam-spin asymmetries.  
In this section, we carry out the analysis for the coherent channel based on 
the Left/Right modules of the RTPC to ensure that the reconstructed asymmetries 
for the two modules of the RTPC are compatible. Figure 
\ref{fig:sides_rtpc_exclusivity} shows the RTPC module dependent exclusive 
distributions for the identified coherent DVCS events. Figure 
\ref{fig:coherent_alu_sides} shows the integrated coherent beam-spin 
asymmetries for the two modules separately, and for the two half together. To 
conclude, the two modules of the RTPC show a very similar performances in terms 
of the DVCS exclusive distributions and the module-dependent asymmetries are 
compatible.

\begin{figure}[tbp]
      \centering
      \includegraphics[height=14.2cm]{fig_dvcs/all_coh_exc_cuts_final_sides.png}
      \caption{The distributions of the exclusive variables for the identified
      coherent DVCS events in the individual modules of the RTPC, Left module 
   in blue and Right module in red.}                             
   \label{fig:sides_rtpc_exclusivity}
   \end{figure}

   \begin{figure}[tbp]
      \centering
      \includegraphics[height=7.0cm]{fig_dvcs/BSA_Coherent_sides.png}
      \caption{The reconstructed integrated-over-full-data beam-spin 
      asymmetries as a function of the hadronic angle $\phi$ in the two modules 
   of the RTPC separately, and the integrated signal over the whole RTPC.}
      \label{fig:coherent_alu_sides}
       \end{figure}

\subsection{Comparison with simulation}
~~~~Coherent DVCS events were simulated according to the procedures described 
in section \ref{Event_generator}. Then, events are selected following the same 
identification criteria as for the experimental data. Finally, We apply similar 
exclusivity cuts as presented for the experimental coherent DVCS events. That 
is each exclusive distribution is fitted by a Gaussian and a 3$\sigma$ cut is 
applied. So the cut are not identical, but obtained with the same method. This 
is done to avoid issues on variables where the peak is not in the exact same 
place in simulation and in data.\\

Figure \ref{fig:coh_comparison_with_simulation_1} shows the comparison between 
the experimental and the simulated DVCS events as a function of the kinematic 
variables: $Q^{2}$, $x_{B}$, $-t$, and $\phi$. Figure 
\ref{fig:coh_comparison_with_simulation_2} shows the comparison as a function 
of the quantities used for the exclusivity cuts. The distributions in the 
latter two figures show a satisfying match between the experimental and the 
simulated data.
\begin{figure}[h!]
\includegraphics[scale=0.31]{fig_dvcs/comp/Q2_Coh.png}
\includegraphics[scale=0.31]{fig_dvcs/comp/xB_Coh.png}
\includegraphics[scale=0.31]{fig_dvcs/comp/t_Coh.png}
\hspace{+0.5in}\includegraphics[scale=0.31]{fig_dvcs/comp/phi_h_Coh.png}
\caption{Comparison between the simulated $e^{4}He\gamma$ DVCS events (in red 
lines) and the experimental DVCS events (in shaded blue) as a function of the 
kinematic variables: $Q^{2}$, $x_{B}$, $-t$, and $\phi$. }
\label{fig:coh_comparison_with_simulation_1}
\end{figure}

\begin{figure}[h!]
\includegraphics[scale=0.36]{fig_dvcs/comp/Coh_delta_phi.png}
\includegraphics[scale=0.36]{fig_dvcs/comp/Coh_e4Hegamma_E_Mis.png}
\includegraphics[scale=0.36]{fig_dvcs/comp/Coh_e4Hegamma_M2_Mis.png}
\includegraphics[scale=0.36]{fig_dvcs/comp/Coh_e4Hegamma_PT_Mis.png}
\includegraphics[scale=0.36]{fig_dvcs/comp/Coh_e4He_M2_Mis.png}
\includegraphics[scale=0.36]{fig_dvcs/comp/Coh_egamma_M2_Mis.png}
\caption{Comparison between simulated and experimental $e^{4}He\gamma$ DVCS events. The distributions from left to right and from top to bottom are: Co-planarity cut, missing energy, missing mass squared and missing transverse momentum in the configuration of detecting all the three final-state particles, missing mass squared in the $e^{4}HeX$ and $e\gamma X$ configurations respectively. The vertical black lines indicate the theoretically expected value for each quantity.} 
\label{fig:coh_comparison_with_simulation_2}
\end{figure}

~\newpage
~\newpage

\section{Incoherent channel}
~~~~In this channel, the DVCS process happens on a bound proton. Thus, the final state has a recoil proton instead of the helium nucleus. Therefore, events with one good electron, one recoil proton, and at least one real photon are the good candidates here. For the rest, we follow the same steps that were introduced for the coherent DVCS selection.

\subsection{Good run list}
~~~~The events rate stability is verified by looking at the rate of the detected number of protons to the detected electrons (<p/e>). Like for the coherent channel, the same technique for the determination of the good run list is followed herein. The results are presented in figure \ref{fig:prot_over_e_Run_sec.png}. 
\begin{figure}[h!]
\includegraphics[scale=0.4]{fig_dvcs/prot_over_e_Run.png}
\includegraphics[scale=0.4]{fig_dvcs/prot_over_e_Run_sec.png}
\caption{On the top: the integrated <$p/e$> ratio as a function of run number. The blue points refer to the good runs, while the black points are the rejected ones. On the bottom: the same ratio for each run, is shown for each sector of CLAS. The colored points indicate the six sectors, while the black points are the sectors of the rejected runs. } 
\label{fig:prot_over_e_Run_sec.png}
\end{figure}

\subsection{Proton DVCS event selection}
~~~~To certify that an event is a proton DVCS one, we require the same DVCS kinematic cuts as those presented for the coherent DVCS selection. Then, the exclusivity of the DVCS reaction is ensured by applying an equivalent set of exclusivity with taking a proton at rest as the target, instead of $^4He$. Figure \ref{fig:incoh_exclusivty_cuts} summarizes these exclusivity cuts.\\

%\paragraph{$\blacklozenge$ DVCS characteristics}
%\begin{itemize}
%\item The invariant mass of the system of the virtual photon and the target proton is greater than $2~GeV/c{^2}$ in order to avoid the excitation of the proton to baryon states and be above the nucleon resonances.
%\item $Q2 > 1 GeV^{2}$: To ensure that we have hard interaction and the applicability of the handbag diagram factorization for the DVCS.
%\item High energetic final state real photon ($E_{\gamma}> 2 GeV$)
%\item $ -t > t_{min}$: The transferred momentum squared to the proton has to be greater than a minimum value defined by the kinematics of the beam and the scattered electron as:
%\begin{equation}
%t_{min} = \frac{- Q^{2}*2(1- x_{B})(1 + \epsilon ^{2} - \sqrt{1 + \epsilon ^{2}})}{4 x_{B}(1-x_{B})+ \epsilon ^{2};}\\
%\end{equation}
%Where $\epsilon ^{2} = \frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$.
%\end{itemize}

%\paragraph{$\blacklozenge$ Exclusivity cuts}~
%~~~~The exclusivity of the proton DVCS events is ensured by applying the following set of cuts:
%\begin{itemize}
%\item The coplanarity cut ($\Delta \phi$) between the recoil proton and the final state real photon. 
%\item Missing energy, mass and transverse momentum ($p_{T} = \sqrt{p^{2}_{x} + p^{2}_{y}}$) cuts in the final state configuration $ep\gamma X$.
%\item Missing mass cuts in the final state configurations $epX$ and $e\gamma X$.
%\item Cone angle cut between the measured real photon and the missed particle in the %configuration $epX$.
%\end{itemize}
\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{fig_dvcs/all_incoh_exc_cuts.png}
\caption{The incoherent DVCS exclusivity cuts. The blue distributions represent all the events with one good electron, one good proton, and at least one photon in the IC. The shaded brown distributions show the incoherent DVCS events which passed all the exclusivity cuts except the one on the quantity drawn. The distributions from left to right and from top to bottom are: the proton-photon coplanarity, the missing energy, missing mass squared, missing transverse momentum from $ep\gamma X$, the missing mass squared $epX$ and the missing mass squared $e\gamma X$, the angle between the missing particle in $epX$ and the measured photon, the missing $P_{x}$ and $P_{y}$ in $ep\gamma X$. The vertical red lines represent 3$\sigma$ cuts. The mean and sigma values of each shaded distribution are listed in table \ref{Table:incoh_exclusivity_cuts}.} 
\label{fig:incoh_exclusivty_cuts}
\end{figure}

\subsection{Comparison with simulation}
~~~~The three particles of the simulated $ep\gamma$ DVCS events are selected applying the previously described identification requirements. The events with three identified particles (e, p, $\gamma$) are required to pass a set of exclusivity cuts such as the ones of the experimental incoherent DVCS events. In this section, a comparison between the experimental and the simulated data is carried out.\\

Figure \ref{fig:incoh_coparison_with_simulation_1} shows the comparison between the simulated (red lines) and the experimental (shaded blue) incoherent DVCS events as a function of the four kinematic variables: $Q^{2}$, $x_{B}$, $-t$, and $\phi$. Figure \ref{fig:incoh_comparison_with_simulation_exclusive_2} shows the comparison as a function of the variables used to select exclusive DVCS events.
\begin{figure}[h!]
\includegraphics[scale=0.35]{fig_dvcs/comp/Q2_InCoh.png}
\includegraphics[scale=0.35]{fig_dvcs/comp/xB_InCoh.png}
\includegraphics[scale=0.35]{fig_dvcs/comp/t_InCoh.png}
\includegraphics[scale=0.35]{fig_dvcs/comp/phi_h_InCoh.png}
\caption{Comparison between the Monte-Carlo simulated $ep\gamma$ DVCS events (red lines) and the experimental ones (blue shaded distributions) in terms of the kinematics: $Q^{2}$, $x_{B}$, $-t$, and $\phi$, respectively from left to right and from top to bottom.}
\label{fig:incoh_coparison_with_simulation_1}
\end{figure}

\begin{figure}[h!]
\includegraphics[scale=0.35]{fig_dvcs/comp/InCoh_delta_phi_InCoh.png}
\includegraphics[scale=0.35]{fig_dvcs/comp/InCoh_epgamma_E_Mis.png}
\includegraphics[scale=0.35]{fig_dvcs/comp/InCoh_epgamma_M2_Mis.png}
\includegraphics[scale=0.35]{fig_dvcs/comp/InCoh_epgamma_PT_Mis.png}
\includegraphics[scale=0.35]{fig_dvcs/comp/InCoh_egamma_M2_Mis_InCoh.png}
\includegraphics[scale=0.35]{fig_dvcs/comp/InCoh_Theta_gammaX_InCoh.png}
\caption{Comparison between simulated and experimental $ep\gamma$ DVCS events in terms of the variables used for exclusivity cuts. The vertical black lines indicate the theoretically expected values for each exclusive quantity.} 
\label{fig:incoh_comparison_with_simulation_exclusive_2}
\end{figure}

~\newpage
~\newpage
\section{Kinematic coverages}
~~~~The one-dimensional distributions of explored kinematical regions can be 
seen in figure \ref{fig:coh_comparison_with_simulation_1} for the coherent, and 
in figure \ref{fig:incoh_coparison_with_simulation_1} for the incoherent DVCS 
channels. In figure \ref{fig:kinematic_coverage}, we show two-dimensional 
distributions of these variables to display the correlations between them. 
%\begin {table}[!h]
%\begin{center}
%\begin{tabular}{|l|l|l|l|}
%\hline
%DVCS channel &  $Q^{2}$~$[GeV^{2}/c^{2}]$  & $~~~~~~x_{B}$  & -t ~$[GeV^{2}/c^{2}]$\\
%\hline
%Helium-4 & [1.0, 3.0] & [0.1, 0.3] & [0.06, 0.2] \\
%\hline
%proton & [1.0, 4.5] & [0.1, 0.55] & [0.03, 2.5] \\
%\hline
%\end{tabular}
%\caption{ The coherent and the incoherent explored kinematic regions.}
%\label{Table:kinematic_ranges}
%\end{center}
%\end{table}

\begin{figure}[h!]
\includegraphics[scale=0.35]{fig_dvcs/coh_Q2_xB.png}
\includegraphics[scale=0.35]{fig_dvcs/incoh_Q2_xB.png}
\includegraphics[scale=0.35]{fig_dvcs/new_t_Q2_Coh.png}
\includegraphics[scale=0.35]{fig_dvcs/new_t_Q2_InCoh.png}
\includegraphics[scale=0.35]{fig_dvcs/new_phi_t_Coh.png}
\includegraphics[scale=0.35]{fig_dvcs/new_phi_t_InCoh.png}
\caption{The distributions of the identified coherent DVCS are on the left 
   panel, while on the right are the incoherent ones. On the top panel: $Q^2$ 
as a function of $x_B$ with W and fixed $-t_{min}$ value cuts in $Q^{2}-x_{B}$ 
plane. On the middle panel: $-t$ as a function of $Q^2$.  On the bottom panel: 
$-t$ as a function of $\phi$.} \label{fig:kinematic_coverage}
\end{figure}

\section{Data binning}
~~~~~The DVCS cross section and $A_{LU}$, equations \ref{BSA_equation} to 
\ref{eq:A_LU-coh}, depend on the four kinematic variables: $Q^{2}$, $x_{B}$, 
$t$, and $\phi$. The number of identified coherent (incoherent) DVCS events is 
about 5000 (30k). Due to our limited statistics only, a two-dimensional binning 
is carried out in this analysis.  The strongest dependence of $A_{LU}$ is on 
the azimuthal angle between the leptonic and the hadronic planes ($\phi$).  
Thus, we construct the two-dimensional bins as follows: the coherent 
(incoherent) measured ranges of $Q^{2}$, $x_{B}$ and $-t$ are binned 
statistically into three (four) bins.  Then, the identified DVCS events in each 
$Q^{2}$, $x_{B}$ and $-t$ bin, are binned into nine bins in $\phi$.  Therefore, 
we are left with $Q^2$-$\phi$ bins integrated over the full ranges of $x_{B}$ 
and $-t$, $x_{B}$-$\phi$ bins integrated over $Q^2$ and $-t$, and $-t$-$\phi$ 
bins integrated over $Q^2$ and $x_{B}$. For instance, figure 
\ref{fig:coh_Q2_bins} shows the one-dimensional bins in $Q^2$ and the 
associated bins in $\phi$.

\begin{figure}[h!]
\centering
\includegraphics[scale=0.36]{fig_results/Q2_Coh_bins.png}
\includegraphics[scale=0.45]{fig_results/bins_Coh_Q2_Phi.png}
\caption{On the top: the $Q^2$ distribution of the collected coherent DVCS events. The different colors indicate the different bins in $Q^2$ integrated over the full ranges of $-t$ and $x_B$. On the bottom: the $\phi$ distributions of the coherent DVCS events for the bins in $Q^2$, which are shown in the top plot. The different colors in each $\phi$ distribution represent the nine bins in $\phi$.} 
\label{fig:coh_Q2_bins}
\end{figure}

\section{Background subtraction}
\label{Background_subtraction}

\subsection{$\pi^0$ contaminations}
~~~~Even with all cuts applied to select the selected DVCS events, the events are not all DVCS events. In our kinematic region, the main contamination comes from the exclusive electroproduction of $\pi^{0}$ ($e ^{4}He \rightarrow e ^{4}He \pi^{0} \rightarrow e ^{4}He \gamma \gamma $, $e p \rightarrow e p \pi^{0} \rightarrow e p \gamma \gamma $), in which one of the two photons of the $\pi^{0}$ decay passes the requirements of the DVCS. Thus, the event is counted as a DVCS event. These events contaminate the DVCS sample and have to be subtracted to obtain the true number of DVCS events. In the case of the coherent channel, this can be formulated as:
\begin{equation}
N^{True}_{e^{4}He\gamma} = N^{Exp.}_{e^{4}He\gamma} -  N^{Exp.}_{e^{4}He\pi^{0}(\gamma)},
\label{equ_back_1}
\end{equation} 
where $N^{True}_{e^{4}He\gamma}$, $N^{Exp.}_{e^{4}He\gamma}$ and $ N^{Exp.}_{e^{4}He\pi^{0}(\gamma)}$ are the true number of coherent DVCS events, the experimentally measured number of $e^{4}He\gamma$ events and the contamination number, respectively. The contamination can be calculated by using real data and simulation. We define, for each kinematic bin and for each beam helicity state
\begin{equation}
N^{Exp.}_{e^{4}He\pi^{0}(\gamma)} = \frac{N^{Sim.}_{e^{4}He\pi^{0}(\gamma)}}{N^{Sim.}_{e^{4}He\pi^{0}(\gamma \gamma)}} * N^{Exp.}_{e^{4}He\pi^{0}(\gamma \gamma)},
\label{equation: background_equ}
\end{equation} 
where $N^{Exp.}_{e^{4}He\pi^{0}(\gamma \gamma)}$ is the number of measured $e^{4}He\pi^{0}$ events, for which both photons of the $\pi^{0}$ have been detected. The quantity $\frac{N^{Sim.}_{e^{4}He\pi^{0}(\gamma)}}{N^{Sim.}_{e^{4}He\pi^{0}(\gamma \gamma)}} $ is the acceptance ratio for detecting a $e^{4}He\gamma$ event that originates from an $e^{4}He\pi^{0}$ event. It can be derived from Monte-Carlo simulations by generating and simulating $e^{4}He\pi^{0}$. $N^{Sim.}_{e^{4}He\pi^{0}(\gamma)}$ is the number of such events passing the DVCS requirements, while $N^{Sim.}_{e^{4}He\pi^{0}(\gamma \gamma)}$ is the number of simulated $e^{4}He\pi^{0}$ events passing the exclusivity cuts for $e^{4}He\pi^{0}$ events.\\

The previous formulas apply to the case of the coherent DVCS. The same procedures hold for the incoherent case by replacing the $^{4}He$ with the proton.\\

The selection of the exclusive $e^{4}He\pi^{0}$ and $ep\pi^{0}$ events requires the detection of one good electron, one good $\pi^{0}$ in the topology ICIC or ICEC, and one good $^{4}He$ track in the coherent case, or one good proton in the incoherent case. In order to ensure that this is a deep process, we apply the same kinematic cuts as DVCS. These cuts and the comparisons with simulation can be found in Appendix \ref{app:Exclusive_pi0_selection}.\\

Figure \ref{fig:coh_acceptance _ratios} shows the coherent acceptance ratio as a function of each of the four kinematic variables ($Q^{2}$, $x_{B}$, $-t$, $\phi_{h}$). These distributions are one-dimensional, i.e. the data are integrated over all kinematical ranges except for the quantity which is binned (along the x-axis). The results  for the incoherent channel can be found in figure \ref{fig:incoh_acceptance _ratios}. The mean value of the acceptance ratio for the coherent channel is around 25$\%$, with some dependence on $x_{B}$ and $\phi$, and almost no dependence on $Q^{2}$ and $-t$. For the incoherent channel, the mean acceptance ratio is around 20$\%$ with some dependence on the four kinematic variables.\\

As presented in the previous section, we construct two-dimensional bins: $Q^2$-$\phi$, $x_B$-$\phi$ and -$t$-$\phi$. Thus, for each bin in $Q^2$, $x_B$ and $-t$, we assume that the acceptance ratio does not change a lot within the bin range and we construct the one-dimensional acceptance ratio as a function of $\phi$. The latter is used to perform the background subtraction as shown in equations \ref{equ_back_1} and \ref{equation: background_equ}.

\begin{figure}[tp]
\centering
\includegraphics[scale=0.30]{fig_dvcs/e4Hegamma_e4Hepi0_Q2.png}
\includegraphics[scale=0.30]{fig_dvcs/e4Hegamma_e4Hepi0_xB.png}
\includegraphics[scale=0.30]{fig_dvcs/e4Hegamma_e4Hepi0_t.png}
\includegraphics[scale=0.30]{fig_dvcs/e4Hegamma_e4Hepi0_Phi.png}
\caption{The coherent channel acceptance ratios as a function of the kinematic variables: $Q^{2}$ (top left), $x_{B}$ (top right), $-t$ (bottom left), and $\phi$ (bottom right). }
\label{fig:coh_acceptance _ratios}
\end{figure}

\begin{figure}[tp]
\centering
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_Q2.png}
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_xB.png}
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_t.png}
\includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_Phi.png}
\caption{The incoherent channel acceptance ratios as a function of the kinematic variables: $Q^{2}$ (top left), $x_{B}$ (top right), $-t$ (bottom left), and $\phi$ (bottom right).  }
\label{fig:incoh_acceptance _ratios}
\end{figure}

\subsection{Accidental contaminations}
~\\

The $\Delta z$ distributions between the recoil hadrons and the scattered 
electrons, see figures \ref{fig:rtpc_delta_z} and 
\ref{fig:proton_delta_z_e_prot}, indicate that accidental background events are 
contributing inside the exclusive DVCS. In order to estimate and correct 
this background contribution, we processed our dataset with the previously 
presented exclusive requirements without any constraints on the z-vertex of the 
final state particle nor on the correspondence between them, $\Delta z$. The 
results for the identified coherent DVCS events are presented in figure 
\ref{fig:delta_z_after_ex}. This guides us to correct for these accidentals in 
our asymmetries in the form: $ A_{LU~~corr.} = \frac{1}{1 - contamination} 
A_{LU}$, with a 4.1$\%$ global accidental contamination for the coherent DVCS 
channel (see numbers in table~\ref{table:Events_numbers}). The same procedures 
were performed on the incoherent channel, and a 
global contamination of 6.5$\%$ has been observed.\\

\begin{figure}[tbp]
\centering
\includegraphics[height=7.2cm]{fig_dvcs/rtpc_delta_z_acc.png}
\caption{The z-vertex correspondence between the scattered electron and the 
   recoil $^{4}He$ for the identified coherent DVCS events after the 
   exclusivity cuts in the two modules of the RTPC separately without any 
   initial constrains on z-vertices of the individual particles.  Table 
\ref{table:Events_numbers} summarizes the cut numerically.}
\label{fig:delta_z_after_ex}
 \end{figure}

\begin{table}[!h]
   \centering
   \begin{center}
      \begin{tabular}{|l|l|l|}
         \hline
         \multicolumn{3}{ |c| }{Number of coherent DVCS events} \\
         \hline
         $\Delta z$ [mm] & Left module & Right module\\
         \hline
         [-50:-30] & 42 & 77 \\
         \hline
         [-20:20]  & 2741 & 2856\\
         \hline
         [30:50]   & 34 &  78 \\
         \hline
         Contamination percentage  & 2.7$\%$  & 5.4$\%$ \\
         \hline 
      \end{tabular}
      \caption{The numbers of the identified coherent DVCS events in the 
      different regions in $\Delta z$ for the two modules of the RTPC.}
      \label{table:Events_numbers}
   \end{center}
\end{table}

~\newpage
\section{Statistical uncertainties}
~~~~~In terms of the collected number of events in each beam-helicity state ($N^{+}$, $N^{-}$), $A_{LU}$ can be expressed as:
\begin{equation}
A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} }.
\label{equation: ALU}
\end{equation}
where $P_{B}$ is the beam polarization, $N^{+}$ and $N^{-}$ are the background-subtracted yields of DVCS events. The statistical uncertainties on the measured $A_{LU}$ can be derived as:
\begin{equation}
\Delta A = \frac{1}{P_{B}} \sqrt{\left(\frac{\partial A}{\partial N^{+}}\right)^{2} (\Delta N^{+})^{2} + \left(\frac{\partial A}{\partial N^{-}}\right)^{2} (\Delta N^{-})^{2}} = \frac{1}{P_{B}} \sqrt{\frac{(2N^{-} \Delta N^{+})^{2} + (2N^{-} \Delta N^{+})^{2}}{(N^{+} + N^{-})^{4} }},
\end{equation}
where $N^{+}$ and $N^{-}$ are
\begin{equation}
N^{\pm} = N^{\pm}_{e^{4}He\gamma} - R ~ N^{\pm}_{e^{4}He\pi^{0}},
\end{equation} 
and $R$ is the calculated background acceptance ratio from the simulation. The statistical uncertainty on the counts ($N^{\pm}$) is
\begin{equation}
(\Delta N^{\pm})^{2} = (\Delta N^{\pm}_{e^{4}He\gamma})^{2} + (R ~ \Delta N^{\pm}_{e^{4}He\pi^{0}})^{2} 
                       =  N^{\pm}_{e^{4}He\gamma} + R^2 N^{\pm}_{e^{4}He\pi^{0}}. 
\end{equation}
The errors on $P_{B}$ and $R$ are not considered statistical errors. They contribute in the systematic uncertainties, as will be discussed in the following section. This derivation is valid for the coherent and the incoherent DVCS channels.

\section{Systematic uncertainties}

~~~~It is particularly convenient to use the $A_{LU}$ as a DVCS observable, 
because most of the experimental systematic uncertainties, such as 
normalization and efficiencies that appear in the cross sections cancel out in 
the asymmetry ratio. However, some sources still affect this asymmetry and 
contribute in the systematic uncertainties on the measured $A_{LU}$. The main 
known sources of systematic errors are: the DVCS selection cuts, the fitting 
sensitivity to our binning, the beam polarization, the background acceptance 
ratio and the radiative corrections. In the following, we present an estimation 
of the contribution from each source.

\paragraph{DVCS selection cuts}
~\\

In order to evaluate the systematic uncertainties stemming from the DVCS 
selection cuts, the analysis was repeated changing cuts. As it can be seen in 
figure \ref{fig:coh_exclusivty_cuts}, the 3$\sigma$ cuts cover up to 97$\%$ of 
the events in all the distributions except the $e^{4}He\gamma$ missing mass 
distribution. In order to investigate the effect of taking different cuts on 
the reconstructed $A_{LU}$, we fix the 3$\sigma$ cuts on all the exclusive 
quantities except for the cut on $e^{4}He\gamma$ missing mass. For the 
incoherent channel, the same procedure is carried out on the $ep\gamma$ missing 
mass distribution. The results can be seen in figure 
\ref{fig:cuts_e4Hegamma_M2_Mis}. The maximum variation that has been observed 
on the $A_{LU}$ observable between 3$\sigma$ cut and the other cuts 
($\frac{\Delta A^{sys. cuts}_{LU}}{A_{LU}}$) is equal to  8$\%$ for the 
coherent channel and to 6$\%$ for the incoherent channel at $\phi = 90^{\circ}$ 
extracted from a fit, in the form of $\frac{\alpha sin(\phi)}{1+\beta cos(\phi) 
+ \eta cos(2\phi)}$, to $A_{LU}(\phi)$ distribution. The fit parameters are 
plotted as functions of the cut widths in figures \ref{fig:sys_fit_alpha} to 
\ref{fig:sys_fit_Alu}.

\begin{figure}[h!]
\includegraphics[scale=0.31]{fig_dvcs/e4Hegamma_M2_Mis_sig.png}
\includegraphics[scale=0.31]{fig_dvcs/e4Hegamma_M2_Mis_sig.png}
\includegraphics[scale=0.31]{fig_dvcs/e4Hegamma_e4Hepi0_Phi_2.png}
\hspace{-0.2in}\includegraphics[scale=0.31]{fig_dvcs/R_epgamma_eppi0_Phi.png}
\includegraphics[scale=0.31]{fig_dvcs/BSA_Coherent_sigmas.png}
\includegraphics[scale=0.31]{fig_dvcs/BSA_InCoherent_sigmas.png}
\caption{The systematic uncertainties stemming from the DVCS selection cuts in 
the coherent (left column) and the incoherent (right column) channels. On the 
top: the missing mass squared of $e^{4}He\gamma$ and $ep\gamma$. The different 
vertical coloured lines indicate the different cuts: 1$\sigma$, 2$\sigma$, ...  
5$\sigma$. In the middle: the coherent (incoherent) acceptance ratios versus 
$\phi$ for the different configurations of the cuts. On the bottom: the 
reconstructed $A_{LU}$ as a function of $\phi_{h}$ for the different cut 
widths.}
\label{fig:cuts_e4Hegamma_M2_Mis}
\end{figure}

\begin{figure}[tbp]
 \includegraphics[height=6.2cm]{fig_dvcs/coh_alpha_Nsig.png}
    \includegraphics[height=6.2cm]{fig_dvcs/incoh_alpha_Nsig.png}
       \caption{The coherent (left) and incoherent (right) $\alpha$ parameter 
          of
       the fits as a function of cut width.  }
       \label{fig:sys_fit_alpha}
    \end{figure}

\begin{figure}[tbp]
      \includegraphics[height=6.2cm]{fig_dvcs/coh_beta_Nsig.png}
         \includegraphics[height=6.2cm]{fig_dvcs/incoh_beta_Nsig.png}
            \caption{The coherent (left) and incoherent (right) $\beta$ 
               parameter of the
            fits as a function of cut width.  }
            \label{fig:sys_fit_beta}
         \end{figure}

\begin{figure}[tbp]
\includegraphics[height=6.2cm]{fig_dvcs/coh_eta_Nsig.png}
\includegraphics[height=6.2cm]{fig_dvcs/incoh_eta_Nsig.png}
   \caption{The coherent (left) and incoherent (right) $\eta$ parameter of the
   fits as a function of cut width.  }
   \label{fig:sys_fit_eta}
\end{figure}

\begin{figure}[tbp]
\includegraphics[height=6.2cm]{fig_dvcs/coh_chi2_Nsig.png}
\includegraphics[height=6.2cm]{fig_dvcs/incoh_chi2_Nsig.png}
   \caption{The coherent (left) and incoherent (right) $\chi^{2}$ parameter of
   the fits as a function of cut width.}
   \label{fig:sys_fit_chi2}
\end{figure}

\begin{figure}[tbp]
\includegraphics[height=6.2cm]{fig_dvcs/coh_Alu_Nsig.png}
\includegraphics[height=6.2cm]{fig_dvcs/incoh_Alu_Nsig.png}
   \caption{The coherent (left) and incoherent (right) 
      beam-spin asymmetry at
   $\phi = 90 ^{\circ}$. }
   \label{fig:sys_fit_Alu}
\end{figure}

\paragraph{Fitting sensitivity to our binning}
~\\

In order to evaluate how sensitive are the fit results to our binning, we 
binned the data into 11 bins in $\phi$ and we compared the reconstructed 
asymmetries to the results from our 9 binning. Figure 
\ref{fig:coh_bins_phi_9_11} shows the coherent reconstructed $A_{LU}$ as a 
function of $\phi$ in $Q^{2}$, $x_B$ and $-t$ bins.  The coherent, figure 
\ref{fig:coh_BSA_9_11}, and the incoherent, figure \ref{fig:incoh_BSA_9_11}, 
measured $A_{LU}$ at $\phi = 90 ^{\circ}$ are showing an overall average of 
5.1$\%$ and 7.1$\%$ systematic uncertainties respectively, which will be added 
to our estimated uncertainties for the extracted asymmetries at $\phi = 
90^{\circ}$.

\begin{figure}[tbp]
   \centering
      \includegraphics[height=6.2cm]{fig_dvcs/sBSA_Coherent_Q2.png}
      \includegraphics[height=6.2cm]{fig_dvcs/sBSA_Coherent_xB.png}
      \includegraphics[height=6.2cm]{fig_dvcs/sBSA_Coherent_t.png}
     \caption{The measured coherent beam-spin asymmetry as
     a function of $\phi$ in $Q^{2}$, $x_B$ and $-t$ bins, using two binning 
  sets in $\phi$: 9 bins (in blue) and 11 bins (in red).}
      \label{fig:coh_bins_phi_9_11}
    \end{figure}

\begin{figure}[tbp]
   \centering
      \includegraphics[height=9.2cm]{fig_dvcs/BSA_Coherent_9_11.png}
      \caption{The coherent $A_{LU}$($\phi = 90 ^{\circ}$), from the fit, as a 
      function of $Q^{2}$, $x_B$ and $-t$, using 9 (in blue) and 11 (in red) 
   bins in $\phi$.}
      \label{fig:coh_BSA_9_11}
    \end{figure}

\begin{figure}[tbp]
   \centering
      \includegraphics[height=9.2cm]{fig_dvcs/BSA_InCoherent_9_11.png}
      \caption{The incoherent $A_{LU}$($\phi = 90 ^{\circ}$), from the fit, as 
         a function of $Q^{2}$, $x_B$ and $-t$, using 9 (in blue) and 11 (in 
      red) bins in $\phi$. }
      \label{fig:incoh_BSA_9_11}
    \end{figure}

\paragraph{Beam polarization}
~\\

The beam polarization has been measured regularly during the CLAS-EG6 data 
taking period by using the Hall B M\o ller polarimeter. This polarimeter 
measures the angular distribution of the M\o ller electrons to obtain the beam 
polarization. Figure \ref{fig:beam_polarization} shows the M\o ller 
measurements taken during the EG6 experiment. A linear fit to these 
measurements yields a mean polarization value of 0.8367. The precision of the 
Hall B M\o ller polarimeter ($\frac{\Delta P}{P})$ was measured to be around 
3.5$\%$ \cite{hallb_polarimeter}. We asume therefore a 3.5$\%$ systematic 
uncertainty on the measured asymmetries ($\frac{\Delta A^{sys.  
p}_{LU}}{A_{LU}}$~=~$\frac{\Delta P}{P}$).

\begin{figure}[tp]
\centering
\includegraphics[scale=0.25]{fig_dvcs/beam_polarization.png}
\caption{Beam polarization measurements during the CLAS-EG6 running period. The red squares are the measurements with a negative current in the Helmholtz coils of the M\o ller polarimeter and the purple triangles are these with a positive current. The figure is taken from \cite{yohann}.} 
\label{fig:beam_polarization}
\end{figure}

\paragraph{Acceptance ratio}
~\\

Predominantly, two techniques are used to estimate the systematic uncertainty associated with the calculated acceptance ratio (R). The first is via repeating the analysis by implementing R differently, while the second technique is by using two generating models to calculate R.\\

Both methods were investigated in this work. Regarding the first method, the analysis was repeated by taking three different values for R: 0.8*R, R and 1.2*R. The beam-spin asymmetries at $\phi = 90^{\circ}$ were extracted and compared, see figure \ref{fig:background_sub_sys_uncer}. A maximum variation of 2$\%$ (0.6$\%$) has been observed on the incoherent (coherent) $A_{LU}$ at $\phi = 90^{\circ}$. \\

\begin{figure}[tp]
\includegraphics[scale=0.30]{fig_dvcs/final_coh_BSA_NR.png}
\includegraphics[scale=0.30]{fig_dvcs/final_incoh_BSA_NR.png}
\caption{The extracted beam-spin asymmetries at $\phi = 90^{\circ}$ as a 
function of three sets of the calculated acceptance ratios: 0.8*R, 1.0*R and 
1.2*R, for the coherent (on the left) and the incoherent (on the right) DVCS 
channels.} \label{fig:background_sub_sys_uncer}
\end{figure}

For the second technique, in fact there is only one event generator available, presented in section \ref{Event_generator}. Nevertheless, one can still use this method by generating events with or without the cross section parametrization. In the absence of the parametrization, the generated events are flat in the four kinematic variables ($Q^2$, $-t$, $x_B$, $\phi$). The calculated coherent and incoherent acceptance ratios (R) with and without the cross section parametrization are shown in figure \ref{fig:accep_ratio_sys_uncer}. One can see that the difference between the calculated acceptance ratios is almost constant. Thus, we can conclude that the first method of taking $\pm$20$\%$ on R is is an adequate way to obtain an estimation of the systematic uncertainty associated to the calculated acceptance ratios.
\begin{figure}[h!]
\includegraphics[scale=0.34]{fig_results/coh_accp_ratio_phi.png}
\includegraphics[scale=0.34]{fig_results/incoh_accp_ratio_phi.png}
\caption{The coherent (on the top) and the incoherent (on the bottom) acceptance ratios ($R$) as function of the angle $\phi$. In both plots, the blue (red) points are the ratios with (without) the cross section parametrization.} 
\label{fig:accep_ratio_sys_uncer}
\end{figure}

\paragraph{Radiative corrections}
~\\

In this analysis, we have assumed that the beam-spin asymmetry arises from the leading twist DVCS amplitude and its interference with the BH process. However, there are higher-order electromagnetic corrections which can affect the beam-spin asymmetry. Andrei V. Afanasev and his collaborators have estimated the corrections to $A_{LU}$ which arise from such effects in a model-independent way \cite{Afanasev}. They have performed one-loop corrections on the outgoing electron as only the radiation from it affects the $A_{LU}$. They found that the correction does not exceed 0.1$\%$ at a 4.25 GeV electron beam energy and Q$^{2}$=1.25 GeV$^{2}$. In our case, as the radiative emission is inversely proportional to the mass of the radiating particle, the helium and the proton contributions are negligible compared to the leptonic one. Therefore, we can still take the result of Afanasev as a good estimation for the radiative  effects on our measured $A_{LU}$.\\

%\paragraph{Beam asymmetry}
%The injector of JLab produces electrons with positive and negative helicities in equal %time in principle. To ensure this equality between the two helicity configurations., %figure \ref{fig:beam_charge} shows the deposited charge ratio of the positive helicity %electrons to the negative ones in the individual runs. A 2$\%$  maximum deviation from %one. Thus, the integrated beam charge ratio induces 1.1$\%$ systematic uncertainty to %$A_{LU}$ on both DVCS channels.\\
%\begin{figure}[h!]
%\hspace{-0.3in}
%\includegraphics[scale=0.4]{fig_bsa/qplus_qminus_RunNum.png}
%\caption{The beam charge ratio between the positive and the negative helicites.} 
%\label{fig:beam_charge}

\paragraph{Systematic uncertainty summary}
~\\
~\\
The total systematic uncertainty is the quadratic sum of the previously described individual uncertainties. Table \ref{Table:systematic_uncertainties} summarizes the sources of systematic uncertainty and their contributions on the measured $A_{LU}$ at $\phi = 90^{\circ}$, that will be added quadratically to the statistical uncertainties on $A_{LU}$.

\begin {table}[!h]
\begin{center}
\begin{tabular}{|l|l|l|l|}
\hline
Systematic source &  Coherent channel  & Incoherent channel &Type of systematic 
error\\
\hline
DVCS cuts & ~~~~~8 $\%$ &  ~~~~~6 $\%$ & bin to bin\\
\hline
Data binning & ~~~~~5.1$\%$ & ~~~~~7.1$\%$ &bin to bin\\
\hline
Beam polarization &  ~~~~~3.5$\%$ &  ~~~~~3.5$\%$& Normalization\\
\hline
Acceptance ratio &  ~~~~~0.6$\%$ &  ~~~~~2.0$\%$ &bin to bin\\
\hline
%Beam charge asymmetry &  ~~~~~1.1$\%$&  ~~~~~1.1$\%$\\
%\hline
Radiative corrections &  ~~~~~0.1$\%$ & ~~~~~0.1$\%$ & bin to bin\\
\hline
\textbf{Total} &  ~~~~~\textbf{10.1}$\%$ &   ~~~~~\textbf{10.1}$\%$ &bin to 
bin\\
\hline
\end{tabular}
\caption{ The systematic uncertainties on the measured coherent and incoherent beam-spin asymmetries at $\phi = 90^{\circ}$.}
\label{Table:systematic_uncertainties}
\end{center}
\end{table}

### 2016-06-27 analysis-note-v2/data_analysis.tex
added the second version of the analysis note

\chapter{Particles reconstruction and simulation}
~~~~The final state of a coherent (incoherent) DVCS event consists of three particles: an electron, a $^4$He (a proton), and a real photon. To identify the DVCS events, we first identify, individually, the different particles of interest. Then, events with three detected final-state particles will be further filtered by imposing the energy-momentum conservation laws, as will be presented in the following chapter.\\

Even after imposing the conservation laws, the DVCS sample will not have 100$\%$ truly DVCS events. In our kinematical region, the main contamination to our DVCS channels comes from the electroproduction of neutral pions. For instance, in the coherent $\pi^0$-electroproduction, when one of the two-photon decay of the $\pi^{0}$ passes the DVCS requirements, it will be counted as a DVCS event. Thus, these events have to be subtracted before looking to any DVCS observable. For this purpose, we perform a technique in which we combine the measured exclusive $\pi^0$-electroproduction data sample with a Monte-Carlo simulation to evaluate the background in the selected DVCS sample. For this technique, we need to identify the experimental $\pi^0$s that come in the coherent and the incoherent $\pi^0$-electroproduction channels.\\

In this chapter, we presents the procedures carried out to identify the final-state particles of interest, the Monte-Carlo simulation we used, and the kinematic corrections we applied on the particles.

\section{Particles identification}

\subsection{Electron identification} \label{Electron_identification}
~~~~The electron detection triggers the data acquisition system to record data from all the sub-detectors of CLAS. In this analysis, a particle which passes the following set of criteria is assumed to be a good electron.

\paragraph{Initial requirements}

\begin{itemize}
\item Negative charge: the torus magnet generates a field which has mainly azimuthal components. Hence, the trajectory of a negative particle will be bent towards the beam line direction without changing azimuth. Consequently, information on its charge is accessible from the curvature of its trajectory.

\item $(DC_{stat}, EC_{stat}, SC_{stat}, CC_{stat}) > 0$: these status variables are linked to the number of hits and the thresholds in the different sub-detectors of CLAS. Thus, we select the electrons which have positive status in the different sub-detectors as a first step to reduce the noise in the data sample.

\item $stat$ > 0: this variable is positive if the trajectory of a particle passes the two steps of the tracking in the DCs, Hit-Based Tracking (HBT) and Time-Based Tracking (TBT).

\item Momentum cut ($p_{e^{-}}$ > 0.8 GeV/c): during the data acquisition, the 
   EC threshold was set to 200 $mV$ corresponding to electrons having a minimum 
   momentum of about 0.7 GeV/c. In this analysis, we apply a conservative cut 
   of 0.8 GeV/c to be above this threshold.

\item Vertex cut: the target is centered at -64 cm with respect to the center of CLAS. Figure \ref{fig:z_cut} shows the reconstructed z-vertices for the collected negative particles. One sees two sharp peaks corresponding to the two aluminum windows at the ends of the target. These particles have to be rejected as they originate from outside the target. As will be emphasized later, we need an accurate determination of the electron's vertex to ensure the correspondence between the final-state particles, which all have to originate from the same point.

\begin{figure}[tp]
\centering
\includegraphics[scale=0.43]{fig_analysis/Z_e.png}
\caption{The reconstructed longitudinal vertex of the collected negative particles. The two dashed red lines represent the chosen cut, -77 cm < $z_{vertex}$ < -50 cm, to eliminate the particles which originate from the windows and outside the target.} 
\label{fig:z_cut}
\end{figure}

\paragraph{Fiducial cuts}
~\\
~\\
~~~~Some regions of CLAS have to be excluded from the analysis to ensure an accurate detection of the different particles. For instance, an electron that hits the edge of the EC will have only part of its electromagnetic shower contained within the detector. Also, the structure of the torus magnet divides CLAS into six separate sectors, which makes edge effects non-negligible. For this reason, the following set of fiducial cuts is applied:

\begin{itemize}
\item EC fiducial cut: each EC has a triangular shape with its three sides labelled as U,V and W. We apply a set of cuts (60 cm < $U$, $V$ < 360 cm, $W$ < 390 cm) to reject the electrons which hit the EC close to the edges, as shown in figure \ref{fig:EC_cut}.
\begin{figure}[tbp]
\hspace{-0.2in}
%\includegraphics[scale=0.22]{fig_analysis/EC.png}
%\includegraphics[scale=0.28]{fig_analysis/el_u.png}
%\includegraphics[scale=0.28]{fig_analysis/el_v.png}
%\includegraphics[scale=0.28]{fig_analysis/el_w.png}
\includegraphics[scale=0.35]{fig_analysis/EC_XY_el_1.png}
\includegraphics[scale=0.35]{fig_analysis/EC_XY_el_2.png}
\caption{On the left: XY distribution for the negative particles in the EC before the $U$, $V$ and $W$ cuts. On the right: the same distribution is plotted after the cuts. $X$ and $Y$ are the coordinates in the EC with respect to the center of CLAS.} 
\label{fig:EC_cut}
\end{figure}

\begin{figure}[tbp]
\hspace{-0.2in}
\includegraphics[scale=0.35]{fig_analysis/CC_el_phi_theta_1.png}
\includegraphics[scale=0.35]{fig_analysis/CC_el_phi_theta_2.png}
\caption{Azimuthal angle as a function of polar angle for the negative particles before (left) and after (right) applying the CC fiducial cut. The angles are calculated with respect to the center of each sector in CLAS.} 
\label{fig:CC_cut}
\end{figure}

\item CC fiducial cut: in reference \cite{CCref}, G. Adams {\it et al.} have studied the efficiency of the CCs. They found that within the fiducial regions, which are defined by the edges of the CCs mirrors, the detection efficiency is stable and is around 98$\%$. Outside the fiducial regions, the efficiency shows strong variations. In reference \cite{Osipenko}, M. Osipenko {\it et al.} have developed a coordinate system to represent the CC hits with respect to the center of each sector in CLAS. In this frame, the CCs mirror edges can be defined as:\\
\begin{multline}  
\phi_{e}  = -63.32792 +11.05609\cdot \theta_{e} -0.6344957\cdot \theta^{2}_{e} +1.873895*10^{-2}\cdot \theta^{3}_{e} \\
- 2.762131*10^{-2}\cdot \theta^{4}_{e}+1.604035*10^{-2}\cdot \theta^{5}_{e}. ~~~~~~~~~~~~~~~~~~~~~~~~~
\end{multline}
Based on these works, we reject all the hits located outside the mirror edges. Figure \ref{fig:CC_cut} shows an illustration of this cut.

\item IC shadow cut: this cut originates from the location of the IC in front of the innermost part of the DCs. The electrons which are produced at polar angles lower than 14$^\circ$ will hit the IC. The left plot of figure \ref{fig:IC_cut} illustrates this effect, and the right plot shows the effect of the cut we apply.
\begin{figure}[tbp]
\hspace{-0.2in}
\includegraphics[scale=0.35]{fig_analysis/el_DC_IC_XY_1.png}
\includegraphics[scale=0.35]{fig_analysis/el_DC_IC_XY_2.png}
\caption{On the left: XY distribution for all the negative particles in the first region of the DC before applying the IC shadow cut. On the right: the same distribution after the cut.} 
\label{fig:IC_cut}
\end{figure}

\item DC fiducial cut: the DCs have low detection efficiency at the edges because only part of the tracks are detected \cite{DCref}. So we apply a fiducial cut to reject the particles at the edges. The left plot of figure \ref{fig:IC_cut} shows the XY distribution of all the negative particles in DC1. The result of applying the DC fiducial cut can be seen in figure \ref{fig:DC_cut}.  
\begin{figure}[tbp]
\centering
\includegraphics[scale=0.35]{fig_analysis/DC_el_2.png}
\caption{ XY distribution for all the negative particles in DC1 after applying the DC fiducial cut.} 
\label{fig:DC_cut}
\end{figure}

\end{itemize}

\paragraph{EC energy cuts}
~\\
~\\
~~~~The Minimum Ionizing particles (MIPs), such as pions, deposit constant 
amounts of energy per distance while traversing the EC.  In contrast, the 
showering particles, such as electrons and photons, deposit energies 
proportional to their momenta. We use two energy cuts to clean the electrons 
from the main contamination, i.e.  $\pi^{-}$s.
\begin{itemize}
\item Minimum deposited energy:
   the inner and the outer parts of the EC have thicknesses 15 cm and 24 cm, 
   respectively. The simulations show that pions deposit a constant energy 
   amount of 2 MeV/cm, independently of their momenta. Figure 
   \ref{fig:Einner_cut} shows the deposited energy in the outer part of the EC 
   (EC$_{out}$) as a function of the energy deposited in the inner part 
   (EC$_{in}$), after the fiducial cuts. On the x-axis, one can see a clear 
   region, around 30 MeV, that comes mainly from the negative pions, which 
   deposit 2 MeV/cm along the 15 cm thickness of the inner EC. We use a cut of 
   60 MeV on EC$_{in}$ to reject these particles.

\item An additional cut, correlating the measured deposited energy and the momentum, is applied. Figure \ref{fig:etot_p_cut} shows the ratio of the total deposited energy in the ECs (EC$_{tot}$ = EC$_{in}$ + EC$_{out}$) to the momentum ($p$) as a function of $p$. One notices that EC$_{tot}$/p varies slightly with the momentum due to variations in the efficiencies of the DC and EC. We apply 2.5$\sigma$ cuts around the mean ($\mu$) to select the good electrons, using to the following parametrizations of the mean ($\mu$) and the width ($\sigma$):
\begin{eqnarray}
\mu (p) = 0.256084 +0.0432374\cdot p -0.00914180\cdot p^{2} +0.00081589 \cdot p^{3} \\
\sigma (p) = 0.0572976 -0.0272689\cdot p +0.008576\cdot p^{2} -0.00097998\cdot p^{3}
\end{eqnarray}

\begin{figure}[tp]
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.3in}
\includegraphics[height=6.2cm]{fig_analysis/eco_eci.png}
\caption{Deposited energies in the EC: $E_{out}$ as a function of $E_{in}$. The dashed red line represents a 60 MeV cut on EC$_{in}$ to reject the $\pi^{-}$s. } 
\label{fig:Einner_cut}
\end{minipage} \hfill
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.2in}
\includegraphics[height=5.3cm]{fig_analysis/etot_p.png}
\caption{$E_{tot}/p$ as a function of $p$. The black dashed line represents the mean value of $E_{tot}/p$ as a function of $p$. The red dashed lines represent the $2.5 \sigma$ cuts. } 
\label{fig:etot_p_cut}
\end{minipage}
\end{figure}

\end{itemize}

\paragraph{CC cut}
~\\
~\\
~~~~The Cherenkov counters have been designed to separate electrons from pions below 2.5 GeV/c momentum. In this region, the pions are not supposed to produce photoelectrons. However, low momentum $\delta$-electrons can be produced from the diffusion of the pions in the Cherenkov gas. These $\delta$-electrons produce a small number of photoelectrons. Figure \ref{fig:Nphe_cut} shows the distributions of the number of photoelectrons ($nphe$) produced by the negative particles for three different stages of the electron selection. \\

One sees from figure \ref{fig:Nphe_cut} that the single-photoelectron peak is 
strongly reduced after applying the energy cuts. We conclude that the particles 
causing the single-photoelectrons peak are linked to particles with low 
deposited energy in the EC$_{in}$, figure \ref{fig:Einner_cut}. We apply a 
final cut on the red distribution in figure \ref{fig:Nphe_cut} ($nphe$~>~2), 
and we assume that the negative particles which pass all the previous 
requirements and produce more than 2 photoelectrons in the CC are good 
electrons.
\begin{figure}[tpb]
\centering
\includegraphics[height=7.0cm]{fig_analysis/nphe_all.png}
\caption{Distribution of number of photoelectrons emitted by negative particles 
in the CC ($nphe\cdot$10). The black curve represents the distribution after 
the initial cuts, the blue curve is after the geometrical cuts and the red 
curve is after applying all the cuts including the EC energy cuts. The dashed 
red line represents the cut we apply ($nphe$~>~2) to select the good 
electrons.} \label{fig:Nphe_cut}
\end{figure}

%\begin{figure}[tbp]
%\centering
%\includegraphics[height=6.8cm]{fig_analysis/e_phi_theta_4.png}
%\caption{$\phi$ vs. $\theta$ distribution of the selected electrons.}
%\label{fig:e_phi_theta_4}
%\end{figure}

\end{itemize}

\subsection{Proton identification}
~~~~Similarly to the electrons, the protons are affected by the geometry and the efficy of the different sub-detectors of CLAS. The following conditions are applied to select the good protons.
\begin{itemize}
\item Coincidence with one and only one good electron.

\item Initial track requirements: the positive charge of the proton results in bending its trajectory away from the beam line direction. Thus, a positive charge is required from the curvature of the track. Like for the electrons, the proton candidates must pass the two steps of the tracking in the DCs, have signal above the threshold in the SCs ($SC_{stat}$ > 0) and originate from a vertex within the target (-77 cm < $z_{vertex}$ < -50 cm).

\item Fiducial cuts: the tracks of the protons detected close to the edges of the DC can only be partially reconstructed. As for the electrons, the protons which are recoiled at polar angles smaller than 14$^{\circ}$ hit the IC. We apply the previously presented (in section \ref{Electron_identification}) DC and IC shadow fiducial cuts to avoid these effects. Figure \ref{fig:proton_DC_IC_cut} shows the XY projection in the DC1 for the collected positive particles which passed the initial track requirements, before and after these two fiducial cuts.
\begin{figure}[tp]
\hspace{-0.2in}
\includegraphics[scale=0.35]{fig_analysis/proton_DC_IC_XY_1.png}
\includegraphics[scale=0.35]{fig_analysis/proton_DC_IC_XY_3.png}
\caption{XY plane projection in DC1 for the positive particles before (left) and after (right) IC shadow and DC fiducial cuts.} 
\label{fig:proton_DC_IC_cut}
\end{figure}

\item Velocity ($\Delta \beta$) cut: the previous cuts do not separate the protons from other positive particles, such as positive pions and kaons. A very clear separation can be obtained by associating the information from the SCs and the DCs. The velocity of a charged particle can be calculated by using the momentum ($p$) reconstructed in the DCs and the Time-Of-Flight ($t_{TOF}$) measured by the SCs. We define:
\begin{equation}
\Delta \beta = \beta_{SC} - \beta_{DC} = \frac{l_{track}}{c \cdot t_{TOF}} - \frac{p}{\sqrt{p^{2} + m^{2}_{p}}}~,
\end{equation}
where $l_{track}$ is the measured track length and $m_{p}$ is the proton mass. On the left plot of figure \ref{fig:proton_delta_beta_cuts}, $\Delta \beta$ is plotted as function of momentum. One can see two main trends in this plot: the region around zero corresponds to the protons, while the one above corresponds to the positive pions ($\pi^{+}$). The right plot shows a one-dimensional distribution of $\Delta \beta$ zoomed in the region of the protons.
\begin{figure}[tbp]
\hspace{-0.2in}
\includegraphics[scale=0.36]{fig_analysis/prot_DeltaBeta_p.png}
\hspace{-0.2in}
\includegraphics[scale=0.36]{fig_analysis/prot_DeltaBeta.png}
\caption{On the left: $\Delta \beta$ as a function of $p$ for the detected positive particles after the fiducial cuts. On the right: one-dimensional distribution of $\Delta \beta$ zoomed in the region of the protons. The red dashed lines represent $\pm$3$\sigma$ cuts around the mean to select good reconstructed protons.} 
\label{fig:proton_delta_beta_cuts}
\end{figure}

\item Vertex matching:  the last cut is the correspondence between the longitudinal vertices of the detected electron and proton. Figure \ref{fig:proton_delta_z_e_prot} shows the difference $\Delta z = z_{e} - z_{p}$ and the chosen cuts (red dashed lines).
\end{itemize}
~~~~Finally, figure \ref{fig:prot_Theta_Phi} shows the azimuthal angle as a function of the polar angle distribution for the identified protons after all the selection cuts. One notices that the population of the protons is different from one sector to another, which comes from the dead regions in some sectors.
\vspace{-0.1in}

\begin{figure}[tbp]
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.3in}
\includegraphics[height=6.0cm]{fig_analysis/proton_delta_z_e_prot.png}
\caption{$\Delta z$ distribution. The red dashed lines indicate $\pm$3$\sigma$ cuts around the mean. } 
\label{fig:proton_delta_z_e_prot}
\end{minipage} \hfill
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.3in}
\includegraphics[height=6.0cm]{fig_analysis/prot_Theta_Phi_2.png}
\caption{$\phi$ vs. $\theta$ for the selected protons.}
\vspace{0.2in}
\label{fig:prot_Theta_Phi}
\end{minipage}
\end{figure}

\subsection{Photon identification}
~~~~CLAS is equipped with two calorimeters that can detect photons: the IC, covering polar angles from 4$^\circ$ to 14$^\circ$, and the EC, covering polar angles from 8$^\circ$ to 45$^\circ$. Like for the other particles, in addition to the coincidence with one good electron, we require a set of criteria to ensure the quality of the detected photons. Due to the efficiency constraints in both calorimeters, we restrict the energy of the selected photons to be greater than 300 MeV. Further requirements are applied depending on each detector.

\subsubsection*{EC photons}
A particle has to pass the following conditions in order to be considered a good photon:

\begin{itemize}
\item Neutral charge: this condition is achievable via the information from the drift chambers. A photon candidate in the EC must not be associated with a track in the DCs.

\item EC fiducial cut:  like for the electrons, this requirement is made to reject the photons which are detected at the edges of the EC. Figure \ref{fig:photons_EC_XY_photon_2.png} shows the XY plane distribution of EC neutral particles. We use the cuts: 100 cm < $U$, $V$ < 360 cm, and $W$ < 390 cm, to select the EC photons.

\item Velocity ($\beta$) cut: the scattered electron and its associated photon originate from the same vertex. Knowing the electron vertex ($\overrightarrow{V_{e}}$) and the photon hit position in the EC ($\overrightarrow{R_{\gamma}}$), one can calculate the photon velocity $\beta$ as:
\begin{equation}
\beta_{\gamma} = \frac{l}{ct} = \frac{|\overrightarrow{R_{\gamma}} - \overrightarrow{V_{e}}|}{c (t_{EC} - t_{trg})}
\end{equation}
where $l$ is the traveled distance from the vertex to the hit point in the EC. The traveling time ($t$) is calculable from the relative difference between the trigger time ($t_{trg}$) and the EC timing ($t_{EC}$). Figure \ref{fig:photons_beta_EC} shows the $\beta$ distribution of the neutral particles in the EC.
\end{itemize}
\begin{figure}[tp]
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.3in}
\includegraphics[height=6.0cm]{fig_analysis/photons_EC_XY_photon_2.png}
\caption{XY projection of the neutral particles in the EC. The coloured regions represent photons which passed the EC fiducial cuts, while the black regions are out of the fiducial cuts.} 
\label{fig:photons_EC_XY_photon_2.png}
\end{minipage} \hfill
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.5in}
\includegraphics[height=6.0cm]{fig_analysis/photons_beta_EC.png}
\caption{$\beta$ distribution of neutral particles in the EC. The two vertical lines represent $\pm$3$\sigma$ cuts around $\beta$~=~1 to select photons.}
\vspace{+0.3in}
\label{fig:photons_beta_EC}
\end{minipage}
\end{figure}

\subsubsection*{IC photons}
For IC photons, we use the following cuts:
\begin{itemize}
\item IC fiducial cuts: the photons which hit the edges of the IC deposit only part of their energies within the calorimeter. For this reason, we reject the photons which hit the innermost or the outermost rings of the IC. Figure \ref{fig:photons_IC_XY_2} illustrates this cut \cite{FX_thesis}.

\item M\o ller electrons reduction: a two-dimensional plot of photon polar angles as a function of the energy shows an overcrowded region at low $\theta$ and low energy. This can be seen in figure \ref{fig:photons_IC_theta_En_1}. This region is mostly populated by the M\o ller electrons and must be excluded from the analysis. We optimized a linear cut for this region, shown by the black dashed line. The vertical extension of this line shows the minimum energy cut ($E_{\gamma}$ > 300 MeV).
\item We do not apply any timing cut on the IC because its timing is not functionning properly for certain channels. Therefore, applying a timing cut would add inefficient regions in the detector that we wanted to avoid. Therefore, we rely mainly on exclusivity cuts to remove any potential contamination.

\end{itemize}
\begin{figure}[tbp]
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.4in}
\includegraphics[height=6.0cm]{fig_analysis/photons_IC_XY_2.png}
\caption{XY distribution for the IC photons. The photons which hit the black innermost and outer regions are excluded from this analysis.} 
\label{fig:photons_IC_XY_2}
\end{minipage} \hfill
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.4in}
\includegraphics[height=6.0cm]{fig_analysis/photons_IC_theta_En_1.png}
\caption{$\theta$ versus $E$ for the IC photons which passed the fiducial cuts. The black dashed line represents the cut to reject the M\o ller electrons.}
\label{fig:photons_IC_theta_En_1}
\end{minipage}
\end{figure}
To summarize the photon selection, the two-dimensional distribution of azimuthal angle as a function of polar angle for IC and EC photons is shown in figure \ref{fig:photon_phi_theta}. 
\begin{figure}[tbp]
\hspace{-0.2in}
\includegraphics[scale=0.35]{fig_analysis/photon_phi_theta_1.png}
\includegraphics[scale=0.35]{fig_analysis/photon_phi_theta_2.png}
\caption{On the left: $\phi$ versus $\theta$ for all the neutral particles before the cuts. On the right: $\phi$ vs. $\theta$ for the the selected photons.} 
\label{fig:photon_phi_theta}
\end{figure}

\subsection{Helium-4 identification}
~~~~Details on the RTPC's structure and the definition of the different 
variables were given in chapter 2, section 2. In the following, we show the 
cuts to select the RTPC good tracks with a 6-GeV beam energy. The distributions 
will be shown for the two independent modules of the RTPC separately, labelled 
as left and right sides. The cuts are:

\begin{itemize}
\item Coincidence with one and only one good electron.  
\item Number of active pads greater than 3: the track has to have recorded hits 
   from at least four different readout pads. Figure \ref{fig:padnb} shows the 
   distribution of the number of active pads as a function of the total 
   momentum measured in the RTPC for the identified good tracks using 6 GeV 
   electron beam energy.

   \begin{figure}[tbp]
      \centering
      \includegraphics[height=7.2cm]{fig_analysis/npd_p.png}
      \caption{The number of active pads versus the measured p for the good 
      tracks collected using 6 GeV electron beam energy.}
      \label{fig:padnb}
   \end{figure}

\item Positive radius of curvature.

\item Vertex cut: figure \ref{fig:rtpc_z} shows the z-vertices of the 
   positive-curvature tracks.

\item Track helix-fit quality: figure \ref{fig:rtpc_X2} shows the $\chi^{2}$ 
   distributions for the positive tracks originating within the RTPC. We apply 
   $\chi^{2}$~<~3.5 to select good $^4$He tracks.

\item $sdist$ and $edist$ cuts: figures \ref{fig:rtpc_sdist} and \ref{fig:rtpc_edist} show the $sdist$ and $edist$ distributions, for the positive tracks, originated within the RTPC, and having good $\chi^{2}$ values.

\item Z-vertex cut: like for the protons, the RTPC's reconstructed track has to originate from the same electron vertex. Figure \ref{fig:rtpc_delta_z} shows the difference between the $z$ of the reconstructed vertices of the electron and the associated RTPC tracks.

\item Fiducial cuts: Figure \ref{fig:rtpc_phi_theta} illustrates the effect of 
   the fiducial cuts we apply on the azimuthal angles.

\begin{figure}[tbp]
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.3in}
\includegraphics[height=6.0cm]{fig_analysis/rtpc_z.png}
\caption{ $z$-vertices for the reconstructed positive tracks with respect to 
the RTPC center (-64 cm with respect to the CLAS center), in the two modules of 
the RTPC. We chose the cut -80  mm < z < 80 mm to select good tracks.} 
\label{fig:rtpc_z}
\end{minipage} \hfill
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.3in}
\includegraphics[height=6.0cm]{fig_analysis/rtpc_X2.png}
\caption{$\chi^{2}$ distribution for the tracks in the two modules of the RTPC, with the cut we require to select good tracks: $\chi^{2}$ < 3.5.}
\vspace{0.5in}
\label{fig:rtpc_X2}
\end{minipage}
\end{figure}

\begin{figure}[tbp]
\vspace{-0.3in}
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.3in}
\includegraphics[height=6.0cm]{fig_analysis/rtpc_sdist.png}
\caption{$sdist$ distribution for the positive tracks in the RTPC. $|sdist|$~<~2.0 mm cut is applied to select good tracks.} 
\label{fig:rtpc_sdist}
\end{minipage} \hfill
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.3in}
\includegraphics[height=6.0cm]{fig_analysis/rtpc_edist.png}
\caption{$edist$ distribution for the positive tracks in the RTPC. We require $-1.0$~mm~<~$edist$~<~5.0 mm to select good tracks.}
\label{fig:rtpc_edist}
\end{minipage}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[scale=0.4]{fig_analysis/rtpc_delta_z.png}
\caption{The correspondence between the z-vertices of the detected electron and 
the good track in the RTPC. We require the absolute value of $\Delta z$ to be 
less than 20 mm.} \label{fig:rtpc_delta_z}
\end{figure}

\item In this work, due to the wide bands in dEdx distributions, we do not use 
   this quantity to select the recoil $^{4}He$ nuclei. We claim that the 
   kinematic exclusivity cuts, that are presented in chapter 4, are sufficient 
   to select coherent $^{4}He$ DVCS events. A systematic check about this question
   is presented in chapter 4.

\end{itemize}

\begin{figure}[tbp]
\hspace{-0.2in}
\includegraphics[scale=0.35]{fig_analysis/rtpc_phi_theta_1.png}
\includegraphics[scale=0.35]{fig_analysis/rtpc_phi_theta_2.png}
\caption{On the left: $\phi$ vs. $\theta$ for the positive-curvature tacks in the RTPC before the cuts. On the right: the same distribution after all the cuts.} 
\label{fig:rtpc_phi_theta}
\end{figure}

\subsection{$\pi^{0}$ identification}
~~~~In this analysis, we identify the $\pi^{0}$s with the goal of DVCS background subtraction as will be addressed in section \ref{Background_subtraction}. The $\pi^{0}$ identification is based on its two real photons decay mode ($\pi^{0} \rightarrow \gamma \gamma$), with a branching ratio around 98.8$\%$. In our experimental configuration, the reconstructed neutral pions can be categorized into three topologies: ICIC (the two photons are detected in the IC), ICEC (one photon in the IC and the second in the EC), and ECEC (the two photons are detected in the EC). The nominal mass of the $\pi^{0}$ is 0.135 GeV/c$^{2}$. The reconstructed invariant mass of the detected pair of photons can be seen in figure \ref{fig:pi0_selection}, for the three topologies. One can see clear peaks corresponding to the neutral pions in the three distributions.
\begin{figure}[tbp]
\hspace{-0.2in}
\includegraphics[scale=0.34]{fig_analysis/m_pi0_icic.png}
\hspace{-0.2in}
\includegraphics[scale=0.34]{fig_analysis/m_pi0_ecic.png}
\hspace*{-0.1in}
\includegraphics[scale=0.34]{fig_analysis/m_pi0_ecec.png}
\hspace{-0.2in}
\includegraphics[scale=0.38]{fig_analysis/sim_photon_phi_theta_2.png}
\caption{The reconstructed invariant mass of the photon pairs in the three topologies: ICIC, ECIC and ECEC. On the bottom-right: $\phi$ vs. $\theta$ distribution for the simulated DVCS photons, shown that most of the DVCS photons are located in the IC.} 
\label{fig:pi0_selection}
\end{figure}\\

One can conclude from the mean and sigma values of the distributions in figure \ref{fig:pi0_selection} that the IC has a better energy resolution than the EC. About 97$\%$ of the simulated DVCS events, as can be seen in the bottom-right plot, have the real photon emitted at very forward angles covered by IC. For these reasons, we chose to exclude the DVCS events which have their photons in the EC. Hence we are left with the two $\pi^{0}$ topologies, ICIC and ICEC, for the background subtraction as will be addressed later in this chapter.

\section{Simulation}
~~~~The Monte-Carlo simulation is used in this analysis for two goals: understanding the behaviour of the particles of interest in the detectors, and computing the acceptance for the DVCS background subtraction. The key stages of the simulation are summarized in figure \ref{fig:simulation_steps}: Monte-Carlo generated events pass in a GEANT3 simulation (GSIM) for the CLAS detector, then are processed with a package called GPP to add resolution and efficiency effects, and finally are reconstructed by a package named RECSIS, from which we obtain the physical quantities of each particle, like it is done for real data. In the following, each simulation stage will be briefly presented.
\begin{figure}[tbp]
\centering
\includegraphics[scale=0.25]{fig_simulation/simulation_steps.png}
\caption{ The scheme shows the main simulation steps.} 
\label{fig:simulation_steps}
\end{figure}

\subsection{Event generator} \label{Event_generator}
~~~~Events are generated in the measured ranges of $Q^{2}$, $x_{B}$, $t$, and 
$\phi$ following a parametrization of the cross section which roughly 
reproduces the DVCS and exclusive $\pi^{0}$ electroproduction data 
\cite{FX_thesis}:
\begin{equation}
\frac{d^{4}\sigma}{dQ^{2}dx_{B}dtd\phi} \propto \left(\frac{Q^{2}_{0}}{Q^{2}}\right)^{\alpha} *  \frac{1}{1 + (\frac{x_{B} - x_{c}}{c})^{2}} * \frac{1}{(1+bt)^{\beta}} * (1-d(1-cos(\phi)).
\label{equ:event_generator}
\end{equation}
This parametrization is the product of four factors which reproduce the DVCS and $\pi^{0}$,  characteristics as follows:
\begin{itemize}
\item the $Q^{2}$-dependent term accounts for the depth of the interaction: $Q^{2}_{0}$ is the minimum allowed value and the $\alpha$ is a parameter which controls the shape of the distribution.   
\item the $x_{B}$ term accounts for the dependence of the cross section on the parton distribution functions, with $x_{c}$ the mean value of the Bjorken variable $x_{B}$.
\item the $t$ term accounts for the t-dependence of the elastic form factors of the helium and of the proton, via the parameters $b$ and $\beta$.
\item the $\phi$ term accounts for the cross section dependence on this angle, via the parameter $d$. The DVCS and the BH have a different behaviour than the $\pi^{0}$ exclusive events. 
\end{itemize}

~~~~Table \ref{Table:event_generator_values} shows the values of the parameters used for the cross section parametrization of the four channels of interest: $e^{4}He\gamma$, $e^{4}He\pi^{0}$, $ep\gamma$, and $ep\pi^{0}$.

\begin {table}[tbp]
\begin{center}
\begin{tabular}{|l|l|l|l|l|}
\hline
Parameter & $e^{4}He\gamma$  & $e^{4}He\pi^{0}$ & $ep\gamma$  & $ep\pi^{0}$ \\
\hline
$Q^{2}_{0}$ & 1.0 $GeV^{2}$/c$^{2}$ & 1.0 $GeV^{2}$/c$^{2}$ & 1.0 $GeV^{2}$/c$^{2}$ & 1.0 $GeV^{2}$/c$^{2}$ \\
\hline
$\alpha$ & 2.5 & 3.0 & 1.5 & 1.5 \\
\hline
b & -11.0 $GeV^{2}$/c$^{2}$ & -8.8 $GeV^{2}$/c$^{2}$ & -1.408 $GeV^{2}$/c$^{2}$& -1.408 $GeV^{2}$/c$^{2}$\\
\hline
$\beta$ & 12.0 & 7.3 & 4.0 & 1.5\\
\hline
$x_{c}$ & 0.2 & 0.3 & 0.2 & 0.5\\
\hline
c & 0.2 & 0.3 & 0.2 & 0.5 \\
\hline
d & 0.4 & 0 & 0.4 & 0 \\
\hline
\end{tabular}
\caption{ Values of the parameters adapted in our event generator.}
\label{Table:event_generator_values}
\end{center}
\end{table}

~~~~Regarding the protons in $ep\gamma$ and $ep\pi^{0}$ channels, we apply the 
Fermi motion on the initial protons based on the parametrization of C. Ciofi 
degli Atii and S. Simula \cite{fermi_motion}. Figure \ref{fig:fermi_mom} shows 
the Fermi momentum distributions of the nucleons inside $^{4}He$, where we 
apply a cut on the high-momentum tail at 0.3 GeV/c, higher momentum should not 
contribute to the final DVCS sample because of our exclusive cuts presented in 
the following chapter.

\begin{figure}[tbp]
\centering
\includegraphics[scale=.55]{fig_analysis/fermi_momentum_dis.png}
\caption{ Fermi momentum distribution of the nucleons inside $^{4}He$, in 
$GeV/c$.} \label{fig:fermi_mom}
\end{figure}

\subsection{GSIM}
~~~~GSIM is a GEANT3-based simulation of the CLAS detector, developed by the CLAS collaboration \cite{GSIM}. This simulation takes into account all the experimental environment, such as the target's position, materials, and geometry, and also the various sub-detectors' materials and geometries, to reproduce the behaviour of particles traversing the detector. {\it Nota Bene} the reconstruction in the RTPC is not implemented in GSIM, however its material is present.

\subsection{GPP}
~~~~For the purpose of making the simulation more realistic, the output of GSIM is fed to the GSIM Post-Processing (GPP) package. This package applies resolution effects on the different measured quantities, and also reads efficiency maps to match the simulation to the real experiment. The resolutions are categorized into three groups, time, position, and energy resolution. In the following, we present the techniques used in this work to extract the smearing factors for the simulation.

\paragraph{SC time smearing}
~\\
~\\
~~~~The GPP takes a single factor to smear the time in a Gaussian form. Figure \ref{fig:SC_smearing_factors} shows an illustration of the time smearing effects, in which $\Delta \beta$ for the protons \\($\Delta \beta~=~\beta_{measured}~-~\beta_{calculated}$~) is compared for data and simulation. The chosen SC smearing factor is 2.1.

\paragraph{DCs position smearing}
~\\
~\\
~~~~The GPP uses three factors to smear the positions of the hits in the DCs, in a Gaussian form. These smearing factors are extracted from comparing simulation to data in terms of the Time-Based Tracking (TBT) residual distributions, i.e. the deviation of the hits in the DCs from the fitted track. Figure \ref{fig:DC_smearing_factors} shows the experimental, initial simulated, and smeared simulated residual distributions for the collected good electrons and protons. The extracted smearing factors are: ($a$, $b$, $c$) = (1.1, 0.85, 1.1), where the factor $a$ stands for smearing of DC1, $b$ for DC2, and $c$ for DC3. One can see the smearing effects by looking to the values of $\sigma$ from the fit in each Super-Layer (SL). We conclude that these factors match the simulation to the data.
\begin{figure}[tbp]
\hspace{-0.7in}
\includegraphics[scale=0.3]{fig_simulation/Exp_proton_delta_beta.png}
\hspace{-0.1in}
\includegraphics[scale=0.32]{fig_simulation/Sim_proton_delta_beta.png}
\centering
\includegraphics[scale=0.32]{fig_simulation/Sim_proton_delta_beta_smeared.png}
\caption{Illustration of the SC time smearing via the $\Delta \beta$ distributions for the protons. On the top left: $\Delta \beta$ distribution of the experimental data. On the top right: the simulated data without smearing. On the bottom: the simulated data after SC time smearing with a factor equal to 2.1.} 
\label{fig:SC_smearing_factors}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[scale=0.47]{fig_simulation/Ele_SL1.png}
\includegraphics[scale=0.47]{fig_simulation/Ele_SL3.png}
\includegraphics[scale=0.47]{fig_simulation/Ele_SL5.png}
\caption{Time-Based Tracking (TBT) residual distributions for the electrons and the protons in the first super-layer (top panel), the second super-layer (middle panel) and the third super-layer (bottom panel) of the experimental data (first column), of the simulation without GPP (second column), and the simulation with GPP DC-position smearing factors: 1.1, 0.85, and 1.1 for $a$, $b$, and $c$ respectively. } 
\label{fig:DC_smearing_factors}
\end{figure}

\paragraph{IC energy smearing}
~\\
~\\
~~~~An energy smearing for the IC photons is also needed. The GPP software uses three factors to perform this smearing: $ic\_a$, $ic\_b$, and $ic\_c$, where $ic\_a$ accounts for the smearing of the width of the noise around zero using a Gaussian, while $ic\_b$ and $ic\_c$ are the smearing factors for the ADC values, using Gaussians as well. Our parameters are: 0.008, 0.036, and 0.024 respectively. Figure \ref{fig:IC_smearing_factors} shows the effect of these smearing factors on the simulated invariant mass of the $\pi^{0}$. The associated experimental distribution can be seen on the top left plot of figure \ref{fig:pi0_selection}. One notices that the smeared width of the simulated distribution matches the measured experimental one.\\

\begin{figure}[tp]
\includegraphics[scale=0.32]{fig_simulation/m_pi0_sim_without_smearing.png}
\includegraphics[scale=0.32]{fig_simulation/m_pi0_sim_with_smearing.png}
\caption{The invariant mass of the Monte-Carlo simulated $\pi^{0}$ without IC energy smearing, on the left, and with smearing, on the right. } 
\label{fig:IC_smearing_factors}
\end{figure}

\subsection{RECSIS}

~~~~RECSIS is the reconstruction package of CLAS which is used for both data 
and simulation. The detector responses, in terms of ADCs and TDCs, are 
converted by RECSIS into physical meaningful physical quantities, such as 
momentum, using lookup tables. In this process, the thresholds on the different 
detectors (DCs, CCs, ECs, SCs, IC, and RTPC) are applied to filter the signals 
before the reconstruction procedures. After this reconstruction, the outputs of 
RECSIS for the experimental and the simulated events can be compared directly, 
as will be presented in the next section.

\subsection{RTPC fastmc}
~~~~All the sub-detectors of CLAS are implemented in the GSIM GEANT3 simulation, 
however the RTPC is only there as dead material. As it is a more recent detector
it has been fully simulated using a stand alone GEANT4 simulation. As a 
first step, we replace this RTPC's simulation by a fast Monte-Carlo (fastmc) 
package at the level of the event generator to make the simulated $^{4}He$ more 
realistic and matching the data. This fastmc smears the $^{4}He$ kinematics and 
applies the RTPC's acceptance. Regarding the smearing, the momentum, polar 
angle, azimuthal angle and z-vertex of the $^{4}He$ are smeared with Gaussians 
using the observed tracking resolutions of the RTPC (see chapter 2, section 3).  
For the acceptance, the fastmc:
\begin{itemize}
\item ensures that the $^{4}He$ track intersects the cathode and the gems of the RTPC.
\item removes the tracks which pass in the dead area between the two modules of the RTPC.
\item removes the track if it goes to the upstream end of the target's holder.
\item applies the RTPC's thresholds on the momentum and the polar angle.
\end{itemize}

The fastmc is applied to the Monte-Carlo generated 
$^{4}He$ for the channels $e^{4}He\gamma$ and $e^{4}He\pi^{0}$. The other 
particles are fed to GSIM through the previously mentioned 
simulation-reconstruction chain procedures.

\section{Kinematic Corrections}
~~~~~The simulation enables us to extract kinematic corrections for the different particles, by comparing the reconstructed physical quantities from the simulation to the initially generated ones. In general, the reconstructed azimuthal angles of all the particles are consistent with the generated ones, while the reconstructed polar angles and momenta show some deviations. Therefore, corrections are required. In the following, the electron and the proton corrections are applied on both data and simulation, while the simulated photons are corrected differently from the experimental ones, as will be explained and justified.

\subsection{Electrons}
~~~~The reconstructed kinematics of the simulated electrons are roughly consistent with the generated quantities, as can be seen in figure \ref{fig:electron_corrections}. Nevertheless, we extracted and applied corrections on the electrons to achieve a higher precision. The corrected polar angles and momenta take the form:
\begin{equation}
\theta_{corr.} = \frac{\theta_{rec.}}{f(\theta_{rec.})} ~~~~~~~ p_{corr.} = \frac{p_{rec.}}{f(p_{rec.})}
\label{equation:correcting_function}
\end{equation}  
where $f(\theta_{Rec.})$ and $f(p_{Rec.})$ are the functions shown, respectively, on the left and right plots of figure \ref{fig:electron_corrections}.
\begin{figure}[tbp]
\centering
\includegraphics[scale=0.41]{fig_simulation/before_electron_Rec_gen.png}
\caption{Electron corrections. On the left: The ratio of the reconstructed to the generated electron polar angles is plotted as a function of the reconstructed polar angle. The mean of the distribution is parametrized by the black curve. On the right: the momentum ratio ($Rec/Gen$) is plotted as a function of the reconstructed momentum and parametrized by the black curve .} 
\label{fig:electron_corrections}
\end{figure}

\subsection{Protons}
~~~~The same procedures for the extraction of the kinematic corrections of the electrons have been carried out for the protons. The results can be seen in figure \ref{fig:proton_corrections}. The corrected polar angles and momenta are obtained using equations \ref{equation:correcting_function} and the functions shown on each plot of figure \ref{fig:proton_corrections}. 
\begin{figure}[tp]
\centering
\includegraphics[scale=0.41]{fig_simulation/before_proton_Rec_gen.png}
\caption{Proton corrections. On the left: the reconstructed-generated polar angle ratio is plotted as a function of the reconstructed angle and fitted with the black curve. On the right: the momentum ratio is plotted as a function of the reconstructed momentum.} 
\label{fig:proton_corrections}
\end{figure}

\subsection{IC photons in simulation} 
~~~~The simulated IC photons shows non-negligible polar angle and energy deviations from the expected kinematics. This can be seen in figure \ref{fig:simulated_ic_corrections}. These deviations are almost systematic shifts, in which the polar angle deviation might be coming from badly defined geometrical values within GSIM. For these photons, we followed the same techniques of comparing the reconstructed quantities to the generated ones in order to extract the correction functions.\\

\begin{figure}[tbp]
\centering
\includegraphics[scale=0.41]{fig_simulation/before_gamma_Rec_gen.png}
\caption{Corrections for the simulated IC photons. On the left: the reconstructed-generated polar angle's ratio is plotted as a function of the reconstructed polar angles. On the right: the energy ratio is plotted.} 
\label{fig:simulated_ic_corrections}
\end{figure}

As an illustration of the corrections, figure \ref{fig:egamma_difference} shows the squared $e\gamma X$ missing mass distribution for the simulated $ep\gamma$ DVCS events before the corrections, on the left, and after the corrections, on the right. In this configuration, the missing particle is the proton, such that the expected mean value should be the mass squared of the proton ($0.938^{2} = 0.8798$). The right value is obtained after the corrections.

\begin{figure}[tp]
\centering
\includegraphics[scale=0.32]{fig_simulation/egamma_MM2_before_corrections.png}
\includegraphics[scale=0.32]{fig_simulation/egamma_MM2_after_corrections.png}
\caption{An illustration of the corrections in terms of the squared $e\gamma X$ missing mass distribution for the $ep\gamma$ simulated DVCS events. } 
\label{fig:egamma_difference}
\end{figure}

\subsection{IC photons in real data} ~~~~For the experimental IC photons, we 
used the reconstructed invariant mass of the $\pi^{0}$ in the ICIC topology to 
ensure the consistency of the IC calibration over the acceptance of the detecor 
and the experimental running time. In this investigation, we require each 
$\pi^{0}$ photon to have a minimum energy of 500 MeV in order to avoid low 
efficiency effects of the IC.

\subsubsection{Run-dependent energy correction}

In the CLAS-EG6 experiment, the reconstructed mass of the $\pi^{0}$ displays a linear dependence on the energy, as can be seen in figure \ref{fig:M_E_pi0_before_corrections}. In order to ensure the consistency of the calibration over time, we extracted this mass-energy dependence for the individual runs. Figure \ref{fig:ic_alpha_beta_fitting} shows the extracted slope ($\alpha$) and offset ($\beta$), from the linear fits of the mass versus the energy of $\pi^{0}$, as a function of run number. One notices a non-negligible variation over the experimental running period due to changes in the experimental conditions, such as changes in trigger requirements and beam position.\\

\begin{figure}[tbp]
\centering
\includegraphics[scale=0.25]{fig_simulation/M_E_pi0_before_corrections.png}
\caption{The invariant mass of the reconstructed $\pi^{0}$ as a function of its energy. The red line represents a linear fit.} 
\label{fig:M_E_pi0_before_corrections}
\end{figure}

\begin{figure}[tbp]
\centering
\includegraphics[scale=0.33]{fig_simulation/Alpha_RunNumber_before_corr.png}
\includegraphics[scale=0.33]{fig_simulation/Beta_RunNumber_before_corr.png}
\caption{The slope ($\alpha$) and the offset ($\beta$) from linear fits of M$_\pi^{0}$ vs. E$_\pi^{0}$, as a function of run number. The red lines represent the fitting functions.} 
\label{fig:ic_alpha_beta_fitting}
\end{figure}

 To extract energy corrections for IC photons, the two distributions of figure \ref{fig:ic_alpha_beta_fitting} have been parametrized by piecewise functions of the form:
\begin{equation}
\alpha (x) = c_{0} + c_{2} \left[ e^{-c_{3}(x - c_{1})} - e^{-c_{4}(x - c_{1})} \right],
\end{equation}
\begin{equation}
\beta (x) = p_{0} + p_{2} \left[ e^{-p_{3}(x - p_{1})} - e^{-p_{4}(x - p_{1})} \right],
\end{equation}
where the values of the parameters of $\alpha$ and $\beta$ can be found in Appendix \ref{App:AppendixA} (tables \ref{Table:ic_alpha_corrections} and \ref{Table:ic_beta_corrections} respectively). The requirement of a 500 MeV maximum difference between the two photons allows to assume that the two photons have approximately the same energy ($E_{\pi^{0}} = 2 E_{\gamma}$). Then, the correction take the form:
\begin{eqnarray}
\frac{E^{\pi^{0}}_{corr}}{M^{\pi^{0}}_{Theoretical} = 0.135 GeV} &=& \frac{E^{\pi^{0}}_{uncorr}}{M^{\pi^{0}}_{uncorr}}\\ 
\Longrightarrow
E^{\gamma}_{corr} &=& \frac{0.135*E^{\gamma}_{uncorr}}{\alpha(run)*2*E^{\gamma}_{uncorr} + \beta(run)}
\label{ic_corrrection_formula}
\end{eqnarray}
which takes as input the measured uncorrected photon energy ($E^{\gamma}_{uncorr}$), and the $\alpha$ and $\beta$ parameters, which depend on the run number. It then returns the corrected energy ($E^{\gamma}_{corr}$).\\

\subsubsection{Position correction}
~~~~Cluster position is reconstructed as a weighted average of its hits' positions.  Those hit positions are taken as the center of the front face of their corresponding crystal.  However, the energy deposition of the shower occurs at some depth into the crystal.  Due to the roughly focusing design of the calorimeter, this effect is negligible for photons originating from a vertex near the cystals' focal point.  However, for an extended target, and EG6 has the longest target used to date with this calorimeter, this effect is significant and a correction necessary.
%It is essentially a geometric projection effect.
%, and can be thought of as a coordinate transformation.

The focusing nature of this calorimeter allows us to treat this correction as only a shift in the radius of the cluster position, $\delta r$ (although other conventions could have been chosen, e.g.~only a shift in cluster $z$-position).  This is essentially a geometric projection effect, and it can be parameterized in terms of shower depth $d$, and the angle of the photon $\theta_\gamma$ with respect to that of the crystal's longitudinal axis, $\theta_C$:

\begin{equation}
  \delta r = \frac{d\sin(\theta_C-\theta_\gamma)}{\cos\theta_C}
  \label{eq:icDepthCorrection}
\end{equation}

Each photon's angle is calculated from its cluster's position ($x,y$) and the corresponding electron's $z$-vertex (or RTPC vertex in the case of EG6's neutral trigger).  The crystal angles are parameterized in terms of cluster position based on the calorimeter design drawings (where 78.3 cm is the focal length):

\begin{equation}
  \tan\theta_C=\frac{\sqrt{x^2+y^2}}{78.3\ \mathrm{cm}}
  \label{eq:cystalAngles}
\end{equation}

The shower depth parameter $d$ was treated as a free parameter and fit to the slope of $\sin(\theta_\gamma-\theta_C)$ versus $\cos\theta_C$, where $\delta r$ was determined by the PDG $\pi^0$ mass.  Energy-dependence of shower depth was investigated but empirically found to be insignificant.  The depth parameter was further tuned to minimize the $z$-dependence of the reconstructed $\pi^0$ mass peak, since $z$ is the most relevant reconstructed quantity least correlated with photon energy.

The resulting shower depth $d$ was estimated to be 5.56 cm in equation~\ref{eq:icDepthCorrection}.  The effect of this correction in terms of $z$-dependence is illustrated in figure~\ref{fig:ic_exp_correction_inv_mass_comp}.

\begin{figure}[tbp]
\centering
\includegraphics[width=8cm,height=6cm]{fig_analysis/NoDepthRunRadialE_finvMass_vz_pi0.png}
\includegraphics[width=8cm,height=6cm]{fig_analysis/NewDepthRunRadialE_finvMass_vz_pi0.png}
\caption{The measured fractional invariant mass of ICIC $\pi^{0}$ as a function of the electron $z$-vertex before (left) and after (right) cluster position corrections for shower depth.} 
\label{fig:ic_exp_correction_inv_mass_comp}
\end{figure}

\subsubsection{Radial-dependent energy correction}\label{sec:icraddepecorr}

After the previous corrections, we observed a remaining radial dependence of the reconstructed $\pi^{0}$ mass \cite{cristina}, where ``radial'' refers to the distance of the cluster from the beamline.  This can be seen in the left panel of figure \ref{fig:icRadiusEnergyData}.  
%We exhausted the possibilities of position corrections playing any role in this, and concluded this must be due 
This is most likely attributed to a systematic error in the original $\pi^0$-based gain calibration, which may not have fully accounted for correlations between crystals and the strong variation in rates with radius.  It is worth noting that this effect has also been observed in the eg1-dvcs experiment in $ep\gamma$ missing mass~\cite{eg1dvcs_photonenergy}.

\begin{figure}[tp]\centering
    \includegraphics[height=5.4cm]{fig_simulation/Mgg_radius_2plateau.png}
    \includegraphics[height=5.4cm]{fig_simulation/m_m0_pi0_radius_nathan.png}
    \caption{IC radial dependence of measured $\pi^0$ mass after all corrections prior to section~\ref{sec:icraddepecorr} (left).  Multidemesional dependence of $\pi^0$ mass on radius and energy for a subset of the data (right).\label{fig:icRadiusEnergyData}}
\end{figure}

To extract a correction for this behavior, photon pairs are selected with cluster radii differing by less than 1 cm and energies differing by less than 500 MeV.  Then the $\pi^0$ mass peak was fit in multidimensional bins of radius and energy.  The result was a clear linear dependence on energy within each radial bin; an example is shown in the right panel of figure~\ref{fig:icRadiusEnergyData}.  By fitting the linear energy-dependence for each radial bin, with results illustrated in figure~\ref{fig:icRadiusEnergySlopeOffset}, a correction function is derived:
\begin{equation}
E^{\gamma}_{final} = \frac{E^{\gamma}_{corr}}{2*S(r)*E^{\gamma}_{corr} + O(r)},
\end{equation}
where $S(r)$ and $O(r)$ are the fitted slope and offset, and $E_{corr}^\gamma$ is the output of equation~\ref{ic_corrrection_formula}.

\begin{figure}[tbp]\centering
\includegraphics[height=5.4cm]{fig_simulation/m_m0_pi0_slope.png}
\includegraphics[height=5.4cm]{fig_simulation/m_m0_pi0_offset.png}
\caption{The slope (left) and offset (right) resulting from the linear fits of the distributions in figure~\ref{fig:icRadiusEnergyData}.  Note that fiducial cuts naturally reject radii below 4.3 cm and above 14.5 cm.}% These figures are from \cite{cristina}.}
\label{fig:icRadiusEnergySlopeOffset}
\end{figure}

\subsubsection{IC Correction Summary}
These corrections for IC photons in real EG6 data have been implemented in pass2 reconstruction in \texttt{\$CLAS\_PACK/icf/eg6iccorr.c} and have been applied to the \texttt{ICPB} bank and used in this analysis.

By construction they put the measured $\pi^0$ mass at 135 MeV over all 
kinematics and detector acceptance.  But large improvements are also seen in 
exclusive DVCS analyses, both coherent and incoherent. Their missing energy 
distributions are shown in Figure \ref{fig:ic_exp_correction_dvcs_comp} before 
and after these $\pi^0$-based IC photon energy corrections. One sees that 
correcting few percent deviations of $\pi^{0}$ mass from the true mass caused 
few hundreds MeV shifts in missing energy of the DVCS events. This large shift 
in missing energy is due to the fact that the corrections are measured in the 
range of $E_\gamma$ available in the IC from $\pi^0\to\gamma\gamma$ decays, 
which is about 0.8 to 2.5 GeV. To apply the correction on a photon, its radius 
is used to get the linear energy dependence, and then that is extrapolated to 
the measured energy of the photon.  For the DVCS photons, this goes well above 
the measured range of photon energies used to derive these corrections, energy 
range is about 2 to 5 GeV.

\begin{figure}[tp]
\centering
\includegraphics[scale=0.30]{fig_simulation/Coh_e4Hegamma_E_Mis.png}
\includegraphics[scale=0.30]{fig_simulation/InCoh_epgamma_E_Mis.png}
\caption{The distributions in black are without the IC photon corrections and in red with the corrections. On the left: the missing energy distribution of $e^{4}He\gamma$ DVCS events for data. On the right: the missing energy distribution of $ep\gamma$ DVCS events for data.} 
\label{fig:ic_exp_correction_dvcs_comp}
\end{figure}

### 2016-06-27 analysis-note-v2/experimental_setup.tex
added the second version of the analysis note

\section{EG6 experimental setup}
The experiment described in this note has been carried out in the Hall B of 
the Thomas Jefferson National Accelerator Facility (JLab), Virginia, USA. Hall 
B houses the CEBAF Large Acceptance Spectrometer (CLAS). Our experiment was 
performed in 2009 with a longitudinally-polarized electron beam of 6.064 GeV 
scattering onto a 6 $atm$ gaseous $^{4}He$ target to study the nuclear medium 
modifications of parton distributions using the DVCS off the target.

\subsection{CLAS detector} To ensure the exclusivity of our reaction, the basic 
setup of CLAS was upgraded with a Radial Time Projection Chamber (RTPC) to 
detect the low-energy recoil nuclei, an additional calorimeter (IC) to 
detect the energetic forward-emitted real photons and a solenoid magnet to 
minimize the effects of M\o ller electrons. In the following subsections, we rapidly 
present the sub-detectors previously used by the collaboration,
the RTPC design and calibration are detailed in the next chapter.

\subsection{Inner calorimeter}
In the basic setup of CLAS, the photons are detected by the forward 
electromagnetic calorimeters (EC) which cover polar angles from 8$^{\circ}$ to 
45$^{\circ}$. With a 6 GeV electron beam, a large part of the DVCS photons are 
produced at polar angles below 15$^{\circ}$, where the acceptance of the EC
is small. In the CLAS-E1DVCS experiment 
(2005), CLAS was upgraded with the addition of an Inner Calorimeter (IC). This 
calorimeter covers completely the polar angles between 5$^{\circ}$ and 15$^{\circ}$. Figure 
\ref{fig:CLAS_RTPC_2} shows a schematic plot of our experimental setup. The front face of the IC is facing the downstream side of 
the Radial TPC (RTPC) and placed at 16 cm from the center of CLAS.\\

\begin{figure}[tp]
\centering
%\vspace{-0.28in}
\includegraphics[scale=0.54]{fig/clas_rtpc_3.png}
\caption{The CLAS-EG6 experimental setup in the y-z plane. The basic apparatus of CLAS is shown in the right top plot, a zoom on the IC is shown on the bottom plot, and a photo of the RTPC and the target are shown in the left top plot. The RTPC is surrounded by a solenoid (in blue).} 
\label{fig:CLAS_RTPC_2}
\end{figure}

The IC is constructed from 424 lead-tungstate (PbWO$_{4}$) crystals. Each 
crystal is 16 cm long (corresponding to 17 radiation lengths) with a 
1.33~$\times$~1.33 cm$^2$ front surface and a 1.6~$\times$~1.6 cm$^2$ back 
surface. The energy resolution is around 3$\%$ for photon energies between 2 
GeV and 5 GeV and the angular resolution is between 3 to 5 mrad for the same 
energy range \cite{Hyon-suk}.

\subsection{Solenoid}
At occupancies greater than 4$\%$, the efficiency of the drift chambers 
starts to drop and the resolution gets worse. The first region of the DCs (R1) 
has a higher occupancy than the other two regions (R2 and R3), mostly due to 
noise. This noise mainly comes from the M\o ller electrons, which are 
low-energy electrons produced in the scattering of the electron beam on the 
target's electrons. To reduce the effect of the noise, CLAS was upgraded by 
adding a solenoid that surrounds the target. The magnet provides a nominal 
field of 4.5 T at the center of the target. This solenoid deflects the produced 
M\o ller electrons to very forward angles preventing them from arriving to the 
drift chamber, the IC or the RTPC. Figure \ref{fig:solenoid} shows a GEANT3 simulation of the 
M\o ller electrons tracks without applying the solenoid field (left), and how 
these electrons are bent to low polar angles, less than 4$^{\circ}$, when the 
solenoid field is applied.\\

\begin{figure}[tp]
\centering
\includegraphics[scale=0.36]{fig/solenoid.png}
\caption{The tracks of the produced M\o ller electrons (in red) without 
applying the solenoid field (left) and with it (right) 
\cite{Hyon-suk}. } \label{fig:solenoid}
\end{figure}

\subsection{Run conditions}

Table \ref{table:eg6_char} summarizes the different beam energies used during 
the experimental run CLAS-EG6 with the details about the beam, the torus, and 
the solenoid currents.

\begin{table}[!h]
   \centering
   \begin{center}
      \begin{tabular}{|l|l|l|l|}
         \hline
         beam energy [GeV] & Beam current [nA] & Torus current [A] & Solenoid 
         current [A] \\ \hline
         1.204 & 150 & 2100 & 450 \\
         \hline
         5.7  & 100 & 1900 & 450 \\
         \hline
         6.064 & 120-150 & 2100 & 450\\
         \hline
         1.269  & 100 & 1900 & 450\\
         \hline
      \end{tabular}
      \caption{The different beam energies used during the experimental run 
      period CLAS-EG6 with the currents in the beam, torus, and the solenoid. }
      \label{table:eg6_char}
   \end{center}
\end{table}

### 2016-06-27 analysis-note-v2/ref.tex
added the second version of the analysis note

\bibliographystyle{unsrt}
\begin{thebibliography}{99}

% nuclear DVCS

\bibitem{M_Polyakov}
M. V. Polyakov, Generalized parton distributions and strong forces inside nucleons and nuclei, Phys. Lett. B 555, 57-62, 2003.

\bibitem{EMC_simonetta}
S. Liuti and K. Taneja, Nuclear Medium Modifications of Hadrons from Generalized Parton Distributions, Phys. Rev. C 72, 034902; arXiv:0504027v2 [hep-ph], 2005.

\bibitem{Kir}
A. Kirchner and D. M{\"u}ller, Deeply virtual Compton scattering off nuclei, Eur. Phys. J. C32, 347-375, 2003.

\bibitem{BM_2009}
A. V. Belitsky and D. M{\"u}ller, Refined analysis of photon leptoproduction 
off spinless target, Phys. Rev. D79, 014017; arXiv:0809.2890 [hep-ph], 2009.

\bibitem{Van}
M. Vanderhaeghen, Gauge invariance of DVCS off an arbitrary spin hadron: the deuteron target case, Eur. Phys. J. A 8, 455, 2000.

\bibitem{simonetta_pre}
S. Liuti, Exploring the transverse partonic structure of nuclei, Workshop on Hard Processes in Nuclei, ECT*, Trento, June 8-12, 2015.

\bibitem{He_4_FF_Frosch}
R. F. Frosch et al., Structure of the He-4 Nucleus from Elastic Electron Scattering, Phys. Rev. 160, 874, 1967.

\bibitem{He_4_FF}
A. Camsonne et al. (Jefferson Lab Hall A Collaboration), JLab Measurement of the $^4$He Charge Form Factor at Large Momentum Transfers, Phys. Rev. Lett. 112, 132503, 2014.

\bibitem{proposal}
K. Hafidi et al., Deeply virtual Comton scattering off $^4He$, JLab proposal to PAC 33, 2007.

\bibitem{EMC_vadim_1}
V. Guzey and M. Strikman, DVCS on spinless nuclear targets in impulse approximation, Phys. Rev. C 68, 015204; arXiv:0301216 [hep-ph], 2003.

\bibitem{EMC_vadim_3}
V. Guzey, Neutron contribution to nuclear DVCS asymmetries, Phys. Rev. C 78, 025211; arXiv: 0801.3235 [nucl-th], 2008.

\bibitem{free_proton_GPDs}
I. V. Musatov and A. V. Radyushkin, Evolution and models for skewed parton distributions, Phys. Rev. D 61, 074027, 2000

\bibitem{guidal_2}
M. Guidal et al., Generalized Parton Distributions in the valence region from Deeply Virtual Compton Scattering, arXiv:1303.6600v1 [hep-ph], 2013.

\bibitem{EMC_vadim_2}
V. Guzey, A.W. Thomas and K. Tsushima, Medium modifications of the bound nucleon GPDs and incoherent DVCS on nuclear targets, Phys. Lett. B 673, 9-14; arXiv:0806.3288 [nucl-th], 2009.

\bibitem{QMC}
D. H. Lu et al., In-medium electron-nucleon scattering, Phys. Lett. B 417, 217, 1998.

\bibitem{simonetta_2}
S. Liuti and K. Taneja, Microscopic Description of Deeply Virtual Compton Scattering off Spin-0 Nuclei, Phys.Rev. C 72, 032201; arXiv:0505123v1 [hep-ph], 2005.

\bibitem{He4_DIS_data}
J. Gomez et al., Measurement of the A-dependence of deep inelastic electron
scattering. Phys. Rev. D 49, 4348-4372, 1994.

\bibitem{HERMES_BSA}
A. Airapetian et al. (HERMES Collaboration), Nuclear-mass dependence of beam-helicity and beam-charge azimuthal asymmetries in DVCS, Phys. Rev. C 81, 035202, 2010.

\bibitem{CLASref}
B.A. Mecking et al., The CEBAF large acceptance spectrometer, Nucl. Inst. and Meth. A 503, 513-553, 2003.

\bibitem{DCref}
M.D. Mestayer et al., The CLAS drift chamber System, Nucl. Inst. and Meth. A 449, 81, 2000.

\bibitem{CCref}
G. Adams et al., The CLAS Cerenkov detector, Nucl. Inst. and Meth. A 465, 414, 2001.

\bibitem{TOFref}
   E.S. Smith et al., The time-of-flight system for CLAS, Nucl. Inst. and Meth.  
   A 432, 265, 1999.

\bibitem{ECref}
   M. Amarian et al., The CLAS forward electromagnetic calorimeter, Nucl. Inst.  
   and Meth. A 460, 239, 2001.

\bibitem{Hyon-suk}
Hyon-Suk Jo, Etude de la Diffusion Compton Profond{\'e}ment Virtuelle Sur le Nucl{\'e}on avec le D{\'e}tecteur CLAS de Jefferson Lab: Mesure des Sections Efficaces polaris{\'e}es et non polaris{\'e}es, IPNO-Thesis, 2007.

\bibitem{BONUS}
S. Tkachenko et al., Measurement of the nearly free neutron structure function using spectator tagging in inelastic $^{2}H(e,e'p)X$ scattering with CLAS, Phys. Rev. C 89, 045206, 2014.

\bibitem{DME}
The PubChem Project. USA: National Center for Biotechnology Information, dimethyl ether - PubChem Public Chemical Database,  \url{http://pubchem.ncbi.nlm.nih.gov/compound/8254}.

\bibitem{BONUS_2}
N. Baillie et al., BoNus Experiment Analysis Note, CLAS internal analysis note, 
\url{https://www.jlab.org/Hall-B/secure/bonus/publication/BonusAnal110117.pdf}

\bibitem{GEM_holes}
J. Beringer et al. (Particle Data Group), Particle detectors at accelerators, Phys. Rev. D 86, 010001, pages: 339-368, 2012.

\bibitem{MAGBOLTZ}
S. Biagi, Monte Carlo simulation of electron drift and diffusion in counting gases under the influence of electric and magnetic fields, Nucl. Inst. and Meth. in Phy. Res. A 421, pp. 234-240, 1999.

\bibitem{NATHAN}
N. Baltzell, New TPC Noise Reduction, \url{https://clasweb.jlab.org/rungroups/lowq/wiki/index.php/New_TPC_Noise_Reduction}

\bibitem{Osipenko}
M. Osipenko et al., Matching between the electron candidate track and the Cherenkov counter hit, CLAS-NOTE-020, 2004.

\bibitem{bethe_block}
J. Beringer et al. (Particle Data Group), Electronic energy loss by heavy particles, Phys. Rev. D 86, 010001, 2012.

\bibitem{FX_thesis}
F.X. Girod, Diffusion Compton profond{\'e}ment virtuelle avec le d{\'e}tecteur CLAS pour une {\'e}tude des distributions de partons g{\'e}n{\'e}ralis{\'e}es, Ph.D-Thesis, 2006.

\bibitem{fermi_motion}
C.Ciofi degli Atti and S.Simula, Realistic model of the nucleon spectral 
function in few- and many-nucleon systems, Phys. Rev. C 53, 1689.

\bibitem{GSIM}
CLAS collaboration, CLAS GEANT3 simulation,  \url{http://nuclear.unh.edu/~maurik/gsim_info.shtml}.

\bibitem{yohann}
Y. Perrin, Etude de la structure partonique du noyau d'h$\'e$lium, Ph.D thesis, 2012.

\bibitem{cristina}
C. Moody and N. Baltzell, IC depth corrections for CLAS-EG6 experiment,  \url{https://clasweb.jlab.org/rungroups/lowq/wiki/index.php/IC_Depth_Correction_Investigation_Creating_a_new_depth_correction
}.

\bibitem{FX_BSA}
F.X. Girod et al. (CLAS Collaboration), Measurement of Deeply Virtual Compton Scattering Beam-Spin Asymmetries, Phys. Rev. Lett. 100, 162002, 2008.

\bibitem{CLAS_cross_section}
H.S. Jo et al. (CLAS Collaboration), Cross sections for the exclusive photon electroproduction on the proton and Generalized Parton Distributions, arXiv:1504.02009v1 [hep-ex], 2015.

\bibitem{Baptiste}
B. Guegan, Study of Generalized Parton Distributions and Deeply Virtual Compton Scattering on the nucleon with the CLAS and CLAS12, Ph.D-thesis, 2013.

\bibitem{Niki}
N. Saylor, A Measurement of Unpolarized Cross Sections and Polarized Cross Section Differences of Deeply Virtual Compton Scattering on the Proton at Jefferson Laboratory using CLAS, Ph.D-thesis, 2013.

\bibitem{hallb_polarimeter}
J. M. Grames et al., Unique electron polarimeter analyzing power comparison and precision spin-based energy measurement, Phys. Rev. Spec. Topics - Accelerators and Beams, Vol.7 , 042802, 2004.

\bibitem{Afanasev}
A.V. Afanasev, M.I. Konchatnij and N.P. Merenkov, Single-spin asymmetries in the Bethe-Heitler process $e^{-} + p \rightarrow  e^{-} + \gamma + p$ from QED radiative corrections, J. of Exp. and Theo. Phys. 102(2), 220-233, 2006.

\bibitem{EMC_vadim_4}
Private communication with V. Guzey based on his model presented in \cite{EMC_vadim_3}.

\bibitem{eg1dvcs_photonenergy}
EG1-DVCS TN027, \url{https://clasweb.jlab.org/rungroups/eg1-dvcs/wiki/index.php/Technical_Notes}.

\bibitem{eg6beamoffset}
RTPC Alignment Calibration for EG6, CLAS-NOTE 2013-007, \url{https://misportal.jlab.org/ul/Physics/Hall-B/clas/viewFile.cfm/2013-007.pdf?documentId=705}.

\bibitem{eg6tpcoffset}
Beam XY-Position at the Target for CLAS/EG6, CLAS-NOTE 2013-008, \url{https://misportal.jlab.org/ul/Physics/Hall-B/clas/viewFile.cfm/2013-008.pdf?documentId=711}.

\bibitem{FX_analysis_note}
F.X. Girod et al. (CLAS Collaboration), Measurement of Deeply Virtual Compton Scattering Beam-Spin Asymmetries, CLAS Note, 2007-026, 2007.

\end{thebibliography}

### 2016-06-27 analysis-note-v2/results.tex
added the second version of the analysis note

\chapter{Results and physics interpretations}
~~~~In this chapter, we present our results after all corrections discussed above and including
all systematic errors. In order to discuss these results, we first present the functional forms
we will use to fit them, which are different for the coherent and incoherent 
channels. For the coherent channel, we use exact formula from \cite{FX_BSA} to 
extract the real and imaginary parts
of the CFF $\mathcal{H}_{A}$ at twist-2. For the incoherent channel, we use a simplified form 
and only extract the asymmetry at $90^{\circ}$. Then we present the beam-spin asymmetry 
measurements for both DVCS channels with their aforementioned fits and draw some first 
conclusions. Finally we present ratios of our asymmetry to free proton results 
from CLAS (E1-DVCS part-1 \cite{FX_BSA, FX_analysis_note}).

\section{Fitting the beam-spin asymmetry} \label{Beam-Spin}
~~~~For a spin-zero target at leading twist, the beam-spin asymmetry ($A_{LU}$) 
can be expressed as follow \cite{BM_2009}
\begin{equation}
A_{LU}(\phi) = \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( 
\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
\label{eq:A_LU-coh}
\end{equation}
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the CFF $\mathcal{H}_{A}$ associated to the GPD $H_A$. The 
$\alpha_{i}$'s are $\phi$-dependent kinematical factors that depend on the 
nuclear form factor $F_A$ and the independent variables $Q^2$, $x_{B}$ and $t$.  
These factors are simplified as:

\small
\begin{eqnarray}
   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S{++}(1) \sin(\phi)\\
    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
C_{++}(1) cos(\phi) \right)\\
\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2}
\end{eqnarray}
\normalsize

Where $S{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
leptonic tensor. Their explicit expressions can be found in Appendix 
\ref{app:Helium_cross_section}.\\

Using the $\alpha_{i}$ factors, one can obtain in a model-independent way $\Im
m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ from fitting the experimental 
$A_{LU}$ as a function of $\phi$ for given values of $Q^2$, $x_B$ and $t$.  
Equation \ref{eq:A_LU-coh} is the functional form we use to fit the coherent asymmetries 
presented in this analysis.

Regarding the incoherent channel, the beam-spin 
asymmetry signals will be fitted by the simple form $\frac{\alpha \sin(\phi)}{1 + 
\beta \cos(\phi)}$, which has been used for DVCS on free proton, see reference 
\cite{FX_BSA, FX_analysis_note}, and allows an easy extraction of 
$A^{90^{\circ}}_{LU}$.

\section{Beam-spin asymmetry results and fit}
~~~~In this section, the beam-spin asymmetries will be compared to the theoretical calculations based on the two models that were presented in section \ref{Theoretical_hypotheses}.\\

\subsection{Coherent beam-spin asymmetry}
~~~~Figure \ref{fig:bsa_coh_Q2_bins} shows the coherent $A_{LU}$ for the three 
sets of two-dimensional bins. The asymmetries are fitted with the form of
equation \ref{eq:A_LU-coh}, where the real and the imaginary part of the CFF 
$\mathcal{H}_{A}$ are the free parameters in the fit.\\

\begin{figure}[tpb]
\centering
\includegraphics[scale=0.42]{fig_ch5/coh_alu_Q2_phi.png} 
\includegraphics[scale=0.42]{fig_ch5/coh_alu_xB_phi.png}
\includegraphics[scale=0.42]{fig_ch5/coh_alu_t_phi.png}
\caption{The coherent $A_{LU}$ as a function of $\phi$ and $Q^2$ (top panel), 
   $x_{B}$ (middle panel), and $-t$~(bottom panel) bins. The blue error bars 
   represent the statistical and the systematic uncertainties, added 
quadratically, shown on the top of green error bars representing only the 
statistical uncertainties. The brown bands represent the full systematic 
uncertainties, including the normalisation systematic uncertainties. The red 
curves represent fits in the form of equation \ref{eq:A_LU-coh}.}
\label{fig:bsa_coh_Q2_bins}
\end{figure}

Figure \ref{fig:coh_Q2_xB_t_ALU} shows the $Q^2$, $x_{B}$, and $-t$-dependencies of the $\alpha$ term of $A_{LU}$. The $x_{B}$ and $-t$-dependencies are compared to theoretical calculations performed by S. Liuti and K. Taneja. Their model relies on the impulse approximation and uses advanced spectral function of the nuclei to calculate the nuclear GPDs and then the observables. The calculations were carried out at slightly different kinematics than ours but provide already some guidance. The experimental results appear to have larger asymmetries compared to the calculations. These differences may arise from nuclear effects which are not taken into account in the model, such as long-range interactions \cite{simonetta_2}. Our measurements also agree with those of HERMES, considering their large uncertainties. \\

\begin{figure}[tpb]
\centering
\includegraphics[scale=0.37]{fig_ch5/coh_alu_Q2_90.png} \\
\includegraphics[scale=0.37]{fig_ch5/coh_alu_xB_90.png} \\
\includegraphics[scale=0.37]{fig_ch5/coh_alu_t_90.png} 
\caption{The $Q^{2}$-dependence (on the top), the $x_{B}$-dependence (on the 
   middle), and the $t$-dependence~(on the bottom) of the fitted coherent 
   $A_{LU}$ signals at $\phi$= 90$^{\circ}$ (black squares). On the middle: the red and the 
   blue curves are theoretical predictions from \cite{simonetta_2} at two 
values of $-t$. On the bottom: the green circles are the HERMES $-A_{LU}$ 
(positron beam was used) inclusive measurements \cite{HERMES_BSA}, and the 
colored curves represent theoretical predictions from \cite{simonetta_2}.} 
\label{fig:coh_Q2_xB_t_ALU}
\end{figure}

\subsection{Incoherent beam-spin asymmetry}
~~~~Figure \ref{fig:bsa_incoh_bins} shows our measured incoherent beam-spin 
asymmetries, for the three sets of the two-dimensional bins as for the coherent 
channel. The $Q^2$, $x_{B}$, and $-t$-dependencies of $A_{LU}$ at 
$\phi$=~90$^{\circ}$ (the $\alpha$ parameter of the fit) are shown in figure 
\ref{fig:incoh_Q2_xB_t_ALU}.\\

The theoretical calculations from S. Liuti and K. Taneja are carried out at slightly different kinematics than our experimental measured values. Nevertheless, one can see that our incoherent asymmetries are not well described by these calculations. For instance, in the top right plot of figure \ref{fig:incoh_Q2_xB_t_ALU}, even though our asymmetries (at $-t$~=~0.2~GeV$^2$/c$^2$) are located between the model's predictions, which are carried out at $-t$~=~0.095 and 0.329~GeV$^2$/c$^2$, they do not show the drop in $<x_B>$, as the model predicted. Similar observation can be seen as a function of $-t$ from the bottom plot.

\begin{figure}[tpb]
\includegraphics[scale=0.40]{fig_ch5/incoh_alu_Q2_phi.png}
\includegraphics[scale=0.40]{fig_ch5/incoh_alu_xB_phi.png}
\includegraphics[scale=0.40]{fig_ch5/incoh_alu_t_phi.png}
\caption{The incoherent $A_{LU}$ as a function of the angle $\phi$ in $Q^2$, 
   $x_B$, and $-t$ bins, respectively from top to bottom. See the caption of 
figure \ref{fig:bsa_coh_Q2_bins} for the color indications. The red lines 
represent fits to the $\frac{\alpha \sin(\phi)}{1 + \beta cos(\phi)}$ function.  
} \label{fig:bsa_incoh_bins}
\end{figure}

\begin{figure}[tpb]
\centering
\vspace{-0.2in}
\includegraphics[scale=0.37]{fig_ch5/incoh_alu_Q2_90.png} \\
\vspace{-0.1in}
\includegraphics[scale=0.37]{fig_ch5/incoh_alu_xB_90.png}\\ 
\vspace{-0.1in}
\includegraphics[scale=0.37]{fig_ch5/incoh_alu_t_90.png} 
\caption{The $Q^{2}$ 
   (top), $x_{B}$ (middle), and $-t$-dependencies (bottom) 
   of the incoherent $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). Middle panel: 
   the red and the blue curves are theoretical calculations from 
   \cite{simonetta_2}. On the bottom: the green circles are the HERMES 
$-A_{LU}$ (positron beam was used) inclusive measurements \cite{HERMES_BSA}, 
the colored curves represent theoretical calculations from \cite{simonetta_2}.  
} \label{fig:incoh_Q2_xB_t_ALU}
\end{figure}

\section{Helium GPD}
~~~~As shown at the beginning of this chapter, one can extract both real and
imaginary parts of the 
$^4$He CFF $\mathcal{H}_A$ from fitting the beam-spin asymmetry signals. This extraction
is fully model independent and, in contrast with the proton's GPD extraction, does not
make any assumption on additional GPDs. In this 
work, we performed the first experimental extraction of $\mathcal{H}_A$ from 
exclusive measurements of the reaction. The results are presented in figure 
\ref{fig:HA_CFF} as function of $Q^{2}$, $x_B$, and $-t$.\\

Within the given uncertainties, our results show a slight dependence on 
$Q^{2}$, $x_B$, and $-t$.  More work is needed on the theoretical models to 
give predictions for $\mathcal{H}_A$.  One can see a difference between the 
precision of the extracted real and imaginary parts, indicating the fact that 
the beam-spin asymmetry is mostly sensitive to the imaginary part of the  CFF 
$\mathcal{H}_A$.

\begin{figure}[h!]
\hspace{-0.5in}\includegraphics[scale=0.38]{fig_ch5/HA_Q2.png}
\hspace{-0.3in}\includegraphics[scale=0.38]{fig_ch5/HA_xB.png}
\centering \includegraphics[scale=0.38]{fig_ch5/HA_t.png}
\caption{The model-independent extraction of the imaginary (blue points) and 
real (red points) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of 
$Q^{2}$ (on the top right), $x_B$ (on the top left), and $t$ (on the bottom).}
\label{fig:HA_CFF}
\end{figure}

\section{Generalized EMC ratios}
~~~~Comparing our measured DVCS channels to the free-proton DVCS reaction 
allows us to investigate the nuclear medium effects at the GPD level. For this 
we use analyzes performed on free-proton with the DVCS data sets taken by the CLAS 
collaboration, during the E1-DVCS experiment (parts 1 and 2). The results of 
part 1 are already published \cite{FX_BSA, CLAS_cross_section}. Herein, our 
coherent and incoherent beam-spin asymmetries are compared to the results of
free proton asymmetries from this publication.

The explored kinematical ranges of $Q^2$, $x_{B}$ and $-t$ of the free-proton 
data are similar to the ones of the incoherent channel, and the two data sets 
were recorded using similar electron-beam energies and experimental setup.  
Therefore, we construct $A_{LU}$ ratios based on choosing the free proton bins 
which have similar $Q^2$, $x_{B}$ and $-t$ values as our bins. The incoherent 
$A_{LU}$ ratios at $\phi$~=~90$^{\circ}$ are shown in figure 
\ref{fig:incoh_EMC_ratio_ALU_proton} as functions of $Q^{2}$, $x_{B}$, and 
$-t$, along with theoretical predictions at similar kinematical values.\\

\begin{figure}[tp]
\centering
\includegraphics[scale=0.38]{fig_ch5/incoh_emc_Q2.png}\\
\includegraphics[scale=0.38]{fig_ch5/incoh_emc_xB.png}\\
\includegraphics[scale=0.38]{fig_ch5/incoh_emc_t.png}
\caption{ The $A_{LU}$ ratio between the bound and the free proton at 
$\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
middle), and $t$ (on the bottom). The black squares are our results, the 
green circles are the HERMES inclusive measurement \cite{HERMES_BSA} results. 
The blue and red curves are from an on-shell calculations from S. Liuti and K. Taneja 
\cite{simonetta_2}.} \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}

Overall the $A_{LU}$ ratios, one can see that the bound protons 
have 20-40$\%$ smaller beam spin asymmetries than the free protons. These measurements 
disagree with the enhancement predicted by the simple impulse approximation of 
V.~Guzey \cite{EMC_vadim_2}, as can be seen in chapter 1, figure 
\ref{fig:EMC_vadim}. The calculations of S. Liuti and K. Taneja \cite{simonetta_2}
also overshoot the data indicating a trend. In particular, the 
anti-shadowing region seems to be absent in terms of the $A_{LU}$ ratio, while
it was predicted by the calculation. Before to draw any strong conclusions on the 
structure of bound protons, it remains to be understood what parasitic
effects can create such a decrease. In particular, final state interactions need
to be evaluated, as they could dilute the signal.  Within the given 
uncertainties, our measured ratios are compatible with the previous measured 
single point from HERMES.\\

 More attention is needed in constructing the coherent $A_{LU}$ ratio between 
 $^4$He and the free proton. One can see from figure 
 \ref{fig:kinematic_coverage} that the coherent experimental ranges of $Q^2$, 
 $x_{B}$ and $-t$ are limited compared to the incoherent channel especially in 
 the $-t$-domain. The latter is due to the fact that the nuclear form factor of 
 the $^4$He has a steeper drop in $-t$ than the nucleonic one. Our coherent 
 DVCS data set was binned in 3 bins in $Q^{2}$ to show
 $Q^{2}$-dependence of the coherent $A_{LU}$ ratio.  Similar procedures were 
 performed to shows the $x_B$-dependence. For the dependence on $-t$, the data 
 are integrated to one bin to optimize a more precise ratio. The results are 
 presented in figure \ref{fig:coh_EMC_ratio_ALU} along with the available 
 theoretical predictions for this ratio. Our measurements shows a nuclear 
 beam-spin asymmetry enhancement compared to the free proton. 
 The measured ratios are not matching the measurement of 
 HERMES collaboration \cite{HERMES_BSA}, pausing the question of weather they
 actually measured coherent DVCS. It is also in conflict with the calculations 
 of Liuti and K.~Taneja \cite{simonetta_2}, which is missing the large observed 
 increase. On the other hand, our measurements seems to agree with the 
 enhancement predicted by V.~Guzey \cite{EMC_vadim_4}.  Moreover, A.  Kirchner 
 and D. Mueller (KM model) \cite{Kir}, using their formalism of GPDs 
 factorization, have predicted a beam-spin asymmetry ratio of 1.4 (0.35/0.25) 
 for all different spin-zero nuclei at $x_{B}$= 0.3, $E_{b}$= 6GeV, -$t$= 0.25 
 GeV$^2$, and $Q^2$= 2.5 GeV$^2$.  \\

\begin{figure}[tp]
\centering
\includegraphics[scale=0.37]{fig_ch5/coh_emc_Q2.png}\\
\includegraphics[scale=0.37]{fig_ch5/coh_emc_xB.png}\\
\includegraphics[scale=0.37]{fig_ch5/coh_emc_t.png}
\caption{The $A_{LU}$ ratio between $^4$He and free proton at 
   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
   middle), and $-t$ (on the bottom). The black squares represent the results of 
   this work and the green circles are the HERMES measurements 
   \cite{HERMES_BSA}. These measurements are compared to theoretical 
   predictions from S. Liuti and K. Taneja \cite{simonetta_2}, the red and the 
blue curves, and the model predictions from V. Guzey et al. based on the 
off-shell calculations \cite{EMC_vadim_4}, in black, purple and brown dashed 
curves.}
\label{fig:coh_EMC_ratio_ALU}
\end{figure}
~\\

### 2016-06-30 2nd_round_comments/DVCS-CAN-Meeting-Comments.tex
added the more answers to the comments

@@
 \section*{\centering{Summary of April 13, 2016 phone conference and requests from the NP-PWG review committee
-M. Garcon, S. Kuhn and Zein-Eddine Meziani\\ 
-to M. Hattawi and co-authors}}
+M. Garcon, S. Kuhn and Zein-Eddine Meziani\\ to M. Hattawy and co-authors}}
 
@@
     \includegraphics[height=14.6cm]{fig/all_sigmas_incoh_exc_cuts.pdf}
-    \caption{ Incoherent exclusivity distributions for the different cut  
-    width on $ep\gamma X$ missing mass squared.}
+    \caption{ Incoherent exclusivity distributions for the different cuts on 
+    $ep\gamma X$ missing mass squared.}
     \label{fig:2d_delta_phi_MM2_InCoh}
@@
    GeV2).  (also see the evolution of the other distributions when doing so).
+
+   \begin{figure}[tbp]
+    \includegraphics[height=14.6cm]{fig/BSA_incoherent_epMM.png}
+    \caption{ The integrated, over $Q^{2}$, $x_{B}$, and $-t$, incoherent 
+    beam-spin asymmetries as a function of $\phi$ for the different cuts on 
+ $epX$ missing mass squared.}
+    \label{fig:BSA_incoherent_epMM}
+    \end{figure}
+
+    \begin{figure}[tbp]
+    \includegraphics[height=14.6cm]{fig/epMM2_incoh_exc_cuts.pdf}
+    \caption{ Incoherent exclusivity distributions for the different cuts on 
+    $epX$ missing mass squared.}
+    \label{fig:epMM2_incoh_exc_cuts}
+    \end{figure}
+
 \end{enumerate}

### 2016-07-08 2nd_round_comments/DVCS-CAN-Meeting-Comments.tex
added figure for the 4D background subtraction

@@
     errors.
+    \begin{figure}[tbp]
+    \includegraphics[height=6.6cm]{fig/BSA_Coherent_xB.png}
+    \includegraphics[height=6.6cm]{fig/diff_BSA_Coherent_xB.png}
+    \caption{On top: the reconstruct coherent beam-spin asymmetries as a 
+    function of $\phi$ in $x_{B}$ bins using 2D (in blue) and 4D (in green) 
+ background subtraction.  On bottom: the difference between the two asymmetries 
+ as a function of $\phi$.}
+    \label{fig:coh_binning}
+    \end{figure}
+
+    \begin{figure}[tbp]
+    \includegraphics[height=5.6cm]{fig/BSA_InCoherent_xB.png}
+    \includegraphics[height=5.6cm]{fig/diff_BSA_InCoherent_xB.png}
+    \caption{On top: the reconstruct incoherent beam-spin asymmetries using 2D   
+    (in blue) and 4D (in green) background subtraction. On bottom: the 
+ difference between the two asymmetries as a function of $\phi$.}
+    \label{fig:incoh_binning}
+    \end{figure}
+
  \item not convinced that comparing 9 phi-bins to 11 is a definitive answer, 

### 2016-07-08 analysis-note-v2/analysis-2.tex
added figure for the 4D background subtraction

@@
 \includegraphics[scale=0.30]{fig_dvcs/e4Hegamma_e4Hepi0_Phi.png}
-\caption{The coherent channel acceptance ratios as a function of the kinematic variables: $Q^{2}$ (top left), $x_{B}$ (top right), $-t$ (bottom left), and $\phi$ (bottom right). }
+\caption{The coherent channel acceptance ratios as a function of the kinematic 
+variables: $Q^{2}$ (top left), $x_{B}$ (top right), $-t$ (bottom left), and 
+$\phi$ (bottom right). }
 \label{fig:coh_acceptance _ratios}
@@
 \includegraphics[scale=0.30]{fig_dvcs/epgamma_eppi0_Phi.png}
-\caption{The incoherent channel acceptance ratios as a function of the kinematic variables: $Q^{2}$ (top left), $x_{B}$ (top right), $-t$ (bottom left), and $\phi$ (bottom right).  }
+\caption{The incoherent channel acceptance ratios as a function of the 
+kinematic variables: $Q^{2}$ (top left), $x_{B}$ (top right), $-t$ (bottom 
+left), and $\phi$ (bottom right).  }
 \label{fig:incoh_acceptance _ratios}
@@
 \caption{Beam polarization measurements during the CLAS-EG6 running period.  
-The red squares are the measurements with a negative current in the Helmholtz coils of the M\o ller polarimeter and the purple triangles are these with a positive current.
-The figure is taken from \cite{yohann}.}
+The red squares are the measurements with a negative current in the Helmholtz 
+coils of the M\o ller polarimeter and the purple triangles are these with a 
+positive current. The figure is taken from \cite{yohann}.} 
 \label{fig:beam_polarization}
@@
 
-Predominantly, two techniques are used to estimate the systematic uncertainty associated with the calculated acceptance ratio (R).
-The first is via repeating the analysis by implementing R differently, while the second technique is by using two generating models to calculate R.\\
+Predominantly, two techniques are used to estimate the systematic uncertainty 
+associated with the calculated acceptance ratio (R). The first is via repeating 
+the analysis by implementing R differently, while the second technique is by 
+using two generating models to calculate R.\\
 
-Both methods were investigated in this work.
-Regarding the first method, the analysis was repeated by taking three different values for R: 0.8*R, R and 1.2*R.
-The beam-spin asymmetries at $\phi = 90^{\circ}$ were extracted and compared, see figure \ref{fig:background_sub_sys_uncer}.
-A maximum variation of 2$\%$ (0.6$\%$) has been observed on the incoherent (coherent) $A_{LU}$ at $\phi = 90^{\circ}$.
-\\
+Both methods were investigated in this work. Regarding the first method, the 
+analysis was repeated by taking three different values for R: 0.8*R, R and 
+1.2*R. The beam-spin asymmetries at $\phi = 90^{\circ}$ were extracted and 
+compared, see figure \ref{fig:background_sub_sys_uncer}. A maximum variation of 
+2$\%$ (0.6$\%$) has been observed on the incoherent (coherent) $A_{LU}$ at 
+$\phi = 90^{\circ}$. \\
 
@@
 
-For the second technique, in fact there is only one event generator available, presented in section \ref{Event_generator}.
-Nevertheless, one can still use this method by generating events with or without the cross section parametrization.
-In the absence of the parametrization, the generated events are flat in the four kinematic variables ($Q^2$, $-t$, $x_B$, $\phi$).
-The calculated coherent and incoherent acceptance ratios (R) with and without the cross section parametrization are shown in figure \ref{fig:accep_ratio_sys_uncer}.
-One can see that the difference between the calculated acceptance ratios is almost constant.
-Thus, we can conclude that the first method of taking $\pm$20$\%$ on R is is an adequate way to obtain an estimation of the systematic uncertainty associated to the calculated acceptance ratios.
+For the second technique, in fact there is only one event generator available, 
+presented in section \ref{Event_generator}. Nevertheless, one can still use 
+this method by generating events with or without the cross section 
+parametrization. In the absence of the parametrization, the generated events 
+are flat in the four kinematic variables ($Q^2$, $-t$, $x_B$, $\phi$). The 
+calculated coherent and incoherent acceptance ratios (R) with and without the 
+cross section parametrization are shown in figure 
+\ref{fig:accep_ratio_sys_uncer}. One can see that the difference between the 
+calculated acceptance ratios is almost constant. Thus, we can conclude that the 
+first method of taking $\pm$20$\%$ on R is is an adequate way to obtain an 
+estimation of the systematic uncertainty associated to the calculated 
+acceptance ratios.
 \begin{figure}[h!]
@@
 \includegraphics[scale=0.34]{fig_results/incoh_accp_ratio_phi.png}
-\caption{The coherent (on the top) and the incoherent (on the bottom) acceptance ratios ($R$) as function of the angle $\phi$.
-In both plots, the blue (red) points are the ratios with (without) the cross section parametrization.}
-\label{fig:accep_ratio_sys_uncer}
+\caption{The coherent (on the left) and the incoherent (on the right) 
+acceptance ratios ($R$) as function of the angle $\phi$. In both plots, the 
+blue (red) points are the ratios with (without) the cross section 
+parametrization.} \label{fig:accep_ratio_sys_uncer}
 \end{figure}
@@
 
-In this analysis, we have assumed that the beam-spin asymmetry arises from the leading twist DVCS amplitude and its interference with the BH process.
-However, there are higher-order electromagnetic corrections which can affect the beam-spin asymmetry.
-Andrei V.
-Afanasev and his collaborators have estimated the corrections to $A_{LU}$ which arise from such effects in a model-independent way \cite{Afanasev}.
-They have performed one-loop corrections on the outgoing electron as only the radiation from it affects the $A_{LU}$.
-They found that the correction does not exceed 0.1$\%$ at a 4.25 GeV electron beam energy and Q$^{2}$=1.25 GeV$^{2}$.
-In our case, as the radiative emission is inversely proportional to the mass of the radiating particle, the helium and the proton contributions are negligible compared to the leptonic one.
-Therefore, we can still take the result of Afanasev as a good estimation for the radiative  effects on our measured $A_{LU}$.\\
+In this analysis, we have assumed that the beam-spin asymmetry arises from the 
+leading twist DVCS amplitude and its interference with the BH process.  
+However, there are higher-order electromagnetic corrections which can affect 
+the beam-spin asymmetry. Andrei V. Afanasev and his collaborators have 
+estimated the corrections to $A_{LU}$ which arise from such effects in a 
+model-independent way \cite{Afanasev}. They have performed one-loop corrections 
+on the outgoing electron as only the radiation from it affects the $A_{LU}$.  
+They found that the correction does not exceed 0.1$\%$ at a 4.25 GeV electron 
+beam energy and Q$^{2}$=1.25 GeV$^{2}$. In our case, as the radiative emission 
+is inversely proportional to the mass of the radiating particle, the helium and 
+the proton contributions are negligible compared to the leptonic one.  
+Therefore, we can still take the result of Afanasev as a good estimation for 
+the radiative  effects on our measured $A_{LU}$.\\
 
 %\paragraph{Beam asymmetry}
-%The injector of JLab produces electrons with positive and negative helicities in equal %time in principle.
-To ensure this equality between the two helicity configurations., %figure \ref{fig:beam_charge} shows the deposited charge ratio of the positive helicity %electrons to the negative ones in the individual runs.
-A 2$\%$  maximum deviation from %one.
-Thus, the integrated beam charge ratio induces 1.1$\%$ systematic uncertainty to %$A_{LU}$ on both DVCS channels.\\
+%The injector of JLab produces electrons with positive and negative helicities 
+%in equal %time in principle. To ensure this equality between the two helicity 
+%configurations., %figure \ref{fig:beam_charge} shows the deposited charge 
+%ratio of the positive helicity %electrons to the negative ones in the 
+%individual runs. A 2$\%$  maximum deviation from %one. Thus, the integrated 
+%beam charge ratio induces 1.1$\%$ systematic uncertainty to %$A_{LU}$ on both 
+%DVCS channels.\\
 %\begin{figure}[h!]
@@
 ~\\
-The total systematic uncertainty is the quadratic sum of the previously described individual uncertainties.
-Table \ref{Table:systematic_uncertainties} summarizes the sources of systematic uncertainty and their contributions on the measured $A_{LU}$ at $\phi = 90^{\circ}$, that will be added quadratically to the statistical uncertainties on $A_{LU}$.
+The total systematic uncertainty is the quadratic sum of the previously 
+described individual uncertainties. Table \ref{Table:systematic_uncertainties} 
+summarizes the sources of systematic uncertainty and their contributions on the 
+measured $A_{LU}$ at $\phi = 90^{\circ}$, that will be added quadratically to 
+the statistical uncertainties on $A_{LU}$.
 
@@
 \end{tabular}
-\caption{ The systematic uncertainties on the measured coherent and incoherent beam-spin asymmetries at $\phi = 90^{\circ}$.}
+\caption{The systematic uncertainties on the measured coherent and incoherent 
+beam-spin asymmetries at $\phi = 90^{\circ}$.}
 \label{Table:systematic_uncertainties}

### 2016-08-01 2nd_round_comments/DVCS-CAN-Meeting-Comments.tex
update the answers

@@
-\section*{\centering{Summary of April 13, 2016 phone conference and requests from the NP-PWG review committee
+\section*{\centering{Summary of April 13, 2016 phone conference and requests 
+      from the NP-PWG review committee
 M. Garcon, S. Kuhn and Zein-Eddine Meziani\\ to M. Hattawy and co-authors}}
@@
   \item 2D missing $ep\gamma X$ M2 vs $\Delta \phi$: is there a gain to be 
-     expected by a contour cut? If yes, implement. Shown in figure 
-     \ref{fig:2d_delta_phi_MM2_InCoh}
-    \begin{figure}[!h]
+     expected by a contour cut? If yes, implement.\\
+    \textcolor{blue}{The results are shown in figure 
+       \ref{fig:2d_delta_phi_MM2_InCoh} before and after the exclusivity cuts.  
+    No clear dependence is observed.}  \begin{figure}[!h]
     \includegraphics[height=5.6cm]{fig/delta_phi_epgamma_M2_Mis.png}
@@
      https://clasweb.jlab.org/rungroups/lowq/wiki/images/a/a0/ExcluCuts-CANeg6.pdf}   
-     for a 2$\sigma$ and 1$\sigma$ cuts on missing $ep\gamma X$ M2.
+     for a 2$\sigma$ and 1$\sigma$ cuts on missing $ep\gamma X$ M2.\\
+     \textcolor{blue}{The coherent and the incoherent distributions are 
+        presented in figure \ref{fig:exc_Coh} and \ref{fig:exc_InCoh} 
+     respectively. No correlations were observed in the coherent DVCS channel, 
+  while a slight correlation was observed between the $ep\gamma$ MM2 and $epX$ 
+  MM2.} \textcolor{red}{Do we have to apply tighter cuts in the incoherent 
+  case?.}
      \begin{figure}[tbp]
     \includegraphics[height=14.6cm]{fig/all_sigmas_coh_exc_cuts.pdf}
-    \caption{Coherent exclusivity distributions for the different cut 
-    width on $e^{4}He\gamma X$ missing mass squared. }
-    \label{fig:2d_delta_phi_MM2_InCoh}
+    \caption{Coherent exclusivity distributions corresponding to different cuts 
+    on $e^{4}He\gamma X$ missing mass squared.}
+    \label{fig:exc_Coh}
     \end{figure}                                                                  
@@
     $ep\gamma X$ missing mass squared.}
-    \label{fig:2d_delta_phi_MM2_InCoh}
+    \label{fig:exc_InCoh}
     \end{figure}
@@
    ep missing M2 right cut, moving it tighter to the left (e.g. 1 and 0.75 
-   GeV2).  (also see the evolution of the other distributions when doing so).
+   GeV2).  (also see the evolution of the other distributions when doing so).\\
+   \textcolor{blue}{The reconstructed incoherent asymmetries are presented in 
+      figure \ref{fig:BSA_incoherent_epMM} with the associated exlcusive 
+      distributions in figure \ref{fig:epMM2_incoh_exc_cuts}. The different 
+   tail cuts show no major effects on the reconstructed ALU.}
 
    \begin{figure}[tbp]
-    \includegraphics[height=14.6cm]{fig/BSA_incoherent_epMM.png}
+    \centering
+    \includegraphics[height=8.6cm]{fig/BSA_incoherent_epMM.png}
     \caption{ The integrated, over $Q^{2}$, $x_{B}$, and $-t$, incoherent 
@@
     \begin{figure}[tbp]
+    \centering
     \includegraphics[height=14.6cm]{fig/epMM2_incoh_exc_cuts.pdf}
@@
     that the effect discussed is small and taken care of in the systematic 
-    errors.
+    errors.\\
+    \textcolor{blue}{We implemented a 4D ratio R for the background 
+       subtraction. The difference between the reconstructed ALU with 2D and 4D 
+       background subtraction are presented in figures \ref{fig:coh_binning} 
+       and \ref{fig:incoh_binning} for the coherent and the incoherent DVCS 
+       channels. Even though the 2D was a good a pproximation, a 4D subtraction 
+    is applied on the final results.} 
     \begin{figure}[tbp]
@@
     size of statistical and systematic errors, would accept that.
+
 \item Your Eq.(4) of "answer" is probably wrong. For our own understanding, 
    look into this argument again.
-\item ...
+
    \end{enumerate}
@@
 \item Request to see the very first draft of the publication.
+
 \end{enumerate}

### 2016-08-09 2nd_round_comments/DVCS-CAN-Meeting-Comments.tex
update the answers

@@
         presented in figure \ref{fig:exc_Coh} and \ref{fig:exc_InCoh} 
-     respectively. No correlations were observed in the coherent DVCS channel, 
+     respectively. The reconstructed coherent and incoherent beam spin 
+  asymmetries are presented in figures \ref{fig:exc_coh-alu} and 
+  \ref{fig:exc_incoh-alu} respectively. In terms of the exclusivity 
+  distributions, no correlations were observed in the coherent DVCS channel, 
   while a slight correlation was observed between the $ep\gamma$ MM2 and $epX$ 
@@
   case?.}
+
   \begin{figure}[tbp]
@@
     \end{figure}
+
+    \begin{figure}[tbp]
+       \centering
+    \includegraphics[height=8.6cm]{fig/ALU_coherent_MM2.pdf}
+    \caption{The integrated coherent beam-spin asymmetries as a function of 
+    $\phi$ corresponding to different cuts on $e^{4}He\gamma X$ missing mass 
+ squared.}
+    \label{fig:exc_coh-alu}
+    \end{figure}
+
     \begin{figure}[tbp]
@@
     \label{fig:exc_InCoh}
+    \end{figure}
+
+    \begin{figure}[tbp]
+       \centering
+    \includegraphics[height=8.6cm]{fig/ALU_incoherent_MM2.pdf}
+    \caption{The integrated incoherent beam-spin asymmetries as a function of 
+    $\phi$ corresponding to different cuts on $e^{4}He\gamma X$ missing mass 
+ squared.}
+    \label{fig:exc_incoh-alu}
     \end{figure}
@@
 asymmetry ratios in the future publication.
+  \begin{figure}[tbp]
+    \includegraphics[height=14.6cm]{fig/ALU-proton-fits.png}
+    \caption{ Fitting e1dvcs1 free proton beam-spin asymmetries. The dashed 
+    curves are fits to the data in the form of 
+ $p_{0}*(t-t_{min})*e^{p_{1}*\sqrt{t}}$, while the solid curves are from 
+ calculations based on fitting the parameters $p_{0}$ and $p_{1}$.}
+    \label{fig:free-proton-alu-fits}
+    \end{figure}
 

### 2016-08-10 coherent/HeliumCohDVCS.tex
Create a sub folder for the letter on Coherent

\documentclass[%
 reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%showpacs,preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-1}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math

\begin{document}

\title{First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei}

\author{M. Hattawy, ...}
\affiliation{...}
\author{R. Dupr\'e}
\affiliation{Institut de Physique Nucl\'eaire d'Orsay, CNRS-IN2P3,\\ 
Universit\'e Paris-Sud, Universit\'e Paris-Saclay, 91406 Orsay, France.}

\date{\today}

\begin{abstract}
We report the first exclusive measurement of deeply virtual Compton scatterring 
(DVCS) off a nuclei with the CLAS detector at the Jefferson laboratory. The 
observed beam spin asymmetries are significantly larger than for proton, 
confirming expectations from plane wave impulse approximation. We present an 
extraction of the unique generalized parton distribution (GPD) of the spin-0 
helium in a completely model independent way. This result demonstrate the 
strength of the method and opens a new unique access into nuclei 3D structure 
in term of quarks and gluons.
\end{abstract}

\pacs{Valid PACS appear here}

\maketitle

%\section{Introduction}
% Now many letters do not put any sections. Maybe we should consider doing the same

The generalized parton distribution (GPD) framework developped in the past two decades
(Need a bunch of refs)~\cite{}
offers a unique access into hadron 3D structure through deeply virtual Compton
scattering (DVCS), depicted in figure~\ref{fig:DVCS} and other exclusive processes. Many measurements on the proton
at several energies have now be reported and have demonstrated the solidity of the
method~\cite{}. %To enhance a little -> CFF

Insert FIGURE DVCS nuclei
%\label{fig:DVCS}
\begin{figure}[htbp]
\caption{\label{fig:DVCS} Coherent DVCS}
\includegraphics[width=8.6cm]{DVCS.png}
\end{figure}

At the same time, the partonic structure of nuclei has remained a mystery
for the past three decades, as we are still unable to explain properly the 
infamous EMC effect~\cite{}. First observed in 197X by the EMC 
collaboration, it describes the difference between the partonic structure of
free and bound nucleons. Understanding the source of this difference remains 
today a topic of active research~\cite{},
questionning our understanding of nuclei and their structure beyond protons
and neutrons~\cite{}. As studies based on inclusive measurements of the
effect seem to be too limited to tackle the question definitively, we can now
apply the GPD framework to study the nuclei in three dimensions and observe
the EMC effect in an unprecedented way.
%Elaborate on non nucleonic degrees of freedom and other interests of He DVCS

The measurement of DVCS on helium 4 is in this regard the perfect experiment for
several reasons. First, Helium 4 is of spin-0, such that a single GPD ($H$) is
necessary for the description of the DVCS at leading order. This feature allows for a
completely model independant extraction of the CFF from data that is impossible for 
protons and neutrons which need 4 GPDs, leading to complex underconstrained 
problems~\cite{}. Second, helium 4, while a small nuclei, is dense and experience 
already a significant EMC effect, while being simple enough that its nuclear
structure is very well known~\cite{} (Low energy struct, FF,...). Third, being 
light enough helium 4 can exit
a light target and be experimentally measured, insuring the exclusivity of the 
measurement. This point is especially important as we are probing with a 
multi-GeV interaction a nuclei bound by only a few MeV, this leads in the 
overwhelming majority of the cases to the incoherent break-up of the target.

%\section{Experiment}
The HERMES collaboration has measured nuclear DVCS~\cite{} without the 
possibility of separating the coherent and incoherent channels leading
to controversy in the interpretation of their results~\cite{}. We report
here our measurement of coherent DVCS off helium-4 at the Jefferson labortory
(JLab), while our results for the incoherent channel will be presented in
another paper~\cite{}. This experimental facility delivers a nearly 100\% duty factor, 6~GeV 
electron linear accelerator into three experimental halls. Our experiment
ran for 3 months in 2009 using the CEBAF Large Acceptance Spectrometer (CLAS).
This detector is covering about 2$\pi$ and is composed of drift chambers, Cherenkov counters, scintillator 
counters and an electro-magnetic calorimeter. It allows to detect accurately
electrons and provides a trigger for the experiment. It is complemented for DVCS experiments with
an inner calorimeter to detect the photons emitted at low angle and a solenoid
to keep the Moller electrons produced along the beam line to get into our detectors.

In order to insure the coherence of the process, we detect all the products
of the reaction. The electron is detected by the CLAS, using the drift chamber 
to reconstruct its trajectory and the combination of the Cherenkov counters
and electromagnetic calorimeter to

we built a small and light 
radial time projection chamber (RTPC) depicted in figure~\ref{fig:rtpc} to 
detect the recoiling helium nuclei. this detector is placed directly ouside of 
our gaseous target filled with 6~atm helium. 
% to complete

\begin{figure}[htbp]
\caption{\label{fig:rtpc} RTPC description}
\includegraphics[width=8cm]{RTPC.png}
\end{figure}

%\section{DVCS Events Selection}

Detection, PID des particules.

\begin{figure*}[htbp]
\caption{\label{fig:exclu} Exclusivity cuts}
\includegraphics[width=17.2cm]{all_coh_exc_cuts.png}
\end{figure*}

We identified several background contributions to the DVCS process, in 
particular accidental events and exclusive deeply virtual $\pi^0$ production (DV$\pi^0$P). The accidental
events happen when an helium nuclei is mistakenly associated with our event, this 
possibility is suppressed by the limited phase space allowed but enhanced by the
low time resolution of the RTPC (~200 ns). We evaluated this contribution by
selecting events passing all our cuts but with particles originating from 
different verteces. With this method, we found this background to represent 
4.1\%. The DV$\pi^0$P events can easily be mistaken
with DVCS events when one of the two photons of $\pi^0$ decay is produced at
low energy in the laboratory frame. In order to estimate the importance of
this background, we developped an event generator DV$\pi^0$P 
that we calibrated to match our experimental yields. We used this generator together 
with a GEANT3~\cite{} simulation of our detection system to estimate the ratio 
of acceptance between measured DV$\pi^0$P and DV$\pi^0$P that would pass our 
DVCS selection cuts. This ratio obtained from simulation is then multiplied by 
the measured yield of DV$\pi^0$P events, indicating a contamination of XX to XX\%. 
%(We NEED a figure of that in the note!!!)

Systematic errors

%\section{Results}

Extraction of assymetries (figure~\ref{fig:assym})

\begin{figure*}[htbp]
\caption{\label{fig:assym} Assymetries}
\includegraphics[width=14cm]{coh_alu_t_phi.png}
\end{figure*}

% This is mainly to compare to existing models
Generalized ratios (figure~\ref{fig:GenR})

\begin{figure}[htbp]
\caption{\label{fig:GenR} Generalized ratio}
\includegraphics[width=7.5cm]{coh_emc_Q2.png}
\includegraphics[width=7.5cm]{coh_emc_t.png}
\includegraphics[width=7.5cm]{coh_emc_xB.png}
\end{figure}

\begin{figure}[htbp]
\caption{\label{fig:CFF} CFF extraction}
\includegraphics[width=8cm]{HA_t.png}
\end{figure}

Model independant extraction of H (figure~\ref{fig:CFF})

%\section{Summary}

Open new perspectives in nuclear physics, mention the 12 GeV program and the EIC

First fully exclusive measurement: very strong BSA, demonstrate the capability to extract GPDs even with limited statistics and kinematic compared to proton.

% If this is line > 400 this is probably getting too long!

\section*{Acknowledgments}
Guzey and Liuti

\section*{Bibliography}
Biblio

\end{document}

### 2016-08-10 NIM/main.tex
Add the NIM paper

\documentclass[reprint, amsmath,amssymb, aps]{revtex4-1}

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\newcommand{\RNum}[1]{\uppercase\expandafter{\romannumeral #1\relax}}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage{amsmath}
\usepackage[english]{babel}
\usepackage{array}
\usepackage{xcolor}
\usepackage{amssymb}
\usepackage{float}
\usepackage{wrapfig}
%\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

%\usepackage[showframe,%Uncomment any one of the following lines to test 
%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
%%text={7in,10in},centering,
%%margin=1.5in,
%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
%%height=10in,a5paper,hmargin={3cm,0.8in},
%]{geometry}

\begin{document}

\preprint{APS/123-QED}

\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A New Radial Time Projection Chamber for CLAS at JLab}}
\author{
\Large{R. Dupr\'e$^{[1][2]}$, M. Hattawy$^{[1][2]}$, ...} \\
\vspace{+5mm}
\normalsize $^{[1]}$Argonne National Laboratory, Argonne IL 60439, USA \\
\normalsize $^{[2]}$Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France \\
\vspace{+5mm}
}

\collaboration{CLAS Collaboration}

\date{\today}% It is always \today, today,
             %  but any date may be explicitly specified

\begin{abstract}
To study coherent Deeply Virtual Compton Scattering (DVCS) and coherent production of mesons on $^4$He, it is necessary to insure that the target nuclei is left intact by the reaction. This experiment is carried on at the CEBAF Large Acceptance Spectrometer (CLAS) at Jefferson laboratory (JLab), which has been used for similar studies on proton targets, however it cannot track low energy $^4$He. We developed for an experiment in 2009 a Radial Time Projection Chamber (RTPC) based on Gas Electron Multipliers (GEMs). The detector was positioned directly around the gaseous target of the experiment, allowing a detection threshold of $~$??? MeV/c for $^4$He. We describe in this article the design of the RTPC, the methods we developed to calibrate it and finally its performances.
\end{abstract}

\maketitle

%\tableofcontents

\section{\label{sec:level1} Introduction}

The CEBAF Large Acceptance Spectrometer (CLAS)~\cite{CLASref} is installed in the Hall-B of the TJNAF in Newport News, Virginia, USA. The spectrometer is measuring charged particles as well as photons. The accelerator of the TJNAF provides a high power electron beam of energy up to 6 GeV and 100$\%$ duty cycle to the hall. The RTPC mentioned in this article has been used during a three months experimental run in 2009 with a longitudinally polarized electron beam of energy 6.064 GeV sent on a gaseous helium-4 target to measure asymmetries in Deep Virtual Compton Scattering (DVCS)~\cite{proposal} and exclusive meson production (Meson Spec Prop). In these experiments, CLAS detects the high energy charged particles and the final real photon, for the latter the coverage has been extended using the optional inner calorimeter (ref).

\begin{figure}[h]
\centering 
\includegraphics[scale=0.3]{fig/test_clas.png}
\caption{\small\sf Three dimensional representation of the primary CLAS setup represents the geometry and the relative position of each subsystem. From outside, the electromagnetic calorimeter (green), time-of-flight system (red), Cherenkov counters (purple), three drift chamber regions (blue) and the superconducting torus coils (yellow).} 
\label{fig:CLAS}
\end{figure}

CLAS is composed of several subdetectors and two magnets. They are designed to track charged particles at momentum greater than 250 MeV/c. Figure~\ref{fig:CLAS} shows the basic setup of CLAS, ordered with respect to their radial distance from the center:

\begin{itemize}
\item Three regions of Drift Chambers (DC) for tracking of charged particles~\cite{DCref}.
\item Superconducting toroidal magnet which enables the tracking by bending the trajectories.
\item Cherenvkov Counters (CC) to separate electrons from negative pions~\cite{CCref}.
\item Scintillation Counters (SC) to identify hadrons via measuring their Time-Of-Flight (TOF)~\cite{TOFref}.
\item Forward Electromagnetic Calorimeter (EC) to detect showering particles (electrons and photons) and neutrons~\cite{ECref}.
\end{itemize}

In addition to the normal CLAS setup, a forward electromagnetic calorimeter (the inner calorimeter) was installed to improve the photon detection acceptance. Moreover, a 5~T solenoid was placed around the target to shield the detectors close to the beam line -- mostly the inner calorimeter and the RTPC -- from Mollers electrons. The solenoid field is also used to calculate the momentum of the alpha particles from their curvature radius measured by the RTPC.

The first implementation of a RTPC in CLAS have been achieved for the BoNuS experiment~\cite{BONUS} in 200x. The success of this detector for the detection of slow protons motivated the development of this new RTPC. For the channel of interests of our experiments, the recoiled $^{4}He$ nuclei have momentum around (150 or 300 ???) MeV/c, the detection of these particles was the primary motivation for using such design.

This paper is organized in this way: section $\RNum{2}$ details the design and the internal structure of the RTPC, while section $\RNum{3}$ points the properties of the readout system. The calibration strategies for such detectors will be discussed in section $\RNum{4}$. Finally, performances are discussed in section $\RNum{5}$.

\section{Design}

The RTPC is a 200~mm long with a 150~mm diameter time projection chamber. The ionized electrons are drifting outward perpendicularly to the beam direction. These electrons are then amplified by three layers of GEMs and detected on 4.45 by 5~mm pads. As for BoNuS, the RTPC has two detection parts but unlike BoNuS they are part of a single chamber. Each part has independent GEM amplification systems that cover around 80\% of the azimuthal angle. Under the effect of the electromagnetic field, the ionization electrons drift to the readout system on the external shell with a curved trajectory as can be seen in the figure~\ref{fig:RTPC_1_4}.

\begin{figure}[tb]
\centering
\includegraphics[scale=0.19]{fig/RTPC_exp.png}
\caption[]{\small\sf View of the RTPC ready to be inserted in the solenoid. } 
\label{fig:RTPC2}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[scale=0.28]{fig/RTPC_1_all.png}
\caption[]{\small\sf Schematic drawing of the RTPC taken on a plane perpendicular to the beam line, see text for description of the elements.} 
\label{fig:RTPC_1_4}
\end{figure}

As seen in figure~\ref{fig:RTPC2}, the RTPC is composed from the beam axis to the exterior by:\\
\begin{itemize}
\item The target, filled with 5~atm $^4$He, has a 3~mm radius with Kapton walls only 27$\mu$m thick.
\item The first gas gap extends from 3 mm to 20 mm radial distance. It is filled with $^{4}He$ gas at 1~atm. During run, this region is swarmed by Moller electrons induced by the beam, such that filling this region with a light gas like $^{4}He$ minimizes secondary interactions. This region is surrounded by a 4 $\mu$m thick window made of aluminized Mylar and connected to ground. 
\item The gap region extends between 20~mm and 30~mm and is filled with a gas mixture of 80$\%$ Neon and 20$\%$ Dimethyl Ether (DME). This region is surrounded by a 4~$\mu$m thick window made of aluminized Mylar, which serves as the cathode.
\item The drift region is filled with the Ne-DME gas mixture, it extends from the cathode to the first Gas Electron Multiplier(GEM), 60 mm away from the central axis. The electric field in this region is around 500~V/cm (???) and perpendicular to the beam. Field cages are installed at both ends of the detector in this region. Progressive voltage depending on radial position is applied on these to maintain a uniform electric field perpendicular to the beam line at the edges of the RTPC.
\item The GEM system is composed of three GEMs located at radii, 60 mm, 63 mm and 66 mm, they amplify the electrons to make a measurable signal.
\item The readout board has internal radius of 69~mm and collects the charges, preamplifiers are plugged directly on its outer side and are transmitting the signal to the data acquisition electronics.
\end{itemize}
\begin{figure}[tb]
\centering
\includegraphics[scale=0.70]{fig/GEM_photo.jpg}
\caption[]{\small\sf A schematic layout of the GEMs system in one module of the RTPC.} 
\label{fig:GEMs}
\end{figure}

The GEM amplification has been mainly chosen for this detector for their flexibility, allowing the curved amplification surface. Also GEM are known to create less sparks than in other gaseous detectors, which is a good thing for the detection of slow nuclei like $^4$He. GEMs are made from an insulator layer (here Kapton) sandwiched between two 5 $\mu$m copper layers. The mesh of each GEM layer is chemically etched with 50$\mu$m diameter holes in double-conical cross section shapes as can be seen in figure~\ref{fig:GEMs}. A potential difference of 400 V is applied between the two copper layers of each GEM creating a very strong electric field in the holes. Such strong fields lead to high ionization from initial electrons and therefore amplification of the signal. Also, a potential difference of 150 V is set between the GEMs to push the amplified electrons toward the readout pads. The gain of each GEM layer is of order 100.\\

\section{Readout System}
The RTPC electron collecting system has 3200 readout pads. These collection elements are located at the end of the amplification region, 69 mm from the central axis.
\begin{figure}[tb]
\centering
%\hspace{-1 cm}
\includegraphics[scale=0.55]{fig/PADs.png}
\caption[]{\small\sf A schematic representation of a part of the readout system. The shaded sixteen pads are a group of pads that are connected to the same pre-amplifier.} 
\label{fig:PADs}
\end{figure}
Figure \ref{fig:PADs} shows a schematic drawing of the size and the alignment configuration of the pads. Each readout pad is 5 mm in length and 4.45 mm in width the shift between the rows allows to reduce aliasing. Each half of the RTPC has 40 rows and 40 columns of pads. The shaded region in the figure~\ref{fig:PADs} shows how pads are grouped to the 16 channels pre-amplifiers. The Time to Digital Converter (TDC) units are 114~ns and indicates the time taken by the electron to drift from the ionization point to the readout board. On the the other side, the charge information is measured in Analog-to-Digital-Converter (ADC) units without specific normalization.

Missing items in description:

Detail the electronic setup: Andrea ? or other Italians?

The gas mixture choice: ???

Discuss HV setting: ???

\section{Calibration}
Two quantities are recorded for each detected electron at the readout board, time (TDCs) and signal amplitude (ADCs) (/!\\ are those amplitude or charge preamps ???). The timing information provides trajectory determination resulting in momentum per unit charge measurement. Going from a collection of the TDCs to a momentum measurement requires good knowledge of the drift speed and paths followed by the electrons released in the gas. The recorded ADCs give the deposited energy per unit of length ($\small{\frac{dE}{dX}}$) which, together with the momentum calculated from the trajectory, enables particle identification.

\subsection{Drift Speed Parametrization}

We can measure the drift speed using the tracks detected in the RTPC, in figure \ref{fig:RTPC_signals} we represent a typical $^{4}He$ track (in green). After it causes ionization in the drift region, the released electrons (in black) drift to the detection plane under the effect of the electric field. The electrons released close to the cathode take the most time to reach the readout pads while the geometrical symmetry insure they always travel the same distance. So by identifying the maximum TDC measured, we can infer the drift speed of the electrons in the RTPC.\\

\begin{figure}[tb]
\centering
\includegraphics[scale=0.35]{fig/RTPC_2.png}
\caption[]{\small\sf A schematic drawing of a $^{4}He$ track (in green) traversing the drift region, with the drift paths followed by the electrons (in black). } 
\label{fig:RTPC_signals}
\end{figure}

We first measure the drift speed along the 200 mm RTPC's length to take into account variations in the electric and magnetic field, some of which are known (see figure \ref{fig:B_MAP}) some might be due to slight shifts in the geometry. We verified this by looking at the TDC profile generated in the chamber by all our tracks (see figure \ref{fig:TDC_profile}). The time profile of registered hits clearly show the dropping edge expected from the geometrical considerations previously mentioned. We define a value named $TDC_{Max/2}$ at which the dropping edge passes half the maximum number of hits in the histogram, this value is inversely proportional to the drift speed. The result can be seen in figure \ref{fig:RunNumber_61551_TDCmax_Zslice} showing the dependence of drift speed with position along the beam line axis in the chamber.

\begin{figure}[tb]
\centering
\includegraphics[scale=0.35]{fig/B_MAP.png}
\caption[]{\small\sf Schematic draw in of the solenoid magnetic vectors inside the RTPC. In this draw, r is the radial distance from the target's axis and z is the longitudinal position along the RTPC with its center at zero.} 
\label{fig:B_MAP}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[scale=0.40]{fig/TDC_profile.png}
\caption[]{\small\sf Time profile of the collected hits in one experimental run. } 
\label{fig:TDC_profile}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[scale=0.4]{fig/RunNumber_61551_TDCmax_Zslice.png}
\caption[]{\small\sf Time profile distribution for the collected hits in one experimental run. } 
\label{fig:RunNumber_61551_TDCmax_Zslice}
\end{figure}

Due to the non perfect experimental conditions and in particular changes in the gas proportions, the drift speed might also change over the 3 months run. Figure \ref{fig:Drift_run_number_1} shows the $TDC_{Max/2}$ values for individual runs (approximately 2 hours long). We observe a significant variation over time that we parametrized with a fit in order to take it into account in the track reconstruction code. Dealing with such situation is possible by adapting the right drift speed to the electrons as a function of geometry and time (we did not see any correlation between the effects). These functions were extracted for our entire data sets and implemented in the reconstructions code.

\begin{figure}[tb]
\hspace*{-1.8cm}
\includegraphics[scale=0.28]{fig/Drift_run_number_1.png}
\caption[]{\small\sf $TDC_{Nbmax/2}$ versus the experimental run numbers (time). } 
\label{fig:Drift_run_number_1}
\end{figure}

\subsection{Drift Paths Parametrization}

The drift path is the trajectory which an electron follows in the gas. The standard software to calculate drift paths is the MAGBOLTZ program ~\cite{MAGBOLTZ}. For its calculations, MAGBOLTZ needs to know the detector's geometry, the exact composition of the gas mixture and of course the electric and the magnetic fields. We used such calculations as a first calibration, but as can be seen with the drift speed, conditions are far from stable in the chamber. Moreover, because we use of a thin foil as a cathode, the geometry knowledge is limited to a millimeter precision. These problems, already encountered for the BoNuS RTPC calibration (ref), have motivated the acquisition of specific calibration runs. These are taken with lower energy electron beam (1.20 and 1.27 GeV) to enhance the cross section of the elastic process ($e ^{4}He \rightarrow e ^{4}He$). In this process the knowledge of the electron kinematic gives us the helium nuclei kinematic and therefore allow us to calibrate our drift paths independently of our knowledge of the exact conditions in the chamber.

The drift paths' parametrization is possible using identified elastic events from our experiment and simulate copy of them in a GEANT4 simulation~\cite{GEANT4}. Then by comparing the GEANT4 calculated position of the helium nuclei to the list of hits effectively measured in the chamber, we can reconstruct the electrons drift path in the RTPC. However, because of the magnetic field, the drift paths are not linear. So to perform the extraction, we make a first assumption of a linear dependence between the radius of emission and the TDC of detection and then refine our result. As it happens, the curvature is minimal and this process converge already on the second iteration. Here are the step of the extraction procedure (we work in a polar coordinate system ($R$,$\phi$), $\Delta\phi$ being the difference between the $\phi$ of the pad measuring a hit and the $\phi$ of the simulated helium):

\begin{figure}[tb]
\centering
%\hspace{-0.95cm}
\includegraphics[scale=0.37]{fig/R_correlation.png}
\caption[]{\small\sf R versus TDC distribution for the simulated hits locating in a single $z$ bin. The maximum $R$ equals 60 mm (close to the anode) at minimum TDCs (Trigger time is 15), and minimum R equals 30 mm (close to the cathode) at maximum TDCs ($\sim75$).}
\label{fig:R_correlation}
\end{figure}

\begin{itemize}
\item The linear assumption between R and time(TDC) is necessary to link the generated hits from GEANT4 to physical hits. Figure \ref{fig:R_correlation} shows our initial $R$ versus TDC. \\
\item For these selected hits, we look at $\Delta\phi$ ($\Delta \phi$ = $\phi_{sim.}$ - $\phi_{hit\_pad}$) versus TDC. We clearly obtain a correlation shown in figure~\ref{fig:1st_pass_delta_phi}. This $\Delta \phi$ change with TDC shows the drift in $phi$ of the electrons due to the Lorentz angle. \\

\begin{figure}[tb]
\centering
\includegraphics[scale=0.37]{fig/1st_pass_delta_phi.png}
\caption[]{\small\sf $\Delta \phi$ versus TDC distribution for the simulated hits locating in one slice centered at 35 mm.}
\label{fig:1st_pass_delta_phi}
\end{figure}

\item Using this first measurement, we can calculate a new correlation between $R$ and TDC. The result, shown in figure~\ref{fig:R_TDC}, is very close to linear explaining the fast convergence of our procedure. \\

\begin{figure}[tb]
\centering
\includegraphics[scale=0.37]{fig/R_TDC.png}
\caption[]{\small\sf The calculated R versus the time is corrected by the parameters of $\Delta \phi$ from the first pass.}
\label{fig:R_TDC}
\end{figure}

\item In the second pass, we associate simulated helium positions to physical hits according to their calculated correlation and obtain new $\Delta \phi$ distributions.\\
\item We finally parametrize the $\Delta\phi$ distributions with a fit as can be seen in figure~\ref{fig:DELTA_PHI_TDC}, which shows the final $\Delta \phi$ versus TDC with a red line representing our drift paths fit.
\end{itemize}

\begin{figure}[tb]
\centering
\includegraphics[scale=0.37]{fig/DELTA_PHI_TDC.png}
\caption[]{\small\sf $\Delta \phi$ versus TDC distribution in the second pass for the slice centered at 35 mm longitudinal position along the RTPC. The red line represents the final drift paths in this slice.}
\label{fig:DELTA_PHI_TDC}
\end{figure}

To verify the stability of the drift paths, this procedure was carried out using both the 1.204 GeV data set from the beginning of the run period and the 1.269 GeV data from the end of the run period. As a result, we found very similar drift paths and reached the conclusion that whatever changed in the setting affected only the drift speed.

\subsection{Gain Calibration}

The parametrization of the drift speed and the drift paths were carried out using only the TDCs, gain calibration goal is to equalize the gains in ADC/MeV over the full RTPC. The gain of each pad is the ratio between the actual deposited energy and the registered ADC value. We identified three different methods to extract such gains. The first is to compare the experimental energy deposit to the expected value calculated from Bethe-Block formula (ref). The second method is to compare the experimental ADCs to the energy deposited in GEANT4 by simulated tracks (using the same elastic events than for the drift paths calibration). In the third method, the ADCs of each pad is compared to the ADCs of the other pads inside each track.

(Detail of 1st method: Nathan)

To perform the second method it requires a very good GEANT4 simulation including drift paths, but also drift and amplification spreads of the charges before reaching the pad, so that the simulated hits match the experimental ones. Moreover, the simulation has to match the data acquisition (DAQ) features that can lead to cutting out hits. After setting the simulation properly, we can compare simulation to data on an event by event basis as in figure~\ref{fig:EVENT_adc_tdc}. In this step, the gain for each pad is defined as the ratio of the measured ADCs to the simulated deposited energy.

(Detail of 3rd method: Mohammad)

\begin{figure}[tb]
\includegraphics[scale=0.350]{fig/EVENT_adc_tdc.png}
\caption[]{\small\sf Simulated (upper) and experimental (lower) ADCs and TDCs distributions of a track. The colors indicate the pads, same color in top and bottom indicate that they are the same pad.}
\label{fig:EVENT_adc_tdc}
\end{figure}

\begin{figure}[tb]
\includegraphics[scale=0.26]{fig/dedx_p_exp_1st.png}
\caption[]{\small\sf $\small{\frac{dE}{dX}}$ vs. p distribution for the left half of the RTPC (left) and for the right half (right). Here, $\small{\frac{dE}{dX}}$ is calculated using the gains of the first method. The lines are theoretical expectations from Bethe-Bloch formula for $^4$He, $^3$He, $^3$H and $^2$H (d).}
\label{fig:dedx_p_exp_1st}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[scale=0.26]{fig/dedx_p_exp_2nd.png}
\caption[]{\small\sf $\small{\frac{dE}{dX}}$ vs. p distribution for the left half of the RTPC (left) and for the right half (right). Here, $\small{\frac{dE}{dX}}$ is calculated using the gains of the second method. The lines are theoretical expectations from Bethe-Bloch formula for $^4$He, $^3$He, $^3$H and $^2$H (d).}
\label{fig:dedx_p_exp_2nd}
\end{figure}

A set of gains has been extracted from each method, in figure~\ref{fig:dedx_p_exp_1st}, we have $\small{\frac{dE}{dX}}$ calculated using the first method's gains, while in Figure~\ref{fig:dedx_p_exp_2nd} we use the second method's gains. From these, we concluded that the gains of the second method match best the theoretical lines. This is not surprising since calibrating with full tracks leads to mixing the gains from the different pads. So it seems that even with several iterations, we could not decipher properly the effects of individual pads with this method.

\subsection{Noise Rejection}

(To be written by Nathan)

\begin{figure}[tb]
\hspace{-0.4cm}
\includegraphics[scale=0.27]{fig/noisy_pad_before_rejection.png}
\caption[]{\small\sf }
\label{fig:noisy_pad_before_rejection}
\end{figure}

\begin{figure}[tb]
\hspace{-0.4cm}
\includegraphics[scale=0.27]{fig/noisy_pad_after_rejection.png}
\caption[]{\small\sf }
\label{fig:noisy_pad_after_rejection}
\end{figure}

\section{Track Reconstruction}

In order to reconstruct tracks we first select good hits. This means rejecting out-of-time hits and hits linked to the electronic noise. The second step is space-reconstructing the hits using the extracted drift speed and drift path parameters. For each registered hit, we calculate a position of emission from the recorded time (TDC) and the position of the recording pad. The third step is to create chains of hits. The maximum distance between two close adjacent hits has to be less than 10.5 mm to chain them, this roughly correspond to neighbors and next to neighbors. Then, we fit the chains that have a minimum of 10 hits. We make the fit in two iterations, first, all the hits of the chain together with the beam line are fitted with a helix. For the second iteration, the hits that are 5 mm or farther from the first fit are excluded.

For the energy deposit, $\frac{dE}{dx}$ is calculated in this way:
\begin{equation}
 \left\langle \frac{dE}{dX} \right\rangle= \frac{\sum\limits_{i} \frac{ADC_{i}}{Gi}}{vtl}
\end{equation}
Where the sum runs over all the hits of the track and $G_{i}$ is the gain of the associated pad. The $vtl$ is the visible track length in the active drift volume.

(We need some performance studies here: Mohammad)

\section{Conclusion}

(TBD)

\begin{thebibliography}{}
\bibitem{CLASref}
B.A. Mecking et al., "The CEBAF large acceptance spectrometer", Nucl. Inst. and Meth. A 503, 513 (2003).

\bibitem{proposal}
K.Hafidi et al., "Deeply virtual Comton scattering off 4He", Jlab proposal to PAC33 (2007).
\bibitem{DCref}
M.D. Mestayer et al., "The CLAS drift chamber System", Nucl. Inst. and Meth. A 449, 81 (2000)

\bibitem{CCref}
G. Adams et al., "The CLAS Cerenkov detector", Nucl. Inst. and Meth. A 465, 414 (2001).

\bibitem{TOFref}E.S. Smith et al., "The time-of-flight system for CLAS", Nucl. Inst. and Meth. A 432, 265 (1999).

\bibitem{ECref}
M. Amarian et al., "The CLAS forward electromagnetic calorimeter", Nucl. Inst. and Meth. A 460, 239 (2001).

\bibitem{BONUS}
S. Tkachenko et al., "Measurement of the nearly free neutron structure function using spectator tagging in inelastic $^{2}H(e,e'p)X$ scattering with CLAS",	Phys. Rev. C 89, 045206 (2014).

\bibitem{MAGBOLTZ}
S. Biagi, "Monte Carlo simulation of electron drift and diffusion in counting gases under the influence of electric and magnetic fields", Nucl. Inst. and Meth. in Phy. Res. A, vol. 421, pp. 234-240, 1999.

\bibitem{GEANT4}
http://geant4.cern.ch

\end{thebibliography}

\end{document}

### 2016-08-17 2nd_round_comments/DVCS-CAN-Meeting-Comments.tex
update the analysis and the answers

@@
 
+  \begin{figure}[tbp]
+    \includegraphics[height=6.6cm]{fig/BSA_ratio_coh_Q2.pdf}
+    \includegraphics[height=6.6cm]{fig/BSA_ratio_coh_x.pdf}
+    \centering
+    \includegraphics[height=6.6cm]{fig/BSA_ratio_coh_t.pdf}
+    \caption{ $A_{LU}$ ratio between $^{4}$He DVCS and free proton at $\phi = 
+    90 ^{\circ}$ as a function of $Q^{2}$, $x_{B}$, and $-t$.}
+    \label{fig:coh-alu-ratios}
+    \end{figure}
+
+ \begin{figure}[tbp]
+    \includegraphics[height=6.6cm]{fig/BSA_ratio_incoh_Q2.pdf}
+    \includegraphics[height=6.6cm]{fig/BSA_ratio_incoh_x.pdf}
+    \centering
+    \includegraphics[height=6.6cm]{fig/BSA_ratio_incoh_t.pdf}
+    \caption{ $A_{LU}$ ratio between bound proton and free proton at $\phi =  
+    90 ^{\circ}$ as a function of $Q^{2}$, $x_{B}$, and $-t$.}
+    \label{fig:incoh-alu-ratios}
+    \end{figure}
+
 \item CFF: the committee acknowledges that the new procedure (2-parameter fit 

### 2016-08-17 analysis-note-v2/results.tex
update the analysis and the answers

@@
 \centering
-\includegraphics[scale=0.42]{fig_ch5/coh_alu_Q2_phi.png} 
-\includegraphics[scale=0.42]{fig_ch5/coh_alu_xB_phi.png}
-\includegraphics[scale=0.42]{fig_ch5/coh_alu_t_phi.png}
+\includegraphics[scale=0.72]{fig_updated/f_coh_alu_Q2_phi.pdf} 
+\includegraphics[scale=0.72]{fig_updated/f_coh_alu_xB_phi.pdf}
+\includegraphics[scale=0.72]{fig_updated/f_coh_alu_t_phi.pdf}
 \caption{The coherent $A_{LU}$ as a function of $\phi$ and $Q^2$ (top panel), 
@@
 \begin{figure}[tpb]
-\includegraphics[scale=0.40]{fig_ch5/incoh_alu_Q2_phi.png}
-\includegraphics[scale=0.40]{fig_ch5/incoh_alu_xB_phi.png}
-\includegraphics[scale=0.40]{fig_ch5/incoh_alu_t_phi.png}
+\includegraphics[scale=0.72]{fig_updated/f_incoh_alu_Q2_phi.pdf}
+\includegraphics[scale=0.72]{fig_updated/f_incoh_alu_xB_phi.pdf}
+\includegraphics[scale=0.72]{fig_updated/f_incoh_alu_t_phi.pdf}
 \caption{The incoherent $A_{LU}$ as a function of the angle $\phi$ in $Q^2$, 
@@
 \vspace{-0.2in}
-\includegraphics[scale=0.37]{fig_ch5/incoh_alu_Q2_90.png} \\
+\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_Q2_90.pdf} \\
 \vspace{-0.1in}
-\includegraphics[scale=0.37]{fig_ch5/incoh_alu_xB_90.png}\\ 
+\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_xB_90.pdf}\\ 
 \vspace{-0.1in}
-\includegraphics[scale=0.37]{fig_ch5/incoh_alu_t_90.png} 
-\caption{The $Q^{2}$ 
-   (top), $x_{B}$ (middle), and $-t$-dependencies (bottom) 
-   of the incoherent $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). Middle panel: 
+\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_t_90.pdf} \caption{The 
+   $Q^{2}$ (top), $x_{B}$ (middle), and $-t$-dependencies (bottom) of the 
+   incoherent $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). Middle panel: 
    the red and the blue curves are theoretical calculations from 
@@
    $-A_{LU}$ (positron beam was used) inclusive measurements \cite{HERMES_BSA}, 
-the colored curves represent theoretical calculations from \cite{simonetta_2}.  
-} \label{fig:incoh_Q2_xB_t_ALU}
+   the colored curves represent theoretical calculations from 
+\cite{simonetta_2}.  } \label{fig:incoh_Q2_xB_t_ALU}
 \end{figure}
@@
 \begin{figure}[h!]
-\hspace{-0.5in}\includegraphics[scale=0.38]{fig_ch5/HA_Q2.png}
-\hspace{-0.3in}\includegraphics[scale=0.38]{fig_ch5/HA_xB.png}
-\centering \includegraphics[scale=0.38]{fig_ch5/HA_t.png}
+\hspace{-0.5in}\includegraphics[scale=0.38]{fig_updated/f_coh_cff_Q2.pdf}
+\hspace{-0.3in}\includegraphics[scale=0.38]{fig_updated/f_coh_cff_xB.pdf}
+\centering \includegraphics[scale=0.38]{fig_updated/f_coh_cff_t.pdf}
 \caption{The model-independent extraction of the imaginary (blue points) and 
@@
 \centering
-\includegraphics[scale=0.38]{fig_ch5/incoh_emc_Q2.png}\\
-\includegraphics[scale=0.38]{fig_ch5/incoh_emc_xB.png}\\
-\includegraphics[scale=0.38]{fig_ch5/incoh_emc_t.png}
+\includegraphics[scale=0.38]{fig_updated/BSA_ratio_coh_Q2.pdf}\\
+\includegraphics[scale=0.38]{fig_updated/BSA_ratio_coh_xB.pdf}\\
+\includegraphics[scale=0.38]{fig_updated/BSA_ratio_coh_t.pdf}
 \caption{ The $A_{LU}$ ratio between the bound and the free proton at 
@@
 \centering
-\includegraphics[scale=0.37]{fig_ch5/coh_emc_Q2.png}\\
-\includegraphics[scale=0.37]{fig_ch5/coh_emc_xB.png}\\
-\includegraphics[scale=0.37]{fig_ch5/coh_emc_t.png}
+\includegraphics[scale=0.37]{fig_updated/BSA_ratio_incoh_Q2.pdf}\\
+\includegraphics[scale=0.37]{fig_updated/BSA_ratio_incoh_xB.pdf}\\
+\includegraphics[scale=0.37]{fig_updated/BSA_ratio_incoh_t.pdf}
 \caption{The $A_{LU}$ ratio between $^4$He and free proton at 

### 2016-08-19 analysis-note-v2/Appendix.tex
updating the RTPC, ch5 and the appendix for the analysis note

@@
 
-\section*{ALU tables}
+\chapter{ALU tables}
 \begin{table}[!h]
@@
          \hline
-         1.143 & 0.136 & 0.096 &  23.32563   &    0.1370716  $\pm$   0.08373948  $\pm$   0.02571563 \\
+         1.143 & 0.136 & 0.096 &  23.32563   &    0.1370716   $\pm$   
+         0.08373948 $\pm$   0.02571563 \\
          1.143 & 0.136 & 0.096 &  59.81847   &    0.3758095  $\pm$   0.07101178  $\pm$   0.01885969 \\
@@
          1.902 & 0.224 & 0.107 &  339.2973   &   -0.184311   $\pm$   0.06150122  $\pm$   0.01635832 \\
-      \hline 
-      \hline
+      \hline \hline
       \end{tabular}
@@
          \hline                                                                         
-
-        1.439 & 0.17 & 0.099 &    21.20114   &    0.1944966  $\pm$   0.06481715    $\pm$   0.023002136   \\
+         1.439 & 0.17 & 0.099 &    21.20114   &    0.1944966  $\pm$   
+         0.06481715    $\pm$   0.023002136   \\
         1.439 & 0.17 & 0.099 &    57.05011   &    0.2135007  $\pm$   0.0688628     $\pm$   0.01959182    \\
@@
         1.439 & 0.17 & 0.099 &    302.6414   &   -0.3697083  $\pm$   0.07362371    $\pm$   0.03312501    \\
-        1.439 & 0.17 & 0.099 &    337.925    &   -0.2626907  $\pm$   0.06672689    $\pm$   0.02543044    \\              
-         \hline
-
-        1.844 & 0.225 & 0.107 &   19.94412   &    0.1199148  $\pm$   0.0610976     $\pm$   0.024893846   \\
+        1.439 & 0.17 & 0.099 &    337.925    &   -0.2626907  $\pm$   0.06672689    
+         $\pm$   0.02543044    \\             
+         \hline                                                                         
+         1.844 & 0.225 & 0.107 &   19.94412   &    0.1199148  $\pm$   0.0610976     
+         $\pm$   0.024893846   \\
         1.844 & 0.225 & 0.107 &   56.1033    &    0.4535308  $\pm$   0.07056983    $\pm$   0.02240954    \\
@@
         1.844 & 0.225 & 0.107 &   340.0658   &   -0.125335   $\pm$   0.06016415    $\pm$   0.01755089    \\
-         \hline  
-         \hline
+         \hline  \hline
       \end{tabular}
@@
  $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
-
-         \hline
-           1.36 & 0.160 & 0.080 &   21.30242  &  0.1531553   $\pm$  0.07225752   $\pm$  0.026305318    \\
+         \hline
+           1.36 & 0.160 & 0.080 &   21.30242  &  0.1531553   $\pm$  0.07225752   
+         $\pm$  0.026305318    \\
            1.36 & 0.160 & 0.080 &   57.11194  &  0.2900274   $\pm$  0.06585235   $\pm$  0.02439207     \\
@@
          \hline                                                                       
-
-           1.610 & 0.193 & 0.127 &  21.08428   & 0.0341355   $\pm$  0.07013161   $\pm$   0.021403381     \\
+         1.610 & 0.193 & 0.127 &  21.08428   & 0.0341355   $\pm$  0.07013161   
+         $\pm$   0.021403381     \\
            1.610 & 0.193 & 0.127 &  59.38832   & 0.4083206   $\pm$  0.07247885   $\pm$   0.02045513      \\
@@
  $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
- \hline  
-  1.395 & 0.166 & 0.407  &   21.10406  &  0.04811468 $\pm$  0.04658231  $\pm$  0.012062557     \\
+ \hline  1.395 & 0.166 & 0.407  &   21.10406  &  0.04811468 $\pm$  0.04658231  
+         $\pm$  0.012062557     \\
   1.395 & 0.166 & 0.407  &   61.33965  &  0.0836005  $\pm$  0.0531715   $\pm$  0.015623204     \\
@@
   1.395 & 0.166 & 0.407  &   303.8597  &  -0.1478417 $\pm$  0.03942399  $\pm$  0.01968592      \\
-  1.395 & 0.166 & 0.407  &   337.5399  &  -0.0844819 $\pm$  0.04879445  $\pm$  0.01425768      \\
- \hline
-
-  1.886 & 0.233 & 0.499 &    20.62881  &  -0.0058365 $\pm$  0.03877985  $\pm$  0.012482536     \\
+  1.395 & 0.166 & 0.407  &   337.5399  &  -0.0844819 $\pm$  0.04879445  $\pm$  
+ 0.01425768      \\
+ \hline                                                                      
+ 1.886 & 0.233 & 0.499 &    20.62881  &  -0.0058365 $\pm$  0.03877985  $\pm$  
+ 0.012482536     \\
   1.886 & 0.233 & 0.499 &    58.90961  &  0.1058029  $\pm$  0.05262749  $\pm$  0.016983385     \\
@@
   3.098 &0.379 & 0.65  &     303.8994  &  -0.178453  $\pm$  0.04217566  $\pm$  0.02211641     \\ 
-  3.098 &0.379 & 0.65  &     340.4588  &  -0.059749  $\pm$  0.03455414  $\pm$  0.01412915     \\ 
- \hline
+  3.098 &0.379 & 0.65  &     340.4588  &  -0.059749  $\pm$  0.03455414  $\pm$  
+ 0.01412915     \\ \hline
  \hline
@@
   2.127 & 0.255 & 0.282  &   95.55563  &  0.22988040   $\pm$ 0.05867932    $\pm$  0.03380763    \\
-  2.127 & 0.255 & 0.282  &   140.5704  &  -0.03154477  $\pm$ 0.08162287    $\pm$  0.0178829     \\
+  2.127 & 0.255 & 0.282  &   140.5704  &  -0.03154477  $\pm$ 0.08162287    
+ $\pm$  0.0178829     \\
   2.127 & 0.255 & 0.282  &   181.2953  &  -0.1565047   $\pm$ 0.10092       $\pm$  0.0298368     \\
@@
  \hline                         
-   2.406 & 0.308 & 0.90 &    20.16669  &  0.01851554   $\pm$ 0.03466921    $\pm$ 0.017815254  \\
-   2.406 & 0.308 & 0.90 &    57.08842  &  0.167122     $\pm$ 0.06853916    $\pm$ 0.01086996   \\
-   2.406 & 0.308 & 0.90 &    93.11341  &  0.07585309   $\pm$ 0.140148      $\pm$ 0.01108901   \\
-   2.406 & 0.308 & 0.90 &    132.8371  &  -0.1390574   $\pm$ 0.4839775     $\pm$ 0.01772069   \\
-   2.406 & 0.308 & 0.90 &    177.344   &  1.854154     $\pm$ 0.5453675     $\pm$ 0.01816686   \\ 
-   2.406 & 0.308 & 0.90 &    228.2105  &  5.778605     $\pm$ 10.58589      $\pm$ 0.01512427   \\
-   2.406 & 0.308 & 0.90 &    263.1194  &  0.02895751   $\pm$ 0.1390042     $\pm$ 0.017122356  \\
-   2.406 & 0.308 & 0.90 &    305.0914  &  -0.1501369   $\pm$ 0.04840413    $\pm$ 0.01297528   \\
-   2.406 & 0.308 & 0.90 &    340.095   &  -0.05253375  $\pm$ 0.03990596    $\pm$ 0.016446498  \\
+   2.406 & 0.308 & 1.107&    20.16669  &  0.01851554   $\pm$ 0.03466921    $\pm$ 0.017815254  \\
+   2.406 & 0.308 & 1.107&    57.08842  &  0.167122     $\pm$ 0.06853916    $\pm$ 0.01086996   \\
+   2.406 & 0.308 & 1.107&    93.11341  &  0.07585309   $\pm$ 0.140148      $\pm$ 0.01108901   \\
+   2.406 & 0.308 & 1.107&    132.8371  &  -0.1390574   $\pm$ 0.4839775     $\pm$ 0.01772069   \\
+   2.406 & 0.308 & 1.107&    177.344   &  1.854154     $\pm$ 0.5453675     $\pm$ 0.01816686   \\ 
+   2.406 & 0.308 & 1.107&    228.2105  &  5.778605     $\pm$ 10.58589      $\pm$ 0.01512427   \\
+   2.406 & 0.308 & 1.107&    263.1194  &  0.02895751   $\pm$ 0.1390042     $\pm$ 0.017122356  \\
+   2.406 & 0.308 & 1.107&    305.0914  &  -0.1501369   $\pm$ 0.04840413    $\pm$ 0.01297528   \\
+   2.406 & 0.308 & 1.107&    340.095   &  -0.05253375  $\pm$ 0.03990596    $\pm$ 0.016446498  \\
  \hline
@@
 \end{table}
+
+\chapter{Free proton beam-spin asymmetry interpolation} 
+\label{app:free-proton-alu}
+Following the discussion in section \ref{sec:Generalized_EMC}, comparing the 
+coherent and the incoherent beam-spin asymmetries to free proton asymmetries 
+reveal new information about the nuclear medium modifications. To construct 
+such ration, the published free proton asymmetries \cite{FX_BSA} have been used 
+in this analysis, see figure \ref{fig:free-proton-alu}. The measured free 
+proton $A_{LU}$ at $\phi = 90^{\circ}$ were fitted as a function of $-t$ in the 
+different bins in $x_B$ and $Q^2$. Then, the parameters of the fits were 
+parametrized as a function of $x_B$ assuming that the dependence on $Q^2$ is 
+negligible, figure \ref{fig:free-proton-alu}. Finally, the free proton 
+asymmetries were calculated at the same incoherent and coherent measured 
+kinematics. The statistical errors on the calculated asymmetries were 
+calculated using the error bars on the fitted parameters $t_{min}$, $p_0$, and 
+$p_1$.\\
+
+\begin{figure}[tpb]
+\centering
+\includegraphics[scale=0.85]{fig_updated/ALU-proton-fits.pdf}
+\caption{Black circles are the free proton beam-spin asymmetries at $\phi = 90 
+^{circ}$ as a function of $-t$ in different ($x_B, Q^2$) bins as measured at 
+CLAS-E1DVCS experiment. The solid red curves are fits to the free proton 
+asymmetries in the form $p_{0}*(t-t_{min})*e^{p_{1}*\sqrt{t}}$. The dashed 
+curves are calculations using the fitted $t_{min}$, $p_0$, and $p_1$ parameters 
+as a function of $x_B$ as shown in figure \ref{fig:fitted-points-xB}. Blue 
+points are the interpolated points corresponding for the incoherent points 
+presented in this analysis. Red points are extrapolated free proton points at 
+the coherent kinematical values.}
+\label{fig:free-proton-alu}
+\end{figure}
+
+\begin{figure}[tpb]
+   \centering
+\includegraphics[scale=0.37]{fig_updated/tmin-xB-fit.png}\\
+\includegraphics[scale=0.37]{fig_updated/p0-xB-fit.png}\\
+\includegraphics[scale=0.37]{fig_updated/p1-xB-fit.png}
+\caption{The fitted $t_{min}$, $p_0$, and $p_1$ parameters as a function of 
+$x_B$.}
+\label{fig:free-proton-alu}
+\end{figure}

### 2016-08-19 analysis-note-v2/RTPC.tex
updating the RTPC, ch5 and the appendix for the analysis note

@@
 \section{RTPC calibration}
-~~~~Reconstructing a trajectory from the recorded time information of the electrons requires a good knowledge of their drift speed and drift paths.
-Also, the gains of the readout pads are required to calculate $\frac{dE}{dx}$ from the recorded ADCs.
-The drift paths and the gain calibration of the RTPC require well identified events, so we decided to use elastic scattering ($e^{4}He \rightarrow e^{4}He$).
-We had specific calibration runs with 1-pass beam energies of 1.024 and 1.269 GeV in order to enhance the cross section of the elastic process at large angles, which is highly suppressed at higher beam energy.\\
+~~~~Reconstructing a trajectory from the recorded time information of the 
+electrons requires a good knowledge of their drift speed and drift paths.  
+Also, the gains of the readout pads are required to calculate $\frac{dE}{dx}$ 
+from the recorded ADCs. The drift paths and the gain calibration of the RTPC 
+require well identified events, so we decided to use elastic scattering 
+($e^{4}He \rightarrow e^{4}He$). We had specific calibration runs with 1-pass 
+beam energies of 1.024 and 1.269 GeV in order to enhance the cross section of 
+the elastic process at large angles, which is highly suppressed at higher beam 
+energy.\\
 
-A GEANT4 simulation for the RTPC has been developed to help reproduce these events in order to properly extract the drift paths and the gains.
-Their extractions are based on comparing the experimentally identified $^4He$ elastic tracks to the GEANT4 simulated ones.
-Indeed, the kinematics of each elastic $^4He$ can be calculated from the electron measured in CLAS and then simulated in GEANT4.
-The output of the simulation is then compared with the measured signals to determine the drift paths.
-\\
+A GEANT4 simulation for the RTPC has been developed to help reproduce these 
+events in order to properly extract the drift paths and the gains. Their 
+extractions are based on comparing the experimentally identified $^4He$ elastic 
+tracks to the GEANT4 simulated ones. Indeed, the kinematics of each elastic 
+$^4He$ can be calculated from the electron measured in CLAS and then simulated 
+in GEANT4. The output of the simulation is then compared with the measured 
+signals to determine the drift paths. \\
 
-This process is iterative since good tracks need to be identified at the beginning of the process.
-For this analysis, we started from a MAGBOLTZ calibration, which was then improved with the method described above with several iterations.
-In particular, changes in the alignment of the RTPC with respect to the beamline, detailed in CLAS-NOTE~\cite{eg6beamoffset}.
-In the following subsections, we present here only the selection of the RTPC tracks and elastic events for the last iteration of our calibration process.
-It is then followed by details on the techniques of calibration.
+This process is iterative since good tracks need to be identified at the 
+beginning of the process. For this analysis, we started from a MAGBOLTZ 
+calibration, which was then improved with the method described above with 
+several iterations. In particular, changes in the alignment of the RTPC with 
+respect to the beamline, detailed in CLAS-NOTE~\cite{eg6beamoffset}. In the 
+following subsections, we present here only the selection of the RTPC tracks 
+and elastic events for the last iteration of our calibration process. It is 
+then followed by details on the techniques of calibration.
 
@@
 
-Because the two modules of the RTPC are electronically separated, we will sometimes show their distributions separately.
-In our angular convention, the right module of the RTPC covers the azimuthal angles between 90$^{\circ}$ and 270$^{\circ}$, while the left-side module covers the rest of the azimuthal angles.
+Because the two modules of the RTPC are electronically separated, we will 
+sometimes show their distributions separately. In our angular convention, the 
+right module of the RTPC covers the azimuthal angles between 90$^{\circ}$ and 
+270$^{\circ}$, while the left-side module covers the rest of the azimuthal 
+angles.
 
-\subsubsection{RTPC good track requirements}
+\subsubsection{RTPC good track requirements} \label{good_track_req}
 
@@
 $\phi^{helix}_{i}$, $z^{helix}_{i}$) is the point on the helix fit that is 
-closest to the reconstructed hit $i$. The resolutions are defined as ($\sigma_{r}$, 
-$\sigma_{\phi}$, $\sigma_{z}$) = (0.53 mm, 2$^{\circ}$, 1.2 mm) based on the size
-of the readout pads were kept identical for all calibration iterations. 
-$N_{pts}$ is the total number of the hits in the chain.  Figure 
-\ref{fig:rrtpc_X2} shows the $\chi^{2}$ distributions for the positive tracks 
-which originate within the RTPC.
+closest, in Euclidean (3D) space, to the reconstructed hit $i$. The resolutions 
+are defined as ($\sigma_{r}$, $\sigma_{\phi}$, $\sigma_{z}$) = (0.53 mm, 
+2$^{\circ}$, 1.2 mm) based on the size
+of the readout pads were kept identical for all calibration iterations. These 
+resolutions were derived by CLAS-BoNus experiment \cite{BONUS}. $N_{pts}$ is 
+the total number of the hits in the chain.  Figure \ref{fig:rrtpc_X2} shows the 
+$\chi^{2}$ distributions for the positive tracks which originate within the 
+RTPC.
 
@@
 
-\item $sdist$ ($\in$ [-2.0,2.0] mm) and $edist$ ($\in$ [-1,5] mm ) cuts: the cuts are applied to ensure that a track is on time, i.e.
-that the first ionization point is close to the cathode and the last point is close to the anode.
-The $sdist$ and $edist$ distributions are shown in figures \ref{fig:rrtpc_sdist} and \ref{fig:rrtpc_edist} respectively\footnote{The long tail on the positive side of the $edist$ distribution is mostly due to electronic noise.
-Note that after applying all the elastic He-4 selection cuts, we observe that most of the tails for both $edist$ and $sdist$ are removed.}.
+\item $sdist$ ($\in$ [-2.0,2.0] mm) and $edist$ ($\in$ [-1,5] mm ) cuts: the 
+   cuts are applied to ensure that a track is on time, i.e. the first 
+   ionization point is close to the cathode and the last point is close to the 
+   anode. For both $sdist$ and $edist$, positive values correspond to tracking 
+   points inside the drift region, while negatives are outside the drift 
+   region. So, in terms of the path length of the track starting from the 
+   vertex, $sdist$ and $edist$ have opposite signs. The $sdist$ and $edist$ 
+   distributions are shown in figures \ref{fig:rrtpc_sdist} and 
+   \ref{fig:rrtpc_edist} respectively\footnote{The long tail on the positive 
+      side of the $edist$ distribution is mostly due to electronic noise.  Note 
+      that after applying all the elastic He-4 selection cuts, we observe that 
+   most of the tails for both $edist$ and $sdist$ are removed.}.
 
-\item Vertex correspondence: the track reconstructed in the RTPC has to originate from the same place as the electron that triggered the event.
-We define $\Delta z$ as the difference between the electron z-vertex and the z-vertex of the RTPC track.
-Due to variations in the electric and the magnetic fields along the 200 cm of length of the RTPC, $\Delta z$ shows a dependence on the longitudinal position along the RTPC ($z_{RTPC}$).
-This can be seen in figure \ref{fig:rrtpc_delta_z}.
-These distributions are fitted to extract the mean and the width of $\Delta z$ as a function of $z_{RTPC}$.
-We then apply a 2$\sigma$ cut around the mean to select the RTPC good tracks.
-The parametrizations of the mean ($\mu$) and the width ($\sigma$) of $\Delta z$ can be found in Appendix \ref{app:RTPC_appendix}.
+\item Vertex correspondence: the track reconstructed in the RTPC has to 
+   originate from the same place as the electron that triggered the event. We 
+   define $\Delta z$ as the difference between the electron z-vertex and the 
+   z-vertex of the RTPC track. Due to variations in the electric and the 
+   magnetic fields along the 200 cm of length of the RTPC, $\Delta z$ shows a 
+   dependence on the longitudinal position along the RTPC ($z_{RTPC}$). This 
+   can be seen in figure \ref{fig:rrtpc_delta_z}. These distributions are 
+   fitted to extract the mean and the width of $\Delta z$ as a function of 
+   $z_{RTPC}$. We then apply a 2$\sigma$ cut around the mean to select the RTPC 
+   good tracks. The parametrizations of the mean ($\mu$) and the width 
+   ($\sigma$) of $\Delta z$ can be found in Appendix \ref{app:RTPC_appendix}.
 
@@
 with the conventions for the variables as in equation \ref{equ:theta_helium}.  
-Figure \ref{fig:W_elastic} shows the W distribution of the events that have a good track in the RTPC and the identified elastic events.
-One can see the good agreement between the helium-4 real mass and the mean value of the identified elastic events.
-The difference in width is related to the different resolutions of the corresponding CLAS sectors.
-The reaction products are emitted back to back resulting in only small regions of overlapping acceptances between the RTPC and CLAS enhancing this effect.
-The reason for this is that local variations of the resolution can be much more important than ones averaged over the full detector.
+Figure \ref{fig:W_elastic} shows the W distribution of the events that have a 
+good track in the RTPC and the identified elastic events. One can see the good 
+agreement between the helium-4 real mass and the mean value of the identified 
+elastic events. The difference in width is related to the different resolutions 
+of the corresponding CLAS sectors. The reaction products are emitted back to 
+back resulting in only small regions of overlapping acceptances between the 
+RTPC and CLAS enhancing this effect. The reason for this is that local 
+variations of the resolution can be much more important than ones averaged over 
+the full detector.
 \\
@@
 electric and magnetic fields within the chamber.
+
+\subsubsection{Checking the initial good track requirements}
+~~~~In this section, we recheck the individual good track requirements 
+presented in section \ref{good_track_req}, where we apply the other good track 
+and elastic requirements and watch the individual variables.
+
+Figure \ref{fig:2-z-vertex} presents the z-vertex distributions of the elastic 
+events, where all the good track and elastic requirements were applied. One 
+sees that the initial [-80:80] mm cuts on the helium z-vertex appear to be 
+suitable cuts to ensure that the reconstructed tracks are within the physical 
+volume of the RTPC.
+\begin{figure}[tp]
+  \centering
+   \includegraphics[scale=0.34]{fig_rtpc/updates/elastic_z_vertex.png}
+\caption{z-vertex distributions for the electrons of the identified elastic 
+events in the two modules of the RTPC.}
+\label{fig:2-z-vertex}
+\end{figure}
+
+In figure \ref{fig:2-r0}, we show the distribution of the radius of curvature 
+for the identified elastic tracks in the RTPC. One sees that applying the other 
+good track and elastic conditions will eliminate all the negative tracks and 
+the tracks with $r_{0}$ less than 30 mm.
+\begin{figure}[tp]
+   \centering
+\includegraphics[scale=0.34]{fig_rtpc/updates/r0_elastic_1p2GeV.png}
+\caption{The radius of curvature distributions of the identified elastic 
+$^{4}$He tracks in the two modules of the RTPC after applying the other good 
+track and elastic events}.
+\label{fig:2-r0}
+\end{figure}
+
+The distributions of $sdist$ and $edist$ for the identified elastic $^4$He 
+elastic tracks, figure \ref{fig:2-sdist-edist}, show that most of the tails, 
+which are mostly due to electronic noise, are removed. Therefore, making 
+tighter cuts would not cause changes in the calibration as the tracks in the 
+tail regions are cleaned by the other good track and elastic cuts.
+
+\begin{figure}[tp]
+\includegraphics[scale=0.34]{fig_rtpc/updates/sdist_elastic_1p2GeV.png}
+\includegraphics[scale=0.34]{fig_rtpc/updates/edist_elastic_1p2GeV.png}
+\caption{ $sdist$ (on left) and $edist$ (on right) distributions for the 
+identified $^4$He elastic tracks in the two modules of the RTPC after applying 
+the other cuts. The vertical dashed red lines indicate the initial cuts were 
+applied to select the good tracks.}
+\label{fig:2-sdist-edist}
+\end{figure}
 
@@
 \subsubsection{Drift paths parametrization}
-~~~~A drift path is the trajectory that an electron follows after being released in the drift region.
-The standard software to calculate these paths is the MAGBOLTZ program \cite{MAGBOLTZ}.
-This program requires precise knowledge of the experimental conditions, such as the detector's geometry, the exact composition of the drift gas and the applied electric and magnetic fields.
-Thus any variation in these conditions would give inaccurate calculated drift paths.
-In the EG6 experiment, MAGBOLTZ has been used to calculate a first set of drift paths, but it was observed for the drift speed that we do not have a perfect knowledge of the RTPC's conditions.
-Therefore, the first set of the drift paths is not accurate.
-For this reason, we chose to calculate the drift paths in a way that does not require an exact knowledge of the conditions in the chamber and is instead based on our experimental data.
-\\
+~~~~A drift path is the trajectory that an electron follows after being 
+released in the drift region. The standard software to calculate these paths is 
+the MAGBOLTZ program \cite{MAGBOLTZ}. This program requires precise knowledge 
+of the experimental conditions, such as the detector's geometry, the exact 
+composition of the drift gas and the applied electric and magnetic fields. Thus 
+any variation in these conditions would give inaccurate calculated drift paths.  
+In the EG6 experiment, MAGBOLTZ has been used to calculate a first set of drift 
+paths, but it was observed for the drift speed that we do not have a perfect 
+knowledge of the RTPC's conditions. Therefore, the first set of the drift paths 
+is not accurate. For this reason, we chose to calculate the drift paths in a 
+way that does not require an exact knowledge of the conditions in the chamber 
+and is instead based on our experimental data.  \\
 

### 2016-08-19 analysis-note-v2/results.tex
updating the RTPC, ch5 and the appendix for the analysis note

@@
 
-Figure \ref{fig:coh_Q2_xB_t_ALU} shows the $Q^2$, $x_{B}$, and $-t$-dependencies of the $\alpha$ term of $A_{LU}$.
-The $x_{B}$ and $-t$-dependencies are compared to theoretical calculations performed by S.
-Liuti and K.
-Taneja.
-Their model relies on the impulse approximation and uses advanced spectral function of the nuclei to calculate the nuclear GPDs and then the observables.
-The calculations were carried out at slightly different kinematics than ours but provide already some guidance.
-The experimental results appear to have larger asymmetries compared to the calculations.
-These differences may arise from nuclear effects which are not taken into account in the model, such as long-range interactions \cite{simonetta_2}.
-Our measurements also agree with those of HERMES, considering their large uncertainties.
-\\
+Figure \ref{fig:coh_Q2_xB_t_ALU} shows the $Q^2$, $x_{B}$, and 
+$-t$-dependencies of the $\alpha$ term of $A_{LU}$. The $x_{B}$ and 
+$-t$-dependencies are compared to theoretical calculations performed by S.  
+Liuti and K. Taneja. Their model relies on the impulse approximation and uses 
+advanced spectral function of the nuclei to calculate the nuclear GPDs and then 
+the observables. The calculations were carried out at slightly different 
+kinematics than ours but provide already some guidance. The experimental 
+results appear to have larger asymmetries compared to the calculations. These 
+differences may arise from nuclear effects which are not taken into account in 
+the model, such as long-range interactions \cite{simonetta_2}. Our measurements 
+also agree with those of HERMES, considering their large uncertainties. \\
 
@@
 
-The theoretical calculations from S.
-Liuti and K.
-Taneja are carried out at slightly different kinematics than our experimental measured values.
-Nevertheless, one can see that our incoherent asymmetries are not well described by these calculations.
-For instance, in the top right plot of figure \ref{fig:incoh_Q2_xB_t_ALU}, even though our asymmetries (at $-t$~=~0.2~GeV$^2$/c$^2$) are located between the model's predictions, which are carried out at $-t$~=~0.095 and 0.329~GeV$^2$/c$^2$, they do not show the drop in $<x_B>$, as the model predicted.
-Similar observation can be seen as a function of $-t$ from the bottom plot.
+The theoretical calculations from S. Liuti and K. Taneja are carried out at 
+slightly different kinematics than our experimental measured values.  
+Nevertheless, one can see that our incoherent asymmetries are not well 
+described by these calculations. For instance, in the top right plot of figure 
+\ref{fig:incoh_Q2_xB_t_ALU}, even though our asymmetries (at 
+$-t$~=~0.2~GeV$^2$/c$^2$) are located between the model's predictions, which 
+are carried out at $-t$~=~0.095 and 0.329~GeV$^2$/c$^2$, they do not show the 
+drop in $<x_B>$, as the model predicted. Similar observation can be seen as a 
+function of $-t$ from the bottom plot.
 
@@
 \begin{figure}[tpb]
-\centering
-\vspace{-0.2in}
-\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_Q2_90.pdf} \\
-\vspace{-0.1in}
-\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_xB_90.pdf}\\ 
-\vspace{-0.1in}
-\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_t_90.pdf} \caption{The 
-   $Q^{2}$ (top), $x_{B}$ (middle), and $-t$-dependencies (bottom) of the 
-   incoherent $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). Middle panel: 
-   the red and the blue curves are theoretical calculations from 
+\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_Q2_90.pdf} 
+\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_xB_90.pdf}
+\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_t_90.pdf} 
+\caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $-t$-dependencies (bottom) of 
+   the incoherent $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). Middle 
+   panel: the red and the blue curves are theoretical calculations from 
    \cite{simonetta_2}. On the bottom: the green circles are the HERMES 
 $-A_{LU}$ (positron beam was used) inclusive measurements \cite{HERMES_BSA}, 
-   the colored curves represent theoretical calculations from 
-\cite{simonetta_2}.  } \label{fig:incoh_Q2_xB_t_ALU}
+the colored curves represent theoretical calculations from \cite{simonetta_2}.  
+} \label{fig:incoh_Q2_xB_t_ALU}
 \end{figure}
@@
 
-\section{Generalized EMC ratios}
+\section{Generalized EMC ratios} \label{sec:Generalized_EMC}
 ~~~~Comparing our measured DVCS channels to the free-proton DVCS reaction 
@@
 \centering
-\includegraphics[scale=0.38]{fig_updated/BSA_ratio_coh_Q2.pdf}\\
-\includegraphics[scale=0.38]{fig_updated/BSA_ratio_coh_xB.pdf}\\
-\includegraphics[scale=0.38]{fig_updated/BSA_ratio_coh_t.pdf}
+\includegraphics[scale=0.38]{fig_updated/BSA_ratio_incoh_Q2.pdf}\\
+\includegraphics[scale=0.38]{fig_updated/BSA_ratio_incoh_xB.pdf}\\
+\includegraphics[scale=0.38]{fig_updated/BSA_ratio_incoh_t.pdf}
 \caption{ The $A_{LU}$ ratio between the bound and the free proton at 
@@
    middle), and $t$ (on the bottom). The black squares are our results, the 
-green circles are the HERMES inclusive measurement \cite{HERMES_BSA} results. 
-The blue and red curves are from an on-shell calculations from S. Liuti and K. Taneja 
-\cite{simonetta_2}.} \label{fig:incoh_EMC_ratio_ALU_proton}
+   green circles are the HERMES inclusive measurement \cite{HERMES_BSA} 
+   results.  The blue and red curves are from an on-shell calculations from S. 
+Liuti and K. Taneja \cite{simonetta_2}.} \label{fig:incoh_EMC_ratio_ALU_proton}
 \end{figure}
@@
 \centering
-\includegraphics[scale=0.37]{fig_updated/BSA_ratio_incoh_Q2.pdf}\\
-\includegraphics[scale=0.37]{fig_updated/BSA_ratio_incoh_xB.pdf}\\
-\includegraphics[scale=0.37]{fig_updated/BSA_ratio_incoh_t.pdf}
+\includegraphics[scale=0.37]{fig_updated/BSA_ratio_coh_Q2.pdf}\\
+\includegraphics[scale=0.37]{fig_updated/BSA_ratio_coh_xB.pdf}\\
+\includegraphics[scale=0.37]{fig_updated/BSA_ratio_coh_t.pdf}
 \caption{The $A_{LU}$ ratio between $^4$He and free proton at 

### 2016-08-23 analysis-note-v2/RTPC.tex
more updates to the second chapter

@@
 \subsubsection{Drift speed parametrization}
-~~~~The electrons follow their drift paths with a certain speed, named drift speed.
-This speed is affected by the experimental conditions, such as the variations in the magnetic field or in the gas composition.
-We can measure this speed using the tracks detected in the RTPC, as it is explained in this section.\\
-
-In our TPC, the electrons released close to the cathode take the maximum drift time ($TDC_{max}$) to reach the readout pads while the geometrical symmetry along the RTPC ensures that these electrons always travel the same distance.
+~~~~The electrons follow their drift paths with a certain speed, named drift 
+speed. This speed is affected by the experimental conditions, such as the 
+variations in the magnetic field or in the gas composition. We can measure this 
+speed using the tracks detected in the RTPC, as it is explained in this 
+section.\\
+
+In our TPC, the electrons released close to the cathode take the maximum drift 
+time ($TDC_{max}$) to reach the readout pads while the geometrical symmetry 
+along the RTPC ensures that these electrons always travel the same distance.  
 Therefore, by identifying the $TDC_{max}$, the drift speed can be deduced.  
-Figure \ref{fig:TDC_profile} shows the time profile of the collected hits for the detected good tracks.
-The experimental drift time ranges between the trigger time (TDC$_{min}$ = 15 TDCs) to 75 TDCs.
-The time profile shows an expected dropping edge at high TDCs due to the geometrical constraints.
-In order to avoid the statistical effects in determining the  $TDC_{max}$, we define a value named as $TDC_{max/2}$ at which the dropping edge passes to half of the maximum number of hits in each hits-time profile.
-$TDC_{max/2}$ is inversely proportional to the drift speed.\\
-
-We measure the $TDC_{max/2}$ along the length of the RTPC to take into account the variations in the electric and magnetic fields.
-The results can be seen in figure \ref{fig:RunNumber_61551_TDCmax_Zslice}, where a clear variation of the drift speed along the RTPC was observed.
-\\
-\begin{figure}[tbp]
+Figure \ref{fig:TDC_profile} shows the time profile of the collected hits for 
+the detected good tracks. The experimental drift time ranges between the 
+trigger time (TDC$_{min}$ = 15 TDCs) to 75 TDCs. The time profile shows an 
+expected dropping edge at high TDCs due to the geometrical constraints. In 
+order to avoid the statistical effects in determining the  $TDC_{max}$, we 
+define a value named as $TDC_{max/2}$ at which the dropping edge passes to half 
+of the maximum number of hits in each hits-time profile. $TDC_{max/2}$ is 
+inversely proportional to the drift speed.\\
+
+We measure the $TDC_{max/2}$ along the length of the RTPC to take into account 
+the variations in the electric and magnetic fields. The results can be seen in 
+figure \ref{fig:RunNumber_61551_TDCmax_Zslice}, where a clear variation of the 
+drift speed along the RTPC was observed. \\ \begin{figure}[tbp]
 \centering
@@
 \includegraphics[scale=0.35]{fig_rtpc/TDC_profile.png}
-\caption{Time profile of the collected hits for the RTPC good tracks in one experimental run, run 61511.
-The $TDC_{max/2}$ is the time at which the dropping edge passes half the maximum number of hits.
-}
+\caption{Time profile of the collected hits for the RTPC good tracks in one 
+   experimental run, run 61511, integrated over the full longitudinal length 
+(z) of the RTPC. The $TDC_{max/2}$ is the time at which the dropping edge 
+passes half the maximum number of hits.}
 \label{fig:TDC_profile}
@@
 
-We also monitor the $TDC_{max/2}$ evolution during the time of the experiment, to take into account variations.
-The EG6 experiment has recorded data with different electron-beam energies: 1.204, 5.7, 6.064 and 1.269 GeV.
-The 5.7 and 6.064 data sets have low elastic cross sections compared to the 1.206 and 1.269 data sets.
-For this reason, we use all the RTPC good tracks and not only the elastic ones for these.
-Before checking the stability of $TDC_{max/2}$ over the experimental running period, we want to check the feasibility of using all good tracks for the purpose of parametrizing the drift speed.
-In this check, the $TDC_{max/2}$ identified using the good tracks of the 1.206-GeV data set is compared to the one identified from the elastic events of the same data sets.
-The result is shown in figure \ref{fig:TDCmax_ratio}, in which the ratio between the two $TDC_{max/2}$ is plotted as a function of the longitudinal position along the RTPC.
-This ratio is consistent with 1, within 1$\%$.
-Thus we can conclude that using the hits of the collected good tracks is a good approximation.
-\\
-
-\begin{figure}[tp]
+We also monitor the $TDC_{max/2}$ evolution during the time of the experiment, 
+to take into account variations. The EG6 experiment has recorded data with 
+different electron-beam energies: 1.204, 5.7, 6.064 and 1.269 GeV. The 5.7 and 
+6.064 data sets have low elastic cross sections compared to the 1.206 and 1.269 
+data sets. For this reason, we use all the RTPC good tracks and not only the 
+elastic ones for these. Before checking the stability of $TDC_{max/2}$ over the 
+experimental running period, we want to check the feasibility of using all good 
+tracks for the purpose of parametrizing the drift speed. In this check, the 
+$TDC_{max/2}$ identified using the good tracks of the 1.206-GeV data set is 
+compared to the one identified from the elastic events of the same data sets.  
+The result is shown in figure \ref{fig:TDCmax_ratio}, in which the ratio 
+between the two $TDC_{max/2}$ is plotted as a function of the longitudinal 
+position along the RTPC. This ratio is consistent with 1, within 1$\%$. Thus we 
+can conclude that using the hits of the collected good tracks is a good 
+approximation. \\
+
+\begin{figure}[tpb]
 \begin{minipage}[c]{.46\linewidth}
@@
 \includegraphics[height=9.5cm]{fig_rtpc/RunNumber_61551_TDCmax_Zslice.png}
-\caption{$TDC_{max/2}$ variation as a function of the longitudinal position along the RTPC in one experimental run, 61510.} 
+ \caption{$TDC_{max/2}$ variation as a function of the longitudinal position 
+ along the RTPC, $z$ position of the hit, in one experimental run, 61510.} 
  \label{fig:RunNumber_61551_TDCmax_Zslice}
@@
 \includegraphics[height=9.0cm]{fig_rtpc/TDCmax_ratio_final.png}
-\caption{Ratio between $TDC_{max/2}$ extracted using the RTPC good tracks and the one extracted using the clean elastic events, both from the 1.204-GeV dataset.}
+\caption{Ratio between $TDC_{max/2}$ extracted using the RTPC good tracks and 
+the one extracted using the clean elastic events, both from the 1.204-GeV 
+dataset, as function of the hit position ($z$).}
 \label{fig:TDCmax_ratio}
@@
 
-The variations with time of $TDC_{max/2}$ are shown in figure \ref{fig:Drift_run_number}, in which each point is a run of about two hours of data taking.
-One can see a non-negligible variation over the three months of data taking due to the changes in the experimental conditions.
-The main cause of these variations is probably the variation of proportions in the drift gas mixture which was not perfectly under control due to leaks in the thin parts of the detector.\\
-
-As $TDC_{max/2} -15 $ ($= 
-\frac{Drift~path~length}{Drift~speed}$) varies with both run number (time) and 
-the geometry of the RTPC ($z$ along the RTPC). We
-parametrize the dependence on $z$ for each run in the form:\\
+The variations with time of $TDC_{max/2}$ are shown in figure 
+\ref{fig:Drift_run_number}, in which each point is a run of about two hours of 
+data taking. One can see a non-negligible variation over the three months of 
+data taking due to the changes in the experimental conditions. The main cause 
+of these variations is probably the variation of proportions in the drift gas 
+mixture which was not perfectly under control due to leaks in the thin parts of 
+the detector.\\
+
+As $TDC_{max/2} -15 $ ($= \frac{Drift~path~length}{Drift~speed}$) varies with 
+both run number (time) and the geometry of the RTPC ($z$ along the RTPC). We
+parametrize the dependence on $z$, hit (pad) position, for each run in the 
+form:\\
 \begin{equation}
@@
 \end{equation}
-Then fits are performed for these parameters as functions of the run number, such that the drift speed parametrization depends on the run and $z$ along the RTPC.
-The numeric parametrizations of $p_{0}$, $p_{1}$, $p_{2}$, and $p_{3}$ can be found in Appendix \ref{app:RTPC_appendix}, table \ref{Table:TDCmax}.
-\\
+Then fits are performed for these parameters as functions of the run number, 
+such that the drift speed parametrization depends on the run and $z$ along the 
+RTPC. The numeric parametrizations of $p_{0}$, $p_{1}$, $p_{2}$, and $p_{3}$ 
+can be found in Appendix \ref{app:RTPC_appendix}, table \ref{Table:TDCmax}. \\
 
@@
 
-\begin{figure}[tp]
+\begin{figure}[tpb]
 \hspace{-0.3in}
-\includegraphics[scale=0.45]{fig_rtpc/Drift_run_number.png}
+\includegraphics[scale=0.9]{fig_rtpc/updates/TDCmax2-run-number.pdf}
 \caption{ The integrated $TDC_{max/2}$ over the full z-RTPC as a function of 
@@
 
-In our alternative method, we use the identified elastic ($e ~ ^{4}He \rightarrow e ~ ^{4}He$) events to extract the drift paths.
-For these events, the kinematics of the recoil $^{4}He$ are calculated from the scattered electron.
-Then the electrons' drift paths can be extracted from comparing the experimentally measured hits in the RTPC to the trajectory of a similar simulated $^{4}He$.
-In this technique, the drift paths are obtained independently of our knowledge of the exact conditions in the RTPC, in particular the electric field and the gas mixture have no impact.
-\\
+In our alternative method, we use the identified elastic ($e ~ ^{4}He 
+\rightarrow e ~ ^{4}He$) events to extract the drift paths. For these events, 
+the kinematics of the recoil $^{4}He$ are calculated from the scattered 
+electron. Then the electrons' drift paths can be extracted from comparing the 
+experimentally measured hits in the RTPC to the trajectory of a similar 
+simulated $^{4}He$. In this technique, the drift paths are obtained 
+independently of our knowledge of the exact conditions in the RTPC, in 
+particular the electric field and the gas mixture have no impact. \\
 
@@
 \end{equation}
-We apply 3 TDCs-wide windows around the linear R-TDC correlation to associate the 
-GEANT4 simulated hits to measured hits.
+We apply 3 TDCs-wide windows around the linear R-TDC correlation to associate 
+the GEANT4 simulated hits to measured hits. Figure \ref{fig:R_correlation} 
+shows the distribution of $R$ versus TDC for the selected simulated hits in a 
+single $z$ bin.
 
@@
 
-\begin{figure}[tp]
+\begin{figure}[tpb]
+\centering
+\includegraphics[scale=0.45]{fig_rtpc/updates/TdcR_check_p1_10.png}
+\caption{(First pass). Distribution of $R$ as a function of TDC for the 
+simulated hits located in one $z$ bin. The width of the bin is 10 mm, with the 
+center at $z$ = 5 mm.}
+\label{fig:R_correlation}
+\end{figure}
+
+\begin{figure}[tpb]
 \centering
@@
 \includegraphics[scale=0.45]{fig_rtpc/TdcR_p2_10.png}
-\caption{(Second pass). The calculated R as a function of TDC is corrected by the $\Delta \phi$ relation extracted from the first pass.}
+\caption{(Second pass). The calculated R as a function of TDC is corrected by 
+the $\Delta \phi$ relation extracted from the first pass.}
 \label{fig:R_TDC}
@@
 
-We performed a third pass in which the R(TDC) correlation is refined using the drift paths from the second pass and new drift paths were extracted.
-As a result, we observed no difference between the drift paths of the second and the third passes.
-In other words, extracting the drift paths from two iterations gives us stable drift paths.
-\\
-
-The first drift paths were extracted using the elastic events from the early 1.204 GeV dataset.
-In order to ensure the consistency of these drift paths over the experimental running period, we extracted another set of drift paths using the elastic events of the 1.269 GeV runs.
-We observed no difference between the two sets of the drift paths, ensuring their stability over the experimental period and leaving the dependence on the TDC and $z$.
-The final drift paths are extracted using both datasets, 1.204 and 1.269 GeV.
-They take the form:
+We performed a third pass in which the R(TDC) correlation is refined using the 
+drift paths from the second pass and new drift paths were extracted. As a 
+result, we observed no difference between the drift paths of the second and the 
+third passes. In other words, extracting the drift paths from two iterations 
+gives us stable drift paths. \\
+
+The first drift paths were extracted using the elastic events from the early 
+1.204 GeV dataset. In order to ensure the consistency of these drift paths over 
+the experimental running period, we extracted another set of drift paths using 
+the elastic events of the 1.269 GeV runs. We observed no difference between the 
+two sets of the drift paths, ensuring their stability over the experimental 
+period and leaving the dependence on the TDC and $z$. The final drift paths are 
+extracted using both datasets, 1.204 and 1.269 GeV. They take the form:
 \vspace{-0.1in}
@@
 \end{equation}
-where the parameters, $p_{0}$, $p_{1}$, $p_{2}$, $p_{3}$ and $p_{4}$ are functions of $z$, as can be seen in Appendix \ref{app:RTPC_appendix}, table \ref{table:drift_paths}.
-The final drift paths are implemented in our reconstruction codes such that the reconstructed position of each hit becomes:
+where the parameters, $p_{0}$, $p_{1}$, $p_{2}$, $p_{3}$ and $p_{4}$ are 
+functions of $z$, as can be seen in Appendix \ref{app:RTPC_appendix}, table 
+\ref{table:drift_paths}. The final drift paths are implemented in our 
+reconstruction codes such that the reconstructed position of each hit becomes:
 \begin{equation}
@@
 
-~~~~It is important to note that the drift paths have shown strong sensitivity to the other RTPC calibrations.
-Therefore, we performed iterative extractions of the drift paths and, as a results, obtained more good tracks with a signal to background ratio largely improved.
-Figure \ref{fig:sdist_comp_pass1v1_v6} shows an illustration of the improvements in terms of the $sdist$ parameter using the same initial collected data with an old drift paths and a newer set.
+~~~~It is important to note that the drift paths have shown strong sensitivity 
+to the other RTPC calibrations. Therefore, we performed iterative extractions 
+of the drift paths and, as a results, obtained more good tracks with a signal 
+to background ratio largely improved. Figure \ref{fig:sdist_comp_pass1v1_v6} 
+shows an illustration of the improvements in terms of the $sdist$ parameter 
+using the same initial collected data with an old drift paths and a newer set.
 
@@
 \includegraphics[scale=0.38]{fig_rtpc/sdist_comp_pass1_v1_v6.png}
-\caption{The $sdist$ distribution for the collected tracks in the RTPC using the same initial collected data with an old set of drift paths, on the left, and a newer set, on the right.}
+\caption{The $sdist$ distribution for the collected tracks in the RTPC using 
+the same initial collected data with an old set of drift paths, on the left, 
+and a newer set, on the right.}
 \label{fig:sdist_comp_pass1v1_v6}
@@
 a similar extraction in the BoNuS analysis note \cite{GEM_holes}.
-Then, we improved this first result with many iterations after
-each change that would affect the drift paths, such as the beam-offset
- and gain calibrations of the RTPC. Moreover after each pass, the number of
- elastic events used for calibration increased, justifying by itself a new calibration. Overall, this was a long
- process that evolved and improved over the years and we concentrated in the
- note on the description of the final iteration of this calibration.
+Then, we improved this first result with many iterations after each change that 
+would affect the drift paths, such as the beam-offset and gain calibrations of 
+the RTPC. Moreover after each pass, the number of elastic events used for 
+calibration increased, justifying by itself a new calibration. Overall, this 
+was a long process that evolved and improved over the years and we concentrated 
+in the note on the description of the final iteration of this calibration.
 
 \subsection{Gain calibration}
-The second important calibration is the amplitude of the signal provided in ADC units.
-Since each charged particle deposits a certain amount of energy ($\small{\frac{dE}{dX}}$) when crossing a material, we can identify particles based on this variable.
-The ($\small{\frac{dE}{dX}}$) depends on the characteristics of the particle, such as its energy, mass and charge, and the nature of the medium as well.
-\\
+The second important calibration is the amplitude of the signal provided in ADC 
+units. Since each charged particle deposits a certain amount of energy 
+($\small{\frac{dE}{dX}}$) when crossing a material, we can identify particles 
+based on this variable. The ($\small{\frac{dE}{dX}}$) depends on the 
+characteristics of the particle, such as its energy, mass and charge, and the 
+nature of the medium as well. \\
 
@@
 \begin{eqnarray}
- \left\langle \frac{dE}{dX} \right\rangle &=& \rho K z^{2} \frac{Z}{A} \frac{1}{\beta^{2}} \left[ \frac{1}{2} ln \left(\frac{2m_{e}c^{2}\beta^{2}\gamma^{2}T_{max}}{I_{max}} \right) - \beta^{2} -\frac{\delta\beta\gamma}{2}\right]\\
+\left\langle \frac{dE}{dX} \right\rangle &=& \rho K z^{2} \frac{Z}{A} 
+   \frac{1}{\beta^{2}} \left[ \frac{1}{2} ln 
+   \left(\frac{2m_{e}c^{2}\beta^{2}\gamma^{2}T_{max}}{I_{max}} \right) - 
+\beta^{2} -\frac{\delta\beta\gamma}{2}\right]\\
 \text{with }
@@
 \end{eqnarray}
-where $T_{max}$ is the maximum kinetic energy of a free electron in a single collision, and $z$, $M$, $\beta$ are the charge, mass and speed (=$p/ \sqrt{M^2 + p^2}$, where $p$ is the momentum) of the particle, respectively.
-$m_{e}$ is the electron mass and the constant $K$ is equal to $4 \pi N_{A} r^{2}_{e}m_{e}c^{2}$ = 0.307075 MeV mol$^{-1}$ cm$^{2}$.
-$Z$, $A$, $I$, $\rho$ are the effective charge, atomic number, mean excitation energy and mass density of the medium.
-In the RTPC, these constants are equal to 66, 126.79 mg mol$^{-1}$, 99.79 eV and 1.03 mg/cm$^3$, respectively.
-\\
+where $T_{max}$ is the maximum kinetic energy of a free electron in a single 
+collision, and $z$, $M$, $\beta$ are the charge, mass and speed (=$p/ \sqrt{M^2 
++ p^2}$, where $p$ is the momentum) of the particle, respectively.  $m_{e}$ is 
+the electron mass and the constant $K$ is equal to $4 \pi N_{A} 
+r^{2}_{e}m_{e}c^{2}$ = 0.307075 MeV mol$^{-1}$ cm$^{2}$. $Z$, $A$, $I$, $\rho$ 
+are the effective charge, atomic number, mean excitation energy and mass 
+density of the medium. In the RTPC, these constants are equal to 66, 126.79 mg 
+mol$^{-1}$, 99.79 eV and 1.03 mg/cm$^3$, respectively. \\
 
@@
 \end{equation}
-where the sum runs over all the pads contributing to a track.
-$ADC_{i}$ is the recorded amplitude in each pad $i$, and $G_{i}$ is its gain.
-The $vtl$ is the total visible length of the track in the active drift volume.
-This is of course assuming the energy loss in the drift region is small in regard to the total energy of the particle, which is true except close to our detection threshold.\\
-
-The electron collection system of the RTPC has 3200 readout pads.
-The gain of each pad is the ratio between the deposited energy and the output recorded value.
-We extracted the gains using two techniques.
-The first one is by comparing the experimental recorded $\small{\frac{dE}{dX}}$ to the expected values calculated from the Bethe-Bloch formula.
-The second technique is based on comparing the experimental ADCs to the GEANT4 simulated ones, track by track.
-We latter refined this second method by comparing the ADCs of each pad to the average ADCs of the other pads in the same track.\\
+where the sum runs over all the pads contributing to a track. $ADC_{i}$ is the 
+recorded amplitude in each pad $i$, and $G_{i}$ is its gain. The $vtl$ is the 
+total visible length of the track in the active drift volume. This is of course 
+assuming the energy loss in the drift region is small in regard to the total 
+energy of the particle, which is true except close to our detection 
+threshold.\\
+
+The electron collection system of the RTPC has 3200 readout pads. The gain of 
+each pad is the ratio between the deposited energy and the output recorded 
+value. We extracted the gains using two techniques. The first one is by 
+comparing the experimental recorded $\small{\frac{dE}{dX}}$ to the expected 
+values calculated from the Bethe-Bloch formula. The second technique is based 
+on comparing the experimental ADCs to the GEANT4 simulated ones, track by 
+track. We latter refined this second method by comparing the ADCs of each pad 
+to the average ADCs of the other pads in the same track.\\
 
@@
 
-~~~~The second method requires improvements in the simulation, in order to match the real experiment. In summary, these improvements are:
+~~~~The second method requires improvements in the simulation, in order to 
+match the real experiment. In summary, these improvements are:
 \begin{itemize}
-\item Implementation in the simulation of the previously extracted parametrizations of the drift speed and the drift paths.
-\item Global ADC normalization to give reasonable simulated values. In the left module, 1 ADC is equal to 
-17 eV, while it is equal to 21 eV in the right module. These normalizations were extracted from the comparison of the data to the GEANT4 simulation.
-\item Rejection of the signals from bad pads.
-During the experiment, the readout system of the RTPC suffered from 555 dead or noisy pads.
-These pads are marked by the dotted squares in figure \ref{fig:pad_row_col}.
-\item Smearing the position of the simulated hits.
-Experimentally, the average number of hits per track is around 80 while the initially reconstructed mean value from the simulation is around 50.
-We apply a Gaussian smearing on the position of the simulated hits to make the simulation more realistic, see figure \ref{fig:NNb_hits}.
-
-\item Application of the TPC's DAQ cut on the simulated data.
-Experimentally, each pad must have at least 3 consecutive time bins, with ADC values above the threshold, 35 ADCs, in order to be recorded.
-Then, the hits of three neighboring bins on each side of the above threshold bins are also recorded, while the other hits are not.
+\item Implementation in the simulation of the previously extracted 
+   parametrizations of the drift speed and the drift paths.
+\item Global ADC normalization to give reasonable simulated values. In the left 
+   module, 1 ADC is equal to 17 eV, while it is equal to 21 eV in the right 
+   module. These normalizations were extracted from the comparison of the data 
+   to the GEANT4 simulation.
+\item Rejection of the signals from bad pads. During the experiment, the 
+   readout system of the RTPC suffered from 555 dead or noisy pads. These pads 
+   are marked by the dotted squares in figure \ref{fig:pad_row_col}.
+\item Smearing the position of the simulated hits. Experimentally, the average 
+   number of hits per track is around 80 while the initially reconstructed mean 
+   value from the simulation is around 50. We apply a Gaussian smearing on the 
+   position of the simulated hits to make the simulation more realistic, see 
+   figure \ref{fig:NNb_hits}.  
+\item Application of the TPC's DAQ cut on the simulated data. Experimentally, 
+   each pad must have at least 3 consecutive time bins, with ADC values above 
+   the threshold, 35 ADCs, in order to be recorded. Then, the hits of three 
+   neighboring bins on each side of the above threshold bins are also recorded, 
+   while the other hits are not.
 \end{itemize}
 
-\begin{figure}[tp]
-\centering
-\includegraphics[scale=0.40]{fig_rtpc/NNb_hits.png}
-\caption{The distributions of the number of hits per track.
-The black, the blue and the red distributions are the number of hits per track  for respectively, the experimental data, simulation before smearing and the simulation with smearing.}
+\begin{figure}[tpb]
+\centering
+\includegraphics[scale=0.35]{fig_rtpc/NNb_hits.png}
+\caption{The distributions of the number of hits per track. The black, the blue 
+and the red distributions are the number of hits per track  for respectively, 
+the experimental data, simulation before smearing and the simulation with 
+smearing.}
 \label{fig:NNb_hits}
@@
 To illustrate the procedure of comparing simulated tracks with real tracks,
-we show in Figure \ref{fig:EVENT_adc_tdc} the simulated ADCs and the 
-experimental ones as a function of the TDCs for the same track. 
-Then, the gain of each pad can be obtained as the ratio of the mean experimental 
-ADCs to the one of the simulated track. For each pad, these gain 
-ratios were collected from all the identified elastic events and fitted by a 
-Landau function to obtain their gains.
-
-As mentionned earlier, we refine this calibration after 
-the extracted gains are applied to the experimental data. We compare the ratio between the 
-mean ADCs of each pad to the mean ADCs of the whole track. This ratio is 
-collected from all the elastic events and a gain correction factor is extracted 
-for each pad. The final gains of the second method are obtained with the application of 
-this extra correction.\\
-
-\begin{figure}[tp]
+we show in Figure \ref{fig:EVENT_adc_tdc} the simulated and the experimental 
+ADCs as a function of the TDCs for the same track. Then, the gain of each pad 
+is defined as the ratio between the mean recorded experimental ADCs to the mean 
+simulated ADCs in the same track. Then for each pad, the gain ratios were 
+collected from all the identified elastic tracks and these gains were fitted by 
+a Landau function to give a first pass gain for each pad as the most probable 
+value of the fit.
+
+\begin{figure}[tpb]
 \centering
 \vspace{-0.1in}
-\includegraphics[scale=0.350]{fig_rtpc/EVENT_adc_tdc.png}
-\caption{The simulated (top) and the experimental (bottom) ADCs versus TDC distributions for the same track.
-The same colors indicate hits that were registered in the same channel for the simulation and the experiment.}
+\includegraphics[scale=0.320]{fig_rtpc/EVENT_adc_tdc.png}
+\caption{The simulated (top) and the experimental (bottom) ADCs versus TDC 
+distributions for the same track. The same colors indicate hits that were 
+registered in the same channel for the simulation and the experiment.}
 \label{fig:EVENT_adc_tdc}
@@
 
-As the two modules of the RTPC are electronically separated, we look at their calibrations separately.
-Figure \ref{fig:dedx_p_exp_2nd} shows the ratio between the calculated $\small{\frac{dE}{dX}}$, using the gains of both methods, and the GEANT4 simulated $\small{\frac{dE}{dX}}$ for the elastic events in the two modules of the RTPC.
-We conclude that extracting the gains from comparing data to simulation in terms of the ADCs of the individual tracks gives more precise gains than solving the series of equations.
-Figure \ref{fig:pad_row_col} shows the gains from the second method, where the dotted squares refer to the dead or noisy pads.
-These are the ones that are implemented in the EG6 reconstruction codes.\\
-
-\begin{figure}[tbp]
-\centering
-\includegraphics[scale=0.400]{fig_rtpc/dedx_p_sim_exp_2nd.png}
-\caption{The ratio between the experimental $dE/dx$, using the gains obtained with the two methods (1$^{st}$ in blue, and 2$^{nd}$ in black), to the GEANT4 simulated $dE/dx$, plotted for the two modules of the RTPC, respectively left and right.
-}
-\label{fig:dedx_p_exp_2nd}
-\end{figure}
+To make sure that the recorded ADCs by a given pad are similar to the recorded 
+ADCs by other pads in the same track, we refined this calibration after the 
+extracted gains were applied to the experimental data. At this step, we 
+compared the mean ADCs of each pad to the mean ADCs of the whole track. This 
+ratio is collected from all the elastic events and a gain correction factor is 
+extracted and applied to get a final gain for each pad, labeled as second pass 
+gain in figure \ref{fig:dedxre}.
+
+As the two modules of the RTPC are electronically separated, we look at their 
+calibrations separately. Figure \ref{fig:dedxre} shows the ratio between the 
+calculated $\small{\frac{dE}{dX}}$, using the gains extracted from first and 
+the second (both passes) meothods, and the GEANT4 simulated 
+$\small{\frac{dE}{dX}}$ for the elastic events in the two modules of the RTPC.  
+From the latter figure, one can see improvments obtained by using this method 
+to fine tune the gains extracted only by comparing data to simulation. We 
+conclude that extracting the gains from comparing data to simulation in terms 
+of the ADCs of the individual tracks gives more precise gains than solving the 
+series of equations. Figure \ref{fig:pad_row_col} shows the gains from the 
+second method, where the dotted squares refer to the dead or noisy pads. These 
+are the ones that are implemented in the EG6 reconstruction codes.\\
+
+\begin{figure}[tpb]
+\hspace{-0.5 cm}
+\includegraphics[height=11.5cm]{fig_rtpc/updates/dedx_ratio_elastic_NAB.png}
+\caption{The ratio between the experimental dEdx and the simulated ones for 
+   different regions along $z$ for the two modules of the RTPC, right module on 
+   top panel and left module on bottom panel. The blue lines are using the 
+   first method of extracting the gains (comparing the experimental recorded 
+   dEdx to the expected values calculated from the Bethe-Block formula). The 
+green lines are using the fist pass of the second method (comparing simulation 
+to data only) with all the elastic event sample. The brown lines are using the 
+final gains extracted from the second method (both passes).}
+\label{fig:dedxre}
+\end{figure}
+
+%\begin{figure}[tbp]
+%\centering
+%\includegraphics[scale=0.400]{fig_rtpc/dedx_p_sim_exp_2nd.png}
+%\caption{The ratio between the experimental $dE/dx$, using the gains obtained 
+%with the two methods (1$^{st}$ in blue, and 2$^{nd}$ in black), to the GEANT4 
+%simulated $dE/dx$, plotted for the two modules of the RTPC, respectively left 
+%nd right. }
+%\label{fig:dedx_p_exp_2nd}
+%\end{figure}
 
@@
 \includegraphics[scale=0.300]{fig_rtpc/pad_row_col.png}
-\caption{The extracted gains from the second method. The dotted squares refer to the position of the excluded pads.}
+\caption{The extracted gains from the second method. The dotted squares refer 
+to the position of the excluded pads.}
 \label{fig:pad_row_col}
@@
 \includegraphics[scale=0.4]{fig_rtpc/Chan_706_2.png}
-\caption{The average ADC vs.
-TDC distributions of the experimental hits recorded for the elastic events in one pad of the left module, pad number 706.
-On the top: the distribution for the elastic tracks in the region where dEdx$_{exp}$/dEdx$_{sim} $ $\sim$ 1.
-On the bottom: the distribution for the elastic tracks that exhibit dEdx$_{exp}$/dEdx$_{sim} $ $\sim$ 0.3.}
+\caption{The average ADC vs. TDC distributions of the experimental hits 
+   recorded for the elastic events in one pad of the left module, pad number 
+   706.  On the top: the distribution for the elastic tracks in the region 
+   where dEdx$_{exp}$/dEdx$_{sim} $ $\sim$ 1. On the bottom: the distribution 
+for the elastic tracks that exhibit dEdx$_{exp}$/dEdx$_{sim} $ $\sim$ 0.3.}
 \label{fig:Chann_706}
@@
 
-To check the validity of the extracted gains, we show $\small{\frac{dE}{dX}}$ versus the momentum (per charge unit) measured in the RTPC for all the collected tracks of the 1.206 GeV data set.
-In the plots, we add the theoretical lines derived from the Bethe-Bloch formula for possible detected particles: $^4He$, $^3He$, $^3H$, Deuterium (d) and the protons.
-\begin{figure}[tbp]
-\includegraphics[scale=0.35]{fig_rtpc/dedx_p_l.png}
-\includegraphics[scale=0.35]{fig_rtpc/dedx_p_r.png}
+To check the validity of the extracted gains, we show $\small{\frac{dE}{dX}}$ 
+versus the momentum (per charge unit) measured in the RTPC for all the 
+collected tracks of the 1.206 GeV data set. In the plots, we add the 
+theoretical lines derived from the Bethe-Bloch formula for possible detected 
+particles: $^4He$, $^3He$, $^3H$, Deuterium (d) and the protons.
+\begin{figure}[tbp]
+\includegraphics[scale=0.35]{fig_rtpc/updates/dedx_p_l.png}
+\includegraphics[scale=0.35]{fig_rtpc/updates/dedx_p_r.png}
 \caption{The experimental $\small{\frac{dE}{dX}}$ calculated using the second method gains versus $p/q$ of all the collected good tracks in the RTPC in the early 1.204 GeV dataset.}

### 2016-08-23 analysis-note-v2/RTPC.tex
more updates to the RTPC and the DVCS checks, and updated the ALU tables after the 4D background subtraction

@@
 \begin{itemize}
-\item The target extends along the RTPC's central z-axis, with a diameter of 6 mm. It is enclosed in a 27-$\mu$m-thick Kapton wall.
-
-\item The first gas gap extends from 3 mm to 20 mm radial distances.
-It is filled with $^{4}He$ gas at one atmospheric pressure.
-This region is swarmed with M\o ller electrons induced by the beam, but filling this region with a light gas like $^{4}He$ at low pressure minimizes their secondary interactions, while the magnetic field of the solenoid keeps them away from the sensitive drift region.
-This gap is surrounded by a grounded window made of 4-$\mu$m-thick aluminized mylar.
-
-\item The second gas gap extends from 20 mm to 30 mm radial distances and is filled with a gas mixture of 80$\%$ Neon (Ne) and 20$\%$ Dimethyl Ether (DME: $C_{2}H_{6}O$).
-This drift gas fills all the following gaps up to the external shell.
-
-\item The cathode foil, which is made of 4-$\mu$m-thick aluminized mylar, surrounds the second gas gap. It is connected to a voltage of 4.3 kV to generate an electric field in the drift region.
-
-\item The drift region is filled with the Ne-DME gas mixture. It extends from the cathode, 30 mm from the beam line, to the first gas electron multiplier layer, 60 mm from the beam line.
-
-\item The amplification system is composed of three Gas Electron Multiplier (GEM) layers located at radii of 60 mm, 63 mm, and 66 mm.
-
-\item The electron collection system has an internal radius of 69 mm and collects the charges. The data are then pre-amplified and transmitted to the data acquisition system.  
-\end{itemize}
-
-The Ne-DME gas mixture has been chosen as the drift gas because of its low-diffusion characteristics and small Lorentz angles (the angles between the drift direction of electrons under the influence of magnetic field and the direction of the electric field).
-These characteristics minimize the changes in the drift velocity of the ionization electrons \cite{DME}.\\
-
-The GEMs amplify the ionized electrons to produce measurable signals.
-Figure \ref{fig:GEMs} shows a microscopic photo of a GEM.
-It is made from an insulator (Kapton) sandwiched between two copper layers.
-The mesh of each GEM layer is chemically etched with 50-$\mu$m-diameter holes in double-conical cross section shapes, as can be seen from the schematic plot on the right.\\
+ \item The target extends along the RTPC's central z-axis, with a diameter of 6 
+    mm. It is enclosed in a 27-$\mu$m-thick Kapton wall.
+
+ \item The first gas gap extends from 3 mm to 20 mm radial distances. It is 
+    filled with $^{4}He$ gas at one atmospheric pressure. This region is 
+    swarmed with M\o ller electrons induced by the beam, but filling this 
+    region with a light gas like $^{4}He$ at low pressure minimizes their 
+    secondary interactions, while the magnetic field of the solenoid keeps them 
+    away from the sensitive drift region. This gap is surrounded by a grounded 
+    window made of 4-$\mu$m-thick aluminized mylar.
+
+ \item The second gas gap extends from 20 mm to 30 mm radial distances and is 
+    filled with a gas mixture of 80$\%$ Neon (Ne) and 20$\%$ Dimethyl Ether 
+    (DME: $C_{2}H_{6}O$). This drift gas fills all the following gaps up to the 
+    external shell.
+
+ \item The cathode foil, which is made of 4-$\mu$m-thick aluminized mylar, 
+    surrounds the second gas gap. It is connected to a voltage of 4.3 kV to 
+    generate an electric field in the drift region.
+
+ \item The drift region is filled with the Ne-DME gas mixture. It extends from 
+    the cathode, 30 mm from the beam line, to the first gas electron multiplier 
+    layer, 60 mm from the beam line.
+
+ \item The amplification system is composed of three Gas Electron Multiplier 
+    (GEM) layers located at radii of 60 mm, 63 mm, and 66 mm.
+
+ \item The electron collection system has an internal radius of 69 mm and 
+ collects the charges. The data are then pre-amplified and transmitted to the 
+ data acquisition system.  \end{itemize}
+
+The Ne-DME gas mixture has been chosen as the drift gas because of its 
+low-diffusion characteristics and small Lorentz angles (the angles between the 
+drift direction of electrons under the influence of magnetic field and the 
+direction of the electric field). These characteristics minimize the changes in 
+the drift velocity of the ionization electrons \cite{DME}.\\
+
+The GEMs amplify the ionized electrons to produce measurable signals. Figure 
+\ref{fig:GEMs} shows a microscopic photo of a GEM. It is made from an insulator 
+(Kapton) sandwiched between two copper layers. The mesh of each GEM layer is 
+chemically etched with 50-$\mu$m-diameter holes in double-conical cross section 
+shapes, as can be seen from the schematic plot on the right.\\
 
@@
 \includegraphics[height=6.0cm]{fig_rtpc/gem_holes.png}
-\caption{On the left: A microscopic image of a GEM shows the amplification holes, and the two copper layers, separated by a Kapton insulator.
-This figure is from \cite{BONUS_2}.
-On the right: Schematic of the hole structure in the GEMs with the electric field lines (solid red) and the equipotentials (dashed blue).
-This figure is from
+\caption{On the left: A microscopic image of a GEM shows the amplification 
+   holes, and the two copper layers, separated by a Kapton insulator. This 
+   figure is from \cite{BONUS_2}. On the right: Schematic of the hole structure 
+   in the GEMs with the electric field lines (solid red) and the equipotentials 
+   (dashed blue). This figure is from
  \cite{GEM_holes}. } 
@@
 
- The electrons amplification is achieved through the holes via the strong electric field, that is generated by a 400-V potential difference between the two copper layers.
-Such a strong field leads to high ionization of the initial electrons and therefore amplification of the signals.
-Furthermore, an additional potential difference of 150 V is set between each two successive GEM layers to push the amplified electrons towards the readout board.
-In this configuration, the gain of each GEM layer is of the order of 100.\\
+The electrons amplification is achieved through the holes via the strong 
+electric field, that is generated by a 400-V potential difference between the 
+two copper layers. Such a strong field leads to high ionization of the initial 
+electrons and therefore amplification of the signals. Furthermore, an 
+additional potential difference of 150 V is set between each two successive GEM 
+layers to push the amplified electrons towards the readout board. In this 
+configuration, the gain of each GEM layer is of the order of 100.\\
 
@@
 RTPC has 40 rows and 40 columns of readout pads, each is 5 mm long and 4.45 mm 
- wide. Each group of 16 pads is connected to a pre-amplifier before the 
- recorded signals are carried to the acquisition electronics. There are 20 
- rows and 5 columns of pre-amplifiers per module. This readout system records 
- the charge information in time bins, in which the charge is measured in 
- Analog-to-Digital-Converter (ADC) units, while the time is 
- recorded in Time-to-Digital-Converter (TDC) units, in which each TDC is equal 
- to 114 ns. This measurement indicating the time taken by the electrons to drift from the 
+wide. Each group of 16 pads is connected to a pre-amplifier before the recorded 
+signals are carried to the acquisition electronics. There are 20 rows and 5 
+columns of pre-amplifiers per module. This readout system records the charge 
+information in time bins, in which the charge is measured in 
+Analog-to-Digital-Converter (ADC) units, while the time is recorded in 
+Time-to-Digital-Converter (TDC) units, in which each TDC is equal to 114 ns.  
+This measurement indicating the time taken by the electrons to drift from the 
 ionization point to the readout board.
@@
 \subsection{Working principle}
-~~~~When a charged particle traverses a gas, it ionizes the gas-atoms along its trajectory.
-In a TPC, the electrons released in the ionization drift towards the readout board under the effect of an applied electric field.
-The drift velocity depends on the gas mixture, and on the electric ($\vec{E}$) and magnetic ($\vec{B}$) fields.
-The recorded time of the electrons provides information on how far the initial ionizations happened in the drift region, leading to reconstruct the original points of ionization, while the recorded ADCs give the deposited energy.\\
-
-In our TPC the cathode and the anode are two cylinders.
-Thus, the generated $\vec{E}$ field in the drift region has a purely radial components, perpendicular to the beam line, with a magnitude around 500 V/cm.
-However, the two-cylinders configuration produces small gradient components at the sides of the RTPC.
-This issue was solved by installing field cages at the ends of the RTPC to keep a regular $\vec{E}$ field.
-These caused some high voltage issues and were disconnected during the experiment, partly justifying the time dependent calibration described below.
-\\
-
- The $\vec{B}$ field is generated by the solenoid.
-Figure \ref{fig:B_MAP} shows the magnetic field vectors in the different regions of the RTPC.
-The presence of the magnetic field enables us to deduce the momentum of a charged particle from the curvature of its track and the known magnetic field.
+~~~~When a charged particle traverses a gas, it ionizes the gas-atoms along its 
+trajectory. In a TPC, the electrons released in the ionization drift towards 
+the readout board under the effect of an applied electric field. The drift 
+velocity depends on the gas mixture, and on the electric ($\vec{E}$) and 
+magnetic ($\vec{B}$) fields. The recorded time of the electrons provides 
+information on how far the initial ionizations happened in the drift region, 
+leading to reconstruct the original points of ionization, while the recorded 
+ADCs give the deposited energy.\\
+
+In our TPC the cathode and the anode are two cylinders. Thus, the generated 
+$\vec{E}$ field in the drift region has a purely radial components, 
+perpendicular to the beam line, with a magnitude around 500 V/cm. However, the 
+two-cylinders configuration produces small gradient components at the sides of 
+the RTPC. This issue was solved by installing field cages at the ends of the 
+RTPC to keep a regular $\vec{E}$ field. These caused some high voltage issues 
+and were disconnected during the experiment, partly justifying the time 
+dependent calibration described below. \\
+
+The $\vec{B}$ field is generated by the solenoid. Figure \ref{fig:B_MAP} shows 
+the magnetic field vectors in the different regions of the RTPC. The presence 
+of the magnetic field enables us to deduce the momentum of a charged particle 
+from the curvature of its track and the known magnetic field.
 % from:
@@
 %\end{equation}
-%where R is the radius of the track's curvature, q and $\theta$ are the charge and the polar angle of the %particle.
+%where R is the radius of the track's curvature, q and $\theta$ are the charge 
+%and the polar angle of the %particle.
 
@@
 \includegraphics[scale=0.40]{fig_rtpc/B_MAP.png}
-\caption[]{The solenoid magnetic field vectors in the RTPC, shown in the $r-z$ plane, where $r$ is the radial distance from the central axis and $z$ represents the longitudinal distance along the RTPC.}
-\label{fig:B_MAP}
+\caption[]{The solenoid magnetic field vectors in the RTPC, shown in the $r-z$ 
+plane, where $r$ is the radial distance from the central axis and $z$ 
+represents the longitudinal distance along the RTPC.} \label{fig:B_MAP}
 \end{figure}
@@
 
-A fit to a chain of hits is performed in two iterations.
-In the first iteration, the hits of the chain are fitted with a helix.
-The helix fit is based on a circle fit in the $x-y$ plane followed by a linear fit in the $s-z$ plane for the hits of the chain, where $s=\sqrt{x^2+y^2}$.
-In the second iteration, the residual between the fit and each hit is calculated.
-If the hit's residual is greater than 5 mm, the hit is excluded from the chain.
-Then the hits are re-fitted with the same previous helix fit giving five final parameters for each track's chain.
-From these five parameters, one can reconstruct all the parameters of a track.
-For example, one can calculate the momentum from the known longitudinal magnetic field ($\vec{B_{z}}$), the radius of curvature of the track ($r_{0}$) and the polar angle ($\theta$), like:
+A fit to a chain of hits is performed in two iterations. In the first 
+iteration, the hits of the chain are fitted with a helix. The helix fit is 
+based on a circle fit in the $x-y$ plane followed by a linear fit in the $s-z$ 
+plane for the hits of the chain, where $s=\sqrt{x^2+y^2}$.  In the second 
+iteration, the residual between the fit and each hit is calculated. If the 
+hit's residual is greater than 5 mm, the hit is excluded from the chain. Then 
+the hits are re-fitted with the same previous helix fit giving five final 
+parameters for each track's chain. From these five parameters, one can 
+reconstruct all the parameters of a track. For example, one can calculate the 
+momentum from the known longitudinal magnetic field ($\vec{B_{z}}$), the radius 
+of curvature of the track ($r_{0}$) and the polar angle ($\theta$), like:
 \begin{eqnarray}
 p_{tot} = \sqrt{p_{\|}^2 + p_{\perp}^2}, ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \\
-\text{with } p_{\perp} = 0.3\cdot q \cdot B_{z} \cdot |r_{0}|\text{and } p_{\|} = p_{\perp}/tan(\theta),\nonumber
+\text{with } p_{\perp} = 0.3\cdot q \cdot B_{z} \cdot |r_{0}|\text{and } p_{\|} 
+= p_{\perp}/tan(\theta),\nonumber
 \end{eqnarray}
-where $p$ is in GeV/c unit, $q$ is the elementary charge, $B_{z}$ is in Tesla (T) and $r_{0}$ is in meters (m).
-For example, In a magnetic field of 4.5 T, the recoil $^4$He nuclei from DVCS (elastic) reaction have kinetic energies in the range [10, 25] ([17, 35]) MeV, from momenta of [260, 450] ([360, 550]) MeV and $r_{0}$ [70, 150] ([130,180]) mm.
+where $p$ is in GeV/c unit, $q$ is the elementary charge, $B_{z}$ is in Tesla 
+(T) and $r_{0}$ is in meters (m). For example, In a magnetic field of 4.5 T, 
+the recoil $^4$He nuclei from DVCS (elastic) reaction have kinetic energies in 
+the range [10, 25] ([17, 35]) MeV, from momenta of [260, 450] ([360, 550]) MeV 
+and $r_{0}$ [70, 150] ([130,180]) mm.
 
@@
 \vspace{-0.1in}
-\caption{Schematic of a segment of the RTPC in a plane perpendicular to the beam line, with a $^4He$ track (in green) crossing the volume.
-See the text for description of the various elements and notations.}
-\label{fig:RTPC_track}
+\caption{Schematic of a segment of the RTPC in a plane perpendicular to the 
+beam line, with a $^4He$ track (in green) crossing the volume. See the text for 
+description of the various elements and notations. $sdist$ and $edist$ are 
+defined position as shown in this sketch.} \label{fig:RTPC_track}
 \end{figure}
@@
 
-\item We apply a cut on the vertex position in $z$ of the reconstructed tracks to insure it is in the RTPC volume, i.e. $z$ $\in$ [-80,80] mm, as illustrated in figure \ref{fig:rtpc_zz}.
+\item We apply a cut on the vertex position in $z$ of the reconstructed tracks 
+   to insure it is in the RTPC volume, i.e. $z$ $\in$ [-80,80] mm, as 
+   illustrated in figure \ref{fig:rtpc_zz}.
 
@@
 
-\item We check the quality of the helix fit with a $\chi^{2}$ cut (< 3.5). The quality of the fit ($\chi^{2}$) is defined as:
+\item We check the quality of the helix fit with a $\chi^{2}$ cut (< 3.5). The 
+   quality of the fit ($\chi^{2}$) is defined as:
 
@@
 
-An algorithm was developed to remove hits corresponding to this noise without suppressing good hits.
-First, the ADC vs TDC noise curve was parameterized.
-Next, for every event and channel independently, the number of hits falling on this curve is counted.
-If a significant number of hits lie far above or below the noise curve, no rejection is performed.
-If most of the hits below TDC=30 fall on the noise curve, all hits below TDC=30 are rejected for that channel.
-Figure \ref{fig:Adcvstdcnoise} shows the effect of this noise reduction for one very noisy pad.
-
-The result of this algorithm is 5$\%$ more good tracks reconstructed, with improved signal to background ratio, as can be seen in figure \ref{fig:noise_edist_}. 
-Further, this allowed to recover 40 channels that had previously been ignored due to high occupancies before this noise rejection.
+An algorithm was developed to remove hits corresponding to this noise without 
+suppressing good hits.  First, the ADC vs TDC noise curve was parameterized.  
+Next, for every event and channel independently, the number of hits falling on 
+this curve is counted.  If a significant number of hits lie far above or below 
+the noise curve, no rejection is performed.  If most of the hits below TDC=30 
+fall on the noise curve, all hits below TDC=30 are rejected for that channel.  
+Figure \ref{fig:Adcvstdcnoise} shows the effect of this noise reduction for one 
+very noisy pad. The result of this algorithm is 5$\%$ more good tracks 
+reconstructed, with improved signal to background ratio, as can be seen in 
+figure \ref{fig:noise_edist_}.  Further, this allowed to recover 40 channels 
+that had previously been ignored due to high occupancies before this noise 
+rejection.
 
@@
 %\vspace{-0.3in}
-\caption{The integrated ADC vs.
-TDC of the hits for good tracks before (left) and after (right) the oscillatory noise reduction, for a particular pad with strong noise.
-The event sample and color scales are identical in both plots.}
+\caption{The integrated ADC vs. TDC of the hits for good tracks before (left) 
+and after (right) the oscillatory noise reduction, for a particular pad with 
+strong noise. The color scale on the z-axis is for the hit yield and identical 
+in both plots as well as the event sample.}
 \label{fig:Adcvstdcnoise}
@@
 %\vspace{-0.1in}
-\caption{The $edist$ (left) and the $\chi^{2}$ (right) distributions for all the tracks collected in the RTPC before (blue) and after (red) the oscillatory noise rejection.
-The event sample and color scales are identical in both plots.}
+\caption{The $edist$ (left) and the $\chi^{2}$ (right) distributions for all 
+the tracks collected in the RTPC before (blue) and after (red) the oscillatory 
+noise rejection. The event sample and color scales are identical in both 
+plots.}
 \label{fig:noise_edist_}
@@
 resolution ($\frac{\Delta p}{p}$) around 0.5$\%$ \cite{CLASref}. The z-vertex 
-resolution of about 3 mm for an extended target in the presence of the 
+resolution is about 3 mm for an extended target in the presence of the 
 solenoid, as can be observed experimentally from the target window, figure 

### 2016-08-23 analysis-note-v2/analysis-2.tex
more updates to the RTPC and the DVCS checks, and updated the ALU tables after the 4D background subtraction

@@
 \hspace*{-0.3in}\includegraphics[scale=0.45]{fig_dvcs/tpc_over_e_Run_sec.png}
-\caption{On the top: The integrated $<tpc/e>$ ratio (over the six sectors of CLAS) for the individual runs.
-The blue points refer to the good runs, while the black ones are the rejected ones.
-On the bottom: the $<tpc/e>$ ratio is shown for each sector of CLAS.
-The colored points indicate the different sectors for each good run, while the black ones are the rejected runs without color difference between the sectors.
-In both plots, the experimental setting changes that might cause a change in the event rate are indicated with vertical colored lines.}
-\label{fig:tpc_over_e_Run_sec.png}
+\caption{On the top: The integrated $<tpc/e>$ ratio (over the six sectors of 
+   CLAS) for the individual runs. The blue points refer to the good runs, while 
+   the black ones are the rejected ones. On the bottom: the $<tpc/e>$ ratio is 
+   shown for each sector of CLAS. The colored points indicate the different 
+   sectors for each good run, while the black ones are the rejected runs 
+without color difference between the sectors. In both plots, the experimental 
+setting changes that might cause a change in the event rate are indicated with 
+vertical colored lines.} \label{fig:tpc_over_e_Run_sec.png}
 \end{figure}
@@
 \subsection{Coherent DVCS event selection}
-~~~~Events with one and only one good electron, one and only one good RTPC track and at least one good photon are considered good coherent DVCS candidates.
-Even though the DVCS reaction has only one real photon in the final state, events with more than one good photon are not discarded at this stage.
-This is motivated by the fact that some photons correspond to random coincidences and discarding these events results in losing good events.
-Then, events with one or more $\pi^{0}$ are removed from the coherent DVCS sample.
-After that, the most energetic photon in each remaining event is chosen as the DVCS photon.
-Next, to consider an event as a clean $^{4}He$ DVCS, it has to pass respectively two sets of requirements: DVCS characteristic cuts and exclusivity cuts.
+~~~~Events with one and only one good electron, one and only one good RTPC 
+track and at least one good photon are considered good coherent DVCS 
+candidates. Even though the DVCS reaction has only one real photon in the final 
+state, events with more than one good photon are not discarded at this stage.  
+This is motivated by the fact that some photons correspond to random 
+coincidences and discarding these events results in losing good events. Then, 
+events with one or more $\pi^{0}$ are removed from the coherent DVCS sample.  
+After that, the most energetic photon in each remaining event is chosen as the 
+DVCS photon. Next, to consider an event as a clean $^{4}He$ DVCS, it has to 
+pass respectively two sets of requirements: DVCS characteristic cuts and 
+exclusivity cuts.
 
@@
 \begin{itemize}
-\item $Q^{2}$ > 1 GeV$^{2}$: to ensure that the interaction occurs at the partonic level and the applicability of the factorization in the DVCS  handbag diagram.
-%\item The invariant mass of the system of the virtual photon and the target 
-   %proton is greater than $2~GeV/c{^2}$. This cut avoids the region of 
-   %excitation of the proton to resonances.
-\item $ -t > -t_{min}$: the transferred momentum squared to the recoil $^{4}He$ has to be greater than a minimum value defined by the kinematics of the beam and the scattered electron as:
+ \item $Q^{2}$ > 1 GeV$^{2}$: to ensure that the interaction occurs at the 
+    partonic level and the applicability of the factorization in the DVCS  
+    handbag diagram.
+\item $ -t > -t_{min}$: the transferred momentum squared to the recoil $^{4}He$ 
+   has to be greater than a minimum value defined by the kinematics of the beam 
+   and the scattered electron as:
 \begin{equation}
@@
 \end{equation}
-where $\epsilon ^{2} = \frac{4M^{2}_{^4He}x^{2}_{A}}{Q^{2}}$, $x_{A} = \frac{M_{p}\cdot x_{B}}{M_{^4He}}$ and $M_{p}$ ($M_{^4He}$) is the proton ($^{4}He$) mass.\\
+where $\epsilon ^{2} = \frac{4M^{2}_{^4He}x^{2}_{A}}{Q^{2}}$, $x_{A} = 
+\frac{M_{p}\cdot x_{B}}{M_{^4He}}$ and $M_{p}$ ($M_{^4He}$) is the proton 
+($^{4}He$) mass.\\
 
-In the case of the proton DVCS, the variable $x_{A}$ is replaced by the Bjorken $x_{B}$ in the formula for $t_{min}$.
+In the case of the proton DVCS, the variable $x_{A}$ is replaced by the Bjorken 
+$x_{B}$ in the formula for $t_{min}$. Figure \ref{fig:tmin_both} presents 
+$t_{min}$ distributions for both DVCS channels.
+
+\item In the case of the incoherent DVCS channel, we apply a cut on the 
+   invariant mass of the virtual photon and the target proton system to be
+   greater than $2~GeV/c{^2}$. This cut avoids the region of excitation of the 
+   proton to resonances.
 
@@
 \begin{figure}[tbp]
+\includegraphics[height=5.0cm]{fig_rtpc/updates/tmin_coh.png}
+\includegraphics[height=5.0cm]{fig_rtpc/updates/tmin_incoh.png}
+\caption{Coherent (left) and incoherent (right) -$t_{min}$ distributions 
+calculated for the experimentally selected DVCS events. We use the experimental 
+$Q^{2}$ and $x_{B}$ of the individual events. }
+\label{fig:tmin_both}
+ \end{figure}
+
+\begin{figure}[tbp]
       \includegraphics[height=5.0cm]{fig_dvcs/photon_energy_coh_sim.png}
       \includegraphics[height=5.5cm]{fig_dvcs/photon_energy_incoh_sim.png}
-          \caption{The energy distribution of the simulated coherent, on top, 
-          and incoherent, on bottom, DVCS photons.}
+      \caption{The energy distribution of the simulated coherent (left) and 
+      incoherent (right) DVCS photons.}
       \label{fig:energy_dvcs_photons}
 \end{figure}
-
 \end{itemize}
 
+\newpage
 \paragraph{Exclusivity cuts}
@@
 \begin{equation}
-e(\mathbf{P}_{e}) + ~~^{4}He(\mathbf{P}_{^{4}He}) \rightarrow e'(\mathbf{P_{e'}}) +  ~~^{4}He'(\mathbf{P}_{^{4}He'}) + \gamma(\mathbf{P}_{\gamma})
+e(\mathbf{P}_{e}) + ~~^{4}He(\mathbf{P}_{^{4}He}) \rightarrow 
+e'(\mathbf{P_{e'}}) +  ~~^{4}He'(\mathbf{P}_{^{4}He'}) + 
+\gamma(\mathbf{P}_{\gamma})
 \label{coh_dvcs_equ}
@@
 \begin{eqnarray}
-\overrightarrow{HP}_{1} &=& \overrightarrow{\mathbf{P}}_{^{4}He'} \times \overrightarrow{\mathbf{P}}_{\gamma^{*}}\\
-\overrightarrow{HP}_{2} &=& \overrightarrow{\mathbf{P}}_{^{4}He'}  \times \overrightarrow{\mathbf{P}}_{\gamma}\\
-\overrightarrow{HP}_{3} &=& \overrightarrow{\mathbf{P}}_{\gamma^{*}} \times \overrightarrow{\mathbf{P}}_{\gamma}
+\overrightarrow{HP}_{1} &=& \overrightarrow{\mathbf{P}}_{^{4}He'} \times 
+   \overrightarrow{\mathbf{P}}_{\gamma^{*}}\\
+\overrightarrow{HP}_{2} &=& \overrightarrow{\mathbf{P}}_{^{4}He'}  \times 
+   \overrightarrow{\mathbf{P}}_{\gamma}\\
+\overrightarrow{HP}_{3} &=& \overrightarrow{\mathbf{P}}_{\gamma^{*}} \times 
+   \overrightarrow{\mathbf{P}}_{\gamma}
 \end{eqnarray}
-$\Delta \phi$ is defined to be the $\phi$ difference between these planes and is calculable from three combinations: ($\overrightarrow{HP}_{1}$, $\overrightarrow{HP}_{2}$), ($\overrightarrow{HP}_{1}$, $\overrightarrow{HP}_{3}$) and ($\overrightarrow{HP}_{2}$, $\overrightarrow{HP}_{3}$).
-We investigated the three combinations and we decided to use the second one as it gives better resolution.
+$\Delta \phi$ is defined to be the $\phi$ difference between these planes and 
+is calculable from three combinations: ($\overrightarrow{HP}_{1}$, 
+$\overrightarrow{HP}_{2}$), ($\overrightarrow{HP}_{1}$, 
+$\overrightarrow{HP}_{3}$) and ($\overrightarrow{HP}_{2}$, 
+$\overrightarrow{HP}_{3}$). We investigated the three combinations and we 
+decided to use the second one as it gives better resolution.
 
-\item Missing energy, mass and transverse momentum ($p^{T}_{X} = \sqrt{(p^{x}_{X})^2 + (p^{y}_{X}})^2$) cuts on $\mathbf{P}^{e^{4}He\gamma}_{X}$.
+\item Missing energy, mass and transverse momentum ($p^{T}_{X} = 
+   \sqrt{(p^{x}_{X})^2 + (p^{y}_{X}})^2$) cuts on 
+   $\mathbf{P}^{e^{4}He\gamma}_{X}$.
 
-\item Missing mass cuts on the $e^{4}HeX$ and $e\gamma X$ systems, which are defined as $(P^{e^{4}He}_{X})^{2}$ and $(P^{e\gamma}_{X})^{2}$ respectively.
+\item Missing mass cuts on the $e^{4}HeX$ and $e\gamma X$ systems, which are 
+   defined as $(P^{e^{4}He}_{X})^{2}$ and $(P^{e\gamma}_{X})^{2}$ respectively.
 
-\item Cone angle cut between the measured real photon and the missing particle in the $e^{4}HeX$ configuration. It is defined as:
+\item Cone angle cut between the measured real photon and the missing particle 
+   in the $e^{4}HeX$ configuration. It is defined as:
 \begin{equation}
-\theta(\gamma, e^{4}HeX) = cos^{-1} \left( \frac{\overrightarrow{\mathbf{P}}_{\gamma} \cdot \overrightarrow{\mathbf{P}}^{e^{4}He}_{X}}{|\overrightarrow{\mathbf{P}}_{\gamma^{}}| |\overrightarrow{\mathbf{P}}^{e^{4}He}_{X}|}   \right).
+\theta(\gamma, e^{4}HeX) = cos^{-1} \left( 
+\frac{\overrightarrow{\mathbf{P}}_{\gamma} \cdot 
+\overrightarrow{\mathbf{P}}^{e^{4}He}_{X}}{|\overrightarrow{\mathbf{P}}_{\gamma^{}}| 
+|\overrightarrow{\mathbf{P}}^{e^{4}He}_{X}|}   \right).
 \end{equation}
@@
 ~~~~~Figure \ref{fig:coh_exclusivty_cuts} summarizes all the exclusivity cuts.  
-In these plots, the blue distributions represent the coherent events after the DVCS characteristic cuts and before all the exclusivity cuts.
-The shaded distributions stand for the events which passed all the exclusivity cuts except the one on the quantity plotted.
-We fitted each shaded distribution by a Gaussian and then we applied  3$\sigma$ cuts around the mean value of each distribution.
-The events which pass these cuts are assumed to be good $^{4}He$ DVCS events.
-~\\
+In these plots, the blue distributions represent the coherent events after the 
+DVCS characteristic cuts and before all the exclusivity cuts. The shaded 
+distributions stand for the events which passed all the exclusivity cuts except 
+the one on the quantity plotted. We fitted each shaded distribution by a 
+Gaussian and then we applied  3$\sigma$ cuts around the mean value of each 
+distribution. The events which pass these cuts are assumed to be good $^{4}He$ 
+DVCS events.  ~\\
 ~\\
@@
 \includegraphics[scale=0.4]{fig_dvcs/all_coh_exc_cuts.png}
-\caption{The coherent DVCS exclusivity cuts.
-The blue distributions represent the coherent DVCS events candidate.
-The shaded distributions represent the events which passed all the exclusivity cuts except the quantity plotted.
-The vertical red lines represent $3\sigma$ cuts.
-The missing momentum in $x$ and $y$ directions in the configuration $e^{4}He\gamma X$, are shown for information.
-The mean and the sigma values of each quantity can be found in Appendix \ref{exclusivity_cuts}, table \ref{Table:coh_exclusivity_cuts}.}
+\caption{The coherent DVCS exclusivity cuts. The blue distributions represent 
+   the coherent DVCS events candidate. The shaded distributions represent the 
+   events which passed all the exclusivity cuts except the quantity plotted.  
+   The vertical red lines represent $3\sigma$ cuts. The missing momentum in $x$ 
+   and $y$ directions in the configuration $e^{4}He\gamma X$, are shown for 
+information. The mean and the sigma values of each quantity can be found in 
+Appendix \ref{exclusivity_cuts}, table \ref{Table:coh_exclusivity_cuts}.} 
 \label{fig:coh_exclusivty_cuts}
@@
 \section{Incoherent channel}
-~~~~In this channel, the DVCS process happens on a bound proton.
-Thus, the final state has a recoil proton instead of the helium nucleus.
-Therefore, events with one good electron, one recoil proton, and at least one real photon are the good candidates here.
-For the rest, we follow the same steps that were introduced for the coherent DVCS selection.
+~~~~In this channel, the DVCS process happens on a bound proton. Thus, the 
+final state has a recoil proton instead of the helium nucleus. Therefore, 
+events with one good electron, one recoil proton, and at least one real photon 
+are the good candidates here. For the rest, we follow the same steps that were 
+introduced for the coherent DVCS selection.
 
 \subsection{Good run list}
-~~~~The events rate stability is verified by looking at the rate of the detected number of protons to the detected electrons (<p/e>).
-Like for the coherent channel, the same technique for the determination of the good run list is followed herein.
-The results are presented in figure \ref{fig:prot_over_e_Run_sec.png}.
-\begin{figure}[h!]
+~~~~The events rate stability is verified by looking at the rate of the 
+detected number of protons to the detected electrons (<p/e>). Like for the 
+coherent channel, the same technique for the determination of the good run list 
+is followed herein. The results are presented in figure 
+\ref{fig:prot_over_e_Run_sec.png}.  \begin{figure}[h!]
 \includegraphics[scale=0.4]{fig_dvcs/prot_over_e_Run.png}
@@
 \caption{On the top: the integrated <$p/e$> ratio as a function of run number.  
-The blue points refer to the good runs, while the black points are the rejected ones.
-On the bottom: the same ratio for each run, is shown for each sector of CLAS.
-The colored points indicate the six sectors, while the black points are the sectors of the rejected runs.
-}
+   The blue points refer to the good runs, while the black points are the 
+rejected ones. On the bottom: the same ratio for each run, is shown for each 
+sector of CLAS. The colored points indicate the six sectors, while the black 
+points are the sectors of the rejected runs. } 
 \label{fig:prot_over_e_Run_sec.png}
@@
 \subsection{Proton DVCS event selection}
-~~~~To certify that an event is a proton DVCS one, we require the same DVCS kinematic cuts as those presented for the coherent DVCS selection.
-Then, the exclusivity of the DVCS reaction is ensured by applying an equivalent set of exclusivity with taking a proton at rest as the target, instead of $^4He$.
+~~~~To certify that an event is a proton DVCS one, we require the same DVCS 
+kinematic cuts as those presented for the coherent DVCS selection. Then, the 
+exclusivity of the DVCS reaction is ensured by applying an equivalent set of 
+exclusivity with taking a proton at rest as the target, instead of $^4He$.  
 Figure \ref{fig:incoh_exclusivty_cuts} summarizes these exclusivity cuts.\\
@@
 \includegraphics[scale=0.4]{fig_dvcs/all_incoh_exc_cuts.png}
-\caption{The incoherent DVCS exclusivity cuts.
-The blue distributions represent all the events with one good electron, one good proton, and at least one photon in the IC.
-The shaded brown distributions show the incoherent DVCS events which passed all the exclusivity cuts except the one on the quantity drawn.
-The distributions from left to right and from top to bottom are: the proton-photon coplanarity, the missing energy, missing mass squared, missing transverse momentum from $ep\gamma X$, the missing mass squared $epX$ and the missing mass squared $e\gamma X$, the angle between the missing particle in $epX$ and the measured photon, the missing $P_{x}$ and $P_{y}$ in $ep\gamma X$.
-The vertical red lines represent 3$\sigma$ cuts.
-The mean and sigma values of each shaded distribution are listed in table \ref{Table:incoh_exclusivity_cuts}.}
-\label{fig:incoh_exclusivty_cuts}
+\caption{The incoherent DVCS exclusivity cuts. The blue distributions represent 
+   all the events with one good electron, one good proton, and at least one 
+   photon in the IC. The shaded brown distributions show the incoherent DVCS 
+   events which passed all the exclusivity cuts except the one on the quantity 
+   drawn. The distributions from left to right and from top to bottom are: the 
+   proton-photon coplanarity, the missing energy, missing mass squared, missing 
+   transverse momentum from $ep\gamma X$, the missing mass squared $epX$ and 
+   the missing mass squared $e\gamma X$, the angle between the missing particle 
+   in $epX$ and the measured photon, the missing $P_{x}$ and $P_{y}$ in 
+   $ep\gamma X$. The vertical red lines represent 3$\sigma$ cuts. The mean and 
+   sigma values of each shaded distribution are listed in table 
+\ref{Table:incoh_exclusivity_cuts}.} \label{fig:incoh_exclusivty_cuts}
 \end{figure}
@@
 \subsection{Comparison with simulation}
-~~~~The three particles of the simulated $ep\gamma$ DVCS events are selected applying the previously described identification requirements.
-The events with three identified particles (e, p, $\gamma$) are required to pass a set of exclusivity cuts such as the ones of the experimental incoherent DVCS events.
-In this section, a comparison between the experimental and the simulated data is carried out.\\
+~~~~The three particles of the simulated $ep\gamma$ DVCS events are selected 
+applying the previously described identification requirements. The events with 
+three identified particles (e, p, $\gamma$) are required to pass a set of 
+exclusivity cuts such as the ones of the experimental incoherent DVCS events.  
+In this section, a comparison between the experimental and the simulated data 
+is carried out.\\
 
-Figure \ref{fig:incoh_coparison_with_simulation_1} shows the comparison between the simulated (red lines) and the experimental (shaded blue) incoherent DVCS events as a function of the four kinematic variables: $Q^{2}$, $x_{B}$, $-t$, and $\phi$.
-Figure \ref{fig:incoh_comparison_with_simulation_exclusive_2} shows the comparison as a function of the variables used to select exclusive DVCS events.
+Figure \ref{fig:incoh_coparison_with_simulation_1} shows the comparison between 
+the simulated (red lines) and the experimental (shaded blue) incoherent DVCS 
+events as a function of the four kinematic variables: $Q^{2}$, $x_{B}$, $-t$, 
+and $\phi$. Figure \ref{fig:incoh_comparison_with_simulation_exclusive_2} shows 
+the comparison as a function of the variables used to select exclusive DVCS 
+events.
 \begin{figure}[h!]
@@
 \includegraphics[scale=0.35]{fig_dvcs/comp/phi_h_InCoh.png}
-\caption{Comparison between the Monte-Carlo simulated $ep\gamma$ DVCS events (red lines) and the experimental ones (blue shaded distributions) in terms of the kinematics: $Q^{2}$, $x_{B}$, $-t$, and $\phi$, respectively from left to right and from top to bottom.}
+\caption{Comparison between the Monte-Carlo simulated $ep\gamma$ DVCS events 
+(red lines) and the experimental ones (blue shaded distributions) in terms of 
+the kinematics: $Q^{2}$, $x_{B}$, $-t$, and $\phi$, respectively from left to 
+right and from top to bottom.}
 \label{fig:incoh_coparison_with_simulation_1}
@@
 \includegraphics[scale=0.35]{fig_dvcs/comp/InCoh_Theta_gammaX_InCoh.png}
-\caption{Comparison between simulated and experimental $ep\gamma$ DVCS events in terms of the variables used for exclusivity cuts.
-The vertical black lines indicate the theoretically expected values for each exclusive quantity.}
+\caption{Comparison between simulated and experimental $ep\gamma$ DVCS events 
+in terms of the variables used for exclusivity cuts. The vertical black lines 
+indicate the theoretically expected values for each exclusive quantity.} 
 \label{fig:incoh_comparison_with_simulation_exclusive_2}
@@
 \includegraphics[scale=0.45]{fig_results/bins_Coh_Q2_Phi.png}
-\caption{On the top: the $Q^2$ distribution of the collected coherent DVCS events.
-The different colors indicate the different bins in $Q^2$ integrated over the full ranges of $-t$ and $x_B$.
-On the bottom: the $\phi$ distributions of the coherent DVCS events for the bins in $Q^2$, which are shown in the top plot.
-The different colors in each $\phi$ distribution represent the nine bins in $\phi$.}
-\label{fig:coh_Q2_bins}
+\caption{On the top: the $Q^2$ distribution of the collected coherent DVCS 
+   events. The different colors indicate the different bins in $Q^2$ integrated 
+   over the full ranges of $-t$ and $x_B$. On the bottom: the $\phi$ 
+   distributions of the coherent DVCS events for the bins in $Q^2$, which are 
+shown in the top plot. The different colors in each $\phi$ distribution 
+represent the nine bins in $\phi$.} \label{fig:coh_Q2_bins}
 \end{figure}
@@
 \subsection{$\pi^0$ contaminations}
-~~~~Even with all cuts applied to select the selected DVCS events, the events are not all DVCS events.
-In our kinematic region, the main contamination comes from the exclusive electroproduction of $\pi^{0}$ ($e ^{4}He \rightarrow e ^{4}He \pi^{0} \rightarrow e ^{4}He \gamma \gamma $, $e p \rightarrow e p \pi^{0} \rightarrow e p \gamma \gamma $), in which one of the two photons of the $\pi^{0}$ decay passes the requirements of the DVCS.
-Thus, the event is counted as a DVCS event.
-These events contaminate the DVCS sample and have to be subtracted to obtain the true number of DVCS events.
-In the case of the coherent channel, this can be formulated as:
+~~~~Even with all cuts applied to select the selected DVCS events, the events 
+are not all DVCS events. In our kinematic region, the main contamination comes 
+from the exclusive electroproduction of $\pi^{0}$ ($e ^{4}He \rightarrow e 
+^{4}He \pi^{0} \rightarrow e ^{4}He \gamma \gamma $, $e p \rightarrow e p 
+\pi^{0} \rightarrow e p \gamma \gamma $), in which one of the two photons of 
+the $\pi^{0}$ decay passes the requirements of the DVCS. Thus, the event is 
+counted as a DVCS event. These events contaminate the DVCS sample and have to 
+be subtracted to obtain the true number of DVCS events. In the case of the 
+coherent channel, this can be formulated as:
 \begin{equation}
@@
 \end{equation}
-where $N^{True}_{e^{4}He\gamma}$, $N^{Exp.}_{e^{4}He\gamma}$ and $ N^{Exp.}_{e^{4}He\pi^{0}(\gamma)}$ are the true number of coherent DVCS events, the experimentally measured number of $e^{4}He\gamma$ events and the contamination number, respectively.
-The contamination can be calculated by using real data and simulation.
-We define, for each kinematic bin and for each beam helicity state
+where $N^{True}_{e^{4}He\gamma}$, $N^{Exp.}_{e^{4}He\gamma}$ and $ 
+N^{Exp.}_{e^{4}He\pi^{0}(\gamma)}$ are the true number of coherent DVCS events, 
+the experimentally measured number of $e^{4}He\gamma$ events and the 
+contamination number, respectively. The contamination can be calculated by 
+using real data and simulation. We define, for each kinematic bin and for each 
+beam helicity state
 \begin{equation}
-N^{Exp.}_{e^{4}He\pi^{0}(\gamma)} = \frac{N^{Sim.}_{e^{4}He\pi^{0}(\gamma)}}{N^{Sim.}_{e^{4}He\pi^{0}(\gamma \gamma)}} * N^{Exp.}_{e^{4}He\pi^{0}(\gamma \gamma)},
+N^{Exp.}_{e^{4}He\pi^{0}(\gamma)} = 
+\frac{N^{Sim.}_{e^{4}He\pi^{0}(\gamma)}}{N^{Sim.}_{e^{4}He\pi^{0}(\gamma 
+\gamma)}} * N^{Exp.}_{e^{4}He\pi^{0}(\gamma \gamma)},
 \label{equation: background_equ}
 \end{equation}
-where $N^{Exp.}_{e^{4}He\pi^{0}(\gamma \gamma)}$ is the number of measured $e^{4}He\pi^{0}$ events, for which both photons of the $\pi^{0}$ have been detected.
-The quantity $\frac{N^{Sim.}_{e^{4}He\pi^{0}(\gamma)}}{N^{Sim.}_{e^{4}He\pi^{0}(\gamma \gamma)}} $ is the acceptance ratio for detecting a $e^{4}He\gamma$ event that originates from an $e^{4}He\pi^{0}$ event.
-It can be derived from Monte-Carlo simulations by generating and simulating $e^{4}He\pi^{0}$.
-$N^{Sim.}_{e^{4}He\pi^{0}(\gamma)}$ is the number of such events passing the DVCS requirements, while $N^{Sim.}_{e^{4}He\pi^{0}(\gamma \gamma)}$ is the number of simulated $e^{4}He\pi^{0}$ events passing the exclusivity cuts for $e^{4}He\pi^{0}$ events.\\
+where $N^{Exp.}_{e^{4}He\pi^{0}(\gamma \gamma)}$ is the number of measured 
+$e^{4}He\pi^{0}$ events, for which both photons of the $\pi^{0}$ have been 
+detected. The quantity 
+$\frac{N^{Sim.}_{e^{4}He\pi^{0}(\gamma)}}{N^{Sim.}_{e^{4}He\pi^{0}(\gamma 
+\gamma)}} $ is the acceptance ratio for detecting a $e^{4}He\gamma$ event that 
+originates from an $e^{4}He\pi^{0}$ event. It can be derived from Monte-Carlo 
+simulations by generating and simulating $e^{4}He\pi^{0}$.  
+$N^{Sim.}_{e^{4}He\pi^{0}(\gamma)}$ is the number of such events passing the 
+DVCS requirements, while $N^{Sim.}_{e^{4}He\pi^{0}(\gamma \gamma)}$ is the 
+number of simulated $e^{4}He\pi^{0}$ events passing the exclusivity cuts for 
+$e^{4}He\pi^{0}$ events.\\
 
-The previous formulas apply to the case of the coherent DVCS. The same procedures hold for the incoherent case by replacing the $^{4}He$ with the proton.\\
+The previous formulas apply to the case of the coherent DVCS. The same 
+procedures hold for the incoherent case by replacing the $^{4}He$ with the 
+proton.\\
 
-The selection of the exclusive $e^{4}He\pi^{0}$ and $ep\pi^{0}$ events requires the detection of one good electron, one good $\pi^{0}$ in the topology ICIC or ICEC, and one good $^{4}He$ track in the coherent case, or one good proton in the incoherent case.
-In order to ensure that this is a deep process, we apply the same kinematic cuts as DVCS.
-These cuts and the comparisons with simulation can be found in Appendix \ref{app:Exclusive_pi0_selection}.\\
+The selection of the exclusive $e^{4}He\pi^{0}$ and $ep\pi^{0}$ events requires 
+the detection of one good electron, one good $\pi^{0}$ in the topology ICIC or 
+ICEC, and one good $^{4}He$ track in the coherent case, or one good proton in 
+the incoherent case. In order to ensure that this is a deep process, we apply 
+the same kinematic cuts as DVCS. These cuts and the comparisons with simulation 
+can be found in Appendix \ref{app:Exclusive_pi0_selection}.\\
 
-Figure \ref{fig:coh_acceptance _ratios} shows the coherent acceptance ratio as a function of each of the four kinematic variables ($Q^{2}$, $x_{B}$, $-t$, $\phi_{h}$).
-These distributions are one-dimensional, i.e.
-the data are integrated over all kinematical ranges except for the quantity which is binned (along the x-axis).
-The results  for the incoherent channel can be found in figure \ref{fig:incoh_acceptance _ratios}.
-The mean value of the acceptance ratio for the coherent channel is around 25$\%$, with some dependence on $x_{B}$ and $\phi$, and almost no dependence on $Q^{2}$ and $-t$.
-For the incoherent channel, the mean acceptance ratio is around 20$\%$ with some dependence on the four kinematic variables.\\
-
-As presented in the previous section, we construct two-dimensional bins: $Q^2$-$\phi$, $x_B$-$\phi$ and -$t$-$\phi$.
-Thus, for each bin in $Q^2$, $x_B$ and $-t$, we assume that the acceptance ratio does not change a lot within the bin range and we construct the one-dimensional acceptance ratio as a function of $\phi$.
-The latter is used to perform the background subtraction as shown in equations \ref{equ_back_1} and \ref{equation: background_equ}.
+Figure \ref{fig:coh_acceptance _ratios} shows the coherent acceptance ratio as 
+a function of each of the four kinematic variables ($Q^{2}$, $x_{B}$, $-t$, 
+$\phi_{h}$). These distributions are one-dimensional, i.e. the data are 
+integrated over all kinematical ranges except for the quantity which is binned 
+(along the x-axis). The results for the incoherent channel can be found in 
+figure \ref{fig:incoh_acceptance _ratios}. The mean value of the acceptance 
+ratio for the coherent channel is around 25$\%$, with some dependence on 
+$x_{B}$ and $\phi$, and almost no dependence on $Q^{2}$ and $-t$. For the 
+incoherent channel, the mean acceptance ratio is around 20$\%$ with some 
+dependence on the four kinematic variables.\\
 
@@
 kinematic variables: $Q^{2}$ (top left), $x_{B}$ (top right), $-t$ (bottom 
-left), and $\phi$ (bottom right).  }
+left), and $\phi$ (bottom right).}
 \label{fig:incoh_acceptance _ratios}
 \end{figure}
+
+As presented in the previous section, we construct two-dimensional bins: 
+$Q^2$-$\phi$, $x_B$-$\phi$ and -$t$-$\phi$. Thus, for each bin in $Q^2$, $x_B$ 
+and $-t$, we assume that the acceptance ratio does not change a lot within the 
+bin range and we construct the one-dimensional acceptance ratio as a function 
+of $\phi$. We also carried out four-dimensional background subtraction, in 
+which the acceptance ratio has been extracted from simulation as a function of 
+$Q^2$, $x_B$, -$t$, and $\phi$. The difference between the reconstructed 
+beam-spin asymmetries using two-dimensional and four-dimensional background 
+subtraction are presented in figures \ref{fig:coh_binning} and 
+\ref{fig:incoh_binning} for the coherent and the incoherent DVCS channels.  
+Even though the two-dimensional subtraction is a good approximation, a 
+four-dimensional subtraction is applied on the final results presented next 
+chapter.
+
+\begin{figure}[tbp]
+   \centering
+    \includegraphics[height=6.0cm]{fig_rtpc/updates/BSA_Coherent_xB.png}
+    \includegraphics[height=6.0cm]{fig_rtpc/updates/diff_BSA_Coherent_xB_2.png}
+    \caption{On top: the reconstruct coherent beam-spin asymmetries as a 
+    function of $\phi$ in $x_{B}$ bins using two-dimensional (in blue) and 
+ four-dimensional (in green) background subtraction.  On bottom: the difference 
+ between the two asymmetries as a function of $\phi$.}
+    \label{fig:coh_binning}
+    \end{figure}
+
+    \begin{figure}[tbp]
+       \centering
+    \includegraphics[height=5.2cm]{fig_rtpc/updates/BSA_InCoherent_xB.png}
+    \includegraphics[height=5.2cm]{fig_rtpc/updates/diff_BSA_InCoherent_xB_2.png}
+    \caption{On top: the reconstruct incoherent beam-spin asymmetries using    
+    two-dimensional (in blue) and four-dimensional (in green) background 
+ subtraction.  On bottom: the difference between the two asymmetries as a 
+ function of $\phi$.}
+    \label{fig:incoh_binning}
+    \end{figure}
+
+Regarding other backgrounds, the procedures carried out in this work followed 
+the same guidelines as for DVCS analysis on the nucleon. The neutral pion 
+production occurs "without threshold" as seen from the $eHe\gamma$ sample, 
+meaning that the contamination from $eHe\pi^0$ with one photon lost is 
+distributed all the way down to the DVCS, in the limit where the second photon 
+energy becomes negligible in the lab. Single charged pion production occurs 
+with a small threshold but is inconsistent with the already detected particles 
+($e$ and $^{4}$He). Two pion production is entirely cleaned up by the 
+exclusivity cuts. Scattering from the windows is excluded by the vertex cuts.  
+As far as accidental, we correct for that as presented in the following 
+section.
 
@@
 \includegraphics[scale=0.31]{fig_dvcs/e4Hegamma_M2_Mis_sig.png}
-\includegraphics[scale=0.31]{fig_dvcs/e4Hegamma_M2_Mis_sig.png}
+\includegraphics[scale=0.31]{fig_dvcs/epgamma_M2_Mis_sig.png}
 \includegraphics[scale=0.31]{fig_dvcs/e4Hegamma_e4Hepi0_Phi_2.png}

### 2016-08-23 analysis-note-v2/data_analysis.tex
more updates to the RTPC and the DVCS checks, and updated the ALU tables after the 4D background subtraction

@@
 \chapter{Particles reconstruction and simulation}
-~~~~The final state of a coherent (incoherent) DVCS event consists of three particles: an electron, a $^4$He (a proton), and a real photon.
-To identify the DVCS events, we first identify, individually, the different particles of interest.
-Then, events with three detected final-state particles will be further filtered by imposing the energy-momentum conservation laws, as will be presented in the following chapter.\\
+~~~~The final state of a coherent (incoherent) DVCS event consists of three 
+particles: an electron, a $^4$He (a proton), and a real photon. To identify the 
+DVCS events, we first identify, individually, the different particles of 
+interest. Then, events with three detected final-state particles will be 
+further filtered by imposing the energy-momentum conservation laws, as will be 
+presented in the following chapter.\\
 
-Even after imposing the conservation laws, the DVCS sample will not have 100$\%$ truly DVCS events.
-In our kinematical region, the main contamination to our DVCS channels comes from the electroproduction of neutral pions.
-For instance, in the coherent $\pi^0$-electroproduction, when one of the two-photon decay of the $\pi^{0}$ passes the DVCS requirements, it will be counted as a DVCS event.
-Thus, these events have to be subtracted before looking to any DVCS observable.
-For this purpose, we perform a technique in which we combine the measured exclusive $\pi^0$-electroproduction data sample with a Monte-Carlo simulation to evaluate the background in the selected DVCS sample.
-For this technique, we need to identify the experimental $\pi^0$s that come in the coherent and the incoherent $\pi^0$-electroproduction channels.\\
+Even after imposing the conservation laws, the DVCS sample will not have 
+100$\%$ truly DVCS events. In our kinematical region, the main contamination to 
+our DVCS channels comes from the electroproduction of neutral pions. For 
+instance, in the coherent $\pi^0$-electroproduction, when one of the two-photon 
+decay of the $\pi^{0}$ passes the DVCS requirements, it will be counted as a 
+DVCS event. Thus, these events have to be subtracted before looking to any DVCS 
+observable. For this purpose, we perform a technique in which we combine the 
+measured exclusive $\pi^0$-electroproduction data sample with a Monte-Carlo 
+simulation to evaluate the background in the selected DVCS sample. For this 
+technique, we need to identify the experimental $\pi^0$s that come in the 
+coherent and the incoherent $\pi^0$-electroproduction channels.\\
 
-In this chapter, we presents the procedures carried out to identify the final-state particles of interest, the Monte-Carlo simulation we used, and the kinematic corrections we applied on the particles.
+In this chapter, we presents the procedures carried out to identify the 
+final-state particles of interest, the Monte-Carlo simulation we used, and the 
+kinematic corrections we applied on the particles.
 
@@
 \subsection{Electron identification} \label{Electron_identification}
-~~~~The electron detection triggers the data acquisition system to record data from all the sub-detectors of CLAS.
-In this analysis, a particle which passes the following set of criteria is assumed to be a good electron.
+~~~~The electron detection triggers the data acquisition system to record data 
+from all the sub-detectors of CLAS. In this analysis, a particle which passes 
+the following set of criteria is assumed to be a good electron.
 
@@
 \begin{itemize}
-\item IC fiducial cuts: the photons which hit the edges of the IC deposit only part of their energies within the calorimeter.
-For this reason, we reject the photons which hit the innermost or the outermost rings of the IC.
+\item IC fiducial cuts: the photons which hit the edges of the IC deposit only 
+   part of their energies within the calorimeter. For this reason, we reject 
+   the photons which hit the innermost or the outermost rings of the IC.  
    Figure \ref{fig:photons_IC_XY_2} illustrates this cut \cite{FX_thesis}.
-
-\item M\o ller electrons reduction: a two-dimensional plot of photon polar angles as a function of the energy shows an overcrowded region at low $\theta$ and low energy.
-This can be seen in figure \ref{fig:photons_IC_theta_En_1}.
-This region is mostly populated by the M\o ller electrons and must be excluded from the analysis.
-We optimized a linear cut for this region, shown by the black dashed line.
-The vertical extension of this line shows the minimum energy cut ($E_{\gamma}$ > 300 MeV).
-\item We do not apply any timing cut on the IC because its timing is not functionning properly for certain channels.
-Therefore, applying a timing cut would add inefficient regions in the detector that we wanted to avoid.
-Therefore, we rely mainly on exclusivity cuts to remove any potential contamination.
+\item M\o ller electrons reduction: a two-dimensional plot of photon polar 
+   angles as a function of the energy shows an overcrowded region at low 
+   $\theta$ and low energy. This can be seen in figure 
+   \ref{fig:photons_IC_theta_En_1}. This region is mostly populated by the M\o 
+   ller electrons and must be excluded from the analysis. We optimized a linear 
+   cut for this region, shown by the black dashed line. The vertical extension 
+   of this line shows the minimum energy cut ($E_{\gamma}$ > 300 MeV).
+\item We do not apply any timing cut to select the photons in the IC because 
+   its timing is not functioning properly for certain channels. Therefore, 
+   applying a timing cut would add inefficient regions in the detector that we 
+   wanted to avoid.  Therefore, we rely mainly on exclusivity cuts to remove 
+   any potential contamination.
 
@@
 
-The fastmc is applied to the Monte-Carlo generated 
-$^{4}He$ for the channels $e^{4}He\gamma$ and $e^{4}He\pi^{0}$. The other 
-particles are fed to GSIM through the previously mentioned 
+The fastmc is applied to the Monte-Carlo generated $^{4}He$ for the channels 
+$e^{4}He\gamma$ and $e^{4}He\pi^{0}$. We do not specifically apply energy loss 
+and multiple scattering in our fastmc, but we do apply resolution effects based 
+on experimental data that include both effects. The plots in figure 
+\ref{fig:comp_He} show the comparison between data and simulation in terms of 
+theta, $phi$ and momentum of the $^{4}$He DVCS nuclei, that will presented in 
+details in the following chapter. The other particles, ($e^{-}$, $p$, 
+$\gamma$), are fed to GSIM through the previously mentioned 
 simulation-reconstruction chain procedures.
+
+\begin{figure}[tpb]
+   \includegraphics[height=5.0cm]{fig_rtpc/updates/He_theta.png}
+   \includegraphics[height=5.0cm]{fig_rtpc/updates/He_phi.png}
+   \centering
+   \includegraphics[height=5.0cm]{fig_rtpc/updates/He_mom.png}
+   \caption{Comparison between experimental (blue) and simulated (red) DVCS 
+   $^{4}$He nuclei in terms of polar angle, azimuthal angle and momentum.}
+   \label{fig:comp_He}
+\end{figure}
 

### 2016-08-23 analysis-note-v2/experimental_setup.tex
more updates to the RTPC and the DVCS checks, and updated the ALU tables after the 4D background subtraction

@@
 produced at polar angles below 15$^{\circ}$, where the acceptance of the EC
-is small. In the CLAS-E1DVCS experiment 
-(2005), CLAS was upgraded with the addition of an Inner Calorimeter (IC). This 
-calorimeter covers completely the polar angles between 5$^{\circ}$ and 15$^{\circ}$. Figure 
-\ref{fig:CLAS_RTPC_2} shows a schematic plot of our experimental setup. The front face of the IC is facing the downstream side of 
-the Radial TPC (RTPC) and placed at 16 cm from the center of CLAS.\\
+is small. In the CLAS-E1DVCS experiment (2005), CLAS was upgraded with the 
+addition of an Inner Calorimeter (IC). This calorimeter covers completely the 
+polar angles between 5$^{\circ}$ and 15$^{\circ}$. Figure \ref{fig:CLAS_RTPC_2} 
+shows a schematic plot of our experimental setup. The front face of the IC is 
+facing the downstream side of the Radial TPC (RTPC) and placed at 16 cm from 
+the center of CLAS.\\
 
@@
 1.33~$\times$~1.33 cm$^2$ front surface and a 1.6~$\times$~1.6 cm$^2$ back 
-surface. The energy resolution is around 3$\%$ for photon energies between 2 
-GeV and 5 GeV and the angular resolution is between 3 to 5 mrad for the same 
+surface. The energy resolution is around 3 to 4$\%$ for photon energies between 
+2 GeV and 5 GeV and the angular resolution is between 3 to 5 mrad for the same 
 energy range \cite{Hyon-suk}.

### 2016-08-24 analysis-note-v2/RTPC.tex
add the pi0 production yield for both DVCS channels in section 4.5.1

@@
 
-In the left module of the RTPC, figure \ref{fig:dedx_p_exp_2nd}, one notices an 
-additional unexpected lower peak (dEdx$_{exp}$/dEdx$_{sim} \sim$ 0.3). These 
-events pass all the elastic requirements but for some reasons they have lower 
-ADC values. They represent around $7\%$ of all the elastic events. After 
-extended studies, the nature of these particles is not identified yet. We note 
-that this is a global phenomenon in the left module as 94$\%$ of the left 
+In the left module of the RTPC, on the bottom panel of figure \ref{fig:dedxre}, 
+one notices an additional unexpected lower peak (dEdx$_{exp}$/dEdx$_{sim} \sim$ 
+0.3). These events pass all the elastic requirements but for some reasons they 
+have lower ADC values. They represent around $7\%$ of all the elastic events.  
+After extended studies, the nature of these particles is not identified yet. We 
+note that this is a global phenomenon in the left module as 94$\%$ of the left 
 module's pads are involved in both some low and high dEdx events. For instance, 
@@
 \begin{figure}[tbp]
-%\hspace{-0.4in}
+\centering
 \includegraphics[scale=0.3]{fig_rtpc/noisy_pad_before_rejection.png}
 \includegraphics[scale=0.3]{fig_rtpc/noisy_pad_after_rejection.png}
-%\vspace{-0.3in}
 \caption{The integrated ADC vs. TDC of the hits for good tracks before (left) 
@@
 
-An event-based method was implemented to treat this noise by computing an event pedestal for the entire group for cases when there exist neighboring hits.
-Hits in the 8x2 with no neighboring hits outside the group were used to calculated an event pedestal for the group.
-That pedestal is subtracted off all hits in the board in that event.
-If there are no neighboring hits outside the 8x2 group, the whole group is rejected in that event.
-
-The effect of this algorithm on a couple reconstructed tracks is shown in figure~\ref{fig:HotBoardSubtract}.
-The overall result was another 5\% increase in good tracks, and this noise subtraction also allowed to recover 32 more channels previously ignored due to high occupancy.
+An event-based method was implemented to treat this noise by computing an event 
+pedestal for the entire group for cases when there exist neighboring hits.
+Hits in the 8x2 with no neighboring hits outside the group were used to 
+calculated an event pedestal for the group. That pedestal is subtracted off all 
+hits in the board in that event. If there are no neighboring hits outside the 
+8x2 group, the whole group is rejected in that event.
+
+The effect of this algorithm on a couple reconstructed tracks is shown in 
+figure~\ref{fig:HotBoardSubtract}.  The overall result was another 5\% increase 
+in good tracks, and this noise subtraction also allowed to recover 32 more 
+channels previously ignored due to high occupancy.
 
@@
 \begin{figure}[htbp]\centering
-  \includegraphics[width=12cm]{fig_rtpc/Occ2d_norej2.png}
-  \includegraphics[width=12cm,trim={2.5cm 0 0 0},clip]{fig_rtpc/Occ2d_rej.png}
+  \includegraphics[width=12.3cm]{fig_rtpc/Occ2d_norej2.png}
+  \includegraphics[width=12cm,trim={1.9cm 0 0 0},clip]{fig_rtpc/Occ2d_rej.png}
   \caption{Occupancies before (top) and after (bottom) the two noise reduction algorithms.  The event sample and occupancy color scales are identical in the two plots.\label{fig:occ_noiserej}}

### 2016-08-24 analysis-note-v2/analysis-2.tex
add the pi0 production yield for both DVCS channels in section 4.5.1

@@
 
-\begin{figure}[tp]
+Figure \ref{fig:cont_yield} presents the measured coherent and incoherent 
+$\pi^{0}$ production yield with respect to the measured DVCS events. On both 
+channels, the yield increases strongly with -$t$, with a mean of 9$\%$ (34$\%$) 
+for the coherent (incoherent) channel. Multiplying the $\pi^{0}$ production 
+yield with the mean coherent (incoherent) acceptance ratio yields to an 
+estimation of the coherent (incoherent) background yield to be about 3$\%$ 
+(7$\%$).\\
+
+\begin{figure}[tpb]
 \centering
@@
 
-\begin{figure}[tp]
+\begin{figure}[tpb]
 \centering
@@
 \label{fig:incoh_acceptance _ratios}
+\end{figure}
+
+\begin{figure}[tpb]
+\includegraphics[scale=0.37]{fig_updated/T_ratio_pi0_dvcs_Coh_t.png}
+\includegraphics[scale=0.37]{fig_updated/T_ratio_pi0_dvcs_InCoh_t.png}
+\caption{The experimental coherent (left) and incoherent (right) $\pi^{0}$ 
+yield with respect to the experimental DVCS events as a function of the 
+transfered momentum squared -$t$. The data is integrated over the kinematical 
+variables $Q^2$, $x_B$, and $\phi$.  }
+\label{fig:cont_yield}
 \end{figure}

### 2016-08-24 analysis-note-v2/results.tex
add the pi0 production yield for both DVCS channels in section 4.5.1

@@
 \begin{figure}[tpb]
-\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_Q2_90.pdf} 
-\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_xB_90.pdf}
-\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_t_90.pdf} 
+   \centering
+\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_Q2_90.pdf}\\ 
+\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_xB_90.pdf}\\
+\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_t_90.pdf} \\ 
 \caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $-t$-dependencies (bottom) of 

### 2016-08-24 analysis-note-v2/Appendix.tex
more updates to the RTPC and the DVCS checks, and updated the ALU tables after the 4D background subtraction
add the pi0 production yield for both DVCS channels in section 4.5.1
added the model interpolation fot the free proton asymmetries

@@
 \end{tabular}
-\caption{ The mean and sigma values of the exclusive $ep\pi^{0}$ quantities drawn in shaded brown in figure \ref{fig:incohpi0_exclusivty_cuts}.}
+\caption{ The mean and sigma values of the exclusive $ep\pi^{0}$ quantities 
+drawn in shaded brown in figure \ref{fig:incohpi0_exclusivty_cuts}.}
 \label{Table:incohpi0_exclusivity_cuts}
@@
          \hline
-         1.143 & 0.136 & 0.096 &  23.32563   &    0.1370716   $\pm$   
-         0.08373948 $\pm$   0.02571563 \\
-         1.143 & 0.136 & 0.096 &  59.81847   &    0.3758095  $\pm$   0.07101178  $\pm$   0.01885969 \\
-         1.143 & 0.136 & 0.096 &  97.78493   &    0.4125528  $\pm$   0.08798407  $\pm$   0.04038886 \\
-         1.143 & 0.136 & 0.096 &  140.0018   &    0.159693   $\pm$   0.1366452   $\pm$   0.02678967 \\
-         1.143 & 0.136 & 0.096 &  179.0882   &    0.1714253  $\pm$   0.1398893   $\pm$   0.02789155 \\
-         1.143 & 0.136 & 0.096 &  219.1279   &   -0.1240822  $\pm$   0.1156237   $\pm$   0.02484531 \\
-         1.143 & 0.136 & 0.096 &  263.7259   &   -0.3608519  $\pm$   0.09411095  $\pm$   0.03891253 \\
-         1.143 & 0.136 & 0.096 &  302.9283   &   -0.1683747  $\pm$   0.07604881  $\pm$   0.02632836 \\
-         1.143 & 0.136 & 0.096 &  337.3336   &   -0.3508557  $\pm$   0.07680001  $\pm$   0.03431105 \\
-         \hline                                                                          
-         1.423 & 0.172 & 0.099 &  19.94307   &    0.1650792  $\pm$   0.067211    $\pm$   0.02673700 \\
-         1.423 & 0.172 & 0.099 &  57.17185   &    0.3028724  $\pm$   0.068908    $\pm$   0.02503328 \\
-         1.423 & 0.172 & 0.099 &  95.77216   &    0.4372785  $\pm$   0.099537    $\pm$   0.04267748 \\
-         1.423 & 0.172 & 0.099 &  137.9543   &    0.1147926  $\pm$   0.142932    $\pm$   0.02500644 \\
-         1.423 & 0.172 & 0.099 &  180.9498   &    0.1924395  $\pm$   0.1806951   $\pm$   0.03026008 \\
-         1.423 & 0.172 & 0.099 &  220.1671   &   -0.2589808  $\pm$   0.1611112   $\pm$   0.03447198 \\
-         1.423 & 0.172 & 0.099 &  263.1496   &   -0.3065283  $\pm$   0.1158366   $\pm$   0.03663218 \\
-         1.423 & 0.172 & 0.099 &  302.3187   &   -0.3646641  $\pm$   0.069707    $\pm$   0.03835156 \\
-         1.423 & 0.172 & 0.099 &  338.0674   &   -0.1660148  $\pm$   0.069482    $\pm$   0.02613428 \\
-         \hline
-
-         1.902 & 0.224 & 0.107 &  20.96588   &    0.0841330  $\pm$   0.06370723  $\pm$   0.02345626 \\
-         1.902 & 0.224 & 0.107 &  56.59966   &    0.3739804  $\pm$   0.06574343  $\pm$   0.01851792 \\
-         1.902 & 0.224 & 0.107 &  95.79632   &    0.1779531  $\pm$   0.1058264   $\pm$   0.0173685  \\
-         1.902 & 0.224 & 0.107 &  139.5123   &    0.1574064  $\pm$   0.1713567   $\pm$   0.01702304 \\
-         1.902 & 0.224 & 0.107 &  179.5613   &   -0.0837227  $\pm$   0.2119008   $\pm$   0.01265815 \\
-         1.902 & 0.224 & 0.107 &  221.6768   &   -0.1251566  $\pm$   0.1783256   $\pm$   0.01528429 \\
-         1.902 & 0.224 & 0.107 &  263.0872   &   -0.3069055  $\pm$   0.1173135   $\pm$   0.02602474 \\
-         1.902 & 0.224 & 0.107 &  303.6431   &   -0.2404473  $\pm$   0.07568278  $\pm$   0.02071202 \\
-         1.902 & 0.224 & 0.107 &  339.2973   &   -0.184311   $\pm$   0.06150122  $\pm$   0.01635832 \\
+  1.143 & 0.136 & 0.096 &  23.4  &  0.1407   $\pm$ 0.0800   $\pm$  0.0257 \\
+  1.143 & 0.136 & 0.096 &  59.9  &  0.3563   $\pm$ 0.0687   $\pm$  0.0188 \\
+  1.143 & 0.136 & 0.096 &  97.6  &  0.4241   $\pm$ 0.0870   $\pm$  0.0403 \\
+  1.143 & 0.136 & 0.096 &  139.9 &  0.1576   $\pm$ 0.1344   $\pm$  0.0267 \\
+  1.143 & 0.136 & 0.096 &  179.1 &  0.1496   $\pm$ 0.1390   $\pm$  0.0278 \\
+  1.143 & 0.136 & 0.096 &  218.9 & -0.1361   $\pm$ 0.1123   $\pm$  0.0248 \\
+  1.143 & 0.136 & 0.096 &  263.5 & -0.3384   $\pm$ 0.0922   $\pm$  0.0389 \\
+  1.143 & 0.136 & 0.096 &  302.9 & -0.1731   $\pm$ 0.0722   $\pm$  0.0263 \\
+  1.143 & 0.136 & 0.096 &  337.5 & -0.3439   $\pm$ 0.0744   $\pm$  0.0343 \\
+  \hline                                                           
+  1.423 & 0.172 & 0.099 &  19.9  &  0.1538   $\pm$ 0.0650   $\pm$  0.0267 \\
+  1.423 & 0.172 & 0.099 &  57.3  &  0.2941   $\pm$ 0.0684   $\pm$  0.0250 \\
+  1.423 & 0.172 & 0.099 &  95.4  &  0.4352   $\pm$ 0.0997   $\pm$  0.0426 \\
+  1.423 & 0.172 & 0.099 &  138.3 &  0.1251   $\pm$ 0.1418   $\pm$  0.0250 \\
+  1.423 & 0.172 & 0.099 &  181.2 &  0.2139   $\pm$ 0.1813   $\pm$  0.0302 \\
+  1.423 & 0.172 & 0.099 &  220.3 & -0.2494   $\pm$ 0.1646   $\pm$  0.0344 \\
+  1.423 & 0.172 & 0.099 &  263.4 & -0.3187   $\pm$ 0.1128   $\pm$  0.0366 \\
+  1.423 & 0.172 & 0.099 &  302.5 & -0.3429   $\pm$ 0.0695   $\pm$  0.0383 \\
+  1.423 & 0.172 & 0.099 &  338.1 & -0.1382   $\pm$ 0.0680   $\pm$  0.0261 \\
+  \hline                                                                    
+  1.902 & 0.224 & 0.107 &  21.0  &  0.0904   $\pm$ 0.0630   $\pm$  0.0234 \\
+  1.902 & 0.224 & 0.107 &  56.6  &  0.3647   $\pm$ 0.0654   $\pm$  0.0185 \\
+  1.902 & 0.224 & 0.107 &  95.7  &  0.1701   $\pm$ 0.1072   $\pm$  0.0173 \\
+  1.902 & 0.224 & 0.107 &  139.6 &  0.0994   $\pm$ 0.1732   $\pm$  0.0170 \\
+  1.902 & 0.224 & 0.107 &  179.5 & -0.0855   $\pm$ 0.2165   $\pm$  0.0126 \\
+  1.902 & 0.224 & 0.107 &  221.6 & -0.1338   $\pm$ 0.1825   $\pm$  0.0152 \\
+  1.902 & 0.224 & 0.107 &  262.7 & -0.2772   $\pm$ 0.1185   $\pm$  0.0260 \\
+  1.902 & 0.224 & 0.107 &  303.5 & -0.2306   $\pm$ 0.0745   $\pm$  0.0207 \\
+  1.902 & 0.224 & 0.107 &  339.2 & -0.1958   $\pm$ 0.0607   $\pm$  0.0163 \\
          \hline \hline
@@
          \hline
-        1.164 & 0.132 & 0.095 &   24.70837  &    -0.0009864  $\pm$   0.1023417     $\pm$   0.02214862    \\
-        1.164 & 0.132 & 0.095 &   60.38457  &     0.394491   $\pm$   0.06742577    $\pm$   0.01984295    \\
-        1.164 & 0.132 & 0.095 &   98.05482  &     0.4169974  $\pm$   0.0822727     $\pm$   0.04084068    \\
-        1.164 & 0.132 & 0.095 &   140.4849  &     0.2629772  $\pm$   0.1287244     $\pm$   0.03336946    \\
-        1.164 & 0.132 & 0.095 &   178.7877  &     0.1917519  $\pm$   0.133959      $\pm$   0.02937379    \\
-        1.164 & 0.132 & 0.095 &   218.4067  &    -0.1139352  $\pm$   0.1099316     $\pm$   0.02438166    \\
-        1.164 & 0.132 & 0.095 &   263.7104  &    -0.3303477  $\pm$   0.08687361    $\pm$   0.0372357     \\
-        1.164 & 0.132 & 0.095 &   302.0021  &    -0.158615   $\pm$   0.06873616    $\pm$   0.02598807    \\
-        1.164 & 0.132 & 0.095 &   335.3734  &    -0.2978278  $\pm$   0.09144179    $\pm$   0.03198552    \\
-         \hline                                                                         
-         1.439 & 0.17 & 0.099 &    21.20114   &    0.1944966  $\pm$   
-         0.06481715    $\pm$   0.023002136   \\
-        1.439 & 0.17 & 0.099 &    57.05011   &    0.2135007  $\pm$   0.0688628     $\pm$   0.01959182    \\
-        1.439 & 0.17 & 0.099 &    95.32827   &    0.3033697  $\pm$   0.1028014     $\pm$   0.0295878     \\
-        1.439 & 0.17 & 0.099 &    137.6747   &    0.1027237  $\pm$   0.134283      $\pm$   0.01876947    \\
-        1.439 & 0.17 & 0.099 &    180.8816   &   -0.0055032  $\pm$   0.1730991     $\pm$   0.0197908     \\
-        1.439 & 0.17 & 0.099 &    220.8371   &   -0.2294214  $\pm$   0.1615644     $\pm$   0.0270881     \\
-        1.439 & 0.17 & 0.099 &    264.4366   &   -0.2758285  $\pm$   0.1156173     $\pm$   0.02923329    \\
-        1.439 & 0.17 & 0.099 &    302.6414   &   -0.3697083  $\pm$   0.07362371    $\pm$   0.03312501    \\
-        1.439 & 0.17 & 0.099 &    337.925    &   -0.2626907  $\pm$   0.06672689    
-         $\pm$   0.02543044    \\             
-         \hline                                                                         
-         1.844 & 0.225 & 0.107 &   19.94412   &    0.1199148  $\pm$   0.0610976     
-         $\pm$   0.024893846   \\
-        1.844 & 0.225 & 0.107 &   56.1033    &    0.4535308  $\pm$   0.07056983    $\pm$   0.02240954    \\
-        1.844 & 0.225 & 0.107 &   95.56723   &    0.2782661  $\pm$   0.1178502     $\pm$   0.02714954    \\
-        1.844 & 0.225 & 0.107 &   139.3193   &   -0.0854730  $\pm$   0.2144445     $\pm$   0.01668931    \\
-        1.844 & 0.225 & 0.107 &   180.6025   &    0.1409771  $\pm$   0.2599303     $\pm$   0.02044162    \\
-        1.844 & 0.225 & 0.107 &   223.7917   &   -0.2456453  $\pm$   0.2105987     $\pm$   0.02706752    \\
-        1.844 & 0.225 & 0.107 &   260.904    &   -0.3907139  $\pm$   0.1417117     $\pm$   0.03533464    \\
-        1.844 & 0.225 & 0.107 &   304.3742   &   -0.2674945  $\pm$   0.08101173    $\pm$   0.02630272    \\
-        1.844 & 0.225 & 0.107 &   340.0658   &   -0.125335   $\pm$   0.06016415    $\pm$   0.01755089    \\
-         \hline  \hline
-      \end{tabular}
-      \caption{The coherent ALU in $x_B$ bins}
+
+  1.164 & 0.132 & 0.095 & 24.7   &  0.0165   $\pm$ 0.0983    $\pm$   0.0221 \\
+  1.164 & 0.132 & 0.095 & 60.5   &  0.3681   $\pm$ 0.0657    $\pm$   0.0198 \\
+  1.164 & 0.132 & 0.095 & 97.8   &  0.4334   $\pm$ 0.0805    $\pm$   0.0408 \\
+  1.164 & 0.132 & 0.095 & 140.4  &  0.2580   $\pm$ 0.1277    $\pm$   0.0333 \\
+  1.164 & 0.132 & 0.095 & 178.8  &  0.1732   $\pm$ 0.1341    $\pm$   0.0293 \\
+  1.164 & 0.132 & 0.095 & 218.2  & -0.1259   $\pm$ 0.1077    $\pm$   0.0243 \\
+  1.164 & 0.132 & 0.095 & 263.5  & -0.3176   $\pm$ 0.0852    $\pm$   0.0372 \\
+  1.164 & 0.132 & 0.095 & 302.0  & -0.1521   $\pm$ 0.0661    $\pm$   0.0259 \\
+  1.164 & 0.132 & 0.095 & 335.4  & -0.2915   $\pm$ 0.0885    $\pm$   0.0319 \\
+   \hline                                                                     
+  1.439 & 0.17 & 0.099 & 21.1    &  0.1815   $\pm$ 0.0628    $\pm$   0.0230 \\
+  1.439 & 0.17 & 0.099 &  57.0   &  0.2075   $\pm$ 0.0672    $\pm$   0.0195 \\
+  1.439 & 0.17 & 0.099 &  95.1   &  0.3013   $\pm$ 0.1042    $\pm$   0.0295 \\
+  1.439 & 0.17 & 0.099 &  137.9  &  0.0939   $\pm$ 0.1335    $\pm$   0.0187 \\
+  1.439 & 0.17 & 0.099 &  181.1  &  0.0167   $\pm$ 0.1741    $\pm$   0.0197 \\
+  1.439 & 0.17 & 0.099 &  221.0  & -0.2219   $\pm$ 0.1641    $\pm$   0.0270 \\
+  1.439 & 0.17 & 0.099 &  264.4  & -0.2657   $\pm$ 0.1120    $\pm$   0.0292 \\
+  1.439 & 0.17 & 0.099 &  302.9  & -0.3816   $\pm$ 0.0716    $\pm$   0.0331 \\
+  1.439 & 0.17 & 0.099 &  338.0  & -0.2336   $\pm$ 0.0657    $\pm$   0.0254 \\
+   \hline                                                                     
+  1.844 & 0.225 & 0.107 & 19.9   &  0.1286   $\pm$ 0.0601    $\pm$   0.0248 \\
+  1.844 & 0.225 & 0.107 & 56.1   &  0.4551   $\pm$ 0.0713    $\pm$   0.0224 \\
+  1.844 & 0.225 & 0.107 & 95.3   &  0.2540   $\pm$ 0.1201    $\pm$   0.0271 \\
+  1.844 & 0.225 & 0.107 & 139.6  & -0.1136   $\pm$ 0.2150    $\pm$   0.0166 \\
+  1.844 & 0.225 & 0.107 & 180.6  &  0.1414   $\pm$ 0.2634    $\pm$   0.0204 \\
+  1.844 & 0.225 & 0.107 & 223.7  & -0.2158   $\pm$ 0.2097    $\pm$   0.0270 \\
+  1.844 & 0.225 & 0.107 & 260.6  & -0.3623   $\pm$ 0.1442    $\pm$   0.0353 \\
+  1.844 & 0.225 & 0.107 & 304.4  & -0.2359   $\pm$ 0.0814    $\pm$   0.0263 \\
+  1.844 & 0.225 & 0.107 & 340.0  & -0.1393   $\pm$ 0.0593    $\pm$   0.0175 \\
+
+         \hline 
+         \hline
+      \end{tabular}
+      \caption{The coherent $A_{LU}$ in $x_B$ bins}
       \label{table:Coh_xB_BSA}
@@
          \hline
-           1.36 & 0.160 & 0.080 &   21.30242  &  0.1531553   $\pm$  0.07225752   
-         $\pm$  0.026305318    \\
-           1.36 & 0.160 & 0.080 &   57.11194  &  0.2900274   $\pm$  0.06585235   $\pm$  0.02439207     \\
-           1.36 & 0.160 & 0.080 &   96.15277  &  0.4041914   $\pm$  0.09641501   $\pm$  0.03947151     \\
-           1.36 & 0.160 & 0.080 &   137.9588  &  0.1402594   $\pm$  0.1434757    $\pm$  0.02522018     \\
-           1.36 & 0.160 & 0.080 &   179.2052  &  0.3218006   $\pm$  0.1641379    $\pm$  0.03717874     \\
-           1.36 & 0.160 & 0.080 &   221.4243  &  -0.3213178  $\pm$  0.1356342    $\pm$  0.03708316     \\
-           1.36 & 0.160 & 0.080 &   265.92    &  -0.392002   $\pm$  0.1066914    $\pm$  0.04038161     \\
-           1.36 & 0.160 & 0.080 &   301.3226  &  -0.2284983  $\pm$  0.07726413   $\pm$  0.02940459     \\
-           1.36 & 0.160 & 0.080 &   339.661   &  -0.2348847  $\pm$  0.06494273   $\pm$  0.02810254     \\
-         \hline                                                                         
-           1.507 & 0.179 & 0.094 &  21.17746   & 0.1631617   $\pm$  0.07120653   $\pm$  0.026711914     \\
-           1.507 & 0.179 & 0.094 &  56.92214   & 0.3715996   $\pm$  0.06870001   $\pm$  0.02842517      \\
-           1.507 & 0.179 & 0.094 &  97.24788   & 0.3145243   $\pm$  0.09659388   $\pm$  0.03076673      \\
-           1.507 & 0.179 & 0.094 &  141.6889   & 0.1388844   $\pm$  0.1607593    $\pm$  0.02150343      \\
-           1.507 & 0.179 & 0.094 &  179.6762   & -0.3612444  $\pm$  0.1723714    $\pm$  0.03603272      \\
-           1.507 & 0.179 & 0.094 &  220.3783   & -0.029479   $\pm$  0.1576259    $\pm$  0.01477838      \\
-           1.507 & 0.179 & 0.094 &  262.64     & -0.2524102  $\pm$  0.1096333    $\pm$  0.02830972      \\
-           1.507 & 0.179 & 0.094 &  303.6787   & -0.282367   $\pm$  0.07599572   $\pm$  0.02864878      \\
-           1.507 & 0.179 & 0.094 &  338.2113   & -0.1464348  $\pm$  0.07113145   $\pm$  0.02012911      \\
-         \hline                                                                       
-         1.610 & 0.193 & 0.127 &  21.08428   & 0.0341355   $\pm$  0.07013161   
-         $\pm$   0.021403381     \\
-           1.610 & 0.193 & 0.127 &  59.38832   & 0.4083206   $\pm$  0.07247885   $\pm$   0.02045513      \\
-           1.610 & 0.193 & 0.127 &  96.08225   & 0.3209038   $\pm$  0.1013991    $\pm$   0.0313346       \\
-           1.610 & 0.193 & 0.127 &  138.5581   & 0.1170443   $\pm$  0.146122     $\pm$   0.02038013      \\
-           1.610 & 0.193 & 0.127 &  180.2608   & 0.3477719   $\pm$  0.1581127    $\pm$   0.0354366       \\
-           1.610 & 0.193 & 0.127 &  218.4883   & -0.091217   $\pm$  0.142311     $\pm$   0.01898904      \\
-           1.610 & 0.193 & 0.127 &  261.3985   & -0.320382   $\pm$  0.1108918    $\pm$   0.0327608       \\
-           1.610 & 0.193 & 0.127 &  303.3648   & -0.266328   $\pm$  0.07080153   $\pm$   0.02802882      \\
-           1.610 & 0.193 & 0.127 &  337.2208   & -0.261976   $\pm$  0.07224138   $\pm$   0.02615273      \\
+  1.36 & 0.160 & 0.080 &  21.3   &  0.1692   $\pm$ 0.0708    $\pm$  0.0263  \\
+  1.36 & 0.160 & 0.080 &  57.2   &  0.2972   $\pm$ 0.0644    $\pm$  0.0243  \\
+  1.36 & 0.160 & 0.080 &  95.9   &  0.4170   $\pm$ 0.0954    $\pm$  0.0394  \\
+  1.36 & 0.160 & 0.080 &  138.1  &  0.1374   $\pm$ 0.1434    $\pm$  0.0252  \\
+  1.36 & 0.160 & 0.080 &  179.2  &  0.3245   $\pm$ 0.1657    $\pm$  0.0371  \\
+  1.36 & 0.160 & 0.080 &  221.6  & -0.2851   $\pm$ 0.1376    $\pm$  0.0370  \\
+  1.36 & 0.160 & 0.080 &  265.6  & -0.4009   $\pm$ 0.1050    $\pm$  0.0403  \\
+  1.36 & 0.160 & 0.080 &  301.6  & -0.2257   $\pm$ 0.0746    $\pm$  0.0294  \\
+  1.36 & 0.160 & 0.080 &  339.7  & -0.2312   $\pm$ 0.0637    $\pm$  0.0281  \\
+\hline                                                              
+  1.507 & 0.179 & 0.094 & 21.2   &  0.1593   $\pm$ 0.0696    $\pm$  0.0267  \\
+  1.507 & 0.179 & 0.094 & 57.0   &  0.3607   $\pm$ 0.0679    $\pm$  0.0284  \\
+  1.507 & 0.179 & 0.094 & 97.0   &  0.2913   $\pm$ 0.0971    $\pm$  0.0307  \\
+  1.507 & 0.179 & 0.094 & 141.6  &  0.1033   $\pm$ 0.1621    $\pm$  0.0215  \\
+  1.507 & 0.179 & 0.094 & 179.6  & -0.3610   $\pm$ 0.1755    $\pm$  0.0360  \\
+  1.507 & 0.179 & 0.094 & 220.1  & -0.0705   $\pm$ 0.1583    $\pm$  0.0147  \\
+  1.507 & 0.179 & 0.094 & 262.5  & -0.1960   $\pm$ 0.1079    $\pm$  0.0283  \\
+  1.507 & 0.179 & 0.094 & 303.5  & -0.2605   $\pm$ 0.0763    $\pm$  0.0286  \\
+  1.507 & 0.179 & 0.094 & 338.2  & -0.1241   $\pm$ 0.0700    $\pm$  0.0201  \\
+\hline                                                                         
+  1.610 & 0.193 & 0.127 & 21.0   &  0.0248   $\pm$ 0.0675    $\pm$  0.0214  \\
+  1.610 & 0.193 & 0.127 & 59.4   &  0.3820   $\pm$ 0.0725    $\pm$  0.0204  \\
+  1.610 & 0.193 & 0.127 & 95.8   &  0.3454   $\pm$ 0.1021    $\pm$  0.0313  \\
+  1.610 & 0.193 & 0.127 & 138.6  &  0.1427   $\pm$ 0.1440    $\pm$  0.0203  \\
+  1.610 & 0.193 & 0.127 & 180.4  &  0.3198   $\pm$ 0.1557    $\pm$  0.0354  \\
+  1.610 & 0.193 & 0.127 & 218.4  & -0.0996   $\pm$ 0.1403    $\pm$  0.0189  \\
+  1.610 & 0.193 & 0.127 & 261.4  & -0.3095   $\pm$ 0.1103    $\pm$  0.0327  \\
+  1.610 & 0.193 & 0.127 & 303.3  & -0.2537   $\pm$ 0.0689    $\pm$  0.0280  \\
+  1.610 & 0.193 & 0.127 & 337.2  & -0.2732   $\pm$ 0.0703    $\pm$  0.0261  \\
+
          \hline
@@
  $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
- \hline  1.395 & 0.166 & 0.407  &   21.10406  &  0.04811468 $\pm$  0.04658231  
-         $\pm$  0.012062557     \\
-  1.395 & 0.166 & 0.407  &   61.33965  &  0.0836005  $\pm$  0.0531715   $\pm$  0.015623204     \\
-  1.395 & 0.166 & 0.407  &   95.84617  &  0.1792438  $\pm$  0.05315892  $\pm$  0.02637904      \\
-  1.395 & 0.166 & 0.407  &   140.0124  &  0.04524659 $\pm$  0.07010027  $\pm$  0.0158652       \\
-  1.395 & 0.166 & 0.407  &   181.9726  &  0.1242038  $\pm$  0.08510458  $\pm$  0.02346724      \\
-  1.395 & 0.166 & 0.407  &   219.0216  &  0.03828423 $\pm$  0.07649991  $\pm$  0.01509915      \\
-  1.395 & 0.166 & 0.407  &   259.0493  &  -0.1422473 $\pm$  0.0495869   $\pm$  0.02266091      \\
-  1.395 & 0.166 & 0.407  &   303.8597  &  -0.1478417 $\pm$  0.03942399  $\pm$  0.01968592      \\
-  1.395 & 0.166 & 0.407  &   337.5399  &  -0.0844819 $\pm$  0.04879445  $\pm$  
- 0.01425768      \\
- \hline                                                                      
- 1.886 & 0.233 & 0.499 &    20.62881  &  -0.0058365 $\pm$  0.03877985  $\pm$  
- 0.012482536     \\
-  1.886 & 0.233 & 0.499 &    58.90961  &  0.1058029  $\pm$  0.05262749  $\pm$  0.016983385     \\
-  1.886 & 0.233 & 0.499 &    95.93819  &  0.1373368  $\pm$  0.06176916  $\pm$  0.02021609      \\
-  1.886 & 0.233 & 0.499 &    141.0758  &  0.2106814  $\pm$  0.09877572  $\pm$  0.02858216      \\
-  1.886 & 0.233 & 0.499 &    179.8328  &  0.06009099 $\pm$  0.1188988   $\pm$  0.01464961      \\
-  1.886 & 0.233 & 0.499 &    220.9095  &  -0.03806458 $\pm$  0.1066278   $\pm$  
- 0.04304848      \\
-  1.886 & 0.233 & 0.499 &    260.608   &  -0.1192977 $\pm$  0.07428519  $\pm$  0.01808374      \\
-  1.886 & 0.233 & 0.499 &    304.2599  &  -0.2011292 $\pm$  0.05552498  $\pm$  0.0198082       \\
-  1.886 & 0.233 & 0.499 &    338.4649  &  -0.0815212 $\pm$  0.0567802   $\pm$  0.01138369      \\
- \hline
-
-  2.338 & 0.29 & 0.521  &    20.72956  &  0.08229175 $\pm$  0.03744839  $\pm$  0.013506039    \\ 
-  2.338 & 0.29 & 0.521  &    56.90895  &  0.155593   $\pm$  0.05379751  $\pm$  0.01010521     \\ 
-  2.338 & 0.29 & 0.521  &    94.91647  &  0.05217237 $\pm$  0.0715696   $\pm$  0.017660975    \\ 
-  2.338 & 0.29 & 0.521  &    141.1955  &  0.1371172  $\pm$  0.1260972   $\pm$  0.01618568     \\ 
-  2.338 & 0.29 & 0.521  &    181.6533  &  -0.2127209 $\pm$  0.1556657   $\pm$  0.02363223     \\ 
-  2.338 & 0.29 & 0.521  &    224.0629  &  0.2006703  $\pm$  0.1501709   $\pm$  0.02122811     \\ 
-  2.338 & 0.29 & 0.521  &    261.0354  &  -0.2716077 $\pm$  0.09343596  $\pm$  0.02419026     \\ 
-  2.338 & 0.29 & 0.521  &    303.8146  &  -0.2199163 $\pm$  0.06880397  $\pm$  0.01534961     \\ 
-  2.338 & 0.29 & 0.521  &    339.3798  &  -0.0379564 $\pm$  0.06803362  $\pm$  0.014507918    \\ 
- \hline
-
-  3.098 &0.379 & 0.65  &     20.11158  &  0.1124871  $\pm$  0.03615842  $\pm$  0.014743619    \\ 
-  3.098 &0.379 & 0.65  &     56.98647  &  0.0725830  $\pm$  0.0555646   $\pm$  0.014717011    \\ 
-  3.098 &0.379 & 0.65  &     95.74599  &  0.1911079  $\pm$  0.07990027  $\pm$  0.02811833     \\ 
-  3.098 &0.379 & 0.65  &     137.8186  &  -0.005798  $\pm$  0.1509773   $\pm$  0.01296021     \\ 
-  3.098 &0.379 & 0.65  &     179.3002  &  -0.605363  $\pm$  0.2490573   $\pm$  0.027008585    \\ 
-  3.098 &0.379 & 0.65  &     227.8571  &  0.1695245  $\pm$  0.1915087   $\pm$  0.02732611     \\ 
-  3.098 &0.379 & 0.65  &     263.4649  &  -0.120036  $\pm$  0.09407594  $\pm$  0.02149023     \\ 
-  3.098 &0.379 & 0.65  &     303.8994  &  -0.178453  $\pm$  0.04217566  $\pm$  0.02211641     \\ 
-  3.098 &0.379 & 0.65  &     340.4588  &  -0.059749  $\pm$  0.03455414  $\pm$  
- 0.01412915     \\ \hline
+ \hline
+
+   1.395 & 0.166 & 0.407  & 21.1  &  0.0458   $\pm$  0.0468   $\pm$   0.0120\\
+   1.395 & 0.166 & 0.407  & 61.3  &  0.0844   $\pm$  0.0539   $\pm$   0.0156  \\
+   1.395 & 0.166 & 0.407  & 95.8  &  0.1808   $\pm$  0.0540   $\pm$   0.0263  \\
+   1.395 & 0.166 & 0.407  & 140.0 &  0.0467   $\pm$  0.0698   $\pm$   0.0158  \\
+   1.395 & 0.166 & 0.407  & 181.9 &  0.1255   $\pm$  0.0856   $\pm$   0.0234  \\
+   1.395 & 0.166 & 0.407  & 219.0 &  0.0400   $\pm$  0.0781   $\pm$   0.0150  \\
+   1.395 & 0.166 & 0.407  & 259.0 & -0.1447   $\pm$  0.0521   $\pm$   0.0226  \\
+   1.395 & 0.166 & 0.407  & 303.8 & -0.1555   $\pm$  0.0462   $\pm$   0.0196  \\
+   1.395 & 0.166 & 0.407  & 337.5 & -0.0785   $\pm$  0.0548   $\pm$   0.0142  \\
+  \hline                                                                        
+   1.886 & 0.233 & 0.499  & 20.6  & -0.0028   $\pm$  0.0393   $\pm$   0.0124  \\
+   1.886 & 0.233 & 0.499  & 58.8  &  0.1047   $\pm$  0.0546   $\pm$   0.0169  \\
+   1.886 & 0.233 & 0.499  & 95.9  &  0.1340   $\pm$  0.0630   $\pm$   0.0202  \\
+   1.886 & 0.233 & 0.499  & 141.0 &  0.2096   $\pm$  0.1020   $\pm$   0.0285  \\
+   1.886 & 0.233 & 0.499  & 179.9 &  0.0636   $\pm$  0.1168   $\pm$   0.0146  \\
+   1.886 & 0.233 & 0.499  & 220.9 & -0.3552   $\pm$  0.0996   $\pm$   0.0430  \\
+   1.886 & 0.233 & 0.499  & 260.6 & -0.1227   $\pm$  0.0663   $\pm$   0.0180  \\
+   1.886 & 0.233 & 0.499  & 304.3 & -0.1557   $\pm$  0.0456   $\pm$   0.0198  \\
+   1.886 & 0.233 & 0.499  & 338.3 & -0.0539   $\pm$  0.0480   $\pm$   0.0113  \\
+  \hline                                                                        
+   2.338 & 0.29 & 0.521   & 20.8  &  0.0846   $\pm$  0.0380   $\pm$   0.0135  \\
+   2.338 & 0.29 & 0.521   & 57.0  &  0.1536   $\pm$  0.0565   $\pm$   0.0101  \\
+   2.338 & 0.29 & 0.521   & 94.9  &  0.0748   $\pm$  0.0740   $\pm$   0.0176  \\
+   2.338 & 0.29 & 0.521   & 141.5 &  0.1261   $\pm$  0.1354   $\pm$   0.0161  \\
+   2.338 & 0.29 & 0.521   & 181.4 & -0.1884   $\pm$  0.1518   $\pm$   0.0236  \\
+   2.338 & 0.29 & 0.521   & 224.3 &  0.1556   $\pm$  0.1398   $\pm$   0.0212  \\
+   2.338 & 0.29 & 0.521   & 261.1 & -0.2427   $\pm$  0.0761   $\pm$   0.0241  \\
+   2.338 & 0.29 & 0.521   & 303.8 & -0.1815   $\pm$  0.0479   $\pm$   0.0153  \\
+   2.338 & 0.29 & 0.521   & 339.3 & -0.0523   $\pm$  0.0446   $\pm$   0.0145  \\
+  \hline                                                                        
+   3.098 &0.379 & 0.65    & 20.0  &  0.1118   $\pm$  0.0360   $\pm$   0.0147  \\
+   3.098 &0.379 & 0.65    & 57.1  &  0.0748   $\pm$  0.0554   $\pm$   0.0147  \\
+   3.098 &0.379 & 0.65    & 95.6  &  0.1828   $\pm$  0.0824   $\pm$   0.0281  \\
+   3.098 &0.379 & 0.65    & 137.9 &  0.0110   $\pm$  0.1556   $\pm$   0.0129  \\
+   3.098 &0.379 & 0.65    & 179.3 & -0.5153   $\pm$  0.2431   $\pm$   0.0270  \\
+   3.098 &0.379 & 0.65    & 227.8 &  0.1851   $\pm$  0.2047   $\pm$   0.0273  \\
+   3.098 &0.379 & 0.65    & 263.4 & -0.1140   $\pm$  0.1028   $\pm$   0.0214  \\
+   3.098 &0.379 & 0.65    & 303.9 & -0.1947   $\pm$  0.0501   $\pm$   0.0221  \\
+   3.098 &0.379 & 0.65    & 340.3 & -0.0634   $\pm$  0.0414   $\pm$   0.0141  \\
+
+ \hline
  \hline
@@
          \hline
-  1.425 & 0.162 & 0.397 &   21.03589  &  0.08658236   $\pm$  0.04970597   $\pm$  0.013707438    \\
-  1.425 & 0.162 & 0.397 &   62.13969  &  0.09617981   $\pm$  0.0520029    $\pm$  0.016508612    \\
-  1.425 & 0.162 & 0.397 &   95.88097  &  0.1468384    $\pm$  0.05007717   $\pm$  0.02161179     \\
-  1.425 & 0.162 & 0.397 &   140.2158  &  0.05840751   $\pm$  0.06522249   $\pm$  0.0149864      \\
-  1.425 & 0.162 & 0.397 &   181.147   &  0.1472116    $\pm$  0.07694323   $\pm$  0.02355567     \\
-  1.425 & 0.162 & 0.397 &   218.8907  &  -0.0045843   $\pm$  0.07180578   $\pm$  0.01995755     \\
-  1.425 & 0.162 & 0.397 &   259.1392  &  -0.1140192   $\pm$  0.04807579   $\pm$  0.01836548     \\
-  1.425 & 0.162 & 0.397 &   303.893   &  -0.1078614   $\pm$  0.04183492   $\pm$  0.01540446     \\
-  1.425 & 0.162 & 0.397 &   337.0219  &  -0.0313563   $\pm$  0.05506042   $\pm$  0.01052464     \\
-  \hline
-
-  1.922 & 0.227 & 0.418 &   22.06063  &  -0.0071624   $\pm$  0.04158333   $\pm$  0.013118195    \\
-  1.922 & 0.227 & 0.418 &   58.5659   &  0.09277118   $\pm$  0.05070619   $\pm$  0.016106517    \\
-  1.922 & 0.227 & 0.418 &   96.23033  &  0.1248119    $\pm$  0.05973952   $\pm$  0.01838518     \\
-  1.922 & 0.227 & 0.418 &   141.4482  &  0.1767175    $\pm$  0.09500723   $\pm$  0.0246086      \\
-  1.922 & 0.227 & 0.418 &   181.8282  &  -0.0887164   $\pm$  0.1180524    $\pm$  0.01655364     \\
-  1.922 & 0.227 & 0.418 &   221.2517  &  -0.2925814   $\pm$  0.102211     $\pm$  0.03431685     \\
-  1.922 & 0.227 & 0.418 &   260.3485  &  -0.1909171   $\pm$  0.06539497   $\pm$  0.02278749     \\
-  1.922 & 0.227 & 0.418 &   303.5284  &  -0.2302893   $\pm$  0.05094602   $\pm$  0.02067598     \\
-  1.922 & 0.227 & 0.418 &   337.3474  &  -0.0637682   $\pm$  0.05413252   $\pm$  0.01008997     \\
-  \hline
-
-  2.354 & 0.287 & 0.492 &   20.85891  &  0.04657884   $\pm$  0.036766     $\pm$  0.01988718     \\
-  2.354 & 0.287 & 0.492 &   57.91331  &  0.1459641    $\pm$  0.0526584    $\pm$  0.019557668    \\
-  2.354 & 0.287 & 0.492 &   94.69206  &  0.128379     $\pm$  0.07104001   $\pm$  0.01884086     \\
-  2.354 & 0.287 & 0.492 &   139.8528  &  0.1707919    $\pm$  0.1258279    $\pm$  0.02424851     \\
-  2.354 & 0.287 & 0.492 &   179.8321  &  -0.3851509   $\pm$  0.1628791    $\pm$  0.014502416    \\
-  2.354 & 0.287 & 0.492 &   225.9931  &  0.359824     $\pm$  0.1375561    $\pm$  0.014015373    \\
-  2.354 & 0.287 & 0.492 &   261.519   &  -0.2473872   $\pm$  0.08518201   $\pm$  0.02723866     \\
-  2.354 & 0.287 & 0.492 &   304.2744  &  -0.1756475   $\pm$  0.04527543   $\pm$  0.01784578     \\
-  2.354 & 0.287 & 0.492 &   338.8707  &  -0.0591266   $\pm$  0.04527858   $\pm$  0.01010778     \\
- \hline
-
-  2.987 & 0.390 & 0.714 &   19.433    &  0.1032664    $\pm$  0.03435814   $\pm$  0.014305278    \\
-  2.987 & 0.390 & 0.714 &   55.24427  &  0.07535726   $\pm$  0.06348906   $\pm$  0.014826822    \\
-  2.987 & 0.390 & 0.714 &   95.27441  &  0.21340720   $\pm$  0.1066241    $\pm$  0.03136377     \\
-  2.987 & 0.390 & 0.714 &   134.3823  &  -0.2684007   $\pm$  0.2723481    $\pm$  0.03863117     \\
-  2.987 & 0.390 & 0.714 &   182.475   &  3.6842530    $\pm$  5.592241     $\pm$  0.03642855     \\
-  2.987 & 0.390 & 0.714 &   232.2045  &  -0.3810377   $\pm$  0.426418     $\pm$  0.04691644     \\
-  2.987 & 0.390 & 0.714 &   264.8367  &  -0.0853021   $\pm$  0.1126019    $\pm$  0.02026491     \\
-  2.987 & 0.390 & 0.714 &   304.1341  &  -0.1678875   $\pm$  0.04062397   $\pm$  0.02296748     \\
-  2.987 & 0.390 & 0.714 &   341.2705  &  -0.0649467   $\pm$  0.03014188   $\pm$  0.01568537     \\
+  1.425 & 0.162 & 0.397 & 21.0  &  0.0851   $\pm$   0.0499   $\pm$   0.0137  \\
+  1.425 & 0.162 & 0.397 & 62.1  &  0.0962   $\pm$   0.0523   $\pm$   0.0165  \\
+  1.425 & 0.162 & 0.397 & 95.9  &  0.1472   $\pm$   0.0512   $\pm$   0.0216  \\
+  1.425 & 0.162 & 0.397 & 140.2 &  0.0597   $\pm$   0.0664   $\pm$   0.0149  \\
+  1.425 & 0.162 & 0.397 & 181.1 &  0.1512   $\pm$   0.0787   $\pm$   0.0235  \\
+  1.425 & 0.162 & 0.397 & 218.9 & -0.0048   $\pm$   0.0739   $\pm$   0.0199  \\
+  1.425 & 0.162 & 0.397 & 259.1 & -0.1158   $\pm$   0.0501   $\pm$   0.0183  \\
+  1.425 & 0.162 & 0.397 & 303.9 & -0.1144   $\pm$   0.0456   $\pm$   0.0154  \\
+  1.425 & 0.162 & 0.397 & 337.0 & -0.0259   $\pm$   0.0593   $\pm$   0.0105  \\
+  \hline                                                                       
+  1.922 & 0.227 & 0.418 & 22.0  & -0.0075   $\pm$   0.0418   $\pm$   0.0131  \\
+  1.922 & 0.227 & 0.418 & 58.6  &  0.0927   $\pm$   0.0521   $\pm$   0.0161  \\
+  1.922 & 0.227 & 0.418 & 96.2  &  0.1255   $\pm$   0.0609   $\pm$   0.0183  \\
+  1.922 & 0.227 & 0.418 & 141.5 &  0.1686   $\pm$   0.0984   $\pm$   0.0246  \\
+  1.922 & 0.227 & 0.418 & 181.9 & -0.0727   $\pm$   0.1182   $\pm$   0.0165  \\
+  1.922 & 0.227 & 0.418 & 221.3 & -0.2948   $\pm$   0.0996   $\pm$   0.0343  \\
+  1.922 & 0.227 & 0.418 & 260.3 & -0.1894   $\pm$   0.0620   $\pm$   0.0227  \\
+  1.922 & 0.227 & 0.418 & 303.5 & -0.1977   $\pm$   0.0445   $\pm$   0.0206  \\
+  1.922 & 0.227 & 0.418 & 337.3 & -0.0491   $\pm$   0.0488   $\pm$   0.0100  \\
+  \hline                                                                       
+  2.354 & 0.287 & 0.492 & 20.9  &  0.0491   $\pm$   0.0367   $\pm$   0.0198  \\
+  2.354 & 0.287 & 0.492 & 58.0  &  0.1337   $\pm$   0.0538   $\pm$   0.0195  \\
+  2.354 & 0.287 & 0.492 & 94.8  &  0.1534   $\pm$   0.0730   $\pm$   0.0188  \\
+  2.354 & 0.287 & 0.492 & 140.0 &  0.1744   $\pm$   0.1359   $\pm$   0.0242  \\
+  2.354 & 0.287 & 0.492 & 179.7 & -0.3678   $\pm$   0.1619   $\pm$   0.0145  \\
+  2.354 & 0.287 & 0.492 & 226.0 &  0.3453   $\pm$   0.1400   $\pm$   0.0140  \\
+  2.354 & 0.287 & 0.492 & 261.5 & -0.2282   $\pm$   0.0813   $\pm$   0.0272  \\
+  2.354 & 0.287 & 0.492 & 304.3 & -0.1633   $\pm$   0.0449   $\pm$   0.0178  \\
+  2.354 & 0.287 & 0.492 & 338.8 & -0.0690   $\pm$   0.0439   $\pm$   0.0101  \\
+ \hline                                                                        
+  2.987 & 0.390 & 0.714 & 19.4  &  0.1056   $\pm$   0.0343   $\pm$   0.0143  \\
+  2.987 & 0.390 & 0.714 & 55.3  &  0.0876   $\pm$   0.0639   $\pm$   0.0148  \\
+  2.987 & 0.390 & 0.714 & 95.2  &  0.1853   $\pm$   0.1072   $\pm$   0.0313  \\
+  2.987 & 0.390 & 0.714 & 134.7 & -0.1877   $\pm$   0.2731   $\pm$   0.0386  \\
+  2.987 & 0.390 & 0.714 & 182.5 & -0.1941   $\pm$   1.1518   $\pm$   0.0364  \\
+  2.987 & 0.390 & 0.714 & 232.2 & -0.2499   $\pm$   0.4586   $\pm$   0.0469  \\
+  2.987 & 0.390 & 0.714 & 264.9 & -0.0713   $\pm$   0.1344   $\pm$   0.0202  \\
+  2.987 & 0.390 & 0.714 & 304.2 & -0.2116   $\pm$   0.0565   $\pm$   0.0229  \\
+  2.987 & 0.390 & 0.714 & 341.1 & -0.0758   $\pm$   0.0401   $\pm$   0.0156  \\
+
          \hline
@@
   \hline
-   1.823 & 0.213 & 0.145 &   22.36456  &   0.08044984  $\pm$  0.044171     $\pm$  0.013519389    \\
-   1.823 & 0.213 & 0.145 &   57.76681  &   0.139094    $\pm$  0.05252524   $\pm$  0.019097037    \\
-   1.823 & 0.213 & 0.145 &   97.34826  &   0.1215345   $\pm$  0.05070444   $\pm$  0.01794958     \\
-   1.823 & 0.213 & 0.145 &   141.6077  &   0.1973951   $\pm$  0.07158507   $\pm$  0.0263301      \\
-   1.823 & 0.213 & 0.145 &   180.9132  &   0.03301465  $\pm$  0.087735     $\pm$  0.01504234     \\
-   1.823 & 0.213 & 0.145 &   219.6382  &   0.00344467  $\pm$  0.07526837   $\pm$  0.018209534    \\
-   1.823 & 0.213 & 0.145 &   261.1274  &  -0.1527359   $\pm$  0.05030086   $\pm$  0.01958999     \\
-   1.823 & 0.213 & 0.145 &   303.674   &  -0.1071745   $\pm$  0.04406731   $\pm$  0.0137369      \\
-   1.823 & 0.213 & 0.145 &   337.0581  &  -0.06869941  $\pm$  0.04715184   $\pm$  0.01004524     \\
- \hline
-
-  2.127 & 0.255 & 0.282  &   21.36259  &  0.07262895   $\pm$ 0.04230211    $\pm$  0.013126559   \\
-  2.127 & 0.255 & 0.282  &   59.22203  &  0.03806518   $\pm$ 0.04905662    $\pm$  0.012518665   \\
-  2.127 & 0.255 & 0.282  &   95.55563  &  0.22988040   $\pm$ 0.05867932    $\pm$  0.03380763    \\
-  2.127 & 0.255 & 0.282  &   140.5704  &  -0.03154477  $\pm$ 0.08162287    
- $\pm$  0.0178829     \\
-  2.127 & 0.255 & 0.282  &   181.2953  &  -0.1565047   $\pm$ 0.10092       $\pm$  0.0298368     \\
-  2.127 & 0.255 & 0.282  &   219.844   &  -0.03787627  $\pm$ 0.09359193    $\pm$  0.01834677    \\
-  2.127 & 0.255 & 0.282  &   259.6599  &  -0.1349929   $\pm$ 0.05604338    $\pm$  0.02535689    \\
-  2.127 & 0.255 & 0.282  &   304.1345  &  -0.1822338   $\pm$ 0.03916768    $\pm$  0.02481545    \\
-  2.127 & 0.255 & 0.282  &   338.5113  &  -0.07208852  $\pm$ 0.04495988    $\pm$  0.01711214    \\
- \hline                                                                          
-  2.308 & 0.284 & 0.490 &    20.67062  &  0.129165     $\pm$ 0.0415758     $\pm$  0.015497728  \\
-  2.308 & 0.284 & 0.490 &    59.71279  &  0.113594     $\pm$ 0.05196332    $\pm$  0.017545246  \\
-  2.308 & 0.284 & 0.490 &    94.41645  &  0.1003674    $\pm$ 0.06511375    $\pm$  0.01472001   \\
-  2.308 & 0.284 & 0.490 &    137.7611  &  0.1088956    $\pm$ 0.1159367     $\pm$  0.01662967   \\
-  2.308 & 0.284 & 0.490 &    181.8561  &  0.3436873    $\pm$ 0.1353462     $\pm$  0.03922332   \\
-  2.308 & 0.284 & 0.490 &    225.1743  &  -0.06749131  $\pm$ 0.1106012     $\pm$  0.01250426   \\
-  2.308 & 0.284 & 0.490 &    259.4171  &  -0.2186645   $\pm$ 0.06202168    $\pm$  0.02341567   \\
-  2.308 & 0.284 & 0.490 &    302.9163  &  -0.1778958   $\pm$ 0.03422616    $\pm$  0.01629588   \\
-  2.308 & 0.284 & 0.490 &    338.8539  &  -0.04591294  $\pm$ 0.03922611    $\pm$  0.017893601  \\
- \hline                         
-   2.406 & 0.308 & 1.107&    20.16669  &  0.01851554   $\pm$ 0.03466921    $\pm$ 0.017815254  \\
-   2.406 & 0.308 & 1.107&    57.08842  &  0.167122     $\pm$ 0.06853916    $\pm$ 0.01086996   \\
-   2.406 & 0.308 & 1.107&    93.11341  &  0.07585309   $\pm$ 0.140148      $\pm$ 0.01108901   \\
-   2.406 & 0.308 & 1.107&    132.8371  &  -0.1390574   $\pm$ 0.4839775     $\pm$ 0.01772069   \\
-   2.406 & 0.308 & 1.107&    177.344   &  1.854154     $\pm$ 0.5453675     $\pm$ 0.01816686   \\ 
-   2.406 & 0.308 & 1.107&    228.2105  &  5.778605     $\pm$ 10.58589      $\pm$ 0.01512427   \\
-   2.406 & 0.308 & 1.107&    263.1194  &  0.02895751   $\pm$ 0.1390042     $\pm$ 0.017122356  \\
-   2.406 & 0.308 & 1.107&    305.0914  &  -0.1501369   $\pm$ 0.04840413    $\pm$ 0.01297528   \\
-   2.406 & 0.308 & 1.107&    340.095   &  -0.05253375  $\pm$ 0.03990596    $\pm$ 0.016446498  \\
+
+   1.823 & 0.213 & 0.145 & 22.4  &  0.0982   $\pm$   0.0432   $\pm$  0.0135  \\
+   1.823 & 0.213 & 0.145 & 57.8  &  0.1317   $\pm$   0.0511   $\pm$  0.0190  \\
+   1.823 & 0.213 & 0.145 & 97.3  &  0.1323   $\pm$   0.0506   $\pm$  0.0179  \\
+   1.823 & 0.213 & 0.145 & 141.7 &  0.1940   $\pm$   0.0722   $\pm$  0.0263  \\
+   1.823 & 0.213 & 0.145 & 180.9 &  0.0430   $\pm$   0.0879   $\pm$  0.0150  \\
+   1.823 & 0.213 & 0.145 & 219.8 & -0.0043   $\pm$   0.0770   $\pm$  0.0182  \\
+   1.823 & 0.213 & 0.145 & 261.2 & -0.1480   $\pm$   0.0515   $\pm$  0.0195  \\
+   1.823 & 0.213 & 0.145 & 303.8 & -0.1063   $\pm$   0.0455   $\pm$  0.0137  \\
+   1.823 & 0.213 & 0.145 & 337.0 & -0.0677   $\pm$   0.0481   $\pm$  0.0100  \\
+ \hline                                                                       
+  2.127 & 0.255 & 0.282  & 21.3  &  0.0649   $\pm$   0.0425   $\pm$  0.0131  \\
+  2.127 & 0.255 & 0.282  & 59.3  &  0.0381   $\pm$   0.0500   $\pm$  0.0125  \\
+  2.127 & 0.255 & 0.282  & 95.6  &  0.2284   $\pm$   0.0594   $\pm$  0.0338  \\
+  2.127 & 0.255 & 0.282  & 140.6 & -0.0309   $\pm$   0.0836   $\pm$  0.0178  \\
+  2.127 & 0.255 & 0.282  & 181.3 & -0.1563   $\pm$   0.1041   $\pm$  0.0298  \\
+  2.127 & 0.255 & 0.282  & 219.8 & -0.0397   $\pm$   0.0986   $\pm$  0.0183  \\
+  2.127 & 0.255 & 0.282  & 259.7 & -0.1446   $\pm$   0.0619   $\pm$  0.0253  \\
+  2.127 & 0.255 & 0.282  & 304.1 & -0.2071   $\pm$   0.0459   $\pm$  0.0248  \\
+  2.127 & 0.255 & 0.282  & 338.5 & -0.0836   $\pm$   0.0521   $\pm$  0.0171  \\
+ \hline                                                                
+  2.308 & 0.284 & 0.490 &  20.7  &  0.1282   $\pm$   0.0430   $\pm$  0.0154  \\
+  2.308 & 0.284 & 0.490 &  59.7  &  0.1127   $\pm$   0.0532   $\pm$  0.0175  \\
+  2.308 & 0.284 & 0.490 &  94.4  &  0.0998   $\pm$   0.0676   $\pm$  0.0147  \\
+  2.308 & 0.284 & 0.490 &  137.8 &  0.1089   $\pm$   0.1253   $\pm$  0.0166  \\
+  2.308 & 0.284 & 0.490 &  181.9 &  0.3437   $\pm$   0.1419   $\pm$  0.0392  \\
+  2.308 & 0.284 & 0.490 &  225.2 & -0.0714   $\pm$   0.1217   $\pm$  0.0125  \\
+  2.308 & 0.284 & 0.490 &  259.4 & -0.2429   $\pm$   0.0733   $\pm$  0.0234  \\
+  2.308 & 0.284 & 0.490 &  302.9 & -0.2047   $\pm$   0.0446   $\pm$  0.0162  \\
+  2.308 & 0.284 & 0.490 &  338.8 & -0.0569   $\pm$   0.0496   $\pm$  0.0178  \\
+ \hline                                                                        
+   2.406 & 0.308 & 1.107&  20.2  &  0.0200   $\pm$   0.0356   $\pm$  0.0178  \\
+   2.406 & 0.308 & 1.107&  57.1  &  0.1588   $\pm$   0.0703   $\pm$  0.0108  \\
+   2.406 & 0.308 & 1.107&  93.1  &  0.0557   $\pm$   0.1459   $\pm$  0.0110  \\
+   2.406 & 0.308 & 1.107&  132.8 & -0.0505   $\pm$   0.4638   $\pm$  0.0177  \\
+   2.406 & 0.308 & 1.107&  177.3 & -0.9949   $\pm$   0.9191   $\pm$  0.0181  \\
+   2.406 & 0.308 & 1.107&  228.2 & -1.6988   $\pm$   2.5306   $\pm$  0.0151  \\
+   2.406 & 0.308 & 1.107&  263.1 &  0.0565   $\pm$   0.1477   $\pm$  0.0171  \\
+   2.406 & 0.308 & 1.107&  305.1 & -0.1556   $\pm$   0.0543   $\pm$  0.0129  \\
+   2.406 & 0.308 & 1.107&  340.1 & -0.0510   $\pm$   0.0430   $\pm$  0.0164  \\
+
  \hline
@@
 \label{app:free-proton-alu}
+\section{Fitting the experimentally measured asymmetries}
 Following the discussion in section \ref{sec:Generalized_EMC}, comparing the 
@@
 \end{figure}
+
+\section{Model-dependent extraction}
+The proton asymmetries have been adjusted using a dispersion calculation 
+including a phenomenological GPD $H$ only. The imaginary part of the amplitude 
+is parameterized as in \cite{GPD_cal_free_p}. The real part of the amplitude is 
+then obtained from the dispersion relation and the D-term as subtraction 
+constant, parameterized as in \cite{GPD_cal_free_p}. The beam spin asymmetries 
+mostly constrain the parameters of the imaginary part, and the unpolarized 
+cross-section mostly constrain the D-term parameters.
+
+\begin{figure}[tpb]
+   \centering
+\includegraphics[scale=0.55]{fig_updated/From_FX_Check_Fit_6GeV_asym.png}
+\caption{The free proton beam-spin asymmetries at $\phi = 90^{circ}$ as a 
+function of $-t$ in different ($x_B, Q^2$) bins as measured at CLAS-E1DVCS 
+experiment. The solid red lines are the model calculations based on the 
+kinematics of each bin. The blue points stand for the interpolated free proton 
+asymmetries at the kinematics of our incoherent and coherent DVCS channels.}
+\label{fig:free-proton-alu}
+\end{figure}

### 2016-08-24 analysis-note-v2/Appendix.tex
update the free proton interpolation chapter in the appendix.

@@
 \end{figure}
+
+\section{Summary}
+In this analysis we use the interpolated values from fitting the experimentally 
+measured free proton asymmetries to construct the beam-spin asymmetry ratios.  
+The differences between the beam-spin asymmetry ratios calculated using the 
+fitting the free proton asymmetries and the model-dependent interpolated values 
+were added as a systematic errors on the constructed beam-spin asymmetry 
+ratios. Table \ref{table:ALU_ratios_} presents the coherent and the incoherent 
+$A_{LU}$ ratios extracted using both methods and the associated systematic 
+uncertainties.
+
+\small
+\begin{landscape}
+\begin{table}[!h]
+   \begin{center}
+      \begin{tabular}{||l|l|l|l|l|l|l||}
+         \hline
+ ($Q^{2}$, $x_{B}$, $-t$) & EG6 $A_{LU}$ $\pm$ stat. &  Exp. fit $\pm$ stat. & Exp. $A_{LU}$ ratio   &  Model extr. & Model $A_{LU}$ ratio &  Diff. (Exp - Model)    \\
+  \hline
+(1.395, 0.166, 0.407) &  0.136 $\pm$ 0.027   &    0.174 $\pm$ 0.030   & 0.781213 $\pm$ 0.171565   &  0.2050 &  0.6634 &  0.1178 \\
+(1.886, 0.233, 0.499) &  0.156 $\pm$ 0.033   &    0.217 $\pm$ 0.046   & 0.71823  $\pm$ 0.171458   &  0.2244 &  0.6951 &  0.0231 \\ 
+(2.338, 0.290, 0.521) &  0.154 $\pm$ 0.038   &    0.220 $\pm$ 0.056   & 0.702512 $\pm$ 0.195657   &  0.2177 &  0.7110 &  0.0084 \\
+(3.098, 0.379, 0.650) &  0.122 $\pm$ 0.042   &    0.184 $\pm$ 0.061   & 0.665608 $\pm$ 0.254408   &  0.2017 &  0.6088 &  0.0568 \\
+  \hline \hline  \hline                                                                                        
+(1.425, 0.162, 0.397) &  0.118 $\pm$ 0.026   &    0.172 $\pm$ 0.029   & 0.687175 $\pm$ 0.164567   &  0.1885 &  0.6302 &  0.0569 \\
+(1.922, 0.227, 0.418) &  0.178 $\pm$ 0.029   &    0.222 $\pm$ 0.045   & 0.805541 $\pm$ 0.157091   &  0.2135 &  0.8379 &  0.0323 \\
+(2.354, 0.287, 0.492) &  0.151 $\pm$ 0.036   &    0.230 $\pm$ 0.057   & 0.657427 $\pm$ 0.179755   &  0.2170 &  0.6972 &  0.0397 \\
+(2.987, 0.390, 0.714) &  0.132 $\pm$ 0.050   &    0.163 $\pm$ 0.057   & 0.808622 $\pm$ 0.342802   &  0.2103 &  0.6281 &  0.1805 \\
+  \hline  \hline  \hline                                                                                       
+(1.823, 0.213, 0.145) &  0.146 $\pm$ 0.027   &    0.238 $\pm$ 0.070   & 0.61362  $\pm$ 0.147379   &  0.2438 &  0.6013 &  0.0123 \\
+(2.127, 0.255, 0.282) &  0.150 $\pm$ 0.031   &    0.280 $\pm$ 0.061   & 0.536143 $\pm$ 0.125386   &  0.2410 &  0.6248 &  0.0886 \\
+(2.308, 0.284, 0.490) &  0.163 $\pm$ 0.039   &    0.229 $\pm$ 0.056   & 0.711628 $\pm$ 0.192687   &  0.2195 &  0.7425 &  0.0308 \\
+(2.406, 0.308, 1.107) &  0.115 $\pm$ 0.054   &    0.080 $\pm$ 0.029   & 1.42796  $\pm$ 0.72146    &  0.1235 &  0.9311 &  0.4968 \\
+  \hline  \hline  \hline                                                                                         
+(1.143, 0.132, 0.096) &  0.332 $\pm$ 0.051   &    0.162 $\pm$ 0.039   & 2.04913  $\pm$ 0.405462   &  0.2447 &  1.3596 &  0.6895 \\
+(1.423, 0.170, 0.099) &  0.353 $\pm$ 0.051   &    0.186 $\pm$ 0.057   & 1.89763  $\pm$ 0.404796   &  0.2518 &  1.4050 &  0.4926 \\
+(1.902, 0.224, 0.107) &  0.258 $\pm$ 0.050   &    0.189 $\pm$ 0.094   & 1.36191  $\pm$ 0.431827   &  0.2359 &  1.0941 &  0.2678 \\
+    \hline \hline  \hline                                                                                      
+(1.164, 0.132, 0.095) &  0.373 $\pm$ 0.073   &    0.160 $\pm$ 0.038   & 2.33093  $\pm$ 0.535511   &  0.2234 &  1.6696 &  0.6613 \\
+(1.439, 0.170, 0.099) &  0.267 $\pm$ 0.086   &    0.186 $\pm$ 0.057   & 1.43489  $\pm$ 0.515672   &  0.2432 &  1.0978 &  0.3370 \\
+(1.844, 0.225, 0.107) &  0.362 $\pm$ 0.092   &    0.188 $\pm$ 0.095   & 1.92214  $\pm$ 0.689863   &  0.2515 &  1.4421 &  0.4800 \\
+     \hline  \hline  \hline                                                                                    
+(1.493, 0.177, 0.1)   &  0.326 $\pm$ 0.030   &    0.189 $\pm$ 0.061   & 1.721    $\pm$ 0.322757   &  0.2453 &  1.3289 &  0.3921 \\                                                                 
+ \hline
+ \end{tabular}
+ \caption{$A_{LU}$ ratios. The first three blocks stand for the incoherent bins 
+ in $Q^{2}$, $x_{B}$, and $-t$, respectively. The last three blocks are for the 
+ coherent bins in $Q^{2}$, $x_{B}$, and $-t$, respectively. The first column 
+ contains the mean value of the kinematical variables for each bin. The second 
+ column contains EG6 measured $A_{LU}$ with the statistical error bars. The 
+ third column ("Exp. fit $\pm$ stat.") contains the interpolated free proton 
+ $A_{LU}$ at EG6 kinematical values from fitting the free proton beam-spin 
+ asymmetries. The forth column ("Exp. $A_{LU}$ ratio") stands for the 
+ calculated $A_{LU}$ ratios using EG6 asymmetries and the fitted free proton 
+ asymmetries. The fifth column ("Model extr.") stands for the model-depended 
+ extracted free proton asymmetries. The sixth column ("Model $A_{LU}$ ratio") 
+ presents the calculated $A_{LU}$ ratios using EG6 asymmetries and the 
+ model-dependent extracted free proton asymmetries. The last column ("Diff.  
+ (Exp - Model)") shows the difference between the two calculated $A_{LU}$ 
+ ratios for each bin.}
+ \label{table:ALU_ratios_}
+ \end{center}
+\end{table}
+\end{landscape}

### 2016-08-25 analysis-note-v2/Appendix.tex
fix a reference in figure G.1
fixed the reference in Appendix G and clean more the text

@@
 \label{app:free-proton-alu}
-\section{Fitting the experimentally measured asymmetries}
+\section{Fitting the experimentally measured asymmetries} \label{fit_int} 
 Following the discussion in section \ref{sec:Generalized_EMC}, comparing the 
@@
 reveal new information about the nuclear medium modifications. To construct 
-such ration, the published free proton asymmetries \cite{FX_BSA} have been used 
+such ratio, the published free proton asymmetries \cite{FX_BSA} have been used 
 in this analysis, see figure \ref{fig:free-proton-alu}. The measured free 
-proton $A_{LU}$ at $\phi = 90^{\circ}$ were fitted as a function of $-t$ in the 
-different bins in $x_B$ and $Q^2$. Then, the parameters of the fits were 
+proton $A_{LU}$ at $\phi = 90^{\circ}$ were fitted as a function of $-t$ for 
+the different bins in $x_B$ and $Q^2$. Then, the parameters of the fits were 
 parametrized as a function of $x_B$ assuming that the dependence on $Q^2$ is 
@@
 asymmetries were calculated at the same incoherent and coherent measured 
-kinematics. The statistical errors on the calculated asymmetries were 
+kinematical values. The statistical errors on the calculated asymmetries were 
 calculated using the error bars on the fitted parameters $t_{min}$, $p_0$, and 
@@
 $x_B$.}
-\label{fig:free-proton-alu}
+\label{fig:fitted-points-xB}
 \end{figure}
 
-\section{Model-dependent extraction}
+\section{Model-dependent extraction} \label{model_int}
 The proton asymmetries have been adjusted using a dispersion calculation 
@@
 mostly constrain the parameters of the imaginary part, and the unpolarized 
-cross-section mostly constrain the D-term parameters.
+cross-section mostly constrain the D-term parameters. Figure 
+\ref{fig:FXfree-proton-alu} presents the published free proton asymmetries with 
+the model calculations, in solid red lines, and the interpolated free proton 
+asymmetries at our incoherent and coherent measured kinematical values.
 
@@
 asymmetries at the kinematics of our incoherent and coherent DVCS channels.}
-\label{fig:free-proton-alu}
+\label{fig:FXfree-proton-alu}
 \end{figure}
@@
 In this analysis we use the interpolated values from fitting the experimentally 
-measured free proton asymmetries to construct the beam-spin asymmetry ratios.  
-The differences between the beam-spin asymmetry ratios calculated using the 
-fitting the free proton asymmetries and the model-dependent interpolated values 
-were added as a systematic errors on the constructed beam-spin asymmetry 
-ratios. Table \ref{table:ALU_ratios_} presents the coherent and the incoherent 
-$A_{LU}$ ratios extracted using both methods and the associated systematic 
-uncertainties.
+measured free proton asymmetries to construct the beam-spin asymmetry ratios, 
+presnted in section \ref{fit_int}.  The differences between the beam-spin 
+asymmetry ratios calculated using the free proton asymmetries fits, section 
+\ref{fit_int}, and the model-dependent interpolated values, section 
+\ref{model_int}, were added as a systematic errors on the constructed beam-spin 
+asymmetry ratios.  Table \ref{table:ALU_ratios_} presents the coherent and the 
+incoherent $A_{LU}$ ratios extracted using both methods and the associated 
+systematic uncertainties.
 

### 2016-08-26 analysis-note-v2/Appendix.tex
update the fits for the free proton asymmetries and update all the ALU ratio plots

--- 2016-08-24 analysis-note-v2/Appendix.tex
@@
 reveal new information about the nuclear medium modifications. To construct 
-such ration, the published free proton asymmetries \cite{FX_BSA} have been used 
+such ratio, the published free proton asymmetries \cite{FX_BSA} have been used 
 in this analysis, see figure \ref{fig:free-proton-alu}. The measured free 
-proton $A_{LU}$ at $\phi = 90^{\circ}$ were fitted as a function of $-t$ in the 
-different bins in $x_B$ and $Q^2$. Then, the parameters of the fits were 
+proton $A_{LU}$ at $\phi = 90^{\circ}$ were fitted as a function of $-t$ for 
+the different bins in $x_B$ and $Q^2$. Then, the parameters of the fits were 
 parametrized as a function of $x_B$ assuming that the dependence on $Q^2$ is 
 negligible, figure \ref{fig:free-proton-alu}. Finally, the free proton 
-asymmetries were calculated at the same incoherent and coherent measured 
-kinematics. The statistical errors on the calculated asymmetries were 
-calculated using the error bars on the fitted parameters $t_{min}$, $p_0$, and 
-$p_1$.\\
+asymmetries were calculated at the same measured incoherent and coherent
+kinematic values.  The statistical errors on the calculated asymmetries were 
+calculated using the error bars on the fitted parameters $a_{i}$s.\\
 
@@
 \caption{Black circles are the free proton beam-spin asymmetries at $\phi = 90 
-^{circ}$ as a function of $-t$ in different ($x_B, Q^2$) bins as measured at 
-CLAS-E1DVCS experiment. The solid red curves are fits to the free proton 
-asymmetries in the form $p_{0}*(t-t_{min})*e^{p_{1}*\sqrt{t}}$. The dashed 
-curves are calculations using the fitted $t_{min}$, $p_0$, and $p_1$ parameters 
-as a function of $x_B$ as shown in figure \ref{fig:fitted-points-xB}. Blue 
-points are the interpolated points corresponding for the incoherent points 
-presented in this analysis. Red points are extrapolated free proton points at 
-the coherent kinematical values.}
+   ^{\circ}$ as a function of $-t$ in different ($x_B, Q^2$) bins as measured 
+   at CLAS-E1DVCS experiment. The solid red curves are fits to the free proton 
+   asymmetries in the form $a_{0}*(\sqrt{t}-a_{1})*e^{a_{2}*\sqrt{t} - a_{3}}$.  
+   The dashed curves are calculations using the fitted $a_{i}$'s parameters as 
+a function of $x_B$ as shown in figure \ref{fig:fitted-points-xB}. Blue points 
+are the interpolated points corresponding for the incoherent points presented 
+in this analysis. The red points stand for the extrapolated free proton 
+asymmetries at the measured coherent kinematics.}
 \label{fig:free-proton-alu}
@@
 \begin{figure}[tpb]
-   \centering
-\includegraphics[scale=0.37]{fig_updated/tmin-xB-fit.png}\\
-\includegraphics[scale=0.37]{fig_updated/p0-xB-fit.png}\\
-\includegraphics[scale=0.37]{fig_updated/p1-xB-fit.png}
-\caption{The fitted $t_{min}$, $p_0$, and $p_1$ parameters as a function of 
+\includegraphics[scale=0.37]{fig_updated/test_a0.pdf}
+\includegraphics[scale=0.37]{fig_updated/test_a1.pdf}
+\includegraphics[scale=0.37]{fig_updated/test_a2.pdf}
+\hspace{1.7cm}
+\includegraphics[scale=0.37]{fig_updated/test_a3.pdf}
+\caption{The fitted $a_0$, $a_1$, $a_2$, and $a_3$ parameters as a function of 
 $x_B$.}
-\label{fig:free-proton-alu}
+\label{fig:fitted-points-xB}
 \end{figure}
 
-\section{Model-dependent extraction}
+\section{Model-dependent extraction} \label{model_int}
 The proton asymmetries have been adjusted using a dispersion calculation 
@@
 mostly constrain the parameters of the imaginary part, and the unpolarized 
-cross-section mostly constrain the D-term parameters.
+cross-section mostly constrain the D-term parameters. Figure 
+\ref{fig:FXfree-proton-alu} presents the published free proton asymmetries with 
+the model calculations, in solid red lines, and the interpolated free proton 
+asymmetries at our measured coherent and incoherent kinematic values.
 
@@
 kinematics of each bin. The blue points stand for the interpolated free proton 
-asymmetries at the kinematics of our incoherent and coherent DVCS channels.}
-\label{fig:free-proton-alu}
+asymmetries at the kinematics of our incoherent DVCS channels.}
+\label{fig:FXfree-proton-alu}
 \end{figure}
+
+\section{Summary}
+In this analysis we use the interpolated values from fitting the experimentally 
+measured free proton asymmetries to construct the beam-spin asymmetry ratios, 
+presnted in section \ref{fit_int}.  The differences between the beam-spin 
+asymmetry ratios calculated using the free proton asymmetries fits, section 
+\ref{fit_int}, and the model-dependent interpolated values, section 
+\ref{model_int}, were added as a systematic errors on the constructed beam-spin 
+asymmetry ratios.  Table \ref{table:ALU_ratios_} presents the coherent and the 
+incoherent $A_{LU}$ ratios extracted using both methods and the associated 
+systematic uncertainties.
+
+\small
+\begin{landscape}
+\begin{table}[!h]
+   \begin{center}
+      \begin{tabular}{||l|l|l|l|l|l|l||}
+         \hline
+ ($Q^{2}$, $x_{B}$, $-t$) & EG6 $A_{LU}$ $\pm$ stat. &  Exp. fit $\pm$ stat. & Exp. $A_{LU}$ ratio   &  Model extr. & Model $A_{LU}$ ratio &  Diff. (Exp - Model)    \\
+  \hline
+(1.395, 0.166, 0.407) &  0.136 $\pm$ 0.027   &    0.1691 $\pm$ 0.0592   &  0.8042 $\pm$ 0.3248  &  0.2050 &  0.6634 &  0.1408 \\
+(1.886, 0.233, 0.499) &  0.156 $\pm$ 0.033   &    0.2081 $\pm$ 0.0738   &  0.7494 $\pm$ 0.3101  &  0.2244 &  0.6951 &  0.0543 \\ 
+(2.338, 0.290, 0.521) &  0.154 $\pm$ 0.038   &    0.2129 $\pm$ 0.0777   &  0.7268 $\pm$ 0.3206  &  0.2177 &  0.7110 &  0.0158 \\
+(3.098, 0.379, 0.650) &  0.122 $\pm$ 0.042   &    0.1765 $\pm$ 0.0676   &  0.6956 $\pm$ 0.3581  &  0.2017 &  0.6088 &  0.0868 \\
+  \hline \hline  \hline                                                                                                
+(1.425, 0.162, 0.397) &  0.118 $\pm$ 0.026   &    0.1686 $\pm$ 0.0587   &  0.7045 $\pm$ 0.2913  &  0.1885 &  0.6302 &  0.0743 \\
+(1.922, 0.227, 0.418) &  0.178 $\pm$ 0.029   &    0.2122 $\pm$ 0.0740   &  0.8429 $\pm$ 0.3257  &  0.2135 &  0.8379 &  0.005  \\
+(2.354, 0.287, 0.492) &  0.151 $\pm$ 0.036   &    0.2209 $\pm$ 0.0795   &  0.6847 $\pm$ 0.2974  &  0.2170 &  0.6972 &  0.0125 \\
+(2.987, 0.390, 0.714) &  0.132 $\pm$ 0.050   &    0.1562 $\pm$ 0.0615   &  0.8457 $\pm$ 0.4661  &  0.2103 &  0.6281 &  0.2176 \\
+  \hline  \hline  \hline                                                                                               
+(1.823, 0.213, 0.145) &  0.146 $\pm$ 0.027   &    0.2304 $\pm$ 0.0677   &  0.6363 $\pm$ 0.2223  &  0.2438 &  0.6013 &  0.035  \\
+(2.127, 0.255, 0.282) &  0.150 $\pm$ 0.031   &    0.2641 $\pm$ 0.0848   &  0.5700 $\pm$ 0.2177  &  0.2410 &  0.6248 &  0.0548 \\
+(2.308, 0.284, 0.490) &  0.163 $\pm$ 0.039   &    0.2200 $\pm$ 0.0791   &  0.7400 $\pm$ 0.3209  &  0.2195 &  0.7425 &  0.0025 \\
+(2.406, 0.308, 1.107) &  0.115 $\pm$ 0.054   &    0.0939 $\pm$ 0.0429   &  1.2240 $\pm$ 0.8030  &  0.1235 &  0.9311 &  0.2929 \\
+  \hline  \hline  \hline                                                                                               
+(1.143, 0.132, 0.096) &  0.332 $\pm$ 0.051   &    0.1821 $\pm$ 0.0528   &  1.8267 $\pm$ 0.6017  &  0.2447 &  1.3596 &  0.4671 \\
+(1.423, 0.170, 0.099) &  0.353 $\pm$ 0.051   &    0.1857 $\pm$ 0.0534   &  1.9044 $\pm$ 0.6146  &  0.2518 &  1.4050 &  0.4994 \\
+(1.902, 0.224, 0.107) &  0.258 $\pm$ 0.050   &    0.1835 $\pm$ 0.0524   &  1.4063 $\pm$ 0.4863  &  0.2359 &  1.0941 &  0.3122 \\
+    \hline \hline  \hline                                                                                              
+(1.164, 0.132, 0.095) &  0.373 $\pm$ 0.073   &    0.1819 $\pm$ 0.0529   &  2.0503 $\pm$ 0.7190  &  0.2234 &  1.6696 &  0.3807 \\
+(1.439, 0.170, 0.099) &  0.267 $\pm$ 0.086   &    0.1859 $\pm$ 0.0535   &  1.4361 $\pm$ 0.6231  &  0.2432 &  1.0978 &  0.3383 \\
+(1.844, 0.225, 0.107) &  0.362 $\pm$ 0.092   &    0.1830 $\pm$ 0.0522   &  1.9812 $\pm$ 0.7571  &  0.2515 &  1.4421 &  0.5391 \\
+     \hline  \hline  \hline                                                                                            
+(1.493, 0.177, 0.1)   &  0.326 $\pm$ 0.030   &    0.1863 $\pm$ 0.0535   &  1.7498 $\pm$ 0.5292  &  0.2453 &  1.3289 &  0.4209 \\
+
+ \hline
+ \end{tabular}
+ \caption{$A_{LU}$ ratios. The first three blocks stand for the incoherent bins 
+ in $Q^{2}$, $x_{B}$, and $-t$, respectively. The last three blocks are for the 
+ coherent bins in $Q^{2}$, $x_{B}$, and $-t$, respectively. The first column 
+ contains the mean value of the kinematical variables for each bin. The second 
+ column contains EG6 measured $A_{LU}$ with the statistical error bars. The 
+ third column ("Exp. fit $\pm$ stat.") contains the interpolated free proton 
+ $A_{LU}$ at EG6 kinematical values from fitting the free proton beam-spin 
+ asymmetries. The forth column ("Exp. $A_{LU}$ ratio") stands for the 
+ calculated $A_{LU}$ ratios using EG6 asymmetries and the fitted free proton 
+ asymmetries. The fifth column ("Model extr.") stands for the model-depended 
+ extracted free proton asymmetries. The sixth column ("Model $A_{LU}$ ratio") 
+ presents the calculated $A_{LU}$ ratios using EG6 asymmetries and the 
+ model-dependent extracted free proton asymmetries. The last column ("Diff.  
+ (Exp - Model)") shows the difference between the two calculated $A_{LU}$ 
+ ratios for each bin.}
+ \label{table:ALU_ratios_}
+ \end{center}
+\end{table}
+\end{landscape}

### 2016-09-02 eg6-letters/coherent/HeliumCohDVCS.tex
Update letter

--- 2016-08-10 coherent/HeliumCohDVCS.tex
@@
 \begin{figure}[htbp]
-\caption{\label{fig:DVCS} Coherent DVCS}
+\caption{\label{fig:DVCS} Diagram for the coherent DVCS in the plane wave approximation.}
 \includegraphics[width=8.6cm]{DVCS.png}
@@
 
-In order to insure the coherence of the process, we detect all the products
-of the reaction. The electron is detected by the CLAS, using the drift chamber 
-to reconstruct its trajectory and the combination of the Cherenkov counters
-and electromagnetic calorimeter to
-
-we built a small and light 
-radial time projection chamber (RTPC) depicted in figure~\ref{fig:rtpc} to 
-detect the recoiling helium nuclei. this detector is placed directly ouside of 
-our gaseous target filled with 6~atm helium. 
-% to complete
-
-\begin{figure}[htbp]
-\caption{\label{fig:rtpc} RTPC description}
-\includegraphics[width=8cm]{RTPC.png}
-\end{figure}
-
-%\section{DVCS Events Selection}
-
-Detection, PID des particules.
-
-\begin{figure*}[htbp]
+\begin{figure*}[tbp]
 \caption{\label{fig:exclu} Exclusivity cuts}
@@
 \end{figure*}
+
+In order to insure the coherence of the process, we detect all the products
+of the reaction. The electron detected by the CLAS, using the drift chamber 
+to reconstruct its trajectory, while the combination of the Cherenkov counters
+and electromagnetic calorimeter signals insure that it is not mistaken with
+a negative pion. The high energy photon is detected in a PbWO calorimeter 
+placed close to the beam line. Finally, we built a small and light 
+radial time projection chamber (RTPC) to 
+detect the recoiling helium nuclei. The chamber is placed directly ouside of 
+a gaseous target filled with 6~atm helium-4 and is 20 cm long with a 3 cm radial
+drift length.
+
+%\begin{figure}[htbp]
+%\caption{\label{fig:rtpc} RTPC description}
+%\includegraphics[width=8cm]{RTPC.png}
+%\end{figure}
+
+%\section{DVCS Events Selection}
+Explain exclusivity cuts
 
@@
 
-% This is mainly to compare to existing models
-Generalized ratios (figure~\ref{fig:GenR})
-
-\begin{figure}[htbp]
-\caption{\label{fig:GenR} Generalized ratio}
-\includegraphics[width=7.5cm]{coh_emc_Q2.png}
-\includegraphics[width=7.5cm]{coh_emc_t.png}
-\includegraphics[width=7.5cm]{coh_emc_xB.png}
-\end{figure}
-
 \begin{figure}[htbp]

### 2016-09-06 2nd_round_comments/DVCS-CAN-Meeting-Comments.tex
added ALU(90 deg) plots for Q.2.a.ii

@@
     \begin{figure}[tbp]
-       \centering
-    \includegraphics[height=8.6cm]{fig/ALU_coherent_MM2.pdf}
-    \caption{The integrated coherent beam-spin asymmetries as a function of 
-    $\phi$ corresponding to different cuts on $e^{4}He\gamma X$ missing mass 
- squared.}
+    \includegraphics[height=6.0cm]{fig/ALU_coherent_MM2.pdf}
+    \includegraphics[height=6.0cm]{fig/ALU_coherent_MM2_90deg.pdf}
+    \caption{On the left: the integrated coherent beam-spin asymmetries as a 
+    function of $\phi$ corresponding to different cuts on $e^{4}He\gamma X$ 
+ missing mass squared. On the right: $A_{LU}$ at 90$^{\circ}$ from fitting the
+  reconstructed asymmetries as a function of the cut width.}
     \label{fig:exc_coh-alu}
@@
     \begin{figure}[tbp]
-       \centering
-    \includegraphics[height=8.6cm]{fig/ALU_incoherent_MM2.pdf}
-    \caption{The integrated incoherent beam-spin asymmetries as a function of 
-    $\phi$ corresponding to different cuts on $e^{4}He\gamma X$ missing mass 
- squared.}
+    \includegraphics[height=6.0cm]{fig/ALU_incoherent_MM2.pdf}
+    \includegraphics[height=6.0cm]{fig/ALU_incoherent_MM2_90deg.pdf}
+    \caption{On the left: the integrated incoherent beam-spin asymmetries as a 
+    function of $\phi$ corresponding to different cuts on $e^{4}He\gamma X$ 
+ missing mass squared. On the right: $A_{LU}$ at 90$^{\circ}$ from fitting the 
+ reconstructed asymmetries as a function of the cut width.}
     \label{fig:exc_incoh-alu}

### 2016-09-06 eg6-letters/coherent/HeliumCohDVCS.tex
added ALU(90 deg) plots for Q.2.a.ii

@@
 \begin{abstract}
-We report the first exclusive measurement of deeply virtual Compton scatterring 
+We report the first exclusive measurement of deeply virtual Compton scattering 
 (DVCS) off a nuclei with the CLAS detector at the Jefferson laboratory. The 

### 2016-09-06 2nd_round_comments/DVCS-CAN-Meeting-Comments.tex
update the answers and minor text cleanings in the note

@@
    \textcolor{blue}{The reconstructed incoherent asymmetries are presented in 
-      figure \ref{fig:BSA_incoherent_epMM} with the associated exlcusive 
-      distributions in figure \ref{fig:epMM2_incoh_exc_cuts}. The different 
-   tail cuts show no major effects on the reconstructed ALU.}
+   figure \ref{fig:BSA_incoherent_epMM} with the associated exclusive 
+distributions in figure \ref{fig:epMM2_incoh_exc_cuts}. We conclude that the 
+different tail cuts show no major effects on the reconstructed $A_{LU}$.}
 
@@
 committee recommends though to be cautious about the statements on the 
-asymmetry ratios in the future publication.
+asymmetry ratios in the future publication.\\
+  \textcolor{blue}{We changed the procedures completely, see Appendix G in the 
+  latest version of the analysis note. We performed fittings for the published 
+  free proton asymmetries. Then we used those fits to extrapolate the free 
+  proton asymmetries at our measured kinematics}.\\
   \begin{figure}[tbp]
@@
 
-Figs 1-4 of \url{https://clasweb.jlab.org/rungroups/lowq/wiki/images/a/a3/Final_1st_round_comments.pdf} 
-Tighter $edist$ cut [-2,+3 mm].
-Otherwise, even if you do not show it in the CAN, mention in one line that a 
-specific study was done.
+Figs 1-4 of 
+\url{https://clasweb.jlab.org/rungroups/lowq/wiki/images/a/a3/Final_1st_round_comments.pdf} 
+Tighter $edist$ cut [-2,+3 mm]. Otherwise, even if you do not show it in the 
+CAN, mention in one line that a specific study was done.\\
+\textcolor{blue}{The analysis note has been updated with all the required 
+plots. See Q.7 for the new updates in the note.}\\
+
 \item Miscellaneous:
@@
        and \ref{fig:incoh_binning} for the coherent and the incoherent DVCS 
-       channels. Even though the 2D was a good a pproximation, a 4D subtraction 
-    is applied on the final results.} 
+    channels. Even though the 2D was a good approximation, a 4D subtraction is 
+ applied on the final results.}
+
  \begin{figure}[tbp]
@@
 \item Your Eq.(4) of "answer" is probably wrong. For our own understanding, 
-   look into this argument again.
+   look into this argument again. \\
+   \textcolor{blue}{Sorry there was a missig sign. This is the correct 
+      dependence.
+      \begin{equation}
+       \frac{\partial MM^2_{e\gamma X}}{\partial E_{\gamma}}
+                     = -2*(E_{\gamma^{*}} + M_{target} - E_{\gamma})
+                      \label{eq:egamma}
+                      \end{equation}
+        }
 
@@
 \item Please keep a record of the changes in the CAN, as we will probably not 
-re-read the whole text.
+   re-read the whole text.\\
+\textcolor{blue}{\begin{enumerate}
+      \item Added the run conditions section 1.2.4.
+      \item Updated figure 2.2.
+      \item Update section 2.1.3 Track reconstruction.
+      \item Update section 2.2.1.1
+      \item Added section 2.2.1.3 Checking the initial good track requirements.
+      \item Cleaning section 2.2.2 with adding a summary for the drift paths 
+         and the drift speed calibrations, section 2.2.2.3
+      \item Cleaning section 2.2.3 Gain calibration with adding more demanded 
+         plots.
+      \item Added section 2.4 RTPC efficiency.
+      \item Cleaned section 3.2.5 with adding the required plots.
+      \item Added the demanded plots in section 4.1.2 and cleaning the writing.
+      \item Added a new section 4.1.3 regarding checking the selected coherent 
+         DVCS events.
+      \item Edited the plots in figure 4.15 with the -tmin lines.
+      \item Cleaning section 4.5 after changing to perform 4D background 
+         subtraction with a summery about other background sources and a new 
+         section for the accidental contaminations.
+      \item Updated section 4.7 Systematic uncertainties with all suggested 
+         studies.
+      \item Updated section 5.1 with the new fitting procedures for the 
+         coherent channel.
+      \item Updated all the figure in chapter 5 with the new results and the 
+         suggested modifications.
+      \item Added Appendix F with $A_{LU}$ tables.
+      \item Added Appendix G for the free proton asymmetry interpolations.
+   \end{enumerate} }
 
 \item Request to see the very first draft of the publication.
+    \textcolor{blue}{Will be provided}.
 

### 2016-09-07 eg6-letters/coherent/HeliumCohDVCS.tex
Update letter

--- 2016-09-02 eg6-letters/coherent/HeliumCohDVCS.tex
@@
 observed beam spin asymmetries are significantly larger than for proton, 
-confirming expectations from plane wave impulse approximation. We present an 
-extraction of the unique generalized parton distribution (GPD) of the spin-0 
-helium in a completely model independent way. This result demonstrate the 
-strength of the method and opens a new unique access into nuclei 3D structure 
-in term of quarks and gluons.
+confirming expectations from calculations using the plane wave impulse 
+approximation. We present an 
+extraction of the single generalized parton distribution (GPD) of the spin-0 
+helium-4 nuclei in a completely model independent way. This result demonstrate the 
+strength of the method and opens a new and unique access into the partonic structure 
+of nuclei.
 \end{abstract}
@@
 
-The generalized parton distribution (GPD) framework developped in the past two decades
-(Need a bunch of refs)~\cite{}
+The generalized parton distribution (GPD) framework developped in the past 
+two decades~\cite{}
 offers a unique access into hadron 3D structure through deeply virtual Compton
-scattering (DVCS), depicted in figure~\ref{fig:DVCS} and other exclusive processes. Many measurements on the proton
-at several energies have now be reported and have demonstrated the solidity of the
-method~\cite{}. %To enhance a little -> CFF
+scattering (DVCS), depicted in figure~\ref{fig:DVCS}, and other exclusive 
+processes. Many measurements on the proton
+at several energies have now be reported~\cite{} and phenomenological work
+have demonstrated the solidity of the method to extract the tomography of the
+nucleon from these data~\cite{}.
 
-Insert FIGURE DVCS nuclei
-%\label{fig:DVCS}
 \begin{figure}[htbp]
@@
 today a topic of active research~\cite{},
-questionning our understanding of nuclei and their structure beyond protons
-and neutrons~\cite{}. As studies based on inclusive measurements of the
-effect seem to be too limited to tackle the question definitively, we can now
-apply the GPD framework to study the nuclei in three dimensions and observe
-the EMC effect in an unprecedented way.
-%Elaborate on non nucleonic degrees of freedom and other interests of He DVCS
+questionning the basics of our understanding of nuclei and their 
+structure~\cite{}. Studies based on inclusive measurements of the
+effect provide a very detailed description~\cite{} but 
+are still unable to tackle the question definitively. Therefore,
+using the GPD framework and exclusive channels to study the nuclei in three 
+dimensions will give completely new information that will affect our understanding
+of the EMC effect in an unprecedented way~\cite{}. 
+%In particular, the GPDs 
+%allow to isolate the components of the nuclei which are not nucleonic~\cite{}.
 
-The measurement of DVCS on helium 4 is in this regard the perfect experiment for
+The measurement of DVCS on helium-4 is in this regard the perfect experiment for
 several reasons. First, Helium 4 is of spin-0, such that a single GPD ($H$) is
@@
 completely model independant extraction of the CFF from data that is impossible for 
-protons and neutrons which need 4 GPDs, leading to complex underconstrained 
-problems~\cite{}. Second, helium 4, while a small nuclei, is dense and experience 
+protons and neutrons which have 4 GPDs~\cite{}. Second, 
+helium 4 is dense and experience 
 already a significant EMC effect, while being simple enough that its nuclear
-structure is very well known~\cite{} (Low energy struct, FF,...). Third, being 
-light enough helium 4 can exit
-a light target and be experimentally measured, insuring the exclusivity of the 
-measurement. This point is especially important as we are probing with a 
+structure is well known~\cite{}. Third, being 
+light enough helium-4 can exit
+a light target and be experimentally measured in a coherent DVCS process, 
+insuring the exclusivity of the 
+measurement. This point is especially important because we are probing with a 
 multi-GeV interaction a nuclei bound by only a few MeV, this leads in the 
@@
 The HERMES collaboration has measured nuclear DVCS~\cite{} without the 
-possibility of separating the coherent and incoherent channels leading
+detection of the recoils separating the coherent and incoherent channels 
+based on the measurement of the transfered 4-momentum $t$, leading
 to controversy in the interpretation of their results~\cite{}. We report
-here our measurement of coherent DVCS off helium-4 at the Jefferson labortory
+here our exclusive measurement of coherent DVCS off helium-4 at the Jefferson labortory
 (JLab), while our results for the incoherent channel will be presented in
-another paper~\cite{}. This experimental facility delivers a nearly 100\% duty factor, 6~GeV 
-electron linear accelerator into three experimental halls. Our experiment
-ran for 3 months in 2009 using the CEBAF Large Acceptance Spectrometer (CLAS).
-This detector is covering about 2$\pi$ and is composed of drift chambers, Cherenkov counters, scintillator 
-counters and an electro-magnetic calorimeter. It allows to detect accurately
-electrons and provides a trigger for the experiment. It is complemented for DVCS experiments with
-an inner calorimeter to detect the photons emitted at low angle and a solenoid
-to keep the Moller electrons produced along the beam line to get into our detectors.
+another paper. JLab delivers a nearly 100\% duty factor, 6~GeV linearly 
+polarized electrons into three experimental halls. Our experiment ran for 3 
+months in 2009 using the CEBAF Large Acceptance Spectrometer (CLAS) in 
+Hall-B. This detector is large acceptance covering nearly 2$\pi$ and is 
+composed of drift chambers, Cherenkov counters, scintillator counters and 
+an electro-magnetic calorimeter. It allows to detect accurately electrons 
+which provide the trigger for the experiment. It is complemented for DVCS 
+experiments with an inner electro-magnetic calorimeter made of PbWO crystals 
+to detect the photons emitted at low angle and with a solenoid to keep the 
+Moller electrons produced along the beam line to get into our detectors.
 
@@
 
-In order to insure the coherence of the process, we detect all the products
-of the reaction. The electron detected by the CLAS, using the drift chamber 
-to reconstruct its trajectory, while the combination of the Cherenkov counters
-and electromagnetic calorimeter signals insure that it is not mistaken with
-a negative pion. The high energy photon is detected in a PbWO calorimeter 
-placed close to the beam line. Finally, we built a small and light 
-radial time projection chamber (RTPC) to 
-detect the recoiling helium nuclei. The chamber is placed directly ouside of 
-a gaseous target filled with 6~atm helium-4 and is 20 cm long with a 3 cm radial
-drift length.
+In order to insure the coherence of the process, we also detect the recoiling 
+helium-4 nuclei. We built a small and light radial time projection chamber 
+(RTPC) to detect recoiling helium nuclei down to energies of few MeVs. The 
+chamber, shown in figure~\ref{fig:rtpc}, is surrounding the gaseous target 
+filled with 6~atm helium-4 and is 20 cm long with a 3 cm radial drift 
+length. The detector was specifically calibrated for helium-4 nuclei using 
+elastic scattering produced with a 1.2~GeV electron beam.
 
-%\begin{figure}[htbp]
-%\caption{\label{fig:rtpc} RTPC description}
-%\includegraphics[width=8cm]{RTPC.png}
-%\end{figure}
+\begin{figure}[htbp]
+\caption{\label{fig:rtpc} RTPC description}
+\includegraphics[width=8cm]{RTPC.png}
+\end{figure}
 

### 2016-09-07 analysis-note-v2/data_analysis.tex

@@
 \ref{fig:comp_He} show the comparison between data and simulation in terms of 
-theta, $phi$ and momentum of the $^{4}$He DVCS nuclei, that will presented in 
-details in the following chapter. The other particles, ($e^{-}$, $p$, 
+$\theta$, $\phi$ and momentum of the $^{4}$He DVCS nuclei, that will presented 
+in details in the following chapter. The other particles, ($e^{-}$, $p$, 
 $\gamma$), are fed to GSIM through the previously mentioned 

### 2016-09-07 analysis-note-v2/analysis-2.tex
added the contamination plots instead of the pi0 production yield plots, section 4.5.2 figure 4.19

--- 2016-08-23 analysis-note-v2/analysis-2.tex
@@
 
-\begin{figure}[tp]
+Figure \ref{fig:cont_yield} presents the measured coherent and incoherent 
+$\pi^{0}$ contmaination with respect to the measured DVCS events. On both 
+channels, the contamination increases strongly with -$t$, with a mean of 2$\%$ 
+(6$\%$) for the coherent (incoherent) channel. \\
+
+\begin{figure}[tpb]
 \centering
@@
 \label{fig:incoh_acceptance _ratios}
+\end{figure}
+
+\begin{figure}[tpb]
+\includegraphics[scale=0.4]{fig_updated/T_ratio_pi0_dvcs_Coh_t.pdf}
+\includegraphics[scale=0.4]{fig_updated/T_ratio_pi0_dvcs_InCoh_t.pdf}
+\caption{The experimental coherent (left) and incoherent (right) $\pi^{0}$ 
+contamination with respect to the experimental DVCS events as a function of the 
+transfered momentum squared -$t$. The data is integrated over the kinematical 
+variables $Q^2$, $x_B$, and $\phi$.  }
+\label{fig:cont_yield}
 \end{figure}

### 2016-09-08 analysis-note-v2/RTPC.tex
update the answers and minor text cleanings in the note
Clean up of the note RTPC chapter

@@
 ~~~~At 6 GeV incident electron beam energy, the recoil $^{4}He$ nuclei from the coherent DVCS channel, have an average momentum around 200 MeV/c.
-CLAS cannot detect such low energy particles, for exemple protons are detected with a threshold of about 250 MeV/c, which will be even worse for helium.
+CLAS cannot detect such low energy particles, for exemple protons are detected with a threshold of about 250 MeV/c, which will be even higher for helium.
 In order to detect such low-energy recoils a Radial TPC (RTPC), similar to the one used during the BoNuS run \cite{BONUS}, was added to CLAS.
@@
 information in time bins, in which the charge is measured in 
-Analog-to-Digital-Converter (ADC) units, while the time is recorded in 
-Time-to-Digital-Converter (TDC) units, in which each TDC is equal to 114 ns.  
-This measurement indicating the time taken by the electrons to drift from the 
+Analog-to-Digital-Converter (ADC) units, while the 114 ns width of the time bins 
+will be refered as Time-to-Digital-Converter (TDC) units.  
+From this measurement, we deduce the time taken by the electrons to drift from the 
 ionization point to the readout board.
@@
 Also, the gains of the readout pads are required to calculate $\frac{dE}{dx}$ 
-from the recorded ADCs. The drift paths and the gain calibration of the RTPC 
+from the recorded ADCs. The determination of the drift paths and the gain 
+calibration of the RTPC 
 require well identified events, so we decided to use elastic scattering 
-($e^{4}He \rightarrow e^{4}He$). We had specific calibration runs with 1-pass 
-beam energies of 1.024 and 1.269 GeV in order to enhance the cross section of 
-the elastic process at large angles, which is highly suppressed at higher beam 
-energy.\\
+($e^{4}He \rightarrow e^{4}He$). However, the cross section of 
+the elastic process at detectable angles is highly suppressed at higher beam 
+energy, so we had specific calibration runs with 1-pass 
+beam energies of 1.024 and 1.269 GeV. \\
 
@@
 $^4He$ can be calculated from the electron measured in CLAS and then simulated 
-in GEANT4. The output of the simulation is then compared with the measured 
-signals to determine the drift paths. \\
+in GEANT4. The output of the simulation gives an expected trajectory that we then
+match to to the measured signals to determine the drift paths. \\
 
 This process is iterative since good tracks need to be identified at the 
-beginning of the process. For this analysis, we started from a MAGBOLTZ 
+beginning of the process and as the calibration improves, more good tracks 
+are identified. For this analysis, we started from a MAGBOLTZ 
 calibration, which was then improved with the method described above with 
-several iterations. In particular, changes in the alignment of the RTPC with 
-respect to the beamline, detailed in CLAS-NOTE~\cite{eg6beamoffset}. In the 
-following subsections, we present here only the selection of the RTPC tracks 
-and elastic events for the last iteration of our calibration process. It is 
-then followed by details on the techniques of calibration.
+several iterations. In particular, it is important that the alignment of the 
+RTPC with respect to the beamline is properly implemented (see details in
+CLAS-NOTE~\cite{eg6beamoffset}). As the process evolved and was improved over 
+time, we present in the following subsections only the method used for the last 
+iteration of our calibration process.
 
@@
 description of the various elements and notations. $sdist$ and $edist$ are 
-defined position as shown in this sketch.} \label{fig:RTPC_track}
+distances between first and last hits and boundaries of the RTPC as shown in 
+this sketch.} \label{fig:RTPC_track}
 \end{figure}
@@
 
-\item We apply a cut on the vertex position in $z$ of the reconstructed tracks 
-   to insure it is in the RTPC volume, i.e. $z$ $\in$ [-80,80] mm, as 
+\item The vertex position in $z$ is in the RTPC volume, i.e. $z$ $\in$ [-80,80] mm, as 
    illustrated in figure \ref{fig:rtpc_zz}.
 
-\item We request a positive radius of curvature ($r_{0}>0$): the $^4He$ is a positively 
+\item The radius of curvature is positive ($r_{0}>0$): the $^4He$ is a positively 
    charged nucleus and the reconstructed track in the RTPC must have positive 
@@
 
-\item We check the quality of the helix fit with a $\chi^{2}$ cut (< 3.5). The 
-   quality of the fit ($\chi^{2}$) is defined as:
-
+\item The helix fit is well reconstructed with a $\chi^{2} < 3.5$. The 
+   quality of the fit ($\chi^{2}$) being defined as:
 \begin{equation}
@@
 $\phi^{helix}_{i}$, $z^{helix}_{i}$) is the point on the helix fit that is 
-closest, in Euclidean (3D) space, to the reconstructed hit $i$. The resolutions 
+closest to the reconstructed hit $i$. The resolutions 
 are defined as ($\sigma_{r}$, $\sigma_{\phi}$, $\sigma_{z}$) = (0.53 mm, 
-2$^{\circ}$, 1.2 mm) based on the size
-of the readout pads were kept identical for all calibration iterations. These 
+2$^{\circ}$, 1.2 mm) based only on the size
+of the readout pads and were kept identical for all calibration iterations. These 
 resolutions were derived by CLAS-BoNus experiment \cite{BONUS}. $N_{pts}$ is 
@@
 
-\item $sdist$ ($\in$ [-2.0,2.0] mm) and $edist$ ($\in$ [-1,5] mm ) cuts: the 
+\item $sdist$ ($\in$ [-2.0,2.0] mm) and $edist$ ($\in$ [-1,5] mm ): these 
    cuts are applied to ensure that a track is on time, i.e. the first 
@@
 
-\subsubsection{Elastic selection}
+\subsubsection{Elastic scattering event selection}
    The elastic process on $^{4}He$ is defined as:
@@
 
- In addition to the previously good-track requirements, in order to select the elastic events we impose further constraints.
+ In addition to the good-track requirements described above, to select elastic events we impose further constraints.
 The co-planarity between the scattered electron and the recoil $^4He$ is ensured using a $\Delta \phi$ (=$\phi_{e}-\phi_{^{4}He}$) cut as shown in Figure \ref{fig:delta_phi_elastic}.
-Like for $\Delta z$, the $\Delta \phi$ 2$\sigma$ cut is dependent on $z$ to account for variations.
+Like for $\Delta z$, the $\Delta \phi$ 2$\sigma$ cut is dependent on $z$ to account for systematic variations.
 Our final parametrizations can be found in Appendix \ref{app:RTPC_appendix} as well.\\
@@
 agreement between the helium-4 real mass and the mean value of the identified 
-elastic events. The difference in width is related to the different resolutions 
-of the corresponding CLAS sectors. The reaction products are emitted back to 
-back resulting in only small regions of overlapping acceptances between the 
-RTPC and CLAS enhancing this effect. The reason for this is that local 
-variations of the resolution can be much more important than ones averaged over 
-the full detector.
-\\
+elastic events. The difference in width is related to differences in 
+resolution in CLAS.
+The large effect is due to the reaction products being emitted back to 
+back resulting in a small overall acceptance for the process. This result is
+therefore very sensitive to the local 
+variations of the resolution, which can be rather important in CLAS.\\
 
@@
 \subsubsection{Checking the initial good track requirements}
-~~~~In this section, we recheck the individual good track requirements 
-presented in section \ref{good_track_req}, where we apply the other good track 
-and elastic requirements and watch the individual variables.
+~~~~In this section, we study some of the good track requirements 
+presented in section \ref{good_track_req}. We apply here all the good track 
+and elastic requirements but the one related to the ploted variable.
 
 Figure \ref{fig:2-z-vertex} presents the z-vertex distributions of the elastic 
-events, where all the good track and elastic requirements were applied. One 
+events. One 
 sees that the initial [-80:80] mm cuts on the helium z-vertex appear to be 
@@
 for the identified elastic tracks in the RTPC. One sees that applying the other 
-good track and elastic conditions will eliminate all the negative tracks and 
+good track and elastic conditions eliminate all the negative tracks as well as
 the tracks with $r_{0}$ less than 30 mm.
@@
 The distributions of $sdist$ and $edist$ for the identified elastic $^4$He 
-elastic tracks, figure \ref{fig:2-sdist-edist}, show that most of the tails, 
+elastic tracks, figure \ref{fig:2-sdist-edist}, show that the tails, 
 which are mostly due to electronic noise, are removed. Therefore, making 
-tighter cuts would not cause changes in the calibration as the tracks in the 
+tighter cuts would not cause significant changes in the calibration as the 
 tail regions are cleaned by the other good track and elastic cuts.
@@
 
-\subsection{drift paths and drift speed calibration}
+\subsection{Drift paths and drift speed calibration}
 
@@
 
-\section{RTPC tracking offsets}
-TBC
-
 \section{RTPC efficiency}

### 2016-09-08 analysis-note-v2/Hadron_structure.tex
Cleaned up some of the weird and random line jumps

@@
 \section{DVCS off Helium-4} \label{Nuclear_DVCS}
-~~~~Nuclear targets provide access to the measurement of two DVCS channels: the coherent and the incoherent.
+Nuclear targets provide access to the measurement of two DVCS channels: the coherent and the incoherent.
 In the coherent channel, the target nucleus remains intact and recoils as a whole while emitting a real photon ($eA \rightarrow e' A' \gamma$).
@@
 Figure \ref{fig:nuclear_DVCS} shows the diagrams of the two DVCS channels.
-\\
 \begin{figure}[tbp]
@@
 $M_{N}$ is the mass of the nucleon and $E(E')$ is the energy of the incident 
-(scattered) electron.\\
+(scattered) electron.
 
@@
 $^{16}O$, is simpler to study as only one GPD ($H_{A}(x,\xi,t)$) arises at 
-leading twist to parametrize their partonic structure.\\
+leading twist to parametrize their partonic structure.
 
@@
  separation ($\beta = b - b'$) between the nucleons in a nucleus 
- \cite{EMC_simonetta}.\\
+ \cite{EMC_simonetta}.
 %\begin{eqnarray}
@@
 These aspects make the $^4$He nucleus an ideal target to be considered for the understanding of the nuclear effects at the partonic level.
-\\
 
@@
 \end{itemize}
-~~~~The $^4$He DVCS amplitude can be expressed as \cite{Kir}:
+
+The $^4$He DVCS amplitude can be expressed as \cite{Kir}:
  \begin{equation}
@@
 \end{equation}
- where the first term on the right-hand side stands for the real part of the CFF $\mathcal{H}_{A}$, while the second term for the imaginary part of $\mathcal{H}_{A}$. \\
+ where the first term on the right-hand side stands for the real part of the CFF $\mathcal{H}_{A}$, while the second term for the imaginary part of $\mathcal{H}_{A}$.
 
@@
 Following the $F_{A}(t)$ parametrization by R.
-Frosch and his collaborators \cite{He_4_FF_Frosch} (valid at the small values of $-t$ which are of interest in this work), figure \ref{fig:BH_cross_section_4He} shows the calculated BH as a function of the azimuthal angle between the leptonic and the hadronic planes ($\phi$), using a 6~GeV electron beam on a $^4$He target.\\
+Frosch and his collaborators \cite{He_4_FF_Frosch} (valid at the small values of $-t$ which are of interest in this work), figure \ref{fig:BH_cross_section_4He} shows the calculated BH as a function of the azimuthal angle between the leptonic and the hadronic planes ($\phi$), using a 6~GeV electron beam on a $^4$He target.
 
@@
 The differential cross section can be written like in Appendix \ref{app:Helium_cross_section}, equation \ref{eq:sigdiff}.
-By generalizing the BMK model \cite{Kir}, the nuclear BH, DVCS and interference scattering amplitudes can be decomposed into a finite series of Fourier harmonics as can be found in Appendix \ref{app:Helium_cross_section}, equations \ref{TTBH}, \ref{TTDVCS} and \ref{TTinter}.\\
+By generalizing the BMK model \cite{Kir}, the nuclear BH, DVCS and interference scattering amplitudes can be decomposed into a finite series of Fourier harmonics as can be found in Appendix \ref{app:Helium_cross_section}, equations \ref{TTBH}, \ref{TTDVCS} and \ref{TTinter}.
 
@@
 \subsection{Beam-spin asymmetry}
-~~~~It is convenient to use the beam-spin asymmetry as DVCS observable because most of the experimental normalization and acceptance issues cancel out in an asymmetry ratio.
+It is convenient to use the beam-spin asymmetry as DVCS observable because most of the experimental normalization and acceptance issues cancel out in an asymmetry ratio.
 The beam-spin asymmetry is measured using a polarized lepton beam on an unpolarized target (U).
@@
   \end{equation}
-  where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the DVCS differential cross section for a positive (negative) beam helicity.\\
+  where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the DVCS differential cross section for a positive (negative) beam helicity.
 
@@
 expressions of these coefficients can be found in Appendix 
-\ref{app:Helium_cross_section}.\\
+\ref{app:Helium_cross_section}.
 
 \subsection{Theoretical predictions} \label{Theoretical_hypotheses}
-\paragraph{On-shell calculations}
-~\\
-~\\  
-~~~~The nuclear GPD $H_{A}$ can be described as the sum of the individual nucleons' GPDs.
+
+\paragraph{On-shell calculations} ~
+
+The nuclear GPD $H_{A}$ can be described as the sum of the individual nucleons' GPDs.
 In the model based on the impulse approximation of V.
@@
 \end{equation}
-The t-dependence of the GPD is introduced through Regge ansatz \cite{guidal_2}, with the slope $\alpha'$ equal to 1.105 GeV$^{-2}$ that allows to recover the ordinary form factors of the nucleons.\\
+The t-dependence of the GPD is introduced through Regge ansatz \cite{guidal_2}, with the slope $\alpha'$ equal to 1.105 GeV$^{-2}$ that allows to recover the ordinary form factors of the nucleons.
 
@@
 This model predicts an enhancement of the bound-proton beam-spin asymmetry, which increases with $t$.
-\\
 \begin{figure}[tbp]
@@
 
-\paragraph{Off-shell calculations}
-~\\
-~\\ 
+\paragraph{Off-shell calculations} ~
+
 Another model for nuclear GPDs in the impulse approximation uses the nuclear spectral function. For a spin-zero nucleus, the GPD $H^{A}$ can be written as \cite{EMC_simonetta}:
@@
 The off-forward nucleon GPDs, $H^{N}_{OFF}$ and $E^{N}_{OFF}$, are characterized by the off-shellness which is linked to $P^2$.
-One recovers the free nucleon GPDs by disregarding this off-shellness.\\
+One recovers the free nucleon GPDs by disregarding this off-shellness.
 
@@
 Figure \ref{fig:4HeEMC_RA} shows the EMC ratios measured via DIS on $^4$He compared to theoretical calculations.
-One can see that the latter calculations by S.~Liuti and K.~Taneja describe the EMC effect differently than the first scenario due to the off-shell effects of the nucleons associated in their calculation.\\
+One can see that the latter calculations by S.~Liuti and K.~Taneja describe the EMC effect differently than the first scenario due to the off-shell effects of the nucleons associated in their calculation.
 
@@
 Figure \ref{fig:EMC_Simonetta} shows the predicted EMC effect in $^4$He in terms of $\frac{A^{Incoh}_{LU}}{A^{p}_{LU}}$ as a function of $x_B$.
-The calculated ratio appears to be very sensitive on $t$, which encodes the information on the transverse degrees of freedom of the partons in the nucleon.\\
+The calculated ratio appears to be very sensitive on $t$, which encodes the information on the transverse degrees of freedom of the partons in the nucleon.
 
@@
 \subsection{Nuclear DVCS measurements}
-~~~~~The first nuclear DVCS experiments were carried out by the HERMES 
+The first nuclear DVCS experiments were carried out by the HERMES 
 collaboration \cite{HERMES_BSA}. In these measurements, 
@@
 amplitude of the coherent and the incoherent beam-spin asymmetries integrated 
-over all the data sample for each target type.\\
+over all the data sample for each target type.
 

### 2016-09-08 analysis-note-v2/RTPC.tex
Cleaned up some of the weird and random line jumps

@@
 
-~~~~At 6 GeV incident electron beam energy, the recoil $^{4}He$ nuclei from the coherent DVCS channel, have an average momentum around 200 MeV/c.
-CLAS cannot detect such low energy particles, for exemple protons are detected with a threshold of about 250 MeV/c, which will be even higher for helium.
-In order to detect such low-energy recoils a Radial TPC (RTPC), similar to the one used during the BoNuS run \cite{BONUS}, was added to CLAS.
-In 2009, the CLAS-EG6 group \cite{proposal} has built this RTPC, figure \ref{fig:RTPC2} shows a close photo of the RTPC, while figure \ref{fig:RTPC_xscetion} shows a schematic drawing of its internal structure.
-It is a 200 mm-long and 150 mm-diameter TPC, composed of two electronically separated modules, each covering about 150$^{\circ}$ of the azimuthal angle.
-The RTPC tracks the charged particles through the ionization centers they leave in the gas-filled detection volume.
-Then, the ionized electrons drift under the effect of an electric field and are amplified by a gas electron multiplier system before to be detected on collection pads.
+At 6 GeV incident electron beam energy, the recoil $^{4}He$ nuclei from 
+the coherent DVCS channel, have an average momentum around 200 MeV/c. CLAS 
+cannot detect such low energy particles, for exemple protons are detected with 
+a threshold of about 250 MeV/c, which will be even higher for helium. In order 
+to detect such low-energy recoils a Radial TPC (RTPC), similar to the one used 
+during the BoNuS run \cite{BONUS}, was added to CLAS. In 2009, the CLAS-EG6 
+group \cite{proposal} has built this RTPC, figure \ref{fig:RTPC2} shows a 
+close photo of the RTPC, while figure \ref{fig:RTPC_xscetion} shows a 
+schematic drawing of its internal structure. It is a 200~mm-long and 
+150~mm-diameter TPC, composed of two electronically separated modules, each 
+covering about 150$^{\circ}$ of the azimuthal angle. The RTPC tracks the 
+charged particles through the ionization centers they leave in the gas-filled 
+detection volume. Then, the ionized electrons drift under the effect of an 
+electric field and are amplified by a gas electron multiplier system before to 
+be detected on collection pads.
 
@@
 \vspace{0.1in}
-\caption{A view of the RTPC before insertion into the solenoid. The incident electron beam comes from the left.} 
+\caption{A view of the RTPC before insertion into the solenoid. The incident 
+electron beam comes from the left.} 
 \label{fig:RTPC2}
@@
 \hspace*{-0.3in}\includegraphics[height=8.0cm]{fig_rtpc/RTPC_1_all.png}
-\caption{A cross section of the RTPC taken on a plane perpendicular to the beam line, with a typical $^4He$ track crossing the drift volume.}
+\caption{A cross section of the RTPC taken on a plane perpendicular to the 
+beam line, with a typical $^4He$ track crossing the drift volume.}
 \label{fig:RTPC_xscetion}
@@
 direction of the electric field). These characteristics minimize the changes in 
-the drift velocity of the ionization electrons \cite{DME}.\\
+the drift velocity of the ionization electrons \cite{DME}.
 
@@
 chemically etched with 50-$\mu$m-diameter holes in double-conical cross section 
-shapes, as can be seen from the schematic plot on the right.\\
+shapes, as can be seen from the schematic plot on the right.
 
@@
 layers to push the amplified electrons towards the readout board. In this 
-configuration, the gain of each GEM layer is of the order of 100.\\
+configuration, the gain of each GEM layer is of the order of 100.
 
@@
 \subsection{Working principle}
-~~~~When a charged particle traverses a gas, it ionizes the gas-atoms along its 
+When a charged particle traverses a gas, it ionizes the gas-atoms along its 
 trajectory. In a TPC, the electrons released in the ionization drift towards 
@@
 leading to reconstruct the original points of ionization, while the recorded 
-ADCs give the deposited energy.\\
+ADCs give the deposited energy.
 
@@
 and were disconnected during the experiment, partly justifying the time 
-dependent calibration described below. \\
+dependent calibration described below.
 
@@
 \subsection{Track reconstruction}
-~~~~In order to reconstruct tracks we must first select the good hits. The 
+In order to reconstruct tracks we must first select the good hits. The 
 first step is the rejection of out-of-time hits and the noise reduction, as 
@@
 them. Then, the number of hits per chain is required to be greater than 10 hits 
-in order to proceed to the fitting step. \\
+in order to proceed to the fitting step.
 
@@
 \section{RTPC calibration}
-~~~~Reconstructing a trajectory from the recorded time information of the 
+Reconstructing a trajectory from the recorded time information of the 
 electrons requires a good knowledge of their drift speed and drift paths.  
@@
 energy, so we had specific calibration runs with 1-pass 
-beam energies of 1.024 and 1.269 GeV. \\
+beam energies of 1.024 and 1.269 GeV.
 
@@
 in GEANT4. The output of the simulation gives an expected trajectory that we then
-match to to the measured signals to determine the drift paths. \\
+match to to the measured signals to determine the drift paths.
 
@@
 \subsection{Event selection}
-~~~~Figure \ref{fig:RTPC_track} shows a drawing of a segment of the RTPC, where a $^4He$ track (in 
+Figure \ref{fig:RTPC_track} shows a drawing of a segment of the RTPC, 
+where a $^4He$ track (in 
 green) crosses the volume of the RTPC, producing a chain of ionization points 
@@
 while the distance between the last point and the anode is labelled as 
-$edist$.\\
+$edist$.
 
@@
 
-~~~~A good RTPC track passes the following requirements:
+A good RTPC track passes the following requirements:
 \begin{itemize}
@@
 \includegraphics[height=6.5cm]{fig_rtpc/rtpc_X2.png}
-\caption{The $\chi^{2}$ distribution for the positive tracks in the RTPC. The red line represents the cut we apply to select good tracks.}
+\caption{The $\chi^{2}$ distribution for the positive tracks in the RTPC. The red 
+line represents the cut we apply to select good tracks.}
 \vspace{+0.1in}
@@
 \includegraphics[height=6.5cm]{fig_rtpc/rtpc_sdist.png}
-\caption{$sdist$ distribution for the positive tracks in the RTPC. We set $|sdist|$ < 2.0 mm to select good tracks.} 
+\caption{$sdist$ distribution for the positive tracks in the RTPC. We set $|sdist| < 2.0$ mm to select good tracks.} 
 \vspace{0.3in}
@@
 \end{equation}
-with the symbols in parenthesis representing the four-momenta of the particles. \\
+with the symbols in parenthesis representing the four-momenta of the particles.
 
@@
 Like for $\Delta z$, the $\Delta \phi$ 2$\sigma$ cut is dependent on $z$ to account for systematic variations.
-Our final parametrizations can be found in Appendix \ref{app:RTPC_appendix} as well.\\
+Our final parametrizations can be found in Appendix \ref{app:RTPC_appendix} as well.
 
@@
 No significant difference was observed between the two modules regarding this quantity.
-The obtained parametrization of the mean and the width of the $\Delta \theta$  distribution can be found in Appendix \ref{app:RTPC_appendix}.\\
+The obtained parametrization of the mean and the width of the $\Delta \theta$  distribution can be found in Appendix \ref{app:RTPC_appendix}.
 
@@
 
-Constructing the invariant mass is one way to verify the efficiency of the previously described selection procedures. For a helium target, the invariant mass (W) is:\\
+Constructing the invariant mass is one way to verify the efficiency of the previously described selection procedures. For a helium target, the invariant mass (W) is:
 \begin{equation}
@@
 therefore very sensitive to the local 
-variations of the resolution, which can be rather important in CLAS.\\
+variations of the resolution, which can be rather important in CLAS.
 
@@
 \subsubsection{Checking the initial good track requirements}
-~~~~In this section, we study some of the good track requirements 
+In this section, we study some of the good track requirements 
 presented in section \ref{good_track_req}. We apply here all the good track 
@@
 \subsubsection{Drift speed parametrization}
-~~~~The electrons follow their drift paths with a certain speed, named drift 
+The electrons follow their drift paths with a certain speed, named drift 
 speed. This speed is affected by the experimental conditions, such as the 
@@
 speed using the tracks detected in the RTPC, as it is explained in this 
-section.\\
+section.
 
@@
 of the maximum number of hits in each hits-time profile. $TDC_{max/2}$ is 
-inversely proportional to the drift speed.\\
+inversely proportional to the drift speed.
 
@@
 figure \ref{fig:RunNumber_61551_TDCmax_Zslice}, where a clear variation of the 
-drift speed along the RTPC was observed. \\ \begin{figure}[tbp]
+drift speed along the RTPC was observed.
+
+\begin{figure}[tbp]
 \centering
@@
 can conclude that using the hits of the collected good tracks is a good 
-approximation. \\
+approximation.
 
@@
 mixture which was not perfectly under control due to leaks in the thin parts of 
-the detector.\\
+the detector.
 
@@
 parametrize the dependence on $z$, hit (pad) position, for each run in the 
-form:\\
+form:
 \begin{equation}
@@
 RTPC. The numeric parametrizations of $p_{0}$, $p_{1}$, $p_{2}$, and $p_{3}$ 
-can be found in Appendix \ref{app:RTPC_appendix}, table \ref{Table:TDCmax}. \\
+can be found in Appendix \ref{app:RTPC_appendix}, table \ref{Table:TDCmax}.
 
@@
 parameters of the reconstructed tracks ($sdist$, $edist$ ... etc) are more likely to pass the 
-selection requirements and so more tracks are found to be good. \\
+selection requirements and so more tracks are found to be good.
 
@@
 \subsubsection{Drift paths parametrization}
-~~~~A drift path is the trajectory that an electron follows after being 
+A drift path is the trajectory that an electron follows after being 
 released in the drift region. The standard software to calculate these paths is 
@@
 way that does not require an exact knowledge of the conditions in the chamber 
-and is instead based on our experimental data.  \\
+and is instead based on our experimental data.
 
@@
 independently of our knowledge of the exact conditions in the RTPC, in 
-particular the electric field and the gas mixture have no impact. \\
+particular the electric field and the gas mixture have no impact.
 
@@
 field and therefore the varying Lorentz angle, the extraction 
-is made in $z$ bins along the RTPC. \\
-
-The procedure steps are:\\
+is made in $z$ bins along the RTPC.
+
+The procedure steps are:
 \begin{itemize}
@@
 third passes. In other words, extracting the drift paths from two iterations 
-gives us stable drift paths. \\
+gives us stable drift paths.
 
@@
 
-~~~~It is important to note that the drift paths have shown strong sensitivity 
+It is important to note that the drift paths have shown strong sensitivity 
 to the other RTPC calibrations. Therefore, we performed iterative extractions 
@@
 characteristics of the particle, such as its energy, mass and charge, and the 
-nature of the medium as well. \\
+nature of the medium as well.
 
@@
 density of the medium. In the RTPC, these constants are equal to 66, 126.79 mg 
-mol$^{-1}$, 99.79 eV and 1.03 mg/cm$^3$, respectively. \\
+mol$^{-1}$, 99.79 eV and 1.03 mg/cm$^3$, respectively.
 
@@
 energy of the particle, which is true except close to our detection 
-threshold.\\
+threshold.
 
@@
 track. We latter refined this second method by comparing the ADCs of each pad 
-to the average ADCs of the other pads in the same track.\\
+to the average ADCs of the other pads in the same track.
 
@@
 
-~~~~The second method requires improvements in the simulation, in order to 
+The second method requires improvements in the simulation, in order to 
 match the real experiment. In summary, these improvements are:
@@
 second method, where the dotted squares refer to the dead or noisy pads. These 
-are the ones that are implemented in the EG6 reconstruction codes.\\
+are the ones that are implemented in the EG6 reconstruction codes.
 
@@
 procedures, the events with low dEdx were excluded as we do not fully 
-understand their nature, see figure \ref{fig:dedx_cal_left}.\\
+understand their nature, see figure \ref{fig:dedx_cal_left}.
 \begin{figure}[tbp]
@@
 \label{sec:noise_rejection}
-~~~~The RTPC was designed to reduce noise and contribution from M\o ller 
+The RTPC was designed to reduce noise and contribution from M\o ller 
 electrons via the first and second 1 atm gas gaps. During data taking, the 
@@
 \section{Tracking resolution}
-~~~~The RTPC tracking resolution is defined as the spread of the reconstructed 
+The RTPC tracking resolution is defined as the spread of the reconstructed 
 track vertex, angles and momentum with respect to their true values. In the EG6 
@@
 solenoid, as can be observed experimentally from the target window, figure 
-\ref{fig:electron_z_vertex_res}. \\
+\ref{fig:electron_z_vertex_res}. 
 \begin{figure}[tbp]
@@
 performance. These resolutions will be used to match the simulated data to the 
-experimental ones, as will be shown in the following chapter.\\
+experimental ones, as will be shown in the following chapter.
 

### 2016-09-08 analysis-note-v2/results.tex
Cleaned up some of the weird and random line jumps

@@
 \chapter{Results and physics interpretations}
-~~~~In this chapter, we present our results after all corrections discussed above and including
+In this chapter, we present our results after all corrections discussed above and including
 all systematic errors. In order to discuss these results, we first present the functional forms
@@
 \section{Fitting the beam-spin asymmetry} \label{Beam-Spin}
-~~~~For a spin-zero target at leading twist, the beam-spin asymmetry ($A_{LU}$) 
+For a spin-zero target at leading twist, the beam-spin asymmetry ($A_{LU}$) 
 can be expressed as follow \cite{BM_2009}
@@
 leptonic tensor. Their explicit expressions can be found in Appendix 
-\ref{app:Helium_cross_section}.\\
+\ref{app:Helium_cross_section}.
 
@@
 \section{Beam-spin asymmetry results and fit}
-~~~~In this section, the beam-spin asymmetries will be compared to the theoretical calculations based on the two models that were presented in section \ref{Theoretical_hypotheses}.\\
+In this section, the beam-spin asymmetries will be compared to the theoretical calculations based on the two models that were presented in section \ref{Theoretical_hypotheses}.
 
 \subsection{Coherent beam-spin asymmetry}
-~~~~Figure \ref{fig:bsa_coh_Q2_bins} shows the coherent $A_{LU}$ for the three 
+Figure \ref{fig:bsa_coh_Q2_bins} shows the coherent $A_{LU}$ for the three 
 sets of two-dimensional bins. The asymmetries are fitted with the form of
 equation \ref{eq:A_LU-coh}, where the real and the imaginary part of the CFF 
-$\mathcal{H}_{A}$ are the free parameters in the fit.\\
+$\mathcal{H}_{A}$ are the free parameters in the fit.
 
@@
 the model, such as long-range interactions \cite{simonetta_2}. Our measurements 
-also agree with those of HERMES, considering their large uncertainties. \\
+also agree with those of HERMES, considering their large uncertainties.
 
@@
 \subsection{Incoherent beam-spin asymmetry}
-~~~~Figure \ref{fig:bsa_incoh_bins} shows our measured incoherent beam-spin 
+Figure \ref{fig:bsa_incoh_bins} shows our measured incoherent beam-spin 
 asymmetries, for the three sets of the two-dimensional bins as for the coherent 
@@
 $\phi$=~90$^{\circ}$ (the $\alpha$ parameter of the fit) are shown in figure 
-\ref{fig:incoh_Q2_xB_t_ALU}.\\
+\ref{fig:incoh_Q2_xB_t_ALU}.
 
@@
 \section{Helium GPD}
-~~~~As shown at the beginning of this chapter, one can extract both real and
+As shown at the beginning of this chapter, one can extract both real and
 imaginary parts of the 
@@
 exclusive measurements of the reaction. The results are presented in figure 
-\ref{fig:HA_CFF} as function of $Q^{2}$, $x_B$, and $-t$.\\
+\ref{fig:HA_CFF} as function of $Q^{2}$, $x_B$, and $-t$.
 
@@
 \section{Generalized EMC ratios} \label{sec:Generalized_EMC}
-~~~~Comparing our measured DVCS channels to the free-proton DVCS reaction 
+Comparing our measured DVCS channels to the free-proton DVCS reaction 
 allows us to investigate the nuclear medium effects at the GPD level. For this 
@@
 \ref{fig:incoh_EMC_ratio_ALU_proton} as functions of $Q^{2}$, $x_{B}$, and 
-$-t$, along with theoretical predictions at similar kinematical values.\\
+$-t$, along with theoretical predictions at similar kinematical values.
 
@@
 uncertainties, our measured ratios are compatible with the previous measured 
-single point from HERMES.\\
+single point from HERMES.
 
@@
  for all different spin-zero nuclei at $x_{B}$= 0.3, $E_{b}$= 6GeV, -$t$= 0.25 
- GeV$^2$, and $Q^2$= 2.5 GeV$^2$.  \\
+ GeV$^2$, and $Q^2$= 2.5 GeV$^2$.
 
@@
 \end{figure}
-~\\

### 2016-09-08 analysis-note-v2/Appendix.tex
update the answers and minor text cleanings in the note
Clarification on calibration and clean up

@@
 
-~~~~~The exclusive selection of the experimental $e^{4}He\pi^{0}$ and $ep\pi^{0}$ events require the detection of only one good electron, one good $\pi^{0}$ in the topology ICIC or ICEC, and one good $^{4}He$ track in the coherent channel or one good proton in the incoherent channel case.
+The exclusive selection of the experimental $e^{4}He\pi^{0}$ and $ep\pi^{0}$ events require the detection of only one good electron, one good $\pi^{0}$ in the topology ICIC or ICEC, and one good $^{4}He$ track in the coherent channel or one good proton in the incoherent channel case.
 Furthermore, in order to ensure that this is a deep process we apply a set of initial requirements.
@@
 
-\paragraph{Initial criteria}
-~\\
-~\\
+\paragraph{Initial criteria} ~\\
 These requirements are made to ensure that the selected events occurre at the partonic level:
@@
 \section{$e^{4}He\pi^{0}$ exclusivity cuts}
-~~~~The events which pass the following exclusivity cuts are assumed to be good $e^{4}He\pi^{0}$ events.
+The events which pass the following exclusivity cuts are assumed to be good $e^{4}He\pi^{0}$ events.
 
@@
 
-\chapter{ALU tables}
+\chapter{$A_{LU}$ tables}
 \begin{table}[!h]

### 2016-09-08 analysis-note-v2/RTPC.tex
Clarification on calibration and clean up

@@
 of these variations is probably the variation of proportions in the drift gas 
-mixture which was not perfectly under control due to leaks in the thin parts of 
-the detector.
+mixture which was not perfectly under control due to leaks in the parts of 
+the detector where the gas is contained by very thin aluminized mylar.
 
@@
 
-These functions are implemented in our reconstruction codes, and, as a result 
-of adapting the drift speed with these functions, more good tracks and elastic 
-events were identified comparing to the previous calibration set. Figure 
-\ref{fig:Drift_run_number} also shows the gain percentages of the good tracks 
-(GT) and the elastic events (El) in few runs. One can see a gradual improvement 
-with time because of giving the right drift speed, which together with the 
-drift paths gives more precise reconstructed hits chain. Therefore, the 
-parameters of the reconstructed tracks ($sdist$, $edist$ ... etc) are more likely to pass the 
-selection requirements and so more tracks are found to be good.
+The implementation of these parametrizations of the drift speed in our 
+reconstruction codes resulted in more good tracks and elastic 
+events identified comparing to the previous calibration sets. Figure 
+\ref{fig:Drift_run_number} also shows these gain percentages of good tracks 
+(GT) and elastic events (El) for a few runs. The gradual improvement 
+with time is due to the improvement on the parameters of the reconstructed 
+tracks ($sdist$, $edist$ ... etc), which are then more likely to pass the 
+selection requirements.
 
@@
 \subsubsection{Drift paths parametrization}
+
 A drift path is the trajectory that an electron follows after being 
@@
 In the EG6 experiment, MAGBOLTZ has been used to calculate a first set of drift 
-paths, but it was observed for the drift speed that we do not have a perfect 
-knowledge of the RTPC's conditions. Therefore, the first set of the drift paths 
-is not accurate. For this reason, we chose to calculate the drift paths in a 
-way that does not require an exact knowledge of the conditions in the chamber 
-and is instead based on our experimental data.
-
-In our alternative method, we use the identified elastic ($e ~ ^{4}He 
+paths, but it was found rapidly that our lack of knowledge on some of the RTPC's 
+conditions was limiting the precision of the calculation. For this reason, we 
+chose to further calibrate the drift paths with a method 
+that does not require an exact knowledge of the conditions in the chamber 
+and is instead based on the experimental data.
+
+In this alternative method, we use the identified elastic ($e ~ ^{4}He 
 \rightarrow e ~ ^{4}He$) events to extract the drift paths. For these events, 
-the kinematics of the recoil $^{4}He$ are calculated from the scattered 
-electron. Then the electrons' drift paths can be extracted from comparing the 
-experimentally measured hits in the RTPC to the trajectory of a similar 
-simulated $^{4}He$. In this technique, the drift paths are obtained 
-independently of our knowledge of the exact conditions in the RTPC, in 
-particular the electric field and the gas mixture have no impact.
-
-Due to the magnetic field, the drift paths are not linear. This is handled by 
-the following procedure, in which we perform the drift paths' extraction in 
-two passes. In the first pass, we assume a linear correlation between the 
+the kinematic of the recoil $^{4}He$ is calculated from the scattered 
+electron. Then the electrons' drift paths is extracted by comparing event
+by event the experimentally measured hits in the RTPC to the 
+trajectory of the corresponding simulated $^{4}He$. With this technique, the 
+drift paths are obtained with limited impact from our knowledge of the 
+conditions in the RTPC, in particular the method is completely independent 
+from both electric field and gas mixture.
+
+We perform the drift paths' extraction in two passes. 
+In the first pass, we assume a linear correlation between the 
 radius of emission $R$ (we work here in radial coordinates: $R$ and $\phi$) and the 
-drift time, to link the GEANT4 hits to the measured hits. Through this association, we obtain an 
-initial set of drift paths in the form of a $\Delta \phi$ distribution as function of time. We define $\Delta \phi$ the 
-difference between the $\phi$ of the simulated hits and the $\phi$ of the pad 
-which measured a hit. In the second pass, we refine the initial 
-correlation between the radius and the time using the initial drift paths, and 
-we extract final drift paths. To take into account the variations of the magnetic 
-field and therefore the varying Lorentz angle, the extraction 
-is made in $z$ bins along the RTPC.
-
-The procedure steps are:
+drift time to link GEANT4 hits along the trajectory to actually measured 
+hits. Based on this association, we obtain a $\Delta \phi$ distribution 
+as function of time. $\Delta \phi$ is the 
+difference between the $\phi$ observed in GEANT4 and the $\phi$ of the pad 
+which actually measured a correlated hit. Assuming we have an axial 
+symmetry of the drift path, $\Delta \phi$ as a function of time indicates 
+how much the electron drifted because of the magnetic field for any hit. 
+This is therefore the relevant information to reconstruct the origin
+of the hits measured in the detector.
+However, the actual correlation between time and radius is not exactly
+linear. So we perform a second pass, in which we refine the initial 
+correlation between the radius and the time using the drift paths obtained 
+in the first path. We then repeat the procedure of the first pass to extract 
+the final drift paths. Because of the variations in the magnetic 
+field along the detector, the extraction is made in $z$ bins.
+
+The detailed steps of the procedure are as follow:
 \begin{itemize}
-\item We first select a sample of well identified elastic events in our experimental data. Using the
+\item We first select a sample of well identified elastic events in our 
+   experimental data. Using the
    kinematics of the scattered electrons in these events, we generate in GEANT4
@@
    maximum $R$ equals 60 mm (close to the anode) at the trigger time, 
-   (TDC$_{min}$ = 15 TDCs), and the minimum R equals 30 mm (close to the 
+   (TDC$_{min}$ = 15 TDCs), and the minimum $R$ equals 30 mm (close to the 
    cathode) at maximum TDC ($TDC_{max}$). Thus, the linear correlations can be 
@@
 the GEANT4 simulated hits to measured hits. Figure \ref{fig:R_correlation} 
-shows the distribution of $R$ versus TDC for the selected simulated hits in a 
-single $z$ bin.
-
-\item From these selected hits, we construct the drift paths $\Delta \phi$ (= 
-   $\phi_{sim.}$ - $\phi_{hit\_pad}$) versus TDC. The results can be seen in 
-   figure \ref{fig:1st_pass_delta_phi}. $\Delta \phi$ at the anode (TDC = 15) 
+shows the distribution of $R$ versus TDC for to select the matched hits.
+\item From these selected matched hits, we obtain $\Delta \phi$ (= 
+   $\phi_{sim.}$ - $\phi_{hit\_pad}$) as a function of time. The results can be seen in 
+   figure \ref{fig:1st_pass_delta_phi}\footnote{$\Delta \phi$ at the anode (TDC = 15) 
    is not equal to zero because there is a drift in $\phi$ between the anode 
    (the first GEM layer at radial distance equal to 60 mm) and the readout pads 
-   (at radial distance equal to 69mm).
-
+   (at radial distance equal to 69mm).}. This figure is fitted to obtain the 
+   parameterization of the drift path.
 \begin{figure}[tpb]
@@
 \includegraphics[scale=0.45]{fig_rtpc/updates/TdcR_check_p1_10.png}
-\caption{(First pass). Distribution of $R$ as a function of TDC for the 
+\caption{(First pass). Distribution of $R$ as a function of time (in TDC) for the 
 simulated hits located in one $z$ bin. The width of the bin is 10 mm, with the 
@@
 \end{figure}
-
 \begin{figure}[tpb]
@@
 \includegraphics[scale=0.45]{fig_rtpc/TdcPhi_p1_10.png}
-\caption{(First pass). Distribution of $\Delta \phi$ as a function of TDC for 
+\caption{(First pass). Distribution of $\Delta \phi$ as a function of time (in TDC) for 
    in one $z$ bin. The width of the bin is 10 mm, 
@@
 \end{figure} 
-
 \begin{figure}[tbp]
@@
 \includegraphics[scale=0.45]{fig_rtpc/TdcR_p2_10.png}
-\caption{(Second pass). The calculated R as a function of TDC is corrected by 
+\caption{(Second pass). The calculated $R$ as a function of time (in TDC) is corrected by 
 the $\Delta \phi$ relation extracted from the first pass.}
@@
 \end{figure}
-
-\item The correlation between R and TDC is refined using the extracted initial 
-   $\Delta \phi$ as a function of TDC as:
+\item The correlation between $R$ and the time is then refined using the extracted  
+   $\Delta \phi$ as a function of time as:
 \begin{equation}
@@
 \ref{equ:R_TDC} and $\Delta \phi (i)$ is the fit in figure 
-\ref{fig:1st_pass_delta_phi}. The sum is multiplied by a TDC (=114 ns) unit.  
-The calculated R, figure \ref{fig:R_TDC}, is very close to a straight line, 
+\ref{fig:1st_pass_delta_phi}. The sum is multiplied by a TDC unit (=114 ns).  
+The calculated R, figure \ref{fig:R_TDC}, is almost linear, 
 indicating that only two itterations are probably enough.
-
-\item In the second pass, we use the newly found R(TDC) relation to construct new $\Delta \phi$ distributions, see figure \ref{fig:final_drift_paths}.
-
+\item In the second pass, we use the newly found $R$(TDC) relation to construct 
+new $\Delta \phi$ distributions, see figure \ref{fig:final_drift_paths} for our final
+result.
 \begin{figure}[tp]
@@
 \includegraphics[scale=0.45]{fig_rtpc/FitResult_p2_10.png}
-\caption{(Second pass). Distribution of $\Delta \phi$ as a function of TDC 
+\caption{(Second pass). Distribution of $\Delta \phi$ as a function of time (in TDC) 
 located in the same $z$ bin shown in figure \ref{fig:1st_pass_delta_phi}. The 
@@
 
-We performed a third pass in which the R(TDC) correlation is refined using the 
-drift paths from the second pass and new drift paths were extracted. As a 
+We performed a third pass in which the $R$(TDC) correlation is refined using the 
+drift paths from the second pass. As a 
 result, we observed no difference between the drift paths of the second and the 
 third passes. In other words, extracting the drift paths from two iterations 
-gives us stable drift paths.
+gives us stable results.
 
 The first drift paths were extracted using the elastic events from the early 
-1.204 GeV dataset. In order to ensure the consistency of these drift paths over 
+1.204~GeV dataset. In order to ensure the consistency of these drift paths over 
 the experimental running period, we extracted another set of drift paths using 
-the elastic events of the 1.269 GeV runs. We observed no difference between the 
-two sets of the drift paths, ensuring their stability over the experimental 
-period and leaving the dependence on the TDC and $z$. The final drift paths are 
+the elastic events of the 1.269 GeV dataset. We observed no difference between the 
+two sets of the drift paths, ensuring the stability over the experimental 
+period. The final drift paths are 
 extracted using both datasets, 1.204 and 1.269 GeV. They take the form:
@@
 
-\subsubsection{summary}
+\subsubsection{Summary}
 The drift paths and drift speed were first extracted using the

### 2016-09-08 analysis-note-v2/analysis-2.tex
Clarification on calibration and clean up

@@
 
-~~~~In the previous chapter, the events were filtered to select the ones which have one and only one good electron, and other good particles in coincidence with the electron.
+In the previous chapter, the events were filtered to select the ones which have one and only one good electron, and other good particles in coincidence with the electron.
 This chapter explains the procedure we used to extract the beam-spin asymmetry observable following this order: clean the DVCS data sample by choosing good run list, ensure the exclusivity of the selected events by imposing the conservation laws, subtract the background by combining data with simulation, and binning the identified DVCS events.
-This chapter contains also an estimation of the systematic uncertainty contribution from each source on the measured beam-spin asymmetry.\\
+This chapter contains also an estimation of the systematic uncertainty contribution from each source on the measured beam-spin asymmetry.
 
@@
 \subsection{Good run list}
-~~~~In principle, with constant beam luminosity, target density and pressure, the event rate has to be constant over the experimental time.
+In principle, with constant beam luminosity, target density and pressure, the event rate has to be constant over the experimental time.
 Due to the changes in the experimental conditions, such as changing a trigger in a detector, a slight shift in the beam position or a system failure somewhere, this rate changes.
@@
 Furthermore, we also look at this ratio in the six sectors of CLAS, as they are independent of each other and their performances might be different.
-\\
 
@@
 
-~~~~Figure \ref{fig:tpc_over_e_Run_sec.png} shows the integrated and the 
+Figure \ref{fig:tpc_over_e_Run_sec.png} shows the integrated and the 
 sector-dependence of <tpc/e> for the individual runs. One notices a universal 
@@
 \subsection{Coherent DVCS event selection}
-~~~~Events with one and only one good electron, one and only one good RTPC 
+Events with one and only one good electron, one and only one good RTPC 
 track and at least one good photon are considered good coherent DVCS 
@@
 \frac{M_{p}\cdot x_{B}}{M_{^4He}}$ and $M_{p}$ ($M_{^4He}$) is the proton 
-($^{4}He$) mass.\\
+($^{4}He$) mass.
 
@@
 \newpage
-\paragraph{Exclusivity cuts}
-
-~\\
+\paragraph{Exclusivity cuts} ~\\
 The coherent DVCS reaction is:
@@
 
-~~~~The exclusivity of the coherent DVCS reaction is ensured by imposing the following conservation laws:
+The exclusivity of the coherent DVCS reaction is ensured by imposing the following conservation laws:
 \begin{itemize}
@@
 \end{itemize}
-~~~~~Figure \ref{fig:coh_exclusivty_cuts} summarizes all the exclusivity cuts.  
+Figure \ref{fig:coh_exclusivty_cuts} summarizes all the exclusivity cuts.  
 In these plots, the blue distributions represent the coherent events after the 
@@
 distribution. The events which pass these cuts are assumed to be good $^{4}He$ 
-DVCS events.  ~\\
-~\\
+DVCS events.
 
@@
 cuts. We performed few checks regarding applying a PID cut, where the full data
-was analyzed in the following three sets:\\
+was analyzed in the following three sets:
 \begin{itemize}
 \item Processing all the reconstructed tracks in each event with the exclusivity
-cuts.\\
+cuts.
 \item Processing events with only one good track in the RTPC being
-reconstructed.\\
-\item Processing events with only one track that passes a dedx cut.\\
+reconstructed.
+\item Processing events with only one track that passes a dedx cut.
 \end{itemize}
@@
 \subsection{Comparison with simulation}
-~~~~Coherent DVCS events were simulated according to the procedures described 
+Coherent DVCS events were simulated according to the procedures described 
 in section \ref{Event_generator}. Then, events are selected following the same 
@@
 is done to avoid issues on variables where the peak is not in the exact same 
-place in simulation and in data.\\
+place in simulation and in data.
 
@@
 \section{Incoherent channel}
-~~~~In this channel, the DVCS process happens on a bound proton. Thus, the 
+In this channel, the DVCS process happens on a bound proton. Thus, the 
 final state has a recoil proton instead of the helium nucleus. Therefore, 
@@
 \subsection{Good run list}
-~~~~The events rate stability is verified by looking at the rate of the 
+The events rate stability is verified by looking at the rate of the 
 detected number of protons to the detected electrons (<p/e>). Like for the 
@@
 \subsection{Proton DVCS event selection}
-~~~~To certify that an event is a proton DVCS one, we require the same DVCS 
+To certify that an event is a proton DVCS one, we require the same DVCS 
 kinematic cuts as those presented for the coherent DVCS selection. Then, the 
@@
 exclusivity with taking a proton at rest as the target, instead of $^4He$.  
-Figure \ref{fig:incoh_exclusivty_cuts} summarizes these exclusivity cuts.\\
+Figure \ref{fig:incoh_exclusivty_cuts} summarizes these exclusivity cuts.
 
@@
 \subsection{Comparison with simulation}
-~~~~The three particles of the simulated $ep\gamma$ DVCS events are selected 
+The three particles of the simulated $ep\gamma$ DVCS events are selected 
 applying the previously described identification requirements. The events with 
@@
 In this section, a comparison between the experimental and the simulated data 
-is carried out.\\
+is carried out.
 
@@
 \section{Kinematic coverages}
-~~~~The one-dimensional distributions of explored kinematical regions can be 
+The one-dimensional distributions of explored kinematical regions can be 
 seen in figure \ref{fig:coh_comparison_with_simulation_1} for the coherent, and 
@@
 \section{Data binning}
-~~~~~The DVCS cross section and $A_{LU}$, equations \ref{BSA_equation} to 
+The DVCS cross section and $A_{LU}$, equations \ref{BSA_equation} to 
 \ref{eq:A_LU-coh}, depend on the four kinematic variables: $Q^{2}$, $x_{B}$, 
@@
 \subsection{$\pi^0$ contaminations}
-~~~~Even with all cuts applied to select the selected DVCS events, the events 
+Even with all cuts applied to select the selected DVCS events, the events 
 are not all DVCS events. In our kinematic region, the main contamination comes 
@@
 number of simulated $e^{4}He\pi^{0}$ events passing the exclusivity cuts for 
-$e^{4}He\pi^{0}$ events.\\
+$e^{4}He\pi^{0}$ events.
 
@@
 procedures hold for the incoherent case by replacing the $^{4}He$ with the 
-proton.\\
+proton.
 
@@
 the same kinematic cuts as DVCS. These cuts and the comparisons with simulation 
-can be found in Appendix \ref{app:Exclusive_pi0_selection}.\\
+can be found in Appendix \ref{app:Exclusive_pi0_selection}.
 
@@
 incoherent channel, the mean acceptance ratio is around 20$\%$ with some 
-dependence on the four kinematic variables.\\
+dependence on the four kinematic variables.
 
@@
 channels, the contamination increases strongly with -$t$, with a mean of 2$\%$ 
-(6$\%$) for the coherent (incoherent) channel. \\
+(6$\%$) for the coherent (incoherent) channel.
 
@@
 \subsection{Accidental contaminations}
-~\\
 
@@
 were performed on the incoherent channel, and a 
-global contamination of 6.5$\%$ has been observed.\\
+global contamination of 6.5$\%$ has been observed.
 
@@
 \section{Statistical uncertainties}
-~~~~~In terms of the collected number of events in each beam-helicity state ($N^{+}$, $N^{-}$), $A_{LU}$ can be expressed as:
+In terms of the collected number of events in each beam-helicity state ($N^{+}$, $N^{-}$), $A_{LU}$ can be expressed as:
 \begin{equation}
@@
 
-~~~~It is particularly convenient to use the $A_{LU}$ as a DVCS observable, 
+It is particularly convenient to use the $A_{LU}$ as a DVCS observable, 
 because most of the experimental systematic uncertainties, such as 
@@
 
-\paragraph{DVCS selection cuts}
-~\\
-
+\paragraph{DVCS selection cuts} ~\\
 In order to evaluate the systematic uncertainties stemming from the DVCS 
@@
 
-\paragraph{Fitting sensitivity to our binning}
-~\\
-
+\paragraph{Fitting sensitivity to our binning} ~\\
 In order to evaluate how sensitive are the fit results to our binning, we 
@@
 
-\paragraph{Beam polarization}
-~\\
-
+\paragraph{Beam polarization} ~\\
 The beam polarization has been measured regularly during the CLAS-EG6 data 
@@
 
-\paragraph{Acceptance ratio}
-~\\
-
+\paragraph{Acceptance ratio} ~\\
 Predominantly, two techniques are used to estimate the systematic uncertainty 
@@
 the analysis by implementing R differently, while the second technique is by 
-using two generating models to calculate R.\\
+using two generating models to calculate R.
 
@@
 2$\%$ (0.6$\%$) has been observed on the incoherent (coherent) $A_{LU}$ at 
-$\phi = 90^{\circ}$. \\
+$\phi = 90^{\circ}$.
 
@@
 
-\paragraph{Radiative corrections}
-~\\
-
+\paragraph{Radiative corrections} ~\\
 In this analysis, we have assumed that the beam-spin asymmetry arises from the 
@@
 Therefore, we can still take the result of Afanasev as a good estimation for 
-the radiative  effects on our measured $A_{LU}$.\\
+the radiative  effects on our measured $A_{LU}$.
 
@@
 
-\paragraph{Systematic uncertainty summary}
-~\\
-~\\
+\paragraph{Systematic uncertainty summary} ~\\
 The total systematic uncertainty is the quadratic sum of the previously 

### 2016-09-15 eg6-letters/NIM/main.tex
added the papers
editing the NIM paper

--- 2016-08-10 NIM/main.tex
@@
-\documentclass[reprint, amsmath,amssymb, aps]{revtex4-1}
+\documentclass[reprint, amsmath,amssymb, aps]{revtex4}
 
@@
 \author{
-\Large{R. Dupr\'e$^{[1][2]}$, M. Hattawy$^{[1][2]}$, ...} \\
+\Large{R. Dupr\'e$^{1,2}$, N. Baltzell$^{1,3}$, K. Hafidi$^{1}$, M.  
+Hattawy$^{1,2}$, S. Stepanyan$^{3}$} \\
 \vspace{+5mm}
-\normalsize $^{[1]}$Argonne National Laboratory, Argonne IL 60439, USA \\
-\normalsize $^{[2]}$Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France \\
-\vspace{+5mm}
+\normalsize $^{1}$ Argonne National Laboratory, Argonne IL 60439, USA \\
+\normalsize $^{2}$ Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and 
+Universit$\acute{e}$ Paris Sud, Orsay, France \\
+\normalsize $^{3}$ Jefferson Laboratory, Newport News, VA 230606, USA.
 }
@@
 
+\vspace{+25mm}
 \begin{abstract}
-To study coherent Deeply Virtual Compton Scattering (DVCS) and coherent production of mesons on $^4$He, it is necessary to insure that the target nuclei is left intact by the reaction.
-This experiment is carried on at the CEBAF Large Acceptance Spectrometer (CLAS) at Jefferson laboratory (JLab), which has been used for similar studies on proton targets, however it cannot track low energy $^4$He.
-We developed for an experiment in 2009 a Radial Time Projection Chamber (RTPC) based on Gas Electron Multipliers (GEMs).
-The detector was positioned directly around the gaseous target of the experiment, allowing a detection threshold of $~$???
-MeV/c for $^4$He.
-We describe in this article the design of the RTPC, the methods we developed to calibrate it and finally its performances.
+A new Radial Time Projection Chamber (RTPC) was developed at Jefferson 
+laboratory (JLab) to track low-energy nuclear recoils for the purpose of 
+measuring nuclear exclusive channels, such as, coherent Deeply Virtual Compton 
+Scattering (DVCS) and coherent production of mesons on $^4$He. In such 
+processes, $^4$He remains intact and recoils as a whole in the final state. 
+This experiment has been carried out using CEBAF Large Acceptance Spectrometer 
+(CLAS) at JLab. The CLAS spectrometer has been used for similar studies on 
+proton targets, however it cannot track recoils with momenta less than 250 
+MeV/c.  We developed for an experiment in 2009 a Radial Time Projection Chamber 
+(RTPC) based on Gas Electron Multipliers (GEMs).  The detector was positioned 
+directly around the gaseous target of the experiment, allowing a detection 
+threshold of $~$???  MeV/c for $^4$He. We describe in this article the design 
+of the RTPC, the methods we developed to calibrate it and finally its 
+performances.
 \end{abstract}
@@
 
-The CEBAF Large Acceptance Spectrometer (CLAS)~\cite{CLASref} is installed in the Hall-B of the TJNAF in Newport News, Virginia, USA.
-The spectrometer is measuring charged particles as well as photons.
-The accelerator of the TJNAF provides a high power electron beam of energy up to 6 GeV and 100$\%$ duty cycle to the hall.
-The RTPC mentioned in this article has been used during a three months experimental run in 2009 with a longitudinally polarized electron beam of energy 6.064 GeV sent on a gaseous helium-4 target to measure asymmetries in Deep Virtual Compton Scattering (DVCS)~\cite{proposal} and exclusive meson production (Meson Spec Prop).
-In these experiments, CLAS detects the high energy charged particles and the final real photon, for the latter the coverage has been extended using the optional inner calorimeter (ref).
+The CEBAF Large Acceptance Spectrometer (CLAS)~\cite{CLASref} is installed in 
+the Hall-B of the Thomas Jefferson National Accelerator Facility (TJNAF) in 
+Newport News, Virginia, USA. The spectrometer is measuring charged particles as 
+well as photons. The accelerator of the TJNAF provides a high power electron 
+beam of energy up to 6 GeV and 100$\%$ duty cycle to the hall. The RTPC 
+mentioned in this article has been used during a three months experimental run 
+in 2009 with a longitudinally polarized electron beam of energy 6.064 GeV sent 
+on a gaseous helium-4 target to measure asymmetries in Deep Virtual Compton 
+Scattering (DVCS)~\cite{proposal} and exclusive meson production (Meson Spec 
+Prop). In these experiments, CLAS detects the high energy charged particles and 
+the final real photon, for the latter the coverage has been extended using the 
+optional inner calorimeter (ref).
 

### 2016-09-16 eg6-letters/NIM/EG6_RTPC_NIM.tex
clean the NIM paper directory and writing

--- 2016-09-15 eg6-letters/NIM/main.tex
@@
-\documentclass[reprint, amsmath,amssymb, aps]{revtex4}
+\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4}
+\usepackage{graphicx}  
+\usepackage{dcolumn}   
+\usepackage{bm}        
+\usepackage{amssymb}
 
-\usepackage{graphicx}% Include figure files
-\usepackage{dcolumn}% Align table columns on decimal point
-\usepackage{bm}% bold math
-\newcommand{\RNum}[1]{\uppercase\expandafter{\romannumeral #1\relax}}
-\usepackage{amsmath}
-\usepackage{url}
-\usepackage{graphicx}
-\usepackage[latin1]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{color}
-\usepackage{amsmath}
-\usepackage[english]{babel}
-\usepackage{array}
-\usepackage{xcolor}
-\usepackage{amssymb}
-\usepackage{float}
-\usepackage{wrapfig}
-%\usepackage{hyperref}% add hypertext capabilities
-%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
-%\linenumbers\relax % Commence numbering lines
-
-%\usepackage[showframe,%Uncomment any one of the following lines to test 
-%%scale=0.7, marginratio={1:1, 2:3}, ignoreall,% default settings
-%%text={7in,10in},centering,
-%%margin=1.5in,
-%%total={6.5in,8.75in}, top=1.2in, left=0.9in, includefoot,
-%%height=10in,a5paper,hmargin={3cm,0.8in},
-%]{geometry}
+% avoids incorrect hyphenation, added Nov/08 by SSR
+\hyphenation{ALPGEN}
+\hyphenation{EVTGEN}
+\hyphenation{PYTHIA}
 
@@
 
-\preprint{APS/123-QED}
+% the following line is for submission, including submission to the arXiv!!
+%\hspace{5.2in} \mbox{Fermilab-Pub-04/xxx-E}
 
 \title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A New Radial Time Projection Chamber for CLAS at JLab}}
-\author{
-\Large{R. Dupr\'e$^{1,2}$, N. Baltzell$^{1,3}$, K. Hafidi$^{1}$, M.  
-Hattawy$^{1,2}$, S. Stepanyan$^{3}$} \\
-\vspace{+5mm}
-\normalsize $^{1}$ Argonne National Laboratory, Argonne IL 60439, USA \\
-\normalsize $^{2}$ Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and 
-Universit$\acute{e}$ Paris Sud, Orsay, France \\
-\normalsize $^{3}$ Jefferson Laboratory, Newport News, VA 230606, USA.
-}
+\input author_list.tex
 
-\collaboration{CLAS Collaboration}
+\date{\today}
 
-\date{\today}% It is always \today, today,
-             %  but any date may be explicitly specified
-
-\vspace{+25mm}
 \begin{abstract}
@@
 Scattering (DVCS) and coherent production of mesons on $^4$He. In such 
-processes, $^4$He remains intact and recoils as a whole in the final state. 
-This experiment has been carried out using CEBAF Large Acceptance Spectrometer 
-(CLAS) at JLab. The CLAS spectrometer has been used for similar studies on 
-proton targets, however it cannot track recoils with momenta less than 250 
-MeV/c.  We developed for an experiment in 2009 a Radial Time Projection Chamber 
-(RTPC) based on Gas Electron Multipliers (GEMs).  The detector was positioned 
-directly around the gaseous target of the experiment, allowing a detection 
-threshold of $~$???  MeV/c for $^4$He. We describe in this article the design 
-of the RTPC, the methods we developed to calibrate it and finally its 
-performances.
+processes, $^4$He remains intact and recoils as a whole in the final state. The 
+CEBAF Large Acceptance Spectrometer (CLAS) at JLab has been used for similar 
+studies on proton targets, however it cannot track recoils with momenta less 
+than 250 MeV/c. In 2009, we carried out measurements on $^4$He target using
+CLAS spectrometer, which was upgraded with a RTPC. The detector was positioned 
+directly around the gaseous target, allowing a detection threshold of $~$125  
+MeV/c for $^4$He. This article discuses the design of our RTPC, the methods we 
+developed to calibrate it and its performances.
 \end{abstract}
@@
 
-This paper is organized in this way: section $\RNum{2}$ details the design and the internal structure of the RTPC, while section $\RNum{3}$ points the properties of the readout system.
-The calibration strategies for such detectors will be discussed in section $\RNum{4}$.
-Finally, performances are discussed in section $\RNum{5}$.
+This paper is organized in this way: section \ref{sec_design} details the design and the internal structure of the RTPC, while section \ref{sec_readout} points the properties of the readout system.
+The calibration strategies for such detectors will be discussed in section \ref{sec_calib}.
+Finally, performances are discussed in section \ref{sec_perf}.
 
-\section{Design}
+\section{Design} \label{sec_design}
 
@@
 
-\section{Readout System}
+\section{Readout System} \label{sec_readout}
 The RTPC electron collecting system has 3200 readout pads. These collection elements are located at the end of the amplification region, 69 mm from the central axis.
@@
 
-\section{Calibration}
+\section{Calibration} \label{sec_calib}
 Two quantities are recorded for each detected electron at the readout board, time (TDCs) and signal amplitude (ADCs) (/!\\ are those amplitude or charge preamps ???).
@@
 
-\section{Track Reconstruction}
+\section{Track Reconstruction}\label{sec_perf}
 
@@
 
-(TBD)
+\input acknowledgement.tex
 
-\begin{thebibliography}{}
+\begin{thebibliography}{99}
+
 \bibitem{CLASref}

### 2016-09-19 NIM/EG6_RTPC_NIM.tex
update the NIM writing and cleaning the directory

--- 2016-09-16 eg6-letters/NIM/EG6_RTPC_NIM.tex
@@
 
-\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A New Radial Time Projection Chamber for CLAS at JLab}}
+\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A New Radial Time 
+Projection Chamber for CLAS at JLab}}
 \input author_list.tex
@@
 Scattering (DVCS) and coherent production of mesons on $^4$He. In such 
-processes, $^4$He remains intact and recoils as a whole in the final state. The 
-CEBAF Large Acceptance Spectrometer (CLAS) at JLab has been used for similar 
-studies on proton targets, however it cannot track recoils with momenta less 
-than 250 MeV/c. In 2009, we carried out measurements on $^4$He target using
-CLAS spectrometer, which was upgraded with a RTPC. The detector was positioned 
-directly around the gaseous target, allowing a detection threshold of $~$125  
-MeV/c for $^4$He. This article discuses the design of our RTPC, the methods we 
-developed to calibrate it and its performances.
+processes, $^4$He nucleus remains intact and recoils as a whole in the final 
+state. The CEBAF Large Acceptance Spectrometer (CLAS) at JLab has been used for 
+similar studies on proton targets, however it cannot track recoils with momenta 
+less than 250 MeV/c. In 2009, we carried out measurements on $^4$He target 
+using CLAS spectrometer, which was upgraded with the RTPC. The detector was 
+positioned directly around the gaseous target, allowing a detection threshold 
+of $~$125  MeV/c for $^4$He. This article discuses the RTPC design, work 
+principle, developed calibration methods and detector performance.
 \end{abstract}
@@
 The CEBAF Large Acceptance Spectrometer (CLAS)~\cite{CLASref} is installed in 
-the Hall-B of the Thomas Jefferson National Accelerator Facility (TJNAF) in 
-Newport News, Virginia, USA. The spectrometer is measuring charged particles as 
-well as photons. The accelerator of the TJNAF provides a high power electron 
-beam of energy up to 6 GeV and 100$\%$ duty cycle to the hall. The RTPC 
-mentioned in this article has been used during a three months experimental run 
-in 2009 with a longitudinally polarized electron beam of energy 6.064 GeV sent 
-on a gaseous helium-4 target to measure asymmetries in Deep Virtual Compton 
-Scattering (DVCS)~\cite{proposal} and exclusive meson production (Meson Spec 
-Prop). In these experiments, CLAS detects the high energy charged particles and 
-the final real photon, for the latter the coverage has been extended using the 
-optional inner calorimeter (ref).
+the Hall-B of the Thomas Jefferson National Accelerator Facility (TJNAF), 
+Newport News, Virginia, USA. The accelerator of TJNAF provides a high power 
+electron beam of energy up to 6 GeV and 100$\%$ duty cycle to three 
+experimental Halls (A, B, C). The CLAS spectrometer is composed of several 
+sub-detectors and two magnets. The spectrometer was designed to track charged 
+particles at momentum greater than 250 MeV/c as well as detecting real photons.  
+Figure~\ref{fig:CLAS} shows CLAS detector, ordered with respect to their radial 
+distance from the center as:
 
-\begin{figure}[h]
-\centering 
-\includegraphics[scale=0.3]{fig/test_clas.png}
-\caption{\small\sf Three dimensional representation of the primary CLAS setup represents the geometry and the relative position of each subsystem.
-From outside, the electromagnetic calorimeter (green), time-of-flight system (red), Cherenkov counters (purple), three drift chamber regions (blue) and the superconducting torus coils (yellow).}
+\begin{itemize}
+ \item Three regions of Drift Chambers (DC) for tracking of charged 
+    particles~\cite{DCref}.
+ \item Superconducting toroidal magnet which enables the tracking by bending 
+    the trajectories.
+ \item Cherenvkov Counters (CC) to separate electrons from negative 
+    pions~\cite{CCref}.
+ \item Scintillation Counters (SC) to identify hadrons via measuring their 
+    Time-Of-Flight (TOF)~\cite{TOFref}.
+ \item Forward Electromagnetic Calorimeter (EC) to detect showering particles 
+    (electrons and photons) and neutrons~\cite{ECref}.
+\end{itemize}
+
+\begin{figure}[tbp]
+\centering \includegraphics[scale=0.3]{fig/test_clas.png}
+\caption{Three dimensional representation of the primary CLAS setup represents 
+   the geometry and the relative position of each subsystem. From outside, the 
+electromagnetic calorimeter (green), time-of-flight system (red), Cherenkov 
+counters (purple), three drift chamber regions (blue) and the superconducting 
+torus coils (yellow).} 
 \label{fig:CLAS}
@@
 
-CLAS is composed of several subdetectors and two magnets.
-They are designed to track charged particles at momentum greater than 250 MeV/c.
-Figure~\ref{fig:CLAS} shows the basic setup of CLAS, ordered with respect to their radial distance from the center:
+In the basic setup of CLAS, the real photons are detected by the forward EC, 
+covering polar angles from 8$^{\circ}$ to 45$^{\circ}$. With a 6 GeV electron 
+beam, a large part of the DVCS photons are produced at polar angles below 
+15$^{\circ}$, where the acceptance of the EC is small. In the CLAS-E1DVCS 
+experiment (2005), CLAS was upgraded with the addition of an Inner Calorimeter 
+(IC). This calorimeter covers polar angles between 5$^{\circ}$ and 
+15$^{\circ}$. The IC is constructed from 424 lead-tungstate (PbWO$_{4}$) 
+crystals. Each crystal is 16 cm long (corresponding to 17 radiation lengths) 
+with a 1.33~$\times$~1.33 cm$^2$ front surface and a 1.6~$\times$~1.6 cm$^2$ 
+back surface. The energy resolution is around 3 to 4$\%$ for photon energies 
+between 2 GeV and 5 GeV and the angular resolution is between 3 to 5 mrad for 
+the same energy range \cite{Hyon-suk}.
 
-\begin{itemize}
-\item Three regions of Drift Chambers (DC) for tracking of charged particles~\cite{DCref}.
-\item Superconducting toroidal magnet which enables the tracking by bending the trajectories.
-\item Cherenvkov Counters (CC) to separate electrons from negative pions~\cite{CCref}.
-\item Scintillation Counters (SC) to identify hadrons via measuring their Time-Of-Flight (TOF)~\cite{TOFref}.
-\item Forward Electromagnetic Calorimeter (EC) to detect showering particles (electrons and photons) and neutrons~\cite{ECref}.
-\end{itemize}
+The developed RTPC has been used during a three months experimental run in 2009 
+with a longitudinally polarized electron beam of energy 6.064 GeV projected 
+onto a gaseous $^{4}$He target to measure asymmetries in Deep Virtual Compton 
+Scattering (DVCS)~\cite{proposal} and exclusive meson production. Moreover, a 
+5~T solenoid was placed around the RTPC-target system to shield the detectors 
+close to the beam line from Mollers electrons. The solenoid field plays also a 
+major rule in finding the momentum of the charged particles in the RTPC by 
+bending their tracks curvature.
 
-In addition to the normal CLAS setup, a forward electromagnetic calorimeter (the inner calorimeter) was installed to improve the photon detection acceptance.
-Moreover, a 5~T solenoid was placed around the target to shield the detectors close to the beam line -- mostly the inner calorimeter and the RTPC -- from Mollers electrons.
-The solenoid field is also used to calculate the momentum of the alpha particles from their curvature radius measured by the RTPC.
+This paper is organized in this way: section \ref{prev_tpc} presents an 
+overview of the TPCs history and previous usage, section \ref{sec_design} 
+details the physics considerations for the RTPC design and its internal 
+structure, while section \ref{sec_readout} points the properties of the 
+read-out system.  The calibration strategies for such detectors will be 
+discussed in section \ref{sec_calib}. Finally, the performance of the RTPC is 
+discussed in section \ref{sec_perf}.
 
-The first implementation of a RTPC in CLAS have been achieved for the BoNuS experiment~\cite{BONUS} in 200x.
-The success of this detector for the detection of slow protons motivated the development of this new RTPC.
-For the channel of interests of our experiments, the recoiled $^{4}He$ nuclei have momentum around (150 or 300 ???) MeV/c, the detection of these particles was the primary motivation for using such design.
+\section{TPCs overview}
+In the late 1970s, David R. Nygren presented the concept of the Time projection 
+Chambers (TPCs) as a new tool to track charged particles based on combining 
+electric and magnetic fields within a sensitive gas volume. The ionized 
+electrons are collected by a position-sensitive electron collection system.  
+Later in 1997, F.~Sauli introduced the Gas Electron Multiplier (GEM) as an 
+effective gas-gain element to improve the tracking efficiency of the TPCs 
+\ref{gem_sauli}.
 
-This paper is organized in this way: section \ref{sec_design} details the design and the internal structure of the RTPC, while section \ref{sec_readout} points the properties of the readout system.
-The calibration strategies for such detectors will be discussed in section \ref{sec_calib}.
-Finally, performances are discussed in section \ref{sec_perf}.
+The first implementation of a RTPC in CLAS have been achieved for the BoNuS 
+experiment~\cite{BONUS} in 200x. The success of this detector for the detection 
+of slow protons motivated the development of this new RTPC. For the channel of 
+interests of our experiments, the recoiled $^{4}He$ nuclei have momentum per 
+charge around 150 MeV/c, the detection of these particles was the primary 
+motivation for using such design.
 
-\section{Design} \label{sec_design}
-
-The RTPC is a 200~mm long with a 150~mm diameter time projection chamber.
-The ionized electrons are drifting outward perpendicularly to the beam direction.
-These electrons are then amplified by three layers of GEMs and detected on 4.45 by 5~mm pads.
-As for BoNuS, the RTPC has two detection parts but unlike BoNuS they are part of a single chamber.
-Each part has independent GEM amplification systems that cover around 80\% of the azimuthal angle.
-Under the effect of the electromagnetic field, the ionization electrons drift to the readout system on the external shell with a curved trajectory as can be seen in the figure~\ref{fig:RTPC_1_4}.
+\section{CLAS-EG6 RTPC design} \label{sec_design}
+The RTPC is a 200~mm long with a 150~mm diameter time projection chamber. The 
+ionized electrons are drifting outward perpendicularly to the beam direction.  
+These electrons are then amplified by three layers of GEMs and detected on 4.45 
+by 5~mm pads. As for BoNuS, the RTPC has two detection parts but unlike BoNuS 
+they are part of a single chamber. Each part has independent GEM amplification 
+systems that cover around 80\% of the azimuthal angle. Under the effect of the 
+electromagnetic field, the ionization electrons drift to the readout system on 
+the external shell with a curved trajectory as can be seen in the 
+figure~\ref{fig:RTPC_1_4}.
 
@@
 \includegraphics[scale=0.28]{fig/RTPC_1_all.png}
-\caption[]{\small\sf Schematic drawing of the RTPC taken on a plane perpendicular to the beam line, see text for description of the elements.} 
+\caption[]{\small\sf Schematic drawing of the RTPC taken on a plane 
+perpendicular to the beam line, see text for description of the elements.} 
 \label{fig:RTPC_1_4}
@@
 
-As seen in figure~\ref{fig:RTPC2}, the RTPC is composed from the beam axis to the exterior by:\\
+As seen in figure~\ref{fig:RTPC2}, the RTPC is composed from the beam axis to 
+the exterior by:\\
 \begin{itemize}
-\item The target, filled with 5~atm $^4$He, has a 3~mm radius with Kapton walls only 27$\mu$m thick.
-\item The first gas gap extends from 3 mm to 20 mm radial distance.
-It is filled with $^{4}He$ gas at 1~atm.
-During run, this region is swarmed by Moller electrons induced by the beam, such that filling this region with a light gas like $^{4}He$ minimizes secondary interactions.
-This region is surrounded by a 4 $\mu$m thick window made of aluminized Mylar and connected to ground.
-\item The gap region extends between 20~mm and 30~mm and is filled with a gas mixture of 80$\%$ Neon and 20$\%$ Dimethyl Ether (DME).
-This region is surrounded by a 4~$\mu$m thick window made of aluminized Mylar, which serves as the cathode.
-\item The drift region is filled with the Ne-DME gas mixture, it extends from the cathode to the first Gas Electron Multiplier(GEM), 60 mm away from the central axis.
-The electric field in this region is around 500~V/cm (???) and perpendicular to the beam.
-Field cages are installed at both ends of the detector in this region.
-Progressive voltage depending on radial position is applied on these to maintain a uniform electric field perpendicular to the beam line at the edges of the RTPC.
-\item The GEM system is composed of three GEMs located at radii, 60 mm, 63 mm and 66 mm, they amplify the electrons to make a measurable signal.
-\item The readout board has internal radius of 69~mm and collects the charges, preamplifiers are plugged directly on its outer side and are transmitting the signal to the data acquisition electronics.
+   \item The target, filled with 5~atm $^4$He, has a 3~mm radius with Kapton 
+      walls only 27$\mu$m thick.
+
+   \item The first gas gap extends from 3 mm to 20 mm radial distance. It is 
+   filled with $^{4}He$ gas at 1~atm. During run, this region is swarmed by 
+   Moller electrons induced by the beam, such that filling this region with a 
+   light gas like $^{4}He$ minimizes secondary interactions. This region is 
+   surrounded by a 4 $\mu$m thick window made of aluminized Mylar and connected 
+to ground.
+
+   \item The gap region extends between 20~mm and 30~mm and is filled with a 
+      gas mixture of 80$\%$ Neon and 20$\%$ Dimethyl Ether (DME).  This region 
+      is surrounded by a 4~$\mu$m thick window made of aluminized Mylar, which 
+      serves as the cathode.
+
+   \item The drift region is filled with the Ne-DME gas mixture, it extends 
+      from the cathode to the first Gas Electron Multiplier(GEM), 60 mm away 
+      from the central axis. The electric field in this region is around 
+      500~V/cm (???) and perpendicular to the beam. Field cages are installed 
+      at both ends of the detector in this region. Progressive voltage 
+      depending on radial position is applied on these to maintain a uniform 
+      electric field perpendicular to the beam line at the edges of the RTPC.
+
+   \item The GEM system is composed of three GEMs located at radii, 60 mm, 63 
+      mm and 66 mm, they amplify the electrons to make a measurable signal.
+
+   \item The readout board has internal radius of 69~mm and collects the 
+      charges, preamplifiers are plugged directly on its outer side and are 
+      transmitting the signal to the data acquisition electronics.
 \end{itemize}
@@
 \includegraphics[scale=0.70]{fig/GEM_photo.jpg}
-\caption[]{\small\sf A schematic layout of the GEMs system in one module of the RTPC.} 
+\caption[]{A schematic layout of the GEMs system in one module of the RTPC.} 
 \label{fig:GEMs}
@@
 
-The GEM amplification has been mainly chosen for this detector for their flexibility, allowing the curved amplification surface.
-Also GEM are known to create less sparks than in other gaseous detectors, which is a good thing for the detection of slow nuclei like $^4$He.
-GEMs are made from an insulator layer (here Kapton) sandwiched between two 5 $\mu$m copper layers.
-The mesh of each GEM layer is chemically etched with 50$\mu$m diameter holes in double-conical cross section shapes as can be seen in figure~\ref{fig:GEMs}.
-A potential difference of 400 V is applied between the two copper layers of each GEM creating a very strong electric field in the holes.
-Such strong fields lead to high ionization from initial electrons and therefore amplification of the signal.
-Also, a potential difference of 150 V is set between the GEMs to push the amplified electrons toward the readout pads.
-The gain of each GEM layer is of order 100.\\
+The GEM amplification has been mainly chosen for this detector for their 
+flexibility, allowing the curved amplification surface. Also GEM are known to 
+create less sparks than in other gaseous detectors, which is a good thing for 
+the detection of slow nuclei like $^4$He. GEMs are made from an insulator layer 
+(here Kapton) sandwiched between two 5 $\mu$m copper layers. The mesh of each 
+GEM layer is chemically etched with 50$\mu$m diameter holes in double-conical 
+cross section shapes as can be seen in figure~\ref{fig:GEMs}. A potential 
+difference of 400 V is applied between the two copper layers of each GEM 
+creating a very strong electric field in the holes. Such strong fields lead to 
+high ionization from initial electrons and therefore amplification of the 
+signal. Also, a potential difference of 150 V is set between the GEMs to push 
+the amplified electrons toward the readout pads. The gain of each GEM layer is 
+of order 100.\\
 
 \section{Readout System} \label{sec_readout}
-The RTPC electron collecting system has 3200 readout pads. These collection elements are located at the end of the amplification region, 69 mm from the central axis.
+The RTPC electron collecting system has 3200 readout pads. These collection 
+elements are located at the end of the amplification region, 69 mm from the 
+central axis.
+
 \begin{figure}[tb]
    \centering
-%\hspace{-1 cm}
    \includegraphics[scale=0.55]{fig/PADs.png}
-\caption[]{\small\sf A schematic representation of a part of the readout system. The shaded sixteen pads are a group of pads that are connected to the same pre-amplifier.} 
-\label{fig:PADs}
+   \caption[]{A schematic representation of a part of the readout system.  The 
+   shaded sixteen pads are a group of pads that are connected to the same 
+pre-amplifier.} \label{fig:PADs}
 \end{figure}
-Figure \ref{fig:PADs} shows a schematic drawing of the size and the alignment configuration of the pads.
-Each readout pad is 5 mm in length and 4.45 mm in width the shift between the rows allows to reduce aliasing.
-Each half of the RTPC has 40 rows and 40 columns of pads.
-The shaded region in the figure~\ref{fig:PADs} shows how pads are grouped to the 16 channels pre-amplifiers.
-The Time to Digital Converter (TDC) units are 114~ns and indicates the time taken by the electron to drift from the ionization point to the readout board.
-On the the other side, the charge information is measured in Analog-to-Digital-Converter (ADC) units without specific normalization.
+
+Figure \ref{fig:PADs} shows a schematic drawing of the size and the alignment 
+configuration of the pads. Each readout pad is 5 mm in length and 4.45 mm in 
+width the shift between the rows allows to reduce aliasing. Each half of the 
+RTPC has 40 rows and 40 columns of pads. The shaded region in the 
+figure~\ref{fig:PADs} shows how pads are grouped to the 16 channels 
+pre-amplifiers. The Time to Digital Converter (TDC) units are 114~ns and 
+indicates the time taken by the electron to drift from the ionization point to 
+the readout board. On the the other side, the charge information is measured in 
+Analog-to-Digital-Converter (ADC) units without specific normalization.
 
@@
 \section{Calibration} \label{sec_calib}
-Two quantities are recorded for each detected electron at the readout board, time (TDCs) and signal amplitude (ADCs) (/!\\ are those amplitude or charge preamps ???).
-The timing information provides trajectory determination resulting in momentum per unit charge measurement.
-Going from a collection of the TDCs to a momentum measurement requires good knowledge of the drift speed and paths followed by the electrons released in the gas.
-The recorded ADCs give the deposited energy per unit of length ($\small{\frac{dE}{dX}}$) which, together with the momentum calculated from the trajectory, enables particle identification.
+Two quantities are recorded for each detected electron at the readout board, 
+time (TDCs) and signal amplitude (ADCs) (/!\\ are those amplitude or charge 
+preamps ???). The timing information provides trajectory determination 
+resulting in momentum per unit charge measurement. Going from a collection of 
+the TDCs to a momentum measurement requires good knowledge of the drift speed 
+and paths followed by the electrons released in the gas. The recorded ADCs give 
+the deposited energy per unit of length ($\small{\frac{dE}{dX}}$) which, 
+together with the momentum calculated from the trajectory, enables particle 
+identification.
 
@@
 
-We can measure the drift speed using the tracks detected in the RTPC, in figure \ref{fig:RTPC_signals} we represent a typical $^{4}He$ track (in green).
-After it causes ionization in the drift region, the released electrons (in black) drift to the detection plane under the effect of the electric field.
-The electrons released close to the cathode take the most time to reach the readout pads while the geometrical symmetry insure they always travel the same distance.
-So by identifying the maximum TDC measured, we can infer the drift speed of the electrons in the RTPC.\\
+We can measure the drift speed using the tracks detected in the RTPC, in figure 
+\ref{fig:RTPC_signals} we represent a typical $^{4}He$ track (in green). After 
+it causes ionization in the drift region, the released electrons (in black) 
+drift to the detection plane under the effect of the electric field. The 
+electrons released close to the cathode take the most time to reach the readout 
+pads while the geometrical symmetry insure they always travel the same 
+distance. So by identifying the maximum TDC measured, we can infer the drift 
+speed of the electrons in the RTPC.\\
 
@@
 
-We first measure the drift speed along the 200 mm RTPC's length to take into account variations in the electric and magnetic field, some of which are known (see figure \ref{fig:B_MAP}) some might be due to slight shifts in the geometry.
-We verified this by looking at the TDC profile generated in the chamber by all our tracks (see figure \ref{fig:TDC_profile}).
-The time profile of registered hits clearly show the dropping edge expected from the geometrical considerations previously mentioned.
-We define a value named $TDC_{Max/2}$ at which the dropping edge passes half the maximum number of hits in the histogram, this value is inversely proportional to the drift speed.
-The result can be seen in figure \ref{fig:RunNumber_61551_TDCmax_Zslice} showing the dependence of drift speed with position along the beam line axis in the chamber.
+We first measure the drift speed along the 200 mm RTPC's length to take into 
+account variations in the electric and magnetic field, some of which are known 
+(see figure \ref{fig:B_MAP}) some might be due to slight shifts in the 
+geometry. We verified this by looking at the TDC profile generated in the 
+chamber by all our tracks (see figure \ref{fig:TDC_profile}). The time profile 
+of registered hits clearly show the dropping edge expected from the geometrical 
+considerations previously mentioned. We define a value named $TDC_{Max/2}$ at 
+which the dropping edge passes half the maximum number of hits in the 
+histogram, this value is inversely proportional to the drift speed. The result 
+can be seen in figure \ref{fig:RunNumber_61551_TDCmax_Zslice} showing the 
+dependence of drift speed with position along the beam line axis in the 
+chamber.
 
@@
    \includegraphics[scale=0.35]{fig/B_MAP.png}
-\caption[]{\small\sf Schematic draw in of the solenoid magnetic vectors inside the RTPC.
-In this draw, r is the radial distance from the target's axis and z is the longitudinal position along the RTPC with its center at zero.}
+   \caption[]{Schematic draw in of the solenoid magnetic vectors inside the 
+   RTPC. In this draw, r is the radial distance from the target's axis and z is 
+the longitudinal position along the RTPC with its center at zero.} 
 \label{fig:B_MAP}
@@
    \includegraphics[scale=0.40]{fig/TDC_profile.png}
-\caption[]{\small\sf Time profile of the collected hits in one experimental run. } 
+   \caption[]{Time profile of the collected hits in one experimental run.  } 
    \label{fig:TDC_profile}
@@
 \bibitem{CLASref}
-B.A. Mecking et al., "The CEBAF large acceptance spectrometer", Nucl. Inst. and Meth. A 503, 513 (2003).
+   B.A. Mecking et al., The CEBAF large acceptance spectrometer, Nucl. Inst. 
+   and Meth. A 503, 513 (2003).
 
 \bibitem{proposal}
-K.Hafidi et al., "Deeply virtual Comton scattering off 4He", Jlab proposal to PAC33 (2007).
+   K.Hafidi et al., Deeply virtual Comton scattering off $^{4}$He, Jlab 
+   proposal to PAC33 (2007).
+
 \bibitem{DCref}
-M.D. Mestayer et al., "The CLAS drift chamber System", Nucl. Inst. and Meth. A 449, 81 (2000)
+   M.D. Mestayer et al., The CLAS drift chamber System, Nucl. Inst.  and Meth.  
+   A 449, 81 (2000).
 
 \bibitem{CCref}
-G. Adams et al., "The CLAS Cerenkov detector", Nucl. Inst. and Meth. A 465, 414 (2001).
+   G. Adams et al., The CLAS Cerenkov detector", Nucl. Inst. and Meth. A 465, 
+   414 (2001).
 
-\bibitem{TOFref}E.S. Smith et al., "The time-of-flight system for CLAS", Nucl. Inst. and Meth. A 432, 265 (1999).
+\bibitem{TOFref}
+   E.S. Smith et al., The time-of-flight system for CLAS, Nucl.  Inst. and 
+   Meth. A 432, 265 (1999).
 
 \bibitem{ECref}
-M. Amarian et al., "The CLAS forward electromagnetic calorimeter", Nucl. Inst. and Meth. A 460, 239 (2001).
+   M. Amarian et al., The CLAS forward electromagnetic calorimeter, Nucl.  
+   Inst. and Meth. A 460, 239 (2001).
+
+\bibitem{Hyon-suk}
+   Hyon-Suk Jo, Etude de la Diffusion Compton Profond{\'e}ment Virtuelle Sur le 
+   Nucl{\'e}on avec le D{\'e}tecteur CLAS de Jefferson Lab: Mesure des Sections 
+   Efficaces polaris{\'e}es et non polaris{\'e}es, IPNO-Thesis, 2007.
+
+\bibitem{gem_sauli}
+   F. Sauli, GEM: A new concept for electron amplification in gas detectors, 
+   Nucl. Instr. and Meth. A 386, 531 (1997).
 
 \bibitem{BONUS}
-S. Tkachenko et al., "Measurement of the nearly free neutron structure function using spectator tagging in inelastic $^{2}H(e,e'p)X$ scattering with CLAS",	Phys. Rev. C 89, 045206 (2014).
+   S. Tkachenko et al., Measurement of the nearly free neutron structure 
+   function using spectator tagging in inelastic $^{2}H(e,e'p)X$ scattering 
+   with CLAS,	Phys. Rev. C 89, 045206 (2014).
 
 \bibitem{MAGBOLTZ}
-S.
-Biagi, "Monte Carlo simulation of electron drift and diffusion in counting gases under the influence of electric and magnetic fields", Nucl.
-Inst.
-and Meth.
-in Phy.
-Res.
-A, vol.
-421, pp.
-234-240, 1999.
+   S. Biagi, Monte Carlo simulation of electron drift and diffusion in counting 
+   gases under the influence of electric and magnetic fields, Nucl.  Inst. and 
+   Meth. in Phy. Res. A, vol. 421, pp. 234-240, 1999.
 

### 2016-09-19 coherent/HeliumCohDVCS.tex
update the NIM writing and cleaning the directory

@@
 \begin{abstract}
-We report the first exclusive measurement of deeply virtual Compton scatterring 
+We report the first exclusive measurement of deeply virtual Compton scattering 
 (DVCS) off a nuclei with the CLAS detector at the Jefferson laboratory. The 
 observed beam spin asymmetries are significantly larger than for proton, 
-confirming expectations from plane wave impulse approximation. We present an 
-extraction of the unique generalized parton distribution (GPD) of the spin-0 
-helium in a completely model independent way. This result demonstrate the 
-strength of the method and opens a new unique access into nuclei 3D structure 
-in term of quarks and gluons.
+confirming expectations from calculations using the plane wave impulse 
+approximation. We present an 
+extraction of the single generalized parton distribution (GPD) of the spin-0 
+helium-4 nuclei in a completely model independent way. This result demonstrate the 
+strength of the method and opens a new and unique access into the partonic structure 
+of nuclei.
 \end{abstract}
@@
 
-The generalized parton distribution (GPD) framework developped in the past two decades
-(Need a bunch of refs)~\cite{}
+The generalized parton distribution (GPD) framework developped in the past 
+two decades~\cite{}
 offers a unique access into hadron 3D structure through deeply virtual Compton
-scattering (DVCS), depicted in figure~\ref{fig:DVCS} and other exclusive processes. Many measurements on the proton
-at several energies have now be reported and have demonstrated the solidity of the
-method~\cite{}. %To enhance a little -> CFF
+scattering (DVCS), depicted in figure~\ref{fig:DVCS}, and other exclusive 
+processes. Many measurements on the proton
+at several energies have now be reported~\cite{} and phenomenological work
+have demonstrated the solidity of the method to extract the tomography of the
+nucleon from these data~\cite{}.
 
-Insert FIGURE DVCS nuclei
-%\label{fig:DVCS}
 \begin{figure}[htbp]
-\caption{\label{fig:DVCS} Coherent DVCS}
+\caption{\label{fig:DVCS} Diagram for the coherent DVCS in the plane wave approximation.}
 \includegraphics[width=8.6cm]{DVCS.png}
@@
 The HERMES collaboration has measured nuclear DVCS~\cite{} without the 
-possibility of separating the coherent and incoherent channels leading
+detection of the recoils separating the coherent and incoherent channels 
+based on the measurement of the transfered 4-momentum $t$, leading
 to controversy in the interpretation of their results~\cite{}. We report
-here our measurement of coherent DVCS off helium-4 at the Jefferson labortory
+here our exclusive measurement of coherent DVCS off helium-4 at the Jefferson labortory
 (JLab), while our results for the incoherent channel will be presented in
-another paper~\cite{}. This experimental facility delivers a nearly 100\% duty factor, 6~GeV 
-electron linear accelerator into three experimental halls. Our experiment
-ran for 3 months in 2009 using the CEBAF Large Acceptance Spectrometer (CLAS).
-This detector is covering about 2$\pi$ and is composed of drift chambers, Cherenkov counters, scintillator 
-counters and an electro-magnetic calorimeter. It allows to detect accurately
-electrons and provides a trigger for the experiment. It is complemented for DVCS experiments with
-an inner calorimeter to detect the photons emitted at low angle and a solenoid
-to keep the Moller electrons produced along the beam line to get into our detectors.
+another paper. JLab delivers a nearly 100\% duty factor, 6~GeV linearly 
+polarized electrons into three experimental halls. Our experiment ran for 3 
+months in 2009 using the CEBAF Large Acceptance Spectrometer (CLAS) in 
+Hall-B. This detector is large acceptance covering nearly 2$\pi$ and is 
+composed of drift chambers, Cherenkov counters, scintillator counters and 
+an electro-magnetic calorimeter. It allows to detect accurately electrons 
+which provide the trigger for the experiment. It is complemented for DVCS 
+experiments with an inner electro-magnetic calorimeter made of PbWO crystals 
+to detect the photons emitted at low angle and with a solenoid to keep the 
+Moller electrons produced along the beam line to get into our detectors.
 
-In order to insure the coherence of the process, we detect all the products
-of the reaction. The electron is detected by the CLAS, using the drift chamber 
-to reconstruct its trajectory and the combination of the Cherenkov counters
-and electromagnetic calorimeter to
-
-we built a small and light 
-radial time projection chamber (RTPC) depicted in figure~\ref{fig:rtpc} to 
-detect the recoiling helium nuclei. this detector is placed directly ouside of 
-our gaseous target filled with 6~atm helium. 
-% to complete
-
-\begin{figure}[htbp]
-\caption{\label{fig:rtpc} RTPC description}
-\includegraphics[width=8cm]{RTPC.png}
-\end{figure}
+In order to ensure the coherence of the process, we also detect the recoiling 
+helium-4 nuclei. We built a small and light radial time projection chamber 
+(RTPC) to detect recoiling helium nuclei down to energies of few MeVs. The 
+chamber, shown in figure~\ref{fig:rtpc}, is surrounding the gaseous target 
+filled with 6~atm helium-4 and is 20 cm long with a 3 cm radial drift 
+length. The detector was specifically calibrated for helium-4 nuclei using 
+elastic scattering produced with a 1.2~GeV electron beam.
+To ensure that the process is exclusive, we apply cuts on 
+several kinematic variables (figure~\ref{fig:exclu}) such as missing energy,
+mass and momentum. The cuts are chosen to represent consistently 3 half width 
+at half maximum in order to avoid any bias in the selection.
 
@@
 
-Detection, PID des particules.
+\begin{figure}[tb!]
+\caption{\label{fig:rtpc} RTPC description}
+\includegraphics[width=7.4cm]{RTPC.png}
+\end{figure}
 
-\begin{figure*}[htbp]
+\begin{figure*}[t!]
 \caption{\label{fig:exclu} Exclusivity cuts}
-\includegraphics[width=17.2cm]{all_coh_exc_cuts.png}
+\includegraphics[width=16.0cm]{all_coh_exc_cuts.png}
 \end{figure*}
@@
 We identified several background contributions to the DVCS process, in 
-particular accidental events and exclusive deeply virtual $\pi^0$ production (DV$\pi^0$P). The accidental
-events happen when an helium nuclei is mistakenly associated with our event, this 
-possibility is suppressed by the limited phase space allowed but enhanced by the
-low time resolution of the RTPC (~200 ns). We evaluated this contribution by
+particular accidental events and exclusive deeply virtual 
+$\pi^0$ production (DV$\pi^0$P). The accidental
+events where the different particles come from different events are 
+suppressed by the limited phase space allowed by the exclusivity cuts. We 
+estimate the accidental events to represent 4.1\% of our sample. This relatively 
+large number is due to the small cross section of the DVCS. We evaluated this contribution by
 selecting events passing all our cuts but with particles originating from 
-different verteces. With this method, we found this background to represent 
-4.1\%. The DV$\pi^0$P events can easily be mistaken
-with DVCS events when one of the two photons of $\pi^0$ decay is produced at
-low energy in the laboratory frame. In order to estimate the importance of
-this background, we developped an event generator DV$\pi^0$P 
-that we calibrated to match our experimental yields. We used this generator together 
-with a GEANT3~\cite{} simulation of our detection system to estimate the ratio 
-of acceptance between measured DV$\pi^0$P and DV$\pi^0$P that would pass our 
+different verteces.
+
+Another important source of background is the deeply virtual 
+$\pi^0$ production (DV$\pi^0$P), which can easily be mistaken
+with DVCS when one of the two photons of the $\pi^0$ decay is produced at
+low energy in the laboratory frame. To estimate the importance of
+this background, we developped an event generator 
+that we calibrated to match our measured experimental yield of exclusive 
+$pi^0$. We used this generator together 
+with a GEANT3 simulation of our detection system to estimate the ratio 
+of acceptance between DV$\pi^0$P where the two photons are detected and those
+where only one photon is detected and would pass our 
 DVCS selection cuts. This ratio obtained from simulation is then multiplied by 
-the measured yield of DV$\pi^0$P events, indicating a contamination of XX to XX\%. 
-%(We NEED a figure of that in the note!!!)
+the measured yield of DV$\pi^0$P events, indicating a contamination of 2 to 4\%.
 
@@
 \end{figure*}
-
-% This is mainly to compare to existing models
-Generalized ratios (figure~\ref{fig:GenR})
-
-\begin{figure}[htbp]
-\caption{\label{fig:GenR} Generalized ratio}
-\includegraphics[width=7.5cm]{coh_emc_Q2.png}
-\includegraphics[width=7.5cm]{coh_emc_t.png}
-\includegraphics[width=7.5cm]{coh_emc_xB.png}
-\end{figure}
 

### 2016-09-19 eg6-letters/analysis-note-v2/data_analysis.tex
merge files

--- 2016-09-07 analysis-note-v2/data_analysis.tex
@@
 \chapter{Particles reconstruction and simulation}
-~~~~The final state of a coherent (incoherent) DVCS event consists of three 
+The final state of a coherent (incoherent) DVCS event consists of three 
 particles: an electron, a $^4$He (a proton), and a real photon. To identify the 
@@
 further filtered by imposing the energy-momentum conservation laws, as will be 
-presented in the following chapter.\\
+presented in the following chapter.
 
@@
 technique, we need to identify the experimental $\pi^0$s that come in the 
-coherent and the incoherent $\pi^0$-electroproduction channels.\\
+coherent and the incoherent $\pi^0$-electroproduction channels.
 
@@
 \subsection{Electron identification} \label{Electron_identification}
-~~~~The electron detection triggers the data acquisition system to record data 
+The electron detection triggers the data acquisition system to record data 
 from all the sub-detectors of CLAS. In this analysis, a particle which passes 
@@
 
-\paragraph{Fiducial cuts}
-~\\
-~\\
-~~~~Some regions of CLAS have to be excluded from the analysis to ensure an accurate detection of the different particles.
+\paragraph{Fiducial cuts} ~\\
+Some regions of CLAS have to be excluded from the analysis to ensure an accurate detection of the different particles.
 For instance, an electron that hits the edge of the EC will have only part of its electromagnetic shower contained within the detector.
@@
 Osipenko {\it et al.} have developed a coordinate system to represent the CC hits with respect to the center of each sector in CLAS.
-In this frame, the CCs mirror edges can be defined as:\\
+In this frame, the CCs mirror edges can be defined as:
 \begin{multline}  
@@
 
-\paragraph{EC energy cuts}
-~\\
-~\\
-~~~~The Minimum Ionizing particles (MIPs), such as pions, deposit constant 
+\paragraph{EC energy cuts} ~\\
+The Minimum Ionizing particles (MIPs), such as pions, deposit constant 
 amounts of energy per distance while traversing the EC.  In contrast, the 
@@
 
-\paragraph{CC cut}
-~\\
-~\\
-~~~~The Cherenkov counters have been designed to separate electrons from pions below 2.5 GeV/c momentum.
+\paragraph{CC cut} ~\\
+The Cherenkov counters have been designed to separate electrons from pions below 2.5 GeV/c momentum.
 In this region, the pions are not supposed to produce photoelectrons.
@@
 Figure \ref{fig:Nphe_cut} shows the distributions of the number of photoelectrons ($nphe$) produced by the negative particles for three different stages of the electron selection.
-\\
 
@@
 \subsection{Proton identification}
-~~~~Similarly to the electrons, the protons are affected by the geometry and the efficy of the different sub-detectors of CLAS. The following conditions are applied to select the good protons.
+Similarly to the electrons, the protons are affected by the geometry and the efficy of the different sub-detectors of CLAS. The following conditions are applied to select the good protons.
 \begin{itemize}
@@
 \end{itemize}
-~~~~Finally, figure \ref{fig:prot_Theta_Phi} shows the azimuthal angle as a function of the polar angle distribution for the identified protons after all the selection cuts.
+Finally, figure \ref{fig:prot_Theta_Phi} shows the azimuthal angle as a function of the polar angle distribution for the identified protons after all the selection cuts.
 One notices that the population of the protons is different from one sector to another, which comes from the dead regions in some sectors.
@@
 \subsection{Photon identification}
-~~~~CLAS is equipped with two calorimeters that can detect photons: the IC, covering polar angles from 4$^\circ$ to 14$^\circ$, and the EC, covering polar angles from 8$^\circ$ to 45$^\circ$.
+CLAS is equipped with two calorimeters that can detect photons: the IC, covering polar angles from 4$^\circ$ to 14$^\circ$, and the EC, covering polar angles from 8$^\circ$ to 45$^\circ$.
 Like for the other particles, in addition to the coincidence with one good electron, we require a set of criteria to ensure the quality of the detected photons.
@@
 \subsection{Helium-4 identification}
-~~~~Details on the RTPC's structure and the definition of the different 
+Details on the RTPC's structure and the definition of the different 
 variables were given in chapter 2, section 2. In the following, we show the 
@@
 \subsection{$\pi^{0}$ identification}
-~~~~In this analysis, we identify the $\pi^{0}$s with the goal of DVCS background subtraction as will be addressed in section \ref{Background_subtraction}.
+In this analysis, we identify the $\pi^{0}$s with the goal of DVCS background subtraction as will be addressed in section \ref{Background_subtraction}.
 The $\pi^{0}$ identification is based on its two real photons decay mode ($\pi^{0} \rightarrow \gamma \gamma$), with a branching ratio around 98.8$\%$.
@@
 \label{fig:pi0_selection}
-\end{figure}\\
+\end{figure}
 
@@
 \section{Simulation}
-~~~~The Monte-Carlo simulation is used in this analysis for two goals: understanding the behaviour of the particles of interest in the detectors, and computing the acceptance for the DVCS background subtraction.
+The Monte-Carlo simulation is used in this analysis for two goals: understanding the behaviour of the particles of interest in the detectors, and computing the acceptance for the DVCS background subtraction.
 The key stages of the simulation are summarized in figure \ref{fig:simulation_steps}: Monte-Carlo generated events pass in a GEANT3 simulation (GSIM) for the CLAS detector, then are processed with a package called GPP to add resolution and efficiency effects, and finally are reconstructed by a package named RECSIS, from which we obtain the physical quantities of each particle, like it is done for real data.
@@
 \subsection{Event generator} \label{Event_generator}
-~~~~Events are generated in the measured ranges of $Q^{2}$, $x_{B}$, $t$, and 
+Events are generated in the measured ranges of $Q^{2}$, $x_{B}$, $t$, and 
 $\phi$ following a parametrization of the cross section which roughly 
@@
 
-~~~~Table \ref{Table:event_generator_values} shows the values of the parameters used for the cross section parametrization of the four channels of interest: $e^{4}He\gamma$, $e^{4}He\pi^{0}$, $ep\gamma$, and $ep\pi^{0}$.
+Table \ref{Table:event_generator_values} shows the values of the parameters used for the cross section parametrization of the four channels of interest: $e^{4}He\gamma$, $e^{4}He\pi^{0}$, $ep\gamma$, and $ep\pi^{0}$.
 
@@
 
-~~~~Regarding the protons in $ep\gamma$ and $ep\pi^{0}$ channels, we apply the 
+Regarding the protons in $ep\gamma$ and $ep\pi^{0}$ channels, we apply the 
 Fermi motion on the initial protons based on the parametrization of C. Ciofi 
@@
 \subsection{GSIM}
-~~~~GSIM is a GEANT3-based simulation of the CLAS detector, developed by the CLAS collaboration \cite{GSIM}.
+GSIM is a GEANT3-based simulation of the CLAS detector, developed by the CLAS collaboration \cite{GSIM}.
 This simulation takes into account all the experimental environment, such as the target's position, materials, and geometry, and also the various sub-detectors' materials and geometries, to reproduce the behaviour of particles traversing the detector.
@@
 \subsection{GPP}
-~~~~For the purpose of making the simulation more realistic, the output of GSIM is fed to the GSIM Post-Processing (GPP) package.
+For the purpose of making the simulation more realistic, the output of GSIM is fed to the GSIM Post-Processing (GPP) package.
 This package applies resolution effects on the different measured quantities, and also reads efficiency maps to match the simulation to the real experiment.
@@
 
-\paragraph{SC time smearing}
-~\\
-~\\
-~~~~The GPP takes a single factor to smear the time in a Gaussian form.
-Figure \ref{fig:SC_smearing_factors} shows an illustration of the time smearing effects, in which $\Delta \beta$ for the protons \\($\Delta \beta~=~\beta_{measured}~-~\beta_{calculated}$~) is compared for data and simulation.
+\paragraph{SC time smearing} ~\\
+The GPP takes a single factor to smear the time in a Gaussian form.
+Figure \ref{fig:SC_smearing_factors} shows an illustration of the time smearing effects, in which $\Delta \beta$ for the protons ($\Delta\beta~=~\beta_{measured}-\beta_{calculated}$) is compared for data and simulation.
 The chosen SC smearing factor is 2.1.
 
-\paragraph{DCs position smearing}
-~\\
-~\\
-~~~~The GPP uses three factors to smear the positions of the hits in the DCs, in a Gaussian form.
+\paragraph{DCs position smearing} ~\\
+The GPP uses three factors to smear the positions of the hits in the DCs, in a Gaussian form.
 These smearing factors are extracted from comparing simulation to data in terms of the Time-Based Tracking (TBT) residual distributions, i.e.
@@
 
-\paragraph{IC energy smearing}
-~\\
-~\\
-~~~~An energy smearing for the IC photons is also needed.
+\paragraph{IC energy smearing} ~\\
+An energy smearing for the IC photons is also needed.
 The GPP software uses three factors to perform this smearing: $ic\_a$, $ic\_b$, and $ic\_c$, where $ic\_a$ accounts for the smearing of the width of the noise around zero using a Gaussian, while $ic\_b$ and $ic\_c$ are the smearing factors for the ADC values, using Gaussians as well.
@@
 The associated experimental distribution can be seen on the top left plot of figure \ref{fig:pi0_selection}.
-One notices that the smeared width of the simulated distribution matches the measured experimental one.\\
+One notices that the smeared width of the simulated distribution matches the measured experimental one.
 
@@
 
-~~~~RECSIS is the reconstruction package of CLAS which is used for both data 
+RECSIS is the reconstruction package of CLAS which is used for both data 
 and simulation. The detector responses, in terms of ADCs and TDCs, are 
@@
 \subsection{RTPC fastmc}
-~~~~All the sub-detectors of CLAS are implemented in the GSIM GEANT3 simulation, 
+All the sub-detectors of CLAS are implemented in the GSIM GEANT3 simulation, 
 however the RTPC is only there as dead material. As it is a more recent detector
@@
 \section{Kinematic Corrections}
-~~~~~The simulation enables us to extract kinematic corrections for the different particles, by comparing the reconstructed physical quantities from the simulation to the initially generated ones.
+The simulation enables us to extract kinematic corrections for the different particles, by comparing the reconstructed physical quantities from the simulation to the initially generated ones.
 In general, the reconstructed azimuthal angles of all the particles are consistent with the generated ones, while the reconstructed polar angles and momenta show some deviations.
@@
 \subsection{Electrons}
-~~~~The reconstructed kinematics of the simulated electrons are roughly consistent with the generated quantities, as can be seen in figure \ref{fig:electron_corrections}.
+The reconstructed kinematics of the simulated electrons are roughly consistent with the generated quantities, as can be seen in figure \ref{fig:electron_corrections}.
 Nevertheless, we extracted and applied corrections on the electrons to achieve a higher precision.
@@
 \subsection{Protons}
-~~~~The same procedures for the extraction of the kinematic corrections of the electrons have been carried out for the protons.
+The same procedures for the extraction of the kinematic corrections of the electrons have been carried out for the protons.
 The results can be seen in figure \ref{fig:proton_corrections}.
@@
 \subsection{IC photons in simulation} 
-~~~~The simulated IC photons shows non-negligible polar angle and energy deviations from the expected kinematics.
+The simulated IC photons shows non-negligible polar angle and energy deviations from the expected kinematics.
 This can be seen in figure \ref{fig:simulated_ic_corrections}.
 These deviations are almost systematic shifts, in which the polar angle deviation might be coming from badly defined geometrical values within GSIM.
-For these photons, we followed the same techniques of comparing the reconstructed quantities to the generated ones in order to extract the correction functions.\\
+For these photons, we followed the same techniques of comparing the reconstructed quantities to the generated ones in order to extract the correction functions.
 
@@
 
-\subsection{IC photons in real data} ~~~~For the experimental IC photons, we 
+\subsection{IC photons in real data} 
+For the experimental IC photons, we 
 used the reconstructed invariant mass of the $\pi^{0}$ in the ICIC topology to 
@@
 Figure \ref{fig:ic_alpha_beta_fitting} shows the extracted slope ($\alpha$) and offset ($\beta$), from the linear fits of the mass versus the energy of $\pi^{0}$, as a function of run number.
-One notices a non-negligible variation over the experimental running period due to changes in the experimental conditions, such as changes in trigger requirements and beam position.\\
+One notices a non-negligible variation over the experimental running period due to changes in the experimental conditions, such as changes in trigger requirements and beam position.
 
@@
 which takes as input the measured uncorrected photon energy ($E^{\gamma}_{uncorr}$), and the $\alpha$ and $\beta$ parameters, which depend on the run number.
-It then returns the corrected energy ($E^{\gamma}_{corr}$).\\
+It then returns the corrected energy ($E^{\gamma}_{corr}$).
 
 \subsubsection{Position correction}
-~~~~Cluster position is reconstructed as a weighted average of its hits' positions.
+Cluster position is reconstructed as a weighted average of its hits' positions.
 Those hit positions are taken as the center of the front face of their corresponding crystal.

### 2016-09-19 eg6-letters/eg6-letters/NIM/author_list.tex
merge files

\affiliation{Argonne National Laboratory, Argonne IL 60439, USA}
\affiliation{Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France}
\affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
%

\author{R.~Dupr\'e}   \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France}
\author{N.~Baltzell}  \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
\author{K.~Hafidi}    \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}
\author{M.~Hattawy}   \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France}
\author{S.~Stepanyan} \affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
%\author{} \affiliation{}
%

\collaboration{The JLab-CLAS Collaboration} 
%
\vskip 0.25cm

### 2016-09-19 eg6-letters/eg6-letters/NIM/fig/dc_mkpage.pl

@@ -1,0 +1,215 @@
+#!/usr/local/bin/perl
+
+
+
+#
+# This prints an HTML document to stdout with information
+# contained in DC_DOCA.map about the CLAS drift chamber 
+# calibration for the given run
+#
+#
+
+if(@ARGV!=1){&PrintUsage;}
+
+
+#-----------------------------------------------------------------#
+#----------------------- Start of Main ---------------------------#
+#-----------------------------------------------------------------#
+
+#
+# Get comments out of map
+#
+
+$run=$ARGV[0];
+$CLAS_PARMS=`printenv CLAS_PARMS`;
+chop $CLAS_PARMS;
+
+#
+#
+# Find run period
+#
+print STDERR "Finding run period for $run...\n";
+@runfile=`find /mss/clas -maxdepth 3 -name "*_*$run.A00"`;
+if(@runfile<1){
+	print STDERR "\tUnable to find file for run $run!\n";
+	$runperiod="unknown";
+}else{
+	$runfile[0] =~ /clas\//;
+	$' =~ /\//;
+	$runperiod=$`;
+}
+
+print STDERR "\tRun $run is in run period $runperiod\n";
+
+if($runperiod =~ /^e1/){
+	$fcolor="#0000FF";
+}elsif ($runperiod =~ /^eg1/){
+	$fcolor="#FF0000";
+}elsif ($runperiod =~ /^g1/){
+	$fcolor="#00FF00";
+}elsif ($runperiod =~ /^g6/){
+	$fcolor="#A07000";
+}elsif ($runperiod =~ /^e2/){
+	$fcolor="#FFA500";
+}else{
+	$fcolor="#000000";
+}
+
+#
+#Print HTML header
+#
+#
+print "\n
+<title>DC calibration run $run</title>
+<body bgcolor=\"#FFFFFF\">
+<h1><center>DC calibration run $run</center></h1>
+<hr>
+
+<center><h2>
+Run Period : <font color=\"$fcolor\">$runperiod</font>
+</h2></center>
+
+<hr>
+This page was generated from values stored in the \"comment\"
+items in the Map (DC_DOCA.map).<br>
+<br>
+The comment date, user, computer name, and host computer values
+are generally stored by the program that wrote the comment. The
+program <A href=\"../dc_tool/index.html\">dc_tool</A> can be used to view,
+add or delete comments for a given run number. Recent versions
+of <A href=\"../dc_calib_check/index.html\">dc_calib_check</A> automatically
[…]

### 2016-09-19 eg6-letters/eg6-letters/NIM/fig/dc_mkpage.pl
clean the directory

@@ -1,215 +1,0 @@
-#!/usr/local/bin/perl
-
-
-
-#
-# This prints an HTML document to stdout with information
-# contained in DC_DOCA.map about the CLAS drift chamber 
-# calibration for the given run
-#
-#
-
-if(@ARGV!=1){&PrintUsage;}
-
-
-#-----------------------------------------------------------------#
-#----------------------- Start of Main ---------------------------#
-#-----------------------------------------------------------------#
-
-#
-# Get comments out of map
-#
-
-$run=$ARGV[0];
-$CLAS_PARMS=`printenv CLAS_PARMS`;
-chop $CLAS_PARMS;
-
-#
-#
-# Find run period
-#
-print STDERR "Finding run period for $run...\n";
-@runfile=`find /mss/clas -maxdepth 3 -name "*_*$run.A00"`;
-if(@runfile<1){
-	print STDERR "\tUnable to find file for run $run!\n";
-	$runperiod="unknown";
-}else{
-	$runfile[0] =~ /clas\//;
-	$' =~ /\//;
-	$runperiod=$`;
-}
-
-print STDERR "\tRun $run is in run period $runperiod\n";
-
-if($runperiod =~ /^e1/){
-	$fcolor="#0000FF";
-}elsif ($runperiod =~ /^eg1/){
-	$fcolor="#FF0000";
-}elsif ($runperiod =~ /^g1/){
-	$fcolor="#00FF00";
-}elsif ($runperiod =~ /^g6/){
-	$fcolor="#A07000";
-}elsif ($runperiod =~ /^e2/){
-	$fcolor="#FFA500";
-}else{
-	$fcolor="#000000";
-}
-
-#
-#Print HTML header
-#
-#
-print "\n
-<title>DC calibration run $run</title>
-<body bgcolor=\"#FFFFFF\">
-<h1><center>DC calibration run $run</center></h1>
-<hr>
-
-<center><h2>
-Run Period : <font color=\"$fcolor\">$runperiod</font>
-</h2></center>
-
-<hr>
-This page was generated from values stored in the \"comment\"
-items in the Map (DC_DOCA.map).<br>
-<br>
-The comment date, user, computer name, and host computer values
-are generally stored by the program that wrote the comment. The
-program <A href=\"../dc_tool/index.html\">dc_tool</A> can be used to view,
-add or delete comments for a given run number. Recent versions
-of <A href=\"../dc_calib_check/index.html\">dc_calib_check</A> automatically
[…]

### 2016-09-27 2nd_round_comments/DVCS-CAN-Meeting-Comments.tex
updating the plots for the second round comments

@@
        \ref{fig:2d_delta_phi_MM2_InCoh} before and after the exclusivity cuts.  
-    No clear dependence is observed.}  \begin{figure}[!h]
+    No clear dependence is observed.} 
+    \begin{figure}[!h]
     \includegraphics[height=5.6cm]{fig/delta_phi_epgamma_M2_Mis.png}
@@
   while a slight correlation was observed between the $ep\gamma$ MM2 and $epX$ 
-  MM2.} \textcolor{red}{Do we have to apply tighter cuts in the incoherent 
-  case?.}
+  MM2.}
 
@@
   \begin{figure}[tbp]
-    \includegraphics[height=14.6cm]{fig/ALU-proton-fits.png}
-    \caption{ Fitting e1dvcs1 free proton beam-spin asymmetries. The dashed 
-    curves are fits to the data in the form of 
- $p_{0}*(t-t_{min})*e^{p_{1}*\sqrt{t}}$, while the solid curves are from 
- calculations based on fitting the parameters $p_{0}$ and $p_{1}$.}
+    \includegraphics[height=14.6cm]{fig/ALU-proton-fits.pdf}
+    \caption{Black circles are the free proton beam-spin asymmetries at $\phi = 
+    90   ^{\circ}$ as a function of $-t$ in different ($x_B, Q^2$) bins as 
+    measured at CLAS-E1DVCS experiment. The solid red curves are fits to the 
+    free proton asymmetries in the form 
+    $a_{0}*(\sqrt{t}-a_{1})*e^{a_{2}*\sqrt{t} - a_{3}}$. The dashed curves are 
+    calculations using the fitted $a_{i}$'s parameters as
+ a function of $x_B$. Blue points are the interpolated points corresponding for 
+ the incoherent points presented
+ in this analysis. The red points stand for the extrapolated free proton
+ asymmetries at the measured coherent kinematics.}
     \label{fig:free-proton-alu-fits}
@@
     \includegraphics[height=6.6cm]{fig/BSA_ratio_coh_Q2.pdf}
-    \includegraphics[height=6.6cm]{fig/BSA_ratio_coh_x.pdf}
+    \includegraphics[height=6.6cm]{fig/BSA_ratio_coh_xB.pdf}
     \centering
@@
     \includegraphics[height=6.6cm]{fig/BSA_ratio_incoh_Q2.pdf}
-    \includegraphics[height=6.6cm]{fig/BSA_ratio_incoh_x.pdf}
+    \includegraphics[height=6.6cm]{fig/BSA_ratio_incoh_xB.pdf}
     \centering

### 2016-10-12 analysis-note-v2/analysis-2.tex
created a directory for the final answers

@@
 
-In the previous chapter, the events were filtered to select the ones which have one and only one good electron, and other good particles in coincidence with the electron.
-This chapter explains the procedure we used to extract the beam-spin asymmetry observable following this order: clean the DVCS data sample by choosing good run list, ensure the exclusivity of the selected events by imposing the conservation laws, subtract the background by combining data with simulation, and binning the identified DVCS events.
-This chapter contains also an estimation of the systematic uncertainty contribution from each source on the measured beam-spin asymmetry.
+In the previous chapter, the events were filtered to select the ones which have 
+one and only one good electron, and other good particles in coincidence with 
+the electron. This chapter explains the procedure we used to extract the 
+beam-spin asymmetry observable following this order: clean the DVCS data sample 
+by choosing good run list, ensure the exclusivity of the selected events by 
+imposing the conservation laws, subtract the background by combining data with 
+simulation, and binning the identified DVCS events. This chapter contains also 
+an estimation of the systematic uncertainty contribution from each source on 
+the measured beam-spin asymmetry.
 
-In the following, the selection procedures of the coherent DVCS events is detailed and generalized to the cases of incoherent DVCS, the coherent $\pi^{0}$, and the incoherent $\pi^{0}$ channels.
+In the following, the selection procedures of the coherent DVCS events is 
+detailed and generalized to the cases of incoherent DVCS, the coherent 
+$\pi^{0}$, and the incoherent $\pi^{0}$ channels.
 
@@
 \subsection{Good run list}
-In principle, with constant beam luminosity, target density and pressure, the event rate has to be constant over the experimental time.
-Due to the changes in the experimental conditions, such as changing a trigger in a detector, a slight shift in the beam position or a system failure somewhere, this rate changes.
-We minimize the effects of these changes on the reconstructed events by selecting the good runs.
-To this aim, we monitor the ratio of the number of the good tracks reconstructed in the RTPC to number of the detected good electrons in CLAS (<tpc/e>) as a function of run number.
-Furthermore, we also look at this ratio in the six sectors of CLAS, as they are independent of each other and their performances might be different.
+In principle, with constant beam luminosity, target density and pressure, the 
+event rate has to be constant over the experimental time. Due to the changes in 
+the experimental conditions, such as changing a trigger in a detector, a slight 
+shift in the beam position or a system failure somewhere, this rate changes. We 
+minimize the effects of these changes on the reconstructed events by selecting 
+the good runs. To this aim, we monitor the ratio of the number of the good 
+tracks reconstructed in the RTPC to number of the detected good electrons in 
+CLAS (<tpc/e>) as a function of run number. Furthermore, we also look at this 
+ratio in the six sectors of CLAS, as they are independent of each other and 
+their performances might be different.
 
@@
 \begin{itemize}
-\item The integrated $<tpc/e>$ rate over the six sectors of CLAS is consistent with the neighboring runs.
+\item The integrated $<tpc/e>$ rate over the six sectors of CLAS is consistent 
+   with the neighboring runs.
 \item The six sectors show small fluctuations for each run. 
@@
 \end{table}
+
+In addition to evaluating the systematic uncertainties on $A_{LU}$ at $\phi = 
+90^{\circ}$, we performed bin by bin, in $\phi$, extraction of these 
+uncertainties. For instance, regarding the bin extraction from the source 'data 
+binning' listed in table \ref{Table:systematic_uncertainties}, the uncertainty 
+is calculated as the difference between the two reconstructed asymmetries.  
+Similar procedures have been carried out for the other studies, and finally all 
+the contributions were added quadratically. These systematic uncertainties will 
+be shown with the final asymmetry results in the following chapter.

### 2016-10-12 final_checks/DVCS-CAN-Meeting-Comments.tex
created a directory for the final answers

\section*{\centering{Answers to the final questions sent on October 7th, 2016}}

"Dear Mohammad,

After consultation of Raphael (who contacted you), the CAN review committee 
would like to request that the study of varying cut in the missing energy 
eHe4gX be repeated with a proper, bin dependent, pi0 subtraction. We understand 
that this may take several days, but feel it is a necessary step to raise any 
doubt about the stability of the result. Optionally, if time allows, add a 
fourth cut which would only get rid of the tails: [-0.45, 0.50].

I also discussed with Raphael the necessity to explain in the section on 
Systematic uncertainties how the corresponding numbers in the numerical tables 
are generated. So far, the discussion is exclusively on the fitted ALU(90°), 
while the numbers in the Tables are bin-dependent.

Thank you and best regards,

Michel."

\begin{enumerate}
   \item \textcolor{blue}{Regarding the stability of the coherent $A_{LU}$ with 
      respect to the missing energy cut. I first remind you about the previous 
   study from the first round comments and the results we got. Then, I will 
present the new results after the CAN review committee suggestions. }

\begin{enumerate}
   \item The first round comment, where the background subtraction have been 
      performed based on the 4D background subtractions without binning in the 
      missing energy distribution: \\
      " 40) Fig.  4.2: I'm bothered by the wide distribution in Emiss (top 
      middle), and don't understand why you use such wide cuts.  Surely, 
      anything above Emiss = 0.4 must have additional particles in it, and even 
      if not, why not cut this tail?  Note that the same tail is absent for the 
      p (Fig. 4.6) where you use indeed a tighter cut, although you don't even 
      account for the proton's initial momentum.\\
   \textcolor{blue}{ We applied 3$\sigma$ based on the comparison between data 
      and simulation, see figure 4.4 in the note. In the following, figure 
      \ref{fig:coherent_ME_bins}, we performed bins in the missing energy 
      distribution and we watch the reconstructed beam-spin asymmetries. As a 
      conclusion, we see that the reconstructed asymmetries are compatible 
   within the given error bars.}" \\

\begin{figure}[tbp]
   \centering
   \includegraphics[height=7.0cm]{fig/coh_ME_bins.png}
   \includegraphics[height=7.0cm]{fig/BSA_coherent_ME.png}
   \includegraphics[height=7.0cm]{fig/coh_ME_alpha.png}
   \caption{Coherent missing energy distributions (top), the reconstructed 
   beam-spin asymmetries as a function of $\phi$ (middle), and the extracted 
asymmetry at $\phi = 90 ^{\circ}$ from fitting the asymmetries as a function of 
the missing energy in each bin. }
   \label{fig:coherent_ME_bins}
    \end{figure}

 \item Following the CAN committee suggestions, we applied the requested cuts 
    to remove the tails and we extracted R for the different bins in the 
    missing energy. The results are presented in figure 
    \ref{fig:coherent_ME_bins_2}. Within the given error bars, the two sets of 
    results are compatible.

    \begin{figure}[tbp]
   \includegraphics[height=6.0cm]{fig/new_ME_Coh_bins.png}
   \includegraphics[height=6.0cm]{fig/e4Hegamma_e4Hepi0_Phi_ME.png}
   \hspace{-3.0cm} \includegraphics[height=6.5cm]{fig/new_BSA_coherent_ME.png}
   \hspace{-1.0cm} \includegraphics[height=6.5cm]{fig/new_coh_ME_alpha.png}
   \caption{from top to bottom and from left to right, coherent missing energy 
      binning, the corresponding background acceptance ratio from simulation, 
      the reconstructed beam-spin asymmetries as a function of $\phi$ (middle), 
   and the extracted asymmetry at $\phi = 90 ^{\circ}$ from fitting the 
asymmetries as a function of the mean missing energy in each bin.  }
   \label{fig:coherent_ME_bins_2}
    \end{figure}
\end{enumerate}

\item \textcolor{blue}{Regarding the listed bin by bin systematic errors, they 
   were extracted from the variation of the reconstructed asymmetries such as 
in figures 4.23 and 4.29 in the analysis note. The text is modified to include 
the extraction details, see the end of section 4.7.}

\end{enumerate}

### 2016-10-14 final_checks/DVCS-CAN-Meeting-Comments.tex
Update on the "final" answers

@@
 Systematic uncertainties how the corresponding numbers in the numerical tables 
-are generated. So far, the discussion is exclusively on the fitted ALU(90°), 
+are generated. So far, the discussion is exclusively on the fitted ALU(90$^\circ$), 
 while the numbers in the Tables are bin-dependent.
@@
    \item \textcolor{blue}{Regarding the stability of the coherent $A_{LU}$ with 
-      respect to the missing energy cut. I first remind you about the previous 
-   study from the first round comments and the results we got. Then, I will 
-present the new results after the CAN review committee suggestions. }
+      respect to the missing energy cut. We first remind the previous 
+      exchange from the first round comments and the results we got. Then, we 
+      present the new study after the CAN review committee suggestion.}
 
@@
 
- \item Following the CAN committee suggestions, we applied the requested cuts 
-    to remove the tails and we extracted R for the different bins in the 
+ \item Following the CAN committee suggestion, we performed this study again
+    recalculating the $\pi^0$ contamination for the different bins in the 
     missing energy. The results are presented in figure 
-    \ref{fig:coherent_ME_bins_2}. Within the given error bars, the two sets of 
-    results are compatible.
+    \ref{fig:coherent_ME_bins_2}. The high missing energy bin is the
+    most affected and goes up, closer to the value from the central point.    
+    This is easily understood as this bin has a significantly higher $\pi^0$
+    contribution. In conclusion, the central bin remains with a stronger 
+    signal, however we want to point out that (i) this feature is not significant 
+    due to the large error bars in regard to the size of the effect and 
+    (ii) the variations are smaller than the 8\% systematic error we evaluated 
+    from the rather arbitrary choice of exclusivity cuts. In conclusion, we
+    believe that the cut is good as it is. The main reason being that 
+    statistical errors already dominate the error budget, so we think it
+    would be counter productive to reduce even more our data sample in hope to
+    reduce the systematic error.
 
+\newpage
     \begin{figure}[tbp]
@@
    were extracted from the variation of the reconstructed asymmetries such as 
-in figures 4.23 and 4.29 in the analysis note. The text is modified to include 
-the extraction details, see the end of section 4.7.}
+in figures 4.23 and 4.29 in the analysis note. The end of section 4.7 has been 
+modified to include the following details on our error bar calculation:}
+
+In addition to evaluating the systematic uncertainties on $A_{LU}$ at $\phi = 
+90^{\circ}$, we performed bin by bin, in $\phi$, extraction of these 
+uncertainties. For instance, regarding the bin extraction from the source 'data 
+binning' listed in table \ref{Table:systematic_uncertainties}, the uncertainty 
+is calculated as the difference between the two reconstructed asymmetries.  
+Similar procedures have been carried out for the other studies, and finally all 
+the contributions were added quadratically. These systematic uncertainties will 
+be shown with the final asymmetry results in the following chapter.
 

### 2016-11-04 final_checks/DVCS-CAN-Meeting-Comments.tex
update the direcotry with the final check results regarding the missing energy binning

@@
-\section*{\centering{Answers to the final questions sent on October 7th, 2016}}
+\section*{\centering{Answers to the final questions sent on October 10th, 
+2016}}
 
@@
 
-\newpage
     \begin{figure}[tbp]
-   \includegraphics[height=6.0cm]{fig/new_ME_Coh_bins.png}
-   \includegraphics[height=6.0cm]{fig/e4Hegamma_e4Hepi0_Phi_ME.png}
-   \hspace{-3.0cm} \includegraphics[height=6.5cm]{fig/new_BSA_coherent_ME.png}
-   \hspace{-1.0cm} \includegraphics[height=6.5cm]{fig/new_coh_ME_alpha.png}
-   \caption{from top to bottom and from left to right, coherent missing energy 
-      binning, the corresponding background acceptance ratio from simulation, 
-      the reconstructed beam-spin asymmetries as a function of $\phi$ (middle), 
-   and the extracted asymmetry at $\phi = 90 ^{\circ}$ from fitting the 
-asymmetries as a function of the mean missing energy in each bin.  }
+     \centering
+       \includegraphics[height=6.5cm]{fig_new/e4Hegamma_e4Hepi0_Phi_ME.png}
+       \includegraphics[height=6.5cm]{fig_new/BSA_coherent_ME.png}
+       \includegraphics[height=6.5cm]{fig_new/coh_ME_alpha.png}
+   \caption{From top to bottom, the corresponding background acceptance ratio 
+in the different missing energy bins, the reconstructed beam-spin asymmetries 
+as a function of $\phi$ (middle), and the extracted asymmetry at $\phi = 90 
+^{\circ}$ from fitting the asymmetries as a function of the mean missing energy 
+in each bin.}
    \label{fig:coherent_ME_bins_2}
     \end{figure}
+
+ \item Regarding the request of cutting the tails and comparing the 
+reconstructed coherent asymmetries to the ones without cutting the tails, the 
+asymmetries are presented in fig \ref{fig:BSA_ME_bins_sig} as a function of 
+$\phi$ in bins in $Q^{2}$, $x_{B}$ and $-t$. The $Q^{2}$, $x_{B}$ and $-t$ 
+dependences of $A_{LU}$ at $\phi = 90 ^{\circ}$, from fitting the signals in 
+fig \ref{fig:BSA_ME_bins_sig}, are presented in fig \ref{ig:ALU_ME_bins_sig} 
+with and without cutting the tails in the missing energy distribution.  One can 
+conclude that the two sets are compatible within the given error bars.
+
+    \begin{figure}[tbp]
+     \centering
+       \includegraphics[height=6.5cm]{fig_new/BSA_Coh_Comb_Q2_ME.png}
+       \includegraphics[height=6.5cm]{fig_new/BSA_Coh_Comb_xB_ME.png}
+       \includegraphics[height=6.5cm]{fig_new/BSA_Coh_Comb_t_ME.png}
+   \caption{From top to bottom, the reconstructed beam-spin asymmetries as a 
+      function of $\phi = 90 ^{\circ}$ in $Q^{2}$,
+$x_{B}$ and $-t$ with cutting the tails in red and without cutting the tails in 
+blue.  }
+   \label{fig:BSA_ME_bins_sig}
+    \end{figure}
+
+    \begin{figure}[tbp]
+     \centering
+       \includegraphics[height=7.5cm]{fig_new/A_LU_He_90_vs_Q2.png}
+       \includegraphics[height=7.5cm]{fig_new/A_LU_He_90_vs_xB.png}
+       \includegraphics[height=7.5cm]{fig_new/A_LU_He_90_vs_t.png}
+       \caption{The extracted asymmetry at $\phi = 90 ^{\circ}$ from
+          fitting the asymmetries in fig \ref{fig:BSA_ME_bins_sig} as a 
+       function of $Q^{2}$, $x_{B}$ and $-t$ with cutting the tails in red and 
+    without cutting the tails in blue.  }
+   \label{fig:ALU_ME_bins_sig}
+    \end{figure}
+
 \end{enumerate}
@@
 uncertainties. For instance, regarding the bin extraction from the source 'data 
-binning' listed in table \ref{Table:systematic_uncertainties}, the uncertainty 
-is calculated as the difference between the two reconstructed asymmetries.  
-Similar procedures have been carried out for the other studies, and finally all 
-the contributions were added quadratically. These systematic uncertainties will 
-be shown with the final asymmetry results in the following chapter.
+binning' listed in table 4.2, the uncertainty is calculated as the difference 
+between the two reconstructed asymmetries.  Similar procedures have been 
+carried out for the other studies, and finally all the contributions were added 
+quadratically. These systematic uncertainties will be shown with the final 
+asymmetry results in the following chapter.
 

### 2016-12-22 analysis-note-vf/TitlePage.tex
update the analysis note with the latest plots for both DVCS channels

\begin{titlepage}
\mainmatter
  {%\fontfamily{ptm}

       \vspace*{+3.0cm}

     \begin{center}
      \noindent {\Large \textbf{Analysis note}} \\

          \vspace*{+1.5cm}         \noindent {\Huge \textbf{Deeply virtual 
          Compton scattering}} \\
       \vspace*{0.15cm}
       \noindent {\Huge \textbf{off $^{4}He$}} \\
       \vspace*{1.0cm}
       \noindent \fontsize{16}{19}\selectfont (EG6 run)  \\
       \vspace*{0.8cm}

       \noindent \fontsize{14}{19}\selectfont M. Hattawy$^{[1]}$, N. Baltzell$^{[2,3]}$, R. Dupr\'e $^{[1]}$, H. Egiyan$^{[2]}$, L. El Fassi$^{[3,4]}$,\\ F.-X. Girod$^{[2]}$, K. Hafidi$^{[3]}$, C. Moody$^{[3]}$, S. Stepanyan$^{[2]}$  \\

       \vspace{+0.8cm}
        \noindent {\Large \textbf{Review committee:}} \\ 
      \vspace{+0.2cm}
       Michel Gar\c{c}on$^{[5]}$ (chair)\\
       Sebastian Kuhn$^{[6]}$ \\
       Zein-Eddine Meziani$^{[7]}$

       \vspace*{1.1cm}

        \normalsize $^{[1]}$Institut de Physique Nucl{\'e}aire d'Orsay, Orsay 91406, France \\
        \normalsize $^{[2]}$Jefferson Laboratory, Newport News, VA 230606, USA\\
        \normalsize $^{[3]}$Argonne National Laboratory, Argonne, IL 60439, USA \\
        \normalsize $^{[4]}$Mississippi State Unvirsity, Mississippi State, MS 39762, USA\\  
        \normalsize $^{[5]}$CEA-Saclay, Gif sur Yvette 91191, France\\  
        \normalsize $^{[6]}$Old Dominion University, Norfolk, VA 23529, USA\\
        \normalsize $^{[7]}$Temple University, Philadelphia, PA 19122, USA\\    
        \vspace{3.0cm}

    \today
     \end{center}

  }

  \newpage
  \thispagestyle{plain}

\end{titlepage}
\sloppy

\titlepage

### 2016-12-22 analysis-note-vf/analysis-2.tex
update the analysis note with the latest plots for both DVCS channels

--- 2016-10-12 analysis-note-v2/analysis-2.tex
@@
 \centering
-\includegraphics[scale=0.4]{fig_dvcs/all_coh_exc_cuts.png}
+\includegraphics[scale=0.9]{fig_Dec2016/all_coh_exc_cuts.pdf}
 \caption{The coherent DVCS exclusivity cuts. The blue distributions represent 
@@
 \centering
-\includegraphics[scale=0.4]{fig_dvcs/all_incoh_exc_cuts.png}
+\includegraphics[scale=0.9]{fig_Dec2016/all_incoh_exc_cuts.pdf}
 \caption{The incoherent DVCS exclusivity cuts. The blue distributions represent 
@@
 \begin{center}
-\begin{tabular}{|l|l|l|l|}
+\begin{tabular}{|l|c|c|c|}
 \hline
-Systematic source &  Coherent channel  & Incoherent channel &Type of systematic 
+\bf Systematic source & \bf  Coherent channel  & \bf Incoherent channel & \bf Type of systematic 
 error\\
 \hline
-DVCS cuts & ~~~~~8 $\%$ &  ~~~~~6 $\%$ & bin to bin\\
+DVCS cuts & 8 $\%$ &  6 $\%$ & bin to bin\\
 \hline
-Data binning & ~~~~~5.1$\%$ & ~~~~~7.1$\%$ &bin to bin\\
+Data binning & 5.1$\%$ & 7.1$\%$ &bin to bin\\
 \hline
-Beam polarization &  ~~~~~3.5$\%$ &  ~~~~~3.5$\%$& Normalization\\
+Beam polarization &  3.5$\%$ &  3.5$\%$& Normalization\\
 \hline
-Acceptance ratio &  ~~~~~0.6$\%$ &  ~~~~~2.0$\%$ &bin to bin\\
+Acceptance ratio &  0.6$\%$ &  2.0$\%$ &bin to bin\\
 \hline
@@
 %\hline
-Radiative corrections &  ~~~~~0.1$\%$ & ~~~~~0.1$\%$ & bin to bin\\
+Radiative corrections &  0.1$\%$ & 0.1$\%$ & bin to bin\\
 \hline
-\textbf{Total} &  ~~~~~\textbf{10.1}$\%$ &   ~~~~~\textbf{10.1}$\%$ &bin to 
+\textbf{Total} &  \textbf{10.1}$\%$ &   \textbf{10.1}$\%$ &bin to 
 bin\\

### 2016-12-22 analysis-note-vf/results.tex
update the analysis note with the latest plots for both DVCS channels

--- 2016-09-08 analysis-note-v2/results.tex
@@
 \centering
-\includegraphics[scale=0.72]{fig_updated/f_coh_alu_Q2_phi.pdf} 
-\includegraphics[scale=0.72]{fig_updated/f_coh_alu_xB_phi.pdf}
-\includegraphics[scale=0.72]{fig_updated/f_coh_alu_t_phi.pdf}
+\includegraphics[scale=0.9]{fig_Dec2016/Coherent_ALU_phi.pdf}
 \caption{The coherent $A_{LU}$ as a function of $\phi$ and $Q^2$ (top panel), 
@@
 \centering
-\includegraphics[scale=0.37]{fig_ch5/coh_alu_Q2_90.png} \\
-\includegraphics[scale=0.37]{fig_ch5/coh_alu_xB_90.png} \\
-\includegraphics[scale=0.37]{fig_ch5/coh_alu_t_90.png} 
+\includegraphics[scale=0.9]{fig_Dec2016/Coherent_ALU_phi_90.pdf}
    \caption{The $Q^{2}$-dependence (on the top), the $x_{B}$-dependence (on the 
       middle), and the $t$-dependence~(on the bottom) of the fitted coherent 
-   $A_{LU}$ signals at $\phi$= 90$^{\circ}$ (black squares). On the middle: the red and the 
-   blue curves are theoretical predictions from \cite{simonetta_2} at two 
-values of $-t$. On the bottom: the green circles are the HERMES $-A_{LU}$ 
-(positron beam was used) inclusive measurements \cite{HERMES_BSA}, and the 
-colored curves represent theoretical predictions from \cite{simonetta_2}.} 
+      $A_{LU}$ signals at $\phi$= 90$^{\circ}$ (black squares). On the middle: 
+      the red and the blue curves are theoretical predictions from 
+      \cite{simonetta_2} at two values of $-t$. On the bottom: the green 
+      circles are the HERMES $-A_{LU}$ (positron beam was used) inclusive 
+      measurements \cite{HERMES_BSA}, and the colored curves represent 
+      theoretical predictions from \cite{simonetta_2}.} 
       \label{fig:coh_Q2_xB_t_ALU}
@@
 \begin{figure}[tpb]
-\includegraphics[scale=0.72]{fig_updated/f_incoh_alu_Q2_phi.pdf}
-\includegraphics[scale=0.72]{fig_updated/f_incoh_alu_xB_phi.pdf}
-\includegraphics[scale=0.72]{fig_updated/f_incoh_alu_t_phi.pdf}
+\includegraphics[scale=0.9]{fig_Dec2016/ALU_phi_p_Q2.pdf}
+\includegraphics[scale=0.9]{fig_Dec2016/ALU_phi_p_x.pdf}
+\includegraphics[scale=0.9]{fig_Dec2016/ALU_phi_p_t.pdf}
 \caption{The incoherent $A_{LU}$ as a function of the angle $\phi$ in $Q^2$, 
@@
    figure \ref{fig:bsa_coh_Q2_bins} for the color indications. The red lines 
-represent fits to the $\frac{\alpha \sin(\phi)}{1 + \beta cos(\phi)}$ function.  
-} \label{fig:bsa_incoh_bins}
+   represent fits to the $\frac{\alpha \sin(\phi)}{1 + \beta cos(\phi)}$ 
+   function.  } \label{fig:bsa_incoh_bins}
 \end{figure}
@@
    \centering
-\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_Q2_90.pdf}\\ 
-\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_xB_90.pdf}\\
-\includegraphics[scale=0.37]{fig_updated/f_incoh_alu_t_90.pdf} \\ 
+\includegraphics[scale=0.48]{fig_Dec2016/ALU_90_p_vs_Q2_shortscenrario.pdf}\\ 
+\includegraphics[scale=0.48]{fig_Dec2016/ALU_90_p_vs_x_shortscenrario.pdf}\\
+\includegraphics[scale=0.48]{fig_Dec2016/ALU_90_p_vs_t_shortscenrario.pdf} \\ 
 \caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $-t$-dependencies (bottom) of 
@@
 \begin{figure}[h!]
-\hspace{-0.5in}\includegraphics[scale=0.38]{fig_updated/f_coh_cff_Q2.pdf}
-\hspace{-0.3in}\includegraphics[scale=0.38]{fig_updated/f_coh_cff_xB.pdf}
-\centering \includegraphics[scale=0.38]{fig_updated/f_coh_cff_t.pdf}
+\includegraphics[scale=0.9]{fig_Dec2016/Coherent_CFF.pdf}
 \caption{The model-independent extraction of the imaginary (blue points) and 
@@
 \centering
-\includegraphics[scale=0.38]{fig_updated/BSA_ratio_incoh_Q2.pdf}\\
-\includegraphics[scale=0.38]{fig_updated/BSA_ratio_incoh_xB.pdf}\\
-\includegraphics[scale=0.38]{fig_updated/BSA_ratio_incoh_t.pdf}
+\includegraphics[scale=0.46]{fig_Dec2016/ALU_ratioInc_Q2_shortscenrario.pdf}\\
+\includegraphics[scale=0.46]{fig_Dec2016/ALU_ratioInc_x_shortscenrario.pdf}\\
+\includegraphics[scale=0.46]{fig_Dec2016/ALU_ratioInc_t_shortscenrario.pdf}
 \caption{ The $A_{LU}$ ratio between the bound and the free proton at 
@@
 \centering
-\includegraphics[scale=0.37]{fig_updated/BSA_ratio_coh_Q2.pdf}\\
-\includegraphics[scale=0.37]{fig_updated/BSA_ratio_coh_xB.pdf}\\
-\includegraphics[scale=0.37]{fig_updated/BSA_ratio_coh_t.pdf}
+\includegraphics[scale=0.9]{fig_Dec2016/Coherent_ALU_ratio.pdf}\\
 \caption{The $A_{LU}$ ratio between $^4$He and free proton at 
    $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
-   middle), and $-t$ (on the bottom). The black squares represent the results of 
-   this work and the green circles are the HERMES measurements 
+   middle), and $-t$ (on the bottom). The black squares represent the results 
+   of this work and the green circles are the HERMES measurements 
    \cite{HERMES_BSA}. These measurements are compared to theoretical 

### 2016-12-22 analysis-note-vf/Appendix.tex
update the analysis note with the latest plots for both DVCS channels
update the He4 pid plots and the appendix with the new free proton fitting.

--- 2016-09-08 analysis-note-v2/Appendix.tex
@@
          \hline
-  1.143 & 0.136 & 0.096 &  23.4  &  0.1407   $\pm$ 0.0800   $\pm$  0.0257 \\
-  1.143 & 0.136 & 0.096 &  59.9  &  0.3563   $\pm$ 0.0687   $\pm$  0.0188 \\
-  1.143 & 0.136 & 0.096 &  97.6  &  0.4241   $\pm$ 0.0870   $\pm$  0.0403 \\
-  1.143 & 0.136 & 0.096 &  139.9 &  0.1576   $\pm$ 0.1344   $\pm$  0.0267 \\
-  1.143 & 0.136 & 0.096 &  179.1 &  0.1496   $\pm$ 0.1390   $\pm$  0.0278 \\
-  1.143 & 0.136 & 0.096 &  218.9 & -0.1361   $\pm$ 0.1123   $\pm$  0.0248 \\
-  1.143 & 0.136 & 0.096 &  263.5 & -0.3384   $\pm$ 0.0922   $\pm$  0.0389 \\
-  1.143 & 0.136 & 0.096 &  302.9 & -0.1731   $\pm$ 0.0722   $\pm$  0.0263 \\
-  1.143 & 0.136 & 0.096 &  337.5 & -0.3439   $\pm$ 0.0744   $\pm$  0.0343 \\
-  \hline                                                           
-  1.423 & 0.172 & 0.099 &  19.9  &  0.1538   $\pm$ 0.0650   $\pm$  0.0267 \\
-  1.423 & 0.172 & 0.099 &  57.3  &  0.2941   $\pm$ 0.0684   $\pm$  0.0250 \\
-  1.423 & 0.172 & 0.099 &  95.4  &  0.4352   $\pm$ 0.0997   $\pm$  0.0426 \\
-  1.423 & 0.172 & 0.099 &  138.3 &  0.1251   $\pm$ 0.1418   $\pm$  0.0250 \\
-  1.423 & 0.172 & 0.099 &  181.2 &  0.2139   $\pm$ 0.1813   $\pm$  0.0302 \\
-  1.423 & 0.172 & 0.099 &  220.3 & -0.2494   $\pm$ 0.1646   $\pm$  0.0344 \\
-  1.423 & 0.172 & 0.099 &  263.4 & -0.3187   $\pm$ 0.1128   $\pm$  0.0366 \\
-  1.423 & 0.172 & 0.099 &  302.5 & -0.3429   $\pm$ 0.0695   $\pm$  0.0383 \\
-  1.423 & 0.172 & 0.099 &  338.1 & -0.1382   $\pm$ 0.0680   $\pm$  0.0261 \\
-  \hline                                                                    
-  1.902 & 0.224 & 0.107 &  21.0  &  0.0904   $\pm$ 0.0630   $\pm$  0.0234 \\
-  1.902 & 0.224 & 0.107 &  56.6  &  0.3647   $\pm$ 0.0654   $\pm$  0.0185 \\
-  1.902 & 0.224 & 0.107 &  95.7  &  0.1701   $\pm$ 0.1072   $\pm$  0.0173 \\
-  1.902 & 0.224 & 0.107 &  139.6 &  0.0994   $\pm$ 0.1732   $\pm$  0.0170 \\
-  1.902 & 0.224 & 0.107 &  179.5 & -0.0855   $\pm$ 0.2165   $\pm$  0.0126 \\
-  1.902 & 0.224 & 0.107 &  221.6 & -0.1338   $\pm$ 0.1825   $\pm$  0.0152 \\
-  1.902 & 0.224 & 0.107 &  262.7 & -0.2772   $\pm$ 0.1185   $\pm$  0.0260 \\
-  1.902 & 0.224 & 0.107 &  303.5 & -0.2306   $\pm$ 0.0745   $\pm$  0.0207 \\
-  1.902 & 0.224 & 0.107 &  339.2 & -0.1958   $\pm$ 0.0607   $\pm$  0.0163 \\
+  1.143 & 0.136 & 0.096 & 24.0  &  0.1575 $\pm$  0.1016 $\pm$ 0.0257 \\
+  1.143 & 0.136 & 0.096 & 60.0  &  0.3656 $\pm$  0.0903 $\pm$ 0.0188 \\
+  1.143 & 0.136 & 0.096 & 98.5  &  0.3586 $\pm$  0.1051 $\pm$ 0.0403 \\
+  1.143 & 0.136 & 0.096 & 141.2 &  0.1498 $\pm$  0.1645 $\pm$ 0.0267 \\
+  1.143 & 0.136 & 0.096 & 177.7 &  0.1849 $\pm$  0.1664 $\pm$ 0.0278 \\
+  1.143 & 0.136 & 0.096 & 219.3 &  0.0555 $\pm$  0.1475 $\pm$ 0.0248 \\
+  1.143 & 0.136 & 0.096 & 263.4 & -0.3184 $\pm$  0.1171 $\pm$ 0.0389 \\
+  1.143 & 0.136 & 0.096 & 302.7 & -0.1160 $\pm$  0.0975 $\pm$ 0.0263 \\
+  1.143 & 0.136 & 0.096 & 337.9 & -0.2805 $\pm$  0.0952 $\pm$ 0.0343 \\
+  \hline                                                               
+  1.423 & 0.172 & 0.099 & 21.1  &  0.1694 $\pm$  0.0858 $\pm$ 0.0267 \\
+  1.423 & 0.172 & 0.099 & 55.9  &  0.2889 $\pm$  0.0859 $\pm$ 0.0250 \\
+  1.423 & 0.172 & 0.099 & 96.7  &  0.4761 $\pm$  0.1304 $\pm$ 0.0426 \\
+  1.423 & 0.172 & 0.099 & 138.9 &  0.2134 $\pm$  0.1784 $\pm$ 0.0250 \\
+  1.423 & 0.172 & 0.099 & 179.8 &  0.2996 $\pm$  0.1967 $\pm$ 0.0302 \\
+  1.423 & 0.172 & 0.099 & 218.7 & -0.2375 $\pm$  0.1913 $\pm$ 0.0344 \\
+  1.423 & 0.172 & 0.099 & 263.5 & -0.2521 $\pm$  0.1398 $\pm$ 0.0366 \\
+  1.423 & 0.172 & 0.099 & 302.6 & -0.3526 $\pm$  0.0855 $\pm$ 0.0383 \\
+  1.423 & 0.172 & 0.099 & 338.0 & -0.2344 $\pm$  0.0801 $\pm$ 0.0261 \\
+  \hline                                                               
+  1.902 & 0.224 & 0.107 & 21.0  &  0.1626 $\pm$  0.0779 $\pm$ 0.0234 \\
+  1.902 & 0.224 & 0.107 & 56.4  &  0.3433 $\pm$  0.0817 $\pm$ 0.0185 \\
+  1.902 & 0.224 & 0.107 & 95.9  &  0.2443 $\pm$  0.1270 $\pm$ 0.0173 \\
+  1.902 & 0.224 & 0.107 & 138.6 &  0.4026 $\pm$  0.2333 $\pm$ 0.0170 \\
+  1.902 & 0.224 & 0.107 & 179.8 &  0.0514 $\pm$  0.2906 $\pm$ 0.0126 \\
+  1.902 & 0.224 & 0.107 & 222.7 & -0.0281 $\pm$  0.2275 $\pm$ 0.0152 \\
+  1.902 & 0.224 & 0.107 & 264.5 & -0.2909 $\pm$  0.1379 $\pm$ 0.0260 \\
+  1.902 & 0.224 & 0.107 & 303.5 & -0.1011 $\pm$  0.0940 $\pm$ 0.0207 \\
+  1.902 & 0.224 & 0.107 & 338.9 & -0.1661 $\pm$  0.0773 $\pm$ 0.0163 \\
          \hline \hline
@@
 
-  1.164 & 0.132 & 0.095 & 24.7   &  0.0165   $\pm$ 0.0983    $\pm$   0.0221 \\
-  1.164 & 0.132 & 0.095 & 60.5   &  0.3681   $\pm$ 0.0657    $\pm$   0.0198 \\
-  1.164 & 0.132 & 0.095 & 97.8   &  0.4334   $\pm$ 0.0805    $\pm$   0.0408 \\
-  1.164 & 0.132 & 0.095 & 140.4  &  0.2580   $\pm$ 0.1277    $\pm$   0.0333 \\
-  1.164 & 0.132 & 0.095 & 178.8  &  0.1732   $\pm$ 0.1341    $\pm$   0.0293 \\
-  1.164 & 0.132 & 0.095 & 218.2  & -0.1259   $\pm$ 0.1077    $\pm$   0.0243 \\
-  1.164 & 0.132 & 0.095 & 263.5  & -0.3176   $\pm$ 0.0852    $\pm$   0.0372 \\
-  1.164 & 0.132 & 0.095 & 302.0  & -0.1521   $\pm$ 0.0661    $\pm$   0.0259 \\
-  1.164 & 0.132 & 0.095 & 335.4  & -0.2915   $\pm$ 0.0885    $\pm$   0.0319 \\
-   \hline                                                                     
-  1.439 & 0.17 & 0.099 & 21.1    &  0.1815   $\pm$ 0.0628    $\pm$   0.0230 \\
-  1.439 & 0.17 & 0.099 &  57.0   &  0.2075   $\pm$ 0.0672    $\pm$   0.0195 \\
-  1.439 & 0.17 & 0.099 &  95.1   &  0.3013   $\pm$ 0.1042    $\pm$   0.0295 \\
-  1.439 & 0.17 & 0.099 &  137.9  &  0.0939   $\pm$ 0.1335    $\pm$   0.0187 \\
-  1.439 & 0.17 & 0.099 &  181.1  &  0.0167   $\pm$ 0.1741    $\pm$   0.0197 \\
-  1.439 & 0.17 & 0.099 &  221.0  & -0.2219   $\pm$ 0.1641    $\pm$   0.0270 \\
-  1.439 & 0.17 & 0.099 &  264.4  & -0.2657   $\pm$ 0.1120    $\pm$   0.0292 \\
-  1.439 & 0.17 & 0.099 &  302.9  & -0.3816   $\pm$ 0.0716    $\pm$   0.0331 \\
-  1.439 & 0.17 & 0.099 &  338.0  & -0.2336   $\pm$ 0.0657    $\pm$   0.0254 \\
-   \hline                                                                     
-  1.844 & 0.225 & 0.107 & 19.9   &  0.1286   $\pm$ 0.0601    $\pm$   0.0248 \\
-  1.844 & 0.225 & 0.107 & 56.1   &  0.4551   $\pm$ 0.0713    $\pm$   0.0224 \\
-  1.844 & 0.225 & 0.107 & 95.3   &  0.2540   $\pm$ 0.1201    $\pm$   0.0271 \\
-  1.844 & 0.225 & 0.107 & 139.6  & -0.1136   $\pm$ 0.2150    $\pm$   0.0166 \\
-  1.844 & 0.225 & 0.107 & 180.6  &  0.1414   $\pm$ 0.2634    $\pm$   0.0204 \\
-  1.844 & 0.225 & 0.107 & 223.7  & -0.2158   $\pm$ 0.2097    $\pm$   0.0270 \\
-  1.844 & 0.225 & 0.107 & 260.6  & -0.3623   $\pm$ 0.1442    $\pm$   0.0353 \\
-  1.844 & 0.225 & 0.107 & 304.4  & -0.2359   $\pm$ 0.0814    $\pm$   0.0263 \\
-  1.844 & 0.225 & 0.107 & 340.0  & -0.1393   $\pm$ 0.0593    $\pm$   0.0175 \\
+  1.164 & 0.132 & 0.095 & 25.4  &  0.0441 $\pm$ 0.1329 $\pm$ 0.0221 \\
+  1.164 & 0.132 & 0.095 & 60.8  &  0.4030 $\pm$ 0.0865 $\pm$ 0.0198 \\
+  1.164 & 0.132 & 0.095 & 98.6  &  0.3878 $\pm$ 0.0984 $\pm$ 0.0408 \\
+  1.164 & 0.132 & 0.095 & 141.7 &  0.2957 $\pm$ 0.1524 $\pm$ 0.0333 \\
+  1.164 & 0.132 & 0.095 & 177.2 &  0.2646 $\pm$ 0.1599 $\pm$ 0.0293 \\
+  1.164 & 0.132 & 0.095 & 218.4 &  0.0127 $\pm$ 0.1364 $\pm$ 0.0243 \\
+  1.164 & 0.132 & 0.095 & 263.2 & -0.2955 $\pm$ 0.1063 $\pm$ 0.0372 \\
+  1.164 & 0.132 & 0.095 & 301.6 & -0.1121 $\pm$ 0.0868 $\pm$ 0.0259 \\
+  1.164 & 0.132 & 0.095 & 335.6 & -0.1940 $\pm$ 0.1149 $\pm$ 0.0319 \\
+   \hline                                                             
+  1.439 & 0.17 & 0.099 &  22.8  &  0.1597 $\pm$ 0.0820 $\pm$ 0.0230 \\
+  1.439 & 0.17 & 0.099 &  55.9  &  0.1592 $\pm$ 0.0857 $\pm$ 0.0195 \\
+  1.439 & 0.17 & 0.099 &  96.7  &  0.2178 $\pm$ 0.1320 $\pm$ 0.0295 \\
+  1.439 & 0.17 & 0.099 &  138.7 &  0.3251 $\pm$ 0.1763 $\pm$ 0.0187 \\
+  1.439 & 0.17 & 0.099 &  180.0 & -0.0093 $\pm$ 0.1947 $\pm$ 0.0197 \\
+  1.439 & 0.17 & 0.099 &  219.8 & -0.1457 $\pm$ 0.2000 $\pm$ 0.0270 \\
+  1.439 & 0.17 & 0.099 &  265.0 & -0.2163 $\pm$ 0.1374 $\pm$ 0.0292 \\
+  1.439 & 0.17 & 0.099 &  302.9 & -0.3729 $\pm$ 0.0907 $\pm$ 0.0331 \\
+  1.439 & 0.17 & 0.099 &  337.9 & -0.2505 $\pm$ 0.0791 $\pm$ 0.0254 \\
+   \hline                                                             
+  1.844 & 0.225 & 0.107 & 19.8  &  0.2355 $\pm$ 0.0732 $\pm$ 0.0248 \\
+  1.844 & 0.225 & 0.107 & 55.8  &  0.4399 $\pm$ 0.0870 $\pm$ 0.0224 \\
+  1.844 & 0.225 & 0.107 & 95.6  &  0.4355 $\pm$ 0.1433 $\pm$ 0.0271 \\
+  1.844 & 0.225 & 0.107 & 136.7 & -0.2736 $\pm$ 0.2804 $\pm$ 0.0166 \\
+  1.844 & 0.225 & 0.107 & 182.7 &  0.5956 $\pm$ 0.3142 $\pm$ 0.0204 \\
+  1.844 & 0.225 & 0.107 & 225.5 & -0.1065 $\pm$ 0.2739 $\pm$ 0.0270 \\
+  1.844 & 0.225 & 0.107 & 263.0 & -0.3547 $\pm$ 0.1728 $\pm$ 0.0353 \\
+  1.844 & 0.225 & 0.107 & 304.2 & -0.1088 $\pm$ 0.1008 $\pm$ 0.0263 \\
+  1.844 & 0.225 & 0.107 & 340.0 & -0.1632 $\pm$ 0.0742 $\pm$ 0.0175 \\
 
@@
          \hline
-  1.36 & 0.160 & 0.080 &  21.3   &  0.1692   $\pm$ 0.0708    $\pm$  0.0263  \\
-  1.36 & 0.160 & 0.080 &  57.2   &  0.2972   $\pm$ 0.0644    $\pm$  0.0243  \\
-  1.36 & 0.160 & 0.080 &  95.9   &  0.4170   $\pm$ 0.0954    $\pm$  0.0394  \\
-  1.36 & 0.160 & 0.080 &  138.1  &  0.1374   $\pm$ 0.1434    $\pm$  0.0252  \\
-  1.36 & 0.160 & 0.080 &  179.2  &  0.3245   $\pm$ 0.1657    $\pm$  0.0371  \\
-  1.36 & 0.160 & 0.080 &  221.6  & -0.2851   $\pm$ 0.1376    $\pm$  0.0370  \\
-  1.36 & 0.160 & 0.080 &  265.6  & -0.4009   $\pm$ 0.1050    $\pm$  0.0403  \\
-  1.36 & 0.160 & 0.080 &  301.6  & -0.2257   $\pm$ 0.0746    $\pm$  0.0294  \\
-  1.36 & 0.160 & 0.080 &  339.7  & -0.2312   $\pm$ 0.0637    $\pm$  0.0281  \\
-\hline                                                              
-  1.507 & 0.179 & 0.094 & 21.2   &  0.1593   $\pm$ 0.0696    $\pm$  0.0267  \\
-  1.507 & 0.179 & 0.094 & 57.0   &  0.3607   $\pm$ 0.0679    $\pm$  0.0284  \\
-  1.507 & 0.179 & 0.094 & 97.0   &  0.2913   $\pm$ 0.0971    $\pm$  0.0307  \\
-  1.507 & 0.179 & 0.094 & 141.6  &  0.1033   $\pm$ 0.1621    $\pm$  0.0215  \\
-  1.507 & 0.179 & 0.094 & 179.6  & -0.3610   $\pm$ 0.1755    $\pm$  0.0360  \\
-  1.507 & 0.179 & 0.094 & 220.1  & -0.0705   $\pm$ 0.1583    $\pm$  0.0147  \\
-  1.507 & 0.179 & 0.094 & 262.5  & -0.1960   $\pm$ 0.1079    $\pm$  0.0283  \\
-  1.507 & 0.179 & 0.094 & 303.5  & -0.2605   $\pm$ 0.0763    $\pm$  0.0286  \\
-  1.507 & 0.179 & 0.094 & 338.2  & -0.1241   $\pm$ 0.0700    $\pm$  0.0201  \\
-\hline                                                                         
-  1.610 & 0.193 & 0.127 & 21.0   &  0.0248   $\pm$ 0.0675    $\pm$  0.0214  \\
-  1.610 & 0.193 & 0.127 & 59.4   &  0.3820   $\pm$ 0.0725    $\pm$  0.0204  \\
-  1.610 & 0.193 & 0.127 & 95.8   &  0.3454   $\pm$ 0.1021    $\pm$  0.0313  \\
-  1.610 & 0.193 & 0.127 & 138.6  &  0.1427   $\pm$ 0.1440    $\pm$  0.0203  \\
-  1.610 & 0.193 & 0.127 & 180.4  &  0.3198   $\pm$ 0.1557    $\pm$  0.0354  \\
-  1.610 & 0.193 & 0.127 & 218.4  & -0.0996   $\pm$ 0.1403    $\pm$  0.0189  \\
-  1.610 & 0.193 & 0.127 & 261.4  & -0.3095   $\pm$ 0.1103    $\pm$  0.0327  \\
-  1.610 & 0.193 & 0.127 & 303.3  & -0.2537   $\pm$ 0.0689    $\pm$  0.0280  \\
-  1.610 & 0.193 & 0.127 & 337.2  & -0.2732   $\pm$ 0.0703    $\pm$  0.0261  \\
+  1.36 & 0.160 & 0.080 & 23.0  &  0.1884 $\pm$ 0.0891 $\pm$ 0.0263 \\
+  1.36 & 0.160 & 0.080 & 57.0  &  0.2973 $\pm$ 0.0848 $\pm$ 0.0243 \\
+  1.36 & 0.160 & 0.080 & 97.6  &  0.4928 $\pm$ 0.1155 $\pm$ 0.0394 \\
+  1.36 & 0.160 & 0.080 & 138.7 &  0.2070 $\pm$ 0.1743 $\pm$ 0.0252 \\
+  1.36 & 0.160 & 0.080 & 178.6 &  0.2466 $\pm$ 0.2021 $\pm$ 0.0371 \\
+  1.36 & 0.160 & 0.080 & 222.1 & -0.1512 $\pm$ 0.1738 $\pm$ 0.0370 \\
+  1.36 & 0.160 & 0.080 & 266.8 & -0.3610 $\pm$ 0.1363 $\pm$ 0.0403 \\
+  1.36 & 0.160 & 0.080 & 300.6 & -0.2254 $\pm$ 0.0953 $\pm$ 0.0294 \\
+  1.36 & 0.160 & 0.080 & 339.4 & -0.1889 $\pm$ 0.0795 $\pm$ 0.0281 \\
+
+         \hline
+
+  1.507 & 0.179 & 0.094 & 20.7  &  0.2291 $\pm$ 0.0874 $\pm$ 0.0267 \\
+  1.507 & 0.179 & 0.094 & 55.4  &  0.3684 $\pm$ 0.0814 $\pm$ 0.0284 \\
+  1.507 & 0.179 & 0.094 & 97.6  &  0.2149 $\pm$ 0.1193 $\pm$ 0.0307 \\
+  1.507 & 0.179 & 0.094 & 141.4 &  0.0640 $\pm$ 0.2113 $\pm$ 0.0215 \\
+  1.507 & 0.179 & 0.094 & 178.3 & -0.2712 $\pm$ 0.1944 $\pm$ 0.0360 \\
+  1.507 & 0.179 & 0.094 & 219.0 &  0.1647 $\pm$ 0.2000 $\pm$ 0.0147 \\
+  1.507 & 0.179 & 0.094 & 263.4 & -0.1991 $\pm$ 0.1284 $\pm$ 0.0283 \\
+  1.507 & 0.179 & 0.094 & 303.8 & -0.1605 $\pm$ 0.0968 $\pm$ 0.0286 \\
+  1.507 & 0.179 & 0.094 & 338.7 & -0.1862 $\pm$ 0.0839 $\pm$ 0.0201 \\
+\hline                                                                
+  1.610 & 0.193 & 0.127 & 21.9  &  0.0517 $\pm$ 0.0882 $\pm$ 0.0214 \\
+  1.610 & 0.193 & 0.127 & 59.8  &  0.3527 $\pm$ 0.0934 $\pm$ 0.0204 \\
+  1.610 & 0.193 & 0.127 & 96.4  &  0.3404 $\pm$ 0.1265 $\pm$ 0.0313 \\
+  1.610 & 0.193 & 0.127 & 139.9 &  0.3285 $\pm$ 0.1842 $\pm$ 0.0203 \\
+  1.610 & 0.193 & 0.127 & 179.5 &  0.6863 $\pm$ 0.1731 $\pm$ 0.0354 \\
+  1.610 & 0.193 & 0.127 & 218.7 & -0.0617 $\pm$ 0.1731 $\pm$ 0.0189 \\
+  1.610 & 0.193 & 0.127 & 261.1 & -0.2876 $\pm$ 0.1321 $\pm$ 0.0327 \\
+  1.610 & 0.193 & 0.127 & 303.7 & -0.2077 $\pm$ 0.0882 $\pm$ 0.0280 \\
+  1.610 & 0.193 & 0.127 & 336.8 & -0.2645 $\pm$ 0.0881 $\pm$ 0.0261 \\
 
@@
 kinematic values.  The statistical errors on the calculated asymmetries were 
-calculated using the error bars on the fitted parameters $a_{i}$s.\\
+calculated using the fit errors.\\
 
@@
 \centering
-\includegraphics[scale=0.85]{fig_updated/ALU-proton-fits.pdf}
+\includegraphics[scale=0.85]{fig_Dec2016/F_ALU-proton-fits.pdf}
 \caption{Black circles are the free proton beam-spin asymmetries at $\phi = 90 
@@
    asymmetries in the form $a_{0}*(\sqrt{t}-a_{1})*e^{a_{2}*\sqrt{t} - a_{3}}$.
-   The dashed curves are calculations using the fitted $a_{i}$'s parameters as 
-a function of $x_B$ as shown in figure \ref{fig:fitted-points-xB}. Blue points 
-are the interpolated points corresponding for the incoherent points presented 
-in this analysis. The red points stand for the extrapolated free proton 
-asymmetries at the measured coherent kinematics.}
+   Blue points are the interpolated points corresponding for the incoherent 
+points presented in this analysis. The red points stand for the extrapolated 
+free proton asymmetries at the measured coherent kinematics.}
 \label{fig:free-proton-alu}
-\end{figure}
-
-\begin{figure}[tpb]
-\includegraphics[scale=0.37]{fig_updated/test_a0.pdf}
-\includegraphics[scale=0.37]{fig_updated/test_a1.pdf}
-\includegraphics[scale=0.37]{fig_updated/test_a2.pdf}
-\hspace{1.7cm}
-\includegraphics[scale=0.37]{fig_updated/test_a3.pdf}
-\caption{The fitted $a_0$, $a_1$, $a_2$, and $a_3$ parameters as a function of 
-$x_B$.}
-\label{fig:fitted-points-xB}
 \end{figure}

### 2016-12-23 analysis-note-vf/analysis-2.tex
update the note with the final tables and texting

@@
 \end{itemize}
-Figure \ref{fig:coh_exclusivty_cuts} summarizes all the exclusivity cuts.  
-In these plots, the blue distributions represent the coherent events after the 
+Figure \ref{fig:coh_exclusivty_cuts} summarizes all the exclusivity cuts.  In 
+these plots, the black distributions represent the coherent events after the 
 DVCS characteristic cuts and before all the exclusivity cuts. The shaded 
@@
 Gaussian and then we applied  3$\sigma$ cuts around the mean value of each 
-distribution. The events which pass these cuts are assumed to be good $^{4}He$ 
-DVCS events.
+distribution except the missing energy distribution for which a final 
+[-0.45:0.5] GeV cut is applied to remove the tails and reduce the background.   
+The events which pass these cuts are assumed to be good $^{4}He$ DVCS events.
 
@@
    events which passed all the exclusivity cuts except the quantity plotted.  
-   The vertical red lines represent $3\sigma$ cuts. The missing momentum in $x$ 
-   and $y$ directions in the configuration $e^{4}He\gamma X$, are shown for 
-information. The mean and the sigma values of each quantity can be found in 
-Appendix \ref{exclusivity_cuts}, table \ref{Table:coh_exclusivity_cuts}.} 
-\label{fig:coh_exclusivty_cuts}
+   The vertical red lines represent $3\sigma$ cuts on all the distribution 
+   except the missing energy distribution for which [-0.45:0.5] GeV cut is 
+   applied.  The missing momentum in $x$ and $y$ directions in the 
+configuration $e^{4}He\gamma X$, are shown for information. The mean and the 
+sigma values of each quantity can be found in Appendix \ref{exclusivity_cuts}, 
+table \ref{Table:coh_exclusivity_cuts}.} \label{fig:coh_exclusivty_cuts}
 \end{figure}
@@
 \includegraphics[scale=0.9]{fig_Dec2016/all_incoh_exc_cuts.pdf}
-\caption{The incoherent DVCS exclusivity cuts. The blue distributions represent 
-   all the events with one good electron, one good proton, and at least one 
-   photon in the IC. The shaded brown distributions show the incoherent DVCS 
-   events which passed all the exclusivity cuts except the one on the quantity 
-   drawn. The distributions from left to right and from top to bottom are: the 
-   proton-photon coplanarity, the missing energy, missing mass squared, missing 
-   transverse momentum from $ep\gamma X$, the missing mass squared $epX$ and 
-   the missing mass squared $e\gamma X$, the angle between the missing particle 
-   in $epX$ and the measured photon, the missing $P_{x}$ and $P_{y}$ in 
-   $ep\gamma X$. The vertical red lines represent 3$\sigma$ cuts. The mean and 
-   sigma values of each shaded distribution are listed in table 
-\ref{Table:incoh_exclusivity_cuts}.} \label{fig:incoh_exclusivty_cuts}
+\caption{The incoherent DVCS exclusivity cuts. The black distributions 
+   represent all the events with one good electron, one good proton, and at 
+   least one photon in the IC. The shaded brown distributions show the 
+   incoherent DVCS events which passed all the exclusivity cuts except the one 
+   on the quantity drawn. The distributions from left to right and from top to 
+   bottom are: the proton-photon coplanarity, the missing energy, missing mass 
+   squared, missing transverse momentum from $ep\gamma X$, the missing mass 
+   squared $epX$ and the missing mass squared $e\gamma X$, the angle between 
+   the missing particle in $epX$ and the measured photon, the missing $P_{x}$ 
+   and $P_{y}$ in $ep\gamma X$. The vertical red lines represent 3$\sigma$ 
+   cuts. The mean and sigma values of each shaded distribution are listed in 
+table \ref{Table:incoh_exclusivity_cuts}.} \label{fig:incoh_exclusivty_cuts}
 \end{figure}

### 2016-12-23 analysis-note-vf/data_analysis.tex
update the note with the final tables and texting

--- 2016-09-19 eg6-letters/analysis-note-v2/data_analysis.tex
@@
 \begin{itemize}
-\item Negative charge: the torus magnet generates a field which has mainly azimuthal components.
-Hence, the trajectory of a negative particle will be bent towards the beam line direction without changing azimuth.
-Consequently, information on its charge is accessible from the curvature of its trajectory.
 
-\item $(DC_{stat}, EC_{stat}, SC_{stat}, CC_{stat}) > 0$: these status variables are linked to the number of hits and the thresholds in the different sub-detectors of CLAS.
-Thus, we select the electrons which have positive status in the different sub-detectors as a first step to reduce the noise in the data sample.
+\item Negative charge: the torus magnet generates a field which has mainly 
+   azimuthal components. Hence, the trajectory of a negative particle will be 
+   bent towards the beam line direction without changing azimuth.  
+   Consequently, information on its charge is accessible from the curvature of 
+   its trajectory.
 
-\item $stat$ > 0: this variable is positive if the trajectory of a particle passes the two steps of the tracking in the DCs, Hit-Based Tracking (HBT) and Time-Based Tracking (TBT).
+\item $(DC_{stat}, EC_{stat}, SC_{stat}, CC_{stat}) > 0$: these status 
+   variables are linked to the number of hits and the thresholds in the 
+   different sub-detectors of CLAS. Thus, we select the electrons which have 
+   positive status in the different sub-detectors as a first step to reduce the 
+   noise in the data sample.
+
+\item $stat$ > 0: this variable is positive if the trajectory of a particle 
+   passes the two steps of the tracking in the DCs, Hit-Based Tracking (HBT) 
+   and Time-Based Tracking (TBT).
 
@@
 
-\item Vertex cut: the target is centered at -64 cm with respect to the center of CLAS.
-Figure \ref{fig:z_cut} shows the reconstructed z-vertices for the collected negative particles.
-One sees two sharp peaks corresponding to the two aluminum windows at the ends of the target.
-These particles have to be rejected as they originate from outside the target.
-As will be emphasized later, we need an accurate determination of the electron's vertex to ensure the correspondence between the final-state particles, which all have to originate from the same point.
+\item Vertex cut: the target is centered at -64 cm with respect to the center 
+   of CLAS. Figure \ref{fig:z_cut} shows the reconstructed z-vertices for the 
+   collected negative particles. One sees two sharp peaks corresponding to the 
+   two aluminum windows at the ends of the target. These particles have to be 
+   rejected as they originate from outside the target. As will be emphasized 
+   later, we need an accurate determination of the electron's vertex to ensure 
+   the correspondence between the final-state particles, which all have to 
+   originate from the same point.
 
@@
    distributions for the positive tracks originating within the RTPC. We apply 
-   $\chi^{2}$~<~3.5 to select good $^4$He tracks.
+   $\chi^{2}$~<~3.0 to select good $^4$He tracks.
 
@@
 \includegraphics[height=6.0cm]{fig_analysis/rtpc_X2.png}
-\caption{$\chi^{2}$ distribution for the tracks in the two modules of the RTPC, with the cut we require to select good tracks: $\chi^{2}$ < 3.5.}
+\caption{$\chi^{2}$ distribution for the tracks in the two modules of the RTPC, 
+with the cut we require to select good tracks: $\chi^{2}$ < 3.}
 \vspace{0.5in}
@@
 \includegraphics[height=6.0cm]{fig_analysis/rtpc_sdist.png}
-\caption{$sdist$ distribution for the positive tracks in the RTPC. $|sdist|$~<~2.0 mm cut is applied to select good tracks.} 
+\caption{$sdist$ distribution for the positive tracks in the RTPC.  
+-3~<~$sdist$~<~2.0 mm cut is applied to select good tracks.} 
 \label{fig:rtpc_sdist}
@@
 \includegraphics[height=6.0cm]{fig_analysis/rtpc_edist.png}
-\caption{$edist$ distribution for the positive tracks in the RTPC. We require $-1.0$~mm~<~$edist$~<~5.0 mm to select good tracks.}
+\caption{$edist$ distribution for the positive tracks in the RTPC. We require 
+$-2.0$~mm~<~$edist$~<~3.0 mm to select good tracks.}
 \label{fig:rtpc_edist}

### 2017-01-10 eg6-letters/analysis-note-vf/experimental_setup.tex
update the NIM paper

--- 2016-08-23 analysis-note-v2/experimental_setup.tex
@@
 facing the downstream side of the Radial TPC (RTPC) and placed at 16 cm from 
-the center of CLAS.\\
+the center of CLAS.
 
@@
 these electrons are bent to low polar angles, less than 4$^{\circ}$, when the 
-solenoid field is applied.\\
+solenoid field is applied.
 

### 2017-01-10 eg6-letters/analysis-note-vf/ref.tex
update the NIM paper

--- 2016-06-27 analysis-note-v2/ref.tex
@@
 \bibitem{FX_analysis_note}
-F.X. Girod et al. (CLAS Collaboration), Measurement of Deeply Virtual Compton Scattering Beam-Spin Asymmetries, CLAS Note, 2007-026, 2007.
+F.X. Girod et al. (CLAS Collaboration), Measurement of Deeply Virtual Compton 
+Scattering Beam-Spin Asymmetries, CLAS Note, 2007-026, 2007.
+
+\bibitem{Vadim_priv}
+   Private communications with V.~Guzey based on reference 
+   \cite{{EMC_vadim_3}}.
+
+\bibitem{Guidal_priv}
+   Private communications with M.~Guidal based on reference:   M.~Guidal, 
+   M.~V.~Polyakov, A.~V.~Radyushkin and M.~Vanderhaeghen, Nucleon form-factors 
+   from generalized parton distributions,
+     Phys.\ Rev.\ D {\bf 72}, 054013, [hep-ph/0410251], 2005.
+
+\bibitem{GonzalezHernandez:2012jv} Private communications with S.~Liuti based 
+   on:  J.~O.~Gonzalez-Hernandez, S.~Liuti, G.~R.~Goldstein and K.~Kathuria,
+     Interpretation of the Flavor Dependence of Nucleon Form Factors in a 
+     Generalized Parton Distribution Model, Phys.\ Rev.\ C {\bf 88}, no. 6, 
+     065206, arXiv:1206.1876 [hep-ph], 2013.
+
+\bibitem{GPD_cal_free_p}
+K. Kumericki, S. Liuti, H. Moutarde, GPD phenomenology and DVCS fitting - 
+Entering the high-precision era, arXiv:1602.02763 [hep-ph], 2016.
 

### 2017-01-10 eg6-letters/eg6-letters/NIM/EG6_RTPC_NIM.tex
update the NIM paper

--- 2016-09-19 NIM/EG6_RTPC_NIM.tex
@@
-\documentclass[aps,prl,twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4}
+\documentclass[twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4}
 \usepackage{graphicx}
@@
 \usepackage{amssymb}  
-
-% avoids incorrect hyphenation, added Nov/08 by SSR
-\hyphenation{ALPGEN}
-\hyphenation{EVTGEN}
-\hyphenation{PYTHIA}
+\usepackage{hyperref}
+\hypersetup{colorlinks=true, urlcolor=blue, citecolor=blue}
 
@@
 less than 250 MeV/c. In 2009, we carried out measurements on $^4$He target 
-using CLAS spectrometer, which was upgraded with the RTPC. The detector was 
-positioned directly around the gaseous target, allowing a detection threshold 
-of $~$125  MeV/c for $^4$He. This article discuses the RTPC design, work 
-principle, developed calibration methods and detector performance.
+using CLAS spectrometer, which was upgraded with the RTPC during the CLAS-EG6 
+experimental run. The detector was positioned directly around the gaseous 
+target, allowing a detection threshold of $~$100  MeV/c for $^4$He. This 
+article discuses the RTPC design, work principle, developed calibration methods 
+and detector performance.
 \end{abstract}
@@
 
-\section{\label{sec:level1} Introduction}
+\section{Introduction} \label{sec:level1}
 
@@
 
-This paper is organized in this way: section \ref{prev_tpc} presents an 
-overview of the TPCs history and previous usage, section \ref{sec_design} 
-details the physics considerations for the RTPC design and its internal 
-structure, while section \ref{sec_readout} points the properties of the 
-read-out system.  The calibration strategies for such detectors will be 
-discussed in section \ref{sec_calib}. Finally, the performance of the RTPC is 
-discussed in section \ref{sec_perf}.
+In this paper we report the progress in designing and calibrating a radial TPC 
+that had been used with JLab-CLAS spectrometer. This paper is organized in this 
+way: section \ref{prev_tpc} presents an overview of the TPCs history and 
+previous usage, section \ref{sec_design} details the physics considerations for 
+the RTPC design and its internal structure, while section \ref{sec_readout} 
+points the properties of the read-out system.  The calibration strategies for 
+such a detector is discussed in section \ref{sec_calib}. Finally, the 
+performance of the RTPC is described
+in section \ref{sec_perf}.
 
-\section{TPCs overview}
+\section{TPC technology} \label{prev_tpc}
 In the late 1970s, David R. Nygren presented the concept of the Time projection 
@@
 effective gas-gain element to improve the tracking efficiency of the TPCs 
-\ref{gem_sauli}.
+\ref{gem_sauli}. Currently, the TPCs are widely used in physics experiments, 
+such as high-energy physics (ALEPH, DELPHI), heavy-ion physics (STAR, ALICE) 
+and rare-event searches (XENON, NEXT).
 
-The first implementation of a RTPC in CLAS have been achieved for the BoNuS 
-experiment~\cite{BONUS} in 200x. The success of this detector for the detection 
-of slow protons motivated the development of this new RTPC. For the channel of 
-interests of our experiments, the recoiled $^{4}He$ nuclei have momentum per 
-charge around 150 MeV/c, the detection of these particles was the primary 
-motivation for using such design.
+The first implementation of a radial TPC with JLab-CLAS spectrometer has been 
+performed by the BoNuS experiment \cite{BONUS} in 2005. The success of the 
+BoNuS-RTPC in detecting the slow protons motivated the development of this new 
+RTPC. For the channel of interests of our experiments, the recoiled $^{4}He$ 
+nuclei have momentum per charge around 150 MeV/c, the detection of these 
+particles was the primary motivation for designing this detector.
 
 \section{CLAS-EG6 RTPC design} \label{sec_design}
-The RTPC is a 200~mm long with a 150~mm diameter time projection chamber. The 
-ionized electrons are drifting outward perpendicularly to the beam direction.  
+The design of CLAS-EG6 RTPC has been chosen according to physics and 
+experimental considerations. At 6 GeV incident electron beam energy, the recoil 
+$^{4}He$ nuclei, from the coherent DVCS channel, have an average momentum (per 
+charge) around 125 MeV/c, while the "standard" CLAS detects charged particles 
+with a threshold of 250 MeV/c. On the experimental site, The chosen design has 
+to fit within the available space of a 5 Tesla Solenoid magnet that surrounds 
+the target \cite{Hyon-suk}. Figure \ref{fig:RTPC2} shows an experimental view 
+of the RTPC before inserting it into the solenoid.
+
+The CLAS-EG6 RTPC is a 200~mm long with a 150~mm diameter time projection 
+chamber. While a charged particle traverses a gas-sensitive volume, the ionized 
+electrons are released and drift outward perpendicularly to the beam direction.  
 These electrons are then amplified by three layers of GEMs and detected on 4.45 
-by 5~mm pads. As for BoNuS, the RTPC has two detection parts but unlike BoNuS 
-they are part of a single chamber. Each part has independent GEM amplification 
-systems that cover around 80\% of the azimuthal angle. Under the effect of the 
-electromagnetic field, the ionization electrons drift to the readout system on 
-the external shell with a curved trajectory as can be seen in the 
-figure~\ref{fig:RTPC_1_4}.
+by 5~mm pads. As for CLAS-BoNuS, the EG6-RTPC has two detection parts but 
+unlike BoNuS they are part of a single chamber. Each part has independent GEM 
+amplification systems that cover around 80\% of the azimuthal angle. Under the 
+effect of the electromagnetic field, the ionization electrons drift to the 
+readout system on the external shell with a curved trajectory as can be seen in 
+the figure~\ref{fig:RTPC_1_4}.
 
@@
 \includegraphics[scale=0.19]{fig/RTPC_exp.png}
-\caption[]{\small\sf View of the RTPC ready to be inserted in the solenoid. } 
+\caption{View of the RTPC ready to be inserted in the solenoid. } 
 \label{fig:RTPC2}
@@
 \includegraphics[scale=0.28]{fig/RTPC_1_all.png}
-\caption[]{\small\sf Schematic drawing of the RTPC taken on a plane 
-perpendicular to the beam line, see text for description of the elements.} 
-\label{fig:RTPC_1_4}
+\caption{Schematic drawing of the RTPC taken on a plane perpendicular to the 
+beam line, see text for description of the elements.} \label{fig:RTPC_1_4}
 \end{figure}
 
-As seen in figure~\ref{fig:RTPC2}, the RTPC is composed from the beam axis to 
-the exterior by:\\
+As seen in figure~\ref{fig:RTPC_1_4}, the RTPC has the following substructure, 
+from the beam axis to the exterior::\\
 \begin{itemize}
-   \item The target, filled with 5~atm $^4$He, has a 3~mm radius with Kapton 
-      walls only 27$\mu$m thick.
+   \item The target extends along the RTPC's central z-axis, with a diameter of 
+      6 mm. It is enclosed in a 27-$\mu$m-thick Kapton wall.
 
@@
    \item The GEM system is composed of three GEMs located at radii, 60 mm, 63 
-      mm and 66 mm, they amplify the electrons to make a measurable signal.
+      mm and 66 mm, they amplify the electrons to make a measurable signal. In 
+      this configuration, the first GEM layer represents the anode.
 
@@
 \end{itemize}
-\begin{figure}[tb]
+
+\begin{figure}[tbp]
 \centering
 \includegraphics[scale=0.70]{fig/GEM_photo.jpg}
-\caption[]{A schematic layout of the GEMs system in one module of the RTPC.} 
+\caption{A schematic layout of the GEMs system in one module of the RTPC.} 
 \label{fig:GEMs}
@@
 \includegraphics[scale=0.4]{fig/RunNumber_61551_TDCmax_Zslice.png}
-\caption[]{\small\sf Time profile distribution for the collected hits in one experimental run. } 
-\label{fig:RunNumber_61551_TDCmax_Zslice}
+\caption{Time profile distribution for the collected hits in one experimental 
+run. } \label{fig:RunNumber_61551_TDCmax_Zslice}
 \end{figure}
 
-Due to the non perfect experimental conditions and in particular changes in the gas proportions, the drift speed might also change over the 3 months run.
-Figure \ref{fig:Drift_run_number_1} shows the $TDC_{Max/2}$ values for individual runs (approximately 2 hours long).
-We observe a significant variation over time that we parametrized with a fit in order to take it into account in the track reconstruction code.
-Dealing with such situation is possible by adapting the right drift speed to the electrons as a function of geometry and time (we did not see any correlation between the effects).
-These functions were extracted for our entire data sets and implemented in the reconstructions code.
+Due to the non perfect experimental conditions and in particular changes in the 
+gas proportions, the drift speed might also change over the 3 months run.  
+Figure \ref{fig:Drift_run_number_1} shows the $TDC_{Max/2}$ values for 
+individual runs (approximately 2 hours long). We observe a significant 
+variation over time that we parametrized with a fit in order to take it into 
+account in the track reconstruction code. Dealing with such situation is 
+possible by adapting the right drift speed to the electrons as a function of 
+geometry and time (we did not see any correlation between the effects). These 
+functions were extracted for our entire data sets and implemented in the 
+reconstructions code.
 
@@
 \includegraphics[scale=0.28]{fig/Drift_run_number_1.png}
-\caption[]{\small\sf $TDC_{Nbmax/2}$ versus the experimental run numbers (time). } 
+\caption{$TDC_{Nbmax/2}$ versus the experimental run numbers (time).  } 
 \label{fig:Drift_run_number_1}
@@
 
-The drift path is the trajectory which an electron follows in the gas.
-The standard software to calculate drift paths is the MAGBOLTZ program ~\cite{MAGBOLTZ}.
-For its calculations, MAGBOLTZ needs to know the detector's geometry, the exact composition of the gas mixture and of course the electric and the magnetic fields.
-We used such calculations as a first calibration, but as can be seen with the drift speed, conditions are far from stable in the chamber.
-Moreover, because we use of a thin foil as a cathode, the geometry knowledge is limited to a millimeter precision.
-These problems, already encountered for the BoNuS RTPC calibration (ref), have motivated the acquisition of specific calibration runs.
-These are taken with lower energy electron beam (1.20 and 1.27 GeV) to enhance the cross section of the elastic process ($e ^{4}He \rightarrow e ^{4}He$).
-In this process the knowledge of the electron kinematic gives us the helium nuclei kinematic and therefore allow us to calibrate our drift paths independently of our knowledge of the exact conditions in the chamber.
+The drift paths are the trajectories which an electron follows in the gas. The 
+standard software to calculate drift paths is the MAGBOLTZ program 
+~\cite{MAGBOLTZ}. For its calculations, MAGBOLTZ needs to know the detector's 
+geometry, the exact composition of the gas mixture and of course the electric 
+and the magnetic fields. We used such calculations as a first calibration, but 
+as can be seen with the drift speed, conditions are far from stable in the 
+chamber. Moreover, because we use of a thin foil as a cathode, the geometry 
+knowledge is limited to a millimeter precision. These problems, already 
+encountered for the BoNuS RTPC calibration (ref), have motivated the 
+acquisition of specific calibration runs. These are taken with lower energy 
+electron beam (1.20 and 1.27 GeV) to enhance the cross section of the elastic 
+process ($e ^{4}He \rightarrow e ^{4}He$). In this process the knowledge of the 
+electron kinematic gives us the helium nuclei kinematic and therefore allow us 
+to calibrate our drift paths independently of our knowledge of the exact 
+conditions in the chamber.
 
-The drift paths' parametrization is possible using identified elastic events from our experiment and simulate copy of them in a GEANT4 simulation~\cite{GEANT4}.
-Then by comparing the GEANT4 calculated position of the helium nuclei to the list of hits effectively measured in the chamber, we can reconstruct the electrons drift path in the RTPC.
-However, because of the magnetic field, the drift paths are not linear.
-So to perform the extraction, we make a first assumption of a linear dependence between the radius of emission and the TDC of detection and then refine our result.
-As it happens, the curvature is minimal and this process converge already on the second iteration.
-Here are the step of the extraction procedure (we work in a polar coordinate system ($R$,$\phi$), $\Delta\phi$ being the difference between the $\phi$ of the pad measuring a hit and the $\phi$ of the simulated helium):
+The drift paths' parametrization is possible using identified elastic events 
+from our experiment and simulate copy of them in a GEANT4 
+simulation~\cite{GEANT4}. Then by comparing the GEANT4 calculated position of 
+the helium nuclei to the list of hits effectively measured in the chamber, we 
+can reconstruct the electrons drift path in the RTPC. However, because of the 
+magnetic field, the drift paths are not linear. So to perform the extraction, 
+we make a first assumption of a linear dependence between the radius of 
+emission and the TDC of detection and then refine our result. As it happens, 
+the curvature is minimal and this process converge already on the second 
+iteration. Here are the step of the extraction procedure (we work in a polar 
+coordinate system ($R$,$\phi$), $\Delta\phi$ being the difference between the 
+$\phi$ of the pad measuring a hit and the $\phi$ of the simulated helium):
 
@@
 %\hspace{-0.95cm}
-\includegraphics[scale=0.37]{fig/R_correlation.png}
-\caption[]{\small\sf R versus TDC distribution for the simulated hits locating in a single $z$ bin.
-The maximum $R$ equals 60 mm (close to the anode) at minimum TDCs (Trigger time is 15), and minimum R equals 30 mm (close to the cathode) at maximum TDCs ($\sim75$).}
+\includegraphics[scale=0.37]{fig/TdcR_check_p1_10.png}
+\caption{R versus TDC distribution for the simulated hits locating in a single 
+$z$ bin. The maximum $R$ equals 60 mm (close to the anode) at minimum TDCs 
+(Trigger time is 15), and minimum R equals 30 mm (close to the cathode) at 
+maximum TDCs ($\sim75$).}
 \label{fig:R_correlation}
@@
 \begin{itemize}
-\item The linear assumption between R and time(TDC) is necessary to link the generated hits from GEANT4 to physical hits. Figure \ref{fig:R_correlation} shows our initial $R$ versus TDC. \\
-\item For these selected hits, we look at $\Delta\phi$ ($\Delta \phi$ = $\phi_{sim.}$ - $\phi_{hit\_pad}$) versus TDC.
-We clearly obtain a correlation shown in figure~\ref{fig:1st_pass_delta_phi}.
-This $\Delta \phi$ change with TDC shows the drift in $phi$ of the electrons due to the Lorentz angle.
-\\
+
+   \item The linear assumption between R and time(TDC) is necessary to link the 
+      generated hits from GEANT4 to physical hits. Figure 
+      \ref{fig:R_correlation} shows our initial $R$ versus TDC.
+
+   \item For these selected hits, we look at $\Delta\phi$ ($\Delta \phi$ = 
+      $\phi_{sim.}$ - $\phi_{hit\_pad}$) versus TDC. We clearly obtain a 
+      correlation shown in figure~\ref{fig:1st_pass_delta_phi}. This $\Delta 
+      \phi$ change with TDC shows the drift in $phi$ of the electrons due to 
+      the Lorentz angle.
 
@@
          \centering
-\includegraphics[scale=0.37]{fig/1st_pass_delta_phi.png}
-\caption[]{\small\sf $\Delta \phi$ versus TDC distribution for the simulated hits locating in one slice centered at 35 mm.}
+         \includegraphics[scale=0.37]{fig/TdcPhi_p1_10.png}
+         \caption{$\Delta \phi$ versus TDC distribution for the simulated hits 
+         locating in one slice centered at 35 mm.}
          \label{fig:1st_pass_delta_phi}
@@
 
-\item Using this first measurement, we can calculate a new correlation between $R$ and TDC.
-The result, shown in figure~\ref{fig:R_TDC}, is very close to linear explaining the fast convergence of our procedure.
-\\
+   \item Using this first measurement, we can calculate a new correlation 
+      between $R$ and TDC. The result, shown in figure~\ref{fig:R_TDC}, is very 
+      close to linear explaining the fast convergence of our procedure.
 
@@
          \includegraphics[scale=0.37]{fig/R_TDC.png}
-\caption[]{\small\sf The calculated R versus the time is corrected by the parameters of $\Delta \phi$ from the first pass.}
+         \caption{The calculated R versus the time is corrected by the 
+         parameters of $\Delta \phi$ from the first pass.}
          \label{fig:R_TDC}
@@
 
-\item In the second pass, we associate simulated helium positions to physical hits according to their calculated correlation and obtain new $\Delta \phi$ distributions.\\
-\item We finally parametrize the $\Delta\phi$ distributions with a fit as can be seen in figure~\ref{fig:DELTA_PHI_TDC}, which shows the final $\Delta \phi$ versus TDC with a red line representing our drift paths fit.
+   \item In the second pass, we associate simulated helium positions to 
+      physical hits according to their calculated correlation and obtain new 
+      $\Delta \phi$ distributions.
+
+   \item We finally parametrize the $\Delta\phi$ distributions with a fit as 
+      can be seen in figure~\ref{fig:DELTA_PHI_TDC}, which shows the final 
+      $\Delta \phi$ versus TDC with a red line representing our drift paths 
+      fit.
 \end{itemize}
@@
 \centering
-\includegraphics[scale=0.37]{fig/DELTA_PHI_TDC.png}
-\caption[]{\small\sf $\Delta \phi$ versus TDC distribution in the second pass for the slice centered at 35 mm longitudinal position along the RTPC.
-The red line represents the final drift paths in this slice.}
+\includegraphics[scale=0.37]{fig/FitResult_p2_10.png}
+\caption{$\Delta \phi$ versus TDC distribution in the second pass for the slice 
+centered at 35 mm longitudinal position along the RTPC. The red line represents 
+the final drift paths in this slice.}
 \label{fig:DELTA_PHI_TDC}
@@
 
-To verify the stability of the drift paths, this procedure was carried out using both the 1.204 GeV data set from the beginning of the run period and the 1.269 GeV data from the end of the run period.
-As a result, we found very similar drift paths and reached the conclusion that whatever changed in the setting affected only the drift speed.
+To verify the stability of the drift paths, this procedure was carried out 
+using both the 1.204 GeV data set from the beginning of the run period and the 
+1.269 GeV data from the end of the run period. As a result, we found very 
+similar drift paths and reached the conclusion that whatever changed in the 
+setting affected only the drift speed.
 
@@
 
-The parametrization of the drift speed and the drift paths were carried out using only the TDCs, gain calibration goal is to equalize the gains in ADC/MeV over the full RTPC.
-The gain of each pad is the ratio between the actual deposited energy and the registered ADC value.
-We identified three different methods to extract such gains.
-The first is to compare the experimental energy deposit to the expected value calculated from Bethe-Block formula (ref).
-The second method is to compare the experimental ADCs to the energy deposited in GEANT4 by simulated tracks (using the same elastic events than for the drift paths calibration).
-In the third method, the ADCs of each pad is compared to the ADCs of the other pads inside each track.
+The parametrization of the drift speed and the drift paths were carried out 
+using only the TDCs, gain calibration goal is to equalize the gains in ADC/MeV 
+over the full RTPC. The gain of each pad is the ratio between the actual 
+deposited energy and the registered ADC value. We identified three different 
+methods to extract such gains. The first is to compare the experimental energy 
+deposit to the expected value calculated from Bethe-Block formula (ref). The 
+second method is to compare the experimental ADCs to the energy deposited in 
+GEANT4 by simulated tracks (using the same elastic events than for the drift 
+paths calibration). In the third method, the ADCs of each pad is compared to 
+the ADCs of the other pads inside each track.
 
@@
 
-To perform the second method it requires a very good GEANT4 simulation including drift paths, but also drift and amplification spreads of the charges before reaching the pad, so that the simulated hits match the experimental ones.
-Moreover, the simulation has to match the data acquisition (DAQ) features that can lead to cutting out hits.
-After setting the simulation properly, we can compare simulation to data on an event by event basis as in figure~\ref{fig:EVENT_adc_tdc}.
-In this step, the gain for each pad is defined as the ratio of the measured ADCs to the simulated deposited energy.
+To perform the second method it requires a very good GEANT4 simulation 
+including drift paths, but also drift and amplification spreads of the charges 
+before reaching the pad, so that the simulated hits match the experimental 
+ones. Moreover, the simulation has to match the data acquisition (DAQ) features 
+that can lead to cutting out hits. After setting the simulation properly, we 
+can compare simulation to data on an event by event basis as in 
+figure~\ref{fig:EVENT_adc_tdc}. In this step, the gain for each pad is defined 
+as the ratio of the measured ADCs to the simulated deposited energy.
 
@@
 \includegraphics[scale=0.350]{fig/EVENT_adc_tdc.png}
-\caption[]{\small\sf Simulated (upper) and experimental (lower) ADCs and TDCs distributions of a track. The colors indicate the pads, same color in top and bottom indicate that they are the same pad.}
+\caption{Simulated (upper) and experimental (lower) ADCs and TDCs distributions 
+of a track. The colors indicate the pads, same color in top and bottom indicate 
+that they are the same pad.}
 \label{fig:EVENT_adc_tdc}
@@
    \includegraphics[scale=0.26]{fig/dedx_p_exp_1st.png}
-\caption[]{\small\sf $\small{\frac{dE}{dX}}$ vs.
-p distribution for the left half of the RTPC (left) and for the right half (right).
-Here, $\small{\frac{dE}{dX}}$ is calculated using the gains of the first method.
-The lines are theoretical expectations from Bethe-Bloch formula for $^4$He, $^3$He, $^3$H and $^2$H (d).}
+   \caption{$\small{\frac{dE}{dX}}$ vs. p distribution for the left half of the 
+      RTPC (left) and for the right half (right). Here, $\small{\frac{dE}{dX}}$ 
+   is calculated using the gains of the first method.  The lines are 
+theoretical expectations from Bethe-Bloch formula for $^4$He, $^3$He, $^3$H and 
+$^2$H (d).}
 \label{fig:dedx_p_exp_1st}
@@
 \includegraphics[scale=0.26]{fig/dedx_p_exp_2nd.png}
-\caption[]{\small\sf $\small{\frac{dE}{dX}}$ vs.
-p distribution for the left half of the RTPC (left) and for the right half (right).
-Here, $\small{\frac{dE}{dX}}$ is calculated using the gains of the second method.
-The lines are theoretical expectations from Bethe-Bloch formula for $^4$He, $^3$He, $^3$H and $^2$H (d).}
+\caption{$\small{\frac{dE}{dX}}$ vs. p distribution for the left half of the 
+   RTPC (left) and for the right half (right). Here, $\small{\frac{dE}{dX}}$ is 
+   calculated using the gains of the second method.  The lines are theoretical 
+   expectations from Bethe-Bloch formula for $^4$He, $^3$He, $^3$H and $^2$H 
+(d).}
 \label{fig:dedx_p_exp_2nd}
@@
 
-A set of gains has been extracted from each method, in figure~\ref{fig:dedx_p_exp_1st}, we have $\small{\frac{dE}{dX}}$ calculated using the first method's gains, while in Figure~\ref{fig:dedx_p_exp_2nd} we use the second method's gains.
-From these, we concluded that the gains of the second method match best the theoretical lines.
-This is not surprising since calibrating with full tracks leads to mixing the gains from the different pads.
-So it seems that even with several iterations, we could not decipher properly the effects of individual pads with this method.
+A set of gains has been extracted from each method, in 
+figure~\ref{fig:dedx_p_exp_1st}, we have $\small{\frac{dE}{dX}}$ calculated 
+using the first method's gains, while in Figure~\ref{fig:dedx_p_exp_2nd} we use 
+the second method's gains. From these, we concluded that the gains of the 
+second method match best the theoretical lines. This is not surprising since 
+calibrating with full tracks leads to mixing the gains from the different pads.  
+So it seems that even with several iterations, we could not decipher properly 
+the effects of individual pads with this method.
 
@@
 \includegraphics[scale=0.27]{fig/noisy_pad_before_rejection.png}
-\caption[]{\small\sf }
+\caption{}
 \label{fig:noisy_pad_before_rejection}
@@
 \includegraphics[scale=0.27]{fig/noisy_pad_after_rejection.png}
-\caption[]{\small\sf }
+\caption{}
 \label{fig:noisy_pad_after_rejection}
@@
 
-In order to reconstruct tracks we first select good hits.
-This means rejecting out-of-time hits and hits linked to the electronic noise.
-The second step is space-reconstructing the hits using the extracted drift speed and drift path parameters.
-For each registered hit, we calculate a position of emission from the recorded time (TDC) and the position of the recording pad.
-The third step is to create chains of hits.
-The maximum distance between two close adjacent hits has to be less than 10.5 mm to chain them, this roughly correspond to neighbors and next to neighbors.
-Then, we fit the chains that have a minimum of 10 hits.
-We make the fit in two iterations, first, all the hits of the chain together with the beam line are fitted with a helix.
-For the second iteration, the hits that are 5 mm or farther from the first fit are excluded.
+In order to reconstruct tracks we first select good hits. This means rejecting 
+out-of-time hits and hits linked to the electronic noise. The second step is 
+space-reconstructing the hits using the extracted drift speed and drift path 
+parameters. For each registered hit, we calculate a position of emission from 
+the recorded time (TDC) and the position of the recording pad. The third step 
+is to create chains of hits. The maximum distance between two close adjacent 
+hits has to be less than 10.5 mm to chain them, this roughly correspond to 
+neighbors and next to neighbors. Then, we fit the chains that have a minimum of 
+10 hits. We make the fit in two iterations, first, all the hits of the chain 
+together with the beam line are fitted with a helix. For the second iteration, 
+the hits that are 5 mm or farther from the first fit are excluded.
 
@@
 \end{equation}
-Where the sum runs over all the hits of the track and $G_{i}$ is the gain of the associated pad. The $vtl$ is the visible track length in the active drift volume.
+Where the sum runs over all the hits of the track and $G_{i}$ is the gain of 
+the associated pad. The $vtl$ is the visible track length in the active drift 
+volume.
 

### 2017-01-10 eg6-letters/final_checks/DVCS-CAN-Meeting-Comments.tex
update the NIM paper

--- 2016-11-04 final_checks/DVCS-CAN-Meeting-Comments.tex
@@
 dependences of $A_{LU}$ at $\phi = 90 ^{\circ}$, from fitting the signals in 
-fig \ref{fig:BSA_ME_bins_sig}, are presented in fig \ref{ig:ALU_ME_bins_sig} 
+fig \ref{fig:BSA_ME_bins_sig}, are presented in fig \ref{fig:ALU_ME_bins_sig} 
 with and without cutting the tails in the missing energy distribution. One can 

### 2017-01-10 eg6-letters/analysis-note-vf/for_tab.C

@@ -1,0 +1,98 @@
+//________________      bins in Q2                  ____________________//                          
+
+     24.0  &  0.1575 $\pm$  0.1016 $\pm$ 0.0257 \\ 
+     60.0  &  0.3656 $\pm$  0.0903 $\pm$ 0.0188 \\ 
+     98.5  &  0.3586 $\pm$  0.1051 $\pm$ 0.0403 \\ 
+     141.2 &  0.1498 $\pm$  0.1645 $\pm$ 0.0267 \\ 
+     177.7 &  0.1849 $\pm$  0.1664 $\pm$ 0.0278 \\ 
+     219.3 &  0.0555 $\pm$  0.1475 $\pm$ 0.0248 \\ 
+     263.4 & -0.3184 $\pm$  0.1171 $\pm$ 0.0389 \\ 
+     302.7 & -0.1160 $\pm$  0.0975 $\pm$ 0.0263 \\ 
+     337.9 & -0.2805 $\pm$  0.0952 $\pm$ 0.0343 \\ 
+                                                  
+     21.1  &  0.1694 $\pm$  0.0858 $\pm$ 0.0267 \\
+     55.9  &  0.2889 $\pm$  0.0859 $\pm$ 0.0250 \\
+     96.7  &  0.4761 $\pm$  0.1304 $\pm$ 0.0426 \\
+     138.9 &  0.2134 $\pm$  0.1784 $\pm$ 0.0250 \\
+     179.8 &  0.2996 $\pm$  0.1967 $\pm$ 0.0302 \\
+     218.7 & -0.2375 $\pm$  0.1913 $\pm$ 0.0344 \\
+     263.5 & -0.2521 $\pm$  0.1398 $\pm$ 0.0366 \\
+     302.6 & -0.3526 $\pm$  0.0855 $\pm$ 0.0383 \\
+     338.0 & -0.2344 $\pm$  0.0801 $\pm$ 0.0261 \\
+                                                  
+     21.0  &  0.1626 $\pm$  0.0779 $\pm$ 0.0234 \\
+     56.4  &  0.3433 $\pm$  0.0817 $\pm$ 0.0185 \\
+     95.9  &  0.2443 $\pm$  0.1270 $\pm$ 0.0173 \\
[…]

### 2017-01-11 eg6-letters/long-paper/prc-dvcshelium.tex
Add long paper properly

\documentclass[aps,prc,preprint,superscriptaddress]{revtex4-1}

\begin{document}

%Title of paper
\title{Measurement of deeply virtual Compton scattering off helium-4}

% repeat the \author .. \affiliation  etc. as needed
% \email, \thanks, \homepage, \altaffiliation all apply to the current
% author. Explanatory text should go in the []'s, actual e-mail
% address or url should go in the {}'s for \email and \homepage.
% Please use the appropriate macro foreach each type of information

% \affiliation command applies to all authors since the last
% \affiliation command. The \affiliation command should follow the
% other information
% \affiliation can be followed by \email, \homepage, \thanks as well.
\author{CLAS et al.}
%\email[]{Your e-mail address}
%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}
\affiliation{JLab et al.}

%Collaboration name if desired (requires use of superscriptaddress
%option in \documentclass). \noaffiliation is required (may also be
%used with the \author command).
%\collaboration can be followed by \email, \homepage, \thanks as well.
\collaboration{CLAS Collaboration}
\noaffiliation

\date{\today}

\begin{abstract}
% insert abstract here
\end{abstract}

% insert suggested PACS numbers in braces on next line
\pacs{}

\maketitle

\section{Introduction}

\section{Theoretical Framework}

  \subsection{The GPD Formalism}

  \subsection{Incoherent Nuclear DVCS}

  \subsection{Coherent Nuclear DVCS}

\section{The E08-024 Experiment}

  \subsection{The CLAS DVCS Setting}

  \subsection{The Radial Time Projection Chamber}

\section{Data Analysis}

  \subsection{Particle Identification}

  \subsection{Monte-Carlo Simulation}

  \subsection{Kinematic Corrections}

  \subsection{Background Reduction}

\section{Incoherent DVCS}

  \subsection{Event Selection}

  \subsection{Systematic Errors}

\section{Coherent DVCS}

  \subsection{Event Selection}

  \subsection{Systematic Errors}

\section{Results}

  \subsection{Incoherent DVCS}

  \subsection{Coherent DVCS}

\section{Summary}

% \begin{figure}
% \includegraphics{}%
% \caption{\label{}}
% \end{figure}

% Surround figure environment with turnpage environment for landscape
% figure
% \begin{turnpage}
% \begin{figure}
% \includegraphics{}%
% \caption{\label{}}
% \end{figure}
% \end{turnpage}

% tables should appear as floats within the text
%
% Here is an example of the general form of a table:
% Fill in the caption in the braces of the \caption{} command. Put the label
% that you will use with \ref{} command in the braces of the \label{} command.
% Insert the column specifiers (l, r, c, d, etc.) in the empty braces of the
% \begin{tabular}{} command.
% The ruledtabular enviroment adds doubled rules to table and sets a
% reasonable default table settings.
% Use the table* environment to get a full-width table in two-column
% Add \usepackage{longtable} and the longtable (or longtable*}
% environment for nicely formatted long tables. Or use the the [H]
% placement option to break a long table (with less control than 
% in longtable).
% \begin{table}%[H] add [H] placement to break table across pages
% \caption{\label{}}
% \begin{ruledtabular}
% \begin{tabular}{}
% Lines of table here ending with \\
% \end{tabular}
% \end{ruledtabular}
% \end{table}

% Specify following sections are appendices. Use \appendix* if there
% only one appendix.
%\appendix
%\section{}

% Surround table environment with turnpage environment for landscape
% table
% \begin{turnpage}
% \begin{table}
% \caption{\label{}}
% \begin{ruledtabular}
% \begin{tabular}{}
% \end{tabular}
% \end{ruledtabular}
% \end{table}
% \end{turnpage}

\begin{acknowledgments}
 Put your acknowledgments here.
\end{acknowledgments}

% Create the reference section using BibTeX:
\bibliography{basename of .bib file}

\end{document}
%
% ****** End of file apstemplate.tex ******

### 2017-01-16 analysis-note-vf/Appendix.tex
some fixing

@@
 \hline
-$\Delta \phi$ &  1.79405e-01 & 4.53791e-01 \\
-\hline
-$E_{X}$ ($e^{4}He\gamma X$) &  1.56814e-02 & 2.51492e-01 \\ 
-\hline
-$M^{2}_{X}$ ($e^{4}He\gamma X$) &  -2.96869e-03 & 9.10158e-03 \\ 
+$\Delta \phi$ &  1.86020e-01 & 4.64936e-01 \\
+\hline
+$E_{X}$ ($e^{4}He\gamma X$) &  1.48023e-02 & 2.51854e-01 \\ 
+\hline
+$M^{2}_{X}$ ($e^{4}He\gamma X$) &  -2.98662e-03 & 9.28645e-03 \\ 
 \hline
@@
 \hline
-$M^{2}_{X}$ ($e^{4}HeX$) &  -1.72013e-02 & 2.33988e-01 \\
-\hline
- $M^{2}_{X}$ ($e\gamma X$) &  1.40066e+01 & 1.85929 \\
+$M^{2}_{X}$ ($e^{4}HeX$) & -3.45128e-02 & 2.28247e-01 \\
+\hline
+$M^{2}_{X}$ ($e\gamma X$) & 1.39930e+01 & 1.61245 \\
 \hline
@@
 proton $A_{LU}$ at $\phi = 90^{\circ}$ were fitted as a function of $-t$ for 
-the different bins in $x_B$ and $Q^2$. Then, the parameters of the fits were 
-parametrized as a function of $x_B$ assuming that the dependence on $Q^2$ is 
-negligible, figure \ref{fig:free-proton-alu}. Finally, the free proton 
-asymmetries were calculated at the same measured incoherent and coherent
-kinematic values.  The statistical errors on the calculated asymmetries were 
-calculated using the fit errors.\\
+the different bins in $x_B$ and $Q^2$, figure \ref{fig:free-proton-alu}.  
+Finally, the free proton asymmetries were calculated at the same measured 
+incoherent and coherent $-t$ values from the t-dependence fit of the closest 
+bin in $x_B$ and $Q^2$.  The statistical errors on the calculated asymmetries 
+were calculated using the fit errors.\\
 
@@
   \hline
-(1.395, 0.166, 0.407) &  0.136 $\pm$ 0.027   &    0.1691 $\pm$ 0.0592   &  0.8042 $\pm$ 0.3248  &  0.2050 &  0.6634 &  0.1408 \\
-(1.886, 0.233, 0.499) &  0.156 $\pm$ 0.033   &    0.2081 $\pm$ 0.0738   &  0.7494 $\pm$ 0.3101  &  0.2244 &  0.6951 &  0.0543 \\ 
-(2.338, 0.290, 0.521) &  0.154 $\pm$ 0.038   &    0.2129 $\pm$ 0.0777   &  0.7268 $\pm$ 0.3206  &  0.2177 &  0.7110 &  0.0158 \\
-(3.098, 0.379, 0.650) &  0.122 $\pm$ 0.042   &    0.1765 $\pm$ 0.0676   &  0.6956 $\pm$ 0.3581  &  0.2017 &  0.6088 &  0.0868 \\
+ (1.395, 0.166, 0.407) &  0.136 $\pm$ 0.027 & 0.2061 $\pm$ 0.0092 & 0.6595 $\pm$ 0.1361 & 0.2050 & 0.6634 & -0.0039 \\
+ (1.886, 0.233, 0.499) &  0.156 $\pm$ 0.033 & 0.2192 $\pm$ 0.0421 & 0.7114 $\pm$ 0.2044 & 0.2244 & 0.6951 &  0.0163 \\
+ (2.338, 0.290, 0.521) &  0.154 $\pm$ 0.038 & 0.2197 $\pm$ 0.0308 & 0.7042 $\pm$ 0.2004 & 0.2177 & 0.7110 & -0.0068 \\
+ (3.098, 0.379, 0.650) &  0.122 $\pm$ 0.042 & 0.2143 $\pm$ 0.0801 & 0.5727 $\pm$ 0.2907 & 0.2017 & 0.6088 & -0.0361 \\
    \hline \hline  \hline
-(1.425, 0.162, 0.397) &  0.118 $\pm$ 0.026   &    0.1686 $\pm$ 0.0587   &  0.7045 $\pm$ 0.2913  &  0.1885 &  0.6302 &  0.0743 \\
-(1.922, 0.227, 0.418) &  0.178 $\pm$ 0.029   &    0.2122 $\pm$ 0.0740   &  0.8429 $\pm$ 0.3257  &  0.2135 &  0.8379 &  0.005  \\
-(2.354, 0.287, 0.492) &  0.151 $\pm$ 0.036   &    0.2209 $\pm$ 0.0795   &  0.6847 $\pm$ 0.2974  &  0.2170 &  0.6972 &  0.0125 \\
-(2.987, 0.390, 0.714) &  0.132 $\pm$ 0.050   &    0.1562 $\pm$ 0.0615   &  0.8457 $\pm$ 0.4661  &  0.2103 &  0.6281 &  0.2176 \\
+ (1.425, 0.162, 0.397) &  0.118 $\pm$ 0.026 & 0.2124 $\pm$ 0.0091 & 0.5591 $\pm$ 0.1273 & 0.1885 & 0.6302 & -0.0711 \\
+ (1.922, 0.227, 0.418) &  0.178 $\pm$ 0.029 & 0.2310 $\pm$ 0.0406 & 0.7743 $\pm$ 0.1874 & 0.2135 & 0.8379 & -0.0636 \\
+ (2.354, 0.287, 0.492) &  0.151 $\pm$ 0.036 & 0.2257 $\pm$ 0.0309 & 0.6701 $\pm$ 0.1873 & 0.2170 & 0.6972 & -0.0271 \\
+ (2.987, 0.390, 0.714) &  0.132 $\pm$ 0.050 & 0.1985 $\pm$ 0.0837 & 0.6654 $\pm$ 0.3802 & 0.2103 & 0.6281 &  0.0373 \\
    \hline  \hline  \hline
-(1.823, 0.213, 0.145) &  0.146 $\pm$ 0.027   &    0.2304 $\pm$ 0.0677   &  0.6363 $\pm$ 0.2223  &  0.2438 &  0.6013 &  0.035  \\
-(2.127, 0.255, 0.282) &  0.150 $\pm$ 0.031   &    0.2641 $\pm$ 0.0848   &  0.5700 $\pm$ 0.2177  &  0.2410 &  0.6248 &  0.0548 \\
-(2.308, 0.284, 0.490) &  0.163 $\pm$ 0.039   &    0.2200 $\pm$ 0.0791   &  0.7400 $\pm$ 0.3209  &  0.2195 &  0.7425 &  0.0025 \\
-(2.406, 0.308, 1.107) &  0.115 $\pm$ 0.054   &    0.0939 $\pm$ 0.0429   &  1.2240 $\pm$ 0.8030  &  0.1235 &  0.9311 &  0.2929 \\
+ (1.823, 0.213, 0.145) &  0.146 $\pm$ 0.027 & 0.2463 $\pm$ 0.0378 & 0.5950 $\pm$ 0.1447 & 0.2438 & 0.6013 & -0.0063 \\
+ (2.127, 0.255, 0.282) &  0.150 $\pm$ 0.031 & 0.2259 $\pm$ 0.0182 & 0.6664 $\pm$ 0.1477 & 0.2410 & 0.6248 &  0.0416 \\
+ (2.308, 0.284, 0.490) &  0.163 $\pm$ 0.039 & 0.2257 $\pm$ 0.0309 & 0.7219 $\pm$ 0.2002 & 0.2195 & 0.7425 & -0.0206 \\
+ (2.406, 0.308, 1.107) &  0.115 $\pm$ 0.054 & 0.1265 $\pm$ 0.0345 & 0.9087 $\pm$ 0.4944 & 0.1235 & 0.9311 & -0.0224 \\
    \hline  \hline  \hline
-(1.143, 0.132, 0.096) &  0.332 $\pm$ 0.051   &    0.1821 $\pm$ 0.0528   &  1.8267 $\pm$ 0.6017  &  0.2447 &  1.3596 &  0.4671 \\
-(1.423, 0.170, 0.099) &  0.353 $\pm$ 0.051   &    0.1857 $\pm$ 0.0534   &  1.9044 $\pm$ 0.6146  &  0.2518 &  1.4050 &  0.4994 \\
-(1.902, 0.224, 0.107) &  0.258 $\pm$ 0.050   &    0.1835 $\pm$ 0.0524   &  1.4063 $\pm$ 0.4863  &  0.2359 &  1.0941 &  0.3122 \\
+ (1.143, 0.132, 0.096) &  0.282 $\pm$ 0.078 & 0.1956 $\pm$ 0.1028 & 1.4444 $\pm$ 0.8584 & 0.2447 & 1.1524 &  0.2920 \\
+ (1.423, 0.170, 0.099) &  0.364 $\pm$ 0.064 & 0.1703 $\pm$ 0.0201 & 2.1366 $\pm$ 0.4529 & 0.2518 & 1.4456 &  0.6910 \\
+ (1.902, 0.224, 0.107) &  0.258 $\pm$ 0.078 & 0.1814 $\pm$ 0.0822 & 1.4239 $\pm$ 0.7774 & 0.2359 & 1.0937 &  0.3302 \\
      \hline \hline  \hline
-(1.164, 0.132, 0.095) &  0.373 $\pm$ 0.073   &    0.1819 $\pm$ 0.0529   &  2.0503 $\pm$ 0.7190  &  0.2234 &  1.6696 &  0.3807 \\
-(1.439, 0.170, 0.099) &  0.267 $\pm$ 0.086   &    0.1859 $\pm$ 0.0535   &  1.4361 $\pm$ 0.6231  &  0.2432 &  1.0978 &  0.3383 \\
-(1.844, 0.225, 0.107) &  0.362 $\pm$ 0.092   &    0.1830 $\pm$ 0.0522   &  1.9812 $\pm$ 0.7571  &  0.2515 &  1.4421 &  0.5391 \\
+ (1.164, 0.132, 0.095) &  0.313 $\pm$ 0.069 & 0.1956 $\pm$ 0.1028 & 1.5999 $\pm$ 0.9132 & 0.2234 & 1.4011 &  0.1988 \\
+ (1.439, 0.170, 0.099) &  0.237 $\pm$ 0.070 & 0.1664 $\pm$ 0.0209 & 1.4251 $\pm$ 0.4563 & 0.2432 & 0.9745 &  0.4506 \\
+ (1.844, 0.225, 0.107) &  0.299 $\pm$ 0.120 & 0.1787 $\pm$ 0.0844 & 1.6736 $\pm$ 1.0599 & 0.2515 & 1.1889 &  0.4847 \\
       \hline  \hline  \hline
-(1.493, 0.177, 0.1)   &  0.326 $\pm$ 0.030   &    0.1863 $\pm$ 0.0535   &  1.7498 $\pm$ 0.5292  &  0.2453 &  1.3289 &  0.4209 \\
+ (1.493, 0.177, 0.1)   &  0.331 $\pm$ 0.030 & 0.1575 $\pm$ 0.0341 & 2.1049 $\pm$ 0.4939 & 0.2453 & 1.3493 &  0.7556 \\
 

### 2017-01-16 analysis-note-vf/RTPC.tex
some fixing

--- 2016-09-08 analysis-note-v2/RTPC.tex
@@
 the coherent DVCS channel, have an average momentum around 200 MeV/c. CLAS 
-cannot detect such low energy particles, for exemple protons are detected with 
+cannot detect such low energy particles, for example protons are detected with 
 a threshold of about 250 MeV/c, which will be even higher for helium. In order 
@@
 during the BoNuS run \cite{BONUS}, was added to CLAS. In 2009, the CLAS-EG6 
-group \cite{proposal} has built this RTPC, figure \ref{fig:RTPC2} shows a 
-close photo of the RTPC, while figure \ref{fig:RTPC_xscetion} shows a 
-schematic drawing of its internal structure. It is a 200~mm-long and 
-150~mm-diameter TPC, composed of two electronically separated modules, each 
-covering about 150$^{\circ}$ of the azimuthal angle. The RTPC tracks the 
-charged particles through the ionization centers they leave in the gas-filled 
-detection volume. Then, the ionized electrons drift under the effect of an 
-electric field and are amplified by a gas electron multiplier system before to 
-be detected on collection pads.
+group \cite{proposal} has built this RTPC, figure \ref{fig:RTPC2} shows a close 
+photo of the RTPC, while figure \ref{fig:RTPC_xscetion} shows a schematic 
+drawing of its internal structure. It is a 200~mm-long and 150~mm-diameter TPC, 
+composed of two electronically separated modules, each covering about 
+150$^{\circ}$ of the azimuthal angle. The RTPC tracks the charged particles 
+through the ionization centers they leave in the gas-filled detection volume.  
+Then, the ionized electrons drift under the effect of an electric field and are 
+amplified by a gas electron multiplier system before to be detected on 
+collection pads.
 

### 2017-01-16 analysis-note-vf/results.tex
some fixing

@@
 As shown at the beginning of this chapter, one can extract both real and
-imaginary parts of the 
-$^4$He CFF $\mathcal{H}_A$ from fitting the beam-spin asymmetry signals. This extraction
-is fully model independent and, in contrast with the proton's GPD extraction, does not
-make any assumption on additional GPDs. In this 
-work, we performed the first experimental extraction of $\mathcal{H}_A$ from 
-exclusive measurements of the reaction. The results are presented in figure 
-\ref{fig:HA_CFF} as function of $Q^{2}$, $x_B$, and $-t$.
+imaginary parts of the $^4$He CFF $\mathcal{H}_A$ from fitting the beam-spin 
+asymmetry signals. This extraction is fully model independent and, in contrast 
+with the proton's GPD extraction, does not make any assumption on additional 
+GPDs. In this work, we performed the first experimental extraction of 
+$\mathcal{H}_A$ from exclusive measurements of the reaction. The results are 
+presented in figure \ref{fig:HA_CFF} as function of $Q^{2}$, $x_B$, and $-t$.
 
 Within the given uncertainties, our results show a slight dependence on 
-$Q^{2}$, $x_B$, and $-t$.  More work is needed on the theoretical models to 
-give predictions for $\mathcal{H}_A$.  One can see a difference between the 
+$Q^{2}$, $x_B$, and $-t$, which are in agreement with the theoretical 
+calculations for $\mathcal{H}_A$.  One can see a difference between the 
 precision of the extracted real and imaginary parts, indicating the fact that 
@@
 \includegraphics[scale=0.9]{fig_Dec2016/Coherent_CFF.pdf}
-\caption{The model-independent extraction of the imaginary (blue points) and 
-real (red points) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of 
-$Q^{2}$ (on the top right), $x_B$ (on the top left), and $t$ (on the bottom).}
+\caption{The model-independent extraction of the imaginary (black full squares 
+in the top panel plots) and real (empty black squares in the bottom panel 
+plots) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of $Q^{2}$ (on the 
+left), $x_B$ (on the middle), and $t$ (on the right). The full and dashed red 
+curves are calculations based on the impulse approximation from 
+\cite{Vadim_priv}.  The black curves in the right plots, t-dependence plots, 
+are calculations from a convolution model based on the VGG model for the 
+nucleon's GPDs \cite{Guidal_priv}. The cyan curve on the top-right plot is from 
+the off-shell calculations presented in section \ref{Theoretical_hypotheses} 
+based on reference \cite{GonzalezHernandez:2012jv}.  }
 \label{fig:HA_CFF}
@@
    results.  The blue and red curves are from an on-shell calculations from S.  
-Liuti and K. Taneja \cite{simonetta_2}.} \label{fig:incoh_EMC_ratio_ALU_proton}
+Liuti and K. Taneja \cite{simonetta_2}. The solid and dashed black curves are 
+from the off-shell calculations \cite{EMC_vadim_2}.} 
+\label{fig:incoh_EMC_ratio_ALU_proton}
 \end{figure}
@@
    blue curves, and the model predictions from V. Guzey et al. based on the 
-off-shell calculations \cite{EMC_vadim_4}, in black, purple and brown dashed 
-curves.}
+off-shell calculations \cite{EMC_vadim_4}, in black, purple and brown curves.}
 \label{fig:coh_EMC_ratio_ALU}

### 2017-01-16 eg6-letters/coherent/HeliumCohDVCS.tex
some fixing

@@
 for the past three decades, as we are still unable to explain properly the 
-infamous EMC effect~\cite{}. First observed in 197X by the EMC 
+infamous EMC effect~\cite{}. First observed in 1983 by the EMC 
 collaboration, it describes the difference between the partonic structure of
@@
 overwhelming majority of the cases to the incoherent break-up of the target.
-
-%\section{Experiment}
 The HERMES collaboration has measured nuclear DVCS~\cite{} without the 
@@
 based on the measurement of the transfered 4-momentum $t$, leading
-to controversy in the interpretation of their results~\cite{}. We report
-here our exclusive measurement of coherent DVCS off helium-4 at the Jefferson labortory
+to controversy in the interpretation of their results~\cite{}.
+
+%\section{Experiment}
+We report here our exclusive measurement of coherent DVCS off helium-4 
+at the Jefferson labortory
 (JLab), while our results for the incoherent channel will be presented in
@@
 
-\begin{figure*}[tbp]
-\caption{\label{fig:exclu} Exclusivity cuts}
-\includegraphics[width=17.2cm]{all_coh_exc_cuts.png}
-\end{figure*}
-
-In order to insure the coherence of the process, we also detect the recoiling 
+In order to ensure the coherence of the process, we also detect the recoiling 
 helium-4 nuclei. We built a small and light radial time projection chamber 
@@
 elastic scattering produced with a 1.2~GeV electron beam.
+To ensure that the process is exclusive, we apply cuts on 
+several kinematic variables (figure~\ref{fig:exclu}) such as missing energy,
+mass and momentum. The cuts are chosen to represent consistently 3 half width 
+at half maximum in order to avoid any bias in the selection.
 
-\begin{figure}[htbp]
-\caption{\label{fig:rtpc} RTPC description}
-\includegraphics[width=8cm]{RTPC.png}
+%\section{DVCS Events Selection}
+
+\begin{figure}[tb!]
+\caption{\label{fig:rtpc} A cross section of the RTPC taken on a plane perpendicular to the 
+beam line, with a typical $^4He$ track crossing the drift volume.}
+\includegraphics[width=7.4cm]{RTPC.png}
 \end{figure}
 
-%\section{DVCS Events Selection}
-Explain exclusivity cuts
+\begin{figure*}[tb!]
+\caption{\label{fig:exclu} The coherent DVCS exclusivity cuts. The blue 
+distributions represent the coherent DVCS events candidate. The shaded 
+distributions represent the events which passed all the exclusivity cuts 
+except the quantity plotted. The vertical red lines represent $3\sigma$ cuts.}
+\includegraphics[width=16.0cm]{all_coh_exc_cuts.png}
+\end{figure*}
 
 We identified several background contributions to the DVCS process, in 
-particular accidental events and exclusive deeply virtual $\pi^0$ production (DV$\pi^0$P). The accidental
-events happen when an helium nuclei is mistakenly associated with our event, this 
-possibility is suppressed by the limited phase space allowed but enhanced by the
-low time resolution of the RTPC (~200 ns). We evaluated this contribution by
+particular accidental events and exclusive deeply virtual 
+$\pi^0$ production (DV$\pi^0$P). The accidental
+events where the different particles come from different events are 
+suppressed by the limited phase space allowed by the exclusivity cuts. We 
+estimate the accidental events to represent 4.1\% of our sample. This relatively 
+large number is due to the small cross section of the DVCS. We evaluated this contribution by
 selecting events passing all our cuts but with particles originating from 
-different verteces. With this method, we found this background to represent 
-4.1\%. The DV$\pi^0$P events can easily be mistaken
-with DVCS events when one of the two photons of $\pi^0$ decay is produced at
-low energy in the laboratory frame. In order to estimate the importance of
-this background, we developped an event generator DV$\pi^0$P 
-that we calibrated to match our experimental yields. We used this generator together 
-with a GEANT3~\cite{} simulation of our detection system to estimate the ratio 
-of acceptance between measured DV$\pi^0$P and DV$\pi^0$P that would pass our 
+different verteces.
+
+Another important source of background is the deeply virtual 
+$\pi^0$ production (DV$\pi^0$P), which can easily be mistaken
+with DVCS when one of the two photons of the $\pi^0$ decay is produced at
+low energy in the laboratory frame. To estimate the importance of
+this background, we developped an event generator 
+that we calibrated to match our measured experimental yield of exclusive 
+$pi^0$. We used this generator together 
+with a GEANT3 simulation of our detection system to estimate the ratio 
+of acceptance between DV$\pi^0$P where the two photons are detected and those
+where only one photon is detected and would pass our 
 DVCS selection cuts. This ratio obtained from simulation is then multiplied by 
-the measured yield of DV$\pi^0$P events, indicating a contamination of XX to XX\%. 
-%(We NEED a figure of that in the note!!!)
-
-Systematic errors
+the measured yield of DV$\pi^0$P events, indicating a contamination of 2 to 4\%. 
+The study of systematics errors showed that the main contributions come from 
+the choice of the DVCS exclusivity cuts (8\%) and the large binning size 
+(5.1\%). However added quadratically, these errors sum up to 10\% which remain 
+for all bins well below the statistical errors.
 
@@
 
-Extraction of assymetries (figure~\ref{fig:assym})
+We show the obtained assymetries after all corrections as a function of 
+$\phi$ and $-t$ in figure~\ref{fig:assym}. The first observation is the
+that the assymetries follow the expected sin($\phi$) dominated shape
+and that the size of these assymetries at $90^\circ$ is much larger than the one
+observed on proton targets~\cite{} (15-20\%). These results were expected from 
+theory~\cite{} and demonstrate that we successfully isolated the coherent
+DVCS channel.
 
 \begin{figure*}[htbp]
-\caption{\label{fig:assym} Assymetries}
+\caption{\label{fig:assym} The coherent $A_{LU}$ as a function of $\phi$ in 
+$-t$ bins. The error bars 
+represent the statistical and the systematic uncertainties added 
+quadratically, shown on top in green are error bars representing only the 
+statistical uncertainties. The brown bands represent the systematic 
+uncertainties, including the normalisation systematic uncertainties. The red 
+curves represent fits in the form of equation \ref{eq:A_LU-coh}.}
 \includegraphics[width=14cm]{coh_alu_t_phi.png}
@@
 \begin{figure}[htbp]
-\caption{\label{fig:CFF} CFF extraction}
+\caption{\label{fig:CFF} The model-independent extraction of the imaginary (blue points) and 
+real (red points) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of 
+$Q^{2}$ (on the top right), $x_B$ (on the top left), and $t$ (on the bottom).
+NEED TO ADD GUZEY MODEL}
 \includegraphics[width=8cm]{HA_t.png}
@@
 
-Model independant extraction of H (figure~\ref{fig:CFF})
+As advertised above, we extract the GPD $H$ in a model independent way 
+(figure~\ref{fig:CFF}). This is possible using the beam-spin asymmetry ($A_{LU}$) 
+expression for spin-zero target at leading twist~\cite{BM_2009}:
+\begin{equation}
+\begin{split}
+A_{LU}(\phi) &= \\
+ \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
+{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
+\big( 
+\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
+\label{eq:A_LU-coh}
+\end{split}
+\end{equation}
+where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
+and real parts of the CFF $\mathcal{H}_{A}$ associated to the GPD $H_A$. The 
+$\alpha_{i}$'s are $\phi$-dependent kinematical factors that depend on the 
+nuclear form factor $F_A$ and the independent variables $Q^2$, $x_{B}$ and $t$.  
+These factors are simplified as:
+\begin{equation}
+   \alpha_0 (\phi) =\frac{x_{A}(1+\epsilon^2)^2}{y} S{++}(1) \sin(\phi)\\
+\end{equation}
+\begin{equation}
+    \alpha_1 (\phi) = c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
+\end{equation}
+\begin{equation}
+   \alpha_2 (\phi) = \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
+C_{++}(1) cos(\phi) \right)\\
+\end{equation}
+\begin{equation}
+\alpha_3 (\phi) = \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
+{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
+\epsilon^2}
+\end{equation}
+Where $S{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
+leptonic tensor. Their explicit expressions can be found in \cite{}.
+
+The result of this extraction shown in figure~\ref{fig:CFF} is very promising.
+We first see that the imaginary part of $H$ comes out of the data with 
+error bars comparable to the statistical error of data. For the real part,
+the extraction appears to be more difficult, which is expected because 
+$\alpha_2$ is suppressed compared to $\alpha_0$ contribution. However,
+we note that the error bars are finite and that the fit converge without 
+placing any bound on the CFF, which is necessary on proton targets.
 
@@
 
-Open new perspectives in nuclear physics, mention the 12 GeV program and the EIC
-
-First fully exclusive measurement: very strong BSA, demonstrate the capability to extract GPDs even with limited statistics and kinematic compared to proton.
-
-% If this is line > 400 this is probably getting too long!
+We presented the first exclusive measurement of coherent nuclear DVCS and the
+first extraction of the CFF of the helium-4 nuclei. These
+results, while limited by statistical precision, show a very strong signal 
+in the beam spin assymetry and demonstrate the possibility to perform a
+completely model independent extraction of the CFF even with large 
+statistical uncertainties. This opens many new perspectives 
+for the study of the structure of nuclei in terms of quarks and gluons
+and pave the way for future more precise measurements at JLab 12~GeV
+and possibly at an Electron-Ion Collider (EIC).
 

### 2017-01-16 eg6-letters/NIM/EG6_RTPC_NIM.tex
update the NIM paper

@@
 Scattering (DVCS) and coherent production of mesons on $^4$He. In such 
-processes, $^4$He remains intact and recoils as a whole in the final state. The 
-CEBAF Large Acceptance Spectrometer (CLAS) at JLab has been used for similar 
-studies on proton targets, however it cannot track recoils with momenta less 
-than 250 MeV/c. In 2009, we carried out measurements on $^4$He target using
-CLAS spectrometer, which was upgraded with a RTPC. The detector was positioned 
-directly around the gaseous target, allowing a detection threshold of $~$125  
-MeV/c for $^4$He. This article discuses the design of our RTPC, the methods we 
-developed to calibrate it and its performances.
+processes, $^4$He nucleus remains intact and recoils as a whole in the final 
+state. The CEBAF Large Acceptance Spectrometer (CLAS) at JLab has been used for 
+similar studies on proton targets, however it cannot track recoils with momenta 
+less than 250 MeV/c. In 2009, we carried out measurements on $^4$He target 
+using CLAS spectrometer, which was upgraded with the RTPC during the CLAS-EG6 
+experimental run. The detector was positioned directly around a gaseous target, 
+allowing a detection threshold of $~$100  MeV/c for $^4$He. This article 
+discuses the RTPC design, work principle, developed calibration methods and 
+detector performance.
 \end{abstract}
@@
 
-\section{\label{sec:level1} Introduction}
+\section{Introduction} \label{sec:level1}
 
 The CEBAF Large Acceptance Spectrometer (CLAS)~\cite{CLASref} is installed in 
-the Hall-B of the Thomas Jefferson National Accelerator Facility (TJNAF) in 
-Newport News, Virginia, USA. The spectrometer is measuring charged particles as 
-well as photons. The accelerator of the TJNAF provides a high power electron 
-beam of energy up to 6 GeV and 100$\%$ duty cycle to the hall. The RTPC 
-mentioned in this article has been used during a three months experimental run 
-in 2009 with a longitudinally polarized electron beam of energy 6.064 GeV sent 
-on a gaseous helium-4 target to measure asymmetries in Deep Virtual Compton 
-Scattering (DVCS)~\cite{proposal} and exclusive meson production (Meson Spec 
-Prop). In these experiments, CLAS detects the high energy charged particles and 
-the final real photon, for the latter the coverage has been extended using the 
-optional inner calorimeter (ref).
+the Hall-B of the Thomas Jefferson National Accelerator Facility (TJNAF), 
+Newport News, Virginia, USA. The accelerator of TJNAF provides, simultaneously, 
+a high power electron beam of energy up to 6 GeV and 100$\%$ duty cycle to 
+three experimental Halls (A, B, C). The CLAS spectrometer, located in Hall-B, 
+is composed of several sub-detectors and two magnets. The spectrometer was 
+designed to track charged particles of momentum greater than 250 MeV/c as well 
+as detecting real photons. Figure~\ref{fig:CLAS} shows a three dimensional 
+representation of the CLAS detector, ordered with respect to their radial 
+distance from the beam line as:
 
-\begin{figure}[h]
-\centering 
-\includegraphics[scale=0.3]{fig/test_clas.png}
-\caption{\small\sf Three dimensional representation of the primary CLAS setup represents the geometry and the relative position of each subsystem.
-From outside, the electromagnetic calorimeter (green), time-of-flight system (red), Cherenkov counters (purple), three drift chamber regions (blue) and the superconducting torus coils (yellow).}
-\label{fig:CLAS}
+\begin{itemize}
+ \item Three regions of Drift Chambers (DC) for tracking of charged 
+    particles~\cite{DCref}.
+ \item Superconducting toroidal magnet which enables the tracking in the DC by 
+    bending the trajectories.
+ \item Cherenvkov Counters (CC) to help in separating electrons from negative 
+    particles, such as pions ~\cite{CCref}.
+ \item Scintillation Counters (SC) to identify hadrons via measuring their 
+    Time-Of-Flight (TOF)~\cite{TOFref}.
+ \item Forward Electromagnetic Calorimeter (EC) which measures the energy of 
+    the showering particles (electrons and photons) and neutrons~\cite{ECref}.
+\end{itemize}
+
+\begin{figure}[tbp]
+\centering \includegraphics[scale=0.3]{fig/test_clas.png}
+\caption{A three dimensional representation of the primary CLAS setup 
+   represents the geometry and the relative position of each subsystem. From 
+   outside, the electromagnetic calorimeter (green), time-of-flight system 
+   (red), Cherenkov counters (purple), three drift chamber regions (blue) and 
+the superconducting torus coils (yellow).} \label{fig:CLAS}
 \end{figure}
 
-CLAS is composed of several subdetectors and two magnets.
-They are designed to track charged particles at momentum greater than 250 MeV/c.
-Figure~\ref{fig:CLAS} shows the basic setup of CLAS, ordered with respect to their radial distance from the center:
+The DVCS process is the exclusive electroproduction of a real photon from a 
+quark of a hadronic target ($H$), $eH \rightarrow e' H' \gamma$. In the basic 
+setup of CLAS, the real photons are detected by the forward EC, which covers 
+polar angles from 8$^{\circ}$ to 45$^{\circ}$. With a 6 GeV electron beam, the 
+majority of the DVCS photons are produced at polar angles below 15$^{\circ}$, 
+where the acceptance of the EC is poor. In CLAS-E1DVCS experiment (2005), CLAS 
+was upgraded with the addition of an Inner Calorimeter (IC). The IC is 
+constructed from 424 lead-tungstate (PbWO$_{4}$) crystals, covering polar 
+angles between 5$^{\circ}$ and 15$^{\circ}$. Each crystal is 16 cm long ,
+corresponding to 17 radiation lengths, with a 1.33~$\times$~1.33 cm$^2$ front 
+surface and a 1.6~$\times$~1.6 cm$^2$ back surface. The achieved energy 
+resolution is around 3 to 4$\%$ for photon energies between 2 GeV and 5 GeV and 
+the angular resolution is between 3 to 5 mrad for the same energy range 
+\cite{Hyon-suk}.
 
-\begin{itemize}
-\item Three regions of Drift Chambers (DC) for tracking of charged particles~\cite{DCref}.
-\item Superconducting toroidal magnet which enables the tracking by bending the trajectories.
-\item Cherenvkov Counters (CC) to separate electrons from negative pions~\cite{CCref}.
-\item Scintillation Counters (SC) to identify hadrons via measuring their Time-Of-Flight (TOF)~\cite{TOFref}.
-\item Forward Electromagnetic Calorimeter (EC) to detect showering particles (electrons and photons) and neutrons~\cite{ECref}.
-\end{itemize}
+The developed RTPC has been used during a three months experimental run in 2009 
+with a longitudinally polarized electron beam of energy 6.064 GeV projected 
+onto a gaseous $^{4}$He target to measure asymmetries in Deep Virtual Compton 
+Scattering (DVCS)~\cite{proposal} and exclusive meson production. Moreover, a 
+5~T solenoid was placed around the RTPC-target system to shield the detectors 
+close to the beam line from Mollers electrons. The solenoid field plays also a 
+major rule in finding the momentum of the charged particles in the RTPC by 
+bending their tracks curvature.
 
-In addition to the normal CLAS setup, a forward electromagnetic calorimeter (the inner calorimeter) was installed to improve the photon detection acceptance.
-Moreover, a 5~T solenoid was placed around the target to shield the detectors close to the beam line -- mostly the inner calorimeter and the RTPC -- from Mollers electrons.
-The solenoid field is also used to calculate the momentum of the alpha particles from their curvature radius measured by the RTPC.
+In this paper we report the progress in designing and calibrating a radial TPC 
+that had been used with JLab-CLAS spectrometer. This paper is organized as 
+follows: section \ref{prev_tpc} presents an overview of the TPCs history and 
+previous usage, section \ref{sec_design} details the physics considerations for 
+the RTPC design and its internal structure, while section \ref{sec_readout} 
+points the properties of the read-out system. The calibration strategies for 
+such a detector are discussed in section \ref{sec_calib}. Finally, the 
+performance of the RTPC is described in section \ref{sec_perf}.
 
-The first implementation of a RTPC in CLAS have been achieved for the BoNuS experiment~\cite{BONUS} in 200x.
-The success of this detector for the detection of slow protons motivated the development of this new RTPC.
-For the channel of interests of our experiments, the recoiled $^{4}He$ nuclei have momentum around (150 or 300 ???) MeV/c, the detection of these particles was the primary motivation for using such design.
+\section{TPC technology} \label{prev_tpc}
+In the late 1970s, David R. Nygren presented the concept of the Time projection 
+Chambers (TPCs) as a new tool to track charged particles based on combining 
+electric and magnetic fields within a sensitive gas volume. The ionized 
+electrons are collected by a position-sensitive electron collection system.  
+Later in 1997, F.~Sauli introduced the Gas Electron Multiplier (GEM) as an 
+effective gas-gain element to improve the tracking efficiency of the TPCs 
+\ref{gem_sauli}. Currently, the TPCs are widely used in physics experiments, 
+such as high-energy physics (ALEPH, DELPHI), heavy-ion physics (STAR, ALICE) 
+and rare-event searches (XENON, NEXT).
 
-This paper is organized in this way: section \ref{sec_design} details the design and the internal structure of the RTPC, while section \ref{sec_readout} points the properties of the readout system.
-The calibration strategies for such detectors will be discussed in section \ref{sec_calib}.
-Finally, performances are discussed in section \ref{sec_perf}.
+The first implementation of a radial TPC with JLab-CLAS spectrometer has been 
+performed by the BoNuS experiment \cite{BONUS} in 2005. The success of the 
+BoNuS-RTPC in detecting the slow protons motivated the development of this new 
+RTPC. For the channel of interests of our experiments, the recoiled $^{4}He$ 
+nuclei have momentum per charge around 150 MeV/c, the detection of these 
+particles was the primary motivation for designing this detector.
 
-\section{Design} \label{sec_design}
+\section{CLAS-EG6 RTPC design} \label{sec_design}
+The design of CLAS-EG6 RTPC has been chosen according to physics and 
+experimental considerations. At 6 GeV incident electron beam energy, the recoil 
+$^{4}He$ nuclei, from the coherent DVCS channel, have an average momentum (per 
+charge) around 125 MeV/c, while the "standard" CLAS detects charged particles 
+with a threshold of 250 MeV/c. On the experimental site, The chosen design has 
+to fit within the available space of a 5 Tesla Solenoid magnet that surrounds 
+the target \cite{Hyon-suk}. Figure \ref{fig:RTPC2} shows an experimental view 
+of the RTPC before inserting it into the solenoid.
 
-The RTPC is a 200~mm long with a 150~mm diameter time projection chamber.
-The ionized electrons are drifting outward perpendicularly to the beam direction.
-These electrons are then amplified by three layers of GEMs and detected on 4.45 by 5~mm pads.
-As for BoNuS, the RTPC has two detection parts but unlike BoNuS they are part of a single chamber.
-Each part has independent GEM amplification systems that cover around 80\% of the azimuthal angle.
-Under the effect of the electromagnetic field, the ionization electrons drift to the readout system on the external shell with a curved trajectory as can be seen in the figure~\ref{fig:RTPC_1_4}.
+The CLAS-EG6 RTPC is a 200~mm long with a 150~mm diameter time projection 
+chamber. While a charged particle traverses a gas-sensitive volume, the ionized 
+electrons are released and drift outward perpendicularly to the beam direction.  
+These electrons are then amplified by three layers of GEMs and detected on 4.45 
+by 5~mm pads. As for CLAS-BoNuS, the EG6-RTPC has two detection parts but 
+unlike BoNuS they are part of a single chamber. Each part has independent GEM 
+amplification systems that cover around 80\% of the azimuthal angle. Under the 
+effect of the electromagnetic field, the ionization electrons drift to the 
+readout system on the external shell with a curved trajectory as can be seen in 
+the figure~\ref{fig:RTPC_1_4}.
 
@@
 \includegraphics[scale=0.28]{fig/RTPC_1_all.png}
-\caption[]{\small\sf Schematic drawing of the RTPC taken on a plane perpendicular to the beam line, see text for description of the elements.} 
-\label{fig:RTPC_1_4}
+\caption{Schematic drawing of the RTPC taken on a plane perpendicular to the 
+beam line, see text for description of the elements.} \label{fig:RTPC_1_4}
 \end{figure}
 
-As seen in figure~\ref{fig:RTPC2}, the RTPC is composed from the beam axis to the exterior by:\\
+As seen in figure~\ref{fig:RTPC_1_4}, the RTPC has the following substructure, 
+from the beam axis to the exterior::\\
 \begin{itemize}
-\item The target, filled with 5~atm $^4$He, has a 3~mm radius with Kapton walls only 27$\mu$m thick.
-\item The first gas gap extends from 3 mm to 20 mm radial distance.
-It is filled with $^{4}He$ gas at 1~atm.
-During run, this region is swarmed by Moller electrons induced by the beam, such that filling this region with a light gas like $^{4}He$ minimizes secondary interactions.
-This region is surrounded by a 4 $\mu$m thick window made of aluminized Mylar and connected to ground.
-\item The gap region extends between 20~mm and 30~mm and is filled with a gas mixture of 80$\%$ Neon and 20$\%$ Dimethyl Ether (DME).
-This region is surrounded by a 4~$\mu$m thick window made of aluminized Mylar, which serves as the cathode.
-\item The drift region is filled with the Ne-DME gas mixture, it extends from the cathode to the first Gas Electron Multiplier(GEM), 60 mm away from the central axis.
-The electric field in this region is around 500~V/cm (???) and perpendicular to the beam.
-Field cages are installed at both ends of the detector in this region.
-Progressive voltage depending on radial position is applied on these to maintain a uniform electric field perpendicular to the beam line at the edges of the RTPC.
-\item The GEM system is composed of three GEMs located at radii, 60 mm, 63 mm and 66 mm, they amplify the electrons to make a measurable signal.
-\item The readout board has internal radius of 69~mm and collects the charges, preamplifiers are plugged directly on its outer side and are transmitting the signal to the data acquisition electronics.
+   \item The target extends along the RTPC's central z-axis, with a diameter of 
+      6 mm. It is enclosed in a 27-$\mu$m-thick Kapton wall.
+
+   \item The first gas gap extends from 3 mm to 20 mm radial distance. It is 
+   filled with $^{4}He$ gas at 1~atm. During run, this region is swarmed by 
+   Moller electrons induced by the beam, such that filling this region with a 
+   light gas like $^{4}He$ minimizes secondary interactions. This region is 
+   surrounded by a 4 $\mu$m thick window made of aluminized Mylar and connected 
+to ground.
+
+   \item The gap region extends between 20~mm and 30~mm and is filled with a 
+      gas mixture of 80$\%$ Neon and 20$\%$ Dimethyl Ether (DME).  This region 
+      is surrounded by a 4~$\mu$m thick window made of aluminized Mylar, which 
+      serves as the cathode.
+
+   \item The drift region is filled with the Ne-DME gas mixture, it extends 
+      from the cathode to the first Gas Electron Multiplier(GEM), 60 mm away 
+      from the central axis. The electric field in this region is around 
+      500~V/cm (???) and perpendicular to the beam. Field cages are installed 
+      at both ends of the detector in this region. Progressive voltage 
+      depending on radial position is applied on these to maintain a uniform 
+      electric field perpendicular to the beam line at the edges of the RTPC.
+
+   \item The GEM system is composed of three GEMs located at radii, 60 mm, 63 
+      mm and 66 mm, they amplify the electrons to make a measurable signal. In 
+      this configuration, the first GEM layer represents the anode.
+
+   \item The readout board has internal radius of 69~mm and collects the 
+      charges, preamplifiers are plugged directly on its outer side and are 
+      transmitting the signal to the data acquisition electronics.
 \end{itemize}
-\begin{figure}[tb]
+
+\begin{figure}[tbp]
 \centering
 \includegraphics[scale=0.70]{fig/GEM_photo.jpg}
-\caption[]{\small\sf A schematic layout of the GEMs system in one module of the RTPC.} 
+\caption{A schematic layout of the GEMs system in one module of the RTPC.} 
 \label{fig:GEMs}
@@
 \includegraphics[scale=0.35]{fig/RTPC_2.png}
-\caption[]{\small\sf A schematic drawing of a $^{4}He$ track (in green) traversing the drift region, with the drift paths followed by the electrons (in black). } 
+\caption[]{A schematic drawing of a $^{4}He$ track (in green) traversing the 
+drift region, with the drift paths followed by the electrons (in black). } 
 \label{fig:RTPC_signals}
@@
    \centering
-\includegraphics[scale=0.40]{fig/TDC_profile.png}
-\caption[]{\small\sf Time profile of the collected hits in one experimental run. } 
+   \includegraphics[scale=0.3]{fig/TDC_profile.png}
+   \caption[]{Time profile of the collected hits in one experimental run.  } 
    \label{fig:TDC_profile}
@@
 \centering
-\includegraphics[scale=0.4]{fig/RunNumber_61551_TDCmax_Zslice.png}
-\caption[]{\small\sf Time profile distribution for the collected hits in one experimental run. } 
-\label{fig:RunNumber_61551_TDCmax_Zslice}
+\includegraphics[scale=0.36]{fig/RunNumber_61551_TDCmax_Zslice.png}
+\caption{Time profile distribution for the collected hits in one experimental 
+run. } \label{fig:RunNumber_61551_TDCmax_Zslice}
 \end{figure}
 
-Due to the non perfect experimental conditions and in particular changes in the gas proportions, the drift speed might also change over the 3 months run.
-Figure \ref{fig:Drift_run_number_1} shows the $TDC_{Max/2}$ values for individual runs (approximately 2 hours long).
-We observe a significant variation over time that we parametrized with a fit in order to take it into account in the track reconstruction code.
-Dealing with such situation is possible by adapting the right drift speed to the electrons as a function of geometry and time (we did not see any correlation between the effects).
-These functions were extracted for our entire data sets and implemented in the reconstructions code.
+Due to the non perfect experimental conditions and in particular changes in the 
+gas proportions, the drift speed might also change over the 3 months run.  
+Figure \ref{fig:Drift_run_number_1} shows the $TDC_{Max/2}$ values for 
+individual runs (approximately 2 hours long). We observe a significant 
+variation over time that we parametrized with a fit in order to take it into 
+account in the track reconstruction code. Dealing with such situation is 
+possible by adapting the right drift speed to the electrons as a function of 
+geometry and time (we did not see any correlation between the effects). These 
+functions were extracted for our entire data sets and implemented in the 
+reconstructions code.
 
@@
 \hspace*{-1.8cm}
-\includegraphics[scale=0.28]{fig/Drift_run_number_1.png}
-\caption[]{\small\sf $TDC_{Nbmax/2}$ versus the experimental run numbers (time). } 
+\includegraphics[scale=0.26]{fig/Drift_run_number_1.png}
+\caption{$TDC_{Nbmax/2}$ versus the experimental run numbers (time).  } 
 \label{fig:Drift_run_number_1}

### 2017-01-17 eg6-letters/NIM/EG6_RTPC_NIM.tex
more updates to the NIM paper

@@
 effective gas-gain element to improve the tracking efficiency of the TPCs 
-\ref{gem_sauli}. Currently, the TPCs are widely used in physics experiments, 
+\ref{gem_sauli}. Nowadays, the TPCs are widely used in physics experiments, 
 such as high-energy physics (ALEPH, DELPHI), heavy-ion physics (STAR, ALICE) 
@@
 BoNuS-RTPC in detecting the slow protons motivated the development of this new 
-RTPC. For the channel of interests of our experiments, the recoiled $^{4}He$ 
-nuclei have momentum per charge around 150 MeV/c, the detection of these 
-particles was the primary motivation for designing this detector.
+RTPC. For the channels of interest in CLAS-EG6 experiment, the recoiled 
+$^{4}He$ nuclei have momentum per charge around 150 MeV/c. The detection of 
+these low-energy nuclei was the primary motivation for designing this detector.
 
@@
 charge) around 125 MeV/c, while the "standard" CLAS detects charged particles 
-with a threshold of 250 MeV/c. On the experimental site, The chosen design has 
-to fit within the available space of a 5 Tesla Solenoid magnet that surrounds 
-the target \cite{Hyon-suk}. Figure \ref{fig:RTPC2} shows an experimental view 
-of the RTPC before inserting it into the solenoid.
+with a threshold of 250 MeV/c. On the experimental site, the chosen design has 
+to fit within the available space inside a 5 Tesla Solenoid magnet that 
+surrounds the target \cite{Hyon-suk}. Figure \ref{fig:RTPC2} shows an 
+experimental view of the RTPC before being inserted into the solenoid.
 
-The CLAS-EG6 RTPC is a 200~mm long with a 150~mm diameter time projection 
-chamber. While a charged particle traverses a gas-sensitive volume, the ionized 
-electrons are released and drift outward perpendicularly to the beam direction.  
-These electrons are then amplified by three layers of GEMs and detected on 4.45 
-by 5~mm pads. As for CLAS-BoNuS, the EG6-RTPC has two detection parts but 
-unlike BoNuS they are part of a single chamber. Each part has independent GEM 
-amplification systems that cover around 80\% of the azimuthal angle. Under the 
-effect of the electromagnetic field, the ionization electrons drift to the 
-readout system on the external shell with a curved trajectory as can be seen in 
-the figure~\ref{fig:RTPC_1_4}.
+The CLAS-EG6 RTPC is a 200~mm long with a 150~mm diameter TPC. While a charged 
+particle traverses a gas-sensitive volume, the ionized electrons are released 
+and drift, under the effect of an applied electromagnetic field, outward 
+perpendicularly to the beam direction. These electrons are then amplified by 
+three layers of GEMs and detected by a curved readout system on the external 
+shell as can be seen in the figure~\ref{fig:RTPC_1_4}. As for CLAS-BoNuS, the 
+EG6-RTPC has two detection halves but unlike BoNuS they are part of a single 
+chamber. Each half has independent GEM amplification systems that cover around 
+80\% of the azimuthal angle.
 
@@
 \includegraphics[scale=0.28]{fig/RTPC_1_all.png}
-\caption{Schematic drawing of the RTPC taken on a plane perpendicular to the 
-beam line, see text for description of the elements.} \label{fig:RTPC_1_4}
+\caption{Schematic drawing of CLAS-EG6 RTPC taken on a plane perpendicular to 
+the beam line, see text for description of the elements.} 
+\label{fig:RTPC_1_4}
 \end{figure}
 
-As seen in figure~\ref{fig:RTPC_1_4}, the RTPC has the following substructure, 
-from the beam axis to the exterior::\\
+As seen in figure~\ref{fig:RTPC_1_4}, the CLAS-EG6 RTPC has the following 
+substructure, from the beam line to the exterior:\\
 \begin{itemize}
@@
 
-   \item The first gas gap extends from 3 mm to 20 mm radial distance. It is 
+   \item The first gas gap extends from 3 mm to 20 mm radial distances. It is 
       filled with $^{4}He$ gas at 1~atm. During run, this region is swarmed by 
-   Moller electrons induced by the beam, such that filling this region with a 
-   light gas like $^{4}He$ minimizes secondary interactions. This region is 
-   surrounded by a 4 $\mu$m thick window made of aluminized Mylar and connected 
-to ground.
-
+      M\o ller electrons induced by the beam, such that filling this region 
+      with a light gas like $^{4}He$ minimizes secondary interactions. This 
+      region is surrounded by a 4 $\mu$m thick window made of aluminized Mylar 
+      and connected to ground.                                                                
    \item The gap region extends between 20~mm and 30~mm and is filled with a 
@@
       from the cathode to the first Gas Electron Multiplier(GEM), 60 mm away 
-      from the central axis. The electric field in this region is around 
-      500~V/cm (???) and perpendicular to the beam. Field cages are installed 
-      at both ends of the detector in this region. Progressive voltage 
-      depending on radial position is applied on these to maintain a uniform 
-      electric field perpendicular to the beam line at the edges of the RTPC.
+      from the beam axis. The electric field in this region is around 500~V/cm 
+      (???) and perpendicular to the beam. Field cages are installed at both 
+      ends of the detector in this region. Progressive voltage depending on 
+      radial position is applied on these to maintain a uniform electric field 
+      perpendicular to the beam line at the edges of the RTPC.
 
-   \item The GEM system is composed of three GEMs located at radii, 60 mm, 63 
-      mm and 66 mm, they amplify the electrons to make a measurable signal. In 
-      this configuration, the first GEM layer represents the anode.
+   \item The electron amplification system is composed of three GEMs located at 
+      radii, 60 mm, 63 mm and 66 mm. In this configuration, the first GEM layer 
+      represents the anode.
 
    \item The readout board has internal radius of 69~mm and collects the 
-      charges, preamplifiers are plugged directly on its outer side and are 
+      charges. Preamplifiers are plugged directly on the outer side and are 
       transmitting the signal to the data acquisition electronics.
@@
 
-The GEM amplification has been mainly chosen for this detector for their 
-flexibility, allowing the curved amplification surface. Also GEM are known to 
-create less sparks than in other gaseous detectors, which is a good thing for 
-the detection of slow nuclei like $^4$He. GEMs are made from an insulator layer 
-(here Kapton) sandwiched between two 5 $\mu$m copper layers. The mesh of each 
-GEM layer is chemically etched with 50$\mu$m diameter holes in double-conical 
-cross section shapes as can be seen in figure~\ref{fig:GEMs}. A potential 
-difference of 400 V is applied between the two copper layers of each GEM 
-creating a very strong electric field in the holes. Such strong fields lead to 
-high ionization from initial electrons and therefore amplification of the 
-signal. Also, a potential difference of 150 V is set between the GEMs to push 
-the amplified electrons toward the readout pads. The gain of each GEM layer is 
-of order 100.\\
+The GEM system has been mainly chosen for this detector for its flexibility, 
+allowing the curved amplification surface. Also GEMs are known to create less 
+sparks than in other gaseous detectors, which provides a cleaner detection of 
+slow nuclei like $^4$He. GEMs are made from an insulator layer, Kapton in our 
+case, sandwiched between two 5 $\mu$m copper layers. The mesh of each GEM layer 
+is chemically etched with 50$\mu$m diameter holes in double-conical cross 
+section shapes as can be seen in figure~\ref{fig:GEMs}. A potential difference 
+of 400 V is applied between the two copper layers of each GEM creating a very 
+strong electric field in the holes. Such strong fields lead to high ionization 
+from initial electrons and therefore amplification of the signal. Also, a 
+potential difference of 150 V is set between the GEMs to push the amplified 
+electrons toward the readout pads. The gain of each GEM layer is of order 100, 
+making a total gain of about $10^{6}$.\\
 

### 2017-01-18 eg6-letters/NIM/EG6_RTPC_NIM.tex
Editing...

@@
 
-\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A New Radial Time 
-Projection Chamber for CLAS at JLab}}
+\title{\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time 
+Projection Chamber for $\alpha$ detection in CLAS at JLab}}
 \input author_list.tex
@@
 allowing a detection threshold of $~$100  MeV/c for $^4$He. This article 
-discuses the RTPC design, work principle, developed calibration methods and 
-detector performance.
+discuses the RTPC design, work principle, calibration methods and 
+performances.
 \end{abstract}
@@
 as detecting real photons. Figure~\ref{fig:CLAS} shows a three dimensional 
-representation of the CLAS detector, ordered with respect to their radial 
-distance from the beam line as:
-
+representation of the baseline CLAS spectrometer, here is a list of the main elements
+depicted in the figure:
 \begin{itemize}
- \item Three regions of Drift Chambers (DC) for tracking of charged 
-    particles~\cite{DCref}.
- \item Superconducting toroidal magnet which enables the tracking in the DC by 
-    bending the trajectories.
- \item Cherenvkov Counters (CC) to help in separating electrons from negative 
-    particles, such as pions ~\cite{CCref}.
- \item Scintillation Counters (SC) to identify hadrons via measuring their 
-    Time-Of-Flight (TOF)~\cite{TOFref}.
- \item Forward Electromagnetic Calorimeter (EC) which measures the energy of 
-    the showering particles (electrons and photons) and neutrons~\cite{ECref}.
+ \item The three regions of Drift Chambers (DC) used for the tracking of charged 
+    particles~\cite{DCref} (in blue on the figure).
+ \item The superconducting toroidal magnet (in yellow) bends the trajectories 
+    of charged particles, thus allowing momentum measurement with the DC tracking information.
+ \item The Cherenvkov Counters (CC) used to separate electrons from other negative 
+    particles, such as pions, at lower energies~\cite{CCref} (in pink).
+ \item The Scintillation Counters (SC) used to identify hadrons by measuring their 
+    Time-Of-Flight (TOF)~\cite{TOFref} (in red).
+ \item The Electromagnetic Calorimeter (EC) used to separate electrons from other negative 
+    particles at higher energies and to detect neutral particles (neutrons and 
+    photons in particular)~\cite{ECref} (in green).
 \end{itemize}
@@
 \centering \includegraphics[scale=0.3]{fig/test_clas.png}
-\caption{A three dimensional representation of the primary CLAS setup 
-   represents the geometry and the relative position of each subsystem. From 
-   outside, the electromagnetic calorimeter (green), time-of-flight system 
-   (red), Cherenkov counters (purple), three drift chamber regions (blue) and 
-the superconducting torus coils (yellow).} \label{fig:CLAS}
+\caption{A three dimensional representation of the baseline CLAS setup. The
+   full description is given in the text.} \label{fig:CLAS}
 \end{figure}
 
-The DVCS process is the exclusive electroproduction of a real photon from a 
-quark of a hadronic target ($H$), $eH \rightarrow e' H' \gamma$. In the basic 
-setup of CLAS, the real photons are detected by the forward EC, which covers 
-polar angles from 8$^{\circ}$ to 45$^{\circ}$. With a 6 GeV electron beam, the 
+The measurement of the DVCS process ($eH \rightarrow e' H' \gamma$, where 
+$H$ is a hadron) necessitates some adaptations in this setup. Indeed, the EC 
+covers only polar angles from 8$^{\circ}$ to 45$^{\circ}$ with a very small
+acceptance at the lowest angles. With a 6 GeV electron beam on a proton target, the 
 majority of the DVCS photons are produced at polar angles below 15$^{\circ}$, 
-where the acceptance of the EC is poor. In CLAS-E1DVCS experiment (2005), CLAS 
-was upgraded with the addition of an Inner Calorimeter (IC). The IC is 
+where the acceptance of the EC is poor. To resolve this issue an additional 
+Inner Calorimeter (IC) has been built for the E01-113 experiment (2005). The IC is 
 constructed from 424 lead-tungstate (PbWO$_{4}$) crystals, covering polar 
-angles between 5$^{\circ}$ and 15$^{\circ}$. Each crystal is 16 cm long ,
-corresponding to 17 radiation lengths, with a 1.33~$\times$~1.33 cm$^2$ front 
-surface and a 1.6~$\times$~1.6 cm$^2$ back surface. The achieved energy 
+angles between 5$^{\circ}$ and 15$^{\circ}$. Each crystal is 16 cm long,
+corresponding to 17 radiation lengths. The achieved energy 
 resolution is around 3 to 4$\%$ for photon energies between 2 GeV and 5 GeV and 
 the angular resolution is between 3 to 5 mrad for the same energy range 
-\cite{Hyon-suk}.
+\cite{Hyon-suk}. The amount of background from Moller electron is however
+very problematic at such small angles, so a 5 Tesla solenoid magnet has been
+added around the target as a magnetic shield against the low energy background.
 

### 2017-01-18 eg6-letters/DVCS-coh-He4/dvcs_he4_prl-orig.tex
added the coherent prl paper I got from Kawtar

\documentclass[nofootinbib,twocolumn,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4-1}
\usepackage{graphicx}
\usepackage{hyperref}
%
\def\Dirac#1{#1\hskip-5pt/}
%
\begin{document}

\title{First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei}

\newcommand*{\ANL}{Argonne National Laboratory, Argonne, Illinois 60439}
\newcommand*{\ANLindex}{1}
\affiliation{\ANL}
\newcommand*{\ORSAY}{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}
\newcommand*{\ORSAYindex}{2}
\affiliation{\ORSAY}
\newcommand*{\JLAB}{Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606}
\newcommand*{\JLABindex}{3}
\affiliation{\JLAB}

\newcommand*{\NOWJLAB}{Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606}
\newcommand*{\NOWODU}{Old Dominion University, Norfolk, Virginia 23529}
 %%%%%%%%%%%%%%% END OF Latex Macros for institute addresses  %%%%%%%%%%%%%%%%%%%%%%%%%

\author {H.~Hattawy}
\affiliation{\ANL}
\affiliation{\ORSAY}
\author {R.~Dupr\'{e}} 
\affiliation{\ANL}
\affiliation{\ORSAY}
\author {N.A.~Baltzell} 
\affiliation{\ANL}
\affiliation{\JLAB}
\author {K.~Hafidi} 
\email[corresponding author: ]{kawtar@anl.gov}
\affiliation{\ANL}

\collaboration{The CLAS Collaboration}
\noaffiliation

%
\date{\today}
%
\begin{abstract}
We report the first exclusive measurement of deeply virtual Compton scattering 
(DVCS) off a nuclei with the CLAS detector at the Jefferson laboratory. The 
observed beam spin asymmetries are significantly larger than for proton, 
confirming expectations from calculations using the plane wave impulse 
approximation. We present an 
extraction of the single generalized parton distribution (GPD) of the spin-0 
helium-4 nuclei in a completely model independent way. This result demonstrate the 
strength of the method and opens a new and unique access into the partonic structure 
of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

\maketitle

The internal structure and dynamics of the proton, the nucleus of the most abundant
chemical element in the visible universe, 
still remain a mystery in many respects,
more than 40 years after the evidence for its quark and gluon substructure.
How are the spatial and momentum distributions of the quarks and gluons (\textit{i.e.},
the partons) correlated inside the nucleon? How do the partons contribute
to the bulk properties of the proton (mass, spin, charge,...)? These are some fundamental
questions at the intersection of nuclear and particle physics which are still to be resolved.

In order to tackle these essential issues, a large experimental program was launched
worldwide at Jefferson Lab (JLab), COMPASS and HERA, facilities using multi-GeV
electromagnetic probes, to study deeply virtual Compton
scattering (DVCS). In the valence-quark region, this corresponds to Compton scattering
at the quark level, with the incoming photon radiated from the lepton beam. As in the study of
atomic or nuclear structure, the energy and angular distributions of the scattered photon reflect
the distribution in momentum and/or space of the targets, which in our case are the quarks
inside the proton. At JLab, electron beams are used and the reaction to study proton
structure is $ep\to e^\prime p^\prime \gamma$.
It was shown~\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}
that this process, at sufficiently large squared electron momentum transfer 
$Q^2=-(e-e^\prime)^2$ 
and small squared proton momentum transfer $t=(p-p^\prime)^2$ (in terms of the electron
and proton four-vectors), could be interpreted in the framework
of Quantum Chromodynamics (QCD), the fundamental theory governing the interaction of quarks and 
gluons, as the product of the elementary Compton scattering at the quark level $\gamma^* q\to 
\gamma q$ with factorizable structure functions called Generalized Parton Distributions (GPDs).
\begin{figure}[tb]
\includegraphics[width=8.9cm]{fig1.pdf}
\vspace{-0.9cm}
\caption{Left: the dominant mechanism for the DVCS process at sufficiently large $Q^2$ and 
small $|t|$, as predicted by the QCD factorization theorem.
Right: the Bethe-Heitler (BH) process, which interferes with the DVCS process in the
$ep\to e^\prime p^\prime \gamma$ reaction.}
\label{fig:diags}
\end{figure}

Figure~\ref{fig:diags} (left) illustrates GPD QCD factorization for the DVCS process.
In a frame where the nucleon moves at the speed of light in a given direction, a quark with 
longitudinal momentum fraction $x+\xi$ absorbs the virtual photon and, after radiating the
final-state photon, the \textit{same} quark returns into the nucleon with a longitudinal momentum
fraction $x-\xi$, plus some transverse kick included in $t$. The GPDs are functions of
$x$, $\xi$, and $t$, and represent the probability amplitude of such a process.
The variable $\xi$ is related to the
Bjorken variable $x_B$: $\xi\approx {{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M\nu}$ with
the proton mass $M$ and $\nu=E_e-E_{e^\prime}$.
Thus, it is determined by the scattered-electron kinematics. The quantity $x$ is
not measurable in the DVCS process.
At leading-order QCD, GPDs do not depend on $Q^2$. At leading-twist QCD, four GPDs enter the
description of the DVCS process: $H$, $\tilde H$, $E$ and $\tilde E$, representing the four
independent helicity-spin transitions of the quark-nucleon system between the initial and
final states. The GPDs are QCD matrix elements that integrate and project on a few variables
the full complexity of the quarks' and gluons' dynamics within the nucleon.

The GPDs embody the longitudinal momentum distribution of the quarks in the nucleon,
their transverse spatial distribution, and the correlation between these two distributions.
One uses the term \textit{nucleon tomography} as
one can probe the transverse size of the nucleon for different quark longitudinal-momentum slices.
For details on the GPD formalism, see the
reviews~\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}.

In the $ep\to e^\prime p^\prime \gamma$ reaction, the DVCS process interferes with the well-known
Bethe-Heitler (BH) process, illustrated in Fig.~\ref{fig:diags} (right), where the final-state
photon is radiated by the incoming or scattered electron.

Extracting the GPDs from the DVCS process requires measuring a series of observables for
the $ep\to e^\prime p^\prime \gamma$ reaction over the broadest
kinematic domain possible. Several
observables, such as the unpolarized cross section and polarized beam or/and target asymmetries, 
are necessary in order to separate the four GPDs. Each 
observable is sensitive to a particular combination of GPDs.

This paper presents a major contribution to this global and long-term endeavour: the extraction of
the $ep\to e^\prime p^\prime \gamma$ (\textit{i.e.}, DVCS+BH) unpolarized and beam-polarized cross
sections over the widest phase space ever explored in the valence-quark region, with 110
($Q^2,x_B,t$) bins covering:
$1.0<Q^2<4.6$~GeV$^2$, $0.10<x_B<0.58$, and $0.09<-t<0.52$~GeV$^2$.
In this kinematic domain, our results strongly enhance the existing set of
measurements of the $ep\to e^\prime p^\prime \gamma$ reaction which consists of:
four ($Q^2,x_B,t$) bins of unpolarized cross sections and 12 bins of beam-polarized cross sections
measured by the JLab Hall A collaboration~\cite{Munoz Camacho:2006hx},
57 bins of beam-spin asymmetries measured by the CLAS collaboration~\cite{Girod:2007aa},
and 18 bins of longitudinal target- and beam-target double-spin asymmetries measured by the
CLAS collaboration~\cite{Seder:2015,Pisano:2015} (in addition to the handful of CLAS pioneering data
points of Refs~\cite{Stepanyan:2001sm,Chen:2006na,Gavalian:2009}).

The experiment took place at JLab during three months in 2005, using the 5.75-GeV polarized
electron beam (79.4\% polarization), a 2.5-cm-long liquid-hydrogen 
target, and the Hall B large-acceptance CLAS spectrometer~\cite{Mecking:2003zu},
operating at a luminosity of 2$\times$10$^{34}$~cm$^{-2}$s$^{-1}$.
A specially designed electromagnetic calorimeter (``inner calorimeter",
IC~\cite{Girod:2007aa}) was added to the CLAS detector and allowed the detection of photons
for polar angles from about 5$^\circ$ to 16$^\circ$, with full azimuthal coverage.
A solenoid magnet was installed around the target in order to magnetically shield the IC from
the copious M{\o}ller background stemming from the target.

The first step of the data analysis was to select events with at least one electron, one proton, and
one photon in the final state.
Electrons were identified by signals in the CLAS drift chambers, scintillators,
Cherenkov counters, and the standard CLAS electromagnetic calorimeters. Protons
were identified by the correlation between their measured momentum and velocity.
The highest-energy particle detected in the IC was considered as a photon candidate.
\begin{figure}[htb]
\vspace{-0.2cm}
\includegraphics[width=9cm]{fig2.pdf}
\vspace{-0.7cm}
\caption{(Color online) Two of the four variables on which $3\sigma$ exclusivity cuts (vertical lines)
were applied to select the $ep\to e^\prime p^\prime \gamma$ reaction: $\Delta \phi$ (left)
and $\theta_{\gamma X}$ (right). 
Black solid distributions correspond to the events with at least one electron and one proton detected
in CLAS, and one photon detected in the IC, after applying the exclusivity cuts on $MM^{2}_{e^\prime p^\prime}$.
Each blue shaded distribution corresponds to the events remaining after
applying the exclusivity cuts on all the variables except for the plotted one.}
\label{fig:cuts}
\end{figure}
Once these three final-state particles were selected and their 3-momenta determined,
the exclusivity of the $ep\to e^\prime p^\prime \gamma$ reaction was ensured by applying $3\sigma$ cuts
on the following four variables: the squared missing mass $MM^{2}_{e^\prime p^\prime}$ of the 
($e^\prime p^\prime X$) system, the coplanarity angle $\Delta \phi$, \textit{i.e.}, the angle between 
the ($\gamma^*,p^\prime$) and ($\gamma^*,\gamma$) planes, the missing transverse momentum of the
($e^\prime p^\prime \gamma$) system, and the angle $\theta_{\gamma X}$ between the measured photon and that
predicted by the kinematics of the ($e^\prime p^\prime X$) system. We also selected the particular kinematics:
$W>2$~GeV, where $W^2=s=(\gamma^*+p)^2$, to minimize contributions from radiative decay of
baryonic resonances, and $Q^2>1$~GeV$^2$ in order to be in the deep virtual regime.
As an example, Figure~\ref{fig:cuts} shows the effect of two of the four exclusivity cuts.

Under these conditions, we ended up with about 300,000 events.
Figure~\ref{fig:ps} shows the resulting ($Q^2,x_B$) and ($-t,x_B$) kinematic coverages
of the data and the adopted binning [21 ($Q^2,x_B$) bins and 6 $t$ bins],
which is finer than the one used in Ref.~\cite{Girod:2007aa}.
Note that the bins and results presented here are limited to the $|t|$ region below
0.52~GeV$^2$ while the actual coverage of the data goes beyond 1~GeV$^2$.
The $ep\to e^\prime p^\prime \gamma$ cross sections vary very rapidly
with kinematics,
primarily due to the BH process.
In order to minimize the uncertainties related to the knowledge of the kinematics, 
we chose to minimize the size of our bins, while keeping comparable statistics in
each bin.
\begin{figure}[htb]
\vspace{-0.3cm}
\includegraphics[width=9cm]{fig3.pdf}
\vspace{-0.8cm}
\caption{(Color online) The ($Q^2,x_B$) (left) and ($-t,x_B$) (right) kinematic coverages
of this experiment, with the corresponding binning.}
\label{fig:ps}
\end{figure}

Due to the azimuthal symmetry when using an unpolarized target,
the $ep\to e^\prime p^\prime \gamma$ reaction depends on four independent variables.
For the study of GPDs, the most appropriate ones are $Q^2$, $x_B$, $t$ and
$\phi$, where $\phi$ is the azimuthal angle between the ($e,e^\prime$) 
and ($\gamma^*,p^\prime$) planes around the virtual photon direction.
We have thus extracted four-fold cross sections as follows:
\begin{equation}
\frac{d^4 \sigma_{ep \rightarrow e^\prime p^\prime \gamma}}{dQ^2 dx_B dt d\phi} =
\frac{N_{ep\to e^\prime p^\prime \gamma}}{\mathcal{L}_{int} \Delta Q^2 \Delta x_B \Delta t \Delta \phi
\ Acc \ F_{rad}}.
\label{eq:sig}
\end{equation}
In Eq.~\ref{eq:sig}, 
$N_{ep\to e^\prime p^\prime \gamma}$ is the number of $ep\to e^\prime p^\prime \gamma$ events in the
($Q^2,x_B,t,\phi$) bin. The aforementioned exclusivity cuts do not fully select a pure
sample of DVCS+BH events. We evaluated the contamination from the $ep\to e^\prime p^\prime \pi^0$
channel where one photon of the $\pi^0$ decay can escape detection, using a combination of
$ep\to e^\prime p^\prime \pi^0$ measurements and Monte-Carlo simulations.
On average, this contamination is less than 9\% and was subtracted on a bin-by-bin basis.
The four-dimensional acceptance/efficiency of the CLAS detector, $Acc$, for the
$ep\to e^\prime p^\prime \gamma$ reaction
was determined for each ($Q^2,x_B,t,\phi$) bin by generating more than 200 million
DVCS+BH events, using a realistic Monte-Carlo generator. The events were processed through 
the GEANT simulation of the CLAS detector, and the same reconstruction
and analysis codes that were used for the data.
The event generator includes radiative effects so that $Acc$
also corrects for a part of the real internal radiative effects.
The factor $F_{rad}$ corrects, for each ($Q^2,x_B,t,\phi$) bin, for the virtual internal
radiative effects and the remainder of the real internal radiative effects, which can be both
calculated theoretically~\cite{Akushevich:2012tw}.
The product ($\Delta Q^2 \Delta x_B \Delta t \Delta \phi$) corresponds to the effective
hypervolume of each bin.
Finally, $\mathcal{L}_{int}$ is the effective integrated luminosity, corrected for the data
acquisition dead time, which was deduced from the integrated charge of the beam measured by a
Faraday cup. In addition, we applied a global renormalization factor of 12.3\%, determined
from the analysis of the elastic scattering $ep\to e^\prime p^\prime$, by comparing the
experimental cross section to the well-known theoretical one. This factor compensates for
various kinematic-independent inefficiencies, not well reproduced by the simulations.

\begin{figure}[htb]
\includegraphics[width=8.7cm]{fig4a.pdf}
\includegraphics[width=8.7cm]{fig4b.pdf}
\vspace{-0.5cm}
\caption{(Color online) Top six plots: unpolarized cross section 
$\frac{d^4 \sigma_{ep\to e^\prime p^\prime \gamma}}{dQ^2 dx_B dt d\phi}$ (top row)
and beam-polarized cross-section difference $\Delta(d^4\sigma)$ for the
$ep\to e^\prime p^\prime \gamma$ reaction, as a function of $\phi$,
for ($Q^2,x_B$)=(1.63 GeV$^2$, 0.185) and for 3 $-t$ values: 0.153, 0.262 and 0.447~GeV$^2$.
Bottom six plots: same observables for ($Q^2,x_B$)=(2.78 GeV$^2$, 0.335) and 
$-t$=0.204, 0.262 and 0.448~GeV$^2$.
The green long-dashed curves show the BH contribution only.
The other curves correspond to the predictions of four GPD models:
VGG~\cite{Vanderhaeghen:1998uc1999xj,Goeke:2001tz,Guidal:2004nd} 
(blue solid curves), KMS~\cite{KMS} (cyan dash-dotted curves),
and two versions of the KM model~\cite{Kumericki:2009uq,Kumericki:2011zc},
KM10 (red dotted curves) and KM10a (red short-dashed curves). The blue bands show the
systematic uncertainties.}
\label{fig:xsec}
\end{figure}

Figure~\ref{fig:xsec} shows, for two selected ($Q^2,x_B$) bins in different parts
of the phase space, the $\phi$-dependence of the $ep\to e^\prime p^\prime \gamma$
unpolarized cross section and beam-polarized cross-section difference.
The latter of these two observables is defined as follows:
\begin{equation}
\Delta(d^4\sigma)=\frac{1}{2}\left[\frac{d^4 \overrightarrow{\sigma}_{ep\to e^\prime p^\prime \gamma}}
{dQ^2 dx_B dt d\phi}
-\frac{d^4 \overleftarrow{\sigma}_{ep\to e^\prime p^\prime \gamma}}{dQ^2 dx_B dt d\phi}\right],
\end{equation}
where the arrows correspond to beam helicity states $+$ and $-$.
For each of these ($Q^2,x_B$) bins, three selected $t$ bins are shown.
In Fig.~\ref{fig:xsec},
the black error bars show the statistical uncertainties of the data [13.9\% on the unpolarized
cross section on average, over the 110 ($Q^2,x_B,t$) bins] and the blue bands show the
systematic uncertainties [14\% on the unpolarized cross section on average].
The contributions to the latter include the uncertainties on the beam energy and
therefore the kinematics and associated corrections (5.7\% on average), 
the acceptance correction (5.3\%), the global renormalization factor (5\%),
the exclusivity cuts (3.5\%), the radiative corrections (2.2\%), the particle selection
(1.6\%), and the $\pi^0$ background subtraction (1\%).

The unpolarized cross sections peak towards
$\phi$=0$^\circ$ and 360$^\circ$ due to the BH process for which the final-state  
photon is predominantly emitted in the direction of the initial or scattered electron.
This is quantitatively confirmed by the calculations shown in Fig.~\ref{fig:xsec},
where the green curves show the BH contribution only. The difference between the BH
curves and the data can thus be attributed to the DVCS process, and therefore linked to GPDs. 
We display in Fig.~\ref{fig:xsec} calculations of four GPD models, listed in the caption.
The modeling of the GPDs in the VGG and KMS models is based on the Double-Distribution 
representation~\cite{Radyushkin:1998es,Radyushkin:1998bz,Mueller:1998fv}. The VGG
calculations in Fig.~\ref{fig:xsec} only include the contribution of the GPD $H$
as the inclusion of the other GPDs barely changes the results. The KM model is based 
on the Mellin-Barnes 
representation~\cite{Kumericki:2009uq, Mueller:2005ed}. The KM10 version of the 
model includes contributions from all four GPDs for which the free parameters
were fitted to the JLab~\cite{Munoz Camacho:2006hx,Girod:2007aa}, 
HERMES~\cite{Airapetian}
and ZEUS/H1~\cite{Chekanov:2003ya,Aktas:2005ty} data.
In that work, it was found that it is possible to fit the JLab Hall A unpolarized cross sections
only at the price of the introduction of a very strong $\tilde H$ contribution~\cite{Htilde}.
The KM10a version is based on a fit which excludes the JLab Hall A unpolarized cross sections~\cite{Munoz Camacho:2006hx} 
and sets $\tilde H$ to zero. Note that none of these four models has been tuned to our data.

Figure~\ref{fig:xsec} shows that the predictions of standard GPD models like VGG, KMS, and KM10a,
whose compatibility is remarkable in spite of their different approaches,
are in good agreement with our unpolarized cross-section data. In contrast, we see that the
KM10 version, which includes the strong $\tilde H$ contribution, tends to overestimate our data.
Over our 110 ($Q^2,x_B,t$) bins, the average $\chi^2$ value
per degree of freedom~\cite{chi2}
is 1.91 for VGG, 1.85 for KMS, 
1.46 for KM10a, and 3.94 for KM10.
We can therefore conclude that standard GPD models with a dominant contribution of the
GPD $H$ to the unpolarized cross section, \textit{i.e.}, without the introduction of a strong
$\tilde H$ contribution, describe the data well. Moreover, the disagreement between our data
and the KM10 model, which instead matches the Hall A results, might reveal an inconsistency
between
the two sets of data. As a check, we performed a dedicated data analysis using the exact same
($Q^2,x_B,t$) bin limits as those used for the Hall A analysis ($Q^2$=2.3~GeV$^2$, $x_B$=0.36,
and $-t=$0.17, 0.23, 0.28 and 0.33~GeV$^2$). However, in this limited and particular
($Q^2,x_B,t$) region, the comparison is hampered by our large statistical
uncertainties and lack of $\phi$-coverage around $\phi=180^\circ$.
Thus no conclusion can be drawn from this comparison.
The Hall A experiment was run at a luminosity almost
three orders of magnitude larger than ours, but in a much more limited phase space.

In general, the four models, including KM10, give a good description of the beam-polarized
cross-section difference and the data barely allow one to distinguish one model from another.
Over our 110 ($Q^2,x_B,t$) bins, the average $\chi^2$ value
per degree of freedom~\cite{chi2}
is 1.40 for VGG, 1.84 for KMS,
1.06 for KM10a, and 1.20 for KM10.

Finally, we attempted to extract directly some GPD information from these two sets of observables.
We used the local-fitting procedure developed in
Refs.~\cite{Guidal:2008ie,Guidal:2009aa,Guidal:2010ig,Guidal:2010de}.
At leading-twist and leading-order, this procedure uses well-established DVCS amplitudes and
does not depend on model parametrizations of the GPDs. We fit simultaneously the
$\phi$-distributions of our unpolarized and beam-polarized cross sections
at a given ($Q^2,x_B,t$) kinematic point by the eight (real) quantities:
\begin{eqnarray}
F_{Re}(\xi,t) &=& {\cal P}\int_{-1}^{1}dx\left[\frac{1}{x-\xi}\mp\frac{1}{x+\xi}\right]
F(x,\xi,t), \nonumber
\end{eqnarray}
\begin{eqnarray}
F_{Im}(\xi,t) &=& F(\xi,\xi,t) \mp F(-\xi,\xi,t). \label{def_cffs}
\end{eqnarray}
In Eq.~\ref{def_cffs}, $F=H, \tilde H, E,\tilde E$, the top and bottom signs apply to the
unpolarized ($H,E$) and polarized ($\tilde H,\tilde E$) GPDs respectively, and ${\cal P}$ is the
principal value integral.
These quantities are called Compton Form Factors (CFFs)~\cite{CFFdef2} in
Refs.~\cite{Guidal:2008ie,Guidal:2009aa,Guidal:2010ig,Guidal:2010de}
and ``sub-CFFs" in Ref.~\cite{Kumericki:2013lia}.
The only model-dependent input in the procedure is that the CFFs are
allowed to vary in a very conservative limited range,
$\pm$5 times the CFFs from the VGG model~\cite{Guidal:2004nd}.
In spite of the underconstrained nature of the problem, \textit{i.e.}, fitting two
observables with eight free parameters, the algorithm manages in general to find well-defined
minimizing values
for $H_{Im}$ and $H_{Re}$. The reason is that the two observables
that we fit are dominated by the contribution of the GPD $H$.

Ideally, one would like to fit all CFFs. However, with only two observables in this case,
this leads to too large uncertainties. We therefore present in Figure~\ref{fig:cff}, for
a selection of three of our 21 ($Q^2,x_B$) bins, the $t$-distribution of the fitted
$H_{Im}$ and $H_{Re}$, computed neglecting the contributions associated with $E$ and
$\tilde E$.
Fig.~\ref{fig:cff} also shows the predictions of the VGG model, which
overestimates the fitted $H_{Im}$ at the smallest values of $x_B$.
\begin{figure}[tb]
\includegraphics[width=8.7cm]{fig5.pdf}
\vspace{-0.7cm}
\caption{(Color online) Results of the CFF fit of our data for
$H_{Im}$ (upper panel) and $H_{Re}$ (lower panel), with only
the GPDs $H$ and $\tilde H$, for three of our ($Q^2,x_B$) bins, as a function of $t$.
The blue solid curves are the predictions of the VGG model.
The black dashed curves show the fit of the results by the function $Ae^{bt}$.}
\label{fig:cff}
\end{figure}

We have fitted, in Fig.~\ref{fig:cff}, the $t$-dependence of $H_{Im}$ by
the function $Ae^{bt}$ with the normalization $A$ and the slope $b$ as free parameters.
Keeping in mind that the $Q^2$ values are different
for the three $x_B$ bins, the results of these fits show 
that $A$ and $b$ increase, in a systematic way, with decreasing $x_B$.
Under the hypothesis of neglecting $Q^2$ higher-twist and evolution effects  
as well as \textit{deskewing} effects~\cite{deskewing},
these behaviors might reveal tomographic features of the quark content of the nucleon. 
Under the mentioned conditions, $b$ is related to the transverse size of the nucleon.
Our data therefore suggest, over the $x_B$ range explored in this experiment, that the size of
the nucleon increases as lower momentum fractions (proportional to $x_B$) are probed.
The rising of $A$ reflects the increase of the partonic content of the nucleon
as lower $x_B$ values are probed.
$H_{Re}$ does not lend itself easily to a simple interpretation
as it involves a weighted-integration of the GPD $H$ over $x$. Nevertheless, its
extraction is of great use to constrain models.

In conclusion, we have measured the unpolarized and beam-polarized four-fold cross sections
$\frac{d^4 \sigma}{dQ^2 dx_B dt d\phi}$
for the $ep\to e^\prime p^\prime \gamma$ reaction, for 110 ($Q^2,x_B,t$) bins, over the
widest phase space ever covered in the valence-quark region. This large set of new data
will provide stringent constraints on GPD models. We have shown that three
well-known GPD models, VGG, KMS, and the KM10a version of the KM model, describe
the data well without additional inputs.
The model interpretation of the present results favors a smaller deviation from the pure
BH process around $\phi=180^{\circ}$ than suggested by the Hall A data.
Within such models, this reinforces the expectation of the $H$-dominance in the
unpolarized cross section.
We have also extracted the $H_{Im}$ and $H_{Re}$ CFFs from our data, fitting simultaneously
both cross-section observables. Under some assumptions, our results tend to show that the
nucleon size increases at lower parton-momentum values, thus revealing a
first tomographic image of the nucleon.

The full data set is available at~\cite{CLASdata}.
A long article is in preparation and will include the results for all our
($Q^2,x_B,t$) bins and a more detailed description of the data analysis.

We thank the staff of the Accelerator and Physics Divisions
at Jefferson Lab for making this experiment possible.
We also thank I.~Akushevich, K.~Kumeri\v{c}ki and D.~Mueller
for informative discussions and making available their calculations.
This work was supported in part by
the U.S. National Science Foundation,
the Chilean Comisi\'on Nacional de Investigaci\'on Cient\'ifica y Tecnol\'ogica (CONICYT),
the French Centre National de la Recherche Scientifique (CNRS),
the French Commissariat \`{a} l'Energie Atomique (CEA),
the French-American Cultural Exchange (FACE),
the Italian Istituto Nazionale di Fisica Nucleare (INFN),
the National Research Foundation of Korea (NRF),
the Scottish Universities Physics Alliance (SUPA),
and the United Kingdom's Science and Technology Facilities Council (STFC).
This work benefited from the support of the French Agence Nationale de la Recherche
(contract ANR-12-MONU-0008-01 PARTONS) and the Joint Research Activity GPDex of
the European program Hadron Physics 3 under the Seventh Framework Programme of the European
Community. This material is based upon work supported by the U.S. Department of Energy,
Office of Science, Office of Nuclear Physics under contract DE-AC05-06OR23177.

\begin{thebibliography}{99}
\bibitem{Mueller:1998fv} 
D. Mueller, D. Robaschik, B. Geyer, F.M. Dittes and J. Horejsi,
Fortsch.\ Phys. {\bf 42}, 101 (1994).

\bibitem{Ji:1996ek} 
X.D. Ji,
Phys.\ Rev.\ Lett. {\bf 78}, 610 (1997).

\bibitem{Ji:1996nm} 
X.D. Ji,
Phys.\ Rev.\ D {\bf 55}, 7114 (1997).

\bibitem{Radyushkin:1996nd}
A.V. Radyushkin,
Phys.\ Lett.\  B {\bf 380}, 417 (1996).

\bibitem{Radyushkin:1997ki} 
A.V. Radyushkin,
Phys.\ Rev.\ D {\bf 56}, 5524 (1997).

\bibitem{Goeke:2001tz}
K. Goeke, M.V. Polyakov and M. Vanderhaeghen,
Prog.\ Part.\ Nucl.\ Phys. {\bf 47}, 401 (2001).

\bibitem{Diehl:2003ny}
M. Diehl,
Phys.\ Rept.  {\bf 388}, 41 (2003).

\bibitem{Ji:2004gf}
X.D. Ji,
Ann.\ Rev.\ Nucl.\ Part.\ Sci. {\bf 54}, 413 (2004).

\bibitem{Belitsky:2005qn}
A.V. Belitsky and A.V. Radyushkin,
Phys.\ Rept. {\bf 418}, 1 (2005).

\bibitem{Boffi:2007yc} 
S. Boffi and B. Pasquini,
Riv.\ Nuovo Cim. {\bf 30}, 387 (2007).

\bibitem{Guidal:2013rya} 
M.~Guidal, H.~Moutarde and M.~Vanderhaeghen,
Rept.\ Prog.\ Phys.\  {\bf 76}, 066202 (2013).

\bibitem{Munoz Camacho:2006hx} 
C. Mu\~noz Camacho {\it et al.} [Jefferson Lab Hall A Collaboration],
Phys.\ Rev.\ Lett. {\bf 97}, 262002 (2006).

\bibitem{Girod:2007aa} 
F.X. Girod {\it et al.} [CLAS Collaboration],
Phys.\ Rev.\ Lett. {\bf 100}, 162002 (2008).
These beam-spin asymmetries were obtained with the same data set
as in the present work.

\bibitem{Seder:2015} 
E. Seder {\it et al.} [CLAS Collaboration],
Phys.\ Rev.\ Lett. {\bf 114}, 032001 (2015).

\bibitem{Pisano:2015} 
S.~Pisano {\it et al.} [CLAS Collaboration],
Phys.\ Rev.\ D {\bf 91}, 052014 (2015).

\bibitem{Stepanyan:2001sm}
S.~Stepanyan {\it et al.} [CLAS Collaboration],
Phys.\ Rev.\ Lett. {\bf 87}, 182002 (2001).

\bibitem{Chen:2006na} 
S.~Chen {\it et al.} [CLAS Collaboration],
Phys.\ Rev.\ Lett.\ {\bf 97}, 072002 (2006).

\bibitem{Gavalian:2009} 
G. Gavalian {\it et al.} [CLAS Collaboration],
Phys.\ Rev.\ C {\bf 80}, 035206 (2009).

\bibitem{Mecking:2003zu} 
B.A.~Mecking {\it et al.},
Nucl.\ Instrum.\ Meth.\ A {\bf 503}, 513 (2003).

\bibitem{Akushevich:2012tw} 
I.~Akushevich and A.~Ilyichev,
Phys.\ Rev.\ D {\bf 85}, 053008 (2012).

\bibitem{Vanderhaeghen:1998uc1999xj} 
M. Vanderhaeghen, P.A.M. Guichon and M. Guidal,
Phys.\ Rev.\ Lett. {\bf 80}, 5064 (1998);
Phys.\ Rev.\ D {\bf 60}, 094017 (1999).

\bibitem{Guidal:2004nd}
M. Guidal, M.V. Polyakov, A.V. Radyushkin and M. Vanderhaeghen,
Phys.\ Rev.\ D {\bf 72}, 054013 (2005).

\bibitem{KMS}
P. Kroll, H. Moutarde, and F. Sabati\'{e},
Eur.\ Phys.\ J.\ C {\bf 73}, 2278 (2013).

\bibitem{Kumericki:2009uq}
K. Kumeri\v{c}ki and D. Mueller,
Nucl.\ Phys.\ B {\bf 841}, 1 (2010).

\bibitem{Kumericki:2011zc}
K. Kumeri\v{c}ki {\it et al.},
arXiv:1105.0899 [hep-ph].

\bibitem{Radyushkin:1998es}
A.V. Radyushkin,
Phys.\ Rev.\  D {\bf 59}, 014030 (1999).

\bibitem{Radyushkin:1998bz} 
A.V. Radyushkin,
Phys.\ Lett.\ B {\bf 449}, 81 (1999).

\bibitem{Mueller:2005ed}
D. Mueller and A. Schafer,
Nucl.\ Phys.\ B {\bf 739}, 1 (2006).

\bibitem{Airapetian}
A. Airapetian {\it et al.} [HERMES Collaboration],
Phys.\ Rev.\ Lett. {\bf 87}, 182001 (2001);
JHEP {\bf 1207}, 032 (2012);
JHEP {\bf 1006}, 019 (2010);
JHEP {\bf 0806}, 066 (2008);
Phys.\ Lett.\ B {\bf 704}, 15 (2011);
Phys.\ Rev.\  D {\bf 75}, 011103 (2007);
JHEP {\bf 0911}, 083 (2009);
Phys.\ Rev.\ C {\bf 81}, 035202 (2010);
JHEP {\bf 1210}, 042 (2012).

\bibitem{Chekanov:2003ya}
S. Chekanov {\it et al.} [ZEUS Collaboration],
Phys.\ Lett.\  B {\bf 573}, 46 (2003).

\bibitem{Aktas:2005ty}
A. Aktas {\it et al.} [H1 Collaboration],
Eur.\ Phys.\ J.\ C {\bf 44}, 1 (2005).

\bibitem{Htilde}
The introduced $\tilde H$ contribution is about a factor 3 larger than values given by
standard parametrizations, such as in VGG, or inferred from simple relations to
polarized Parton Distribution Functions.

\bibitem{chi2}
The $\chi^2$ values, integrated over all the bins, give a general indication but the level
of agreement or disagreement between each GPD model's predictions and the data varies as a
function of the kinematics.

\bibitem{Guidal:2008ie}
M. Guidal,
Eur.\ Phys.\ J.\ A {\bf 37}, 319 (2008)
[Erratum-ibid.\ A {\bf 40}, 119 (2009)].

\bibitem{Guidal:2009aa}
M. Guidal and H. Moutarde,
Eur.\ Phys.\ J.\ A {\bf 42}, 71 (2009).

\bibitem{Guidal:2010ig}
M. Guidal,
Phys.\ Lett.\ B {\bf 689}, 156 (2010).

\bibitem{Guidal:2010de}
M. Guidal,
Phys.\ Lett.\ B {\bf 693}, 17 (2010).

\bibitem{CFFdef2}
The CFFs are alternatively defined as four complex quantities whose real and imaginary
parts are respectively as: 
$\Re{\rm e}{\cal F}(\xi,t) = F_{Re}(\xi,t)$ and 
$\Im{\rm m}{\cal F}(\xi,t) = -\pi F_{Im}(\xi,t)$.

\bibitem{Kumericki:2013lia}
K. Kumeri\v{c}ki, D. Mueller and M. Murray,
Nuovo Cim.\ C {\bf 036}, 159-165 (2013).

\bibitem{deskewing}
The transition $H(\xi,\xi,t)\to H(\xi,0,t)$ was estimated in a model-dependent
fashion to be of the order of 20\% in Ref.~\cite{Guidal:2013rya}.

\bibitem{CLASdata}
CLAS Physics Database,
\url{http://clasweb.jlab.org/physicsdb/}

\end{thebibliography}

\end{document}

### 2017-01-18 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
added the coherent prl paper I got from Kawtar

\documentclass[nofootinbib,twocolumn,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
\usepackage{graphicx}
\usepackage{hyperref}
%
\def\Dirac#1{#1\hskip-5pt/}
%
\begin{document}

\title{First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei}

\newcommand*{\ANL}{Argonne National Laboratory, Argonne, Illinois 60439}
\newcommand*{\ANLindex}{1}
\affiliation{\ANL}
\newcommand*{\ORSAY}{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}
\newcommand*{\ORSAYindex}{2}
\affiliation{\ORSAY}
\newcommand*{\JLAB}{Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606}
\newcommand*{\JLABindex}{3}
\affiliation{\JLAB}

\newcommand*{\NOWJLAB}{Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606}
\newcommand*{\NOWODU}{Old Dominion University, Norfolk, Virginia 23529}
 %%%%%%%%%%%%%%% END OF Latex Macros for institute addresses  %%%%%%%%%%%%%%%%%%%%%%%%%

\author {M.~Hattawy}
\affiliation{\ANL}
\affiliation{\ORSAY}
\author {R.~Dupr\'{e}} 
\affiliation{\ANL}
\affiliation{\ORSAY}
\author {N.A.~Baltzell} 
\affiliation{\ANL}
\affiliation{\JLAB}
\author {K.~Hafidi} 
\email[corresponding author: ]{kawtar@anl.gov}
\affiliation{\ANL}

\collaboration{The CLAS Collaboration}
\noaffiliation

%
\date{\today}
%
\begin{abstract}
We report the first exclusive measurements of deeply virtual Compton scattering (DVCS) off a nucleus, where all the products of the reaction including the recoil $^4$He nucleus were detected. The experiment was performed using the Jefferson Lab CEBAF Large Acceptance Spectrometer (CLAS) enhanced with a radial time projection chamber (RTPC) to detect the recoiling $^4$He nuclei. We measure large beam spin asymmetries comparable to the proton's ones and extract in a model independent way, the single chirally-even generalized parton distribution of the $^4$He nucleus. These are pioneering measurements and will lead the way toward the 3D imaging of the partonic structure of nuclei. 
\end{abstract}
\pacs{Valid PACS appear here}

\maketitle

A wealth of information on the quantum chromodynamics (QCD) structure of hadrons lies in the correlations between the momentum and spatial degrees of freedom of the constituent partons. Such correlations are accessible via the generalized parton distributions (GPDs). The GPDs correspond to the coherence between quantum states of different (or same) helicity, longitudinal momentum, and transverse position. In an impact parameter space, they can be interpreted as a distribution in the transverse plane of partons carrying a certain longitudinal momentum \cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep}. A crucial feature of GPDs is the access to the transverse position of partons which, combined with their longitudinal momentum, leads to the total angular momentum of partons \cite{Burkardt:2005hp}. Deep virtual Compton scattering (DVCS) corresponding to hard exclusive electroproduction of a real photon, is considered the cleanest probes to access GPDs and thus study the 3D imaging of nucleons and nuclei.

DVCS measurements have been the focus of a worldwide effort \cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz Camacho:2006hx,Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  CERN. The vast majority of the experiments focused on the study of the nucleon's structure. The deuterium was also investigated at HERMES and JLab \cite{Mazouz:2007aa} mainly as a neutron target. Studying the 3D imaging of the nucleon is terms of its fundamental constituents is a very important goal. Understanding how these distributions are modified to provide the binding and structure in a nucleus is as fascinating of a question and an integral part of our quest of using QCD to explore nuclear matter. The study of nuclear DVCS is still in its infancy due to the challenging detection of the low energy recoil nucleus. Until very recently, the HERMES experiment \cite{Ellinghaus:2002zw} was the only one to measure DVCS off heavier nuclei such as $^4$He, N, Ne, Kr and Xe, where only the scattered electron and the real photon are detected. In this paper, we report the first exclusive measurements of DVCS off $^4$He where all products of the reaction are detected including the recoiling $^4$He nucleus.

\begin{figure}[tb]
\includegraphics[width=6.5cm]{figs/DVCS_diagram.pdf}
\vspace{-0.cm}
\caption{Deep virtual Compton scattering process in the handbag approximation.}
\label{fig:diags}
\end{figure}

\begin{figure}[tb]
\includegraphics[width=6.5cm,angle=-90]{figs/RTPC.pdf}
\vspace{-0.9cm}
\caption{Left: A picture of the \it{eg6} RTPC before insertion into the solenoid. Right: A cross section of the \it{eg6} RTPC perpendicular to the beam direction. An illustration of a $^4$He track originating from the pressurized straw target is shown along with the electrons produced in the drift region.}
\label{fig:RTPC}
\end{figure}

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coh_exc_cuts.pdf}
\vspace{-0.9cm}
\caption{}
\label{fig:kin-cuts}
\end{figure}

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coherent-ALU.pdf}
\vspace{-0.9cm}
\caption{}
\label{fig:alu}
\end{figure}

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/coherent-ALU_90.pdf}
\vspace{-0.9cm}
\caption{}
\label{fig:alu90}
\end{figure}

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/updated_CFFs.pdf}
\vspace{-0.9cm}
\caption{}
\label{fig:CFF_HA}
\end{figure}

We thank the staff of the Accelerator and Physics Divisions
at Jefferson Lab for making this experiment possible.

\begin{thebibliography}{99}

\bibitem{Burkardt:2000za} 
  M.~Burkardt,
  Phys.\ Rev.\ D {\bf 62}, 071503 (2000)
  Erratum: [Phys.\ Rev.\ D {\bf 66}, 119903 (2002)]

\bibitem{Diehl:2002he} 
  M.~Diehl,
  Eur.\ Phys.\ J.\ C {\bf 25}, 223 (2002)
  Erratum: [Eur.\ Phys.\ J.\ C {\bf 31}, 277 (2003)]

\bibitem{Belitsky:2002ep} 
  A.~V.~Belitsky and D.~Mueller,
  Nucl.\ Phys.\ A {\bf 711}, 118 (2002)

\bibitem{Burkardt:2005hp} 
  M.~Burkardt,
  Phys.\ Rev.\ D {\bf 72}, 094020 (2005)

\bibitem{Stepanyan:2001sm}
S.~Stepanyan {\it et al.} [CLAS Collaboration],
Phys.\ Rev.\ Lett. {\bf 87}, 182002 (2001).

\bibitem{Airapetian}
A. Airapetian {\it et al.} [HERMES Collaboration],
Phys.\ Rev.\ Lett. {\bf 87}, 182001 (2001);
JHEP {\bf 1207}, 032 (2012);
JHEP {\bf 1006}, 019 (2010);
JHEP {\bf 0806}, 066 (2008);
Phys.\ Lett.\ B {\bf 704}, 15 (2011);
Phys.\ Rev.\  D {\bf 75}, 011103 (2007);
JHEP {\bf 0911}, 083 (2009);
Phys.\ Rev.\ C {\bf 81}, 035202 (2010);
JHEP {\bf 1210}, 042 (2012).

\bibitem{Chekanov:2003ya}
S. Chekanov {\it et al.} [ZEUS Collaboration],
Phys.\ Lett.\  B {\bf 573}, 46 (2003).

\bibitem{Aktas:2005ty}
A. Aktas {\it et al.} [H1 Collaboration],
Eur.\ Phys.\ J.\ C {\bf 44}, 1 (2005).

\bibitem{Chen:2006na} 
S.~Chen {\it et al.} [CLAS Collaboration],
Phys.\ Rev.\ Lett.\ {\bf 97}, 072002 (2006).

\bibitem{Munoz Camacho:2006hx} 
C. Mu\~noz Camacho {\it et al.} [Jefferson Lab Hall A Collaboration],
Phys.\ Rev.\ Lett. {\bf 97}, 262002 (2006).

\bibitem{Girod:2007aa} 
F.X. Girod {\it et al.} [CLAS Collaboration],
Phys.\ Rev.\ Lett. {\bf 100}, 162002 (2008).

\bibitem{Gavalian:2009} 
G. Gavalian {\it et al.} [CLAS Collaboration],
Phys.\ Rev.\ C {\bf 80}, 035206 (2009).

\bibitem{Seder:2015} 
E. Seder {\it et al.} [CLAS Collaboration],
Phys.\ Rev.\ Lett. {\bf 114}, 032001 (2015).

\bibitem{Pisano:2015} 
S.~Pisano {\it et al.} [CLAS Collaboration],
Phys.\ Rev.\ D {\bf 91}, 052014 (2015).

\bibitem{Jo:2015ema} 
  H.~S.~Jo {\it et al.} [CLAS Collaboration],
  Phys.\ Rev.\ Lett.\  {\bf 115}, no. 21, 212003 (2015)

\bibitem{Mazouz:2007aa} 
  M.~Mazouz {\it et al.} [Jefferson Lab Hall A Collaboration],
   Phys.\ Rev.\ Lett.\  {\bf 99}, 242501 (2007)

\bibitem{Ellinghaus:2002zw} 
  F.~Ellinghaus {\it et al.} [HERMES Collaboration],
  AIP Conf.\ Proc.\  {\bf 675}, 303 (2003)

\end{thebibliography}

\end{document}

### 2017-01-19 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
more writing in the coherent prl paper

@@
 \usepackage{hyperref}
+\usepackage{amsmath}
+\usepackage{dcolumn}% Align table columns on decimal point
+\usepackage{bm}% bold math
+
 %
@@
 \begin{abstract}
-We report the first exclusive measurements of deeply virtual Compton scattering (DVCS) off a nucleus, where all the products of the reaction including the recoil $^4$He nucleus were detected.
-The experiment was performed using the Jefferson Lab CEBAF Large Acceptance Spectrometer (CLAS) enhanced with a radial time projection chamber (RTPC) to detect the recoiling $^4$He nuclei.
-We measure large beam spin asymmetries comparable to the proton's ones and extract in a model independent way, the single chirally-even generalized parton distribution of the $^4$He nucleus.
-These are pioneering measurements and will lead the way toward the 3D imaging of the partonic structure of nuclei.
+We report the first exclusive measurements of deeply virtual Compton scattering 
+(DVCS) off a nucleus, where all the products of the reaction including the 
+recoil $^4$He nucleus were detected. The experiment was performed using the 
+Jefferson Lab CEBAF Large Acceptance Spectrometer (CLAS) enhanced with a radial 
+time projection chamber (RTPC) to detect the recoiling $^4$He nuclei. We 
+measure large beam spin asymmetries comparable to the proton's ones and extract 
+in a model independent way, the single chirally-even generalized parton 
+distribution of the $^4$He nucleus. These are pioneering measurements and will 
+lead the way toward the 3D imaging of the partonic structure of nuclei.  
 \end{abstract}
@@
 
-A wealth of information on the quantum chromodynamics (QCD) structure of hadrons lies in the correlations between the momentum and spatial degrees of freedom of the constituent partons.
-Such correlations are accessible via the generalized parton distributions (GPDs).
-The GPDs correspond to the coherence between quantum states of different (or same) helicity, longitudinal momentum, and transverse position.
-In an impact parameter space, they can be interpreted as a distribution in the transverse plane of partons carrying a certain longitudinal momentum \cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep}.
-A crucial feature of GPDs is the access to the transverse position of partons which, combined with their longitudinal momentum, leads to the total angular momentum of partons \cite{Burkardt:2005hp}.
-Deep virtual Compton scattering (DVCS) corresponding to hard exclusive electroproduction of a real photon, is considered the cleanest probes to access GPDs and thus study the 3D imaging of nucleons and nuclei.
+A wealth of information on the quantum chromodynamics (QCD) structure of 
+hadrons lies in the correlations between the momentum and spatial degrees of 
+freedom of the fundamental constituent partons, quarks and gluons. Such 
+correlations are accessible via the generalized parton distributions (GPDs).  
+The GPDs correspond to the coherence between quantum states of different (or 
+same) helicity, longitudinal momentum, and transverse position. In an impact 
+parameter space, they can be interpreted as a distribution in the transverse 
+plane of partons carrying a certain longitudinal momentum 
+\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep}. A crucial feature of GPDs 
+is the access to the transverse position of partons which, combined with their 
+longitudinal momentum, leads to the total angular momentum of partons 
+\cite{Burkardt:2005hp}. Deep virtual Compton scattering (DVCS) corresponding to 
+hard exclusive electroproduction of a real photon, which is considered as the 
+cleanest probe to access GPDs and thus study the 3D imaging of nucleons and 
+nuclei.
 
-DVCS measurements have been the focus of a worldwide effort \cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz Camacho:2006hx,Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  CERN.
-The vast majority of the experiments focused on the study of the nucleon's structure.
-The deuterium was also investigated at HERMES and JLab \cite{Mazouz:2007aa} mainly as a neutron target.
-Studying the 3D imaging of the nucleon is terms of its fundamental constituents is a very important goal.
-Understanding how these distributions are modified to provide the binding and structure in a nucleus is as fascinating of a question and an integral part of our quest of using QCD to explore nuclear matter.
-The study of nuclear DVCS is still in its infancy due to the challenging detection of the low energy recoil nucleus.
-Until very recently, the HERMES experiment \cite{Ellinghaus:2002zw} was the only one to measure DVCS off heavier nuclei such as $^4$He, N, Ne, Kr and Xe, where only the scattered electron and the real photon are detected.
-In this paper, we report the first exclusive measurements of DVCS off $^4$He where all products of the reaction are detected including the recoiling $^4$He nucleus.
+DVCS measurements have been the focus of a worldwide effort 
+\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
+Camacho:2006hx,Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
+involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
+CERN. The vast majority of the experiments focused on the study of the 
+nucleon's structure. The deuterium was also investigated at HERMES and JLab 
+\cite{Mazouz:2007aa} mainly as a neutron target. However, studying the 3D 
+imaging of the nucleon is a very important goal, understanding how these 
+distributions are modified to provide the binding and structure in a nucleus is 
+as fascinating of a question and an integral part of our quest of using QCD to 
+explore nuclear matter.
+
+A DVCS process on a nuclear target differ from single nucleon scattering in 
+providing access to the measure two DVCS channels. In the coherent DVCS 
+channel, the target nucleus remains intact and recoils as a whole while 
+emitting a real photon ($eA \rightarrow e' A' \gamma$), allowing to measure the 
+nuclear GPDs of the target. In the incoherent channel, the nucleus breaks up 
+and the DVCS takes place on a bound nucleon that emits the final photon ($eA 
+\rightarrow e' N' \gamma$ X), enabling the GPDs measurement of the bound 
+nucleons and to study the medium modifications of the nucleons in the nuclear 
+medium via the GPDs.  Figure \ref{fig:diags} illustrates the dominant mechanism 
+for the coherent DVCS channel on $^4$He. At sufficiently large squared electron 
+momentum transfer $Q^2$ ($= -(k-k')^{2}$) and small squared momentum transfer 
+$t$ ($= (p-p')^{2}$), the QCD factorization theorem predicts that the DVCS 
+handbag diagram can be factorized into two parts, hard and soft parts 
+\cite{Freund_Collins,Ji_Osborne}. The hard part includes photons-quark 
+interaction and it is calculable through perturbative methods, while the 
+soft/non-perturbative part is parametrized in terms of GPDs, which embed the 
+partonic structure of the hadron.
 
@@
 
+%introduction
+The GPDs are defined for each quark flavor and gluon as matrix
+elements of the light cone operators \cite{Belitsky}, describing the transition 
+between the initial and final states of a hadron. The GPDs depend on two 
+longitudinal momentum fraction variables ($x$, $\xi$) and on the momentum 
+transfer $t$ to the target. $x$ is the average longitudinal momentum fraction 
+of the parton involved in the process and $\xi$ is the longitudinal fraction of 
+the momentum transfer $t$, which is related to the Bjorken variable $x_{B}$: 
+$\xi\approx {{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M\nu}$ with
+the proton mass $M$ and $\nu=E_e-E_{e^\prime}$. The GPDs $x$ variable cannot be 
+measured experimentally in a DVCS reaction. Hence, we measure the GPDs 
+convolutions on $x$, the so-called Compton Form Factors (CFF) 
+\cite{Guidal:2013rya}.  In a DVCS process, the number of GPDs needed to 
+parametrize the partonic structure of a hadron depends on the different 
+configurations between the spin of the hadron and the helicity direction of the 
+struck quark.  Therefore, the partonic structure of spin zero nuclei, such as 
+$^4He$ and $^{12}C$, is parametrized by only one GPD ($H_{A}(x,\xi,t)$) at 
+leading twist, while 4 GPDs arise in the nucleon case.  In this work, we have 
+chose the $^4$He nucleus as our target of interest because of it's spinless 
+nature and it shows a clear EMC effect \cite{JSeely}, in addition of having a 
+high density and it is a well-known few-body system.
+
+The study of nuclear DVCS is still in its infancy due to the challenging 
+detection of the low-energy recoil nuclei in fixed target experiments. Until 
+very recently, the HERMES experiment \cite{Ellinghaus:2002zw} was the only one 
+to measure DVCS off heavier nuclei such as $^4$He, N, Ne, Kr and Xe, where only 
+the scattered electron and the real photon are detected. In this paper, we 
+report the first exclusive measurements of coherent DVCS channel off $^4$He 
+where all products of the reaction are detected including the recoiling $^4$He 
+nucleus. The incoherent DVCS channel measurement from the same data set in in 
+preparation and will reported in another publication.
+
+%experimental setup
+
 \begin{figure}[tb]
@@
 \vspace{-0.9cm}
-\caption{Left: A picture of the \it{eg6} RTPC before insertion into the solenoid.
-Right: A cross section of the \it{eg6} RTPC perpendicular to the beam direction.
-An illustration of a $^4$He track originating from the pressurized straw target is shown along with the electrons produced in the drift region.}
+\caption{Left: A picture of the CLAS-EG6 RTPC before insertion into the 
+   solenoid.  Right: A cross section of the CLAS-EG6 RTPC perpendicular to the 
+beam direction. An illustration of a $^4$He track originating from the 
+pressurized straw target is shown along with the electrons produced in the 
+drift region.}
 \label{fig:RTPC}
@@
 
+%DVCS selection
 \begin{figure}[tb]
 \includegraphics[width=8.9cm]{figs/coh_exc_cuts.pdf}
-\vspace{-0.9cm}
-\caption{}
+\caption{ The coherent DVCS exclusivity cuts. The black
+distributions represent the coherent DVCS events candidate. The shaded
+distributions represent the events which passed all the exclusivity cuts
+except the quantity plotted. The vertical red lines represent $3\sigma$ cuts.}
 \label{fig:kin-cuts}
@@
 
+%asymmetries 
 \begin{figure}[tb]
 \includegraphics[width=8.9cm]{figs/coherent-ALU.pdf}
-\vspace{-0.9cm}
-\caption{}
+\caption{The coherent $A_{LU}$ as a function of $\phi$ in
+   $Q^{2}$(top panel), $x_{B}$ (middle panel), and $-t$ (bottom panel) bins.  
+   The error bars represent the statistical and the systematic uncertainties 
+   added quadratically, shown on top in green are error bars representing only 
+   the statistical uncertainties. The brown bands represent the systematic
+uncertainties, including the normalisation systematic uncertainties. The red
+curves represent fits in the form of equation \ref{eq:A_LU-coh}.}
 \label{fig:alu}
@@
 
+%CFF
+we extract the GPD $H$ in a model independent way (figure~\ref{fig:CFF}). This 
+is possible using the beam-spin asymmetry ($A_{LU}$) expression for spin-zero 
+target at leading twist~\cite{BM_2009}:
+\small
+\begin{equation}
+\begin{split}
+A_{LU}(\phi) =~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
+ \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
+{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
+\big( 
+\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
+\label{eq:A_LU-coh}
+\end{split}
+\end{equation}
+\normalsize
+%
+where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary and real parts of the CFF $\mathcal{H}_{A}$ associated to the GPD $H_A$.
+The $\alpha_{i}$'s are $\phi$-dependent kinematical factors that depend on the nuclear form factor $F_A$ and the independent variables $Q^2$, $x_{B}$ and $t$.
+These factors are simplified as:
+%
+\small
+\begin{eqnarray}
+   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
+    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
+   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
+C_{++}(1) cos(\phi) \right)\\
+\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
+{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
+\epsilon^2}
+\end{eqnarray}
+\normalsize
+%
+
+Where $S{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
+leptonic tensor. Their explicit expressions can be found in .
+
 \begin{figure}[tb]
@@
 \vspace{-0.9cm}
-\caption{}
+\caption{The model-independent extraction of the imaginary (blue points) and
+real (red points) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of
+$Q^{2}$ (on the top right), $x_B$ (on the top left), and $t$ (on the bottom).}
 \label{fig:CFF_HA}
 \end{figure}
+
+%interpretations
+
+%conclusion
+
+%Acknowledgments
 
@@
 
-\bibitem{Jo:2015ema} 
-  H.~S.~Jo {\it et al.} [CLAS Collaboration],
+\bibitem{Jo:2015ema} H.~S.~Jo {\it et al.} [CLAS Collaboration],
   Phys.\ Rev.\ Lett.\  {\bf 115}, no. 21, 212003 (2015)
@@
 
-\bibitem{Ellinghaus:2002zw} 
-  F.~Ellinghaus {\it et al.} [HERMES Collaboration],
+\bibitem{Freund_Collins}
+A.~Freund and J.C.~Collins, Phys.\ Rev.\ D {\bf 59}, 074009 (1998)
+
+\bibitem{Ji_Osborne}
+   X.-D.~Ji and J.~Osborne, Phys.\ Rev.\ D {\bf 58}, 094018 (1998)
+
+\bibitem{Belitsky}
+A.~V.~Belitsky and A.~V.~Radyushkin, Phys.\ Rept.\ vol. 418 (2005)
+
+\bibitem{Guidal:2013rya}
+ M.~Guidal, H.~Moutarde and M.~Vanderhaeghen,
+ Rept.\ Prog.\ Phys.\  {\bf 76}, 066202 (2013)
+
+\bibitem{JSeely}
+ J. Seely {\it et al.} Phys.\ Rev.\ Lett.\ {\bf 103}, 202301 (2009)
+
+\bibitem{Ellinghaus:2002zw} F.~Ellinghaus {\it et al.} [HERMES Collaboration],
   AIP Conf.\ Proc.\  {\bf 675}, 303 (2003)

### 2017-01-19 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
updating the experimental setup and some of the figures

@@
 the proton mass $M$ and $\nu=E_e-E_{e^\prime}$. The GPDs $x$ variable cannot be 
-measured experimentally in a DVCS reaction. Hence, we measure the GPDs 
+measured experimentally in a DVCS reaction. Hence, we measure the their 
 convolutions on $x$, the so-called Compton Form Factors (CFF) 
@@
 the scattered electron and the real photon are detected. In this paper, we 
-report the first exclusive measurements of coherent DVCS channel off $^4$He 
+report the first exclusive measurements of the coherent DVCS channel off $^4$He 
 where all products of the reaction are detected including the recoiling $^4$He 
-nucleus. The incoherent DVCS channel measurement from the same data set in in 
-preparation and will reported in another publication.
+nucleus. Following this exclusive measurement, the $^4$He CFF 
+($\mathcal{H}_{A}$) will be extracted experimentally in a fully model 
+independent way for the first time ever. The incoherent DVCS channel 
+measurement from the same data set in in preparation and will reported in 
+another publication.
 
 %experimental setup
+
+The experiment, CLAS-EG6, took place the experimental Hall-B of Jefferson 
+labortory (JLab) in 2009.  JLab delivers a nearly 100\% duty factor, 6~GeV 
+linearly polarized electrons into three experimental halls. The data were 
+collected over three months via projecting a 6.064 GeV longitudinally ploarized 
+beam, (83$\%$ polarization), on a 6 atm gasous $^4$He target, 20 cm long. The 
+CEBAF Large Acceptance Spectrometer (CLAS) was upgraded during the CLAS-EG6 
+running. This detector is large acceptance covering nearly 2$\pi$ and is 
+composed of drift chambers, Cherenkov counters, scintillator counters and an 
+electro-magnetic calorimeter. It allows to detect accurately electrons which 
+provide the trigger for the experiment. It is complemented for DVCS experiments 
+with an inner electro-magnetic calorimeter made of PbWO crystals to detect the 
+photons emitted at low angle and with a solenoid to keep the Moller electrons 
+produced along the beam line to get into our detectors.
+
+In order to ensure the coherence of the process, we also detect the recoiling 
+helium-4 nuclei. We built a small and light radial time projection chamber 
+(RTPC) to detect recoiling helium nuclei down to energies of few MeVs. The 
+chamber, shown in figure~\ref{fig:rtpc}, is surrounding the gaseous target 
+filled with 6~atm helium-4 and is 20 cm long with a 3 cm radial drift 
+length. The detector was specifically calibrated for helium-4 nuclei using 
+elastic scattering produced with a 1.2~GeV electron beam.
+To ensure that the process is exclusive, we apply cuts on 
+several kinematic variables (figure~\ref{fig:exclu}) such as missing energy,
+mass and momentum. The cuts are chosen to represent consistently 3 half width 
+at half maximum in order to avoid any bias in the selection.
 
@@
 \begin{figure}[tb]
-\includegraphics[width=8.9cm]{figs/updated_CFFs.pdf}
+\includegraphics[width=8.9cm]{figs/Coherent_CFF.pdf}
 \vspace{-0.9cm}

### 2017-01-19 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
fix references for some figures

@@
 (RTPC) to detect recoiling helium nuclei down to energies of few MeVs. The 
-chamber, shown in figure~\ref{fig:rtpc}, is surrounding the gaseous target 
-filled with 6~atm helium-4 and is 20 cm long with a 3 cm radial drift 
-length. The detector was specifically calibrated for helium-4 nuclei using 
-elastic scattering produced with a 1.2~GeV electron beam.
-To ensure that the process is exclusive, we apply cuts on 
-several kinematic variables (figure~\ref{fig:exclu}) such as missing energy,
+chamber, shown in figure~\ref{fig:RTPC}, is surrounding the gaseous target 
+filled with 6~atm helium-4 and is 20 cm long with a 3 cm radial drift length.  
+The detector was specifically calibrated for helium-4 nuclei using elastic 
+scattering produced with a 1.2~GeV electron beam.
+To ensure that the process is exclusive, we apply cuts on several kinematic 
+variables (figure~\ref{fig:kin-cuts}) such as missing energy,
 mass and momentum. The cuts are chosen to represent consistently 3 half width 
@@
 %CFF
-we extract the GPD $H$ in a model independent way (figure~\ref{fig:CFF}). This 
-is possible using the beam-spin asymmetry ($A_{LU}$) expression for spin-zero 
-target at leading twist~\cite{BM_2009}:
+we extract the GPD $H$ in a model independent way (figure~\ref{fig:CFF_HA}).  
+This is possible using the beam-spin asymmetry ($A_{LU}$) expression for 
+spin-zero target at leading twist~\cite{BM_2009}:
 \small

### 2017-01-20 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
update the experimental setup part in the coherent prl paper

--- 2017-01-19 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
@@
 the scattered electron and the real photon are detected. In this paper, we 
-report the first exclusive measurements of coherent DVCS channel off $^4$He 
+report the first exclusive measurements of the coherent DVCS channel off $^4$He 
 where all products of the reaction are detected including the recoiling $^4$He 
-nucleus. The incoherent DVCS channel measurement from the same data set in in 
-preparation and will reported in another publication.
+nucleus. Following this exclusive measurement, the $^4$He CFF 
+($\mathcal{H}_{A}$) will be extracted experimentally in a fully model 
+independent way for the first time ever. The incoherent DVCS channel 
+measurement from the same data set in in preparation and will reported in 
+another publication.
 
@@
 
+The experiment, CLAS-EG6, took place in the experimental Hall-B of Jefferson 
+labortory (JLab) in 2009. JLab delivers, simultaneously, a nearly 100\% duty 
+factor polarized electrons into three experimental Halls (A, B, C). The data 
+were collected over three months via projecting a 6.064 GeV longitudinally 
+ploarized beam, (83$\%$ polarization), on a 6 atm gasous $^4$He target.  The 
+Hall-B Large Acceptance Spectrometer (CLAS) basic desing \cite{CLAS_ref} was 
+upgraded, during the CLAS-E1DVCS1 experimental run \cite{Girod:2007aa} in 2005, 
+with a specially designed electromagnetic calorimeneter, Inner calorimeter 
+(IC). The IC has extended the photon detection acceptance of CLAS, which is 
+origionally from 15$^{\circ}$ to 45$^{\circ}$, to polar angle reach as minimum 
+as 4$^{\circ}$. During the same experiment, a 5 Tesla solenoid was added around 
+the target to shield the inner detectors from the low-energy M\o ller 
+electrons.
+
+At 6 GeV incident electron beam energy, the recoil $^4$He nuclei, from the 
+coherent DVCS channel, have an average momentum (per charge) around 125 MeV/c, 
+while the CLAS spectrometer detects charged particles with a threshold of 250 
+MeV/c. In order to ensure the exculsitivy of the our coherent DVCS channel, we 
+built a small and light radial time projection chamber (RTPC) to detect 
+recoiling nuclei down to energies of few MeVs. Figure~\ref{fig:RTPC} presents 
+our cylinderical RTPC, which is 20 cm long and 15 cm diameter, surrounding the 
+$^4$He gaseous target, with a 3 cm radial drift length. The detector was 
+specifically calibrated for $^4$He nuclei using elastic scattering produced 
+with a 1.2~GeV electron beam.
+
 \begin{figure}[tb]
-\includegraphics[width=6.5cm,angle=-90]{figs/RTPC.pdf}
+\includegraphics[width=7.0cm,angle=-90]{figs/RTPC.pdf}
 \vspace{-0.9cm}
@@
 \end{figure}
+
+To ensure that the process is exclusive, we apply cuts on several kinematic 
+variables (figure~\ref{fig:kin-cuts}) such as missing energy,
+mass and momentum. The cuts are chosen to represent consistently 3 half width 
+at half maximum in order to avoid any bias in the selection.
 
@@
 
+\bibitem{CLAS_ref}
+   B.A. Mecking {\it et al.}, Nucl.\ Inst.\ and Meth.\ A 503, 513 (2003).
+
 \bibitem{Ellinghaus:2002zw} F.~Ellinghaus {\it et al.} [HERMES Collaboration],

### 2017-01-20 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
add the DVCS exclusive selection part in the coherent prl paper

@@
 The experiment, CLAS-EG6, took place in the experimental Hall-B of Jefferson 
-labortory (JLab) in 2009. JLab delivers, simultaneously, a nearly 100\% duty 
+laboratory (JLab) in 2009. JLab delivers, simultaneously, a nearly 100\% duty 
 factor polarized electrons into three experimental Halls (A, B, C). The data 
 were collected over three months via projecting a 6.064 GeV longitudinally 
-ploarized beam, (83$\%$ polarization), on a 6 atm gasous $^4$He target.  The 
-Hall-B Large Acceptance Spectrometer (CLAS) basic desing \cite{CLAS_ref} was 
+polarized beam, (83$\%$ polarization), on a 6 atm gaseous $^4$He target.  The 
+Hall-B Large Acceptance Spectrometer (CLAS) basic design \cite{CLAS_ref} was 
 upgraded, during the CLAS-E1DVCS1 experimental run \cite{Girod:2007aa} in 2005, 
-with a specially designed electromagnetic calorimeneter, Inner calorimeter 
-(IC). The IC has extended the photon detection acceptance of CLAS, which is 
-origionally from 15$^{\circ}$ to 45$^{\circ}$, to polar angle reach as minimum 
+with a specially designed electromagnetic calorimeter, Inner calorimeter (IC).  
+The IC has extended the photon detection acceptance of CLAS, which is 
+originally from 15$^{\circ}$ to 45$^{\circ}$, to polar angle reach as minimum 
 as 4$^{\circ}$. During the same experiment, a 5 Tesla solenoid was added around 
@@
 while the CLAS spectrometer detects charged particles with a threshold of 250 
-MeV/c. In order to ensure the exculsitivy of the our coherent DVCS channel, we 
+MeV/c. In order to ensure the exclusivity of the our coherent DVCS channel, we 
 built a small and light radial time projection chamber (RTPC) to detect 
 recoiling nuclei down to energies of few MeVs. Figure~\ref{fig:RTPC} presents 
-our cylinderical RTPC, which is 20 cm long and 15 cm diameter, surrounding the 
+our cylindrical RTPC, which is 20 cm long and 15 cm diameter, surrounding the 
 $^4$He gaseous target, with a 3 cm radial drift length. The detector was 
@@
 
-To ensure that the process is exclusive, we apply cuts on several kinematic 
-variables (figure~\ref{fig:kin-cuts}) such as missing energy,
-mass and momentum. The cuts are chosen to represent consistently 3 half width 
-at half maximum in order to avoid any bias in the selection.
+%DVCS selection
+Identifying the coherent DVCS candidates is the first step of the data 
+analysis. These are the events with one electron, one $^4$He, and at least one 
+photon in the final state. Electrons were identified by passing the fiducial 
+cuts and having signals in all the sub-detectors of CLAS spectrometer (drift 
+chambers, Cherenkov counters, the standard CLAS electromagnetic calorimeter, 
+and scintillators). $^4$He tracks were identified by passing all the 
+geometrical, timing and quality cuts in the RTPC detector. The most energetic 
+IC photon was considered as the DVCS photon candidate. Next, a 
+$Q^{2}~>~[GeV^{2}/c^{2}]$ cut is applied on the DVCS candidates in order to 
+ensure that the interaction occurs at the partonic level and the applicability
+of the factorization in the DVCS handbag diagram. One the three final state 
+particles were identified with their 3-momentum vectors, the exclusivity of the 
+coherent DVCS events were ensured by applied a set of 3$\sigma$ exclusivity 
+cuts. The exclusive cuts are: the co-planarity angle ($\Delta \phi$), missing 
+energy, missing mass squared and missing transverse momentum in the 
+$e'~^4He'~\gamma~X$ final state configuration, the missing mass squared in the 
+$e'~^4He'~X$ and $e'~\gamma~X$ configurations, and finally the cone angle 
+($\theta$) between the measured real photon and the missing particle in the 
+$e'~^4He'~X$ configuration. Figure~\ref{fig:kin-cuts} presents four of the 
+applied exclusivity cuts.
 
-%DVCS selection
 \begin{figure}[tb]

### 2017-01-21 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
more writing in the dvcs selection part

@@
 providing access to the measure two DVCS channels. In the coherent DVCS 
-channel, the target nucleus remains intact and recoils as a whole while 
+channel, the target nucleus ($A$) remains intact and recoils as a whole while 
 emitting a real photon ($eA \rightarrow e' A' \gamma$), allowing to measure the 
 nuclear GPDs of the target. In the incoherent channel, the nucleus breaks up 
-and the DVCS takes place on a bound nucleon that emits the final photon ($eA 
-\rightarrow e' N' \gamma$ X), enabling the GPDs measurement of the bound 
+and the DVCS takes place on a bound nucleon ($N$) that emits the final photon 
+($eA \rightarrow e' N' \gamma$ X), enabling the GPDs measurement of the bound 
 nucleons and to study the medium modifications of the nucleons in the nuclear 
@@
 our cylindrical RTPC, which is 20 cm long and 15 cm diameter, surrounding the 
-$^4$He gaseous target, with a 3 cm radial drift length. The detector was 
-specifically calibrated for $^4$He nuclei using elastic scattering produced 
-with a 1.2~GeV electron beam.
+$^4$He gaseous target and being inside the available space inside the solenoid 
+, with a 3 cm radial drift length. The detector was specifically calibrated for 
+$^4$He nuclei using elastic scattering produced with a 1.2~GeV electron beam.
 
@@
 
+\begin{figure}[tb]
+\hspace{-0.45cm}
+\includegraphics[width=9.0cm]{figs/Q2_xB_t_Coh.pdf}
+\caption{The $Q^{2}$ as a function of $x_{B}$ (left) and the $Q^{2}$ as a 
+function of $-t$ (right) for the identified coherent DVCS events after the 
+exclusivity cuts.}
+\label{fig:kin-coverage}
+\end{figure}
+
 %asymmetries
+
+We identified several background contributions to the DVCS process, in 
+particular accidental events and exclusive deeply virtual $\pi^0$ production 
+(DV$\pi^0$P). The accidental
+events where the different particles come from different events are 
+suppressed by the limited phase space allowed by the exclusivity cuts. We 
+estimate the accidental events to represent 4.1\% of our sample. This 
+relatively large number is due to the small cross section of the DVCS. We 
+evaluated this contribution by selecting events passing all our cuts but with 
+particles originating from different vertices.
+
+Another important source of background is the deeply virtual 
+$\pi^0$ production (DV$\pi^0$P), which can easily be mistaken
+with DVCS when one of the two photons of the $\pi^0$ decay is produced at
+low energy in the laboratory frame. To estimate the importance of
+this background, we developped an event generator 
+that we calibrated to match our measured experimental yield of exclusive 
+$pi^0$. We used this generator together 
+with a GEANT3 simulation of our detection system to estimate the ratio 
+of acceptance between DV$\pi^0$P where the two photons are detected and those
+where only one photon is detected and would pass our 
+DVCS selection cuts. This ratio obtained from simulation is then multiplied by 
+the measured yield of DV$\pi^0$P events, indicating a contamination of 2 to 4\%. 
+The study of systematics errors showed that the main contributions come from 
+the choice of the DVCS exclusivity cuts (8\%) and the large binning size 
+(5.1\%). However added quadratically, these errors sum up to 10\% which remain 
+for all bins well below the statistical errors.
+
+The beam-spin asymmetry is measurable using a polarized lepton beam on an 
+unpolarized target (U). It is convenient to use the beam-spin asymmetry as a 
+DVCS observable because most of the experimental normalization and acceptance 
+issues cancel out in the asymmetry ratio. It is defined as in terms of the 
+cross sections as:
+  \begin{equation}
+  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
+                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
+    \label{BSA_equation}
+  \end{equation}
+  where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the DVCS differential cross section for a positive (negative) beam helicity.
+
+In terms of the collected number of events in each beam-helicity state 
+($N^{+}$, $N^{-}$), A LU can be
+expressed as:
+
+\begin{equation}
+A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} }.
+\end{equation}
+%
+where $P_{B}$ is the beam polarization, and $N^{+}$ and $N^{-}$ are the number of events detected with positive and negative electron helicity, respectively. The statistical uncertainty of $A_{LU}$ is
+%
+\begin{equation}
+   \sigma_{A_{LU}} = \frac{1}{P_{B}} \sqrt{ \frac{1 - (P_{B}A_{LU})^{2}}{N}}
+\end{equation}
+%
+where $N (N^{+} + N^{-}) $ is the total number of measured events.
+%
+
 \begin{figure}[tb]

### 2017-01-23 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
added the BH reaction and the BKM equations

@@
 ($eA \rightarrow e' N' \gamma$ X), enabling the GPDs measurement of the bound 
-nucleons and to study the medium modifications of the nucleons in the nuclear 
-medium via the GPDs.  Figure \ref{fig:diags} illustrates the dominant mechanism 
-for the coherent DVCS channel on $^4$He. At sufficiently large squared electron 
-momentum transfer $Q^2$ ($= -(k-k')^{2}$) and small squared momentum transfer 
-$t$ ($= (p-p')^{2}$), the QCD factorization theorem predicts that the DVCS 
-handbag diagram can be factorized into two parts, hard and soft parts 
+nucleons and to study their modifications in the nuclear medium via the GPDs.  
+Figure \ref{fig:diags} illustrates the dominant mechanism for the coherent DVCS 
+channel on $^4$He. At sufficiently large squared electron momentum transfer 
+$Q^2$ ($= -(k-k')^{2}$) and small squared momentum transfer $t$ ($= 
+(p-p')^{2}$), the QCD factorization theorem predicts that the DVCS handbag 
+diagram can be factorized into two parts, hard and soft parts 
 \cite{Freund_Collins,Ji_Osborne}. The hard part includes photons-quark 
@@
 soft/non-perturbative part is parametrized in terms of GPDs, which embed the 
-partonic structure of the hadron.
+partonic structure of the hadron. Experimentally, the DVCS reaction is 
+indistinguishable from the Bethe-Heitler (BH) process, which is the reaction 
+where the final photon is emitted either from the incoming or the outgoing 
+leptons. The BH process is not sensitive to GPDs and does not carry information 
+about the partonic structure of the hadronic target. The BH cross section is 
+calculable from the well-known electromagnetic form factors.
 
@@
 Identifying the coherent DVCS candidates is the first step of the data 
-analysis. These are the events with one electron, one $^4$He, and at least one 
-photon in the final state. Electrons were identified by passing the fiducial 
-cuts and having signals in all the sub-detectors of CLAS spectrometer (drift 
-chambers, Cherenkov counters, the standard CLAS electromagnetic calorimeter, 
-and scintillators). $^4$He tracks were identified by passing all the 
-geometrical, timing and quality cuts in the RTPC detector. The most energetic 
-IC photon was considered as the DVCS photon candidate. Next, a 
-$Q^{2}~>~[GeV^{2}/c^{2}]$ cut is applied on the DVCS candidates in order to 
-ensure that the interaction occurs at the partonic level and the applicability
-of the factorization in the DVCS handbag diagram. One the three final state 
-particles were identified with their 3-momentum vectors, the exclusivity of the 
-coherent DVCS events were ensured by applied a set of 3$\sigma$ exclusivity 
-cuts. The exclusive cuts are: the co-planarity angle ($\Delta \phi$), missing 
-energy, missing mass squared and missing transverse momentum in the 
-$e'~^4He'~\gamma~X$ final state configuration, the missing mass squared in the 
-$e'~^4He'~X$ and $e'~\gamma~X$ configurations, and finally the cone angle 
-($\theta$) between the measured real photon and the missing particle in the 
-$e'~^4He'~X$ configuration. Figure~\ref{fig:kin-cuts} presents four of the 
-applied exclusivity cuts.
+analysis. These events have one electron, one $^4$He, and at least one photon 
+in the final state. Electrons were identified by passing the fiducial cuts and 
+having signals in all the sub-detectors of CLAS spectrometer (drift chambers, 
+Cherenkov counters, the standard CLAS electromagnetic calorimeter, and 
+scintillators). $^4$He tracks were identified by passing all the geometrical, 
+timing and quality cuts in the RTPC detector. The most energetic IC photon was 
+considered as the DVCS photon candidate. Next, a $Q^{2}>1~[GeV^{2}/c^{2}]$ cut 
+is applied on the DVCS candidates in order to ensure that the interaction 
+occurs at the partonic level and the applicability of the factorization in the 
+DVCS handbag diagram. Once the three final state particles were identified with 
+their 3-momentum vectors, the exclusivity of the coherent DVCS events were 
+ensured by applied a set of 3$\sigma$ exclusivity cuts. The exclusive cuts are: 
+the co-planarity angle ($\Delta \phi$), missing energy, missing mass squared 
+and missing transverse momentum in the $e'~^4He'~\gamma~X$ final state 
+configuration, the missing mass squared in the $e'~^4He'~X$ and $e'~\gamma~X$ 
+configurations, and finally the cone angle ($\theta$) between the measured real 
+photon and the missing particle in the $e'~^4He'~X$ configuration.  
+Figure~\ref{fig:kin-cuts} presents four of the applied exclusivity cuts.
 
@@
 \includegraphics[width=8.9cm]{figs/coh_exc_cuts.pdf}
-\caption{ The coherent DVCS exclusivity cuts. The black
+\caption{Four of the seven coherent DVCS exclusivity cuts. The black 
 distributions represent the coherent DVCS events candidate. The shaded 
-distributions represent the events which passed all the exclusivity cuts
-except the quantity plotted. The vertical red lines represent $3\sigma$ cuts.}
+distributions represent the events which passed all the exclusivity cuts except 
+the quantity plotted. The vertical red lines represent $3\sigma$ cuts. The 
+distributions from left to right and from top to bottoms are: $\Delta \phi$, 
+missing energy and missing mass squared in $e'~^4He'~\gamma~X$, and the cone 
+angle ($\theta$) between the measured and the calculated final state real 
+photon.}
 \label{fig:kin-cuts}
 \end{figure}
+After all the particle identification requirements on the individual particle 
+of the coherent DVCS events and after all the exclusivity cuts, we ended up 
+with about 3500 events. Figure \ref{fig:kin-coverage} presents the 
+($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$) kinematic coverage of the collected DVCS 
+events.
 
@@
 %asymmetries
+Even with all the previously presented exclusive cuts, the selected events are
+not all true DVCS events. We identified several background contributions to the 
+coherent DVCS process, in particular accidental events and exclusive Deeply 
+Virtual $\pi^0$ Production (DV$\pi^0$P). The accidental events where the 
+different particles come from different events are suppressed by the limited 
+phase space allowed by the exclusivity cuts. We estimate the accidental events 
+to represent 4.1\% of our sample. This relatively large number is due to the 
+small cross section of the DVCS. We evaluated this contribution by selecting 
+events passing all our cuts but with particles originating from different 
+vertices. Regarding the DV$\pi^0$P, which can easily be mistaken with DVCS when 
+one of the two photons of the $\pi^0$ decay is produced at low energy in the 
+laboratory frame. To estimate the importance of this background, we developed 
+an event generator that we calibrated to match our measured experimental yield 
+of exclusive $\pi^0$. We used this generator together with a GEANT3 simulation 
+of our detection system to estimate the ratio of acceptance between DV$\pi^0$P 
+where the two photons are detected and those where only one photon is detected 
+and would pass our DVCS selection cuts. This ratio obtained from simulation is 
+then multiplied by the measured yield of DV$\pi^0$P events, indicating a 
+contamination of 2 to 4\%. The study of systematics errors showed that the main 
+contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
+large binning size (5.1\%). However added quadratically, these errors sum up to 
+10\% which remain for all bins well below the statistical errors.
 
-We identified several background contributions to the DVCS process, in 
-particular accidental events and exclusive deeply virtual $\pi^0$ production 
-(DV$\pi^0$P). The accidental
-events where the different particles come from different events are 
-suppressed by the limited phase space allowed by the exclusivity cuts. We 
-estimate the accidental events to represent 4.1\% of our sample. This 
-relatively large number is due to the small cross section of the DVCS. We 
-evaluated this contribution by selecting events passing all our cuts but with 
-particles originating from different vertices.
-
-Another important source of background is the deeply virtual 
-$\pi^0$ production (DV$\pi^0$P), which can easily be mistaken
-with DVCS when one of the two photons of the $\pi^0$ decay is produced at
-low energy in the laboratory frame. To estimate the importance of
-this background, we developped an event generator 
-that we calibrated to match our measured experimental yield of exclusive 
-$pi^0$. We used this generator together 
-with a GEANT3 simulation of our detection system to estimate the ratio 
-of acceptance between DV$\pi^0$P where the two photons are detected and those
-where only one photon is detected and would pass our 
-DVCS selection cuts. This ratio obtained from simulation is then multiplied by 
-the measured yield of DV$\pi^0$P events, indicating a contamination of 2 to 4\%. 
-The study of systematics errors showed that the main contributions come from 
-the choice of the DVCS exclusivity cuts (8\%) and the large binning size 
-(5.1\%). However added quadratically, these errors sum up to 10\% which remain 
-for all bins well below the statistical errors.
-
-The beam-spin asymmetry is measurable using a polarized lepton beam on an 
-unpolarized target (U). It is convenient to use the beam-spin asymmetry as a 
-DVCS observable because most of the experimental normalization and acceptance 
-issues cancel out in the asymmetry ratio. It is defined as in terms of the 
-cross sections as:
+The beam-spin asymmetry is our DVCS observable, which is measurable using a 
+polarized lepton beam on an unpolarized target (U). It is convenient to use the 
+beam-spin asymmetry as a DVCS observable because most of the experimental 
+normalization and acceptance issues cancel out in the asymmetry ratio. It is 
+defined in terms of the cross sections as:
   \begin{equation}
@@
   \end{equation}
-  where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the DVCS differential cross section for a positive (negative) beam helicity.
-
-In terms of the collected number of events in each beam-helicity state 
-($N^{+}$, $N^{-}$), A LU can be
-expressed as:
-
+  where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the DVCS differential cross 
+  section for a positive (negative) beam helicity. $A_{LU}$ can be simplified 
+  in terms of the collected number of events in each beam-helicity state 
+  ($N^{+}$, $N^{-}$) as:
 \begin{equation}
@@
 \end{equation}
-%
-where $P_{B}$ is the beam polarization, and $N^{+}$ and $N^{-}$ are the number of events detected with positive and negative electron helicity, respectively. The statistical uncertainty of $A_{LU}$ is
-%
+where $P_{B}$ is the beam polarization, and $N^{+}$ and $N^{-}$ are the number 
+of events detected with positive and negative electron helicity, respectively.  
+The statistical uncertainty of $A_{LU}$ is
 \begin{equation}
@@
 \end{equation}
-%
 where $N (N^{+} + N^{-}) $ is the total number of measured events.
-%
+
+%CFF
+we extract the GPD $H$ in a model independent way (figure~\ref{fig:CFF_HA}).  
+This is possible using the beam-spin asymmetry ($A_{LU}$) expression for 
+spin-zero target at leading twist \cite{Kirchner:2003wt,Belitsky:2008bz}:
+\small
+\begin{equation}
+\begin{split}
+A_{LU}(\phi) =~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
+ \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
+{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
+\big( 
+\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
+\label{eq:A_LU-coh}
+\end{split}
+\end{equation}
+\normalsize
+where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
+and real parts of the CFF $\mathcal{H}_{A}$ associated to the GPD $H_A$. The 
+$\alpha_{i}$'s are $\phi$-dependent kinematical factors that depend on the 
+nuclear form factor $F_A$ and the independent variables $Q^2$, $x_{B}$ and $t$.  
+These factors are simplified as:
+\small
+\begin{eqnarray}
+   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
+    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
+   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
+C_{++}(1) cos(\phi) \right)\\
+\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
+{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
+\epsilon^2}
+\end{eqnarray}
+\normalsize
+
+Where $S{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
+leptonic tensor. Their explicit expressions can be found in .
 
@@
 \end{figure}
-
-%CFF
-we extract the GPD $H$ in a model independent way (figure~\ref{fig:CFF_HA}).  
-This is possible using the beam-spin asymmetry ($A_{LU}$) expression for 
-spin-zero target at leading twist~\cite{BM_2009}:
-\small
-\begin{equation}
-\begin{split}
-A_{LU}(\phi) =~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
- \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
-{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
-\big( 
-\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
-\label{eq:A_LU-coh}
-\end{split}
-\end{equation}
-\normalsize
-%
-where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary and real parts of the CFF $\mathcal{H}_{A}$ associated to the GPD $H_A$.
-The $\alpha_{i}$'s are $\phi$-dependent kinematical factors that depend on the nuclear form factor $F_A$ and the independent variables $Q^2$, $x_{B}$ and $t$.
-These factors are simplified as:
-%
-\small
-\begin{eqnarray}
-   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
-    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
-   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
-C_{++}(1) cos(\phi) \right)\\
-\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
-{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
-\epsilon^2}
-\end{eqnarray}
-\normalsize
-%
-
-Where $S{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
-leptonic tensor. Their explicit expressions can be found in .
 
@@
 \bibitem{CLAS_ref}
-   B.A. Mecking {\it et al.}, Nucl.\ Inst.\ and Meth.\ A 503, 513 (2003).
+   B.A. Mecking {\it et al.}, Nucl.\ Inst.\ and Meth.\ A 503, 513 (2003)
+
+\bibitem{Kirchner:2003wt} 
+   A.~Kirchner and D.~Mueller, Eur.\ Phys.\ J.\ C {\bf 32}, 347 (2003)
+
+\bibitem{Belitsky:2008bz} A.~V.~Belitsky and D.~Mueller,
+     Phys.\ Rev.\ D {\bf 79}, 014017 (2009)
 

### 2017-01-24 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
edit the main latex file
writing the results section

@@
 soft/non-perturbative part is parametrized in terms of GPDs, which embed the 
-partonic structure of the hadron. Experimentally, the DVCS reaction is 
-indistinguishable from the Bethe-Heitler (BH) process, which is the reaction 
-where the final photon is emitted either from the incoming or the outgoing 
-leptons. The BH process is not sensitive to GPDs and does not carry information 
-about the partonic structure of the hadronic target. The BH cross section is 
-calculable from the well-known electromagnetic form factors.
-
+partonic structure of the hadron.  
 \begin{figure}[tb]
@@
 
+This work presents the first exclusive measurement of the beam-spin asymmetry 
+of the reaction $e~^{4}He\rightarrow e'~^{4}He~\gamma$.This DVCS sensitive 
+observable is measurable using a polarized lepton beam on an unpolarized target 
+(U). It is convenient to use the beam-spin asymmetry as a DVCS observable 
+because most of the experimental normalization and acceptance issues cancel out 
+in the asymmetry ratio. It is defined in terms of the cross sections as:
+  \begin{equation}
+  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
+                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
+    \label{BSA_equation}
+  \end{equation}
+where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the DVCS differential cross 
+section for a positive (negative) beam helicity. Experimentally, the DVCS 
+reaction is indistinguishable from the Bethe-Heitler (BH) process, where the 
+final photon is emitted either from the incoming or the outgoing leptons. The 
+BH process is not sensitive to GPDs and does not carry information about the 
+partonic structure of the hadronic target, and it's amplitude is calculable 
+from the well-known electromagnetic form factors.
+
+The photon-electroproduction cross section can be decomposed into a BH,
+a DVCS, and an interference terms. At leading twist, the amplitudes of the 
+three terms can be decomposed into a finite sum of Fourier harmonics, the 
+so-called BMK formalism, as shown for the nucleon DVCS in 
+\cite{Belitsky:2001ns} and for the spinless nuclei in 
+\cite{Kirchner:2003wt,Belitsky:2008bz}. Therefore, the beam-spin asymmetry 
+($A_{LU}$) with the two opposite helicities of a longitudinally-polarized 
+electron beam (L) on a spin-zero target (U) can be written as:
+\small
+\begin{equation}
+\begin{split}
+A_{LU}(\phi) =~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
+ \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
+{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
+\big( 
+\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
+\label{eq:A_LU-coh}
+\end{split}
+\end{equation}
+\normalsize
+where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
+and real parts of the $^4$He CFF $\mathcal{H}_{A}$ associated to the GPD $H_A$.  
+The $\alpha_{i}$'s are $\phi$-dependent kinematical factors that depend on the 
+nuclear form factor ($F_{A}(t)$) and the independent variables $Q^2$, $x_{B}$ 
+and $t$. These factors are simplified as:
+\small
+\begin{eqnarray}
+   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
+    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
+   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
+C_{++}(1) cos(\phi) \right)\\
+\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
+{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
+\epsilon^2}
+\end{eqnarray}
+\normalsize
+
+Where $S{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
+leptonic tensor. Their explicit expressions can be found in 
+\cite{Belitsky:2008bz}. Therefore, Using the $\alpha_{i}$ factors, one can 
+obtain in a totally model-independent way $\Im m(\mathcal{H}_{A})$ and $\Re 
+e(\mathcal{H}_{A})$ from fitting the experimental $A_{LU}$ as a function of 
+$\phi$, the azimuthal angle between the ($e$,$e'$) and ($\gamma^{*}$,$^4$He$'$) 
+planes, for given values of $Q^2$, $x_{B}$, and $t$.
+
 %experimental setup
@@
 Hall-B Large Acceptance Spectrometer (CLAS) basic design \cite{CLAS_ref} was 
-upgraded, during the CLAS-E1DVCS1 experimental run \cite{Girod:2007aa} in 2005, 
-with a specially designed electromagnetic calorimeter, Inner calorimeter (IC).  
-The IC has extended the photon detection acceptance of CLAS, which is 
+supplemented, during the CLAS-E1DVCS1 experimental run \cite{Girod:2007aa} in 
+2005, with a specially designed electromagnetic calorimeter, Inner calorimeter 
+(IC). The IC has extended the photon detection acceptance of CLAS, which is 
 originally from 15$^{\circ}$ to 45$^{\circ}$, to polar angle reach as minimum 
-as 4$^{\circ}$. During the same experiment, a 5 Tesla solenoid was added around 
-the target to shield the inner detectors from the low-energy M\o ller 
+as 4$^{\circ}$.  During the same experiment, a 5 Tesla solenoid was added 
+around the target to shield the inner detectors from the low-energy M\o ller 
 electrons.
@@
 \includegraphics[width=7.0cm,angle=-90]{figs/RTPC.pdf}
-\vspace{-0.9cm}
+\vspace{-1.1cm}
 \caption{Left: A picture of the CLAS-EG6 RTPC before insertion into the 
@@
 their 3-momentum vectors, the exclusivity of the coherent DVCS events were 
-ensured by applied a set of 3$\sigma$ exclusivity cuts. The exclusive cuts are: 
-the co-planarity angle ($\Delta \phi$), missing energy, missing mass squared 
-and missing transverse momentum in the $e'~^4He'~\gamma~X$ final state 
-configuration, the missing mass squared in the $e'~^4He'~X$ and $e'~\gamma~X$ 
-configurations, and finally the cone angle ($\theta$) between the measured real 
-photon and the missing particle in the $e'~^4He'~X$ configuration.  
-Figure~\ref{fig:kin-cuts} presents four of the applied exclusivity cuts.
+ensured by applying a set of exclusive cuts, which are: the co-planarity angle 
+($\Delta \phi$), missing energy, missing mass squared and missing transverse 
+momentum in the $e'^4He'\gamma X$ final state configuration, the missing mass 
+squared in the $e'^4He'X$ and $e'\gamma X$ configurations, and finally the cone 
+angle ($\theta$) between the measured real photon and the missing particle in 
+the $e'^4He'X$ configuration. Figure~\ref{fig:kin-cuts} presents four of the 
+applied exclusivity cuts, where 3$\sigma$ cuts are applied on all the exclusive 
+quantities except the missing energy, for which a [-0.45,0.5] GeV cut was 
+adopted to reduce the background contribution.
 
@@
 distributions represent the events which passed all the exclusivity cuts except 
-the quantity plotted. The vertical red lines represent $3\sigma$ cuts. The 
-distributions from left to right and from top to bottoms are: $\Delta \phi$, 
-missing energy and missing mass squared in $e'~^4He'~\gamma~X$, and the cone 
-angle ($\theta$) between the measured and the calculated final state real 
-photon.}
+the quantity plotted. The vertical red lines represent the applied exclusivity 
+cuts. The distributions from left to right and from top to bottoms are: $\Delta 
+\phi$, missing energy and missing mass squared in $e'^4He'\gamma X$, and the 
+cone angle ($\theta$) between the measured and the calculated photons.}
 \label{fig:kin-cuts}
 \end{figure}
-After all the particle identification requirements on the individual particle 
-of the coherent DVCS events and after all the exclusivity cuts, we ended up 
-with about 3500 events. Figure \ref{fig:kin-coverage} presents the 
-($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$) kinematic coverage of the collected DVCS 
-events.
+After all the requirements on the individual final state particles of the 
+coherent DVCS events and the exclusivity cuts, we ended up with about 3500 
+events. Figure \ref{fig:kin-coverage} presents the ($Q^{2}$,$x_{B}$) and 
+($Q^{2}$,$-t$) kinematic coverage of the collected DVCS events.
 
@@
 large binning size (5.1\%). However added quadratically, these errors sum up to 
-10\% which remain for all bins well below the statistical errors.
+10\%, which remain for all bins well below the statistical errors.
 
-The beam-spin asymmetry is our DVCS observable, which is measurable using a 
-polarized lepton beam on an unpolarized target (U). It is convenient to use the 
-beam-spin asymmetry as a DVCS observable because most of the experimental 
-normalization and acceptance issues cancel out in the asymmetry ratio. It is 
-defined in terms of the cross sections as:
-  \begin{equation}
-  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
-                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
-    \label{BSA_equation}
-  \end{equation}
-  where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the DVCS differential cross 
-  section for a positive (negative) beam helicity. $A_{LU}$ can be simplified 
-  in terms of the collected number of events in each beam-helicity state 
-  ($N^{+}$, $N^{-}$) as:
+$A_{LU}$ can be simplified in terms of the collected number of events in each 
+beam-helicity state ($N^{+}$, $N^{-}$) as:
 \begin{equation}
@@
 where $P_{B}$ is the beam polarization, and $N^{+}$ and $N^{-}$ are the number 
-of events detected with positive and negative electron helicity, respectively.  
-The statistical uncertainty of $A_{LU}$ is
+of DVCS events detected with positive and negative electron helicity with 
+respect to the beam direction. The statistical uncertainty of $A_{LU}$ is
 \begin{equation}
@@
 
-%CFF
-we extract the GPD $H$ in a model independent way (figure~\ref{fig:CFF_HA}).  
-This is possible using the beam-spin asymmetry ($A_{LU}$) expression for 
-spin-zero target at leading twist \cite{Kirchner:2003wt,Belitsky:2008bz}:
-\small
-\begin{equation}
-\begin{split}
-A_{LU}(\phi) =~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
- \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
-{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
-\big( 
-\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
-\label{eq:A_LU-coh}
-\end{split}
-\end{equation}
-\normalsize
-where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
-and real parts of the CFF $\mathcal{H}_{A}$ associated to the GPD $H_A$. The 
-$\alpha_{i}$'s are $\phi$-dependent kinematical factors that depend on the 
-nuclear form factor $F_A$ and the independent variables $Q^2$, $x_{B}$ and $t$.  
-These factors are simplified as:
-\small
-\begin{eqnarray}
-   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
-    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
-   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
-C_{++}(1) cos(\phi) \right)\\
-\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
-{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
-\epsilon^2}
-\end{eqnarray}
-\normalsize
+Due to our limited statistics only, a two-dimensional binning is carried out in 
+this work. The strongest dependence of $A_{LU}$ is on the azimuthal angle 
+($\phi$). Thus, the coherent measured ranges of $Q^{2}$, $x_{B}$ and $t$ are 
+binned statistically into three bins. Then, the identified DVCS events in each 
+bin are binned into nine bins in $\phi$.  Therefore, we are left
+with $Q^{2}$-$\phi$ bins integrated over the full ranges of $x_{B}$ and $t$, 
+$x_{B}$-$\phi$ bins integrated over $Q^{2}$ and $t$, and $t$-$\phi$ bins 
+integrated over $Q^{2}$ and $x_{B}$.
 
-Where $S{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
-leptonic tensor. Their explicit expressions can be found in .
+Figure \ref{fig:A_LU-coh} presents the coherent $A_{LU}$ for the three
+sets of two-dimensional bins. The asymmetries are fitted with the form of
+equation \ref{eq:A_LU-coh}, where the real and the imaginary part of the CFF
+$\mathcal{H}_{A}$ are the free parameters in the fit. Figure \ref{fig:alu90} 
+shows the $Q^2$, $x_{B}$, and $-t$-dependencies of the fitted $A_{LU}$ signals 
+at $\phi$~=~90$^{\circ}$. The $x_{B}$ and $-t$-dependencies are compared to 
+theoretical calculations performed by S.~Liuti and K.~Taneja 
+\cite{simonetta_2}.  Their model relies on the impulse approximation and uses 
+advanced spectral function of the nuclei to calculate the nuclear GPDs and then 
+the observables. The calculations were carried out at slightly different 
+kinematics than ours but provide already some guidance. The experimental 
+results appear to have larger asymmetries compared to the calculations.  These 
+differences may arise from nuclear effects which are not taken into account in 
+the model, such as long-range interactions. Our measurements also agree with 
+those of HERMES, considering their large uncertainties.
 
@@
    added quadratically, shown on top in green are error bars representing only 
-   the statistical uncertainties. The brown bands represent the systematic
-uncertainties, including the normalisation systematic uncertainties. The red
-curves represent fits in the form of equation \ref{eq:A_LU-coh}.}
+   the statistical uncertainties. The bluish-gray bands represent the 
+   systematic uncertainties, including the normalisation systematic 
+uncertainties. The red curves represent fits in the form of equation 
+\ref{eq:A_LU-coh}.}
 \label{fig:alu}
@@
 \includegraphics[width=8.9cm]{figs/coherent-ALU_90.pdf}
-\vspace{-0.9cm}
-\caption{}
+\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $-t$-dependencies (right) of
+   the coherent $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
+   middle plot: the full-red and the dashed-blue curves are theoretical 
+   calculations from \cite{simonetta_2}. On the right: the green circles are 
+   the HERMES $-A_{LU}$ (positron beam was used) inclusive measurements 
+   \cite{HERMES_BSA}, the colored curves represent theoretical calculations 
+from \cite{simonetta_2}.}
 \label{fig:alu90}
@@
 \includegraphics[width=8.9cm]{figs/Coherent_CFF.pdf}
-\vspace{-0.9cm}
 \caption{The model-independent extraction of the imaginary (blue points) and
 real (red points) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of
-$Q^{2}$ (on the top right), $x_B$ (on the top left), and $t$ (on the bottom).}
+$Q^{2}$ (on the top right), $x_B$ (on the top left), and $t$ (on the bottom).  
+The full red curves are calculations based on the impulse approximation from
+\cite{Vadim_priv}. The black-dashed curves in the right plots are calculations 
+from a convolution model based on the VGG model for the nucleons' GPDs 
+\cite{Guidal_priv}. The blue long-dashed curve on the top-right plot is from
+the off-shell calculations based on reference \cite{GonzalezHernandez:2012jv}.}
 \label{fig:CFF_HA}
@@
 
+\bibitem{Belitsky:2001ns} A.~V.~Belitsky, D.~Mueller and A.~Kirchner,
+     Nucl.\ Phys.\ B {\bf 629}, 323 (2002)
+
 \bibitem{Kirchner:2003wt} 
@@
 
+\bibitem{simonetta_2}
+   S.~Liuti and K.~Taneja, Phys.\ Rev.\ C {\bf 72}, 032201 (2005)
+
+\bibitem{HERMES_BSA}
+   A. Airapetian et al. (HERMES Collaboration), Phys.\ Rev.\ C {\bf 81}, 035202 
+   (2010)
+
+\bibitem{Vadim_priv}
+   Private communications with V.~Guzey based on: 
+   V.~Guzey, Phys.\ Rev.\ C {\bf 78}, 025211 (2008).
+
+\bibitem{Guidal_priv}
+   Private communications with M.~Guidal based on: M.~Guidal, M.~V.~Polyakov, 
+   A.~V.~Radyushkin and M.~Vanderhaeghen, Phys.\ Rev.\ D {\bf 72}, 054013
+   (2005).
+
+\bibitem{GonzalezHernandez:2012jv} 
+   Private communications with S.~Liuti based on: J.~O.~Gonzalez-Hernandez, 
+   S.~Liuti, G.~R.~Goldstein and K.~Kathuria,
+   Phys.\ Rev.\ C {\bf 88}, no. 6, 065206, (2013).
+
 \end{thebibliography}

### 2017-01-24 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
added the theoretical models, the results interpretations and the summary

@@
 \includegraphics[width=6.5cm]{figs/DVCS_diagram.pdf}
-\vspace{-0.cm}
-\caption{Deep virtual Compton scattering process in the handbag approximation.}
+\caption{Representation of the leading-order, twist-2, handbag diagram of the 
+DVCS process off $^4$He.}
 \label{fig:diags}
@@
 scintillators). $^4$He tracks were identified by passing all the geometrical, 
-timing and quality cuts in the RTPC detector. The most energetic IC photon was 
-considered as the DVCS photon candidate. Next, a $Q^{2}>1~[GeV^{2}/c^{2}]$ cut 
-is applied on the DVCS candidates in order to ensure that the interaction 
-occurs at the partonic level and the applicability of the factorization in the 
-DVCS handbag diagram. Once the three final state particles were identified with 
-their 3-momentum vectors, the exclusivity of the coherent DVCS events were 
-ensured by applying a set of exclusive cuts, which are: the co-planarity angle 
-($\Delta \phi$), missing energy, missing mass squared and missing transverse 
-momentum in the $e'^4He'\gamma X$ final state configuration, the missing mass 
-squared in the $e'^4He'X$ and $e'\gamma X$ configurations, and finally the cone 
-angle ($\theta$) between the measured real photon and the missing particle in 
-the $e'^4He'X$ configuration. Figure~\ref{fig:kin-cuts} presents four of the 
-applied exclusivity cuts, where 3$\sigma$ cuts are applied on all the exclusive 
-quantities except the missing energy, for which a [-0.45,0.5] GeV cut was 
-adopted to reduce the background contribution.
+timing and quality cuts in the RTPC detector. In principle, with constant beam 
+luminosity, target density and pressure, the event rate has to be constant over 
+the experimental time. Due to the changes in the experimental conditions, such 
+as changing a trigger in a detector, a slight shift in the beam position or a 
+system failure somewhere, this rate changes. We minimize the effects of these 
+changes on the reconstructed events by selecting the good runs. To this aim, we 
+monitor the ratio between the number of the good tracks reconstructed in the 
+RTPC to number of the detected good electrons in the CLAS detector as a 
+function of run number \cite{eg6_note}.
+
+Even though the DVCS reaction has only one real photon in the final state, 
+events with more than one good photon are not discarded at this stage. This is 
+motivated by the fact that some photons correspond to random coincidences and 
+discarding these events results in losing good events. Then, events with one or 
+more $\pi^{0}$ are removed from the coherent DVCS sample. After that, the most 
+energetic IC photon was considered as the DVCS photon candidate. Next, a 
+$Q^{2}>1~[GeV^{2}/c^{2}]$ cut is applied on the DVCS candidates in order to 
+ensure that the interaction occurs at the partonic level and the applicability 
+of the factorization in the DVCS handbag diagram.  Once the three final state 
+particles were identified with their 3-momentum vectors, the exclusivity of the 
+coherent DVCS events were ensured by applying a set of exclusive cuts, which 
+are: the co-planarity angle ($\Delta \phi$), missing energy, missing mass 
+squared and missing transverse momentum in the $e'^4He'\gamma X$ final state 
+configuration, the missing mass squared in the $e'^4He'X$ and $e'\gamma X$ 
+configurations, and finally the cone angle ($\theta$) between the measured real 
+photon and the missing particle in the $e'^4He'X$ configuration.  
+Figure~\ref{fig:kin-cuts} presents four of the applied exclusivity cuts, where 
+3$\sigma$ cuts are applied on all the exclusive quantities except the missing 
+energy, for which a [-0.45,0.5] GeV cut was adopted to reduce the background 
+contribution. Finally,
 
@@
 
-Figure \ref{fig:A_LU-coh} presents the coherent $A_{LU}$ for the three
+Figure \ref{fig:alu} presents the coherent $A_{LU}$ for the three
 sets of two-dimensional bins. The asymmetries are fitted with the form of
@@
 
+As has been advertised previously, the $^4$He CFF $\mathcal{H}_A$ can be 
+extracted from fitting the experimentally measured coherent $A_{LU}$ in a 
+totally model independent way, which is not the case of nucleon targets. For 
+the later, four CFFs exist and extracting them is always made by making 
+limitations according some theoretical models and by neglecting some CFFs 
+\cite{Jo:2015ema}. Figure \ref{fig:CFF_HA} presents our extracted imaginary and 
+real parts of the CFF $\mathcal{H}_A$ as function of the kinematical variable 
+($Q^{2}$, $x_B$,$-t$), and compared to some theoretical calculations.
+
 \begin{figure}[tb]
 \includegraphics[width=8.9cm]{figs/Coherent_CFF.pdf}
-\caption{The model-independent extraction of the imaginary (blue points) and
-real (red points) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of
-$Q^{2}$ (on the top right), $x_B$ (on the top left), and $t$ (on the bottom).  
-The full red curves are calculations based on the impulse approximation from
-\cite{Vadim_priv}. The black-dashed curves in the right plots are calculations 
-from a convolution model based on the VGG model for the nucleons' GPDs 
-\cite{Guidal_priv}. The blue long-dashed curve on the top-right plot is from
-the off-shell calculations based on reference \cite{GonzalezHernandez:2012jv}.}
+\caption{The model-independent extraction of the imaginary (top panel) and
+real (bottom panel) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of
+$Q^{2}$ (right panel), $x_B$ (middle panel), and $t$ (left panel). The full red 
+curves are calculations based on an on-shell model from
+\cite{Vadim_priv}. The black-dashed curves are calculations from a convolution 
+model based on the VGG model for the nucleons' GPDs \cite{Guidal_priv}. The 
+blue long-dashed curve on the top-right plot is from
+an off-shell model based on \cite{GonzalezHernandez:2012jv}.}
 \label{fig:CFF_HA}
@@
 
-%interpretations
+We display in figure \ref{fig:CFF_HA} calculations for $\mathcal{H}_A$ from 
+three GPD models: On-shell, Convolution, and off-shell models. In the On-shell 
+model \cite{Vadim_priv}, a nucleus is assumed to be composed of 
+non-relativistic non-interacting nucleons, and these nucleons interact 
+independently with the probe. For the nucleons, the GPDs are modeled according 
+to the dual parametrization \cite{Guzey:2006xi}. In the Convolution model, the 
+same assumption has been made for the nucleus, while the nucleon GPDs were 
+extracted from the VGG model, which is based on the double distributions ansatz 
+\cite{DD_model}. The Off-shell model \cite{GonzalezHernandez:2012jv} relies on 
+the impulse approximation also, but uses advanced spectral function of the 
+nuclei that accounts for all configurations of the final nuclear system and the 
+binding effects between the nucleons.
+
+In figure \ref{fig:CFF_HA}, within the given uncertainties, the extracted CFF 
+shows a slight dependence on $Q^{2}$, $x_B$, and $-t$, which are in agreement 
+with the theoretical calculations. One can see a difference between the 
+precision of the extracted imaginary and real parts, which is expected because 
+$\alpha_2$ is suppressed compared to $\alpha_0$ contribution. However, we note 
+that the error bars are finite and that the fit converge without placing any 
+bound on the CFF, which is necessary on proton targets.
 
 %conclusion
+In summary, we presented the first exclusive measurement of the coherent DVCS 
+off $^4$He using CLAS spectrometer, supplemented with an inner calorimeter, a 5 
+Tesla solenoid, and a specially designed radial TPC. This dataset represents a 
+unique source for the nuclear DVCS global dataset, which will be used to 
+constrain GPD models. The measured beam-spin asymmetries show a very strong 
+signal and allowed to perform the first fully model-independent extraction of 
+the $^4$He CFF $\mathcal{H}_A$. The extracted CFFs, while limited by 
+statistics, are in a good agreement with the available GPD models. This opens 
+many new perspectives to study the nuclear structure within the GPDs framework 
+and pave the way for future more precise measurements at JLab 12~GeV program 
+and possibly at the Electron-Ion Collider (EIC) to achieve better understanding 
+of the nuclear effects.
 
@@
 
-We thank the staff of the Accelerator and Physics Divisions
-at Jefferson Lab for making this experiment possible.
+We acknowledge the staff of the Accelerator and Physics Divisions at Jefferson 
+Lab for making this experiment possible. This work is supported by the U.S.  
+Department of Energy, Office of Science, Office of Nuclear Physics contract 
+DE-AC05-06OR23177.
 
@@
 
+\bibitem{eg6_note}
+M. Hattawy {\it et al.} (CLAS-EG6 Working Group), CLAS internal analysis note, 
+2016.
+
 \bibitem{simonetta_2}
@@
 
+\bibitem{Guzey:2006xi} V.~Guzey and T.~Teckentrup,
+     Phys.\ Rev.\ D {\bf 74}, 054027 (2006)
+
 \bibitem{Guidal_priv}
@@
    (2005).
+
+\bibitem{DD_model}
+I.~V.~Musatov and A.~V.~Radyushkin, Phys.\ Rev.\ D {\bf 61}, 074027 (2000).
 

### 2017-01-24 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
update the paper with definitions of some varaibles

@@
 and real parts of the $^4$He CFF $\mathcal{H}_{A}$ associated to the GPD $H_A$. 
-The $\alpha_{i}$'s are $\phi$-dependent kinematical factors that depend on the 
-nuclear form factor ($F_{A}(t)$) and the independent variables $Q^2$, $x_{B}$ 
-and $t$. These factors are simplified as:
+$\phi$ is the azimuthal angle between the ($e$,$e'$) and 
+($\gamma^{*}$,$^4$He$'$) planes. The $\alpha_{i}$'s are $\phi$-dependent 
+kinematical factors that depend on the nuclear form factor ($F_{A}(t)$) and the 
+independent variables $Q^2$, $x_{B}$ and $t$. These factors are simplified as:
 \small
@@
 
-Where $S{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
-leptonic tensor. Their explicit expressions can be found in 
-\cite{Belitsky:2008bz}. Therefore, Using the $\alpha_{i}$ factors, one can 
-obtain in a totally model-independent way $\Im m(\mathcal{H}_{A})$ and $\Re 
-e(\mathcal{H}_{A})$ from fitting the experimental $A_{LU}$ as a function of 
-$\phi$, the azimuthal angle between the ($e$,$e'$) and ($\gamma^{*}$,$^4$He$'$) 
-planes, for given values of $Q^2$, $x_{B}$, and $t$.
+Where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$ is the $^4$He mass, 
+$\mathcal{P}_1(\phi)$ and $\mathcal {P}_2(\phi)$ are the Bethe-Heitler
+propagators. The factors: $c_{0,1,2}^{BH}$, $c_0^{DVCS}$, $c_{0,1}^{INT}$ and
+$s_1^{INT}$ are the Fourier coefficients of the BH, $S{++}(1)$, $C_{++}(0)$, 
+and $C_{++}(1)$ are the Fourier harmonics in the leptonic tensor. Their 
+explicit expressions can be found in \cite{Belitsky:2008bz}.  Therefore, Using 
+the $\alpha_{i}$ factors, one can obtain in a totally model-independent way 
+$\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ from fitting the 
+experimental $A_{LU}$ as a function of $\phi$ for given values of $Q^2$, 
+$x_{B}$, and $t$.
 

### 2017-01-24 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
more cleaning

@@
 
-The photon-electroproduction cross section can be decomposed into a BH,
-a DVCS, and an interference terms. At leading twist, the amplitudes of the 
-three terms can be decomposed into a finite sum of Fourier harmonics, the 
-so-called BMK formalism, as shown for the nucleon DVCS in 
-\cite{Belitsky:2001ns} and for the spinless nuclei in 
-\cite{Kirchner:2003wt,Belitsky:2008bz}. Therefore, the beam-spin asymmetry 
-($A_{LU}$) with the two opposite helicities of a longitudinally-polarized 
-electron beam (L) on a spin-zero target (U) can be written as:
+At leading twist order, the photon-electroproduction cross section can be 
+decomposed into a BH, a DVCS, and an interference terms. The amplitudes of the 
+three terms is approximated as a finite sum of Fourier harmonics, the so-called 
+BMK approximation, as shown for the nucleon DVCS in \cite{Belitsky:2001ns} and 
+for the spinless nuclei in \cite{Kirchner:2003wt,Belitsky:2008bz}. Therefore, 
+the beam-spin asymmetry ($A_{LU}$) with the two opposite helicities of a 
+longitudinally-polarized electron beam (L) on a spin-zero target (U) can be 
+simplified as:
 \small

### 2017-01-27 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
minor fixing
formating the references
Edit first 3 paragraphs

@@
 \begin{abstract}
-We report the first exclusive measurements of deeply virtual Compton scattering 
-(DVCS) off a nucleus, where all the products of the reaction including the 
-recoil $^4$He nucleus were detected. The experiment was performed using the 
-Jefferson Lab CEBAF Large Acceptance Spectrometer (CLAS) enhanced with a radial 
-time projection chamber (RTPC) to detect the recoiling $^4$He nuclei. We 
-measure large beam spin asymmetries comparable to the proton's ones and extract 
-in a model independent way, the single chirally-even generalized parton 
-distribution of the $^4$He nucleus. These are pioneering measurements and will 
-lead the way toward the 3D imaging of the partonic structure of nuclei.  
+We report the first fully exclusive measurement of deeply virtual Compton 
+scattering (DVCS) off a nucleus for $A>1$. The experiment used the 6 GeV 
+electron beam from Jefferson Lab projected onto a $^4$He target in the center of the CEBAF 
+Large Acceptance Spectrometer (CLAS). An additional radial time projection 
+chamber (RTPC) was used to detect the recoiling $^4$He nuclei and ensure the 
+exclusivity of the process. We measured beam spin asymmetries significantly
+larger than the one observed on proton targets and extract,
+in a completely model independent way, the chiral even generalized parton 
+distribution (GPD) of the $^4$He nucleus. This pioneering measurement 
+leads the way toward the 3D imaging of the partonic structure of nuclei.
 \end{abstract}
@@
 
-A wealth of information on the quantum chromodynamics (QCD) structure of 
-hadrons lies in the correlations between the momentum and spatial degrees of 
-freedom of the fundamental constituent partons, quarks and gluons. Such 
-correlations are accessible via the generalized parton distributions (GPDs).  
-The GPDs correspond to the coherence between quantum states of different (or 
-same) helicity, longitudinal momentum, and transverse position. In an impact 
-parameter space, they can be interpreted as a distribution in the transverse 
-plane of partons carrying a certain longitudinal momentum 
-\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep}. A crucial feature of GPDs 
-is the access to the transverse position of partons which, combined with their 
-longitudinal momentum, leads to the total angular momentum of partons 
-\cite{Burkardt:2005hp}. Deep virtual Compton scattering (DVCS) corresponding to 
-hard exclusive electroproduction of a real photon, which is considered as the 
-cleanest probe to access GPDs and thus study the 3D imaging of nucleons and 
-nuclei.
+A wealth of information on the quantum chromodynamics (QCD) lies in the 
+internal structure of hadrons. In the recent past, the development of the 
+generalized parton distributions (GPDs) framework has offered the possibility
+to obtain new information about the momentum and spatial degrees of 
+freedom of the quark and gluons inside hadrons [Add ref Mueller, Ji, Rad.]. 
+In impact parameter space, the GPDs are indeed interpreted as a tomography of the 
+transverse plane for partons carrying a certain longitudinal momentum 
+\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep}.
 
-DVCS measurements have been the focus of a worldwide effort 
+The main access to GPDs is through the measurement of deep virtual Compton 
+scattering (DVCS), i.e. the hard exclusive electroproduction of a real photon. 
+While other processes are known to be sensitive to GPDs, the measurement of the
+DVCS is considered as the cleanest probe and has been the focus of a worldwide effort 
 \cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
 Camacho:2006hx,Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
+[Should we cite less publications on the topic or a review?]
 involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
-CERN. The vast majority of the experiments focused on the study of the 
-nucleon's structure. The deuterium was also investigated at HERMES and JLab 
-\cite{Mazouz:2007aa} mainly as a neutron target. However, studying the 3D 
-imaging of the nucleon is a very important goal, understanding how these 
-distributions are modified to provide the binding and structure in a nucleus is 
-as fascinating of a question and an integral part of our quest of using QCD to 
-explore nuclear matter.
+CERN. The vast majority of these measurements was focused on the study of the 
+proton structure and allow the extraction of the tomography of the nucleon [refs].
 
-A DVCS process on a nuclear target differ from single nucleon scattering in 
-providing access to the measure two DVCS channels. In the coherent DVCS 
-channel, the target nucleus ($A$) remains intact and recoils as a whole while 
-emitting a real photon ($eA \rightarrow e' A' \gamma$), allowing to measure the 
-nuclear GPDs of the target. In the incoherent channel, the nucleus breaks up 
-and the DVCS takes place on a bound nucleon ($N$) that emits the final photon 
-($eA \rightarrow e' N' \gamma$ X), enabling the GPDs measurement of the bound 
-nucleons and to study their modifications in the nuclear medium via the GPDs.  
-Figure \ref{fig:diags} illustrates the dominant mechanism for the coherent DVCS 
-channel on $^4$He. At sufficiently large squared electron momentum transfer 
-$Q^2$ ($= -(k-k')^{2}$) and small squared momentum transfer $t$ ($= 
-(p-p')^{2}$), the QCD factorization theorem predicts that the DVCS handbag 
-diagram can be factorized into two parts, hard and soft parts 
-\cite{Freund_Collins,Ji_Osborne}. The hard part includes photons-quark 
-interaction and it is calculable through perturbative methods, while the 
-soft/non-perturbative part is parametrized in terms of GPDs, which embed the 
-partonic structure of the hadron.  
+This framework is also applicable to nuclei, giving access to completely new 
+information about the nuclear structure in terms of quarks and gluons[refs to add].
+The study of the 3D structure of the nuclei appears to be especially important
+in light of the large nuclear effects observed in nuclear parton distribution 
+functions [ref to EMC reviews]. Experimentally, the coherent DVCS channel is 
+difficult to measure because of its small cross section and the necessity to
+ensure that the target remains intact while emitting a hard photon 
+($eA \rightarrow e' A' \gamma$). Figure \ref{fig:diags} illustrates the 
+hand bag diagram for the coherent DVCS on $^4$He.
+
 \begin{figure}[tb]
@@
 
-%introduction
+Similarly to the proton case, at large photon's 4-momentum square  
+$Q^2$ ($= -(k-k')^{2}$) and small squared momentum transfer $t$ ($= 
+(p-p')^{2}$), the DVCS handbag diagram can be factorized into two parts 
+\cite{Freund_Collins,Ji_Osborne}. The hard part includes photons-quark 
+interaction and is calculable with perturbative QED, while the 
+soft/non-perturbative part is parametrized in terms of GPDs, which embed the 
+partonic structure of the hadron.
+
 The GPDs are defined for each quark flavor and gluon as matrix
@@
 \bibitem{Freund_Collins}
-A.~Freund and J.C.~Collins, Phys.\ Rev.\ D {\bf 59}, 074009 (1998)
+A.~Freund and J.C.~Collins, 
+Phys.\ Rev.\ D {\bf 59}, 074009 (1998)
 
 \bibitem{Ji_Osborne}
-   X.-D.~Ji and J.~Osborne, Phys.\ Rev.\ D {\bf 58}, 094018 (1998)
+X.-D.~Ji and J.~Osborne, 
+Phys.\ Rev.\ D {\bf 58}, 094018 (1998)
 
 \bibitem{Belitsky}
-A.~V.~Belitsky and A.~V.~Radyushkin, Phys.\ Rept.\ vol. 418 (2005)
+A.~V.~Belitsky and A.~V.~Radyushkin, 
+Phys.\ Rept.\ vol. 418 (2005)
 
@@
 \bibitem{JSeely}
- J. Seely {\it et al.} Phys.\ Rev.\ Lett.\ {\bf 103}, 202301 (2009)
+J. Seely {\it et al.} 
+Phys.\ Rev.\ Lett.\ {\bf 103}, 202301 (2009)
 
 \bibitem{CLAS_ref}
-   B.A. Mecking {\it et al.}, Nucl.\ Inst.\ and Meth.\ A 503, 513 (2003)
+B.A. Mecking {\it et al.}, 
+Nucl.\ Inst.\ and Meth.\ A 503, 513 (2003)
 
-\bibitem{Belitsky:2001ns} A.~V.~Belitsky, D.~Mueller and A.~Kirchner,
+\bibitem{Belitsky:2001ns}
+A.~V.~Belitsky, D.~Mueller and A.~Kirchner,
 Nucl.\ Phys.\ B {\bf 629}, 323 (2002)
@@
 \bibitem{Kirchner:2003wt}
-   A.~Kirchner and D.~Mueller, Eur.\ Phys.\ J.\ C {\bf 32}, 347 (2003)
+A.~Kirchner and D.~Mueller, 
+Eur.\ Phys.\ J.\ C {\bf 32}, 347 (2003)
 
-\bibitem{Belitsky:2008bz} A.~V.~Belitsky and D.~Mueller,
+\bibitem{Belitsky:2008bz}
+A.~V.~Belitsky and D.~Mueller,
 Phys.\ Rev.\ D {\bf 79}, 014017 (2009)
 
-\bibitem{Ellinghaus:2002zw} F.~Ellinghaus {\it et al.} [HERMES Collaboration],
+\bibitem{Ellinghaus:2002zw}
+F.~Ellinghaus {\it et al.} [HERMES Collaboration],
 AIP Conf.\ Proc.\  {\bf 675}, 303 (2003)
@@
 \bibitem{eg6_note}
-M. Hattawy {\it et al.} (CLAS-EG6 Working Group), CLAS internal analysis note, 
-2016.
+M. Hattawy {\it et al.} (CLAS-EG6 Working Group), 
+CLAS internal analysis note, 2016.
 
 \bibitem{simonetta_2}
-   S.~Liuti and K.~Taneja, Phys.\ Rev.\ C {\bf 72}, 032201 (2005)
+S.~Liuti and K.~Taneja, 
+Phys.\ Rev.\ C {\bf 72}, 032201 (2005)
 
 \bibitem{HERMES_BSA}
-   A. Airapetian et al. (HERMES Collaboration), Phys.\ Rev.\ C {\bf 81}, 035202 
-   (2010)
+A. Airapetian et al. (HERMES Collaboration), 
+Phys.\ Rev.\ C {\bf 81}, 035202 (2010)
 
@@
 
-\bibitem{Guzey:2006xi} V.~Guzey and T.~Teckentrup,
+\bibitem{Guzey:2006xi}
+V.~Guzey and T.~Teckentrup,
 Phys.\ Rev.\ D {\bf 74}, 054027 (2006)
@@
 \bibitem{Guidal_priv}
-   Private communications with M.~Guidal based on: M.~Guidal, M.~V.~Polyakov, 
-   A.~V.~Radyushkin and M.~Vanderhaeghen, Phys.\ Rev.\ D {\bf 72}, 054013
-   (2005).
+Private communications with M.~Guidal based on: 
+M.~Guidal, M.~V.~Polyakov, A.~V.~Radyushkin and M.~Vanderhaeghen, 
+Phys.\ Rev.\ D {\bf 72}, 054013 (2005).
 
 \bibitem{DD_model}
-I.~V.~Musatov and A.~V.~Radyushkin, Phys.\ Rev.\ D {\bf 61}, 074027 (2000).
+I.~V.~Musatov and A.~V.~Radyushkin, 
+Phys.\ Rev.\ D {\bf 61}, 074027 (2000).
 
 \bibitem{GonzalezHernandez:2012jv}
-   Private communications with S.~Liuti based on: J.~O.~Gonzalez-Hernandez, 
-   S.~Liuti, G.~R.~Goldstein and K.~Kathuria,
+Private communications with S.~Liuti based on: 
+J.~O.~Gonzalez-Hernandez, S.~Liuti, G.~R.~Goldstein and K.~Kathuria,
 Phys.\ Rev.\ C {\bf 88}, no. 6, 065206, (2013).

### 2017-01-31 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
Edit continued

@@
 proton structure and allow the extraction of the tomography of the nucleon [refs].
-
 This framework is also applicable to nuclei, giving access to completely new 
@@
 in light of the large nuclear effects observed in nuclear parton distribution 
-functions [ref to EMC reviews]. Experimentally, the coherent DVCS channel is 
-difficult to measure because of its small cross section and the necessity to
-ensure that the target remains intact while emitting a hard photon 
-($eA \rightarrow e' A' \gamma$). Figure \ref{fig:diags} illustrates the 
-hand bag diagram for the coherent DVCS on $^4$He.
+functions [ref to EMC reviews].
 
@@
 
-Similarly to the proton case, at large photon's 4-momentum square  
-$Q^2$ ($= -(k-k')^{2}$) and small squared momentum transfer $t$ ($= 
-(p-p')^{2}$), the DVCS handbag diagram can be factorized into two parts 
+Experimentally, the coherent nuclear DVCS channel is difficult to measure because of 
+its small cross section and the necessity to ensure that the target remains 
+intact while emitting a hard photon ($eA \rightarrow e' A' \gamma$). Figure 
+\ref{fig:diags} illustrates the hand bag diagram for the coherent DVCS on 
+$^4$He. Similarly to the proton case, at large photon's 4-momentum square 
+$Q^2$ ($= -(k-k')^{2}$) and small squared momentum transfer $t$ 
+($= (p-p')^{2}$), the DVCS handbag diagram can be factorized into two parts 
 \cite{Freund_Collins,Ji_Osborne}. The hard part includes photons-quark 
-interaction and is calculable with perturbative QED, while the 
-soft/non-perturbative part is parametrized in terms of GPDs, which embed the 
-partonic structure of the hadron.
-
-The GPDs are defined for each quark flavor and gluon as matrix
-elements of the light cone operators \cite{Belitsky}, describing the transition 
-between the initial and final states of a hadron. The GPDs depend on two 
-longitudinal momentum fraction variables ($x$, $\xi$) and on the momentum 
-transfer $t$ to the target. $x$ is the average longitudinal momentum fraction 
-of the parton involved in the process and $\xi$ is the longitudinal fraction of 
-the momentum transfer $t$, which is related to the Bjorken variable $x_{B}$: 
-$\xi\approx {{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M\nu}$ with
-the proton mass $M$ and $\nu=E_e-E_{e^\prime}$. The GPDs $x$ variable cannot be 
-measured experimentally in a DVCS reaction. Hence, we measure the their 
-convolutions on $x$, the so-called Compton Form Factors (CFF) 
-\cite{Guidal:2013rya}.  In a DVCS process, the number of GPDs needed to 
-parametrize the partonic structure of a hadron depends on the different 
-configurations between the spin of the hadron and the helicity direction of the 
-struck quark.  Therefore, the partonic structure of spin zero nuclei, such as 
-$^4He$ and $^{12}C$, is parametrized by only one GPD ($H_{A}(x,\xi,t)$) at 
-leading twist, while 4 GPDs arise in the nucleon case.  In this work, we have 
-chose the $^4$He nucleus as our target of interest because of it's spinless 
-nature and it shows a clear EMC effect \cite{JSeely}, in addition of having a 
-high density and it is a well-known few-body system.
+interaction and is calculable with perturbative QED, while the non-perturbative 
+part is parametrized in terms of GPDs, which embed the partonic structure of 
+the hadron. The GPDs depend on three variables $x$, $\xi$ and $t$, which are 
+indicated in Figure \ref{fig:diags} for the DVCS process. In DVCS, $\xi$ can 
+be related to the Bjorken variable $x_{B}$: $\xi\approx {{x_B}\over{2-x_B}}$, 
+where $x_B=\frac{Q^2}{2M\nu}$ with the proton mass $M$ and 
+$\nu=E_e-E_{e^\prime}$. One can easily access $t$ as the squared momentum 
+transfered to the target, however the $x$ variable cannot be experimentally 
+accessed in a DVCS reaction. Hence, we measure only complex Compton Form 
+Factors (CFF) [need reference] defined as: [add FORMULA for CFFs].
 
@@
 
+In a DVCS process, the number of GPDs needed to 
+parametrize the partonic structure of a hadron depends on the different 
+configurations between the spin of the hadron and the helicity direction of the 
+struck quark.  Therefore, the partonic structure of spin zero nuclei, such as 
+$^4He$ and $^{12}C$, is parametrized by only one GPD ($H_{A}(x,\xi,t)$) at 
+leading twist, while 4 GPDs arise in the nucleon case.  In this work, we have 
+chose the $^4$He nucleus as our target of interest because of it's spinless 
+nature and it shows a clear EMC effect \cite{JSeely}, in addition of having a 
+high density and it is a well-known few-body system.
+
 This work presents the first exclusive measurement of the beam-spin asymmetry 
-of the reaction $e~^{4}He\rightarrow e'~^{4}He~\gamma$.This DVCS sensitive 
+of the reaction $e~^{4}He\rightarrow e'~^{4}He~\gamma$. This DVCS sensitive 
 observable is measurable using a polarized lepton beam on an unpolarized target 

### 2017-01-31 eg6-letters/NIM/EG6_RTPC_NIM.tex
added updated plots and cleaning the coherent asymmetry phi plot

@@
 less than 250 MeV/c. In 2009, we carried out measurements on $^4$He target 
-using CLAS spectrometer, which was upgraded with the RTPC during the CLAS-EG6 
-experimental run. The detector was positioned directly around a gaseous target, 
-allowing a detection threshold of $~$100  MeV/c for $^4$He. This article 
-discuses the RTPC design, work principle, calibration methods and 
-performances.
+using CLAS spectrometer, which was supplemented with the RTPC during the 
+CLAS-EG6 experimental run. The detector was positioned directly around a 
+gaseous target, allowing a detection threshold as low as $~$100  MeV/c for 
+$^4$He. This article discuses the RTPC design, work principle, calibration 
+methods and performances.
 \end{abstract}

### 2017-01-31 analysis-note-vf/results.tex
update the note and the coherent paper with the latest plots

@@
 \section{Beam-spin asymmetry results and fit}
-In this section, the beam-spin asymmetries will be compared to the theoretical calculations based on the two models that were presented in section \ref{Theoretical_hypotheses}.
+In this section, the beam-spin asymmetries will be compared to the theoretical 
+calculations based on the two models that were presented in section 
+\ref{Theoretical_hypotheses}.
 
@@
 \centering
-\includegraphics[scale=0.9]{fig_Dec2016/Coherent_ALU_phi.pdf}
+\includegraphics[scale=0.85]{fig_Dec2016/Coherent_ALU_phi.pdf}
 \caption{The coherent $A_{LU}$ as a function of $\phi$ and $Q^2$ (top panel), 
-   $x_{B}$ (middle panel), and $-t$~(bottom panel) bins. The blue error bars 
-   represent the statistical and the systematic uncertainties, added 
-   quadratically, shown on the top of green error bars representing only the 
-statistical uncertainties.  The brown bands represent the full systematic 
-uncertainties, including the normalisation systematic uncertainties. The red 
-curves represent fits in the form of equation \ref{eq:A_LU-coh}.}
+   $x_{B}$ (middle panel), and $-t$~(bottom panel) bins. The black error bars 
+   represent the statistical uncertainties. The bluish-gray bands represent the 
+systematic uncertainties, including the normalisation systematic uncertainties.  
+The red curves represent fits, in the form of equation \ref{eq:A_LU-coh}, for 
+the asymmetries with the statistical and the systematic uncertainties added   
+quadratically.}
 \label{fig:bsa_coh_Q2_bins}
@@
    \centering
-\includegraphics[scale=0.48]{fig_Dec2016/ALU_90_p_vs_Q2_shortscenrario.pdf}\\ 
-\includegraphics[scale=0.48]{fig_Dec2016/ALU_90_p_vs_x_shortscenrario.pdf}\\
-\includegraphics[scale=0.48]{fig_Dec2016/ALU_90_p_vs_t_shortscenrario.pdf} \\ 
+\includegraphics[scale=0.52]{fig_Dec2016/ALU_90_p_vs_Q2_shortscenrario.pdf}\\ 
+\includegraphics[scale=0.52]{fig_Dec2016/ALU_90_p_vs_x_shortscenrario.pdf}\\
+\includegraphics[scale=0.52]{fig_Dec2016/ALU_90_p_vs_t_shortscenrario.pdf} \\ 
 \caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $-t$-dependencies (bottom) of 
@@
 \begin{figure}[h!]
-\includegraphics[scale=0.9]{fig_Dec2016/Coherent_CFF.pdf}
+\includegraphics[scale=0.8]{fig_Dec2016/Coherent_CFF.pdf}
 \caption{The model-independent extraction of the imaginary (black full squares 
@@
 plots) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of $Q^{2}$ (on the 
-left), $x_B$ (on the middle), and $t$ (on the right). The full and dashed red 
-curves are calculations based on the impulse approximation from 
-\cite{Vadim_priv}.  The black curves in the right plots, t-dependence plots, 
-are calculations from a convolution model based on the VGG model for the 
-nucleon's GPDs \cite{Guidal_priv}. The cyan curve on the top-right plot is from 
-the off-shell calculations presented in section \ref{Theoretical_hypotheses} 
-based on reference \cite{GonzalezHernandez:2012jv}.  }
+left), $x_B$ (on the middle), and $t$ (on the right). The full red curves are 
+calculations based on the impulse approximation from \cite{Vadim_priv}.  The 
+black dashed curves are calculations from a convolution model based on the VGG 
+model for the nucleon's GPDs \cite{Guidal_priv}. The blue long-dashed curve on 
+the top-right plot is from the off-shell calculations presented in section 
+\ref{Theoretical_hypotheses} based on reference 
+\cite{GonzalezHernandez:2012jv}.  }
 \label{fig:HA_CFF}
@@
 \centering
-\includegraphics[scale=0.46]{fig_Dec2016/ALU_ratioInc_Q2_shortscenrario.pdf}\\
-\includegraphics[scale=0.46]{fig_Dec2016/ALU_ratioInc_x_shortscenrario.pdf}\\
-\includegraphics[scale=0.46]{fig_Dec2016/ALU_ratioInc_t_shortscenrario.pdf}
+\includegraphics[scale=0.52]{fig_Dec2016/ALU_ratioInc_Q2_shortscenrario.pdf}\\
+\includegraphics[scale=0.52]{fig_Dec2016/ALU_ratioInc_x_shortscenrario.pdf}\\
+\includegraphics[scale=0.52]{fig_Dec2016/ALU_ratioInc_t_shortscenrario.pdf}
 \caption{ The $A_{LU}$ ratio between the bound and the free proton at 

### 2017-01-31 analysis-note-vf/for_tab.C

@@ -1,98 +1,0 @@
-//________________      bins in Q2                  ____________________//                          
-
-     24.0  &  0.1575 $\pm$  0.1016 $\pm$ 0.0257 \\ 
-     60.0  &  0.3656 $\pm$  0.0903 $\pm$ 0.0188 \\ 
-     98.5  &  0.3586 $\pm$  0.1051 $\pm$ 0.0403 \\ 
-     141.2 &  0.1498 $\pm$  0.1645 $\pm$ 0.0267 \\ 
-     177.7 &  0.1849 $\pm$  0.1664 $\pm$ 0.0278 \\ 
-     219.3 &  0.0555 $\pm$  0.1475 $\pm$ 0.0248 \\ 
-     263.4 & -0.3184 $\pm$  0.1171 $\pm$ 0.0389 \\ 
-     302.7 & -0.1160 $\pm$  0.0975 $\pm$ 0.0263 \\ 
-     337.9 & -0.2805 $\pm$  0.0952 $\pm$ 0.0343 \\ 
-                                                  
-     21.1  &  0.1694 $\pm$  0.0858 $\pm$ 0.0267 \\
-     55.9  &  0.2889 $\pm$  0.0859 $\pm$ 0.0250 \\
-     96.7  &  0.4761 $\pm$  0.1304 $\pm$ 0.0426 \\
-     138.9 &  0.2134 $\pm$  0.1784 $\pm$ 0.0250 \\
-     179.8 &  0.2996 $\pm$  0.1967 $\pm$ 0.0302 \\
-     218.7 & -0.2375 $\pm$  0.1913 $\pm$ 0.0344 \\
-     263.5 & -0.2521 $\pm$  0.1398 $\pm$ 0.0366 \\
-     302.6 & -0.3526 $\pm$  0.0855 $\pm$ 0.0383 \\
-     338.0 & -0.2344 $\pm$  0.0801 $\pm$ 0.0261 \\
-                                                  
-     21.0  &  0.1626 $\pm$  0.0779 $\pm$ 0.0234 \\
-     56.4  &  0.3433 $\pm$  0.0817 $\pm$ 0.0185 \\
-     95.9  &  0.2443 $\pm$  0.1270 $\pm$ 0.0173 \\
[…]

### 2017-02-02 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
update the note and the coherent paper with the latest plots
Continue editing the coherent paper

@@
 be related to the Bjorken variable $x_{B}$: $\xi\approx {{x_B}\over{2-x_B}}$, 
-where $x_B=\frac{Q^2}{2M\nu}$ with the proton mass $M$ and 
+where $x_B=\frac{Q^2}{2M\nu}$ with $M$ the proton mass and 
 $\nu=E_e-E_{e^\prime}$. One can easily access $t$ as the squared momentum 
@@
 
-The study of nuclear DVCS is still in its infancy due to the challenging 
-detection of the low-energy recoil nuclei in fixed target experiments. Until 
-very recently, the HERMES experiment \cite{Ellinghaus:2002zw} was the only one 
-to measure DVCS off heavier nuclei such as $^4$He, N, Ne, Kr and Xe, where only 
-the scattered electron and the real photon are detected. In this paper, we 
-report the first exclusive measurements of the coherent DVCS channel off $^4$He 
-where all products of the reaction are detected including the recoiling $^4$He 
-nucleus. Following this exclusive measurement, the $^4$He CFF 
-($\mathcal{H}_{A}$) will be extracted experimentally in a fully model 
-independent way for the first time ever. The incoherent DVCS channel 
-measurement from the same data set in in preparation and will reported in 
-another publication.
+The main challenge to study nuclear DVCS is to ensure the exclusivity of the 
+reaction. Until now, the only available data set of nuclear DVCS
+was from the HERMES experiment \cite{Ellinghaus:2002zw}, where exclusivity is 
+based on kinematic cuts on the measured scattered electron and real photon only. 
+The measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and 
+Xe) but has been critisized for mixing coherent and incoherent processes 
+[ref]. In this regard, the direct detection of the low-energy recoil nuclei is the best way to
+garanty that the nuclei is intact and that the reaction did not occur on a 
+bound nucleon. The CEBAF Large Acceptance Spectrometer (CLAS) setting  in the
+Hall-B of JLab being already optimized for DVCS measurments 
+[refs], we built a dedicated radial time projection chamber (RTPC) for 
+the detection of the recoiling low energy nuclei in order to complete this
+experimental setting. The $^4$He nucleus is an ideal experimental target in
+this regard as it is light enough to be detected in such a setting, while it
+is subject to significant nuclear effects \cite{JSeely} and has rather high 
+density. Using a helium target leads to another important advantage, the number of GPDs 
+defined for a hadron depends on its spin. The structure of a spin zero nuclei, such as 
+$^4He$, is parametrized by only one chiral even GPD ($H_{A}(x,\xi,t)$) at 
+leading twist, while 4 GPDs arise in the nucleon case. That significantly
+simplifies the interpretation of the data and allow a model independent
+extraction of the $^4$He CFF ($\mathcal{H}_{A}$) that will be presented at the
+end of this letter.
 
-In a DVCS process, the number of GPDs needed to 
-parametrize the partonic structure of a hadron depends on the different 
-configurations between the spin of the hadron and the helicity direction of the 
-struck quark.  Therefore, the partonic structure of spin zero nuclei, such as 
-$^4He$ and $^{12}C$, is parametrized by only one GPD ($H_{A}(x,\xi,t)$) at 
-leading twist, while 4 GPDs arise in the nucleon case.  In this work, we have 
-chose the $^4$He nucleus as our target of interest because of it's spinless 
-nature and it shows a clear EMC effect \cite{JSeely}, in addition of having a 
-high density and it is a well-known few-body system.
+%experimental setup
 
+The experiment E08-024 took place in the experimental Hall-B of Jefferson 
+laboratory (JLab) in 2009 using the nearly 100\% duty factor longitudinally 
+polarized electron beam (83$\%$ polarization) at its full energy of 6.064 
+GeV. The data were collected over three months using a 6 atm gaseous $^4$He 
+target placed in the center of CLAS. For DVCS experiments, the CLAS base line 
+design \cite{CLAS_ref} is supplemented with an inner calorimeter (IC) and a
+solenoid. The IC extends the photon detection acceptance of CLAS, which is 
+originally from 15$^{\circ}$ to 45$^{\circ}$, to polar angle as low 
+as 4$^{\circ}$. At these small angles the low-energy M\o{}ller 
+electrons produced in the target form a very high rate background that is
+suppressed by a 5 Tesla solenoid placed around the target.
+
+Because the coherent DVCS cross section is peaked at low $-t$, the recoil 
+$^4$He nuclei produced in DVCS have a low average momentum around 250 MeV/c.
+The CLAS cannot detect such low energy $\alpha$ particles, so in order to 
+ensure the exclusivity of the measurement, we 
+built a small and light RTPC to complement CLAS. Figure~\ref{fig:RTPC} presents 
+the design of this RTPC that is surrounding the 
+$^4$He gaseous target and inside the solenoid magnet.
+The detector was specifically calibrated for the detection of
+$^4$He nuclei using elastic scattering produced with a 1.2~GeV electron beam.
+
+\begin{figure}[tb]
+\vspace{-1.1cm}
+\includegraphics[width=7.0cm,angle=-90]{figs/RTPC.pdf}
+\vspace{-1.1cm}
+\caption{Left: A picture of the E08-024 RTPC before insertion into the 
+   solenoid. Right: A cross section of the E08-024 RTPC perpendicular to the 
+   beam direction. An illustration of a $^4$He track originating from the 
+   pressurized straw target is shown along with the electrons produced in the 
+   drift region.}
+\label{fig:RTPC}
+\end{figure}
+
+%DVCS selection
+To identify the coherent DVCS events, we first select events where one 
+electron, one $^4$He and at least one photon are detected in the final state. 
+Electrons are identified by using fiducial cuts and detecting a good
+signals in all the sub-detectors of the base line CLAS (drift chambers, 
+Cherenkov counters, electromagnetic calorimeter, and time of flight 
+scintillators). The $^4$He tracks are identified with fiducial, 
+timing and track quality cuts in the RTPC detector. In addition,
+we apply a vertex matching cut to make sure the electron and the helium
+nuclei originate from the same place. The photons are detected either
+in the IC or the CLAS electromagnetic calorimeter, note that even though the 
+DVCS reaction has only one real photon in the final state, 
+events with more than one good photon are not discarded at this stage. This is 
+motivated by the fact that soft photons are likely to be produced in random 
+coincidences, but cannot be mistaken for DVCS photons which are always at high
+energies ($>2$ GeV).
+
+Then, events with one or 
+more $\pi^{0}$ are removed from the coherent DVCS sample. After that, the most 
+energetic IC photon was considered as the DVCS photon candidate. Next, a 
+$Q^{2}>1~[GeV^{2}/c^{2}]$ cut is applied on the DVCS candidates in order to 
+ensure that the interaction occurs at the partonic level and the applicability 
+of the factorization in the DVCS handbag diagram.  Once the three final state 
+particles were identified with their 3-momentum vectors, the exclusivity of the 
+coherent DVCS events were ensured by applying a set of exclusive cuts, which 
+are: the co-planarity angle ($\Delta \phi$), missing energy, missing mass 
+squared and missing transverse momentum in the $e'^4He'\gamma X$ final state 
+configuration, the missing mass squared in the $e'^4He'X$ and $e'\gamma X$ 
+configurations, and finally the cone angle ($\theta$) between the measured real 
+photon and the missing particle in the $e'^4He'X$ configuration.  
+Figure~\ref{fig:kin-cuts} presents four of the applied exclusivity cuts, where 
+3$\sigma$ cuts are applied on all the exclusive quantities except the missing 
+energy, for which a [-0.45,0.5] GeV cut was adopted to reduce the background 
+contribution. Finally,
+
+\begin{figure}[tb]
+\includegraphics[width=8.9cm]{figs/coh_exc_cuts.pdf}
+\caption{Four of the seven coherent DVCS exclusivity cuts. The black 
+distributions represent the coherent DVCS events candidate. The shaded 
+distributions represent the events which passed all the exclusivity cuts except 
+the quantity plotted. The vertical red lines represent the applied exclusivity 
+cuts. The distributions from left to right and from top to bottoms are: $\Delta 
+\phi$, missing energy and missing mass squared in $e'^4He'\gamma X$, and the 
+cone angle ($\theta$) between the measured and the calculated photons.}
+\label{fig:kin-cuts}
+\end{figure}
+After all the requirements on the individual final state particles of the 
+coherent DVCS events and the exclusivity cuts, we ended up with about 3500 
+events. Figure \ref{fig:kin-coverage} presents the ($Q^{2}$,$x_{B}$) and 
+($Q^{2}$,$-t$) kinematic coverage of the collected DVCS events.
+
+\begin{figure}[tb]
+\hspace{-0.45cm}
+\includegraphics[width=9.0cm]{figs/Q2_xB_t_Coh.pdf}
+\caption{The $Q^{2}$ as a function of $x_{B}$ (left) and the $Q^{2}$ as a 
+function of $-t$ (right) for the identified coherent DVCS events after the 
+exclusivity cuts.}
+\label{fig:kin-coverage}
+\end{figure}
+
+Even with all the previously presented exclusive cuts, the selected events are
+not all true DVCS events. We identified several background contributions to the 
+coherent DVCS process, in particular accidental events and exclusive Deeply 
+Virtual $\pi^0$ Production (DV$\pi^0$P). The accidental events where the 
+different particles come from different events are suppressed by the limited 
+phase space allowed by the exclusivity cuts. We estimate the accidental events 
+to represent 4.1\% of our sample. This relatively large number is due to the 
+small cross section of the DVCS. We evaluated this contribution by selecting 
+events passing all our cuts but with particles originating from different 
+vertices. Regarding the DV$\pi^0$P, which can easily be mistaken with DVCS when 
+one of the two photons of the $\pi^0$ decay is produced at low energy in the 
+laboratory frame. To estimate the importance of this background, we developed 
+an event generator that we calibrated to match our measured experimental yield 
+of exclusive $\pi^0$. We used this generator together with a GEANT3 simulation 
+of our detection system to estimate the ratio of acceptance between DV$\pi^0$P 
+where the two photons are detected and those where only one photon is detected 
+and would pass our DVCS selection cuts. This ratio obtained from simulation is 
+then multiplied by the measured yield of DV$\pi^0$P events, indicating a 
+contamination of 2 to 4\%. The study of systematics errors showed that the main 
+contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
+large binning size (5.1\%). However added quadratically, these errors sum up to 
+10\%, which remain for all bins well below the statistical errors.
+
+%asymmetries
+Different observables are available in DVCS, the cross sections, the BSA...
 This work presents the first exclusive measurement of the beam-spin asymmetry 
@@
 
-%experimental setup
-
-The experiment, CLAS-EG6, took place in the experimental Hall-B of Jefferson 
-laboratory (JLab) in 2009. JLab delivers, simultaneously, a nearly 100\% duty 
-factor polarized electrons into three experimental Halls (A, B, C). The data 
-were collected over three months via projecting a 6.064 GeV longitudinally 
-polarized beam, (83$\%$ polarization), on a 6 atm gaseous $^4$He target.  The 
-Hall-B Large Acceptance Spectrometer (CLAS) basic design \cite{CLAS_ref} was 
-supplemented, during the CLAS-E1DVCS1 experimental run \cite{Girod:2007aa} in 
-2005, with a specially designed electromagnetic calorimeter, Inner calorimeter 
-(IC). The IC has extended the photon detection acceptance of CLAS, which is 
-originally from 15$^{\circ}$ to 45$^{\circ}$, to polar angle reach as minimum 
-as 4$^{\circ}$.  During the same experiment, a 5 Tesla solenoid was added 
-around the target to shield the inner detectors from the low-energy M\o ller 
-electrons.
-
-At 6 GeV incident electron beam energy, the recoil $^4$He nuclei, from the 
-coherent DVCS channel, have an average momentum (per charge) around 125 MeV/c, 
-while the CLAS spectrometer detects charged particles with a threshold of 250 
-MeV/c. In order to ensure the exclusivity of the our coherent DVCS channel, we 
-built a small and light radial time projection chamber (RTPC) to detect 
-recoiling nuclei down to energies of few MeVs. Figure~\ref{fig:RTPC} presents 
-our cylindrical RTPC, which is 20 cm long and 15 cm diameter, surrounding the 
-$^4$He gaseous target and being inside the available space inside the solenoid 
-, with a 3 cm radial drift length. The detector was specifically calibrated for 
-$^4$He nuclei using elastic scattering produced with a 1.2~GeV electron beam.
-
-\begin{figure}[tb]
-\includegraphics[width=7.0cm,angle=-90]{figs/RTPC.pdf}
-\vspace{-1.1cm}
-\caption{Left: A picture of the CLAS-EG6 RTPC before insertion into the 
-   solenoid. Right: A cross section of the CLAS-EG6 RTPC perpendicular to the 
-   beam direction. An illustration of a $^4$He track originating from the 
-   pressurized straw target is shown along with the electrons produced in the 
-drift region.}
-\label{fig:RTPC}
-\end{figure}
-
-%DVCS selection
-Identifying the coherent DVCS candidates is the first step of the data 
-analysis. These events have one electron, one $^4$He, and at least one photon 
-in the final state. Electrons were identified by passing the fiducial cuts and 
-having signals in all the sub-detectors of CLAS spectrometer (drift chambers, 
-Cherenkov counters, the standard CLAS electromagnetic calorimeter, and 
-scintillators). $^4$He tracks were identified by passing all the geometrical, 
-timing and quality cuts in the RTPC detector. In principle, with constant beam 
-luminosity, target density and pressure, the event rate has to be constant over 
-the experimental time. Due to the changes in the experimental conditions, such 
-as changing a trigger in a detector, a slight shift in the beam position or a 
-system failure somewhere, this rate changes. We minimize the effects of these 
-changes on the reconstructed events by selecting the good runs. To this aim, we 
-monitor the ratio between the number of the good tracks reconstructed in the 
-RTPC to number of the detected good electrons in the CLAS detector as a 
-function of run number \cite{eg6_note}.
-
-Even though the DVCS reaction has only one real photon in the final state, 
-events with more than one good photon are not discarded at this stage. This is 
-motivated by the fact that some photons correspond to random coincidences and 
-discarding these events results in losing good events. Then, events with one or 
-more $\pi^{0}$ are removed from the coherent DVCS sample. After that, the most 
-energetic IC photon was considered as the DVCS photon candidate. Next, a 
-$Q^{2}>1~[GeV^{2}/c^{2}]$ cut is applied on the DVCS candidates in order to 
-ensure that the interaction occurs at the partonic level and the applicability 
-of the factorization in the DVCS handbag diagram.  Once the three final state 
-particles were identified with their 3-momentum vectors, the exclusivity of the 
-coherent DVCS events were ensured by applying a set of exclusive cuts, which 
-are: the co-planarity angle ($\Delta \phi$), missing energy, missing mass 
-squared and missing transverse momentum in the $e'^4He'\gamma X$ final state 
-configuration, the missing mass squared in the $e'^4He'X$ and $e'\gamma X$ 
-configurations, and finally the cone angle ($\theta$) between the measured real 
-photon and the missing particle in the $e'^4He'X$ configuration.  
-Figure~\ref{fig:kin-cuts} presents four of the applied exclusivity cuts, where 
-3$\sigma$ cuts are applied on all the exclusive quantities except the missing 
-energy, for which a [-0.45,0.5] GeV cut was adopted to reduce the background 
-contribution. Finally,
-
-\begin{figure}[tb]
-\includegraphics[width=8.9cm]{figs/coh_exc_cuts.pdf}
-\caption{Four of the seven coherent DVCS exclusivity cuts. The black 
-distributions represent the coherent DVCS events candidate. The shaded 
-distributions represent the events which passed all the exclusivity cuts except 
-the quantity plotted. The vertical red lines represent the applied exclusivity 
-cuts. The distributions from left to right and from top to bottoms are: $\Delta 
-\phi$, missing energy and missing mass squared in $e'^4He'\gamma X$, and the 
-cone angle ($\theta$) between the measured and the calculated photons.}
-\label{fig:kin-cuts}
-\end{figure}
-After all the requirements on the individual final state particles of the 
-coherent DVCS events and the exclusivity cuts, we ended up with about 3500 
-events. Figure \ref{fig:kin-coverage} presents the ($Q^{2}$,$x_{B}$) and 
-($Q^{2}$,$-t$) kinematic coverage of the collected DVCS events.
-
-\begin{figure}[tb]
-\hspace{-0.45cm}
-\includegraphics[width=9.0cm]{figs/Q2_xB_t_Coh.pdf}
-\caption{The $Q^{2}$ as a function of $x_{B}$ (left) and the $Q^{2}$ as a 
-function of $-t$ (right) for the identified coherent DVCS events after the 
-exclusivity cuts.}
-\label{fig:kin-coverage}
-\end{figure}
-
-%asymmetries
-Even with all the previously presented exclusive cuts, the selected events are
-not all true DVCS events. We identified several background contributions to the 
-coherent DVCS process, in particular accidental events and exclusive Deeply 
-Virtual $\pi^0$ Production (DV$\pi^0$P). The accidental events where the 
-different particles come from different events are suppressed by the limited 
-phase space allowed by the exclusivity cuts. We estimate the accidental events 
-to represent 4.1\% of our sample. This relatively large number is due to the 
-small cross section of the DVCS. We evaluated this contribution by selecting 
-events passing all our cuts but with particles originating from different 
-vertices. Regarding the DV$\pi^0$P, which can easily be mistaken with DVCS when 
-one of the two photons of the $\pi^0$ decay is produced at low energy in the 
-laboratory frame. To estimate the importance of this background, we developed 
-an event generator that we calibrated to match our measured experimental yield 
-of exclusive $\pi^0$. We used this generator together with a GEANT3 simulation 
-of our detection system to estimate the ratio of acceptance between DV$\pi^0$P 
-where the two photons are detected and those where only one photon is detected 
-and would pass our DVCS selection cuts. This ratio obtained from simulation is 
-then multiplied by the measured yield of DV$\pi^0$P events, indicating a 
-contamination of 2 to 4\%. The study of systematics errors showed that the main 
-contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
-large binning size (5.1\%). However added quadratically, these errors sum up to 
-10\%, which remain for all bins well below the statistical errors.
-
 $A_{LU}$ can be simplified in terms of the collected number of events in each 
@@
    $Q^{2}$(top panel), $x_{B}$ (middle panel), and $-t$ (bottom panel) bins.  
-   The error bars represent the statistical and the systematic uncertainties 
-   added quadratically, shown on top in green are error bars representing only 
-   the statistical uncertainties. The bluish-gray bands represent the 
-   systematic uncertainties, including the normalisation systematic 
-uncertainties. The red curves represent fits in the form of equation 
+   The error bars represent the statistical uncertainties. The bluish-gray 
+   bands represent the systematic uncertainties, including the normalisation 
+systematic uncertainties. The red curves represent fits in the form of equation 
 \ref{eq:A_LU-coh}.}
@@
 
+The incoherent DVCS channel 
+measurement from the same data set in in preparation and will reported in 
+another publication. 
 %Acknowledgments

### 2017-02-02 eg6-letters/coherent/dvcs_he4_prl.tex
Edition of letter in progress and file clean up

--- 2017-02-02 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
@@
 to obtain new information about the momentum and spatial degrees of 
-freedom of the quark and gluons inside hadrons [Add ref Mueller, Ji, Rad.]. 
+freedom of the quark and gluons inside hadrons 
+\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.
 In impact parameter space, the GPDs are indeed interpreted as a tomography of the 
@@
 CERN. The vast majority of these measurements was focused on the study of the 
-proton structure and allow the extraction of the tomography of the nucleon [refs].
+proton structure and allow the extraction of the tomography of the nucleon,
+for details on the formalism see 
+\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}.
 This framework is also applicable to nuclei, giving access to completely new 
-information about the nuclear structure in terms of quarks and gluons[refs to add].
+information about the nuclear structure in terms of quarks and 
+gluons \cite{Dupre:2015jha}.
 The study of the 3D structure of the nuclei appears to be especially important
 in light of the large nuclear effects observed in nuclear parton distribution 
-functions [ref to EMC reviews].
+functions \cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.
 
@@
 coincidences, but cannot be mistaken for DVCS photons which are always at high
-energies ($>2$ GeV).
+energies ($>2$ GeV). So, the most energetic photon is always considered as 
+the DVCS photon candidate.
 
-Then, events with one or 
-more $\pi^{0}$ are removed from the coherent DVCS sample. After that, the most 
-energetic IC photon was considered as the DVCS photon candidate. Next, a 
-$Q^{2}>1~[GeV^{2}/c^{2}]$ cut is applied on the DVCS candidates in order to 
-ensure that the interaction occurs at the partonic level and the applicability 
-of the factorization in the DVCS handbag diagram.  Once the three final state 
-particles were identified with their 3-momentum vectors, the exclusivity of the 
-coherent DVCS events were ensured by applying a set of exclusive cuts, which 
-are: the co-planarity angle ($\Delta \phi$), missing energy, missing mass 
-squared and missing transverse momentum in the $e'^4He'\gamma X$ final state 
-configuration, the missing mass squared in the $e'^4He'X$ and $e'\gamma X$ 
-configurations, and finally the cone angle ($\theta$) between the measured real 
-photon and the missing particle in the $e'^4He'X$ configuration.  
-Figure~\ref{fig:kin-cuts} presents four of the applied exclusivity cuts, where 
-3$\sigma$ cuts are applied on all the exclusive quantities except the missing 
-energy, for which a [-0.45,0.5] GeV cut was adopted to reduce the background 
-contribution. Finally,
+The main backgroud to the measurement of DVCS is the coherent $\pi^{0}$ 
+production. Therefore, we remove events where a $\pi^{0}$ can be identified 
+by invariant mass reconstruction of two photons.  To ensure that the 
+interaction occurs at the partonic level and that the DVCS handbag diagram is 
+applicable we select events with $Q^{2}>1~[GeV^{2}/c^{2}]$. The exclusivity of 
+the events is obtained by applying a set of cuts on the following kinematic 
+variables: the co-planarity angle ($\Delta \phi$), the missing energy, the 
+missing mass squared, the missing transverse momentum, the missing mass 
+squared of the $e'^4He'$ system and the angle ($\theta$) between the measured 
+photon and the missing momentum of the $e'^4He'$ system. The most relevant of 
+these cuts are presented in Figure~\ref{fig:kin-cuts}, these are 3$\sigma$ 
+cuts except for the missing energy that appears to be too large and for which 
+we reduced the cut window to [-0.45,0.5] GeV. After these requirements, we 
+have about 3500 events left, Figure \ref{fig:kin-coverage} presents their
+kinematic distributions in ($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$).
 
@@
 \includegraphics[width=8.9cm]{figs/coh_exc_cuts.pdf}
-\caption{Four of the seven coherent DVCS exclusivity cuts. The black 
+\caption{Four of the six coherent DVCS exclusivity cuts. The black 
 distributions represent the coherent DVCS events candidate. The shaded 
@@
 cuts. The distributions from left to right and from top to bottoms are: $\Delta 
-\phi$, missing energy and missing mass squared in $e'^4He'\gamma X$, and the 
+\phi$, missing energy, missing mass squared and the 
 cone angle ($\theta$) between the measured and the calculated photons.}
@@
 \end{figure}
-After all the requirements on the individual final state particles of the 
-coherent DVCS events and the exclusivity cuts, we ended up with about 3500 
-events. Figure \ref{fig:kin-coverage} presents the ($Q^{2}$,$x_{B}$) and 
-($Q^{2}$,$-t$) kinematic coverage of the collected DVCS events.
 
@@
 \includegraphics[width=9.0cm]{figs/Q2_xB_t_Coh.pdf}
-\caption{The $Q^{2}$ as a function of $x_{B}$ (left) and the $Q^{2}$ as a 
-function of $-t$ (right) for the identified coherent DVCS events after the 
+\caption{Coherent DVCS event distributions for $Q^{2}$ as a function of 
+$x_{B}$ (left) and $Q^{2}$ as a function of $-t$ (right) after the 
 exclusivity cuts.}
@@
 
-Even with all the previously presented exclusive cuts, the selected events are
-not all true DVCS events. We identified several background contributions to the 
-coherent DVCS process, in particular accidental events and exclusive Deeply 
-Virtual $\pi^0$ Production (DV$\pi^0$P). The accidental events where the 
-different particles come from different events are suppressed by the limited 
-phase space allowed by the exclusivity cuts. We estimate the accidental events 
-to represent 4.1\% of our sample. This relatively large number is due to the 
-small cross section of the DVCS. We evaluated this contribution by selecting 
-events passing all our cuts but with particles originating from different 
-vertices. Regarding the DV$\pi^0$P, which can easily be mistaken with DVCS when 
+We identified two main background to our measurement, the accidental 
+coincidences and the exclusive $\pi^0$ production. The accidental events have 
+particles coming from different events, we estimate their  contribution
+to 4.1\% of our sample. We evaluated this contribution by selecting events 
+passing all our cuts but with an electron and an helium originating from different 
+vertices. Regarding the $\pi^0$ production, it can easily be mistaken with DVCS when 
 one of the two photons of the $\pi^0$ decay is produced at low energy in the 
-laboratory frame. To estimate the importance of this background, we developed 
-an event generator that we calibrated to match our measured experimental yield 
-of exclusive $\pi^0$. We used this generator together with a GEANT3 simulation 
-of our detection system to estimate the ratio of acceptance between DV$\pi^0$P 
-where the two photons are detected and those where only one photon is detected 
-and would pass our DVCS selection cuts. This ratio obtained from simulation is 
-then multiplied by the measured yield of DV$\pi^0$P events, indicating a 
-contamination of 2 to 4\%. The study of systematics errors showed that the main 
+laboratory frame and remain undetected. To estimate the importance of this 
+background, we developed an event generator calibrated on the experimental yield 
+of exclusive $\pi^0$ measured by our experiment. We used this generator together 
+with a GEANT3 simulation of our detection system to estimate the ratio between
+the number of $\pi^0$ events where the two photons are detected and those that 
+would be mistaken for DVCS. This ratio is then multiplied by the measured yield 
+of exclusive $\pi^0$ events to correct the DVCS data. Depending on the bins, we
+found contaminations of 2 to 4\%. The study of systematics errors showed that the main 
 contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
-large binning size (5.1\%). However added quadratically, these errors sum up to 
-10\%, which remain for all bins well below the statistical errors.
+large binning size (5.1\%) [Is that right to add it here?]. However, added quadratically, these 
+errors sum up to about 10\%, which always remain significantly smaller than the 
+statistical errors.
 
 %asymmetries
-Different observables are available in DVCS, the cross sections, the BSA...
-This work presents the first exclusive measurement of the beam-spin asymmetry 
-of the reaction $e~^{4}He\rightarrow e'~^{4}He~\gamma$. This DVCS sensitive 
+Several observables related to DVCS are of interest, in this work we focus 
+only on the beam-spin asymmetry. This  
 observable is measurable using a polarized lepton beam on an unpolarized target 
-(U). It is convenient to use the beam-spin asymmetry as a DVCS observable 
+(U). It is convenient to use the beam-spin asymmetry
 because most of the experimental normalization and acceptance issues cancel out 
@@
 where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the DVCS differential cross 
-section for a positive (negative) beam helicity. Experimentally, the DVCS 
-reaction is indistinguishable from the Bethe-Heitler (BH) process, where the 
-final photon is emitted either from the incoming or the outgoing leptons. The 
-BH process is not sensitive to GPDs and does not carry information about the 
-partonic structure of the hadronic target, and it's amplitude is calculable 
-from the well-known electromagnetic form factors.
+section for a positive (negative) beam helicity. Experimentally, $A_{LU}$ 
+can be expressed in terms of the collected number of events in each 
+beam-helicity state ($N^{+}$, $N^{-}$) as:
+\begin{equation}
+A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} }.
+\end{equation}
+where $P_{B}$ is the beam polarization, and $N^{+}$ and $N^{-}$ are the number 
+of DVCS events detected with positive and negative electron helicity with 
+respect to the beam direction.
 
-At leading twist order, the photon-electroproduction cross section can be 
-decomposed into a BH, a DVCS, and an interference terms. The amplitudes of the 
-three terms is approximated as a finite sum of Fourier harmonics, the so-called 
-BMK approximation, as shown for the nucleon DVCS in \cite{Belitsky:2001ns} and 
-for the spinless nuclei in \cite{Kirchner:2003wt,Belitsky:2008bz}. Therefore, 
-the beam-spin asymmetry ($A_{LU}$) with the two opposite helicities of a 
-longitudinally-polarized electron beam (L) on a spin-zero target (U) can be 
-simplified as:
+To interpret the DVCS, one has to keep in mind that this reaction is 
+indistinguishable from the Bethe-Heitler (BH) process, where the final photon 
+is emitted either from the incoming or the outgoing leptons. At leading twist 
+and leading order, the deeply virtual photon production cross section is 
+composed of a BH, a DVCS, and an interference terms. The amplitudes of the 
+three terms can be approximated as a finite sum of Fourier harmonics as shown 
+for the nucleon in \cite{Belitsky:2001ns} and for the spinless targets in 
+\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on these calculations, the 
+beam-spin asymmetry ($A_{LU}$) can then be expressed as:
 \small
@@
 kinematical factors that depend on the nuclear form factor ($F_{A}(t)$) and the 
-independent variables $Q^2$, $x_{B}$ and $t$. These factors are simplified as:
+independent variables $Q^2$, $x_{B}$ and $t$. These factors are expressed as:
 \small
@@
 \normalsize
-
 Where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$ is the $^4$He mass, 
@@
 $s_1^{INT}$ are the Fourier coefficients of the BH, $S{++}(1)$, $C_{++}(0)$, 
-and $C_{++}(1)$ are the Fourier harmonics in the leptonic tensor. Their 
-explicit expressions can be found in \cite{Belitsky:2008bz}.  Therefore, Using 
-the $\alpha_{i}$ factors, one can obtain in a totally model-independent way 
-$\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ from fitting the 
-experimental $A_{LU}$ as a function of $\phi$ for given values of $Q^2$, 
-$x_{B}$, and $t$.
+and $C_{++}(1)$ are the Fourier harmonics in the leptonic tensor. The 
+explicit expressions of these terms can be found in \cite{Belitsky:2008bz}. 
+We see that using the $\sin(\phi)$ and $\cos(\phi)$ contributions, it is 
+possible to extract 
+$\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ from the beam spin
+asymmetry.
 
-$A_{LU}$ can be simplified in terms of the collected number of events in each 
-beam-helicity state ($N^{+}$, $N^{-}$) as:
-\begin{equation}
-A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} }.
-\end{equation}
-where $P_{B}$ is the beam polarization, and $N^{+}$ and $N^{-}$ are the number 
-of DVCS events detected with positive and negative electron helicity with 
-respect to the beam direction. The statistical uncertainty of $A_{LU}$ is
-\begin{equation}
-   \sigma_{A_{LU}} = \frac{1}{P_{B}} \sqrt{ \frac{1 - (P_{B}A_{LU})^{2}}{N}}
-\end{equation}
-where $N (N^{+} + N^{-}) $ is the total number of measured events.
-
-Due to our limited statistics only, a two-dimensional binning is carried out in 
-this work. The strongest dependence of $A_{LU}$ is on the azimuthal angle 
-($\phi$). Thus, the coherent measured ranges of $Q^{2}$, $x_{B}$ and $t$ are 
-binned statistically into three bins. Then, the identified DVCS events in each 
-bin are binned into nine bins in $\phi$. Therefore, we are left
-with $Q^{2}$-$\phi$ bins integrated over the full ranges of $x_{B}$ and $t$, 
-$x_{B}$-$\phi$ bins integrated over $Q^{2}$ and $t$, and $t$-$\phi$ bins 
-integrated over $Q^{2}$ and $x_{B}$.
-
-Figure \ref{fig:alu} presents the coherent $A_{LU}$ for the three
-sets of two-dimensional bins. The asymmetries are fitted with the form of
+Due to our limited statistics, we only bin  our data 
+ on the azimuthal angle ($\phi$) and either one of the kinemtical variables 
+$Q^{2}$, $x_{B}$ and $t$. Figure \ref{fig:alu} presents the $A_{LU}$ for the three
+sets of binning. The asymmetries are fitted with the form of
 equation \ref{eq:A_LU-coh}, where the real and the imaginary part of the CFF
-$\mathcal{H}_{A}$ are the free parameters in the fit. Figure \ref{fig:alu90} 
+$\mathcal{H}_{A}$ are the free parameters of the fit. Figure \ref{fig:alu90} 
 shows the $Q^2$, $x_{B}$, and $-t$-dependencies of the fitted $A_{LU}$ signals 
 at $\phi$~=~90$^{\circ}$. The $x_{B}$ and $-t$-dependencies are compared to 
-theoretical calculations performed by S.~Liuti and K.~Taneja 
+the theoretical calculations performed by S.~Liuti and K.~Taneja 
 \cite{simonetta_2}. Their model relies on the impulse approximation and uses 
-advanced spectral function of the nuclei to calculate the nuclear GPDs and then 
-the observables. The calculations were carried out at slightly different 
-kinematics than ours but provide already some guidance. The experimental 
-results appear to have larger asymmetries compared to the calculations.  These 
+advanced spectral function of the nuclei. The calculations are at slightly different 
+kinematics than ours but provide some guidance. The experimental 
+results appear to have larger asymmetries than the calculations. These 
 differences may arise from nuclear effects which are not taken into account in 
-the model, such as long-range interactions. Our measurements also agree with 
-those of HERMES, considering their large uncertainties.
+the model, such as long-range interactions.
 
@@
 \includegraphics[width=8.9cm]{figs/coherent-ALU.pdf}
-\caption{The coherent $A_{LU}$ as a function of $\phi$ in
-   $Q^{2}$(top panel), $x_{B}$ (middle panel), and $-t$ (bottom panel) bins.  
-   The error bars represent the statistical uncertainties. The bluish-gray 
+\caption{The coherent $A_{LU}$ as a function of $\phi$. Results are presented
+   for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle panel), and 
+   $-t$ bins (bottom panel).  
+   The error bars represent the statistical uncertainties. The gray 
    bands represent the systematic uncertainties, including the normalisation 
-systematic uncertainties. The red curves represent fits in the form of equation 
-\ref{eq:A_LU-coh}.}
+   uncertainties. The red curves are the results of our fits with the form of 
+   equation \ref{eq:A_LU-coh}.}
 \label{fig:alu}
@@
 \caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $-t$-dependencies (right) of
-   the coherent $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
+   the $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
    middle plot: the full-red and the dashed-blue curves are theoretical 
@@
 \end{figure}
-
-As has been advertised previously, the $^4$He CFF $\mathcal{H}_A$ can be 
-extracted from fitting the experimentally measured coherent $A_{LU}$ in a 
-totally model independent way, which is not the case of nucleon targets. For 
-the later, four CFFs exist and extracting them is always made by making 
-limitations according some theoretical models and by neglecting some CFFs 
-\cite{Jo:2015ema}. Figure \ref{fig:CFF_HA} presents our extracted imaginary and 
-real parts of the CFF $\mathcal{H}_A$ as function of the kinematical variable 
-($Q^{2}$, $x_B$,$-t$), and compared to some theoretical calculations.
 
@@
 
-We display in figure \ref{fig:CFF_HA} calculations for $\mathcal{H}_A$ from 
-three GPD models: On-shell, Convolution, and off-shell models. In the On-shell 
-model \cite{Vadim_priv}, a nucleus is assumed to be composed of 
+We display in figure \ref{fig:CFF_HA} our extraction of the $^4$He CFF 
+$\mathcal{H}_A$ together with theoretical calculations from two models 
+labeled: convolution, and off-shell models. In the convolution 
+model \cite{Vadim_priv}, the nucleus is assumed to be composed of 
 non-relativistic non-interacting nucleons, and these nucleons interact 
-independently with the probe. For the nucleons, the GPDs are modeled according 
-to the dual parametrization \cite{Guzey:2006xi}. In the Convolution model, the 
-same assumption has been made for the nucleus, while the nucleon GPDs were 
-extracted from the VGG model, which is based on the double distributions ansatz 
+independently with the probe. The convolution/dual model is based on nucleon GPDs from 
+the dual parametrization \cite{Guzey:2006xi}, the convolution/VGG uses nucleon GPDs  
+from the VGG model, which is based on the double distributions ansatz 
 \cite{DD_model}. The Off-shell model \cite{GonzalezHernandez:2012jv} relies on 
-the impulse approximation also, but uses advanced spectral function of the 
+impulse approximation and uses advanced spectral function of the 
 nuclei that accounts for all configurations of the final nuclear system and the 
 binding effects between the nucleons.
+[These need to be renamed on the figure, it does not make sense to call differently
+models that are identical. We should also request the projections from Vadim
+model: hep-ph/0509158.]
 
@@
 another publication.
+
+[order biblio]
+
 %Acknowledgments
@@
 \begin{thebibliography}{99}
+\bibitem{Mueller:1998fv} 
+D. Mueller, D. Robaschik, B. Geyer, F.M. Dittes and J. Horejsi,
+Fortsch.\ Phys. {\bf 42}, 101 (1994).
+
+\bibitem{Ji:1996ek} 
+X.D. Ji,
+Phys.\ Rev.\ Lett. {\bf 78}, 610 (1997).
+
+\bibitem{Ji:1996nm} 
+X.D. Ji,
+Phys.\ Rev.\ D {\bf 55}, 7114 (1997).
+
+\bibitem{Radyushkin:1996nd}
+A.V. Radyushkin,
+Phys.\ Lett.\  B {\bf 380}, 417 (1996).
+
+\bibitem{Radyushkin:1997ki} 
+A.V. Radyushkin,
+Phys.\ Rev.\ D {\bf 56}, 5524 (1997).
 
@@
 
+\bibitem{Goeke:2001tz}
+K. Goeke, M.V. Polyakov and M. Vanderhaeghen,
+Prog.\ Part.\ Nucl.\ Phys. {\bf 47}, 401 (2001).
+
+\bibitem{Diehl:2003ny}
+M. Diehl,
+Phys.\ Rept.  {\bf 388}, 41 (2003).
+
+\bibitem{Ji:2004gf}
+X.D. Ji,
+Ann.\ Rev.\ Nucl.\ Part.\ Sci. {\bf 54}, 413 (2004).
+
+\bibitem{Belitsky:2005qn}
+A.V. Belitsky and A.V. Radyushkin,
+Phys.\ Rept. {\bf 418}, 1 (2005).
+
+\bibitem{Boffi:2007yc} 
+S. Boffi and B. Pasquini,
+Riv.\ Nuovo Cim. {\bf 30}, 387 (2007).
+
+\bibitem{Guidal:2013rya} 
+M.~Guidal, H.~Moutarde and M.~Vanderhaeghen,
+Rept.\ Prog.\ Phys.\  {\bf 76}, 066202 (2013).
+
+\bibitem{Dupre:2015jha} 
+  R.~Dupr\'e and S.~Scopetta,
+  Eur.\ Phys.\ J.\ A {\bf 52}, no. 6, 159 (2016)
+
+\bibitem{Hen:2016kwk} 
+  O.~Hen, G.~A.~Miller, E.~Piasetzky and L.~B.~Weinstein,
+  arXiv:1611.09748 [nucl-ex].
+
+\bibitem{Norton:2003cb} 
+  P.~R.~Norton,
+  Rept.\ Prog.\ Phys.\  {\bf 66}, 1253 (2003).
+
+\bibitem{Geesaman:1995yd} 
+  D.~F.~Geesaman, K.~Saito and A.~W.~Thomas,
+  Ann.\ Rev.\ Nucl.\ Part.\ Sci.\  {\bf 45}, 337 (1995).
+
 \end{thebibliography}

### 2017-02-02 eg6-letters/coherent/dvcs_he4_prl.tex
CLeaning the reference list, added the CFF formulas, and some minor fixings

@@
 transverse plane for partons carrying a certain longitudinal momentum 
-\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep}.
+\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep,Burkardt:2005hp}.
 
@@
 \cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
-Camacho:2006hx,Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
+Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
 [Should we cite less publications on the topic or a review?]
@@
 $\nu=E_e-E_{e^\prime}$. One can easily access $t$ as the squared momentum 
-transfered to the target, however the $x$ variable cannot be experimentally 
+transferred to the target, however the $x$ variable cannot be experimentally 
 accessed in a DVCS reaction. Hence, we measure only complex Compton Form 
-Factors (CFF) [need reference] defined as: [add FORMULA for CFFs].
+Factors (CFF) \cite{Guidal:2013rya}. That is, for a GPD at a given ($x,\xi,t$), 
+we can measure experimentally the real ($\mathcal{P} 
+\int_{0}^{1}dx[GPD(x,\xi,t)-GPD(-x,\xi,t)] \, C^{+}(x,\xi)$, with $\mathcal{P}$ 
+stands for the Cauchy principal value integral and $C^{+}(x,\xi)$ is a 
+coefficient function ($=  \frac{1}{x-\xi} + \frac{1}{x+\xi}$)) and the 
+imaginary $(GPD(\xi,\xi,t)-GPD(-\xi,\xi,t)$) parts of it's corresponding CFF.
 
-The main challenge to study nuclear DVCS is to ensure the exclusivity of the 
-reaction. Until now, the only available data set of nuclear DVCS
+The main challenge in exploring nuclear DVCS is to ensure the exclusivity of 
+the reaction. Until now, the only available data set of nuclear DVCS
 was from the HERMES experiment \cite{Ellinghaus:2002zw}, where exclusivity is 
@@
 The measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and 
-Xe) but has been critisized for mixing coherent and incoherent processes 
-[ref]. In this regard, the direct detection of the low-energy recoil nuclei is the best way to
-garanty that the nuclei is intact and that the reaction did not occur on a 
-bound nucleon. The CEBAF Large Acceptance Spectrometer (CLAS) setting  in the
-Hall-B of JLab being already optimized for DVCS measurments 
-[refs], we built a dedicated radial time projection chamber (RTPC) for 
-the detection of the recoiling low energy nuclei in order to complete this
-experimental setting. The $^4$He nucleus is an ideal experimental target in
-this regard as it is light enough to be detected in such a setting, while it
+Xe) but has been criticized for mixing coherent and incoherent processes 
+\cite{HERMES_BSA}. In this regard, the direct detection of the low-energy 
+recoil nuclei is the best way to guarantee that the nucleus is intact and that 
+the reaction did not occur on a bound nucleon. The CEBAF Large Acceptance 
+Spectrometer (CLAS) setting  in the Hall-B of JLab being already optimized for 
+DVCS measurements 
+\cite{Mecking:2003zu,Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}, 
+we built a dedicated radial time projection chamber (RTPC) for the detection of 
+the recoiling low energy nuclei in order to complete this experimental setting.  
+The $^4$He nucleus is an ideal experimental target in this regard as it is 
+light enough to be detected in such a setting, while it
 is subject to significant nuclear effects \cite{JSeely} and has rather high 
@@
 target placed in the center of CLAS. For DVCS experiments, the CLAS base line 
-design \cite{CLAS_ref} is supplemented with an inner calorimeter (IC) and a
-solenoid. The IC extends the photon detection acceptance of CLAS, which is 
-originally from 15$^{\circ}$ to 45$^{\circ}$, to polar angle as low 
-as 4$^{\circ}$. At these small angles the low-energy M\o{}ller 
-electrons produced in the target form a very high rate background that is
+design \cite{Mecking:2003zu} is supplemented with an inner calorimeter (IC) and 
+a solenoid. The IC extends the photon detection acceptance of CLAS, which is 
+originally from 15$^{\circ}$ to 45$^{\circ}$, to polar angle as low as 
+4$^{\circ}$. At these small angles the low-energy M\o{}ller electrons produced 
+in the target form a very high rate background that is
 suppressed by a 5 Tesla solenoid placed around the target.
@@
 Because the coherent DVCS cross section is peaked at low $-t$, the recoil 
-$^4$He nuclei produced in DVCS have a low average momentum around 250 MeV/c.
-The CLAS cannot detect such low energy $\alpha$ particles, so in order to 
-ensure the exclusivity of the measurement, we 
-built a small and light RTPC to complement CLAS. Figure~\ref{fig:RTPC} presents 
-the design of this RTPC that is surrounding the 
-$^4$He gaseous target and inside the solenoid magnet.
-The detector was specifically calibrated for the detection of
+$^4$He nuclei produced in DVCS have a low average momentum ($p/q$) around 150 
+MeV/c. The CLAS spectrometer cannot detect such low energy $\alpha$ particles, 
+so in order to ensure the exclusivity of the measurement, we built a small and 
+light RTPC to complement CLAS. Figure~\ref{fig:RTPC} presents the design of 
+this RTPC that is surrounding the $^4$He gaseous target and inside the solenoid 
+magnet. The detector was specifically calibrated for the detection of
 $^4$He nuclei using elastic scattering produced with a 1.2~GeV electron beam.
@@
 
-The main backgroud to the measurement of DVCS is the coherent $\pi^{0}$ 
-production. Therefore, we remove events where a $\pi^{0}$ can be identified 
-by invariant mass reconstruction of two photons.  To ensure that the 
-interaction occurs at the partonic level and that the DVCS handbag diagram is 
-applicable we select events with $Q^{2}>1~[GeV^{2}/c^{2}]$. The exclusivity of 
-the events is obtained by applying a set of cuts on the following kinematic 
-variables: the co-planarity angle ($\Delta \phi$), the missing energy, the 
-missing mass squared, the missing transverse momentum, the missing mass 
-squared of the $e'^4He'$ system and the angle ($\theta$) between the measured 
-photon and the missing momentum of the $e'^4He'$ system. The most relevant of 
-these cuts are presented in Figure~\ref{fig:kin-cuts}, these are 3$\sigma$ 
-cuts except for the missing energy that appears to be too large and for which 
-we reduced the cut window to [-0.45,0.5] GeV. After these requirements, we 
-have about 3500 events left, Figure \ref{fig:kin-coverage} presents their
+The main background to the measurement of DVCS is the coherent $\pi^{0}$ 
+production. Therefore, we remove events where a $\pi^{0}$ can be identified by 
+invariant mass reconstruction of two photons.  To ensure that the interaction 
+occurs at the partonic level and that the DVCS handbag diagram is applicable we 
+select events with $Q^{2}>1~[GeV^{2}/c^{2}]$. The exclusivity of the events is 
+obtained by applying a set of cuts on the following kinematic variables: the 
+co-planarity angle ($\Delta \phi$), the missing energy, the missing mass 
+squared, the missing transverse momentum, the missing mass squared of the 
+$e'^4He'$ system and the angle ($\theta$) between the measured photon and the 
+missing momentum of the $e'^4He'$ system. The most relevant of these cuts are 
+presented in Figure~\ref{fig:kin-cuts}, these are 3$\sigma$ cuts except for the 
+missing energy that appears to be too large and for which we reduced the cut 
+window to [-0.45,0.5] GeV. After these requirements, we have about 3200 events 
+left, Figure \ref{fig:kin-coverage} presents their
 kinematic distributions in ($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$).
@@
 cuts. The distributions from left to right and from top to bottoms are: $\Delta 
-\phi$, missing energy, missing mass squared and the 
-cone angle ($\theta$) between the measured and the calculated photons.}
+\phi$, missing energy, missing mass squared and the cone angle ($\theta$) 
+between the measured and the calculated photons.}
 \label{fig:kin-cuts}
@@
 %asymmetries
-Several observables related to DVCS are of interest, in this work we focus 
-only on the beam-spin asymmetry. This  
-observable is measurable using a polarized lepton beam on an unpolarized target 
-(U). It is convenient to use the beam-spin asymmetry
-because most of the experimental normalization and acceptance issues cancel out 
-in the asymmetry ratio. It is defined in terms of the cross sections as:
+Several observables related to DVCS are of interest, in this work we focus only 
+on the beam-spin asymmetry. This  observable is measurable using a polarized 
+lepton beam on an unpolarized target (U). It is convenient to use the beam-spin 
+asymmetry because most of the experimental normalization and acceptance issues 
+cancel out in the asymmetry ratio. It is defined in terms of the cross sections 
+as:
   \begin{equation}
@@
 three terms can be approximated as a finite sum of Fourier harmonics as shown 
-for the nucleon in \cite{Belitsky:2001ns} and for the spinless targets in 
+for the nucleon in \cite{Belitsky:2001ns} and for the spin-zero targets in 
 \cite{Kirchner:2003wt,Belitsky:2008bz}. Based on these calculations, the 
-beam-spin asymmetry ($A_{LU}$) can then be expressed as:
+beam-spin asymmetry ($A_{LU}$) of a spin-zero hadron can then be expressed as:
+
 \small
@@
 models that are identical. We should also request the projections from Vadim
-model: hep-ph/0509158.]
+model: hep-ph/0509158. (Mohammad to Raphael, the projections shown in figure 5 
+are for Carbon-12. Why would we added them?]
 
@@
   Phys.\ Rev.\ D {\bf 62}, 071503 (2000)
-  Erratum: [Phys.\ Rev.\ D {\bf 66}, 119903 (2002)]
+  Erratum: Phys.\ Rev.\ D {\bf 66}, 119903 (2002)
 
@@
   Eur.\ Phys.\ J.\ C {\bf 25}, 223 (2002)
-  Erratum: [Eur.\ Phys.\ J.\ C {\bf 31}, 277 (2003)]
+  Erratum: Eur.\ Phys.\ J.\ C {\bf 31}, 277 (2003)
 
@@
 
+\bibitem{Mazouz:2007aa} 
+   M.~Mazouz {\it et al.} [Jefferson Lab Hall A Collaboration],
+   Phys.\ Rev.\ Lett.\  {\bf 99}, 242501 (2007)
+
 \bibitem{Gavalian:2009} 
@@
 
-\bibitem{Mazouz:2007aa} 
-  M.~Mazouz {\it et al.} [Jefferson Lab Hall A Collaboration],
-   Phys.\ Rev.\ Lett.\  {\bf 99}, 242501 (2007)
+\bibitem{Goeke:2001tz}
+K. Goeke, M.V. Polyakov and M. Vanderhaeghen,
+Prog.\ Part.\ Nucl.\ Phys. {\bf 47}, 401 (2001).
+
+\bibitem{Diehl:2003ny}
+M. Diehl,
+Phys.\ Rept.  {\bf 388}, 41 (2003).
+
+\bibitem{Ji:2004gf}
+X.D. Ji,
+Ann.\ Rev.\ Nucl.\ Part.\ Sci. {\bf 54}, 413 (2004).
+
+\bibitem{Belitsky:2005qn}
+A.V. Belitsky and A.V. Radyushkin,
+Phys.\ Rept. {\bf 418}, 1 (2005).
+
+\bibitem{Boffi:2007yc} S. Boffi and B. Pasquini,
+Riv.\ Nuovo Cim. {\bf 30}, 387 (2007).
+
+\bibitem{Guidal:2013rya} 
+M.~Guidal, H.~Moutarde and M.~Vanderhaeghen,
+Rept.\ Prog.\ Phys.\  {\bf 76}, 066202 (2013).
+
+\bibitem{Dupre:2015jha} 
+  R.~Dupr\'e and S.~Scopetta,
+  Eur.\ Phys.\ J.\ A {\bf 52}, no. 6, 159 (2016)
+
+\bibitem{Hen:2016kwk} 
+  O.~Hen, G.~A.~Miller, E.~Piasetzky and L.~B.~Weinstein,
+  arXiv:1611.09748 [nucl-ex].
+
+\bibitem{Norton:2003cb} 
+  P.~R.~Norton,
+  Rept.\ Prog.\ Phys.\  {\bf 66}, 1253 (2003).
+
+\bibitem{Geesaman:1995yd} 
+  D.~F.~Geesaman, K.~Saito and A.~W.~Thomas,
+  Ann.\ Rev.\ Nucl.\ Part.\ Sci.\  {\bf 45}, 337 (1995).
 
@@
 
-\bibitem{Belitsky}
-A.~V.~Belitsky and A.~V.~Radyushkin, 
-Phys.\ Rept.\ vol. 418 (2005)
+\bibitem{Ellinghaus:2002zw}
+F.~Ellinghaus {\it et al.} [HERMES Collaboration],
+AIP Conf.\ Proc.\  {\bf 675}, 303 (2003)
 
-\bibitem{Guidal:2013rya}
-M.~Guidal, H.~Moutarde and M.~Vanderhaeghen,
-Rept.\ Prog.\ Phys.\  {\bf 76}, 066202 (2013)
+\bibitem{HERMES_BSA}
+A. Airapetian et al. (HERMES Collaboration), 
+Phys.\ Rev.\ C {\bf 81}, 035202 (2010)
+
+\bibitem{Mecking:2003zu} 
+   B.~A.~Mecking {\it et al.} [CLAS Collaboration],
+   Nucl.\ Instrum.\ Meth.\ A {\bf 503}, 513 (2003).
 
@@
 Phys.\ Rev.\ Lett.\ {\bf 103}, 202301 (2009)
-
-\bibitem{CLAS_ref}
-B.A. Mecking {\it et al.}, 
-Nucl.\ Inst.\ and Meth.\ A 503, 513 (2003)
 
@@
 
-\bibitem{Ellinghaus:2002zw}
-F.~Ellinghaus {\it et al.} [HERMES Collaboration],
-AIP Conf.\ Proc.\  {\bf 675}, 303 (2003)
-
-\bibitem{eg6_note}
-M. Hattawy {\it et al.} (CLAS-EG6 Working Group), 
-CLAS internal analysis note, 2016.
+%\bibitem{eg6_note}
+%M. Hattawy {\it et al.} (CLAS-EG6 Working Group), CLAS internal analysis note, 
+%2016.
 
@@
 Phys.\ Rev.\ C {\bf 72}, 032201 (2005)
-
-\bibitem{HERMES_BSA}
-A. Airapetian et al. (HERMES Collaboration), 
-Phys.\ Rev.\ C {\bf 81}, 035202 (2010)
 
@@
 
-\bibitem{Goeke:2001tz}
-K. Goeke, M.V. Polyakov and M. Vanderhaeghen,
-Prog.\ Part.\ Nucl.\ Phys. {\bf 47}, 401 (2001).
-
-\bibitem{Diehl:2003ny}
-M. Diehl,
-Phys.\ Rept.  {\bf 388}, 41 (2003).
-
-\bibitem{Ji:2004gf}
-X.D. Ji,
-Ann.\ Rev.\ Nucl.\ Part.\ Sci. {\bf 54}, 413 (2004).
-
-\bibitem{Belitsky:2005qn}
-A.V. Belitsky and A.V. Radyushkin,
-Phys.\ Rept. {\bf 418}, 1 (2005).
-
-\bibitem{Boffi:2007yc} 
-S. Boffi and B. Pasquini,
-Riv.\ Nuovo Cim. {\bf 30}, 387 (2007).
-
-\bibitem{Guidal:2013rya} 
-M.~Guidal, H.~Moutarde and M.~Vanderhaeghen,
-Rept.\ Prog.\ Phys.\  {\bf 76}, 066202 (2013).
-
-\bibitem{Dupre:2015jha} 
-  R.~Dupr\'e and S.~Scopetta,
-  Eur.\ Phys.\ J.\ A {\bf 52}, no. 6, 159 (2016)
-
-\bibitem{Hen:2016kwk} 
-  O.~Hen, G.~A.~Miller, E.~Piasetzky and L.~B.~Weinstein,
-  arXiv:1611.09748 [nucl-ex].
-
-\bibitem{Norton:2003cb} 
-  P.~R.~Norton,
-  Rept.\ Prog.\ Phys.\  {\bf 66}, 1253 (2003).
-
-\bibitem{Geesaman:1995yd} 
-  D.~F.~Geesaman, K.~Saito and A.~W.~Thomas,
-  Ann.\ Rev.\ Nucl.\ Part.\ Sci.\  {\bf 45}, 337 (1995).
-
 \end{thebibliography}

### 2017-02-03 eg6-letters/coherent/dvcs_he4_prl.tex
Finished editing the coherent paper

@@
 accessed in a DVCS reaction. Hence, we measure only complex Compton Form 
-Factors (CFF) \cite{Guidal:2013rya}. That is, for a GPD at a given ($x,\xi,t$), 
-we can measure experimentally the real ($\mathcal{P} 
-\int_{0}^{1}dx[GPD(x,\xi,t)-GPD(-x,\xi,t)] \, C^{+}(x,\xi)$, with $\mathcal{P}$ 
-stands for the Cauchy principal value integral and $C^{+}(x,\xi)$ is a 
-coefficient function ($=  \frac{1}{x-\xi} + \frac{1}{x+\xi}$)) and the 
-imaginary $(GPD(\xi,\xi,t)-GPD(-\xi,\xi,t)$) parts of it's corresponding CFF.
+Factors (CFF) \cite{Guidal:2013rya} defined as:
+\begin{align}
+\begin{split}
+\Re e(&\mathcal{H}_{A}) = \\
+    &\mathcal{P} 
+\int_{0}^{1}dx[H_A(x,\xi,t)-H_A(-x,\xi,t)] \, C^{+}(x,\xi), 
+\end{split} \\
+\Im m(&\mathcal{H}_{A}) = H_A(\xi,\xi,t)-H_A(-\xi,\xi,t),
+\end{align}
+with $H_A$ the GPD, $\mathcal{P}$ 
+the Cauchy principal value integral and $C^{+}(x,\xi)$ a 
+coefficient function ($=  \frac{1}{x-\xi} + \frac{1}{x+\xi}$)).
 
-The main challenge in exploring nuclear DVCS is to ensure the exclusivity of 
+The main challenge to study nuclear DVCS is to ensure the exclusivity of 
 the reaction. Until now, the only available data set of nuclear DVCS
@@
 The measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and 
-Xe) but has been criticized for mixing coherent and incoherent processes 
-\cite{HERMES_BSA}. In this regard, the direct detection of the low-energy 
+Xe) but the mixing of the coherent and incoherent processes could affect the
+measurement significantly \cite{Guzey:2003jh}. In this regard, the direct 
+detection of the low-energy 
 recoil nuclei is the best way to guarantee that the nucleus is intact and that 
-the reaction did not occur on a bound nucleon. The CEBAF Large Acceptance 
-Spectrometer (CLAS) setting  in the Hall-B of JLab being already optimized for 
+the reaction did not occur on a bound nucleon. The 
+CEBAF Large Acceptance 
+Spectrometer (CLAS) setting  in the Hall-B of JLab is already optimized for 
 DVCS measurements 
-\cite{Mecking:2003zu,Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}, 
-we built a dedicated radial time projection chamber (RTPC) for the detection of 
+\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}, 
+so we built a dedicated radial time projection chamber (RTPC) for the detection of 
 the recoiling low energy nuclei in order to complete this experimental setting.  
@@
 Because the coherent DVCS cross section is peaked at low $-t$, the recoil 
-$^4$He nuclei produced in DVCS have a low average momentum ($p/q$) around 150 
-MeV/c. The CLAS spectrometer cannot detect such low energy $\alpha$ particles, 
+$^4$He nuclei produced in DVCS have a low average momentum around 300 
+MeV/c. CLAS cannot detect such low energy $\alpha$ particles, 
 so in order to ensure the exclusivity of the measurement, we built a small and 
 light RTPC to complement CLAS. Figure~\ref{fig:RTPC} presents the design of 
-this RTPC that is surrounding the $^4$He gaseous target and inside the solenoid 
-magnet. The detector was specifically calibrated for the detection of
+this RTPC and the $^4$He gaseous target in its center. The detector was 
+specifically calibrated for the detection of
 $^4$He nuclei using elastic scattering produced with a 1.2~GeV electron beam.
@@
 beam-spin asymmetry ($A_{LU}$) of a spin-zero hadron can then be expressed as:
-
 \small
@@
 models that are identical. We should also request the projections from Vadim
-model: hep-ph/0509158. (Mohammad to Raphael, the projections shown in figure 5 
-are for Carbon-12. Why would we added them?]
+model: hep-ph/0509158.]
 
-In figure \ref{fig:CFF_HA}, within the given uncertainties, the extracted CFF 
-shows a slight dependence on $Q^{2}$, $x_B$, and $-t$, which are in agreement 
+The results of Figure \ref{fig:CFF_HA} show that the extraction of the CFF
+from the beam spin asymmetry is possible without any model dependent 
+assumptions. The amplitude and the dependences observed as a function of 
+$Q^{2}$, $x_B$, and $-t$ are in agreement 
 with the theoretical calculations. One can see a difference between the 
-precision of the extracted imaginary and real parts, which is expected because 
-$\alpha_2$ is suppressed compared to $\alpha_0$ contribution. However, we note 
-that the error bars are finite and that the fit converge without placing any 
-bound on the CFF, which is necessary on proton targets.
+precision of the extracted imaginary and real parts, which is expected from
+equation \ref{eq:A_LU-coh} because $\alpha_2$ is smaller than $\alpha_0$. 
+While these results are not precise enough to discriminate between the models,
+they are very promising for future exeperiments as they show our hability
+to directly extract the CFF of the helium nucleus in a completely model
+independent way.
 
@@
 In summary, we presented the first exclusive measurement of the coherent DVCS 
-off $^4$He using CLAS spectrometer, supplemented with an inner calorimeter, a 5 
-Tesla solenoid, and a specially designed radial TPC. This dataset represents a 
-unique source for the nuclear DVCS global dataset, which will be used to 
-constrain GPD models. The measured beam-spin asymmetries show a very strong 
-signal and allowed to perform the first fully model-independent extraction of 
-the $^4$He CFF $\mathcal{H}_A$. The extracted CFFs, while limited by 
-statistics, are in a good agreement with the available GPD models. This opens 
-many new perspectives to study the nuclear structure within the GPDs framework 
-and pave the way for future more precise measurements at JLab 12~GeV program 
-and possibly at the Electron-Ion Collider (EIC) to achieve better understanding 
-of the nuclear effects.
-
-The incoherent DVCS channel 
-measurement from the same data set in in preparation and will reported in 
-another publication.
-
-[order biblio]
+off $^4$He using the CLAS spectrometer supplemented  
+by a specially designed RTPC. This dataset represents a 
+unique source as the first exclusive coherent nuclear DVCS measurement, which 
+can be used to directly constrain GPD models. The measured beam-spin asymmetries 
+show a signal stronger than for the proton and allow to perform a fully 
+model-independent extraction of the $^4$He CFF $\mathcal{H}_A$. The extracted 
+CFF is in a good agreement with the available models. This opens 
+many new perspectives to study the nuclear structure within the GPD framework 
+and pave the way for future more precise measurements at JLab 12~GeV to 
+eventualy localize nuclear effects in the transverse plane.
 
@@
 
-\bibitem{HERMES_BSA}
-A. Airapetian et al. (HERMES Collaboration), 
-Phys.\ Rev.\ C {\bf 81}, 035202 (2010)
+\bibitem{Guzey:2003jh} 
+  V.~Guzey and M.~Strikman,
+  Phys.\ Rev.\ C {\bf 68}, 015204 (2003)
+
+\bibitem{JSeely}
+J. Seely {\it et al.} 
+Phys.\ Rev.\ Lett.\ {\bf 103}, 202301 (2009)
 
@@
    Nucl.\ Instrum.\ Meth.\ A {\bf 503}, 513 (2003).
-
-\bibitem{JSeely}
-J. Seely {\it et al.} 
-Phys.\ Rev.\ Lett.\ {\bf 103}, 202301 (2009)
 

### 2017-02-03 eg6-letters/coherent/dvcs_he4_prl.tex
preprint option in the header
minor edit

@@
-\documentclass[nofootinbib,twocolumn,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
+\documentclass[nofootinbib,twocolumn,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix,preprint]{revtex4}
 \usepackage{graphicx}
@@
 with $H_A$ the GPD, $\mathcal{P}$ 
-the Cauchy principal value integral and $C^{+}(x,\xi)$ a 
-coefficient function ($=  \frac{1}{x-\xi} + \frac{1}{x+\xi}$)).
+the Cauchy principal value integral and $C^{+}(x,\xi)$ a coefficient function 
+($=  \frac{1}{x-\xi} + \frac{1}{x+\xi}$).
 

### 2017-02-08 eg6-letters/coherent/dvcs_he4_prl.tex
added the lines numbers
dvcs_he4_prl.tex:  nathans language adjustments

--- 2017-02-03 eg6-letters/coherent/dvcs_he4_prl.tex
@@
-\documentclass[nofootinbib,twocolumn,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
+\RequirePackage{lineno}
+\documentclass[preprint,nofootinbib,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
 \usepackage{graphicx}
@@
 \usepackage{bm}% bold math
-
 %
@@
 %
+\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
+\expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
+\expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
+\renewenvironment{#1}%
+{\linenomath\csname old#1\endcsname}%
+{\csname oldend#1\endcsname\endlinenomath}}%
+\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
+\patchAmsMathEnvironmentForLineno{#1}%
+\patchAmsMathEnvironmentForLineno{#1*}}%
+\AtBeginDocument{%
+\patchBothAmsMathEnvironmentsForLineno{equation}%
+\patchBothAmsMathEnvironmentsForLineno{align}%
+\patchBothAmsMathEnvironmentsForLineno{flalign}%
+\patchBothAmsMathEnvironmentsForLineno{alignat}%
+\patchBothAmsMathEnvironmentsForLineno{gather}%
+\patchBothAmsMathEnvironmentsForLineno{multline}%
+}
+
+%
 \begin{document}
+\linenumbers
 
@@
 \date{\today}
-%
 \begin{abstract}
@@
 scattering (DVCS) off a nucleus for $A>1$. The experiment used the 6 GeV 
-electron beam from Jefferson Lab projected onto a $^4$He target in the center of the CEBAF 
-Large Acceptance Spectrometer (CLAS). An additional radial time projection 
-chamber (RTPC) was used to detect the recoiling $^4$He nuclei and ensure the 
-exclusivity of the process. We measured beam spin asymmetries significantly
-larger than the one observed on proton targets and extract,
+electron beam from Jefferson Lab projected onto a $^4$He target in the center 
+of the CEBAF Large Acceptance Spectrometer (CLAS). An additional radial time 
+projection chamber (RTPC) was used to detect the recoiling $^4$He nuclei and 
+ensure the exclusivity of the process. We measured beam spin asymmetries 
+significantly larger than that observed on proton targets and extracted,
 in a completely model independent way, the chiral even generalized parton 
@@
 
-A wealth of information on the quantum chromodynamics (QCD) lies in the 
-internal structure of hadrons. In the recent past, the development of the 
+A wealth of information on quantum chromodynamics (QCD) lies in the 
+internal structure of hadrons. In the recent past, development of the 
 generalized parton distributions (GPDs) framework has offered the possibility
@@
 scattering (DVCS), i.e. the hard exclusive electroproduction of a real photon. 
-While other processes are known to be sensitive to GPDs, the measurement of the
-DVCS is considered as the cleanest probe and has been the focus of a worldwide effort 
+While other processes are known to be sensitive to GPDs, the measurement of
+DVCS is considered the cleanest probe and has been the focus of a worldwide effort 
 \cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
@@
 involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
-CERN. The vast majority of these measurements was focused on the study of the 
-proton structure and allow the extraction of the tomography of the nucleon,
-for details on the formalism see 
-\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}.
+CERN. The vast majority of these measurements focused on the study of 
+proton structure and allowed extraction of the tomography of the nucleon (for details on the formalism, see 
+\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
 This framework is also applicable to nuclei, giving access to completely new 
-information about the nuclear structure in terms of quarks and 
+information about nuclear structure in terms of quarks and 
 gluons \cite{Dupre:2015jha}.
-The study of the 3D structure of the nuclei appears to be especially important
+Study of the 3D structure of nuclei appears to be especially important
 in light of the large nuclear effects observed in nuclear parton distribution 
@@
 
-Experimentally, the coherent nuclear DVCS channel is difficult to measure because of 
-its small cross section and the necessity to ensure that the target remains 
+The coherent nuclear DVCS channel is experimentally difficult due to  
+its small cross section and the necessity to ensure the target remains 
 intact while emitting a hard photon ($eA \rightarrow e' A' \gamma$). Figure 
-\ref{fig:diags} illustrates the hand bag diagram for the coherent DVCS on 
-$^4$He. Similarly to the proton case, at large photon's 4-momentum square 
-$Q^2$ ($= -(k-k')^{2}$) and small squared momentum transfer $t$ 
-($= (p-p')^{2}$), the DVCS handbag diagram can be factorized into two parts 
-\cite{Freund_Collins,Ji_Osborne}. The hard part includes photons-quark 
-interaction and is calculable with perturbative QED, while the non-perturbative 
+\ref{fig:diags} illustrates the hand bag diagram for coherent DVCS on 
+$^4$He. Similar to the proton case, at large virtual photon's 4-momentum square 
+$Q^2=-(k-k')^{2}$ and small squared momentum transfer $t=(p-p')^{2}$,
+the DVCS handbag diagram can be factorized into two parts 
+\cite{Freund_Collins,Ji_Osborne}. The hard part includes the photon-quark 
+interaction and is calculable with perturbative QED.  The non-perturbative 
 part is parametrized in terms of GPDs, which embed the partonic structure of 
-the hadron. The GPDs depend on three variables $x$, $\xi$ and $t$, which are 
+the hadron. The GPDs depend on the three variables $x_B$, $\xi$ and $t$, which are 
 indicated in Figure \ref{fig:diags} for the DVCS process. In DVCS, $\xi$ can 
@@
 where $x_B=\frac{Q^2}{2M\nu}$ with $M$ the proton mass and 
-$\nu=E_e-E_{e^\prime}$. One can easily access $t$ as the squared momentum 
-transferred to the target, however the $x$ variable cannot be experimentally 
+$\nu=E_e-E_{e^\prime}$. One can access $t$ as the squared momentum 
+transferred to the target, however $x_B$ cannot be experimentally 
 accessed in a DVCS reaction. Hence, we measure only complex Compton Form 
@@
 with $H_A$ the GPD, $\mathcal{P}$ 
-the Cauchy principal value integral and $C^{+}(x,\xi)$ a 
-coefficient function ($=  \frac{1}{x-\xi} + \frac{1}{x+\xi}$)).
+the Cauchy principal value integral, and $C^{+}(x,\xi)$ a coefficient function 
+($=  \frac{1}{x-\xi} + \frac{1}{x+\xi}$).
 
-The main challenge to study nuclear DVCS is to ensure the exclusivity of 
+The main challenge in studying nuclear DVCS is ensuring the exclusivity of 
 the reaction. Until now, the only available data set of nuclear DVCS
-was from the HERMES experiment \cite{Ellinghaus:2002zw}, where exclusivity is 
-based on kinematic cuts on the measured scattered electron and real photon only. 
-The measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and 
-Xe) but the mixing of the coherent and incoherent processes could affect the
-measurement significantly \cite{Guzey:2003jh}. In this regard, the direct 
+was from the HERMES experiment \cite{Ellinghaus:2002zw}, where exclusivity was 
+based only on kinematic cuts on the measured scattered electron and real photon. 
+That measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and 
+Xe), but the mixing of the coherent and incoherent processes could affect the
+measurement significantly \cite{Guzey:2003jh}. In this regard, direct 
 detection of the low-energy 
-recoil nuclei is the best way to guarantee that the nucleus is intact and that 
+recoil nucleus is the best way to guarantee the nucleus remains intact and that 
 the reaction did not occur on a bound nucleon. The 
 CEBAF Large Acceptance 
-Spectrometer (CLAS) setting  in the Hall-B of JLab is already optimized for 
+Spectrometer (CLAS) in Hall-B at JLab is already optimized for 
 DVCS measurements 
@@
 the recoiling low energy nuclei in order to complete this experimental setting.  
-The $^4$He nucleus is an ideal experimental target in this regard as it is 
+The $^4$He nucleus is an ideal experimental target in this regard, as it is 
 light enough to be detected in such a setting, while it
 is subject to significant nuclear effects \cite{JSeely} and has rather high 
-density. Using a helium target leads to another important advantage, the number of GPDs 
-defined for a hadron depends on its spin. The structure of a spin zero nuclei, such as 
-$^4He$, is parametrized by only one chiral even GPD ($H_{A}(x,\xi,t)$) at 
-leading twist, while 4 GPDs arise in the nucleon case. That significantly
-simplifies the interpretation of the data and allow a model independent
-extraction of the $^4$He CFF ($\mathcal{H}_{A}$) that will be presented at the
+density.  A helium target leads to another important advantage, as the number of GPDs 
+defined for a hadron depends on its spin. The structure of a spin zero nucleus, such as 
+$^4$He, is parametrized by only one chiral even GPD ($H_{A}(x,\xi,t)$) at 
+leading twist, while 4 GPDs arise in the nucleon case. This significantly
+simplifies the interpretation of the data and allows a model independent
+extraction of the $^4$He CFF ($\mathcal{H}_{A}$) presented at the
 end of this letter.
@@
 
-The experiment E08-024 took place in the experimental Hall-B of Jefferson 
-laboratory (JLab) in 2009 using the nearly 100\% duty factor longitudinally 
+The experiment E08-024 took place in Hall-B at JLab
+in 2009 using the nearly 100\% duty factor, longitudinally 
 polarized electron beam (83$\%$ polarization) at its full energy of 6.064 
 GeV. The data were collected over three months using a 6 atm gaseous $^4$He 
-target placed in the center of CLAS. For DVCS experiments, the CLAS base line 
+target placed in the center of CLAS. For DVCS experiments, the CLAS baseline 
 design \cite{Mecking:2003zu} is supplemented with an inner calorimeter (IC) and 
-a solenoid. The IC extends the photon detection acceptance of CLAS, which is 
-originally from 15$^{\circ}$ to 45$^{\circ}$, to polar angle as low as 
+a solenoid. The IC extends the photon detection acceptance of CLAS, which was 
+originally from 15$^{\circ}$ to 45$^{\circ}$, to polar angles as low as 
 4$^{\circ}$. At these small angles the low-energy M\o{}ller electrons produced 
@@
 this RTPC and the $^4$He gaseous target in its center. The detector was 
-specifically calibrated for the detection of
-$^4$He nuclei using elastic scattering produced with a 1.2~GeV electron beam.
+calibrated specifically for the detection of
+$^4$He nuclei based on elastic scattering with a 1.2~GeV electron beam.
 
@@
 %DVCS selection
-To identify the coherent DVCS events, we first select events where one 
-electron, one $^4$He and at least one photon are detected in the final state. 
-Electrons are identified by using fiducial cuts and detecting a good
-signals in all the sub-detectors of the base line CLAS (drift chambers, 
+To identify coherent DVCS events, we first select events where one 
+electron, one $^4$He, and at least one photon are detected in the final state. 
+Electrons are identified by using fiducial cuts and requiring appropriate
+signals in all the sub-detectors of the baseline CLAS (drift chambers, 
 Cherenkov counters, electromagnetic calorimeter, and time of flight 
@@
 timing and track quality cuts in the RTPC detector. In addition,
-we apply a vertex matching cut to make sure the electron and the helium
-nuclei originate from the same place. The photons are detected either
-in the IC or the CLAS electromagnetic calorimeter, note that even though the 
+we apply a vertex matching cut to ensure the electron and helium
+nucleus originate from the same position. The photons are detected in either
+the IC or the CLAS electromagnetic calorimeter.  Note that even though the 
 DVCS reaction has only one real photon in the final state, 
 events with more than one good photon are not discarded at this stage. This is 
-motivated by the fact that soft photons are likely to be produced in random 
-coincidences, but cannot be mistaken for DVCS photons which are always at high
-energies ($>2$ GeV). So, the most energetic photon is always considered as 
-the DVCS photon candidate.
+motivated by the fact that, while soft photons are likely to be produced in random 
+coincidence, they cannot be mistaken for the large energy DVCS photons ($>2$ GeV).
+The most energetic photon is always considered as the DVCS photon candidate.
 
-The main background to the measurement of DVCS is the coherent $\pi^{0}$ 
+The main background in the measurement of DVCS is coherent $\pi^{0}$ 
 production. Therefore, we remove events where a $\pi^{0}$ can be identified by 
-invariant mass reconstruction of two photons.  To ensure that the interaction 
-occurs at the partonic level and that the DVCS handbag diagram is applicable we 
+invariant mass reconstruction of two photons.  To ensure the interaction 
+occurs at the partonic level and the DVCS handbag diagram is dominant, we 
 select events with $Q^{2}>1~[GeV^{2}/c^{2}]$. The exclusivity of the events is 
@@
 squared, the missing transverse momentum, the missing mass squared of the 
-$e'^4He'$ system and the angle ($\theta$) between the measured photon and the 
+$e'^4He'$ system, and the angle ($\theta$) between the measured photon and the 
 missing momentum of the $e'^4He'$ system. The most relevant of these cuts are 
-presented in Figure~\ref{fig:kin-cuts}, these are 3$\sigma$ cuts except for the 
-missing energy that appears to be too large and for which we reduced the cut 
-window to [-0.45,0.5] GeV. After these requirements, we have about 3200 events 
-left, Figure \ref{fig:kin-coverage} presents their
+presented in Figure~\ref{fig:kin-cuts}, which shows 3$\sigma$ cuts except for the 
+missing energy (which appears to be too large and for which we reduced the cut 
+window to [-0.45,0.5] GeV). After these requirements, we have about 3200 events 
+left, and Figure \ref{fig:kin-coverage} presents their
 kinematic distributions in ($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$).
@@
 
-We identified two main background to our measurement, the accidental 
-coincidences and the exclusive $\pi^0$ production. The accidental events have 
-particles coming from different events, we estimate their  contribution
-to 4.1\% of our sample. We evaluated this contribution by selecting events 
+We identified two main backgrounds to our measurement, accidental 
+coincidences and exclusive $\pi^0$ production. The accidental events have 
+particles coming from different events, and we estimate their  contribution
+to be 4.1\% of our sample. We evaluated this contribution by selecting events 
 passing all our cuts but with an electron and an helium originating from different 
-vertices. Regarding the $\pi^0$ production, it can easily be mistaken with DVCS when 
+vertices. Regarding the $\pi^0$ production, it can easily be mistaken for DVCS when 
 one of the two photons of the $\pi^0$ decay is produced at low energy in the 
-laboratory frame and remain undetected. To estimate the importance of this 
+laboratory frame and remains undetected. To estimate the importance of this 
 background, we developed an event generator calibrated on the experimental yield 
@@
 would be mistaken for DVCS. This ratio is then multiplied by the measured yield 
-of exclusive $\pi^0$ events to correct the DVCS data. Depending on the bins, we
+of exclusive $\pi^0$ events to correct the DVCS data. Depending on the kinematics, we
 found contaminations of 2 to 4\%. The study of systematics errors showed that the main 
@@
 %asymmetries
-Several observables related to DVCS are of interest, in this work we focus only 
+Several observables related to DVCS are of interest, but in this work we focus only 
 on the beam-spin asymmetry. This  observable is measurable using a polarized 
@@
   \end{equation}
-where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the DVCS differential cross 
+where $d^{5}\sigma^{+(-)}$ is the DVCS differential cross 
 section for a positive (negative) beam helicity. Experimentally, $A_{LU}$ 
-can be expressed in terms of the collected number of events in each 
+can be expressed in terms of the measured number of events in each 
 beam-helicity state ($N^{+}$, $N^{-}$) as:
@@
 
-To interpret the DVCS, one has to keep in mind that this reaction is 
+To interpret DVCS, one has to keep in mind that this reaction is 
 indistinguishable from the Bethe-Heitler (BH) process, where the final photon 
@@
 and leading order, the deeply virtual photon production cross section is 
-composed of a BH, a DVCS, and an interference terms. The amplitudes of the 
-three terms can be approximated as a finite sum of Fourier harmonics as shown 
+composed of BH, DVCS, and interference terms. The amplitudes of the 
+three terms can be approximated as a finite sum of Fourier harmonics, as shown 
 for the nucleon in \cite{Belitsky:2001ns} and for the spin-zero targets in 
@@
 where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
-and real parts of the $^4$He CFF $\mathcal{H}_{A}$ associated to the GPD $H_A$. 
-$\phi$ is the azimuthal angle between the ($e$,$e'$) and 
+and real parts of the $^4$He CFF $\mathcal{H}_{A}$ associated with the GPD $H_A$,
+and $\phi$ is the azimuthal angle between the ($e$,$e'$) and 
 ($\gamma^{*}$,$^4$He$'$) planes. The $\alpha_{i}$'s are $\phi$-dependent 
@@
 \normalsize
-Where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$ is the $^4$He mass, 
-$\mathcal{P}_1(\phi)$ and $\mathcal {P}_2(\phi)$ are the Bethe-Heitler
-propagators. The factors: $c_{0,1,2}^{BH}$, $c_0^{DVCS}$, $c_{0,1}^{INT}$ and
-$s_1^{INT}$ are the Fourier coefficients of the BH, $S{++}(1)$, $C_{++}(0)$, 
+Where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$ the $^4$He mass and 
+$\mathcal{P}_1(\phi)$ and $\mathcal {P}_2(\phi)$ the Bethe-Heitler
+propagators. The factors $c_{0,1,2}^{BH}$, $c_0^{DVCS}$, $c_{0,1}^{INT}$ and
+$s_1^{INT}$ are the Fourier coefficients of the BH, and $S{++}(1)$, $C_{++}(0)$, 
 and $C_{++}(1)$ are the Fourier harmonics in the leptonic tensor. The 
 explicit expressions of these terms can be found in \cite{Belitsky:2008bz}. 
-We see that using the $\sin(\phi)$ and $\cos(\phi)$ contributions, it is 
+We see that by using the $\sin(\phi)$ and $\cos(\phi)$ contributions, it is 
 possible to extract 
@@
 
-Due to our limited statistics, we only bin  our data 
- on the azimuthal angle ($\phi$) and either one of the kinemtical variables 
-$Q^{2}$, $x_{B}$ and $t$. Figure \ref{fig:alu} presents the $A_{LU}$ for the three
+Due to limited statistics, we only bin  our data two-dimensionally 
+ in the azimuthal angle ($\phi$) and one of the kinemtical variables 
+$Q^{2}$, $x_{B}$ and $t$. Figure \ref{fig:alu} presents $A_{LU}$ for the three
 sets of binning. The asymmetries are fitted with the form of
-equation \ref{eq:A_LU-coh}, where the real and the imaginary part of the CFF
+equation \ref{eq:A_LU-coh}, where the real and imaginary part of the CFF
 $\mathcal{H}_{A}$ are the free parameters of the fit. Figure \ref{fig:alu90} 
@@
 at $\phi$~=~90$^{\circ}$. The $x_{B}$ and $-t$-dependencies are compared to 
-the theoretical calculations performed by S.~Liuti and K.~Taneja 
+theoretical calculations performed by S.~Liuti and K.~Taneja 
 \cite{simonetta_2}. Their model relies on the impulse approximation and uses 
-advanced spectral function of the nuclei. The calculations are at slightly different 
-kinematics than ours but provide some guidance. The experimental 
+advanced spectral functions of nuclei. The calculations are at slightly different 
+kinematics than our data but still provide some guidance. The experimental 
 results appear to have larger asymmetries than the calculations. These 
@@
 We display in figure \ref{fig:CFF_HA} our extraction of the $^4$He CFF 
-$\mathcal{H}_A$ together with theoretical calculations from two models 
-labeled: convolution, and off-shell models. In the convolution 
+$\mathcal{H}_A$, together with theoretical calculations from two models, 
+labelled {\em convolution} and {\em off-shell}. In the convolution 
 model \cite{Vadim_priv}, the nucleus is assumed to be composed of 
-non-relativistic non-interacting nucleons, and these nucleons interact 
+non-relativistic non-interacting nucleons, where these nucleons interact 
 independently with the probe. The convolution/dual model is based on nucleon GPDs from 
-the dual parametrization \cite{Guzey:2006xi}, the convolution/VGG uses nucleon GPDs  
-from the VGG model, which is based on the double distributions ansatz 
-\cite{DD_model}. The Off-shell model \cite{GonzalezHernandez:2012jv} relies on 
-impulse approximation and uses advanced spectral function of the 
-nuclei that accounts for all configurations of the final nuclear system and the 
+the dual parametrization \cite{Guzey:2006xi}, where the convolution/VGG uses nucleon GPDs  
+from the VGG model and is based on the double distributions ansatz 
+\cite{DD_model}. The off-shell model \cite{GonzalezHernandez:2012jv} relies on the 
+impulse approximation and uses advanced spectral functions of  
+nuclei that account for all configurations of the final nuclear system and the 
 binding effects between the nucleons.
@@
 
-The results of Figure \ref{fig:CFF_HA} show that the extraction of the CFF
+The results in Figure \ref{fig:CFF_HA} show that the extraction of the CFF
 from the beam spin asymmetry is possible without any model dependent 
-assumptions. The amplitude and the dependences observed as a function of 
+assumptions. The amplitude and the dependencies observed as a function of 
 $Q^{2}$, $x_B$, and $-t$ are in agreement 
@@
 While these results are not precise enough to discriminate between the models,
-they are very promising for future exeperiments as they show our hability
+they are very promising for future exeperiments and demonstrate our ability
 to directly extract the CFF of the helium nucleus in a completely model
@@
 %conclusion
-In summary, we presented the first exclusive measurement of the coherent DVCS 
+In summary, we present the first exclusive measurement of coherent DVCS 
 off $^4$He using the CLAS spectrometer supplemented  
 by a specially designed RTPC. This dataset represents a 
-unique source as the first exclusive coherent nuclear DVCS measurement, which 
+unique source as the first exclusive coherent nuclear DVCS measurement which 
 can be used to directly constrain GPD models. The measured beam-spin asymmetries 

### 2017-02-08 eg6-letters/coherent/dvcs_he4_prl.tex
nathan:  missed a bit in the last paragraph

@@
 many new perspectives to study the nuclear structure within the GPD framework 
-and pave the way for future more precise measurements at JLab 12~GeV to 
+and paves the way for future, more precise measurements at JLab 12~GeV to 
 eventualy localize nuclear effects in the transverse plane.

### 2017-02-08 eg6-letters/coherent/dvcs_he4_prl.tex
Minor update for x vs. x_B confusions

@@
 part is parametrized in terms of GPDs, which embed the partonic structure of 
-the hadron. The GPDs depend on the three variables $x_B$, $\xi$ and $t$, which are 
+the hadron. The GPDs depend on the three variables $x$, $\xi$ and $t$, which are 
 indicated in Figure \ref{fig:diags} for the DVCS process. In DVCS, $\xi$ can 
@@
 $\nu=E_e-E_{e^\prime}$. One can access $t$ as the squared momentum 
-transferred to the target, however $x_B$ cannot be experimentally 
+transferred to the target, however $x$ cannot be experimentally 
 accessed in a DVCS reaction. Hence, we measure only complex Compton Form 

### 2017-02-08 eg6-letters/coherent/dvcs_he4_prl.tex
minor corrections after Nathan suggestions

@@
 
-The coherent nuclear DVCS channel is experimentally difficult due to  
-its small cross section and the necessity to ensure the target remains 
-intact while emitting a hard photon ($eA \rightarrow e' A' \gamma$). Figure 
-\ref{fig:diags} illustrates the hand bag diagram for coherent DVCS on 
-$^4$He. Similar to the proton case, at large virtual photon's 4-momentum square 
+The coherent nuclear DVCS channel, $eA \rightarrow e' A' \gamma$, is 
+experimentally difficult due to  its small cross section and the necessity to 
+ensure the target remains intact while emitting a hard photon.  Figure 
+\ref{fig:diags} illustrates the hand bag diagram for coherent DVCS on $^4$He.  
+Similar to the proton case, at large virtual photon's 4-momentum square 
 $Q^2=-(k-k')^{2}$ and small squared momentum transfer $t=(p-p')^{2}$,
@@
 Xe), but the mixing of the coherent and incoherent processes could affect the
-measurement significantly \cite{Guzey:2003jh}. In this regard, direct 
-detection of the low-energy 
-recoil nucleus is the best way to guarantee the nucleus remains intact and that 
-the reaction did not occur on a bound nucleon. The 
-CEBAF Large Acceptance 
-Spectrometer (CLAS) in Hall-B at JLab is already optimized for 
-DVCS measurements 
-\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}, 
-so we built a dedicated radial time projection chamber (RTPC) for the detection of 
+measurement significantly \cite{Guzey:2003jh}. In this regard, direct detection 
+of the low-energy recoil nucleus is the best way to guarantee the nucleus 
+remains intact and that the reaction did not occur on a bound nucleon. The 
+CEBAF Large Acceptance Spectrometer (CLAS) in Hall-B at JLab is already 
+optimized for DVCS measurements 
+\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}, so we 
+built a dedicated radial time projection chamber (RTPC) for the detection of 
 the recoiling low energy nuclei in order to complete this experimental setting.  
@@
 model \cite{Vadim_priv}, the nucleus is assumed to be composed of 
-non-relativistic non-interacting nucleons, where these nucleons interact 
-independently with the probe. The convolution/dual model is based on nucleon GPDs from 
-the dual parametrization \cite{Guzey:2006xi}, where the convolution/VGG uses nucleon GPDs  
-from the VGG model and is based on the double distributions ansatz 
-\cite{DD_model}. The off-shell model \cite{GonzalezHernandez:2012jv} relies on the 
-impulse approximation and uses advanced spectral functions of  
-nuclei that account for all configurations of the final nuclear system and the 
-binding effects between the nucleons.
+non-relativistic and non-interacting nucleons, where these nucleons interact 
+independently with the probe. The convolution/dual model is based on nucleon 
+GPDs from the dual parametrization \cite{Guzey:2006xi}, where the 
+convolution/VGG uses nucleon GPDs  from the VGG model and is based on the 
+double distributions ansatz \cite{DD_model}. The off-shell model 
+\cite{GonzalezHernandez:2012jv} relies on the impulse approximation and uses 
+advanced spectral functions of  nuclei that account for all configurations of 
+the final nuclear system and the binding effects between the nucleons.
 [These need to be renamed on the figure, it does not make sense to call differently
@@
 While these results are not precise enough to discriminate between the models,
-they are very promising for future exeperiments and demonstrate our ability
+they are very promising for future experiments and demonstrate our ability
 to directly extract the CFF of the helium nucleus in a completely model

### 2017-02-10 eg6-letters/incoherent/incoherent_prl.tex
push the first comment on the incoherent prl

--- 2017-02-08 eg6-letters/coherent/dvcs_he4_prl.tex
@@
 \RequirePackage{lineno}
-\documentclass[preprint,nofootinbib,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
+\documentclass[twocolumn,nofootinbib,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
 \usepackage{graphicx}
@@
 \begin{document}
-\linenumbers
+%\linenumbers
 
-\title{First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei}
+\title{Incoherent Deep Virtual Compton Scattering off $^4$He using CLAS 
+spectrometer}
 
@@
 \begin{abstract}
-We report the first fully exclusive measurement of deeply virtual Compton 
-scattering (DVCS) off a nucleus for $A>1$. The experiment used the 6 GeV 
-electron beam from Jefferson Lab projected onto a $^4$He target in the center 
-of the CEBAF Large Acceptance Spectrometer (CLAS). An additional radial time 
-projection chamber (RTPC) was used to detect the recoiling $^4$He nuclei and 
-ensure the exclusivity of the process. We measured beam spin asymmetries 
-significantly larger than that observed on proton targets and extracted,
-in a completely model independent way, the chiral even generalized parton 
-distribution (GPD) of the $^4$He nucleus. This pioneering measurement 
-leads the way toward the 3D imaging of the partonic structure of nuclei.
+We report the incoherent beam-spin asymmetry measurement of deeply virtual 
+Compton scattering (DVCS) off $^4$He. The experiment used the 6 GeV electron 
+beam from Jefferson Lab projected onto a $^4$He target in the center of the 
+CEBAF Large Acceptance Spectrometer (CLAS).
 \end{abstract}
@@
 \maketitle
-
-A wealth of information on quantum chromodynamics (QCD) lies in the 
-internal structure of hadrons. In the recent past, development of the 
-generalized parton distributions (GPDs) framework has offered the possibility
-to obtain new information about the momentum and spatial degrees of 
-freedom of the quark and gluons inside hadrons 
-\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.
-In impact parameter space, the GPDs are indeed interpreted as a tomography of the 
-transverse plane for partons carrying a certain longitudinal momentum 
-\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep,Burkardt:2005hp}.
 
@@
 Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}
-[Should we cite less publications on the topic or a review?]
 involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
-CERN. The vast majority of these measurements focused on the study of 
-proton structure and allowed extraction of the tomography of the nucleon (for details on the formalism, see 
+CERN. The vast majority of these measurements focused on the study of proton 
+structure and allowed extraction of the tomography of the nucleon (for details 
+on the formalism, see 
 \cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
-This framework is also applicable to nuclei, giving access to completely new 
-information about nuclear structure in terms of quarks and 
-gluons \cite{Dupre:2015jha}.
-Study of the 3D structure of nuclei appears to be especially important
-in light of the large nuclear effects observed in nuclear parton distribution 
-functions \cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.
 
 \begin{figure}[tb]
-\includegraphics[width=6.5cm]{figs/DVCS_diagram.pdf}
+\includegraphics[width=7.5cm]{figs/handbag_incoherent.pdf}
 \caption{Representation of the leading-order, twist-2, handbag diagram of the 
-DVCS process off $^4$He.}
+incoherent DVCS process off $^4$He.}
 \label{fig:diags}
 \end{figure}
-
-The coherent nuclear DVCS channel is experimentally difficult due to  
-its small cross section and the necessity to ensure the target remains 
-intact while emitting a hard photon ($eA \rightarrow e' A' \gamma$). Figure 
-\ref{fig:diags} illustrates the hand bag diagram for coherent DVCS on 
-$^4$He. Similar to the proton case, at large virtual photon's 4-momentum square 
-$Q^2=-(k-k')^{2}$ and small squared momentum transfer $t=(p-p')^{2}$,
-the DVCS handbag diagram can be factorized into two parts 
-\cite{Freund_Collins,Ji_Osborne}. The hard part includes the photon-quark 
-interaction and is calculable with perturbative QED.  The non-perturbative 
-part is parametrized in terms of GPDs, which embed the partonic structure of 
-the hadron. The GPDs depend on the three variables $x$, $\xi$ and $t$, which are 
-indicated in Figure \ref{fig:diags} for the DVCS process. In DVCS, $\xi$ can 
-be related to the Bjorken variable $x_{B}$: $\xi\approx {{x_B}\over{2-x_B}}$, 
-where $x_B=\frac{Q^2}{2M\nu}$ with $M$ the proton mass and 
-$\nu=E_e-E_{e^\prime}$. One can access $t$ as the squared momentum 
-transferred to the target, however $x$ cannot be experimentally 
-accessed in a DVCS reaction. Hence, we measure only complex Compton Form 
-Factors (CFF) \cite{Guidal:2013rya} defined as:
-\begin{align}
-\begin{split}
-\Re e(&\mathcal{H}_{A}) = \\
-    &\mathcal{P} 
-\int_{0}^{1}dx[H_A(x,\xi,t)-H_A(-x,\xi,t)] \, C^{+}(x,\xi), 
-\end{split} \\
-\Im m(&\mathcal{H}_{A}) = H_A(\xi,\xi,t)-H_A(-\xi,\xi,t),
-\end{align}
-with $H_A$ the GPD, $\mathcal{P}$ 
-the Cauchy principal value integral, and $C^{+}(x,\xi)$ a coefficient function 
-($=  \frac{1}{x-\xi} + \frac{1}{x+\xi}$).
-
-The main challenge in studying nuclear DVCS is ensuring the exclusivity of 
-the reaction. Until now, the only available data set of nuclear DVCS
-was from the HERMES experiment \cite{Ellinghaus:2002zw}, where exclusivity was 
-based only on kinematic cuts on the measured scattered electron and real photon. 
-That measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and 
-Xe), but the mixing of the coherent and incoherent processes could affect the
-measurement significantly \cite{Guzey:2003jh}. In this regard, direct 
-detection of the low-energy 
-recoil nucleus is the best way to guarantee the nucleus remains intact and that 
-the reaction did not occur on a bound nucleon. The 
-CEBAF Large Acceptance 
-Spectrometer (CLAS) in Hall-B at JLab is already optimized for 
-DVCS measurements 
-\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}, 
-so we built a dedicated radial time projection chamber (RTPC) for the detection of 
-the recoiling low energy nuclei in order to complete this experimental setting.  
-The $^4$He nucleus is an ideal experimental target in this regard, as it is 
-light enough to be detected in such a setting, while it
-is subject to significant nuclear effects \cite{JSeely} and has rather high 
-density.  A helium target leads to another important advantage, as the number of GPDs 
-defined for a hadron depends on its spin. The structure of a spin zero nucleus, such as 
-$^4$He, is parametrized by only one chiral even GPD ($H_{A}(x,\xi,t)$) at 
-leading twist, while 4 GPDs arise in the nucleon case. This significantly
-simplifies the interpretation of the data and allows a model independent
-extraction of the $^4$He CFF ($\mathcal{H}_{A}$) presented at the
-end of this letter.
 
@@
 
-Because the coherent DVCS cross section is peaked at low $-t$, the recoil 
-$^4$He nuclei produced in DVCS have a low average momentum around 300 
-MeV/c. CLAS cannot detect such low energy $\alpha$ particles, 
-so in order to ensure the exclusivity of the measurement, we built a small and 
-light RTPC to complement CLAS. Figure~\ref{fig:RTPC} presents the design of 
-this RTPC and the $^4$He gaseous target in its center. The detector was 
-calibrated specifically for the detection of
-$^4$He nuclei based on elastic scattering with a 1.2~GeV electron beam.
+%DVCS selection
+To identify incoherent DVCS events, we first select events where one electron, 
+one proton, and at least one photon are detected in the final state. Electrons 
+are identified by using fiducial cuts and requiring appropriate signals in all 
+the sub-detectors of the baseline CLAS (drift chambers, Cherenkov counters, 
+electromagnetic calorimeter, and time of flight scintillators). Protons were 
+identified with fiducial and timing cuts using the CLAS drift chambers and time 
+of flight scintillators. In addition, we apply a vertex matching cut to ensure 
+the electron and the proton originate from the same position. The photons are 
+detected in either the IC or the CLAS electromagnetic calorimeter.  Note that 
+even though the DVCS reaction has only one real photon in the final state, 
+events with more than one good photon are not discarded at this stage. This is 
+motivated by the fact that, while soft photons are likely to be produced in 
+random coincidence, they cannot be mistaken for the large energy DVCS photons 
+($>2$ GeV). The most energetic photon is always considered as the DVCS photon 
+candidate.
 
-\begin{figure}[tb]
-\vspace{-1.1cm}
-\includegraphics[width=7.0cm,angle=-90]{figs/RTPC.pdf}
-\vspace{-1.1cm}
-\caption{Left: A picture of the E08-024 RTPC before insertion into the 
-   solenoid. Right: A cross section of the E08-024 RTPC perpendicular to the 
-   beam direction. An illustration of a $^4$He track originating from the 
-   pressurized straw target is shown along with the electrons produced in the 
-   drift region.}
-\label{fig:RTPC}
-\end{figure}
-
-%DVCS selection
-To identify coherent DVCS events, we first select events where one 
-electron, one $^4$He, and at least one photon are detected in the final state. 
-Electrons are identified by using fiducial cuts and requiring appropriate
-signals in all the sub-detectors of the baseline CLAS (drift chambers, 
-Cherenkov counters, electromagnetic calorimeter, and time of flight 
-scintillators). The $^4$He tracks are identified with fiducial, 
-timing and track quality cuts in the RTPC detector. In addition,
-we apply a vertex matching cut to ensure the electron and helium
-nucleus originate from the same position. The photons are detected in either
-the IC or the CLAS electromagnetic calorimeter.  Note that even though the 
-DVCS reaction has only one real photon in the final state, 
-events with more than one good photon are not discarded at this stage. This is 
-motivated by the fact that, while soft photons are likely to be produced in random 
-coincidence, they cannot be mistaken for the large energy DVCS photons ($>2$ GeV).
-The most energetic photon is always considered as the DVCS photon candidate.
-
-The main background in the measurement of DVCS is coherent $\pi^{0}$ 
+The main background in the measurement of DVCS is incoherent $\pi^{0}$ 
 production. Therefore, we remove events where a $\pi^{0}$ can be identified by 
-invariant mass reconstruction of two photons.  To ensure the interaction 
-occurs at the partonic level and the DVCS handbag diagram is dominant, we 
-select events with $Q^{2}>1~[GeV^{2}/c^{2}]$. The exclusivity of the events is 
+invariant mass reconstruction of two photons. To ensure the interaction occurs 
+at the partonic level and the DVCS handbag diagram is dominant, we select 
+events with $Q^{2}>1~[GeV^{2}/c^{2}]$. The exclusivity of the events is 
 obtained by applying a set of cuts on the following kinematic variables: the 
@@
 $e'^4He'$ system, and the angle ($\theta$) between the measured photon and the 
-missing momentum of the $e'^4He'$ system. The most relevant of these cuts are 
-presented in Figure~\ref{fig:kin-cuts}, which shows 3$\sigma$ cuts except for the 
-missing energy (which appears to be too large and for which we reduced the cut 
-window to [-0.45,0.5] GeV). After these requirements, we have about 3200 events 
-left, and Figure \ref{fig:kin-coverage} presents their
+missing momentum of the $e'^4He'$ system. The cuts are presented in 
+Figure~\ref{fig:kin-cuts}, which shows 3$\sigma$ cuts except for the missing.  
+After these requirements, we have about 20k events left, and Figure 
+\ref{fig:kin-coverage} presents their
 kinematic distributions in ($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$).
@@
 \begin{figure}[tb]
-\includegraphics[width=8.9cm]{figs/coh_exc_cuts.pdf}
-\caption{Four of the six coherent DVCS exclusivity cuts. The black 
-distributions represent the coherent DVCS events candidate. The shaded 
-distributions represent the events which passed all the exclusivity cuts except 
-the quantity plotted. The vertical red lines represent the applied exclusivity 
+\includegraphics[width=8.9cm]{figs/incoh_exc_cuts_final.pdf}
+\caption{The incoherent DVCS exclusivity cuts. The black distributions 
+   represent the coherent DVCS events candidate. The shaded distributions 
+   represent the events which passed all the exclusivity cuts except the 
+   quantity plotted. The vertical red lines represent the applied exclusivity 
 cuts. The distributions from left to right and from top to bottoms are: $\Delta 
-\phi$, missing energy, missing mass squared and the cone angle ($\theta$) 
+\phi$, missing energy, missing masses squared and the cone angle ($\theta$) 
 between the measured and the calculated photons.}
@@
 \hspace{-0.45cm}
-\includegraphics[width=9.0cm]{figs/Q2_xB_t_Coh.pdf}
-\caption{Coherent DVCS event distributions for $Q^{2}$ as a function of 
-$x_{B}$ (left) and $Q^{2}$ as a function of $-t$ (right) after the 
-exclusivity cuts.}
+\includegraphics[width=9.0cm]{figs/Q2_xB_t_InCoh.pdf}
+\caption{Incoherent DVCS event distributions for $Q^{2}$ as a function of 
+$x_{B}$ (left) and $Q^{2}$ as a function of $-t$ (right) after the exclusivity 
+cuts.}
 \label{fig:kin-coverage}
@@
 
-We identified two main backgrounds to our measurement, accidental 
-coincidences and exclusive $\pi^0$ production. The accidental events have 
-particles coming from different events, and we estimate their  contribution
-to be 4.1\% of our sample. We evaluated this contribution by selecting events 
-passing all our cuts but with an electron and an helium originating from different 
-vertices. Regarding the $\pi^0$ production, it can easily be mistaken for DVCS when 
-one of the two photons of the $\pi^0$ decay is produced at low energy in the 
-laboratory frame and remains undetected. To estimate the importance of this 
-background, we developed an event generator calibrated on the experimental yield 
-of exclusive $\pi^0$ measured by our experiment. We used this generator together 
-with a GEANT3 simulation of our detection system to estimate the ratio between
-the number of $\pi^0$ events where the two photons are detected and those that 
-would be mistaken for DVCS. This ratio is then multiplied by the measured yield 
-of exclusive $\pi^0$ events to correct the DVCS data. Depending on the kinematics, we
-found contaminations of 2 to 4\%. The study of systematics errors showed that the main 
-contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
-large binning size (5.1\%) [Is that right to add it here?]. However, added quadratically, these 
-errors sum up to about 10\%, which always remain significantly smaller than the 
-statistical errors.
+%We identified two main backgrounds to our measurement, accidental coincidences 
+%and exclusive $\pi^0$ production. The accidental events have particles coming 
+%from different events, and we estimate their  contribution
+%to be 4.1\% of our sample. We evaluated this contribution by selecting events 
+%passing all our cuts but with an electron and an helium originating from 
+%different vertices. Regarding the $\pi^0$ production, it can easily be 
+%mistaken for DVCS when one of the two photons of the $\pi^0$ decay is produced 
+%at low energy in the laboratory frame and remains undetected. To estimate the 
+%importance of this background, we developed an event generator calibrated on 
+%the experimental yield of exclusive $\pi^0$ measured by our experiment. We 
+%used this generator together with a GEANT3 simulation of our detection system 
+%to estimate the ratio between
+%the number of $\pi^0$ events where the two photons are detected and those that 
+%would be mistaken for DVCS. This ratio is then multiplied by the measured 
+%yield of exclusive $\pi^0$ events to correct the DVCS data. Depending on the 
+%kinematics, we
+%found contaminations of 2 to 4\%. The study of systematics errors showed that 
+%the main contributions come from the choice of the DVCS exclusivity cuts (8\%) 
+%and the large binning size (5.1\%) [Is that right to add it here?]. However, 
+%added quadratically, these errors sum up to about 10\%, which always remain 
+%significantly smaller than the statistical errors.
 
@@
 three terms can be approximated as a finite sum of Fourier harmonics, as shown 
-for the nucleon in \cite{Belitsky:2001ns} and for the spin-zero targets in 
-\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on these calculations, the 
-beam-spin asymmetry ($A_{LU}$) of a spin-zero hadron can then be expressed as:
-\small
-\begin{equation}
-\begin{split}
-A_{LU}(\phi) =~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
- \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
-{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
-\big( 
-\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
-\label{eq:A_LU-coh}
-\end{split}
-\end{equation}
-\normalsize
-where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
-and real parts of the $^4$He CFF $\mathcal{H}_{A}$ associated with the GPD $H_A$,
-and $\phi$ is the azimuthal angle between the ($e$,$e'$) and 
-($\gamma^{*}$,$^4$He$'$) planes. The $\alpha_{i}$'s are $\phi$-dependent 
-kinematical factors that depend on the nuclear form factor ($F_{A}(t)$) and the 
-independent variables $Q^2$, $x_{B}$ and $t$. These factors are expressed as:
-\small
-\begin{eqnarray}
-   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
-    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
-   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
-C_{++}(1) cos(\phi) \right)\\
-\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
-{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
-\epsilon^2}
-\end{eqnarray}
-\normalsize
-Where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$ the $^4$He mass and 
-$\mathcal{P}_1(\phi)$ and $\mathcal {P}_2(\phi)$ the Bethe-Heitler
-propagators. The factors $c_{0,1,2}^{BH}$, $c_0^{DVCS}$, $c_{0,1}^{INT}$ and
-$s_1^{INT}$ are the Fourier coefficients of the BH, and $S{++}(1)$, $C_{++}(0)$, 
-and $C_{++}(1)$ are the Fourier harmonics in the leptonic tensor. The 
-explicit expressions of these terms can be found in \cite{Belitsky:2008bz}. 
-We see that by using the $\sin(\phi)$ and $\cos(\phi)$ contributions, it is 
-possible to extract 
-$\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ from the beam spin
-asymmetry.
+for the nucleon in \cite{Belitsky:2001ns}.
 
@@
 $Q^{2}$, $x_{B}$ and $t$. Figure \ref{fig:alu} presents $A_{LU}$ for the three
-sets of binning. The asymmetries are fitted with the form of
-equation \ref{eq:A_LU-coh}, where the real and imaginary part of the CFF
-$\mathcal{H}_{A}$ are the free parameters of the fit. Figure \ref{fig:alu90} 
-shows the $Q^2$, $x_{B}$, and $-t$-dependencies of the fitted $A_{LU}$ signals 
-at $\phi$~=~90$^{\circ}$. The $x_{B}$ and $-t$-dependencies are compared to 
+sets of binning. The asymmetries are fitted with the form of $\frac{\alpha 
+sin(\phi)}{1+ \beta cos(\phi)}$.  Figure \ref{fig:alu90} shows the $Q^2$, 
+$x_{B}$, and $-t$-dependencies of the fitted $A_{LU}$ signals at 
+$\phi$~=~90$^{\circ}$. The $x_{B}$ and $-t$-dependencies are compared to 
 theoretical calculations performed by S.~Liuti and K.~Taneja 
 \cite{simonetta_2}. Their model relies on the impulse approximation and uses 
-advanced spectral functions of nuclei. The calculations are at slightly different 
-kinematics than our data but still provide some guidance. The experimental 
-results appear to have larger asymmetries than the calculations. These 
-differences may arise from nuclear effects which are not taken into account in 
-the model, such as long-range interactions.
+advanced spectral functions of nuclei.  The calculations are at slightly 
+different kinematics than our data but still provide some guidance. The 
+experimental results appear to have larger asymmetries than the calculations.  
+These differences may arise from nuclear effects which are not taken into 
+account in the model, such as long-range interactions.
 
 \begin{figure}[tb]
-\includegraphics[width=8.9cm]{figs/coherent-ALU.pdf}
-\caption{The coherent $A_{LU}$ as a function of $\phi$. Results are presented
+\includegraphics[width=8.9cm]{figs/ALU_phi_p_Q2.pdf}
+\includegraphics[width=8.9cm]{figs/ALU_phi_p_x.pdf}
+\includegraphics[width=8.9cm]{figs/ALU_phi_p_t.pdf}
+\caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
    for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle panel), and 
-   $-t$ bins (bottom panel).  
-   The error bars represent the statistical uncertainties. The gray 
-   bands represent the systematic uncertainties, including the normalisation 
-   uncertainties. The red curves are the results of our fits with the form of 
-   equation \ref{eq:A_LU-coh}.}
+   $-t$ bins (bottom panel).  The error bars represent the statistical 
+uncertainties. The gray bands represent the systematic uncertainties, including 
+the normalisation uncertainties. The red curves are the results of our fits 
+with the form $\frac{\alpha sin(\phi)}{1+ \beta cos(\phi)}$.}
 \label{fig:alu}
@@
 \begin{figure}[tb]
-\includegraphics[width=8.9cm]{figs/coherent-ALU_90.pdf}
+\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_Q2_shortscenrario.pdf}
+\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_x_shortscenrario.pdf}
+\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_t_shortscenrario.pdf}
 \caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $-t$-dependencies (right) of
@@
 
-\begin{figure}[tb]
-\includegraphics[width=8.9cm]{figs/Coherent_CFF.pdf}
-\caption{The model-independent extraction of the imaginary (top panel) and
-real (bottom panel) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of
-$Q^{2}$ (right panel), $x_B$ (middle panel), and $t$ (left panel). The full red 
-curves are calculations based on an on-shell model from
-\cite{Vadim_priv}. The black-dashed curves are calculations from a convolution 
-model based on the VGG model for the nucleons' GPDs \cite{Guidal_priv}. The 
-blue long-dashed curve on the top-right plot is from
-an off-shell model based on \cite{GonzalezHernandez:2012jv}.}
-\label{fig:CFF_HA}
-\end{figure}
-
-We display in figure \ref{fig:CFF_HA} our extraction of the $^4$He CFF 
-$\mathcal{H}_A$, together with theoretical calculations from two models, 
-labelled {\em convolution} and {\em off-shell}. In the convolution 
-model \cite{Vadim_priv}, the nucleus is assumed to be composed of 
-non-relativistic non-interacting nucleons, where these nucleons interact 
-independently with the probe. The convolution/dual model is based on nucleon GPDs from 
-the dual parametrization \cite{Guzey:2006xi}, where the convolution/VGG uses nucleon GPDs  
-from the VGG model and is based on the double distributions ansatz 
-\cite{DD_model}. The off-shell model \cite{GonzalezHernandez:2012jv} relies on the 
-impulse approximation and uses advanced spectral functions of  
-nuclei that account for all configurations of the final nuclear system and the 
-binding effects between the nucleons.
-[These need to be renamed on the figure, it does not make sense to call differently
-models that are identical. We should also request the projections from Vadim
-model: hep-ph/0509158.]
-
-The results in Figure \ref{fig:CFF_HA} show that the extraction of the CFF
-from the beam spin asymmetry is possible without any model dependent 
-assumptions. The amplitude and the dependencies observed as a function of 
-$Q^{2}$, $x_B$, and $-t$ are in agreement 
-with the theoretical calculations. One can see a difference between the 
-precision of the extracted imaginary and real parts, which is expected from
-equation \ref{eq:A_LU-coh} because $\alpha_2$ is smaller than $\alpha_0$. 
-While these results are not precise enough to discriminate between the models,
-they are very promising for future exeperiments and demonstrate our ability
-to directly extract the CFF of the helium nucleus in a completely model
-independent way.
-
 %conclusion
-In summary, we present the first exclusive measurement of coherent DVCS 
-off $^4$He using the CLAS spectrometer supplemented  
-by a specially designed RTPC. This dataset represents a 
-unique source as the first exclusive coherent nuclear DVCS measurement which 
-can be used to directly constrain GPD models. The measured beam-spin asymmetries 
-show a signal stronger than for the proton and allow to perform a fully 
-model-independent extraction of the $^4$He CFF $\mathcal{H}_A$. The extracted 
-CFF is in a good agreement with the available models. This opens 
-many new perspectives to study the nuclear structure within the GPD framework 
-and paves the way for future, more precise measurements at JLab 12~GeV to 
-eventualy localize nuclear effects in the transverse plane.
 

### 2017-02-10 eg6-letters/coherent/dvcs_he4_prl.tex
nathans 2nd suggestions

@@
 
-The main background in the measurement of DVCS is coherent $\pi^{0}$ 
-production. Therefore, we remove events where a $\pi^{0}$ can be identified by 
-invariant mass reconstruction of two photons.  To ensure the interaction 
+%The main background in the measurement of DVCS is coherent $\pi^{0}$ 
+%production. Therefore, we remove events where a $\pi^{0}$ can be identified by 
+%invariant mass reconstruction of two photons.
+
+To ensure the interaction 
 occurs at the partonic level and the DVCS handbag diagram is dominant, we 
-select events with $Q^{2}>1~[GeV^{2}/c^{2}]$. The exclusivity of the events is 
-obtained by applying a set of cuts on the following kinematic variables: the 
+select events with $Q^{2}>1~[GeV^{2}/c^{2}]$. Exclusivity of the coherent DVCS reaction is 
+optimized by applying a set of cuts on the following kinematic variables: the 
 co-planarity angle ($\Delta \phi$), the missing energy, the missing mass 
@@
 missing energy (which appears to be too large and for which we reduced the cut 
-window to [-0.45,0.5] GeV). After these requirements, we have about 3200 events 
-left, and Figure \ref{fig:kin-coverage} presents their
-kinematic distributions in ($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$).
+window to [-0.45,0.5] GeV).  We also reject events where a $\pi^0$ is identified
+by invariant mass reconstruction of two photons.  After these requirements, we have
+about 3200 events left, and Figure \ref{fig:kin-coverage} presents their kinematic
+distributions in ($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$).
 
@@
 We identified two main backgrounds to our measurement, accidental 
-coincidences and exclusive $\pi^0$ production. The accidental events have 
-particles coming from different events, and we estimate their  contribution
+coincidences and exclusive, coherent $\pi^0$ production. The accidentals have 
+particles originating from different events, and we estimate their  contribution
 to be 4.1\% of our sample. We evaluated this contribution by selecting events 
-passing all our cuts but with an electron and an helium originating from different 
+passing all our cuts but with an electron and helium originating from different 
 vertices. Regarding the $\pi^0$ production, it can easily be mistaken for DVCS when 
-one of the two photons of the $\pi^0$ decay is produced at low energy in the 
+one of the two photons from the $\pi^0$ decay is produced at low energy in the 
 laboratory frame and remains undetected. To estimate the importance of this 
@@
    the HERMES $-A_{LU}$ (positron beam was used) inclusive measurements 
-   \cite{HERMES_BSA}, the colored curves represent theoretical calculations 
+   \cite{Airapetian}, the colored curves represent theoretical calculations 
+   %\cite{HERMES_BSA}, the colored curves represent theoretical calculations 
    from \cite{simonetta_2}.}

### 2017-02-10 eg6-letters/coherent/dvcs_he4_prl.tex
renaming the GPD models in the CFF plot and cleaning the text

@@
 non-relativistic and non-interacting nucleons, where these nucleons interact 
-independently with the probe. The convolution/dual model is based on nucleon 
+independently with the probe. The Convolution-Dual model is based on nucleon 
 GPDs from the dual parametrization \cite{Guzey:2006xi}, where the 
-convolution/VGG uses nucleon GPDs  from the VGG model and is based on the 
+Convolution-VGG uses nucleon GPDs  from the VGG model and is based on the 
 double distributions ansatz \cite{DD_model}. The off-shell model 
@@
 the final nuclear system and the binding effects between the nucleons.
-[These need to be renamed on the figure, it does not make sense to call differently
-models that are identical. We should also request the projections from Vadim
-model: hep-ph/0509158.]
 

### 2017-02-10 eg6-letters/coherent/dvcs_he4_prl.tex
Correct Author list to match previous discussions

@@
 \affiliation{\ORSAY}
-\author {R.~Dupr\'{e}} 
-\affiliation{\ANL}
-\affiliation{\ORSAY}
 \author {N.A.~Baltzell} 
@@
 \affiliation{\JLAB}
+\author {R.~Dupr\'{e}} 
+\email[corresponding author: ]{dupre@ipno.in2p3.fr}
+\affiliation{\ANL}
+\affiliation{\ORSAY}
 \author {K.~Hafidi} 
-\email[corresponding author: ]{kawtar@anl.gov}
 \affiliation{\ANL}
+\author{S.~Stepanyan}
+\affiliation{\JLAB}
 
@@
 The coherent nuclear DVCS channel, $eA \rightarrow e' A' \gamma$, is 
-experimentally difficult due to  its small cross section and the necessity to 
+difficult to measure due to its small cross section and the necessity to 
 ensure the target remains intact while emitting a hard photon.  Figure 

### 2017-02-10 eg6-letters/coherent/dvcs_he4_prl.tex
start to implement Stepan's suggestions

--- 2017-02-10 eg6-letters/coherent/dvcs_he4_prl.tex
@@
 \begin{abstract}
-We report the first fully exclusive measurement of deeply virtual Compton 
-scattering (DVCS) off a nucleus for $A>1$. The experiment used the 6 GeV 
-electron beam from Jefferson Lab projected onto a $^4$He target in the center 
-of the CEBAF Large Acceptance Spectrometer (CLAS). An additional radial time 
-projection chamber (RTPC) was used to detect the recoiling $^4$He nuclei and 
-ensure the exclusivity of the process. We measured beam spin asymmetries 
-significantly larger than that observed on proton targets and extracted,
-in a completely model independent way, the chiral even generalized parton 
-distribution (GPD) of the $^4$He nucleus. This pioneering measurement 
-leads the way toward the 3D imaging of the partonic structure of nuclei.
+We report the first fully exclusive measurement of Deeply Virtual Compton 
+Scattering (DVCS) off a nucleus for $A>1$. The experiment used the 6 GeV 
+electron beam from CEBAF machine at Jefferson Lab projected onto a $^4$He gas 
+target in the center of the CEBAF Large Acceptance Spectrometer (CLAS). A new 
+radial time projection chamber (RTPC) was used to detect the recoiling $^4$He 
+nuclei and ensure the exclusivity of the process. The measured Beam Spin 
+Asymmetries (BSA) are significantly larger than that observed on the proton in 
+the same kinematic domain. Since $^4$He is a spin zero target, we were able to 
+extract, in a completely model independent way, chiral even Generalized Parton 
+Distribution (GPD) H of $^4$He.
+
+We measured beam spin asymmetries significantly larger than that observed on 
+proton targets and extracted, in a completely model independent way, the chiral 
+even generalized parton distribution (GPD) of the $^4$He nucleus. This 
+pioneering measurement leads the way toward the 3D imaging of the partonic 
+structure of nuclei.
 \end{abstract}

### 2017-02-10 eg6-letters/coherent/dvcs_he4_prl.tex
added the suggestions from Stepan

@@
 the same kinematic domain. Since $^4$He is a spin zero target, we were able to 
-extract, in a completely model independent way, chiral even Generalized Parton 
-Distribution (GPD) H of $^4$He.
-
-We measured beam spin asymmetries significantly larger than that observed on 
-proton targets and extracted, in a completely model independent way, the chiral 
-even generalized parton distribution (GPD) of the $^4$He nucleus. This 
-pioneering measurement leads the way toward the 3D imaging of the partonic 
-structure of nuclei.
+extract, in a completely model independent way, the chiral even Generalized 
+Parton Distribution (GPD) $H_{A}$ of $^4$He. This pioneering measurement leads 
+the way toward the 3D imaging of the partonic structure of nuclei.
 \end{abstract}
@@
 
-A wealth of information on quantum chromodynamics (QCD) lies in the 
-internal structure of hadrons. In the recent past, development of the 
-generalized parton distributions (GPDs) framework has offered the possibility
-to obtain new information about the momentum and spatial degrees of 
-freedom of the quark and gluons inside hadrons 
+Rich information on Quantum Chromodynamics (QCD) lies in the internal structure 
+of hadrons. In the recent past, development of the Generalized Parton 
+Distributions (GPDs) framework has offered a possibility to obtain new 
+information about the momentum and spatial degrees of freedom of the quark and 
+gluons inside hadrons 
 \cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.
@@
 
-The main access to GPDs is through the measurement of deep virtual Compton 
-scattering (DVCS), i.e. the hard exclusive electroproduction of a real photon. 
-While other processes are known to be sensitive to GPDs, the measurement of
-DVCS is considered the cleanest probe and has been the focus of a worldwide effort 
+The most promising way to access GPDs experimentally is through the measurement 
+of deep virtual Compton scattering (DVCS), i.e.  the hard exclusive 
+electroproduction of a real photon.  While other processes are known to be 
+sensitive to GPDs, the measurement of DVCS is considered the cleanest probe and 
+has been the focus of a worldwide effort 
 \cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
 Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
-[Should we cite less publications on the topic or a review?]
 involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
-CERN. The vast majority of these measurements focused on the study of 
-proton structure and allowed extraction of the tomography of the nucleon (for details on the formalism, see 
+CERN.  The vast majority of these measurements focused on the study of proton 
+structure and allowed extraction of the tomography of the nucleon (for details 
+on the formalism, see 
 \cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
@@
 
-The coherent nuclear DVCS channel, $eA \rightarrow e' A' \gamma$, is 
-difficult to measure due to its small cross section and the necessity to 
-ensure the target remains intact while emitting a hard photon.  Figure 
-\ref{fig:diags} illustrates the hand bag diagram for coherent DVCS on $^4$He.  
-Similar to the proton case, at large virtual photon's 4-momentum square 
-$Q^2=-(k-k')^{2}$ and small squared momentum transfer $t=(p-p')^{2}$,
-the DVCS handbag diagram can be factorized into two parts 
-\cite{Freund_Collins,Ji_Osborne}. The hard part includes the photon-quark 
-interaction and is calculable with perturbative QED.  The non-perturbative 
-part is parametrized in terms of GPDs, which embed the partonic structure of 
-the hadron. The GPDs depend on the three variables $x$, $\xi$ and $t$, which are 
-indicated in Figure \ref{fig:diags} for the DVCS process. In DVCS, $\xi$ can 
-be related to the Bjorken variable $x_{B}$: $\xi\approx {{x_B}\over{2-x_B}}$, 
+The coherent nuclear DVCS reaction, $eA \rightarrow e' A' \gamma$, is difficult 
+to measure due to its small cross section and the necessity to ensure 
+exclusivity of the reaction, i.e. the target nucleus. Figure \ref{fig:diags} 
+illustrates the hand bag diagram for coherent DVCS on $^4$He.  Similar to the 
+proton case, at large virtual photon's 4-momentum square $Q^2=-(k-k')^{2}$ and 
+small squared momentum transfer $t=(p-p')^{2}$ (in terms of the electron, 
+$k(k')$, and $^4$He, $p(p')$, four-vectors), the DVCS handbag diagram can be 
+factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The hard part 
+includes the photon-quark interaction and is calculable in perturbative QCD.  
+The non-perturbative part is parametrized in terms of GPDs, which embed the 
+partonic structure of the hadron. The GPDs depend on the three variables $x$, 
+$\xi$ and $t$ as introduced in Figure \ref{fig:diags}. The parameter $\xi$
+relates to the Bjorken variable $x_{B}$: $\xi\approx {{x_B}\over{2-x_B}}$, 
 where $x_B=\frac{Q^2}{2M\nu}$ with $M$ the proton mass and  
-$\nu=E_e-E_{e^\prime}$. One can access $t$ as the squared momentum 
-transferred to the target, however $x$ cannot be experimentally 
-accessed in a DVCS reaction. Hence, we measure only complex Compton Form 
-Factors (CFF) \cite{Guidal:2013rya} defined as:
+$\nu=k^0-k^{0\prime}$, the $t$ is squared momentum transfer to the target. The 
+parameter $x$ is the quark's internal loop momentum fraction and cannot be 
+accessed experimentally. In the experiment we measure Compton Form
+Factors (CFF) \cite{Guidal:2013rya}, complex amplitudes defined as:
+
 \begin{align}
@@
 
-The main challenge in studying nuclear DVCS is ensuring the exclusivity of 
-the reaction. Until now, the only available data set of nuclear DVCS
-was from the HERMES experiment \cite{Ellinghaus:2002zw}, where exclusivity was 
-based only on kinematic cuts on the measured scattered electron and real photon. 
-That measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and 
-Xe), but the mixing of the coherent and incoherent processes could affect the
+The main challenge in studying nuclear DVCS is ensuring the exclusivity of the 
+reaction. Until now, the only available data on nuclear DVCS was from the 
+HERMES experiment \cite{Ellinghaus:2002zw}, where exclusivity was based only on 
+kinematic cuts on the measured scattered electron and real photon.  That 
+measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and Xe), 
+but the mixing of the coherent and incoherent processes could affect the
 measurement significantly \cite{Guzey:2003jh}. In this regard, direct detection 
@@
 \cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}, so we 
-built a dedicated radial time projection chamber (RTPC) for the detection of 
-the recoiling low energy nuclei in order to complete this experimental setting.  
-The $^4$He nucleus is an ideal experimental target in this regard, as it is 
-light enough to be detected in such a setting, while it
+built a specialized radial time projection chamber (RTPC) for detection of a 
+low energy recoiling light nuclei in order to ensure exclusivity of the 
+reaction. The $^4$He nucleus is an ideal experimental target in this regard, as 
+it is light enough to be detected in such a setting, while it
 is subject to significant nuclear effects \cite{JSeely} and has rather high 
@@
 
-The experiment E08-024 took place in Hall-B at JLab
-in 2009 using the nearly 100\% duty factor, longitudinally 
-polarized electron beam (83$\%$ polarization) at its full energy of 6.064 
-GeV. The data were collected over three months using a 6 atm gaseous $^4$He 
-target placed in the center of CLAS. For DVCS experiments, the CLAS baseline 
-design \cite{Mecking:2003zu} is supplemented with an inner calorimeter (IC) and 
-a solenoid. The IC extends the photon detection acceptance of CLAS, which was 
-originally from 15$^{\circ}$ to 45$^{\circ}$, to polar angles as low as 
-4$^{\circ}$. At these small angles the low-energy M\o{}ller electrons produced 
-in the target form a very high rate background that is
-suppressed by a 5 Tesla solenoid placed around the target.
+The experiment E08-024 took place in Hall-B at Jefferson Lab in 2009 using the 
+nearly 100\% duty factor, longitudinally polarized electron beam (83$\%$ 
+polarization) at energy of 6.064 GeV. The data were collected over 40 days 
+using a 6 atm gaseous $^4$He target placed in the center of CLAS. For DVCS 
+experiments, the CLAS baseline design \cite{Mecking:2003zu} is supplemented 
+with an inner calorimeter (IC) and a solenoid. The IC extends the photon 
+detection acceptance of CLAS to polar angles as low as 4$^{\circ}$. The 
+low-energy M\o{}ller electrons produced in the target form a very high rate 
+background that is suppressed by a 5 Tesla solenoid placed around the target.
 
-Because the coherent DVCS cross section is peaked at low $-t$, the recoil 
-$^4$He nuclei produced in DVCS have a low average momentum around 300 
-MeV/c. CLAS cannot detect such low energy $\alpha$ particles, 
-so in order to ensure the exclusivity of the measurement, we built a small and 
-light RTPC to complement CLAS. Figure~\ref{fig:RTPC} presents the design of 
-this RTPC and the $^4$He gaseous target in its center. The detector was 
-calibrated specifically for the detection of
-$^4$He nuclei based on elastic scattering with a 1.2~GeV electron beam.
+In our kinematics, the recoil 4He nuclei produced in DVCS have a low average 
+momentum around 300 MeV/c. CLAS cannot detect such low energy $\alpha$ 
+particles, so in order to ensure the exclusivity of the measurement, we built a 
+small and light RTPC to complement CLAS. In Figure~\ref{fig:RTPC} a picture of 
+RTPC installed in the experimental hall, and the rendering showing detector 
+components and the $^4$He detection concept are presented. The $^4$He gaseous 
+target, a $25$ cm long, $27~\mu$m wall Kapton straw, in the center was part of 
+the RTPC assembly. The detector was calibrated specifically for the detection 
+of $^4$He nuclei using elastic scattering with a 1.2~GeV electron beam.
 
@@
 electron, one $^4$He, and at least one photon are detected in the final state.
-Electrons are identified by using fiducial cuts and requiring appropriate
-signals in all the sub-detectors of the baseline CLAS (drift chambers, 
-Cherenkov counters, electromagnetic calorimeter, and time of flight 
-scintillators). The $^4$He tracks are identified with fiducial, 
-timing and track quality cuts in the RTPC detector. In addition,
-we apply a vertex matching cut to ensure the electron and helium
+Electrons are identified using measured momentum, time and energy in fiducial 
+volume of CLAS drift chambers, Cerenkov counters, scintillator counters, and 
+electromagnetic calorimeters. The $^4$He are identified in the RTPC using time, 
+track quality, and energy loss cut for tracks in the fiducial region. In 
+addition, we apply a vertex matching cut to ensure that the electron and helium
 nucleus originate from the same position. The photons are detected in either
-the IC or the CLAS electromagnetic calorimeter.  Note that even though the 
-DVCS reaction has only one real photon in the final state, 
-events with more than one good photon are not discarded at this stage. This is 
-motivated by the fact that, while soft photons are likely to be produced in random 
-coincidence, they cannot be mistaken for the large energy DVCS photons ($>2$ GeV).
+the IC or the CLAS electromagnetic calorimeter. Note that even though the DVCS 
+reaction has only one real photon in the final state, events with more than one 
+good photon are not discarded at this stage. This is motivated by the fact 
+that, while soft photons are likely to be produced in random coincidence, they 
+cannot be mistaken for the large energy DVCS photons ($>2$ GeV).
 The most energetic photon is always considered as the DVCS photon candidate.
@@
 
-To ensure the interaction 
-occurs at the partonic level and the DVCS handbag diagram is dominant, we 
-select events with $Q^{2}>1~[GeV^{2}/c^{2}]$. Exclusivity of the coherent DVCS reaction is 
-optimized by applying a set of cuts on the following kinematic variables: the 
-co-planarity angle ($\Delta \phi$), the missing energy, the missing mass 
-squared, the missing transverse momentum, the missing mass squared of the 
-$e'^4He'$ system, and the angle ($\theta$) between the measured photon and the 
-missing momentum of the $e'^4He'$ system. The most relevant of these cuts are 
-presented in Figure~\ref{fig:kin-cuts}, which shows 3$\sigma$ cuts except for the 
-missing energy (which appears to be too large and for which we reduced the cut 
-window to [-0.45,0.5] GeV).  We also reject events where a $\pi^0$ is identified
-by invariant mass reconstruction of two photons.  After these requirements, we have
-about 3200 events left, and Figure \ref{fig:kin-coverage} presents their kinematic
-distributions in ($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$).
+To ensure the interaction occurs at the partonic level and the DVCS handbag 
+diagram is dominant, we select events with $Q^{2}>1~[GeV^{2}/c^{2}]$.  
+Exclusivity of the coherent DVCS reaction is optimized by applying a set of 
+cuts on the following kinematic variables: the co-planarity angle ($\Delta 
+\phi$), \textit{i.e.}, the angle between the ($\gamma,\gamma^*$) and 
+($\gamma^*,^4He'$) planes, the missing energy, the missing mass squared, the 
+missing transverse momentum of the $e'^4He'\gamma$ system, the missing mass 
+squared of the $e'^4He'$ system, and the angle ($\theta$) between the measured 
+photon and the missing momentum of the $e'^4He'$ system. The most relevant of 
+these cuts are presented in Figure~\ref{fig:kin-cuts}, which shows 3$\sigma$ 
+cuts except for the missing energy (which appears to be too large and for which 
+we reduced the cut window to [-0.45,0.5] GeV).  We also reject events where a 
+$\pi^0$ is identified by invariant mass reconstruction of two photons.  After 
+these requirements, we have about 3200 DVCS events left, and Figure 
+\ref{fig:kin-coverage} presents their kinematic distributions in 
+($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$).
 
@@
 
-We identified two main backgrounds to our measurement, accidental 
-coincidences and exclusive, coherent $\pi^0$ production. The accidentals have 
-particles originating from different events, and we estimate their  contribution
-to be 4.1\% of our sample. We evaluated this contribution by selecting events 
-passing all our cuts but with an electron and helium originating from different 
-vertices. Regarding the $\pi^0$ production, it can easily be mistaken for DVCS when 
-one of the two photons from the $\pi^0$ decay is produced at low energy in the 
-laboratory frame and remains undetected. To estimate the importance of this 
-background, we developed an event generator calibrated on the experimental yield 
-of exclusive $\pi^0$ measured by our experiment. We used this generator together 
-with a GEANT3 simulation of our detection system to estimate the ratio between
-the number of $\pi^0$ events where the two photons are detected and those that 
-would be mistaken for DVCS. This ratio is then multiplied by the measured yield 
-of exclusive $\pi^0$ events to correct the DVCS data. Depending on the kinematics, we
-found contaminations of 2 to 4\%. The study of systematics errors showed that the main 
-contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
-large binning size (5.1\%) [Is that right to add it here?]. However, added quadratically, these 
-errors sum up to about 10\%, which always remain significantly smaller than the 
-statistical errors.
-
 %asymmetries
-Several observables related to DVCS are of interest, but in this work we focus only 
-on the beam-spin asymmetry. This  observable is measurable using a polarized 
-lepton beam on an unpolarized target (U). It is convenient to use the beam-spin 
-asymmetry because most of the experimental normalization and acceptance issues 
-cancel out in the asymmetry ratio. It is defined in terms of the cross sections 
-as:
+In this work, the physics observable extracted using coherent DVCS events is
+the Beam Spin Asymmetry (BSA). The BSA on unpolarized target (U), $A_{LU}$, is 
+measurable by the difference of cross sections of the reaction at opposite beam 
+helicities normalized to the total cross section. It is written as:
   \begin{equation}
@@
 of DVCS events detected with positive and negative electron helicity with 
-respect to the beam direction.
+respect to the beam direction. In this ratio most of uncertainties of the 
+experimental normalization and in detector efficiencies will cancel out.
 
@@
 equation \ref{eq:A_LU-coh}, where the real and imaginary part of the CFF
-$\mathcal{H}_{A}$ are the free parameters of the fit. Figure \ref{fig:alu90} 
-shows the $Q^2$, $x_{B}$, and $-t$-dependencies of the fitted $A_{LU}$ signals 
-at $\phi$~=~90$^{\circ}$. The $x_{B}$ and $-t$-dependencies are compared to 
-theoretical calculations performed by S.~Liuti and K.~Taneja 
-\cite{simonetta_2}. Their model relies on the impulse approximation and uses 
-advanced spectral functions of nuclei. The calculations are at slightly different 
-kinematics than our data but still provide some guidance. The experimental 
-results appear to have larger asymmetries than the calculations. These 
-differences may arise from nuclear effects which are not taken into account in 
-the model, such as long-range interactions.
+$\mathcal{H}_{A}$ are the free parameters of the fit. We identified two main 
+backgrounds to our measurement, accidental coincidences and exclusive, coherent 
+$\pi^0$ production. The accidentals have particles originating from different 
+events, and we estimate their  contribution to be 4.1\% of our sample. We 
+evaluated this contribution by selecting events passing all our cuts but with 
+an electron and helium originating from different vertices. Regarding the 
+$\pi^0$ production, it can easily be mistaken for DVCS when one of the two 
+photons from the $\pi^0$ decay is produced at low energy in the laboratory 
+frame and remains undetected. To estimate the importance of this background, we 
+developed an event generator calibrated on the experimental yield of exclusive 
+$\pi^0$ measured by our experiment. We used this generator together with a 
+GEANT3 simulation of our detector to estimate the ratio between the number of 
+$\pi^0$ events where the two photons are detected and those that is 
+misidentified as DVCS events. This ratio is then multiplied by the measured 
+yield of exclusive $\pi^0$ events to correct the DVCS data. Depending on the 
+kinematics, we found contaminations of 2 to 4\%. The study of systematics 
+uncertainties showed that the main contributions come from the choice of the 
+DVCS exclusivity cuts (8\%) and the large binning size (5.1\%). However, added 
+quadratically,the total systematic uncertainty is about 10\%, which is 
+significantly smaller than statistical uncertainties in all kinematical bins. 
+Figure \ref{fig:alu90} shows the $Q^2$, $x_{B}$, and $-t$-dependencies of the 
+fitted $A_{LU}$ signals at $\phi$~=~90$^{\circ}$. The $x_{B}$ and 
+$-t$-dependencies are compared to theoretical calculations performed by 
+S.~Liuti and K.~Taneja \cite{simonetta_2}. Their model relies on the impulse 
+approximation and uses advanced spectral functions of nuclei. The calculations 
+are at slightly different kinematics than our data but still provide some 
+guidance. The experimental results appear to have larger asymmetries than the 
+calculations. These differences may arise from nuclear effects which are not 
+taken into account in the model, such as long-range interactions.
 

### 2017-02-13 eg6-letters/NIM/EG6_RTPC_NIM.tex
cleanup noise figures
donot use vtl, use L

@@
 
-(To be written by Nathan)
-
-\begin{figure}[tb]
-\hspace{-0.4cm}
-\includegraphics[scale=0.27]{fig/noisy_pad_before_rejection.png}
-\caption{}
-\label{fig:noisy_pad_before_rejection}
+\begin{figure}[tb]\centering
+\includegraphics[scale=0.27]{fig/noisy_pad_before_rejection2.png}
+\includegraphics[scale=0.27]{fig/noisy_pad_after_rejection2.png}
+\caption{The ADC vs.
+TDC spectrum for an example noisy channel before (top) and after (bottom) noise rejection algorithms.
+Only hits associated with tracks are included, and the selection of events and tracks is the same in both plots.}
+\label{fig:noise}
 \end{figure}
 
-\begin{figure}[tb]
-\hspace{-0.4cm}
-\includegraphics[scale=0.27]{fig/noisy_pad_after_rejection.png}
-\caption{}
-\label{fig:noisy_pad_after_rejection}
-\end{figure}
+%\begin{figure}[tb]
+%\hspace{-0.4cm}
+%\includegraphics[scale=0.27]{fig/noisy_pad_after_rejection.png}
+%\caption{}
+%\label{fig:noisy_pad_after_rejection}
+%\end{figure}
 
@@
 \begin{equation}
- \left\langle \frac{dE}{dX} \right\rangle= \frac{\sum\limits_{i} \frac{ADC_{i}}{Gi}}{vtl}
+ \left\langle \frac{dE}{dX} \right\rangle= \frac{\sum\limits_{i} \frac{ADC_{i}}{G_i}}{L}
 \end{equation}
-Where the sum runs over all the hits of the track and $G_{i}$ is the gain of 
-the associated pad. The $vtl$ is the visible track length in the active drift 
+Where the sum runs over all the hits of the track, $G_{i}$ is the gain of 
+the associated pad, and $L$ is the visible track length in the active drift 
 volume.

### 2017-02-13 eg6-letters/NIM/EG6_RTPC_NIM.tex
add noise text, change all $He$ to He

@@
 RTPC. For the channels of interest in CLAS-EG6 experiment, the recoiled 
-$^{4}He$ nuclei have momentum per charge around 150 MeV/c. The detection of 
+$^{4}$He nuclei have momentum per charge around 150 MeV/c. The detection of 
 these low-energy nuclei was the primary motivation for designing this detector.
@@
 experimental considerations. At 6 GeV incident electron beam energy, the recoil 
-$^{4}He$ nuclei, from the coherent DVCS channel, have an average momentum (per 
+$^{4}$He nuclei, from the coherent DVCS channel, have an average momentum (per 
 charge) around 125 MeV/c, while the "standard" CLAS detects charged particles 
@@
    \item The first gas gap extends from 3 mm to 20 mm radial distances. It is 
-      filled with $^{4}He$ gas at 1~atm. During run, this region is swarmed by 
+      filled with $^{4}$He gas at 1~atm. During run, this region is swarmed by 
       M\o ller electrons induced by the beam, such that filling this region 
-      with a light gas like $^{4}He$ minimizes secondary interactions. This 
+      with a light gas like $^{4}$He minimizes secondary interactions. This 
       region is surrounded by a 4 $\mu$m thick window made of aluminized Mylar 
@@
 We can measure the drift speed using the tracks detected in the RTPC, in figure 
-\ref{fig:RTPC_signals} we represent a typical $^{4}He$ track (in green). After 
+\ref{fig:RTPC_signals} we represent a typical $^{4}$He track (in green). After 
 it causes ionization in the drift region, the released electrons (in black) 
@@
 \includegraphics[scale=0.35]{fig/RTPC_2.png}
-\caption[]{A schematic drawing of a $^{4}He$ track (in green) traversing the 
+\caption[]{A schematic drawing of a $^{4}$He track (in green) traversing the 
 drift region, with the drift paths followed by the electrons (in black). } 
@@
 electron beam (1.20 and 1.27 GeV) to enhance the cross section of the elastic 
-process ($e ^{4}He \rightarrow e ^{4}He$). In this process the knowledge of the 
+process ($e^{4}$He$\rightarrow e^{4}$He). In this process the knowledge of the 
 electron kinematic gives us the helium nuclei kinematic and therefore allow us 
@@
 \subsection{Noise Rejection}
+Two different characteristic noise signatures were identified and removed during track reconstruction.
+
+The first was an oscillatory noise located early in the readout time window in many channels, shown in the top panel of Figure~\ref{fig:noise}.
+The amplitude of the noise is not dissimilar to those of real tracks.
+About N\% of the channels exhibit this noise signature.
+Due to its unique time-energy correlation for a given channel, the noise could be removed on an event by event and channel by channel basis, without any loss of good signals and the result is illustrated in the bottom panel of Figure~\ref{fig:noise}.
 
@@
 
-For the energy deposit, $\frac{dE}{dx}$ is calculated in this way:
+For energy deposition, the mean $\frac{dE}{dx}$ is calculated as
 \begin{equation}
- \left\langle \frac{dE}{dX} \right\rangle= \frac{\sum\limits_{i} \frac{ADC_{i}}{G_i}}{L}
+ \left\langle \frac{dE}{dX} \right\rangle= \frac{\sum\limits_{i} \frac{ADC_{i}}{G_i}}{L},
 \end{equation}
-Where the sum runs over all the hits of the track, $G_{i}$ is the gain of 
+where the sum runs over all the hits of the track, $G_{i}$ is the gain of 
 the associated pad, and $L$ is the visible track length in the active drift 

### 2017-02-13 eg6-letters/coherent/dvcs_he4_prl.tex
update the paper with the remaining suggestions from Stepan

@@
   A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
-                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
+                {d^{5}\sigma^{+} + d^{5}\sigma^{-}},
     \label{BSA_equation}
@@
 \begin{equation}
-A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} }.
+A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} },
 \end{equation}
@@
 
-To interpret DVCS, one has to keep in mind that this reaction is 
-indistinguishable from the Bethe-Heitler (BH) process, where the final photon 
-is emitted either from the incoming or the outgoing leptons. At leading twist 
-and leading order, the deeply virtual photon production cross section is 
-composed of BH, DVCS, and interference terms. The amplitudes of the 
-three terms can be approximated as a finite sum of Fourier harmonics, as shown 
-for the nucleon in \cite{Belitsky:2001ns} and for the spin-zero targets in 
-\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on these calculations, the 
-beam-spin asymmetry ($A_{LU}$) of a spin-zero hadron can then be expressed as:
+The DVCS reaction is experimentally indistinguishable from the well-known 
+Bethe-Heitler (BH) process, where the final photon is emitted either from the 
+incoming or the outgoing leptons. At leading twist and leading order, the 
+deeply virtual photon production cross section is composed of BH, DVCS, and 
+interference terms. While the BH is not sensitive to GPDs and does not carry 
+information about the partonic structure of the hadronic target, its 
+interference with the DVCS reaction is sensitive to GPDs enhancing the DVCS 
+small cross section at the kinematical regions explored at Jefferson Lab. The 
+amplitudes of the three terms can be approximated as a finite sum of Fourier 
+harmonics, as shown for the nucleon in \cite{Belitsky:2001ns} and for the 
+spin-zero targets in \cite{Kirchner:2003wt,Belitsky:2008bz}. Based on these 
+approximations, the beam-spin asymmetry ($A_{LU}$) of a spin-zero hadron can 
+then be expressed as:
 \small
@@
 {\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
-\big( 
-\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
+\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)},
 \label{eq:A_LU-coh}
@@
 where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
-and real parts of the $^4$He CFF $\mathcal{H}_{A}$ associated with the GPD $H_A$,
-and $\phi$ is the azimuthal angle between the ($e$,$e'$) and 
-($\gamma^{*}$,$^4$He$'$) planes. The $\alpha_{i}$'s are $\phi$-dependent 
-kinematical factors that depend on the nuclear form factor ($F_{A}(t)$) and the 
-independent variables $Q^2$, $x_{B}$ and $t$. These factors are expressed as:
+and real parts of the $^4$He CFF $\mathcal{H}_{A}$ that depends on the GPD 
+$H_A$. In Eq.~\ref{eq:A_LU-coh}, $\phi$ is the azimuthal angle between the 
+($e$,$e'$) and ($\gamma^{*}$,$^4$He$'$) planes. The $\alpha_i$’s are kinematic 
+factors that depend on azimuthal angle $\phi$, the nuclear form factor 
+$F_A(t)$, $Q^2$, and $x_B$. These factors are expressed as:
 \small
 \begin{eqnarray}
-   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
-    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
-   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
-C_{++}(1) cos(\phi) \right)\\
+   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi),\\
+    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} 
+   \cos(2\phi),\\ \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( 
+C_{++}(0) +  C_{++}(1) cos(\phi) \right),\\
 \alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
 {\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
-\epsilon^2}
+\epsilon^2},
 \end{eqnarray}
 \normalsize
-Where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$ the $^4$He mass and 
-$\mathcal{P}_1(\phi)$ and $\mathcal {P}_2(\phi)$ the Bethe-Heitler
-propagators. The factors $c_{0,1,2}^{BH}$, $c_0^{DVCS}$, $c_{0,1}^{INT}$ and
-$s_1^{INT}$ are the Fourier coefficients of the BH, and $S{++}(1)$, $C_{++}(0)$, 
-and $C_{++}(1)$ are the Fourier harmonics in the leptonic tensor. The 
-explicit expressions of these terms can be found in \cite{Belitsky:2008bz}. 
-We see that by using the $\sin(\phi)$ and $\cos(\phi)$ contributions, it is 
-possible to extract 
-$\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ from the beam spin
+where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$($M_{N}$) is the $^4$He 
+(nucleon) mass, $\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$ and 
+$y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, $\mathcal{P}_1(\phi)$ and $\mathcal 
+{P}_2(\phi)$ are the Bethe-Heitler propagators. The factors $c_{0,1,2}^{BH}$, 
+$c_0^{DVCS}$, $c_{0,1}^{INT}$ and $s_1^{INT}$ are the Fourier coefficients of 
+the BH, and $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics 
+in the leptonic tensor.  The explicit expressions of these terms can be found 
+in \cite{Belitsky:2008bz}.  We see that by using the $\sin(\phi)$ and 
+$\cos(\phi)$ contributions, it is possible to extract $\Im m(\mathcal{H}_{A})$ 
+and $\Re e(\mathcal{H}_{A})$ from the beam spin
 asymmetry.
 
-Due to limited statistics, we only bin  our data two-dimensionally 
- in the azimuthal angle ($\phi$) and one of the kinemtical variables 
-$Q^{2}$, $x_{B}$ and $t$. Figure \ref{fig:alu} presents $A_{LU}$ for the three
-sets of binning. The asymmetries are fitted with the form of
-equation \ref{eq:A_LU-coh}, where the real and imaginary part of the CFF
-$\mathcal{H}_{A}$ are the free parameters of the fit. We identified two main 
-backgrounds to our measurement, accidental coincidences and exclusive, coherent 
-$\pi^0$ production. The accidentals have particles originating from different 
-events, and we estimate their  contribution to be 4.1\% of our sample. We 
-evaluated this contribution by selecting events passing all our cuts but with 
-an electron and helium originating from different vertices. Regarding the 
-$\pi^0$ production, it can easily be mistaken for DVCS when one of the two 
-photons from the $\pi^0$ decay is produced at low energy in the laboratory 
-frame and remains undetected. To estimate the importance of this background, we 
-developed an event generator calibrated on the experimental yield of exclusive 
-$\pi^0$ measured by our experiment. We used this generator together with a 
-GEANT3 simulation of our detector to estimate the ratio between the number of 
-$\pi^0$ events where the two photons are detected and those that is 
-misidentified as DVCS events. This ratio is then multiplied by the measured 
-yield of exclusive $\pi^0$ events to correct the DVCS data. Depending on the 
-kinematics, we found contaminations of 2 to 4\%. The study of systematics 
-uncertainties showed that the main contributions come from the choice of the 
-DVCS exclusivity cuts (8\%) and the large binning size (5.1\%). However, added 
-quadratically,the total systematic uncertainty is about 10\%, which is 
-significantly smaller than statistical uncertainties in all kinematical bins. 
-Figure \ref{fig:alu90} shows the $Q^2$, $x_{B}$, and $-t$-dependencies of the 
-fitted $A_{LU}$ signals at $\phi$~=~90$^{\circ}$. The $x_{B}$ and 
+In this work the azimuthal dependence of the BSA, $A_{LU}$, has been studied 
+for a wide range of kinematics. We identified two main backgrounds to our 
+measurement, accidental coincidences and exclusive coherent $\pi^0$ production.  
+The accidentals have particles originating from different events, and we 
+estimate their  contribution to be 4.1\% of our sample. We evaluated this 
+contribution by selecting events passing all our cuts but with an electron and 
+helium originating from different vertices. Regarding the $\pi^0$ production, 
+it can easily be mistaken for DVCS when one of the two photons from the $\pi^0$ 
+decay is produced at low energy in the laboratory frame and remains undetected.  
+To estimate the importance of this background, we developed an event generator 
+calibrated on the experimental yield of exclusive $\pi^0$ measured by our 
+experiment. We used this generator together with a GEANT3 simulation of our 
+detector to estimate the ratio between the number of $\pi^0$ events where the 
+two photons are detected and those that is misidentified as DVCS events. This 
+ratio is then multiplied by the measured yield of exclusive $\pi^0$ events to 
+correct the DVCS data.  Depending on the kinematics, we found contaminations of 
+2 to 4\%. The study of systematics uncertainties showed that the main 
+contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
+large binning size (5.1\%). However, added quadratically,the total systematic 
+uncertainty is about 10\%, which is significantly smaller than statistical 
+uncertainties in all kinematical bins.
+
+Due to limited statistics, dependence on the kinematical variables $Q^2$, 
+$x_B$, and $t$ has been studied separately. In Figure \ref{fig:alu}, $A_{LU}$ 
+for the three sets of binning is presented. The curves on the plots are fits 
+with the function presented in Eq.~\ref{eq:A_LU-coh}, where the real and 
+imaginary part of the CFF $\mathcal{H}_{A}$ are the free parameters of the fit. 
+In Figure \ref{fig:alu90} the $Q^2$, $x_{B}$, and $-t$-dependencies of the 
+fitted $A_{LU}$ signals at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and 
 $-t$-dependencies are compared to theoretical calculations performed by 
-S.~Liuti and K.~Taneja \cite{simonetta_2}. Their model relies on the impulse 
+S.~Liuti and K.~Taneja \cite{simonetta_2}. The model relies on the impulse 
 approximation and uses advanced spectral functions of nuclei. The calculations 
@@
 guidance. The experimental results appear to have larger asymmetries than the 
-calculations. These differences may arise from nuclear effects which are not 
-taken into account in the model, such as long-range interactions.
+calculations. These differences may arise from nuclear effects, such as 
+long-rage interactions, which are not taken into account in the model.
 
@@
 
-We display in figure \ref{fig:CFF_HA} our extraction of the $^4$He CFF 
-$\mathcal{H}_A$, together with theoretical calculations from two models, 
-labelled {\em convolution} and {\em off-shell}. In the convolution 
-model \cite{Vadim_priv}, the nucleus is assumed to be composed of 
-non-relativistic and non-interacting nucleons, where these nucleons interact 
-independently with the probe. The Convolution-Dual model is based on nucleon 
-GPDs from the dual parametrization \cite{Guzey:2006xi}, where the 
-Convolution-VGG uses nucleon GPDs  from the VGG model and is based on the 
-double distributions ansatz \cite{DD_model}. The off-shell model 
-\cite{GonzalezHernandez:2012jv} relies on the impulse approximation and uses 
-advanced spectral functions of  nuclei that account for all configurations of 
-the final nuclear system and the binding effects between the nucleons.
+The $Q^2$, $X_B$, and $t$ dependencies of the $^4$He CFF $\mathcal{H}_A$ 
+extracted from the fit to the azimuthal dependence of $A_{LU}$ are shown in 
+Figure \ref{fig:CFF_HA}. Curves on the graphs are model calculations, labelled 
+{\it convolution} and {\it off-shell}. In the convolution model 
+\cite{Vadim_priv}, the nucleus is assumed to be composed of non-relativistic 
+and non-interacting nucleons, where these nucleons interact independently with 
+the probe. The Convolution-Dual model is based on nucleon GPDs from the dual 
+parametrization \cite{Guzey:2006xi}, where the Convolution-VGG uses nucleon 
+GPDs  from the VGG model and is based on the double distributions ansatz 
+\cite{DD_model}. The off-shell model \cite{GonzalezHernandez:2012jv} relies on 
+the impulse approximation and uses advanced spectral functions of  nuclei that 
+account for all configurations of the final nuclear system and the binding 
+effects between the nucleons.
 
@@
 precision of the extracted imaginary and real parts, which is expected from
-equation \ref{eq:A_LU-coh} because $\alpha_2$ is smaller than $\alpha_0$. 
-While these results are not precise enough to discriminate between the models,
-they are very promising for future experiments and demonstrate our ability
-to directly extract the CFF of the helium nucleus in a completely model
+Eq.~\ref{eq:A_LU-coh} because $\alpha_2$ is smaller than $\alpha_0$. While the 
+accuracy of our results does not allow to discriminate between the models, they 
+demonstrate possibility of extraction of the CFF of spin 0 target in a model 
 independent way.
@@
 %conclusion
-In summary, we present the first exclusive measurement of coherent DVCS 
-off $^4$He using the CLAS spectrometer supplemented  
-by a specially designed RTPC. This dataset represents a 
-unique source as the first exclusive coherent nuclear DVCS measurement which 
-can be used to directly constrain GPD models. The measured beam-spin asymmetries 
-show a signal stronger than for the proton and allow to perform a fully 
-model-independent extraction of the $^4$He CFF $\mathcal{H}_A$. The extracted 
-CFF is in a good agreement with the available models. This opens 
-many new perspectives to study the nuclear structure within the GPD framework 
-and paves the way for future, more precise measurements at JLab 12~GeV to 
-eventualy localize nuclear effects in the transverse plane.
+In summary, we presented the first exclusive measurement of coherent DVCS off 
+$^4$He using the CLAS spectrometer supplemented with a Radial Time Projection 
+Chamber and a high pressure gaseous target. This setup allowed detection of the 
+low energy $^4$He recoils in order to ensure the DVCS exclusivity.
+The azimuthal dependence of the measured beam spin asymmetry ($A_{LU}$) has 
+been used to extract, in model independent way, the real and the imaginary 
+parts of the $^4$He CFF, $\mathcal{H}_A$. The extracted CFF is in a good 
+agreement with predictions of the available models. This first fully exclusive 
+experiment opens new perspectives for studying the nuclear structure with the 
+GPD framework and paves a way for future measurements at JLAB using 12 GeV 
+CEBAF and upgraded equipment.
 

### 2017-02-13 eg6-letters/coherent/dvcs_he4_prl.tex
more writting corrections

@@
 target in the center of the CEBAF Large Acceptance Spectrometer (CLAS). A new 
-radial time projection chamber (RTPC) was used to detect the recoiling $^4$He 
+Radial Time Projection Chamber (RTPC) was used to detect the recoiling $^4$He
 nuclei and ensure the exclusivity of the process. The measured Beam Spin 
@@
 The most promising way to access GPDs experimentally is through the measurement 
-of deep virtual Compton scattering (DVCS), i.e.  the hard exclusive 
+of Deep Virtual Compton Scattering (DVCS), i.e.  the hard exclusive 
 electroproduction of a real photon.  While other processes are known to be 

### 2017-02-13 eg6-letters/coherent/dvcs_he4_prl.tex
minor edit
added the two columns style

@@
 \RequirePackage{lineno}
-\documentclass[preprint,nofootinbib,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
+%\documentclass[preprint,nofootinbib,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
+\documentclass[twocolumn,nofootinbib,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
 \usepackage{graphicx}
@@
 
-In our kinematics, the recoil 4He nuclei produced in DVCS have a low average 
+In our kinematics, the recoil $^4$He nuclei produced in DVCS have a low average 
 momentum around 300 MeV/c. CLAS cannot detect such low energy $\alpha$ 

### 2017-02-13 eg6-letters/NIM/EG6_RTPC_NIM.tex
add noise description

@@
 as detecting real photons. Figure~\ref{fig:CLAS} shows a three dimensional 
-representation of the baseline CLAS spectrometer, here is a list of the main elements
-depicted in the figure:
+representation of the baseline CLAS spectrometer:
 \begin{itemize}
@@
       correlation shown in figure~\ref{fig:1st_pass_delta_phi}. This $\Delta 
-      \phi$ change with TDC shows the drift in $phi$ of the electrons due to 
+      \phi$ change with TDC shows the azimuthal drift of the electrons due to 
       the Lorentz angle.
@@
 \subsection{Noise Rejection}
-Two different characteristic noise signatures were identified and removed during track reconstruction.
+Two different noise signatures were identified in the raw data and removed in software prior to track reconstruction.
 
-The first was an oscillatory noise located early in the readout time window in many channels, shown in the top panel of Figure~\ref{fig:noise}.
-The amplitude of the noise is not dissimilar to those of real tracks.
-About N\% of the channels exhibit this noise signature.
-Due to its unique time-energy correlation for a given channel, the noise could be removed on an event by event and channel by channel basis, without any loss of good signals and the result is illustrated in the bottom panel of Figure~\ref{fig:noise}.
+The first is a transient oscillatory noise located early in the readout time window, shown in the top panel of Figure~\ref{fig:noise} for a particularly noisy channel.
+Its amplitude is not dissimilar to those of real tracks, and about 18\% of the readout channels exhibit large contributions from this noise characteristic.
+Due to its unique time-energy correlation for the given channels, the noise could be removed on an event by event and channel by channel basis without significant loss of good signals, and the result is illustrated in the bottom panel of Figure~\ref{fig:noise}.
+
+The second is a coherent noise affecting about 25\% of the pramplifiers, where the signature is simultaneous hits in most of the 16 channels in a preamp group.
+This noise signature is also transient.
+An event-based technique to identify and remove it was developed based on counting simultaneous hits in preamp group, and, if sufficiently large, perform a dynamic pedestal subtraction based on the average ADC of the channels' neighbors within the preamp group.
+
+The source of these noises was not determined, but rejection techniques allowed to reconstruct 10\% more good tracks and recover 70 channels that were previously ignored due to high noise levels.
 

### 2017-02-13 eg6-letters/NIM/EG6_RTPC_NIM.tex
noise cleanup

@@
 \subsection{Noise Rejection}
-Two different noise signatures were identified in the raw data and removed in software prior to track reconstruction.
+Two independent noise signatures were identified in the raw data and removed in software prior to track reconstruction.  Both are transient and isolated to a subset of the readout channels.
 
-The first is a transient oscillatory noise located early in the readout time window, shown in the top panel of Figure~\ref{fig:noise} for a particularly noisy channel.
+The first is an oscillatory noise located early in the readout time window, shown in the top panel of Figure~\ref{fig:noise} for a particularly noisy channel.
 Its amplitude is not dissimilar to those of real tracks, and about 18\% of the readout channels exhibit large contributions from this noise characteristic.
@@
 The second is a coherent noise affecting about 25\% of the pramplifiers, where the signature is simultaneous hits in most of the 16 channels in a preamp group.
-This noise signature is also transient.
 An event-based technique to identify and remove it was developed based on counting simultaneous hits in preamp group, and, if sufficiently large, perform a dynamic pedestal subtraction based on the average ADC of the channels' neighbors within the preamp group.
 
-The source of these noises was not determined, but rejection techniques allowed to reconstruct 10\% more good tracks and recover 70 channels that were previously ignored due to high noise levels.
+The sources of these effects were not determined, but rejection techniques allowed to reconstruct 10\% more good tracks with no significant loss and recover 70 channels that were previously ignored due to high noise levels.
 

### 2017-02-13 eg6-letters/NIM/EG6_RTPC_NIM.tex
abstract/introduction updates

@@
 A new Radial Time Projection Chamber (RTPC) was developed at Jefferson 
-laboratory (JLab) to track low-energy nuclear recoils for the purpose of 
-measuring nuclear exclusive channels, such as, coherent Deeply Virtual Compton 
-Scattering (DVCS) and coherent production of mesons on $^4$He. In such 
-processes, $^4$He nucleus remains intact and recoils as a whole in the final 
+Laboratory (JLab) to track low-energy nuclear recoils for the purpose of 
+measuring exclusive nuclear channels, such as coherent Deeply Virtual Compton 
+Scattering (DVCS) and coherent meson production on $^4$He. In such 
+processes, the $^4$He nucleus remains intact and recoils as a whole in the final 
 state. The CEBAF Large Acceptance Spectrometer (CLAS) at JLab has been used for 
 similar studies on proton targets, however it cannot track recoils with momenta 
-less than 250 MeV/c. In 2009, we carried out measurements on $^4$He target 
-using CLAS spectrometer, which was supplemented with the RTPC during the 
-CLAS-EG6 experimental run. The detector was positioned directly around a 
-gaseous target, allowing a detection threshold as low as $~$100  MeV/c for 
-$^4$He. This article discuses the RTPC design, work principle, calibration 
-methods and performances.
+less than 250 MeV/c.
+In 2009, we carried out measurements using the CLAS spectrometer supplemented by the RTPC positioned directly around a gaseous $^4$He target, allowing a detection threshold as low as $~$100  MeV/c for
+$^4$He. This article discuses the design, work principle, calibration 
+methods and performances of the RTPC.
 \end{abstract}
@@
 
-The CEBAF Large Acceptance Spectrometer (CLAS)~\cite{CLASref} is installed in 
-the Hall-B of the Thomas Jefferson National Accelerator Facility (TJNAF), 
-Newport News, Virginia, USA. The accelerator of TJNAF provides, simultaneously, 
-a high power electron beam of energy up to 6 GeV and 100$\%$ duty cycle to 
-three experimental Halls (A, B, C). The CLAS spectrometer, located in Hall-B, 
+Thomas Jefferson National Accelerator Facility (TJNAF),
+in Newport News, Virginia, USA, provides 
+high power electron beams of energy up to 6 GeV and 100$\%$ duty cycle to 
+three experimental Halls (A, B, C) simultaneously. The CLAS spectrometer, located in Hall-B, 
 is composed of several sub-detectors and two magnets. The spectrometer was 
@@
 \begin{itemize}
- \item The three regions of Drift Chambers (DC) used for the tracking of charged 
+ \item Three regions of Drift Chambers (DC) used for the tracking of charged 
     particles~\cite{DCref} (in blue on the figure).
- \item The superconducting toroidal magnet (in yellow) bends the trajectories 
+ \item Superconducting toroidal magnet (in yellow) bends the trajectories 
     of charged particles, thus allowing momentum measurement with the DC tracking information.
- \item The Cherenvkov Counters (CC) used to separate electrons from other negative 
+ \item Cherenvkov Counters (CC) used to distinguish electrons from other negative 
     particles, such as pions, at lower energies~\cite{CCref} (in pink).
- \item The Scintillation Counters (SC) used to identify hadrons by measuring their 
-    Time-Of-Flight (TOF)~\cite{TOFref} (in red).
- \item The Electromagnetic Calorimeter (EC) used to separate electrons from other negative 
+ \item Scintillation Counters (SC) used to identify hadrons by measuring their 
+    time of flight (TOF)~\cite{TOFref} (in red).
+ \item Electromagnetic Calorimeters (EC) used to distinguish electrons from other negative 
     particles at higher energies and to detect neutral particles (neutrons and 
@@
 
-The measurement of the DVCS process ($eH \rightarrow e' H' \gamma$, where 
-$H$ is a hadron) necessitates some adaptations in this setup. Indeed, the EC 
-covers only polar angles from 8$^{\circ}$ to 45$^{\circ}$ with a very small
-acceptance at the lowest angles. With a 6 GeV electron beam on a proton target, the 
-majority of the DVCS photons are produced at polar angles below 15$^{\circ}$, 
-where the acceptance of the EC is poor. To resolve this issue an additional 
-Inner Calorimeter (IC) has been built for the E01-113 experiment (2005). The IC is 
+Measurement of the DVCS process ($eH \rightarrow e' H' \gamma$, where 
+$H$ is a hadron) necessitates some adaptations in this setup.
+With a 6 GeV electron beam, the 
+majority of DVCS photons are produced at very forward angles where the  
+acceptance of the EC is poor. To extend the range, an additional 
+Inner Calorimeter (IC) was built for the E01-113 experiment in 2005. The IC is 
 constructed from 424 lead-tungstate (PbWO$_{4}$) crystals, covering polar 
@@
 corresponding to 17 radiation lengths. The achieved energy 
-resolution is around 3 to 4$\%$ for photon energies between 2 GeV and 5 GeV and 
-the angular resolution is between 3 to 5 mrad for the same energy range 
-\cite{Hyon-suk}. The amount of background from Moller electron is however
-very problematic at such small angles, so a 5 Tesla solenoid magnet has been
-added around the target as a magnetic shield against the low energy background.
+resolution is around 3 to 4$\%$ for photon energies between 2 GeV and 5 GeV, with
+an angular resolution between 3 and 5 mrad 
+\cite{Hyon-suk}.
 
-The developed RTPC has been used during a three months experimental run in 2009 
-with a longitudinally polarized electron beam of energy 6.064 GeV projected 
-onto a gaseous $^{4}$He target to measure asymmetries in Deep Virtual Compton 
-Scattering (DVCS)~\cite{proposal} and exclusive meson production. Moreover, a 
-5~T solenoid was placed around the RTPC-target system to shield the detectors 
-close to the beam line from Mollers electrons. The solenoid field plays also a 
-major rule in finding the momentum of the charged particles in the RTPC by 
-bending their tracks curvature.
+%M{\o}ller electrons can be
+%very problematic at such small angles, so a 5 Tesla solenoid magnet has been
+%added around the target as a magnetic shield against this low energy background.
 
-In this paper we report the progress in designing and calibrating a radial TPC 
-that had been used with JLab-CLAS spectrometer. This paper is organized as 
-follows: section \ref{prev_tpc} presents an overview of the TPCs history and 
-previous usage, section \ref{sec_design} details the physics considerations for 
-the RTPC design and its internal structure, while section \ref{sec_readout} 
-points the properties of the read-out system. The calibration strategies for 
-such a detector are discussed in section \ref{sec_calib}. Finally, the 
+For coherent nuclear processes, the RTPC was developed to extend the tracking range of CLAS to low energy nuclei and was used during a one month experimental run in 2009 
+with a longitudinally polarized electron beam of energy 6.064 GeV incident 
+on a gaseous $^{4}$He target.
+%, with the goal of measuring asymmetries in Deep Virtual Compton 
+%Scattering (DVCS)~\cite{proposal} and exclusive meson production.
+
+Moreover, a 
+5~T solenoid was placed around the RTPC-target system to shield the IC and RTPC from the large flux of low energy M{\o}ller electrons. The solenoid field serves also as the
+analyzing magnet for charged particle tracking by the RTPC.
+
+In this paper we report the design, calibration, and performance of the radial TPC, organized as follows.
+Section \ref{prev_tpc} presents an overview of the history of TPCs.
+Section \ref{sec_design} details the physics considerations for 
+our RTPC's design and internal structure. Section \ref{sec_readout} 
+describes the properties of the read-out system.  Calibration strategies are
+discussed in section \ref{sec_calib}. Finally, the 
 performance of the RTPC is described in section \ref{sec_perf}.
@@
 \section{TPC technology} \label{prev_tpc}
-In the late 1970s, David R. Nygren presented the concept of the Time projection 
+In the late 1970s, David R. Nygren presented the concept of the Time Projection 
 Chambers (TPCs) as a new tool to track charged particles based on combining 
@@
 
-The first implementation of a radial TPC with JLab-CLAS spectrometer has been 
+The first implementation of a radial TPC was  
 performed by the BoNuS experiment \cite{BONUS} in 2005. The success of the 
 BoNuS-RTPC in detecting the slow protons motivated the development of this new 
-RTPC. For the channels of interest in CLAS-EG6 experiment, the recoiled 
+RTPC. For the channels of interest in CLAS-EG6 experiment, the recoiling 
 $^{4}$He nuclei have momentum per charge around 150 MeV/c. The detection of 

### 2017-02-14 eg6-letters/NIM/EG6_RTPC_NIM.tex
quick edits, incomplete, just commit it for now

@@
 effective gas-gain element to improve the tracking efficiency of the TPCs 
-\ref{gem_sauli}. Nowadays, the TPCs are widely used in physics experiments, 
+\ref{gem_sauli}. Presently, TPCs are widely used in physics experiments, 
 such as high-energy physics (ALEPH, DELPHI), heavy-ion physics (STAR, ALICE) 
@@
 The design of CLAS-EG6 RTPC has been chosen according to physics and 
-experimental considerations. At 6 GeV incident electron beam energy, the recoil 
-$^{4}$He nuclei, from the coherent DVCS channel, have an average momentum (per 
-charge) around 125 MeV/c, while the "standard" CLAS detects charged particles 
-with a threshold of 250 MeV/c. On the experimental site, the chosen design has 
-to fit within the available space inside a 5 Tesla Solenoid magnet that 
-surrounds the target \cite{Hyon-suk}. Figure \ref{fig:RTPC2} shows an 
-experimental view of the RTPC before being inserted into the solenoid.
+experimental requirements.  At 6 GeV incident electron beam energy, the recoil 
+$^{4}$He nuclei from coherent DVCS have an average momentum (per 
+charge) around 125 MeV/c, while the ``standard'' CLAS detects charged particles 
+above a threshold of 250 MeV/c. The chosen design also has 
+to fit within the available space inside a 5 Tesla Solenoid magnet
+surrounding the target \cite{Hyon-suk}. Figure \ref{fig:RTPC2} shows a photograph of the RTPC before being inserted into the solenoid.
 
-The CLAS-EG6 RTPC is a 200~mm long with a 150~mm diameter TPC. While a charged 
-particle traverses a gas-sensitive volume, the ionized electrons are released 
+The CLAS-EG6 RTPC is a 200~mm long cylinder with a diameter of 150~mm. While a charged 
+particle traverses the sensitive gas volume, ionized electrons are released 
 and drift, under the effect of an applied electromagnetic field, outward 
@@
 
-The sources of these effects were not determined, but rejection techniques allowed to reconstruct 10\% more good tracks with no significant loss and recover 70 channels that were previously ignored due to high noise levels.
+The sources of these effects were not determined, but rejection techniques allowed to reconstruct 10\% more good tracks, with no significant loss, and recover 70 channels that were previously ignored due to excessive noise levels.
 

### 2017-02-14 eg6-letters/coherent/dvcs_he4_prl.tex
remove abbreviations from abstract

@@
 We report the first fully exclusive measurement of Deeply Virtual Compton 
-Scattering (DVCS) off a nucleus for $A>1$. The experiment used the 6 GeV 
+Scattering off a nucleus for $A>1$. The experiment used the 6 GeV 
 electron beam from CEBAF machine at Jefferson Lab projected onto a $^4$He gas 
-target in the center of the CEBAF Large Acceptance Spectrometer (CLAS). A new 
-Radial Time Projection Chamber (RTPC) was used to detect the recoiling $^4$He
+target in the center of the CEBAF Large Acceptance Spectrometer. A new 
+Radial Time Projection Chamber was used to detect the recoiling $^4$He
 nuclei and ensure the exclusivity of the process. The measured Beam Spin 
-Asymmetries (BSA) are significantly larger than that observed on the proton in 
+Asymmetries are significantly larger than that observed on the proton in 
 the same kinematic domain. Since $^4$He is a spin zero target, we were able to 
 extract, in a completely model independent way, the chiral even Generalized 
-Parton Distribution (GPD) $H_{A}$ of $^4$He. This pioneering measurement leads 
+Parton Distribution $H_{A}$ of $^4$He. This pioneering measurement leads 
 the way toward the 3D imaging of the partonic structure of nuclei.

### 2017-02-14 eg6-letters/coherent/dvcs_he4_prl.tex
implement stepans 3rd comments

@@
 \begin{abstract}
-We report the first fully exclusive measurement of Deeply Virtual Compton 
+We report the first fully exclusive measurement of coherent Deeply Virtual Compton 
 Scattering off a nucleus for $A>1$. The experiment used the 6 GeV 
-electron beam from CEBAF machine at Jefferson Lab projected onto a $^4$He gas 
+electron beam from the CEBAF machine at Jefferson Lab incident on a $^4$He gas 
 target in the center of the CEBAF Large Acceptance Spectrometer. A new 
@@
 nuclei and ensure the exclusivity of the process. The measured Beam Spin 
-Asymmetries are significantly larger than that observed on the proton in 
+Asymmetries are larger than that observed on the proton in 
 the same kinematic domain. Since $^4$He is a spin zero target, we were able to 
-extract, in a completely model independent way, the chiral even Generalized 
-Parton Distribution $H_{A}$ of $^4$He. This pioneering measurement leads 
-the way toward the 3D imaging of the partonic structure of nuclei.
+extract, in a completely model independent way, the real and imaginary of the $^4$He Compton Form Factors, $\cal H_A$, which are functions of the Generalized Parton Distribution $H_A$. 
+This pioneering measurement of coherent Deeply Virtual Compton Scattering on the $^4$He nucleus, with a fully exclusive final state via nuclear recoil tagging, leads the way toward 3D imaging of the partonic structure of nuclei.
 \end{abstract}
@@
 
-Rich information on Quantum Chromodynamics (QCD) lies in the internal structure 
+Rich information on Quantum Chromodynamics (QCD) can be extracted from the internal structure 
 of hadrons. In the recent past, development of the Generalized Parton 
 Distributions (GPDs) framework has offered a possibility to obtain new 
-information about the momentum and spatial degrees of freedom of the quark and 
+information about the momentum and spatial degrees of freedom of the quarks and 
 gluons inside hadrons 
@@
 sensitive to GPDs, the measurement of DVCS is considered the cleanest probe and 
-has been the focus of a worldwide effort 
+has been the focus of worldwide efforts 
 \cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
@@
 
-The coherent nuclear DVCS reaction, $eA \rightarrow e' A' \gamma$, is difficult 
-to measure due to its small cross section and the necessity to ensure 
-exclusivity of the reaction, i.e. the target nucleus. Figure \ref{fig:diags} 
+One must overcome two major experimental challenges in measuring coherent nuclear DVCS, $eA\rightarrow^\prime A^\prime\gamma$.
+First, the cross section of coherent scattering is suppressed due to the nuclear form factor, and second, the recoil nucleus ($A^\prime$) must be detected to ensure coherence.
+%The coherent nuclear DVCS reaction, $eA \rightarrow e' A' \gamma$, is difficult 
+%to measure due to its small cross section and the necessity to ensure 
+%exclusivity of the reaction, i.e. the target nucleus.
+Figure \ref{fig:diags} 
 illustrates the hand bag diagram for coherent DVCS on $^4$He.  Similar to the 
@@
 
-The main challenge in studying nuclear DVCS is ensuring the exclusivity of the 
-reaction. Until now, the only available data on nuclear DVCS was from the 
-HERMES experiment \cite{Ellinghaus:2002zw}, where exclusivity was based only on 
+%The main challenge in studying nuclear DVCS is ensuring the exclusivity of the reaction. 
+Until now, the only available data on nuclear DVCS was from the 
+HERMES experiment \cite{Ellinghaus:2002zw}, where coherence in the reaction was based only on 
 kinematic cuts on the measured scattered electron and real photon. That 
@@
 optimized for DVCS measurements 
-\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}, so we 
-built a specialized radial time projection chamber (RTPC) for detection of a 
+\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.
+
+In order to measure DVCS on $^4$He with a fully exclusive final state, we 
+built a specialized radial time projection chamber (RTPC) for detection and identification of
 low energy recoiling light nuclei in order to ensure exclusivity of the 
@@
 polarization) at energy of 6.064 GeV. The data were collected over 40 days 
-using a 6 atm gaseous $^4$He target placed in the center of CLAS. For DVCS 
+using a 6 atm gaseous $^4$He target placed 64 cm upstream of the nominal center of CLAS. For DVCS 
 experiments, the CLAS baseline design \cite{Mecking:2003zu} is supplemented 
@@
 components and the $^4$He detection concept are presented. The $^4$He gaseous 
-target, a $25$ cm long, $27~\mu$m wall Kapton straw, in the center was part of 
-the RTPC assembly. The detector was calibrated specifically for the detection 
+target, a $25$ cm long Kapton straw with $27~\mu$m thick wall, was part of the RTPC
+assembly and installed on the axis of the detector. The RTPC was calibrated specifically for the detection 
 of $^4$He nuclei using elastic scattering with a 1.2~GeV electron beam.
@@
 electron, one $^4$He, and at least one photon are detected in the final state.
-Electrons are identified using measured momentum, time and energy in fiducial 
-volume of CLAS drift chambers, Cerenkov counters, scintillator counters, and 
-electromagnetic calorimeters. The $^4$He are identified in the RTPC using time, 
-track quality, and energy loss cut for tracks in the fiducial region. In 
+Electrons are identified using measured momentum, time, and energy in the fiducial 
+volume of the CLAS system's drift chambers, Cerenkov counters, scintillator counters, and 
+electromagnetic calorimeters. The recoiling $^4$He nuclei are identified in the RTPC using time, 
+track quality, and energy loss cuts for tracks in the fiducial region. In 
 addition, we apply a vertex matching cut to ensure that the electron and helium
@@
 In this work, the physics observable extracted using coherent DVCS events is
-the Beam Spin Asymmetry (BSA). The BSA on unpolarized target (U), $A_{LU}$, is 
-measurable by the difference of cross sections of the reaction at opposite beam 
-helicities normalized to the total cross section. It is written as:
+the Beam Spin Asymmetry (BSA). The BSA on an unpolarized target, $A_{LU}$, is 
+measured as the difference of cross sections of the reaction at opposite beam 
+helicities normalized to the total cross section:
   \begin{equation}
@@
 where $d^{5}\sigma^{+(-)}$ is the DVCS differential cross 
-section for a positive (negative) beam helicity. Experimentally, $A_{LU}$ 
-can be expressed in terms of the measured number of events in each 
-beam-helicity state ($N^{+}$, $N^{-}$) as:
+section for a positive (negative) beam helicity. 
+In this ratio, luminosity normalization and
+detector efficiencies largely cancel and $A_{LU}$ can be expressed in
+terms of helicity-state yields ($N^{+/-}$)
 \begin{equation}
@@
 \end{equation}
-where $P_{B}$ is the beam polarization, and $N^{+}$ and $N^{-}$ are the number 
-of DVCS events detected with positive and negative electron helicity with 
-respect to the beam direction. In this ratio most of uncertainties of the 
-experimental normalization and in detector efficiencies will cancel out.
+where $P_{B}$ is the beam polarization.
+
+%most of uncertainties of the 
+%experimental normalization and in detector efficiencies will cancel out.
 
@@
 $H_A$. In Eq.~\ref{eq:A_LU-coh}, $\phi$ is the azimuthal angle between the 
-($e$,$e'$) and ($\gamma^{*}$,$^4$He$'$) planes. The $\alpha_i$’s are kinematic 
-factors that depend on azimuthal angle $\phi$, the nuclear form factor 
-$F_A(t)$, $Q^2$, and $x_B$. These factors are expressed as:
+($e$,$e'$) and ($\gamma^{*}$,$^4$He$'$) planes. The kinematic factors $\alpha_i$
+depend on azimuthal angle $\phi$, the nuclear form factor 
+$F_A(t)$, $Q^2$ and $x_B$. These factors are expressed as:
 \small
@@
 in the leptonic tensor.  The explicit expressions of these terms can be found 
-in \cite{Belitsky:2008bz}.  We see that by using the $\sin(\phi)$ and 
+in \cite{Belitsky:2008bz} and show that, by using the $\sin(\phi)$ and 
 $\cos(\phi)$ contributions, it is possible to extract $\Im m(\mathcal{H}_{A})$ 
@@
 correct the DVCS data.  Depending on the kinematics, we found contaminations of 
-2 to 4\%. The study of systematics uncertainties showed that the main 
+2 to 4\%. The study of systematic uncertainties showed that the main 
 contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
@@
 with the function presented in Eq.~\ref{eq:A_LU-coh}, where the real and 
-imaginary part of the CFF $\mathcal{H}_{A}$ are the free parameters of the fit. 
+imaginary parts of the CFF $\mathcal{H}_{A}$ are the free parameters of the fit. 
 In Figure \ref{fig:alu90} the $Q^2$, $x_{B}$, and $-t$-dependencies of the 
-fitted $A_{LU}$ signals at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and 
+fitted $A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and 
 $-t$-dependencies are compared to theoretical calculations performed by 
@@
 \cite{Vadim_priv}, the nucleus is assumed to be composed of non-relativistic 
-and non-interacting nucleons, where these nucleons interact independently with 
+nucleons, each interacting independently with 
 the probe. The Convolution-Dual model is based on nucleon GPDs from the dual 
@@
 $Q^{2}$, $x_B$, and $-t$ are in agreement 
-with the theoretical calculations. One can see a difference between the 
+with the theoretical expectations. One can see a difference between the 
 precision of the extracted imaginary and real parts, which is expected from
@@
 %conclusion
-In summary, we presented the first exclusive measurement of coherent DVCS off 
+In summary, we present the first exclusive measurement of coherent DVCS off 
 $^4$He using the CLAS spectrometer supplemented with a Radial Time Projection 
 Chamber and a high pressure gaseous target. This setup allowed detection of the 
-low energy $^4$He recoils in order to ensure the DVCS exclusivity.
+low energy $^4$He recoils in order to ensure an exclusive measurement of the
+coherent DVCS process.
 The azimuthal dependence of the measured beam spin asymmetry ($A_{LU}$) has 
 been used to extract, in model independent way, the real and the imaginary 
-parts of the $^4$He CFF, $\mathcal{H}_A$. The extracted CFF is in a good 
+parts of the $^4$He CFF, $\mathcal{H}_A$. The extracted CFF is in  
 agreement with predictions of the available models. This first fully exclusive 

### 2017-02-14 eg6-letters/coherent/dvcs_he4_prl.tex
bug fix in abstract

@@
 the same kinematic domain. Since $^4$He is a spin zero target, we were able to 
-extract, in a completely model independent way, the real and imaginary of the $^4$He Compton Form Factors, $\cal H_A$, which are functions of the Generalized Parton Distribution $H_A$. 
+extract, in a completely model independent way, the real and imaginary parts of the $^4$He Compton Form Factors, $\cal H_A$, which are functions of the Generalized Parton Distribution $H_A$. 
 This pioneering measurement of coherent Deeply Virtual Compton Scattering on the $^4$He nucleus, with a fully exclusive final state via nuclear recoil tagging, leads the way toward 3D imaging of the partonic structure of nuclei.

### 2017-02-14 eg6-letters/coherent/dvcs_he4_prl.tex
remove double speak

@@
 built a specialized radial time projection chamber (RTPC) for detection and identification of
-low energy recoiling light nuclei in order to ensure exclusivity of the 
-reaction. The $^4$He nucleus is an ideal experimental target in this regard, as 
+low energy recoiling light nuclei. The $^4$He nucleus is an ideal experimental target in this regard, as 
 it is light enough to be detected in such a setting, while it

### 2017-02-14 eg6-letters/coherent/dvcs_he4_prl.tex
Implement Stepan iremark and clean latex syntax

@@
 \includegraphics[width=6.5cm]{figs/DVCS_diagram.pdf}
-\caption{Representation of the leading-order, twist-2, handbag diagram of the 
+\caption{Representation of the leading order handbag diagram of the 
 DVCS process off $^4$He.}
@@
 
-One must overcome two major experimental challenges in measuring coherent nuclear DVCS, $eA\rightarrow^\prime A^\prime\gamma$.
-First, the cross section of coherent scattering is suppressed due to the nuclear form factor, and second, the recoil nucleus ($A^\prime$) must be detected to ensure coherence.
-%The coherent nuclear DVCS reaction, $eA \rightarrow e' A' \gamma$, is difficult 
-%to measure due to its small cross section and the necessity to ensure 
-%exclusivity of the reaction, i.e. the target nucleus.
+One must overcome two major experimental challenges in measuring coherent 
+nuclear DVCS, $eA\rightarrow^\prime A^\prime\gamma$. First, the cross section 
+of coherent scattering is suppressed due to the nuclear form factor, and 
+second, the recoil nucleus ($A^\prime$) must be detected to ensure coherence. 
 Figure \ref{fig:diags} 
@@
 
-%The main challenge in studying nuclear DVCS is ensuring the exclusivity of the reaction. 
 Until now, the only available data on nuclear DVCS was from the 
@@
 
-%The main background in the measurement of DVCS is coherent $\pi^{0}$ 
-%production. Therefore, we remove events where a $\pi^{0}$ can be identified by 
-%invariant mass reconstruction of two photons.
-
 To ensure the interaction occurs at the partonic level and the DVCS handbag 
@@
 
-%most of uncertainties of the 
-%experimental normalization and in detector efficiencies will cancel out.
-
-The DVCS reaction is experimentally indistinguishable from the well-known 
-Bethe-Heitler (BH) process, where the final photon is emitted either from the 
-incoming or the outgoing leptons. At leading twist and leading order, the 
-deeply virtual photon production cross section is composed of BH, DVCS, and 
-interference terms. While the BH is not sensitive to GPDs and does not carry 
-information about the partonic structure of the hadronic target, its 
-interference with the DVCS reaction is sensitive to GPDs enhancing the DVCS 
-small cross section at the kinematical regions explored at Jefferson Lab. The 
-amplitudes of the three terms can be approximated as a finite sum of Fourier 
-harmonics, as shown for the nucleon in \cite{Belitsky:2001ns} and for the 
-spin-zero targets in \cite{Kirchner:2003wt,Belitsky:2008bz}. Based on these 
-approximations, the beam-spin asymmetry ($A_{LU}$) of a spin-zero hadron can 
-then be expressed as:
-\small
+The DVCS and the well-known Bethe-Heitler (BH) process, where the final real 
+photon is emitted by the incoming or the outgoing lepton, have the same final 
+state and are indistinguishable. The amplitude of the real photon 
+electroproduction is a sum of amplitudes of these two processes. The BH 
+amplitude is defined by the target form factors, where the DVCS amplitude is 
+a combination of the form factors and GPDs. In our kinematics, the cross 
+section of the real photon electroproduction is dominated by the BH 
+contribution, while the DVCS contribution is very small. Its effect is however
+enhanced in the observables sensitive to the interference term, {\it e.g.} 
+beam spin asymmetry. The three terms entering in the cross section calculation, 
+BH and DVCS amplitude squared, and the interference of the BH and DVCS amplitudes 
+can be expressed by a finite sum of Fourier harmonics, as shown for the nucleon 
+in \cite{Belitsky:2001ns} and for the spin-zero targets in 
+\cite{Kirchner:2003wt,Belitsky:2008bz}. Base on this work, the beam-spin 
+asymmetry ($A_{LU}$) of a spin-zero hadron can be expressed as:
 \begin{equation}
 \begin{split}
-A_{LU}(\phi) =~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
- \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
+&A_{LU}(\phi) = \\
+&\frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
 {\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
 \big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)},
+\end{split}
 \label{eq:A_LU-coh}
-\end{split}
 \end{equation}
-\normalsize
 where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
@@
 $F_A(t)$, $Q^2$ and $x_B$. These factors are expressed as:
-\small
-\begin{eqnarray}
-   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi),\\
-    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} 
-   \cos(2\phi),\\ \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( 
-C_{++}(0) +  C_{++}(1) cos(\phi) \right),\\
-\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
+\begin{align}
+   \alpha_0 (\phi) & = \frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi), \\
+   \alpha_1 (\phi) & = c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi), \\ 
+   \alpha_2 (\phi) & = \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( 
+      C_{++}(0) +  C_{++}(1) cos(\phi) \right), \\
+   \alpha_3 (\phi) &= \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
       {\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
       \epsilon^2},
-\end{eqnarray}
-\normalsize
+\end{align}
 where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$($M_{N}$) is the $^4$He 

### 2017-02-14 eg6-letters/coherent/dvcs_he4_prl.tex
english tweaks after stepans new paragraph

@@
 
-The DVCS and the well-known Bethe-Heitler (BH) process, where the final real 
+The DVCS and well-known Bethe-Heitler (BH) processes, where the real 
 photon is emitted by the incoming or the outgoing lepton, have the same final 
-state and are indistinguishable. The amplitude of the real photon 
-electroproduction is a sum of amplitudes of these two processes. The BH 
-amplitude is defined by the target form factors, where the DVCS amplitude is 
-a combination of the form factors and GPDs. In our kinematics, the cross 
-section of the real photon electroproduction is dominated by the BH 
+state and are indistinguishable. The amplitude of real photon 
+electroproduction is a sum of the amplitudes of these two processes. The BH 
+amplitude is defined by the target form factors, while the DVCS amplitude is 
+a combination of the form factors and GPDs. At our kinematics, the cross 
+section of real photon electroproduction is dominated by the BH 
 contribution, while the DVCS contribution is very small. Its effect is however
 enhanced in the observables sensitive to the interference term, {\it e.g.} 
-beam spin asymmetry. The three terms entering in the cross section calculation, 
-BH and DVCS amplitude squared, and the interference of the BH and DVCS amplitudes 
+beam spin asymmetry. The three terms entering the cross section calculation, the 
+BH and DVCS amplitudes squared and their interference term, 
 can be expressed by a finite sum of Fourier harmonics, as shown for the nucleon 
 in \cite{Belitsky:2001ns} and for the spin-zero targets in 
-\cite{Kirchner:2003wt,Belitsky:2008bz}. Base on this work, the beam-spin 
+\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the beam-spin 
 asymmetry ($A_{LU}$) of a spin-zero hadron can be expressed as:

### 2017-02-14 eg6-letters/coherent/dvcs_he4_prl.tex
stepans 4th comments

@@
 \affiliation{\JLAB}
+\newcommand*{\ODU}{Old Dominion University, Norfolk, Virginia 23529}
+\newcommand*{\ODUindex}{4}
+\newcommand*{\INFNGE}{INFN, Sezione di Genova, 16146 Genova, Italy}
+\newcommand*{\INFNGEindex}{5}
+\newcommand*{\UTFSM}{Universidad T\'{e}cnica Federico Santa Mar\'{i}a, Casilla 110-V Valpara\'{i}so, Chile}
+\newcommand*{\UTFSMindex}{6}
+\newcommand*{\MISS}{Mississippi State University, Mississippi State, MS 39762-5167}
+\newcommand*{\MISSindex}{7}
+\newcommand*{\VIRGINIA}{University of Virginia, Charlottesville, Virginia 22901}
+\newcommand*{\VIRGINIAindex}{8}
 
@@
 \affiliation{\JLAB}
+\author {S.~Bultmann} 
+\affiliation{\ODU}
+\author{R.~De~Vita} 
+\affiliation{\INFNGE}
+\author {A.~El~Alaoui} 
+\affiliation{\ANL}
+\affiliation{\UTFSM}
+\author {L.~El~Fassi} 
+\affiliation{\MISS}
+\author{H.~Egiyan}
+\affiliation{\JLAB}
+\author{F.X.~Girod} 
+\affiliation{\JLAB}
+\author{S.~Liuti} 
+\affiliation{\VIRGINIA}
+\author {B.~Torayev} 
+\affiliation{\ODU}
+\author {E.~Voutier} 
+\affiliation{\ORSAY}
 
@@
 enhanced in the observables sensitive to the interference term, {\it e.g.} 
-beam spin asymmetry. The three terms entering the cross section calculation, the 
-BH and DVCS amplitudes squared and their interference term, 
-can be expressed by a finite sum of Fourier harmonics, as shown for the nucleon 
-in \cite{Belitsky:2001ns} and for the spin-zero targets in 
-\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the beam-spin 
+beam spin asymmetry. The three terms entering the cross section calculation,
+the BH and DVCS amplitudes squared and their interference term, 
+can be decomposed into a finite sum of Fourier harmonics in the azimuthal angle
+$\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes, as
+shown for the nucleon in \cite{Belitsky:2001ns} and for the spin-zero targets
+in \cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the beam-spin 
 asymmetry ($A_{LU}$) of a spin-zero hadron can be expressed as:
@@
 depend on azimuthal angle $\phi$, the nuclear form factor 
-$F_A(t)$, $Q^2$ and $x_B$. These factors are expressed as:
+$F_A(t)$, $Q^2$ and $x_B$. These factors are written as:
 \begin{align}
@@
 To estimate the importance of this background, we developed an event generator 
-calibrated on the experimental yield of exclusive $\pi^0$ measured by our 
+tuned on the experimental yield of exclusive $\pi^0$ measured by our 
 experiment. We used this generator together with a GEANT3 simulation of our 

### 2017-02-15 eg6-letters/coherent/dvcs_he4_prl.tex
alpha0->alpha1 in sensitivity discussion

@@
 precision of the extracted imaginary and real parts, which is expected from
-Eq.~\ref{eq:A_LU-coh} because $\alpha_2$ is smaller than $\alpha_0$. While the 
+Eq.~\ref{eq:A_LU-coh} because $\alpha_2$ is much smaller than $\alpha_1$. While the 
 accuracy of our results does not allow to discriminate between the models, they 

### 2017-02-16 for_eg6_group/DVCS_EG6_meeting.tex
udate some studies for the incoherent channel

\section*{\centering{Tuning the incoherent exclusivity cuts}}

\begin{figure}[h!]
\includegraphics[height=15.0cm]{incoh/old_all_incoh_exc_cuts.pdf}
\caption{Old set of cuts}
\label{fig:cuts}
\end{figure}

\begin{figure}[h!]
   \includegraphics[height=15.0cm]{incoh/all_incoh_exc_cuts_test.pdf}
\caption{Suggested new set of cuts}
\label{fig:cuts}
\end{figure}

\begin{figure}[h!]
   \includegraphics[height=6.0cm]{incoh/ALU_phi_p_Q2.pdf}
   \includegraphics[height=5.2cm]{incoh/BSA_InCoherent_Q2.png}
\caption{}
\label{fig:cuts}
\end{figure}

\begin{figure}[h!]
   \includegraphics[height=6.0cm]{incoh/ALU_phi_p_x.pdf}
   \includegraphics[height=5.2cm]{incoh/BSA_InCoherent_xB.png}
\caption{}
\label{fig:cuts}
\end{figure}

\begin{figure}[h!]
   \includegraphics[height=6.0cm]{incoh/ALU_phi_p_t.pdf}
   \includegraphics[height=5.2cm]{incoh/BSA_InCoherent_t.png}
\caption{}
\label{fig:cuts}
\end{figure}

### 2017-02-16 eg6-letters/coherent/dvcs_he4_prl.tex
correct the contract nuber in the acknowledgements.

@@
 \newcommand*{\VIRGINIAindex}{8}
+\newcommand*{\VIRGINIATECH}{Virginia Polytechnic Institute and State University, Blacksburg, Virginia, 24061}
+\newcommand*{\VIRGINIATECHindex}{9}
 
@@
 \affiliation{\JLAB}
+\author{D.~Jenkins}
+\affiliation{\VIRGINIATECH}
 \author{S.~Liuti} 
 \affiliation{\VIRGINIA}
+\author{Y.~Perrin}
+\affiliation{\ORSAY}
 \author {B.~Torayev} 
@@
 Lab for making this experiment possible. This work is supported by the U.S.  
-Department of Energy, Office of Science, Office of Nuclear Physics contract 
-DE-AC05-06OR23177.
+Department of Energy, Office of Science, Office of Nuclear Physics, under 
+contract DE-AC02-06CH11357.
 

### 2017-02-18 eg6-letters/NIM/EG6_RTPC_NIM.tex
NIM:  various updates

@@
 A new Radial Time Projection Chamber (RTPC) was developed at Jefferson 
-Laboratory (JLab) to track low-energy nuclear recoils for the purpose of 
-measuring exclusive nuclear channels, such as coherent Deeply Virtual Compton 
-Scattering (DVCS) and coherent meson production on $^4$He. In such 
-processes, the $^4$He nucleus remains intact and recoils as a whole in the final 
-state. The CEBAF Large Acceptance Spectrometer (CLAS) at JLab has been used for 
-similar studies on proton targets, however it cannot track recoils with momenta 
-less than 250 MeV/c.
-In 2009, we carried out measurements using the CLAS spectrometer supplemented by the RTPC positioned directly around a gaseous $^4$He target, allowing a detection threshold as low as $~$100  MeV/c for
-$^4$He. This article discuses the design, work principle, calibration 
-methods and performances of the RTPC.
+Laboratory to track low-energy nuclear recoils for the purpose of measuring
+exclusive nuclear channels, such as coherent Deeply Virtual Compton Scattering
+and coherent meson production on $^4$He. In such processes, the $^4$He nucleus
+remains intact and recoils as a whole in the final state. The CEBAF Large
+Acceptance Spectrometer (CLAS) has been used for similar studies on proton
+targets, however it cannot track recoils with momenta less than 250 MeV/c. In
+2009, we carried out measurements using the CLAS spectrometer supplemented by
+the RTPC positioned directly around a gaseous $^4$He target, allowing a detection
+threshold as low as $~$100  MeV/c for $^4$He. This article discuses the design,
+work principle, calibration methods and performances of the RTPC.
 \end{abstract}
@@
 
-Thomas Jefferson National Accelerator Facility (TJNAF),
-in Newport News, Virginia, USA, provides 
-high power electron beams of energy up to 6 GeV and 100$\%$ duty cycle to 
-three experimental Halls (A, B, C) simultaneously. The CLAS spectrometer, located in Hall-B, 
-is composed of several sub-detectors and two magnets. The spectrometer was 
-designed to track charged particles of momentum greater than 250 MeV/c as well 
+Thomas Jefferson National Accelerator Facility (TJNAF), in Newport News, Virginia,
+USA, provides high power electron beams of energy up to 6 GeV and 100$\%$ duty cycle
+to three experimental Halls (A, B, C) simultaneously. The CLAS spectrometer, located
+in Hall-B, is composed of several sub-detectors and two magnets. The spectrometer
+was designed to track charged particles of momentum greater than 250 MeV/c as well 
 as detecting real photons. Figure~\ref{fig:CLAS} shows a three dimensional 
@@
 \begin{itemize}
- \item Three regions of Drift Chambers (DC) used for the tracking of charged 
+ \item Three regions of Drift Chambers (DC) for the tracking of charged 
     particles~\cite{DCref} (in blue on the figure).
- \item Superconducting toroidal magnet (in yellow) bends the trajectories 
+ \item Superconducting toroidal magnet (in yellow) to bend the trajectories 
     of charged particles, thus allowing momentum measurement with the DC tracking information.
- \item Cherenvkov Counters (CC) used to distinguish electrons from other negative 
+ \item Cherenvkov Counters (CC) to distinguish electrons from other negative 
     particles, such as pions, at lower energies~\cite{CCref} (in pink).
- \item Scintillation Counters (SC) used to identify hadrons by measuring their 
+ \item Scintillation Counters (SC) to identify hadrons by measuring their 
     time of flight (TOF)~\cite{TOFref} (in red).
- \item Electromagnetic Calorimeters (EC) used to distinguish electrons from other negative 
+ \item Electromagnetic Calorimeters (EC) to distinguish electrons from other negative 
     particles at higher energies and to detect neutral particles (neutrons and 
@@
 
-Measurement of the DVCS process ($eH \rightarrow e' H' \gamma$, where 
-$H$ is a hadron) necessitates some adaptations in this setup.
-With a 6 GeV electron beam, the 
-majority of DVCS photons are produced at very forward angles where the  
-acceptance of the EC is poor. To extend the range, an additional 
-Inner Calorimeter (IC) was built for the E01-113 experiment in 2005. The IC is 
-constructed from 424 lead-tungstate (PbWO$_{4}$) crystals, covering polar 
-angles between 5$^{\circ}$ and 15$^{\circ}$. Each crystal is 16 cm long,
-corresponding to 17 radiation lengths. The achieved energy 
-resolution is around 3 to 4$\%$ for photon energies between 2 GeV and 5 GeV, with
-an angular resolution between 3 and 5 mrad 
+Measurement of the Deeply Virtual Compton Scattering (DVCS) process
+($eH \rightarrow e' H' \gamma$, where $H$ is a hadron) necessitates some adaptations
+in this setup.  With a 6 GeV electron beam, the majority of DVCS photons are produced
+at very forward angles where the acceptance of the EC is poor. To extend the range,
+an additional Inner Calorimeter (IC) was built for the E01-113 experiment in 2005.
+The IC is constructed from 424 lead-tungstate (PbWO$_{4}$) crystals, covering polar 
+angles between 5$^{\circ}$ and 15$^{\circ}$. Each crystal is 16 cm long, corresponding
+to 17 radiation lengths. The achieved energy resolution is around 3 to 4$\%$ for photon
+energies between 2 GeV and 5 GeV, with an angular resolution between 3 and 5 mrad 
 \cite{Hyon-suk}.
@@
 %added around the target as a magnetic shield against this low energy background.
-
-For coherent nuclear processes, the RTPC was developed to extend the tracking range of CLAS to low energy nuclei and was used during a one month experimental run in 2009 
-with a longitudinally polarized electron beam of energy 6.064 GeV incident 
+For coherent nuclear processes, the RTPC was developed to extend the tracking
+range of CLAS to low energy nuclei and was used during a one month experimental run
+in 2009 with a longitudinally polarized electron beam of energy 6.064 GeV incident 
 on a gaseous $^{4}$He target.
@@
 
-Moreover, a 
-5~T solenoid was placed around the RTPC-target system to shield the IC and RTPC from the large flux of low energy M{\o}ller electrons. The solenoid field serves also as the
-analyzing magnet for charged particle tracking by the RTPC.
+Moreover, a 5~T solenoid was placed around the RTPC-target system to shield the IC
+and RTPC from the large flux of low energy M{\o}ller electrons. The solenoid field
+serves also as the analyzing magnet for charged particle tracking by the RTPC.
 
-In this paper we report the design, calibration, and performance of the radial TPC, organized as follows.
-Section \ref{prev_tpc} presents an overview of the history of TPCs.
-Section \ref{sec_design} details the physics considerations for 
-our RTPC's design and internal structure. Section \ref{sec_readout} 
-describes the properties of the read-out system.  Calibration strategies are
-discussed in section \ref{sec_calib}. Finally, the 
-performance of the RTPC is described in section \ref{sec_perf}.
+In this paper we report the design, calibration, and performance of the radial TPC,
+organized as follows.  Section \ref{prev_tpc} presents an overview of the history of
+TPCs.  Section \ref{sec_design} details the physics considerations for our RTPC's
+design and internal structure. Section \ref{sec_readout} describes the properties
+of the read-out system.  Calibration strategies are discussed in section \ref{sec_calib}.
+Finally, the performance of the RTPC is described in section \ref{sec_perf}.
 
@@
 
-The first implementation of a radial TPC was  
-performed by the BoNuS experiment \cite{BONUS} in 2005. The success of the 
-BoNuS-RTPC in detecting the slow protons motivated the development of this new 
-RTPC. For the channels of interest in CLAS-EG6 experiment, the recoiling 
-$^{4}$He nuclei have momentum per charge around 150 MeV/c. The detection of 
-these low-energy nuclei was the primary motivation for designing this detector.
+The first implementation of a radial TPC was performed by the BoNuS experiment
+\cite{BONUS} in 2005. The success of the BoNuS-RTPC in detecting the slow protons
+motivated the development of this new RTPC. For the channels of interest in
+CLAS-EG6 experiment, the recoiling $^{4}$He nuclei have momentum per charge
+around 150 MeV/c. The detection of these low-energy nuclei was the primary
+motivation for designing this detector.
 
@@
 The design of CLAS-EG6 RTPC has been chosen according to physics and 
-experimental requirements.  At 6 GeV incident electron beam energy, the recoil 
-$^{4}$He nuclei from coherent DVCS have an average momentum (per 
-charge) around 125 MeV/c, while the ``standard'' CLAS detects charged particles 
-above a threshold of 250 MeV/c. The chosen design also has 
-to fit within the available space inside a 5 Tesla Solenoid magnet
-surrounding the target \cite{Hyon-suk}. Figure \ref{fig:RTPC2} shows a photograph of the RTPC before being inserted into the solenoid.
+experimental requirements.  At 6 GeV incident electron beam energy, recoiling 
+$^{4}$He nuclei from coherent DVCS have an average momentum (per charge) around
+125 MeV/c, while the ``standard'' CLAS detects charged particles above a threshold
+of 250 MeV/c. The chosen design also has to fit within the available space inside
+a 5 Tesla solenoid magnet surrounding the target \cite{Hyon-suk}. Figure
+\ref{fig:RTPC2} shows a photograph of the RTPC before being inserted into the solenoid.
 
-The CLAS-EG6 RTPC is a 200~mm long cylinder with a diameter of 150~mm. While a charged 
-particle traverses the sensitive gas volume, ionized electrons are released 
-and drift, under the effect of an applied electromagnetic field, outward 
-perpendicularly to the beam direction. These electrons are then amplified by 
-three layers of GEMs and detected by a curved readout system on the external 
-shell as can be seen in the figure~\ref{fig:RTPC_1_4}. As for CLAS-BoNuS, the 
-EG6-RTPC has two detection halves but unlike BoNuS they are part of a single 
-chamber. Each half has independent GEM amplification systems that cover around 
-80\% of the azimuthal angle.
+The CLAS-EG6 RTPC is a 200~mm long cylinder with a diameter of 150~mm. As charged 
+particles traverse the sensitive gas volume, ionized electrons are released and
+drift, under the effect of an applied electromagnetic field, outward perpendicularly
+to the beam direction. These electrons are then amplified by three layers of GEMs
+and detected by a curved readout system on the external shell, as can be seen in
+the figure~\ref{fig:RTPC_1_4}. The EG6-RTPC has two detection halves, but, unlike
+the BoNuS RTPC, they share a single chamber.  Each half has independent GEM
+amplification systems that cover about 80\% of the azimuthal angle.
 
@@
 \includegraphics[scale=0.28]{fig/RTPC_1_all.png}
-\caption{Schematic drawing of CLAS-EG6 RTPC taken on a plane perpendicular to 
-the beam line, see text for description of the elements.} 
+\caption{Schematic drawing of CLAS-EG6 RTPC in a plane perpendicular to 
+the beam direction.  See text for description of the elements.} 
 \label{fig:RTPC_1_4}
@@
    \item The target extends along the RTPC's central z-axis, with a diameter of 
-      6 mm. It is enclosed in a 27-$\mu$m-thick Kapton wall.
+      6 mm and enclosed by a 27-$\mu$m-thick Kapton wall.
 
-   \item The first gas gap extends from 3 mm to 20 mm radial distances. It is 
-      filled with $^{4}$He gas at 1~atm. During run, this region is swarmed by 
-      M\o ller electrons induced by the beam, such that filling this region 
-      with a light gas like $^{4}$He minimizes secondary interactions. This 
+   \item The first gas gap covers a radial range of 3 mm to 20 mm. It is 
+      filled with $^{4}$He gas at 1~atm to minimize secondary interactions induced
+      by M\o ller electrons scattered by the beam. This 
       region is surrounded by a 4 $\mu$m thick window made of aluminized Mylar 
-      and connected to ground.                                                                
-   \item The gap region extends between 20~mm and 30~mm and is filled with a 
+      and electronically grounded.                                                                
+   \item The second gap region extends between 20~mm and 30~mm and is filled with a 
       gas mixture of 80$\%$ Neon and 20$\%$ Dimethyl Ether (DME). This region 
@@
 
-   \item The drift region is filled with the Ne-DME gas mixture, it extends 
+   \item The drift region is filled with the same Ne-DME gas mixture and extends 
       from the cathode to the first Gas Electron Multiplier(GEM), 60 mm away 
@@
    \item The electron amplification system is composed of three GEMs located at 
-      radii, 60 mm, 63 mm and 66 mm. In this configuration, the first GEM layer 
+      radii of 60, 63 and 66 mm. In this configuration, the first GEM layer 
       represents the anode.
 
-   \item The readout board has internal radius of 69~mm and collects the 
-      charges. Preamplifiers are plugged directly on the outer side and are 
-      transmitting the signal to the data acquisition electronics.
+   \item The readout board has an internal radius of 69~mm and collects charge
+     from the GEMs. Preamplifiers are plugged directly on its outer side and
+     transmit the signal to the data acquisition electronics.
 \end{itemize}
@@
 The GEM system has been mainly chosen for this detector for its flexibility, 
-allowing the curved amplification surface. Also GEMs are known to create less 
-sparks than in other gaseous detectors, which provides a cleaner detection of 
-slow nuclei like $^4$He. GEMs are made from an insulator layer, Kapton in our 
-case, sandwiched between two 5 $\mu$m copper layers. The mesh of each GEM layer 
-is chemically etched with 50$\mu$m diameter holes in double-conical cross 
-section shapes as can be seen in figure~\ref{fig:GEMs}. A potential difference 
-of 400 V is applied between the two copper layers of each GEM creating a very 
-strong electric field in the holes. Such strong fields lead to high ionization 
+allowing a curved amplification surface. Also, GEMs are  known to create less 
+sparks than other amplicifation technologies for gaseous detectors, which
+provides a cleaner detection of slow nuclei like $^4$He. The GEMs for the EG6-RTPC
+are made from a Kapton insulator layer sandwiched between two 5 $\mu$m copper
+layers. The mesh of each GEM layer is chemically etched with 50$\mu$m diameter
+holes with double-conical shapes as can be seen in figure~\ref{fig:GEMs}. A
+potential difference of 400 V is applied between the two copper layers of each
+GEM, creating a very strong electric field leading to high ionization 
 from initial electrons and therefore amplification of the signal. Also, a 
@@
 \section{Readout System} \label{sec_readout}
-The RTPC electron collecting system has 3200 readout pads. These collection 
-elements are located at the end of the amplification region, 69 mm from the 
-central axis.
+The RTPC electron collection system has 3200 readout pads. These elements are
+located at the end of the amplification region, 69 mm from the central axis.
 
@@
 configuration of the pads. Each readout pad is 5 mm in length and 4.45 mm in 
-width the shift between the rows allows to reduce aliasing. Each half of the 
-RTPC has 40 rows and 40 columns of pads. The shaded region in the 
-figure~\ref{fig:PADs} shows how pads are grouped to the 16 channels 
-pre-amplifiers. The Time to Digital Converter (TDC) units are 114~ns and 
-indicates the time taken by the electron to drift from the ionization point to 
-the readout board. On the the other side, the charge information is measured in 
-Analog-to-Digital-Converter (ADC) units without specific normalization.
+width.  The shift between the rows allows to reduce aliasing. Each half of the 
+RTPC has 40 rows and 40 columns of pads. The shaded region in figure~\ref{fig:PADs}
+shows how pads are grouped to 16 channels pre-amplifiers.  A Time to Digital
+Converter (TDC) with 114~ns samples is used to measure the time taken by
+the electrons to drift from the ionization point to the readout board.  Signal
+amplitude is is measured with an Analog-to-Digital-Converter (ADC) without
+specific normalization.
+
+Mention ALTRO chip and reference.
+
+Sparcification.  3 consecutive ADC samples above a threshold of ?, and the three
+samples before and after.
 
@@
 
+{\bf Don't we want to have description and quality of elastic event selection in here somewhere?}
+
 \subsection{Drift Speed Parametrization}
 
-We can measure the drift speed using the tracks detected in the RTPC, in figure 
-\ref{fig:RTPC_signals} we represent a typical $^{4}$He track (in green). After 
+We measure the drift speed using tracks detected in the RTPC. In figure 
+\ref{fig:RTPC_signals}, a typical $^{4}$He track is represented (in green). After 
 it causes ionization in the drift region, the released electrons (in black) 
-drift to the detection plane under the effect of the electric field. The 
+drift to the cylindrical detection plane under the effect of the electric field. The 
 electrons released close to the cathode take the most time to reach the readout 
-pads while the geometrical symmetry insure they always travel the same 
-distance. So by identifying the maximum TDC measured, we can infer the drift 
+pads, but geometrical symmetry insures they always travel the same 
+distance. By identifying the maximum TDC measured, we can infer the drift 
 speed of the electrons in the RTPC.\\
@@
 which the dropping edge passes half the maximum number of hits in the 
-histogram, this value is inversely proportional to the drift speed. The result 
-can be seen in figure \ref{fig:RunNumber_61551_TDCmax_Zslice} showing the 
-dependence of drift speed with position along the beam line axis in the 
-chamber.
+histogram, and this value is inversely proportional to the drift speed. The
+result in figure \ref{fig:RunNumber_61551_TDCmax_Zslice} shows the dependence of
+the drift speed on position along the beam line axis in the chamber.
 
@@
    \includegraphics[scale=0.35]{fig/B_MAP.png}
-   \caption[]{Schematic draw in of the solenoid magnetic vectors inside the 
-   RTPC. In this draw, r is the radial distance from the target's axis and z is 
-the longitudinal position along the RTPC with its center at zero.} 
+   \caption[]{Schematic drawing of the solenoid magnetic field vectors inside the 
+   RTPC. The $y$-axis is the radial distance from the center of the target, and the
+   $x$-axis is the longitudinal position along the RTPC (with its center at $z=0$).} 
 \label{fig:B_MAP}
@@
 
-Due to the non perfect experimental conditions and in particular changes in the 
-gas proportions, the drift speed might also change over the 3 months run.  
+Due to the non perfect experimental conditions including variations in the 
+gas mixture, the drift speed might also change during the month long experimental run.  
 Figure \ref{fig:Drift_run_number_1} shows the $TDC_{Max/2}$ values for 
 individual runs (approximately 2 hours long). We observe a significant 
-variation over time that we parametrized with a fit in order to take it into 
-account in the track reconstruction code. Dealing with such situation is 
-possible by adapting the right drift speed to the electrons as a function of 
+variation over time and accounted for these changes in the drift speed in the
+track reconstruction. Dealing with such situations is 
+possible by adapting the drift speed as a function of 
 geometry and time (we did not see any correlation between the effects). These 
-functions were extracted for our entire data sets and implemented in the 
+functions were extracted for our entire data set and implemented in the 
 reconstructions code.
@@
 
-The drift paths are the trajectories which an electron follows in the gas. The 
+The drift paths are the trajectories the electrons follows in the gas. The 
 standard software to calculate drift paths is the MAGBOLTZ program 
-~\cite{MAGBOLTZ}. For its calculations, MAGBOLTZ needs to know the detector's 
-geometry, the exact composition of the gas mixture and of course the electric 
-and the magnetic fields. We used such calculations as a first calibration, but 
+~\cite{MAGBOLTZ}, which requires knowledge of the detector's 
+geometry, the exact composition of the gas mixture, and of course the electric 
+and the magnetic fields. We used such calculations as a first calibration, but, 
 as can be seen with the drift speed, conditions are far from stable in the 
-chamber. Moreover, because we use of a thin foil as a cathode, the geometry 
-knowledge is limited to a millimeter precision. These problems, already 
-encountered for the BoNuS RTPC calibration (ref), have motivated the 
-acquisition of specific calibration runs. These are taken with lower energy 
+chamber. Moreover, because we use a thin foil as a cathode, the geometry 
+knowledge is limited to millimeter precision. These problems, already 
+encountered for the BoNuS RTPC calibration (ref), motivated the 
+acquisition of specific calibration runs. These are taken with a lower energy 
 electron beam (1.20 and 1.27 GeV) to enhance the cross section of the elastic 
-process ($e^{4}$He$\rightarrow e^{4}$He). In this process the knowledge of the 
-electron kinematic gives us the helium nuclei kinematic and therefore allow us 
-to calibrate our drift paths independently of our knowledge of the exact 
+process ($e^{4}$He$\rightarrow e^{4}$He). In this process, measurement of only the 
+electron kinematics gives the Helium nucleus's kinematic and therefore allows 
+to calibrate the drift paths independently of our knowledge of the exact 
 conditions in the chamber.
@@
 The drift paths' parametrization is possible using identified elastic events 
-from our experiment and simulate copy of them in a GEANT4 
-simulation~\cite{GEANT4}. Then by comparing the GEANT4 calculated position of 
-the helium nuclei to the list of hits effectively measured in the chamber, we 
+from our experiment and a simulated copy of them in a GEANT4 
+simulation~\cite{GEANT4}. Then by comparing the calculated GEANT4 position of 
+the Helium nuclei to the corresponding hits measured in the chamber, we 
 can reconstruct the electrons drift path in the RTPC. However, because of the 
 magnetic field, the drift paths are not linear. So to perform the extraction, 
-we make a first assumption of a linear dependence between the radius of 
-emission and the TDC of detection and then refine our result. As it happens, 
+we make a first approximation with a linear dependence between the radius of 
+emission and the TDC of detection, and then refine our result. As it happens, 
 the curvature is minimal and this process converge already on the second 
-iteration. Here are the step of the extraction procedure (we work in a polar 
-coordinate system ($R$,$\phi$), $\Delta\phi$ being the difference between the 
-$\phi$ of the pad measuring a hit and the $\phi$ of the simulated helium):
+iteration.
+
+The steps of the extraction procedure are as follows, where we work
+in a polar coordinate system ($R$,$\phi$).  The azimuthal difference between
+the measured and simulated hit position is $\Delta\phi$.
 
@@
 \includegraphics[scale=0.37]{fig/TdcR_check_p1_10.png}
-\caption{R versus TDC distribution for the simulated hits locating in a single 
-$z$ bin. The maximum $R$ equals 60 mm (close to the anode) at minimum TDCs 
-(Trigger time is 15), and minimum R equals 30 mm (close to the cathode) at 
+\caption{$R$ versus TDC distribution for the simulated hits in a single 
+$z$-bin. The maximum $R$ is 60 mm (close to the anode) at minimum TDCs 
+(the trigger time is 15), and the minimum $R$ is 30 mm (close to the cathode) at 
 maximum TDCs ($\sim75$).}
@@
 
-\begin{itemize}
+\begin{enumerate}
 
-   \item The linear assumption between R and time(TDC) is necessary to link the 
+   \item The linear assumption between R and time (TDC) is necessary to link the 
       generated hits from GEANT4 to physical hits. Figure 
@@
 
-   \item For these selected hits, we look at $\Delta\phi$ ($\Delta \phi$ = 
-      $\phi_{sim.}$ - $\phi_{hit\_pad}$) versus TDC. We clearly obtain a 
-      correlation shown in figure~\ref{fig:1st_pass_delta_phi}. This $\Delta 
-      \phi$ change with TDC shows the azimuthal drift of the electrons due to 
+   \item For these selected hits, we look at $\Delta\phi$ ($\phi_{sim.}-\phi_{hit\_pad}$)
+     versus TDC. We clearly obtain a 
+      correlation shown in figure~\ref{fig:1st_pass_delta_phi}. The relationship
+      between $\Delta\phi$ and TDC encodes the azimuthal drift of the electrons due to 
       the Lorentz angle.
@@
          \caption{$\Delta \phi$ versus TDC distribution for the simulated hits 
-         locating in one slice centered at 35 mm.}
+         with $z$ near 35 mm.}
          \label{fig:1st_pass_delta_phi}
@@
       between $R$ and TDC. The result, shown in figure~\ref{fig:R_TDC}, is very 
-      close to linear explaining the fast convergence of our procedure.
+      close to linear and explains the fast convergence of our procedure.
 
@@
          \includegraphics[scale=0.37]{fig/R_TDC.png}
-         \caption{The calculated R versus the time is corrected by the 
+         \caption{The calculated $R$ versus the time is corrected by the 
          parameters of $\Delta \phi$ from the first pass.}
@@
       can be seen in figure~\ref{fig:DELTA_PHI_TDC}, which shows the final 
-      $\Delta \phi$ versus TDC with a red line representing our drift paths 
+      $\Delta \phi$ versus TDC with a black line representing our drift paths 
       fit.
-\end{itemize}
+\end{enumerate}
 
@@
 \includegraphics[scale=0.37]{fig/FitResult_p2_10.png}
-\caption{$\Delta \phi$ versus TDC distribution in the second pass for the slice 
-centered at 35 mm longitudinal position along the RTPC. The red line represents 
+\caption{$\Delta \phi$ versus TDC distribution in the second pass for tracks
+near 35 mm longitudinal position along the RTPC. The black line represents 
 the final drift paths in this slice.}
@@
 To verify the stability of the drift paths, this procedure was carried out 
-using both the 1.204 GeV data set from the beginning of the run period and the 
-1.269 GeV data from the end of the run period. As a result, we found very 
-similar drift paths and reached the conclusion that whatever changed in the 
-setting affected only the drift speed.
+using both the 1.204 GeV data from the beginning of the run period and the 
+1.269 GeV data from the end of the run period. We found very similar drift paths
+for the two data sets and concluded that any changes in the system only
+significantly affected the drift speed.
 
@@
 over the full RTPC. The gain of each pad is the ratio between the actual 
-deposited energy and the registered ADC value. We identified three different 
-methods to extract such gains. The first is to compare the experimental energy 
-deposit to the expected value calculated from Bethe-Block formula (ref). The 
-second method is to compare the experimental ADCs to the energy deposited in 
+deposited energy and the registered ADC value. We implemented three different 
+methods to extract such gains, with varying degrees of success.
+
+The first method is based on the measured average $\small{\frac{dE}{dX}}$
+and the expected value based on the Bethe-Bloch formula (PDG REF).  The total energy
+deposition for each $^4$He track is calculated as the sum of all ADC hits
+attributed to the track.  The path length of that energy deposition is
+calculated as the distance along the reconstructed trajectory between the first
+and last hits on the track and corrected to account for regions
+of bad channels along the track.  The measured average energy loss is then the
+ratio of deposited energy and path length.  The Bethe-Bloch formula is
+evaluated at the track's reconstructed momentum, and the ratio with the measured
+$\small{\frac{dE}{dX}}$ is taken as a gain scaling factor.  This average gain is
+attributed equally to each readout channel contributing to the track, and each
+channel's gain is averaged over many tracks.  This gain calibration method is
+inherently iterative, and, while it does result in measured $\small{\frac{dE}{dX}}$
+much closer to the expected Bethe-Bloch curve than prior to calibration, the
+results were not very satisfactory.
+
+The second method is to compare the experimental ADCs to the energy deposited in 
 GEANT4 by simulated tracks (using the same elastic events than for the drift 
-paths calibration). In the third method, the ADCs of each pad is compared to 
-the ADCs of the other pads inside each track.
-
-(Detail of 1st method: Nathan)
-
-To perform the second method it requires a very good GEANT4 simulation 
+paths calibration).  This requires a very good GEANT4 simulation 
 including drift paths, but also drift and amplification spreads of the charges 
@@
 
+In the third method, the ADC value of each pad is compared to 
+the ADCs of the other pads inside each track.
 (Detail of 3rd method: Mohammad)
+
+Do you want to show $log(dE/dX)$?
 

### 2017-02-20 analysis-note-vf/results.tex
add subdirectory for the fermi motion study

@@
 Figure \ref{fig:bsa_incoh_bins} shows our measured incoherent beam-spin 
-asymmetries, for the three sets of the two-dimensional bins as for the coherent 
-channel. The $Q^2$, $x_{B}$, and $-t$-dependencies of $A_{LU}$ at 
+asymmetries, for the three sets of the two-dimensional bins as for the 
+incoherent channel. The $Q^2$, $x_{B}$, and $-t$-dependencies of $A_{LU}$ at 
 $\phi$=~90$^{\circ}$ (the $\alpha$ parameter of the fit) are shown in figure 

### 2017-02-20 for_eg6_group/incoh-2/Incoh.tex
add subdirectory for the fermi motion study

%\documentclass[a4paper,11pt,twoside]{ThesisStyle}
\documentclass[a4paper,11pt,twoside]{article}

\date{\today}
\include{formatAndDefs}
\begin{document}

\title{\centering{Investigating the Fermi motion effects on the incoherent DVCS 
channel}}
\maketitle

In our DVCS analysis, we considered the initial proton of the incoherent 
channel to be at rest, while this is not totally true because of the Fermi 
motion. Does this assumption is a good approximation? what other options can be 
used to minimize this effect on the calculated exclusive quantities?\\

Figure \ref{fig:handbag} presents the leading order handbag diagram of the 
incoherent DVCS channel off $^4$He, where the nucleus breaks and the DVCS 
occurs on a bound nucleon. Ideally, the transferred momentum squared ($t$) is 
defined using the initial and the final nucleons' 4-vectors as $(p-p')^{2}$.  
Then as a DVCS requirement, $t$ has to be greater than a certain value 
($t_{min}$), that is defined using the kinematics of the incoming and the 
scattered electrons. Due to the knowledge lack of the initial proton's 
momentum, this cut maybe inaccurate causes loosing some good DVCS events. In 
this work, we try to tackle this issue and check the stability of the 
reconstructed beam-spin asymmetry, as being our DVCS observable.\\

\begin{figure}[h!]
\includegraphics[height=10.0cm]{fig/handbag_incoherent.pdf}
\caption{Representation of the leading order handbag diagram of the incoherent 
DVCS process off $^4$He}
\label{fig:handbag}
\end{figure}

Typically, the transferred momentum squared $t$ is equal to the transferred 
momentum squared ($t'$) defined between the virtual photon and the final-state 
real photon, as shown in Figure \ref{fig:handbag}.  While defining the momentum 
transferred as $t'$ is a good way to pass the Fermi motion effect on the 
initial bound proton, it is more smeared than than $t$ due to bigger energy 
resolutions of the photons. Figure \ref{fig:tprime} shows the distributions of 
the coherent and the incoherent relative difference between $t$ and $t'$. One 
can see that the coherent DVCS channel, the distributions is symmetric and 
centered at zero as expected due to our good knowledge on the initial $^4$He 
target, while it is not exactly the case for the incoherent case due to the 
Fermi motion.\\

\begin{figure}[h!]
\includegraphics[height=5.0cm]{fig/T_tprime_Coh.png}
\includegraphics[height=5.0cm]{fig/T_tprime_InCoh.png}
\caption{On the left: the coherent relative difference between $t$ and $t'$.  
On the right: the incoherent relative difference.}
\label{fig:tprime}
\end{figure}

In the following, we check the effects of defining the transferred momentum 
squared as $t$ and $t'$ on the exclusive distributions and on the reconstructed 
beam-spin asymmetries. Figure \ref{fig:cuts_t} presents the exclusive 
distributions of the incoherent DVCS events where the transferred momentum
squared is defined as $t$, while it is define as $t'$ in figure 
\ref{fig:cuts_tprime}. To minimize the smearing effects of $t'$ on the 
exclusive distributions, 2$\sigma$ exclusive cuts were optimized compared to 
3$\sigma$ cuts which were applied in the $t$ case. In terms of collected 
statistics, the 2$\sigma$ cuts using $t'$ gave almost the same statistics using 
$t$. From comparing the exclusive distributions, especially the $ep\gamma$ 
missing energy and the missing mass squared, one sees that using $t'$ gives 
more Gaussian missing energy distributions and cleaner missing mass squared 
distribution.\\

\begin{figure}[h!]
\includegraphics[height=15.0cm]{fig/old_all_incoh_exc_cuts.pdf}
\caption{The old set of exclusive cuts with $t$>$t_{min}$. The black
   distributions represent the incoherent DVCS events candidate. The shaded
   distributions represent the events which passed all the exclusivity cuts
   except the quantity plotted. The vertical red lines represent the applied
exclusivity, 3$\sigma$ cuts.}
\label{fig:cuts_t}
\end{figure}

\begin{figure}[h!]
   \includegraphics[height=15.0cm]{fig/all_incoh_exc_cuts_test.pdf}
   \caption{New set of exclusive cuts with $t'$>$t_{min}$. The black
      distributions represent the incoherent DVCS events candidate. The shaded
      distributions represent the events which passed all the exclusivity cuts
      except the quantity plotted. The vertical red lines represent the applied 
   exclusivity, 2$\sigma$ cuts.}
\label{fig:cuts_tprime}
\end{figure}

Figure \ref{fig:bsa_incoh_bins} shows our measured incoherent beam-spin
asymmetries, for the three sets of the two-dimensional bins, in the two 
scinarios of defining the transferred momentum squared. The $Q^2$, $x_{B}$, and 
$-t$-dependencies of $A_{LU}$ at $\phi$=~90$^{\circ}$ (the $\alpha$ parameter 
of the fit) are shown in figure \ref{fig:incoh_Q2_xB_t_ALU}.

\begin{figure}[h!]
   \includegraphics[height=6.0cm]{fig/ALU_phi_p_Q2.pdf}
   \includegraphics[height=6.0cm]{fig/ALU_phi_p_x.pdf}
   \includegraphics[height=6.0cm]{fig/ALU_phi_p_t.pdf}
\caption{The reconstructed incoherent $A_{LU}$ as a function of the angle 
   $\phi$ in $Q^2$, $x_B$, and $-t$ bins, respectively from top to bottom using 
$t$>$t_{min}$ in black squares, and $t'$>$t_{min}$ in red squares.}
   \label{fig:bsa_incoh_bins}
\end{figure}

\begin{figure}[h!]
   \centering
   \includegraphics[height=6.0cm]{fig/ALU_90_p_vs_Q2_shortscenrario.pdf}\\
   \includegraphics[height=6.0cm]{fig/ALU_90_p_vs_x_shortscenrario.pdf}\\
   \includegraphics[height=6.0cm]{fig/ALU_90_p_vs_t_shortscenrario.pdf}
   \caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $-t$-dependencies (bottom) 
      of the incoherent $A_{LU}$ at $\phi$~=~90$^{\circ}$, using the 
   $t$>$t_{min}$ cut and the corresponding exclusive cuts in black squares, and 
in red squares using the $t'$>$t_{min}$ and it's exclusive cuts.  The curves 
are theoretical calculations. On the bottom: the green circles are the HERMES 
$-A_{LU}$ (positron beam was used) inclusive measurements.}
\label{fig:incoh_Q2_xB_t_ALU}
\end{figure}

\section*{Conclusions}
In summary, we have studied the effects of Fermi motion on the measured 
incoherent beam-spin asymmetries by defining the transferred momentum squared 
through the nucleons in one case and through the photons in the other case. In 
terms of collected statistics, 2$\sigma$ exclusive cuts using the photons 
produced the same statistics as 3$\sigma$ cuts. The exclusive distributions 
using $t'$, through the photons, have shown more acceptable distributions in 
terms of being more symmetric in some cases and cleaner on others. The 
reconstructed asymmetries in the two cases of defining the transferred momentum 
squared are compatible and while the given error bars. As a suggestion, we 
would like to consider the $t'$ analysis as the final set for publications 
unless a major objections appear.

\end{document}

### 2017-02-25 analysis-note-vf/Appendix.tex
update the note and the coherent paper with the latest plots
added a subdirectory for eg6 comments on the coherent paper and another subdirectory for the incoherent channel inestigation.

@@
          \hline
-  1.143 & 0.136 & 0.096 & 24.0  &  0.1575 $\pm$  0.1016 $\pm$ 0.0257 \\
-  1.143 & 0.136 & 0.096 & 60.0  &  0.3656 $\pm$  0.0903 $\pm$ 0.0188 \\
-  1.143 & 0.136 & 0.096 & 98.5  &  0.3586 $\pm$  0.1051 $\pm$ 0.0403 \\
-  1.143 & 0.136 & 0.096 & 141.2 &  0.1498 $\pm$  0.1645 $\pm$ 0.0267 \\
-  1.143 & 0.136 & 0.096 & 177.7 &  0.1849 $\pm$  0.1664 $\pm$ 0.0278 \\
-  1.143 & 0.136 & 0.096 & 219.3 &  0.0555 $\pm$  0.1475 $\pm$ 0.0248 \\
-  1.143 & 0.136 & 0.096 & 263.4 & -0.3184 $\pm$  0.1171 $\pm$ 0.0389 \\
-  1.143 & 0.136 & 0.096 & 302.7 & -0.1160 $\pm$  0.0975 $\pm$ 0.0263 \\
-  1.143 & 0.136 & 0.096 & 337.9 & -0.2805 $\pm$  0.0952 $\pm$ 0.0343 \\
-  \hline                                                               
-  1.423 & 0.172 & 0.099 & 21.1  &  0.1694 $\pm$  0.0858 $\pm$ 0.0267 \\
-  1.423 & 0.172 & 0.099 & 55.9  &  0.2889 $\pm$  0.0859 $\pm$ 0.0250 \\
-  1.423 & 0.172 & 0.099 & 96.7  &  0.4761 $\pm$  0.1304 $\pm$ 0.0426 \\
-  1.423 & 0.172 & 0.099 & 138.9 &  0.2134 $\pm$  0.1784 $\pm$ 0.0250 \\
-  1.423 & 0.172 & 0.099 & 179.8 &  0.2996 $\pm$  0.1967 $\pm$ 0.0302 \\
-  1.423 & 0.172 & 0.099 & 218.7 & -0.2375 $\pm$  0.1913 $\pm$ 0.0344 \\
-  1.423 & 0.172 & 0.099 & 263.5 & -0.2521 $\pm$  0.1398 $\pm$ 0.0366 \\
-  1.423 & 0.172 & 0.099 & 302.6 & -0.3526 $\pm$  0.0855 $\pm$ 0.0383 \\
-  1.423 & 0.172 & 0.099 & 338.0 & -0.2344 $\pm$  0.0801 $\pm$ 0.0261 \\
-  \hline                                                               
-  1.902 & 0.224 & 0.107 & 21.0  &  0.1626 $\pm$  0.0779 $\pm$ 0.0234 \\
-  1.902 & 0.224 & 0.107 & 56.4  &  0.3433 $\pm$  0.0817 $\pm$ 0.0185 \\
-  1.902 & 0.224 & 0.107 & 95.9  &  0.2443 $\pm$  0.1270 $\pm$ 0.0173 \\
-  1.902 & 0.224 & 0.107 & 138.6 &  0.4026 $\pm$  0.2333 $\pm$ 0.0170 \\
-  1.902 & 0.224 & 0.107 & 179.8 &  0.0514 $\pm$  0.2906 $\pm$ 0.0126 \\
-  1.902 & 0.224 & 0.107 & 222.7 & -0.0281 $\pm$  0.2275 $\pm$ 0.0152 \\
-  1.902 & 0.224 & 0.107 & 264.5 & -0.2909 $\pm$  0.1379 $\pm$ 0.0260 \\
-  1.902 & 0.224 & 0.107 & 303.5 & -0.1011 $\pm$  0.0940 $\pm$ 0.0207 \\
-  1.902 & 0.224 & 0.107 & 338.9 & -0.1661 $\pm$  0.0773 $\pm$ 0.0163 \\
+  1.143 & 0.136 & 0.096 & 24.3  &  0.1327 $\pm$ 0.1088 $\pm$ 0.0257 \\                                             
+  1.143 & 0.136 & 0.096 & 61.1  &  0.3210 $\pm$ 0.0932 $\pm$ 0.0188 \\                                             
+  1.143 & 0.136 & 0.096 & 98.9  &  0.3709 $\pm$ 0.1026 $\pm$ 0.0403 \\                                             
+  1.143 & 0.136 & 0.096 & 140.9 &  0.2452 $\pm$ 0.1517 $\pm$ 0.0267 \\                                             
+  1.143 & 0.136 & 0.096 & 178.4 &  0.0225 $\pm$ 0.1632 $\pm$ 0.0278 \\                                             
+  1.143 & 0.136 & 0.096 & 219.1 & -0.0526 $\pm$ 0.1475 $\pm$ 0.0248 \\                                             
+  1.143 & 0.136 & 0.096 & 262.9 & -0.2642 $\pm$ 0.1196 $\pm$ 0.0389 \\                                             
+  1.143 & 0.136 & 0.096 & 301.9 & -0.1761 $\pm$ 0.0968 $\pm$ 0.0263 \\                                             
+  1.143 & 0.136 & 0.096 & 337.7 & -0.2791 $\pm$ 0.1047 $\pm$ 0.0343 \\                                             
+  \hline                                                                                                           
+  1.423 & 0.172 & 0.099 & 21.1  &  0.1917 $\pm$ 0.0892 $\pm$ 0.0267 \\                                             
+  1.423 & 0.172 & 0.099 & 56.6  &  0.2819 $\pm$ 0.0866 $\pm$ 0.0250 \\                                             
+  1.423 & 0.172 & 0.099 & 96.9  &  0.4855 $\pm$ 0.1291 $\pm$ 0.0426 \\                                             
+  1.423 & 0.172 & 0.099 & 139.9 &  0.0996 $\pm$ 0.1679 $\pm$ 0.0250 \\                                             
+  1.423 & 0.172 & 0.099 & 180.3 &  0.1458 $\pm$ 0.1906 $\pm$ 0.0302 \\                                             
+  1.423 & 0.172 & 0.099 & 218.7 & -0.1109 $\pm$ 0.1853 $\pm$ 0.0344 \\                                             
+  1.423 & 0.172 & 0.099 & 263.1 & -0.3516 $\pm$ 0.1371 $\pm$ 0.0366 \\                                             
+  1.423 & 0.172 & 0.099 & 302.2 & -0.4141 $\pm$ 0.0842 $\pm$ 0.0383 \\                                             
+  1.423 & 0.172 & 0.099 & 338.2 & -0.2786 $\pm$ 0.0836 $\pm$ 0.0261 \\                                             
+  \hline                                                                                                           
+  1.902 & 0.224 & 0.107 & 21.4  &  0.1803 $\pm$ 0.0805 $\pm$ 0.0234 \\                                             
+  1.902 & 0.224 & 0.107 & 57.2  &  0.3501 $\pm$ 0.0824 $\pm$ 0.0185 \\                                             
+  1.902 & 0.224 & 0.107 & 96.2  &  0.2701 $\pm$ 0.1230 $\pm$ 0.0173 \\                                             
+  1.902 & 0.224 & 0.107 & 139.5 &  0.3053 $\pm$ 0.2390 $\pm$ 0.0170 \\                                             
+  1.902 & 0.224 & 0.107 & 178.2 &  0.1028 $\pm$ 0.2670 $\pm$ 0.0126 \\                                             
+  1.902 & 0.224 & 0.107 & 221.4 & -0.2118 $\pm$ 0.2147 $\pm$ 0.0152 \\                                             
+  1.902 & 0.224 & 0.107 & 263.3 & -0.3060 $\pm$ 0.1306 $\pm$ 0.0260 \\                                             
+  1.902 & 0.224 & 0.107 & 303.3 & -0.1384 $\pm$ 0.0944 $\pm$ 0.0207 \\                                             
+  1.902 & 0.224 & 0.107 & 338.5 & -0.1633 $\pm$ 0.0791 $\pm$ 0.0163 \\                                             
          \hline \hline
@@
 
-  1.164 & 0.132 & 0.095 & 25.4  &  0.0441 $\pm$ 0.1329 $\pm$ 0.0221 \\
-  1.164 & 0.132 & 0.095 & 60.8  &  0.4030 $\pm$ 0.0865 $\pm$ 0.0198 \\
-  1.164 & 0.132 & 0.095 & 98.6  &  0.3878 $\pm$ 0.0984 $\pm$ 0.0408 \\
-  1.164 & 0.132 & 0.095 & 141.7 &  0.2957 $\pm$ 0.1524 $\pm$ 0.0333 \\
-  1.164 & 0.132 & 0.095 & 177.2 &  0.2646 $\pm$ 0.1599 $\pm$ 0.0293 \\
-  1.164 & 0.132 & 0.095 & 218.4 &  0.0127 $\pm$ 0.1364 $\pm$ 0.0243 \\
-  1.164 & 0.132 & 0.095 & 263.2 & -0.2955 $\pm$ 0.1063 $\pm$ 0.0372 \\
-  1.164 & 0.132 & 0.095 & 301.6 & -0.1121 $\pm$ 0.0868 $\pm$ 0.0259 \\
-  1.164 & 0.132 & 0.095 & 335.6 & -0.1940 $\pm$ 0.1149 $\pm$ 0.0319 \\
-   \hline                                                             
-  1.439 & 0.17 & 0.099 &  22.8  &  0.1597 $\pm$ 0.0820 $\pm$ 0.0230 \\
-  1.439 & 0.17 & 0.099 &  55.9  &  0.1592 $\pm$ 0.0857 $\pm$ 0.0195 \\
-  1.439 & 0.17 & 0.099 &  96.7  &  0.2178 $\pm$ 0.1320 $\pm$ 0.0295 \\
-  1.439 & 0.17 & 0.099 &  138.7 &  0.3251 $\pm$ 0.1763 $\pm$ 0.0187 \\
-  1.439 & 0.17 & 0.099 &  180.0 & -0.0093 $\pm$ 0.1947 $\pm$ 0.0197 \\
-  1.439 & 0.17 & 0.099 &  219.8 & -0.1457 $\pm$ 0.2000 $\pm$ 0.0270 \\
-  1.439 & 0.17 & 0.099 &  265.0 & -0.2163 $\pm$ 0.1374 $\pm$ 0.0292 \\
-  1.439 & 0.17 & 0.099 &  302.9 & -0.3729 $\pm$ 0.0907 $\pm$ 0.0331 \\
-  1.439 & 0.17 & 0.099 &  337.9 & -0.2505 $\pm$ 0.0791 $\pm$ 0.0254 \\
-   \hline                                                             
-  1.844 & 0.225 & 0.107 & 19.8  &  0.2355 $\pm$ 0.0732 $\pm$ 0.0248 \\
-  1.844 & 0.225 & 0.107 & 55.8  &  0.4399 $\pm$ 0.0870 $\pm$ 0.0224 \\
-  1.844 & 0.225 & 0.107 & 95.6  &  0.4355 $\pm$ 0.1433 $\pm$ 0.0271 \\
-  1.844 & 0.225 & 0.107 & 136.7 & -0.2736 $\pm$ 0.2804 $\pm$ 0.0166 \\
-  1.844 & 0.225 & 0.107 & 182.7 &  0.5956 $\pm$ 0.3142 $\pm$ 0.0204 \\
-  1.844 & 0.225 & 0.107 & 225.5 & -0.1065 $\pm$ 0.2739 $\pm$ 0.0270 \\
-  1.844 & 0.225 & 0.107 & 263.0 & -0.3547 $\pm$ 0.1728 $\pm$ 0.0353 \\
-  1.844 & 0.225 & 0.107 & 304.2 & -0.1088 $\pm$ 0.1008 $\pm$ 0.0263 \\
-  1.844 & 0.225 & 0.107 & 340.0 & -0.1632 $\pm$ 0.0742 $\pm$ 0.0175 \\
+  1.164 & 0.132 & 0.095 & 25.6  &  0.0174 $\pm$ 0.1440 $\pm$ 0.0221 \\                                            
+  1.164 & 0.132 & 0.095 & 61.6  &  0.3478 $\pm$ 0.0867 $\pm$ 0.0198 \\                                            
+  1.164 & 0.132 & 0.095 & 99.0  &  0.3808 $\pm$ 0.0948 $\pm$ 0.0408 \\                                            
+  1.164 & 0.132 & 0.095 & 141.7 &  0.2943 $\pm$ 0.1379 $\pm$ 0.0333 \\                                            
+  1.164 & 0.132 & 0.095 & 178.1 &  0.0433 $\pm$ 0.1519 $\pm$ 0.0293 \\                                            
+  1.164 & 0.132 & 0.095 & 218.5 & -0.0352 $\pm$ 0.1316 $\pm$ 0.0243 \\                                            
+  1.164 & 0.132 & 0.095 & 262.7 & -0.2771 $\pm$ 0.1050 $\pm$ 0.0372 \\                                            
+  1.164 & 0.132 & 0.095 & 300.7 & -0.2138 $\pm$ 0.0836 $\pm$ 0.0259 \\                                            
+  1.164 & 0.132 & 0.095 & 335.2 & -0.2339 $\pm$ 0.1221 $\pm$ 0.0319 \\                                            
+   \hline                                                                                                         
+  1.439 & 0.17 & 0.099 &  22.9  &  0.1579 $\pm$ 0.0853 $\pm$ 0.0230 \\                                            
+  1.439 & 0.17 & 0.099 &  57.1  &  0.1733 $\pm$ 0.0880 $\pm$ 0.0195 \\                                            
+  1.439 & 0.17 & 0.099 &  96.3  &  0.2259 $\pm$ 0.1331 $\pm$ 0.0295 \\                                            
+  1.439 & 0.17 & 0.099 &  139.1 &  0.2454 $\pm$ 0.1758 $\pm$ 0.0187 \\                                            
+  1.439 & 0.17 & 0.099 &  180.1 & -0.1021 $\pm$ 0.1918 $\pm$ 0.0197 \\                                            
+  1.439 & 0.17 & 0.099 &  218.9 & -0.2876 $\pm$ 0.1909 $\pm$ 0.0270 \\                                            
+  1.439 & 0.17 & 0.099 &  263.9 & -0.2943 $\pm$ 0.1360 $\pm$ 0.0292 \\                                            
+  1.439 & 0.17 & 0.099 &  302.5 & -0.3979 $\pm$ 0.0921 $\pm$ 0.0331 \\                                            
+  1.439 & 0.17 & 0.099 &  338.1 & -0.2692 $\pm$ 0.0834 $\pm$ 0.0254 \\                                            
+   \hline                                                                                                         
+  1.844 & 0.225 & 0.107 & 20.1  &  0.2626 $\pm$ 0.0755 $\pm$ 0.0248 \\                                            
+  1.844 & 0.225 & 0.107 & 55.9  &  0.4281 $\pm$ 0.0887 $\pm$ 0.0224 \\                                            
+  1.844 & 0.225 & 0.107 & 96.4  &  0.4925 $\pm$ 0.1390 $\pm$ 0.0271 \\                                            
+  1.844 & 0.225 & 0.107 & 137.7 & -0.2736 $\pm$ 0.2804 $\pm$ 0.0166 \\                                            
+  1.844 & 0.225 & 0.107 & 179.8 &  0.8470 $\pm$ 0.2497 $\pm$ 0.0204 \\                                            
+  1.844 & 0.225 & 0.107 & 224.7 & -0.0513 $\pm$ 0.2811 $\pm$ 0.0270 \\                                            
+  1.844 & 0.225 & 0.107 & 262.8 & -0.3416 $\pm$ 0.1694 $\pm$ 0.0353 \\                                            
+  1.844 & 0.225 & 0.107 & 304.5 & -0.1359 $\pm$ 0.1025 $\pm$ 0.0263 \\                                            
+  1.844 & 0.225 & 0.107 & 339.8 & -0.1658 $\pm$ 0.0770 $\pm$ 0.0175 \\
 
@@
   \hline
-  1.36 & 0.160 & 0.080 & 23.0  &  0.1884 $\pm$ 0.0891 $\pm$ 0.0263 \\
-  1.36 & 0.160 & 0.080 & 57.0  &  0.2973 $\pm$ 0.0848 $\pm$ 0.0243 \\
-  1.36 & 0.160 & 0.080 & 97.6  &  0.4928 $\pm$ 0.1155 $\pm$ 0.0394 \\
-  1.36 & 0.160 & 0.080 & 138.7 &  0.2070 $\pm$ 0.1743 $\pm$ 0.0252 \\
-  1.36 & 0.160 & 0.080 & 178.6 &  0.2466 $\pm$ 0.2021 $\pm$ 0.0371 \\
-  1.36 & 0.160 & 0.080 & 222.1 & -0.1512 $\pm$ 0.1738 $\pm$ 0.0370 \\
-  1.36 & 0.160 & 0.080 & 266.8 & -0.3610 $\pm$ 0.1363 $\pm$ 0.0403 \\
-  1.36 & 0.160 & 0.080 & 300.6 & -0.2254 $\pm$ 0.0953 $\pm$ 0.0294 \\
-  1.36 & 0.160 & 0.080 & 339.4 & -0.1889 $\pm$ 0.0795 $\pm$ 0.0281 \\
-
-         \hline
-
-  1.507 & 0.179 & 0.094 & 20.7  &  0.2291 $\pm$ 0.0874 $\pm$ 0.0267 \\
-  1.507 & 0.179 & 0.094 & 55.4  &  0.3684 $\pm$ 0.0814 $\pm$ 0.0284 \\
-  1.507 & 0.179 & 0.094 & 97.6  &  0.2149 $\pm$ 0.1193 $\pm$ 0.0307 \\
-  1.507 & 0.179 & 0.094 & 141.4 &  0.0640 $\pm$ 0.2113 $\pm$ 0.0215 \\
-  1.507 & 0.179 & 0.094 & 178.3 & -0.2712 $\pm$ 0.1944 $\pm$ 0.0360 \\
-  1.507 & 0.179 & 0.094 & 219.0 &  0.1647 $\pm$ 0.2000 $\pm$ 0.0147 \\
-  1.507 & 0.179 & 0.094 & 263.4 & -0.1991 $\pm$ 0.1284 $\pm$ 0.0283 \\
-  1.507 & 0.179 & 0.094 & 303.8 & -0.1605 $\pm$ 0.0968 $\pm$ 0.0286 \\
-  1.507 & 0.179 & 0.094 & 338.7 & -0.1862 $\pm$ 0.0839 $\pm$ 0.0201 \\
-\hline                                                                
-  1.610 & 0.193 & 0.127 & 21.9  &  0.0517 $\pm$ 0.0882 $\pm$ 0.0214 \\
-  1.610 & 0.193 & 0.127 & 59.8  &  0.3527 $\pm$ 0.0934 $\pm$ 0.0204 \\
-  1.610 & 0.193 & 0.127 & 96.4  &  0.3404 $\pm$ 0.1265 $\pm$ 0.0313 \\
-  1.610 & 0.193 & 0.127 & 139.9 &  0.3285 $\pm$ 0.1842 $\pm$ 0.0203 \\
-  1.610 & 0.193 & 0.127 & 179.5 &  0.6863 $\pm$ 0.1731 $\pm$ 0.0354 \\
-  1.610 & 0.193 & 0.127 & 218.7 & -0.0617 $\pm$ 0.1731 $\pm$ 0.0189 \\
-  1.610 & 0.193 & 0.127 & 261.1 & -0.2876 $\pm$ 0.1321 $\pm$ 0.0327 \\
-  1.610 & 0.193 & 0.127 & 303.7 & -0.2077 $\pm$ 0.0882 $\pm$ 0.0280 \\
-  1.610 & 0.193 & 0.127 & 336.8 & -0.2645 $\pm$ 0.0881 $\pm$ 0.0261 \\
-
+  1.36 & 0.160 & 0.080  & 22.8  &  0.2378 $\pm$ 0.0928 $\pm$ 0.0263 \\                                            
+  1.36 & 0.160 & 0.080  & 57.6  &  0.3014 $\pm$ 0.0874 $\pm$ 0.0243 \\                                            
+  1.36 & 0.160 & 0.080  & 98.1  &  0.4896 $\pm$ 0.1118 $\pm$ 0.0394 \\                                            
+  1.36 & 0.160 & 0.080  & 139.3 &  0.1965 $\pm$ 0.1595 $\pm$ 0.0252 \\                                            
+  1.36 & 0.160 & 0.080  & 178.8 &  0.0577 $\pm$ 0.1923 $\pm$ 0.0371 \\                                            
+  1.36 & 0.160 & 0.080  & 222.6 & -0.1651 $\pm$ 0.1640 $\pm$ 0.0370 \\                                            
+  1.36 & 0.160 & 0.080  & 265.6 & -0.3467 $\pm$ 0.1339 $\pm$ 0.0403 \\                                            
+  1.36 & 0.160 & 0.080  & 300.0 & -0.2891 $\pm$ 0.0928 $\pm$ 0.0294 \\                                            
+  1.36 & 0.160 & 0.080  & 339.3 & -0.1849 $\pm$ 0.0856 $\pm$ 0.0281 \\                                            
+  \hline                                                                
+  1.507 & 0.179 & 0.094 & 21.1  &  0.2481 $\pm$ 0.0931 $\pm$ 0.0267 \\                                            
+  1.507 & 0.179 & 0.094 & 56.4  &  0.3386 $\pm$ 0.0828 $\pm$ 0.0284 \\                                            
+  1.507 & 0.179 & 0.094 & 97.5  &  0.3467 $\pm$ 0.1156 $\pm$ 0.0307 \\                                            
+  1.507 & 0.179 & 0.094 & 141.9 &  0.1464 $\pm$ 0.1887 $\pm$ 0.0215 \\                                            
+  1.507 & 0.179 & 0.094 & 179.5 & -0.2814 $\pm$ 0.1864 $\pm$ 0.0360 \\                                            
+  1.507 & 0.179 & 0.094 & 218.5 &  0.2104 $\pm$ 0.1998 $\pm$ 0.0147 \\                                            
+  1.507 & 0.179 & 0.094 & 262.8 & -0.2399 $\pm$ 0.1280 $\pm$ 0.0283 \\                                            
+  1.507 & 0.179 & 0.094 & 303.5 & -0.1989 $\pm$ 0.0955 $\pm$ 0.0286 \\                                            
+  1.507 & 0.179 & 0.094 & 338.5 & -0.2098 $\pm$ 0.0875 $\pm$ 0.0201 \\                                            
+  \hline                                                                                                                 
+  1.610 & 0.193 & 0.127 & 22.3  &  0.0280 $\pm$ 0.0909 $\pm$ 0.0214 \\                                            
+  1.610 & 0.193 & 0.127 & 60.7  &  0.3582 $\pm$ 0.0932 $\pm$ 0.0204 \\                                            
+  1.610 & 0.193 & 0.127 & 96.8  &  0.2559 $\pm$ 0.1269 $\pm$ 0.0313 \\                                            
+  1.610 & 0.193 & 0.127 & 139.9 &  0.2207 $\pm$ 0.1930 $\pm$ 0.0203 \\                                            
+  1.610 & 0.193 & 0.127 & 178.5 &  0.5138 $\pm$ 0.1832 $\pm$ 0.0354 \\                                            
+  1.610 & 0.193 & 0.127 & 217.5 & -0.2473 $\pm$ 0.1664 $\pm$ 0.0189 \\                                            
+  1.610 & 0.193 & 0.127 & 260.9 & -0.2919 $\pm$ 0.1295 $\pm$ 0.0327 \\                                            
+  1.610 & 0.193 & 0.127 & 303.4 & -0.2488 $\pm$ 0.0892 $\pm$ 0.0280 \\                                            
+  1.610 & 0.193 & 0.127 & 336.8 & -0.2825 $\pm$ 0.0901 $\pm$ 0.0261 \\                                            
          \hline
@@
  \hline 
-
-   1.395 & 0.166 & 0.407  & 21.1  &  0.0458   $\pm$  0.0468   $\pm$   0.0120\\
-   1.395 & 0.166 & 0.407  & 61.3  &  0.0844   $\pm$  0.0539   $\pm$   0.0156  \\
-   1.395 & 0.166 & 0.407  & 95.8  &  0.1808   $\pm$  0.0540   $\pm$   0.0263  \\
-   1.395 & 0.166 & 0.407  & 140.0 &  0.0467   $\pm$  0.0698   $\pm$   0.0158  \\
-   1.395 & 0.166 & 0.407  & 181.9 &  0.1255   $\pm$  0.0856   $\pm$   0.0234  \\
-   1.395 & 0.166 & 0.407  & 219.0 &  0.0400   $\pm$  0.0781   $\pm$   0.0150  \\
-   1.395 & 0.166 & 0.407  & 259.0 & -0.1447   $\pm$  0.0521   $\pm$   0.0226  \\
-   1.395 & 0.166 & 0.407  & 303.8 & -0.1555   $\pm$  0.0462   $\pm$   0.0196  \\
-   1.395 & 0.166 & 0.407  & 337.5 & -0.0785   $\pm$  0.0548   $\pm$   0.0142  \\
-  \hline                                                                        
-   1.886 & 0.233 & 0.499  & 20.6  & -0.0028   $\pm$  0.0393   $\pm$   0.0124  \\
-   1.886 & 0.233 & 0.499  & 58.8  &  0.1047   $\pm$  0.0546   $\pm$   0.0169  \\
-   1.886 & 0.233 & 0.499  & 95.9  &  0.1340   $\pm$  0.0630   $\pm$   0.0202  \\
-   1.886 & 0.233 & 0.499  & 141.0 &  0.2096   $\pm$  0.1020   $\pm$   0.0285  \\
-   1.886 & 0.233 & 0.499  & 179.9 &  0.0636   $\pm$  0.1168   $\pm$   0.0146  \\
-   1.886 & 0.233 & 0.499  & 220.9 & -0.3552   $\pm$  0.0996   $\pm$   0.0430  \\
-   1.886 & 0.233 & 0.499  & 260.6 & -0.1227   $\pm$  0.0663   $\pm$   0.0180  \\
-   1.886 & 0.233 & 0.499  & 304.3 & -0.1557   $\pm$  0.0456   $\pm$   0.0198  \\
-   1.886 & 0.233 & 0.499  & 338.3 & -0.0539   $\pm$  0.0480   $\pm$   0.0113  \\
-  \hline                                                                        
-   2.338 & 0.29 & 0.521   & 20.8  &  0.0846   $\pm$  0.0380   $\pm$   0.0135  \\
-   2.338 & 0.29 & 0.521   & 57.0  &  0.1536   $\pm$  0.0565   $\pm$   0.0101  \\
-   2.338 & 0.29 & 0.521   & 94.9  &  0.0748   $\pm$  0.0740   $\pm$   0.0176  \\
-   2.338 & 0.29 & 0.521   & 141.5 &  0.1261   $\pm$  0.1354   $\pm$   0.0161  \\
-   2.338 & 0.29 & 0.521   & 181.4 & -0.1884   $\pm$  0.1518   $\pm$   0.0236  \\
-   2.338 & 0.29 & 0.521   & 224.3 &  0.1556   $\pm$  0.1398   $\pm$   0.0212  \\
-   2.338 & 0.29 & 0.521   & 261.1 & -0.2427   $\pm$  0.0761   $\pm$   0.0241  \\
-   2.338 & 0.29 & 0.521   & 303.8 & -0.1815   $\pm$  0.0479   $\pm$   0.0153  \\
-   2.338 & 0.29 & 0.521   & 339.3 & -0.0523   $\pm$  0.0446   $\pm$   0.0145  \\
-  \hline                                                                        
-   3.098 &0.379 & 0.65    & 20.0  &  0.1118   $\pm$  0.0360   $\pm$   0.0147  \\
-   3.098 &0.379 & 0.65    & 57.1  &  0.0748   $\pm$  0.0554   $\pm$   0.0147  \\
-   3.098 &0.379 & 0.65    & 95.6  &  0.1828   $\pm$  0.0824   $\pm$   0.0281  \\
-   3.098 &0.379 & 0.65    & 137.9 &  0.0110   $\pm$  0.1556   $\pm$   0.0129  \\
-   3.098 &0.379 & 0.65    & 179.3 & -0.5153   $\pm$  0.2431   $\pm$   0.0270  \\
-   3.098 &0.379 & 0.65    & 227.8 &  0.1851   $\pm$  0.2047   $\pm$   0.0273  \\
-   3.098 &0.379 & 0.65    & 263.4 & -0.1140   $\pm$  0.1028   $\pm$   0.0214  \\
-   3.098 &0.379 & 0.65    & 303.9 & -0.1947   $\pm$  0.0501   $\pm$   0.0221  \\
-   3.098 &0.379 & 0.65    & 340.3 & -0.0634   $\pm$  0.0414   $\pm$   0.0141  \\
-
+   1.395 & 0.166 & 0.407 & 21.2  &  0.0641 $\pm$ 0.0456 $\pm$ 0.0120 \\
+   1.395 & 0.166 & 0.407 & 62.1  &  0.0820 $\pm$ 0.0486 $\pm$ 0.0156 \\
+   1.395 & 0.166 & 0.407 & 95.4  &  0.2205 $\pm$ 0.0488 $\pm$ 0.0263 \\
+   1.395 & 0.166 & 0.407 & 139.8 &  0.0623 $\pm$ 0.0590 $\pm$ 0.0158 \\
+   1.395 & 0.166 & 0.407 & 182.2 &  0.0324 $\pm$ 0.0736 $\pm$ 0.0234 \\
+   1.395 & 0.166 & 0.407 & 219.4 &  0.0042 $\pm$ 0.0686 $\pm$ 0.0150 \\
+   1.395 & 0.166 & 0.407 & 258.2 & -0.1746 $\pm$ 0.0476 $\pm$ 0.0226 \\
+   1.395 & 0.166 & 0.407 & 303.4 & -0.1058 $\pm$ 0.0425 $\pm$ 0.0196 \\
+   1.395 & 0.166 & 0.407 & 337.5 & -0.0506 $\pm$ 0.0535 $\pm$ 0.0142 \\
+  \hline                                                               
+   1.886 & 0.233 & 0.499 & 20.5  & -0.0108 $\pm$ 0.0368 $\pm$ 0.0124 \\
+   1.886 & 0.233 & 0.499 & 60.0  &  0.0913 $\pm$ 0.0499 $\pm$ 0.0169 \\
+   1.886 & 0.233 & 0.499 & 95.9  &  0.1217 $\pm$ 0.0549 $\pm$ 0.0202 \\
+   1.886 & 0.233 & 0.499 & 140.4 &  0.1636 $\pm$ 0.0825 $\pm$ 0.0285 \\
+   1.886 & 0.233 & 0.499 & 180.2 &  0.1547 $\pm$ 0.0955 $\pm$ 0.0146 \\
+   1.886 & 0.233 & 0.499 & 221.7 & -0.3104 $\pm$ 0.0881 $\pm$ 0.0430 \\
+   1.886 & 0.233 & 0.499 & 260.4 & -0.1210 $\pm$ 0.0594 $\pm$ 0.0180 \\
+   1.886 & 0.233 & 0.499 & 303.7 & -0.1937 $\pm$ 0.0414 $\pm$ 0.0198 \\
+   1.886 & 0.233 & 0.499 & 338.2 &  0.0015 $\pm$ 0.0460 $\pm$ 0.0113 \\
+  \hline                                                               
+   2.338 & 0.29 & 0.521  & 20.8  &  0.0995 $\pm$ 0.0351 $\pm$ 0.0135 \\
+   2.338 & 0.29 & 0.521  & 58.0  &  0.1429 $\pm$ 0.0506 $\pm$ 0.0101 \\
+   2.338 & 0.29 & 0.521  & 95.0  &  0.1229 $\pm$ 0.0609 $\pm$ 0.0176 \\
+   2.338 & 0.29 & 0.521  & 141.0 &  0.0447 $\pm$ 0.1034 $\pm$ 0.0161 \\
+   2.338 & 0.29 & 0.521  & 182.4 &  0.0946 $\pm$ 0.1361 $\pm$ 0.0236 \\
+   2.338 & 0.29 & 0.521  & 224.7 &  0.0720 $\pm$ 0.1129 $\pm$ 0.0212 \\
+   2.338 & 0.29 & 0.521  & 260.8 & -0.2414 $\pm$ 0.0623 $\pm$ 0.0241 \\
+   2.338 & 0.29 & 0.521  & 303.4 & -0.2037 $\pm$ 0.0417 $\pm$ 0.0153 \\
+   2.338 & 0.29 & 0.521  & 339.1 & -0.0854 $\pm$ 0.0419 $\pm$ 0.0145 \\
+  \hline                                                               
+   3.098 &0.379 & 0.65   & 20.0  &  0.1025 $\pm$ 0.0327 $\pm$ 0.0147 \\
+   3.098 &0.379 & 0.65   & 57.3  &  0.0915 $\pm$ 0.0501 $\pm$ 0.0147 \\
+   3.098 &0.379 & 0.65   & 94.4  &  0.1381 $\pm$ 0.0714 $\pm$ 0.0281 \\
+   3.098 &0.379 & 0.65   & 138.0 &  0.1012 $\pm$ 0.1458 $\pm$ 0.0129 \\
+   3.098 &0.379 & 0.65   & 179.9 & -0.4236 $\pm$ 0.1925 $\pm$ 0.0270 \\
+   3.098 &0.379 & 0.65   & 226.6 &  0.1298 $\pm$ 0.1728 $\pm$ 0.0273 \\
+   3.098 &0.379 & 0.65   & 263.6 & -0.1795 $\pm$ 0.0883 $\pm$ 0.0214 \\
+   3.098 &0.379 & 0.65   & 303.2 & -0.1856 $\pm$ 0.0447 $\pm$ 0.0221 \\
+   3.098 &0.379 & 0.65   & 340.3 & -0.0677 $\pm$ 0.0387 $\pm$ 0.0141 \\
  \hline
@@
          \hline
-  1.425 & 0.162 & 0.397 & 21.0  &  0.0851   $\pm$   0.0499   $\pm$   0.0137  \\
-  1.425 & 0.162 & 0.397 & 62.1  &  0.0962   $\pm$   0.0523   $\pm$   0.0165  \\
-  1.425 & 0.162 & 0.397 & 95.9  &  0.1472   $\pm$   0.0512   $\pm$   0.0216  \\
-  1.425 & 0.162 & 0.397 & 140.2 &  0.0597   $\pm$   0.0664   $\pm$   0.0149  \\
-  1.425 & 0.162 & 0.397 & 181.1 &  0.1512   $\pm$   0.0787   $\pm$   0.0235  \\
-  1.425 & 0.162 & 0.397 & 218.9 & -0.0048   $\pm$   0.0739   $\pm$   0.0199  \\
-  1.425 & 0.162 & 0.397 & 259.1 & -0.1158   $\pm$   0.0501   $\pm$   0.0183  \\
-  1.425 & 0.162 & 0.397 & 303.9 & -0.1144   $\pm$   0.0456   $\pm$   0.0154  \\
-  1.425 & 0.162 & 0.397 & 337.0 & -0.0259   $\pm$   0.0593   $\pm$   0.0105  \\
-  \hline                                                                       
-  1.922 & 0.227 & 0.418 & 22.0  & -0.0075   $\pm$   0.0418   $\pm$   0.0131  \\
-  1.922 & 0.227 & 0.418 & 58.6  &  0.0927   $\pm$   0.0521   $\pm$   0.0161  \\
-  1.922 & 0.227 & 0.418 & 96.2  &  0.1255   $\pm$   0.0609   $\pm$   0.0183  \\
-  1.922 & 0.227 & 0.418 & 141.5 &  0.1686   $\pm$   0.0984   $\pm$   0.0246  \\
-  1.922 & 0.227 & 0.418 & 181.9 & -0.0727   $\pm$   0.1182   $\pm$   0.0165  \\
-  1.922 & 0.227 & 0.418 & 221.3 & -0.2948   $\pm$   0.0996   $\pm$   0.0343  \\
-  1.922 & 0.227 & 0.418 & 260.3 & -0.1894   $\pm$   0.0620   $\pm$   0.0227  \\
-  1.922 & 0.227 & 0.418 & 303.5 & -0.1977   $\pm$   0.0445   $\pm$   0.0206  \\
-  1.922 & 0.227 & 0.418 & 337.3 & -0.0491   $\pm$   0.0488   $\pm$   0.0100  \\
-  \hline                                                                       
-  2.354 & 0.287 & 0.492 & 20.9  &  0.0491   $\pm$   0.0367   $\pm$   0.0198  \\
-  2.354 & 0.287 & 0.492 & 58.0  &  0.1337   $\pm$   0.0538   $\pm$   0.0195  \\
-  2.354 & 0.287 & 0.492 & 94.8  &  0.1534   $\pm$   0.0730   $\pm$   0.0188  \\
-  2.354 & 0.287 & 0.492 & 140.0 &  0.1744   $\pm$   0.1359   $\pm$   0.0242  \\
-  2.354 & 0.287 & 0.492 & 179.7 & -0.3678   $\pm$   0.1619   $\pm$   0.0145  \\
-  2.354 & 0.287 & 0.492 & 226.0 &  0.3453   $\pm$   0.1400   $\pm$   0.0140  \\
-  2.354 & 0.287 & 0.492 & 261.5 & -0.2282   $\pm$   0.0813   $\pm$   0.0272  \\
-  2.354 & 0.287 & 0.492 & 304.3 & -0.1633   $\pm$   0.0449   $\pm$   0.0178  \\
-  2.354 & 0.287 & 0.492 & 338.8 & -0.0690   $\pm$   0.0439   $\pm$   0.0101  \\
- \hline                                                                        
-  2.987 & 0.390 & 0.714 & 19.4  &  0.1056   $\pm$   0.0343   $\pm$   0.0143  \\
-  2.987 & 0.390 & 0.714 & 55.3  &  0.0876   $\pm$   0.0639   $\pm$   0.0148  \\
-  2.987 & 0.390 & 0.714 & 95.2  &  0.1853   $\pm$   0.1072   $\pm$   0.0313  \\
-  2.987 & 0.390 & 0.714 & 134.7 & -0.1877   $\pm$   0.2731   $\pm$   0.0386  \\
-  2.987 & 0.390 & 0.714 & 182.5 & -0.1941   $\pm$   1.1518   $\pm$   0.0364  \\
-  2.987 & 0.390 & 0.714 & 232.2 & -0.2499   $\pm$   0.4586   $\pm$   0.0469  \\
-  2.987 & 0.390 & 0.714 & 264.9 & -0.0713   $\pm$   0.1344   $\pm$   0.0202  \\
-  2.987 & 0.390 & 0.714 & 304.2 & -0.2116   $\pm$   0.0565   $\pm$   0.0229  \\
-  2.987 & 0.390 & 0.714 & 341.1 & -0.0758   $\pm$   0.0401   $\pm$   0.0156  \\
-
+  1.425 & 0.162 & 0.397 & 21.1  &  0.1016 $\pm$ 0.0470 $\pm$ 0.0137 \\
+  1.425 & 0.162 & 0.397 & 63.0  &  0.0703 $\pm$ 0.0463 $\pm$ 0.0165 \\
+  1.425 & 0.162 & 0.397 & 95.6  &  0.1623 $\pm$ 0.0454 $\pm$ 0.0216 \\
+  1.425 & 0.162 & 0.397 & 140.1 &  0.0485 $\pm$ 0.0545 $\pm$ 0.0149 \\
+  1.425 & 0.162 & 0.397 & 181.4 &  0.0863 $\pm$ 0.0664 $\pm$ 0.0235 \\
+  1.425 & 0.162 & 0.397 & 219.2 & -0.0144 $\pm$ 0.0642 $\pm$ 0.0199 \\
+  1.425 & 0.162 & 0.397 & 258.4 & -0.1444 $\pm$ 0.0451 $\pm$ 0.0183 \\
+  1.425 & 0.162 & 0.397 & 303.3 & -0.0688 $\pm$ 0.0413 $\pm$ 0.0154 \\
+  1.425 & 0.162 & 0.397 & 337.1 &  0.0020 $\pm$ 0.0563 $\pm$ 0.0105 \\
+  \hline                                                              
+  1.922 & 0.227 & 0.418 & 21.9  &  0.0007 $\pm$ 0.0390 $\pm$ 0.0131 \\
+  1.922 & 0.227 & 0.418 & 59.7  &  0.1077 $\pm$ 0.0474 $\pm$ 0.0161 \\
+  1.922 & 0.227 & 0.418 & 96.1  &  0.1179 $\pm$ 0.0521 $\pm$ 0.0183 \\
+  1.922 & 0.227 & 0.418 & 140.9 &  0.1508 $\pm$ 0.0817 $\pm$ 0.0246 \\
+  1.922 & 0.227 & 0.418 & 182.2 &  0.0958 $\pm$ 0.0979 $\pm$ 0.0165 \\
+  1.922 & 0.227 & 0.418 & 222.7 & -0.2464 $\pm$ 0.0867 $\pm$ 0.0343 \\
+  1.922 & 0.227 & 0.418 & 260.2 & -0.1612 $\pm$ 0.0543 $\pm$ 0.0227 \\
+  1.922 & 0.227 & 0.418 & 303.2 & -0.2401 $\pm$ 0.0387 $\pm$ 0.0206 \\
+  1.922 & 0.227 & 0.418 & 336.9 & -0.0309 $\pm$ 0.0460 $\pm$ 0.0100 \\
+  \hline                                                              
+  2.354 & 0.287 & 0.492 & 20.9  &  0.0567 $\pm$ 0.0343 $\pm$ 0.0198 \\
+  2.354 & 0.287 & 0.492 & 58.7  &  0.1136 $\pm$ 0.0488 $\pm$ 0.0195 \\
+  2.354 & 0.287 & 0.492 & 94.5  &  0.1973 $\pm$ 0.0627 $\pm$ 0.0188 \\
+  2.354 & 0.287 & 0.492 & 139.3 &  0.1860 $\pm$ 0.1161 $\pm$ 0.0242 \\
+  2.354 & 0.287 & 0.492 & 180.5 & -0.2835 $\pm$ 0.1568 $\pm$ 0.0145 \\
+  2.354 & 0.287 & 0.492 & 225.8 &  0.1616 $\pm$ 0.1198 $\pm$ 0.0140 \\
+  2.354 & 0.287 & 0.492 & 261.2 & -0.3132 $\pm$ 0.0695 $\pm$ 0.0272 \\
+  2.354 & 0.287 & 0.492 & 303.7 & -0.1591 $\pm$ 0.0405 $\pm$ 0.0178 \\
+  2.354 & 0.287 & 0.492 & 338.6 & -0.0642 $\pm$ 0.0420 $\pm$ 0.0101 \\
+ \hline                                                               
+  2.987 & 0.390 & 0.714 & 19.4  &  0.0985 $\pm$ 0.0315 $\pm$ 0.0143 \\
+  2.987 & 0.390 & 0.714 & 55.4  &  0.1165 $\pm$ 0.0589 $\pm$ 0.0148 \\
+  2.987 & 0.390 & 0.714 & 93.7  &  0.1715 $\pm$ 0.0944 $\pm$ 0.0313 \\
+  2.987 & 0.390 & 0.714 & 135.2 & -0.0928 $\pm$ 0.2481 $\pm$ 0.0386 \\
+  2.987 & 0.390 & 0.714 & 181.8 & -0.1085 $\pm$ 0.5511 $\pm$ 0.0364 \\
+  2.987 & 0.390 & 0.714 & 230.1 & -0.2193 $\pm$ 0.3567 $\pm$ 0.0469 \\
+  2.987 & 0.390 & 0.714 & 265.3 & -0.0848 $\pm$ 0.1166 $\pm$ 0.0202 \\
+  2.987 & 0.390 & 0.714 & 303.4 & -0.2246 $\pm$ 0.0520 $\pm$ 0.0229 \\
+  2.987 & 0.390 & 0.714 & 341.2 & -0.0844 $\pm$ 0.0378 $\pm$ 0.0156 \\
  \hline
@@
 
-   1.823 & 0.213 & 0.145 & 22.4  &  0.0982   $\pm$   0.0432   $\pm$  0.0135  \\
-   1.823 & 0.213 & 0.145 & 57.8  &  0.1317   $\pm$   0.0511   $\pm$  0.0190  \\
-   1.823 & 0.213 & 0.145 & 97.3  &  0.1323   $\pm$   0.0506   $\pm$  0.0179  \\
-   1.823 & 0.213 & 0.145 & 141.7 &  0.1940   $\pm$   0.0722   $\pm$  0.0263  \\
-   1.823 & 0.213 & 0.145 & 180.9 &  0.0430   $\pm$   0.0879   $\pm$  0.0150  \\
-   1.823 & 0.213 & 0.145 & 219.8 & -0.0043   $\pm$   0.0770   $\pm$  0.0182  \\
-   1.823 & 0.213 & 0.145 & 261.2 & -0.1480   $\pm$   0.0515   $\pm$  0.0195  \\
-   1.823 & 0.213 & 0.145 & 303.8 & -0.1063   $\pm$   0.0455   $\pm$  0.0137  \\
-   1.823 & 0.213 & 0.145 & 337.0 & -0.0677   $\pm$   0.0481   $\pm$  0.0100  \\
- \hline                                                                       
-  2.127 & 0.255 & 0.282  & 21.3  &  0.0649   $\pm$   0.0425   $\pm$  0.0131  \\
-  2.127 & 0.255 & 0.282  & 59.3  &  0.0381   $\pm$   0.0500   $\pm$  0.0125  \\
-  2.127 & 0.255 & 0.282  & 95.6  &  0.2284   $\pm$   0.0594   $\pm$  0.0338  \\
-  2.127 & 0.255 & 0.282  & 140.6 & -0.0309   $\pm$   0.0836   $\pm$  0.0178  \\
-  2.127 & 0.255 & 0.282  & 181.3 & -0.1563   $\pm$   0.1041   $\pm$  0.0298  \\
-  2.127 & 0.255 & 0.282  & 219.8 & -0.0397   $\pm$   0.0986   $\pm$  0.0183  \\
-  2.127 & 0.255 & 0.282  & 259.7 & -0.1446   $\pm$   0.0619   $\pm$  0.0253  \\
-  2.127 & 0.255 & 0.282  & 304.1 & -0.2071   $\pm$   0.0459   $\pm$  0.0248  \\
-  2.127 & 0.255 & 0.282  & 338.5 & -0.0836   $\pm$   0.0521   $\pm$  0.0171  \\
- \hline                                                                
-  2.308 & 0.284 & 0.490 &  20.7  &  0.1282   $\pm$   0.0430   $\pm$  0.0154  \\
-  2.308 & 0.284 & 0.490 &  59.7  &  0.1127   $\pm$   0.0532   $\pm$  0.0175  \\
-  2.308 & 0.284 & 0.490 &  94.4  &  0.0998   $\pm$   0.0676   $\pm$  0.0147  \\
-  2.308 & 0.284 & 0.490 &  137.8 &  0.1089   $\pm$   0.1253   $\pm$  0.0166  \\
-  2.308 & 0.284 & 0.490 &  181.9 &  0.3437   $\pm$   0.1419   $\pm$  0.0392  \\
-  2.308 & 0.284 & 0.490 &  225.2 & -0.0714   $\pm$   0.1217   $\pm$  0.0125  \\
-  2.308 & 0.284 & 0.490 &  259.4 & -0.2429   $\pm$   0.0733   $\pm$  0.0234  \\
-  2.308 & 0.284 & 0.490 &  302.9 & -0.2047   $\pm$   0.0446   $\pm$  0.0162  \\
-  2.308 & 0.284 & 0.490 &  338.8 & -0.0569   $\pm$   0.0496   $\pm$  0.0178  \\
- \hline                                                                        
-   2.406 & 0.308 & 1.107&  20.2  &  0.0200   $\pm$   0.0356   $\pm$  0.0178  \\
-   2.406 & 0.308 & 1.107&  57.1  &  0.1588   $\pm$   0.0703   $\pm$  0.0108  \\
-   2.406 & 0.308 & 1.107&  93.1  &  0.0557   $\pm$   0.1459   $\pm$  0.0110  \\
-   2.406 & 0.308 & 1.107&  132.8 & -0.0505   $\pm$   0.4638   $\pm$  0.0177  \\
-   2.406 & 0.308 & 1.107&  177.3 & -0.9949   $\pm$   0.9191   $\pm$  0.0181  \\
-   2.406 & 0.308 & 1.107&  228.2 & -1.6988   $\pm$   2.5306   $\pm$  0.0151  \\
-   2.406 & 0.308 & 1.107&  263.1 &  0.0565   $\pm$   0.1477   $\pm$  0.0171  \\
-   2.406 & 0.308 & 1.107&  305.1 & -0.1556   $\pm$   0.0543   $\pm$  0.0129  \\
-   2.406 & 0.308 & 1.107&  340.1 & -0.0510   $\pm$   0.0430   $\pm$  0.0164  \\
+   1.823 & 0.213 & 0.145 & 22.0  &  0.0968 $\pm$ 0.0402 $\pm$ 0.0135 \\
+   1.823 & 0.213 & 0.145 & 58.7  &  0.1156 $\pm$ 0.0471 $\pm$ 0.0190 \\
+   1.823 & 0.213 & 0.145 & 96.9  &  0.1270 $\pm$ 0.0449 $\pm$ 0.0179 \\
+   1.823 & 0.213 & 0.145 & 141.2 &  0.1544 $\pm$ 0.0598 $\pm$ 0.0263 \\
+   1.823 & 0.213 & 0.145 & 180.5 &  0.0308 $\pm$ 0.0748 $\pm$ 0.0150 \\
+   1.823 & 0.213 & 0.145 & 219.9 & -0.0366 $\pm$ 0.0661 $\pm$ 0.0182 \\
+   1.823 & 0.213 & 0.145 & 260.7 & -0.1370 $\pm$ 0.0457 $\pm$ 0.0195 \\
+   1.823 & 0.213 & 0.145 & 303.4 & -0.1286 $\pm$ 0.0412 $\pm$ 0.0137 \\
+   1.823 & 0.213 & 0.145 & 336.8 & -0.0421 $\pm$ 0.0465 $\pm$ 0.0100 \\
+ \hline                                    
+  2.127 & 0.255 & 0.282  & 21.2  &  0.0431 $\pm$ 0.0396 $\pm$ 0.0131 \\
+  2.127 & 0.255 & 0.282  & 60.3  &  0.0441 $\pm$ 0.0464 $\pm$ 0.0125 \\
+  2.127 & 0.255 & 0.282  & 95.4  &  0.2261 $\pm$ 0.0521 $\pm$ 0.0338 \\
+  2.127 & 0.255 & 0.282  & 141.0 &  0.0325 $\pm$ 0.0724 $\pm$ 0.0178 \\
+  2.127 & 0.255 & 0.282  & 182.5 & -0.1014 $\pm$ 0.0889 $\pm$ 0.0298 \\
+  2.127 & 0.255 & 0.282  & 220.8 &  0.0106 $\pm$ 0.0867 $\pm$ 0.0183 \\
+  2.127 & 0.255 & 0.282  & 259.1 & -0.1522 $\pm$ 0.0562 $\pm$ 0.0253 \\
+  2.127 & 0.255 & 0.282  & 303.6 & -0.1996 $\pm$ 0.0411 $\pm$ 0.0248 \\
+  2.127 & 0.255 & 0.282  & 338.2 & -0.1026 $\pm$ 0.0497 $\pm$ 0.0171 \\
+ \hline                                   
+  2.308 & 0.284 & 0.490  & 20.4  &  0.1388 $\pm$ 0.0392 $\pm$ 0.0154 \\
+  2.308 & 0.284 & 0.490  & 60.3  &  0.1168 $\pm$ 0.0472 $\pm$ 0.0175 \\
+  2.308 & 0.284 & 0.490  & 94.0  &  0.1236 $\pm$ 0.0590 $\pm$ 0.0147 \\
+  2.308 & 0.284 & 0.490  & 137.2 &  0.0764 $\pm$ 0.1034 $\pm$ 0.0166 \\
+  2.308 & 0.284 & 0.490  & 182.5 &  0.3871 $\pm$ 0.1189 $\pm$ 0.0392 \\
+  2.308 & 0.284 & 0.490  & 225.9 & -0.1565 $\pm$ 0.1064 $\pm$ 0.0125 \\
+  2.308 & 0.284 & 0.490  & 259.1 & -0.2829 $\pm$ 0.0646 $\pm$ 0.0234 \\
+  2.308 & 0.284 & 0.490  & 302.4 & -0.1768 $\pm$ 0.0403 $\pm$ 0.0162 \\
+  2.308 & 0.284 & 0.490  & 338.6 & -0.0512 $\pm$ 0.0472 $\pm$ 0.0178 \\
+ \hline                                    
+   2.406 & 0.308 & 1.107 & 20.3  &  0.0428 $\pm$ 0.0336 $\pm$ 0.0178 \\
+   2.406 & 0.308 & 1.107 & 57.7  &  0.1460 $\pm$ 0.0609 $\pm$ 0.0108 \\
+   2.406 & 0.308 & 1.107 & 92.7  &  0.1593 $\pm$ 0.1114 $\pm$ 0.0110 \\
+   2.406 & 0.308 & 1.107 & 133.6 & -0.1661 $\pm$ 0.2523 $\pm$ 0.0177 \\
+   2.406 & 0.308 & 1.107 & 176.7 & -0.7014 $\pm$ 0.6435 $\pm$ 0.0181 \\
+   2.406 & 0.308 & 1.107 & 224.8 & -0.5821 $\pm$ 0.5513 $\pm$ 0.0151 \\
+   2.406 & 0.308 & 1.107 & 263.1 & -0.1527 $\pm$ 0.1123 $\pm$ 0.0171 \\
+   2.406 & 0.308 & 1.107 & 304.4 & -0.1831 $\pm$ 0.0480 $\pm$ 0.0129 \\
+   2.406 & 0.308 & 1.107 & 340.1 & -0.0293 $\pm$ 0.0400 $\pm$ 0.0164 \\
 
@@
    \begin{center}
-      \begin{tabular}{||l|l|l|l|l|l|l||}
-         \hline
- ($Q^{2}$, $x_{B}$, $-t$) & EG6 $A_{LU}$ $\pm$ stat. &  Exp. fit $\pm$ stat. & Exp. $A_{LU}$ ratio   &  Model extr. & Model $A_{LU}$ ratio &  Diff. (Exp - Model)    \\
-  \hline
- (1.395, 0.166, 0.407) &  0.136 $\pm$ 0.027 & 0.2061 $\pm$ 0.0092 & 0.6595 $\pm$ 0.1361 & 0.2050 & 0.6634 & -0.0039 \\
- (1.886, 0.233, 0.499) &  0.156 $\pm$ 0.033 & 0.2192 $\pm$ 0.0421 & 0.7114 $\pm$ 0.2044 & 0.2244 & 0.6951 &  0.0163 \\
- (2.338, 0.290, 0.521) &  0.154 $\pm$ 0.038 & 0.2197 $\pm$ 0.0308 & 0.7042 $\pm$ 0.2004 & 0.2177 & 0.7110 & -0.0068 \\
- (3.098, 0.379, 0.650) &  0.122 $\pm$ 0.042 & 0.2143 $\pm$ 0.0801 & 0.5727 $\pm$ 0.2907 & 0.2017 & 0.6088 & -0.0361 \\
+      \begin{tabular}{||l|l|l|l|l|l||}
+         \hline
+ ($Q^{2}$, $x_{B}$, $-t$) & EG6 $A_{LU}$ $\pm$ stat. &  Exp. fit $\pm$ stat. & Exp. $A_{LU}$ ratio   &  Model extr. & Model $A_{LU}$ ratio \\
+  \hline
+ (1.395, 0.166, 0.407) & 0.147 $\pm$ 0.023 & 0.206 $\pm$ 0.009 & 0.715 $\pm$ 0.117 & 0.205 & 0.717 \\
+ (1.886, 0.233, 0.499) & 0.153 $\pm$ 0.028 & 0.219 $\pm$ 0.042 & 0.702 $\pm$ 0.188 & 0.224 & 0.683 \\
+ (2.338, 0.290, 0.521) & 0.166 $\pm$ 0.032 & 0.219 $\pm$ 0.030 & 0.758 $\pm$ 0.182 & 0.217 & 0.764 \\
+ (3.098, 0.379, 0.650) & 0.132 $\pm$ 0.039 & 0.214 $\pm$ 0.080 & 0.619 $\pm$ 0.296 & 0.201 & 0.656 \\
    \hline \hline  \hline                                                                     
- (1.425, 0.162, 0.397) &  0.118 $\pm$ 0.026 & 0.2124 $\pm$ 0.0091 & 0.5591 $\pm$ 0.1273 & 0.1885 & 0.6302 & -0.0711 \\
- (1.922, 0.227, 0.418) &  0.178 $\pm$ 0.029 & 0.2310 $\pm$ 0.0406 & 0.7743 $\pm$ 0.1874 & 0.2135 & 0.8379 & -0.0636 \\
- (2.354, 0.287, 0.492) &  0.151 $\pm$ 0.036 & 0.2257 $\pm$ 0.0309 & 0.6701 $\pm$ 0.1873 & 0.2170 & 0.6972 & -0.0271 \\
- (2.987, 0.390, 0.714) &  0.132 $\pm$ 0.050 & 0.1985 $\pm$ 0.0837 & 0.6654 $\pm$ 0.3802 & 0.2103 & 0.6281 &  0.0373 \\
+ (1.425, 0.162, 0.397) & 0.115 $\pm$ 0.022 & 0.212 $\pm$ 0.009 & 0.545 $\pm$ 0.106 & 0.188 & 0.611 \\
+ (1.922, 0.227, 0.418) & 0.182 $\pm$ 0.025 & 0.231 $\pm$ 0.040 & 0.790 $\pm$ 0.176 & 0.213 & 0.854 \\
+ (2.354, 0.287, 0.492) & 0.192 $\pm$ 0.030 & 0.225 $\pm$ 0.030 & 0.851 $\pm$ 0.178 & 0.217 & 0.884 \\
+ (2.987, 0.390, 0.714) & 0.149 $\pm$ 0.046 & 0.198 $\pm$ 0.083 & 0.754 $\pm$ 0.396 & 0.210 & 0.709 \\
    \hline  \hline  \hline                                                                    
- (1.823, 0.213, 0.145) &  0.146 $\pm$ 0.027 & 0.2463 $\pm$ 0.0378 & 0.5950 $\pm$ 0.1447 & 0.2438 & 0.6013 & -0.0063 \\
- (2.127, 0.255, 0.282) &  0.150 $\pm$ 0.031 & 0.2259 $\pm$ 0.0182 & 0.6664 $\pm$ 0.1477 & 0.2410 & 0.6248 &  0.0416 \\
- (2.308, 0.284, 0.490) &  0.163 $\pm$ 0.039 & 0.2257 $\pm$ 0.0309 & 0.7219 $\pm$ 0.2002 & 0.2195 & 0.7425 & -0.0206 \\
- (2.406, 0.308, 1.107) &  0.115 $\pm$ 0.054 & 0.1265 $\pm$ 0.0345 & 0.9087 $\pm$ 0.4944 & 0.1235 & 0.9311 & -0.0224 \\
+ (1.823, 0.213, 0.145) & 0.142 $\pm$ 0.023 & 0.246 $\pm$ 0.037 & 0.576 $\pm$ 0.131 & 0.243 & 0.584 \\
+ (2.127, 0.255, 0.282) & 0.155 $\pm$ 0.027 & 0.225 $\pm$ 0.018 & 0.688 $\pm$ 0.131 & 0.241 & 0.643 \\
+ (2.308, 0.284, 0.490) & 0.183 $\pm$ 0.034 & 0.225 $\pm$ 0.030 & 0.811 $\pm$ 0.188 & 0.219 & 0.835 \\
+ (2.406, 0.308, 1.107) & 0.170 $\pm$ 0.051 & 0.126 $\pm$ 0.034 & 1.343 $\pm$ 0.545 & 0.123 & 1.382 \\
    \hline  \hline  \hline                                                                    
- (1.143, 0.132, 0.096) &  0.282 $\pm$ 0.078 & 0.1956 $\pm$ 0.1028 & 1.4444 $\pm$ 0.8584 & 0.2447 & 1.1524 &  0.2920 \\
- (1.423, 0.170, 0.099) &  0.364 $\pm$ 0.064 & 0.1703 $\pm$ 0.0201 & 2.1366 $\pm$ 0.4529 & 0.2518 & 1.4456 &  0.6910 \\
- (1.902, 0.224, 0.107) &  0.258 $\pm$ 0.078 & 0.1814 $\pm$ 0.0822 & 1.4239 $\pm$ 0.7774 & 0.2359 & 1.0937 &  0.3302 \\
+ (1.143, 0.132, 0.096) & 0.303 $\pm$ 0.051 & 0.195 $\pm$ 0.102 & 1.552 $\pm$ 0.857 & 0.244 & 1.241 \\
+ (1.423, 0.170, 0.099) & 0.364 $\pm$ 0.059 & 0.170 $\pm$ 0.020 & 2.137 $\pm$ 0.431 & 0.251 & 1.450 \\
+ (1.902, 0.224, 0.107) & 0.294 $\pm$ 0.060 & 0.181 $\pm$ 0.082 & 1.624 $\pm$ 0.808 & 0.235 & 1.251 \\
      \hline \hline  \hline                                                                   
- (1.164, 0.132, 0.095) &  0.313 $\pm$ 0.069 & 0.1956 $\pm$ 0.1028 & 1.5999 $\pm$ 0.9132 & 0.2234 & 1.4011 &  0.1988 \\
- (1.439, 0.170, 0.099) &  0.237 $\pm$ 0.070 & 0.1664 $\pm$ 0.0209 & 1.4251 $\pm$ 0.4563 & 0.2432 & 0.9745 &  0.4506 \\
- (1.844, 0.225, 0.107) &  0.299 $\pm$ 0.120 & 0.1787 $\pm$ 0.0844 & 1.6736 $\pm$ 1.0599 & 0.2515 & 1.1889 &  0.4847 \\
+ (1.164, 0.132, 0.095) & 0.319 $\pm$ 0.044 & 0.195 $\pm$ 0.102 & 1.633 $\pm$ 0.888 & 0.223 & 1.430 \\
+ (1.439, 0.170, 0.099) & 0.278 $\pm$ 0.078 & 0.166 $\pm$ 0.020 & 1.670 $\pm$ 0.518 & 0.243 & 1.144 \\
+ (1.844, 0.225, 0.107) & 0.319 $\pm$ 0.161 & 0.178 $\pm$ 0.084 & 1.788 $\pm$ 1.235 & 0.251 & 1.270 \\
       \hline  \hline  \hline                                                                 
- (1.493, 0.177, 0.1)   &  0.331 $\pm$ 0.030 & 0.1575 $\pm$ 0.0341 & 2.1049 $\pm$ 0.4939 & 0.2453 & 1.3493 &  0.7556 \\
-
+ (1.493, 0.177, 0.1)   & 0.349 $\pm$ 0.029 & 0.157 $\pm$ 0.034 & 2.214 $\pm$ 0.515 & 0.245 & 1.424 \\                                                               
  \hline
@@
  presents the calculated $A_{LU}$ ratios using EG6 asymmetries and the 
- model-dependent extracted free proton asymmetries. The last column ("Diff.  
- (Exp - Model)") shows the difference between the two calculated $A_{LU}$ 
- ratios for each bin.}
+ model-dependent extracted free proton asymmetries. }
  \label{table:ALU_ratios_}
@@
 \end{landscape}
+
+\chapter{Investigating the Fermi motion effects on the incoherent DVCS channel}
+
+In our DVCS analysis, we considered the initial proton of the incoherent 
+channel to be at rest, while this is not totally true because of the Fermi 
+motion. Does this assumption is a good approximation? What other options can be 
+used to minimize this effect on the calculated exclusive quantities?\\
+
+Figure \ref{fig:handbag} presents the leading order handbag diagram of the 
+incoherent DVCS channel off $^4$He, where the nucleus breaks and the DVCS 
+occurs on a bound nucleon. Ideally, the transferred momentum squared ($t$) is 
+defined using the initial and the final nucleons' 4-vectors as $(p-p')^{2}$.  
+Then as a DVCS requirement, $t$ has to be greater than a certain value 
+($t_{min}$), that is defined using the kinematics of the incoming and the 
+scattered electrons. Due to the knowledge lack of the initial proton's 
+momentum, this cut maybe inaccurate causes loosing some good DVCS events. In 
+this work, we try to tackle this issue and check the stability of the 
+reconstructed beam-spin asymmetry, as being our DVCS observable.\\
+
+\begin{figure}[h!]
+   \centering
+\includegraphics[height=10.0cm]{fig-incoh/handbag_incoherent.pdf}
+\caption{Representation of the leading order handbag diagram of the incoherent 
+DVCS process off $^4$He}
+\label{fig:handbag}
+\end{figure}
+
+Typically, the transferred momentum squared $t$ is equal to the transferred 
+momentum squared ($t'$) defined between the virtual photon and the final-state 
+real photon, as shown in Figure \ref{fig:handbag}.  While defining the momentum 
+transferred as $t'$ is a good way to pass the Fermi motion effect on the 
+initial bound proton, it is more smeared than than $t$ due to bigger energy 
+resolutions of the photons. Figure \ref{fig:tprime} shows the distributions of 
+the coherent and the incoherent relative difference between $t$ and $t'$. One 
+can see that the coherent DVCS channel, the distributions is symmetric and 
+centered at zero as expected due to our good knowledge on the initial $^4$He 
+target, while it is not exactly the case for the incoherent case due to the 
+Fermi motion.\\
+
+\begin{figure}[h!]
+\includegraphics[height=5.0cm]{fig-incoh/T_tprime_Coh.png}
+\includegraphics[height=5.0cm]{fig-incoh/T_tprime_InCoh.png}
+\caption{On the left: the coherent relative difference between $t$ and $t'$.  
+On the right: the incoherent relative difference.}
+\label{fig:tprime}
+\end{figure}
+
+In the following, we check the effects of defining the transferred momentum 
+squared as $t$ and $t'$ on the exclusive distributions and on the reconstructed 
+beam-spin asymmetries. Figure \ref{fig:cuts_t} presents the exclusive 
+distributions of the incoherent DVCS events where the transferred momentum
+squared is defined as $t$, while it is define as $t'$ in figure 
+\ref{fig:cuts_tprime}. To minimize the smearing effects of $t'$ on the 
+exclusive distributions, 2$\sigma$ exclusive cuts were optimized compared to 
+3$\sigma$ cuts which were applied in the $t$ case. In terms of collected 
+statistics, the 2$\sigma$ cuts using $t'$ gave almost the same statistics using 
+$t$. From comparing the exclusive distributions, especially the $ep\gamma$ 
+missing energy and the missing mass squared, one sees that using $t'$ gives 
+more Gaussian missing energy distributions and cleaner missing mass squared 
+distribution.\\
+
+\begin{figure}[h!]
+\includegraphics[height=15.0cm]{fig-incoh/old_all_incoh_exc_cuts.pdf}
+\caption{The old set of exclusive cuts with $t$>$t_{min}$. The black
+   distributions represent the incoherent DVCS events candidate. The shaded
+   distributions represent the events which passed all the exclusivity cuts
+   except the quantity plotted. The vertical red lines represent the applied
+exclusivity, 3$\sigma$ cuts.}
+\label{fig:cuts_t}
+\end{figure}
+
+\begin{figure}[h!]
+   \includegraphics[height=15.0cm]{fig-incoh/all_incoh_exc_cuts_test.pdf}
+   \caption{New set of exclusive cuts with $t'$>$t_{min}$. The black
+      distributions represent the incoherent DVCS events candidate. The shaded
+      distributions represent the events which passed all the exclusivity cuts
+      except the quantity plotted. The vertical red lines represent the applied 
+   exclusivity, 2$\sigma$ cuts.}
+\label{fig:cuts_tprime}
+\end{figure}
+
+\begin{figure}[h!]
+   \includegraphics[height=6.0cm]{fig-incoh/ALU_phi_p_Q2.pdf}
+   \includegraphics[height=6.0cm]{fig-incoh/ALU_phi_p_x.pdf}
+   \includegraphics[height=6.0cm]{fig-incoh/ALU_phi_p_t.pdf}
+\caption{The reconstructed incoherent $A_{LU}$ as a function of the angle 
+   $\phi$ in $Q^2$, $x_B$, and $-t$ bins, respectively from top to bottom using 
+$t$>$t_{min}$ in black squares, and $t'$>$t_{min}$ in red squares.}
+   \label{fig:bsa_incoh_bins}
+\end{figure}
+
+\begin{figure}[h!]
+   \centering
+   \includegraphics[height=6.0cm]{fig-incoh/ALU_90_p_vs_Q2_shortscenrario.pdf}\\
+   \includegraphics[height=6.0cm]{fig-incoh/ALU_90_p_vs_x_shortscenrario.pdf}\\
+   \includegraphics[height=6.0cm]{fig-incoh/ALU_90_p_vs_t_shortscenrario.pdf}
+   \caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $-t$-dependencies (bottom) 
+      of the incoherent $A_{LU}$ at $\phi$~=~90$^{\circ}$, using the 
+   $t$>$t_{min}$ cut and the corresponding exclusive cuts in black squares, and 
+in red squares using the $t'$>$t_{min}$ and it's exclusive cuts.  The curves 
+are theoretical calculations. On the bottom: the green circles are the HERMES 
+$-A_{LU}$ (positron beam was used) inclusive measurements.}
+\label{fig:incoh_Q2_xB_t_ALU}
+\end{figure}
+
+\section*{Conclusions}
+In summary, we have studied the effects of Fermi motion on the measured 
+incoherent beam-spin asymmetries by defining the transferred momentum squared 
+through the nucleons in one case and through the photons in the other case. In 
+terms of collected statistics, 2$\sigma$ exclusive cuts using the photons 
+produced the same statistics as 3$\sigma$ cuts. The exclusive distributions 
+using $t'$, through the photons, have shown more acceptable distributions in 
+terms of being more symmetric in some cases and cleaner on others. The 
+reconstructed asymmetries in the two cases of defining the transferred momentum 
+squared are compatible and while the given error bars. As a suggestion, we 
+would like to consider the $t'$ analysis as the final set for publications 
+unless a major objections appear.

### 2017-02-25 eg6-letters/coherent/EG6-group-comments/eg6_comments.tex
added a subdirectory for eg6 comments on the coherent paper and another subdirectory for the incoherent channel inestigation.

%\documentclass[a4paper,11pt,twoside]{ThesisStyle}
\documentclass[a4paper,11pt,twoside]{article}

\date{\today}
\include{formatAndDefs}
\begin{document}

\section{Comments from Whitney}

\begin{enumerate}
\item In general I think there are too many figures for a PRL.
Figures 1-5 can probably be removed or reduced.\\
\textcolor{blue}{I kept all the figures for now, but thinking in removing 
figure 2, the RTPC. }

\item "Deeply Virtual Compton Scattering" -> "deeply virtual Compton
scattering (DVCS)"\\
\textcolor{blue}{Done. }

\item "Radial Time Projection Chamber" -> "radial time projection chamber
(RTPC)"\\
\textcolor{blue}{Done. }

\item "Beam Spin Asymmetries" -> "beam spin asymmetries"\\
\textcolor{blue}{Done. }

\item "Compton Form Factors" -> "Compton form factors"\\
\textcolor{blue}{Done. }

\item "Generalized Parton Distribution" -> "generalized parton distribution"\\
\textcolor{blue}{Done. }

\item Line 17: "Quantum Chromodynamics (QCD)" -> "quantum chromodynamics
(QCD)"\\
\textcolor{blue}{Done. }

\item Line 19: "development of the Generalized Parton Distributions (GPDs)
..." -> "development of the generalized parton distribution (GPD) ...",
assuming the acronym isn't already defined in abstract.\\
\textcolor{blue}{Done. }

\item Line 23: Unnecessary comma.\\
\textcolor{blue}{Done. }

\item Line 23: Last sentence in paragraph could be improved. It is at a
critical location in the paper so you might want to reword for clarity.\\

 "In impact parameter space, the GPDs are indeed interpreted as a tomography of 
 the transverse plane for partons carrying a certain longitudinal momentum"\\

Perhaps ...\\

"Impact parameter GPDs provide a tomographic image of the partons
carrying fixed values of longitudinal momentum."\\
\textcolor{blue}{We would like to keep the sentence as it is. }

\item Line 28: "Deeply Virtual Compton Scattering" -> "deeply virtual Compton
scattering" and remove "(DVCS)" if acronym defined  in  abstract.\\
\textcolor{blue}{Done.}

\item Line 29: ", i.e. the " -> ", \textit{i.e.}, the"\\
\textcolor{blue}{Done. }

\item Line 34: Technically "JLab" isn't an acronym since it has lower case
letters -- it is just another name. Furthermore, if you are going to
define the JLab acronym anyway, shouldn't you do the same for CERN and
HERA? I suggest just leaving it as "JLab" or "Jefferson Lab".\\
\textcolor{blue}{Removed JLab and keep it as Jefferson Lab. }

\item Line 48: "Figure 1" -> "FIG. 1"\\
\textcolor{blue}{Done.}

\item Line 50: Sentence is hard to read. Maybe define the invariants $Q^2$ and t
in one sentence. Then describe the kinematic regime for factorization.\\
\textcolor{blue}{Left as it is for now. }

\item Line 59: Oxford comma?  "x, $\xi$, and t"\\
\textcolor{blue}{Done. }

\item Line 59: "Figure 1" -> "FIG. 1"\\
\textcolor{blue}{Done. }

\item Line 61: " with M the proton mass ..." ->
", $\nu = k^0-k^{\prime0}$, and M is the proton mass." Note that t is
already defined defined (see Line 50 comment).\\
\textcolor{blue}{Cleaned and removed $t$ from here.}

\item Line 65: "Compton Form Factors" -> "Compton form factors"\\
\textcolor{blue}{Done. }

\item Line 66: "... defined as" -> "... defined at leading order as"
The coefficient function is the LO one and it should be noted.\\
\textcolor{blue}{Done.}

\item Line 69: Paragraph needs improved. Perhaps get to the point quickly ...
"The HERMES experiment measured this process with a few nuclear targets
(N, Ne, KR, and XE), however, they did not measure the recoil nucleus.
Therefore, the coherence of the reaction possibly suffers from large
contaminations ..."\\
\textcolor{blue}{Kept the same for now. }

\item Line 79: Shouldn't "CLAS" have already been defined in the abstract?\\
\textcolor{blue}{ We define it here.}

\item Line 83: Is this the first definition of RTPC? (But note the correct
capitalization of "radial time projection chamber")\\
\textcolor{blue}{ Yes and corrected for the capitalization.}

\item Line 85:  The sentence beginning here seems out of place. "... while it
is subject to significant nuclear effects". Is this accidental mixing
with the incoherent paper?\\
\textcolor{blue}{I don't see why it is out of place.}

\item Line 100: "at energy of " -> "at an energy of"\\
\textcolor{blue}{Done.}

\item Line 115: "In Figure 2 a picture of RTPC installed in the experimental
hall, and the rendering showing detector components and the 4 He
detection concept are presented." ->
"Presented in FIG. 2 are a picture of RTPC installed in the experimental
hall and a diagram showing the basic detection technique."\\
\textcolor{blue}{the sentence is cleaned. }

\item Line 134: "The photons are detected in either the IC or
the CLAS electromagnetic calorimeter." Is this true?\\
\textcolor{blue}{Yes for the case of the ICEC pio topology needed for the 
background subtraction. }

\item Line 146: "events with ... " -> "events with $Q^2$ > 1 GeV$^2$/c$^2$."\\
\textcolor{blue}{Extra spaces? yes done. }

\item Line 160: "After these requirements, we ... " -> "About 3200 events pass
these requirements and are shown in FIG. 4..."\\
\textcolor{blue}{Edited.}

\end{enumerate}

\section{Comments from Hovanes}

\begin{enumerate}
\item In the abstract there is a statement about the BSA size relative to
the BSA on the proton, but there
is not such statement or comparison in the article (I might have missed
it). I would suggest either removing
this statement from the abstract or add graph(s) comparing the two BSAs
to support such a statement.\\
\textcolor{blue}{What about adding the t-dependence plot of the ALU ratio? }

\item line 36 : "allowed extraction of the tomography of the nucleon" could
be changed "allowed for extraction
of the three-dimensional picture of the nucleon" . The way "tomography"
is used in lines 24 and 37 is a little
unusual.\\
\textcolor{blue}{Cleaned. }

\item line 49 : "hand bag diagram" -> "hand-bag diagram"\\
\textcolor{blue}{Done here and in the caption.}

\item line 78 : I suggest removing "and that the reaction did not occur on
a bound nucleon".\\
\textcolor{blue}{Removed. }

\item line 80 : CLAS was not designed for study of DVCS, therefore the
statement that it is optimized for DVCS
is not a justified statement. One can simply say " ... in Hall-B at
Jefferson Lab has been previously used for DVCS
measurements on nucleon."\\
\textcolor{blue}{Cleaned.}

\item Line 194 : "and a solenoid." -> "and a solenoid magnet."\\
\textcolor{blue}{Added. }

\item Line 198 "... 5 Tesla solenoid ..." -> "... 5 Tesla solenoid magnet
... "\\
\textcolor{blue}{Added. }

\item Figure 3 : The histograms titles need to be removed from the top of
the graphs and put as x-axis titles.\\
\textcolor{blue}{I will update them.}

\item Line 196 " ... that depends ..." -> "... that depend ..." .\\
\textcolor{blue}{Corrected. }

\item Line 152 and line 198 : The font for 'He4 changes throughout the paper.\\
\textcolor{blue}{Corrected.}

\item Figures 3, 5, 6, 7 : axis titles labels and legends are totally
illegible. At some point these will have to be improved.
\textcolor{blue}{I will work on them.}

\item Line 271. I am not sure how the results in Figure 7 support the
argument that the extraction of CFF is
model independent. The applicability of Eq. 5 presumably determines if
this extraction is model independent or not,
either way the fits would produce some results.
\textcolor{blue}{ }

\end{enumerate}

\section{Comments from Eric}
I will concur with other remarks that you may try to concentrate on a reduced 
set of figures. It is always difficult to squeeze everything in the PRL and I 
apologize in advance for my next remark asking to potentially say more. It 
would be valuable to have a direct comparison between proton and He4 on the 
basis of the amplitude of the asymmetries at 90°. The ratio He4/proton would 
give the so-called generalized EMC ratio that already encode some nuclear 
effects. It would be interesting to know whether or not this comparison yields 
conclusive physics input.
\textcolor{blue}{We may remove Figure 2 and add a t-dependence for the ratio! }

\section{Comments from Lamiaa}

\begin{enumerate}

\item Would it possible to define some acronyms in the abstract especially the ones that will be used again there like DVCS (some published PRLs did, e.g. the latest CLAS PRL of 2015, they used CLAS acronym w/o. definition (!), defined GPDs acronym in the abstract to avoid writing generalized parton distributions twice, and all others including JLab were defined in the core.

I believe according to the abbreviation guidelines below, you could either define the acronym DVCS using deeply virtual Compton scattering or Deeply Virtual Compton Scattering but e.g. the above letter used the former!
\textcolor{blue}{Thanks! }

\item In Eq. 1 $\&$ 2 you gave the expression of the real and comlplex CFF amplitudes, hence, shouldn't be "real and complex amplitudes" in line 66?
\textcolor{blue}{Edited.}

\item While the PRL link below contains some comments about the letter length, number of words, and figures size which It will be nice to review, I have a comment about some figures:
   a. To gain some space you could move a figure's caption a little bit up using:

         vglue -xxxcm caption{}               ! e.g. vglue -0.5cm

   b. Some figures are more shifted to the left, e.g. Fig. 3, Fig. 5, 6 $\&$ 7, if centering under\\

       begin{figure*}\\
       centering \\
         includegraphics[]{}\\
          vglue -0.55cm caption{}\\
          label\\
         end{figure*}\\

       is not doing the job. You could force it by adding vspace*{-xxxcm} just after begin{figure*}.
       (a simple trick that works!)
\textcolor{blue}{I will work on them. }

\item It will be nice to rephrase some sentences to read better such as:
    a. Line 207, "The explicit expressions of these terms can be found in [40] 
    and show that, by using the sin( $\phi$) and cos( $\phi$) contributions, it 
    is possible to extract Im(HA) and Re(HA) from the beam spin asymmetry."\\

    b.  Line 236, "However, added quadratically,the total systematic 
    uncertainty is about 10\%, which is significantly smaller than statistical 
    uncertainties in all kinematical bins."\\

    c. Line 278, "While the accuracy of our results does not allow to 
    discriminate between the models, they demonstrate possibility of extraction 
    of the CFF of spin 0 target in a model independent way."\\
    \textcolor{blue}{ }

\item Line 256, $Q^2$, $x_B$, and t dependencies.........
\textcolor{blue}{Done. }

\end{enumerate}

\end{document}

### 2017-02-25 eg6-letters/coherent/dvcs_he4_prl.tex
added a subdirectory for eg6 comments on the coherent paper and another subdirectory for the incoherent channel inestigation.

@@
 \begin{abstract}
-We report the first fully exclusive measurement of coherent Deeply Virtual Compton 
-Scattering off a nucleus for $A>1$. The experiment used the 6 GeV 
+We report the first fully exclusive measurement of coherent deeply virtual 
+Compton scattering off a nucleus for $A>1$. The experiment used the 6 GeV 
 electron beam from the CEBAF machine at Jefferson Lab incident on a $^4$He gas 
-target in the center of the CEBAF Large Acceptance Spectrometer. A new 
-Radial Time Projection Chamber was used to detect the recoiling $^4$He
-nuclei and ensure the exclusivity of the process. The measured Beam Spin 
-Asymmetries are larger than that observed on the proton in 
-the same kinematic domain. Since $^4$He is a spin zero target, we were able to 
-extract, in a completely model independent way, the real and imaginary parts of the $^4$He Compton Form Factors, $\cal H_A$, which are functions of the Generalized Parton Distribution $H_A$. 
-This pioneering measurement of coherent Deeply Virtual Compton Scattering on the $^4$He nucleus, with a fully exclusive final state via nuclear recoil tagging, leads the way toward 3D imaging of the partonic structure of nuclei.
+target in the center of the CEBAF large acceptance spectrometer. A new radial 
+time projection chamber (RTPC) was used to detect the recoiling $^4$He
+nuclei and ensure the exclusivity of the process. The measured beam spin 
+asymmetries are larger than that observed on the proton in the same kinematic 
+domain. Since $^4$He is a spin zero target, we were able to extract, in a 
+completely model independent way, the real and imaginary parts of the $^4$He 
+Compton form factors, $\cal H_A$, which are functions of the generalized parton 
+distribution $H_A$. This pioneering measurement of coherent deeply virtual 
+Compton scattering on the $^4$He nucleus, with a fully exclusive final state 
+via nuclear recoil tagging, leads the way toward 3D imaging of the partonic 
+structure of nuclei.
 \end{abstract}
@@
 
-Rich information on Quantum Chromodynamics (QCD) can be extracted from the internal structure 
-of hadrons. In the recent past, development of the Generalized Parton 
-Distributions (GPDs) framework has offered a possibility to obtain new 
-information about the momentum and spatial degrees of freedom of the quarks and 
-gluons inside hadrons 
+Rich information on quantum chromodynamics (QCD) can be extracted from the 
+internal structure of hadrons. In the recent past, development of the 
+generalized parton distribution (GPD) framework has offered a possibility to 
+obtain new information about the momentum and spatial degrees of freedom of the 
+quarks and gluons inside hadrons 
 \cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.
-In impact parameter space, the GPDs are indeed interpreted as a tomography of the 
-transverse plane for partons carrying a certain longitudinal momentum 
+In impact parameter space the GPDs are indeed interpreted as a tomography of 
+the transverse plane for partons carrying a certain longitudinal momentum 
 \cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep,Burkardt:2005hp}.
@@
 The most promising way to access GPDs experimentally is through the measurement 
-of Deep Virtual Compton Scattering (DVCS), i.e.  the hard exclusive 
+of deeply virtual Compton scattering (DVCS), \textit{i.e.}, the hard exclusive 
 electroproduction of a real photon.  While other processes are known to be 
@@
 Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
-involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
-CERN.  The vast majority of these measurements focused on the study of proton 
-structure and allowed extraction of the tomography of the nucleon (for details 
-on the formalism, see 
+involving several accelerator facilities such as Jefferson Lab, HERA and  CERN.  
+The vast majority of these measurements focused on the study of proton 
+structure and allowed for extraction of the three-dimensional picture of the 
+nucleon (for details on the formalism, see 
 \cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
@@
 \includegraphics[width=6.5cm]{figs/DVCS_diagram.pdf}
-\caption{Representation of the leading order handbag diagram of the 
-DVCS process off $^4$He.}
+\caption{Representation of the leading order hand-bag diagram of the DVCS 
+process off $^4$He.}
 \label{fig:diags}
@@
 second, the recoil nucleus ($A^\prime$) must be detected to ensure coherence.  
-Figure \ref{fig:diags} 
-illustrates the hand bag diagram for coherent DVCS on $^4$He.  Similar to the 
-proton case, at large virtual photon's 4-momentum square $Q^2=-(k-k')^{2}$ and 
-small squared momentum transfer $t=(p-p')^{2}$ (in terms of the electron, 
-$k(k')$, and $^4$He, $p(p')$, four-vectors), the DVCS handbag diagram can be 
-factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The hard part 
-includes the photon-quark interaction and is calculable in perturbative QCD.  
-The non-perturbative part is parametrized in terms of GPDs, which embed the 
-partonic structure of the hadron. The GPDs depend on the three variables $x$, 
-$\xi$ and $t$ as introduced in Figure \ref{fig:diags}. The parameter $\xi$
-relates to the Bjorken variable $x_{B}$: $\xi\approx {{x_B}\over{2-x_B}}$, 
-where $x_B=\frac{Q^2}{2M\nu}$ with $M$ the proton mass and  
-$\nu=k^0-k^{0\prime}$, the $t$ is squared momentum transfer to the target. The 
-parameter $x$ is the quark's internal loop momentum fraction and cannot be 
-accessed experimentally. In the experiment we measure Compton Form
-Factors (CFF) \cite{Guidal:2013rya}, complex amplitudes defined as:
+FIG.~\ref{fig:diags} illustrates the hand-bag diagram for coherent DVCS on 
+$^4$He. Similar to the proton case, at large virtual photon's 4-momentum square 
+$Q^2=-(k-k')^{2}$ and small squared momentum transfer $t=(p-p')^{2}$ (in terms 
+of the electron, $k(k')$, and $^4$He, $p(p')$, four-vectors), the DVCS handbag 
+diagram can be factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The 
+hard part includes the photon-quark interaction and is calculable in 
+perturbative QCD. The non-perturbative part is parametrized in terms of GPDs, 
+which embed the partonic structure of the hadron. The GPDs depend on the three 
+variables $x$, $\xi$, and $t$ as introduced in FIG.~\ref{fig:diags}. The 
+parameter $\xi$ relates to the Bjorken variable $x_{B}$: $\xi\approx 
+{{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M\nu}$, $\nu=k^0-k^{0\prime}$, and 
+$M$ is the proton mass. The parameter $x$ is the quark's internal loop momentum 
+fraction and cannot be accessed experimentally. In the experiment we measure 
+Compton form factors (CFF) \cite{Guidal:2013rya}, for which their real and 
+complex amplitudes are defined at leading order as:
 
@@
 
-Until now, the only available data on nuclear DVCS was from the 
-HERMES experiment \cite{Ellinghaus:2002zw}, where coherence in the reaction was based only on 
-kinematic cuts on the measured scattered electron and real photon. That 
+Until now, the only available data on nuclear DVCS was from the HERMES 
+experiment \cite{Ellinghaus:2002zw}, where coherence in the reaction was based 
+only on kinematic cuts on the measured scattered electron and real photon. That 
 measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and Xe), 
@@
 measurement significantly \cite{Guzey:2003jh}. In this regard, direct detection 
-of the low-energy recoil nucleus is the best way to guarantee the nucleus 
-remains intact and that the reaction did not occur on a bound nucleon. The 
-CEBAF Large Acceptance Spectrometer (CLAS) in Hall-B at JLab is already 
-optimized for DVCS measurements 
+of the low-energy recoil nucleus is the best way to guarantee that the nucleus 
+remains intact. The CEBAF large acceptance spectrometer (CLAS) in Hall-B at 
+Jefferson Lab has been previously used for DVCS measurements on nucleon
 \cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.
 
-In order to measure DVCS on $^4$He with a fully exclusive final state, we 
-built a specialized radial time projection chamber (RTPC) for detection and identification of
-low energy recoiling light nuclei. The $^4$He nucleus is an ideal experimental target in this regard, as 
-it is light enough to be detected in such a setting, while it
-is subject to significant nuclear effects \cite{JSeely} and has rather high 
-density.  A helium target leads to another important advantage, as the number of GPDs 
-defined for a hadron depends on its spin. The structure of a spin zero nucleus, such as 
-$^4$He, is parametrized by only one chiral even GPD ($H_{A}(x,\xi,t)$) at 
-leading twist, while 4 GPDs arise in the nucleon case. This significantly
-simplifies the interpretation of the data and allows a model independent
-extraction of the $^4$He CFF ($\mathcal{H}_{A}$) presented at the
-end of this letter.
+In order to measure DVCS on $^4$He with a fully exclusive final state, we built 
+a specialized radial time projection chamber (RTPC) for detection and 
+identification of low energy recoiling light nuclei. The $^4$He nucleus is an 
+ideal experimental target in this regard, as it is light enough to be detected 
+in such a setting, while it is subject to significant nuclear effects 
+\cite{JSeely} and has rather high density. A helium target leads to another 
+important advantage, as the number of GPDs defined for a hadron depends on its 
+spin. The structure of a spin zero nucleus, such as $^4$He, is parametrized by 
+only one chiral even GPD ($H_{A}(x,\xi,t)$) at leading twist, while 4 GPDs 
+arise in the nucleon case. This significantly simplifies the interpretation of 
+the data and allows a model independent extraction of the $^4$He CFF 
+($\mathcal{H}_{A}$) presented at the end of this letter.
 
@@
 nearly 100\% duty factor, longitudinally polarized electron beam (83$\%$ 
-polarization) at energy of 6.064 GeV. The data were collected over 40 days 
-using a 6 atm gaseous $^4$He target placed 64 cm upstream of the nominal center of CLAS. For DVCS 
-experiments, the CLAS baseline design \cite{Mecking:2003zu} is supplemented 
-with an inner calorimeter (IC) and a solenoid. The IC extends the photon 
-detection acceptance of CLAS to polar angles as low as 4$^{\circ}$. The 
-low-energy M\o{}ller electrons produced in the target form a very high rate 
-background that is suppressed by a 5 Tesla solenoid placed around the target.
+polarization) at an energy of 6.064 GeV. The data were collected over 40 days 
+using a 6 atm gaseous $^4$He target placed 64 cm upstream of the nominal center 
+of CLAS. For DVCS experiments, the CLAS baseline design \cite{Mecking:2003zu} 
+is supplemented with an inner calorimeter (IC) and a solenoid magnet. The IC 
+extends the photon detection acceptance of CLAS to polar angles as low as 
+4$^{\circ}$. The low-energy M\o{}ller electrons produced in the target form a 
+very high rate background that is suppressed by a 5 Tesla solenoid magnet 
+placed around the target.
 
@@
 particles, so in order to ensure the exclusivity of the measurement, we built a 
-small and light RTPC to complement CLAS. In Figure~\ref{fig:RTPC} a picture of 
-RTPC installed in the experimental hall, and the rendering showing detector 
-components and the $^4$He detection concept are presented. The $^4$He gaseous 
-target, a $25$ cm long Kapton straw with $27~\mu$m thick wall, was part of the RTPC
-assembly and installed on the axis of the detector. The RTPC was calibrated specifically for the detection 
-of $^4$He nuclei using elastic scattering with a 1.2~GeV electron beam.
+small and light RTPC to complement CLAS. Presented in FIG.~\ref{fig:RTPC} are a 
+picture of RTPC installed in the experimental hall and a diagram showing the 
+basic detection technique. The $^4$He gaseous target, a $25$ cm long Kapton 
+straw with $27~\mu$m thick wall, was part of the RTPC assembly and installed on 
+the axis of the detector. The RTPC was calibrated specifically for the 
+detection of $^4$He nuclei using elastic scattering with a 1.2~GeV electron 
+beam.
 
@@
 %DVCS selection
-To identify coherent DVCS events, we first select events where one 
-electron, one $^4$He, and at least one photon are detected in the final state.
-Electrons are identified using measured momentum, time, and energy in the fiducial 
-volume of the CLAS system's drift chambers, Cerenkov counters, scintillator counters, and 
-electromagnetic calorimeters. The recoiling $^4$He nuclei are identified in the RTPC using time, 
-track quality, and energy loss cuts for tracks in the fiducial region. In 
-addition, we apply a vertex matching cut to ensure that the electron and helium
-nucleus originate from the same position. The photons are detected in either
-the IC or the CLAS electromagnetic calorimeter. Note that even though the DVCS 
-reaction has only one real photon in the final state, events with more than one 
-good photon are not discarded at this stage. This is motivated by the fact 
-that, while soft photons are likely to be produced in random coincidence, they 
-cannot be mistaken for the large energy DVCS photons ($>2$ GeV).
-The most energetic photon is always considered as the DVCS photon candidate.
+To identify coherent DVCS events, we first select events where one electron, 
+one $^4$He, and at least one photon are detected in the final state. Electrons 
+are identified using measured momentum, time, and energy in the fiducial volume 
+of the CLAS system's drift chambers, Cerenkov counters, scintillator counters, 
+and electromagnetic calorimeters. The recoiling $^4$He nuclei are identified in 
+the RTPC using time, track quality, and energy loss cuts for tracks in the 
+fiducial region. In addition, we apply a vertex matching cut to ensure that the 
+electron and helium nucleus originate from the same position. The photons are 
+detected in either the IC or the CLAS electromagnetic calorimeter. Note that 
+even though the DVCS reaction has only one real photon in the final state, 
+events with more than one good photon are not discarded at this stage. This is 
+motivated by the fact that, while soft photons are likely to be produced in 
+random coincidence, they cannot be mistaken for the large energy DVCS photons 
+($>2$ GeV). The most energetic photon is always considered as the DVCS photon 
+candidate.
 
 To ensure the interaction occurs at the partonic level and the DVCS handbag 
-diagram is dominant, we select events with $Q^{2}>1~[GeV^{2}/c^{2}]$.  
-Exclusivity of the coherent DVCS reaction is optimized by applying a set of 
-cuts on the following kinematic variables: the co-planarity angle ($\Delta 
-\phi$), \textit{i.e.}, the angle between the ($\gamma,\gamma^*$) and 
-($\gamma^*,^4He'$) planes, the missing energy, the missing mass squared, the 
-missing transverse momentum of the $e'^4He'\gamma$ system, the missing mass 
-squared of the $e'^4He'$ system, and the angle ($\theta$) between the measured 
-photon and the missing momentum of the $e'^4He'$ system. The most relevant of 
-these cuts are presented in Figure~\ref{fig:kin-cuts}, which shows 3$\sigma$ 
-cuts except for the missing energy (which appears to be too large and for which 
-we reduced the cut window to [-0.45,0.5] GeV).  We also reject events where a 
-$\pi^0$ is identified by invariant mass reconstruction of two photons.  After 
-these requirements, we have about 3200 DVCS events left, and Figure 
-\ref{fig:kin-coverage} presents their kinematic distributions in 
+diagram is dominant, we select events with $Q^{2}$ greater than 1 
+$[GeV^{2}/c^{2}]$. Exclusivity of the coherent DVCS reaction is optimized by 
+applying a set of cuts on the following kinematic variables: the co-planarity 
+angle ($\Delta \phi$), \textit{i.e.}, the angle between the ($\gamma,\gamma^*$) 
+and ($\gamma^*$,$^4$He$'$) planes, the missing energy, the missing mass 
+squared, the missing transverse momentum of the $e'^4$He$'\gamma$ system, the 
+missing mass squared of the $e'^4$He$'$ system, and the angle ($\theta$) 
+between the measured photon and the missing momentum of the $e'^4$He$'$ system.  
+The most relevant of these cuts are presented in Figure~\ref{fig:kin-cuts}, 
+which shows 3$\sigma$ cuts except for the missing energy (which appears to be 
+too large and for which we reduced the cut window to [-0.45,0.5] GeV).  We also 
+reject events where a $\pi^0$ is identified by invariant mass reconstruction of 
+two photons.  About 3200 events pass these requirements and are shown in 
+FIG.~\ref{fig:kin-coverage} as their kinematic distributions in 
 ($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$).
@@
 where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
-and real parts of the $^4$He CFF $\mathcal{H}_{A}$ that depends on the GPD 
+and real parts of the $^4$He CFF $\mathcal{H}_{A}$ that depend on the GPD 
 $H_A$. In Eq.~\ref{eq:A_LU-coh}, $\phi$ is the azimuthal angle between the 
-($e$,$e'$) and ($\gamma^{*}$,$^4$He$'$) planes. The kinematic factors $\alpha_i$
+($e$,$e'$) and ($\gamma^{*}$,$^4$He$'$) planes. The kinematic factors 
+$\alpha_i$
 depend on azimuthal angle $\phi$, the nuclear form factor 
@@
 
-The $Q^2$, $X_B$, and $t$ dependencies of the $^4$He CFF $\mathcal{H}_A$ 
+The $Q^2$, $x_B$, and $t$ dependencies of the $^4$He CFF $\mathcal{H}_A$ 
 extracted from the fit to the azimuthal dependence of $A_{LU}$ are shown in 
@@
 \cite{Vadim_priv}, the nucleus is assumed to be composed of non-relativistic 
-nucleons, each interacting independently with 
-the probe. The Convolution-Dual model is based on nucleon GPDs from the dual 
-parametrization \cite{Guzey:2006xi}, where the Convolution-VGG uses nucleon 
-GPDs  from the VGG model and is based on the double distributions ansatz 
-\cite{DD_model}. The off-shell model \cite{GonzalezHernandez:2012jv} relies on 
-the impulse approximation and uses advanced spectral functions of  nuclei that 
-account for all configurations of the final nuclear system and the binding 
-effects between the nucleons.
+nucleons, each interacting independently with the probe. The Convolution-Dual 
+model is based on nucleon GPDs from the dual parametrization 
+\cite{Guzey:2006xi}, where the Convolution-VGG uses nucleon GPDs  from the VGG 
+model and is based on the double distributions ansatz \cite{DD_model}. The 
+off-shell model \cite{GonzalezHernandez:2012jv} relies on the impulse 
+approximation and uses advanced spectral functions of  nuclei that account for 
+all configurations of the final nuclear system and the binding effects between 
+the nucleons.
 

### 2017-02-25 for_eg6_group/incoh-2/Incoh.tex
added a subdirectory for eg6 comments on the coherent paper and another subdirectory for the incoherent channel inestigation.

@@
 
+%\begin{figure}[h!]
+%\includegraphics[height=5.0cm]{fig/T_tprime_Coh.png}
+%\includegraphics[height=5.0cm]{fig/T_tprime_InCoh.png}
+%\caption{On the left: the coherent relative difference between $t$ and $t'$.  
+%On the right: the incoherent relative difference.}
+%\label{fig:tprime}
+%\end{figure}
+
 \begin{figure}[h!]
-\includegraphics[height=5.0cm]{fig/T_tprime_Coh.png}
-\includegraphics[height=5.0cm]{fig/T_tprime_InCoh.png}
-\caption{On the left: the coherent relative difference between $t$ and $t'$.  
-On the right: the incoherent relative difference.}
+\includegraphics[height=20.0cm]{fig/bins_InCoh_t_tc_tprime.pdf}
+\caption{t, tc, and t' for incoherent DVCS events}
 \label{fig:tprime}
@@
 
+\newpage
+\newpage
+\newpage
+\newpage
+\newpage
+\section*{t, tc, and t' for coherent and incoherent DVCS channels}
+
+%\begin{figure}[h!]
+%\includegraphics[height=20.0cm]{fig/t_tc_trpime_Coh_bins.pdf}
+%\caption{}
+%\label{fig:}
+%\end{figure}
+
 \end{document}

### 2017-02-27 eg6-letters/coherent/dvcs_he4_prl.tex
update the labels on figures 3 and 4 in the coherent paper and update the reponse to eg6 comments

@@
 Compton form factors (CFF) \cite{Guidal:2013rya}, for which their real and 
-complex amplitudes are defined at leading order as:
+complex amplitudes are defined at leading order as
 
@@
 diagram is dominant, we select events with $Q^{2}$ greater than 1 
-$[GeV^{2}/c^{2}]$. Exclusivity of the coherent DVCS reaction is optimized by 
+$GeV^{2}/c^{2}$. Exclusivity of the coherent DVCS reaction is optimized by 
 applying a set of cuts on the following kinematic variables: the co-planarity 
@@
 between the measured photon and the missing momentum of the $e'^4$He$'$ system.  
-The most relevant of these cuts are presented in Figure~\ref{fig:kin-cuts}, 
-which shows 3$\sigma$ cuts except for the missing energy (which appears to be 
-too large and for which we reduced the cut window to [-0.45,0.5] GeV).  We also 
+The most relevant of these cuts are presented in FIG.~\ref{fig:kin-cuts}, which 
+shows 3$\sigma$ cuts except for the missing energy (which appears to be too 
+large and for which we reduced the cut window to [-0.45,0.5] GeV).  We also 
 reject events where a $\pi^0$ is identified by invariant mass reconstruction of 
-two photons.  About 3200 events pass these requirements and are shown in 
-FIG.~\ref{fig:kin-coverage} as their kinematic distributions in 
-($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$).
+two photons. About 3200 events pass these requirements. Their kinematic 
+distributions are shown in FIG.~\ref{fig:kin-coverage}.
 
@@
 the quantity plotted. The vertical red lines represent the applied exclusivity 
-cuts. The distributions from left to right and from top to bottoms are: $\Delta 
+cuts. The distributions from left to right and from top to bottom are: $\Delta 
 \phi$, missing energy, missing mass squared and the cone angle ($\theta$) 
@@
 in \cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the beam-spin 
-asymmetry ($A_{LU}$) of a spin-zero hadron can be expressed as:
+asymmetry of a spin-zero hadron can be expressed as
 \begin{equation}
@@
 where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
-and real parts of the $^4$He CFF $\mathcal{H}_{A}$ that depend on the GPD 
-$H_A$. In Eq.~\ref{eq:A_LU-coh}, $\phi$ is the azimuthal angle between the 
-($e$,$e'$) and ($\gamma^{*}$,$^4$He$'$) planes. The kinematic factors 
-$\alpha_i$
-depend on azimuthal angle $\phi$, the nuclear form factor 
-$F_A(t)$, $Q^2$ and $x_B$. These factors are written as:
+and real parts of the $^4$He CFF $\mathcal{H}_{A}$ and depend on the GPD $H_A$.  
+The kinematic factors $\alpha_i$ depend on azimuthal angle $\phi$, the nuclear 
+form factor $F_A(t)$, $Q^2$ and $x_B$. These factors are written as
 \begin{align}
@@
 \end{align}
-where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$($M_{N}$) is the $^4$He 
+where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$($M_{N}$) the $^4$He 
 (nucleon) mass, $\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$ and 
-$y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, $\mathcal{P}_1(\phi)$ and $\mathcal 
+$y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, and $\mathcal{P}_1(\phi)$ and $\mathcal 
 {P}_2(\phi)$ are the Bethe-Heitler propagators. The factors $c_{0,1,2}^{BH}$, 
@@
 Due to limited statistics, dependence on the kinematical variables $Q^2$, 
-$x_B$, and $t$ has been studied separately. In Figure \ref{fig:alu}, $A_{LU}$ 
-for the three sets of binning is presented. The curves on the plots are fits 
-with the function presented in Eq.~\ref{eq:A_LU-coh}, where the real and 
-imaginary parts of the CFF $\mathcal{H}_{A}$ are the free parameters of the fit. 
-In Figure \ref{fig:alu90} the $Q^2$, $x_{B}$, and $-t$-dependencies of the 
-fitted $A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and 
-$-t$-dependencies are compared to theoretical calculations performed by 
-S.~Liuti and K.~Taneja \cite{simonetta_2}. The model relies on the impulse 
-approximation and uses advanced spectral functions of nuclei. The calculations 
-are at slightly different kinematics than our data but still provide some 
-guidance. The experimental results appear to have larger asymmetries than the 
-calculations. These differences may arise from nuclear effects, such as 
-long-rage interactions, which are not taken into account in the model.
+$x_B$, and $t$ has been studied separately. In FIG.~\ref{fig:alu}, $A_{LU}$ for 
+the three sets of binning is presented. The curves on the plots are fits with 
+the function presented in Eq.~\ref{eq:A_LU-coh}, where the real and imaginary 
+parts of the CFF $\mathcal{H}_{A}$ are the free parameters of the fit.  In 
+FIG.~\ref{fig:alu90} the $Q^2$, $x_{B}$, and $t$-dependencies of the fitted 
+$A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and $t$-dependencies 
+are compared to theoretical calculations performed by S.~Liuti and K.~Taneja 
+\cite{simonetta_2}. The model relies on the impulse approximation and uses 
+advanced spectral functions of nuclei. The calculations are at slightly 
+different kinematics than our data but still provide some guidance. The 
+experimental results appear to have larger asymmetries than the calculations.  
+These differences may arise from nuclear effects, such as long-rage 
+interactions, which are not taken into account in the model.
 
@@
 \caption{The coherent $A_{LU}$ as a function of $\phi$. Results are presented
-   for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle panel), and 
-   $-t$ bins (bottom panel).  
-   The error bars represent the statistical uncertainties. The gray 
-   bands represent the systematic uncertainties, including the normalisation 
-   uncertainties. The red curves are the results of our fits with the form of 
-   equation \ref{eq:A_LU-coh}.}
+   for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle panel), and $t$ 
+   bins (bottom panel).  The error bars represent the statistical 
+   uncertainties. The gray bands represent the systematic uncertainties, 
+   including the normalisation uncertainties. The red curves are the results of 
+our fits with the form of equation \ref{eq:A_LU-coh}.}
 \label{fig:alu}
@@
 \includegraphics[width=8.9cm]{figs/coherent-ALU_90.pdf}
-\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $-t$-dependencies (right) of
+\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $t$-dependencies (right) of
    the $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
@@
 extracted from the fit to the azimuthal dependence of $A_{LU}$ are shown in 
-Figure \ref{fig:CFF_HA}. Curves on the graphs are model calculations, labelled 
+FIG.~\ref{fig:CFF_HA}. Curves on the graphs are model calculations, labelled 
 {\it convolution} and {\it off-shell}. In the convolution model 
@@
 
-The results in Figure \ref{fig:CFF_HA} show that the extraction of the CFF
+The results in FIG.~\ref{fig:CFF_HA} show that the extraction of the CFF
 from the beam spin asymmetry is possible without any model dependent 
 assumptions. The amplitude and the dependencies observed as a function of 
-$Q^{2}$, $x_B$, and $-t$ are in agreement 
-with the theoretical expectations. One can see a difference between the 
-precision of the extracted imaginary and real parts, which is expected from
+$Q^{2}$, $x_B$, and $t$ are in agreement with the theoretical expectations. One 
+can see a difference between the precision of the extracted imaginary and real 
+parts, which is expected from
 Eq.~\ref{eq:A_LU-coh} because $\alpha_2$ is much smaller than $\alpha_1$. While the 
@@
 agreement with predictions of the available models. This first fully exclusive 
-experiment opens new perspectives for studying the nuclear structure with the 
-GPD framework and paves a way for future measurements at JLAB using 12 GeV 
-CEBAF and upgraded equipment.
+experiment opens new perspectives for studying nuclear structure with the GPD 
+framework and paves a way for future measurements at JLAB using 12 GeV CEBAF 
+and upgraded equipment.
 

### 2017-02-28 eg6-letters/coherent/dvcs_he4_prl_liuti.tex
Comments from S. Liuti

--- 2017-02-16 eg6-letters/coherent/dvcs_he4_prl.tex
@@
 \documentclass[twocolumn,nofootinbib,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
-\usepackage{graphicx}
+\usepackage{color,graphicx}
 \usepackage{hyperref}
@@
 In impact parameter space, the GPDs are indeed interpreted as a tomography of the 
-transverse plane for partons carrying a certain longitudinal momentum 
+transverse plane for partons carrying a 
+%certain 
+\textcolor{magenta}{given fraction of the proton}
+longitudinal momentum 
 \cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep,Burkardt:2005hp}.
@@
 CERN.  The vast majority of these measurements focused on the study of proton 
-structure and allowed extraction of the tomography of the nucleon (for details 
+structure and allowed \textcolor{magenta}{for an} extraction of the tomography of the nucleon (for details 
 on the formalism, see 
-\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
+\textcolor{magenta}{\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya,Kumericki:2016ehc}}).
 This framework is also applicable to nuclei, giving access to completely new 
@@
 gluons \cite{Dupre:2015jha}.
-Study of the 3D structure of nuclei appears to be especially important
+\textcolor{magenta}{A} study of the 3D structure of nuclei appears to be especially important
 in light of the large nuclear effects observed in nuclear parton distribution 
@@
 Figure \ref{fig:diags} 
-illustrates the hand bag diagram for coherent DVCS on $^4$He.  Similar to the 
+illustrates the hand bag diagram for coherent DVCS on $^4$He.  Similarly to the 
 proton case, at large virtual photon's 4-momentum square $Q^2=-(k-k')^{2}$ and 
@@
 parameter $x$ is the quark's internal loop momentum fraction and cannot be 
-accessed experimentally. In the experiment we measure Compton Form
-Factors (CFF) \cite{Guidal:2013rya}, complex amplitudes defined as:
+accessed experimentally. In the experiment we measure the Compton Form
+Factors (CFF) \cite{Guidal:2013rya} \textcolor{magenta}{which are} complex amplitudes defined as:
 
@@
 
-The DVCS and well-known Bethe-Heitler (BH) processes, where the real 
+The DVCS and %well-known 
+Bethe-Heitler (BH) processes, where the real 
 photon is emitted by the incoming or the outgoing lepton, have the same final 
@@
 the BH and DVCS amplitudes squared and their interference term, 
-can be decomposed into a finite sum of Fourier harmonics in the azimuthal angle
+%can be decomposed into a finite sum of Fourier harmonics is written in terms of 
+\textcolor{magenta}{depend on} the azimuthal angle
 $\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes, as
@@
 ($e$,$e'$) and ($\gamma^{*}$,$^4$He$'$) planes. The kinematic factors $\alpha_i$
-depend on azimuthal angle $\phi$, the nuclear form factor 
-$F_A(t)$, $Q^2$ and $x_B$. These factors are written as:
-\begin{align}
-   \alpha_0 (\phi) & = \frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi), \\
-   \alpha_1 (\phi) & = c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi), \\ 
-   \alpha_2 (\phi) & = \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( 
-      C_{++}(0) +  C_{++}(1) cos(\phi) \right), \\
-   \alpha_3 (\phi) &= \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
-      {\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
-      \epsilon^2},
-\end{align}
-where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$($M_{N}$) is the $^4$He 
-(nucleon) mass, $\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$ and 
-$y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, $\mathcal{P}_1(\phi)$ and $\mathcal 
-{P}_2(\phi)$ are the Bethe-Heitler propagators. The factors $c_{0,1,2}^{BH}$, 
-$c_0^{DVCS}$, $c_{0,1}^{INT}$ and $s_1^{INT}$ are the Fourier coefficients of 
-the BH, and $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics 
-in the leptonic tensor.  The explicit expressions of these terms can be found 
+%depend 
+\textcolor{magenta}{were written in Ref.\cite{Belitsky:2008bz})} as a function of  
+Fourier harmonics in the azimuthal angle $\phi$, the nuclear form factor 
+$F_A(t)$, and \textcolor{magenta}{the kinematic invariants}, $Q^2$, $x_B$, \textcolor{magenta}{$x_{A} = \displaystyle\frac{x_{B}M_{N}}{M_{A}}$, 
+$y=\displaystyle\frac{Q^2}{2x_{A} M_A E_{beam}}$,
+and $\epsilon = \displaystyle\frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$, where $M_{A}$($M_{N}$) is the $^4$He 
+(nucleon) mass.} 
+%These factors are written as:
+%\begin{align}
+%   \alpha_0 (\phi) & = \frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi), \\
+ %  \alpha_1 (\phi) & = c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi), \\ 
+%   \alpha_2 (\phi) & = \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( 
+%      C_{++}(0) +  C_{++}(1) cos(\phi) \right), \\
+%   \alpha_3 (\phi) &= \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
+%      {\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
+%      \epsilon^2},
+%\end{align}
+%where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$($M_{N}$) is the $^4$He 
+%(nucleon) mass, $\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$ and 
+%$y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, $\mathcal{P}_1(\phi)$ and $\mathcal 
+%{P}_2(\phi)$ are the Bethe-Heitler propagators. The factors $c_{0,1,2}^{BH}$, 
+%$c_0^{DVCS}$, $c_{0,1}^{INT}$ and $s_1^{INT}$ are the Fourier coefficients of 
+%the BH, and $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics 
+%in the leptonic tensor.  
+The explicit expressions of these terms can be found 
 in \cite{Belitsky:2008bz} and show that, by using the $\sin(\phi)$ and 
@@
 $-t$-dependencies are compared to theoretical calculations performed by 
-S.~Liuti and K.~Taneja \cite{simonetta_2}. The model relies on the impulse 
-approximation and uses advanced spectral functions of nuclei. The calculations 
+S.~Liuti and K.~Taneja \cite{simonetta_2}. 
+%The model relies on the impulse 
+%approximation and uses advanced spectral functions of nuclei. 
+\textcolor{magenta}{The model takes into account 
+the effect on the quark distribution of the high virtuality/off-shellness of the nucleon with 
+four-momentum squared not equal to the square of their mass.}
+The calculations 
 are at slightly different kinematics than our data but still provide some 
-guidance. The experimental results appear to have larger asymmetries than the 
-calculations. These differences may arise from nuclear effects, such as 
-long-rage interactions, which are not taken into account in the model.
+guidance. The experimental results appear to have \textcolor{magenta}{a larger asymmetry  than the 
+calculation in the $x_B=0.307$ bin.  This difference arises from the theoretical 
+uncertainty in the determination of the crossing
+point between the antishadowing region, where the parton nuclear distribution is larger than the nucleon one, and 
+the EMC effect region, where the nuclear effect reverses its sign.}
+%These differences may arise from nuclear effects, such as 
+%long-rage interactions, which are not taken into account in the model.
 
@@
 
-The $Q^2$, $X_B$, and $t$ dependencies of the $^4$He CFF $\mathcal{H}_A$ 
+The $Q^2$, $x_B$, and $t$ dependencies of the $^4$He CFF $\mathcal{H}_A$ 
 extracted from the fit to the azimuthal dependence of $A_{LU}$ are shown in 
 Figure \ref{fig:CFF_HA}. Curves on the graphs are model calculations, labelled 
-{\it convolution} and {\it off-shell}. In the convolution model 
+{\it convolution} and {\it off-shell}. \textcolor{magenta}{The off-shell model is the same as in Fig.\ref{fig:alu90}, using an improved 
+GPD model for the free nucleon \cite{GonzalezHernandez:2012jv}}. In the convolution model 
 \cite{Vadim_priv}, the nucleus is assumed to be composed of non-relativistic 
@@
 GPDs  from the VGG model and is based on the double distributions ansatz 
-\cite{DD_model}. The off-shell model \cite{GonzalezHernandez:2012jv} relies on 
-the impulse approximation and uses advanced spectral functions of  nuclei that 
-account for all configurations of the final nuclear system and the binding 
-effects between the nucleons.
+\cite{DD_model}. 
+%The off-shell model \cite{GonzalezHernandez:2012jv} relies on 
+%the impulse approximation and uses advanced spectral functions of  nuclei that 
+%account for all configurations of the final nuclear system and the binding 
+%effects between the nucleons.
 
@@
 
+\bibitem{Kumericki:2016ehc} 
+  K.~Kumericki, S.~Liuti and H.~Moutarde,
+  %``GPD phenomenology and DVCS fitting : Entering the high-precision era,''
+  Eur.\ Phys.\ J.\ A {\bf 52}, no. 6, 157 (2016)
+
 \bibitem{Dupre:2015jha} 

### 2017-02-28 eg6-letters/coherent/dvcs_he4_prl.tex
Implement comments from Simonetta and myself

@@
 In impact parameter space the GPDs are indeed interpreted as a tomography of 
-the transverse plane for partons carrying a certain longitudinal momentum 
+the transverse plane for partons carrying a given fraction of the proton 
+longitudinal momentum 
 \cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep,Burkardt:2005hp}.
@@
 The vast majority of these measurements focused on the study of proton 
-structure and allowed for extraction of the three-dimensional picture of the 
+structure and allowed for an extraction of the three-dimensional picture of the 
 nucleon (for details on the formalism, see 
@@
 $M$ is the proton mass. The parameter $x$ is the quark's internal loop momentum 
-fraction and cannot be accessed experimentally. In the experiment we measure 
-Compton form factors (CFF) \cite{Guidal:2013rya}, for which their real and 
-complex amplitudes are defined at leading order as
+fraction and cannot be accessed experimentally. We in fact measure 
+Compton form factors (CFF) \cite{Guidal:2013rya}, which are
+complex amplitudes defined as:
 
@@
 \vspace{-1.1cm}
-\includegraphics[width=7.0cm,angle=-90]{figs/RTPC.pdf}
+\includegraphics[width=6.5cm,angle=-90]{figs/RTPC.pdf}
 \vspace{-1.1cm}
@@
 \begin{figure}[tb]
-\includegraphics[width=8.9cm]{figs/coh_exc_cuts.pdf}
+\includegraphics[width=8cm]{figs/coh_exc_cuts.pdf}
 \caption{Four of the six coherent DVCS exclusivity cuts. The black 
@@
 \hspace{-0.45cm}
-\includegraphics[width=9.0cm]{figs/Q2_xB_t_Coh.pdf}
+\includegraphics[width=8.0cm]{figs/Q2_xB_t_Coh.pdf}
 \caption{Coherent DVCS event distributions for $Q^{2}$ as a function of 
@@
 In this work, the physics observable extracted using coherent DVCS events is
-the Beam Spin Asymmetry (BSA). The BSA on an unpolarized target, $A_{LU}$, is 
+the beam spin asymmetry (BSA). The BSA on an unpolarized target, $A_{LU}$, is 
 measured as the difference of cross sections of the reaction at opposite beam 
@@
 enhanced in the observables sensitive to the interference term, {\it e.g.} 
-beam spin asymmetry. The three terms entering the cross section calculation,
-the BH and DVCS amplitudes squared and their interference term, 
-can be decomposed into a finite sum of Fourier harmonics in the azimuthal angle
+BSA. The three terms entering the cross section calculation,
+the BH and DVCS amplitudes squared and their interference term depend on the
+azimuthal angle
 $\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes, as
 shown for the nucleon in \cite{Belitsky:2001ns} and for the spin-zero targets
-in \cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the beam-spin 
-asymmetry of a spin-zero hadron can be expressed as
+in \cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the BSA 
+of a spin-zero hadron can be expressed as
 \begin{equation}
@@
 and real parts of the $^4$He CFF $\mathcal{H}_{A}$ and depend on the GPD $H_A$.  
-The kinematic factors $\alpha_i$ depend on azimuthal angle $\phi$, the nuclear 
-form factor $F_A(t)$, $Q^2$ and $x_B$. These factors are written as
-\begin{align}
-   \alpha_0 (\phi) & = \frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi), \\
-   \alpha_1 (\phi) & = c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi), \\ 
-   \alpha_2 (\phi) & = \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( 
-      C_{++}(0) +  C_{++}(1) cos(\phi) \right), \\
-   \alpha_3 (\phi) &= \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
-      {\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
-      \epsilon^2},
-\end{align}
-where $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$ with $M_{A}$($M_{N}$) the $^4$He 
-(nucleon) mass, $\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$ and 
-$y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, and $\mathcal{P}_1(\phi)$ and $\mathcal 
-{P}_2(\phi)$ are the Bethe-Heitler propagators. The factors $c_{0,1,2}^{BH}$, 
-$c_0^{DVCS}$, $c_{0,1}^{INT}$ and $s_1^{INT}$ are the Fourier coefficients of 
-the BH, and $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics 
-in the leptonic tensor.  The explicit expressions of these terms can be found 
-in \cite{Belitsky:2008bz} and show that, by using the $\sin(\phi)$ and 
-$\cos(\phi)$ contributions, it is possible to extract $\Im m(\mathcal{H}_{A})$ 
-and $\Re e(\mathcal{H}_{A})$ from the beam spin
-asymmetry.
+The explicit expression of the kinematic factors $\alpha_i$ are written in 
+\cite{Belitsky:2008bz}, they are functions of Fourier harmonics in the 
+azimuthal angle $\phi$, the nuclear form factor $F_A(t)$, $Q^2$ and $x_B$,
+$x_{A} = \frac{x_{B}M_{N}}{M_{A}}$, $y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, and 
+$\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$, where $M_{A}$($M_{N}$) is the $^4$He 
+(nucleon) mass. Using the different $\sin(\phi)$ and $\cos(\phi)$ contributions 
+in these factors, it is possible to extract unequivocally both imaginary and real 
+parts of $\mathcal{H}_{A}$ from the BSA.
 
@@
 are compared to theoretical calculations performed by S.~Liuti and K.~Taneja 
-\cite{simonetta_2}. The model relies on the impulse approximation and uses 
-advanced spectral functions of nuclei. The calculations are at slightly 
+\cite{simonetta_2}. The model takes into account the effect on the quark 
+distribution of the virtuality of the nucleon ({\it i.e.} with four-momentum 
+squared not equal to the square of their mass). The calculations are at slightly 
 different kinematics than our data but still provide some guidance. The 
-experimental results appear to have larger asymmetries than the calculations.  
-These differences may arise from nuclear effects, such as long-rage 
-interactions, which are not taken into account in the model.
+experimental results appear to have a larger asymmetries than the calculations
+in the $x_B = 0.307$ bin. The difference may arise from the theoretical 
+uncertainty in the determination of the crossing point between the 
+antishadowing region, where the parton nuclear distribution is larger than the 
+nucleon one, and the EMC effect region, where the nuclear effect reverses its 
+sign.
 
 \begin{figure}[tb]
-\includegraphics[width=8.9cm]{figs/coherent-ALU.pdf}
+\includegraphics[width=8cm]{figs/coherent-ALU.pdf}
 \caption{The coherent $A_{LU}$ as a function of $\phi$. Results are presented
@@
 
-\begin{figure}[tb]
-\includegraphics[width=8.9cm]{figs/coherent-ALU_90.pdf}
+\begin{figure*}[tb]
+\includegraphics[width=17cm]{figs/coherent-ALU_90.pdf}
 \caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $t$-dependencies (right) of
@@
    \cite{Airapetian}, the colored curves represent theoretical calculations 
-   %\cite{HERMES_BSA}, the colored curves represent theoretical calculations 
    from \cite{simonetta_2}.}
 \label{fig:alu90}
-\end{figure}
+\end{figure*}
 
 \begin{figure}[tb]
-\includegraphics[width=8.9cm]{figs/Coherent_CFF.pdf}
+\includegraphics[width=8cm]{figs/Coherent_CFF.pdf}
 \caption{The model-independent extraction of the imaginary (top panel) and
@@
 model and is based on the double distributions ansatz \cite{DD_model}. The 
-off-shell model \cite{GonzalezHernandez:2012jv} relies on the impulse 
-approximation and uses advanced spectral functions of  nuclei that account for 
-all configurations of the final nuclear system and the binding effects between 
-the nucleons.
+off-shell model is the same as in Figure \ref{fig:alu90} using an improved
+GPD model for the nucleon \cite{GonzalezHernandez:2012jv}.
 
 The results in FIG.~\ref{fig:CFF_HA} show that the extraction of the CFF
-from the beam spin asymmetry is possible without any model dependent 
+from the BSA is possible without any model dependent 
 assumptions. The amplitude and the dependencies observed as a function of 
@@
 coherent DVCS process.
-The azimuthal dependence of the measured beam spin asymmetry ($A_{LU}$) has 
+The azimuthal dependence of the measured BSA ($A_{LU}$) has 
 been used to extract, in model independent way, the real and the imaginary 
@@
 \bibitem{GonzalezHernandez:2012jv}
-Private communications with S.~Liuti based on: 
 J.~O.~Gonzalez-Hernandez, S.~Liuti, G.~R.~Goldstein and K.~Kathuria,

### 2017-02-28 eg6-letters/coherent/dvcs_he4_prl.tex
removed figure 2 and cleaned the related text.

@@
 particles, so in order to ensure the exclusivity of the measurement, we built a 
-small and light RTPC to complement CLAS. Presented in FIG.~\ref{fig:RTPC} are a 
-picture of RTPC installed in the experimental hall and a diagram showing the 
-basic detection technique. The $^4$He gaseous target, a $25$ cm long Kapton 
-straw with $27~\mu$m thick wall, was part of the RTPC assembly and installed on 
-the axis of the detector. The RTPC was calibrated specifically for the 
-detection of $^4$He nuclei using elastic scattering with a 1.2~GeV electron 
-beam.
+small and light RTPC to complement CLAS. The RTPC is a $20$ cm long cylinder 
+with a diameter of $15$ cm, positioned directly around the $^4$He gaseous 
+target. The target is a $25$ cm long and $6$ mm diameter Kapton straw with 
+$27~\mu$m thick wall. The RTPC was calibrated specifically for the detection of 
+$^4$He nuclei using elastic scattering with a 1.2~GeV electron beam.
 
-\begin{figure}[tb]
-\vspace{-1.1cm}
-\includegraphics[width=6.5cm,angle=-90]{figs/RTPC.pdf}
-\vspace{-1.1cm}
-\caption{Left: A picture of the E08-024 RTPC before insertion into the 
-   solenoid. Right: A cross section of the E08-024 RTPC perpendicular to the 
-   beam direction. An illustration of a $^4$He track originating from the 
-   pressurized straw target is shown along with the electrons produced in the 
-   drift region.}
-\label{fig:RTPC}
-\end{figure}
+%\begin{figure}[tb]
+%\vspace{-1.1cm}
+%\includegraphics[width=6.5cm,angle=-90]{figs/RTPC.pdf}
+%\vspace{-1.1cm}
+%\caption{Left: A picture of the E08-024 RTPC before insertion into the 
+%solenoid. Right: A cross section of the E08-024 RTPC perpendicular to the beam 
+%direction. An illustration of a $^4$He track originating from the pressurized 
+%straw target is shown along with the electrons produced in the drift region.}
+%\label{fig:RTPC}
+%\end{figure}
 

### 2017-03-23 eg6-letters/incoherent/incoherent_prl.tex
update the incoherent channel investigation regarading t, t' and update the incoherent prl

@@
    the HERMES $-A_{LU}$ (positron beam was used) inclusive measurements 
-   \cite{HERMES_BSA}, the colored curves represent theoretical calculations 
-   from \cite{simonetta_2}.}
+\cite{Airapetian}, the colored curves represent theoretical calculations from 
+\cite{simonetta_2}.}
 \label{fig:alu90}
+\end{figure}
+
+\begin{figure}[tp]
+\centering
+\includegraphics[width=6.9cm]{figs/ALU_ratioInc_Q2_shortscenrario.pdf}\\
+\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}\\
+\includegraphics[width=6.9cm]{figs/ALU_ratioInc_t_shortscenrario.pdf}
+\caption{ The $A_{LU}$ ratio between the bound and the free proton at 
+   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
+   middle), and $t$ (on the bottom). The black squares are our results, the 
+   green circles are the HERMES inclusive measurement \cite{Airapetian} 
+   results.  The blue and red curves are from an on-shell calculations from S.  
+   Liuti and K.  Taneja \cite{simonetta_2}. The solid and dashed black curves 
+are from the off-shell calculations \cite{Guzey:2008fe}.} 
+\label{fig:incoh_EMC_ratio_ALU_proton}
 \end{figure}
@@
 
-\bibitem{Vadim_priv}
-Private communications with V.~Guzey based on: 
-V.~Guzey, Phys.\ Rev.\ C {\bf 78}, 025211 (2008).
-
 \bibitem{Guzey:2006xi}
@@
 
-\bibitem{Guidal_priv}
-Private communications with M.~Guidal based on: 
-M.~Guidal, M.~V.~Polyakov, A.~V.~Radyushkin and M.~Vanderhaeghen, 
-Phys.\ Rev.\ D {\bf 72}, 054013 (2005).
+%\cite{Guzey:2008fe}
+\bibitem{Guzey:2008fe} 
+   V.~Guzey, A.~W.~Thomas and K.~Tsushima,
+  Phys.\ Lett.\ B {\bf 673}, 9 (2009)
 
@@
 
-\bibitem{GonzalezHernandez:2012jv}
-Private communications with S.~Liuti based on: 
-J.~O.~Gonzalez-Hernandez, S.~Liuti, G.~R.~Goldstein and K.~Kathuria,
-Phys.\ Rev.\ C {\bf 88}, no. 6, 065206, (2013).
-
 \end{thebibliography}

### 2017-03-23 for_eg6_group/incoh_t_EG6_E1DVCS1_2/Incoh.tex
update the incoherent channel investigation regarading t, t' and update the incoherent prl

%\documentclass[a4paper,11pt,twoside]{ThesisStyle}
\documentclass[a4paper,11pt,twoside]{article}
\author{M. Hattawy}
\date{\today}
\include{formatAndDefs}
\begin{document}

\title{\centering{Follow up on the incoherent t, t'}}
\maketitle

\section{Overview}
In our DVCS analysis, we considered the initial proton of the incoherent 
channel to be at rest, while this is not totally true because of the Fermi 
motion. Does this assumption is a good approximation? What other options can be 
used to minimize this effect on the calculated exclusive quantities?\\

Figure \ref{fig:handbag} presents the leading order handbag diagram of the 
incoherent DVCS channel off $^4$He. Ideally, the transferred momentum squared 
($t$) is defined using the initial and the final nucleons' 4-vectors as 
$(p-p')^{2}$. Then as a DVCS requirement, $t$ has to be greater than a certain 
value ($t_{min}$), which is defined using the kinematics of the incoming and 
the scattered electrons. Due to the knowledge lack of the initial proton's 
momentum, this cut maybe inaccurate, causes loosing some good DVCS events and 
leading to inaccurate determination of the exclusivity cuts.\\

\begin{figure}[h!]
\centering
   \includegraphics[height=8.0cm]{fig/handbag_incoherent.pdf}
\caption{Representation of the leading order handbag diagram of the incoherent 
DVCS process off $^4$He}
\label{fig:handbag}
\end{figure}

\section{Investigating the free proton DVCS data}

Typically, the transferred momentum squared $t$ is equal to the transferred 
momentum squared ($t'$) defined between the virtual photon and the final-state 
real photon, as shown in Figure \ref{fig:handbag}.  While defining the momentum 
transferred as $t'$ is a good way to pass the Fermi motion effect on the 
initial bound proton, $t'$ suffers from the radiative effects. In this work, we 
study the radiative effects on $t'$ using the CLAS available free proton DVCS 
data sets, E1-DVCS1 and E1-DVCS2.

Figure \ref{fig:tprime_eg6} presents the collected incoherent DVCS events from 
EG6 data binned into four bins in $t$. In order to evaluate the radiative 
effects on $t'$ we carried out a full analysis on E1-DVCS1 and E1-DVCS2 data 
sets (free proton data). The collected free proton DVCS events in the two data 
sets were binned into similar bins as our incoherent DVCS events. The results 
are presented in figure \ref{fig:tprime_e1dvcs2}.  While the EG6 incoherent 
DVCS events show a relatively more smeared $\frac{t'-t}{t}$ distributions than 
the free proton data sets, the free proton sets show a significant shifts 
specially at low $t$ values.

\begin{figure}[h!]
\centering
\includegraphics[height=19.0cm]{fig/t_tprime_Incoh.pdf}
\caption{The EG6 incoherent DVCS sample. The first row presents the four bins 
in $t$. The second row shows the distribution of $t'$ for the DVCS events in 
each bin in $t$ in the first row plots. The third row shows $\frac{t'-t}{t}$.  
The 4$^{th}$ shows $\frac{t-t'}{t'}$, and the 5$^{th}$ shows $t-t'$.}
\label{fig:tprime_eg6}
\end{figure}

%\begin{figure}[h!]
%\centering
%\includegraphics[height=19.0cm]{fig/E1-dvcs1-t_tprime_Incoh.pdf}
%\caption{The E1-DVCS1 free proton DVCS sample. See the caption of figure 
%\ref{fig:tprime_eg6} for plots description.}
%\label{fig:tprime_e1dvcs1}
%\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[height=19.0cm]{fig/before_corrections_E1-dvcs2-t_tprime_Incoh.pdf}
\caption{The E1-DVCS2 free proton DVCS sample BEFORE correcting $t'$. See the 
caption of figure \ref{fig:tprime_eg6} for plots description.}
\label{fig:tprime_e1dvcs2}
\end{figure}

\section{$t'$ correction}
One can see from the free proton DVCS sample, figure \ref{fig:tprime_e1dvcs2}, 
that $t'$ is slightly shifted compared to $t$, which is considered as the true 
value in the free proton case. This shift in $t'$ is mainly induced by the 
radiative effects on the leptons. Before considering $t'$ in the incoherent EG6 
analysis, $t'$ has to be corrected and the reconstructed free proton 
asymmetries have to be verified in order to estimate the associated systematic 
uncertainties. Figure \ref{fig:corrections_tprime_e1dvcs2} presents the 
distributions of $t-t'$ as a function of $t'$ for the free proton DVCS sample 
from E1-DVCS2 data before and after correcting $t'$. In figure 
\ref{fig:after_tprime_e1dvcs2}, the distributions of figure 
\ref{fig:tprime_e1dvcs2} are shown after the $t'$ corrections.

\begin{figure}[h!]
\centering
\includegraphics[height=10.0cm]{fig/before_corrections_tprimet_t_InCoh.pdf}
\includegraphics[height=10.0cm]{fig/after_corrections_tprimet_t_InCoh.pdf}
\caption{On top: $t-t'$ as a function of $t'$ for the E1-DVCS2 free proton DVCS 
sample BEFORE correcting $t'$. The red line is the extracted correction for 
$t'$. On bottom: $t-t'$ as a function of $t'$ after correcting $t'$.}
\label{fig:corrections_tprime_e1dvcs2}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[height=19.0cm]{fig/after_corrections_E1-dvcs2-t_tprime_Incoh.pdf}
\caption{The E1-DVCS2 free proton DVCS sample AFTER correcting $t'$. See the 
caption of figure \ref{fig:tprime_eg6} for plots description.}
\label{fig:after_tprime_e1dvcs2}
\end{figure}

\section{Comparing the $t$ and the corrected $t'$ asymmetries in the E1-DVCS2 
data set}
Here we compare the E1-DVCS2 free proton DVCS beam-spin asymmetries using $t$ 
and the corrected $t'$ to estimate the associated systematic uncertainties.  
Figure \ref{t_tprime_ALU_phi} presents the reconstructed $A_{LU}$ as a function 
of $\phi$ in the same binning as the incoherent EG6 DVCS channel. The binning 
in $t$ and the corrected $t'$ are the same. Figure \ref{fig:t_tprime_ALU_90} 
presents the $A_{LU}$ at $\phi = 90^{\circ}$ from the fits in figure 
\ref{fig:t_tprime_ALU_phi}, as a function of $t$ and the corrected $t'$ showing 
the estimated systematic uncertainties. No induced systematic uncertainties are 
observed on the $Q^{2}$ and $x_B$, while some appear on $t$, which will be 
added to the EG6 incoherent asymmetries.

\begin{figure}[h!]
\centering
\includegraphics[height=6.0cm]{fig/E1DVCS2-ALU_phi_p_Q2.pdf}
\includegraphics[height=6.0cm]{fig/E1DVCS2-ALU_phi_p_x.pdf}
\includegraphics[height=6.0cm]{fig/E1DVCS2-ALU_phi_p_t.pdf}
\caption{The reconstructed $A_{LU}$ as a function of $\phi$ for the collected 
E1-DVCS2 free proton DVCS sample using $t$ in black points and using the 
corrected $t'$ in red points. The lines represent fits in the form of 
$\frac{\alpha sin(\phi)}{1+\beta cos(\phi)}$ for the two sets of analysis.}
\label{fig:t_tprime_ALU_phi}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[height=7.0cm]{fig/E1DVCS2-ALU_90_p_vs_Q2_shortscenrario.pdf}
\includegraphics[height=7.0cm]{fig/E1DVCS2-ALU_90_p_vs_x_shortscenrario.pdf}
\includegraphics[height=7.0cm]{fig/E1DVCS2-ALU_90_p_vs_t_shortscenrario.pdf}
\caption{$A_{LU}$ at $\phi = 90^{\circ}$ from the fits in figure 
\ref{fig:t_tprime_ALU_phi} as a function of $t$ in black points and as a 
function of the corrected $t'$ in red points.}
\label{fig:t_tprime_ALU_90}
\end{figure}

\section{EG6 Incoherent DVCS channel}
Here we apply the $t'$ corrections that were extracted from the free proton 
asymmetries  to the EG6 incoherent DVCS channel. Then, the asymmetries using 
$t$ are compared to the ones reconstructed using the corrected $t'$. The 
results are presented in figures \ref{fig:alu} and \ref{fig:alu90}.

\begin{figure}[tb]
   \centering
\includegraphics[width=15cm]{fig/ALU_phi_p_Q2.pdf}
\includegraphics[width=15cm]{fig/ALU_phi_p_x.pdf}
\includegraphics[width=15cm]{fig/ALU_phi_p_t.pdf}
\caption{The EG6 incoherent $A_{LU}$ as a function of $\phi$. Results are 
   presented for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle 
panel), and $t$ bins (bottom panel) using $t$ in black points and using the 
corrected $t'$ in red points.  The red curves are the results of our fits with 
the form $\frac{\alpha sin(\phi)}{1+ \beta cos(\phi)}$.}
\label{fig:alu}
\end{figure}

\begin{figure}[tb]
   \centering
\includegraphics[width=12cm]{fig/ALU_90_p_vs_Q2_shortscenrario.pdf}
\includegraphics[width=12cm]{fig/ALU_90_p_vs_x_shortscenrario.pdf}
\includegraphics[width=12cm]{fig/ALU_90_p_vs_t_shortscenrario.pdf}
\caption{The EG6 incoherent $Q^{2}$ (left), $x_{B}$ (middle), and 
$t$-dependencies (right) of the $A_{LU}$ at $\phi$~=~90$^{\circ}$ using $t$ in 
black points and using the corrected $t'$ in red points. }
\label{fig:alu90}
\end{figure}

\section{Conclusions}
We improved the EG6 incoherent DVCS channel via the $t'$ that is calculated 
using the virtual and the final state real photons with corrections based on 
similar analysis on the free proton DVCS sample using the same setup of CLAS 
detector. The $Q^{2}$ and $x_B$ dependences of the asymmetries have shown 
slight changes using $t'$ rather than $t$, while the effect is bigger on the 
t-dependence, with overall changes are compatible with the statistical error 
bars.  Based on the free proton DVCS data, no induced systematic uncertainties 
are observed on the $Q^{2}$ and $x_B$, while some appear on $t$, which will be 
added to the EG6 incoherent asymmetries.

\end{document}

### 2017-04-03 eg6-letters/NIM/EG6_RTPC_NIM.tex
Correction section 1 of NIM

@@
 Acceptance Spectrometer (CLAS) has been used for similar studies on proton
-targets, however it cannot track recoils with momenta less than 250 MeV/c. In
+targets, however it cannot track low energy $\alpha$ particles. In
 2009, we carried out measurements using the CLAS spectrometer supplemented by
 the RTPC positioned directly around a gaseous $^4$He target, allowing a detection
-threshold as low as $~$100  MeV/c for $^4$He. This article discuses the design,
+threshold as low as $~$150  MeV/c for $^4$He. This article discuses the design,
 work principle, calibration methods and performances of the RTPC.
@@
 Measurement of the Deeply Virtual Compton Scattering (DVCS) process
-($eH \rightarrow e' H' \gamma$, where $H$ is a hadron) necessitates some adaptations
-in this setup.  With a 6 GeV electron beam, the majority of DVCS photons are produced
-at very forward angles where the acceptance of the EC is poor. To extend the range,
-an additional Inner Calorimeter (IC) was built for the E01-113 experiment in 2005.
+($eH \rightarrow e' H' \gamma$, where $H$ is a hadron) necessitates an upgrade
+of this setup.  With a 6 GeV electron beam, the majority of DVCS photons are produced
+at very forward angles, where the acceptance of the EC is poor. To extend the detection range,
+an inner calorimeter (IC) was built for the E01-113 experiment in 2005.
 The IC is constructed from 424 lead-tungstate (PbWO$_{4}$) crystals, covering polar 
@@
 energies between 2 GeV and 5 GeV, with an angular resolution between 3 and 5 mrad 
-\cite{Hyon-suk}.
-
-%M{\o}ller electrons can be
-%very problematic at such small angles, so a 5 Tesla solenoid magnet has been
-%added around the target as a magnetic shield against this low energy background.
-For coherent nuclear processes, the RTPC was developed to extend the tracking
-range of CLAS to low energy nuclei and was used during a one month experimental run
-in 2009 with a longitudinally polarized electron beam of energy 6.064 GeV incident 
+\cite{Hyon-suk}. To protect this detector from the large flux of low energy M{\o}ller 
+electrons, a 5~T solenoid was placed around the target to shield the IC. 
+In addition, the recoil nuclei of the coherent DVCS on helium was detected 
+using a RTPC developed to track low energy nuclear fragments. The solenoid field
+serving as the analyzing magnet for the particle tracking in the RTPC. This 
+setup was used during a three months experimental run
+in 2009 with a longitudinally polarized electron beam of 6.064 GeV incident 
 on a gaseous $^{4}$He target.
-%, with the goal of measuring asymmetries in Deep Virtual Compton 
-%Scattering (DVCS)~\cite{proposal} and exclusive meson production.
-
-Moreover, a 5~T solenoid was placed around the RTPC-target system to shield the IC
-and RTPC from the large flux of low energy M{\o}ller electrons. The solenoid field
-serves also as the analyzing magnet for charged particle tracking by the RTPC.
 
 In this paper we report the design, calibration, and performance of the radial TPC,
-organized as follows.  Section \ref{prev_tpc} presents an overview of the history of
-TPCs.  Section \ref{sec_design} details the physics considerations for our RTPC's
+organized as follows. Section \ref{sec_design} details the physics considerations for our RTPC's
 design and internal structure. Section \ref{sec_readout} describes the properties
@@
 Finally, the performance of the RTPC is described in section \ref{sec_perf}.
-
-\section{TPC technology} \label{prev_tpc}
-In the late 1970s, David R. Nygren presented the concept of the Time Projection 
-Chambers (TPCs) as a new tool to track charged particles based on combining 
-electric and magnetic fields within a sensitive gas volume. The ionized 
-electrons are collected by a position-sensitive electron collection system.  
-Later in 1997, F.~Sauli introduced the Gas Electron Multiplier (GEM) as an 
-effective gas-gain element to improve the tracking efficiency of the TPCs 
-\ref{gem_sauli}. Presently, TPCs are widely used in physics experiments, 
-such as high-energy physics (ALEPH, DELPHI), heavy-ion physics (STAR, ALICE) 
-and rare-event searches (XENON, NEXT).
-
-The first implementation of a radial TPC was performed by the BoNuS experiment
-\cite{BONUS} in 2005. The success of the BoNuS-RTPC in detecting the slow protons
-motivated the development of this new RTPC. For the channels of interest in
-CLAS-EG6 experiment, the recoiling $^{4}$He nuclei have momentum per charge
-around 150 MeV/c. The detection of these low-energy nuclei was the primary
-motivation for designing this detector.
 

### 2017-04-04 eg6-letters/NIM/EG6_RTPC_NIM.tex
Corrections of section 2

@@
 
-\section{CLAS-EG6 RTPC design} \label{sec_design}
-The design of CLAS-EG6 RTPC has been chosen according to physics and 
-experimental requirements.  At 6 GeV incident electron beam energy, recoiling 
-$^{4}$He nuclei from coherent DVCS have an average momentum (per charge) around
-125 MeV/c, while the ``standard'' CLAS detects charged particles above a threshold
-of 250 MeV/c. The chosen design also has to fit within the available space inside
-a 5 Tesla solenoid magnet surrounding the target \cite{Hyon-suk}. Figure
-\ref{fig:RTPC2} shows a photograph of the RTPC before being inserted into the solenoid.
+\section{CLAS RTPC design} \label{sec_design}
 
-The CLAS-EG6 RTPC is a 200~mm long cylinder with a diameter of 150~mm. As charged 
-particles traverse the sensitive gas volume, ionized electrons are released and
-drift, under the effect of an applied electromagnetic field, outward perpendicularly
-to the beam direction. These electrons are then amplified by three layers of GEMs
-and detected by a curved readout system on the external shell, as can be seen in
-the figure~\ref{fig:RTPC_1_4}. The EG6-RTPC has two detection halves, but, unlike
-the BoNuS RTPC, they share a single chamber.  Each half has independent GEM
-amplification systems that cover about 80\% of the azimuthal angle.
-
-\begin{figure}[tb]
-\centering
-\includegraphics[scale=0.19]{fig/RTPC_exp.png}
-\caption{View of the RTPC ready to be inserted in the solenoid. } 
-\label{fig:RTPC2}
-\end{figure}
+With a 6 GeV incident electron energy, the recoiling $^{4}$He nuclei from coherent 
+DVCS have an average momentum around 250 MeV/c. Such low energy $\alpha$ 
+particles are stopped very rapidly, so the RTPC was designed to be as close 
+as possible to the target and fitting within the 230~mm diameter 
+of the 5 Tesla solenoid magnet surrounding the target \cite{Hyon-suk}.
 
@@
 \includegraphics[scale=0.28]{fig/RTPC_1_all.png}
-\caption{Schematic drawing of CLAS-EG6 RTPC in a plane perpendicular to 
+\caption{Schematic drawing of CLAS RTPC in a plane perpendicular to 
 the beam direction.  See text for description of the elements.} 
@@
 
-As seen in figure~\ref{fig:RTPC_1_4}, the CLAS-EG6 RTPC has the following 
-substructure, from the beam line to the exterior:\\
+The CLAS RTPC is a 250~mm long cylinder of 158~mm diameter, leaving just enough 
+room to fit pre-amplifiers between the RTPC outer shell and the solenoid. The 
+electromagnetic field is directed perpendicularly to the beam direction, 
+such that drifting electrons are pushed away from the beam line. These electrons 
+are amplified by three layers of curved GEMs and detected by the readout system 
+on the external shell of the detector as illustrated in the figure~\ref{fig:RTPC_1_4}. The CLAS 
+RTPC is segmented into two halves with independent GEM amplification systems that 
+cover about 80\% of the azimuthal angle.
+
+We detail here the different regions shown in figure~\ref{fig:RTPC_1_4} starting 
+from the beam line and towards larger radius:\\
 \begin{itemize}
-   \item The target extends along the RTPC's central z-axis, with a diameter of 
-      6 mm and enclosed by a 27-$\mu$m-thick Kapton wall.
-
-   \item The first gas gap covers a radial range of 3 mm to 20 mm. It is 
-      filled with $^{4}$He gas at 1~atm to minimize secondary interactions induced
-      by M\o ller electrons scattered by the beam. This 
+   \item First, the 6 atm helium-4 target extends along the beam line axis, it 
+      is 284~mm long with a 3~mm radius wall made of a 27-$\mu$m-thick Kapton.
+   \item The first gas gap covers a radial range from 3 mm to 20 mm. It is 
+      filled with $^{4}$He gas at 1~atm to minimize secondary interactions from
+      M\o ller electrons scattered by the beam. This 
       region is surrounded by a 4 $\mu$m thick window made of aluminized Mylar 
@@
       is surrounded by a 4~$\mu$m thick window made of aluminized Mylar, which 
-      serves as the cathode.
-
+      serves as the cathode. {\bf \color{red} What Voltage ?}
    \item The drift region is filled with the same Ne-DME gas mixture and extends 
@@
       from the beam axis. The electric field in this region is around 500~V/cm 
-      (???) and perpendicular to the beam. Field cages are installed at both 
-      ends of the detector in this region. Progressive voltage depending on 
-      radial position is applied on these to maintain a uniform electric field 
-      perpendicular to the beam line at the edges of the RTPC.
-
+      {\bf \color{red} Give exact value.} and perpendicular to the beam.
    \item The electron amplification system is composed of three GEMs located at 
       radii of 60, 63 and 66 mm. In this configuration, the first GEM layer 
-      represents the anode.
-
+      represents the anode. {\bf \color{red} What bias voltage ?}
    \item The readout board has an internal radius of 69~mm and collects charge
@@
 \includegraphics[scale=0.70]{fig/GEM_photo.jpg}
-\caption{A schematic layout of the GEMs system in one module of the RTPC.} 
+\caption{Picture of a GEM foil similar to the one used for our RTPC.} 
 \label{fig:GEMs}
@@
 
-The GEM system has been mainly chosen for this detector for its flexibility, 
-allowing a curved amplification surface. Also, GEMs are  known to create less 
-sparks than other amplicifation technologies for gaseous detectors, which
-provides a cleaner detection of slow nuclei like $^4$He. The GEMs for the EG6-RTPC
-are made from a Kapton insulator layer sandwiched between two 5 $\mu$m copper
+The GEM technology has been chosen for this RTPC for its flexibility, 
+allowing a curved amplification surface. Also, GEMs are known to rarely create 
+sparks{\bf \color{red} Need reference.}, which is important when trying to 
+detect highly ionizing slow nuclei that deposit large amount of energy. The 
+GEMs for this RTPC are made from a Kapton insulator layer 
+{\bf \color{red} Thickness?} sandwiched between two 5 $\mu$m copper
 layers. The mesh of each GEM layer is chemically etched with 50$\mu$m diameter
-holes with double-conical shapes as can be seen in figure~\ref{fig:GEMs}. A
-potential difference of 400 V is applied between the two copper layers of each
-GEM, creating a very strong electric field leading to high ionization 
-from initial electrons and therefore amplification of the signal. Also, a 
-potential difference of 150 V is set between the GEMs to push the amplified 
-electrons toward the readout pads. The gain of each GEM layer is of order 100, 
-making a total gain of about $10^{6}$.\\
+holes with double-conical shapes as illustrated in figure~\ref{fig:GEMs}. A
+potential difference of 400 V {\bf \color{red} To be checked and set as above.} 
+is applied between the two copper layers of the
+GEM, creating a very strong electric field in each hole leading to high ionization 
+and therefore amplification of the incoming electrons. A 
+potential of 150 V {\bf \color{red} To be checked.} 
+is set between the GEMs to push the electrons toward the next GEM and eventually 
+the readout pads. The gain of each GEM layer is of order 100, making a total gain 
+of about $10^{6}$. {\bf \color{red} We should quote a realistic overall gain or nothing.}\\
+
+{\bf \color{red} We should shortly discuss the choice of drift gas.}
 
 \section{Readout System} \label{sec_readout}
+
 The RTPC electron collection system has 3200 readout pads. These elements are

### 2017-04-10 eg6-letters/NIM/EG6_RTPC_NIM.tex
NIM in progress...

@@
 
-{\bf \color{red} We should shortly discuss the choice of drift gas.}
+{\bf \color{red} To be added:
+
+Discuss the choice of drift gas
+
+Discuss the self supporting mechanic of the GEMs.}
 
 \section{Readout System} \label{sec_readout}
-
-The RTPC electron collection system has 3200 readout pads. These elements are
-located at the end of the amplification region, 69 mm from the central axis.
 
@@
 
-Figure \ref{fig:PADs} shows a schematic drawing of the size and the alignment 
+The RTPC electron collection system has 3200 readout pads. These elements are
+located at the end of the amplification region, 69 mm from the central axis.
+Figure \ref{fig:PADs} shows a schematic drawing of the size and 
 configuration of the pads. Each readout pad is 5 mm in length and 4.45 mm in 
@@
 
-Mention ALTRO chip and reference.
+{\bf \color{red} 
+Andrea:
 
-Sparcification.  3 consecutive ADC samples above a threshold of ?, and the three
-samples before and after.
+- Mention ALTRO chip and reference.
 
-Missing items in description:
+- Sparcification method (3 consecutive ADC samples above a threshold of xxx ?, and three
+samples before and after)
 
-Detail the electronic setup: Andrea ? or other Italians?
+- Preamplifiers were from Bonus ?
 
-The gas mixture choice: ???
+- Basics of JLab fADC (is there a reference?)
 
-Discuss HV setting: ???
+- Other relevant information ?
+}
 
 \section{Calibration} \label{sec_calib}
-Two quantities are recorded for each detected electron at the readout board, 
-time (TDCs) and signal amplitude (ADCs) (/!\\ are those amplitude or charge 
-preamps ???). The timing information provides trajectory determination 
-resulting in momentum per unit charge measurement. Going from a collection of 
-the TDCs to a momentum measurement requires good knowledge of the drift speed 
-and paths followed by the electrons released in the gas. The recorded ADCs give 
+
+{\bf \color{red} The use of the term TDC is improper and should be removed
+everywhere. Replace by T.}
+
+Two quantities are recorded at the readout board, 
+time (T) and signal amplitude (ADC). The timing information is used to infer 
+the origin of the charge and then the trajectory of the detected particle
+resulting in momentum measurement. Going from a collection of 
+times to a momentum measurement requires a good knowledge of the drift speed 
+and drift paths followed by the electrons released in the gas. The recorded ADCs give 
 the deposited energy per unit of length ($\small{\frac{dE}{dX}}$) which, 
@@
 identification.
+
+In this section we will detail the methods used to calibrate the drift speed,
+drift paths and gains of the detector. Note that for drift speed and drift
+path we use the symetry of the detector and ...
 

### 2017-04-11 eg6-letters/NIM/EG6_RTPC_NIM.tex
Add a paragraph of context in the calibration section

@@
 In this section we will detail the methods used to calibrate the drift speed,
-drift paths and gains of the detector. Note that for drift speed and drift
-path we use the symetry of the detector and ...
-
-{\bf Don't we want to have description and quality of elastic event selection in here somewhere?}
+drift paths and gains of the detector. Drift speed and paths were initially
+calculated using the MAGBOLTZ~\cite{MAGBOLTZ} program, then refined using
+data to account for variations of the run conditions. We still always assume 
+cylindrical symmetry in the chamber for the calibration, such that none of
+the parameters depend on the asimuthal angle $\phi$. The initial MAGBOLTZ
+calibration was improved through several iterations of the
+process described below, each iteration increasing the number of events 
+properly reconstructed in the RTPC. The figures presented in this section
+are the one obtained while performing the last iteration of this long 
+calibration process.
 
@@
 
-We measure the drift speed using tracks detected in the RTPC. In figure 
+We determine the drift speed using tracks reconstructed in the RTPC. In figure 
 \ref{fig:RTPC_signals}, a typical $^{4}$He track is represented (in green). After 

### 2017-04-12 eg6-letters/NIM/EG6_RTPC_NIM.tex
NIM paper corrections

@@
 \begin{document}
-
-% the following line is for submission, including submission to the arXiv!!
-%\hspace{5.2in} \mbox{Fermilab-Pub-04/xxx-E}
 
@@
 \maketitle
-
-%\tableofcontents
 
@@
 on a gaseous $^{4}$He target.
+{\bf \color{red} Add beam current or luminosity.}
 
@@
 
+- Mention trigger time.
+
 - Preamplifiers were from Bonus ?
@@
 electrons released close to the cathode take the most time to reach the readout 
-pads, but geometrical symmetry insures they always travel the same 
+pads, but cylindrical symmetry insures they always travel the same 
 distance. By identifying the maximum TDC measured, we can infer the drift 
@@
 
-We first measure the drift speed along the 200 mm RTPC's length to take into 
-account variations in the electric and magnetic field, some of which are known 
-(see figure \ref{fig:B_MAP}) some might be due to slight shifts in the 
-geometry. We verified this by looking at the TDC profile generated in the 
-chamber by all our tracks (see figure \ref{fig:TDC_profile}). The time profile 
-of registered hits clearly show the dropping edge expected from the geometrical 
-considerations previously mentioned. We define a value named $TDC_{Max/2}$ at 
+To measure the drift speed, we use the time profile of all hits in the 
+chamber shown in figure \ref{fig:TDC_profile}. We can clearly observe the 
+dropping edge expected from geometrical considerations. We define a value $T_{Max/2}$ at 
 which the dropping edge passes half the maximum number of hits in the 
-histogram, and this value is inversely proportional to the drift speed. The
-result in figure \ref{fig:RunNumber_61551_TDCmax_Zslice} shows the dependence of
-the drift speed on position along the beam line axis in the chamber.
-
-\begin{figure}[tb]
-   \centering
-   \includegraphics[scale=0.35]{fig/B_MAP.png}
-   \caption[]{Schematic drawing of the solenoid magnetic field vectors inside the 
-   RTPC. The $y$-axis is the radial distance from the center of the target, and the
-   $x$-axis is the longitudinal position along the RTPC (with its center at $z=0$).} 
-\label{fig:B_MAP}
-\end{figure}
+histogram. This value is measure in bins along the 200 mm RTPC's length to take into 
+account variations in the electric and magnetic field in the RTPC (see figure 
+\ref{fig:RunNumber_61551_TDCmax_Zslice}).
 
@@
 
-Due to the non perfect experimental conditions including variations in the 
-gas mixture, the drift speed might also change during the month long experimental run.  
-Figure \ref{fig:Drift_run_number_1} shows the $TDC_{Max/2}$ values for 
+Due to the non perfect experimental conditions, in particular variations in the 
+gas mixture\footnote{It was noted during the experiment that leaks appeared
+and the gas flow had to be increased in few occasions to compensate for this.}, 
+the drift speed changes during the three months long experimental run.  
+Figure \ref{fig:Drift_run_number_1} shows the $T_{Max/2}$ values for 
 individual runs (approximately 2 hours long). We observe a significant 
-variation over time and accounted for these changes in the drift speed in the
-track reconstruction. Dealing with such situations is 
-possible by adapting the drift speed as a function of 
-geometry and time (we did not see any correlation between the effects). These 
+variation of the drift speed over time and accounted for it in the drift 
+speed used for the track reconstruction.
+
+In summary, we obtain from our calibration a parametrization of the drift speed 
+as a function of both position along the beam axis and run number (we did not 
+observe any correlation between the effects). These 
 functions were extracted for our entire data set and implemented in the 
-reconstructions code.
+track reconstructions code.
 
@@
 
-\subsection{Drift Paths Parametrization}
+\subsection{Drift Paths Calibration}
 
-The drift paths are the trajectories the electrons follows in the gas. The 
-standard software to calculate drift paths is the MAGBOLTZ program 
-~\cite{MAGBOLTZ}, which requires knowledge of the detector's 
-geometry, the exact composition of the gas mixture, and of course the electric 
-and the magnetic fields. We used such calculations as a first calibration, but, 
-as can be seen with the drift speed, conditions are far from stable in the 
-chamber. Moreover, because we use a thin foil as a cathode, the geometry 
-knowledge is limited to millimeter precision. These problems, already 
-encountered for the BoNuS RTPC calibration (ref), motivated the 
+The drift path is the trajectory followed by the electrons released through 
+ionization in the gas. Software exists to calculate the drift paths, in particular
+MAGBOLTZ~\cite{MAGBOLTZ}, but it requires knowledge of the detector's 
+geometry, gas mixture composition, and of course the electric and magnetic 
+fields over the whole volume of the detector. We used such calculation as a 
+first calibration, but, 
+as can be seen with the drift speed, gas composition is far from stable in the 
+chamber. Moreover, the 4 $\mu$m foil used as a cathode is easily deformed, such
+that we expect the geometry accuracy to be around the millimeter precision. 
+These problems, already 
+encountered for the BoNuS RTPC calibration~\cite{BONUS-NIM}, motivated the 
 acquisition of specific calibration runs. These are taken with a lower energy 
 electron beam (1.20 and 1.27 GeV) to enhance the cross section of the elastic 
-process ($e^{4}$He$\rightarrow e^{4}$He). In this process, measurement of only the 
-electron kinematics gives the Helium nucleus's kinematic and therefore allows 
-to calibrate the drift paths independently of our knowledge of the exact 
-conditions in the chamber.
+process ($e^{4}$He$\rightarrow e^{4}$He)
+{\bf \color{red} Specify luminosity ?}. In this process, the measurement of
+electron kinematics allows to calculate the Helium nucleus kinematic. It is
+by comparing this calculated kinematic to the measured one that we fine tune
+the drift paths independently of our knowledge of the exact conditions in the 
+chamber.
 
-The drift paths' parametrization is possible using identified elastic events 
-from our experiment and a simulated copy of them in a GEANT4 
-simulation~\cite{GEANT4}. Then by comparing the calculated GEANT4 position of 
-the Helium nuclei to the corresponding hits measured in the chamber, we 
-can reconstruct the electrons drift path in the RTPC. However, because of the 
-magnetic field, the drift paths are not linear. So to perform the extraction, 
+The drift paths are ajusted using a set of identified elastic events 
+from our lower beam energy run. Based on the kinematic of the electrons in
+these events, we generate the helium nucleus in a GEANT4 
+simulation~\cite{GEANT4} of our RTPC. Then we compare the calculated GEANT4 trajectory of 
+the Helium nuclei to the hits measured in the chamber.
+
+Because of the 
+magnetic field, the drift paths are not linear in the RTPC. So to perform the extraction, 
 we make a first approximation with a linear dependence between the radius of 
-emission and the TDC of detection, and then refine our result. As it happens, 
+emission and the time of detection, and then refine our result. As it happens, 
 the curvature is minimal and this process converge already on the second 
@@
 
-The steps of the extraction procedure are as follows, where we work
-in a polar coordinate system ($R$,$\phi$).  The azimuthal difference between
-the measured and simulated hit position is $\Delta\phi$.
-
-\begin{figure}[tb]
-\centering
-%\hspace{-0.95cm}
-\includegraphics[scale=0.37]{fig/TdcR_check_p1_10.png}
-\caption{$R$ versus TDC distribution for the simulated hits in a single 
-$z$-bin. The maximum $R$ is 60 mm (close to the anode) at minimum TDCs 
-(the trigger time is 15), and the minimum $R$ is 30 mm (close to the cathode) at 
-maximum TDCs ($\sim75$).}
-\label{fig:R_correlation}
-\end{figure}
-
-\begin{enumerate}
-
-   \item The linear assumption between R and time (TDC) is necessary to link the 
-      generated hits from GEANT4 to physical hits. Figure 
-      \ref{fig:R_correlation} shows our initial $R$ versus TDC.
-
-   \item For these selected hits, we look at $\Delta\phi$ ($\phi_{sim.}-\phi_{hit\_pad}$)
-     versus TDC. We clearly obtain a 
-      correlation shown in figure~\ref{fig:1st_pass_delta_phi}. The relationship
-      between $\Delta\phi$ and TDC encodes the azimuthal drift of the electrons due to 
-      the Lorentz angle.
-
-      \begin{figure}[tb]
-         \centering
-         \includegraphics[scale=0.37]{fig/TdcPhi_p1_10.png}
-         \caption{$\Delta \phi$ versus TDC distribution for the simulated hits 
-         with $z$ near 35 mm.}
-         \label{fig:1st_pass_delta_phi}
-      \end{figure}
-
-   \item Using this first measurement, we can calculate a new correlation 
-      between $R$ and TDC. The result, shown in figure~\ref{fig:R_TDC}, is very 
-      close to linear and explains the fast convergence of our procedure.
-
-      \begin{figure}[tb]
-         \centering
-         \includegraphics[scale=0.37]{fig/R_TDC.png}
-         \caption{The calculated $R$ versus the time is corrected by the 
-         parameters of $\Delta \phi$ from the first pass.}
-         \label{fig:R_TDC}
-      \end{figure}
-
-   \item In the second pass, we associate simulated helium positions to 
-      physical hits according to their calculated correlation and obtain new 
-      $\Delta \phi$ distributions.
-
-   \item We finally parametrize the $\Delta\phi$ distributions with a fit as 
-      can be seen in figure~\ref{fig:DELTA_PHI_TDC}, which shows the final 
-      $\Delta \phi$ versus TDC with a black line representing our drift paths 
-      fit.
-\end{enumerate}
+At the end of the extraction procedure, where we work in a polar coordinate 
+system ($R$,$\phi$), the azimuthal difference between the detection pad and 
+the ionization point ($\Delta\phi$) is extracted as a function of time. 
+In figure~\ref{fig:DELTA_PHI_TDC}, we show the resulting data points for one 
+bin, where the drift paths is easily identified and eventually fitted for 
+implementation in our reconstruction codes.
 
@@
 using both the 1.204 GeV data from the beginning of the run period and the 
-1.269 GeV data from the end of the run period. We found very similar drift paths
+1.269 GeV data from the end of the run period (shown in blue on 
+figure~\ref{fig:Drift_run_number_1}). Strangely, we found very similar drift paths
 for the two data sets and concluded that any changes in the system only
@@
 
+\bibitem{BONUS-NIM}
+Howard C. Fenker et al., BoNuS: Development and Use of a Radial TPC using Cylindrical GEMs, Nucl. Instrum. Meth. A592, 273-286 (2008)
 \end{thebibliography}

### 2017-04-14 eg6-letters/NIM/EG6_RTPC_NIM.tex
Finished reread of NIM

@@
 
-- Mention trigger time.
+- Mention trigger time T=15.
 
@@
 - Basics of JLab fADC (is there a reference?)
+
+- Mention max rate we ran
 
@@
 
-The parametrization of the drift speed and the drift paths were carried out 
-using only the TDCs, gain calibration goal is to equalize the gains in ADC/MeV 
-over the full RTPC. The gain of each pad is the ratio between the actual 
-deposited energy and the registered ADC value. We implemented three different 
+The gain of each pad is defined as the ratio between the actual 
+deposited energy and the registered ADC value. We tested two different 
 methods to extract such gains, with varying degrees of success.
@@
 The first method is based on the measured average $\small{\frac{dE}{dX}}$
-and the expected value based on the Bethe-Bloch formula (PDG REF).  The total energy
+and the expected value based on the Bethe-Bloch formula. The total energy
 deposition for each $^4$He track is calculated as the sum of all ADC hits
@@
 much closer to the expected Bethe-Bloch curve than prior to calibration, the
-results were not very satisfactory.
+results shown in figure~\ref{fig:dedx_p_exp_1st} are not very satisfactory.
+
+\begin{figure}[tb]
+   \includegraphics[scale=0.26]{fig/dedx_p_exp_1st.png}
+   \caption{$\small{\frac{dE}{dX}}$ vs. $p$ distribution for the left half of the 
+      RTPC (left) and for the right half (right). Here, $\small{\frac{dE}{dX}}$ 
+   is calculated using the gains of the first method.  The lines are 
+theoretical expectations from Bethe-Bloch formula for $^4$He, $^3$He, $^3$H and 
+$^2$H (d).{\bf \color{red} Mohammad: Did you multiply p/c by 2 in the figure? If no 
+change the caption, if yes check remove the single charge nuclei from the figure 
+because there is a consistency issue.}}
+\label{fig:dedx_p_exp_1st}
+\end{figure}
 
 The second method is to compare the experimental ADCs to the energy deposited in 
-GEANT4 by simulated tracks (using the same elastic events than for the drift 
+GEANT4 by similar simulated tracks (using the same elastic events than for the drift 
 paths calibration). This requires a very good GEANT4 simulation 
-including drift paths, but also drift and amplification spreads of the charges 
+including drift paths, but also the spread of the charges along the path
 before reaching the pad, so that the simulated hits match the experimental 
@@
 that can lead to cutting out hits. After setting the simulation properly, we 
-can compare simulation to data on an event by event basis as in 
+compared simulation to experiment on an event by event basis as in 
 figure~\ref{fig:EVENT_adc_tdc}. In this step, the gain for each pad is defined 
 as the ratio of the measured ADCs to the simulated deposited energy.
-
-In the third method, the ADC value of each pad is compared to 
+Then, the ADC value of each pad is compared to 
 the ADCs of the other pads inside each track.
-(Detail of 3rd method: Mohammad)
-
-Do you want to show $log(dE/dX)$?
+{\bf \color{red} Mohammad: Detail are missing here.}
+Results of this second method are shown in Figure~\ref{fig:dedx_p_exp_2nd},
+from these we concluded that the gains of the 
+second method match best the theoretical lines.
 
@@
 \begin{figure}[tb]
-   \includegraphics[scale=0.26]{fig/dedx_p_exp_1st.png}
-   \caption{$\small{\frac{dE}{dX}}$ vs. p distribution for the left half of the 
-      RTPC (left) and for the right half (right). Here, $\small{\frac{dE}{dX}}$ 
-   is calculated using the gains of the first method.  The lines are 
-theoretical expectations from Bethe-Bloch formula for $^4$He, $^3$He, $^3$H and 
-$^2$H (d).}
-\label{fig:dedx_p_exp_1st}
-\end{figure}
-
-\begin{figure}[tb]
 \centering
 \includegraphics[scale=0.26]{fig/dedx_p_exp_2nd.png}
-\caption{$\small{\frac{dE}{dX}}$ vs. p distribution for the left half of the 
+\caption{$\small{\frac{dE}{dX}}$ vs. $p$ distribution for the left half of the 
    RTPC (left) and for the right half (right). Here, $\small{\frac{dE}{dX}}$ is 
@@
    expectations from Bethe-Bloch formula for $^4$He, $^3$He, $^3$H and $^2$H 
-(d).}
+(d).{\bf \color{red} Mohammad: Did you multiply p/c by 2 in the figure? If no 
+change the caption, if yes check remove the single charge nuclei from the figure 
+because there is a consistency issue.}}
 \label{fig:dedx_p_exp_2nd}
 \end{figure}
-
-A set of gains has been extracted from each method, in 
-figure~\ref{fig:dedx_p_exp_1st}, we have $\small{\frac{dE}{dX}}$ calculated 
-using the first method's gains, while in Figure~\ref{fig:dedx_p_exp_2nd} we use 
-the second method's gains. From these, we concluded that the gains of the 
-second method match best the theoretical lines. This is not surprising since 
-calibrating with full tracks leads to mixing the gains from the different pads.  
-So it seems that even with several iterations, we could not decipher properly 
-the effects of individual pads with this method.
 
@@
 
-%\begin{figure}[tb]
-%\hspace{-0.4cm}
-%\includegraphics[scale=0.27]{fig/noisy_pad_after_rejection.png}
-%\caption{}
-%\label{fig:noisy_pad_after_rejection}
-%\end{figure}
-
 \section{Track Reconstruction}\label{sec_perf}
@@
 out-of-time hits and hits linked to the electronic noise. The second step is 
-space-reconstructing the hits using the extracted drift speed and drift path 
+to reconstruct the spacial origin of the hits using the extracted drift speed and drift path 
 parameters. For each registered hit, we calculate a position of emission from 
-the recorded time (TDC) and the position of the recording pad. The third step 
+the recorded time and the position of the recording pad. The third step 
 is to create chains of hits. The maximum distance between two close adjacent 
@@
 
-(We need some performance studies here: Mohammad)
+{\bf \color{red} Mohammad: We need some performance studies here, I remember we had
+figures showing efficiency, we need to add them.}
 
 \section{Conclusion}
+
+We reported on the construction, operation and calibration of a small RTPC 
+designed to measure helium-4 nuclei in high rate environnement. The operation
+of the detector was successful and allowed to detect helium nuclei at a rate
+of several kHz in coincidence with the detection of high energy electrons and 
+photons in the CLAS spectrometer.
 

### 2017-04-20 eg6-letters/coherent/dvcs_he4_prl.tex
change the scale of fig 2 in the coherent prl

@@
 Compton scattering off a nucleus for $A>1$. The experiment used the 6 GeV 
-electron beam from the CEBAF machine at Jefferson Lab incident on a $^4$He gas 
-target in the center of the CEBAF large acceptance spectrometer. A new radial 
+electron beam from the CEBAF accelerator at Jefferson Lab incident on a $^4$He gas 
+target in the center of the CEBAF large acceptance spectrometer (CLAS). A new radial 
 time projection chamber (RTPC) was used to detect the recoiling $^4$He
-nuclei and ensure the exclusivity of the process. The measured beam spin 
+nuclei and ensure the exclusivity of the process. The measured beam-spin 
 asymmetries are larger than that observed on the proton in the same kinematic 
-domain. Since $^4$He is a spin zero target, we were able to extract, in a 
-completely model independent way, the real and imaginary parts of the $^4$He 
+domain. Since $^4$He is a spin-zero target, we were able to extract, in a 
+completely model-independent way, the real and imaginary parts of the $^4$He 
 Compton form factors, $\cal H_A$, which are functions of the generalized parton 
@@
 Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
-involving several accelerator facilities such as Jefferson Lab, HERA and  CERN.  
+involving several accelerator facilities such as Jefferson Lab, HERA, and CERN.  
 The vast majority of these measurements focused on the study of proton 
@@
 \includegraphics[width=6.5cm]{figs/DVCS_diagram.pdf}
-\caption{Representation of the leading order hand-bag diagram of the DVCS 
+\caption{Representation of the leading order handbag diagram of the DVCS 
 process off $^4$He.}
@@
 One must overcome two major experimental challenges in measuring coherent 
-nuclear DVCS, $eA\rightarrow^\prime A^\prime\gamma$. First, the cross section 
+nuclear DVCS, $eA\rightarrow e^\prime A^\prime\gamma$. First, the cross section 
 of coherent scattering is suppressed due to the nuclear form factor, and 
 second, the recoil nucleus ($A^\prime$) must be detected to ensure coherence.  
-FIG.~\ref{fig:diags} illustrates the hand-bag diagram for coherent DVCS on 
+Figure \ref{fig:diags} illustrates the handbag diagram for coherent DVCS on 
 $^4$He. Similar to the proton case, at large virtual photon's 4-momentum square 
@@
 which embed the partonic structure of the hadron. The GPDs depend on the three 
-variables $x$, $\xi$, and $t$ as introduced in FIG.~\ref{fig:diags}. The 
+variables $x$, $\xi$, and $t$ as introduced in Fig.~\ref{fig:diags}. The 
 parameter $\xi$ relates to the Bjorken variable $x_{B}$: $\xi\approx 
@@
 experiment \cite{Ellinghaus:2002zw}, where coherence in the reaction was based 
-only on kinematic cuts on the measured scattered electron and real photon. That 
+only on kinematic cuts on the measured scattered electron and real photon. The 
 measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and Xe), 
@@
 of the low-energy recoil nucleus is the best way to guarantee that the nucleus 
-remains intact. The CEBAF large acceptance spectrometer (CLAS) in Hall-B at 
-Jefferson Lab has been previously used for DVCS measurements on nucleon
+remains intact. The CEBAF large acceptance spectrometer in Hall-B at 
+Jefferson Lab has been previously used successfully for DVCS measurements on the nucleon
 \cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.
@@
 In order to measure DVCS on $^4$He with a fully exclusive final state, we built 
-a specialized radial time projection chamber (RTPC) for detection and 
-identification of low energy recoiling light nuclei. The $^4$He nucleus is an 
+a specialized radial time projection chamber (RTPC) for the detection and 
+identification of low-energy recoiling light nuclei. The $^4$He nucleus is an 
 ideal experimental target in this regard, as it is light enough to be detected 
@@
 important advantage, as the number of GPDs defined for a hadron depends on its 
-spin. The structure of a spin zero nucleus, such as $^4$He, is parametrized by 
+spin. The structure of a spin-zero nucleus, such as $^4$He, is parametrized by 
 only one chiral even GPD ($H_{A}(x,\xi,t)$) at leading twist, while 4 GPDs 
@@
 4$^{\circ}$. The low-energy M\o{}ller electrons produced in the target form a 
-very high rate background that is suppressed by a 5 Tesla solenoid magnet 
+very high rate background that is suppressed by a 5-Tesla solenoid magnet 
 placed around the target.
 
-In our kinematics, the recoil $^4$He nuclei produced in DVCS have a low average 
-momentum around 300 MeV/c. CLAS cannot detect such low energy $\alpha$ 
+In our kinematics, the recoil $^4$He nuclei produced in DVCS have low momentum,
+averaging \~300 MeV/c. CLAS cannot detect such low energy $\alpha$ 
 particles, so in order to ensure the exclusivity of the measurement, we built a 
@@
 with a diameter of $15$ cm, positioned directly around the $^4$He gaseous 
-target. The target is a $25$ cm long and $6$ mm diameter Kapton straw with 
-$27~\mu$m thick wall. The RTPC was calibrated specifically for the detection of 
-$^4$He nuclei using elastic scattering with a 1.2~GeV electron beam.
+target. The target is a $25$-cm-long and $6$-mm-diameter Kapton straw with 
+$27~\mu$m thick walls. The RTPC was calibrated specifically for the detection of 
+$^4$He nuclei by utilizing elastic scattering $e^4$He$\to e^\prime$$^4$He with
+a 1.2~GeV electron beam.
 
@@
 one $^4$He, and at least one photon are detected in the final state. Electrons 
-are identified using measured momentum, time, and energy in the fiducial volume 
-of the CLAS system's drift chambers, Cerenkov counters, scintillator counters, 
+are identified using their measured momentum, time, and energy obtained from 
+the CLAS drift chambers, Cerenkov counters, scintillator counters, 
 and electromagnetic calorimeters. The recoiling $^4$He nuclei are identified in 
-the RTPC using time, track quality, and energy loss cuts for tracks in the 
-fiducial region. In addition, we apply a vertex matching cut to ensure that the 
-electron and helium nucleus originate from the same position. The photons are 
+the RTPC using time, track quality, and energy-loss cuts for tracks in the 
+fiducial region. In addition, we apply a vertex-matching cut to ensure that the 
+electron and helium nucleus originate from a common reaction vertex in the target cell. The photons are 
 detected in either the IC or the CLAS electromagnetic calorimeter. Note that 
@@
 diagram is dominant, we select events with $Q^{2}$ greater than 1 
-$GeV^{2}/c^{2}$. Exclusivity of the coherent DVCS reaction is optimized by 
+GeV$^{2}/$c$^{2}$. Exclusivity of the coherent DVCS reaction is optimized by 
 applying a set of cuts on the following kinematic variables: the co-planarity 
-angle ($\Delta \phi$), \textit{i.e.}, the angle between the ($\gamma,\gamma^*$) 
+angle ($\Delta\phi$), \textit{i.e.}, the angle between the ($\gamma,\gamma^*$) 
 and ($\gamma^*$,$^4$He$'$) planes, the missing energy, the missing mass 
@@
 between the measured photon and the missing momentum of the $e'^4$He$'$ system.
-The most relevant of these cuts are presented in FIG.~\ref{fig:kin-cuts}, which 
-shows 3$\sigma$ cuts except for the missing energy (which appears to be too 
-large and for which we reduced the cut window to [-0.45,0.5] GeV).  We also 
+
+The experimental data for the most relevant observables and applied
+cuts is shown in Fig.~\ref{fig:kin-cuts}.
+%The most relevant of these cuts are presented in Fig.~\ref{fig:kin-cuts}, which 
+%shows 3$\sigma$ cuts except for the missing energy (which appears to be too 
+%large and for which we reduced the cut window to [-0.45,0.5] GeV).
+We also 
 reject events where a $\pi^0$ is identified by invariant mass reconstruction of 
 two photons. About 3200 events pass these requirements. Their kinematic 
-distributions are shown in FIG.~\ref{fig:kin-coverage}.
+distributions are shown in Fig.~\ref{fig:kin-coverage}.
 
 \begin{figure}[tb]
-\includegraphics[width=8cm]{figs/coh_exc_cuts.pdf}
+\includegraphics[width=9cm]{figs/coh_exc_cuts.pdf}
 \caption{Four of the six coherent DVCS exclusivity cuts. The black 
-distributions represent the coherent DVCS events candidate. The shaded 
+distributions represent the coherent DVCS events candidates. The shaded 
 distributions represent the events which passed all the exclusivity cuts except 
@@
 \phi$, missing energy, missing mass squared and the cone angle ($\theta$) 
-between the measured and the calculated photons.}
+between the measured and the calculated photon.}
 \label{fig:kin-cuts}
@@
 In this work, the physics observable extracted using coherent DVCS events is
-the beam spin asymmetry (BSA). The BSA on an unpolarized target, $A_{LU}$, is 
-measured as the difference of cross sections of the reaction at opposite beam 
+the beam-spin asymmetry (BSA). The BSA on an unpolarized target, $A_{LU}$, is 
+measured as the difference of cross sections for the reaction with opposite beam 
 helicities normalized to the total cross section:
@@
 where $d^{5}\sigma^{+(-)}$ is the DVCS differential cross 
-section for a positive (negative) beam helicity. 
+section for positive (negative) beam helicity. 
 In this ratio, luminosity normalization and
-detector efficiencies largely cancel and $A_{LU}$ can be expressed in
-terms of helicity-state yields ($N^{+/-}$)
+detector efficiencies largely cancel and $A_{LU}$ can be 
+extracted from the reaction yields for the two helicities ($N^{+/-}$)
+%expressed in terms of helicity-state yields ($N^{+/-}$)
 \begin{equation}
@@
 \end{equation}
-where $P_{B}$ is the beam polarization.
+where $P_{B}$ is the degree of longitudinal polarization of the incident electron beam.
 
-The DVCS and well-known Bethe-Heitler (BH) processes, where the real 
+The DVCS and well-known Bethe-Heitler (BH) processes, in which the real 
 photon is emitted by the incoming or the outgoing lepton, have the same final 
-state and are indistinguishable. The amplitude of real photon 
-electroproduction is a sum of the amplitudes of these two processes. The BH 
+state and are indistinguishable. The amplitude of electroproduction of real
+photons includes a sum of the amplitudes of these two processes. The BH 
 amplitude is defined by the target form factors, while the DVCS amplitude is 
-a combination of the form factors and GPDs. At our kinematics, the cross 
+a combination of the form factors and GPDs. For our kinematics, the cross 
 section of real photon electroproduction is dominated by the BH 
@@
 BSA. The three terms entering the cross section calculation,
-the BH and DVCS amplitudes squared and their interference term depend on the
+the square of the BH and DVCS amplitudes and their interference term, depend on the
 azimuthal angle
 $\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes, as
-shown for the nucleon in \cite{Belitsky:2001ns} and for the spin-zero targets
-in \cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the BSA 
+shown for the nucleon in Ref.~\cite{Belitsky:2001ns} and for the spin-zero targets
+in Refs.~\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the BSA 
 of a spin-zero hadron can be expressed as
@@
 The explicit expression of the kinematic factors $\alpha_i$ are written in
-\cite{Belitsky:2008bz}, they are functions of Fourier harmonics in the 
-azimuthal angle $\phi$, the nuclear form factor $F_A(t)$, $Q^2$ and $x_B$,
+Ref.~\cite{Belitsky:2008bz} and are functions of Fourier harmonics in the 
+azimuthal angle $\phi$, the nuclear form factor $F_A(t)$, $Q^2$, $x_B$,
 $x_{A} = \frac{x_{B}M_{N}}{M_{A}}$, $y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, and 
@@
 (nucleon) mass. Using the different $\sin(\phi)$ and $\cos(\phi)$ contributions 
-in these factors, it is possible to extract unequivocally both imaginary and real 
+in these factors, it is possible to unequivocally extract both imaginary and real 
 parts of $\mathcal{H}_{A}$ from the BSA.
 
-In this work the azimuthal dependence of the BSA, $A_{LU}$, has been studied 
+In this work, the azimuthal dependence of the BSA, $A_{LU}$, has been studied 
 for a wide range of kinematics. We identified two main backgrounds to our 
@@
 The accidentals have particles originating from different events, and we 
-estimate their  contribution to be 4.1\% of our sample. We evaluated this 
+estimated their contribution to be 4.1\% of our sample. We evaluated this 
 contribution by selecting events passing all our cuts but with an electron and 
-helium originating from different vertices. Regarding the $\pi^0$ production, 
-it can easily be mistaken for DVCS when one of the two photons from the $\pi^0$ 
+helium originating from different vertices. The $\pi^0$ production can easily
+be mistaken for DVCS when one of the two photons from the $\pi^0$ 
 decay is produced at low energy in the laboratory frame and remains undetected.  
-To estimate the importance of this background, we developed an event generator 
+To estimate the effect of this background, we developed an event generator 
 tuned on the experimental yield of exclusive $\pi^0$ measured by our 
@@
 detector to estimate the ratio between the number of $\pi^0$ events where the 
-two photons are detected and those that is misidentified as DVCS events. This 
+two photons are detected and those that are misidentified as DVCS events. This 
 ratio is then multiplied by the measured yield of exclusive $\pi^0$ events to 
@@
 contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
-large binning size (5.1\%). However, added quadratically,the total systematic 
+large binning size (5.1\%). However, added quadratically, the total systematic 
 uncertainty is about 10\%, which is significantly smaller than statistical 
@@
 
-Due to limited statistics, dependence on the kinematical variables $Q^2$, 
-$x_B$, and $t$ has been studied separately. In FIG.~\ref{fig:alu}, $A_{LU}$ for 
-the three sets of binning is presented. The curves on the plots are fits with 
-the function presented in Eq.~\ref{eq:A_LU-coh}, where the real and imaginary 
+Due to limited statistics, dependence of the extracted asymmetries on the kinematical variables $Q^2$, 
+$x_B$, and $t$ has been studied separately. In Fig.~\ref{fig:alu}, $A_{LU}$ for 
+bins in each of the three variables is presented. The curves on the plots are fits with 
+the function presented in Eq.~(\ref{eq:A_LU-coh}), where the real and imaginary 
 parts of the CFF $\mathcal{H}_{A}$ are the free parameters of the fit.  In 
-FIG.~\ref{fig:alu90} the $Q^2$, $x_{B}$, and $t$-dependencies of the fitted 
+Fig.~\ref{fig:alu90} the $Q^2$, $x_{B}$, and $t$-dependencies of the fitted 
 $A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and $t$-dependencies 
 are compared to theoretical calculations performed by S.~Liuti and K.~Taneja 
-\cite{simonetta_2}. The model takes into account the effect on the quark 
-distribution of the virtuality of the nucleon ({\it i.e.} with four-momentum 
-squared not equal to the square of their mass). The calculations are at slightly 
+\cite{simonetta_2}. The model accounts for the effect on the quark 
+distribution of the virtuality (off-shellness) of the nucleon. The calculations are at slightly 
 different kinematics than our data but still provide some guidance. The 
@@
 $Q^{2}$ (right panel), $x_B$ (middle panel), and $t$ (left panel). The full red 
-curves are calculations based on an on-shell model from
-\cite{Vadim_priv}. The black-dashed curves are calculations from a convolution 
+curves are calculations based on an on-shell model from Ref.~\cite{Vadim_priv}.
+The black-dashed curves are calculations from a convolution 
 model based on the VGG model for the nucleons' GPDs \cite{Guidal_priv}. The 
 blue long-dashed curve on the top-right plot is from
-an off-shell model based on \cite{GonzalezHernandez:2012jv}.}
+an off-shell model as described in Ref.~\cite{GonzalezHernandez:2012jv}.}
 \label{fig:CFF_HA}
@@
 extracted from the fit to the azimuthal dependence of $A_{LU}$ are shown in 
-FIG.~\ref{fig:CFF_HA}. Curves on the graphs are model calculations, labelled 
+Fig.~\ref{fig:CFF_HA}. Curves on the graphs are model calculations, labelled 
 {\it convolution} and {\it off-shell}. In the convolution model 
@@
 
-The results in FIG.~\ref{fig:CFF_HA} show that the extraction of the CFF
+The results in Fig.~\ref{fig:CFF_HA} show that the extraction of the CFF
 from the BSA is possible without any model dependent 
@@
 parts, which is expected from
-Eq.~\ref{eq:A_LU-coh} because $\alpha_2$ is much smaller than $\alpha_1$. While the 
+Eq.~(\ref{eq:A_LU-coh}) because $\alpha_2$ is much smaller than $\alpha_1$. While the 
 accuracy of our results does not allow to discriminate between the models, they 
@@
 The azimuthal dependence of the measured BSA ($A_{LU}$) has 
-been used to extract, in model independent way, the real and the imaginary 
+been used to extract, in a model independent way, the real and the imaginary 
 parts of the $^4$He CFF, $\mathcal{H}_A$. The extracted CFF is in  
@@
 experiment opens new perspectives for studying nuclear structure with the GPD 
-framework and paves a way for future measurements at JLAB using 12 GeV CEBAF 
+framework and paves the way for future measurements at JLab using 12 GeV CEBAF 
 and upgraded equipment.
@@
 \begin{thebibliography}{99}
+
 \bibitem{Mueller:1998fv} 
@@
 \bibitem{Stepanyan:2001sm}
-S.~Stepanyan {\it et al.} [CLAS Collaboration],
+%S.~Stepanyan {\it et al.} [CLAS Collaboration],
+S.~Stepanyan {\it et al.},
 Phys.\ Rev.\ Lett. {\bf 87}, 182002 (2001).
@@
 \bibitem{Airapetian}
-A. Airapetian {\it et al.} [HERMES Collaboration],
+%A. Airapetian {\it et al.} [HERMES Collaboration],
+A. Airapetian {\it et al.},
 Phys.\ Rev.\ Lett. {\bf 87}, 182001 (2001);
@@
 \bibitem{Chekanov:2003ya}
-S. Chekanov {\it et al.} [ZEUS Collaboration],
+%S. Chekanov {\it et al.} [ZEUS Collaboration],
+S. Chekanov {\it et al.},
 Phys.\ Lett.\  B {\bf 573}, 46 (2003).
@@
 \bibitem{Aktas:2005ty}
-A. Aktas {\it et al.} [H1 Collaboration],
+%A. Aktas {\it et al.} [H1 Collaboration],
+A. Aktas {\it et al.},
 Eur.\ Phys.\ J.\ C {\bf 44}, 1 (2005).
@@
 \bibitem{Chen:2006na} 
-S.~Chen {\it et al.} [CLAS Collaboration],
+%S.~Chen {\it et al.} [CLAS Collaboration],
+S.~Chen {\it et al.},
 Phys.\ Rev.\ Lett.\ {\bf 97}, 072002 (2006).
@@
 \bibitem{Munoz Camacho:2006hx} 
-C. Mu\~noz Camacho {\it et al.} [Jefferson Lab Hall A Collaboration],
+%C. Mu\~noz Camacho {\it et al.} [Jefferson Lab Hall A Collaboration],
+C. Mu\~noz Camacho {\it et al.},
 Phys.\ Rev.\ Lett. {\bf 97}, 262002 (2006).
@@
 \bibitem{Girod:2007aa} 
-F.X. Girod {\it et al.} [CLAS Collaboration],
+%F.X. Girod {\it et al.} [CLAS Collaboration],
+F.X. Girod {\it et al.},
 Phys.\ Rev.\ Lett. {\bf 100}, 162002 (2008).
@@
 \bibitem{Mazouz:2007aa} 
-   M.~Mazouz {\it et al.} [Jefferson Lab Hall A Collaboration],
+%   M.~Mazouz {\it et al.} [Jefferson Lab Hall A Collaboration],
+   M.~Mazouz {\it et al.},
    Phys.\ Rev.\ Lett.\  {\bf 99}, 242501 (2007)
@@
 \bibitem{Gavalian:2009} 
-G. Gavalian {\it et al.} [CLAS Collaboration],
+%G. Gavalian {\it et al.} [CLAS Collaboration],
+G. Gavalian {\it et al.},
 Phys.\ Rev.\ C {\bf 80}, 035206 (2009).
@@
 \bibitem{Seder:2015} 
-E. Seder {\it et al.} [CLAS Collaboration],
+%E. Seder {\it et al.} [CLAS Collaboration],
+E. Seder {\it et al.},
 Phys.\ Rev.\ Lett. {\bf 114}, 032001 (2015).
@@
 \bibitem{Pisano:2015} 
-S.~Pisano {\it et al.} [CLAS Collaboration],
+%S.~Pisano {\it et al.} [CLAS Collaboration],
+S.~Pisano {\it et al.},
 Phys.\ Rev.\ D {\bf 91}, 052014 (2015).
 
-\bibitem{Jo:2015ema} H.~S.~Jo {\it et al.} [CLAS Collaboration],
+\bibitem{Jo:2015ema}
+%H.~S.~Jo {\it et al.} [CLAS Collaboration],
+H.~S.~Jo {\it et al.},
   Phys.\ Rev.\ Lett.\  {\bf 115}, no. 21, 212003 (2015)
@@
 \bibitem{Ellinghaus:2002zw}
-F.~Ellinghaus {\it et al.} [HERMES Collaboration],
+%F.~Ellinghaus {\it et al.} [HERMES Collaboration],
+F.~Ellinghaus {\it et al.},
 AIP Conf.\ Proc.\  {\bf 675}, 303 (2003)
@@
 \bibitem{Mecking:2003zu} 
-   B.~A.~Mecking {\it et al.} [CLAS Collaboration],
+%B.~A.~Mecking {\it et al.} [CLAS Collaboration],
+   B.~A.~Mecking {\it et al.},
    Nucl.\ Instrum.\ Meth.\ A {\bf 503}, 513 (2003).

### 2017-04-20 eg6-letters/coherent/dvcs_he4_prl.tex
implementing adhoc comments, part B

@@
 Figure \ref{fig:diags} illustrates the handbag diagram for coherent DVCS on 
-$^4$He. Similar to the proton case, at large virtual photon's 4-momentum square 
-$Q^2=-(k-k')^{2}$ and small squared momentum transfer $t=(p-p')^{2}$ (in terms 
-of the electron, $k(k')$, and $^4$He, $p(p')$, four-vectors), the DVCS handbag 
+$^4$He, where four-vectors of the electrons, photons, and $^4$He are denoted by
+$k/k^\prime$, $q/q^\prime$, and $p/p^\prime$ respectively. 
+For large virtual photon's 4-momentum squared, $Q^2=-(k-k')^{2}$, and small squared momentum transfer, $t=(p-p')^{2}$, the DVCS handbag 
 diagram can be factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The 
@@
 measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and Xe), 
-but the mixing of the coherent and incoherent processes could affect the
-measurement significantly \cite{Guzey:2003jh}. In this regard, direct detection 
-of the low-energy recoil nucleus is the best way to guarantee that the nucleus 
-remains intact. The CEBAF large acceptance spectrometer in Hall-B at 
-Jefferson Lab has been previously used successfully for DVCS measurements on the nucleon
-\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.
+but contamination from incoherent processes could influence the
+measurement significantly \cite{Guzey:2003jh}.  Accordingly, direct detection 
+of the low-energy recoil nucleus is critical in guaranteeing the nucleus 
+remains intact.
 
-In order to measure DVCS on $^4$He with a fully exclusive final state, we built 
-a specialized radial time projection chamber (RTPC) for the detection and 
-identification of low-energy recoiling light nuclei. The $^4$He nucleus is an 
+The $^4$He nucleus is an 
 ideal experimental target in this regard, as it is light enough to be detected 
@@
 ($\mathcal{H}_{A}$) presented at the end of this letter.
+
+The CEBAF large acceptance spectrometer in Hall-B at 
+Jefferson Lab has been previously used successfully for DVCS measurements on the nucleon
+\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.
+
+In order to measure DVCS on $^4$He with a fully exclusive final state, we built 
+a specialized radial time projection chamber (RTPC) for the detection and 
+identification of low-energy recoiling light nuclei.
 
@@
 In our kinematics, the recoil $^4$He nuclei produced in DVCS have low momentum,
-averaging \~300 MeV/c. CLAS cannot detect such low energy $\alpha$ 
+averaging 300 MeV/c. CLAS cannot detect such low energy $\alpha$ 
 particles, so in order to ensure the exclusivity of the measurement, we built a 
-small and light RTPC to complement CLAS. The RTPC is a $20$ cm long cylinder 
+small and light RTPC to complement CLAS. The RTPC is a $20$-cm-long cylinder 
 with a diameter of $15$ cm, positioned directly around the $^4$He gaseous 
 target. The target is a $25$-cm-long and $6$-mm-diameter Kapton straw with 
-$27~\mu$m thick walls. The RTPC was calibrated specifically for the detection of 
+$27$-$\mu$m-thick walls. The RTPC was calibrated specifically for the detection of 
 $^4$He nuclei by utilizing elastic scattering $e^4$He$\to e^\prime$$^4$He with
@@
 GeV$^{2}/$c$^{2}$. Exclusivity of the coherent DVCS reaction is optimized by 
-applying a set of cuts on the following kinematic variables: the co-planarity 
-angle ($\Delta\phi$), \textit{i.e.}, the angle between the ($\gamma,\gamma^*$) 
-and ($\gamma^*$,$^4$He$'$) planes, the missing energy, the missing mass 
-squared, the missing transverse momentum of the $e'^4$He$'\gamma$ system, the 
-missing mass squared of the $e'^4$He$'$ system, and the angle ($\theta$) 
+applying a set of cuts on the following kinematic variables: the coplanarity 
+angle ($\Delta\phi$) between the ($\gamma,\gamma^*$) 
+and ($\gamma^*$,$^4$He$'$) planes, the missing energy, mass, and transverse
+momentum of the $e'^4$He$'\gamma$ system, the missing mass squared of the $e'^4$He$'$ system, and the angle ($\theta$) 
 between the measured photon and the missing momentum of the $e'^4$He$'$ system.
@@
 \hspace{-0.45cm}
-\includegraphics[width=8.0cm]{figs/Q2_xB_t_Coh.pdf}
+\includegraphics[width=8.5cm]{figs/Q2_xB_t_Coh.pdf}
 \caption{Coherent DVCS event distributions for $Q^{2}$ as a function of 
@@
 and real parts of the $^4$He CFF $\mathcal{H}_{A}$ and depend on the GPD $H_A$.  
-The explicit expression of the kinematic factors $\alpha_i$ are written in
+Explicit expressions of the purely kinematic factors $\alpha_i$ are written in
 Ref.~\cite{Belitsky:2008bz} and are functions of Fourier harmonics in the 
@@
 
-In this work, the azimuthal dependence of the BSA, $A_{LU}$, has been studied 
-for a wide range of kinematics. We identified two main backgrounds to our 
+In this work, the azimuthal dependence of the beam-spin asymmetry has been studied 
+for a wide range of kinematics ($Q^2$ between 1 and 2.2 GeV$^2$/c$^2$, $x_B$ between 0.1 and 0.3, and $-t$ between 0.07 and 0.16 GeV$^2$/c$^2$). We identified two main backgrounds to our 
 measurement, accidental coincidences and exclusive coherent $\pi^0$ production.  
@@
 contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
-large binning size (5.1\%). However, added quadratically, the total systematic 
-uncertainty is about 10\%, which is significantly smaller than statistical 
-uncertainties in all kinematical bins.
+large binning size (5.1\%), where the values are relative and for $A_{LU}$ at $\phi=90^\circ$.
+However, added quadratically, the total systematic uncertainty is about 10\%,
+which is significantly smaller than statistical  uncertainties in all kinematical bins.
 
@@
 Department of Energy, Office of Science, Office of Nuclear Physics, under 
-contract DE-AC02-06CH11357.
+contracts DE-AC02-06CH11357 and DE-AC05-06OR23177.
 

### 2017-04-20 eg6-letters/coherent/dvcs_he4_prl.tex
eg6-letters/coherent:  implementing adhoc comments, Part C.  Remainder is restructure of experimental setup (paragraphs starting at lines 82 and 112) and multi-gamma explanation (line 137)

@@
 of coherent scattering is suppressed due to the nuclear form factor, and 
-second, the recoil nucleus ($A^\prime$) must be detected to ensure coherence.  
+second, the intact recoil nucleus ($A^\prime$) must be detected to ensure coherence.  
 Figure \ref{fig:diags} illustrates the handbag diagram for coherent DVCS on 
@@
 
-The $^4$He nucleus is an 
-ideal experimental target in this regard, as it is light enough to be detected 
-in such a setting, while it is subject to significant nuclear effects 
+The $^4$He nucleus is an ideal experimental target for DVCS on nuclei, as it is light enough to be detected in such a setting, while it is subject to significant nuclear effects 
 \cite{JSeely} and has rather high density. A helium target leads to another 
@@
 
-The CEBAF large acceptance spectrometer in Hall-B at 
-Jefferson Lab has been previously used successfully for DVCS measurements on the nucleon
-\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.
-
-In order to measure DVCS on $^4$He with a fully exclusive final state, we built 
-a specialized radial time projection chamber (RTPC) for the detection and 
-identification of low-energy recoiling light nuclei.
-
-%experimental setup
-
+The CEBAF large acceptance spectrometer in Hall-B at Jefferson Lab has been
+previously used successfully for DVCS measurements on the nucleon
+\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.  In order
+to extend its capabilities to nuclear DVCS with a fully exclusive final state,
+we built a specialized radial time projection chamber (RTPC) for the detection
+and identification of low-energy recoiling light nuclei. 
 The experiment E08-024 took place in Hall-B at Jefferson Lab in 2009 using the 
@@
 the square of the BH and DVCS amplitudes and their interference term, depend on the
-azimuthal angle
-$\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes, as
-shown for the nucleon in Ref.~\cite{Belitsky:2001ns} and for the spin-zero targets
+azimuthal angle $\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes,
+as shown for the nucleon in Ref.~\cite{Belitsky:2001ns} and for the spin-zero targets
 in Refs.~\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the BSA 
@@
 in these factors, it is possible to unequivocally extract both imaginary and real 
-parts of $\mathcal{H}_{A}$ from the BSA.
+parts of $\mathcal{H}_{A}$ by fitting the $A_{LU}(\phi)$ distrubution.
 
 In this work, the azimuthal dependence of the beam-spin asymmetry has been studied 
-for a wide range of kinematics ($Q^2$ between 1 and 2.2 GeV$^2$/c$^2$, $x_B$ between 0.1 and 0.3, and $-t$ between 0.07 and 0.16 GeV$^2$/c$^2$). We identified two main backgrounds to our 
-measurement, accidental coincidences and exclusive coherent $\pi^0$ production.  
-The accidentals have particles originating from different events, and we 
-estimated their contribution to be 4.1\% of our sample. We evaluated this 
+for a wide range of kinematics ($Q^2$ between 1 and 2.2 GeV$^2$/c$^2$, $x_B$ between
+0.1 and 0.3, and $-t$ between 0.07 and 0.16 GeV$^2$/c$^2$). We identified two main
+backgrounds to our measurement, accidental coincidences and exclusive coherent
+$\pi^0$ production.  The accidentals have particles originating from different events,
+and we estimated their contribution to be 4.1\% of our sample. We evaluated this 
 contribution by selecting events passing all our cuts but with an electron and 
@@
 experiment. We used this generator together with a GEANT3 simulation of our 
-detector to estimate the ratio between the number of $\pi^0$ events where the 
-two photons are detected and those that are misidentified as DVCS events. This 
+detector to estimate the ratio of the number of $\pi^0$ events where the 
+two photons are detected to those that are misidentified as DVCS events. This 
 ratio is then multiplied by the measured yield of exclusive $\pi^0$ events to 
 correct the DVCS data.  Depending on the kinematics, we found contaminations of 
-2 to 4\%. The study of systematic uncertainties showed that the main 
-contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
-large binning size (5.1\%), where the values are relative and for $A_{LU}$ at $\phi=90^\circ$.
-However, added quadratically, the total systematic uncertainty is about 10\%,
-which is significantly smaller than statistical  uncertainties in all kinematical bins.
+2 to 4\%.  Studies of systematic uncertainties showed that the main 
+contributions come from the choice of DVCS exclusivity cuts (8\%) and the 
+large binning size (5.1\%), where the values are relative and quoted for $A_{LU}$
+at $\phi=90^\circ$.  Added quadratically, the total systematic uncertainty
+is about 10\% at $90^\circ$ (or 0.03, absolute), which is significantly smaller
+than the statistical uncertainties in all kinematical bins.
 

### 2017-04-21 eg6-letters/coherent/dvcs_he4_prl.tex
Corrections to the PRL coherent

@@
 \affiliation{\JLAB}
+\author {M.~Guidal} 
+\affiliation{\ORSAY}
 \author{D.~Jenkins}
@@
 $^4$He, where four-vectors of the electrons, photons, and $^4$He are denoted by
-$k/k^\prime$, $q/q^\prime$, and $p/p^\prime$ respectively. 
-For large virtual photon's 4-momentum squared, $Q^2=-(k-k')^{2}$, and small squared momentum transfer, $t=(p-p')^{2}$, the DVCS handbag 
+$k/k^\prime$, $q/q^\prime$, and $p/p^\prime$ respectively. For large virtual photon's 
+4-momentum squared, $Q^2=-(k-k')^{2}$, and small squared momentum transfer, $t=(p-p')^{2}$, the DVCS handbag 
 diagram can be factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The 
@@
 
-The $^4$He nucleus is an ideal experimental target for DVCS on nuclei, as it is light enough to be detected in such a setting, while it is subject to significant nuclear effects 
-\cite{JSeely} and has rather high density. A helium target leads to another 
+The $^4$He nucleus is an ideal experimental target for DVCS on nuclei, as it 
+is light enough to be detected in such a setting, while it is subject to 
+significant nuclear effects~\cite{JSeely} and has a spin-0. A helium target leads to another 
 important advantage, as the number of GPDs defined for a hadron depends on its 
@@
 even though the DVCS reaction has only one real photon in the final state, 
-events with more than one good photon are not discarded at this stage. This is 
-motivated by the fact that, while soft photons are likely to be produced in 
-random coincidence, they cannot be mistaken for the large energy DVCS photons 
-($>2$ GeV). The most energetic photon is always considered as the DVCS photon 
-candidate.
+events with more than one good photon are not discarded at this stage. Indeed,
+soft photons are produced at very high rates by the electron beam and create 
+numerous accidental coincidences. These do not affect directly our mesurement, 
+where only the most energetic photon is considered as DVCS photon candidate.
+This prescription however slightly increases the corrections associated with
+the $\pi^0$ and the accidental backgrounds discussed below.
 
@@
 different kinematics than our data but still provide some guidance. The 
-experimental results appear to have a larger asymmetries than the calculations
-in the $x_B = 0.307$ bin. The difference may arise from the theoretical 
-uncertainty in the determination of the crossing point between the 
-antishadowing region, where the parton nuclear distribution is larger than the 
-nucleon one, and the EMC effect region, where the nuclear effect reverses its 
-sign.
+experimental results appear to have a larger asymmetries than the calculations. 
+The difference may arise from the theoretical uncertainty in the determination 
+of the crossing point where the parton nuclear distribution becomes larger than the 
+nucleon one, and reverses the sign of the nuclear effect.
 

### 2017-04-28 eg6-letters/NIM/EG6_RTPC_NIM.tex

@@
       is surrounded by a 4~$\mu$m thick window made of aluminized Mylar, which 
-      serves as the cathode. {\bf \color{red} What Voltage ?}
+      serves as the cathode and is set at 4260~V.
    \item The drift region is filled with the same Ne-DME gas mixture and extends 
       from the cathode to the first Gas Electron Multiplier(GEM), 60 mm away 
-      from the beam axis. The electric field in this region is around 500~V/cm 
-      {\bf \color{red} Give exact value.} and perpendicular to the beam.
+      from the beam axis. The electric field in this region is about 550~V/cm 
+      and perpendicular to the beam.
    \item The electron amplification system is composed of three GEMs located at 
       radii of 60, 63 and 66 mm. In this configuration, the first GEM layer 
-      represents the anode. {\bf \color{red} What bias voltage ?}
+      serves as the anode and each subsequent GEM is set at a lower voltage to
+      obtain a strong ($\sim$1600 V/cm) electric field between the GEM foils. A 
+      275~V bias is applied to each GEM for amplification.
    \item The readout board has an internal radius of 69~mm and collects charge

### 2017-04-28 for_eg6_group/t_tprime_April_2017/Incoh.tex

--- 2017-03-23 for_eg6_group/incoh_t_EG6_E1DVCS1_2/Incoh.tex
@@
 
-\section{$t'$ correction}
+\section{$t'$ corrections}
 One can see from the free proton DVCS sample, figure \ref{fig:tprime_e1dvcs2}, 
@@
 uncertainties. Figure \ref{fig:corrections_tprime_e1dvcs2} presents the 
-distributions of $t-t'$ as a function of $t'$ for the free proton DVCS sample 
-from E1-DVCS2 data before and after correcting $t'$. In figure 
-\ref{fig:after_tprime_e1dvcs2}, the distributions of figure 
-\ref{fig:tprime_e1dvcs2} are shown after the $t'$ corrections.
+correlation between $t$ and $t'$ with proposed correcting functions.
 
@@
 \centering
-\includegraphics[height=10.0cm]{fig/before_corrections_tprimet_t_InCoh.pdf}
-\includegraphics[height=10.0cm]{fig/after_corrections_tprimet_t_InCoh.pdf}
-\caption{On top: $t-t'$ as a function of $t'$ for the E1-DVCS2 free proton DVCS 
-sample BEFORE correcting $t'$. The red line is the extracted correction for 
-$t'$. On bottom: $t-t'$ as a function of $t'$ after correcting $t'$.}
+\includegraphics[height=7.0cm]{fig/h_tprimet_t_InCoh_1.pdf}
+\includegraphics[height=7.0cm]{fig/h_tprimet_t_InCoh_2.pdf}
+\includegraphics[height=7.0cm]{fig/h_tprimet_t_InCoh_3.pdf}
+\caption{On top and middle: $t-t'$ as a function of $t'$ for the E1-DVCS2 free 
+proton DVCS sample BEFORE correcting $t'$. On bottom: $t$ versus $t'$.  The red 
+lines are proposed correction functions for $t'$.}
 \label{fig:corrections_tprime_e1dvcs2}
@@
 
-\begin{figure}[h!]
-\centering
-\includegraphics[height=19.0cm]{fig/after_corrections_E1-dvcs2-t_tprime_Incoh.pdf}
-\caption{The E1-DVCS2 free proton DVCS sample AFTER correcting $t'$. See the 
-caption of figure \ref{fig:tprime_eg6} for plots description.}
-\label{fig:after_tprime_e1dvcs2}
-\end{figure}
+%\begin{figure}[h!]
+%\centering
+%\includegraphics[height=19.0cm]{fig/after_corrections_E1-dvcs2-t_tprime_Incoh.pdf}
+%\caption{The E1-DVCS2 free proton DVCS sample AFTER correcting $t'$. See the 
+%caption of figure \ref{fig:tprime_eg6} for plots description.}
+%\label{fig:after_tprime_e1dvcs2}
+%\end{figure}
 
@@
 Here we apply the $t'$ corrections that were extracted from the free proton 
-asymmetries  to the EG6 incoherent DVCS channel. Then, the asymmetries using 
-$t$ are compared to the ones reconstructed using the corrected $t'$. The 
-results are presented in figures \ref{fig:alu} and \ref{fig:alu90}.
+asymmetries to EG6 incoherent DVCS channel. Then, the asymmetries using $t$ are 
+compared to the ones reconstructed using the corrected $t'$. The results are 
+presented in figures \ref{fig:alu} and \ref{fig:alu90}.
+
+Note: In black are the bins in $t$, in Red, blue and brown are the bins in $t'$ 
+using the corrections presented in figure \ref{fig:corrections_tprime_e1dvcs2}, 
+respectively.
 
@@
    \centering
-\includegraphics[width=15cm]{fig/ALU_phi_p_Q2.pdf}
-\includegraphics[width=15cm]{fig/ALU_phi_p_x.pdf}
-\includegraphics[width=15cm]{fig/ALU_phi_p_t.pdf}
+\includegraphics[width=18cm]{fig/t_tprime_ALU_phi_p_Q2.pdf}
+\includegraphics[width=18cm]{fig/t_tprime_ALU_phi_p_x.pdf}
+\includegraphics[width=18cm]{fig/t_tprime_ALU_phi_p_t.pdf}
 \caption{The EG6 incoherent $A_{LU}$ as a function of $\phi$. Results are 
@@
    panel), and $t$ bins (bottom panel) using $t$ in black points and using the 
-corrected $t'$ in red points.  The red curves are the results of our fits with 
-the form $\frac{\alpha sin(\phi)}{1+ \beta cos(\phi)}$.}
+   corrected $t'$ in red points.  The red curves are the results of our fits 
+   with the form $\frac{\alpha sin(\phi)}{1+ \beta cos(\phi)}$.}
 \label{fig:alu}
@@
    \centering
-\includegraphics[width=12cm]{fig/ALU_90_p_vs_Q2_shortscenrario.pdf}
-\includegraphics[width=12cm]{fig/ALU_90_p_vs_x_shortscenrario.pdf}
-\includegraphics[width=12cm]{fig/ALU_90_p_vs_t_shortscenrario.pdf}
+\includegraphics[width=9cm]{fig/t_tprime_ALU_90_p_vs_Q2_shortscenrario.pdf}
+\includegraphics[width=9cm]{fig/t_tprime_ALU_90_p_vs_x_shortscenrario.pdf}
+\includegraphics[width=9cm]{fig/t_tprime_ALU_90_p_vs_t_shortscenrario.pdf}
 \caption{The EG6 incoherent $Q^{2}$ (left), $x_{B}$ (middle), and 
@@
 
-\section{Conclusions}
-We improved the EG6 incoherent DVCS channel via the $t'$ that is calculated 
-using the virtual and the final state real photons with corrections based on 
-similar analysis on the free proton DVCS sample using the same setup of CLAS 
-detector. The $Q^{2}$ and $x_B$ dependences of the asymmetries have shown 
-slight changes using $t'$ rather than $t$, while the effect is bigger on the 
-t-dependence, with overall changes are compatible with the statistical error 
-bars.  Based on the free proton DVCS data, no induced systematic uncertainties 
-are observed on the $Q^{2}$ and $x_B$, while some appear on $t$, which will be 
-added to the EG6 incoherent asymmetries.
+%\section{Conclusions}
+%We improved the EG6 incoherent DVCS channel via the $t'$ that is calculated 
+%using the virtual and the final state real photons with corrections based on 
+%similar analysis on the free proton DVCS sample using the same setup of CLAS 
+%detector. The $Q^{2}$ and $x_B$ dependences of the asymmetries have shown 
+%slight changes using $t'$ rather than $t$, while the effect is bigger on the 
+%t-dependence, with overall changes are compatible with the statistical error 
+%bars.  Based on the free proton DVCS data, no induced systematic uncertainties 
+%are observed on the $Q^{2}$ and $x_B$, while some appear on $t$, which will be 
+%added to the EG6 incoherent asymmetries.
 

### 2017-05-01 eg6-letters/NIM/EG6_RTPC_NIM.tex
update the nim paper with the proper dedx vs p/q distributions

@@
 setup was used during a three months experimental run
-in 2009 with a longitudinally polarized electron beam of 6.064 GeV incident 
-on a gaseous $^{4}$He target.
+in 2009 with a longitudinally polarized electron beam of {\color{blue} 130 nA 
+and energy of 6.064 GeV} incident on a gaseous $^{4}$He target.
 {\bf \color{red} Add beam current or luminosity.}
 
-In this paper we report the design, calibration, and performance of the radial TPC,
-organized as follows. Section \ref{sec_design} details the physics considerations for our RTPC's
-design and internal structure. Section \ref{sec_readout} describes the properties
-of the read-out system. Calibration strategies are discussed in section \ref{sec_calib}.
-Finally, the performance of the RTPC is described in section \ref{sec_perf}.
+In this paper we report the design, calibration, and performance of the radial 
+TPC, organized as follows. Section \ref{sec_design} details the physics 
+considerations for our RTPC's design and internal structure. Section 
+\ref{sec_readout} describes the properties of the read-out system. Calibration 
+strategies are discussed in section \ref{sec_calib}. Finally, the performance 
+of the RTPC is described in section \ref{sec_perf}.
 
@@
 allowing a curved amplification surface. Also, GEMs are known to rarely create 
-sparks{\bf \color{red} Need reference.}, which is important when trying to 
-detect highly ionizing slow nuclei that deposit large amount of energy. The 
-GEMs for this RTPC are made from a Kapton insulator layer 
-{\bf \color{red} Thickness?} sandwiched between two 5 $\mu$m copper
-layers. The mesh of each GEM layer is chemically etched with 50$\mu$m diameter
-holes with double-conical shapes as illustrated in figure~\ref{fig:GEMs}. A
-potential difference of 400 V {\bf \color{red} To be checked and set as above.} 
-is applied between the two copper layers of the
-GEM, creating a very strong electric field in each hole leading to high ionization 
-and therefore amplification of the incoming electrons. A 
-potential of 150 V {\bf \color{red} To be checked.} 
-is set between the GEMs to push the electrons toward the next GEM and eventually 
-the readout pads. The gain of each GEM layer is of order 100, making a total gain 
-of about $10^{6}$. {\bf \color{red} We should quote a realistic overall gain or nothing.}\\
+sparks{\color{blue} \cite{GEM_ref}}, which is important when trying to detect 
+highly ionizing slow nuclei that deposit large amount of energy. The GEMs for 
+this RTPC are made from a Kapton insulator layer, {\color{blue}50~$\mu$m 
+thick}, sandwiched between two 5~$\mu$m copper layers. The mesh of each GEM 
+layer is chemically etched with 50~$\mu$m diameter holes with double-conical 
+shapes as illustrated in figure~\ref{fig:GEMs}. A potential difference of 400 V 
+{\bf \color{red} To be checked and set as above.} is applied between the two 
+copper layers of the GEM, creating a very strong electric field in each hole 
+leading to high ionization and therefore amplification of the incoming 
+electrons. A potential of 150 V {\bf \color{red} To be checked.} is set between 
+the GEMs to push the electrons toward the next GEM and eventually the readout 
+pads. The gain of each GEM layer is of order 100, making a total gain of about 
+$10^{6}$.  {\bf \color{red} We should quote a realistic overall gain or 
+nothing.}\\
 
@@
 \begin{figure}[tb]
-   \includegraphics[scale=0.26]{fig/dedx_p_exp_1st.png}
-   \caption{$\small{\frac{dE}{dX}}$ vs. $p$ distribution for the left half of the 
-      RTPC (left) and for the right half (right). Here, $\small{\frac{dE}{dX}}$ 
-   is calculated using the gains of the first method.  The lines are 
-theoretical expectations from Bethe-Bloch formula for $^4$He, $^3$He, $^3$H and 
-$^2$H (d).{\bf \color{red} Mohammad: Did you multiply p/c by 2 in the figure? If no 
-change the caption, if yes check remove the single charge nuclei from the figure 
-because there is a consistency issue.}}
+   \centering
+   \includegraphics[scale=0.45]{fig/f_dedx_p_exp_1st.pdf}
+   \caption{$\small{\frac{dE}{dX}}$ vs. $p/q$ distribution for the left half of 
+      the RTPC (left) and for the right half (right). Here, 
+      $\small{\frac{dE}{dX}}$ is calculated using the gains of the first 
+      method.  The lines are theoretical expectations from Bethe-Bloch formula 
+   for $^4$He, $^3$He, $^3$H and $^2$H (d).}
 \label{fig:dedx_p_exp_1st}
@@
 \begin{figure}[tb]
+   \centering
 \includegraphics[scale=0.350]{fig/EVENT_adc_tdc.png}
@@
 \centering
-\includegraphics[scale=0.26]{fig/dedx_p_exp_2nd.png}
-\caption{$\small{\frac{dE}{dX}}$ vs. $p$ distribution for the left half of the 
-   RTPC (left) and for the right half (right). Here, $\small{\frac{dE}{dX}}$ is 
-   calculated using the gains of the second method.  The lines are theoretical 
-   expectations from Bethe-Bloch formula for $^4$He, $^3$He, $^3$H and $^2$H 
-(d).{\bf \color{red} Mohammad: Did you multiply p/c by 2 in the figure? If no 
-change the caption, if yes check remove the single charge nuclei from the figure 
-because there is a consistency issue.}}
+\includegraphics[scale=0.45]{fig/f_dedx_p_exp_2nd.pdf}
+\caption{$\small{\frac{dE}{dX}}$ vs. $p/q$ distribution for the left half of 
+   the RTPC (left) and for the right half (right). Here, 
+   $\small{\frac{dE}{dX}}$ is calculated using the gains of the second method.  
+   The lines are theoretical expectations from Bethe-Bloch formula for $^4$He, 
+$^3$He, $^3$H and $^2$H (d).}
 \label{fig:dedx_p_exp_2nd}
@@
 
+\bibitem{GEM_ref}
+   J. Beringer et al. (Particle Data Group), Particle detectors at 
+   accelerators, Phys. Rev. D 86, 010001, pages: 339-368, 2012.
+
 \bibitem{gem_sauli}

### 2017-05-02 eg6-letters/NIM/EG6_RTPC_NIM.tex
Addition of the paragraph about drift gas and mechanical structure. Plus several minor fixes.

@@
 setup was used during a three months experimental run
-in 2009 with a longitudinally polarized electron beam of {\color{blue} 130 nA 
-and energy of 6.064 GeV} incident on a gaseous $^{4}$He target.
-{\bf \color{red} Add beam current or luminosity.}
+in 2009 with a longitudinally polarized electron beam of 130 nA 
+and energy of 6.064 GeV incident on a gaseous $^{4}$He target.
+{\bf \color{red} Add luminosity.}
 
 In this paper we report the design, calibration, and performance of the radial 
-TPC, organized as follows. Section \ref{sec_design} details the physics 
-considerations for our RTPC's design and internal structure. Section 
-\ref{sec_readout} describes the properties of the read-out system. Calibration 
-strategies are discussed in section \ref{sec_calib}. Finally, the performance 
-of the RTPC is described in section \ref{sec_perf}.
+TPC, organized as follows. In section \ref{sec_design}, we detail the design 
+and internal structure of the detector. Section \ref{sec_readout} is focused 
+on the properties of the read-out system. Calibration 
+strategies are discussed in section \ref{sec_calib}. Finally, the performances
+of the RTPC are described in section \ref{sec_perf}.
 
@@
    \item The second gap region extends between 20~mm and 30~mm and is filled with a 
-      gas mixture of 80$\%$ Neon and 20$\%$ Dimethyl Ether (DME). This region 
+      gas mixture of 80$\%$ neon and 20$\%$ dimethyl ether (DME). This region 
       is surrounded by a 4~$\mu$m thick window made of aluminized Mylar, which 
@@
 layer is chemically etched with 50~$\mu$m diameter holes with double-conical 
-shapes as illustrated in figure~\ref{fig:GEMs}. A potential difference of 400 V 
-{\bf \color{red} To be checked and set as above.} is applied between the two 
+shapes as illustrated in figure~\ref{fig:GEMs}. A potential difference of 275 V 
+is applied between the two 
 copper layers of the GEM, creating a very strong electric field in each hole 
 leading to high ionization and therefore amplification of the incoming 
-electrons. A potential of 150 V {\bf \color{red} To be checked.} is set between 
+electrons. A high potential of about 1600 V/cm is set between 
 the GEMs to push the electrons toward the next GEM and eventually the readout 
-pads. The gain of each GEM layer is of order 100, making a total gain of about 
-$10^{6}$.  {\bf \color{red} We should quote a realistic overall gain or 
-nothing.}\\
+pads. \\
 
-{\bf \color{red} To be added:
+The drift gas used in the experiment is a 80-20\% neon-DME mixtur, this choice 
+has been made in order to balance the good drift properties with a reasonnable
+Lorentz angle. Calculations using the MAGBOLTZ program~\cite{MAGBOLTZ} 
+showed that with the perpendicular 5~T field, we would have a Lorentz angle of 
+about {\bf \color{red} (To be added) } with this mixture. As can be seen, the
+Lorentz angle is already significant, a larger angle would increase significantly
+the length of the drift paths as the electron would spiral around the beam line.
+{\bf \color{red} (To be continued commenting on higher/lower proportion of gas 
+and other gas) }
 
-Discuss the choice of drift gas
-
-Discuss the self supporting mechanic of the GEMs.}
+One of the important problematic to develop the radial TPC was to obtain a 
+good support structure of the GEM foils, allowing an easy installation of the 
+GEM in good conditions and with high precision. At the same time, we wanted to 
+keep the material budget small in the forward region where we detect other 
+particles in subsequent detectors. We successfuly realized these prerequisites 
+by using fiber glass rings glued to each ends of the GEM foils to form self 
+supporting cylinders that could be installed independently in the RTPC after 
+all gluing and soldering operations.  Because the rigidity of the high 
+rigidity of the GEM foil, the strcture was selfsupporting and only the 
+backward part of the cylinder was fixed to the main mechanical structure. This 
+design only left a light fiberglass ring in the forward region, reducing to a 
+minimum secondary interactions.
 
@@
 pads, but cylindrical symmetry insures they always travel the same 
-distance. By identifying the maximum TDC measured, we can infer the drift 
+distance. By identifying the maximum time T measured, we can infer the drift 
 speed of the electrons in the RTPC.\\
@@
 \includegraphics[scale=0.26]{fig/Drift_run_number_1.png}
-\caption{$TDC_{Nbmax/2}$ versus the experimental run numbers (time).  } 
+\caption{$T_{Nbmax/2}$ versus the experimental run numbers (time).  } 
 \label{fig:Drift_run_number_1}
@@
 \includegraphics[scale=0.37]{fig/FitResult_p2_10.png}
-\caption{$\Delta \phi$ versus TDC distribution in the second pass for tracks
+\caption{$\Delta \phi$ versus T distribution in the second pass for tracks
 near 35 mm longitudinal position along the RTPC. The black line represents 
@@
 \includegraphics[scale=0.350]{fig/EVENT_adc_tdc.png}
-\caption{Simulated (upper) and experimental (lower) ADCs and TDCs distributions 
+\caption{Simulated (upper) and experimental (lower) ADC and T distributions 
 of a track. The colors indicate the pads, same color in top and bottom indicate 
@@
 \caption{The ADC vs.
-TDC spectrum for an example noisy channel before (top) and after (bottom) noise rejection algorithms.
+T spectrum for an example noisy channel before (top) and after (bottom) noise rejection algorithms.
 Only hits associated with tracks are included, and the selection of events and tracks is the same in both plots.}

### 2017-05-03 eg6-letters/coherent/dvcs_he4_prl.tex
dvcs_he4_prl.tex:  add mohammad thesis

@@
 the RTPC using time, track quality, and energy-loss cuts for tracks in the 
-fiducial region. In addition, we apply a vertex-matching cut to ensure that the 
+fiducial region \cite{Hattawy:thesis}. In addition, we apply a vertex-matching cut to ensure that the 
 electron and helium nucleus originate from a common reaction vertex in the target cell. The photons are 
@@
 between the measured photon and the missing momentum of the $e'^4$He$'$ system.  
-
-The experimental data for the most relevant observables and applied
-cuts is shown in Fig.~\ref{fig:kin-cuts}.
+The experimental data for the most relevant exclusivity observables and applied
+cuts is shown in Fig.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for additional details).
 %The most relevant of these cuts are presented in Fig.~\ref{fig:kin-cuts}, which 
@@
 reject events where a $\pi^0$ is identified by invariant mass reconstruction of 
-two photons. About 3200 events pass these requirements. Their kinematic 
+two photons. About 3200 events pass these requirements, and their kinematic 
 distributions are shown in Fig.~\ref{fig:kin-coverage}.
@@
 \caption{Four of the six coherent DVCS exclusivity cuts. The black 
-distributions represent the coherent DVCS events candidates. The shaded 
-distributions represent the events which passed all the exclusivity cuts except 
-the quantity plotted. The vertical red lines represent the applied exclusivity 
-cuts. The distributions from left to right and from top to bottom are: $\Delta 
+distributions represent the initial candidate events, while the shaded 
+distributions represent those which which passed all the exclusivity cuts except 
+the quantity plotted. The vertical red lines represent the applied cuts.
+The distributions from left to right and from top to bottom are: $\Delta 
 \phi$, missing energy, missing mass squared and the cone angle ($\theta$) 
@@
 
+\bibitem{Hattawy:thesis}
+M.~Hattawy, Ph.D. thesis, Universit{\'e} Paris Sud - Paris XI, France 
+[Institution Report No. 2015PA112161].
+
 \bibitem{Belitsky:2001ns}

### 2017-05-08 eg6-letters/NIM/EG6_RTPC_NIM.tex
update the nim paper

--- 2017-05-01 eg6-letters/NIM/EG6_RTPC_NIM.tex
@@
 that can lead to cutting out hits. After setting the simulation properly, we 
-compared simulation to experiment on an event by event basis as in 
+compared simulation to experiment on an event by event basis as shown in 
 figure~\ref{fig:EVENT_adc_tdc}. In this step, the gain for each pad is defined 
 as the ratio of the measured ADCs to the simulated deposited energy.  
-Then, the ADC value of each pad is compared to 
-the ADCs of the other pads inside each track.
+{\color{blue} Then, the gain of each readout pad is corrected by a factor, that 
+is defined as the ratio of the ADC value of each pad to the ADCs of the other 
+pads inside each track to make sure that the recorded ADCs by a given pad are 
+similar to the recorded ADCs recorded by other pads in the same track.}
+
 {\bf \color{red} Mohammad: Detail are missing here.}

### 2017-05-09 eg6-letters/coherent/dvcs_he4_prl.tex
Implement comments from BR and VB

@@
 \begin{abstract}
-We report the first fully exclusive measurement of coherent deeply virtual 
+We report the first exclusive measurement of coherent deeply virtual 
 Compton scattering off a nucleus for $A>1$. The experiment used the 6 GeV 
-electron beam from the CEBAF accelerator at Jefferson Lab incident on a $^4$He gas 
-target in the center of the CEBAF large acceptance spectrometer (CLAS). A new radial 
+electron beam from the CEBAF accelerator at Jefferson Lab incident on a 
+$^4$He gas target in the center of the CEBAF large acceptance spectrometer 
+(CLAS). A specially designed radial 
 time projection chamber (RTPC) was used to detect the recoiling $^4$He
@@
 domain. Since $^4$He is a spin-zero target, we were able to extract, in a 
-completely model-independent way, the real and imaginary parts of the $^4$He 
+model-independent way, the real and imaginary parts of the $^4$He 
 Compton form factors, $\cal H_A$, which are functions of the generalized parton 
@@
 sensitive to GPDs, the measurement of DVCS is considered the cleanest probe and 
-has been the focus of worldwide efforts 
+has been the focus of efforts at Jefferson Lab, HERA, and CERN
 \cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
-Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
-involving several accelerator facilities such as Jefferson Lab, HERA, and CERN.  
+Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.  
 The vast majority of these measurements focused on the study of proton 
-structure and allowed for an extraction of the three-dimensional picture of the 
-nucleon (for details on the formalism, see 
+structure and allowed for an extraction of the three-dimensional image of the 
+proton (for details on the formalism, see 
 \cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
-This framework is also applicable to nuclei, giving access to completely new 
+This framework is also applicable to nuclei, giving access to novel 
 information about nuclear structure in terms of quarks and 
@@
 \includegraphics[width=6.5cm]{figs/DVCS_diagram.pdf}
-\caption{Representation of the leading order handbag diagram of the DVCS 
+\caption{Representation of the leading-order handbag diagram of the DVCS 
 process off $^4$He.}
@@
 second, the intact recoil nucleus ($A^\prime$) must be detected to ensure coherence.  
-Figure \ref{fig:diags} illustrates the handbag diagram for coherent DVCS on 
+Fig.~\ref{fig:diags} illustrates the handbag diagram for coherent DVCS on 
 $^4$He, where four-vectors of the electrons, photons, and $^4$He are denoted by
@@
 
-The CEBAF large acceptance spectrometer in Hall-B at Jefferson Lab has been
+The CEBAF large acceptance spectrometer (CLAS) in Hall-B at Jefferson Lab has been
 previously used successfully for DVCS measurements on the nucleon
@@
 using a 6 atm gaseous $^4$He target placed 64 cm upstream of the nominal center 
-of CLAS. For DVCS experiments, the CLAS baseline design \cite{Mecking:2003zu} 
+of CLAS. For DVCS experiments, the CLAS 
+baseline design~\cite{Mecking:2003zu} 
 is supplemented with an inner calorimeter (IC) and a solenoid magnet. The IC 
 extends the photon detection acceptance of CLAS to polar angles as low as 
-4$^{\circ}$. The low-energy M\o{}ller electrons produced in the target form a 
-very high rate background that is suppressed by a 5-Tesla solenoid magnet 
-placed around the target.
+4$^{\circ}$. The 5 T solenoid magnet has two functions; it provides the magnetic 
+field for the momentum analysis in the RTPC, and at the same time acts as 
+the guiding field for the low-energy M\o{}ller electrons, that are absorbed in a  
+heavy shield placed around the beam line.
 
 In our kinematics, the recoil $^4$He nuclei produced in DVCS have low momentum,
-averaging 300 MeV/c. CLAS cannot detect such low energy $\alpha$ 
+averaging 300 MeV/c. CLAS cannot detect such low-energy $\alpha$ 
 particles, so in order to ensure the exclusivity of the measurement, we built a 
@@
 with a diameter of $15$ cm, positioned directly around the $^4$He gaseous 
-target. The target is a $25$-cm-long and $6$-mm-diameter Kapton straw with 
+target. The target is a $25$-cm-long and $6$-mm-diameter Kapton tube with 
 $27$-$\mu$m-thick walls. The RTPC was calibrated specifically for the detection of 
@@
 are identified using their measured momentum, time, and energy obtained from 
-the CLAS drift chambers, Cerenkov counters, scintillator counters, 
+the CLAS drift chambers, \^{C}erenkov counters, scintillator counters, 
 and electromagnetic calorimeters. The recoiling $^4$He nuclei are identified in 
 the RTPC using time, track quality, and energy-loss cuts for tracks in the 
-fiducial region \cite{Hattawy:thesis}. In addition, we apply a vertex-matching cut to ensure that the 
-electron and helium nucleus originate from a common reaction vertex in the target cell. The photons are 
+fiducial region \cite{Hattawy:thesis}. In addition, we apply a vertex-matching 
+cut to ensure that the 
+electron and helium nucleus originate from a common reaction vertex in the 
+target cell. The photons are 
 detected in either the IC or the CLAS electromagnetic calorimeter. Note that 
 even though the DVCS reaction has only one real photon in the final state, 
-events with more than one good photon are not discarded at this stage. Indeed,
-soft photons are produced at very high rates by the electron beam and create 
-numerous accidental coincidences. These do not affect directly our mesurement, 
-where only the most energetic photon is considered as DVCS photon candidate.
+events with more than one good photon are not discarded at this stage. These
+are caused by accidental coincidences of soft photons that do not affect 
+directly our measurement. We consider only the most energetic photon of an 
+event as a DVCS photon candidate.
 This prescription however slightly increases the corrections associated with
@@
 applying a set of cuts on the following kinematic variables: the coplanarity 
-angle ($\Delta\phi$) between the ($\gamma,\gamma^*$) 
+angle $\Delta\phi$ between the ($\gamma,\gamma^*$) 
 and ($\gamma^*$,$^4$He$'$) planes, the missing energy, mass, and transverse
-momentum of the $e'^4$He$'\gamma$ system, the missing mass squared of the $e'^4$He$'$ system, and the angle ($\theta$) 
+momentum of the $e'^4$He$'\gamma$ system, the missing mass squared of 
+the $e'^4$He$'$ system, and the angle $\theta$
 between the measured photon and the missing momentum of the $e'^4$He$'$ system.  
 The experimental data for the most relevant exclusivity observables and applied
-cuts is shown in Fig.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for additional details).
+cuts are shown in Fig.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for additional details).
 %The most relevant of these cuts are presented in Fig.~\ref{fig:kin-cuts}, which 
@@
 the quantity plotted. The vertical red lines represent the applied cuts.
-The distributions from left to right and from top to bottom are: $\Delta 
-\phi$, missing energy, missing mass squared and the cone angle ($\theta$) 
-between the measured and the calculated photon.}
+The distributions from left to right and from top to bottom are: coplanarity 
+angle $\Delta \phi$, missing energy $E_X$, missing-mass-squared $M_X^2$, and 
+the cone angle $\theta$ between the measured photon and the missing momentum 
+of the $e^\prime$He$^\prime$ system.}
 \label{fig:kin-cuts}
@@
 \includegraphics[width=8.5cm]{figs/Q2_xB_t_Coh.pdf}
-\caption{Coherent DVCS event distributions for $Q^{2}$ as a function of 
-$x_{B}$ (left) and $Q^{2}$ as a function of $-t$ (right) after the 
-exclusivity cuts.}
+\caption{Coherent DVCS event distributions for $Q^2$ after exclusivity cuts. 
+The distributions are shown as a function of Bjorken variable $x_B$ (left) 
+and as a function of squared-momentum transfer $-t$ (right).}
 \label{fig:kin-coverage}
@@
 section of real photon electroproduction is dominated by the BH 
-contribution, while the DVCS contribution is very small. Its effect is however
+contribution, while the DVCS contribution is very small. However, the DVCS contribution is
 enhanced in the observables sensitive to the interference term, {\it e.g.} 
@@
 $\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$, where $M_{A}$($M_{N}$) is the $^4$He 
-(nucleon) mass. Using the different $\sin(\phi)$ and $\cos(\phi)$ contributions 
-in these factors, it is possible to unequivocally extract both imaginary and real 
-parts of $\mathcal{H}_{A}$ by fitting the $A_{LU}(\phi)$ distrubution.
+(nucleon) mass. Using the different $\sin(\phi)$ and $\cos(\phi)$ contributions, 
+both imaginary and real parts of $\mathcal{H}_{A}$ can be extracted unambiguously
+by fitting the $A_{LU}(\phi)$ distribution.
 
@@
 correct the DVCS data.  Depending on the kinematics, we found contaminations of 
-2 to 4\%.  Studies of systematic uncertainties showed that the main 
-contributions come from the choice of DVCS exclusivity cuts (8\%) and the 
+2 to 4\%. Studies of systematic uncertainties showed that the main contributions 
+come from the choice of DVCS exclusivity cuts (8\% systematic uncertainty) and the 
 large binning size (5.1\%), where the values are relative and quoted for $A_{LU}$
@@
 $A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and $t$-dependencies 
-are compared to theoretical calculations performed by S.~Liuti and K.~Taneja 
+are compared to theoretical calculations by S.~Liuti and K.~Taneja 
 \cite{simonetta_2}. The model accounts for the effect on the quark 
 distribution of the virtuality (off-shellness) of the nucleon. The calculations are at slightly 
-different kinematics than our data but still provide some guidance. The 
+different kinematics than our data but still allow drawing some conclusions. The 
 experimental results appear to have a larger asymmetries than the calculations. 
@@
 \includegraphics[width=8cm]{figs/coherent-ALU.pdf}
-\caption{The coherent $A_{LU}$ as a function of $\phi$. Results are presented
+\caption{The coherent $A_{LU}$ as a function of azimuthal angle $\phi$. Results are presented
    for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle panel), and $t$ 
@@
 model and is based on the double distributions ansatz \cite{DD_model}. The 
-off-shell model is the same as in Figure \ref{fig:alu90} using an improved
+off-shell model is the same as in Fig.~\ref{fig:alu90} using an improved
 GPD model for the nucleon \cite{GonzalezHernandez:2012jv}.
@@
 can see a difference between the precision of the extracted imaginary and real 
-parts, which is expected from
-Eq.~(\ref{eq:A_LU-coh}) because $\alpha_2$ is much smaller than $\alpha_1$. While the 
-accuracy of our results does not allow to discriminate between the models, they 
-demonstrate possibility of extraction of the CFF of spin 0 target in a model 
-independent way.
+parts, this result is expected because of Eq.~(\ref{eq:A_LU-coh}) where 
+$\alpha_2$ is much smaller than $\alpha_1$. While the precision of this 
+measurement is not at a sufficient level to discriminate between the models, 
+these results demonstrate the possibility of extracting the CFF of a spin 0 
+target in a model independent way directly from a BSA measurement.
 

### 2017-05-10 eg6-letters/coherent/dvcs_he4_prl.tex
Add Grenoble institution
added a second plot for alu @ 90 with slight shift on hermes point at t = 0.1
Comments from MG

@@
 \newcommand*{\INFNGEindex}{5}
+\newcommand*{\LPSC}{LPSC, Universit\'e Grenoble-Alpes, CNRS/IN2P3, Grenoble, France}
+\newcommand*{\LPSCindex}{6}
 \newcommand*{\UTFSM}{Universidad T\'{e}cnica Federico Santa Mar\'{i}a, Casilla 110-V Valpara\'{i}so, Chile}
-\newcommand*{\UTFSMindex}{6}
+\newcommand*{\UTFSMindex}{7}
 \newcommand*{\MISS}{Mississippi State University, Mississippi State, MS 39762-5167}
-\newcommand*{\MISSindex}{7}
+\newcommand*{\MISSindex}{8}
 \newcommand*{\VIRGINIA}{University of Virginia, Charlottesville, Virginia 22901}
-\newcommand*{\VIRGINIAindex}{8}
+\newcommand*{\VIRGINIAindex}{9}
 \newcommand*{\VIRGINIATECH}{Virginia Polytechnic Institute and State University, Blacksburg, Virginia, 24061}
-\newcommand*{\VIRGINIATECHindex}{9}
+\newcommand*{\VIRGINIATECHindex}{10}
 
@@
 \author{Y.~Perrin}
-\affiliation{\ORSAY}
+\affiliation{\LPSC}
 \author {B.~Torayev} 
@@
 \author {E.~Voutier} 
+\affiliation{\LPSC}
 \affiliation{\ORSAY}
@@
 \begin{abstract}
-We report the first exclusive measurement of coherent deeply virtual 
+We report on the first measurement of the beam-spin asymmetry in the 
+exclusive process of coherent deeply virtual 
 Compton scattering off a nucleus for $A>1$. The experiment used the 6 GeV 
 electron beam from the CEBAF accelerator at Jefferson Lab incident on a 
-$^4$He gas target in the center of the CEBAF large acceptance spectrometer 
-(CLAS). A specially designed radial 
-time projection chamber (RTPC) was used to detect the recoiling $^4$He
+$^4$He gas target in front of the CEBAF large acceptance spectrometer 
+(CLAS). While the electron was detected by CLAS and the gamma by a dedicated
+electromagnetic calorimeter at forward angles, a specially designed radial 
+time projection chamber was used to detect the recoiling $^4$He
 nuclei and ensure the exclusivity of the process. The measured beam-spin 
-asymmetries are larger than that observed on the proton in the same kinematic 
+asymmetries are larger than that observed on the free proton in the same kinematic 
 domain. Since $^4$He is a spin-zero target, we were able to extract, in a 
-model-independent way, the real and imaginary parts of the $^4$He 
-Compton form factors, $\cal H_A$, which are functions of the generalized parton 
-distribution $H_A$. This pioneering measurement of coherent deeply virtual 
+model-independent way, the real and imaginary parts of its unique 
+Compton form factor, $\cal H_A$. This pioneering measurement of coherent deeply virtual 
 Compton scattering on the $^4$He nucleus, with a fully exclusive final state 
@@
 
-Rich information on quantum chromodynamics (QCD) can be extracted from the 
-internal structure of hadrons. In the recent past, development of the 
-generalized parton distribution (GPD) framework has offered a possibility to 
-obtain new information about the momentum and spatial degrees of freedom of the 
+The generalized parton distribution (GPD) framework offers the opportunity to 
+obtain information about the momentum and spatial degrees of freedom of the 
 quarks and gluons inside hadrons 
@@
 \cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep,Burkardt:2005hp}. 
-
 The most promising way to access GPDs experimentally is through the measurement 
 of deeply virtual Compton scattering (DVCS), \textit{i.e.}, the hard exclusive 
-electroproduction of a real photon.  While other processes are known to be 
+electroproduction of a real photon on a hadron. While other processes are known to be 
 sensitive to GPDs, the measurement of DVCS is considered the cleanest probe and 
@@
 \cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
-Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.  
+Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,
+Jo:2015ema,Joerg:2016hhs}.  
 The vast majority of these measurements focused on the study of proton 
 structure and allowed for an extraction of the three-dimensional image of the 
-proton (for details on the formalism, see 
-\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
+proton (for reviews of the field, see~\cite{Goeke:2001tz,Diehl:2003ny,
+Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
 This framework is also applicable to nuclei, giving access to novel 
 information about nuclear structure in terms of quarks and 
-gluons \cite{Dupre:2015jha}.
+gluons (see~\cite{Dupre:2015jha} and references therein).
 Study of the 3D structure of nuclei appears to be especially important
 in light of the large nuclear effects observed in nuclear parton distribution 
-functions \cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.
+functions~\cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.
 
@@
 
-One must overcome two major experimental challenges in measuring coherent 
-nuclear DVCS, $eA\rightarrow e^\prime A^\prime\gamma$. First, the cross section 
-of coherent scattering is suppressed due to the nuclear form factor, and 
-second, the intact recoil nucleus ($A^\prime$) must be detected to ensure coherence.  
 Fig.~\ref{fig:diags} illustrates the handbag diagram for coherent DVCS on 
-$^4$He, where four-vectors of the electrons, photons, and $^4$He are denoted by
-$k/k^\prime$, $q/q^\prime$, and $p/p^\prime$ respectively. For large virtual photon's 
-4-momentum squared, $Q^2=-(k-k')^{2}$, and small squared momentum transfer, $t=(p-p')^{2}$, the DVCS handbag 
+$^4$He, where the four-vectors of the electrons, photons, and $^4$He are denoted 
+by $k/k^\prime$, $q/q^\prime$, and $p/p^\prime$ respectively. For large 
+virtual photon's 4-momentum squared, $Q^2=-(k-k')^{2}$, and small squared 
+momentum transfer, $t=(p-p')^{2}$, the DVCS handbag 
 diagram can be factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The 
 hard part includes the photon-quark interaction and is calculable in 
-perturbative QCD. The non-perturbative part is parametrized in terms of GPDs, 
+perturbative QED. The non-perturbative part is parametrized in terms of GPDs, 
 which embed the partonic structure of the hadron. The GPDs depend on the three 
-variables $x$, $\xi$, and $t$ as introduced in Fig.~\ref{fig:diags}. The 
+variables $x$, $\xi$, and $t$. The 
 parameter $\xi$ relates to the Bjorken variable $x_{B}$: $\xi\approx 
-{{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M\nu}$, $\nu=k^0-k^{0\prime}$, and 
-$M$ is the proton mass. The parameter $x$ is the quark's internal loop momentum 
+{{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M_N\nu}$, $\nu=k^0-k^{0\prime}$, and 
+$M_N$ is the nucleon mass. The parameter $x$ is the quark's internal loop momentum 
 fraction and cannot be accessed experimentally. We in fact measure 
-Compton form factors (CFF) \cite{Guidal:2013rya}, which are
-complex amplitudes defined as:
+Compton form factors (CFF), which are complex quantities defined as:
 
@@
 \end{align}
-with $H_A$ the GPD, $\mathcal{P}$ 
+with $H_A$ the GPDs, $\mathcal{P}$ 
 the Cauchy principal value integral, and $C^{+}(x,\xi)$ a coefficient function 
@@
 measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and Xe), 
-but contamination from incoherent processes could influence the
-measurement significantly \cite{Guzey:2003jh}. Accordingly, direct detection 
-of the low-energy recoil nucleus is critical in guaranteeing the nucleus 
-remains intact.
+but contamination from incoherent processes could influence the measurement 
+significantly~\cite{Guzey:2003jh}. The direct detection of the recoil nucleus 
+can however guaranty that the nucleus remains intact.
 
-The $^4$He nucleus is an ideal experimental target for DVCS on nuclei, as it 
-is light enough to be detected in such a setting, while it is subject to 
-significant nuclear effects~\cite{JSeely} and has a spin-0. A helium target leads to another 
-important advantage, as the number of GPDs defined for a hadron depends on its 
-spin. The structure of a spin-zero nucleus, such as $^4$He, is parametrized by 
+The $^4$He nucleus is an ideal experimental target for nuclear DVCS, as it 
+is light enough to be detected by our experimental setting, while it is subject to 
+sizeable nuclear effects~\cite{JSeely} easily observable. Its spin-zero leads 
+to another important advantage, as the number of GPDs defined for a hadron 
+depends on its spin. The structure of a spin-zero hadron is parametrized by 
 only one chiral even GPD ($H_{A}(x,\xi,t)$) at leading twist, while 4 GPDs 
@@
 The CEBAF large acceptance spectrometer (CLAS) in Hall-B at Jefferson Lab has been
-previously used successfully for DVCS measurements on the nucleon
-\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.  In order
-to extend its capabilities to nuclear DVCS with a fully exclusive final state,
-we built a specialized radial time projection chamber (RTPC) for the detection
-and identification of low-energy recoiling light nuclei. 
-The experiment E08-024 took place in Hall-B at Jefferson Lab in 2009 using the 
-nearly 100\% duty factor, longitudinally polarized electron beam (83$\%$ 
-polarization) at an energy of 6.064 GeV. The data were collected over 40 days 
-using a 6 atm gaseous $^4$He target placed 64 cm upstream of the nominal center 
-of CLAS. For DVCS experiments, the CLAS 
-baseline design~\cite{Mecking:2003zu} 
-is supplemented with an inner calorimeter (IC) and a solenoid magnet. The IC 
+previously supplemented with an inner calorimeter (IC) and a solenoid magnet to
+measure DVCS observables on the nucleon
+\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}. The IC 
 extends the photon detection acceptance of CLAS to polar angles as low as 
-4$^{\circ}$. The 5 T solenoid magnet has two functions; it provides the magnetic 
-field for the momentum analysis in the RTPC, and at the same time acts as 
-the guiding field for the low-energy M\o{}ller electrons, that are absorbed in a  
+4$^{\circ}$. The 5 T solenoid magnet acts as a guiding field for the 
+low-energy M\o{}ller electrons, that are absorbed in a  
 heavy shield placed around the beam line.
@@
 particles, so in order to ensure the exclusivity of the measurement, we built a 
-small and light RTPC to complement CLAS. The RTPC is a $20$-cm-long cylinder 
-with a diameter of $15$ cm, positioned directly around the $^4$He gaseous 
-target. The target is a $25$-cm-long and $6$-mm-diameter Kapton tube with 
-$27$-$\mu$m-thick walls. The RTPC was calibrated specifically for the detection of 
-$^4$He nuclei by utilizing elastic scattering $e^4$He$\to e^\prime$$^4$He with
-a 1.2~GeV electron beam.
-
-%\begin{figure}[tb]
-%\vspace{-1.1cm}
-%\includegraphics[width=6.5cm,angle=-90]{figs/RTPC.pdf}
-%\vspace{-1.1cm}
-%\caption{Left: A picture of the E08-024 RTPC before insertion into the 
-%solenoid. Right: A cross section of the E08-024 RTPC perpendicular to the beam 
-%direction. An illustration of a $^4$He track originating from the pressurized 
-%straw target is shown along with the electrons produced in the drift region.}
-%\label{fig:RTPC}
-%\end{figure}
+small and light radial time projection chamber (RTPC) to complement CLAS. The 
+RTPC is a $20$-cm-long cylinder with a diameter of $15$ cm, positioned in the 
+solenoid magnet. In the center of the RTPC is the target, a $25$-cm-long 
+and $6$-mm-diameter Kapton tube with $27$-$\mu$m-thick walls filled with 
+6~atm of gaseous $^4$He. The experiment (E08-024) collected
+data over 40 days at the end of 2009 using a 
+nearly 100\% duty factor, longitudinally polarized electron beam (83$\%$ 
+polarization) at an energy of 6.064 GeV. The RTPC was calibrated specifically 
+for the detection of $^4$He nuclei by utilizing elastic scattering 
+$e^4$He$\to e^\prime$$^4$He with a 1.2~GeV electron beam.
 
@@
 one $^4$He, and at least one photon are detected in the final state. Electrons 
-are identified using their measured momentum, time, and energy obtained from 
+are identified using their measured momentum, light yield, time, and energy obtained from 
 the CLAS drift chambers, \^{C}erenkov counters, scintillator counters, 
-and electromagnetic calorimeters. The recoiling $^4$He nuclei are identified in 
-the RTPC using time, track quality, and energy-loss cuts for tracks in the 
-fiducial region \cite{Hattawy:thesis}. In addition, we apply a vertex-matching 
+and electromagnetic calorimeters, respectively. The recoiling $^4$He nuclei 
+are identified in the RTPC using time and energy-loss cuts for tracks in the 
+fiducial region~\cite{Hattawy:thesis}. In addition, we apply a vertex-matching 
 cut to ensure that the 
@@
 The experimental data for the most relevant exclusivity observables and applied
-cuts are shown in Fig.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for additional details).
-%The most relevant of these cuts are presented in Fig.~\ref{fig:kin-cuts}, which 
-%shows 3$\sigma$ cuts except for the missing energy (which appears to be too 
-%large and for which we reduced the cut window to [-0.45,0.5] GeV).
-We also 
+cuts are shown in Fig.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for 
+additional details). We also 
 reject events where a $\pi^0$ is identified by invariant mass reconstruction of 
@@
 distributions represent the initial candidate events, while the shaded 
-distributions represent those which which passed all the exclusivity cuts except 
+distributions represent those which passed all the exclusivity cuts except 
 the quantity plotted. The vertical red lines represent the applied cuts.
@@
 
+We identified two main backgrounds to our measurement, accidental coincidences 
+and exclusive coherent
+$\pi^0$ production. The accidentals have particles originating from different events,
+and we estimated their contribution to be 4.1\% of our sample. We evaluated this 
+contribution by selecting events passing all our cuts but with an electron and 
+helium originating from different vertices. The $\pi^0$ production can easily
+be mistaken for DVCS when one of the two photons from the $\pi^0$ 
+decay is produced at low energy in the laboratory frame and remains undetected.  
+To estimate the effect of this contamination, we developed an event generator 
+tuned on the experimental yield of exclusive $\pi^0$ with two photons measured. 
+We used this generator together with a GEANT3 simulation of our 
+detectors to estimate the ratio of the number of $\pi^0$ events where the 
+two photons are detected to those that are misidentified as DVCS events. This 
+ratio is then multiplied by the measured yield of exclusive $\pi^0$ events to 
+correct the DVCS data. Depending on the kinematics, we found contaminations of 
+2 to 4\%.
+
 %asymmetries
 In this work, the physics observable extracted using coherent DVCS events is
-the beam-spin asymmetry (BSA). The BSA on an unpolarized target, $A_{LU}$, is 
-measured as the difference of cross sections for the reaction with opposite beam 
+the beam-spin asymmetry, noted $A_{LU}$. On an unpolarized target, $A_{LU}$ is 
+defined as the difference of cross sections for the reaction with opposite beam 
 helicities normalized to the total cross section:
@@
 extracted from the reaction yields for the two helicities ($N^{+/-}$)
-%expressed in terms of helicity-state yields ($N^{+/-}$)
 \begin{equation}
@@
 
-The DVCS and well-known Bethe-Heitler (BH) processes, in which the real 
-photon is emitted by the incoming or the outgoing lepton, have the same final 
-state and are indistinguishable. The amplitude of electroproduction of real
+There is an additional process contributing to the same final state as the 
+DVCS, the so called Bethe-Heitler (BH) process, where the real photon is 
+emitted by the incoming or the outgoing lepton. The DVCS and BH processes are 
+indistinguishable experimentally and the amplitude of electroproduction of real
 photons includes a sum of the amplitudes of these two processes. The BH 
-amplitude is defined by the target form factors, while the DVCS amplitude is 
-a combination of the form factors and GPDs. For our kinematics, the cross 
-section of real photon electroproduction is dominated by the BH 
-contribution, while the DVCS contribution is very small. However, the DVCS contribution is
+amplitude depends of the target form factors, while the DVCS amplitude 
+depends on GPDs. For our kinematics, the cross section of real photon 
+electroproduction is dominated by the BH contribution, while the DVCS 
+contribution is very small. However, the DVCS contribution is
 enhanced in the observables sensitive to the interference term, {\it e.g.} 
-BSA. The three terms entering the cross section calculation,
+$A_{LU}$. The three terms entering the cross section calculation,
 the square of the BH and DVCS amplitudes and their interference term, depend on the
@@
 as shown for the nucleon in Ref.~\cite{Belitsky:2001ns} and for the spin-zero targets
-in Refs.~\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the BSA 
+in Refs.~\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the $A_{LU}$ 
 of a spin-zero hadron can be expressed as
@@
 \end{equation}
-where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
-and real parts of the $^4$He CFF $\mathcal{H}_{A}$ and depend on the GPD $H_A$.  
-Explicit expressions of the purely kinematic factors $\alpha_i$ are written in
+explicit expressions of the kinematic factors $\alpha_i$ are written in
 Ref.~\cite{Belitsky:2008bz} and are functions of Fourier harmonics in the 
@@
 
-In this work, the azimuthal dependence of the beam-spin asymmetry has been studied 
-for a wide range of kinematics ($Q^2$ between 1 and 2.2 GeV$^2$/c$^2$, $x_B$ between
-0.1 and 0.3, and $-t$ between 0.07 and 0.16 GeV$^2$/c$^2$). We identified two main
-backgrounds to our measurement, accidental coincidences and exclusive coherent
-$\pi^0$ production.  The accidentals have particles originating from different events,
-and we estimated their contribution to be 4.1\% of our sample. We evaluated this 
-contribution by selecting events passing all our cuts but with an electron and 
-helium originating from different vertices. The $\pi^0$ production can easily
-be mistaken for DVCS when one of the two photons from the $\pi^0$ 
-decay is produced at low energy in the laboratory frame and remains undetected.  
-To estimate the effect of this background, we developed an event generator 
-tuned on the experimental yield of exclusive $\pi^0$ measured by our 
-experiment. We used this generator together with a GEANT3 simulation of our 
-detector to estimate the ratio of the number of $\pi^0$ events where the 
-two photons are detected to those that are misidentified as DVCS events. This 
-ratio is then multiplied by the measured yield of exclusive $\pi^0$ events to 
-correct the DVCS data.  Depending on the kinematics, we found contaminations of 
-2 to 4\%. Studies of systematic uncertainties showed that the main contributions 
-come from the choice of DVCS exclusivity cuts (8\% systematic uncertainty) and the 
-large binning size (5.1\%), where the values are relative and quoted for $A_{LU}$
-at $\phi=90^\circ$.  Added quadratically, the total systematic uncertainty
-is about 10\% at $90^\circ$ (or 0.03, absolute), which is significantly smaller
-than the statistical uncertainties in all kinematical bins.
-
-Due to limited statistics, dependence of the extracted asymmetries on the kinematical variables $Q^2$, 
-$x_B$, and $t$ has been studied separately. In Fig.~\ref{fig:alu}, $A_{LU}$ for 
-bins in each of the three variables is presented. The curves on the plots are fits with 
-the function presented in Eq.~(\ref{eq:A_LU-coh}), where the real and imaginary 
-parts of the CFF $\mathcal{H}_{A}$ are the free parameters of the fit.  In 
-Fig.~\ref{fig:alu90} the $Q^2$, $x_{B}$, and $t$-dependencies of the fitted 
-$A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and $t$-dependencies 
-are compared to theoretical calculations by S.~Liuti and K.~Taneja 
-\cite{simonetta_2}. The model accounts for the effect on the quark 
-distribution of the virtuality (off-shellness) of the nucleon. The calculations are at slightly 
-different kinematics than our data but still allow drawing some conclusions. The 
-experimental results appear to have a larger asymmetries than the calculations. 
-The difference may arise from the theoretical uncertainty in the determination 
-of the crossing point where the parton nuclear distribution becomes larger than the 
-nucleon one, and reverses the sign of the nuclear effect.
+We present in Fig.~\ref{fig:alu} $A_{LU}$ as a function of azimuthal angle 
+$\phi$ and the kinematical variables $Q^2$, $x_B$, and $t$. Due to our limited 
+statistics, the latter are studied separately with independent binning. The curves on 
+the plots are fits using the function presented in Eq.~(\ref{eq:A_LU-coh}), 
+where the real and imaginary parts of the CFF $\mathcal{H}_{A}$ are the only 
+free parameters.
 
@@
    bins (bottom panel).  The error bars represent the statistical 
-   uncertainties. The gray bands represent the systematic uncertainties, 
+   uncertainties. The grey bands represent the systematic uncertainties, 
    including the normalisation uncertainties. The red curves are the results of 
@@
 
+Studies of systematic uncertainties showed that the main contributions 
+come from the choice of DVCS exclusivity cuts (8\% systematic uncertainty) and the 
+large binning size (5.1\%). The values are relative and quoted for $A_{LU}$
+at $\phi=90^\circ$. Added quadratically, the total systematic uncertainty
+is about 10\% at $90^\circ$ (or 0.03, in absolute), which is significantly smaller
+than the statistical uncertainties in all kinematical bins.
+
+In Fig.~\ref{fig:alu90}, the $Q^2$, $x_{B}$, and $t$-dependencies of the fitted 
+$A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and $t$-dependencies 
+are compared to theoretical calculations by S.~Liuti and K.~Taneja 
+\cite{simonetta_2}. The model accounts for the effect on the quark distribution 
+of the virtuality (off-shellness) of the nucleon. The calculations are at slightly 
+different kinematics than our data but still allow drawing some conclusions. The 
+calculations appear to have smaller asymmetries than observed. 
+The difference may arise from the theoretical uncertainty in the determination 
+of the crossing point where the parton nuclear distribution becomes larger than the 
+nucleon one, and reverses the sign of the nuclear effect.
+
 \begin{figure*}[tb]
-\includegraphics[width=17cm]{figs/coherent-ALU_90.pdf}
+\includegraphics[width=17cm]{figs/coherent-ALU_90_2.pdf}
 \caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $t$-dependencies (right) of
@@
    calculations from \cite{simonetta_2}. On the right: the green circles are 
-   the HERMES $-A_{LU}$ (positron beam was used) inclusive measurements 
-   \cite{Airapetian}, the colored curves represent theoretical calculations 
+   the HERMES $-A_{LU}$ (a positron beam was used) inclusive measurements 
+   \cite{Airapetian}, the curves represent the theoretical calculations 
    from \cite{simonetta_2}.}
@@
 real (bottom panel) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of
-$Q^{2}$ (right panel), $x_B$ (middle panel), and $t$ (left panel). The full red 
-curves are calculations based on an on-shell model from Ref.~\cite{Vadim_priv}.
-The black-dashed curves are calculations from a convolution 
-model based on the VGG model for the nucleons' GPDs \cite{Guidal_priv}. The 
+$Q^{2}$ (left panel), $x_B$ (middle panel), and $t$ (right panel). The full red 
+curves are the calculations based on the convolution model from Ref.~\cite{Vadim_priv}.
+The black-dashed curves are calculations from the same 
+model using different GPDs for the nucleons (VGG model~\cite{Guidal_priv}). The 
 blue long-dashed curve on the top-right plot is from
-an off-shell model as described in Ref.~\cite{GonzalezHernandez:2012jv}.}
+the off-shell model as described in Ref.~\cite{GonzalezHernandez:2012jv}.}
 \label{fig:CFF_HA}
@@
 The results in Fig.~\ref{fig:CFF_HA} show that the extraction of the CFF
-from the BSA is possible without any model dependent 
-assumptions. The amplitude and the dependencies observed as a function of 
+from the $A_{LU}$ is possible without model dependent assumptions beyond
+leading-twist and leading-order dominance. The amplitude and the dependencies 
+observed as a function of 
 $Q^{2}$, $x_B$, and $t$ are in agreement with the theoretical expectations. One 
@@
 these results demonstrate the possibility of extracting the CFF of a spin 0 
-target in a model independent way directly from a BSA measurement.
+target directly from a $A_{LU}$ measurement.
 
 %conclusion
-In summary, we present the first exclusive measurement of coherent DVCS off 
-$^4$He using the CLAS spectrometer supplemented with a Radial Time Projection 
-Chamber and a high pressure gaseous target. This setup allowed detection of the 
+In summary, we have presented the first measurement of the beam-spin asymmetry
+of exclusive coherent DVCS off $^4$He using the CLAS spectrometer supplemented 
+with a RTPC. This setup allowed detection of the 
 low energy $^4$He recoils in order to ensure an exclusive measurement of the
-coherent DVCS process.
-The azimuthal dependence of the measured BSA ($A_{LU}$) has 
+coherent DVCS process. The azimuthal dependence of the measured $A_{LU}$ has 
 been used to extract, in a model independent way, the real and the imaginary 
@@
 
+\bibitem{Joerg:2016hhs} 
+  P.~Joerg [COMPASS Collaboration],
+  %``The $t$-dependence of the pure DVCS cross-section at COMPASS,''
+  PoS DIS {\bf 2016}, 235 (2016).
+
 \bibitem{Goeke:2001tz}

### 2017-05-10 eg6-letters/coherent/dvcs_he4_prl.tex
add Carmans comments, part A

@@
 
-\title{First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei}
+\title{First Exclusive Measurement of Deeply Virtual Compton Scattering off $^4$He: Toward the 3D Tomography of Nuclei}
 
@@
 electron beam from the CEBAF accelerator at Jefferson Lab incident on a 
-$^4$He gas target in front of the CEBAF large acceptance spectrometer 
+$^4$He gas target in front of the CEBAF Large Acceptance Spectrometer 
 (CLAS). While the electron was detected by CLAS and the gamma by a dedicated
@@
 time projection chamber was used to detect the recoiling $^4$He
-nuclei and ensure the exclusivity of the process. The measured beam-spin 
-asymmetries are larger than that observed on the free proton in the same kinematic 
+nuclei and to ensure the exclusivity of the process. The measured beam-spin 
+asymmetries are larger than those observed on the free proton in the same kinematic 
 domain. Since $^4$He is a spin-zero target, we were able to extract, in a 
@@
 by $k/k^\prime$, $q/q^\prime$, and $p/p^\prime$ respectively. For large 
-virtual photon's 4-momentum squared, $Q^2=-(k-k')^{2}$, and small squared 
+virtual photon 4-momentum squared, $Q^2=-(k-k')^{2}$, and small squared 
 momentum transfer, $t=(p-p')^{2}$, the DVCS handbag 
@@
 parameter $\xi$ relates to the Bjorken variable $x_{B}$: $\xi\approx 
-{{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M_N\nu}$, $\nu=k^0-k^{0\prime}$, and 
+{{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M_N\nu}$, $\nu$ is the energy of the virtual photon, and 
 $M_N$ is the nucleon mass. The parameter $x$ is the quark's internal loop momentum 
@@
 only on kinematic cuts on the measured scattered electron and real photon. The 
-measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and Xe), 
+measurement was performed on a large set of nuclei ($^4$He, $^{14}$N, $^{20}$Ne, $^{85}$Kr and $^{131}$Xe), 
 but contamination from incoherent processes could influence the measurement 
 significantly~\cite{Guzey:2003jh}. The direct detection of the recoil nucleus 
-can however guaranty that the nucleus remains intact.
+can however guarantee that the nucleus remains intact.
 
@@
 
-The CEBAF large acceptance spectrometer (CLAS) in Hall-B at Jefferson Lab has been
+The CEBAF Large Acceptance Spectrometer (CLAS) in Hall B at Jefferson Lab has been
 previously supplemented with an inner calorimeter (IC) and a solenoid magnet to
@@
 \cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}. The IC 
-extends the photon detection acceptance of CLAS to polar angles as low as 
-4$^{\circ}$. The 5 T solenoid magnet acts as a guiding field for the 
-low-energy M\o{}ller electrons, that are absorbed in a  
+extended the photon detection acceptance of CLAS to polar angles as low as 
+4$^{\circ}$. The 5 T solenoid magnet acted as a guiding field for the 
+low-energy M\o{}ller electrons that were absorbed in a  
 heavy shield placed around the beam line.
@@
 In our kinematics, the recoil $^4$He nuclei produced in DVCS have low momentum,
-averaging 300 MeV/c. CLAS cannot detect such low-energy $\alpha$ 
+averaging 300 MeV/c. CLAS could not detect such low-energy $\alpha$ 
 particles, so in order to ensure the exclusivity of the measurement, we built a 
 small and light radial time projection chamber (RTPC) to complement CLAS. The 
-RTPC is a $20$-cm-long cylinder with a diameter of $15$ cm, positioned in the 
-solenoid magnet. In the center of the RTPC is the target, a $25$-cm-long 
+RTPC was a $20$-cm-long cylinder with a diameter of $15$ cm, positioned in the 
+solenoid magnet. In the center of the RTPC was the target, a $25$-cm-long 
 and $6$-mm-diameter Kapton tube with $27$-$\mu$m-thick walls filled with 
@@
 %DVCS selection
-To identify coherent DVCS events, we first select events where one electron, 
-one $^4$He, and at least one photon are detected in the final state. Electrons 
-are identified using their measured momentum, light yield, time, and energy obtained from 
+To identify coherent DVCS events, we first selected events where one electron, 
+one $^4$He, and at least one photon were detected in the final state. Electrons 
+were identified using their measured momentum, light yield, time, and energy obtained from 
 the CLAS drift chambers, \^{C}erenkov counters, scintillator counters, 
 and electromagnetic calorimeters, respectively. The recoiling $^4$He nuclei 
-are identified in the RTPC using time and energy-loss cuts for tracks in the 
-fiducial region~\cite{Hattawy:thesis}. In addition, we apply a vertex-matching 
+were identified in the RTPC using time and energy-loss cuts for tracks in the 
+fiducial region~\cite{Hattawy:thesis}. In addition, we applied a vertex-matching 
 cut to ensure that the 
-electron and helium nucleus originate from a common reaction vertex in the 
-target cell. The photons are 
-detected in either the IC or the CLAS electromagnetic calorimeter. Note that 
+electron and helium nucleus originated from a common reaction vertex in the 
+target cell. The photons were 
+detected in either the IC or the CLAS electromagnetic calorimeters. Note that 
 even though the DVCS reaction has only one real photon in the final state, 
-events with more than one good photon are not discarded at this stage. These
-are caused by accidental coincidences of soft photons that do not affect 
+events with more than one good photon were not discarded at this stage. These
+were caused by accidental coincidences of soft photons and did not affect 
 directly our measurement. We consider only the most energetic photon of an 
 event as a DVCS photon candidate.
-This prescription however slightly increases the corrections associated with
+This prescription however slightly increased the corrections associated with
 the $\pi^0$ and the accidental backgrounds discussed below.
 
-To ensure the interaction occurs at the partonic level and the DVCS handbag 
-diagram is dominant, we select events with $Q^{2}$ greater than 1 
-GeV$^{2}/$c$^{2}$. Exclusivity of the coherent DVCS reaction is optimized by 
+To ensure the interaction occurred at the partonic level and that the DVCS handbag 
+diagram was dominant, we selected events with $Q^{2}$ greater than 1 
+GeV$^{2}/$c$^{2}$. Exclusivity of the coherent DVCS reaction was optimized by 
 applying a set of cuts on the following kinematic variables: the coplanarity 
@@
 additional details). We also 
-reject events where a $\pi^0$ is identified by invariant mass reconstruction of 
-two photons. About 3200 events pass these requirements, and their kinematic 
+rejected events where a $\pi^0$ was identified by the invariant mass reconstruction of 
+two photons. About 3200 events passed these requirements, and their kinematic 
 distributions are shown in Fig.~\ref{fig:kin-coverage}.
@@
 distributions represent the initial candidate events, while the shaded 
-distributions represent those which passed all the exclusivity cuts except 
+distributions represent those that passed all of the exclusivity cuts except 
 the quantity plotted. The vertical red lines represent the applied cuts.
@@
 the cone angle $\theta$ between the measured photon and the missing momentum 
-of the $e^\prime$He$^\prime$ system.}
+of the $e^\prime{^4}$He$^\prime$ system.}
 \label{fig:kin-cuts}
@@
 \includegraphics[width=8.5cm]{figs/Q2_xB_t_Coh.pdf}
-\caption{Coherent DVCS event distributions for $Q^2$ after exclusivity cuts. 
-The distributions are shown as a function of Bjorken variable $x_B$ (left) 
-and as a function of squared-momentum transfer $-t$ (right).}
+\caption{Coherent DVCS event distributions for $Q^2$ after the exclusivity cuts. 
+The distributions are shown as a function of Bjorken $x_B$ (left) 
+and as a function of the squared-momentum transfer $-t$ (right).}
 \label{fig:kin-coverage}
@@
 and we estimated their contribution to be 4.1\% of our sample. We evaluated this 
-contribution by selecting events passing all our cuts but with an electron and 
-helium originating from different vertices. The $\pi^0$ production can easily
+contribution by selecting events passing all our cuts but with the scattered electron and 
+$^4$He originating from different vertices. The $\pi^0$ production can easily
 be mistaken for DVCS when one of the two photons from the $\pi^0$ 
@@
 (nucleon) mass. Using the different $\sin(\phi)$ and $\cos(\phi)$ contributions, 
-both imaginary and real parts of $\mathcal{H}_{A}$ can be extracted unambiguously
+both the imaginary and real parts of $\mathcal{H}_{A}$ can be extracted unambiguously
 by fitting the $A_{LU}(\phi)$ distribution.
@@
    including the normalisation uncertainties. The red curves are the results of 
-our fits with the form of equation \ref{eq:A_LU-coh}.}
+our fits with the form of equation Eq.~(\ref{eq:A_LU-coh}).}
 \label{fig:alu}
@@
 \caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $t$-dependencies (right) of
-   the $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
+   $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
    middle plot: the full-red and the dashed-blue curves are theoretical 
@@
    the HERMES $-A_{LU}$ (a positron beam was used) inclusive measurements 
-   \cite{Airapetian}, the curves represent the theoretical calculations 
+   \cite{Airapetian}, and the curves represent the theoretical calculations 
    from \cite{simonetta_2}.}
@@
 \caption{The model-independent extraction of the imaginary (top panel) and
-real (bottom panel) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of
+real (bottom panel) parts of the $^4$He CFF $\mathcal{H}_A$, as a function of
 $Q^{2}$ (left panel), $x_B$ (middle panel), and $t$ (right panel). The full red 
@@
 extracted from the fit to the azimuthal dependence of $A_{LU}$ are shown in 
-Fig.~\ref{fig:CFF_HA}. Curves on the graphs are model calculations, labelled 
+Fig.~\ref{fig:CFF_HA}. The curves on the graphs are model calculations, labelled 
 {\it convolution} and {\it off-shell}. In the convolution model 
@@
 The results in Fig.~\ref{fig:CFF_HA} show that the extraction of the CFF
-from the $A_{LU}$ is possible without model dependent assumptions beyond
+from the $A_{LU}$ is possible without model-dependent assumptions beyond
 leading-twist and leading-order dominance. The amplitude and the dependencies 
@@
 can see a difference between the precision of the extracted imaginary and real 
-parts, this result is expected because of Eq.~(\ref{eq:A_LU-coh}) where 
+parts, which is expected because of Eq.~(\ref{eq:A_LU-coh}) where 
 $\alpha_2$ is much smaller than $\alpha_1$. While the precision of this 
 measurement is not at a sufficient level to discriminate between the models, 
-these results demonstrate the possibility of extracting the CFF of a spin 0 
+these results demonstrate the possibility of extracting the CFF of a spin-0 
 target directly from a $A_{LU}$ measurement.

### 2017-05-10 eg6-letters/coherent/dvcs_he4_prl.tex
eg6-letters/coherent:  implement Carmans comments, part B

@@
 
-The CEBAF Large Acceptance Spectrometer (CLAS) in Hall B at Jefferson Lab has been
+The CEBAF Large Acceptance Spectrometer (CLAS) in Hall B at Jefferson Lab ~\cite{Mecking:2003zu} has been
 previously supplemented with an inner calorimeter (IC) and a solenoid magnet to

### 2017-05-10 eg6-letters/coherent/dvcs_he4_prl.tex
update all the figures in the coherent paper

--- 2017-05-10 eg6-letters/coherent/dvcs_he4_prl.tex
@@
 \begin{abstract}
-We report on the first measurement of the beam-spin asymmetry in the 
-exclusive process of coherent deeply virtual 
+We report the first exclusive measurement of coherent deeply virtual 
 Compton scattering off a nucleus for $A>1$. The experiment used the 6 GeV 
 electron beam from the CEBAF accelerator at Jefferson Lab incident on a 
-$^4$He gas target in front of the CEBAF large acceptance spectrometer 
-(CLAS). While the electron was detected by CLAS and the gamma by a dedicated
-electromagnetic calorimeter at forward angles, a specially designed radial 
-time projection chamber was used to detect the recoiling $^4$He
+$^4$He gas target in the center of the CEBAF large acceptance spectrometer 
+(CLAS). A specially designed radial 
+time projection chamber (RTPC) was used to detect the recoiling $^4$He
 nuclei and ensure the exclusivity of the process. The measured beam-spin 
-asymmetries are larger than that observed on the free proton in the same kinematic 
+asymmetries are larger than that observed on the proton in the same kinematic 
 domain. Since $^4$He is a spin-zero target, we were able to extract, in a 
-model-independent way, the real and imaginary parts of its unique 
-Compton form factor, $\cal H_A$. This pioneering measurement of coherent deeply virtual 
+model-independent way, the real and imaginary parts of the $^4$He 
+Compton form factors, $\cal H_A$, which are functions of the generalized parton 
+distribution $H_A$. This pioneering measurement of coherent deeply virtual 
 Compton scattering on the $^4$He nucleus, with a fully exclusive final state 
@@
 
-The generalized parton distribution (GPD) framework offers the opportunity to 
-obtain information about the momentum and spatial degrees of freedom of the 
+Rich information on quantum chromodynamics (QCD) can be extracted from the 
+internal structure of hadrons. In the recent past, development of the 
+generalized parton distribution (GPD) framework has offered a possibility to 
+obtain new information about the momentum and spatial degrees of freedom of the 
 quarks and gluons inside hadrons 
@@
 \cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep,Burkardt:2005hp}.
+
 The most promising way to access GPDs experimentally is through the measurement 
 of deeply virtual Compton scattering (DVCS), \textit{i.e.}, the hard exclusive 
-electroproduction of a real photon on a hadron. While other processes are known to be 
+electroproduction of a real photon.  While other processes are known to be 
 sensitive to GPDs, the measurement of DVCS is considered the cleanest probe and 
@@
 \cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
-Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,
-Jo:2015ema,Joerg:2016hhs}.  
+Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.  
 The vast majority of these measurements focused on the study of proton 
 structure and allowed for an extraction of the three-dimensional image of the 
-proton (for reviews of the field, see~\cite{Goeke:2001tz,Diehl:2003ny,
-Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
+proton (for details on the formalism, see 
+\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
 This framework is also applicable to nuclei, giving access to novel 
 information about nuclear structure in terms of quarks and 
-gluons (see~\cite{Dupre:2015jha} and references therein).
+gluons \cite{Dupre:2015jha}.
 Study of the 3D structure of nuclei appears to be especially important
 in light of the large nuclear effects observed in nuclear parton distribution 
-functions~\cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.
+functions \cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.
 
@@
 
+One must overcome two major experimental challenges in measuring coherent 
+nuclear DVCS, $eA\rightarrow e^\prime A^\prime\gamma$. First, the cross section 
+of coherent scattering is suppressed due to the nuclear form factor, and 
+second, the intact recoil nucleus ($A^\prime$) must be detected to ensure coherence.  
 Fig.~\ref{fig:diags} illustrates the handbag diagram for coherent DVCS on 
-$^4$He, where the four-vectors of the electrons, photons, and $^4$He are denoted 
-by $k/k^\prime$, $q/q^\prime$, and $p/p^\prime$ respectively. For large 
-virtual photon's 4-momentum squared, $Q^2=-(k-k')^{2}$, and small squared 
-momentum transfer, $t=(p-p')^{2}$, the DVCS handbag 
+$^4$He, where four-vectors of the electrons, photons, and $^4$He are denoted by
+$k/k^\prime$, $q/q^\prime$, and $p/p^\prime$ respectively. For large virtual photon's 
+4-momentum squared, $Q^2=-(k-k')^{2}$, and small squared momentum transfer, $t=(p-p')^{2}$, the DVCS handbag 
 diagram can be factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The 
 hard part includes the photon-quark interaction and is calculable in 
-perturbative QED. The non-perturbative part is parametrized in terms of GPDs, 
+perturbative QCD. The non-perturbative part is parametrized in terms of GPDs, 
 which embed the partonic structure of the hadron. The GPDs depend on the three 
-variables $x$, $\xi$, and $t$. The 
+variables $x$, $\xi$, and $t$ as introduced in Fig.~\ref{fig:diags}. The 
 parameter $\xi$ relates to the Bjorken variable $x_{B}$: $\xi\approx 
-{{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M_N\nu}$, $\nu=k^0-k^{0\prime}$, and 
-$M_N$ is the nucleon mass. The parameter $x$ is the quark's internal loop momentum 
+{{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M\nu}$, $\nu=k^0-k^{0\prime}$, and 
+$M$ is the proton mass. The parameter $x$ is the quark's internal loop momentum 
 fraction and cannot be accessed experimentally. We in fact measure 
-Compton form factors (CFF), which are complex quantities defined as:
+Compton form factors (CFF) \cite{Guidal:2013rya}, which are
+complex amplitudes defined as:
 
@@
 \end{align}
-with $H_A$ the GPDs, $\mathcal{P}$ 
+with $H_A$ the GPD, $\mathcal{P}$ 
 the Cauchy principal value integral, and $C^{+}(x,\xi)$ a coefficient function 
@@
 measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and Xe), 
-but contamination from incoherent processes could influence the measurement 
-significantly~\cite{Guzey:2003jh}. The direct detection of the recoil nucleus 
-can however guaranty that the nucleus remains intact.
+but contamination from incoherent processes could influence the
+measurement significantly \cite{Guzey:2003jh}. Accordingly, direct detection 
+of the low-energy recoil nucleus is critical in guaranteeing the nucleus 
+remains intact.
 
-The $^4$He nucleus is an ideal experimental target for nuclear DVCS, as it 
-is light enough to be detected by our experimental setting, while it is subject to 
-sizeable nuclear effects~\cite{JSeely} easily observable. Its spin-zero leads 
-to another important advantage, as the number of GPDs defined for a hadron 
-depends on its spin. The structure of a spin-zero hadron is parametrized by 
+The $^4$He nucleus is an ideal experimental target for DVCS on nuclei, as it 
+is light enough to be detected in such a setting, while it is subject to 
+significant nuclear effects~\cite{JSeely} and has a spin-0. A helium target leads to another 
+important advantage, as the number of GPDs defined for a hadron depends on its 
+spin. The structure of a spin-zero nucleus, such as $^4$He, is parametrized by 
 only one chiral even GPD ($H_{A}(x,\xi,t)$) at leading twist, while 4 GPDs 
@@
 The CEBAF large acceptance spectrometer (CLAS) in Hall-B at Jefferson Lab has been
-previously supplemented with an inner calorimeter (IC) and a solenoid magnet to
-measure DVCS observables on the nucleon
-\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}. The IC 
+previously used successfully for DVCS measurements on the nucleon
+\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.  In order
+to extend its capabilities to nuclear DVCS with a fully exclusive final state,
+we built a specialized radial time projection chamber (RTPC) for the detection
+and identification of low-energy recoiling light nuclei. 
+The experiment E08-024 took place in Hall-B at Jefferson Lab in 2009 using the 
+nearly 100\% duty factor, longitudinally polarized electron beam (83$\%$ 
+polarization) at an energy of 6.064 GeV. The data were collected over 40 days 
+using a 6 atm gaseous $^4$He target placed 64 cm upstream of the nominal center 
+of CLAS. For DVCS experiments, the CLAS 
+baseline design~\cite{Mecking:2003zu} 
+is supplemented with an inner calorimeter (IC) and a solenoid magnet. The IC 
 extends the photon detection acceptance of CLAS to polar angles as low as 
-4$^{\circ}$. The 5 T solenoid magnet acts as a guiding field for the 
-low-energy M\o{}ller electrons, that are absorbed in a  
+4$^{\circ}$. The 5 T solenoid magnet has two functions; it provides the magnetic 
+field for the momentum analysis in the RTPC, and at the same time acts as 
+the guiding field for the low-energy M\o{}ller electrons, that are absorbed in a  
 heavy shield placed around the beam line.
@@
 particles, so in order to ensure the exclusivity of the measurement, we built a 
-small and light radial time projection chamber (RTPC) to complement CLAS. The 
-RTPC is a $20$-cm-long cylinder with a diameter of $15$ cm, positioned in the 
-solenoid magnet. In the center of the RTPC is the target, a $25$-cm-long 
-and $6$-mm-diameter Kapton tube with $27$-$\mu$m-thick walls filled with 
-6~atm of gaseous $^4$He. The experiment (E08-024) collected
-data over 40 days at the end of 2009 using a 
-nearly 100\% duty factor, longitudinally polarized electron beam (83$\%$ 
-polarization) at an energy of 6.064 GeV. The RTPC was calibrated specifically 
-for the detection of $^4$He nuclei by utilizing elastic scattering 
-$e^4$He$\to e^\prime$$^4$He with a 1.2~GeV electron beam.
+small and light RTPC to complement CLAS. The RTPC is a $20$-cm-long cylinder 
+with a diameter of $15$ cm, positioned directly around the $^4$He gaseous 
+target. The target is a $25$-cm-long and $6$-mm-diameter Kapton tube with 
+$27$-$\mu$m-thick walls. The RTPC was calibrated specifically for the detection of 
+$^4$He nuclei by utilizing elastic scattering $e^4$He$\to e^\prime$$^4$He with
+a 1.2~GeV electron beam.
+
+%\begin{figure}[tb]
+%\vspace{-1.1cm}
+%\includegraphics[width=6.5cm,angle=-90]{figs/RTPC.pdf}
+%\vspace{-1.1cm}
+%\caption{Left: A picture of the E08-024 RTPC before insertion into the 
+%solenoid. Right: A cross section of the E08-024 RTPC perpendicular to the beam 
+%direction. An illustration of a $^4$He track originating from the pressurized 
+%straw target is shown along with the electrons produced in the drift region.}
+%\label{fig:RTPC}
+%\end{figure}
 
@@
 one $^4$He, and at least one photon are detected in the final state. Electrons 
-are identified using their measured momentum, light yield, time, and energy obtained from 
+are identified using their measured momentum, time, and energy obtained from 
 the CLAS drift chambers, \^{C}erenkov counters, scintillator counters, 
-and electromagnetic calorimeters, respectively. The recoiling $^4$He nuclei 
-are identified in the RTPC using time and energy-loss cuts for tracks in the 
-fiducial region~\cite{Hattawy:thesis}. In addition, we apply a vertex-matching 
+and electromagnetic calorimeters. The recoiling $^4$He nuclei are identified in 
+the RTPC using time, track quality, and energy-loss cuts for tracks in the 
+fiducial region \cite{Hattawy:thesis}. In addition, we apply a vertex-matching 
 cut to ensure that the 
@@
 The experimental data for the most relevant exclusivity observables and applied
-cuts are shown in Fig.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for 
-additional details). We also 
+cuts are shown in Fig.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for additional details).
+%The most relevant of these cuts are presented in Fig.~\ref{fig:kin-cuts}, which 
+%shows 3$\sigma$ cuts except for the missing energy (which appears to be too 
+%large and for which we reduced the cut window to [-0.45,0.5] GeV).
+We also 
 reject events where a $\pi^0$ is identified by invariant mass reconstruction of 
@@
 \begin{figure}[tb]
-\includegraphics[width=9cm]{figs/coh_exc_cuts.pdf}
+\includegraphics[width=9cm]{figs/F_all_coh_exc_cuts-pub.pdf}
 \caption{Four of the six coherent DVCS exclusivity cuts. The black 
 distributions represent the initial candidate events, while the shaded 
-distributions represent those which passed all the exclusivity cuts except 
+distributions represent those which which passed all the exclusivity cuts except 
 the quantity plotted. The vertical red lines represent the applied cuts.
@@
 \hspace{-0.45cm}
-\includegraphics[width=8.5cm]{figs/Q2_xB_t_Coh.pdf}
+\includegraphics[width=9cm]{figs/F_Q2_xB_t_Coh.pdf}
 \caption{Coherent DVCS event distributions for $Q^2$ after exclusivity cuts. 
@@
 
-We identified two main backgrounds to our measurement, accidental coincidences 
-and exclusive coherent
-$\pi^0$ production. The accidentals have particles originating from different events,
-and we estimated their contribution to be 4.1\% of our sample. We evaluated this 
-contribution by selecting events passing all our cuts but with an electron and 
-helium originating from different vertices. The $\pi^0$ production can easily
-be mistaken for DVCS when one of the two photons from the $\pi^0$ 
-decay is produced at low energy in the laboratory frame and remains undetected.  
-To estimate the effect of this contamination, we developed an event generator 
-tuned on the experimental yield of exclusive $\pi^0$ with two photons measured. 
-We used this generator together with a GEANT3 simulation of our 
-detectors to estimate the ratio of the number of $\pi^0$ events where the 
-two photons are detected to those that are misidentified as DVCS events. This 
-ratio is then multiplied by the measured yield of exclusive $\pi^0$ events to 
-correct the DVCS data. Depending on the kinematics, we found contaminations of 
-2 to 4\%.
-
 %asymmetries
 In this work, the physics observable extracted using coherent DVCS events is
-the beam-spin asymmetry, noted $A_{LU}$. On an unpolarized target, $A_{LU}$ is 
-defined as the difference of cross sections for the reaction with opposite beam 
+the beam-spin asymmetry (BSA). The BSA on an unpolarized target, $A_{LU}$, is 
+measured as the difference of cross sections for the reaction with opposite beam 
 helicities normalized to the total cross section:
@@
 extracted from the reaction yields for the two helicities ($N^{+/-}$)
+%expressed in terms of helicity-state yields ($N^{+/-}$)
 \begin{equation}
@@
 
-There is an additional process contributing to the same final state as the 
-DVCS, the so called Bethe-Heitler (BH) process, where the real photon is 
-emitted by the incoming or the outgoing lepton. The DVCS and BH processes are 
-indistinguishable experimentally and the amplitude of electroproduction of real
+The DVCS and well-known Bethe-Heitler (BH) processes, in which the real 
+photon is emitted by the incoming or the outgoing lepton, have the same final 
+state and are indistinguishable. The amplitude of electroproduction of real
 photons includes a sum of the amplitudes of these two processes. The BH 
-amplitude depends of the target form factors, while the DVCS amplitude 
-depends on GPDs. For our kinematics, the cross section of real photon 
-electroproduction is dominated by the BH contribution, while the DVCS 
-contribution is very small. However, the DVCS contribution is
+amplitude is defined by the target form factors, while the DVCS amplitude is 
+a combination of the form factors and GPDs. For our kinematics, the cross 
+section of real photon electroproduction is dominated by the BH 
+contribution, while the DVCS contribution is very small. However, the DVCS contribution is
 enhanced in the observables sensitive to the interference term, {\it e.g.} 
-$A_{LU}$. The three terms entering the cross section calculation,
+BSA. The three terms entering the cross section calculation,
 the square of the BH and DVCS amplitudes and their interference term, depend on the
@@
 as shown for the nucleon in Ref.~\cite{Belitsky:2001ns} and for the spin-zero targets
-in Refs.~\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the $A_{LU}$ 
+in Refs.~\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the BSA 
 of a spin-zero hadron can be expressed as
@@
 \end{equation}
-explicit expressions of the kinematic factors $\alpha_i$ are written in
+where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
+and real parts of the $^4$He CFF $\mathcal{H}_{A}$ and depend on the GPD $H_A$.  
+Explicit expressions of the purely kinematic factors $\alpha_i$ are written in
 Ref.~\cite{Belitsky:2008bz} and are functions of Fourier harmonics in the 
@@
 
-We present in Fig.~\ref{fig:alu} $A_{LU}$ as a function of azimuthal angle 
-$\phi$ and the kinematical variables $Q^2$, $x_B$, and $t$. Due to our limited 
-statistics, the latter are studied separately with independent binning. The curves on 
-the plots are fits using the function presented in Eq.~(\ref{eq:A_LU-coh}), 
-where the real and imaginary parts of the CFF $\mathcal{H}_{A}$ are the only 
-free parameters.
+In this work, the azimuthal dependence of the beam-spin asymmetry has been studied 
+for a wide range of kinematics ($Q^2$ between 1 and 2.2 GeV$^2$/c$^2$, $x_B$ between
+0.1 and 0.3, and $-t$ between 0.07 and 0.16 GeV$^2$/c$^2$). We identified two main
+backgrounds to our measurement, accidental coincidences and exclusive coherent
+$\pi^0$ production.  The accidentals have particles originating from different events,
+and we estimated their contribution to be 4.1\% of our sample. We evaluated this 
+contribution by selecting events passing all our cuts but with an electron and 
+helium originating from different vertices. The $\pi^0$ production can easily
+be mistaken for DVCS when one of the two photons from the $\pi^0$ 
+decay is produced at low energy in the laboratory frame and remains undetected.  
+To estimate the effect of this background, we developed an event generator 
+tuned on the experimental yield of exclusive $\pi^0$ measured by our 
+experiment. We used this generator together with a GEANT3 simulation of our 
+detector to estimate the ratio of the number of $\pi^0$ events where the 
+two photons are detected to those that are misidentified as DVCS events. This 
+ratio is then multiplied by the measured yield of exclusive $\pi^0$ events to 
+correct the DVCS data.  Depending on the kinematics, we found contaminations of 
+2 to 4\%. Studies of systematic uncertainties showed that the main contributions 
+come from the choice of DVCS exclusivity cuts (8\% systematic uncertainty) and the 
+large binning size (5.1\%), where the values are relative and quoted for $A_{LU}$
+at $\phi=90^\circ$.  Added quadratically, the total systematic uncertainty
+is about 10\% at $90^\circ$ (or 0.03, absolute), which is significantly smaller
+than the statistical uncertainties in all kinematical bins.
+
+Due to limited statistics, dependence of the extracted asymmetries on the kinematical variables $Q^2$, 
+$x_B$, and $t$ has been studied separately. In Fig.~\ref{fig:alu}, $A_{LU}$ for 
+bins in each of the three variables is presented. The curves on the plots are fits with 
+the function presented in Eq.~(\ref{eq:A_LU-coh}), where the real and imaginary 
+parts of the CFF $\mathcal{H}_{A}$ are the free parameters of the fit.  In 
+Fig.~\ref{fig:alu90} the $Q^2$, $x_{B}$, and $t$-dependencies of the fitted 
+$A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and $t$-dependencies 
+are compared to theoretical calculations by S.~Liuti and K.~Taneja 
+\cite{simonetta_2}. The model accounts for the effect on the quark 
+distribution of the virtuality (off-shellness) of the nucleon. The calculations are at slightly 
+different kinematics than our data but still allow drawing some conclusions. The 
+experimental results appear to have a larger asymmetries than the calculations. 
+The difference may arise from the theoretical uncertainty in the determination 
+of the crossing point where the parton nuclear distribution becomes larger than the 
+nucleon one, and reverses the sign of the nuclear effect.
 
 \begin{figure}[tb]
-\includegraphics[width=8cm]{figs/coherent-ALU.pdf}
+\includegraphics[width=9cm]{figs/F_Coherent_ALU_phi.pdf}
 \caption{The coherent $A_{LU}$ as a function of azimuthal angle $\phi$. Results are presented
@@
    bins (bottom panel).  The error bars represent the statistical 
-   uncertainties. The grey bands represent the systematic uncertainties, 
+   uncertainties. The gray bands represent the systematic uncertainties, 
    including the normalisation uncertainties. The red curves are the results of 
@@
 
-Studies of systematic uncertainties showed that the main contributions 
-come from the choice of DVCS exclusivity cuts (8\% systematic uncertainty) and the 
-large binning size (5.1\%). The values are relative and quoted for $A_{LU}$
-at $\phi=90^\circ$. Added quadratically, the total systematic uncertainty
-is about 10\% at $90^\circ$ (or 0.03, in absolute), which is significantly smaller
-than the statistical uncertainties in all kinematical bins.
-
-In Fig.~\ref{fig:alu90}, the $Q^2$, $x_{B}$, and $t$-dependencies of the fitted 
-$A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and $t$-dependencies 
-are compared to theoretical calculations by S.~Liuti and K.~Taneja 
-\cite{simonetta_2}. The model accounts for the effect on the quark distribution 
-of the virtuality (off-shellness) of the nucleon. The calculations are at slightly 
-different kinematics than our data but still allow drawing some conclusions. The 
-calculations appear to have smaller asymmetries than observed. 
-The difference may arise from the theoretical uncertainty in the determination 
-of the crossing point where the parton nuclear distribution becomes larger than the 
-nucleon one, and reverses the sign of the nuclear effect.
-
 \begin{figure*}[tb]
-\includegraphics[width=17cm]{figs/coherent-ALU_90_2.pdf}
+\includegraphics[width=17cm]{figs/F_Coherent_ALU_phi_90.pdf}
 \caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $t$-dependencies (right) of
@@
    calculations from \cite{simonetta_2}. On the right: the green circles are 
-   the HERMES $-A_{LU}$ (a positron beam was used) inclusive measurements 
-   \cite{Airapetian}, the curves represent the theoretical calculations 
+   the HERMES $-A_{LU}$ (positron beam was used) inclusive measurements 
+   \cite{Airapetian}, the colored curves represent theoretical calculations 
    from \cite{simonetta_2}.}
@@
 \begin{figure}[tb]
-\includegraphics[width=8cm]{figs/Coherent_CFF.pdf}
+\includegraphics[width=8.5cm]{figs/F_Coherent_CFF.pdf}
 \caption{The model-independent extraction of the imaginary (top panel) and
 real (bottom panel) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of
-$Q^{2}$ (left panel), $x_B$ (middle panel), and $t$ (right panel). The full red 
-curves are the calculations based on the convolution model from Ref.~\cite{Vadim_priv}.
-The black-dashed curves are calculations from the same 
-model using different GPDs for the nucleons (VGG model~\cite{Guidal_priv}). The 
+$Q^{2}$ (right panel), $x_B$ (middle panel), and $t$ (left panel). The full red 
+curves are calculations based on an on-shell model from Ref.~\cite{Vadim_priv}.
+The black-dashed curves are calculations from a convolution 
+model based on the VGG model for the nucleons' GPDs \cite{Guidal_priv}. The 
 blue long-dashed curve on the top-right plot is from
-the off-shell model as described in Ref.~\cite{GonzalezHernandez:2012jv}.}
+an off-shell model as described in Ref.~\cite{GonzalezHernandez:2012jv}.}
 \label{fig:CFF_HA}
@@
 The results in Fig.~\ref{fig:CFF_HA} show that the extraction of the CFF
-from the $A_{LU}$ is possible without model dependent assumptions beyond
-leading-twist and leading-order dominance. The amplitude and the dependencies 
-observed as a function of 
+from the BSA is possible without any model dependent 
+assumptions. The amplitude and the dependencies observed as a function of 
 $Q^{2}$, $x_B$, and $t$ are in agreement with the theoretical expectations. One 
@@
 these results demonstrate the possibility of extracting the CFF of a spin 0 
-target directly from a $A_{LU}$ measurement.
+target in a model independent way directly from a BSA measurement.
 
 %conclusion
-In summary, we have presented the first measurement of the beam-spin asymmetry
-of exclusive coherent DVCS off $^4$He using the CLAS spectrometer supplemented 
-with a RTPC. This setup allowed detection of the 
+In summary, we present the first exclusive measurement of coherent DVCS off 
+$^4$He using the CLAS spectrometer supplemented with a Radial Time Projection 
+Chamber and a high pressure gaseous target. This setup allowed detection of the 
 low energy $^4$He recoils in order to ensure an exclusive measurement of the
-coherent DVCS process. The azimuthal dependence of the measured $A_{LU}$ has 
+coherent DVCS process.
+The azimuthal dependence of the measured BSA ($A_{LU}$) has 
 been used to extract, in a model independent way, the real and the imaginary 
@@
 
-\bibitem{Joerg:2016hhs} 
-  P.~Joerg [COMPASS Collaboration],
-  %``The $t$-dependence of the pure DVCS cross-section at COMPASS,''
-  PoS DIS {\bf 2016}, 235 (2016).
-
 \bibitem{Goeke:2001tz}

### 2017-05-11 eg6-letters/coherent/dvcs_he4_prl.tex

--- 2017-05-10 eg6-letters/coherent/dvcs_he4_prl.tex
@@
 \begin{figure}[tb]
-\includegraphics[width=9cm]{figs/coh_exc_cuts.pdf}
+\includegraphics[width=9cm]{figs/F_all_coh_exc_cuts-pub.pdf}
 \caption{Four of the six coherent DVCS exclusivity cuts. The black 
@@
 \hspace{-0.45cm}
-\includegraphics[width=8.5cm]{figs/Q2_xB_t_Coh.pdf}
-\caption{Coherent DVCS event distributions for $Q^2$ after the exclusivity cuts. 
-The distributions are shown as a function of Bjorken $x_B$ (left) 
-and as a function of the squared-momentum transfer $-t$ (right).}
+\includegraphics[width=9cm]{figs/F_Q2_xB_t_Coh.pdf}
+\caption{Coherent DVCS event distributions for $Q^2$ after exclusivity cuts. 
+The distributions are shown as a function of Bjorken variable $x_B$ (left) 
+and as a function of squared-momentum transfer $-t$ (right).}
 \label{fig:kin-coverage}
@@
 \begin{figure}[tb]
-\includegraphics[width=8cm]{figs/coherent-ALU.pdf}
+\includegraphics[width=9cm]{figs/F_Coherent_ALU_phi.pdf}
 \caption{The coherent $A_{LU}$ as a function of azimuthal angle $\phi$. Results are presented
@@
 \begin{figure*}[tb]
-\includegraphics[width=17cm]{figs/coherent-ALU_90_2.pdf}
+\includegraphics[width=17cm]{figs/F_Coherent_ALU_phi_90.pdf}
 \caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $t$-dependencies (right) of
@@
 \begin{figure}[tb]
-\includegraphics[width=8cm]{figs/Coherent_CFF.pdf}
+\includegraphics[width=8.5cm]{figs/F_Coherent_CFF.pdf}
 \caption{The model-independent extraction of the imaginary (top panel) and

### 2017-05-11 eg6-letters/coherent/dvcs_he4_prl.tex
Comments from SS

@@
 exclusive process of coherent deeply virtual 
-Compton scattering off a nucleus for $A>1$. The experiment used the 6 GeV 
+Compton scattering off a nucleus. The experiment used the 6 GeV 
 electron beam from the CEBAF accelerator at Jefferson Lab incident on a 
@@
 are compared to theoretical calculations by S.~Liuti and K.~Taneja 
-\cite{simonetta_2}. The model accounts for the effect on the quark distribution 
-of the virtuality (off-shellness) of the nucleon. The calculations are at slightly 
+\cite{simonetta_2}. The model accounts for the effect of the nucleon virtuality 
+(off-shellness) on the quark distribution. The calculations are at slightly 
 different kinematics than our data but still allow drawing some conclusions. The 

### 2017-05-11 eg6-letters/coherent/dvcs_he4_prl.tex
update the coherent alu plot vs phi
Polishing the text

@@
 \begin{abstract}
-We report on the first measurement of the beam-spin asymmetry in the 
-exclusive process of coherent deeply virtual 
-Compton scattering off a nucleus. The experiment used the 6 GeV 
-electron beam from the CEBAF accelerator at Jefferson Lab incident on a 
-$^4$He gas target in front of the CEBAF Large Acceptance Spectrometer 
-(CLAS). While the electron was detected by CLAS and the gamma by a dedicated
-electromagnetic calorimeter at forward angles, a specially designed radial 
-time projection chamber was used to detect the recoiling $^4$He
-nuclei and to ensure the exclusivity of the process. The measured beam-spin 
-asymmetries are larger than those observed on the free proton in the same kinematic 
-domain. Since $^4$He is a spin-zero target, we were able to extract, in a 
-model-independent way, the real and imaginary parts of its unique 
-Compton form factor, $\cal H_A$. This pioneering measurement of coherent deeply virtual 
-Compton scattering on the $^4$He nucleus, with a fully exclusive final state 
-via nuclear recoil tagging, leads the way toward 3D imaging of the partonic 
-structure of nuclei.
+We report on the first measurement of the beam-spin asymmetry in the exclusive 
+process of coherent deeply virtual Compton scattering off a nucleus. The 
+experiment used the 6 GeV electron beam from the CEBAF accelerator at Jefferson 
+Lab incident on a $^4$He gas target in front of the CEBAF large acceptance 
+spectrometer (CLAS). The scattered electron was detected by CLAS and the gamma 
+by a dedicated electromagnetic calorimeter at forward angles. To ensure the 
+exclusivity of the process, a specially designed radial time projection chamber 
+was used to detect the recoiling $^4$He nuclei. We measured beam-spin 
+asymmetries larger than those observed on the free proton in the same kinematic 
+domain. From these, we were able to extract, in a model-independent way, the 
+real and imaginary parts of the $^4$He unique Compton form factor, $\cal H_A$. 
+This pioneering measurement of coherent deeply virtual Compton scattering on 
+the $^4$He nucleus, with a fully exclusive final state via nuclear recoil 
+tagging, leads the way toward 3D imaging of the partonic structure of nuclei.
 \end{abstract}
@@
 obtain information about the momentum and spatial degrees of freedom of the 
-quarks and gluons inside hadrons 
-\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.
-In impact parameter space the GPDs are indeed interpreted as a tomography of 
-the transverse plane for partons carrying a given fraction of the proton 
-longitudinal momentum 
-\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep,Burkardt:2005hp}. 
-The most promising way to access GPDs experimentally is through the measurement 
-of deeply virtual Compton scattering (DVCS), \textit{i.e.}, the hard exclusive 
-electroproduction of a real photon on a hadron. While other processes are known to be 
-sensitive to GPDs, the measurement of DVCS is considered the cleanest probe and 
-has been the focus of efforts at Jefferson Lab, HERA, and CERN
-\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
-Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,
-Jo:2015ema,Joerg:2016hhs}.  
-The vast majority of these measurements focused on the study of proton 
-structure and allowed for an extraction of the three-dimensional image of the 
-proton (for reviews of the field, see~\cite{Goeke:2001tz,Diehl:2003ny,
-Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
-This framework is also applicable to nuclei, giving access to novel 
-information about nuclear structure in terms of quarks and 
-gluons (see~\cite{Dupre:2015jha} and references therein).
-Study of the 3D structure of nuclei appears to be especially important
-in light of the large nuclear effects observed in nuclear parton distribution 
-functions~\cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.
+quarks and gluons inside hadrons \cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,
+Radyushkin:1996nd,Radyushkin:1997ki}. In impact parameter space the GPDs are 
+indeed interpreted as a tomography of the transverse plane for partons 
+carrying a given fraction of the proton longitudinal momentum 
+\cite{Burkardt:2000za,Diehl:2002he,Belitsky:2002ep,Burkardt:2005hp}. The most 
+promising way to access GPDs experimentally is through the measurement of 
+deeply virtual Compton scattering (DVCS), \textit{i.e.}, the hard exclusive 
+electroproduction of a real photon on a hadron. While other processes are known 
+to be sensitive to GPDs, the measurement of DVCS is considered the cleanest 
+probe and has been the focus of efforts at Jefferson Lab, HERA, and CERN 
+\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,
+MunozCamacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,
+Pisano:2015,Jo:2015ema,Joerg:2016hhs}. The vast majority of these measurements 
+focused on the study of the proton and allowed for an extraction of its 
+three-dimensional image (for reviews of the field, see~\cite{Goeke:2001tz,
+Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}). This 
+recent progress could also be applicable to nuclei, giving access to novel 
+information about nuclear structure in terms of quarks and gluons 
+(see~\cite{Dupre:2015jha} and references therein). Such a study of the 3D 
+structure of nuclei appears to be especially interesting in light of the large, 
+yet unresolved, nuclear effects observed in nuclear parton distribution 
+functions~\cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}. The results 
+presented in this letter demonstrate the feasability of such an approach and 
+constitute a first step toward a tomography of nuclei.
 
@@
 $M_N$ is the nucleon mass. The parameter $x$ is the quark's internal loop momentum 
-fraction and cannot be accessed experimentally. We in fact measure 
+fraction and cannot be accessed experimentally in DVCS. We in fact measure 
 Compton form factors (CFF), which are complex quantities defined as:
@@
 
-The $^4$He nucleus is an ideal experimental target for nuclear DVCS, as it 
-is light enough to be detected by our experimental setting, while it is subject to 
-sizeable nuclear effects~\cite{JSeely} easily observable. Its spin-zero leads 
-to another important advantage, as the number of GPDs defined for a hadron 
-depends on its spin. The structure of a spin-zero hadron is parametrized by 
-only one chiral even GPD ($H_{A}(x,\xi,t)$) at leading twist, while 4 GPDs 
-arise in the nucleon case. This significantly simplifies the interpretation of 
-the data and allows a model independent extraction of the $^4$He CFF 
+The $^4$He nucleus is an ideal experimental target for nuclear DVCS, as it is 
+light enough to be detected by our experimental setting, while it is subject 
+to interesting nuclear effects~\cite{JSeely}. Its spin-zero also leads to an 
+important simplification, as a spin-zero hadron is parametrized by only one 
+chiral even GPD ($H_{A}(x,\xi,t)$) at leading twist, while four GPDs arise for 
+the spin-half nucleon. This significantly simplifies the interpretation of the 
+data and allows a model independent extraction of the $^4$He CFF 
 ($\mathcal{H}_{A}$) presented at the end of this letter.
 
-The CEBAF Large Acceptance Spectrometer (CLAS) in Hall B at Jefferson Lab ~\cite{Mecking:2003zu} has been
-previously supplemented with an inner calorimeter (IC) and a solenoid magnet to
-measure DVCS observables on the nucleon
+The CEBAF large acceptance spectrometer (CLAS) in Hall B at Jefferson 
+Lab~\cite{Mecking:2003zu} has been previously supplemented with an inner 
+calorimeter (IC) and a solenoid magnet to measure DVCS observables on the nucleon
 \cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}. The IC 
 extended the photon detection acceptance of CLAS to polar angles as low as 
-4$^{\circ}$. The 5 T solenoid magnet acted as a guiding field for the 
+4$^{\circ}$. The 5~T solenoid magnet acted as a guiding field for the 
 low-energy M\o{}ller electrons that were absorbed in a  
@@
 In our kinematics, the recoil $^4$He nuclei produced in DVCS have low momentum,
-averaging 300 MeV/c. CLAS could not detect such low-energy $\alpha$ 
+averaging 300 MeV. CLAS could not detect such low-energy $\alpha$ 
 particles, so in order to ensure the exclusivity of the measurement, we built a 
@@
 polarization) at an energy of 6.064 GeV. The RTPC was calibrated specifically 
-for the detection of $^4$He nuclei by utilizing elastic scattering 
-$e^4$He$\to e^\prime$$^4$He with a 1.2~GeV electron beam.
+for the detection of $^4$He nuclei using elastic scattering 
+($e^4$He$\to e^\prime$$^4$He) with a 1.2~GeV electron beam.
 
@@
 To ensure the interaction occurred at the partonic level and that the DVCS handbag 
-diagram was dominant, we selected events with $Q^{2}$ greater than 1 
-GeV$^{2}/$c$^{2}$. Exclusivity of the coherent DVCS reaction was optimized by 
+diagram was dominant, we selected events with $Q^{2}$ greater than 
+1~GeV$^{2}$. Exclusivity of the coherent DVCS reaction was optimized by 
 applying a set of cuts on the following kinematic variables: the coplanarity 
@@
 rejected events where a $\pi^0$ was identified by the invariant mass reconstruction of 
-two photons. About 3200 events passed these requirements, and their kinematic 
+two photons. About 3200 events passed all these requirements, their kinematic 
 distributions are shown in Fig.~\ref{fig:kin-coverage}.
@@
 \begin{figure*}[tb]
-\includegraphics[width=17cm]{figs/F_Coherent_ALU_phi_90.pdf}
+\includegraphics[width=16cm]{figs/F_Coherent_ALU_phi_90.pdf}
 \caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $t$-dependencies (right) of
@@
 
-\bibitem{Munoz Camacho:2006hx} 
+\bibitem{MunozCamacho:2006hx} 
 %C. Mu\~noz Camacho {\it et al.} [Jefferson Lab Hall A Collaboration],

### 2017-05-13 eg6-letters/coherent/dvcs_he4_prl.tex
Remarks from EV, MG and MD added.

@@
 experiment used the 6 GeV electron beam from the CEBAF accelerator at Jefferson 
-Lab incident on a $^4$He gas target in front of the CEBAF large acceptance 
-spectrometer (CLAS). The scattered electron was detected by CLAS and the gamma 
+Lab incident on a pressured $^4$He gaseous target in front of the CEBAF large acceptance 
+spectrometer (CLAS). The scattered electron was detected by CLAS and the photon 
 by a dedicated electromagnetic calorimeter at forward angles. To ensure the 
@@
 domain. From these, we were able to extract, in a model-independent way, the 
-real and imaginary parts of the $^4$He unique Compton form factor, $\cal H_A$. 
+real and imaginary parts of the $^4$He only Compton form factor, $\cal H_A$. 
 This pioneering measurement of coherent deeply virtual Compton scattering on 
@@
 probe and has been the focus of efforts at Jefferson Lab, HERA, and CERN 
-\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,
-MunozCamacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,
+\cite{Stepanyan:2001sm,Airapetian,Airapetian:2010nu,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,
+MunozCamacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Defurne:2015kxq,
 Pisano:2015,Jo:2015ema,Joerg:2016hhs}. The vast majority of these measurements 
@@
 presented in this letter demonstrate the feasability of such an approach and 
-constitute a first step toward a tomography of nuclei.
+constitute the first step toward a tomography of nuclei.
 
@@
 \end{align}
-with $H_A$ the GPDs, $\mathcal{P}$ 
+with $H_A$ a GPD, $\mathcal{P}$ 
 the Cauchy principal value integral, and $C^{+}(x,\xi)$ a coefficient function 
@@
 Until now, the only available data on nuclear DVCS was from the HERMES 
-experiment \cite{Ellinghaus:2002zw}, where coherence in the reaction was based 
-only on kinematic cuts on the measured scattered electron and real photon. The 
-measurement was performed on a large set of nuclei ($^4$He, $^{14}$N, $^{20}$Ne, $^{85}$Kr and $^{131}$Xe), 
+experiment \cite{Airapetian:2010nu}. In this experiment, the exclusivity of 
+the reaction was obtained through kinematic cuts using only the measured 
+scattered electron and real photon. The measurement was performed on a large 
+set of nuclei ($^4$He, $^{14}$N, $^{20}$Ne, $^{85}$Kr and $^{131}$Xe), 
 but contamination from incoherent processes could influence the measurement 
@@
 
-In our kinematics, the recoil $^4$He nuclei produced in DVCS have low momentum,
-averaging 300 MeV. CLAS could not detect such low-energy $\alpha$ 
+In the kinematic range of the present experiment, the recoil $^4$He nuclei 
+have low momentum, averaging 300 MeV. CLAS could not detect such low-energy $\alpha$ 
 particles, so in order to ensure the exclusivity of the measurement, we built a 
-small and light radial time projection chamber (RTPC) to complement CLAS. The 
+small and light radial time projection chamber (RTPC). The 
 RTPC was a $20$-cm-long cylinder with a diameter of $15$ cm, positioned in the 
@@
 and $6$-mm-diameter Kapton tube with $27$-$\mu$m-thick walls filled with 
-6~atm of gaseous $^4$He. The experiment (E08-024) collected
+gaseous $^4$He at 6~atm. The experiment (E08-024)~\cite{Hafidi:2008pr} collected
 data over 40 days at the end of 2009 using a 
-nearly 100\% duty factor, longitudinally polarized electron beam (83$\%$ 
-polarization) at an energy of 6.064 GeV. The RTPC was calibrated specifically 
+nearly 100\% duty factor, longitudinally polarized electron beam (83.7$\pm 3.5 \%$ 
+polarization~\cite{Perrin:thesis}) at an energy of 6.064 GeV. The RTPC was calibrated specifically 
 for the detection of $^4$He nuclei using elastic scattering 
@@
 were identified using their measured momentum, light yield, time, and energy obtained from 
-the CLAS drift chambers, \^{C}erenkov counters, scintillator counters, 
+the CLAS drift chambers, \v{C}erenkov counters, scintillator counters, 
 and electromagnetic calorimeters, respectively. The recoiling $^4$He nuclei 
@@
 were caused by accidental coincidences of soft photons and did not affect 
-directly our measurement. We consider only the most energetic photon of an 
-event as a DVCS photon candidate.
+directly the measurement as only the most energetic photon of an 
+event was considered a DVCS photon candidate.
 This prescription however slightly increased the corrections associated with
@@
 \begin{figure}[tb]
+\centering
+\hspace{-0.45cm}
 \includegraphics[width=9cm]{figs/F_all_coh_exc_cuts-pub.pdf}
@@
 
-We identified two main backgrounds to our measurement, accidental coincidences 
-and exclusive coherent
+We identified two main backgrounds, accidental coincidences and exclusive coherent
 $\pi^0$ production. The accidentals have particles originating from different events,
 and we estimated their contribution to be 4.1\% of our sample. We evaluated this 
-contribution by selecting events passing all our cuts but with the scattered electron and 
+contribution by selecting events passing all the cuts but with the scattered electron and 
 $^4$He originating from different vertices. The $\pi^0$ production can easily
@@
   \end{equation}
-where $d^{5}\sigma^{+(-)}$ is the DVCS differential cross 
+where $d^{5}\sigma^{\pm}$ is the DVCS differential cross 
 section for positive (negative) beam helicity. 
@@
 detector efficiencies largely cancel and $A_{LU}$ can be 
-extracted from the reaction yields for the two helicities ($N^{+/-}$)
+extracted from the reaction yields for the two helicities ($N^{\pm}$)
 \begin{equation}
@@
 photons includes a sum of the amplitudes of these two processes. The BH 
-amplitude depends of the target form factors, while the DVCS amplitude 
-depends on GPDs. For our kinematics, the cross section of real photon 
+amplitude depends on the target form factors, which are well known in this
+kinematic region, while the DVCS amplitude depends on the GPDs we are trying to
+measure. For our kinematics, the cross section of real photon 
 electroproduction is dominated by the BH contribution, while the DVCS 
@@
 \end{equation}
-explicit expressions of the kinematic factors $\alpha_i$ are written in
+explicit expressions of the kinematic factors $\alpha_i$ are derived in
 Ref.~\cite{Belitsky:2008bz} and are functions of Fourier harmonics in the 
-azimuthal angle $\phi$, the nuclear form factor $F_A(t)$, $Q^2$, $x_B$,
-$x_{A} = \frac{x_{B}M_{N}}{M_{A}}$, $y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, and 
-$\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$, where $M_{A}$($M_{N}$) is the $^4$He 
-(nucleon) mass. Using the different $\sin(\phi)$ and $\cos(\phi)$ contributions, 
+azimuthal angle $\phi$, the nuclear form factor $F_A(t)$ and kinematical
+factors. Using the different $\sin(\phi)$ and $\cos(\phi)$ contributions, 
 both the imaginary and real parts of $\mathcal{H}_{A}$ can be extracted unambiguously
@@
 We present in Fig.~\ref{fig:alu} $A_{LU}$ as a function of azimuthal angle 
-$\phi$ and the kinematical variables $Q^2$, $x_B$, and $t$. Due to our limited 
-statistics, the latter are studied separately with independent binning. The curves on 
+$\phi$ and the kinematical variables $Q^2$, $x_B$, and $t$. Due to limited 
+statistics, these latter variables are studied separately with independent 
+binning. The curves on 
 the plots are fits using the function presented in Eq.~(\ref{eq:A_LU-coh}), 
@@
 \begin{figure}[tb]
-\includegraphics[width=9cm]{figs/F_Coherent_ALU_phi.pdf}
-\caption{The coherent $A_{LU}$ as a function of azimuthal angle $\phi$. Results are presented
+   \centering
+\includegraphics[width=8.5cm]{figs/F_Coherent_ALU_phi.pdf}
+\caption{$A_{LU}$ as a function of azimuthal angle $\phi$. Results are presented
    for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle panel), and $t$ 
@@
    including the normalisation uncertainties. The red curves are the results of 
-our fits with the form of equation Eq.~(\ref{eq:A_LU-coh}).}
+   fits with Eq.~(\ref{eq:A_LU-coh}).}
 \label{fig:alu}
@@
 is about 10\% at $90^\circ$ (or 0.03, in absolute), which is significantly smaller
-than the statistical uncertainties in all kinematical bins.
+than the statistical uncertainties at all kinematical bins.
 
 In Fig.~\ref{fig:alu90}, the $Q^2$, $x_{B}$, and $t$-dependencies of the fitted 
-$A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and $t$-dependencies 
-are compared to theoretical calculations by S.~Liuti and K.~Taneja 
+$A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The comparison to HERMES data
+shows that we obtain the same sign, but the size of the error bars and the difference
+of kinematics do not permit to say much more. The $x_{B}$ and $t$-dependencies 
+are also compared to theoretical calculations by S.~Liuti and K.~Taneja 
 \cite{simonetta_2}. The model accounts for the effect of the nucleon virtuality 
@@
    the HERMES $-A_{LU}$ (a positron beam was used) inclusive measurements 
-   \cite{Airapetian}, and the curves represent the theoretical calculations 
-   from \cite{simonetta_2}.}
+   \cite{Airapetian}, and the curves are the theoretical calculations 
+   from \cite{simonetta_2}. The grey bands represent the systematic errors.}
 \label{fig:alu90}
@@
 can see a difference between the precision of the extracted imaginary and real 
-parts, which is expected because of Eq.~(\ref{eq:A_LU-coh}) where 
+parts, which is built in Eq.~(\ref{eq:A_LU-coh}) where 
 $\alpha_2$ is much smaller than $\alpha_1$. While the precision of this 
@@
 \bibitem{Stepanyan:2001sm}
-%S.~Stepanyan {\it et al.} [CLAS Collaboration],
-S.~Stepanyan {\it et al.},
+S.~Stepanyan {\it et al.} [CLAS Collaboration],
 Phys.\ Rev.\ Lett. {\bf 87}, 182002 (2001).
@@
 \bibitem{Airapetian}
-%A. Airapetian {\it et al.} [HERMES Collaboration],
-A. Airapetian {\it et al.},
+A. Airapetian {\it et al.} [HERMES Collaboration],
 Phys.\ Rev.\ Lett. {\bf 87}, 182001 (2001);
+Phys.\ Rev.\  D {\bf 75}, 011103 (2007);
+JHEP {\bf 0806}, 066 (2008);
+JHEP {\bf 0911}, 083 (2009);
+JHEP {\bf 1006}, 019 (2010);
+Phys.\ Lett.\ B {\bf 704}, 15 (2011);
 JHEP {\bf 1207}, 032 (2012);
-JHEP {\bf 1006}, 019 (2010);
-JHEP {\bf 0806}, 066 (2008);
-Phys.\ Lett.\ B {\bf 704}, 15 (2011);
-Phys.\ Rev.\  D {\bf 75}, 011103 (2007);
-JHEP {\bf 0911}, 083 (2009);
-Phys.\ Rev.\ C {\bf 81}, 035202 (2010);
 JHEP {\bf 1210}, 042 (2012).
 
+\bibitem{Airapetian:2010nu}
+A. Airapetian {\it et al.} [HERMES Collaboration],
+Phys.\ Rev.\ C {\bf 81}, 035202 (2010).
+
 \bibitem{Chekanov:2003ya}
-%S. Chekanov {\it et al.} [ZEUS Collaboration],
-S. Chekanov {\it et al.},
+S. Chekanov {\it et al.} [ZEUS Collaboration],
 Phys.\ Lett.\  B {\bf 573}, 46 (2003).
@@
 \bibitem{Aktas:2005ty}
-%A. Aktas {\it et al.} [H1 Collaboration],
-A. Aktas {\it et al.},
+A. Aktas {\it et al.} [H1 Collaboration],
 Eur.\ Phys.\ J.\ C {\bf 44}, 1 (2005).
@@
 \bibitem{Chen:2006na} 
-%S.~Chen {\it et al.} [CLAS Collaboration],
-S.~Chen {\it et al.},
+S.~Chen {\it et al.} [CLAS Collaboration],
 Phys.\ Rev.\ Lett.\ {\bf 97}, 072002 (2006).
@@
 \bibitem{MunozCamacho:2006hx} 
-%C. Mu\~noz Camacho {\it et al.} [Jefferson Lab Hall A Collaboration],
-C. Mu\~noz Camacho {\it et al.},
+C. Mu\~noz Camacho {\it et al.} [Jefferson Lab Hall A Collaboration],
 Phys.\ Rev.\ Lett. {\bf 97}, 262002 (2006).
@@
 \bibitem{Girod:2007aa} 
-%F.X. Girod {\it et al.} [CLAS Collaboration],
-F.X. Girod {\it et al.},
+F.X. Girod {\it et al.} [CLAS Collaboration],
 Phys.\ Rev.\ Lett. {\bf 100}, 162002 (2008).
@@
 \bibitem{Mazouz:2007aa} 
-%   M.~Mazouz {\it et al.} [Jefferson Lab Hall A Collaboration],
-   M.~Mazouz {\it et al.},
+   M.~Mazouz {\it et al.} [Jefferson Lab Hall A Collaboration],
    Phys.\ Rev.\ Lett.\  {\bf 99}, 242501 (2007)
@@
 \bibitem{Gavalian:2009} 
-%G. Gavalian {\it et al.} [CLAS Collaboration],
-G. Gavalian {\it et al.},
+G. Gavalian {\it et al.} [CLAS Collaboration],
 Phys.\ Rev.\ C {\bf 80}, 035206 (2009).
@@
 \bibitem{Seder:2015} 
-%E. Seder {\it et al.} [CLAS Collaboration],
-E. Seder {\it et al.},
+E. Seder {\it et al.} [CLAS Collaboration],
 Phys.\ Rev.\ Lett. {\bf 114}, 032001 (2015).
 
+\bibitem{Defurne:2015kxq} 
+  M.~Defurne {\it et al.} [Jefferson Lab Hall A Collaboration],
+  Phys.\ Rev.\ C {\bf 92}, no. 5, 055202 (2015).
+
 \bibitem{Pisano:2015} 
-%S.~Pisano {\it et al.} [CLAS Collaboration],
-S.~Pisano {\it et al.},
+S.~Pisano {\it et al.} [CLAS Collaboration],
 Phys.\ Rev.\ D {\bf 91}, 052014 (2015).
@@
 \bibitem{Jo:2015ema}
-%H.~S.~Jo {\it et al.} [CLAS Collaboration],
-H.~S.~Jo {\it et al.},
+H.~S.~Jo {\it et al.} [CLAS Collaboration],
   Phys.\ Rev.\ Lett.\  {\bf 115}, no. 21, 212003 (2015)
@@
   P.~Joerg [COMPASS Collaboration],
-  %``The $t$-dependence of the pure DVCS cross-section at COMPASS,''
   PoS DIS {\bf 2016}, 235 (2016).
@@
 
-\bibitem{Ellinghaus:2002zw}
-%F.~Ellinghaus {\it et al.} [HERMES Collaboration],
-F.~Ellinghaus {\it et al.},
-AIP Conf.\ Proc.\  {\bf 675}, 303 (2003)
-
 \bibitem{Guzey:2003jh} 
@@
 \bibitem{Mecking:2003zu} 
-%B.~A.~Mecking {\it et al.} [CLAS Collaboration],
-   B.~A.~Mecking {\it et al.},
+B.~A.~Mecking {\it et al.} [CLAS Collaboration],
    Nucl.\ Instrum.\ Meth.\ A {\bf 503}, 513 (2003).
 
+\bibitem{Hafidi:2008pr} 
+   K.~Hafidi {\it et al.},
+   Proposal PR-08-024 to JLab PAC33.
+
+\bibitem{Perrin:thesis}
+Y.~Perrin, Ph.D. thesis (2012), Universit{\'e} de Grenoble, France
+[Institution Report No. 2012GRENY092].
+
 \bibitem{Hattawy:thesis}
-M.~Hattawy, Ph.D. thesis, Universit{\'e} Paris Sud - Paris XI, France 
+M.~Hattawy, Ph.D. thesis (2015), Universit{\'e} Paris Sud - Paris XI, France 
 [Institution Report No. 2015PA112161].
@@
 Phys.\ Rev.\ D {\bf 79}, 014017 (2009)
-
-%\bibitem{eg6_note}
-%M. Hattawy {\it et al.} (CLAS-EG6 Working Group), CLAS internal analysis note, 
-%2016.
 

### 2017-05-13 eg6-letters/coherent/dvcs_he4_prl.tex
dvcs_he4_prl.tex:  minor updates

@@
 experiment used the 6 GeV electron beam from the CEBAF accelerator at Jefferson 
-Lab incident on a pressured $^4$He gaseous target in front of the CEBAF large acceptance 
+Lab incident on a pressurized $^4$He gaseous target in front of the CEBAF large acceptance 
 spectrometer (CLAS). The scattered electron was detected by CLAS and the photon 
@@
 domain. From these, we were able to extract, in a model-independent way, the 
-real and imaginary parts of the $^4$He only Compton form factor, $\cal H_A$. 
+real and imaginary parts of the only $^4$He Compton form factor, $\cal H_A$. 
 This pioneering measurement of coherent deeply virtual Compton scattering on 
@@
 light enough to be detected by our experimental setting, while it is subject 
-to interesting nuclear effects~\cite{JSeely}. Its spin-zero also leads to an 
+to interesting nuclear effects~\cite{JSeely}. Its zero spin also leads to an 
 important simplification, as a spin-zero hadron is parametrized by only one 
 chiral even GPD ($H_{A}(x,\xi,t)$) at leading twist, while four GPDs arise for 
-the spin-half nucleon. This significantly simplifies the interpretation of the 
+the spin-$\frac{1}{2}$ nucleon. This significantly simplifies the interpretation of the 
 data and allows a model independent extraction of the $^4$He CFF 
@@
 events with more than one good photon were not discarded at this stage. These
-were caused by accidental coincidences of soft photons and did not affect 
-directly the measurement as only the most energetic photon of an 
+were caused by accidental coincidences of soft photons and did not directly
+affect this measurement, as only the most energetic photon of an 
 event was considered a DVCS photon candidate.
@@
 In this work, the physics observable extracted using coherent DVCS events is
-the beam-spin asymmetry, noted $A_{LU}$. On an unpolarized target, $A_{LU}$ is 
+the beam-spin asymmetry, $A_{LU}$. On an unpolarized target, $A_{LU}$ is 
 defined as the difference of cross sections for the reaction with opposite beam 
@@
 detector efficiencies largely cancel and $A_{LU}$ can be 
-extracted from the reaction yields for the two helicities ($N^{\pm}$)
+extracted from the reaction yields for the two helicities ($N^{\pm}$):
 \begin{equation}
@@
 There is an additional process contributing to the same final state as the 
-DVCS, the so called Bethe-Heitler (BH) process, where the real photon is 
+DVCS, the so-called Bethe-Heitler (BH) process, where the real photon is 
 emitted by the incoming or the outgoing lepton. The DVCS and BH processes are 
@@
 $A_{LU}$. The three terms entering the cross section calculation,
-the square of the BH and DVCS amplitudes and their interference term, depend on the
+the squares of the BH and DVCS amplitudes and their interference term, depend on the
 azimuthal angle $\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes,
@@
 \end{equation}
-explicit expressions of the kinematic factors $\alpha_i$ are derived in
+where explicit expressions of the kinematic factors $\alpha_i$ are derived in
 Ref.~\cite{Belitsky:2008bz} and are functions of Fourier harmonics in the 
@@
    uncertainties. The grey bands represent the systematic uncertainties, 
-   including the normalisation uncertainties. The red curves are the results of 
+   including the normalization uncertainties. The red curves are the results of 
    fits with Eq.~(\ref{eq:A_LU-coh}).}
@@
 come from the choice of DVCS exclusivity cuts (8\% systematic uncertainty) and the 
-large binning size (5.1\%). The values are relative and quoted for $A_{LU}$
+large binning size (5.1\%). These values are relative and quoted for $A_{LU}$
 at $\phi=90^\circ$. Added quadratically, the total systematic uncertainty
-is about 10\% at $90^\circ$ (or 0.03, in absolute), which is significantly smaller
+is about 10\% at $90^\circ$ (or 0.03, absolute), which is significantly smaller
 than the statistical uncertainties at all kinematical bins.
@@
 can see a difference between the precision of the extracted imaginary and real 
-parts, which is built in Eq.~(\ref{eq:A_LU-coh}) where 
-$\alpha_2$ is much smaller than $\alpha_1$. While the precision of this 
-measurement is not at a sufficient level to discriminate between the models, 
-these results demonstrate the possibility of extracting the CFF of a spin-0 
-target directly from a $A_{LU}$ measurement.
+parts, which is is due to $\alpha_2$ being much smaller than $\alpha_1$ in
+Eq.~(\ref{eq:A_LU-coh}). While the precision of this measurement is not at a
+sufficient level to discriminate between the models, these results demonstrate
+the possibility of extracting the CFF of a spin-0 target directly from a $A_{LU}$
+measurement.
 

### 2017-05-14 eg6-letters/coherent/dvcs_he4_prl.tex
dvcs_he4_prl.tex:  minor grammar suggestion updates (forgotten or overwritten) before resending

@@
 experiment used the 6 GeV electron beam from the CEBAF accelerator at Jefferson 
-Lab incident on a pressurized $^4$He gaseous target in front of the CEBAF large acceptance 
-spectrometer (CLAS). The scattered electron was detected by CLAS and the photon 
+Lab incident on a pressurized $^4$He gaseous target in front of the CEBAF Large Acceptance 
+Spectrometer (CLAS). The scattered electron was detected by CLAS and the photon 
 by a dedicated electromagnetic calorimeter at forward angles. To ensure the 
@@
 important simplification, as a spin-zero hadron is parametrized by only one 
-chiral even GPD ($H_{A}(x,\xi,t)$) at leading twist, while four GPDs arise for 
+chiral even GPD ($H_{A}(x,\xi,t)$) at leading-twist, while four GPDs arise for 
 the spin-$\frac{1}{2}$ nucleon. This significantly simplifies the interpretation of the 
@@
 
-The CEBAF large acceptance spectrometer (CLAS) in Hall B at Jefferson 
+The CEBAF Large Acceptance Spectrometer (CLAS) in Hall B at Jefferson 
 Lab~\cite{Mecking:2003zu} has been previously supplemented with an inner 
@@
 extended the photon detection acceptance of CLAS to polar angles as low as 
-4$^{\circ}$. The 5~T solenoid magnet acted as a guiding field for the 
+4$^{\circ}$. The 5-T solenoid magnet acted as a guiding field for the 
 low-energy M\o{}ller electrons that were absorbed in a  
@@
 be mistaken for DVCS when one of the two photons from the $\pi^0$ 
-decay is produced at low energy in the laboratory frame and remains undetected.  
+decay is produced at low-energy in the laboratory frame and remains undetected.  
 To estimate the effect of this contamination, we developed an event generator 
@@
 with a RTPC. This setup allowed detection of the 
-low energy $^4$He recoils in order to ensure an exclusive measurement of the
+low-energy $^4$He recoils in order to ensure an exclusive measurement of the
 coherent DVCS process. The azimuthal dependence of the measured $A_{LU}$ has 

### 2017-05-15 eg6-letters/coherent/dvcs_he4_prl.tex
Comments from SN

--- 2017-05-13 eg6-letters/coherent/dvcs_he4_prl.tex
@@
 experiment used the 6 GeV electron beam from the CEBAF accelerator at Jefferson 
-Lab incident on a pressured $^4$He gaseous target in front of the CEBAF large acceptance 
+Lab incident on a pressured $^4$He gaseous target placed in front of the CEBAF large acceptance 
 spectrometer (CLAS). The scattered electron was detected by CLAS and the photon 
@@
 deeply virtual Compton scattering (DVCS), \textit{i.e.}, the hard exclusive 
-electroproduction of a real photon on a hadron. While other processes are known 
+electroproduction of a real photon on a hadron. While other processes are also known 
 to be sensitive to GPDs, the measurement of DVCS is considered the cleanest 
@@
 three-dimensional image (for reviews of the field, see~\cite{Goeke:2001tz,
-Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}). This 
-recent progress could also be applicable to nuclei, giving access to novel 
+Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}). These 
+recent developments could also be applicable to nuclei, giving access to novel 
 information about nuclear structure in terms of quarks and gluons 
@@
 
-Fig.~\ref{fig:diags} illustrates the handbag diagram for coherent DVCS on 
+Figure~\ref{fig:diags} illustrates the handbag diagram for coherent DVCS on 
 $^4$He, where the four-vectors of the electrons, photons, and $^4$He are denoted 
@@
 which embed the partonic structure of the hadron. The GPDs depend on the three 
-variables $x$, $\xi$, and $t$. The 
-parameter $\xi$ relates to the Bjorken variable $x_{B}$: $\xi\approx 
+variables $x$, $\xi$, and $t$. $\xi$ relates to the Bjorken variable $x_{B}$: $\xi\approx 
 {{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M_N\nu}$, $\nu$ is the energy of the virtual photon, and 
-$M_N$ is the nucleon mass. The parameter $x$ is the quark's internal loop momentum 
+$M_N$ is the nucleon mass. $x$ is the quark's internal loop momentum 
 fraction and cannot be accessed experimentally in DVCS. We in fact measure 
 Compton form factors (CFF), which are complex quantities defined as:
-
 \begin{align}
@@
 
-Until now, the only available data on nuclear DVCS was from the HERMES 
+Until now, the only available data on nuclear DVCS were from the HERMES 
 experiment \cite{Airapetian:2010nu}. In this experiment, the exclusivity of 
 the reaction was obtained through kinematic cuts using only the measured 
-scattered electron and real photon. The measurement was performed on a large 
+scattered electron and real photon. This measurement was performed on a large 
 set of nuclei ($^4$He, $^{14}$N, $^{20}$Ne, $^{85}$Kr and $^{131}$Xe), 
-but contamination from incoherent processes could influence the measurement 
+but contamination from incoherent processes can be suspected to influence the results 
 significantly~\cite{Guzey:2003jh}. The direct detection of the recoil nucleus 
@@
 to interesting nuclear effects~\cite{JSeely}. Its spin-zero also leads to an 
-important simplification, as a spin-zero hadron is parametrized by only one 
-chiral even GPD ($H_{A}(x,\xi,t)$) at leading twist, while four GPDs arise for 
+important simplification, as spinless hadrons are parametrized by only one 
+chiral-even GPD ($H_{A}(x,\xi,t)$) at leading twist, while four GPDs arise for 
 the spin-half nucleon. This significantly simplifies the interpretation of the 
-data and allows a model independent extraction of the $^4$He CFF 
+data and allows a model-independent extraction of the $^4$He CFF 
 ($\mathcal{H}_{A}$) presented at the end of this letter.
@@
 events with more than one good photon were not discarded at this stage. These
-were caused by accidental coincidences of soft photons and did not affect 
+were mainly caused by accidental coincidences of soft photons and did not affect 
 directly the measurement as only the most energetic photon of an 
@@
 diagram was dominant, we selected events with $Q^{2}$ greater than 
-1~GeV$^{2}$. Exclusivity of the coherent DVCS reaction was optimized by 
+1~GeV$^{2}$. The exclusivity of the coherent DVCS reaction was ensured by 
 applying a set of cuts on the following kinematic variables: the coplanarity 
@@
 between the measured photon and the missing momentum of the $e'^4$He$'$ system.  
-The experimental data for the most relevant exclusivity observables and applied
+The experimental data for the most relevant exclusivity variables and applied
 cuts are shown in Fig.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for 
 additional details). We also 
-rejected events where a $\pi^0$ was identified by the invariant mass reconstruction of 
+rejected events where a $\pi^0$ was identified by the invariant mass of 
 two photons. About 3200 events passed all these requirements, their kinematic 
@@
 $\pi^0$ production. The accidentals have particles originating from different events,
-and we estimated their contribution to be 4.1\% of our sample. We evaluated this 
+and we estimated their contribution to be 4.1\% of the data sample. We evaluated this 
 contribution by selecting events passing all the cuts but with the scattered electron and 
-$^4$He originating from different vertices. The $\pi^0$ production can easily
+$^4$He originating from different vertices. The $\pi^0$ production can
 be mistaken for DVCS when one of the two photons from the $\pi^0$ 
@@
   \begin{equation}
-  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
-                {d^{5}\sigma^{+} + d^{5}\sigma^{-}},
+  A_{LU} = \frac{d^{4}\sigma^{+} - d^{4}\sigma^{-} }
+                {d^{4}\sigma^{+} + d^{4}\sigma^{-}},
     \label{BSA_equation}
   \end{equation}
-where $d^{5}\sigma^{\pm}$ is the DVCS differential cross 
+where $d^{4}\sigma^{\pm}$ is the DVCS differential cross 
 section for positive (negative) beam helicity. 
@@
 There is an additional process contributing to the same final state as the 
-DVCS, the so called Bethe-Heitler (BH) process, where the real photon is 
+DVCS, the Bethe-Heitler (BH) process, where the real photon is 
 emitted by the incoming or the outgoing lepton. The DVCS and BH processes are 
@@
 $A_{LU}$. The three terms entering the cross section calculation,
-the square of the BH and DVCS amplitudes and their interference term, depend on the
+the squares of the BH and DVCS amplitudes and their interference term, depend on the
 azimuthal angle $\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes,
 as shown for the nucleon in Ref.~\cite{Belitsky:2001ns} and for the spin-zero targets
-in Refs.~\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the $A_{LU}$ 
-of a spin-zero hadron can be expressed as
+in Refs.~\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, $A_{LU}$ 
+for a spin-zero hadron can be expressed as
 \begin{equation}
@@
 {\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
-\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)},
+\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}.
 \end{split}
@@
 \end{equation}
-explicit expressions of the kinematic factors $\alpha_i$ are derived in
+Explicit expressions of the kinematic factors $\alpha_i$ are derived in
 Ref.~\cite{Belitsky:2008bz} and are functions of Fourier harmonics in the 
@@
 $\phi$ and the kinematical variables $Q^2$, $x_B$, and $t$. Due to limited 
-statistics, these latter variables are studied separately with independent 
-binning. The curves on 
+statistics, these latter variables are studied separately with a two-dimensional 
+data binning. The curves on 
 the plots are fits using the function presented in Eq.~(\ref{eq:A_LU-coh}), 
@@
 free parameters. 
+%Could add a sentence to mention that it is sin phi dominated as expected 
+% also that assymetries are larger than protons ?
 
@@
 (off-shellness) on the quark distribution. The calculations are at slightly 
-different kinematics than our data but still allow drawing some conclusions. The 
-calculations appear to have smaller asymmetries than observed. 
+different kinematics than the data but still allow us to draw some conclusions. The 
+model appear to predict smaller asymmetries than observed. 
 The difference may arise from the theoretical uncertainty in the determination 
@@
 model and is based on the double distributions ansatz \cite{DD_model}. The 
-off-shell model is the same as in Fig.~\ref{fig:alu90} using an improved
+off-shell model is the same as in Fig.~\ref{fig:alu90} using a more recent
 GPD model for the nucleon \cite{GonzalezHernandez:2012jv}.
@@
 coherent DVCS process. The azimuthal dependence of the measured $A_{LU}$ has 
-been used to extract, in a model independent way, the real and the imaginary 
+been used to extract, in a model-independent way, the real and the imaginary 
 parts of the $^4$He CFF, $\mathcal{H}_A$. The extracted CFF is in  
@@
 \bibitem{Mueller:1998fv} 
-D. Mueller, D. Robaschik, B. Geyer, F.M. Dittes and J. Horejsi,
+D. Mueller, D. Robaschik, B. Geyer, F.M. Dittes and J.~Horejsi,
 Fortsch.\ Phys. {\bf 42}, 101 (1994).
@@
   M.~Burkardt,
-  Phys.\ Rev.\ D {\bf 62}, 071503 (2000)
-  Erratum: Phys.\ Rev.\ D {\bf 66}, 119903 (2002)
+  Phys.\ Rev.\ D {\bf 62}, 071503 (2000);
+  Erratum: Phys.\ Rev.\ D {\bf 66}, 119903 (2002).
 
@@
   M.~Diehl,
-  Eur.\ Phys.\ J.\ C {\bf 25}, 223 (2002)
-  Erratum: Eur.\ Phys.\ J.\ C {\bf 31}, 277 (2003)
+  Eur.\ Phys.\ J.\ C {\bf 25}, 223 (2002);
+  Erratum: Eur.\ Phys.\ J.\ C {\bf 31}, 277 (2003).
 
@@
   A.~V.~Belitsky and D.~Mueller,
-  Nucl.\ Phys.\ A {\bf 711}, 118 (2002)
+  Nucl.\ Phys.\ A {\bf 711}, 118 (2002).
 
@@
   M.~Burkardt,
-  Phys.\ Rev.\ D {\bf 72}, 094020 (2005)
+  Phys.\ Rev.\ D {\bf 72}, 094020 (2005).
 
@@
    M.~Mazouz {\it et al.} [Jefferson Lab Hall A Collaboration],
-   Phys.\ Rev.\ Lett.\  {\bf 99}, 242501 (2007)
+   Phys.\ Rev.\ Lett.\  {\bf 99}, 242501 (2007).
 
@@
 H.~S.~Jo {\it et al.} [CLAS Collaboration],
-  Phys.\ Rev.\ Lett.\  {\bf 115}, no. 21, 212003 (2015)
+  Phys.\ Rev.\ Lett.\  {\bf 115}, no. 21, 212003 (2015).
 
@@
   R.~Dupr\'e and S.~Scopetta,
-  Eur.\ Phys.\ J.\ A {\bf 52}, no. 6, 159 (2016)
+  Eur.\ Phys.\ J.\ A {\bf 52}, no. 6, 159 (2016).
 
@@
 A.~Freund and J.C.~Collins, 
-Phys.\ Rev.\ D {\bf 59}, 074009 (1998)
+Phys.\ Rev.\ D {\bf 59}, 074009 (1998).
 
@@
 X.-D.~Ji and J.~Osborne, 
-Phys.\ Rev.\ D {\bf 58}, 094018 (1998)
+Phys.\ Rev.\ D {\bf 58}, 094018 (1998).
 
@@
   V.~Guzey and M.~Strikman,
-  Phys.\ Rev.\ C {\bf 68}, 015204 (2003)
+  Phys.\ Rev.\ C {\bf 68}, 015204 (2003).
 
@@
 J. Seely {\it et al.} 
-Phys.\ Rev.\ Lett.\ {\bf 103}, 202301 (2009)
+Phys.\ Rev.\ Lett.\ {\bf 103}, 202301 (2009).
 
@@
 A.~V.~Belitsky, D.~Mueller and A.~Kirchner,
-Nucl.\ Phys.\ B {\bf 629}, 323 (2002)
+Nucl.\ Phys.\ B {\bf 629}, 323 (2002).
 
@@
 A.~Kirchner and D.~Mueller, 
-Eur.\ Phys.\ J.\ C {\bf 32}, 347 (2003)
+Eur.\ Phys.\ J.\ C {\bf 32}, 347 (2003).
 
@@
 A.~V.~Belitsky and D.~Mueller,
-Phys.\ Rev.\ D {\bf 79}, 014017 (2009)
+Phys.\ Rev.\ D {\bf 79}, 014017 (2009).
 
@@
 S.~Liuti and K.~Taneja, 
-Phys.\ Rev.\ C {\bf 72}, 032201 (2005)
+Phys.\ Rev.\ C {\bf 72}, 032201 (2005).
 
@@
 V.~Guzey and T.~Teckentrup,
-Phys.\ Rev.\ D {\bf 74}, 054027 (2006)
+Phys.\ Rev.\ D {\bf 74}, 054027 (2006).
 

### 2017-05-15 eg6-letters/coherent/dvcs_he4_prl.tex

@@
 experiment used the 6 GeV electron beam from the CEBAF accelerator at Jefferson 
-Lab incident on a pressured $^4$He gaseous target placed in front of the CEBAF large acceptance 
-spectrometer (CLAS). The scattered electron was detected by CLAS and the photon 
+Lab incident on a pressurized $^4$He gaseous target placed in front of the CEBAF Large Acceptance 
+Spectrometer (CLAS). The scattered electron was detected by CLAS and the photon 
 by a dedicated electromagnetic calorimeter at forward angles. To ensure the 
@@
 to interesting nuclear effects~\cite{JSeely}. Its spin-zero also leads to an 
-important simplification, as spinless hadrons are parametrized by only one 
-chiral-even GPD ($H_{A}(x,\xi,t)$) at leading twist, while four GPDs arise for 
-the spin-half nucleon. This significantly simplifies the interpretation of the 
-data and allows a model-independent extraction of the $^4$He CFF 
+important simplification, as a spin-zero hadron is parametrized by only one 
+chiral even GPD ($H_{A}(x,\xi,t)$) at leading-twist, while four GPDs arise for 
+the spin-$\frac{1}{2}$ nucleon. This significantly simplifies the interpretation of the 
+data and allows a model independent extraction of the $^4$He CFF 
 ($\mathcal{H}_{A}$) presented at the end of this letter.
 
-The CEBAF large acceptance spectrometer (CLAS) in Hall B at Jefferson 
+The CEBAF Large Acceptance Spectrometer (CLAS) in Hall B at Jefferson 
 Lab~\cite{Mecking:2003zu} has been previously supplemented with an inner 
@@
 events with more than one good photon were not discarded at this stage. These
-were mainly caused by accidental coincidences of soft photons and did not affect 
-directly the measurement as only the most energetic photon of an 
+were mainly caused by accidental coincidences of soft photons and did not directly
+affect this measurement, as only the most energetic photon of an 
 event was considered a DVCS photon candidate.
@@
 There is an additional process contributing to the same final state as the 
-DVCS, the Bethe-Heitler (BH) process, where the real photon is 
+DVCS, the so-called Bethe-Heitler (BH) process, where the real photon is 
 emitted by the incoming or the outgoing lepton. The DVCS and BH processes are 

### 2017-05-18 eg6-letters/NIM/EG6_RTPC_NIM.tex
Added changes from Andrea

@@
 and energy of 6.064 GeV incident on a gaseous $^{4}$He target.
-{\bf \color{red} Add luminosity.}
 
@@
 TPC, organized as follows. In section \ref{sec_design}, we detail the design 
-and internal structure of the detector. Section \ref{sec_readout} is focused 
-on the properties of the read-out system. Calibration 
+and internal structure of the detector. Section \ref{sec_readout} describes 
+the properties of the read-out system. Calibration 
 strategies are discussed in section \ref{sec_calib}. Finally, the performances
@@
 RTPC has 40 rows and 40 columns of pads. The shaded region in figure~\ref{fig:PADs} 
-shows how pads are grouped to 16 channels pre-amplifiers. A Time to Digital
-Converter (TDC) with 114~ns samples is used to measure the time taken by
-the electrons to drift from the ionization point to the readout board.  Signal
-amplitude is is measured with an Analog-to-Digital-Converter (ADC) without
-specific normalization.
+shows how pads are grouped to 16 channels pre-amplifiers. The pre-amplifier boards, 
+already employed in the BoNuS RTPC \cite{BONUS-NIM}, serve the dual purpose of 
+inverting the RTPC signals polarity -- from negative to positive -- to match the 
+requirements of the subsequent readout system, and driving the 6m long ribbon 
+cable that connects to it.
 
-{\bf \color{red} 
-Andrea:
+The readout system is based on the Front End Electronic (FEE) boards originally 
+developed for the ALICE TPC readout system at Cern~\cite{ALICE-FEE}. Each 
+readout channel is made of three main components: a charge sensitive, low 
+impedance shaping amplifier, a 10 bit, 25-MHz digitizer, and a digital circuit 
+that implements online-processing algorithms (pedestal subtraction, zero 
+suppression, ad tail cancellation). The amplifier is implemented in a 
+fully-analogue ASIC, PASA~\cite{ALICE-PASA}, while the subsequent signal 
+digitization and elaboration part is implemented in a digital ASIC, 
+ALTRO~\cite{ALICE-ALTRO}. Both ASICs host 16 channels. The full readout 
+chain is implemented on a single Front End Card (FEC), hosting 128 channels. 
+FECs are hosted in custom crates, mounted close to the detector. A Readout 
+Control Unit (ROC) board is used to distribute the trigger signal to FECs 
+and for data readout. Each RCU can handle up to 25 FECs. Communication 
+between ROC and FECs is performed trough a custom backplane, implementing 
+a low-voltage signal bus. The RCU communicates with the CLAS DAQ system 
+trough a 200 MB/s optical link, connected to a data acquisition PC hosting 
+a ReadOut Receiver Card (RORC). This PC hosts the readout controller 
+application (ROC) used to interface with the CLAS DAQ system. An Ethernet 
+link is also present, for slow-controls and monitoring.
 
-- Mention ALTRO chip and reference.
+Triggering and data-readout scheme is as follows. When a Level-1 (L1) trigger 
+is received by a FEC-board, a programmable number of samples $N_0$ is digitized 
+and stored in a data memory, and hence processed by the digital circuit. Upon 
+arrival of Level-2 trigger, the latest processed samples are saved in a 
+multi-event memory, invididual to each-channel, ready for readout by the RCU. 
+In our setup, the RCU receives the trigger signal from the CLAS Trigger 
+Supervisor system, and distributes both L1 and L2 signals to all the FECs in 
+the crate, with a definite L1-L2 trigger latency. Such latency is programmable, 
+and has to be longh enough to accomodate the digitization of the $N_0$ samples 
+per channel. In the current implementation, $N_0=100$ samples/channel are 
+acquired for each trigger, operating ALTRO at the reduced sampling frequency 
+of $10 MHz$. The L1-L2 latency is thus fixed to 15 $\mu$s.
 
-- Sparcification method (3 consecutive ADC samples above a threshold of xxx ?, and three
-samples before and after)
+The trigger signal also initiates RCU readout operation from FEC boards. All 
+the measured samples from active channels are reported, together with a channel 
+identifier and a timestamp, to the ROC application, that in turns sends them on 
+the main event builder. During data reconstruction, the acquired samples are 
+processed to obtain, for each readout pad, the accumulated charge (ADC) and 
+the pulse time (T). Since pulse time was obtained as the time-stamp of the 
+first sample above threshold, referred to to the trigger time, the resolution 
+is equivalent to the ALTRO sampling time, 100~ns.
 
-- Mention trigger time T=15.
+\begin{figure}[tb]
+   \centering
+   \includegraphics[width=.5\textwidth]{fig/ReadoutScheme.png}
+   \caption[]{Schematic representation of the RTPC readout system, showing} 
+   \label{fig:ReadoutScheme}
+\end{figure}
 
-- Preamplifiers were from Bonus ?
+In order to reduce the data size, ALTRO is operated in zero-suppression mode: 
+only samples above a programmable threshold are stored in the ALTRO on-board 
+memory and then written to tape. A glitch-filter permits to reject spurious 
+pulses due to noise, by requiring the presence of a minimum number of samples 
+over threshold $N_{MINSEQ}$ to validate a sample. To properly reconstruct 
+the signal shape, $N_{PRE}$ samples before threshold-crossing and $N_{POST}$ 
+samles after the signal returns below threshold are saved. In the present 
+configuration, $N_{MINSEQ}=N_{PRE}=N_{POST}=3$, while threshold is set 
+just above the noise level.
 
-- Basics of JLab fADC (is there a reference?)
-
-- Mention max rate we ran
-
-- Other relevant information ?
-}
+In order to read all the detector readout pads, four FEC crates are used, 
+each equipped with 6 boards, plus a ROC. A schematic of the readout system, 
+for a single crate, is reported in figure~\ref{fig:ReadoutScheme}. This 
+configuration permits to reduce the dead time associated to FEC readout 
+operations, scaling linearly with the number of boards in the crate. During 
+the 2009 run, the system was succesfully operated with a DAQ rate of 3.1 kHz, 
+with a live time of $70 \%$.
 
@@
 
+ \bibitem{ALICE-FEE}
+ L. Musa et al., The ALICE TPC front end electronics, 2003 IEEE Nuclear 
+ Science Symposium, 2003, pp. 3647-3651 Vol.5
+
+ \bibitem{ALICE-PASA}
+   H.~K.~Soltveit {\it et al.},
+   ``The Preamplifier shaper for the ALICE TPC-Detector,''
+   Nucl.\ Instrum.\ Meth.\ A {\bf 676} (2012) 106
+
+ \bibitem{ALICE-ALTRO},
+ R. E. Bosch, {\it et al.}, ``The ALTRO chip: a 16-channel A/D converter and 
+ digital processor for gas detectors'', IEEE Transactions on Nuclear Science, 
+ vol. 50, no. 6, pp. 2460-2469, Dec. 2003.
+
 \bibitem{gem_sauli}

### 2017-05-23 eg6-letters/NIM/EG6_RTPC_NIM.tex
Small edits

@@
 allowing a curved amplification surface. Also, GEMs are known to rarely create 
-sparks{\color{blue} \cite{GEM_ref}}, which is important when trying to detect 
+sparks~\cite{GEM_ref}, which is important when trying to detect 
 highly ionizing slow nuclei that deposit large amount of energy. The GEMs for 
-this RTPC are made from a Kapton insulator layer, {\color{blue}50~$\mu$m 
-thick}, sandwiched between two 5~$\mu$m copper layers. The mesh of each GEM 
+this RTPC are made from a Kapton insulator layer, 50~$\mu$m 
+thick, sandwiched between two 5~$\mu$m copper layers. The mesh of each GEM 
 layer is chemically etched with 50~$\mu$m diameter holes with double-conical 
@@
 
-The drift gas used in the experiment is a 80-20\% neon-DME mixtur, this choice 
-has been made in order to balance the good drift properties with a reasonnable
+The drift gas used in the experiment is a 80-20\% neon-DME mixture, this choice 
+has been made in order to balance the energy deposit with a reasonnable
 Lorentz angle. Calculations using the MAGBOLTZ program~\cite{MAGBOLTZ} 
 showed that with the perpendicular 5~T field, we would have a Lorentz angle of 
-about {\bf \color{red} (To be added) } with this mixture. As can be seen, the
-Lorentz angle is already significant, a larger angle would increase significantly
-the length of the drift paths as the electron would spiral around the beam line.
-{\bf \color{red} (To be continued commenting on higher/lower proportion of gas 
-and other gas) }
+about 23$^\circ$ with this mixture. This is already significant and a heavier
+gas would have larger angle increasing significantly
+the length of the drift paths as the electron would 
+make a long spiral around the beam line before to reach the GEMs.
 
@@
 all gluing and soldering operations.  Because the rigidity of the high 
-rigidity of the GEM foil, the strcture was selfsupporting and only the 
+rigidity of the GEM foil, the structure was selfsupporting and only the 
 backward part of the cylinder was fixed to the main mechanical structure. This 
@@
 electron beam (1.20 and 1.27 GeV) to enhance the cross section of the elastic 
-process ($e^{4}$He$\rightarrow e^{4}$He)
-{\bf \color{red} Specify luminosity ?}. In this process, the measurement of
+process ($e^{4}$He$\rightarrow e^{4}$He). In this process, the measurement of
 electron kinematics allows to calculate the Helium nucleus kinematic. It is
@@
 compared simulation to experiment on an event by event basis as shown in 
-figure~\ref{fig:EVENT_adc_tdc}. In this step, the gain for each pad is defined 
+figure~\ref{fig:EVENT_adc_tdc}. In this step, the gain for each pad is calculated 
 as the ratio of the measured ADCs to the simulated deposited energy.  
-{\color{blue} Then, the gain of each readout pad is corrected by a factor, that 
-is defined as the ratio of the ADC value of each pad to the ADCs of the other 
-pads inside each track to make sure that the recorded ADCs by a given pad are 
-similar to the recorded ADCs recorded by other pads in the same track.}
-
-{\bf \color{red} Mohammad: Detail are missing here.}
+Then, these gains are refined using correcting factors obtained from a 
+sample of good tracks. For each track, we calculate the corrected 
+energy deposit on a pad and compare it to the average
+deposit recorded by the other pads. 
 Results of this second method are shown in Figure~\ref{fig:dedx_p_exp_2nd},

### 2017-05-24 eg6-letters/NIM/EG6_RTPC_NIM.tex
added the performance section

@@
 
-\section{Track Reconstruction}\label{sec_perf}
-
+\section{Track Reconstruction}\label{sec_rec}
 In order to reconstruct tracks we first select good hits. This means rejecting 
@@
 
-{\bf \color{red} Mohammad: We need some performance studies here, I remember we had
-figures showing efficiency, we need to add them.}
+\section{Performance Studies}\label{sec_perfor}
+The previous discussions have shown that the two modules of the RTPC have 
+slightly different yield, however this yield should not be linked to a 
+different performance of the RTPC. The differences are mainly due to 
+complicated convolution of CLAS and the RTPC acceptances. We measured the 
+efficiency of the RTPC using the elastic scattering on $^4$He, where the 
+exclusive elastic yield is compared to the inclusive yield for the two modules 
+of the detector. Here the inclusive yields are the number of electrons in the 
+elastic invariant mass peak whose corresponding elastically scattered $^4$He 
+would have been in the acceptance of the RTPC, and the exclusive yields require 
+the additional detection of the $^4$He. As a result, we found that the left and 
+the right modules have similar efficiencies except near the target windows, as 
+shown in figure \ref{fig:rtpc_eff}.
+
+\begin{figure}[tb]
+\centering
+\includegraphics[width=8cm]{fig/tpceff.png}
+\caption{The RTPC $^4$He detection efficiency as a function of the longitudinal 
+   position along the detector.
+ \label{fig:rtpc_eff}}
+ \end{figure}
 

### 2017-05-24 eg6-letters/coherent/dvcs_he4_prl.tex

@@
 recent developments could also be applicable to nuclei, giving access to novel 
-information about nuclear structure in terms of quarks and gluons 
-(see~\cite{Dupre:2015jha} and references therein). Such a study of the 3D 
+information about nuclear structure in terms of quarks and gluons~\cite{Berger:2001zb,
+Cano:2003ju,Guzey:2005ba,Dupre:2015jha}. Such a study of the 3D 
 structure of nuclei appears to be especially interesting in light of the large, 
@@
 
+\bibitem{Berger:2001zb} 
+  E.~R.~Berger, F.~Cano, M.~Diehl and B.~Pire,
+  %``Generalized parton distributions in the deuteron,''
+  Phys.\ Rev.\ Lett.\  {\bf 87}, 142302 (2001)
+  doi:10.1103/PhysRevLett.87.142302
+  [hep-ph/0106192].
+
+\bibitem{Cano:2003ju} 
+  F.~Cano and B.~Pire,
+  %``Deep electroproduction of photons and mesons on the deuteron,''
+  Eur.\ Phys.\ J.\ A {\bf 19}, 423 (2004)
+  doi:10.1140/epja/i2003-10127-x
+  [hep-ph/0307231].
+
+\bibitem{Guzey:2005ba} 
+  V.~Guzey and M.~Siddikov,
+  %``On the A-dependence of nuclear generalized parton distributions,''
+  J.\ Phys.\ G {\bf 32}, 251 (2006)
+  doi:10.1088/0954-3899/32/3/002
+  [hep-ph/0509158].
+
 \bibitem{Dupre:2015jha} 

### 2017-05-24 eg6-letters/NIM/EG6_RTPC_NIM.tex
editing the figures for the nim paper
update figure 8 in the NIM
update figure 7 in the NIM paper

@@
    \centering
-   \includegraphics[scale=0.3]{fig/TDC_profile.png}
+   \includegraphics[scale=0.42]{fig_2017/hits_time_profile.pdf}
    \caption[]{Time profile of the collected hits in one experimental run.  } 
@@
 \centering
-\includegraphics[scale=0.36]{fig/RunNumber_61551_TDCmax_Zslice.png}
+\includegraphics[scale=0.42]{fig_2017/RunNumber_61452_TDCmax_Zslice.pdf}
 \caption{Time profile distribution for the collected hits in one experimental 
@@
 \begin{figure}[tb]
-\hspace*{-1.8cm}
-\includegraphics[scale=0.26]{fig/Drift_run_number_1.png}
+\centering
+\includegraphics[scale=0.45]{fig_2017/Drift_run_number.pdf}
 \caption{$T_{Nbmax/2}$ versus the experimental run numbers (time).  } 

### 2017-05-24 eg6-letters/NIM/fig_2017/hits_time_profile.C

@@ -1,0 +1,437 @@
+void hits_time_profile()
+{
+//=========Macro generated from canvas: c/
+//=========  (Wed May 24 14:24:46 2017) by ROOT version6.09/01
+
+   gStyle->SetStatFontSize(0.12);
+   gStyle->SetStatW(0.25);
+   gROOT->Reset();
+   gStyle->SetOptStat(kFALSE);
+   gStyle->SetOptFit(0);
+   gStyle->SetPalette(55);   
+   gStyle->SetLabelSize(0.03,"xyz"); // size of axis value font 
+   gStyle->SetTitleSize(0.035,"xyz"); // size of axis title font 
+   gStyle->SetTitleFont(22,"xyz"); // font option 
+   gStyle->SetLabelFont(22,"xyz");
+   gStyle->SetTitleOffset(1.2,"y");
+   gStyle->SetCanvasBorderMode(0);
+   gStyle->SetCanvasBorderSize(0);
+   gStyle->SetPadBottomMargin(0.15); //margins... 
+   gStyle->SetPadTopMargin(0.04);
+   gStyle->SetPadLeftMargin(0.15);
+   gStyle->SetPadRightMargin(0.1);
+   gStyle->SetFrameBorderMode(0);
+   gStyle->SetPaperSize(20,24);
+   gStyle->SetLabelSize(0.05,"xy");
+   gStyle->SetTitleSize(0.06,"xy");
+
+
+   TCanvas *c = new TCanvas("c", "",1,1,650,430);
+   gStyle->SetOptFit(1);
+   c->Range(-19.25,-386.4461,93.25,3478.014);
+   c->SetFillColor(0);
+   c->SetBorderMode(0);
+   c->SetBorderSize(2);
+   c->SetFrameBorderMode(0);
+   c->SetFrameBorderMode(0);
+   
+   Double_t Graph0_fx2933[75] = {
+   0,
+   1,
+   2,
+   3,
+   4,
+   5,
+   6,
+   7,
+   8,
+   9,
+   10,
+   11,
+   12,
+   13,
+   14,
+   15,
+   16,
+   17,
+   18,
+   19,
+   20,
+   21,
+   22,
+   23,
+   24,
+   25,
+   26,
+   27,
+   28,
+   29,
+   30,
+   31,
+   32,
+   33,
+   34,
+   35,
+   36,
+   37,
+   38,
+   39,
+   40,
+   41,
[…]

### 2017-05-25 eg6-letters/NIM/EG6_RTPC_NIM.tex
update figure 12 in the NIM paper
Fix Fig 9

@@
    \centering
-   \includegraphics[width=.5\textwidth]{fig/ReadoutScheme.png}
+   \includegraphics[width=.45\textwidth]{fig/ReadoutScheme.png}
    \caption[]{Schematic representation of the RTPC readout system, showing} 
@@
 
+\begin{figure*}[tb]
+\centering
+\includegraphics[width=16.5cm]{fig_2017/Drift_run_number.pdf}
+\caption{$T_{max/2}$ versus the experimental run numbers.} 
+\label{fig:Drift_run_number_1}
+\end{figure*}
+
 In summary, we obtain from our calibration a parametrization of the drift speed 
@@
 track reconstructions code.
-
-\begin{figure}[tb]
-\centering
-\includegraphics[scale=0.45]{fig_2017/Drift_run_number.pdf}
-\caption{$T_{Nbmax/2}$ versus the experimental run numbers (time).  } 
-\label{fig:Drift_run_number_1}
-\end{figure}
 
@@
 \centering
-\includegraphics[scale=0.37]{fig/FitResult_p2_10.png}
+\includegraphics[scale=0.36]{fig/FitResult_p2_10.png}
 \caption{$\Delta \phi$ versus T distribution in the second pass for tracks
@@
    \centering
-   \includegraphics[scale=0.45]{fig/f_dedx_p_exp_1st.pdf}
+   \includegraphics[scale=0.43]{fig/f_dedx_p_exp_1st.pdf}
    \caption{$\small{\frac{dE}{dX}}$ vs. $p/q$ distribution for the left half of 
@@
    \centering
-\includegraphics[scale=0.350]{fig/EVENT_adc_tdc.png}
+\includegraphics[scale=0.42]{fig_2017/Event_ADC_Graph_8799283.pdf}
 \caption{Simulated (upper) and experimental (lower) ADC and T distributions 

### 2017-05-25 eg6-letters/NIM/EG6_RTPC_NIM.tex
update figures 2, 6, and 10 in the nim paper

--- 2017-05-24 eg6-letters/NIM/EG6_RTPC_NIM.tex
@@
 \centering
-\includegraphics[scale=0.28]{fig/RTPC_1_all.png}
-\caption{Schematic drawing of CLAS RTPC in a plane perpendicular to 
-the beam direction.  See text for description of the elements.} 
-\label{fig:RTPC_1_4}
+\includegraphics[{trim={0 12cm 0 0},clip, scale=0.4}]{fig_2017/RTPC_1_all.pdf}
+\caption{Schematic drawing of CLAS RTPC in a plane perpendicular to the beam 
+direction.  See text for description of the elements.} \label{fig:RTPC_1_4}
 \end{figure}
@@
 arrival of Level-2 trigger, the latest processed samples are saved in a 
-multi-event memory, invididual to each-channel, ready for readout by the RCU. 
+multi-event memory, individual to each-channel, ready for readout by the RCU.  
 In our setup, the RCU receives the trigger signal from the CLAS Trigger 
@@
 the crate, with a definite L1-L2 trigger latency. Such latency is programmable, 
-and has to be longh enough to accomodate the digitization of the $N_0$ samples 
+and has to be long enough to accommodate the digitization of the $N_0$ samples 
 per channel.  In the current implementation, $N_0=100$ samples/channel are 
-acquired for each trigger, operating ALTRO at the reduced sampling frequency 
-of $10 MHz$. The L1-L2 latency is thus fixed to 15 $\mu$s.
+acquired for each trigger, operating ALTRO at the reduced sampling frequency of 
+$10 MHz$. The L1-L2 latency is thus fixed to 15 $\mu$s.
 
@@
 the measured samples from active channels are reported, together with a channel 
-identifier and a timestamp, to the ROC application, that in turns sends them on 
-the main event builder. During data reconstruction, the acquired samples are 
-processed to obtain, for each readout pad, the accumulated charge (ADC) and 
-the pulse time (T). Since pulse time was obtained as the time-stamp of the 
-first sample above threshold, referred to to the trigger time, the resolution 
-is equivalent to the ALTRO sampling time, 100~ns.
+identifier and a time-stamp, to the ROC application, that in turns sends them 
+on the main event builder. During data reconstruction, the acquired samples are 
+processed to obtain, for each readout pad, the accumulated charge (ADC) and the 
+pulse time (T). Since pulse time was obtained as the time-stamp of the first 
+sample above threshold, referred to to the trigger time, the resolution is 
+equivalent to the ALTRO sampling time, 100~ns.
 
@@
 the signal shape, $N_{PRE}$ samples before threshold-crossing and $N_{POST}$ 
-samles after the signal returns below threshold are saved. In the present 
-configuration, $N_{MINSEQ}=N_{PRE}=N_{POST}=3$, while threshold is set 
-just above the noise level.
+samples after the signal returns below threshold are saved. In the present 
+configuration, $N_{MINSEQ}=N_{PRE}=N_{POST}=3$, while threshold is set just 
+above the noise level.
 
@@
 \centering
-\includegraphics[scale=0.35]{fig/RTPC_2.png}
+%\includegraphics[scale=0.4][trim={0 5cm 0 0},clip]{fig_2017/RTPC_1_4.pdf}
+\includegraphics[{trim={0 12cm 0 0},clip, scale=0.4}]{fig_2017/RTPC_1_4.pdf}
 \caption[]{A schematic drawing of a $^{4}$He track (in green) traversing the 
@@
 \centering
-\includegraphics[scale=0.37]{fig/FitResult_p2_10.png}
+\includegraphics[scale=0.42]{fig_2017/FitResult_p2_11.pdf}
 \caption{$\Delta \phi$ versus T distribution in the second pass for tracks

### 2017-05-25 eg6-letters/NIM/EG6_RTPC_NIM.tex

@@
    \centering
-   \includegraphics[scale=0.45]{fig/f_dedx_p_exp_1st.pdf}
+   \includegraphics[scale=0.43]{fig_2017/f_dedx_p_exp_1st.pdf}
    \caption{$\small{\frac{dE}{dX}}$ vs. $p/q$ distribution for the left half of 
@@
 \centering
-\includegraphics[scale=0.45]{fig/f_dedx_p_exp_2nd.pdf}
+\includegraphics[scale=0.45]{fig_2017/f_dedx_p_exp_2nd.pdf}
 \caption{$\small{\frac{dE}{dX}}$ vs. $p/q$ distribution for the left half of 

### 2017-05-25 eg6-letters/coherent/dvcs_he4_prl.tex

@@
 We acknowledge the staff of the Accelerator and Physics Divisions at Jefferson 
-Lab for making this experiment possible. This work is supported by the U.S.  
-Department of Energy, Office of Science, Office of Nuclear Physics, under 
-contracts DE-AC02-06CH11357 and DE-AC05-06OR23177.
+Lab for making this experiment possible.
+
+Dave Ireland- the United Kingdom's Science and Technology Facilities Council
+
+Lamiaa- the Physics and Astronomy Department and the Office of Research and 
+Economic Development at Mississippi State University, and the US Department of 
+Energy Award DE-FG02-07ER41528.
+
+- This work is supported by the U.S.  Department of Energy, Office of Science, 
+Office of Nuclear Physics, under contracts DE-AC02-06CH11357 and 
+DE-AC05-06OR23177.
 

### 2017-05-30 eg6-letters/NIM/EG6_RTPC_NIM.tex
some cleaning
Few minor edits

@@
 and coherent meson production on $^4$He. In such processes, the $^4$He nucleus
-remains intact and recoils as a whole in the final state. The CEBAF Large
-Acceptance Spectrometer (CLAS) has been used for similar studies on proton
-targets, however it cannot track low energy $\alpha$ particles. In
+remains intact in the final state, however the CEBAF Large
+Acceptance Spectrometer (CLAS) cannot track the low energy $\alpha$ particles. In
 2009, we carried out measurements using the CLAS spectrometer supplemented by
 the RTPC positioned directly around a gaseous $^4$He target, allowing a detection
-threshold as low as $~$150  MeV/c for $^4$He. This article discuses the design,
-work principle, calibration methods and performances of the RTPC.
+threshold as low as 300~MeV/c for $^4$He. This article discuses the design,
+work principle, calibration methods and performances of this RTPC.
 \end{abstract}
@@
 USA, provides high power electron beams of energy up to 6 GeV and 100$\%$ duty cycle
-to three experimental Halls (A, B, C) simultaneously. The CLAS spectrometer, located
-in Hall-B, is composed of several sub-detectors and two magnets. The spectrometer
-was designed to track charged particles of momentum greater than 250 MeV/c as well 
-as detecting real photons. Figure~\ref{fig:CLAS} shows a three dimensional 
+to three experimental Halls (A, B, C) simultaneously. The CLAS 
+spectrometer~\cite{CLASref}, located
+in Hall-B, is composed of several sub-detectors and two magnets. 
+Figure~\ref{fig:CLAS} shows a three dimensional 
 representation of the baseline CLAS spectrometer:
@@
 serving as the analyzing magnet for the particle tracking in the RTPC. This 
-setup was used during a three months experimental run
-in 2009 with a longitudinally polarized electron beam of 130 nA 
+setup was used during a three months experimental run~\cite{proposal1,proposal2}
+in 2009 with a longitudinally polarized electron beam of 130~nA 
 and energy of 6.064 GeV incident on a gaseous $^{4}$He target.
@@
 strategies are discussed in section \ref{sec_calib}. Finally, the performances
-of the RTPC are described in section \ref{sec_perf}.
+of the RTPC are described in section \ref{sec_perfor}.
 
@@
 as possible to the target and fitting within the 230~mm diameter 
-of the 5 Tesla solenoid magnet surrounding the target \cite{Hyon-suk}.
+of the 5 Tesla solenoid magnet surrounding the target.
 
@@
       region is surrounded by a 4 $\mu$m thick window made of aluminized Mylar 
-      and electronically grounded.
+      is electronically grounded.
    \item The second gap region extends between 20~mm and 30~mm and is filled with a 
@@
       from the cathode to the first Gas Electron Multiplier(GEM), 60 mm away 
-      from the beam axis. The electric field in this region is about 550~V/cm 
+      from the beam axis. The average electric field in this region is about 550~V/cm 
       and perpendicular to the beam.
@@
 \includegraphics[scale=0.70]{fig/GEM_photo.jpg}
-\caption{Picture of a GEM foil similar to the one used for our RTPC.} 
+\caption{Picture of a GEM foil similar to the one used for our RTPC. {\color{red} Source?}} 
 \label{fig:GEMs}
@@
 
-The GEM technology has been chosen for this RTPC for its flexibility, 
-allowing a curved amplification surface. Also, GEMs are known to rarely create 
+The GEM technology has been chosenfor its flexibility as it
+allows for a curved amplification surface. Also, GEMs are known to rarely create 
 sparks~\cite{GEM_ref}, which is important when trying to detect 
@@
 layer is chemically etched with 50~$\mu$m diameter holes with double-conical 
-shapes as illustrated in figure~\ref{fig:GEMs}. A potential difference of 275 V 
-is applied between the two 
-copper layers of the GEM, creating a very strong electric field in each hole 
-leading to high ionization and therefore amplification of the incoming 
-electrons. A high potential of about 1600 V/cm is set between 
-the GEMs to push the electrons toward the next GEM and eventually the readout 
-pads. \\
+shapes as illustrated in figure~\ref{fig:GEMs}. The potential difference 
+applied between the two copper layers of the GEM creates a very strong 
+electric field in each hole leading to high ionization and amplification.
 
@@
 showed that with the perpendicular 5~T field, we would have a Lorentz angle of 
-about 23$^\circ$ with this mixture. This is already significant and a heavier
-gas would have larger angle increasing significantly
+about 23$^\circ$ with this gas mixture. This is already a significant angle,
+a heavier gas would have larger angle increasing significantly
 the length of the drift paths as the electron would 
@@
 supporting cylinders that could be installed independently in the RTPC after 
-all gluing and soldering operations.  Because the rigidity of the high 
-rigidity of the GEM foil, the structure was selfsupporting and only the 
+all gluing and soldering operations. The rigidity of the GEM foil is enough
+for the structure to be selfsupporting and only the 
 backward part of the cylinder was fixed to the main mechanical structure. This 
@@
 
-{\bf \color{red} The use of the term TDC is improper and should be removed
-everywhere. Replace by T.}
-
-Two quantities are recorded at the readout board, 
-time (T) and signal amplitude (ADC). The timing information is used to infer 
-the origin of the charge and then the trajectory of the detected particle
+Two quantities are recorded at the readout board, time (T) and signal amplitude 
+(ADC). The timing information is used to infer the origin of the charge and 
+then the trajectory of the detected particle
 resulting in momentum measurement. Going from a collection of 
@@
 
-\bibitem{proposal}
-   K.Hafidi et al., Deeply virtual Comton scattering off $^{4}$He, Jlab 
-   proposal to PAC33 (2007).
-
 \bibitem{DCref}
@@
    Efficaces polaris{\'e}es et non polaris{\'e}es, IPNO-Thesis, 2007.
+
+\bibitem{proposal1}
+   G Asryan et al., Meson spectroscopy in the Coherent Production on $^{4}$He with CLAS, Jlab 
+   proposal to PAC31 (2007).
+
+\bibitem{proposal2}
+   K. Hafidi et al., Deeply virtual Comton scattering off $^{4}$He, Jlab 
+   proposal to PAC33 (2008).
 

### 2017-06-01 eg6-letters/NIM/EG6_RTPC_NIM.tex

@@
 inverting the RTPC signals polarity -- from negative to positive -- to match the 
-requirements of the subsequent readout system, and driving the 6m long ribbon 
+requirements of the subsequent readout system, and driving the 6~m long ribbon 
 cable that connects to it.
@@
 pulse time (T). Since pulse time was obtained as the time-stamp of the first 
-sample above threshold, referred to to the trigger time, the resolution is 
-equivalent to the ALTRO sampling time, 100~ns.
+sample above threshold, the resolution is equivalent to the ALTRO sampling 
+time, 100~ns.
 
@@
 
-Two quantities are recorded at the readout board, time (T) and signal amplitude 
-(ADC). The timing information is used to infer the origin of the charge and 
+The timing information is used to infer the origin of the charge and 
 then the trajectory of the detected particle
@@
 calculated using the MAGBOLTZ~\cite{MAGBOLTZ} program, then refined using
-data to account for variations of the run conditions. We still always assume 
+data to account for variations of the run conditions. We always assume 
 cylindrical symmetry in the chamber for the calibration, such that none of
@@
 pads, but cylindrical symmetry insures they always travel the same 
-distance. By identifying the maximum time T measured, we can infer the drift 
+distance. By identifying the maximum time measured ($T_{Max}$), we can infer the drift 
 speed of the electrons in the RTPC.\\

### 2017-06-02 eg6-letters/NIM/EG6_RTPC_NIM.tex
Edits from RD to NIM

@@
 such that drifting electrons are pushed away from the beam line. These electrons 
-are amplified by three layers of curved GEMs and detected by the readout system 
+are amplified by three layers of curved Gas Electron Multiplier 
+(GEM)~\cite{gem_sauli} and detected by the readout system 
 on the external shell of the detector as illustrated in the figure~\ref{fig:RTPC_1_4}. The CLAS 
@@
    \item The drift region is filled with the same Ne-DME gas mixture and extends 
-      from the cathode to the first Gas Electron Multiplier(GEM), 60 mm away 
+      from the cathode to the first GEM, 60 mm away 
       from the beam axis. The average electric field in this region is about 550~V/cm 
@@
 Due to the non perfect experimental conditions, in particular variations in the 
-gas mixture\footnote{It was noted during the experiment that leaks appeared
+gas mixture~\footnote{It was noted during the experiment that leaks appeared
 and the gas flow had to be increased in few occasions to compensate for this.}, 
@@
 chamber. Moreover, the 4 $\mu$m foil used as a cathode is easily deformed, such
-that we expect the geometry accuracy to be around the millimeter precision. 
-These problems, already 
+that we expect the geometry accuracy to be of few millimeters, directly impacting 
+our knowledge of the electric field. These problems, already 
 encountered for the BoNuS RTPC calibration~\cite{BONUS-NIM}, motivated the 
-acquisition of specific calibration runs. These are taken with a lower energy 
+acquisition of specific calibration runs. These were taken with a lower energy 
 electron beam (1.20 and 1.27 GeV) to enhance the cross section of the elastic 
-process ($e^{4}$He$\rightarrow e^{4}$He). In this process, the measurement of
-electron kinematics allows to calculate the Helium nucleus kinematic. It is
+scatering ($e^{4}$He$\rightarrow e^{4}$He). In this process, the measurement of
+the electron kinematic allows to calculate the Helium nucleus kinematic. It is
 by comparing this calculated kinematic to the measured one that we fine tune
@@
 
-The drift paths are ajusted using a set of identified elastic events 
-from our lower beam energy run. Based on the kinematic of the electrons in
-these events, we generate the helium nucleus in a GEANT4 
-simulation~\cite{GEANT4} of our RTPC. Then we compare the calculated GEANT4 trajectory of 
-the Helium nuclei to the hits measured in the chamber.
-
-Because of the 
+The drift paths are ajusted using a set of identified elastic events. We generate 
+a helium nucleus in a GEANT4 simulation~\cite{GEANT4} of our RTPC for each event
+based on the measured electron kinematic. Then, we compare the simulated trajectory of 
+the Helium nuclei to the hits measured in the chamber. Because of the 
 magnetic field, the drift paths are not linear in the RTPC. So to perform the extraction, 
@@
 
-At the end of the extraction procedure, where we work in a polar coordinate 
-system ($R$,$\phi$), the azimuthal difference between the detection pad and 
+At the end of the extraction procedure, the azimuthal difference between the detection pad and 
 the ionization point ($\Delta\phi$) is extracted as a function of time. 
@@
 1.269 GeV data from the end of the run period (shown in blue on 
-figure~\ref{fig:Drift_run_number_1}). Strangely, we found very similar drift paths
+figure~\ref{fig:Drift_run_number_1}). Interestingly, we found very similar drift paths
 for the two data sets and concluded that any changes in the system only
@@
 compared simulation to experiment on an event by event basis as shown in 
-figure~\ref{fig:EVENT_adc_tdc}. In this step, the gain for each pad is calculated 
+Figure~\ref{fig:EVENT_adc_tdc}. In this step, the gain for each pad is calculated 
 as the ratio of the measured ADCs to the simulated deposited energy.  
@@
 \section{Performance Studies}\label{sec_perfor}
+
 The previous discussions have shown that the two modules of the RTPC have 
-slightly different yield, however this yield should not be linked to a 
-different performance of the RTPC. The differences are mainly due to 
-complicated convolution of CLAS and the RTPC acceptances. We measured the 
-efficiency of the RTPC using the elastic scattering on $^4$He, where the 
-exclusive elastic yield is compared to the inclusive yield for the two modules 
-of the detector. Here the inclusive yields are the number of electrons in the 
-elastic invariant mass peak whose corresponding elastically scattered $^4$He 
-would have been in the acceptance of the RTPC, and the exclusive yields require 
-the additional detection of the $^4$He. As a result, we found that the left and 
+slightly different behavior and give also different particle yield. However, 
+this should not necessarily be linked to a different performance of the RTPC. 
+Indeed, there is a complicated convolution of CLAS and the RTPC acceptances 
+that can significantly affect the yields and the kinematic of the detected 
+particles. To clarify this question, we measured the 
+efficiency of the RTPC using the elastic scattering on $^4$He, by comparing the 
+ the inclusive yield based on electron detection only to the exclusive elastic 
+yield where we also detect the Helium recoil. We present in 
+Figure~\ref{fig:rtpc_eff} the results for the two modules 
+of the detector. We observe that the left and 
 the right modules have similar efficiencies except near the target windows, as 
@@
 
-We reported on the construction, operation and calibration of a small RTPC 
-designed to measure helium-4 nuclei in high rate environnement. The operation
+We reported on the construction, operation and calibration of a small GEM based RTPC 
+designed to measure helium-4 nuclei in a high rate environnement. The operation
 of the detector was successful and allowed to detect helium nuclei at a rate
-of several kHz in coincidence with the detection of high energy electrons and 
+of 3.1 kHz in coincidence with the detection of high energy electrons and 
 photons in the CLAS spectrometer.
@@
 
+\bibitem{gem_sauli}
+   F. Sauli, GEM: A new concept for electron amplification in gas detectors, 
+   Nucl. Instr. and Meth. A 386, 531 (1997).
+
 \bibitem{GEM_ref}
@@
    accelerators, Phys. Rev. D 86, 010001, pages: 339-368, 2012.
+
+\bibitem{MAGBOLTZ}
+   S. Biagi, Monte Carlo simulation of electron drift and diffusion in counting 
+   gases under the influence of electric and magnetic fields, Nucl.  Inst. and 
+   Meth. in Phy. Res. A, vol. 421, pp. 234-240, 1999.
+
+\bibitem{BONUS-NIM}
+   Howard C. Fenker et al., BoNuS: Development and Use of a Radial TPC using 
+   Cylindrical GEMs, Nucl. Instrum. Meth. A592, 273-286 (2008)
 
@@
 
-\bibitem{gem_sauli}
-   F. Sauli, GEM: A new concept for electron amplification in gas detectors, 
-   Nucl. Instr. and Meth. A 386, 531 (1997).
-
-\bibitem{BONUS}
-   S. Tkachenko et al., Measurement of the nearly free neutron structure 
-   function using spectator tagging in inelastic $^{2}H(e,e'p)X$ scattering 
-   with CLAS,	Phys. Rev. C 89, 045206 (2014).
-
-\bibitem{MAGBOLTZ}
-   S. Biagi, Monte Carlo simulation of electron drift and diffusion in counting 
-   gases under the influence of electric and magnetic fields, Nucl.  Inst. and 
-   Meth. in Phy. Res. A, vol. 421, pp. 234-240, 1999.
-
 \bibitem{GEANT4}
@@
 
-\bibitem{BONUS-NIM}
-Howard C. Fenker et al., BoNuS: Development and Use of a Radial TPC using Cylindrical GEMs, Nucl. Instrum. Meth. A592, 273-286 (2008)
 \end{thebibliography}

### 2017-06-02 eg6-letters/NIM/author_list.tex
some fixing
Edits from RD to NIM

--- 2016-09-19 eg6-letters/eg6-letters/NIM/author_list.tex
@@
 \author{R.~Dupr\'e}   \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France}
+\author{S.~Stepanyan} \affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
+\author{M.~Hattawy}   \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France}
 \author{N.~Baltzell}  \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
+\author{S.~Bueltmann} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
+\author{A.~Celentano} \affiliation{INFN, Sezione di Genova, 16146 Genova, Italy}
+\author{R.~De~Vita} \affiliation{INFN, Sezione di Genova, 16146 Genova, Italy}
 \author{K.~Hafidi}    \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}
-\author{M.~Hattawy}   \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France}
-\author{S.~Stepanyan} \affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
+\author{S.~Kuhn} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
+
 %\author{} \affiliation{}
@@
 
-\collaboration{The JLab-CLAS Collaboration} 
+\collaboration{The CLAS Collaboration} 
 %
-\vskip 0.25cm
+%\vskip 2.0cm

### 2017-06-02 eg6-letters/NIM/EG6_RTPC_NIM.tex
some cleaning

--- 2017-06-01 eg6-letters/NIM/EG6_RTPC_NIM.tex
@@
 are amplified by three layers of curved GEMs and detected by the readout system 
-on the external shell of the detector as illustrated in the figure~\ref{fig:RTPC_1_4}. The CLAS 
-RTPC is segmented into two halves with independent GEM amplification systems that 
-cover about 80\% of the azimuthal angle.
+on the external shell of the detector as illustrated in the 
+figure~\ref{fig:RTPC_1_4}. The CLAS RTPC is segmented into two halves with 
+independent GEM amplification systems that cover about 80\% of the azimuthal 
+angle.
 
@@
 \includegraphics[scale=0.70]{fig/GEM_photo.jpg}
-\caption{Picture of a GEM foil similar to the one used for our RTPC. {\color{red} Source?}} 
-\label{fig:GEMs}
+\caption{Picture of a typical GEM foil similar to the one used for our RTPC.  
+{\color{red} Source?}} \label{fig:GEMs}
 \end{figure}
 
-The GEM technology has been chosenfor its flexibility as it
+The GEM technology has been chosen for its flexibility as it
 allows for a curved amplification surface. Also, GEMs are known to rarely create 
@@
 The drift gas used in the experiment is a 80-20\% neon-DME mixture, this choice 
-has been made in order to balance the energy deposit with a reasonnable
+has been made in order to balance the energy deposit with a reasonable
 Lorentz angle. Calculations using the MAGBOLTZ program~\cite{MAGBOLTZ} 
@@
 keep the material budget small in the forward region where we detect other 
-particles in subsequent detectors. We successfuly realized these prerequisites 
+particles in subsequent detectors. We successfully realized these prerequisites 
 by using fiber glass rings glued to each ends of the GEM foils to form self 
@@
 all gluing and soldering operations. The rigidity of the GEM foil is enough
-for the structure to be selfsupporting and only the 
-backward part of the cylinder was fixed to the main mechanical structure. This 
-design only left a light fiberglass ring in the forward region, reducing to a 
-minimum secondary interactions.
+for the structure to be self-supporting and only the backward part of the 
+cylinder was fixed to the main mechanical structure. This design only left a 
+light fiberglass ring in the forward region, reducing to a minimum secondary 
+interactions.
 
@@
 configuration permits to reduce the dead time associated to FEC readout 
-operations, scaling linearly with the number of boards in the crate. During 
-the 2009 run, the system was succesfully operated with a DAQ rate of 3.1 kHz, 
-with a live time of $70 \%$.
+operations, scaling linearly with the number of boards in the crate. During the 
+2009 run, the system was successfully operated with a DAQ rate of 3.1 kHz, with 
+a live time of $70 \%$.
 
@@
 cylindrical symmetry in the chamber for the calibration, such that none of
-the parameters depend on the asimuthal angle $\phi$. The initial MAGBOLTZ
+the parameters depend on the azimuthal angle $\phi$. The initial MAGBOLTZ
 calibration was improved through several iterations of the
@@
 
-The drift paths are ajusted using a set of identified elastic events 
-from our lower beam energy run. Based on the kinematic of the electrons in
-these events, we generate the helium nucleus in a GEANT4 
-simulation~\cite{GEANT4} of our RTPC. Then we compare the calculated GEANT4 trajectory of 
-the Helium nuclei to the hits measured in the chamber.
+The drift paths are adjusted using a set of identified elastic events from our 
+lower beam energy run. Based on the kinematic of the electrons in these events, 
+we generate the helium nucleus in a GEANT4 simulation~\cite{GEANT4} of our 
+RTPC. Then we compare the calculated GEANT4 trajectory of the Helium nuclei to 
+the hits measured in the chamber.
 
-Because of the 
-magnetic field, the drift paths are not linear in the RTPC. So to perform the extraction, 
-we make a first approximation with a linear dependence between the radius of 
-emission and the time of detection, and then refine our result. As it happens, 
-the curvature is minimal and this process converge already on the second 
-iteration.
+Because of the magnetic field, the drift paths are not linear in the RTPC. So 
+to perform the extraction, we make a first approximation with a linear 
+dependence between the radius of emission and the time of detection, and then 
+refine our result. As it happens, the curvature is minimal and this process 
+converge already on the second iteration.
 
@@
 
-The second is a coherent noise affecting about 25\% of the pramplifiers, where the signature is simultaneous hits in most of the 16 channels in a preamp group.
-An event-based technique to identify and remove it was developed based on counting simultaneous hits in preamp group, and, if sufficiently large, perform a dynamic pedestal subtraction based on the average ADC of the channels' neighbors within the preamp group.
+The second is a coherent noise affecting about 25\% of the preamplifiers, where 
+the signature is simultaneous hits in most of the 16 channels in a preamp 
+group.   An event-based technique to identify and remove it was developed based 
+on counting simultaneous hits in preamp group, and, if sufficiently large, 
+perform a dynamic pedestal subtraction based on the average ADC of the 
+channels' neighbors within the preamp group.
 
-The sources of these effects were not determined, but rejection techniques allowed to reconstruct 10\% more good tracks, with no significant loss, and recover 70 channels that were previously ignored due to excessive noise levels.
+The sources of these effects were not determined, but rejection techniques 
+allowed to reconstruct 10\% more good tracks, with no significant loss, and 
+recover 70 channels that were previously ignored due to excessive noise levels.
 
@@
 \includegraphics[scale=0.27]{fig/noisy_pad_after_rejection2.png}
-\caption{The ADC vs.
-T spectrum for an example noisy channel before (top) and after (bottom) noise rejection algorithms.
-Only hits associated with tracks are included, and the selection of events and tracks is the same in both plots.}
+\caption{The ADC vs. T spectrum for an example noisy channel before (top) and 
+after (bottom) noise rejection algorithms.  Only hits associated with tracks 
+are included, and the selection of events and tracks is the same in both 
+plots.}
 \label{fig:noise}
@@
 We reported on the construction, operation and calibration of a small RTPC 
-designed to measure helium-4 nuclei in high rate environnement. The operation
+designed to measure helium-4 nuclei in high rate environment. The operation
 of the detector was successful and allowed to detect helium nuclei at a rate

### 2017-06-06 eg6-letters/NIM/EG6_RTPC_NIM.tex
add the reference for figure 3
Check typos

--- 2017-06-02 eg6-letters/NIM/EG6_RTPC_NIM.tex
@@
     of charged particles, thus allowing momentum measurement with the DC tracking information.
- \item Cherenvkov Counters (CC) to distinguish electrons from other negative 
+ \item Cerenkov Counters (CC) to distinguish electrons from other negative 
     particles, such as pions, at lower energies~\cite{CCref} (in pink).
@@
 
-The GEM technology has been chosenfor its flexibility as it
+The GEM technology has been chosen for its flexibility as it
 allows for a curved amplification surface. Also, GEMs are known to rarely create 
@@
 all gluing and soldering operations. The rigidity of the GEM foil is enough
-for the structure to be selfsupporting and only the 
+for the structure to be self supporting and only the 
 backward part of the cylinder was fixed to the main mechanical structure. This 
@@
 The readout system is based on the Front End Electronic (FEE) boards originally 
-developed for the ALICE TPC readout system at Cern~\cite{ALICE-FEE}. Each 
+developed for the ALICE TPC readout system at CERN~\cite{ALICE-FEE}. Each 
 readout channel is made of three main components: a charge sensitive, low 
@@
 and for data readout. Each RCU can handle up to 25 FECs. Communication 
-between ROC and FECs is performed trough a custom backplane, implementing 
+between ROC and FECs is performed trough a custom back-plane, implementing 
 a low-voltage signal bus. The RCU communicates with the CLAS DAQ system 
@@
 operations, scaling linearly with the number of boards in the crate. During 
-the 2009 run, the system was succesfully operated with a DAQ rate of 3.1 kHz, 
+the 2009 run, the system was successfully operated with a DAQ rate of 3.1 kHz, 
 with a live time of $70 \%$.
@@
 electron beam (1.20 and 1.27 GeV) to enhance the cross section of the elastic 
-scatering ($e^{4}$He$\rightarrow e^{4}$He). In this process, the measurement of
+scattering ($e^{4}$He$\rightarrow e^{4}$He). In this process, the measurement of
 the electron kinematic allows to calculate the Helium nucleus kinematic. It is
@@
 
-The drift paths are ajusted using a set of identified elastic events. We generate 
+The drift paths are adjusted using a set of identified elastic events. We generate 
 a helium nucleus in a GEANT4 simulation~\cite{GEANT4} of our RTPC for each event
@@
 
-The second is a coherent noise affecting about 25\% of the pramplifiers, where the signature is simultaneous hits in most of the 16 channels in a preamp group.
+The second is a coherent noise affecting about 25\% of the pre-amplifiers, where the signature is simultaneous hits in most of the 16 channels in a preamp group.
 An event-based technique to identify and remove it was developed based on counting simultaneous hits in preamp group, and, if sufficiently large, perform a dynamic pedestal subtraction based on the average ADC of the channels' neighbors within the preamp group.
@@
 We reported on the construction, operation and calibration of a small GEM based RTPC 
-designed to measure helium-4 nuclei in a high rate environnement. The operation
+designed to measure helium-4 nuclei in a high rate environment. The operation
 of the detector was successful and allowed to detect helium nuclei at a rate
@@
 
-\input acknowledgement.tex
+\input acknowledgment.tex
 

### 2017-06-06 eg6-letters/NIM/EG6_RTPC_NIM.tex

@@
 such that drifting electrons are pushed away from the beam line. These electrons 
-are amplified by three layers of curved Gas Electron Multiplier 
-(GEM)~\cite{gem_sauli} and detected by the readout system 
-on the external shell of the detector as illustrated in the figure~\ref{fig:RTPC_1_4}. The CLAS 
-RTPC is segmented into two halves with independent GEM amplification systems that 
-cover about 80\% of the azimuthal angle.
+are amplified by three layers of curved GEMs and detected by the readout system 
+on the external shell of the detector as illustrated in the 
+figure~\ref{fig:RTPC_1_4}. The CLAS RTPC is segmented into two halves with 
+independent GEM amplification systems that cover about 80\% of the azimuthal 
+angle.
 
@@
    \item The readout board has an internal radius of 69~mm and collects charge
-     from the GEMs. Preamplifiers are plugged directly on its outer side and
+     from the GEMs. Pre-amplifiers are plugged directly on its outer side and
      transmit the signal to the data acquisition electronics.
@@
 \includegraphics[scale=0.70]{fig/GEM_photo.jpg}
-\caption{Picture of a GEM foil similar to the one used for our RTPC. {\color{red} Source?}} 
+\caption{Image of a typical GEM foil similar to the one used for our RTPC 
+\cite{GEM_ref_pic}.}
+
    \label{fig:GEMs}
@@
 all gluing and soldering operations. The rigidity of the GEM foil is enough
-for the structure to be self supporting and only the 
-backward part of the cylinder was fixed to the main mechanical structure. This 
-design only left a light fiberglass ring in the forward region, reducing to a 
-minimum secondary interactions.
+for the structure to be self-supporting and only the backward part of the 
+cylinder was fixed to the main mechanical structure. This design only left a 
+light fiberglass ring in the forward region, reducing to a minimum secondary 
+interactions.
 
@@
 configuration permits to reduce the dead time associated to FEC readout 
-operations, scaling linearly with the number of boards in the crate. During 
-the 2009 run, the system was successfully operated with a DAQ rate of 3.1 kHz, 
-with a live time of $70 \%$.
+operations, scaling linearly with the number of boards in the crate. During the 
+2009 run, the system was successfully operated with a DAQ rate of 3.1 kHz, with 
+a live time of $70 \%$.
 
@@
 
-The drift paths are adjusted using a set of identified elastic events. We generate 
-a helium nucleus in a GEANT4 simulation~\cite{GEANT4} of our RTPC for each event
-based on the measured electron kinematic. Then, we compare the simulated trajectory of 
-the Helium nuclei to the hits measured in the chamber. Because of the 
-magnetic field, the drift paths are not linear in the RTPC. So to perform the extraction, 
-we make a first approximation with a linear dependence between the radius of 
-emission and the time of detection, and then refine our result. As it happens, 
-the curvature is minimal and this process converge already on the second 
-iteration.
+The drift paths are adjusted using a set of identified elastic events from our 
+lower beam energy run. Based on the kinematic of the electrons in these events, 
+we generate the helium nucleus in a GEANT4 simulation~\cite{GEANT4} of our 
+RTPC. Then we compare the calculated GEANT4 trajectory of the Helium nuclei to 
+the hits measured in the chamber.
+
+Because of the magnetic field, the drift paths are not linear in the RTPC. So 
+to perform the extraction, we make a first approximation with a linear 
+dependence between the radius of emission and the time of detection, and then 
+refine our result. As it happens, the curvature is minimal and this process 
+converge already on the second iteration.
 
@@
 
-The second is a coherent noise affecting about 25\% of the pre-amplifiers, where the signature is simultaneous hits in most of the 16 channels in a preamp group.
-An event-based technique to identify and remove it was developed based on counting simultaneous hits in preamp group, and, if sufficiently large, perform a dynamic pedestal subtraction based on the average ADC of the channels' neighbors within the preamp group.
+The second is a coherent noise affecting about 25\% of the preamplifiers, where 
+the signature is simultaneous hits in most of the 16 channels in a preamp 
+group.   An event-based technique to identify and remove it was developed based 
+on counting simultaneous hits in preamp group, and, if sufficiently large, 
+perform a dynamic pedestal subtraction based on the average ADC of the 
+channels' neighbors within the preamp group.
 
-The sources of these effects were not determined, but rejection techniques allowed to reconstruct 10\% more good tracks, with no significant loss, and recover 70 channels that were previously ignored due to excessive noise levels.
+The sources of these effects were not determined, but rejection techniques 
+allowed to reconstruct 10\% more good tracks, with no significant loss, and 
+recover 70 channels that were previously ignored due to excessive noise levels.
 
@@
 
-We reported on the construction, operation and calibration of a small GEM based RTPC 
-designed to measure helium-4 nuclei in a high rate environment. The operation
+We reported on the construction, operation and calibration of a small RTPC 
+designed to measure helium-4 nuclei in high rate environment. The operation
 of the detector was successful and allowed to detect helium nuclei at a rate
@@
 
-\bibitem{gem_sauli}
-   F. Sauli, GEM: A new concept for electron amplification in gas detectors, 
-   Nucl. Instr. and Meth. A 386, 531 (1997).
+\bibitem{GEM_ref_pic}
+   F. Sauli, The Gas Electron Multiplier (GEM): Operating Principles and 
+   Applications, Nucl. Instr. and Meth, A805(2016)2
 

### 2017-06-06 eg6-letters/NIM/author_list.tex
Add Eric et Yohann to authors

@@
 \author{S.~Kuhn} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
-
+\author{Y.~Perrin} \affiliation{LPSC, Universit\'e Grenoble-Alpes, CNRS/IN2P3, Grenoble, France}
+\author {E.~Voutier} \affiliation{Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France}\affiliation{LPSC, Universit\'e Grenoble-Alpes, CNRS/IN2P3, Grenoble, France}
 %\author{} \affiliation{}

### 2017-06-06 eg6-letters/NIM/author_list.tex
Add authors

--- 2017-06-02 eg6-letters/NIM/author_list.tex
@@
 \author{R.~De~Vita} \affiliation{INFN, Sezione di Genova, 16146 Genova, Italy}
+\author{H.~Egiyan} \affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
 \author{K.~Hafidi}    \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}
 \author{S.~Kuhn} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
-
+\author{Y.~Perrin} \affiliation{LPSC, Universit\'e Grenoble-Alpes, CNRS/IN2P3, Grenoble, France}
+\author{B.~Torayev} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
+\author{E.~Voutier} \affiliation{Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France}\affiliation{LPSC, Universit\'e Grenoble-Alpes, CNRS/IN2P3, Grenoble, France}
 %\author{} \affiliation{}

### 2017-06-08 eg6-letters/NIM/author_list.tex
Add author
Various fixes for NIM and coherent letter

@@
 
-\author{R.~Dupr\'e}   \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France}
+\author{R.~Dupr\'e} \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}
 \author{S.~Stepanyan} \affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
-\author{M.~Hattawy}   \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France}
+\author{M.~Hattawy} \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}
 \author{N.~Baltzell} \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
@@
 \author{H.~Egiyan} \affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
+\author{H.~Fenker} \affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
 \author{K.~Hafidi} \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}
@@
 \author{B.~Torayev} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
-\author{E.~Voutier} \affiliation{Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France}\affiliation{LPSC, Universit\'e Grenoble-Alpes, CNRS/IN2P3, Grenoble, France}
+\author{E.~Voutier} \affiliation{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}\affiliation{LPSC, Universit\'e Grenoble-Alpes, CNRS/IN2P3, Grenoble, France}
 %\author{} \affiliation{}

### 2017-06-08 eg6-letters/coherent/dvcs_he4_prl.tex
add Kim's acknowledgment
Various fixes for NIM and coherent letter

@@
 which embed the partonic structure of the hadron. The GPDs depend on the three 
-variables $x$, $\xi$, and $t$. $\xi$ relates to the Bjorken variable $x_{B}$: $\xi\approx 
-{{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M_N\nu}$, $\nu$ is the energy of the virtual photon, and 
-$M_N$ is the nucleon mass. $x$ is the quark's internal loop momentum 
+variables $x$, $\xi$, and $t$. $\xi$ relates to the Bjorken variable 
+$x_{A}$: $\xi\approx {{x_A}\over{2-x_A}}$, where $x_A=\frac{Q^2}{2M_A\nu}$, 
+$\nu$ is the energy of the virtual photon, and 
+$M_A$ is the nuclei mass. $x$ is the quark's internal loop momentum 
 fraction and cannot be accessed experimentally in DVCS. We in fact measure 
@@
 \end{equation}
-Explicit expressions of the kinematic factors $\alpha_i$ are derived in
+Explicit expressions of the kinematic factors $\alpha_i$ are derived 
+from expressions in
 Ref.~\cite{Belitsky:2008bz} and are functions of Fourier harmonics in the 
@@
 Energy Award DE-FG02-07ER41528.
+
+Kim- The National Research Foundation of Korea
 

### 2017-06-08 eg6-letters/coherent/dvcs_he4_prl.tex
Add full CLAS author list

@@
 
-\newcommand*{\ANL}{Argonne National Laboratory, Argonne, Illinois 60439}
-\newcommand*{\ANLindex}{1}
-\affiliation{\ANL}
-\newcommand*{\ORSAY}{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}
-\newcommand*{\ORSAYindex}{2}
-\affiliation{\ORSAY}
-\newcommand*{\JLAB}{Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606}
-\newcommand*{\JLABindex}{3}
-\affiliation{\JLAB}
-\newcommand*{\ODU}{Old Dominion University, Norfolk, Virginia 23529}
-\newcommand*{\ODUindex}{4}
-\newcommand*{\INFNGE}{INFN, Sezione di Genova, 16146 Genova, Italy}
-\newcommand*{\INFNGEindex}{5}
-\newcommand*{\LPSC}{LPSC, Universit\'e Grenoble-Alpes, CNRS/IN2P3, Grenoble, France}
-\newcommand*{\LPSCindex}{6}
-\newcommand*{\UTFSM}{Universidad T\'{e}cnica Federico Santa Mar\'{i}a, Casilla 110-V Valpara\'{i}so, Chile}
-\newcommand*{\UTFSMindex}{7}
-\newcommand*{\MISS}{Mississippi State University, Mississippi State, MS 39762-5167}
-\newcommand*{\MISSindex}{8}
-\newcommand*{\VIRGINIA}{University of Virginia, Charlottesville, Virginia 22901}
-\newcommand*{\VIRGINIAindex}{9}
-\newcommand*{\VIRGINIATECH}{Virginia Polytechnic Institute and State University, Blacksburg, Virginia, 24061}
-\newcommand*{\VIRGINIATECHindex}{10}
-
-\newcommand*{\NOWJLAB}{Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606}
-\newcommand*{\NOWODU}{Old Dominion University, Norfolk, Virginia 23529}
- %%%%%%%%%%%%%%% END OF Latex Macros for institute addresses  %%%%%%%%%%%%%%%%%%%%%%%%%
-
-\author {M.~Hattawy}
-\affiliation{\ANL}
-\affiliation{\ORSAY}
-\author {N.A.~Baltzell} 
-\affiliation{\ANL}
-\affiliation{\JLAB}
-\author {R.~Dupr\'{e}} 
-\email[corresponding author: ]{dupre@ipno.in2p3.fr}
-\affiliation{\ANL}
-\affiliation{\ORSAY}
-\author {K.~Hafidi} 
-\affiliation{\ANL}
-\author{S.~Stepanyan}
-\affiliation{\JLAB}
-\author {S.~Bultmann} 
-\affiliation{\ODU}
-\author{R.~De~Vita} 
-\affiliation{\INFNGE}
-\author {A.~El~Alaoui} 
-\affiliation{\ANL}
-\affiliation{\UTFSM}
-\author {L.~El~Fassi} 
-\affiliation{\MISS}
-\author{H.~Egiyan}
-\affiliation{\JLAB}
-\author{F.X.~Girod} 
-\affiliation{\JLAB}
-\author {M.~Guidal} 
-\affiliation{\ORSAY}
-\author{D.~Jenkins}
-\affiliation{\VIRGINIATECH}
-\author{S.~Liuti} 
-\affiliation{\VIRGINIA}
-\author{Y.~Perrin}
-\affiliation{\LPSC}
-\author {B.~Torayev} 
-\affiliation{\ODU}
-\author {E.~Voutier} 
-\affiliation{\LPSC}
-\affiliation{\ORSAY}
-
-\collaboration{The CLAS Collaboration}
-\noaffiliation
-
+\input author_list.tex
 %

### 2017-06-08 eg6-letters/coherent/dvcs_he4_prl.tex
Acknowlegments updated.

@@
 %Acknowledgments
-
-We acknowledge the staff of the Accelerator and Physics Divisions at Jefferson 
-Lab for making this experiment possible.
-
-Dave Ireland- the United Kingdom's Science and Technology Facilities Council
-
-Lamiaa- the Physics and Astronomy Department and the Office of Research and 
-Economic Development at Mississippi State University, and the US Department of 
-Energy Award DE-FG02-07ER41528.
-
-Kim- The National Research Foundation of Korea
-
-- This work is supported by the U.S.  Department of Energy, Office of Science, 
-Office of Nuclear Physics, under contracts DE-AC02-06CH11357 and 
-DE-AC05-06OR23177.
+The authors thank the staff of the Accelerator and Physics Divisions at the 
+Thomas Jefferson National Accelerator Facility who made this experiment 
+possible. This work was supported in part by the Chilean Comisi\'on Nacional 
+de Investigaci\'on Cient\'ifica y Tecnol\'ogica (CONICYT), the Italian 
+Instituto Nazionale di Fisica Nucleare, the French Centre National de la 
+Recherche Scientifique, the French Commissariat \`a l'Energie Atomique, the 
+U.S. Department of Energy, the UK Science and Technology Facilities Council 
+(STFC), the Scottish Universities Physics Alliance (SUPA), the National 
+Research Foundation of Korea, and the Office of Research and Economic 
+Development at Mississippi State University.  The author (M.~Hattawy) also 
+acknowledge the support of the Consulat G\'en\'eral de France \`a J\'erusalem. 
+The Southeastern Universities Research Association operates the Thomas 
+Jefferson National Accelerator Facility for the United States Department of 
+Energy under contract DE-AC05-06OR23177.
 

### 2017-06-08 eg6-letters/coherent/dvcs_he4_prl.tex
Implementing M.Garcon's comments

@@
 real and imaginary parts of the only $^4$He Compton form factor, $\cal H_A$. 
-This pioneering measurement of coherent deeply virtual Compton scattering on 
+This first measurement of coherent deeply virtual Compton scattering on 
 the $^4$He nucleus, with a fully exclusive final state via nuclear recoil 
@@
 RTPC was a $20$-cm-long cylinder with a diameter of $15$ cm, positioned in the 
-solenoid magnet. In the center of the RTPC was the target, a $25$-cm-long 
+solenoid magnet. In the center of the RTPC was the target cell, a $25$-cm-long 
 and $6$-mm-diameter Kapton tube with $27$-$\mu$m-thick walls filled with 
@@
 two photons. About 3200 events passed all these requirements, their kinematic 
-distributions are shown in Fig.~\ref{fig:kin-coverage}.
+distributions\footnote{We use here and for other results 
+$x_B =\frac{Q^2}{2M_N\nu}$ with $M_N$ the proton mass instead of $x_A$ for 
+easier comparison with proton data.} are shown in Fig.~\ref{fig:kin-coverage}.
 
@@
 section for positive (negative) beam helicity.
+
 In this ratio, luminosity normalization and
@@
 photons includes a sum of the amplitudes of these two processes. The BH 
-amplitude depends on the target form factors, which are well known in this
+amplitude depends on the target elastic form factors, which are well known in this
 kinematic region, while the DVCS amplitude depends on the GPDs we are trying to
@@
 in Refs.~\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, $A_{LU}$ 
-for a spin-zero hadron can be expressed as
+for a spin-zero hadron can be expressed at leading-twist as
 \begin{equation}
@@
 \includegraphics[width=8.5cm]{figs/F_Coherent_CFF.pdf}
-\caption{The model-independent extraction of the imaginary (top panel) and
+\caption{The leading-twist model-independent extraction of the imaginary (top panel) and
 real (bottom panel) parts of the $^4$He CFF $\mathcal{H}_A$, as a function of

### 2017-06-09 eg6-letters/NIM/EG6_RTPC_NIM.tex
Implement remark from Howard F.

@@
 
-In this paper we report the design, calibration, and performance of the radial 
-TPC, organized as follows. In section \ref{sec_design}, we detail the design 
-and internal structure of the detector. Section \ref{sec_readout} describes 
-the properties of the read-out system. Calibration 
-strategies are discussed in section \ref{sec_calib}. Finally, the performances
+The original design of the RTPC~\cite{BONUS-NIM} was developed for the BoNuS 
+experiment at Jefferson Lab which took data in CLAS in 2005. An enhanced design 
+for use in the 2009 DVCS experiment is described in section \ref{sec_design} 
+of this paper. Significant improvements were made to the RTPC mechanical 
+structure and fabrication technique that both increased the acceptance and 
+reduced the amount of material in the path of the outgoing particles. The 
+data acquisition system described in section \ref{sec_readout} was reconfigured 
+to increase the event readout rate. The calibration strategy and results for 
+the RTPC are discussed in section \ref{sec_calib}. Finally, the performances
 of the RTPC are described in section \ref{sec_perfor}.
@@
 shows how pads are grouped to 16 channels pre-amplifiers. The pre-amplifier boards, 
-already employed in the BoNuS RTPC \cite{BONUS-NIM}, serve the dual purpose of 
+already employed in the BoNuS RTPC~\cite{BONUS-NIM}, serve the dual purpose of 
 inverting the RTPC signals polarity -- from negative to positive -- to match the 
@@
 of the detector. We observe that the left and 
-the right modules have similar efficiencies except near the target windows, as 
-shown in figure \ref{fig:rtpc_eff}.
+the right modules have similar efficiencies except near the target windows.
 

### 2017-06-09 eg6-letters/NIM/author_list.tex
update author list

@@
 \author{N.~Baltzell} \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
+\author{K.~Hafidi} \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}
 \author{S.~Bueltmann} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
@@
 \author{R.~De~Vita} \affiliation{INFN, Sezione di Genova, 16146 Genova, Italy}
+\author{A.~El~Alaoui} \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Universidad T\'ecnica Federico Santa Mar\'ia, Casilla 110-V Valpara\'iso, Chile}
+\author{L.~El~Fassi} \affiliation{Mississippi State University, Mississippi State, MS 39762-5167}
 \author{H.~Egiyan} \affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
 \author{H.~Fenker} \affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
-\author{K.~Hafidi} \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}
+\author{K.~Kosheleva} \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}
 \author{S.~Kuhn} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
@@
 %\author{} \affiliation{}
-%
 

### 2017-06-09 eg6-letters/coherent/dvcs_he4_prl.tex
Finish M.Garcon comments

@@
 \end{split} \\
-\Im m(&\mathcal{H}_{A}) = H_A(\xi,\xi,t)-H_A(-\xi,\xi,t),
+\Im m(&\mathcal{H}_{A}) = - \pi ( H_A(\xi,\xi,t)-H_A(-\xi,\xi,t)),
 \end{align}
@@
 
-To ensure the interaction occurred at the partonic level and that the DVCS handbag 
-diagram was dominant, we selected events with $Q^{2}$ greater than 
-1~GeV$^{2}$. The exclusivity of the coherent DVCS reaction was ensured by 
+We selected events with $Q^{2}$ greater than 1~GeV$^{2}$ for which the DVCS handbag 
+diagram is believed to be dominant. Then the exclusivity of the reaction was ensured by 
 applying a set of cuts on the following kinematic variables: the coplanarity 
@@
   Phys.\ Rev.\ Lett.\  {\bf 87}, 142302 (2001)
-  doi:10.1103/PhysRevLett.87.142302
   [hep-ph/0106192].
@@
   Eur.\ Phys.\ J.\ A {\bf 19}, 423 (2004)
-  doi:10.1140/epja/i2003-10127-x
   [hep-ph/0307231].
@@
   J.\ Phys.\ G {\bf 32}, 251 (2006)
-  doi:10.1088/0954-3899/32/3/002
   [hep-ph/0509158].

### 2017-06-12 eg6-letters/NIM/EG6_RTPC_NIM.tex
Implement Lamiaa's remarks

@@
 The original design of the RTPC~\cite{BONUS-NIM} was developed for the BoNuS 
-experiment at Jefferson Lab which took data in CLAS in 2005. An enhanced design 
-for use in the 2009 DVCS experiment is described in section \ref{sec_design} 
+experiment at Jefferson Lab which took data in CLAS in 2005. An enhanced design, 
+used in the 2009 DVCS experiment, is described in section \ref{sec_design} 
 of this paper. Significant improvements were made to the RTPC mechanical 
@@
 to increase the event readout rate. The calibration strategy and results for 
-the RTPC are discussed in section \ref{sec_calib}. Finally, the performances
-of the RTPC are described in section \ref{sec_perfor}.
+the RTPC are discussed in section \ref{sec_calib}. Finally, the overall performance
+of the RTPC is described in section \ref{sec_perfor}.
 
@@
 on the external shell of the detector as illustrated in the 
-figure~\ref{fig:RTPC_1_4}. The CLAS RTPC is segmented into two halves with 
+Fig.~\ref{fig:RTPC_1_4}. The CLAS RTPC is segmented into two halves with 
 independent GEM amplification systems that cover about 80\% of the azimuthal 
@@
 
-We detail here the different regions shown in figure~\ref{fig:RTPC_1_4} starting 
-from the beam line and towards larger radius:\\
+We detail here the different regions shown in Fig.~\ref{fig:RTPC_1_4} starting 
+from the beam line towards larger radius:\\
 \begin{itemize}
@@
       region is surrounded by a 4 $\mu$m thick window made of aluminized Mylar 
-      is electronically grounded.
+      that is electronically grounded.
    \item The second gap region extends between 20~mm and 30~mm and is filled with a 
-      gas mixture of 80$\%$ neon and 20$\%$ dimethyl ether (DME). This region 
+      gas mixture of 80$\%$ neon (Ne) and 20$\%$ dimethyl ether (DME). This region 
       is surrounded by a 4~$\mu$m thick window made of aluminized Mylar, which 
@@
 
-The GEM technology has been chosen for its flexibility as it
-allows for a curved amplification surface. Also, GEMs are known to rarely create 
-sparks~\cite{GEM_ref}, which is important when trying to detect 
+The GEM technology has been chosen for the flexibility of the GEM foils,
+which can be easily used to produce a curved amplification surface. Also, 
+GEMs are known to have relatively low sparks rate~\cite{GEM_ref}, which 
+is important when trying to detect 
 highly ionizing slow nuclei that deposit large amount of energy. The GEMs for 
@@
 layer is chemically etched with 50~$\mu$m diameter holes with double-conical 
-shapes as illustrated in figure~\ref{fig:GEMs}. The potential difference 
+shapes as illustrated in Fig.~\ref{fig:GEMs}. The potential difference 
 applied between the two copper layers of the GEM creates a very strong 
@@
 
-The drift gas used in the experiment is a 80-20\% neon-DME mixture, this choice 
+The drift gas used in the experiment is a 80-20\% Ne-DME mixture, this choice 
 has been made in order to balance the energy deposit with a reasonable
@@
 the length of the drift paths as the electron would 
-make a long spiral around the beam line before to reach the GEMs.
+make a long spiral around the beam line to reach the GEMs.
 
-One of the important problematic to develop the radial TPC was to obtain a 
-good support structure of the GEM foils, allowing an easy installation of the 
-GEM in good conditions and with high precision. At the same time, we wanted to 
+One of the important challenge in developing the radial TPC was how to obtain a 
+good support structure of the GEM foils to allow a tractable but highly precise 
+installation of the GEMs. At the same time, we wanted to 
 keep the material budget small in the forward region where we detect other 
@@
 supporting cylinders that could be installed independently in the RTPC after 
-all gluing and soldering operations. The rigidity of the GEM foil is enough
+all gluing and soldering operations. The rigidity of the GEM foils was enough
 for the structure to be self-supporting and only the backward part of the 
@@
 located at the end of the amplification region, 69 mm from the central axis.
-Figure \ref{fig:PADs} shows a schematic drawing of the size and 
+Figure~\ref{fig:PADs} shows a schematic drawing of the size and 
 configuration of the pads. Each readout pad is 5 mm in length and 4.45 mm in 
-width.  The shift between the rows allows to reduce aliasing. Each half of the 
-RTPC has 40 rows and 40 columns of pads. The shaded region in figure~\ref{fig:PADs} 
+width. The shift between the rows permits the reduction of aliasing. Each half of the 
+RTPC has 40 rows and 40 columns of pads. The shaded region in Fig.~\ref{fig:PADs} 
 shows how pads are grouped to 16 channels pre-amplifiers. The pre-amplifier boards, 
@@
 inverting the RTPC signals polarity -- from negative to positive -- to match the 
-requirements of the subsequent readout system, and driving the 6~m long ribbon 
+requirements of the subsequent readout system, and driv the 6~m long ribbon 
 cable that connects to it.
@@
 that implements online-processing algorithms (pedestal subtraction, zero 
-suppression, ad tail cancellation). The amplifier is implemented in a 
+suppression, and tail cancellation). The amplifier is implemented in a 
 fully-analogue ASIC, PASA~\cite{ALICE-PASA}, while the subsequent signal 
@@
 chain is implemented on a single Front End Card (FEC), hosting 128 channels. 
-FECs are hosted in custom crates, mounted close to the detector. A Readout 
-Control Unit (ROC) board is used to distribute the trigger signal to FECs 
-and for data readout. Each RCU can handle up to 25 FECs. Communication 
-between ROC and FECs is performed trough a custom back-plane, implementing 
-a low-voltage signal bus. The RCU communicates with the CLAS DAQ system 
+FECs are hosted in custom crates, mounted close to the detector. A readout 
+control unit (RCU) board is used to distribute the trigger signal to FECs 
+and for data readout. Each RCU can handle up to 25 FECs with communication 
+between them performed trough a 
+custom back-plane, implementing a low-voltage signal bus. The RCU communicates 
+with the CLAS data acquisition (DAQ) system 
 trough a 200 MB/s optical link, connected to a data acquisition PC hosting 
-a ReadOut Receiver Card (RORC). This PC hosts the readout controller 
-application (ROC) used to interface with the CLAS DAQ system. An Ethernet 
-link is also present, for slow-controls and monitoring.
+a ReadOut Receiver Card (RORC) used to interface with 
+the CLAS DAQ system. An Ethernet link is also present, for slow-controls and 
+monitoring.
 
@@
 acquired for each trigger, operating ALTRO at the reduced sampling frequency of 
-$10 MHz$. The L1-L2 latency is thus fixed to 15 $\mu$s.
+$10$~MHz. The L1-L2 latency is thus fixed to 15 $\mu$s.
 
@@
 sample above threshold, the resolution is equivalent to the ALTRO sampling 
-time, 100~ns.
+time of 100~ns.
 
@@
 each equipped with 6 boards, plus a ROC. A schematic of the readout system, 
-for a single crate, is reported in figure~\ref{fig:ReadoutScheme}. This 
+for a single crate, is reported in Fig.~\ref{fig:ReadoutScheme}. This 
 configuration permits to reduce the dead time associated to FEC readout 
-operations, scaling linearly with the number of boards in the crate. During the 
+operations and to scale linearly with the number of boards in the crate. During the 
 2009 run, the system was successfully operated with a DAQ rate of 3.1 kHz, with 
@@
 the deposited energy per unit of length ($\small{\frac{dE}{dX}}$) which, 
-together with the momentum calculated from the trajectory, enables particle 
+together with the momentum calculated from the trajectory, enable the particle 
 identification.
@@
 
-We determine the drift speed using tracks reconstructed in the RTPC. In figure 
-\ref{fig:RTPC_signals}, a typical $^{4}$He track is represented (in green). After 
+We determine the drift speed using tracks reconstructed in the RTPC. In 
+Fig.~\ref{fig:RTPC_signals}, a typical $^{4}$He track is represented (in green). After 
 it causes ionization in the drift region, the released electrons (in black) 
@@
 To measure the drift speed, we use the time profile of all hits in the 
-chamber shown in figure \ref{fig:TDC_profile}. We can clearly observe the 
+chamber shown in Fig.~\ref{fig:TDC_profile}. We can clearly observe the 
 dropping edge expected from geometrical considerations. We define a value $T_{Max/2}$ at 
 which the dropping edge passes half the maximum number of hits in the 
-histogram. This value is measure in bins along the 200 mm RTPC's length to take into 
-account variations in the electric and magnetic field in the RTPC (see figure 
-\ref{fig:RunNumber_61551_TDCmax_Zslice}).
+histogram. This value was measured in bins along the 200 mm RTPC's length to take into 
+account variations in the electric and magnetic field in the RTPC (see 
+Fig.~\ref{fig:RunNumber_61551_TDCmax_Zslice}).
 
@@
 the drift speed changes during the three months long experimental run.  
-Figure \ref{fig:Drift_run_number_1} shows the $T_{Max/2}$ values for 
+Figure~\ref{fig:Drift_run_number_1} shows the $T_{Max/2}$ values for 
 individual runs (approximately 2 hours long). We observe a significant 
@@
 In summary, we obtain from our calibration a parametrization of the drift speed 
-as a function of both position along the beam axis and run number (we did not 
-observe any correlation between the effects). These 
+as a function of both position along the beam axis and the run number. These 
 functions were extracted for our entire data set and implemented in the 
@@
 scattering ($e^{4}$He$\rightarrow e^{4}$He). In this process, the measurement of
-the electron kinematic allows to calculate the Helium nucleus kinematic. It is
-by comparing this calculated kinematic to the measured one that we fine tune
-the drift paths independently of our knowledge of the exact conditions in the 
-chamber.
+the electron kinematic allows to calculate directly the Helium nucleus one. 
+By comparing this calculated kinematic to the measurement in the RTPC, we fine tuned
+the drift paths independently of our knowledge of the exact chamber's conditions.
 
 The drift paths are adjusted using a set of identified elastic events from our 
-lower beam energy run. Based on the kinematic of the electrons in these events, 
-we generate the helium nucleus in a GEANT4 simulation~\cite{GEANT4} of our 
-RTPC. Then we compare the calculated GEANT4 trajectory of the Helium nuclei to 
+lower beam energy run. Based on the kinematic of electrons in these events, 
+we generate the helium nucleus in our RTPC GEANT4 simulation~\cite{GEANT4}. Then 
+we compare the calculated GEANT4 trajectory of the Helium nuclei to 
 the hits measured in the chamber.
@@
 the ionization point ($\Delta\phi$) is extracted as a function of time. 
-In figure~\ref{fig:DELTA_PHI_TDC}, we show the resulting data points for one 
+In Fig.~\ref{fig:DELTA_PHI_TDC}, we show the resulting data points for one 
 bin, where the drift paths is easily identified and eventually fitted for 
@@
 1.269 GeV data from the end of the run period (shown in blue on 
-figure~\ref{fig:Drift_run_number_1}). Interestingly, we found very similar drift paths
+Fig.~\ref{fig:Drift_run_number_1}). Interestingly, we found very similar drift paths
 for the two data sets and concluded that any changes in the system only
@@
 much closer to the expected Bethe-Bloch curve than prior to calibration, the
-results shown in figure~\ref{fig:dedx_p_exp_1st} are not very satisfactory.
+results shown in Fig.~\ref{fig:dedx_p_exp_1st} are not very satisfactory.
 
@@
 before reaching the pad, so that the simulated hits match the experimental 
-ones. Moreover, the simulation has to match the data acquisition (DAQ) features 
+ones. Moreover, the simulation has to match the DAQ features 
 that can lead to cutting out hits. After setting the simulation properly, we 
 compared simulation to experiment on an event by event basis as shown in 
-Figure~\ref{fig:EVENT_adc_tdc}. In this step, the gain for each pad is calculated 
+Fig.~\ref{fig:EVENT_adc_tdc}. In this step, the gain for each pad is calculated 
 as the ratio of the measured ADCs to the simulated deposited energy.  
@@
 deposit recorded by the other pads. 
-Results of this second method are shown in Figure~\ref{fig:dedx_p_exp_2nd},
+Results of this second method are shown in Fig.~\ref{fig:dedx_p_exp_2nd},
 from these we concluded that the gains of the 
@@
 
-The first is an oscillatory noise located early in the readout time window, shown in the top panel of Figure~\ref{fig:noise} for a particularly noisy channel.
-Its amplitude is not dissimilar to those of real tracks, and about 18\% of the readout channels exhibit large contributions from this noise characteristic.
-Due to its unique time-energy correlation for the given channels, the noise could be removed on an event by event and channel by channel basis without significant loss of good signals, and the result is illustrated in the bottom panel of Figure~\ref{fig:noise}.
+The first is an oscillatory noise located early in the readout time window, 
+shown in the top panel of Fig.~\ref{fig:noise} for a particularly noisy 
+channel. Its amplitude is not dissimilar to those of real tracks, and about 
+18\% of the readout channels exhibit large contributions from this noise 
+characteristic. Due to its unique time-energy correlation for the given 
+channels, the noise could be removed on an event by event and channel by 
+channel basis without significant loss of good signals. The result of the
+procedure is illustrated in the bottom panel of Fig.~\ref{fig:noise}.
 
@@
 In order to reconstruct tracks we first select good hits. This means rejecting 
-out-of-time hits and hits linked to the electronic noise. The second step is 
+out-of-time hits as well as the hits linked to the electronic noise. The second step is 
 to reconstruct the spacial origin of the hits using the extracted drift speed and drift path 
@@
 is to create chains of hits. The maximum distance between two close adjacent 
-hits has to be less than 10.5 mm to chain them, this roughly correspond to 
-neighbors and next to neighbors. Then, we fit the chains that have a minimum of 
-10 hits. We make the fit in two iterations, first, all the hits of the chain 
-together with the beam line are fitted with a helix. For the second iteration, 
+hits has to be less than 10.5 mm to chain them, which roughly corresponds to 
+neighbors and next to neighbors. Then, we fit with a helix the chains that have a minimum of 
+10 hits. We make the fit in two iterations, first with all the hits of the chain 
+and the beam line, then, in the second iteration, 
 the hits that are 5 mm or farther from the first fit are excluded.
@@
 efficiency of the RTPC using the elastic scattering on $^4$He, by comparing the 
- the inclusive yield based on electron detection only to the exclusive elastic 
-yield where we also detect the Helium recoil. We present in 
-Figure~\ref{fig:rtpc_eff} the results for the two modules 
+inclusive yield based only on electron detection to the exclusive elastic 
+yield where the Helium recoil is also detected. We present in 
+Fig.~\ref{fig:rtpc_eff} the results for the two modules 
 of the detector. We observe that the left and 

### 2017-06-12 eg6-letters/NIM/acknowledgment.tex
Add contact and acknowledgments.

\section{Acknowledgments}

The authors thank the staff of the Accelerator and Physics Divisions at the 
Thomas Jefferson National Accelerator Facility who made this work 
possible. This work was supported in part by the French Centre National de la 
Recherche Scientifique and the U.S. Department of Energy. One of the 
author (M.H.) also 
acknowledge the support of the Consulat G\'en\'eral de France \`a J\'erusalem. 
The Southeastern Universities Research Association operates the Thomas 
Jefferson National Accelerator Facility for the United States Department of 
Energy under contract DE-AC05-06OR23177.

### 2017-06-12 eg6-letters/NIM/author_list.tex
RTPC NIM:  add Michael Oliver
Add contact and acknowledgments.

@@
 
-\author{R.~Dupr\'e} \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}
+\author{R.~Dupr\'e}\email[corresponding author: ]{dupre@ipno.in2p3.fr} \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}
 \author{S.~Stepanyan} \affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
@@
 \author{S.~Kuhn} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
+\author{M.~Oliver} \affiliation{University of Chicago, Chicago, IL 60637, United States}
 \author{Y.~Perrin} \affiliation{LPSC, Universit\'e Grenoble-Alpes, CNRS/IN2P3, Grenoble, France}

### 2017-06-16 eg6-letters/NIM/author_list.tex
Add MB to authors
Update to elsevier framework

--- 2017-06-08 eg6-letters/NIM/author_list.tex
@@
-\affiliation{Argonne National Laboratory, Argonne IL 60439, USA}
-\affiliation{Institut de Physique Nucl$\acute{e}$aire, CNRS/IN2P3 and Universit$\acute{e}$ Paris Sud, Orsay, France}
-\affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
-%
+\author[anl,ipn]{R.~Dupr\'e\corref{cor}}\ead{dupre@ipno.in2p3.fr} 
+\author[jlab]{S.~Stepanyan} 
+\author[anl,ipn]{M.~Hattawy} 
+\author[anl,jlab]{N.~Baltzell} 
+\author[anl]{K.~Hafidi} 
+\author[infn]{M.~Battaglieri} 
+\author[odu]{S.~Bueltmann} 
+\author[infn]{A.~Celentano} 
+\author[infn]{R.~De~Vita} 
+\author[anl,utfsm]{A.~El~Alaoui} 
+\author[msu]{L.~El~Fassi} 
+\author[jlab]{H.~Egiyan} 
+\author[jlab]{H.~Fenker} 
+\author[anl]{K.~Kosheleva} 
+\author[odu]{S.~Kuhn} 
+\author[uc]{M.~Oliver} 
+\author[lpsc]{Y.~Perrin} 
+\author[odu]{B.~Torayev}
+\author[ipn,lpsc]{E.~Voutier}
 
-\author{R.~Dupr\'e} \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}
-\author{S.~Stepanyan} \affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
-\author{M.~Hattawy} \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}
-\author{N.~Baltzell} \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}\affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
-\author{S.~Bueltmann} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
-\author{A.~Celentano} \affiliation{INFN, Sezione di Genova, 16146 Genova, Italy}
-\author{R.~De~Vita} \affiliation{INFN, Sezione di Genova, 16146 Genova, Italy}
-\author{H.~Egiyan} \affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
-\author{H.~Fenker} \affiliation{Jefferson Laboratory, Newport News, VA 230606, USA}
-\author{K.~Hafidi} \affiliation{Argonne National Laboratory, Argonne IL 60439, USA}
-\author{S.~Kuhn} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
-\author{Y.~Perrin} \affiliation{LPSC, Universit\'e Grenoble-Alpes, CNRS/IN2P3, Grenoble, France}
-\author{B.~Torayev} \affiliation{Old Dominion University, Norfolk, VA 23529, United States}
-\author{E.~Voutier} \affiliation{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}\affiliation{LPSC, Universit\'e Grenoble-Alpes, CNRS/IN2P3, Grenoble, France}
-%\author{} \affiliation{}
-%
+\address[anl]{Argonne National Laboratory, Argonne IL 60439, USA}
+\address[ipn]{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}
+\address[jlab]{Jefferson Laboratory, Newport News, VA 230606, USA}
+\address[infn]{INFN, Sezione di Genova, 16146 Genova, Italy}
+\address[odu]{Old Dominion University, Norfolk, VA 23529, United States}
+\address[utfsm]{Universidad T\'ecnica Federico Santa Mar\'ia, Casilla 110-V Valpara\'iso, Chile}
+\address[msu]{Mississippi State University, Mississippi State, MS 39762-5167}
+\address[uc]{University of Chicago, Chicago, IL 60637, United States}
+\address[lpsc]{LPSC, Universit\'e Grenoble-Alpes, CNRS/IN2P3, Grenoble, France}
 
-\collaboration{The CLAS Collaboration} 
-%
-%\vskip 2.0cm
+\cortext[cor]{Corresponding author}

### 2017-06-16 eg6-letters/NIM/EG6_RTPC_NIM.tex
Update to elsevier framework
Comments from Sebastian

@@
-\documentclass[twocolumn,showpacs,superscriptaddress,groupedaddress]{revtex4}
+\documentclass[preprint,5p]{elsarticle}
 \usepackage{graphicx}
@@
 \hypersetup{colorlinks=true, urlcolor=blue, citecolor=blue}
-
+\usepackage[displaymath]{lineno}
+\linenumbers
 \begin{document}
@@
 
-Thomas Jefferson National Accelerator Facility (TJNAF), in Newport News, Virginia,
-USA, provides high power electron beams of energy up to 6 GeV and 100$\%$ duty cycle
-to three experimental Halls (A, B, C) simultaneously. The CLAS 
-spectrometer~\cite{CLASref}, located
+Until recently, Thomas Jefferson National Accelerator Facility (TJNAF), in 
+Newport News, Virginia, USA, has provided high power electron beams of energy 
+up to 6 GeV and 100$\%$ duty cycle to three experimental Halls (A, B, C) 
+simultaneously. The CLAS spectrometer~\cite{CLASref}, located
 in Hall-B, is composed of several sub-detectors and two magnets. 
@@
 Measurement of the Deeply Virtual Compton Scattering (DVCS) process
-($eH \rightarrow e' H' \gamma$, where $H$ is a hadron) necessitates an upgrade
+($eH \rightarrow e' H' \gamma$, where $H$ is a nucleon or nuclei) necessitates an upgrade
 of this setup.  With a 6 GeV electron beam, the majority of DVCS photons are produced
 at very forward angles, where the acceptance of the EC is poor. To extend the detection range,
-an inner calorimeter (IC) was built for the E01-113 experiment in 2005.
+an inner calorimeter (IC) was built for the E01-113 experiment in 2005~\cite{FX}.
 The IC is constructed from 424 lead-tungstate (PbWO$_{4}$) crystals, covering polar 
@@
 energies between 2 GeV and 5 GeV, with an angular resolution between 3 and 5 mrad 
-\cite{Hyon-suk}. To protect this detector from the large flux of low energy M{\o}ller 
+\cite{Hyon-suk}. To protect this detector and CLAS from the large flux of low energy M{\o}ller 
 electrons, a 5~T solenoid was placed around the target to shield the IC. 
-In addition, the recoil nuclei of the coherent DVCS on helium was detected 
+In addition, the recoil nuclei from the coherent DVCS on helium was detected 
 using a RTPC developed to track low energy nuclear fragments. The solenoid field
-serving as the analyzing magnet for the particle tracking in the RTPC. This 
+serving as the analyzing magnet for particle tracking in the RTPC. This 
 setup was used during a three months experimental run~\cite{proposal1,proposal2}
@@
 
-\section{CLAS RTPC design} \label{sec_design}
+\section{RTPC design} \label{sec_design}
 
@@
 
-The CLAS RTPC is a 250~mm long cylinder of 158~mm diameter, leaving just enough 
+The new CLAS RTPC is a 250~mm long cylinder of 158~mm diameter, leaving just enough 
 room to fit pre-amplifiers between the RTPC outer shell and the solenoid. The 
-electromagnetic field is directed perpendicularly to the beam direction, 
+electric field is directed perpendicularly to the beam direction, 
 such that drifting electrons are pushed away from the beam line. These electrons 
@@
 on the external shell of the detector as illustrated in the 
-Fig.~\ref{fig:RTPC_1_4}. The CLAS RTPC is segmented into two halves with 
+Fig.~\ref{fig:RTPC_1_4}. The RTPC is segmented into two halves with 
 independent GEM amplification systems that cover about 80\% of the azimuthal 
@@
 \begin{itemize}
-   \item First, the 6 atm helium-4 target extends along the beam line axis, it 
+   \item First, the 6 atm helium-4 target extends along the beam line axis; it 
       is 284~mm long with a 3~mm radius wall made of a 27-$\mu$m-thick Kapton.
@@
       radii of 60, 63 and 66 mm. In this configuration, the first GEM layer 
-      serves as the anode and each subsequent GEM is set at a lower voltage to
+      serves as the anode and each subsequent GEM is set at a lower Voltage to
       obtain a strong ($\sim$1600 V/cm) electric field between the GEM foils. A 
-      275~V bias is applied to each GEM for amplification.
+      275~V bias is applied across each GEM for amplification.
    \item The readout board has an internal radius of 69~mm and collects charge
@@
 
-The drift gas used in the experiment is a 80-20\% Ne-DME mixture, this choice 
-has been made in order to balance the energy deposit with a reasonable
+The drift gas used in the experiment is a 80-20\% Ne-DME mixture. This choice 
+has been made in order to balance the energy deposit, which is critical
+for proper particle identification, with a reasonable
 Lorentz angle. Calculations using the MAGBOLTZ program~\cite{MAGBOLTZ} 
-showed that with the perpendicular 5~T field, we would have a Lorentz angle of 
+showed that with the axial 5~T field, we would have a Lorentz angle of 
 about 23$^\circ$ with this gas mixture. This is already a significant angle,
@@
 One of the important challenge in developing the radial TPC was how to obtain a 
-good support structure of the GEM foils to allow a tractable but highly precise 
+good support structure for the GEM foils to allow a tractable 
 installation of the GEMs. At the same time, we wanted to 
@@
 particles in subsequent detectors. We successfully realized these prerequisites 
-by using fiber glass rings glued to each ends of the GEM foils to form self 
+by using fiber glass rings glued to each end of the GEM foils to form self 
 supporting cylinders that could be installed independently in the RTPC after 
@@
 The RTPC electron collection system has 3200 readout pads. These elements are
-located at the end of the amplification region, 69 mm from the central axis.
+parallel to the GEMs, 69 mm from the central axis.
 Figure~\ref{fig:PADs} shows a schematic drawing of the size and 
@@
 RTPC has 40 rows and 40 columns of pads. The shaded region in Fig.~\ref{fig:PADs} 
-shows how pads are grouped to 16 channels pre-amplifiers. The pre-amplifier boards, 
+shows how pads are grouped to 16 channel pre-amplifiers. The pre-amplifier boards, 
 already employed in the BoNuS RTPC~\cite{BONUS-NIM}, serve the dual purpose of 
@@
 cable that connects to it.
+
+\begin{figure*}[tb]
+   \centering
+   \includegraphics[width=.75\textwidth]{fig/ReadoutScheme.png}
+   \caption[]{Schematic representation of the RTPC readout system, showing
+   the different elements of the front end electronics.} 
+   \label{fig:ReadoutScheme}
+\end{figure*}
 
@@
 between them performed trough a 
-custom back-plane, implementing a low-voltage signal bus. The RCU communicates 
+custom back-plane, implementing a low-Voltage signal bus. The RCU communicates 
 with the CLAS data acquisition (DAQ) system 
@@
 
-Triggering and data-readout scheme is as follows. When a Level-1 (L1) trigger 
+The triggering and data-readout scheme is as follows. When a Level-1 (L1) trigger 
 is received by a FEC-board, a programmable number of samples $N_0$ is digitized 
@@
 the measured samples from active channels are reported, together with a channel 
-identifier and a time-stamp, to the ROC application, that in turns sends them 
-on the main event builder. During data reconstruction, the acquired samples are 
+identifier and a time-stamp, to the RCU application, that in turns sends them 
+on to the main event builder. During data reconstruction, the acquired samples are 
 processed to obtain, for each readout pad, the accumulated charge (ADC) and the 
@@
 time of 100~ns.
-
-\begin{figure}[tb]
-   \centering
-   \includegraphics[width=.45\textwidth]{fig/ReadoutScheme.png}
-   \caption[]{Schematic representation of the RTPC readout system, showing} 
-   \label{fig:ReadoutScheme}
-\end{figure}
 
@@
 In order to read all the detector readout pads, four FEC crates are used, 
-each equipped with 6 boards, plus a ROC. A schematic of the readout system, 
+each equipped with 6 boards, plus a RCU. A schematic of the readout system, 
 for a single crate, is reported in Fig.~\ref{fig:ReadoutScheme}. This 
@@
 
-The timing information is used to infer the origin of the charge and 
-then the trajectory of the detected particle
-resulting in momentum measurement. Going from a collection of 
-times to a momentum measurement requires a good knowledge of the drift speed 
+The timing information collected for each signal above threshold
+is used to infer the origin of the ionization electrons and 
+then the trajectory of the detected particle. Going from a collection of 
+times to a momentum measurement based on the curvature of a track 
+requires a good knowledge of the drift speed 
 and drift paths followed by the electrons released in the gas. The recorded ADCs give 
@@
 properly reconstructed in the RTPC. The figures presented in this section
-are the one obtained while performing the last iteration of this long 
+are the ones obtained while performing the last iteration of this long 
 calibration process.
@@
    \includegraphics[scale=0.42]{fig_2017/hits_time_profile.pdf}
-   \caption[]{Time profile of the collected hits in one experimental run.  } 
+   \caption[]{Time distribution of the collected hits in one experimental run. Trigger
+              time is defined as T=15, the time unit is the ALTRO sampling time of 100~ns.} 
    \label{fig:TDC_profile}
@@
 \includegraphics[scale=0.42]{fig_2017/RunNumber_61452_TDCmax_Zslice.pdf}
-\caption{Time profile distribution for the collected hits in one experimental 
-run. } \label{fig:RunNumber_61551_TDCmax_Zslice}
+\caption{Maximum time of collected hits as a function of the track
+              position on the $z$-axis for one experimental run. } 
+\label{fig:RunNumber_61551_TDCmax_Zslice}
 \end{figure}
@@
 refine our result. As it happens, the curvature is minimal and this process 
-converge already on the second iteration.
+converges already on the second iteration.
 
@@
 In Fig.~\ref{fig:DELTA_PHI_TDC}, we show the resulting data points for one 
-bin, where the drift paths is easily identified and eventually fitted for 
+bin, where the drift path is easily identified and eventually fitted for 
 implementation in our reconstruction codes.
@@
 
-\begin{figure}[tb]
+\begin{figure*}[tb]
    \centering
-   \includegraphics[scale=0.43]{fig_2017/f_dedx_p_exp_1st.pdf}
+   \includegraphics[scale=0.73]{fig_2017/f_dedx_p_exp_1st.pdf}
    \caption{$\small{\frac{dE}{dX}}$ vs. $p/q$ distribution for the left half of 
@@
       method.  The lines are theoretical expectations from Bethe-Bloch formula 
-   for $^4$He, $^3$He, $^3$H and $^2$H (d).}
+   for $^4$He (red), $^3$He (black), $^3$H (blue), $^2$H (pink) and protons (grey).}
 \label{fig:dedx_p_exp_1st}
-\end{figure}
+\end{figure*}
 
-The second method is to compare the experimental ADCs to the energy deposited in 
-GEANT4 by similar simulated tracks (using the same elastic events than for the drift 
+The second method is to compare the experimental ADCs to the energy deposited 
+for each pad individually in GEANT4 by similar simulated tracks (using the 
+same elastic events as for the drift 
 paths calibration). This requires a very good GEANT4 simulation 
@@
 
-\begin{figure}[tb]
+\begin{figure}[tb!]
    \centering
@@
 
-\begin{figure}[tb]
+\begin{figure*}[tb]
 \centering
-\includegraphics[scale=0.45]{fig_2017/f_dedx_p_exp_2nd.pdf}
+\includegraphics[scale=0.73]{fig_2017/f_dedx_p_exp_2nd.pdf}
 \caption{$\small{\frac{dE}{dX}}$ vs. $p/q$ distribution for the left half of 
@@
    $\small{\frac{dE}{dX}}$ is calculated using the gains of the second method.  
-   The lines are theoretical expectations from Bethe-Bloch formula for $^4$He, 
-$^3$He, $^3$H and $^2$H (d).}
+   The lines are theoretical expectations from Bethe-Bloch formula for $^4$He 
+   (red), $^3$He (black), $^3$H (blue), $^2$H (pink) and protons (grey).}
 \label{fig:dedx_p_exp_2nd}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}[tb]\centering
-\includegraphics[scale=0.27]{fig/noisy_pad_before_rejection2.png}
-\includegraphics[scale=0.27]{fig/noisy_pad_after_rejection2.png}
+\begin{figure}[tb!]\centering
+\includegraphics[scale=0.25]{fig/noisy_pad_before_rejection2.png}
+\includegraphics[scale=0.25]{fig/noisy_pad_after_rejection2.png}
 \caption{The ADC vs. T spectrum for an example noisy channel before (top) and 
@@
 \bibitem{CCref}
-   G. Adams et al., The CLAS Cerenkov detector", Nucl. Inst. and Meth. A 465, 
+   G. Adams et al., The CLAS Cerenkov detector, Nucl. Inst. and Meth. A 465, 
    414 (2001).
@@
    Inst. and Meth. A 460, 239 (2001).
+
+\bibitem{FX}
+   F.X. Girod et al. (CLAS Collaboration), Measurement of Deeply virtual Compton 
+   scattering beam-spin asymmetries, Phys.Rev.Lett. 100 (2008) 162002
 
@@
 
+\bibitem{BONUS-NIM}
+   Howard C. Fenker et al., BoNuS: Development and Use of a Radial TPC using 
+   Cylindrical GEMs, Nucl. Instrum. Meth. A592, 273-286 (2008)
+
 \bibitem{GEM_ref_pic}
@@
    Meth. in Phy. Res. A, vol. 421, pp. 234-240, 1999.
-
-\bibitem{BONUS-NIM}
-   Howard C. Fenker et al., BoNuS: Development and Use of a Radial TPC using 
-   Cylindrical GEMs, Nucl. Instrum. Meth. A592, 273-286 (2008)
 

### 2017-06-19 eg6-letters/NIM/EG6_RTPC_NIM.tex
Add gem production company

@@
 such that drifting electrons are pushed away from the beam line. These electrons 
-are amplified by three layers of curved GEMs and detected by the readout system 
+are amplified by three layers of curved gas electron multipliers (GEM) and 
+detected by the readout system 
 on the external shell of the detector as illustrated in the 
 Fig.~\ref{fig:RTPC_1_4}. The RTPC is segmented into two halves with 
-independent GEM amplification systems that cover about 80\% of the azimuthal 
+independent GEM amplification systems\footnote{The foils were produced by 
+Tech-Etch, Inc.} that cover about 80\% of the azimuthal 
 angle.
@@
 \cite{GEM_ref_pic}.} 
-
    \label{fig:GEMs}

### 2017-06-21 eg6-letters/coherent/dvcs_he4_prl.tex
dvcs_he4_prl.tex:  minor suggestion from adhoc
Edit note

@@
 with $H_A$ a GPD, $\mathcal{P}$ 
-the Cauchy principal value integral, and $C^{+}(x,\xi)$ a coefficient function 
-($=  \frac{1}{x-\xi} + \frac{1}{x+\xi}$).
+the Cauchy principal value integral, and a coefficient function $C^{+}= 
+\frac{1}{x-\xi} + \frac{1}{x+\xi}$.
 
@@
 distributions\footnote{We use here and for other results 
-$x_B =\frac{Q^2}{2M_N\nu}$ with $M_N$ the proton mass instead of $x_A$ for 
-easier comparison with proton data.} are shown in Fig.~\ref{fig:kin-coverage}.
+$x_B =\frac{Q^2}{2M_N\nu}$ with $M_N$ the proton mass instead of $x_A$.
+This makes it easier to compare these results with the proton DVCS data
+available in the litterature.} are shown in Fig.~\ref{fig:kin-coverage}.
 

### 2017-06-22 eg6-letters/NIM/EG6_RTPC_NIM.tex
NIM:  add resolution and elastic scattering paragraphs

@@
 
+The primary data sample used for calibration and performance assessment of the
+RTPC was elastic scattering with a 1.2 GeV electron beam.  The electron's momentum
+and direction is measured with CLAS, which uniquely determines the expected recoiling
+$^4$He kinematics.  Matching requirements between reconstructed and expected $z$-vertex
+and direction of the RTPC track provides a clean selection of elastically-scattered
+$^4$He, showin in Fig.~\ref{fig:w}.
+
+\begin{figure}[tb]\centering
+  \includegraphics[width=8cm]{fig/fit_W_distribution_l.png}
+  \caption{The $W$ distribution calculated from electron kinematics before (``inclusive'')
+  and after (``exclusive'') requiring a matching track in the RTPC.\label{fig:w}}
+\end{figure}
+
+\subsection{Resolution}
+Elastic scattering was used to estimate the tracking resolution of the RTPC 
+based on the residual between the expected and measured $^4$He tracks.  The RTPC
+resolutions, after removing contributions from the electron, are shown in Table
+~\ref{tab:reso}, and are very similar for the two halves of the RTPC.  Note, the
+$\theta$- and $z$-resolutions are highly correlated.
+\begin{table}[htbp]
+\begin{center}
+\begin{tabular}{|l|cccc|}
+  \hline
+& $\sigma_{z}$ &  $\sigma_{\theta}$ & $\sigma_{\phi}$ & $\sigma_{p}$\\
+\hline
+Left &  6.0 mm & 3.8$^{\circ}$ & 1.9$^{\circ}$ & 9$\%$ \\
+Right & 7.4 mm & 4.0$^{\circ}$ & 1.9$^{\circ}$ & 8$\%$\\
+\hline
+\end{tabular}
+\caption{The resolutions of the two modules of the RTPC for $z$-vertex, polar and azimuthal angles, and momentum.}
+\label{tab:reso}
+\end{center}
+\end{table}
+
+\subsection{Efficiency}
 The previous discussions have shown that the two modules of the RTPC have 
@@
 Indeed, there is a complicated convolution of CLAS and the RTPC acceptances 
-that can significantly affect the yields and the kinematic of the detected 
-particles. To clarify this question, we measured the 
-efficiency of the RTPC using the elastic scattering on $^4$He, by comparing the 
-inclusive yield based only on electron detection to the exclusive elastic 
-yield where the Helium recoil is also detected. We present in 
-Fig.~\ref{fig:rtpc_eff} the results for the two modules 
-of the detector. We observe that the left and 
+that can significantly affect the yields and kinematics of the detected 
+particles. To clarify this question, we measured the efficiency of the RTPC
+using elastic scattering on $^4$He by comparing the inclusive yield, based
+only on electron detection, to the exclusive elastic yield, where the Helium
+recoil is also detected (see Fig.~\ref{fig:w}). We present in Fig.~\ref{fig:rtpc_eff}
+the results for the two modules of the detector. We observe that the left and 
 the right modules have similar efficiencies except near the target windows.

### 2017-06-23 eg6-letters/coherent/dvcs_he4_prl.tex
remove line numbers
typo corrections
dvcs_he4_prl.tex:  litterature->literature

@@
-\RequirePackage{lineno}
 %\documentclass[preprint,nofootinbib,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
@@
 %
-\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
-\expandafter\let\csname old#1\expandafter\endcsname\csname #1\endcsname
-\expandafter\let\csname oldend#1\expandafter\endcsname\csname end#1\endcsname
-\renewenvironment{#1}%
-{\linenomath\csname old#1\endcsname}%
-{\csname oldend#1\endcsname\endlinenomath}}%
-\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
-\patchAmsMathEnvironmentForLineno{#1}%
-\patchAmsMathEnvironmentForLineno{#1*}}%
-\AtBeginDocument{%
-\patchBothAmsMathEnvironmentsForLineno{equation}%
-\patchBothAmsMathEnvironmentsForLineno{align}%
-\patchBothAmsMathEnvironmentsForLineno{flalign}%
-\patchBothAmsMathEnvironmentsForLineno{alignat}%
-\patchBothAmsMathEnvironmentsForLineno{gather}%
-\patchBothAmsMathEnvironmentsForLineno{multline}%
-}
 
-%
 \begin{document}
-\linenumbers
 
@@
 This makes it easier to compare these results with the proton DVCS data
-available in the litterature.} are shown in Fig.~\ref{fig:kin-coverage}.
+available in the literature.} are shown in Fig.~\ref{fig:kin-coverage}.
 
@@
 Development at Mississippi State University.  The author (M.~Hattawy) also 
-acknowledge the support of the Consulat G\'en\'eral de France \`a J\'erusalem. 
-The Southeastern Universities Research Association operates the Thomas 
+acknowledges the support of the Consulat G\'en\'eral de France \`a J\'erusalem. The Southeastern Universities Research Association operates the Thomas 
 Jefferson National Accelerator Facility for the United States Department of 

### 2017-06-27 eg6-letters/NIM/EG6_RTPC_NIM.tex
Add Stepan's comments

@@
 Laboratory to track low-energy nuclear recoils for the purpose of measuring
-exclusive nuclear channels, such as coherent Deeply Virtual Compton Scattering
+exclusive nuclear reactions, such as coherent Deeply Virtual Compton Scattering
 and coherent meson production on $^4$He. In such processes, the $^4$He nucleus
@@
 the RTPC positioned directly around a gaseous $^4$He target, allowing a detection
-threshold as low as 300~MeV/c for $^4$He. This article discuses the design,
-work principle, calibration methods and performances of this RTPC.
+threshold as low as 12~MeV for $^4$He. This article discuses the design,
+work principle, calibration methods and the performance of this RTPC.
 \end{abstract}
@@
 
-Until recently, Thomas Jefferson National Accelerator Facility (TJNAF), in 
-Newport News, Virginia, USA, has provided high power electron beams of energy 
-up to 6 GeV and 100$\%$ duty cycle to three experimental Halls (A, B, C) 
+Until recently, Thomas Jefferson National Accelerator Facility, in 
+Newport News, Virginia, USA, has provided high power electron beams of 
+up to 6 GeV energy and 100$\%$ duty cycle to three experimental Halls (A, B, C) 
 simultaneously. The CLAS spectrometer~\cite{CLASref}, located
-in Hall-B, is composed of several sub-detectors and two magnets. 
-Figure~\ref{fig:CLAS} shows a three dimensional 
+in Hall-B, is based on a superconducting toroidal magnet and composed of 
+several sub-detectors. Figure~\ref{fig:CLAS} shows a three dimensional 
 representation of the baseline CLAS spectrometer:
@@
        of charged particles, thus allowing momentum measurement with the DC tracking information.
- \item Cerenkov Counters (CC) to distinguish electrons from other negative 
-    particles, such as pions, at lower energies~\cite{CCref} (in pink).
- \item Scintillation Counters (SC) to identify hadrons by measuring their 
+ \item Threshold Cherenkov Counters (CC) for electron identification at momenta 
+       $<2.7$ GeV~\cite{CCref} (in pink).
+ \item Scintillation Counters (SC) to identify charged hadrons by measuring their 
        time of flight (TOF)~\cite{TOFref} (in red).
- \item Electromagnetic Calorimeters (EC) to distinguish electrons from other negative 
-    particles at higher energies and to detect neutral particles (neutrons and 
-    photons in particular)~\cite{ECref} (in green).
+ \item Electromagnetic Calorimeters (EC) for identification of electrons, 
+       photons and neutrons~\cite{ECref} (in green).
 \end{itemize}
@@
 energies between 2 GeV and 5 GeV, with an angular resolution between 3 and 5 mrad 
-\cite{Hyon-suk}. To protect this detector and CLAS from the large flux of low energy M{\o}ller 
-electrons, a 5~T solenoid was placed around the target to shield the IC. 
-In addition, the recoil nuclei from the coherent DVCS on helium was detected 
-using a RTPC developed to track low energy nuclear fragments. The solenoid field
-serving as the analyzing magnet for particle tracking in the RTPC. This 
+\cite{Hyon-suk}. To protect the CLAS detector and the IC from the large flux 
+of low energy M{\o}ller 
+electrons, a 5~T solenoid was placed around the target to shield the detectors. 
+To detect recoiling $\alpha$ particles from the coherent DVCS on helium, a new 
+radial time projection chamber was developed to track low energy nuclear 
+fragments. The solenoid field was used to track and measure momentum of 
+particles in RTPC. This 
 setup was used during a three months experimental run~\cite{proposal1,proposal2}
@@
 With a 6 GeV incident electron energy, the recoiling $^{4}$He nuclei from coherent 
-DVCS have an average momentum around 250 MeV/c. Such low energy $\alpha$ 
+DVCS have an average momentum around 300 MeV/c (12 MeV kinetic energy). Such low energy $\alpha$ 
 particles are stopped very rapidly, so the RTPC was designed to be as close 
-as possible to the target and fitting within the 230~mm diameter 
-of the 5 Tesla solenoid magnet surrounding the target.
+as possible to the target and fit inside the 230 mm diameter bore of the 
+5 Tesla solenoid magnet.
 
@@
 such that drifting electrons are pushed away from the beam line. These electrons 
-are amplified by three layers of curved gas electron multipliers (GEM) and 
+are amplified by three layers of cylindrical gas electron multipliers (GEM) and 
 detected by the readout system 
@@
 \begin{itemize}
-   \item First, the 6 atm helium-4 target extends along the beam line axis; it 
-      is 284~mm long with a 3~mm radius wall made of a 27-$\mu$m-thick Kapton.
+   \item The 6 atm helium-4 target extends along the beam line axis; it 
+      is a 284~mm long, 6~mm in diameter straw with a 27-$\mu$m Kapton wall.
    \item The first gas gap covers a radial range from 3 mm to 20 mm. It is 
       filled with $^{4}$He gas at 1~atm to minimize secondary interactions from
-      M\o ller electrons scattered by the beam. This 
+      M\o{}ller electrons scattered by the beam. This 
       region is surrounded by a 4 $\mu$m thick window made of aluminized Mylar 
       that is electronically grounded.
-   \item The second gap region extends between 20~mm and 30~mm and is filled with a 
+   \item The second gap region extends between 20~mm and 30~mm and is filled with the 
       gas mixture of 80$\%$ neon (Ne) and 20$\%$ dimethyl ether (DME). This region 
@@
 which can be easily used to produce a curved amplification surface. Also, 
-GEMs are known to have relatively low sparks rate~\cite{GEM_ref}, which 
+GEMs are known to have relatively low spark rate~\cite{GEM_ref}, which 
 is important when trying to detect 
 highly ionizing slow nuclei that deposit large amount of energy. The GEMs for 
-this RTPC are made from a Kapton insulator layer, 50~$\mu$m 
+this RTPC are made from a Kapton insulator layer, 300~$\mu$m 
 thick, sandwiched between two 5~$\mu$m copper layers. The mesh of each GEM 
@@
 all gluing and soldering operations. The rigidity of the GEM foils was enough
-for the structure to be self-supporting and only the backward part of the 
-cylinder was fixed to the main mechanical structure. This design only left a 
-light fiberglass ring in the forward region, reducing to a minimum secondary 
+for the structure to be self-supporting and only the upstream end of the cylinder 
+was fixed to the main mechanical structure. This design only left a 
+light fiberglass ring in the downstream end, reducing to a minimum secondary 
 interactions.
@@
 properly reconstructed in the RTPC. The figures presented in this section
-are the ones obtained while performing the last iteration of this long 
+are the ones obtained while performing the last iteration of this
 calibration process.
@@
 
-We determine the drift speed using tracks reconstructed in the RTPC. In 
-Fig.~\ref{fig:RTPC_signals}, a typical $^{4}$He track is represented (in green). After 
-it causes ionization in the drift region, the released electrons (in black) 
+After the ionization, the released electrons 
 drift to the cylindrical detection plane under the effect of the electric field. The 
 electrons released close to the cathode take the most time to reach the readout 
-pads, but cylindrical symmetry insures they always travel the same 
-distance. By identifying the maximum time measured ($T_{Max}$), we can infer the drift 
+pads, but cylindrical symmetry insures that they always travel the same 
+distance. We illustrate this in Fig.~\ref{fig:RTPC_signals}, where we depict a 
+typical $^{4}$He track. By measuring the maximum time ($T_{Max}$), we can infer the drift 
 speed of the electrons in the RTPC.\\
@@
 The drift path is the trajectory followed by the electrons released through 
-ionization in the gas. Software exists to calculate the drift paths, in particular
+ionization in the gas. Software exists to calculate them, in particular
 MAGBOLTZ~\cite{MAGBOLTZ}, but it requires knowledge of the detector's 
@@
 scattering ($e^{4}$He$\rightarrow e^{4}$He). In this process, the measurement of
-the electron kinematic allows to calculate directly the Helium nucleus one. 
-By comparing this calculated kinematic to the measurement in the RTPC, we fine tuned
-the drift paths independently of our knowledge of the exact chamber's conditions.
+the electron kinematic allows to calculate directly the kinematic of the Helium nucleus. 
+By comparing the alpha particle's calculated momentum and angle of recoil to the 
+measurement in the RTPC, we tuned the drift paths independently of our 
+knowledge of the exact chamber's conditions.
 
-The drift paths are adjusted using a set of identified elastic events from our 
-lower beam energy run. Based on the kinematic of electrons in these events, 
+Based on the kinematic of electrons in the calibration data, 
 we generate the helium nucleus in our RTPC GEANT4 simulation~\cite{GEANT4}. Then 
@@
 the hits measured in the chamber. 
-
 Because of the magnetic field, the drift paths are not linear in the RTPC. So 
@@
 The gain of each pad is defined as the ratio between the actual 
-deposited energy and the registered ADC value. We tested two different 
-methods to extract such gains, with varying degrees of success.
-
-The first method is based on the measured average $\small{\frac{dE}{dX}}$
-and the expected value based on the Bethe-Bloch formula. The total energy
-deposition for each $^4$He track is calculated as the sum of all ADC hits
-attributed to the track. The path length of that energy deposition is
-calculated as the distance along the reconstructed trajectory between the first
-and last hits on the track and corrected to account for regions
-of bad channels along the track. The measured average energy loss is then the
-ratio of deposited energy and path length. The Bethe-Bloch formula is
-evaluated at the track's reconstructed momentum, and the ratio with the measured
-$\small{\frac{dE}{dX}}$ is taken as a gain scaling factor. This average gain is
-attributed equally to each readout channel contributing to the track, and each
-channel's gain is averaged over many tracks. This gain calibration method is
-inherently iterative, and, while it does result in measured $\small{\frac{dE}{dX}}$
-much closer to the expected Bethe-Bloch curve than prior to calibration, the
-results shown in Fig.~\ref{fig:dedx_p_exp_1st} are not very satisfactory.
-
-\begin{figure*}[tb]
-   \centering
-   \includegraphics[scale=0.73]{fig_2017/f_dedx_p_exp_1st.pdf}
-   \caption{$\small{\frac{dE}{dX}}$ vs. $p/q$ distribution for the left half of 
-      the RTPC (left) and for the right half (right). Here, 
-      $\small{\frac{dE}{dX}}$ is calculated using the gains of the first 
-      method.  The lines are theoretical expectations from Bethe-Bloch formula 
-   for $^4$He (red), $^3$He (black), $^3$H (blue), $^2$H (pink) and protons (grey).}
-\label{fig:dedx_p_exp_1st}
-\end{figure*}
-
-The second method is to compare the experimental ADCs to the energy deposited 
+deposited energy and the registered ADC value. 
+To do so we compare the experimental ADCs to the energy deposited 
 for each pad individually in GEANT4 by similar simulated tracks (using the 
@@
 compared simulation to experiment on an event by event basis as shown in 
-Fig.~\ref{fig:EVENT_adc_tdc}. In this step, the gain for each pad is calculated 
+Fig.~\ref{fig:EVENT_adc_tdc}. The gain for each pad is calculated 
 as the ratio of the measured ADCs to the simulated deposited energy.  
@@
 energy deposit on a pad and compare it to the average
-deposit recorded by the other pads. 
-Results of this second method are shown in Fig.~\ref{fig:dedx_p_exp_2nd},
-from these we concluded that the gains of the 
-second method match best the theoretical lines.
+deposit recorded by the other pads. This last step was implemented to 
+avoid any bias from this simulation based calibration method.
+Final results are shown in Fig.~\ref{fig:dedx_p_exp_2nd}.
 
@@
 \caption{$\small{\frac{dE}{dX}}$ vs. $p/q$ distribution for the left half of 
-   the RTPC (left) and for the right half (right). Here, 
-   $\small{\frac{dE}{dX}}$ is calculated using the gains of the second method.  
+   the RTPC (left) and for the right half (right) after gain calibration.  
    The lines are theoretical expectations from Bethe-Bloch formula for $^4$He 
@@
 \subsection{Noise Rejection}
-Two independent noise signatures were identified in the raw data and removed in software prior to track reconstruction.  Both are transient and isolated to a subset of the readout channels.
+Two independent noise signatures were identified in the raw data and removed 
+in software prior to track reconstruction. Both are transient and isolated to 
+a subset of the readout channels.
 

### 2017-06-27 eg6-letters/NIM/EG6_RTPC_NIM.tex
Add comments from E. Voutier

@@
 \begin{abstract}
-A new Radial Time Projection Chamber (RTPC) was developed at Jefferson 
+A new Radial Time Projection Chamber (RTPC) was developed at the Jefferson 
 Laboratory to track low-energy nuclear recoils for the purpose of measuring
 exclusive nuclear reactions, such as coherent Deeply Virtual Compton Scattering
-and coherent meson production on $^4$He. In such processes, the $^4$He nucleus
+and coherent meson production off $^4$He. In such processes, the $^4$He nucleus
 remains intact in the final state, however the CEBAF Large
@@
 threshold as low as 12~MeV for $^4$He. This article discuses the design,
-work principle, calibration methods and the performance of this RTPC.
+principle of operation, calibration methods and the performances of this RTPC.
 \end{abstract}
@@
 
-Until recently, Thomas Jefferson National Accelerator Facility, in 
+Until recently, the Thomas Jefferson National Accelerator Facility, in 
 Newport News, Virginia, USA, has provided high power electron beams of 
-up to 6 GeV energy and 100$\%$ duty cycle to three experimental Halls (A, B, C) 
+up to 6 GeV energy and 100$\%$ duty factor to three experimental Halls (A, B, C) 
 simultaneously. The CLAS spectrometer~\cite{CLASref}, located
@@
 \begin{itemize}
- \item Three regions of Drift Chambers (DC) for the tracking of charged 
-       particles~\cite{DCref} (in blue on the figure).
- \item Superconducting toroidal magnet (in yellow) to bend the trajectories 
+ \item Three regions of Drift Chambers for the tracking of charged 
+       particles~\cite{DCref}.
+ \item Superconducting toroidal magnet to bend the trajectories 
        of charged particles, thus allowing momentum measurement with the DC tracking information.
- \item Threshold Cherenkov Counters (CC) for electron identification at momenta 
-       $<2.7$ GeV~\cite{CCref} (in pink).
- \item Scintillation Counters (SC) to identify charged hadrons by measuring their 
-       time of flight (TOF)~\cite{TOFref} (in red).
+ \item Threshold Cherenkov Counters for electron identification at momenta 
+       $<2.7$ GeV~\cite{CCref}.
+ \item Scintillation Counters to identify charged hadrons by measuring their 
+       time of flight~\cite{TOFref}.
  \item Electromagnetic Calorimeters (EC) for identification of electrons, 
-       photons and neutrons~\cite{ECref} (in green).
+       photons and neutrons~\cite{ECref}.
 \end{itemize}
@@
 The IC is constructed from 424 lead-tungstate (PbWO$_{4}$) crystals, covering polar 
-angles between 5$^{\circ}$ and 15$^{\circ}$. Each crystal is 16 cm long, corresponding
-to 17 radiation lengths. The achieved energy resolution is around 3 to 4$\%$ for photon
-energies between 2 GeV and 5 GeV, with an angular resolution between 3 and 5 mrad 
-\cite{Hyon-suk}. To protect the CLAS detector and the IC from the large flux 
-of low energy M{\o}ller 
+angles between 5$^{\circ}$ and 15$^{\circ}$~\cite{Hyon-suk}. To protect the 
+CLAS detector and the IC from the large flux of low energy M{\o}ller 
 electrons, a 5~T solenoid was placed around the target to shield the detectors. 
@@
       filled with $^{4}$He gas at 1~atm to minimize secondary interactions from
-      M\o{}ller electrons scattered by the beam. This 
-      region is surrounded by a 4 $\mu$m thick window made of aluminized Mylar 
-      that is electronically grounded.
+      M\o{}ller electrons scattered by the beam. This region is surrounded by 
+      a 4 $\mu$m thick window made of grounded aluminized Mylar.
    \item The second gap region extends between 20~mm and 30~mm and is filled with the 
       gas mixture of 80$\%$ neon (Ne) and 20$\%$ dimethyl ether (DME). This region 
-      is surrounded by a 4~$\mu$m thick window made of aluminized Mylar, which 
-      serves as the cathode and is set at 4260~V.
+      is surrounded by a 4~$\mu$m thick window made of aluminized Mylar set at 4260~V 
+      to serve as the cathode.
    \item The drift region is filled with the same Ne-DME gas mixture and extends 
-      from the cathode to the first GEM, 60 mm away 
-      from the beam axis. The average electric field in this region is about 550~V/cm 
-      and perpendicular to the beam.
+      from the cathode to the first GEM, 60 mm away from the beam axis. The average 
+      electric field in this region is perpendicular to the beam and about 550~V/cm.
    \item The electron amplification system is composed of three GEMs located at 
@@
 about 23$^\circ$ with this gas mixture. This is already a significant angle,
-a heavier gas would have larger angle increasing significantly
-the length of the drift paths as the electron would 
+and heavier gas have a tendency to give larger angle, increasing significantly
+the length of the drift paths as the electrons would 
 make a long spiral around the beam line to reach the GEMs.
@@
 supporting cylinders that could be installed independently in the RTPC after 
-all gluing and soldering operations. The rigidity of the GEM foils was enough
+gluing and soldering operations. The rigidity of the GEM foils was enough
 for the structure to be self-supporting and only the upstream end of the cylinder 
@@
 suppression, and tail cancellation). The amplifier is implemented in a 
-fully-analogue ASIC, PASA~\cite{ALICE-PASA}, while the subsequent signal 
-digitization and elaboration part is implemented in a digital ASIC, 
+fully-analogue ASIC, PASA~\cite{ALICE-PASA}, while the signal 
+digitization and elaboration part is implemented in the digital ASIC, 
 ALTRO~\cite{ALICE-ALTRO}. Both ASICs host 16 channels. The full readout 

### 2017-06-27 eg6-letters/NIM/EG6_RTPC_NIM.tex
Minor edits in NIM paper

@@
 \begin{itemize}
- \item Three regions of Drift Chambers for the tracking of charged 
+ \item Three regions of Drift Chambers (DC) for the tracking of charged 
        particles~\cite{DCref}.
@@
 To detect recoiling $\alpha$ particles from the coherent DVCS on helium, a new 
-radial time projection chamber was developed to track low energy nuclear 
+radial time projection chamber (RTPC) was developed to track low energy nuclear 
 fragments. The solenoid field was used to track and measure momentum of 
@@
 data acquisition system described in section \ref{sec_readout} was reconfigured 
-to increase the event readout rate. The calibration strategy and results for 
-the RTPC are discussed in section \ref{sec_calib}. Finally, the overall performance
+to increase the event readout rate. The calibration methods 
+are discussed in section \ref{sec_calib}. Finally, the overall performance
 of the RTPC is described in section \ref{sec_perfor}.
@@
 particles are stopped very rapidly, so the RTPC was designed to be as close 
-as possible to the target and fit inside the 230 mm diameter bore of the 
+as possible to the target and fit inside the 230~mm diameter bore of the 
 5 Tesla solenoid magnet.
@@
    \item The 6 atm helium-4 target extends along the beam line axis; it 
-      is a 284~mm long, 6~mm in diameter straw with a 27-$\mu$m Kapton wall.
+      is a 284~mm long, 6~mm diameter straw with a 27-$\mu$m Kapton wall.
    \item The first gas gap covers a radial range from 3 mm to 20 mm. It is 
@@
 
-One of the important challenge in developing the radial TPC was how to obtain a 
+One of the important challenge in developing the radial TPC was to obtain a 
 good support structure for the GEM foils to allow a tractable 
@@
 inverting the RTPC signals polarity -- from negative to positive -- to match the 
-requirements of the subsequent readout system, and driv the 6~m long ribbon 
+requirements of the subsequent readout system, and drive the 6~m long ribbon 
 cable that connects to it.
@@
 individual runs (approximately 2 hours long). We observe a significant 
-variation of the drift speed over time and accounted for it in the drift 
-speed used for the track reconstruction.
+variation of the drift speed over time that need to be accounted for 
+in track reconstruction.
 
@@
 acquisition of specific calibration runs. These were taken with a lower energy 
-electron beam (1.20 and 1.27 GeV) to enhance the cross section of the elastic 
+electron beam (1.204 and 1.269 GeV) to enhance the cross section of the elastic 
 scattering ($e^{4}$He$\rightarrow e^{4}$He). In this process, the measurement of
@@
 
-The gain of each pad is defined as the ratio between the actual 
-deposited energy and the registered ADC value. 
-To do so we compare the experimental ADCs to the energy deposited 
+To calibrate the gains, we compare the experimental ADCs to the energy deposited 
 for each pad individually in GEANT4 by similar simulated tracks (using the 
@@
 
+\section{Track Reconstruction}
+
 \subsection{Noise Rejection}
@@
 
-\section{Track Reconstruction}\label{sec_rec}
-In order to reconstruct tracks we first select good hits. This means rejecting 
-out-of-time hits as well as the hits linked to the electronic noise. The second step is 
-to reconstruct the spacial origin of the hits using the extracted drift speed and drift path 
+\subsection{Track Fitting}\label{sec_rec}
+We start with reconstructing the spacial origin of the hits using the extracted drift speed and drift path 
 parameters. For each registered hit, we calculate a position of emission from 
@@
 slightly different behavior and give also different particle yield. However, 
-this should not necessarily be linked to a different performance of the RTPC. 
+this should not necessarily be linked to different efficiencies within the RTPC. 
 Indeed, there is a complicated convolution of CLAS and the RTPC acceptances 
@@
 designed to measure helium-4 nuclei in high rate environment. The operation
-of the detector was successful and allowed to detect helium nuclei at a rate
-of 3.1 kHz in coincidence with the detection of high energy electrons and 
+of the detector was successful and allowed to detect helium nuclei with a 75\%
+efficiency and a readout rate
+of 3.1 kHz triggered by the detection of high energy electrons and 
 photons in the CLAS spectrometer.

### 2017-06-27 eg6-letters/NIM/EG6_RTPC_NIM.tex
Typo

@@
 and direction of the RTPC track provides a clean selection of elastically-scattered
-$^4$He, showin in Fig.~\ref{fig:w}.
+$^4$He, shown in Fig.~\ref{fig:w}.
 

### 2017-06-28 eg6-letters/NIM/acknowledgment.tex
typo corrections
Updates authors and acknow. of NIM paper

@@
 possible. This work was supported in part by the French Centre National de la 
-Recherche Scientifique and the U.S. Department of Energy. One of the 
-author (M.H.) also 
-acknowledge the support of the Consulat G\'en\'eral de France \`a J\'erusalem. 
+Recherche Scientifique (CNRS), the Italian Istituto Nazionale di Fisica Nucleare (INFN) 
+and the U.S. Department of Energy. The 
+author (M.~Hattawy) also acknowledges the support of the {\it Consulat 
+G\'en\'eral de France \`a J\'erusalem}. 
 The Southeastern Universities Research Association operates the Thomas 

### 2017-06-29 eg6-letters/NIM/EG6_RTPC_NIM.tex
Typo in the NIM abstract
Couple of typos

@@
 the RTPC positioned directly around a gaseous $^4$He target, allowing a detection
-threshold as low as 12~MeV for $^4$He. This article discuses the design,
+threshold as low as 12~MeV for $^4$He. This article discusses the design,
 principle of operation, calibration methods and the performances of this RTPC.
@@
 and for data readout. Each RCU can handle up to 25 FECs with communication 
-between them performed trough a 
+between them performed through a 
 custom back-plane, implementing a low-Voltage signal bus. The RCU communicates 
@@
 Due to the non perfect experimental conditions, in particular variations in the 
-gas mixture~\footnote{It was noted during the experiment that leaks appeared
+gas mixture\footnote{It was noted during the experiment that leaks appeared,
+most likely in one of the $4 \mu$m foils between the beam and drift regions,
 and the gas flow had to be increased in few occasions to compensate for this.}, 

### 2017-07-04 eg6-letters/coherent/dvcs_he4_prl.tex
Add reference to the technical RTPC paper

@@
 and $6$-mm-diameter Kapton tube with $27$-$\mu$m-thick walls filled with 
-gaseous $^4$He at 6~atm. The experiment (E08-024)~\cite{Hafidi:2008pr} collected
+gaseous $^4$He at 6~atm (see~\cite{Dupre:2017upj} for a detailed description of 
+the RTPC and its performances). The experiment (E08-024)~\cite{Hafidi:2008pr} collected
 data over 40 days at the end of 2009 using a 
@@
 
+\bibitem{Dupre:2017upj} 
+  R.~Dupré {\it et al.},
+  arXiv:1706.10160 [physics.ins-det].
+  (submitted to Nucl.\ Instrum.\ Meth.\ A)
+
 \bibitem{Hafidi:2008pr} 

### 2017-07-04 eg6-letters/NIM/EG6_RTPC_NIM.tex
NIM:  z-resolutions now after subtracting CLAS contribution
rm Line numbers
Add Stepan's comments

@@
 \usepackage[displaymath]{lineno}
-\linenumbers
 \begin{document}
@@
 simultaneously. The CLAS spectrometer~\cite{CLASref}, located
-in Hall-B, is based on a superconducting toroidal magnet and composed of 
+in Hall-B, was based on a superconducting toroidal magnet and composed of 
 several sub-detectors. Figure~\ref{fig:CLAS} shows a three dimensional 
@@
        of charged particles, thus allowing momentum measurement with the DC tracking information.
- \item Threshold Cherenkov Counters for electron identification at momenta 
+ \item Threshold Cherenkov Counters (CC) for electron identification at momenta 
        $<2.7$ GeV~\cite{CCref}.
- \item Scintillation Counters to identify charged hadrons by measuring their 
+ \item Scintillation Counters (SC) to identify charged hadrons by measuring their 
        time of flight~\cite{TOFref}.
@@
 
-Measurement of the Deeply Virtual Compton Scattering (DVCS) process
-($eH \rightarrow e' H' \gamma$, where $H$ is a nucleon or nuclei) necessitates an upgrade
-of this setup.  With a 6 GeV electron beam, the majority of DVCS photons are produced
-at very forward angles, where the acceptance of the EC is poor. To extend the detection range,
-an inner calorimeter (IC) was built for the E01-113 experiment in 2005~\cite{FX}.
-The IC is constructed from 424 lead-tungstate (PbWO$_{4}$) crystals, covering polar 
-angles between 5$^{\circ}$ and 15$^{\circ}$~\cite{Hyon-suk}. To protect the 
+For certain experiments the base CLAS system was complimented with ancillary 
+detectors. For exemple, the measurement of the Deeply Virtual Compton 
+Scattering (DVCS) process ($eH \rightarrow e' H' \gamma$, where $H$ is a 
+nucleon or nuclei) necessitates an upgrade of the photon detection system. 
+Indeed, with a 6 GeV electron beam, the majority of DVCS photons are produced 
+at very forward angles, where the acceptance of the EC was poor. To extend the 
+detection range, an inner calorimeter (IC) was built for the E01-113 
+experiment in 2005~\cite{FX}. The IC is constructed from 424 lead-tungstate 
+(PbWO$_{4}$) crystals, covering polar angles between 5$^{\circ}$ and 
+15$^{\circ}$~\cite{Hyon-suk}. To protect the 
 CLAS detector and the IC from the large flux of low energy M{\o}ller 
@@
 fragments. The solenoid field was used to track and measure momentum of 
-particles in RTPC. This 
-setup was used during a three months experimental run~\cite{proposal1,proposal2}
+particles in RTPC. The CLAS detector supplemented with IC and RTPC was used 
+during a three months experimental run~\cite{proposal1,proposal2}
 in 2009 with a longitudinally polarized electron beam of 130~nA 
@@
 
-The original design of the RTPC~\cite{BONUS-NIM} was developed for the BoNuS 
-experiment at Jefferson Lab which took data in CLAS in 2005. An enhanced design, 
+The original design of the RTPC was developed for the BoNuS 
+experiment at Jefferson Lab which took data in CLAS in 2005~\cite{BONUS-NIM}. An enhanced design, 
 used in the 2009 DVCS experiment, is described in section \ref{sec_design} 
@@
 data acquisition system described in section \ref{sec_readout} was reconfigured 
-to increase the event readout rate. The calibration methods 
+to increase the event readout rate. The tracking algorithm is discussed in section
+\ref{sec_tracking}. The calibration methods 
 are discussed in section \ref{sec_calib}. Finally, the overall performance
@@
       gas mixture of 80$\%$ neon (Ne) and 20$\%$ dimethyl ether (DME). This region 
-      is surrounded by a 4~$\mu$m thick window made of aluminized Mylar set at 4260~V 
+      is surrounded by a 4~$\mu$m thick window made of aluminized Mylar set at $- 4260$~V 
       to serve as the cathode.
@@
       radii of 60, 63 and 66 mm. In this configuration, the first GEM layer 
-      serves as the anode and each subsequent GEM is set at a lower Voltage to
+      serves as the anode and each subsequent GEM is set at a lower voltage to
       obtain a strong ($\sim$1600 V/cm) electric field between the GEM foils. A 
@@
 showed that with the axial 5~T field, we would have a Lorentz angle of 
-about 23$^\circ$ with this gas mixture. This is already a significant angle,
-and heavier gas have a tendency to give larger angle, increasing significantly
-the length of the drift paths as the electrons would 
-make a long spiral around the beam line to reach the GEMs.
+about 23$^\circ$ with this gas mixture.
 
@@
 for the structure to be self-supporting and only the upstream end of the cylinder 
-was fixed to the main mechanical structure. This design only left a 
+was fixed to the main mechanical support structure. This design only left a 
 light fiberglass ring in the downstream end, reducing to a minimum secondary 
@@
 RTPC has 40 rows and 40 columns of pads. The shaded region in Fig.~\ref{fig:PADs} 
-shows how pads are grouped to 16 channel pre-amplifiers. The pre-amplifier boards, 
+shows how pads were grouped on 16 channel pre-amplifiers. The pre-amplifier boards, 
 already employed in the BoNuS RTPC~\cite{BONUS-NIM}, serve the dual purpose of 
@@
 between them performed through a 
-custom back-plane, implementing a low-Voltage signal bus. The RCU communicates 
+custom back-plane, implementing a low-voltage signal bus. The RCU communicates 
 with the CLAS data acquisition (DAQ) system 
@@
 which the dropping edge passes half the maximum number of hits in the 
-histogram. This value was measured in bins along the 200 mm RTPC's length to take into 
+histogram. This value was measured in bins along the 200~mm RTPC's length to take into 
 account variations in the electric and magnetic field in the RTPC (see 
@@
 
-Due to the non perfect experimental conditions, in particular variations in the 
-gas mixture\footnote{It was noted during the experiment that leaks appeared,
-most likely in one of the $4 \mu$m foils between the beam and drift regions,
-and the gas flow had to be increased in few occasions to compensate for this.}, 
-the drift speed changes during the three months long experimental run.  
+Due to the non perfect experimental conditions, in particular possible contaminations 
+of our gas mixture, the drift speed changed during the three months long experimental 
+run\footnote{We had to increase the gas flow during the experiment due to a small leak 
+in the RTPC, which concurred to the large shift of drift time observed around run number 
+61600. While our gas system was kept slightly over 
+atmospheric pressure to avoid contamination from air or other external gases, it 
+is likely that this leak was the source of modification of the gas mixture.}.  
 Figure~\ref{fig:Drift_run_number_1} shows the $T_{Max/2}$ values for 
@@
 
-In summary, we obtain from our calibration a parametrization of the drift speed 
+In summary, we obtain from our calibration a parame\-tri\-zation of the drift speed 
 as a function of both position along the beam axis and the run number. These 
@@
 The drift path is the trajectory followed by the electrons released through 
-ionization in the gas. Software exists to calculate them, in particular
+ionization in the gas. We calculate them with
 MAGBOLTZ~\cite{MAGBOLTZ}, but it requires knowledge of the detector's 
@@
 first calibration, but, 
-as can be seen with the drift speed, gas composition is far from stable in the 
+as can be seen with the drift speed, experimental conditions were unstable in the 
 chamber. Moreover, the 4 $\mu$m foil used as a cathode is easily deformed, such
@@
 scattering ($e^{4}$He$\rightarrow e^{4}$He). In this process, the measurement of
-the electron kinematic allows to calculate directly the kinematic of the Helium nucleus. 
-By comparing the alpha particle's calculated momentum and angle of recoil to the 
+the electron kinematics allows to calculate directly the kinematics of the Helium nucleus. 
+By comparing the calculated momentum and angle of the recoil alpha particle to the 
 measurement in the RTPC, we tuned the drift paths independently of our 
-knowledge of the exact chamber's conditions.
+knowledge of the chamber's conditions.
 
-Based on the kinematic of electrons in the calibration data, 
+Based on the kinematics of the electrons in the calibration data, 
 we generate the helium nucleus in our RTPC GEANT4 simulation~\cite{GEANT4}. Then 
@@
 as the ratio of the measured ADCs to the simulated deposited energy.  
-Then, these gains are refined using correcting factors obtained from a 
+Then, these gains are refined using correction factors obtained from a 
 sample of good tracks. For each track, we calculate the corrected 
@@
 avoid any bias from this simulation based calibration method.
-Final results are shown in Fig.~\ref{fig:dedx_p_exp_2nd}.
+Final results are shown in Fig.~\ref{fig:dedx_p_exp_2nd}, where energy 
+loss of particles is plotted against momentum over charge ration. One can 
+clearly see the band for $^4$He in its expected position.
 
@@
 \section{Track Reconstruction}
+\label{sec_tracking}
 
@@
 shown in the top panel of Fig.~\ref{fig:noise} for a particularly noisy 
-channel. Its amplitude is not dissimilar to those of real tracks, and about 
+channel. Its amplitude is not dissimilar to those of real tracks. About 
 18\% of the readout channels exhibit large contributions from this noise 
@@
 
-The second is a coherent noise affecting about 25\% of the preamplifiers, where 
-the signature is simultaneous hits in most of the 16 channels in a preamp 
-group.   An event-based technique to identify and remove it was developed based 
+The second noise signature was a coherent noise affecting about 25\% of the 
+amplifiers boards, when simultaneous hits in most of the 16 channels of the
+board were recorded. An event-based technique to identify and remove this noise was developed based 
 on counting simultaneous hits in preamp group, and, if sufficiently large, 
@@
 \hline
-Left &  6.0 mm & 3.8$^{\circ}$ & 1.9$^{\circ}$ & 9$\%$ \\
-Right & 7.4 mm & 4.0$^{\circ}$ & 1.9$^{\circ}$ & 8$\%$\\
+Left &  5.3 mm & 3.8$^{\circ}$ & 1.9$^{\circ}$ & 9$\%$ \\
+Right & 6.5 mm & 4.0$^{\circ}$ & 1.9$^{\circ}$ & 8$\%$\\
 \hline
@@
 \subsection{Efficiency}
-The previous discussions have shown that the two modules of the RTPC have 
-slightly different behavior and give also different particle yield. However, 
-this should not necessarily be linked to different efficiencies within the RTPC. 
-Indeed, there is a complicated convolution of CLAS and the RTPC acceptances 
-that can significantly affect the yields and kinematics of the detected 
-particles. To clarify this question, we measured the efficiency of the RTPC
+We measured the efficiency of the RTPC
 using elastic scattering on $^4$He by comparing the inclusive yield, based
@@
 recoil is also detected (see Fig.~\ref{fig:w}). We present in Fig.~\ref{fig:rtpc_eff}
-the results for the two modules of the detector. We observe that the left and 
-the right modules have similar efficiencies except near the target windows.
+the results for the two halves of the detector. We observe that the left and 
+the right modules have similar efficiencies except near the upstream target 
+window. This difference is due to the large number of dead channels in this 
+area of the detector, which are concentrated on the left.
 

### 2017-07-05 eg6-letters/NIM/EG6_RTPC_NIM.tex
New wave of Stepan's comments

@@
 The original design of the RTPC was developed for the BoNuS 
-experiment at Jefferson Lab which took data in CLAS in 2005~\cite{BONUS-NIM}. An enhanced design, 
+experiment at Jefferson Lab which took data with CLAS in 2005~\cite{BONUS-NIM}. An enhanced design, 
 used in the 2009 DVCS experiment, is described in section \ref{sec_design} 
@@
 data acquisition system described in section \ref{sec_readout} was reconfigured 
-to increase the event readout rate. The tracking algorithm is discussed in section
-\ref{sec_tracking}. The calibration methods 
-are discussed in section \ref{sec_calib}. Finally, the overall performance
+to increase the event readout rate. The calibration methods 
+are discussed in section \ref{sec_calib}. The tracking algorithm is discussed in section
+\ref{sec_tracking}. Finally, the overall performance
 of the RTPC is described in section \ref{sec_perfor}.
@@
 \begin{itemize}
-   \item The 6 atm helium-4 target extends along the beam line axis; it 
+   \item The 6 atm helium-4 target extends along the beam axis; it 
       is a 284~mm long, 6~mm diameter straw with a 27-$\mu$m Kapton wall.
-   \item The first gas gap covers a radial range from 3 mm to 20 mm. It is 
+   \item The first gas gap covers the radial range from 3 mm to 20 mm. It is 
       filled with $^{4}$He gas at 1~atm to minimize secondary interactions from
@@
 calibration was improved through several iterations of the
-process described below, each iteration increasing the number of events 
+process described below, with each time an increasing number of events 
 properly reconstructed in the RTPC. The figures presented in this section
@@
 electrons released close to the cathode take the most time to reach the readout 
-pads, but cylindrical symmetry insures that they always travel the same 
-distance. We illustrate this in Fig.~\ref{fig:RTPC_signals}, where we depict a 
+pads, the cylindrical symmetry insures that the maximum distance is the same for all 
+tracks. We illustrate this in Fig.~\ref{fig:RTPC_signals}, where we depict a 
 typical $^{4}$He track. By measuring the maximum time ($T_{Max}$), we can infer the drift 
@@
 
-Due to the non perfect experimental conditions, in particular possible contaminations 
+Due to the non perfect experimental conditions, in particular possible contamination 
 of our gas mixture, the drift speed changed during the three months long experimental 
@@
 Figure~\ref{fig:Drift_run_number_1} shows the $T_{Max/2}$ values for 
-individual runs (approximately 2 hours long). We observe a significant 
-variation of the drift speed over time that need to be accounted for 
-in track reconstruction.
+individual runs (approximately 2 hours long). We observe significant change in 
+the drift speed before and after run 61600, while variations within these periods 
+are ~2\%. These variations of the drift speed were accounted in the track reconstruction
 
@@
 first calibration, but, 
-as can be seen with the drift speed, experimental conditions were unstable in the 
-chamber. Moreover, the 4 $\mu$m foil used as a cathode is easily deformed, such
+as can be seen with the drift speed, conditions in the chamber were changing 
+over time. Moreover, the 4 $\mu$m foil used as a cathode is easily deformed, such
 that we expect the geometry accuracy to be of few millimeters, directly impacting 
@@
 paths calibration). This requires a very good GEANT4 simulation 
-including drift paths, but also the spread of the charges along the path
+including drift paths, but also the spread of the charge along the path
 before reaching the pad, so that the simulated hits match the experimental 
@@
 Final results are shown in Fig.~\ref{fig:dedx_p_exp_2nd}, where energy 
-loss of particles is plotted against momentum over charge ration. One can 
+loss of particles is plotted against momentum over charge ratio. One can 
 clearly see the band for $^4$He in its expected position.
@@
 shown in the top panel of Fig.~\ref{fig:noise} for a particularly noisy 
-channel. Its amplitude is not dissimilar to those of real tracks. About 
+channel. Its amplitude is similar to those of real tracks. About 
 18\% of the readout channels exhibit large contributions from this noise 
@@
 board were recorded. An event-based technique to identify and remove this noise was developed based 
-on counting simultaneous hits in preamp group, and, if sufficiently large, 
-perform a dynamic pedestal subtraction based on the average ADC of the 
-channels' neighbors within the preamp group.
+on counting simultaneous hits in each pre-amplifier group, and, if sufficiently large, 
+perform a dynamic pedestal subtraction based on the average ADC of neighboring 
+channels within this group.
 
 The sources of these effects were not determined, but rejection techniques 
-allowed to reconstruct 10\% more good tracks, with no significant loss, and 
+allowed to reconstruct 10\% more good tracks and 
 recover 70 channels that were previously ignored due to excessive noise levels.
@@
 hits has to be less than 10.5 mm to chain them, which roughly corresponds to 
-neighbors and next to neighbors. Then, we fit with a helix the chains that have a minimum of 
-10 hits. We make the fit in two iterations, first with all the hits of the chain 
-and the beam line, then, in the second iteration, 
-the hits that are 5 mm or farther from the first fit are excluded.
+neighbors and next to neighbors. Then, we fit the chains with a helix if they have a minimum of 
+10 hits. We then eliminate from the chain the hits that are 5 mm or farther from the fit
+as they are not likely part of the same track.
+This new reduced chain is used for a second and final helix fit.
 
@@
 the right modules have similar efficiencies except near the upstream target 
-window. This difference is due to the large number of dead channels in this 
-area of the detector, which are concentrated on the left.
+window. This difference is due to the large number of dead channels concentrated
+in this part of the left half of the detector
 

### 2017-07-06 eg6-letters/incoherent/figs-sources/ALU_90_p_vs_Q2_shortscenrario.C
update the incoherent plots

@@ -1,0 +1,167 @@
+void ALU_90_p_vs_Q2_shortscenrario()
+{
+//=========Macro generated from canvas: Can_p_Q2/DVCS Helium BoNuS
+//=========  (Thu Jul  6 14:04:33 2017) by ROOT version6.09/01
+   TCanvas *Can_p_Q2 = new TCanvas("Can_p_Q2", "DVCS Helium BoNuS",0,0,600,450);
+   gStyle->SetOptFit(1);
+   Can_p_Q2->SetHighLightColor(2);
+   Can_p_Q2->Range(-0.2792208,-0.2168831,4.915584,0.5623377);
+   Can_p_Q2->SetFillColor(0);
+   Can_p_Q2->SetBorderMode(0);
+   Can_p_Q2->SetBorderSize(2);
+   Can_p_Q2->SetLeftMargin(0.15);
+   Can_p_Q2->SetRightMargin(0.08);
+   Can_p_Q2->SetTopMargin(0.08);
+   Can_p_Q2->SetBottomMargin(0.15);
+   Can_p_Q2->SetFrameBorderMode(0);
+   Can_p_Q2->SetFrameBorderMode(0);
+   
+   TH2F *HALU_p_vs_Q2__1 = new TH2F("HALU_p_vs_Q2__1","",100,0.5,4.5,100,-0.1,0.5);
+   HALU_p_vs_Q2__1->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   HALU_p_vs_Q2__1->SetLineColor(ci);
+   HALU_p_vs_Q2__1->GetXaxis()->SetTitle("Q^{2} [GeV^{2}]");
+   HALU_p_vs_Q2__1->GetXaxis()->CenterTitle(true);
+   HALU_p_vs_Q2__1->GetXaxis()->SetNdivisions(605);
+   HALU_p_vs_Q2__1->GetXaxis()->SetLabelFont(22);
+   HALU_p_vs_Q2__1->GetXaxis()->SetLabelSize(0.05);
+   HALU_p_vs_Q2__1->GetXaxis()->SetTitleSize(0.07);
+   HALU_p_vs_Q2__1->GetXaxis()->SetTitleFont(22);
+   HALU_p_vs_Q2__1->GetYaxis()->SetTitle("A_{LU}^{Incoh}(90#circ)");
+   HALU_p_vs_Q2__1->GetYaxis()->CenterTitle(true);
[…]

### 2017-07-06 eg6-letters/incoherent/figs-sources/ALU_90_p_vs_t_shortscenrario.C

@@ -1,0 +1,407 @@
+void ALU_90_p_vs_t_shortscenrario()
+{
+//=========Macro generated from canvas: Can_p_t/DVCS Helium BoNuS
+//=========  (Thu Jul  6 14:04:34 2017) by ROOT version6.09/01
+   TCanvas *Can_p_t = new TCanvas("Can_p_t", "DVCS Helium BoNuS",0,0,600,450);
+   gStyle->SetOptFit(1);
+   Can_p_t->SetHighLightColor(2);
+   Can_p_t->Range(-0.2337662,-0.2168831,1.324675,0.5623377);
+   Can_p_t->SetFillColor(0);
+   Can_p_t->SetBorderMode(0);
+   Can_p_t->SetBorderSize(2);
+   Can_p_t->SetLeftMargin(0.15);
+   Can_p_t->SetRightMargin(0.08);
+   Can_p_t->SetTopMargin(0.08);
+   Can_p_t->SetBottomMargin(0.15);
+   Can_p_t->SetFrameBorderMode(0);
+   Can_p_t->SetFrameBorderMode(0);
+   
+   TH2F *HALU_p_vs_t__5 = new TH2F("HALU_p_vs_t__5","",100,0,1.2,100,-0.1,0.5);
+   HALU_p_vs_t__5->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   HALU_p_vs_t__5->SetLineColor(ci);
+   HALU_p_vs_t__5->GetXaxis()->SetTitle("-t [GeV^{2}]");
+   HALU_p_vs_t__5->GetXaxis()->CenterTitle(true);
+   HALU_p_vs_t__5->GetXaxis()->SetNdivisions(605);
+   HALU_p_vs_t__5->GetXaxis()->SetLabelFont(22);
+   HALU_p_vs_t__5->GetXaxis()->SetLabelSize(0.05);
+   HALU_p_vs_t__5->GetXaxis()->SetTitleSize(0.07);
+   HALU_p_vs_t__5->GetXaxis()->SetTitleFont(22);
+   HALU_p_vs_t__5->GetYaxis()->SetTitle("A_{LU}^{Incoh}(90#circ)");
+   HALU_p_vs_t__5->GetYaxis()->CenterTitle(true);
+   HALU_p_vs_t__5->GetYaxis()->SetNdivisions(605);
[…]

### 2017-07-06 eg6-letters/incoherent/figs-sources/ALU_90_p_vs_x_shortscenrario.C

@@ -1,0 +1,313 @@
+void ALU_90_p_vs_x_shortscenrario()
+{
+//=========Macro generated from canvas: Can_p_x/DVCS Helium BoNuS
+//=========  (Thu Jul  6 14:04:33 2017) by ROOT version6.09/01
+   TCanvas *Can_p_x = new TCanvas("Can_p_x", "DVCS Helium BoNuS",0,0,600,450);
+   gStyle->SetOptFit(1);
+   Can_p_x->SetHighLightColor(2);
+   Can_p_x->Range(-0.1363636,-0.2168831,0.7727273,0.5623377);
+   Can_p_x->SetFillColor(0);
+   Can_p_x->SetBorderMode(0);
+   Can_p_x->SetBorderSize(2);
+   Can_p_x->SetLeftMargin(0.15);
+   Can_p_x->SetRightMargin(0.08);
+   Can_p_x->SetTopMargin(0.08);
+   Can_p_x->SetBottomMargin(0.15);
+   Can_p_x->SetFrameBorderMode(0);
+   Can_p_x->SetFrameBorderMode(0);
+   
+   TH2F *HALU_p_vs_x__3 = new TH2F("HALU_p_vs_x__3","",100,0,0.7,100,-0.1,0.5);
+   HALU_p_vs_x__3->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   HALU_p_vs_x__3->SetLineColor(ci);
+   HALU_p_vs_x__3->GetXaxis()->SetTitle("x_{B}");
+   HALU_p_vs_x__3->GetXaxis()->CenterTitle(true);
+   HALU_p_vs_x__3->GetXaxis()->SetNdivisions(605);
+   HALU_p_vs_x__3->GetXaxis()->SetLabelFont(22);
+   HALU_p_vs_x__3->GetXaxis()->SetLabelSize(0.05);
+   HALU_p_vs_x__3->GetXaxis()->SetTitleSize(0.07);
+   HALU_p_vs_x__3->GetXaxis()->SetTitleFont(22);
+   HALU_p_vs_x__3->GetYaxis()->SetTitle("A_{LU}^{Incoh}(90#circ)");
+   HALU_p_vs_x__3->GetYaxis()->CenterTitle(true);
+   HALU_p_vs_x__3->GetYaxis()->SetNdivisions(605);
[…]

### 2017-07-06 eg6-letters/incoherent/figs-sources/ALU_ratioInc_Q2_shortscenrario.C

@@ -1,0 +1,117 @@
+void ALU_ratioInc_Q2_shortscenrario()
+{
+//=========Macro generated from canvas: Can/DVCS Helium BoNuS
+//=========  (Thu Jul  6 14:04:33 2017) by ROOT version6.09/01
+   TCanvas *Can = new TCanvas("Can", "DVCS Helium BoNuS",0,0,600,450);
+   gStyle->SetOptFit(1);
+   Can->SetHighLightColor(2);
+   Can->Range(-0.1818182,-0.09220779,4.363636,1.855844);
+   Can->SetFillColor(0);
+   Can->SetBorderMode(0);
+   Can->SetBorderSize(2);
+   Can->SetLeftMargin(0.15);
+   Can->SetRightMargin(0.08);
+   Can->SetTopMargin(0.08);
+   Can->SetBottomMargin(0.15);
+   Can->SetFrameBorderMode(0);
+   Can->SetFrameBorderMode(0);
+   
+   TH2F *HALU_RATIO_Q2__2 = new TH2F("HALU_RATIO_Q2__2","",100,0.5,4,100,0.2,1.7);
+   HALU_RATIO_Q2__2->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   HALU_RATIO_Q2__2->SetLineColor(ci);
+   HALU_RATIO_Q2__2->GetXaxis()->SetTitle("Q^{2} [GeV^{2}]");
+   HALU_RATIO_Q2__2->GetXaxis()->CenterTitle(true);
+   HALU_RATIO_Q2__2->GetXaxis()->SetNdivisions(605);
+   HALU_RATIO_Q2__2->GetXaxis()->SetLabelFont(22);
+   HALU_RATIO_Q2__2->GetXaxis()->SetLabelSize(0.05);
+   HALU_RATIO_Q2__2->GetXaxis()->SetTitleSize(0.07);
+   HALU_RATIO_Q2__2->GetXaxis()->SetTitleFont(22);
+   HALU_RATIO_Q2__2->GetYaxis()->SetTitle("A_{LU}^{Incoh}/A_{LU}^{p}(90#circ)");
+   HALU_RATIO_Q2__2->GetYaxis()->CenterTitle(true);
[…]

### 2017-07-06 eg6-letters/incoherent/figs-sources/ALU_ratioInc_t_shortscenrario.C

@@ -1,0 +1,489 @@
+void ALU_ratioInc_t_shortscenrario()
+{
+//=========Macro generated from canvas: Can_R_t/
+//=========  (Thu Jul  6 14:04:34 2017) by ROOT version6.09/01
+   TCanvas *Can_R_t = new TCanvas("Can_R_t", "",0,0,600,450);
+   gStyle->SetOptFit(1);
+   Can_R_t->SetHighLightColor(2);
+   Can_R_t->Range(-0.2337662,0.1467533,1.324675,1.835065);
+   Can_R_t->SetFillColor(0);
+   Can_R_t->SetBorderMode(0);
+   Can_R_t->SetBorderSize(2);
+   Can_R_t->SetLeftMargin(0.15);
+   Can_R_t->SetRightMargin(0.08);
+   Can_R_t->SetTopMargin(0.08);
+   Can_R_t->SetBottomMargin(0.15);
+   Can_R_t->SetFrameBorderMode(0);
+   Can_R_t->SetFrameBorderMode(0);
+   
+   TH2F *HALU_RATIO_t__6 = new TH2F("HALU_RATIO_t__6","",100,0,1.2,100,0.4,1.7);
+   HALU_RATIO_t__6->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   HALU_RATIO_t__6->SetLineColor(ci);
+   HALU_RATIO_t__6->GetXaxis()->SetTitle("-t [GeV^{2}]");
+   HALU_RATIO_t__6->GetXaxis()->CenterTitle(true);
+   HALU_RATIO_t__6->GetXaxis()->SetNdivisions(605);
+   HALU_RATIO_t__6->GetXaxis()->SetLabelFont(22);
+   HALU_RATIO_t__6->GetXaxis()->SetLabelSize(0.05);
+   HALU_RATIO_t__6->GetXaxis()->SetTitleSize(0.07);
+   HALU_RATIO_t__6->GetXaxis()->SetTitleFont(22);
+   HALU_RATIO_t__6->GetYaxis()->SetTitle("A_{LU}^{Incoh}/A_{LU}^{p} (90#circ)");
+   HALU_RATIO_t__6->GetYaxis()->CenterTitle(true);
+   HALU_RATIO_t__6->GetYaxis()->SetNdivisions(605);
+   HALU_RATIO_t__6->GetYaxis()->SetLabelFont(22);
[…]

### 2017-07-06 eg6-letters/incoherent/figs-sources/ALU_ratioInc_x_shortscenrario.C

@@ -1,0 +1,418 @@
+void ALU_ratioInc_x_shortscenrario()
+{
+//=========Macro generated from canvas: Can_R_x/DVCS Helium BoNuS
+//=========  (Thu Jul  6 14:04:34 2017) by ROOT version6.09/01
+   TCanvas *Can_R_x = new TCanvas("Can_R_x", "DVCS Helium BoNuS",0,0,600,450);
+   gStyle->SetOptFit(1);
+   Can_R_x->SetHighLightColor(2);
+   Can_R_x->Range(-0.1558442,0.02727273,0.8831169,1.845455);
+   Can_R_x->SetFillColor(0);
+   Can_R_x->SetBorderMode(0);
+   Can_R_x->SetBorderSize(2);
+   Can_R_x->SetLeftMargin(0.15);
+   Can_R_x->SetRightMargin(0.08);
+   Can_R_x->SetTopMargin(0.08);
+   Can_R_x->SetBottomMargin(0.15);
+   Can_R_x->SetFrameBorderMode(0);
+   Can_R_x->SetFrameBorderMode(0);
+   
+   TH2F *HALU_RATIO_x__4 = new TH2F("HALU_RATIO_x__4","",100,0,0.8,100,0.3,1.7);
+   HALU_RATIO_x__4->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   HALU_RATIO_x__4->SetLineColor(ci);
+   HALU_RATIO_x__4->GetXaxis()->SetTitle("x_{B}");
+   HALU_RATIO_x__4->GetXaxis()->CenterTitle(true);
+   HALU_RATIO_x__4->GetXaxis()->SetNdivisions(605);
+   HALU_RATIO_x__4->GetXaxis()->SetLabelFont(22);
+   HALU_RATIO_x__4->GetXaxis()->SetLabelSize(0.05);
+   HALU_RATIO_x__4->GetXaxis()->SetTitleSize(0.07);
+   HALU_RATIO_x__4->GetXaxis()->SetTitleFont(22);
+   HALU_RATIO_x__4->GetYaxis()->SetTitle("A_{LU}^{Incoh}/A_{LU}^{p} (90#circ)");
+   HALU_RATIO_x__4->GetYaxis()->CenterTitle(true);
[…]

### 2017-07-06 eg6-letters/incoherent/figs-sources/incoherent_ALU_phi.C

@@ -1,0 +1,4209 @@
+void incoherent_ALU_phi()
+{
+//=========Macro generated from canvas: c15/
+//=========  (Thu Jul  6 14:04:35 2017) by ROOT version6.09/01
+   TCanvas *c15 = new TCanvas("c15", "",0,0,1200,900);
+   gStyle->SetOptFit(1);
+   c15->Range(0,0,1,1);
+   c15->SetFillColor(0);
+   c15->SetBorderMode(0);
+   c15->SetBorderSize(2);
+   c15->SetLeftMargin(0.06395349);
+   c15->SetRightMargin(0.01968414);
+   c15->SetTopMargin(0.02680798);
+   c15->SetBottomMargin(0.08527131);
+   c15->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: c15_1
+   TPad *c15_1 = new TPad("c15_1", "_1",0,0.6772185,0.2930441,0.973192);
+   c15_1->Draw();
+   c15_1->cd();
+   c15_1->Range(-135.625,-0.35,375,0.35);
+   c15_1->SetFillColor(0);
+   c15_1->SetBorderMode(0);
+   c15_1->SetBorderSize(2);
+   c15_1->SetLeftMargin(0.255814);
+   c15_1->SetRightMargin(0);
+   c15_1->SetTopMargin(0);
+   c15_1->SetBottomMargin(0);
+   c15_1->SetFrameBorderMode(0);
+   c15_1->SetFrameBorderMode(0);
+   
+   TMultiGraph *multigraph = new TMultiGraph();
+   multigraph->SetName("");
+   multigraph->SetTitle("");
+   
+   Double_t Graph_fx1011[9] = {
+   21.0166,
+   62.924,
+   95.4492,
+   140.122,
+   182.321,
+   220.463,
+   258.455,
+   303.145,
+   337.42};
+   Double_t Graph_fy1011[9] = {
+   0.0541395,
+   0.0771959,
+   0.191317,
+   0.107603,
+   0.0448121,
+   -0.0294133,
+   -0.126129,
+   -0.12384,
+   -0.0122601};
+   Double_t Graph_fex1011[9] = {
+   0,
+   0,
+   0,
+   0,
+   0,
+   0,
+   0,
+   0,
+   0};
+   Double_t Graph_fey1011[9] = {
+   0.04257746,
+   0.04345303,
+   0.03915796,
+   0.0538811,
[…]

### 2017-07-06 eg6-letters/NIM/EG6_RTPC_NIM.tex

@@
 A new Radial Time Projection Chamber (RTPC) was developed at the Jefferson 
-Laboratory to track low-energy nuclear recoils for the purpose of measuring
-exclusive nuclear reactions, such as coherent Deeply Virtual Compton Scattering
-and coherent meson production off $^4$He. In such processes, the $^4$He nucleus
-remains intact in the final state, however the CEBAF Large
-Acceptance Spectrometer (CLAS) cannot track the low energy $\alpha$ particles. In
-2009, we carried out measurements using the CLAS spectrometer supplemented by
+Laboratory to track low-energy nuclear recoils to measure
+exclusive nuclear reactions, such as coherent deeply virtual Compton scattering
+and coherent meson production off $^4$He. In
+2009, we carried out these measurements using the CEBAF Large
+Acceptance Spectrometer (CLAS) supplemented by
 the RTPC positioned directly around a gaseous $^4$He target, allowing a detection
 threshold as low as 12~MeV for $^4$He. This article discusses the design,
-principle of operation, calibration methods and the performances of this RTPC.
+principle of operation, calibration methods and performances of this RTPC.
 \end{abstract}
@@
 For certain experiments the base CLAS system was complimented with ancillary 
-detectors. For exemple, the measurement of the Deeply Virtual Compton 
+detectors. For example, the measurement of the Deeply Virtual Compton 
 Scattering (DVCS) process ($eH \rightarrow e' H' \gamma$, where $H$ is a 
@@
 detection range, an inner calorimeter (IC) was built for the E01-113 
-experiment in 2005~\cite{FX}. The IC is constructed from 424 lead-tungstate 
+experiment in 2005~\cite{FX}. The IC was constructed from 424 lead-tungstate 
 (PbWO$_{4}$) crystals, covering polar angles between 5$^{\circ}$ and 
@@
 fragments. The solenoid field was used to track and measure momentum of 
-particles in RTPC. The CLAS detector supplemented with IC and RTPC was used 
+particles in the RTPC. The CLAS detector supplemented with both IC and RTPC was used 
 during a three months experimental run~\cite{proposal1,proposal2}
@@
 The original design of the RTPC was developed for the BoNuS 
-experiment at Jefferson Lab which took data with CLAS in 2005~\cite{BONUS-NIM}. An enhanced design, 
+experiment at Jefferson Lab which took data with CLAS in 
+2005~\cite{BONUS-NIM}. Significant improvements were made to the RTPC mechanical 
+structure and fabrication technique that both increased the acceptance and 
+reduced the amount of material in the path of the outgoing particles. The enhanced design, 
 used in the 2009 DVCS experiment, is described in section \ref{sec_design} 
-of this paper. Significant improvements were made to the RTPC mechanical 
-structure and fabrication technique that both increased the acceptance and 
-reduced the amount of material in the path of the outgoing particles. The 
+of this paper. The 
 data acquisition system described in section \ref{sec_readout} was reconfigured 
 to increase the event readout rate. The calibration methods 
-are discussed in section \ref{sec_calib}. The tracking algorithm is discussed in section
+are discussed in section \ref{sec_calib} and the tracking algorithm in section
 \ref{sec_tracking}. Finally, the overall performance
@@
 \includegraphics[{trim={0 12cm 0 0},clip, scale=0.4}]{fig_2017/RTPC_1_all.pdf}
-\caption{Schematic drawing of CLAS RTPC in a plane perpendicular to the beam 
+\caption{Schematic drawing of the CLAS RTPC in a plane perpendicular to the beam 
 direction. See text for description of the elements.} \label{fig:RTPC_1_4}
@@
    \includegraphics[scale=0.55]{fig/PADs.png}
-   \caption[]{A schematic representation of a part of the readout system.  The 
+   \caption[]{A schematic representation of the readout pads. The 
    shaded sixteen pads are a group of pads that are connected to the same 
@@
 
-The RTPC electron collection system has 3200 readout pads. These elements are
-parallel to the GEMs, 69 mm from the central axis.
-Figure~\ref{fig:PADs} shows a schematic drawing of the size and 
-configuration of the pads. Each readout pad is 5 mm in length and 4.45 mm in 
-width. The shift between the rows permits the reduction of aliasing. Each half of the 
-RTPC has 40 rows and 40 columns of pads. The shaded region in Fig.~\ref{fig:PADs} 
-shows how pads were grouped on 16 channel pre-amplifiers. The pre-amplifier boards, 
+The RTPC electron collection system had 3200 readout pads. These elements were
+located at the end of the amplification region, 69 mm from the central axis.
+Figure \ref{fig:PADs} illustrates the configuration of the 5 by 4.45 mm pads,
+where the shift between the rows was implemented to reduce aliasing. Each half of the 
+RTPC had 40 rows and 40 columns of pads. The shaded region in Fig.~\ref{fig:PADs} 
+shows how pads were grouped to 16 channels pre-amplifiers. The pre-amplifier boards, 
 already employed in the BoNuS RTPC~\cite{BONUS-NIM}, serve the dual purpose of 
 inverting the RTPC signals polarity -- from negative to positive -- to match the 
-requirements of the subsequent readout system, and drive the 6~m long ribbon 
+requirements of the subsequent readout system, and driving the 6-m long ribbon 
 cable that connects to it.
@@
 
-The readout system is based on the Front End Electronic (FEE) boards originally 
-developed for the ALICE TPC readout system at CERN~\cite{ALICE-FEE}. Each 
-readout channel is made of three main components: a charge sensitive, low 
-impedance shaping amplifier, a 10 bit, 25-MHz digitizer, and a digital circuit 
-that implements online-processing algorithms (pedestal subtraction, zero 
-suppression, and tail cancellation). The amplifier is implemented in a 
-fully-analogue ASIC, PASA~\cite{ALICE-PASA}, while the signal 
-digitization and elaboration part is implemented in the digital ASIC, 
-ALTRO~\cite{ALICE-ALTRO}. Both ASICs host 16 channels. The full readout 
-chain is implemented on a single Front End Card (FEC), hosting 128 channels. 
-FECs are hosted in custom crates, mounted close to the detector. A readout 
-control unit (RCU) board is used to distribute the trigger signal to FECs 
-and for data readout. Each RCU can handle up to 25 FECs with communication 
-between them performed through a 
-custom back-plane, implementing a low-voltage signal bus. The RCU communicates 
-with the CLAS data acquisition (DAQ) system 
-trough a 200 MB/s optical link, connected to a data acquisition PC hosting 
-a ReadOut Receiver Card (RORC) used to interface with 
-the CLAS DAQ system. An Ethernet link is also present, for slow-controls and 
+The readout system, similar to the original BoNuS RTPC system~\cite{BONUS-NIM}, 
+was based on the front end electronic boards originally 
+developed for the ALICE TPC readout system at CERN~\cite{ALICE-FEE}. 
+The Front End Card (FEC) 
+hosted the analogue receiver circuit and the subsequent amplification and 
+digitization stage, based on the PASA~\cite{ALICE-PASA} and ALTRO~\cite{ALICE-ALTRO} 
+ASICS. A Readout Control Unit (RCU) board was used to distribute the trigger signal 
+to FECs and for data readout, with each RCU handling up to 25 FECs. Communication 
+between readout controller application (ROC) and FECs was performed trough a custom 
+backplane, implementing a low-voltage signal bus. The RCU communicated with the 
+CLAS DAQ system trough a 200 MB/s optical link, connected to a data acquisition 
+PC hosting a ReadOut Receiver Card (RORC). This PC hosted the ROC used to interface 
+with the CLAS DAQ system. An Ethernet link was also present, for slow-controls and 
 monitoring.
 
-The triggering and data-readout scheme is as follows. When a Level-1 (L1) trigger 
-is received by a FEC-board, a programmable number of samples $N_0$ is digitized 
-and stored in a data memory, and hence processed by the digital circuit. Upon 
-arrival of Level-2 trigger, the latest processed samples are saved in a 
-multi-event memory, individual to each-channel, ready for readout by the RCU.  
-In our setup, the RCU receives the trigger signal from the CLAS Trigger 
-Supervisor system, and distributes both L1 and L2 signals to all the FECs in 
-the crate, with a definite L1-L2 trigger latency. Such latency is programmable, 
-and has to be long enough to accommodate the digitization of the $N_0$ samples 
-per channel.  In the current implementation, $N_0=100$ samples/channel are 
-acquired for each trigger, operating ALTRO at the reduced sampling frequency of 
-$10$~MHz. The L1-L2 latency is thus fixed to 15 $\mu$s.
+The standard CLAS electron trigger was used to initiate the RTPC readout. For each 
+event, 100 samples/channel were digitized and processed by the ALTRO ASIC. In order 
+to reduce the data size, ALTRO was operated in zero-suppression mode, keeping only 
+samples from channels above a programmable threshold set just above the noise level. 
+Samples were pre-processed 
+by a glitch-filter to reject noise and spurious pulses. To properly reconstruct the 
+signal shape, $N_{PRE}=3$ samples before threshold-crossing and $N_{POST}=3$ samples 
+after the signal returns below threshold were saved.
 
-The trigger signal also initiates RCU readout operation from FEC boards. All 
-the measured samples from active channels are reported, together with a channel 
-identifier and a time-stamp, to the RCU application, that in turns sends them 
-on to the main event builder. During data reconstruction, the acquired samples are 
-processed to obtain, for each readout pad, the accumulated charge (ADC) and the 
-pulse time (T). Since pulse time was obtained as the time-stamp of the first 
-sample above threshold, the resolution is equivalent to the ALTRO sampling 
-time of 100~ns.
+The trigger signal also initiates RCU readout operation from FEC boards. All the 
+measured samples from active channels are reported, together with a channel 
+identifier and a timestamp, to the ROC application, that in turns sends them on 
+the main event builder. Readout from FECs occurs in ``block-transfer'' mode, 
+making use of the ALTRO internal multi-event buffer. This feature could be 
+exploited thanks to the new RCU boards developed for the RTPC readout 
+system\footnote{In the original BONUS system, the U2F readout controller had 
+no multi-event capability and used a USB connection rather than fiber 
+optics for readout. These factors limited the maximum readout rate from the 
+BONUS detector to about 500 Hz.}. In order to read all the detector readout 
+pads, four FEC crates were used, each equipped with 6 boards, plus a ROC. A 
+schematic of the readout system, for a single crate, is reported in 
+figure~\ref{fig:ReadoutScheme}. This configuration permitted to reduce the dead 
+time associated to FEC readout operations, which is scaling linearly with the number of 
+boards in the crate. During the 2009 run, the system was successfully operated 
+with a DAQ rate of 3.1 kHz and a live time of $70 \%$, for a luminosity of 
+about $10^{34}$~cm$^{-2}$.s$^{-1}$ and a beam energy of 6.067 GeV.
 
-In order to reduce the data size, ALTRO is operated in zero-suppression mode: 
-only samples above a programmable threshold are stored in the ALTRO on-board 
-memory and then written to tape. A glitch-filter permits to reject spurious 
-pulses due to noise, by requiring the presence of a minimum number of samples 
-over threshold $N_{MINSEQ}$ to validate a sample. To properly reconstruct 
-the signal shape, $N_{PRE}$ samples before threshold-crossing and $N_{POST}$ 
-samples after the signal returns below threshold are saved. In the present 
-configuration, $N_{MINSEQ}=N_{PRE}=N_{POST}=3$, while threshold is set just 
-above the noise level.
-
-In order to read all the detector readout pads, four FEC crates are used, 
-each equipped with 6 boards, plus a RCU. A schematic of the readout system, 
-for a single crate, is reported in Fig.~\ref{fig:ReadoutScheme}. This 
-configuration permits to reduce the dead time associated to FEC readout 
-operations and to scale linearly with the number of boards in the crate. During the 
-2009 run, the system was successfully operated with a DAQ rate of 3.1 kHz, with 
-a live time of $70 \%$.
+Finally, during data reconstruction, the acquired samples were processed to obtain, 
+for each readout pad, the accumulated charge (ADC) and the pulse time (T). Since 
+pulse time was obtained as the time-stamp of the first sample above threshold, 
+referred to to the trigger time, the resolution is equivalent to the ALTRO 
+sampling time, 100 ns.
 
@@
 The timing information collected for each signal above threshold
-is used to infer the origin of the ionization electrons and 
-then the trajectory of the detected particle. Going from a collection of 
-times to a momentum measurement based on the curvature of a track 
-requires a good knowledge of the drift speed 
-and drift paths followed by the electrons released in the gas. The recorded ADCs give 
+was used to infer the origin of the ionization electrons and 
+then the trajectory of the detected particle. The recorded ADCs were used to reconstruct 
 the deposited energy per unit of length ($\small{\frac{dE}{dX}}$) which, 
-together with the momentum calculated from the trajectory, enable the particle 
+together with the momentum calculated from the trajectory, enabled the particle 
 identification.
@@
 calibration was improved through several iterations of the
-process described below, with each time an increasing number of events 
-properly reconstructed in the RTPC. The figures presented in this section
+process described below, with each time an increasing number of tracks 
+reconstructed in the RTPC. The figures presented in this section
 are the ones obtained while performing the last iteration of this
@@
 electrons released close to the cathode take the most time to reach the readout 
-pads, the cylindrical symmetry insures that the maximum distance is the same for all 
+pads, the cylindrical symmetry insures that this maximum drift distance is the same for all 
 tracks. We illustrate this in Fig.~\ref{fig:RTPC_signals}, where we depict a 
-typical $^{4}$He track. By measuring the maximum time ($T_{Max}$), we can infer the drift 
+typical $^{4}$He track. By measuring the maximum time ($T_{Max}$), we can therefore infer the drift 
 speed of the electrons in the RTPC.\\
@@
 
-To measure the drift speed, we use the time profile of all hits in the 
-chamber shown in Fig.~\ref{fig:TDC_profile}. We can clearly observe the 
+To measure the maximum drift time, we used the time profile of hits from identified tracks 
+shown in Fig.~\ref{fig:TDC_profile}. We can clearly observe the 
 dropping edge expected from geometrical considerations. We define a value $T_{Max/2}$ at 
@@
    \includegraphics[scale=0.42]{fig_2017/hits_time_profile.pdf}
-   \caption[]{Time distribution of the collected hits in one experimental run. Trigger
+   \caption[]{Time distribution of the hits associated with a track in one experimental run. Trigger
               time is defined as T=15, the time unit is the ALTRO sampling time of 100~ns.} 
@@
 61600. While our gas system was kept slightly over 
-atmospheric pressure to avoid contamination from air or other external gases, it 
-is likely that this leak was the source of modification of the gas mixture.}.  
+atmospheric pressure to limit contamination from air or other external gases, it 
+is likely that this leak was the source of modification of the drift speed.}.  
 Figure~\ref{fig:Drift_run_number_1} shows the $T_{Max/2}$ values for 
@@
 the drift speed before and after run 61600, while variations within these periods 
-are ~2\%. These variations of the drift speed were accounted in the track reconstruction
+are ~2\%.
 
@@
 \centering
-\includegraphics[width=16.5cm]{fig_2017/Drift_run_number.pdf}
+\includegraphics[width=15.5cm]{fig_2017/Drift_run_number.pdf}
 \caption{$T_{max/2}$ versus the experimental run numbers.} 
@@
 The drift path is the trajectory followed by the electrons released through 
-ionization in the gas. We calculate them with
+ionization in the gas. We calculated them with
 MAGBOLTZ~\cite{MAGBOLTZ}, but it requires knowledge of the detector's 
 geometry, gas mixture composition, and of course the electric and magnetic 
-fields over the whole volume of the detector. We used such calculation as a 
+fields over the whole volume of the detector. We this calculation as a 
 first calibration, but, 
@@
 Based on the kinematics of the electrons in the calibration data, 
-we generate the helium nucleus in our RTPC GEANT4 simulation~\cite{GEANT4}. Then 
-we compare the calculated GEANT4 trajectory of the Helium nuclei to 
-the hits measured in the chamber. 
-Because of the magnetic field, the drift paths are not linear in the RTPC. So 
-to perform the extraction, we make a first approximation with a linear 
-dependence between the radius of emission and the time of detection, and then 
-refine our result. As it happens, the curvature is minimal and this process 
-converges already on the second iteration.
+we generated the helium nucleus in our RTPC GEANT4 simulation~\cite{GEANT4}. Then,
+we compared the calculated GEANT4 trajectory of the Helium nuclei to 
+the hits measured in the chamber. To perform this drift path extraction, 
+we made a first approximation assuming a linear dependence between the radius 
+of emission of the charge and its time of detection, and then refined our 
+result. Indeed, because of the magnetic field, the drift paths are not linear 
+in the RTPC, but the curvature was minimal and this process converged already 
+on the second iteration.
 
 At the end of the extraction procedure, the azimuthal difference between the detection pad and 
-the ionization point ($\Delta\phi$) is extracted as a function of time. 
+the ionization point ($\Delta\phi$) was extracted as a function of time. 
 In Fig.~\ref{fig:DELTA_PHI_TDC}, we show the resulting data points for one 
@@
 \includegraphics[scale=0.42]{fig_2017/FitResult_p2_11.pdf}
-\caption{$\Delta \phi$ versus T distribution in the second pass for tracks
-near 35 mm longitudinal position along the RTPC. The black line represents 
-the final drift paths in this slice.}
+\caption{$\Delta \phi$ versus T distribution for tracks
+from one bin in longitudinal position along the RTPC. The black line represents 
+the final drift paths in this bin.}
 \label{fig:DELTA_PHI_TDC}
@@
 
-To calibrate the gains, we compare the experimental ADCs to the energy deposited 
+To calibrate the gains, we compared the experimental ADCs to the energy deposited 
 for each pad individually in GEANT4 by similar simulated tracks (using the 
@@
 compared simulation to experiment on an event by event basis as shown in 
-Fig.~\ref{fig:EVENT_adc_tdc}. The gain for each pad is calculated 
+Fig.~\ref{fig:EVENT_adc_tdc}. The gain for each pad was calculated 
 as the ratio of the measured ADCs to the simulated deposited energy.  
-Then, these gains are refined using correction factors obtained from a 
+Then, these gains were refined using correction factors obtained from a 
 sample of good tracks. For each track, we calculate the corrected 
-energy deposit on a pad and compare it to the average
+energy deposit on a pad and compared it to the average
 deposit recorded by the other pads. This last step was implemented to 
@@
 \includegraphics[scale=0.73]{fig_2017/f_dedx_p_exp_2nd.pdf}
-\caption{$\small{\frac{dE}{dX}}$ vs. $p/q$ distribution for the left half of 
-   the RTPC (left) and for the right half (right) after gain calibration.  
-   The lines are theoretical expectations from Bethe-Bloch formula for $^4$He 
-   (red), $^3$He (black), $^3$H (blue), $^2$H (pink) and protons (grey).}
+\caption{$\small{\frac{dE}{dX}}$ vs. $p/q$ distributions for the left (on the 
+   left) and for the right (on the right) half of the RTPC after gain 
+   calibration. The lines are theoretical expectations from the Bethe-Bloch 
+   formula for $^4$He 
+   (red), $^3$He (black), $^3$H (blue), $^2$H (pink) and protons (gray).}
 \label{fig:dedx_p_exp_2nd}
@@
 \subsection{Track Fitting}\label{sec_rec}
-We start with reconstructing the spacial origin of the hits using the extracted drift speed and drift path 
+
+The tracking starts with reconstructing the spacial origin of the hits using the extracted drift speed and drift path 
 parameters. For each registered hit, we calculate a position of emission from 
-the recorded time and the position of the recording pad. The third step 
+the signal time and the pad position. The third step 
 is to create chains of hits. The maximum distance between two close adjacent 
 hits has to be less than 10.5 mm to chain them, which roughly corresponds to 
-neighbors and next to neighbors. Then, we fit the chains with a helix if they have a minimum of 
-10 hits. We then eliminate from the chain the hits that are 5 mm or farther from the fit
+neighbors and next to neighbors. We fit the chains with a helix if they have a minimum of 
+10 hits. We then eliminate from the chain the hits that are 5 mm or farther from the fit,
 as they are not likely part of the same track.
@@
 \subsection{Resolution}
+
 Elastic scattering was used to estimate the tracking resolution of the RTPC 
@@
 resolutions, after removing contributions from the electron, are shown in Table
-~\ref{tab:reso}, and are very similar for the two halves of the RTPC.  Note, the
+~\ref{tab:reso}, and are very similar for the two halves of the RTPC.  Note that the
 $\theta$- and $z$-resolutions are highly correlated.
@@
 \subsection{Efficiency}
+
 We measured the efficiency of the RTPC

### 2017-07-07 eg6-letters/NIM/EG6_RTPC_NIM.tex
Add Stepan's comment

@@
 CLAS detector and the IC from the large flux of low energy M{\o}ller 
-electrons, a 5~T solenoid was placed around the target to shield the detectors. 
+electrons, a 5~T solenoid magnet was placed around the target to shield the detectors. 
 To detect recoiling $\alpha$ particles from the coherent DVCS on helium, a new 
@@
 particles are stopped very rapidly, so the RTPC was designed to be as close 
-as possible to the target and fit inside the 230~mm diameter bore of the 
-5 Tesla solenoid magnet.
+as possible to the target and fit inside the 230~mm diameter shell and cryostat 
+wall of the solenoid magnet bore.
 
@@
 Fig.~\ref{fig:RTPC_1_4}. The RTPC is segmented into two halves with 
-independent GEM amplification systems\footnote{The foils were produced by 
-Tech-Etch, Inc.} that cover about 80\% of the azimuthal 
+independent GEM amplification systems that cover about 80\% of the azimuthal 
 angle.
@@
    \item The 6 atm helium-4 target extends along the beam axis; it 
-      is a 284~mm long, 6~mm diameter straw with a 27-$\mu$m Kapton wall.
+      is a 284~mm long, 6~mm diameter Kapton straw with a 27-$\mu$m wall.
    \item The first gas gap covers the radial range from 3 mm to 20 mm. It is 
@@
 this RTPC are made from a Kapton insulator layer, 300~$\mu$m 
-thick, sandwiched between two 5~$\mu$m copper layers. The mesh of each GEM 
+thick, sandwiched between two 5~$\mu$m copper layers\footnote{The GEM foils were produced by 
+Tech-Etch, Inc.}. The mesh of each GEM 
 layer is chemically etched with 50~$\mu$m diameter holes with double-conical 
@@
 RTPC had 40 rows and 40 columns of pads. The shaded region in Fig.~\ref{fig:PADs} 
-shows how pads were grouped to 16 channels pre-amplifiers. The pre-amplifier boards, 
+shows how pads were grouped to 16 channels pre-amplifier boards. The pre-amplifier boards, 
 already employed in the BoNuS RTPC~\cite{BONUS-NIM}, serve the dual purpose of 
@@
 pulse time was obtained as the time-stamp of the first sample above threshold, 
-referred to to the trigger time, the resolution is equivalent to the ALTRO 
+referred to the trigger time, the resolution is equivalent to the ALTRO 
 sampling time, 100 ns.
@@
 geometry, gas mixture composition, and of course the electric and magnetic 
-fields over the whole volume of the detector. We this calculation as a 
+fields over the whole volume of the detector. We used this calculation as a 
 first calibration, but, 
@@
 over time. Moreover, the 4 $\mu$m foil used as a cathode is easily deformed, such
-that we expect the geometry accuracy to be of few millimeters, directly impacting 
+that we expect the geometrical accuracy to be of few millimeters, directly impacting 
 our knowledge of the electric field. These problems, already 
@@
 The second noise signature was a coherent noise affecting about 25\% of the 
-amplifiers boards, when simultaneous hits in most of the 16 channels of the
+pre-amplifiers boards, when simultaneous hits in most of the 16 channels of the
 board were recorded. An event-based technique to identify and remove this noise was developed based 

### 2017-07-07 eg6-letters/NIM/EG6_RTPC_NIM.tex
NIM:  add section on eloss, capitalize helium in various places

@@
 electrons, a 5~T solenoid magnet was placed around the target to shield the detectors. 
-To detect recoiling $\alpha$ particles from the coherent DVCS on helium, a new 
+To detect recoiling $\alpha$ particles from the coherent DVCS on Helium, a new 
 radial time projection chamber (RTPC) was developed to track low energy nuclear 
@@
 \begin{itemize}
-   \item The 6 atm helium-4 target extends along the beam axis; it 
-      is a 284~mm long, 6~mm diameter Kapton straw with a 27-$\mu$m wall.
+  \item The 6-atm $^4$He target extends along the beam axis; it 
+      is a 284-mm-long, 6-mm-diameter Kapton straw with a 27-$\mu$m wall.
    \item The first gas gap covers the radial range from 3 mm to 20 mm. It is 
@@
 Based on the kinematics of the electrons in the calibration data, 
-we generated the helium nucleus in our RTPC GEANT4 simulation~\cite{GEANT4}. Then,
+we generated the Helium nucleus in our RTPC GEANT4 simulation~\cite{GEANT4}. Then,
 we compared the calculated GEANT4 trajectory of the Helium nuclei to 
@@
 
+\subsection{Energy Loss Corrections}\label{sec_eloss}
+Energy loss between the target and drift region was significant in the RTPC and necessitated a correction for optimal momentum reconstruction at the primary interaction vertex.
+The dominant loss was in the 27-$\mu$m-thick Kapton target wall, with significant contributions also from the pressurized target gas and the foils before reaching the drift region.
+Corrections were developed based on GEANT4 simulations with the full RTPC geometry and parameterized in terms of recoil curvature in the drift region and polar angle, separetely for all recoil hypotheses ($p$, $d$, $^3$H, $^3$He, $^4$He).
+At our average coherent $^4$He DVCS kinematics, energy losses were about 5 MeV, while for $e-^4$He elastic scattering losses were about 3 MeV, which corresponds to momentum corrections of 25\% and 15\%, respectively.
+
 \section{Performance Studies}\label{sec_perfor}
@@
 We reported on the construction, operation and calibration of a small RTPC 
-designed to measure helium-4 nuclei in high rate environment. The operation
-of the detector was successful and allowed to detect helium nuclei with a 75\%
+designed to measure Helium-4 nuclei in high rate environment. The operation
+of the detector was successful and allowed to detect Helium nuclei with a 75\%
 efficiency and a readout rate

### 2017-07-07 eg6-letters/incoherent/figs-sources/incoh_exc_cuts_final.C
cleaning the non used plots for the coherent paper and add source files for the incoherent channel

@@ -1,0 +1,3585 @@
+void incoh_exc_cuts_final()
+{
+//=========Macro generated from canvas: aall_cuts/
+//=========  (Thu Jul  6 16:33:57 2017) by ROOT version6.09/01
+   TCanvas *aall_cuts = new TCanvas("aall_cuts", "",1,1,900,1176);
+   gStyle->SetOptStat(0);
+   aall_cuts->Range(0,0,1,1);
+   aall_cuts->SetFillColor(0);
+   aall_cuts->SetBorderMode(0);
+   aall_cuts->SetBorderSize(0);
+   aall_cuts->SetTopMargin(0.01);
+   aall_cuts->SetBottomMargin(0.2);
+   aall_cuts->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: aall_cuts_1
+   TPad *aall_cuts_1 = new TPad("aall_cuts_1", "aall_cuts_1",0.01,0.6766667,0.49,0.99);
+   aall_cuts_1->Draw();
+   aall_cuts_1->cd();
+   aall_cuts_1->Range(-10,-223.0633,10,892.2532);
+   aall_cuts_1->SetFillColor(0);
+   aall_cuts_1->SetBorderMode(0);
+   aall_cuts_1->SetBorderSize(2);
+   aall_cuts_1->SetTopMargin(0.01);
+   aall_cuts_1->SetBottomMargin(0.2);
+   aall_cuts_1->SetFrameBorderMode(0);
+   aall_cuts_1->SetFrameBorderMode(0);
+   
+   TH1D *h2_delta_phi_InCoh__249 = new TH1D("h2_delta_phi_InCoh__249"," ",300,-8,8);
+   h2_delta_phi_InCoh__249->SetBinContent(3,3);
+   h2_delta_phi_InCoh__249->SetBinContent(4,1);
+   h2_delta_phi_InCoh__249->SetBinContent(5,1);
+   h2_delta_phi_InCoh__249->SetBinContent(6,1);
+   h2_delta_phi_InCoh__249->SetBinContent(7,1);
+   h2_delta_phi_InCoh__249->SetBinContent(8,1);
+   h2_delta_phi_InCoh__249->SetBinContent(9,2);
+   h2_delta_phi_InCoh__249->SetBinContent(10,2);
+   h2_delta_phi_InCoh__249->SetBinContent(12,2);
+   h2_delta_phi_InCoh__249->SetBinContent(13,3);
+   h2_delta_phi_InCoh__249->SetBinContent(14,3);
[…]

### 2017-07-07 for_eg6_group/Final_t_tprime_work/Incoh.tex
some cleaning

--- 2017-04-28 for_eg6_group/t_tprime_April_2017/Incoh.tex
@@
 \centering
-\includegraphics[height=7.0cm]{fig/h_tprimet_t_InCoh_1.pdf}
+%\includegraphics[height=7.0cm]{fig/h_tprimet_t_InCoh_1.pdf}
 \includegraphics[height=7.0cm]{fig/h_tprimet_t_InCoh_2.pdf}
 \includegraphics[height=7.0cm]{fig/h_tprimet_t_InCoh_3.pdf}
-\caption{On top and middle: $t-t'$ as a function of $t'$ for the E1-DVCS2 free 
-proton DVCS sample BEFORE correcting $t'$. On bottom: $t$ versus $t'$.  The red 
-lines are proposed correction functions for $t'$.}
+\caption{On top: $t-t'$ as a function of $t'$ for the E1-DVCS2 free proton DVCS 
+sample BEFORE correcting $t'$. On bottom: $t$ versus $t'$. The red lines are 
+proposed first and second correction functions for $t'$.}
 \label{fig:corrections_tprime_e1dvcs2}

### 2017-07-07 for_eg6_group/tuning-the-coherent-parameters/old_DVCS_EG6_meeting.tex
some cleaning

\section*{\centering{DVCS analysis update for EG6 meeting}}

\subsection*{\centering{Tuning the $^{4}He$ track parameters}}
- After the first and the second round comments, the $^{4}He$ track parameters 
have been tuned by looking at these parameters after the DVCS exclusivity 
cuts.\\
- In figure \ref{fig:He_pid_cuts}, I list the $^{4}He$ DVCS track parameters 
with the updated cuts.\\
- These cuts were applied to the following two analysis sets, except sdist cut 
on the old analysis set was [-3:3].\\

\begin{figure}[h!]
\includegraphics[height=6.0cm]{new_plots/rtpc_sdist.png}
\includegraphics[height=6.0cm]{new_plots/after_rtpc_edist.png}
\includegraphics[height=6.0cm]{new_plots/after_rtpc_X2.png}
\includegraphics[height=6.0cm]{new_plots/after_rtpc_delta_z.png}
\caption{The distributions of the $^{4}He$ DVCS track parameters after applying 
the exclusivity cuts with the final cuts.}
\label{fig:He_pid_cuts}
\end{figure}

\subsection*{\centering{Exclusive distributions and reconstructed $A_{LU}$}}
After the suggestion from the review committee, I have changed the cut one the 
missing energy to be from [-0.45, 0.5] instead of a 3$\sigma$ cut on the 
distribution and refined all the other exclusive cuts. Figure 
\ref{fig:exc_cuts} presents the old and the new distributions for the exclusive 
variables.\\

- Note in the following plots, I will label the two analysis sets as "old", 3 
sigma cuts on all the variables, and "new", with the new missing energy cut and 
the corresponding updated 3 sigma cuts on the other variables.

\begin{figure}[h!]
\centering
\includegraphics[height=10.0cm]{old_plots/all_coh_exc_cuts.png}
\includegraphics[height=10.0cm]{new_plots/all_coh_exc_cuts.pdf}
\caption{ }
\label{fig:exc_cuts}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[height=7.5cm]{old_plots/f_coh_alu_Q2_phi.pdf}
\includegraphics[height=7.5cm]{new_plots/Coh_ALU_Q2_phi.pdf}
\caption{Coherent $A_{LU}$ as a function of $\phi$ in $Q^{2}$ bins for old 
(top) and new (bottom) selection sets.}
\label{fig:ALU_Q2_phi}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[height=7.5cm]{old_plots/f_coh_alu_xB_phi.pdf}
\includegraphics[height=7.5cm]{new_plots/Coh_ALU_xB_phi.pdf}
\caption{Coherent $A_{LU}$ as a function of $\phi$ in $x_{B}$ bins for old 
(top) and new (bottom) selection sets.}
\label{fig:ALU_xB_phi}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[height=7.5cm]{old_plots/f_coh_alu_t_phi.pdf}
\includegraphics[height=7.5cm]{new_plots/Coh_ALU_t_phi.pdf}
\caption{Coherent $A_{LU}$ as a function of $\phi$ in $-t$ bins for old (top) 
and new (bottom) selection sets.}
\label{fig:ALU_t_phi}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[height=7.0cm]{old_plots/coherent-ALU_90.pdf}
\includegraphics[height=7.0cm]{new_plots/Coh_ALU_phi_90.pdf}
\caption{Coherent $A_{LU}$ at $\phi = 90^{\circ}$ for old (top) and new 
(bottom) selection sets.}
\label{fig:ALU_90}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[height=10.0cm]{old_plots/updated_CFFs.pdf}
\includegraphics[height=10.0cm]{new_plots/CFF_Im_Re.pdf}
\caption{$H_{A}$ CFF from old (top) and new (bottom) selection sets.}
\label{fig:CFFs}
\end{figure}

### 2017-07-11 eg6-letters/NIM/EG6_RTPC_NIM.tex
Reorganize for arxiv submission NIM and coherent

@@
 \begin{figure}[tbp]
-\centering \includegraphics[scale=0.3]{fig/test_clas.png}
+\centering \includegraphics[scale=0.3]{test_clas.png}
 \caption{A three dimensional representation of the baseline CLAS setup. The
@@
 \centering
-\includegraphics[{trim={0 12cm 0 0},clip, scale=0.4}]{fig_2017/RTPC_1_all.pdf}
+\includegraphics[{trim={0 12cm 0 0},clip, scale=0.4}]{RTPC_1_all.pdf}
 \caption{Schematic drawing of the CLAS RTPC in a plane perpendicular to the beam 
@@
 \centering
-\includegraphics[scale=0.70]{fig/GEM_photo.jpg}
+\includegraphics[scale=0.70]{GEM_photo.jpg}
 \caption{Image of a typical GEM foil similar to the one used for our RTPC 
@@
    \centering
-   \includegraphics[scale=0.55]{fig/PADs.png}
+   \includegraphics[scale=0.55]{PADs.png}
    \caption[]{A schematic representation of the readout pads. The 
@@
    \centering
-   \includegraphics[width=.75\textwidth]{fig/ReadoutScheme.png}
+   \includegraphics[width=.75\textwidth]{ReadoutScheme.png}
    \caption[]{Schematic representation of the RTPC readout system, showing
@@
 \centering
-%\includegraphics[scale=0.4][trim={0 5cm 0 0},clip]{fig_2017/RTPC_1_4.pdf}
-\includegraphics[{trim={0 12cm 0 0},clip, scale=0.4}]{fig_2017/RTPC_1_4.pdf}
+\includegraphics[{trim={0 12cm 0 0},clip, scale=0.4}]{RTPC_1_4.pdf}
 \caption[]{A schematic drawing of a $^{4}$He track (in green) traversing the 
@@
    \centering
-   \includegraphics[scale=0.42]{fig_2017/hits_time_profile.pdf}
+   \includegraphics[scale=0.42]{hits_time_profile.pdf}
    \caption[]{Time distribution of the hits associated with a track in one experimental run. Trigger
@@
 \centering
-\includegraphics[scale=0.42]{fig_2017/RunNumber_61452_TDCmax_Zslice.pdf}
+\includegraphics[scale=0.42]{RunNumber_61452_TDCmax_Zslice.pdf}
 \caption{Maximum time of collected hits as a function of the track
@@
 \centering
-\includegraphics[width=15.5cm]{fig_2017/Drift_run_number.pdf}
+\includegraphics[width=15.5cm]{Drift_run_number.pdf}
 \caption{$T_{max/2}$ versus the experimental run numbers.} 
@@
 \centering
-\includegraphics[scale=0.42]{fig_2017/FitResult_p2_11.pdf}
+\includegraphics[scale=0.42]{FitResult_p2_11.pdf}
 \caption{$\Delta \phi$ versus T distribution for tracks
@@
    \centering
-\includegraphics[scale=0.42]{fig_2017/Event_ADC_Graph_8799283.pdf}
+\includegraphics[scale=0.42]{Event_ADC_Graph_8799283.pdf}
 \caption{Simulated (upper) and experimental (lower) ADC and T distributions 
@@
 \centering
-\includegraphics[scale=0.73]{fig_2017/f_dedx_p_exp_2nd.pdf}
+\includegraphics[scale=0.73]{f_dedx_p_exp_2nd.pdf}
 \caption{$\small{\frac{dE}{dX}}$ vs. $p/q$ distributions for the left (on the 
@@
 \begin{figure}[tb!]\centering
-\includegraphics[scale=0.25]{fig/noisy_pad_before_rejection2.png}
-\includegraphics[scale=0.25]{fig/noisy_pad_after_rejection2.png}
+\includegraphics[scale=0.25]{noisy_pad_before_rejection2.png}
+\includegraphics[scale=0.25]{noisy_pad_after_rejection2.png}
 \caption{The ADC vs. T spectrum for an example noisy channel before (top) and 
@@
 \begin{figure}[tb]\centering
-  \includegraphics[width=8cm]{fig/fit_W_distribution_l.png}
+  \includegraphics[width=8cm]{fit_W_distribution_l.png}
   \caption{The $W$ distribution calculated from electron kinematics before (``inclusive'')
@@
 \centering
-\includegraphics[width=8cm]{fig/tpceff.png}
+\includegraphics[width=8cm]{tpceff.png}
 \caption{The RTPC $^4$He detection efficiency as a function of the longitudinal 

### 2017-07-11 eg6-letters/coherent/dvcs_he4_prl.tex
Reorganize for arxiv submission NIM and coherent

@@
 \begin{figure}[tb]
-\includegraphics[width=6.5cm]{figs/DVCS_diagram.pdf}
+\includegraphics[width=6.5cm]{DVCS_diagram.pdf}
 \caption{Representation of the leading-order handbag diagram of the DVCS 
@@
 \hspace{-0.45cm}
-\includegraphics[width=9cm]{figs/F_all_coh_exc_cuts-pub.pdf}
+\includegraphics[width=9cm]{F_all_coh_exc_cuts-pub.pdf}
 \caption{Four of the six coherent DVCS exclusivity cuts. The black 
@@
 \hspace{-0.45cm}
-\includegraphics[width=9cm]{figs/F_Q2_xB_t_Coh.pdf}
+\includegraphics[width=9cm]{F_Q2_xB_t_Coh.pdf}
 \caption{Coherent DVCS event distributions for $Q^2$ after exclusivity cuts. 
@@
    \centering
-\includegraphics[width=8.5cm]{figs/F_Coherent_ALU_phi.pdf}
+\includegraphics[width=8.5cm]{F_Coherent_ALU_phi.pdf}
 \caption{$A_{LU}$ as a function of azimuthal angle $\phi$. Results are presented
@@
 \begin{figure*}[tb]
-\includegraphics[width=16cm]{figs/F_Coherent_ALU_phi_90.pdf}
+\includegraphics[width=16cm]{F_Coherent_ALU_phi_90.pdf}
 \caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $t$-dependencies (right) of
@@
 \begin{figure}[tb]
-\includegraphics[width=8.5cm]{figs/F_Coherent_CFF.pdf}
+\includegraphics[width=8.5cm]{F_Coherent_CFF.pdf}
 \caption{The leading-twist model-independent extraction of the imaginary (top panel) and

### 2017-07-13 eg6-letters/coherent/dvcs_he4_prl.tex
Changes in ref for coherent submission to PRL

@@
   Phys.\ Rev.\ D {\bf 62}, 071503 (2000);
-  Erratum: Phys.\ Rev.\ D {\bf 66}, 119903 (2002).
+  Erratum: Phys.\ Rev.\ D {\bf 66}, 119903(E) (2002).
 
@@
 \bibitem{Freund_Collins}
-A.~Freund and J.C.~Collins, 
-Phys.\ Rev.\ D {\bf 59}, 074009 (1998).
+J.C.~Collins and A.~Freund, 
+Phys.\ Rev.\ D {\bf 59}, 074009 (1999).
 
@@
 \bibitem{simonetta_2}
-S.~Liuti and K.~Taneja, 
+S.~Liuti and S.K.~Taneja, 
 Phys.\ Rev.\ C {\bf 72}, 032201 (2005).

### 2017-08-21 eg6-letters/coherent/dvcs_he4_prl.tex
update the paper with the support statment in the acknowledgments
edit the acknowledgments
edit the Acknowledgments in the coherent paper

@@
 Recherche Scientifique, the French Commissariat \`a l'Energie Atomique, the 
-U.S. Department of Energy, the UK Science and Technology Facilities Council 
-(STFC), the Scottish Universities Physics Alliance (SUPA), the National 
-Research Foundation of Korea, and the Office of Research and Economic 
+U.S.
+Department of Energy under contract number DE-AC02-06CH11357, the UK Science and Technology Facilities Council (STFC), the Scottish Universities Physics Alliance (SUPA), the National Research Foundation of Korea, and the Office of Research and Economic
 Development at Mississippi State University. The author (M.~Hattawy) also 
-acknowledges the support of the Consulat G\'en\'eral de France \`a J\'erusalem. The Southeastern Universities Research Association operates the Thomas 
+acknowledges the support of the Consulat G\'en\'eral de France \`a J\'erusalem.  
+The Southeastern Universities Research Association operates the Thomas 
 Jefferson National Accelerator Facility for the United States Department of 

### 2017-08-29 eg6-letters/coherent/dvcs_he4_prl.tex
Started answer to the PRL referees

@@
 can see a difference between the precision of the extracted imaginary and real 
-parts, which is is due to $\alpha_2$ being much smaller than $\alpha_1$ in
+parts, which is due to $\alpha_2$ being much smaller than $\alpha_1$ in
 Eq.~(\ref{eq:A_LU-coh}). While the precision of this measurement is not at a

### 2017-08-29 eg6-letters/coherent/dvcs_he4_prl.tex
Add answers to coherent review

@@
 probe and has been the focus of efforts at Jefferson Lab, HERA, and CERN 
-\cite{Stepanyan:2001sm,Airapetian,Airapetian:2010nu,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,
+\cite{Stepanyan:2001sm,Airapetian,Airapetian:2010nu,Chekanov:2003ya,Adloff:2001cn,Aktas:2005ty,Chen:2006na,
 MunozCamacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Defurne:2015kxq,
@@
 for the detection of $^4$He nuclei using elastic scattering 
-($e^4$He$\to e^\prime$$^4$He) with a 1.2~GeV electron beam.
+($e^4$He $\to e^\prime$$^4$He$'$) with a 1.2~GeV electron beam.
 
@@
 in Refs.~\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, $A_{LU}$ 
-for a spin-zero hadron can be expressed at leading-twist as
+for a spin-zero hadron can be expressed at leading-order and leading-twist as
 \begin{equation}
@@
 The black-dashed curves are calculations from the same 
-model using different GPDs for the nucleons (VGG model~\cite{Guidal_priv}). The 
+model using different GPDs for the nucleons (VGG model~\cite{Guidal:2004nd}). The 
 blue long-dashed curve on the top-right plot is from
@@
 nucleons, each interacting independently with the probe. The Convolution-Dual 
-model is based on nucleon GPDs from the dual parametrization 
-\cite{Guzey:2006xi}, where the Convolution-VGG uses nucleon GPDs  from the VGG 
-model and is based on the double distributions ansatz \cite{DD_model}. The 
+model is based on nucleon GPDs from the dual parametrization~\cite{Guzey:2006xi}, 
+where the Convolution-VGG uses nucleon GPDs from the VGG model~\cite{Guidal_priv} 
+and is based on the double distributions ansatz \cite{DD_model}. The 
 off-shell model is the same as in Fig.~\ref{fig:alu90} using a more recent
@@
 Phys.\ Rev.\ C {\bf 81}, 035202 (2010).
+
+\bibitem{Adloff:2001cn} 
+  C.~Adloff {\it et al.} [H1 Collaboration],
+  Phys.\ Lett.\ B {\bf 517}, 47 (2001)
 
@@
 \bibitem{Dupre:2017upj} 
-  R.~Dupré {\it et al.},
+  R.~Dupr\'e {\it et al.},
   arXiv:1706.10160 [physics.ins-det].
@@
 
-\bibitem{Guidal_priv}
-Private communications with M.~Guidal based on: 
+\bibitem{Guidal:2004nd}
 M.~Guidal, M.~V.~Polyakov, A.~V.~Radyushkin and M.~Vanderhaeghen, 

### 2017-08-30 eg6-letters/coherent/dvcs_he4_prl.tex
Progress on review answers

@@
 Recherche Scientifique, the French Commissariat \`a l'Energie Atomique, the 
-U.S.
-Department of Energy under contract number DE-AC02-06CH11357, the UK Science and Technology Facilities Council (STFC), the Scottish Universities Physics Alliance (SUPA), the National Research Foundation of Korea, and the Office of Research and Economic
+U.S. Department of Energy under contract number DE-AC02-06CH11357, the UK 
+Science and Technology Facilities Council (STFC), the Scottish Universities 
+Physics Alliance (SUPA), the National Research Foundation of Korea, and the 
+Office of Research and Economic 
 Development at Mississippi State University. The author (M.~Hattawy) also 
@@
   E.~R.~Berger, F.~Cano, M.~Diehl and B.~Pire,
-  %``Generalized parton distributions in the deuteron,''
   Phys.\ Rev.\ Lett.\  {\bf 87}, 142302 (2001)
@@
   F.~Cano and B.~Pire,
-  %``Deep electroproduction of photons and mesons on the deuteron,''
   Eur.\ Phys.\ J.\ A {\bf 19}, 423 (2004)
@@
   V.~Guzey and M.~Siddikov,
-  %``On the A-dependence of nuclear generalized parton distributions,''
   J.\ Phys.\ G {\bf 32}, 251 (2006)
@@
 \bibitem{Guidal:2004nd}
-M.~Guidal, M.~V.~Polyakov, A.~V.~Radyushkin and M.~Vanderhaeghen, 
-Phys.\ Rev.\ D {\bf 72}, 054013 (2005).
+M.~Vanderhaeghen, P.A.M.~Guichon and M.~Guidal, Phys.Rev.Lett.{\bf 80} 5064 (1998), 
+Phys.Rev. D {\bf 60}, 094017 (1999);
+K.~Goeke, M.V.~Polyakov and M.~Vanderhaeghen, Prog.Part. Nucl. Phys. {\bf 47}, 401 (2001);
+M.~Guidal, M.V.~Polyakov, A.V.~Radyushkin and M.~Vanderhaeghen, Phys.\ Rev.\ D {\bf 72}, 054013 (2005).
 

### 2017-09-11 eg6-letters/coherent/dvcs_he4_prl.tex
Answers to PRL review

@@
 functions~\cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}. The results 
-presented in this letter demonstrate the feasability of such an approach and 
+presented in this letter demonstrate the feasibility of such an approach and 
 constitute the first step toward a tomography of nuclei.
@@
 emitted by the incoming or the outgoing lepton. The DVCS and BH processes are 
-indistinguishable experimentally and the amplitude of electroproduction of real
-photons includes a sum of the amplitudes of these two processes. The BH 
-amplitude depends on the target elastic form factors, which are well known in this
-kinematic region, while the DVCS amplitude depends on the GPDs we are trying to
-measure. For our kinematics, the cross section of real photon 
-electroproduction is dominated by the BH contribution, while the DVCS 
-contribution is very small. However, the DVCS contribution is
-enhanced in the observables sensitive to the interference term, {\it e.g.} 
-$A_{LU}$. The three terms entering the cross section calculation,
-the squares of the BH and DVCS amplitudes and their interference term, depend on the
-azimuthal angle $\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes,
-as shown for the nucleon in Ref.~\cite{Belitsky:2001ns} and for the spin-zero targets
-in Refs.~\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, $A_{LU}$ 
-for a spin-zero hadron can be expressed at leading-order and leading-twist as
+indistinguishable experimentally and the amplitude of the electroproduction of 
+a real photon includes a sum of the amplitudes of these two processes. The BH 
+amplitude depends on the target elastic form factors, which are well known in 
+this kinematic region, while the DVCS amplitude depends on the GPDs. In our 
+kinematics, the cross section of the real photon electroproduction is dominated 
+by the BH contribution varying strongly with $\phi$, the azimuthal angle 
+between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes. The DVCS 
+contribution is smaller by about a factor two, but independent of $\phi$ at twist-2~%
+\cite{Belitsky:2001ns}, thus it is possible to separate these contributions 
+with a cross section measurement. However, the DVCS-BH interference term offers 
+an easier experimental access by generating spin asymmetries. We have, in 
+particular, for a spin-zero target the beam spin asymmetry, $A_{LU}$, which 
+can be expressed at leading-order and leading-twist~\cite{Kirchner:2003wt,
+Belitsky:2008bz} as
 \begin{equation}
@@
 extracted from the fit to the azimuthal dependence of $A_{LU}$ are shown in 
-Fig.~\ref{fig:CFF_HA}. The curves on the graphs are model calculations, labelled 
+Fig.~\ref{fig:CFF_HA}. The curves on the graphs are model calculations, labeled 
 {\it convolution} and {\it off-shell}. In the convolution model 

### 2017-09-11 eg6-letters/coherent/dvcs_he4_prl.tex
Update coherent letter

@@
 light enough to be detected by our experimental setting, while it is subject 
-to interesting nuclear effects~\cite{JSeely}. Its spin-zero also leads to an 
+to interesting nuclear effects~\cite{JSeely}. Its zero spin also leads to an 
 important simplification, as a spin-zero hadron is parametrized by only one 
@@
 kinematics, the cross section of the real photon electroproduction is dominated 
-by the BH contribution varying strongly with $\phi$, the azimuthal angle 
+by BH contribution, which varies strongly with $\phi$, the azimuthal angle 
 between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes. The DVCS 
-contribution is smaller by about a factor two, but independent of $\phi$ at twist-2~%
-\cite{Belitsky:2001ns}, thus it is possible to separate these contributions 
+contribution is smaller by about a factor of two, but independent of $\phi$ at twist-2~%
+\cite{Belitsky:2001ns}, and thus it is possible to separate these contributions 
 with a cross section measurement. However, the DVCS-BH interference term offers 
@@
 model is based on nucleon GPDs from the dual parametrization~\cite{Guzey:2006xi}, 
-where the Convolution-VGG uses nucleon GPDs from the VGG model~\cite{Guidal_priv} 
+where the Convolution-VGG uses nucleon GPDs from the VGG model~\cite{Guidal:2004nd} 
 and is based on the double distributions ansatz \cite{DD_model}. The 

### 2017-09-19 eg6-letters/long-paper/prc-dvcshelium.tex
some fixing
added the abstract

@@
-\documentclass[aps,prc,preprint,superscriptaddress]{revtex4-1}
+\documentclass[aps,prc,preprint,superscriptaddress]{revtex4}
 
@@
 %Title of paper
-\title{Measurement of deeply virtual Compton scattering off helium-4}
+\title{Measurement of deeply virtual Compton scattering off Helium-4}
 
-% repeat the \author .. \affiliation  etc. as needed
-% \email, \thanks, \homepage, \altaffiliation all apply to the current
-% author. Explanatory text should go in the []'s, actual e-mail
-% address or url should go in the {}'s for \email and \homepage.
-% Please use the appropriate macro foreach each type of information
-
-% \affiliation command applies to all authors since the last
-% \affiliation command. The \affiliation command should follow the
-% other information
-% \affiliation can be followed by \email, \homepage, \thanks as well.
-\author{CLAS et al.}
-%\email[]{Your e-mail address}
-%\homepage[]{Your web page}
-%\thanks{}
-%\altaffiliation{}
-\affiliation{JLab et al.}
-
-%Collaboration name if desired (requires use of superscriptaddress
-%option in \documentclass). \noaffiliation is required (may also be
-%used with the \author command).
-%\collaboration can be followed by \email, \homepage, \thanks as well.
-\collaboration{CLAS Collaboration}
-\noaffiliation
+\input author_list.tex
 
@@
 \begin{abstract}
-% insert abstract here
+Measurements of the beam-spin asymmetry in the deeply virtual Compton 
+scattering off $^4$He using the CEBAF Large Acceptance Spectrometer (CLAS) are 
+reported. A 6 GeV longitudinally polarized electron beam was incident on a 
+pressurized $^4$He gaseous target to study the partonic structure of the 
+nucleus and the bound nucleons. To ensure the exclusivity of the reactions, 
+CLAS was upgraded with a radial time projection chamber to detect the 
+low-energy recoiling $^4$He nuclei and an inner calorimeter to extend the 
+photon detection acceptance to very forward angles. Our results confirm the 
+theoretically predicted enhancement of the coherent 
+($e^4$He~$\to~e'$$^4$He$'\gamma'$) beam-spin asymmetries compared to those 
+observed on the free proton, while the incoherent 
+($e^4$He~$\to~e'$p$'\gamma'$X$'$) asymmetries exhibit a 30$\%$ suppression.  
+From the coherent data, we were able to extract, in a model-independent way, 
+the real and imaginary parts of the only $^4$He Compton form factor, $\cal 
+H_A$, leading the way toward 3D imaging of the partonic structure of nuclei.
+
 \end{abstract}
@@
 \end{document}
-%
-% ****** End of file apstemplate.tex ******

### 2017-10-03 eg6-letters/coherent/dvcs_he4_prl.tex
Implemented remarks from round 2 to coherent letter

@@
 \end{equation}
-Explicit expressions of the kinematic factors $\alpha_i$ are derived 
-from expressions in
-Ref.~\cite{Belitsky:2008bz} and are functions of Fourier harmonics in the 
-azimuthal angle $\phi$, the nuclear form factor $F_A(t)$ and kinematical
-factors. Using the different $\sin(\phi)$ and $\cos(\phi)$ contributions, 
+Where $F_A(t)$ is the nuclear form factor and explicit expressions of the 
+kinematic factors $\alpha_i$ are derived from expressions in Ref.~\cite{Belitsky:2008bz}
+These factors can be simplified as:
+\begin{equation}
+\begin{split}
+&\alpha_0 (\phi)  = \frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi) \\
+&\alpha_1 (\phi)  =  c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi) \\
+&\alpha_2 (\phi)  =  \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
+C_{++}(1) cos(\phi) \right) \\
+&\alpha_3 (\phi) = \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
+{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
+\epsilon^2}
+\end{split}
+\end{equation}
+Where $S_{++}(1)$, $C_{++}(0)$ and $C_{++}(1)$ are the Fourier harmonics in the 
+leptonic tensor, and with ${\mathcal P}_1(\phi)$ and ${\mathcal P}_2(\phi)$ the BH
+propagators, which include only $\cos(\phi)$ dependencies. Their explicit 
+expressions can be found in Appendix~A of \cite{Armstrong:2017wfw}.
+
+ and are functions of Fourier harmonics in the 
+azimuthal angle $\phi$,. Using the different $\sin(\phi)$ and $\cos(\phi)$ contributions, 
 both the imaginary and real parts of $\mathcal{H}_{A}$ can be extracted unambiguously
@@
    the HERMES $-A_{LU}$ (a positron beam was used) inclusive measurements 
-   \cite{Airapetian}, and the curves are the theoretical calculations 
+   \cite{Airapetian:2010nu}, and the curve is the theoretical calculation 
    from \cite{simonetta_2}. The grey bands represent the systematic errors.}
@@
 framework and paves the way for future measurements at JLab using 12 GeV CEBAF 
-and upgraded equipment.
+and upgraded equipment~\cite{Armstrong:2017wfw}.
 
@@
 
+\bibitem{Armstrong:2017wfw} 
+  W.~Armstrong {\it et al.},
+  arXiv:1708.00888 [nucl-ex].
+
 \bibitem{simonetta_2}

### 2017-10-03 eg6-letters/coherent/dvcs_he4_prl.tex
update coherent letter

@@
 \end{equation}
-Where $F_A(t)$ is the nuclear form factor and explicit expressions of the 
-kinematic factors $\alpha_i$ are derived from expressions in Ref.~\cite{Belitsky:2008bz}
-These factors can be simplified as:
+Explicit expressions of the kinematic factors $\alpha_i$ are derived from 
+expressions in Ref.~\cite{Belitsky:2008bz}:
 \begin{equation}
@@
 Where $S_{++}(1)$, $C_{++}(0)$ and $C_{++}(1)$ are the Fourier harmonics in the 
-leptonic tensor, and with ${\mathcal P}_1(\phi)$ and ${\mathcal P}_2(\phi)$ the BH
+leptonic tensor, while ${\mathcal P}_1(\phi)$ and ${\mathcal P}_2(\phi)$ are the BH
 propagators, which include only $\cos(\phi)$ dependencies. Their explicit 

### 2017-10-03 eg6-letters/coherent/dvcs_he4_prl.tex
More corrections to coherent letter
Clean up of the wording

@@
 leptonic tensor, while ${\mathcal P}_1(\phi)$ and ${\mathcal P}_2(\phi)$ are the BH
-propagators, which include only $\cos(\phi)$ dependencies. Their explicit 
-expressions can be found in Appendix~A of \cite{Armstrong:2017wfw}.
-
- and are functions of Fourier harmonics in the 
-azimuthal angle $\phi$,. Using the different $\sin(\phi)$ and $\cos(\phi)$ contributions, 
-both the imaginary and real parts of $\mathcal{H}_{A}$ can be extracted unambiguously
-by fitting the $A_{LU}(\phi)$ distribution.
+propagators and include only $\cos(\phi)$ dependencies\footnote{The explicit 
+expression of all these terms can be found in Appendix~A of \cite{Armstrong:2017wfw}.}.
+We observe that using the different $\sin(\phi)$, $\cos(\phi)$ and $\cos(2\phi)$ contributions, 
+one can extract unambiguously both the imaginary and real parts of $\mathcal{H}_{A}$
+with a fit of the $A_{LU}(\phi)$ distribution.
 

### 2017-10-03 eg6-letters/coherent/dvcs_he4_prl.tex
some cleaning after equation 6

@@
 \end{equation}
-Where $S_{++}(1)$, $C_{++}(0)$ and $C_{++}(1)$ are the Fourier harmonics in the 
-leptonic tensor, while ${\mathcal P}_1(\phi)$ and ${\mathcal P}_2(\phi)$ are the BH
-propagators and include only $\cos(\phi)$ dependencies\footnote{The explicit 
+Where $S_{++}(1)$ and $C_{++}(0,1)$ are the Fourier harmonics in the 
+leptonic tensor of the interference amplitude, while $c_{0,1,2}^{BH}$ 
+are the Fourier harmonics of the BH amplitude\footnote{The explicit 
 expression of all these terms can be found in Appendix~A of \cite{Armstrong:2017wfw}.}.
+${\mathcal P}_1(\phi)$ and ${\mathcal P}_2(\phi)$ are the BH
+propagators and only include $\cos(\phi)$ dependencies.
 We observe that using the different $\sin(\phi)$, $\cos(\phi)$ and $\cos(2\phi)$ contributions, 

### 2017-10-03 eg6-letters/coherent/dvcs_he4_prl.tex
more cleaning to the parapgraph after equation 6

@@
 \end{equation}
-Where $S_{++}(1)$ and $C_{++}(0,1)$ are the Fourier harmonics in the 
-leptonic tensor of the interference amplitude, while $c_{0,1,2}^{BH}$ 
+Where $S_{++}(1)$ and $C_{++}(0,1)$ are the Fourier harmonics of the 
+interference amplitude in the leptonic tensor, while $c_{0,1,2}^{BH}$ 
 are the Fourier harmonics of the BH amplitude\footnote{The explicit 

### 2017-10-03 eg6-letters/coherent/dvcs_he4_prl.tex
minor correction after Nathan's suggestion

@@
 {\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
-\epsilon^2}
+\epsilon^2},
 \end{split}
 \end{equation}
-Where $S_{++}(1)$ and $C_{++}(0,1)$ are the Fourier harmonics of the 
+where $S_{++}(1)$ and $C_{++}(0,1)$ are the Fourier harmonics of the 
 interference amplitude in the leptonic tensor, while $c_{0,1,2}^{BH}$ 

### 2017-10-03 eg6-letters/coherent/dvcs_he4_prl.tex

@@
 where $S_{++}(1)$ and $C_{++}(0,1)$ are the Fourier harmonics of the 
-interference amplitude in the leptonic tensor, while $c_{0,1,2}^{BH}$ 
-are the Fourier harmonics of the BH amplitude\footnote{The explicit 
+interference amplitude in the leptonic tensor, $c_{0,1,2}^{BH}$ 
+the Fourier harmonics of the BH amplitude, and
+finally ${\mathcal P}_{1,2}(\phi)$ the BH
+propagators, which include $\cos(\phi)$ dependencies\footnote{The explicit 
 expression of all these terms can be found in Appendix~A of \cite{Armstrong:2017wfw}.}.
-${\mathcal P}_1(\phi)$ and ${\mathcal P}_2(\phi)$ are the BH
-propagators and only include $\cos(\phi)$ dependencies.
 We observe that using the different $\sin(\phi)$, $\cos(\phi)$ and $\cos(2\phi)$ contributions, 

### 2017-10-10 analysis-note-vf/results.tex
update the analysis note with the latest incoherent results

@@
 \begin{eqnarray}
-   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S{++}(1) \sin(\phi)\\
+   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
     \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
@@
 
-Where $S{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
+Where $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
 leptonic tensor. Their explicit expressions can be found in Appendix 
@@
 \begin{figure}[tpb]
-\includegraphics[scale=0.9]{fig_Dec2016/ALU_phi_p_Q2.pdf}
-\includegraphics[scale=0.9]{fig_Dec2016/ALU_phi_p_x.pdf}
-\includegraphics[scale=0.9]{fig_Dec2016/ALU_phi_p_t.pdf}
+\includegraphics[scale=0.9]{fig_Dec2016/incoherent_ALU_phi.pdf}
 \caption{The incoherent $A_{LU}$ as a function of the angle $\phi$ in $Q^2$, 

### 2017-10-16 eg6-letters/NIM/review-1/review-1.tex
added the comments from the reviewers for the RTPC nim paper

%\documentclass[a4paper,11pt,twoside]{ThesisStyle}
\documentclass[a4paper,11pt,twoside]{article}

\date{\today}
\include{formatAndDefs}
\begin{document}

\section*{Reviewers' comments (11 Oct 2017)}

Reviewer #1: Dear Author, please find here a list of comments from my side.

Summary: the article describes the layout, operation and performances of a Radial Time Projection Chamber with the electron amplification stage provided by three layers of GEM. The main novelty is the application of the electron multiplier for the amplification stage in a TPC on a semi-cylindrical shaped plane. The detector, originally built for the BoNuS experiment, is in fact formed by two semi-cylindrically shaped halves connected together, with the axis coincident with the beam line. 
The detector was implemented to measure DVCS of electrons on different light nuclei and the performances were evaluated on electron - 4He elastic scattering runs.
Chapter 1 describes the CLAS @ JLab detector, inside which the RTPC was installed and took data. 
Chapter 2 focuses on the RTPC mechanical and electrical layout. From inner to outer, there are: the 4He gas target, a 4He gas gap, the actual time projection chamber. The time projection chamber is a 200 long detector composed by different gas gaps limited by concentric electrodes around the axis: cathode (R=30mm), G1(R=60mm), G2(R=63mm), G3(R=66mm), readout plane (R=69mm). Everything fits inside a 5T solenoidal magnetic field. It provides both time and charge measurements.
Chapter 3 is a short description of the electronics and readout, mainly inherited from ALICE and BoNuS. The improvement stands in the higher readout rate capability.
Chapter 4 talks about calibration of drift velocity, drift paths and energy loss measurements by the usage of simulations with MAGBOLTZ and tuning the results on elastic scattering data.
Chapter 5 concentrates on track finding/fitting procedure and noise evaluation and subtraction.
Chapter 6 reports on resolution and efficiency from the elastic scattering reconstruction of 2 GeV electrons on 4He and Chapter 7 concludes the paper.

The article main points of interest are the followings:
a)  the usage of GEMs as avalanche creators inside the time projection chamber. As far as I know other TPC with the wires substituted by GEM layers have been (or are being) realized, like ALICE TPC upgrade or the FOPI one (proposed for PANDA), but in those cases the GEM are planar and on the end plane of the TPC, not around the beamline.
b) The shaping of the GEM foils around the target. However, since now a fully cylindrical GEM foil has been realized (for the KLOE-2 detector and for the next BESIII inner tracker) I would not call these "cylindrical" GEMs, but "semi-cylindrical" GEMs to point out the difference (which reflects in the construction procedure).
Maybe these other experiments using GEMs should be mentioned due to the similarities, thought they are successive in time to this RTPC construction.
Concerning the work description, it is mainly exhaustive, but in some points there are open questions that I would like to submit to the authors in the following.
--------------------------------------------------

Chapter by chapter comments:

* Chapter 2:
1)	As already said I would not speak of cylindrical GEMs but semi-cylindrical. Moreover, please add the reference to Sauli's paper [11] when speaking the first time about GEM in the text.
2)	In my opinion, this chapter should highlight better which are the improvements w.r.t. BoNuS detector to underline the originality of this work. For example, better acceptance? Higher gain? Higher electric stability? Lower material budget? Please quote some old and new values, maybe in a table, to make them evident.
3)	Relevant length and thicknesses of the various elements are reported in the text and in the figure, can you please add also the z position of the target w.r.t the detector? To give the complete information, I would also add the value of the induction gap electric field, which is the only missing field value and the value of the reached amplification gain with the three GEM.
4)	When speaking of low spark rate the reference [12] is quoted, which is the PDG. Maybe it is better to quote more specific studies like the ones by Bachmann et al.
5)	line 119: is the Kapton of the GEM foil really 300 mum thick? It is usually very thin, like 50 mum, in order to have low material budget and very high fields.

* Chapter 3:
6)	The description of the electronics looks to me a little not well organized, like a collection of info from previous descriptions from ALICE and BoNuS. It is a series of details, some of which not really relevant for the good understanding of the work described in the paper. So, I would put only some general info (the number of channels/pad, the number of time samples and their width for each channel and the number of  ADC samples and their width for each channel) with the reference where to find more material and just write explicitly the novelties, such as the fact that the acquisition rate was increased (footnote 2).
7)	Also, I understand that fig. 5 comes from reference [14], updated with the values of the RTPC instead of the ALICE-TPC, but it seems to me that there are some parts of the picture which have to be fixed. I list them here:
- why does it say 768 pads?
- why 7.6 microsec?
- the anode wire e grid make no sense here
- why L1 and L2 (trigger levels?)

* Chapter 4:
	/paragraph 4.1
8)	I would really prefer to call it drift "velocity" instead of drift "speed"
9)	I don't really understand the procedure to find the drift velocity described here and fig. 7. What is Nb_max e Nb_max/2? Why does T_max/2 correspond to Nb_max/2 and why is it used as T_max? If I make a quick calculation and use T_max ~ 65 * 100ns and a drift length of ~ 3cm /cos(23°) ~ 7.5 cm I get a v_drift ~ 1.15 cm/microsec << 5 cm/microsec which is the average value of drift velocity in drift chambers.
The procedure according to me would be:
- for each hit associated to a track, whose time information is available, take the drift time t_drift_i;
- plot the distribution of these t_drift_i;
- find the T_min = minimum t_drift_i and T_max = maximum t_drift_i
- compute delta_t = T_max - T_min and extract the drift velocity by dividing the track length / delta_t. Figure 8 would have the delta_t instead of the T_max vs z.
Please provide more details on the applied procedure, since I have the open questions I wrote before and I could not understand it properly. Moreover, please quote the value of the found drift velocity. Is it in accordance with the simulations?
10)	Figure 6: why are T_min and T_max not at the drift gap extremities?

        /paragraph 4.2
11)	line 306: "in one bin" should be explained better. I understood it is the subdivision in bins of the z coordinate, but it was not so obvious at the first reading
12)	Has the stability of the drift path been counterchecked with simulations varying the field according to the cathode radius variation? How much is the field variation if the radius have some mm of uncertainty?

        /paragraph 4.3
13)	The gain calibration is very quick. I would like more details, e.g. "setting the simulation properly" intends only GEANT4 or also MAGBOLTZ or GARFIELD? Were they used to simulate the drift and avalanche formation of the electrons? And the diffusion from the gas? Was a specific code written to simulate the electronics?
14)	line 330: "correction factors" are mentioned. On what? Why haven't only good tracks been used for calibration? Lack of statistics?
15)	When it says that the pad charge is "compared" to the neighboring ones, what happens next? Is it the noise reduction step described later? If so, please write it. 
16)	Figure 11: I don't understand it. How many tracks does the histo contain? If the single pad has 128 channels, how many channels does the single bin contain? Moreover, is the dE calculated on pad by pad basis? In that case, why don't you put just one point in the histo for each pad? What is the mean number of channels or pads fired by one track? Sorry for the list of questions, but I could not understand the figure.
17)	Figure 12 - please, put if after figure 11. Moreover, please change dEdx to dE/dx on y axis. Why are the left and right pictures so different? Talking about the deuteron band which is present only in the left figure and the smear on the top part of the right picture.

* Chapter 5
	/paragraph 5.1	
18)	Please detail a little bit more the procedure to remove the oscillatory noise. It says "event by event and channel by channel": if the ADC threshold is passed then a noise level is subtracted? If so, how is it calculated?
        /paragraph 5.2
19)	How was "10.5 mm" cut chosen? is it in xy plane or in 3-dimensions?
20)	How was the "10 hits" cut chosen? What is the mean number of primary ionization in this gas mixture?
21)	< dE/dx > is computed here as corrected Etot divided total track length. Usually the mean dE/dx is computed with the truncated mean of the specific energy losses of each hit. Isn't it possible to compute it like this here? dx for each hit can be (maybe) computed from the difference in the hit times. Sum dE_i / Sum dx_i is not equal to Sum (dE_i/dx_i).

* Chapter 6
	/paragraph 6.2
22)	I understand that efficiency is a ratio between two integrals, each integral being the area of the Gaussian which fits the recoil mass distribution in the inclusive and exclusive case. If so, would it be possible to please draw both fits on the figure 14 and provide the integrals to compute the mean efficiency? If I misunderstood, please comment.

* Chapter 7 
23)	Is it "high rate environment" or "high readout rate"? They are connected, but what is the rate the RTPC underwent during data taking?
24)	I understand the resolution and efficiency have been evaluated with the 2 GeV electrons. Is it foreseen to analyze also the 6 GeV electron runs, which were the actual data taking? Is there an evaluation of the foreseen RTPC performances in that case?

----------------------------------------------
Some general remarks on the layout:
25)	I would add to the keywords also GEM or gas electron multipliers or multi pattern gas detectors (it depends on what is available).
26)	Please put the units on the axis of every figure, together with the physical quantity. In some figures it is only written in the caption or in the text.
27)	Sometimes to explain the dimension of something something like "250 mm long" (line 67) while some other times "84-mm-long" (on line 83) is written. Please make this uniform in the whole text (I just quoted two examples, but there are more in the text).
28)	In footnote 2, BoNuS is written BONUS and somewhere else in the text also BoNus. Please uniform this to the correct one, which I think is BoNuS.
29)	Please make the bibliography entries uniform: they are not all written with the same layout.

List of in text corrections:
30)	line 17: "GeV" --> "GeV/c"
31)	line 26: "nuclei" --> "nucleus"
32)	line 40: "to track" --> "to bend tracks"(since the magnetic field just bends the track and then the detector tracks them)
33)	line 91: "second gap" --> "second gas gap"
34)	line 110: "from the GEMs" -->  something like "after they have been multiplied by the GEMs" or "induced in the last gas gap" since the GEM is the amplification system.
35)	line 131: "axial magnetic field" --> "solenoidal magnetic field"
36)	line 133: "challenge" --> "challenges"
37)	line 133-134: "radial TPC" it would be better to uniform the way to write it in the whole text (like, "RTPC")
38)	line 167: "stage" --> "stages"
39)	line 176: "ReadOut" should always be written in the same way (see line 168) unless this was specifically written in a different way in the cited articles
40)	line 208: cm^{-1} . s^{-1} --> cm^{-1} \cdot s^{-1} (the dot is not in the center vertically)
41)	line 208 again: "6.067" before it said "6.064", please fix the wrong one
42)	line 263: "2%" --> I would put "around 2%"
43)	line 268: "reconstructions" --> "reconstruction"
44)	line 269: "Paths" --> "Path"
45)	line 308: "codes" --> "code"
46)	line 405: "electron's" --> "electron"
47)	fig14 - caption: "W distribution" --> I would put "recoil mass W distribution"
48)	table 1: sigma_p is actually sigma_p/p, since it is in percentage
49)	line 432: "Helium-4" --> "4He" (for uniformity, as was written before)
50)	line 488: There is an extra "," at the beginning of the item

The topic of the article is interesting but I would recommend a revision. Please I would like the authors to address the questions asked and provide the required changes or explain why they think those changes are not necessary/correct. Thank you. Best regards.

\begin{enumerate}
\item 
\textcolor{blue}{ }

\end{enumerate}

\end{document}

### 2017-10-16 eg6-letters/NIM/review-1/review-1.tex
more updates to the comments on the nim rtpc nim paper

@@
 
-The article main points of interest are the followings:
+The article main points of interest are the followings:\\
 a)  the usage of GEMs as avalanche creators inside the time projection chamber.
-As far as I know other TPC with the wires substituted by GEM layers have been (or are being) realized, like ALICE TPC upgrade or the FOPI one (proposed for PANDA), but in those cases the GEM are planar and on the end plane of the TPC, not around the beamline.
+As far as I know other TPC with the wires substituted by GEM layers have been (or are being) realized, like ALICE TPC upgrade or the FOPI one (proposed for PANDA), but in those cases the GEM are planar and on the end plane of the TPC, not around the beamline.\\
 b) The shaping of the GEM foils around the target.
-However, since now a fully cylindrical GEM foil has been realized (for the KLOE-2 detector and for the next BESIII inner tracker) I would not call these "cylindrical" GEMs, but "semi-cylindrical" GEMs to point out the difference (which reflects in the construction procedure).
+However, since now a fully cylindrical GEM foil has been realized (for the KLOE-2 detector and for the next BESIII inner tracker) I would not call these "cylindrical" GEMs, but "semi-cylindrical" GEMs to point out the difference (which reflects in the construction procedure).\\
 Maybe these other experiments using GEMs should be mentioned due to the similarities, thought they are successive in time to this RTPC construction.
@@
 
-Chapter by chapter comments:
+\section*{Chapter by chapter comments}:
 
-* Chapter 2:
+\begin{enumerate}
+
+\subsection*{Chapter 2}
 1)	As already said I would not speak of cylindrical GEMs but semi-cylindrical. Moreover, please add the reference to Sauli's paper [11] when speaking the first time about GEM in the text.
@@
 
-* Chapter 3:
+\subsection*{ Chapter 3}
 6)	The description of the electronics looks to me a little not well organized, like a collection of info from previous descriptions from ALICE and BoNuS.
@@
 
-* Chapter 4:
+\subsection*{ Chapter 4}
 	/paragraph 4.1
@@
 
-* Chapter 5
+\subsection*{ Chapter 5}
 	/paragraph 5.1	
@@
 
-* Chapter 6
+\subsection*{ Chapter 6}
 	/paragraph 6.2
@@
 
-* Chapter 7 
+\subsection*{ Chapter 7} 
 23)	Is it "high rate environment" or "high readout rate"? They are connected, but what is the rate the RTPC underwent during data taking?
@@
 ----------------------------------------------
-Some general remarks on the layout:
+\subsection*{ Some general remarks on the layout}
 25)	I would add to the keywords also GEM or gas electron multipliers or multi pattern gas detectors (it depends on what is available).
@@
 
-\begin{enumerate}
 \item 

### 2017-10-16 eg6-letters/NIM/review-1/review-1.tex
more updates to the comments

@@
 
-Reviewer #1: Dear Author, please find here a list of comments from my side.
+Reviewer \#1: Dear Author, please find here a list of comments from my side.
 
@@
 \subsection*{Chapter 2}
-1)	As already said I would not speak of cylindrical GEMs but semi-cylindrical. Moreover, please add the reference to Sauli's paper [11] when speaking the first time about GEM in the text.
-2)	In my opinion, this chapter should highlight better which are the improvements w.r.t.
+\item As already said I would not speak of cylindrical GEMs but semi-cylindrical. Moreover, please add the reference to Sauli's paper [11] when speaking the first time about GEM in the text.
+\textcolor{blue}{ }
+
+\item In my opinion, this chapter should highlight better which are the improvements w.r.t.
 BoNuS detector to underline the originality of this work.
@@
 Please quote some old and new values, maybe in a table, to make them evident.
-3)	Relevant length and thicknesses of the various elements are reported in the text and in the figure, can you please add also the z position of the target w.r.t the detector?
+\textcolor{blue}{ }
+
+\item Relevant length and thicknesses of the various elements are reported in the text and in the figure, can you please add also the z position of the target w.r.t the detector?
 To give the complete information, I would also add the value of the induction gap electric field, which is the only missing field value and the value of the reached amplification gain with the three GEM.
-4)	When speaking of low spark rate the reference [12] is quoted, which is the PDG. Maybe it is better to quote more specific studies like the ones by Bachmann et al.
-5)	line 119: is the Kapton of the GEM foil really 300 mum thick? It is usually very thin, like 50 mum, in order to have low material budget and very high fields.
+\textcolor{blue}{ }
+
+\item When speaking of low spark rate the reference [12] is quoted, which is the PDG. Maybe it is better to quote more specific studies like the ones by Bachmann et al.
+\textcolor{blue}{ }
+
+\item line 119: is the Kapton of the GEM foil really 300 mum thick? It is usually very thin, like 50 mum, in order to have low material budget and very high fields.
+\textcolor{blue}{ }
 
 \subsection*{ Chapter 3}
-6)	The description of the electronics looks to me a little not well organized, like a collection of info from previous descriptions from ALICE and BoNuS.
+\item The description of the electronics looks to me a little not well organized, like a collection of info from previous descriptions from ALICE and BoNuS.
 It is a series of details, some of which not really relevant for the good understanding of the work described in the paper.
 So, I would put only some general info (the number of channels/pad, the number of time samples and their width for each channel and the number of  ADC samples and their width for each channel) with the reference where to find more material and just write explicitly the novelties, such as the fact that the acquisition rate was increased (footnote 2).
-7)	Also, I understand that fig.
+\textcolor{blue}{ }
+
+\item Also, I understand that fig.
 5 comes from reference [14], updated with the values of the RTPC instead of the ALICE-TPC, but it seems to me that there are some parts of the picture which have to be fixed.
@@
 - why L1 and L2 (trigger levels?) 
+\textcolor{blue}{ }
 
@@
 	/paragraph 4.1
-8)	I would really prefer to call it drift "velocity" instead of drift "speed"
-9)	I don't really understand the procedure to find the drift velocity described here and fig.
+\item I would really prefer to call it drift "velocity" instead of drift "speed"
+\textcolor{blue}{ }
+
+\item I don't really understand the procedure to find the drift velocity described here and fig.
 7.
-What is Nb_max e Nb_max/2?
-Why does T_max/2 correspond to Nb_max/2 and why is it used as T_max?
-If I make a quick calculation and use T_max ~ 65 * 100ns and a drift length of ~ 3cm /cos(23°) ~ 7.5 cm I get a v_drift ~ 1.15 cm/microsec << 5 cm/microsec which is the average value of drift velocity in drift chambers.
+What is $Nb_{max}$ e $Nb_{max/2}$?
+Why does $T_{max/2}$ correspond to $Nb_{max/2}$ and why is it used as $T_{max}$?
+If I make a quick calculation and use $T_{max}$ ~ 65 * 100ns and a drift length of ~ 3cm /cos(23°) ~ 7.5 cm I get a $v_{drift}$ ~ 1.15 cm/microsec << 5 cm/microsec which is the average value of drift velocity in drift chambers.
 The procedure according to me would be:
-- for each hit associated to a track, whose time information is available, take the drift time t_drift_i;
-- plot the distribution of these t_drift_i;
-- find the T_min = minimum t_drift_i and T_max = maximum t_drift_i
-- compute delta_t = T_max - T_min and extract the drift velocity by dividing the track length / delta_t. Figure 8 would have the delta_t instead of the T_max vs z.
+- for each hit associated to a track, whose time information is available, take the drift time $t_{drift_{i}}$;
+- plot the distribution of these $t_{drift_{i}}$;
+- find the $T_{min}$ = minimum $t_{drift_{i}}$ and $T_{max}$ = maximum $t_{drift_{i}}$
+- compute $delta_{t} = T_{max} - T_{min}$ and extract the drift velocity by dividing the track length / $delta_{t}$. Figure 8 would have the $delta_{t}$ instead of the $T_{max}$ vs z.
 Please provide more details on the applied procedure, since I have the open questions I wrote before and I could not understand it properly.
@@
 Is it in accordance with the simulations?
-10)	Figure 6: why are T_min and T_max not at the drift gap extremities?
+\textcolor{blue}{ }
+
+\item Figure 6: why are $T_{min}$ and $T_{max}$ not at the drift gap extremities?
+\textcolor{blue}{ }
 
         /paragraph 4.2
-11)	line 306: "in one bin" should be explained better. I understood it is the subdivision in bins of the z coordinate, but it was not so obvious at the first reading
-12)	Has the stability of the drift path been counterchecked with simulations varying the field according to the cathode radius variation?
+
+\item line 306: "in one bin" should be explained better. I understood it is the subdivision in bins of the z coordinate, but it was not so obvious at the first reading
+\textcolor{blue}{ }
+
+\item Has the stability of the drift path been counterchecked with simulations varying the field according to the cathode radius variation?
 How much is the field variation if the radius have some mm of uncertainty?
+\textcolor{blue}{ }
 
         /paragraph 4.3
-13)	The gain calibration is very quick.
+\item The gain calibration is very quick.
 I would like more details, e.g.
@@
 Was a specific code written to simulate the electronics?
-14)	line 330: "correction factors" are mentioned. On what? Why haven't only good tracks been used for calibration? Lack of statistics?
-15)	When it says that the pad charge is "compared" to the neighboring ones, what happens next? Is it the noise reduction step described later? If so, please write it. 
-16)	Figure 11: I don't understand it.
+\textcolor{blue}{ }
+
+\item line 330: "correction factors" are mentioned. On what? Why haven't only good tracks been used for calibration? Lack of statistics?
+\textcolor{blue}{ }
+
+\item When it says that the pad charge is "compared" to the neighboring ones, what happens next? Is it the noise reduction step described later? If so, please write it. 
+\textcolor{blue}{ }
+
+\item Figure 11: I don't understand it.
 How many tracks does the histo contain?
@@
 Sorry for the list of questions, but I could not understand the figure.
-17)	Figure 12 - please, put if after figure 11.
+\textcolor{blue}{ }
+
+\item Figure 12 - please, put if after figure 11.
 Moreover, please change dEdx to dE/dx on y axis.
@@
 Talking about the deuteron band which is present only in the left figure and the smear on the top part of the right picture.
+\textcolor{blue}{ }
 
@@
 	/paragraph 5.1	
-18)	Please detail a little bit more the procedure to remove the oscillatory noise.
+\item Please detail a little bit more the procedure to remove the oscillatory noise.
 It says "event by event and channel by channel": if the ADC threshold is passed then a noise level is subtracted?
 If so, how is it calculated?
+\textcolor{blue}{ } 
         /paragraph 5.2
-19)	How was "10.5 mm" cut chosen? is it in xy plane or in 3-dimensions?
-20)	How was the "10 hits" cut chosen? What is the mean number of primary ionization in this gas mixture?
-21)	< dE/dx > is computed here as corrected Etot divided total track length.
+\item How was "10.5 mm" cut chosen? is it in xy plane or in 3-dimensions?
+\textcolor{blue}{ }
+
+\item How was the "10 hits" cut chosen? What is the mean number of primary ionization in this gas mixture?
+\textcolor{blue}{ }
+
+\item < dE/dx > is computed here as corrected Etot divided total track length.
 Usually the mean dE/dx is computed with the truncated mean of the specific energy losses of each hit.
@@
 dx for each hit can be (maybe) computed from the difference in the hit times.
-Sum dE_i / Sum dx_i is not equal to Sum (dE_i/dx_i).
+Sum $dE_{i}$/Sum $dx_{i}$ is not equal to Sum ($dE_{i}/dx_{i}$).
+\textcolor{blue}{ }
 
@@
 	/paragraph 6.2
-22)	I understand that efficiency is a ratio between two integrals, each integral being the area of the Gaussian which fits the recoil mass distribution in the inclusive and exclusive case.
+\item I understand that efficiency is a ratio between two integrals, each integral being the area of the Gaussian which fits the recoil mass distribution in the inclusive and exclusive case.
 If so, would it be possible to please draw both fits on the figure 14 and provide the integrals to compute the mean efficiency?
 If I misunderstood, please comment.
+\textcolor{blue}{ }
 
 \subsection*{ Chapter 7} 
-23)	Is it "high rate environment" or "high readout rate"? They are connected, but what is the rate the RTPC underwent during data taking?
-24)	I understand the resolution and efficiency have been evaluated with the 2 GeV electrons.
+\item Is it "high rate environment" or "high readout rate"? They are connected, but what is the rate the RTPC underwent during data taking?
+\textcolor{blue}{ }
+
+\item I understand the resolution and efficiency have been evaluated with the 2 GeV electrons.
 Is it foreseen to analyze also the 6 GeV electron runs, which were the actual data taking?
 Is there an evaluation of the foreseen RTPC performances in that case?
+\textcolor{blue}{ }
 
@@
 \subsection*{ Some general remarks on the layout}
-25)	I would add to the keywords also GEM or gas electron multipliers or multi pattern gas detectors (it depends on what is available).
-26)	Please put the units on the axis of every figure, together with the physical quantity. In some figures it is only written in the caption or in the text.
-27)	Sometimes to explain the dimension of something something like "250 mm long" (line 67) while some other times "84-mm-long" (on line 83) is written.
+
+\item I would add to the keywords also GEM or gas electron multipliers or multi pattern gas detectors (it depends on what is available).
+\textcolor{blue}{ }
+
+\item Please put the units on the axis of every figure, together with the physical quantity. In some figures it is only written in the caption or in the text.
+\textcolor{blue}{ }
+
+\item Sometimes to explain the dimension of something something like "250 mm long" (line 67) while some other times "84-mm-long" (on line 83) is written.
 Please make this uniform in the whole text (I just quoted two examples, but there are more in the text).
-28)	In footnote 2, BoNuS is written BONUS and somewhere else in the text also BoNus. Please uniform this to the correct one, which I think is BoNuS.
-29)	Please make the bibliography entries uniform: they are not all written with the same layout.
+\textcolor{blue}{ }
+
+\item In footnote 2, BoNuS is written BONUS and somewhere else in the text also BoNus. Please uniform this to the correct one, which I think is BoNuS.
+\textcolor{blue}{ }
+
+\item Please make the bibliography entries uniform: they are not all written with the same layout.
+\textcolor{blue}{ }
 
 List of in text corrections:
-30)	line 17: "GeV" --> "GeV/c"
-31)	line 26: "nuclei" --> "nucleus"
-32)	line 40: "to track" --> "to bend tracks"(since the magnetic field just bends the track and then the detector tracks them)
-33)	line 91: "second gap" --> "second gas gap"
-34)	line 110: "from the GEMs" -->  something like "after they have been multiplied by the GEMs" or "induced in the last gas gap" since the GEM is the amplification system.
-35)	line 131: "axial magnetic field" --> "solenoidal magnetic field"
-36)	line 133: "challenge" --> "challenges"
-37)	line 133-134: "radial TPC" it would be better to uniform the way to write it in the whole text (like, "RTPC")
-38)	line 167: "stage" --> "stages"
-39)	line 176: "ReadOut" should always be written in the same way (see line 168) unless this was specifically written in a different way in the cited articles
-40)	line 208: cm^{-1} . s^{-1} --> cm^{-1} \cdot s^{-1} (the dot is not in the center vertically)
-41)	line 208 again: "6.067" before it said "6.064", please fix the wrong one
-42)	line 263: "2%" --> I would put "around 2%"
-43)	line 268: "reconstructions" --> "reconstruction"
-44)	line 269: "Paths" --> "Path"
-45)	line 308: "codes" --> "code"
-46)	line 405: "electron's" --> "electron"
-47)	fig14 - caption: "W distribution" --> I would put "recoil mass W distribution"
-48)	table 1: sigma_p is actually sigma_p/p, since it is in percentage
-49)	line 432: "Helium-4" --> "4He" (for uniformity, as was written before)
-50)	line 488: There is an extra "," at the beginning of the item
+
+\item line 17: "GeV" --> "GeV/c"
+\textcolor{blue}{ }
+
+\item line 26: "nuclei" --> "nucleus"
+\textcolor{blue}{ }
+
+\item line 40: "to track" --> "to bend tracks"(since the magnetic field just bends the track and then the detector tracks them)
+\textcolor{blue}{ }
+
+\item line 91: "second gap" --> "second gas gap"
+\textcolor{blue}{ }
+
+\item line 110: "from the GEMs" -->  something like "after they have been multiplied by the GEMs" or "induced in the last gas gap" since the GEM is the amplification system.
+\textcolor{blue}{ }
+
+\item line 131: "axial magnetic field" --> "solenoidal magnetic field"
+\textcolor{blue}{ }
+
+\item line 133: "challenge" --> "challenges"
+\textcolor{blue}{ }
+
+\item line 133-134: "radial TPC" it would be better to uniform the way to write it in the whole text (like, "RTPC")
+\textcolor{blue}{ }
+
+\item line 167: "stage" --> "stages"
+\textcolor{blue}{ }
+
+\item line 176: "ReadOut" should always be written in the same way (see line 168) unless this was specifically written in a different way in the cited articles
+\textcolor{blue}{ }
+
+\item line 208: cm$^{-1}$ . s$^{-1}$ --> cm$^{-1}$ cdot s$^{-1}$ (the dot is not in the center vertically)
+\textcolor{blue}{ }
+
+\item line 208 again: "6.067" before it said "6.064", please fix the wrong one
+\textcolor{blue}{ }
+
+\item line 263: "2\%" --> I would put "around 2\%"
+\textcolor{blue}{ }
+
+\item line 268: "reconstructions" --> "reconstruction"
+\textcolor{blue}{ }
+
+\item line 269: "Paths" --> "Path"
+\textcolor{blue}{ }
+
+\item line 308: "codes" --> "code"
+\textcolor{blue}{ }
+
+\item line 405: "electron's" --> "electron"
+\textcolor{blue}{ }
+
+\item fig14 - caption: "W distribution" --> I would put "recoil mass W distribution"
+\textcolor{blue}{ }
+
+\item table 1: $sigma_{p}$ is actually $sigma_{p/p}$, since it is in percentage
+\textcolor{blue}{ }
+
+\item line 432: "Helium-4" --> "4He" (for uniformity, as was written before)
+\textcolor{blue}{ }
+
+\item line 488: There is an extra "," at the beginning of the item
+\textcolor{blue}{ }
 
@@
 
-\item 
-\textcolor{blue}{ }
-
 \end{enumerate}

### 2017-10-16 eg6-letters/NIM/review-1/review-1.tex
more updates

@@
 The main novelty is the application of the electron multiplier for the amplification stage in a TPC on a semi-cylindrical shaped plane.
-The detector, originally built for the BoNuS experiment, is in fact formed by two semi-cylindrically shaped halves connected together, with the axis coincident with the beam line.
-The detector was implemented to measure DVCS of electrons on different light nuclei and the performances were evaluated on electron - 4He elastic scattering runs.
-Chapter 1 describes the CLAS @ JLab detector, inside which the RTPC was installed and took data. 
+The detector, originally built for the BoNuS experiment, is in fact formed by two semi-cylindrically shaped halves connected together, with the axis coincident with the beam line.\\
+
+The detector was implemented to measure DVCS of electrons on different light nuclei and the performances were evaluated on electron - 4He elastic scattering runs.\\
+
+Chapter 1 describes the CLAS @ JLab detector, inside which the RTPC was installed and took data.\\ 
 Chapter 2 focuses on the RTPC mechanical and electrical layout.
@@
 Everything fits inside a 5T solenoidal magnetic field.
-It provides both time and charge measurements.
-Chapter 3 is a short description of the electronics and readout, mainly inherited from ALICE and BoNuS. The improvement stands in the higher readout rate capability.
-Chapter 4 talks about calibration of drift velocity, drift paths and energy loss measurements by the usage of simulations with MAGBOLTZ and tuning the results on elastic scattering data.
-Chapter 5 concentrates on track finding/fitting procedure and noise evaluation and subtraction.
-Chapter 6 reports on resolution and efficiency from the elastic scattering reconstruction of 2 GeV electrons on 4He and Chapter 7 concludes the paper.
+It provides both time and charge measurements.\\
+Chapter 3 is a short description of the electronics and readout, mainly inherited from ALICE and BoNuS. The improvement stands in the higher readout rate capability.\\
+Chapter 4 talks about calibration of drift velocity, drift paths and energy loss measurements by the usage of simulations with MAGBOLTZ and tuning the results on elastic scattering data.\\
+Chapter 5 concentrates on track finding/fitting procedure and noise evaluation and subtraction.\\
+Chapter 6 reports on resolution and efficiency from the elastic scattering reconstruction of 2 GeV electrons on 4He and Chapter 7 concludes the paper.\\
 
@@
 However, since now a fully cylindrical GEM foil has been realized (for the KLOE-2 detector and for the next BESIII inner tracker) I would not call these "cylindrical" GEMs, but "semi-cylindrical" GEMs to point out the difference (which reflects in the construction procedure).\\
-Maybe these other experiments using GEMs should be mentioned due to the similarities, thought they are successive in time to this RTPC construction.
-Concerning the work description, it is mainly exhaustive, but in some points there are open questions that I would like to submit to the authors in the following.
---------------------------------------------------
 
-\section*{Chapter by chapter comments}:
+Maybe these other experiments using GEMs should be mentioned due to the similarities, thought they are successive in time to this RTPC construction.\\
+
+Concerning the work description, it is mainly exhaustive, but in some points there are open questions that I would like to submit to the authors in the following.\\
+--------------------------------------------------\\
+
+\section*{Chapter by chapter comments}
 

### 2017-10-17 eg6-letters/NIM/EG6_RTPC_NIM.tex
With line numbers for NIM submission
added the answers for the last 25 questions

@@
 \usepackage{hyperref}
+\providecommand{\keywords}[1]{\textbf{\textit{Keywords:}} #1}
 \hypersetup{colorlinks=true, urlcolor=blue, citecolor=blue}
 \usepackage[displaymath]{lineno}
+\linenumbers
 \begin{document}
@@
 
+%\begin{keywords}
+%\textcolor{red}{Raphael please add the list you provided originally},
+%gas electron multipliers.
+%\end{keywords}
+
 \section{Introduction} \label{sec:level1}
@@
 up to 6 GeV energy and 100$\%$ duty factor to three experimental Halls (A, B, C) 
-simultaneously. The CLAS spectrometer~\cite{CLASref}, located
+simultaneously. The CLAS spectrometer~\cite{Mecking:2003zu}, located
 in Hall-B, was based on a superconducting toroidal magnet and composed of 
@@
  \item Three regions of Drift Chambers (DC) for the tracking of charged 
-       particles~\cite{DCref}.
+       particles~\cite{Mestayer:2000we}.
  \item Superconducting toroidal magnet to bend the trajectories 
@@
  \item Threshold Cherenkov Counters (CC) for electron identification at momenta 
-       $<2.7$ GeV~\cite{CCref}.
+    $<2.7$ GeV/c~\cite{Adams:2001kk}.
  \item Scintillation Counters (SC) to identify charged hadrons by measuring their 
-       time of flight~\cite{TOFref}.
+       time of flight~\cite{Smith:1999ii}.
  \item Electromagnetic Calorimeters (EC) for identification of electrons, 
-       photons and neutrons~\cite{ECref}.
+       photons and neutrons~\cite{Amarian:2001zs}.
 \end{itemize}
@@
 Scattering (DVCS) process ($eH \rightarrow e' H' \gamma$, where $H$ is a 
-nucleon or nuclei) necessitates an upgrade of the photon detection system. 
+nucleon or nucleus) necessitates an upgrade of the photon detection system.  
 Indeed, with a 6 GeV electron beam, the majority of DVCS photons are produced 
 at very forward angles, where the acceptance of the EC was poor. To extend the 
-detection range, an inner calorimeter (IC) was built for the E01-113 
-experiment in 2005~\cite{FX}. The IC was constructed from 424 lead-tungstate 
+detection range, an inner calorimeter (IC) was built for the E01-113 experiment 
+in 2005~\cite{Girod:2007aa}. The IC was constructed from 424 lead-tungstate 
 (PbWO$_{4}$) crystals, covering polar angles between 5$^{\circ}$ and 
-15$^{\circ}$~\cite{Hyon-suk}. To protect the 
-CLAS detector and the IC from the large flux of low energy M{\o}ller 
-electrons, a 5~T solenoid magnet was placed around the target to shield the detectors. 
-To detect recoiling $\alpha$ particles from the coherent DVCS on Helium, a new 
-radial time projection chamber (RTPC) was developed to track low energy nuclear 
-fragments. The solenoid field was used to track and measure momentum of 
-particles in the RTPC. The CLAS detector supplemented with both IC and RTPC was used 
-during a three months experimental run~\cite{proposal1,proposal2}
+15$^{\circ}$~\cite{Hyon-suk}. To protect the CLAS detector and the IC from the 
+large flux of low energy M{\o}ller electrons, a 5~T solenoid magnet was placed 
+around the target to shield the detectors.  To detect recoiling $\alpha$ 
+particles from the coherent DVCS on Helium, a new radial time projection 
+chamber (RTPC) was developed to track low energy nuclear fragments. The 
+solenoid field was used to bend tracks and measure momentum of particles in the 
+RTPC. The CLAS detector supplemented with both IC and RTPC was used during a 
+three months experimental run~\cite{proposal1,proposal2}
 in 2009 with a longitudinally polarized electron beam of 130~nA 
@@
 experiment at Jefferson Lab which took data with CLAS in 
-2005~\cite{BONUS-NIM}. Significant improvements were made to the RTPC mechanical 
+2005~\cite{Fenker:2008zz}. Significant improvements were made to the RTPC mechanical 
 structure and fabrication technique that both increased the acceptance and 
@@
 
-With a 6 GeV incident electron energy, the recoiling $^{4}$He nuclei from coherent 
-DVCS have an average momentum around 300 MeV/c (12 MeV kinetic energy). Such low energy $\alpha$ 
-particles are stopped very rapidly, so the RTPC was designed to be as close 
-as possible to the target and fit inside the 230~mm diameter shell and cryostat 
-wall of the solenoid magnet bore.
+With a 6 GeV incident electron energy, the recoiling $^{4}$He nuclei from 
+coherent DVCS have an average momentum around 300~MeV/c (12~MeV kinetic 
+energy). Such low energy $\alpha$ particles are stopped very rapidly, so the 
+RTPC was designed to be as close as possible to the target and fit inside the 
+230~mm diameter shell and cryostat wall of the solenoid magnet bore.
 
@@
 are amplified by three layers of cylindrical gas electron multipliers (GEM) and 
-detected by the readout system 
-on the external shell of the detector as illustrated in the 
-Fig.~\ref{fig:RTPC_1_4}. The RTPC is segmented into two halves with 
-independent GEM amplification systems that cover about 80\% of the azimuthal 
-angle.
+detected by the readout system on the external shell of the detector as 
+illustrated in Figure~\ref{fig:RTPC_1_4}. The RTPC is segmented into two halves 
+with independent GEM amplification systems that cover about 80\% of the 
+azimuthal angle.
 
-We detail here the different regions shown in Fig.~\ref{fig:RTPC_1_4} starting 
-from the beam line towards larger radius:\\
+We detail here the different regions shown in Figure~\ref{fig:RTPC_1_4} 
+starting from the beam line towards larger radius:\\
 \begin{itemize}
-  \item The 6-atm $^4$He target extends along the beam axis; it 
-      is a 284-mm-long, 6-mm-diameter Kapton straw with a 27-$\mu$m wall.
-   \item The first gas gap covers the radial range from 3 mm to 20 mm. It is 
+  \item The 6~atm $^4$He target extends along the beam axis; it is a 284~mm 
+     long, 6~mm diameter Kapton straw with a 27~$\mu$m wall.
+   \item The first gas gap covers the radial range from 3~mm to 20~mm. It is 
       filled with $^{4}$He gas at 1~atm to minimize secondary interactions from
@@
       a 4 $\mu$m thick window made of grounded aluminized Mylar.
-   \item The second gap region extends between 20~mm and 30~mm and is filled with the 
-      gas mixture of 80$\%$ neon (Ne) and 20$\%$ dimethyl ether (DME). This region 
-      is surrounded by a 4~$\mu$m thick window made of aluminized Mylar set at $- 4260$~V 
-      to serve as the cathode.
-   \item The drift region is filled with the same Ne-DME gas mixture and extends 
-      from the cathode to the first GEM, 60 mm away from the beam axis. The average 
-      electric field in this region is perpendicular to the beam and about 550~V/cm.
+   \item The second gas gap region extends between 20~mm and 30~mm and is 
+      filled with the gas mixture of 80$\%$ neon (Ne) and 20$\%$ dimethyl ether 
+      (DME).  This region is surrounded by a 4~$\mu$m thick window made of 
+      aluminized Mylar set at $-4260$~V to serve as the cathode.
+   \item The drift region is filled with the same Ne-DME gas mixture and 
+      extends from the cathode to the first GEM, 60~mm away from the beam axis.  
+      The average electric field in this region is perpendicular to the beam 
+      and about 550~V/cm.
    \item The electron amplification system is composed of three GEMs located at 
-      radii of 60, 63 and 66 mm. In this configuration, the first GEM layer 
+      radii of 60, 63 and 66~mm. In this configuration, the first GEM layer 
       serves as the anode and each subsequent GEM is set at a lower voltage to
-      obtain a strong ($\sim$1600 V/cm) electric field between the GEM foils. A 
+      obtain a strong ($\sim$1600~V/cm) electric field between the GEM foils. A 
       275~V bias is applied across each GEM for amplification.
-   \item The readout board has an internal radius of 69~mm and collects charge
-     from the GEMs. Pre-amplifiers are plugged directly on its outer side and
-     transmit the signal to the data acquisition electronics.
+   \item The readout board has an internal radius of 69~mm and collects charges 
+      after they have been multiplied by the GEMs. Pre-amplifiers are plugged 
+      directly on its outer side and transmit the signal to the data 
+      acquisition electronics.
 \end{itemize}
@@
 \caption{Image of a typical GEM foil similar to the one used for our RTPC 
-\cite{GEM_ref_pic}.} 
+\cite{Sauli:2016eeu}.} 
    \label{fig:GEMs}
@@
 which can be easily used to produce a curved amplification surface. Also, 
-GEMs are known to have relatively low spark rate~\cite{GEM_ref}, which 
+GEMs are known to have relatively low spark rate~\cite{Beringer:1900zz}, which 
 is important when trying to detect 
@@
 layer is chemically etched with 50~$\mu$m diameter holes with double-conical 
-shapes as illustrated in Fig.~\ref{fig:GEMs}. The potential difference 
-applied between the two copper layers of the GEM creates a very strong 
-electric field in each hole leading to high ionization and amplification.
+shapes as illustrated in Figure~\ref{fig:GEMs}. The potential difference 
+applied between the two copper layers of the GEM creates a very strong electric 
+field in each hole leading to high ionization and amplification.
 
@@
 for proper particle identification, with a reasonable
-Lorentz angle. Calculations using the MAGBOLTZ program~\cite{MAGBOLTZ} 
-showed that with the axial 5~T field, we would have a Lorentz angle of 
-about 23$^\circ$ with this gas mixture.
+Lorentz angle. Calculations using the MAGBOLTZ program~\cite{Biagi:1999nwa} 
+showed that with the 5~T solenoidal magnetic field, we would have a Lorentz 
+angle of about 23$^\circ$ with this gas mixture.
 
-One of the important challenge in developing the radial TPC was to obtain a 
-good support structure for the GEM foils to allow a tractable 
-installation of the GEMs. At the same time, we wanted to 
-keep the material budget small in the forward region where we detect other 
-particles in subsequent detectors. We successfully realized these prerequisites 
-by using fiber glass rings glued to each end of the GEM foils to form self 
-supporting cylinders that could be installed independently in the RTPC after 
-gluing and soldering operations. The rigidity of the GEM foils was enough
+One of the important challenges in developing the RTPC was to obtain a good 
+support structure for the GEM foils to allow a tractable installation of the 
+GEMs. At the same time, we wanted to keep the material budget small in the 
+forward region where we detect other particles in subsequent detectors. We 
+successfully realized these prerequisites by using fiber glass rings glued to 
+each end of the GEM foils to form self supporting cylinders that could be 
+installed independently in the RTPC after gluing and soldering operations. The 
+rigidity of the GEM foils was enough
 for the structure to be self-supporting and only the upstream end of the cylinder 
@@
 The RTPC electron collection system had 3200 readout pads. These elements were
-located at the end of the amplification region, 69 mm from the central axis.
-Figure \ref{fig:PADs} illustrates the configuration of the 5 by 4.45 mm pads,
-where the shift between the rows was implemented to reduce aliasing. Each half of the 
-RTPC had 40 rows and 40 columns of pads. The shaded region in Fig.~\ref{fig:PADs} 
-shows how pads were grouped to 16 channels pre-amplifier boards. The pre-amplifier boards, 
-already employed in the BoNuS RTPC~\cite{BONUS-NIM}, serve the dual purpose of 
-inverting the RTPC signals polarity -- from negative to positive -- to match the 
-requirements of the subsequent readout system, and driving the 6-m long ribbon 
-cable that connects to it.
+located at the end of the amplification region, 69~mm from the central axis.
+Figure \ref{fig:PADs} illustrates the configuration of the 5 by 4.45~mm pads,
+where the shift between the rows was implemented to reduce aliasing. Each half 
+of the RTPC had 40 rows and 40 columns of pads. The shaded region in 
+Figure~\ref{fig:PADs} shows how pads were grouped to 16 channels pre-amplifier 
+boards. The pre-amplifier boards, already employed in the BoNuS 
+RTPC~\cite{Fenker:2008zz}, serve the dual purpose of inverting the RTPC signals 
+polarity -- from negative to positive -- to match the requirements of the 
+subsequent readout system, and driving the 6~m long ribbon cable that connects 
+to it.
 
@@
 
-The readout system, similar to the original BoNuS RTPC system~\cite{BONUS-NIM}, 
-was based on the front end electronic boards originally 
-developed for the ALICE TPC readout system at CERN~\cite{ALICE-FEE}. 
-The Front End Card (FEC) 
-hosted the analogue receiver circuit and the subsequent amplification and 
-digitization stage, based on the PASA~\cite{ALICE-PASA} and ALTRO~\cite{ALICE-ALTRO} 
-ASICS. A Readout Control Unit (RCU) board was used to distribute the trigger signal 
-to FECs and for data readout, with each RCU handling up to 25 FECs. Communication 
-between readout controller application (ROC) and FECs was performed trough a custom 
-backplane, implementing a low-voltage signal bus. The RCU communicated with the 
-CLAS DAQ system trough a 200 MB/s optical link, connected to a data acquisition 
-PC hosting a ReadOut Receiver Card (RORC). This PC hosted the ROC used to interface 
-with the CLAS DAQ system. An Ethernet link was also present, for slow-controls and 
+The readout system, similar to the original BoNuS RTPC system~\cite{Fenker:2008zz}, 
+was based on the front end electronic boards originally developed for the ALICE 
+TPC readout system at CERN~\cite{ALICE-FEE}. The Front End Card (FEC) hosted 
+the analogue receiver circuit and the subsequent amplification and digitization 
+stages, based on the PASA~\cite{Soltveit:2012jp} and 
+ALTRO~\cite{EsteveBosch:2003bj} ASICS. A Readout Control Unit (RCU) board was 
+used to distribute the trigger signal to FECs and for data readout, with each 
+RCU handling up to 25 FECs. Communication between readout controller 
+application (ROC) and FECs was performed trough a custom backplane, 
+implementing a low-voltage signal bus. The RCU communicated with the CLAS DAQ 
+system trough a 200 MB/s optical link, connected to a data acquisition PC 
+hosting a readout receiver card. This PC hosted the ROC used to interface with 
+the CLAS DAQ system. An Ethernet link was also present, for slow-controls and 
 monitoring.
@@
 exploited thanks to the new RCU boards developed for the RTPC readout 
-system\footnote{In the original BONUS system, the U2F readout controller had 
-no multi-event capability and used a USB connection rather than fiber 
-optics for readout. These factors limited the maximum readout rate from the 
-BONUS detector to about 500 Hz.}. In order to read all the detector readout 
-pads, four FEC crates were used, each equipped with 6 boards, plus a ROC. A 
-schematic of the readout system, for a single crate, is reported in 
-figure~\ref{fig:ReadoutScheme}. This configuration permitted to reduce the dead 
-time associated to FEC readout operations, which is scaling linearly with the number of 
-boards in the crate. During the 2009 run, the system was successfully operated 
-with a DAQ rate of 3.1 kHz and a live time of $70 \%$, for a luminosity of 
-about $10^{34}$~cm$^{-2}$.s$^{-1}$ and a beam energy of 6.067 GeV.
+system\footnote{In the original BoNuS system, the U2F readout controller had no 
+multi-event capability and used a USB connection rather than fiber optics for 
+readout. These factors limited the maximum readout rate from the BoNuS detector 
+to about 500 Hz.}. In order to read all the detector readout pads, four FEC 
+crates were used, each equipped with 6 boards, plus a ROC. A schematic of the 
+readout system, for a single crate, is reported in 
+Figure~\ref{fig:ReadoutScheme}. This configuration permitted to reduce the dead 
+time associated to FEC readout operations, which is scaling linearly with the 
+number of boards in the crate. During the 2009 run, the system was successfully 
+operated with a DAQ rate of 3.1 kHz and a live time of $70 \%$, for a 
+luminosity of about $10^{34}$~cm$^{-2}\cdot$s$^{-1}$ and a beam energy of 
+6.064~GeV.
 
@@
 referred to the trigger time, the resolution is equivalent to the ALTRO 
-sampling time, 100 ns.
+sampling time, 100~ns.
 
@@
 drift paths and gains of the detector. Drift speed and paths were initially
-calculated using the MAGBOLTZ~\cite{MAGBOLTZ} program, then refined using
+calculated using the MAGBOLTZ~\cite{Biagi:1999nwa} program, then refined using
 data to account for variations of the run conditions. We always assume 
@@
 electrons released close to the cathode take the most time to reach the readout 
-pads, the cylindrical symmetry insures that this maximum drift distance is the same for all 
-tracks. We illustrate this in Fig.~\ref{fig:RTPC_signals}, where we depict a 
-typical $^{4}$He track. By measuring the maximum time ($T_{Max}$), we can therefore infer the drift 
-speed of the electrons in the RTPC.\\
+pads, the cylindrical symmetry insures that this maximum drift distance is the 
+same for all tracks. We illustrate this in Figure~\ref{fig:RTPC_signals}, where 
+we depict a typical $^{4}$He track. By measuring the maximum time ($T_{Max}$), 
+we can therefore infer the drift speed of the electrons in the RTPC.\\
 
@@
 
-To measure the maximum drift time, we used the time profile of hits from identified tracks 
-shown in Fig.~\ref{fig:TDC_profile}. We can clearly observe the 
-dropping edge expected from geometrical considerations. We define a value $T_{Max/2}$ at 
-which the dropping edge passes half the maximum number of hits in the 
-histogram. This value was measured in bins along the 200~mm RTPC's length to take into 
-account variations in the electric and magnetic field in the RTPC (see 
-Fig.~\ref{fig:RunNumber_61551_TDCmax_Zslice}).
+To measure the maximum drift time, we used the time profile of hits from 
+identified tracks shown in Figure~\ref{fig:TDC_profile}. We can clearly observe 
+the dropping edge expected from geometrical considerations. We define a value 
+$T_{Max/2}$ at which the dropping edge passes half the maximum number of hits 
+in the histogram. This value was measured in bins along the 200~mm RTPC's 
+length to take into account variations in the electric and magnetic field in 
+the RTPC (see Figure~\ref{fig:RunNumber_61551_TDCmax_Zslice}).
 
@@
 \includegraphics[scale=0.42]{hits_time_profile.pdf}
-   \caption[]{Time distribution of the hits associated with a track in one experimental run. Trigger
-              time is defined as T=15, the time unit is the ALTRO sampling time of 100~ns.} 
+\caption[]{Time distribution of the hits associated with a track in one 
+experimental run. Trigger time is defined as T=15, the time unit is the ALTRO 
+sampling time of 100~ns.} 
 \label{fig:TDC_profile}
@@
 run\footnote{We had to increase the gas flow during the experiment due to a small leak 
-in the RTPC, which concurred to the large shift of drift time observed around run number 
-61600. While our gas system was kept slightly over 
-atmospheric pressure to limit contamination from air or other external gases, it 
-is likely that this leak was the source of modification of the drift speed.}.  
-Figure~\ref{fig:Drift_run_number_1} shows the $T_{Max/2}$ values for 
-individual runs (approximately 2 hours long). We observe significant change in 
-the drift speed before and after run 61600, while variations within these periods 
-are ~2\%.
+in the RTPC, which concurred to the large shift of drift time observed around 
+run number 61600. While our gas system was kept slightly over atmospheric 
+pressure to limit contamination from air or other external gases, it is likely 
+that this leak was the source of modification of the drift speed.}.  
+Figure~\ref{fig:Drift_run_number_1} shows the $T_{Max/2}$ values for individual 
+runs (approximately 2 hours long). We observe significant change in the drift 
+speed before and after run 61600, while variations within these periods are 
+around 2\%.
 
@@
 
-In summary, we obtain from our calibration a parame\-tri\-zation of the drift speed 
+In summary, we obtain from our calibration a parametrization of the drift speed 
 as a function of both position along the beam axis and the run number.  These 
-functions were extracted for our entire data set and implemented in the 
-track reconstructions code.
+functions were extracted for our entire data set and implemented in the track 
+reconstruction code.
 
-\subsection{Drift Paths Calibration}
+\subsection{Drift Path Calibration}
 
@@
 ionization in the gas. We calculated them with
-MAGBOLTZ~\cite{MAGBOLTZ}, but it requires knowledge of the detector's 
+MAGBOLTZ~\cite{Biagi:1999nwa}, but it requires knowledge of the detector's 
 geometry, gas mixture composition, and of course the electric and magnetic 
@@
 our knowledge of the electric field. These problems, already 
-encountered for the BoNuS RTPC calibration~\cite{BONUS-NIM}, motivated the 
+encountered for the BoNuS RTPC calibration~\cite{Fenker:2008zz}, motivated the 
 acquisition of specific calibration runs. These were taken with a lower energy 
@@
 At the end of the extraction procedure, the azimuthal difference between the detection pad and 
-the ionization point ($\Delta\phi$) was extracted as a function of time. 
-In Fig.~\ref{fig:DELTA_PHI_TDC}, we show the resulting data points for one 
-bin, where the drift path is easily identified and eventually fitted for 
-implementation in our reconstruction codes.
+the ionization point ($\Delta\phi$) was extracted as a function of time.  In 
+Figure~\ref{fig:DELTA_PHI_TDC}, we show the resulting data points for one bin, 
+where the drift path is easily identified and eventually fitted for 
+implementation in our reconstruction code.
 
@@
 1.269 GeV data from the end of the run period (shown in blue on 
-Fig.~\ref{fig:Drift_run_number_1}). Interestingly, we found very similar drift paths
+Figure~\ref{fig:Drift_run_number_1}). Interestingly, we found very similar 
+drift paths
 for the two data sets and concluded that any changes in the system only
@@
 compared simulation to experiment on an event by event basis as shown in 
-Fig.~\ref{fig:EVENT_adc_tdc}. The gain for each pad was calculated 
-as the ratio of the measured ADCs to the simulated deposited energy.  
-Then, these gains were refined using correction factors obtained from a 
-sample of good tracks. For each track, we calculate the corrected 
-energy deposit on a pad and compared it to the average
+Figure~\ref{fig:EVENT_adc_tdc}. The gain for each pad was calculated as the 
+ratio of the measured ADCs to the simulated deposited energy.  Then, these 
+gains were refined using correction factors obtained from a sample of good 
+tracks. For each track, we calculate the corrected energy deposit on a pad and 
+compared it to the average
 deposit recorded by the other pads. This last step was implemented to 
 avoid any bias from this simulation based calibration method.
-Final results are shown in Fig.~\ref{fig:dedx_p_exp_2nd}, where energy 
-loss of particles is plotted against momentum over charge ratio. One can 
-clearly see the band for $^4$He in its expected position.
+Final results are shown in Figure~\ref{fig:dedx_p_exp_2nd}, where energy loss 
+of particles is plotted against momentum over charge ratio. One can clearly see 
+the band for $^4$He in its expected position.
 
@@
 The first is an oscillatory noise located early in the readout time window, 
-shown in the top panel of Fig.~\ref{fig:noise} for a particularly noisy 
-channel. Its amplitude is similar to those of real tracks. About 
-18\% of the readout channels exhibit large contributions from this noise 
-characteristic. Due to its unique time-energy correlation for the given 
-channels, the noise could be removed on an event by event and channel by 
-channel basis without significant loss of good signals. The result of the
-procedure is illustrated in the bottom panel of Fig.~\ref{fig:noise}.
+shown in the top panel of Figure~\ref{fig:noise} for a particularly noisy 
+channel.  Its amplitude is similar to those of real tracks. About 18\% of the 
+readout channels exhibit large contributions from this noise characteristic.  
+Due to its unique time-energy correlation for the given channels, the noise 
+could be removed on an event by event and channel by channel basis without 
+significant loss of good signals. The result of the
+procedure is illustrated in the bottom panel of Figure~\ref{fig:noise}.
 
@@
 \subsection{Energy Loss Corrections}\label{sec_eloss}
-Energy loss between the target and drift region was significant in the RTPC and necessitated a correction for optimal momentum reconstruction at the primary interaction vertex.
-The dominant loss was in the 27-$\mu$m-thick Kapton target wall, with significant contributions also from the pressurized target gas and the foils before reaching the drift region.
-Corrections were developed based on GEANT4 simulations with the full RTPC geometry and parameterized in terms of recoil curvature in the drift region and polar angle, separetely for all recoil hypotheses ($p$, $d$, $^3$H, $^3$He, $^4$He).
-At our average coherent $^4$He DVCS kinematics, energy losses were about 5 MeV, while for $e-^4$He elastic scattering losses were about 3 MeV, which corresponds to momentum corrections of 25\% and 15\%, respectively.
+Energy loss between the target and drift region was significant in the RTPC and 
+necessitated a correction for optimal momentum reconstruction at the primary 
+interaction vertex.  The dominant loss was in the 27~$\mu$m thick Kapton target 
+wall, with significant contributions also from the pressurized target gas and 
+the foils before reaching the drift region.  Corrections were developed based 
+on GEANT4 simulations with the full RTPC geometry and parameterized in terms of 
+recoil curvature in the drift region and polar angle, separetely for all recoil 
+hypotheses ($p$, $d$, $^3$H, $^3$He, $^4$He).  At our average coherent $^4$He 
+DVCS kinematics, energy losses were about 5 MeV, while for $e-^4$He elastic 
+scattering losses were about 3 MeV, which corresponds to momentum corrections 
+of 25\% and 15\%, respectively.
 
@@
 The primary data sample used for calibration and performance assessment of the
-RTPC was elastic scattering with a 1.2 GeV electron beam. The electron's momentum
+RTPC was elastic scattering with a 1.2 GeV electron beam. The electron momentum
 and direction is measured with CLAS, which uniquely determines the expected recoiling
@@
 and direction of the RTPC track provides a clean selection of elastically-scattered
-$^4$He, shown in Fig.~\ref{fig:w}.
+$^4$He, shown in Figure~\ref{fig:w}.
 
@@
   \includegraphics[width=8cm]{fit_W_distribution_l.png}
-  \caption{The $W$ distribution calculated from electron kinematics before (``inclusive'')
-  and after (``exclusive'') requiring a matching track in the RTPC.\label{fig:w}}
+  \caption{The recoil mass $W$ distribution calculated from electron kinematics 
+  before (``inclusive'') and after (``exclusive'') requiring a matching track 
+  in the RTPC.\label{fig:w}}
 \end{figure}
@@
   \hline
-& $\sigma_{z}$ &  $\sigma_{\theta}$ & $\sigma_{\phi}$ & $\sigma_{p}$\\
+& $\sigma_{z}$ &  $\sigma_{\theta}$ & $\sigma_{\phi}$ & $\sigma_{p}/p$\\
 \hline
@@
 only on electron detection, to the exclusive elastic yield, where the Helium
-recoil is also detected (see Fig.~\ref{fig:w}). We present in Fig.~\ref{fig:rtpc_eff}
-the results for the two halves of the detector. We observe that the left and 
-the right modules have similar efficiencies except near the upstream target 
-window. This difference is due to the large number of dead channels concentrated
-in this part of the left half of the detector
+recoil is also detected (see Figure~\ref{fig:w}). We present in 
+Figure~\ref{fig:rtpc_eff} the results for the two halves of the detector. We 
+observe that the left and the right modules have similar efficiencies except 
+near the upstream target window. This difference is due to the large number of 
+dead channels concentrated in this part of the left half of the detector
 
@@
 We reported on the construction, operation and calibration of a small RTPC 
-designed to measure Helium-4 nuclei in high rate environment. The operation
+designed to measure $^4$He nuclei in high rate environment. The operation
 of the detector was successful and allowed to detect Helium nuclei with a 75\%
@@
 
-\bibitem{CLASref}
-   B.A. Mecking et al., The CEBAF large acceptance spectrometer, Nucl. Inst. 
-   and Meth. A 503, 513 (2003).
+\bibitem{Mecking:2003zu} 
+   B.~A.~Mecking {\it et al.} [CLAS Collaboration],
+  The CEBAF Large Acceptance Spectrometer (CLAS),
+  Nucl.\ Instrum.\ Meth.\ A {\bf 503}, 513 (2003).
+  %doi:10.1016/S0168-9002(03)01001-5
 
-\bibitem{DCref}
-   M.D. Mestayer et al., The CLAS drift chamber System, Nucl. Inst.  and Meth.  
-   A 449, 81 (2000).
+\bibitem{Mestayer:2000we} 
+   M.~D.~Mestayer {\it et al.},
+  The CLAS drift chamber system,
+  Nucl.\ Instrum.\ Meth.\ A {\bf 449}, 81 (2000).
+  %doi:10.1016/S0168-9002(00)00151-0
 
-\bibitem{CCref}
-   G. Adams et al., The CLAS Cerenkov detector, Nucl. Inst. and Meth. A 465, 
-   414 (2001).
+\bibitem{Adams:2001kk} 
+   G.~Adams {\it et al.},
+  The CLAS Cherenkov detector,
+  Nucl.\ Instrum.\ Meth.\ A {\bf 465}, 414 (2001).
+  %doi:10.1016/S0168-9002(00)01313-9
 
-\bibitem{TOFref}
-   E.S. Smith et al., The time-of-flight system for CLAS, Nucl.  Inst. and 
-   Meth. A 432, 265 (1999).
+\bibitem{Smith:1999ii} 
+   E.~S.~Smith {\it et al.},
+  The time-of-flight system for CLAS,
+  Nucl.\ Instrum.\ Meth.\ A {\bf 432}, 265 (1999).
+  %doi:10.1016/S0168-9002(99)00484-2
 
-\bibitem{ECref}
-   M. Amarian et al., The CLAS forward electromagnetic calorimeter, Nucl.  
-   Inst. and Meth. A 460, 239 (2001).
+\bibitem{Amarian:2001zs} 
+   M.~Amarian {\it et al.},
+  The CLAS forward electromagnetic calorimeter,
+  Nucl.\ Instrum.\ Meth.\ A {\bf 460}, 239 (2001).
+  %doi:10.1016/S0168-9002(00)00996-7
 
-\bibitem{FX}
-   F.X. Girod et al. (CLAS Collaboration), Measurement of Deeply virtual Compton 
-   scattering beam-spin asymmetries, Phys.Rev.Lett. 100 (2008) 162002
+\bibitem{Girod:2007aa} 
+   F.~X.~Girod {\it et al.} [CLAS Collaboration],
+  Measurement of Deeply virtual Compton scattering beam-spin asymmetries,
+  Phys.\ Rev.\ Lett.\  {\bf 100}, 162002 (2008).
+  %doi:10.1103/PhysRevLett.100.162002
+  %[arXiv:0711.4805 [hep-ex]].
 
@@
    Nucl{\'e}on avec le D{\'e}tecteur CLAS de Jefferson Lab: Mesure des Sections 
-   Efficaces polaris{\'e}es et non polaris{\'e}es, IPNO-Thesis, 2007.
+   Efficaces polaris{\'e}es et non polaris{\'e}es, IPNO-Thesis (2007).
 
 \bibitem{proposal1}
-   G Asryan et al., Meson spectroscopy in the Coherent Production on $^{4}$He with CLAS, Jlab 
-   proposal to PAC31 (2007).
+   G.~Asryan et al., Meson spectroscopy in the Coherent Production on $^{4}$He 
+   with CLAS, Jlab proposal to PAC31 (2007).
 
 \bibitem{proposal2}
-   K. Hafidi et al., Deeply virtual Comton scattering off $^{4}$He, Jlab 
+   K.~Hafidi et al., Deeply virtual Comton scattering off $^{4}$He, Jlab 
    proposal to PAC33 (2008).
 
-\bibitem{BONUS-NIM}
-   Howard C. Fenker et al., BoNuS: Development and Use of a Radial TPC using 
-   Cylindrical GEMs, Nucl. Instrum. Meth. A592, 273-286 (2008)
+\bibitem{Fenker:2008zz} 
+   H.~C.~Fenker {\it et al.},
+  BoNuS: Development and Use of a Radial TPC using Cylindrical GEMs,
+  Nucl.\ Instrum.\ Meth.\ A {\bf 592}, 273 (2008).
+  %doi:10.1016/j.nima.2008.04.047
 
-\bibitem{GEM_ref_pic}
-   F. Sauli, The Gas Electron Multiplier (GEM): Operating Principles and 
-   Applications, Nucl. Instr. and Meth, A805(2016)2
+\bibitem{Sauli:2016eeu} 
+   F.~Sauli,
+  The gas electron multiplier (GEM): Operating principles and applications,
+  Nucl.\ Instrum.\ Meth.\ A {\bf 805}, 2 (2016).
+  %doi:10.1016/j.nima.2015.07.060
 
-\bibitem{GEM_ref}
-   J. Beringer et al. (Particle Data Group), Particle detectors at 
-   accelerators, Phys. Rev. D 86, 010001, pages: 339-368, 2012.
+\bibitem{Beringer:1900zz} 
+   J.~Beringer {\it et al.} [Particle Data Group],
+  Review of Particle Physics (RPP),
+  Phys.\ Rev.\ D {\bf 86}, 010001 (2012).
+  %doi:10.1103/PhysRevD.86.010001
 
-\bibitem{MAGBOLTZ}
-   S. Biagi, Monte Carlo simulation of electron drift and diffusion in counting 
-   gases under the influence of electric and magnetic fields, Nucl.  Inst. and 
-   Meth. in Phy. Res. A, vol. 421, pp. 234-240, 1999.
+\bibitem{Biagi:1999nwa} 
+   S.~F.~Biagi,
+  Monte Carlo simulation of electron drift and diffusion in counting gases 
+  under the influence of electric and magnetic fields,
+  Nucl.\ Instrum.\ Meth.\ A {\bf 421}, no. 1-2, 234 (1999).
+  %doi:10.1016/S0168-9002(98)01233-9
 
  \bibitem{ALICE-FEE}
- L. Musa et al., The ALICE TPC front end electronics, 2003 IEEE Nuclear 
- Science Symposium, 2003, pp. 3647-3651 Vol.5
+ L. Musa et al., The ALICE TPC front end Electronics Nuclear Science Symposium 
+ Conference Record, 2003 IEEE, 5 3647-3651 Vol.5, Oct (2003).
 
- \bibitem{ALICE-PASA}
+\bibitem{Soltveit:2012jp} 
    H.~K.~Soltveit {\it et al.},
-   ``The Preamplifier shaper for the ALICE TPC-Detector,''
-   Nucl.\ Instrum.\ Meth.\ A {\bf 676} (2012) 106
+  The Preamplifier shaper for the ALICE TPC-Detector,
+  Nucl.\ Instrum.\ Meth.\ A {\bf 676}, 106 (2012).
+  %doi:10.1016/j.nima.2012.02.012
+  %[arXiv:1203.3564 [physics.ins-det]].
 
- \bibitem{ALICE-ALTRO},
- R. E. Bosch, {\it et al.}, ``The ALTRO chip: a 16-channel A/D converter and 
- digital processor for gas detectors'', IEEE Transactions on Nuclear Science, 
- vol. 50, no. 6, pp. 2460-2469, Dec. 2003.
+\bibitem{EsteveBosch:2003bj} 
+   R.~Esteve Bosch, A.~Jimenez de Parga, B.~Mota and L.~Musa,
+  The ALTRO chip: A 16-channel A/D converter and digital processor for gas 
+  detectors,
+  IEEE Trans.\ Nucl.\ Sci.\  {\bf 50}, 2460 (2003).
+  %doi:10.1109/TNS.2003.820629
 

### 2017-10-17 eg6-letters/NIM/review-1/review-1.tex
added the answers for the last 25 questions

--- 2017-10-16 eg6-letters/NIM/review-1/review-1.tex
@@
 
-\section*{Reviewers' comments (11 Oct 2017)}
+\section*{Reviewers' comments (Oct. 11th, 2017)}
 
@@
 
-Summary: the article describes the layout, operation and performances of a Radial Time Projection Chamber with the electron amplification stage provided by three layers of GEM.
-The main novelty is the application of the electron multiplier for the amplification stage in a TPC on a semi-cylindrical shaped plane.
-The detector, originally built for the BoNuS experiment, is in fact formed by two semi-cylindrically shaped halves connected together, with the axis coincident with the beam line.
-The detector was implemented to measure DVCS of electrons on different light nuclei and the performances were evaluated on electron - 4He elastic scattering runs.
-Chapter 1 describes the CLAS @ JLab detector, inside which the RTPC was installed and took data. 
-Chapter 2 focuses on the RTPC mechanical and electrical layout.
-From inner to outer, there are: the 4He gas target, a 4He gas gap, the actual time projection chamber.
-The time projection chamber is a 200 long detector composed by different gas gaps limited by concentric electrodes around the axis: cathode (R=30mm), G1(R=60mm), G2(R=63mm), G3(R=66mm), readout plane (R=69mm).
-Everything fits inside a 5T solenoidal magnetic field.
-It provides both time and charge measurements.
-Chapter 3 is a short description of the electronics and readout, mainly inherited from ALICE and BoNuS. The improvement stands in the higher readout rate capability.
-Chapter 4 talks about calibration of drift velocity, drift paths and energy loss measurements by the usage of simulations with MAGBOLTZ and tuning the results on elastic scattering data.
-Chapter 5 concentrates on track finding/fitting procedure and noise evaluation and subtraction.
-Chapter 6 reports on resolution and efficiency from the elastic scattering reconstruction of 2 GeV electrons on 4He and Chapter 7 concludes the paper.
+Summary: the article describes the layout, operation and performances of a 
+Radial Time Projection Chamber with the electron amplification stage provided 
+by three layers of GEM. The main novelty is the application of the electron 
+multiplier for the amplification stage in a TPC on a semi-cylindrical shaped 
+plane. The detector, originally built for the BoNuS experiment, is in fact 
+formed by two semi-cylindrically shaped halves connected together, with the 
+axis coincident with the beam line.\\
 
-The article main points of interest are the followings:\\
-a)  the usage of GEMs as avalanche creators inside the time projection chamber.
-As far as I know other TPC with the wires substituted by GEM layers have been (or are being) realized, like ALICE TPC upgrade or the FOPI one (proposed for PANDA), but in those cases the GEM are planar and on the end plane of the TPC, not around the beamline.\\
-b) The shaping of the GEM foils around the target.
-However, since now a fully cylindrical GEM foil has been realized (for the KLOE-2 detector and for the next BESIII inner tracker) I would not call these "cylindrical" GEMs, but "semi-cylindrical" GEMs to point out the difference (which reflects in the construction procedure).\\
-Maybe these other experiments using GEMs should be mentioned due to the similarities, thought they are successive in time to this RTPC construction.
-Concerning the work description, it is mainly exhaustive, but in some points there are open questions that I would like to submit to the authors in the following.
---------------------------------------------------
+The detector was implemented to measure DVCS of electrons on different light 
+nuclei and the performances were evaluated on electron-$^4$He elastic 
+scattering runs.\\
 
-\section*{Chapter by chapter comments}:
+Chapter 1 describes the CLAS@JLab detector, inside which the RTPC was installed 
+and took data. Chapter 2 focuses on the RTPC mechanical and electrical layout.  
+From inner to outer, there are: the $^4$He gas target, a $^4$He gas gap, the 
+actual time projection chamber. The time projection chamber is a 200~mm long 
+detector composed by different gas gaps limited by concentric electrodes around 
+the axis: cathode (R= 30~mm), G1(R= 60~mm), G2(R= 63~mm), G3(R= 66~mm), readout 
+plane (R= 69~mm). Everything fits inside a 5T solenoidal magnetic field. It 
+provides both time and charge measurements. Chapter 3 is a short description of 
+the electronics and readout, mainly inherited from ALICE and BoNuS. The 
+improvement stands in the higher readout rate capability. Chapter 4 talks about 
+calibration of drift velocity, drift paths and energy loss measurements by the 
+usage of simulations with MAGBOLTZ and tuning the results on elastic scattering 
+data. Chapter 5 concentrates on track finding/fitting procedure and noise 
+evaluation and subtraction. Chapter 6 reports on resolution and efficiency from 
+the elastic scattering reconstruction of 1 GeV electrons on 4He and Chapter 7 
+concludes the paper.\\
+
+The article main points of interest are the followings:
+
+a) The usage of GEMs as avalanche creators inside the time projection chamber.  
+As far as I know other TPC with the wires substituted by GEM layers have been 
+(or are being) realized, like ALICE TPC upgrade or the FOPI one (proposed for 
+PANDA), but in those cases the GEM are planar and on the end plane of the TPC, 
+not around the beamline.
+
+b) The shaping of the GEM foils around the target. However, since now a fully 
+cylindrical GEM foil has been realized (for the KLOE-2 detector and for the 
+next BESIII inner tracker) I would not call these "cylindrical" GEMs, but 
+"semi-cylindrical" GEMs to point out the difference (which reflects in the 
+construction procedure). Maybe these other experiments using GEMs should be 
+mentioned due to the similarities, thought they are successive in time to this 
+RTPC construction.\\
+
+Concerning the work description, it is mainly exhaustive, but in some points 
+there are open questions that I would like to submit to the authors in the 
+following.
+
+\newpage
+\section*{Chapter by chapter comments}
 
@@
 \subsection*{Chapter 2}
-\item As already said I would not speak of cylindrical GEMs but semi-cylindrical. Moreover, please add the reference to Sauli's paper [11] when speaking the first time about GEM in the text.
+\item As already said I would not speak of cylindrical GEMs but 
+   semi-cylindrical. Moreover, please add the reference to Sauli's paper [11] 
+   when speaking the first time about GEM in the text.\\
 \textcolor{blue}{ }
 
-\item In my opinion, this chapter should highlight better which are the improvements w.r.t.
-BoNuS detector to underline the originality of this work.
-For example, better acceptance?
-Higher gain?
-Higher electric stability?
-Lower material budget?
-Please quote some old and new values, maybe in a table, to make them evident.
+\item In my opinion, this chapter should highlight better which are the 
+   improvements w.r.t. BoNuS detector to underline the originality of this 
+   work. For example, better acceptance? Higher gain? Higher electric 
+   stability? Lower material budget? Please quote some old and new values, 
+   maybe in a table, to make them evident.\\
 \textcolor{blue}{ }
 
-\item Relevant length and thicknesses of the various elements are reported in the text and in the figure, can you please add also the z position of the target w.r.t the detector?
-To give the complete information, I would also add the value of the induction gap electric field, which is the only missing field value and the value of the reached amplification gain with the three GEM.
+\item Relevant length and thicknesses of the various elements are reported in 
+   the text and in the figure, can you please add also the z position of the 
+   target w.r.t the detector? To give the complete information, I would also 
+   add the value of the induction gap electric field, which is the only missing 
+   field value and the value of the reached amplification gain with the three 
+   GEM.\\
 \textcolor{blue}{ }
 
-\item When speaking of low spark rate the reference [12] is quoted, which is the PDG. Maybe it is better to quote more specific studies like the ones by Bachmann et al.
+\item When speaking of low spark rate the reference [12] is quoted, which is 
+   the PDG. Maybe it is better to quote more specific studies like the ones by 
+   Bachmann et al.\\
 \textcolor{blue}{ }
 
-\item line 119: is the Kapton of the GEM foil really 300 mum thick? It is usually very thin, like 50 mum, in order to have low material budget and very high fields.
+\item line 119: is the Kapton of the GEM foil really 300 mum thick? It is 
+   usually very thin, like 50 mum, in order to have low material budget and 
+   very high fields.\\
 \textcolor{blue}{ }
@@
 \subsection*{ Chapter 3}
-\item The description of the electronics looks to me a little not well organized, like a collection of info from previous descriptions from ALICE and BoNuS.
-It is a series of details, some of which not really relevant for the good understanding of the work described in the paper.
-So, I would put only some general info (the number of channels/pad, the number of time samples and their width for each channel and the number of  ADC samples and their width for each channel) with the reference where to find more material and just write explicitly the novelties, such as the fact that the acquisition rate was increased (footnote 2).
+\item The description of the electronics looks to me a little not well 
+   organized, like a collection of info from previous descriptions from ALICE 
+   and BoNuS. It is a series of details, some of which not really relevant for 
+   the good understanding of the work described in the paper. So, I would put 
+   only some general info (the number of channels/pad, the number of time 
+   samples and their width for each channel and the number of  ADC samples and 
+   their width for each channel) with the reference where to find more material 
+   and just write explicitly the novelties, such as the fact that the 
+   acquisition rate was increased (footnote 2).\\
 \textcolor{blue}{ }
 
-\item Also, I understand that fig.
-5 comes from reference [14], updated with the values of the RTPC instead of the ALICE-TPC, but it seems to me that there are some parts of the picture which have to be fixed.
-I list them here:
-- why does it say 768 pads?
-- why 7.6 microsec?
-- the anode wire e grid make no sense here
-- why L1 and L2 (trigger levels?) 
+\item Also, I understand that fig. 5 comes from reference [14], updated with 
+   the values of the RTPC instead of the ALICE-TPC, but it seems to me that 
+   there are some parts of the picture which have to be fixed. I list them 
+   here:\\
+- why does it say 768 pads?\\
+- why 7.6 microsec?\\
+- the anode wire e grid make no sense here\\
+- why L1 and L2 (trigger levels?) \\
 \textcolor{blue}{ }
@@
 	/paragraph 4.1
-\item I would really prefer to call it drift "velocity" instead of drift "speed"
+\item I would really prefer to call it drift "velocity" instead of drift 
+   "speed"\\
 \textcolor{blue}{ }
 
-\item I don't really understand the procedure to find the drift velocity described here and fig.
-7.
-What is $Nb_{max}$ e $Nb_{max/2}$?
-Why does $T_{max/2}$ correspond to $Nb_{max/2}$ and why is it used as $T_{max}$?
-If I make a quick calculation and use $T_{max}$ ~ 65 * 100ns and a drift length of ~ 3cm /cos(23°) ~ 7.5 cm I get a $v_{drift}$ ~ 1.15 cm/microsec << 5 cm/microsec which is the average value of drift velocity in drift chambers.
-The procedure according to me would be:
-- for each hit associated to a track, whose time information is available, take the drift time $t_{drift_{i}}$;
-- plot the distribution of these $t_{drift_{i}}$;
-- find the $T_{min}$ = minimum $t_{drift_{i}}$ and $T_{max}$ = maximum $t_{drift_{i}}$
-- compute $delta_{t} = T_{max} - T_{min}$ and extract the drift velocity by dividing the track length / $delta_{t}$. Figure 8 would have the $delta_{t}$ instead of the $T_{max}$ vs z.
-Please provide more details on the applied procedure, since I have the open questions I wrote before and I could not understand it properly.
-Moreover, please quote the value of the found drift velocity.
-Is it in accordance with the simulations?
+\item I don't really understand the procedure to find the drift velocity 
+   described here and fig. 7. What is $Nb_{max}$ e $Nb_{max/2}$? Why does 
+   $T_{max/2}$ correspond to $Nb_{max/2}$ and why is it used as $T_{max}$? If I 
+   make a quick calculation and use $T_{max}$ ~ 65 * 100ns and a drift length 
+   of ~ 3cm /cos(23°) ~ 7.5 cm I get a $v_{drift}$ ~ 1.15 cm/microsec << 5 
+   cm/microsec which is the average value of drift velocity in drift 
+   chambers.\\
+The procedure according to me would be:\\
+- for each hit associated to a track, whose time information is available, take 
+the drift time $t_{drift_{i}}$;\\
+- plot the distribution of these $t_{drift_{i}}$;\\
+- find the $T_{min}$ = minimum $t_{drift_{i}}$ and $T_{max}$ = maximum 
+$t_{drift_{i}}$\\
+- compute $delta_{t} = T_{max} - T_{min}$ and extract the drift velocity by 
+dividing the track length / $delta_{t}$. Figure 8 would have the $delta_{t}$ 
+instead of the $T_{max}$ vs z.\\
+Please provide more details on the applied procedure, since I have the open 
+questions I wrote before and I could not understand it properly. Moreover, 
+please quote the value of the found drift velocity. Is it in accordance with 
+the simulations?\\
 \textcolor{blue}{ }
 
-\item Figure 6: why are $T_{min}$ and $T_{max}$ not at the drift gap extremities?
+\item Figure 6: why are $T_{min}$ and $T_{max}$ not at the drift gap 
+   extremities?\\
 \textcolor{blue}{ }
@@
 
-\item line 306: "in one bin" should be explained better. I understood it is the subdivision in bins of the z coordinate, but it was not so obvious at the first reading
+\item line 306: "in one bin" should be explained better. I understood it is the 
+   subdivision in bins of the z coordinate, but it was not so obvious at the 
+   first reading\\
 \textcolor{blue}{ }
 
-\item Has the stability of the drift path been counterchecked with simulations varying the field according to the cathode radius variation?
-How much is the field variation if the radius have some mm of uncertainty?
+\item Has the stability of the drift path been counterchecked with simulations 
+   varying the field according to the cathode radius variation? How much is the 
+   field variation if the radius have some mm of uncertainty?\\
 \textcolor{blue}{ }
@@
         /paragraph 4.3
-\item The gain calibration is very quick.
-I would like more details, e.g.
-"setting the simulation properly" intends only GEANT4 or also MAGBOLTZ or GARFIELD?
-Were they used to simulate the drift and avalanche formation of the electrons?
-And the diffusion from the gas?
-Was a specific code written to simulate the electronics?
+\item The gain calibration is very quick. I would like more details, e.g. 
+   "setting the simulation properly" intends only GEANT4 or also MAGBOLTZ or 
+   GARFIELD? Were they used to simulate the drift and avalanche formation of 
+   the electrons? And the diffusion from the gas? Was a specific code written 
+   to simulate the electronics?\\
 \textcolor{blue}{ }
 
-\item line 330: "correction factors" are mentioned. On what? Why haven't only good tracks been used for calibration? Lack of statistics?
+\item line 330: "correction factors" are mentioned. On what? Why haven't only 
+   good tracks been used for calibration? Lack of statistics?\\
 \textcolor{blue}{ }
 
-\item When it says that the pad charge is "compared" to the neighboring ones, what happens next? Is it the noise reduction step described later? If so, please write it. 
+\item When it says that the pad charge is "compared" to the neighboring ones, 
+   what happens next? Is it the noise reduction step described later? If so, 
+   please write it. \\
 \textcolor{blue}{ }
 
-\item Figure 11: I don't understand it.
-How many tracks does the histo contain?
-If the single pad has 128 channels, how many channels does the single bin contain?
-Moreover, is the dE calculated on pad by pad basis?
-In that case, why don't you put just one point in the histo for each pad?
-What is the mean number of channels or pads fired by one track?
-Sorry for the list of questions, but I could not understand the figure.
+\item Figure 11: I don't understand it. How many tracks does the histo contain? 
+   If the single pad has 128 channels, how many channels does the single bin 
+   contain? Moreover, is the dE calculated on pad by pad basis? In that case, 
+   why don't you put just one point in the histo for each pad? What is the mean 
+   number of channels or pads fired by one track? Sorry for the list of 
+   questions, but I could not understand the figure.\\
 \textcolor{blue}{ }
 
-\item Figure 12 - please, put if after figure 11.
-Moreover, please change dEdx to dE/dx on y axis.
-Why are the left and right pictures so different?
-Talking about the deuteron band which is present only in the left figure and the smear on the top part of the right picture.
+\item Figure 12 - please, put if after figure 11. Moreover, please change dEdx 
+   to dE/dx on y axis. Why are the left and right pictures so different? 
+   Talking about the deuteron band which is present only in the left figure and 
+   the smear on the top part of the right picture. \\
 \textcolor{blue}{ }
@@
 \subsection*{ Chapter 5}
-	/paragraph 5.1	
-\item Please detail a little bit more the procedure to remove the oscillatory noise.
-It says "event by event and channel by channel": if the ADC threshold is passed then a noise level is subtracted?
-If so, how is it calculated?
-\textcolor{blue}{ } 
-        /paragraph 5.2
-\item How was "10.5 mm" cut chosen? is it in xy plane or in 3-dimensions?
+        /paragraph 5.1	\item Please detail a little bit more the procedure to 
+           remove the oscillatory noise. It says "event by event and channel by 
+           channel": if the ADC threshold is passed then a noise level is 
+           subtracted? If so, how is it calculated?\\
 \textcolor{blue}{ }
 
-\item How was the "10 hits" cut chosen? What is the mean number of primary ionization in this gas mixture?
+/paragraph 5.2
+\item How was "10.5 mm" cut chosen? is it in xy plane or in 3-dimensions?\\
+\textcolor{blue}{ }
+
+\item How was the "10 hits" cut chosen? What is the mean number of primary 
+   ionization in this gas mixture?\\
 \textcolor{blue}{ }
@@
 \item < dE/dx > is computed here as corrected Etot divided total track length. 
-Usually the mean dE/dx is computed with the truncated mean of the specific energy losses of each hit.
-Isn't it possible to compute it like this here?
-dx for each hit can be (maybe) computed from the difference in the hit times.
-Sum $dE_{i}$/Sum $dx_{i}$ is not equal to Sum ($dE_{i}/dx_{i}$).
+   Usually the mean dE/dx is computed with the truncated mean of the specific 
+   energy losses of each hit. Isn't it possible to compute it like this here? 
+   dx for each hit can be (maybe) computed from the difference in the hit 
+   times. Sum $dE_{i}$/Sum $dx_{i}$ is not equal to Sum ($dE_{i}/dx_{i}$).\\
 \textcolor{blue}{ }
@@
 \subsection*{ Chapter 6}
+
         /paragraph 6.2
-\item I understand that efficiency is a ratio between two integrals, each integral being the area of the Gaussian which fits the recoil mass distribution in the inclusive and exclusive case.
-If so, would it be possible to please draw both fits on the figure 14 and provide the integrals to compute the mean efficiency?
-If I misunderstood, please comment.
+\item I understand that efficiency is a ratio between two integrals, each 
+   integral being the area of the Gaussian which fits the recoil mass 
+   distribution in the inclusive and exclusive case. If so, would it be 
+   possible to please draw both fits on the figure 14 and provide the integrals 
+   to compute the mean efficiency? If I misunderstood, please comment.\\
 \textcolor{blue}{ }
 
-\subsection*{ Chapter 7} 
-\item Is it "high rate environment" or "high readout rate"? They are connected, but what is the rate the RTPC underwent during data taking?
+\subsection*{ Chapter 7} \item Is it "high rate environment" or "high readout 
+   rate"? They are connected, but what is the rate the RTPC underwent during 
+   data taking?\\
 \textcolor{blue}{ }
 
-\item I understand the resolution and efficiency have been evaluated with the 2 GeV electrons.
-Is it foreseen to analyze also the 6 GeV electron runs, which were the actual data taking?
-Is there an evaluation of the foreseen RTPC performances in that case?
+\item I understand the resolution and efficiency have been evaluated with the 2 
+   GeV electrons. Is it foreseen to analyze also the 6 GeV electron runs, which 
+   were the actual data taking? Is there an evaluation of the foreseen RTPC 
+   performances in that case?\\
 \textcolor{blue}{ }
 
-----------------------------------------------
 \subsection*{ Some general remarks on the layout}
 
-\item I would add to the keywords also GEM or gas electron multipliers or multi pattern gas detectors (it depends on what is available).
+\item I would add to the keywords also GEM or gas electron multipliers or multi 
+   pattern gas detectors (it depends on what is available).\\
+\textcolor{blue}{Updated}
+
+\item Please put the units on the axis of every figure, together with the 
+   physical quantity. In some figures it is only written in the caption or in 
+   the text.\\
 \textcolor{blue}{ }
 
-\item Please put the units on the axis of every figure, together with the physical quantity. In some figures it is only written in the caption or in the text.
-\textcolor{blue}{ }
+\item Sometimes to explain the dimension of something something like "250 mm 
+   long" (line 67) while some other times "84-mm-long" (on line 83) is written. 
+   Please make this uniform in the whole text (I just quoted two examples, but 
+   there are more in the text).\\
+\textcolor{blue}{Updated everywhere}
 
-\item Sometimes to explain the dimension of something something like "250 mm long" (line 67) while some other times "84-mm-long" (on line 83) is written.
-Please make this uniform in the whole text (I just quoted two examples, but there are more in the text).
-\textcolor{blue}{ }
+\item In footnote 2, BoNuS is written BONUS and somewhere else in the text also 
+   BoNus. Please uniform this to the correct one, which I think is BoNuS.\\
+\textcolor{blue}{Updated to BoNuS everywhere}
 
-\item In footnote 2, BoNuS is written BONUS and somewhere else in the text also BoNus. Please uniform this to the correct one, which I think is BoNuS.
-\textcolor{blue}{ }
-
-\item Please make the bibliography entries uniform: they are not all written with the same layout.
-\textcolor{blue}{ }
+\item Please make the bibliography entries uniform: they are not all written 
+   with the same layout.\\
+\textcolor{blue}{Updated}
 
@@
 
-\item line 17: "GeV" --> "GeV/c"
-\textcolor{blue}{ }
+\item line 17: "GeV" --> "GeV/c"\\
+\textcolor{blue}{Corrected}
 
-\item line 26: "nuclei" --> "nucleus"
-\textcolor{blue}{ }
+\item line 26: "nuclei" --> "nucleus"\\
+\textcolor{blue}{Corrected}
 
-\item line 40: "to track" --> "to bend tracks"(since the magnetic field just bends the track and then the detector tracks them)
-\textcolor{blue}{ }
+\item line 40: "to track" --> "to bend tracks"(since the magnetic field just 
+   bends the track and then the detector tracks them)\\
+\textcolor{blue}{Added}
 
-\item line 91: "second gap" --> "second gas gap"
-\textcolor{blue}{ }
+\item line 91: "second gap" --> "second gas gap"\\
+\textcolor{blue}{Added}
 
-\item line 110: "from the GEMs" -->  something like "after they have been multiplied by the GEMs" or "induced in the last gas gap" since the GEM is the amplification system.
-\textcolor{blue}{ }
+\item line 110: "from the GEMs" -->  something like "after they have been 
+   multiplied by the GEMs" or "induced in the last gas gap" since the GEM is 
+   the amplification system.\\
+\textcolor{blue}{Added}
 
-\item line 131: "axial magnetic field" --> "solenoidal magnetic field"
-\textcolor{blue}{ }
+\item line 131: "axial magnetic field" --> "solenoidal magnetic field"\\
+\textcolor{blue}{Replaced}
 
-\item line 133: "challenge" --> "challenges"
-\textcolor{blue}{ }
+\item line 133: "challenge" --> "challenges"\\
+\textcolor{blue}{Added}
 
-\item line 133-134: "radial TPC" it would be better to uniform the way to write it in the whole text (like, "RTPC")
-\textcolor{blue}{ }
+\item line 133-134: "radial TPC" it would be better to uniform the way to write 
+   it in the whole text (like, "RTPC")\\
+\textcolor{blue}{Uniformed}
 
-\item line 167: "stage" --> "stages"
-\textcolor{blue}{ }
+\item line 167: "stage" --> "stages"\\
+\textcolor{blue}{Corrected}
 
-\item line 176: "ReadOut" should always be written in the same way (see line 168) unless this was specifically written in a different way in the cited articles
-\textcolor{blue}{ }
+\item line 176: "ReadOut" should always be written in the same way (see line 
+   168) unless this was specifically written in a different way in the cited 
+   articles\\
+\textcolor{blue}{Uniformed}
 
-\item line 208: cm$^{-1}$ . s$^{-1}$ --> cm$^{-1}$ cdot s$^{-1}$ (the dot is not in the center vertically)
-\textcolor{blue}{ }
+\item line 208: cm$^{-1}$ . s$^{-1}$ --> cm$^{-1}$ cdot s$^{-1}$ (the dot is 
+   not in the center vertically)\\
+\textcolor{blue}{Corrected}
 
 \item line 208 again: "6.067" before it said "6.064", please fix the wrong one
-\textcolor{blue}{ }
+\textcolor{blue}{Corrected. It is 6.064} \\
 
-\item line 263: "2\%" --> I would put "around 2\%"
-\textcolor{blue}{ }
+\item line 263: "2\%" --> I would put "around 2\%"\\
+\textcolor{blue}{Added}
 
-\item line 268: "reconstructions" --> "reconstruction"
-\textcolor{blue}{ }
+\item line 268: "reconstructions" --> "reconstruction"\\
+\textcolor{blue}{Corrected }
 
-\item line 269: "Paths" --> "Path"
-\textcolor{blue}{ }
+\item line 269: "Paths" --> "Path"\\
+\textcolor{blue}{Corrected}
 
-\item line 308: "codes" --> "code"
-\textcolor{blue}{ }
+\item line 308: "codes" --> "code"\\
+\textcolor{blue}{Corrected}
 
-\item line 405: "electron's" --> "electron"
-\textcolor{blue}{ }
+\item line 405: "electron's" --> "electron"\\
+\textcolor{blue}{Corrected}
 
-\item fig14 - caption: "W distribution" --> I would put "recoil mass W distribution"
-\textcolor{blue}{ }
+\item fig14 - caption: "W distribution" --> I would put "recoil mass W 
+   distribution"\\
+\textcolor{blue}{Added}
 
-\item table 1: $sigma_{p}$ is actually $sigma_{p/p}$, since it is in percentage
-\textcolor{blue}{ }
+\item table 1: $sigma_{p}$ is actually $sigma_{p/p}$, since it is in 
+   percentage\\
+\textcolor{blue}{Yes it is. Corrected }
 
-\item line 432: "Helium-4" --> "4He" (for uniformity, as was written before)
-\textcolor{blue}{ }
+\item line 432: "Helium-4" --> "4He" (for uniformity, as was written before)\\
+\textcolor{blue}{Changed to $^4$He}
 
-\item line 488: There is an extra "," at the beginning of the item
-\textcolor{blue}{ }
+\item line 488: There is an extra "," at the beginning of the item\\
+\textcolor{blue}{Cleaned}\\
+~\\
+\end{enumerate}
 
 The topic of the article is interesting but I would recommend a revision.  
-Please I would like the authors to address the questions asked and provide the required changes or explain why they think those changes are not necessary/correct.
-Thank you.
-Best regards.
-
-\end{enumerate}
+Please I would like the authors to address the questions asked and provide the 
+required changes or explain why they think those changes are not 
+necessary/correct. Thank you. Best regards.\\
 

### 2017-10-17 eg6-letters/NIM/EG6_RTPC_NIM.tex
more updates to the comments on the nim paper

@@
 such that drifting electrons are pushed away from the beam line. These electrons 
-are amplified by three layers of cylindrical gas electron multipliers (GEM) and 
-detected by the readout system on the external shell of the detector as 
-illustrated in Figure~\ref{fig:RTPC_1_4}. The RTPC is segmented into two halves 
-with independent GEM amplification systems that cover about 80\% of the 
-azimuthal angle.
+are amplified by three layers of semi-cylindrical gas electron multipliers 
+(GEM)~\cite{Sauli:2016eeu} and detected by the readout system on the external 
+shell of the detector as illustrated in Figure~\ref{fig:RTPC_1_4}. The RTPC is 
+segmented into two halves with independent GEM amplification systems that cover 
+about 80\% of the azimuthal angle.
 
@@
 installed independently in the RTPC after gluing and soldering operations. The 
-rigidity of the GEM foils was enough
-for the structure to be self-supporting and only the upstream end of the cylinder 
-was fixed to the main mechanical support structure. This design only left a 
-light fiberglass ring in the downstream end, reducing to a minimum secondary 
-interactions.
+rigidity of the GEM foils was enough for the structure to be self-supporting 
+and only the upstream end of the cylinder was fixed to the main mechanical 
+support structure. This design only left a light fiberglass ring in the 
+downstream end, reducing to a minimum secondary interactions.
 

### 2017-10-18 eg6-letters/NIM/EG6_RTPC_NIM.tex
more answers and implementations of the comments on the NIM paper

@@
 %\begin{keywords}
-%\textcolor{red}{Raphael please add the list you provided originally},
-%gas electron multipliers.
+%Time projection chamber, gas electron multipliers, alpha particles, DVCS, 
+%Nuclear physics
 %\end{keywords}
@@
 \begin{itemize}
-  \item The 6~atm $^4$He target extends along the beam axis; it is a 284~mm 
-     long, 6~mm diameter Kapton straw with a 27~$\mu$m wall.
+  \item The 6~atm $^4$He target forms the detector central z-axis which is 
+     along the beamline ; it is a 284~mm long, 6~mm diameter Kapton straw with 
+     a 27~$\mu$m wall.
    \item The first gas gap covers the radial range from 3~mm to 20~mm. It is 
@@
 The GEM technology has been chosen for the flexibility of the GEM foils,
-which can be easily used to produce a curved amplification surface. Also, 
-GEMs are known to have relatively low spark rate~\cite{Beringer:1900zz}, which 
-is important when trying to detect 
-highly ionizing slow nuclei that deposit large amount of energy. The GEMs for 
-this RTPC are made from a Kapton insulator layer, 300~$\mu$m 
-thick, sandwiched between two 5~$\mu$m copper layers\footnote{The GEM foils were produced by 
-Tech-Etch, Inc.}. The mesh of each GEM 
-layer is chemically etched with 50~$\mu$m diameter holes with double-conical 
-shapes as illustrated in Figure~\ref{fig:GEMs}. The potential difference 
-applied between the two copper layers of the GEM creates a very strong electric 
-field in each hole leading to high ionization and amplification.
+which can be easily used to produce a curved amplification surface. Also, GEMs 
+are known to have relatively low spark rate~\cite{Bachmann:2000kj}, which is 
+important when trying to detect highly ionizing slow nuclei that deposit large 
+amount of energy. The GEMs for this RTPC are made from a Kapton insulator 
+layer, 50~$\mu$m thick, sandwiched between two 5~$\mu$m copper 
+layers\footnote{The GEM foils were produced by Tech-Etch, Inc.}. The mesh of 
+each GEM layer is chemically etched with 50~$\mu$m diameter holes with 
+double-conical shapes as illustrated in Figure~\ref{fig:GEMs}. The potential 
+difference applied between the two copper layers of the GEM creates a very 
+strong electric field in each hole leading to high ionization and 
+amplification.
 
@@
 fields over the whole volume of the detector. We used this calculation as a 
-first calibration, but, 
-as can be seen with the drift speed, conditions in the chamber were changing 
-over time. Moreover, the 4 $\mu$m foil used as a cathode is easily deformed, such
-that we expect the geometrical accuracy to be of few millimeters, directly impacting 
-our knowledge of the electric field. These problems, already 
-encountered for the BoNuS RTPC calibration~\cite{Fenker:2008zz}, motivated the 
-acquisition of specific calibration runs. These were taken with a lower energy 
-electron beam (1.204 and 1.269 GeV) to enhance the cross section of the elastic 
-scattering ($e^{4}$He$\rightarrow e^{4}$He). In this process, the measurement of
+first calibration, but, as can be seen with the drift speed, conditions in the 
+chamber were changing over time. Moreover, the 4 $\mu$m foil used as a cathode 
+is easily deformed, such that we expect the geometrical accuracy to be of few 
+millimeters, directly impacting our knowledge of the electric field. These 
+problems, already encountered for the BoNuS RTPC 
+calibration~\cite{Fenker:2008zz}, motivated the acquisition of specific 
+calibration runs. These were taken with a lower energy electron beam (1.204 and 
+1.269 GeV) to enhance the cross section of the elastic scattering 
+($e^{4}$He$\rightarrow e^{4}$He). In this process, the measurement of
 the electron kinematics allows to calculate directly the kinematics of the Helium nucleus. 
@@
 
-Based on the kinematics of the electrons in the calibration data, 
-we generated the Helium nucleus in our RTPC GEANT4 simulation~\cite{GEANT4}. Then,
+Based on the kinematics of the electrons in the calibration data, we generated 
+the Helium nucleus in our RTPC GEANT4 simulation~\cite{GEANT4}. Then,
 we compared the calculated GEANT4 trajectory of the Helium nuclei to 
@@
 
-At the end of the extraction procedure, the azimuthal difference between the detection pad and 
-the ionization point ($\Delta\phi$) was extracted as a function of time.  In 
-Figure~\ref{fig:DELTA_PHI_TDC}, we show the resulting data points for one bin, 
-where the drift path is easily identified and eventually fitted for 
-implementation in our reconstruction code.
+At the end of the extraction procedure, the azimuthal difference between the 
+detection pad and the ionization point ($\Delta\phi$) was extracted as a 
+function of time. In Figure~\ref{fig:DELTA_PHI_TDC}, we show the resulting data 
+points for one bin in z-coordinate of the RTPC, where the drift path is easily 
+identified and eventually fitted for implementation in our reconstruction code.
 
@@
 Figure~\ref{fig:Drift_run_number_1}). Interestingly, we found very similar 
-drift paths
-for the two data sets and concluded that any changes in the system only
-significantly affected the drift speed.
+drift paths for the two data sets and concluded that any changes in the system 
+only significantly affected the drift speed.
 
@@
 
-\bibitem{Beringer:1900zz} 
-   J.~Beringer {\it et al.} [Particle Data Group],
-  Review of Particle Physics (RPP),
-  Phys.\ Rev.\ D {\bf 86}, 010001 (2012).
-  %doi:10.1103/PhysRevD.86.010001
+\bibitem{Bachmann:2000kj} S.~Bachmann {\it et al.},
+ Performance of GEM detectors in high intensity particle beams,
+ Nucl.\ Instrum.\ Meth.\ A {\bf 470}, 548 (2001).
+ %doi:10.1016/S0168-9002(01)00802-6
 

### 2017-10-18 eg6-letters/NIM/acknowledgment.tex
updated the acknowledgments of the NIM paper
more answers and implementations of the comments on the NIM paper

@@
 The authors thank the staff of the Accelerator and Physics Divisions at the 
-Thomas Jefferson National Accelerator Facility who made this work 
-possible. This work was supported in part by the French Centre National de la 
-Recherche Scientifique (CNRS), the Italian Istituto Nazionale di Fisica Nucleare (INFN) 
-and the U.S. Department of Energy. The 
-author (M.~Hattawy) also acknowledges the support of the {\it Consulat 
-G\'en\'eral de France \`a J\'erusalem}. 
-The Southeastern Universities Research Association operates the Thomas 
-Jefferson National Accelerator Facility for the United States Department of 
-Energy under contract DE-AC05-06OR23177.
+Thomas Jefferson National Accelerator Facility who made this work possible.  
+This work was supported in part by the French Centre National de la Recherche 
+Scientifique (CNRS), the Italian Istituto Nazionale di Fisica Nucleare (INFN) 
+and the U.S. Department of Energy. M.~Hattawy also acknowledges the support of 
+the {\it Consulat G\'en\'eral de France \`a J\'erusalem}.  The Southeastern 
+Universities Research Association operates the Thomas Jefferson National 
+Accelerator Facility for the United States Department of Energy under contract 
+DE-AC05-06OR23177. This material is based upon work supported by the U.S.  
+Department of Energy, Office of Science, Office of Nuclear Physics, under 
+contract number DE-AC02-06CH11357.

### 2017-10-18 eg6-letters/NIM/review-1/review-1.tex
more updates to the comments on the nim paper
more answers and implementations of the comments on the NIM paper

@@
    when speaking the first time about GEM in the text.\\
-\textcolor{blue}{ }
+\textcolor{blue}{cylinderical GEMs-> semi-cylinderical. The reference has been added.}
 
@@
    maybe in a table, to make them evident.\\
-\textcolor{blue}{ }
+\textcolor{red}{To the group: Do we have such a comparison? }
 
@@
    GEM.\\
-\textcolor{blue}{ }
+\textcolor{blue}{- The target tube is the central z-axis of the detector. The 
+text is modified to make it clean.\\}
+\textcolor{red}{- Regarding the electric field, it was 2.8 kV/cm in BoNuS, does 
+anyone know our exact field in this gap?\\}
+\textcolor{blue}{- The gain of such GEM configuration has been studied by 
+   CERN's Gas Detector Development Group (Fabio Sauli, Progress with the Gas 
+   Electron Multiplier, 2nd Workshop on Advanced Transition Radiation Detectors 
+   for Accelerator and Space Applications (Bari, Sept. 4-7, 2003), Nucl. Instr. 
+   and Meth. A522(2004)93). The results, see the reference, demonstrate that 
+one should not simply add gains to each other for multilayer GEM 
+amplifications.  We did not evaluate precisely the overall gain in our chamber, 
+so we do not have a value for our RTPC GEM system at this point.}
 
@@
    Bachmann et al.\\
-\textcolor{blue}{ }
+\textcolor{blue}{Thanks. It has been replaced.}
 
@@
    very high fields.\\
-\textcolor{blue}{ }
+\textcolor{blue}{Sorry typo. It is 50 $mu$m}
 
@@
    acquisition rate was increased (footnote 2).\\
-\textcolor{blue}{ }
+\textcolor{red}{Raphael, Can you check here?}
 
@@
 - why L1 and L2 (trigger levels?) \\
-\textcolor{blue}{ }
+\textcolor{red}{Raphael, Can you check here? }
 
@@
    "speed"\\
-\textcolor{blue}{ }
+\textcolor{red}{To the group: We do have radial and azimuthal drift velocities, 
+but we measure the average of their sum. }
 
 \item I don't really understand the procedure to find the drift velocity 
-   described here and fig. 7. What is $Nb_{max}$ e $Nb_{max/2}$? Why does 
+   described here and fig. 7. What is $Nb_{max}$ and $Nb_{max/2}$? Why does 
    $T_{max/2}$ correspond to $Nb_{max/2}$ and why is it used as $T_{max}$? If I 
@@
    extremities?\\
-\textcolor{blue}{ }
+   \textcolor{blue}{This is a schematic to illustrate the definitions of 
+   $T_{min}$ and $T_{max}$ for a chain hits. The figure can be modified if 
+needed.}
 
@@
    first reading\\
-\textcolor{blue}{ }
+\textcolor{blue}{Cleared}
 
-\item Has the stability of the drift path been counterchecked with simulations 
+\item Has the stability of the drift path been counter checked with simulations 
    varying the field according to the cathode radius variation? How much is the 
    field variation if the radius have some mm of uncertainty?\\
-\textcolor{blue}{ }
+\textcolor{blue}{We did not study this case.}
 
@@
 \subsection*{ Chapter 5}
-        /paragraph 5.1	\item Please detail a little bit more the procedure to 
-           remove the oscillatory noise. It says "event by event and channel by 
-           channel": if the ADC threshold is passed then a noise level is 
-           subtracted? If so, how is it calculated?\\
-\textcolor{blue}{ }
+        /paragraph 5.1
+
+\item Please detail a little bit more the procedure to remove the oscillatory 
+   noise. It says "event by event and channel by channel": if the ADC threshold 
+   is passed then a noise level is subtracted? If so, how is it calculated?\\
+\textcolor{red}{Nathan, Can you work on it. }
 
@@
 \item How was "10.5 mm" cut chosen? is it in xy plane or in 3-dimensions?\\
-\textcolor{blue}{ }
+\textcolor{blue}{The distance between hits are calculated in 3D. This cut has 
+been chosen because it enables us to jump longer gaps from dead areas of the 
+readout pads without increasing the level of spurious tracks.}
 
@@
    ionization in this gas mixture?\\
-\textcolor{blue}{ }
+   \textcolor{blue}{Figure \ref{fig:nb_hits} shows the number of hits 
+   distribution for the collected elastic $^4$He tracks from the 1.2 GeV 
+dataset. The mean number of hits is around 135 and the 10 hits cut at the 
+reconstruction level is a loose cut to reduce the level of the spurious 
+tracks.}
+
+\begin{figure}[h!]
+   \centering
+   \includegraphics[scale=0.45]{nb_hits.png}
+   \caption{the number of hits distribution for the collected elastic $^4$He 
+   tracks from the 1.2 GeV dataset.} \label{fig:nb_hits}
+\end{figure}
 
@@
    to compute the mean efficiency? If I misunderstood, please comment.\\
-\textcolor{blue}{ }
+\textcolor{red}{Nathan, do you still have the individual integrals? }
 
-\subsection*{ Chapter 7} \item Is it "high rate environment" or "high readout 
-   rate"? They are connected, but what is the rate the RTPC underwent during 
-   data taking?\\
-\textcolor{blue}{ }
+\subsection*{ Chapter 7}
+
+\item Is it "high rate environment" or "high readout rate"? They are connected, 
+   but what is the rate the RTPC underwent during data taking?\\
+\textcolor{red}{Can we find such information in the logbook?}
 
@@
    performances in that case?\\
-\textcolor{blue}{ }
+\textcolor{blue}{Typically, the elastic reaction is used for such performance 
+evaluation. But the elastic cross sections is really small at 6 GeV beam 
+energy.}
 

### 2017-10-18 eg6-letters/NIM/EG6_RTPC_NIM.tex
more updated to the NIM paper

@@
 
-%\begin{keywords}
-%Time projection chamber, gas electron multipliers, alpha particles, DVCS, 
-%Nuclear physics
-%\end{keywords}
+\begin{keywords}
+Time projection chamber, gas electron multipliers, alpha particles, DVCS, 
+Nuclear physics
+\end{keywords}
 
@@
 
-To calibrate the gains, we compared the experimental ADCs to the energy deposited 
-for each pad individually in GEANT4 by similar simulated tracks (using the 
-same elastic events as for the drift 
-paths calibration). This requires a very good GEANT4 simulation 
-including drift paths, but also the spread of the charge along the path
-before reaching the pad, so that the simulated hits match the experimental 
-ones. Moreover, the simulation has to match the DAQ features 
-that can lead to cutting out hits. After setting the simulation properly, we 
-compared simulation to experiment on an event by event basis as shown in 
-Figure~\ref{fig:EVENT_adc_tdc}. The gain for each pad was calculated as the 
-ratio of the measured ADCs to the simulated deposited energy.  Then, these 
-gains were refined using correction factors obtained from a sample of good 
-tracks. For each track, we calculate the corrected energy deposit on a pad and 
-compared it to the average
-deposit recorded by the other pads. This last step was implemented to 
-avoid any bias from this simulation based calibration method.
-Final results are shown in Figure~\ref{fig:dedx_p_exp_2nd}, where energy loss 
-of particles is plotted against momentum over charge ratio. One can clearly see 
-the band for $^4$He in its expected position.
+To calibrate the gains, we compared the experimental ADCs to the energy 
+deposited for each pad individually in GEANT4 by similar simulated tracks 
+(using the same elastic events as for the drift paths calibration). This 
+requires a very good GEANT4 simulation including drift paths and the spread of 
+the charge along the path before reaching the pad, so that the simulated hits 
+match the experimental ones. Moreover, the simulation has to match the DAQ 
+features that can lead to cutting out some hits. After setting the simulation 
+properly, we compared simulation to experiment on an event by event basis as 
+shown in Figure~\ref{fig:EVENT_adc_tdc}. The gain for each pad was calculated 
+as the ratio of the measured ADCs to the simulated deposited energy. Then, This 
+set of the gains was applied to the experimental data. We noticed that some 
+pads record lower ADCs than expected. For this reason, we wanted to make sure 
+that the recorded ADCs by a given pad are similar to the ADCs recorded by other 
+pads in the same track. At this step, we compared the mean ADCs of each
+pad to the mean ADCs of the whole track. This ratio is collected for each pad 
+from a sample of elastic events and a gain correction factor is extracted and 
+applied to the first extracted gain ratio giving a final gain for each readout 
+pad. Final results are shown in Figure~\ref{fig:dedx_p_exp_2nd}, where energy 
+loss of particles is plotted against momentum over charge ratio. One can 
+clearly see the band for $^4$He in its expected position.
 
-\begin{figure}[tb!]
+\begin{figure}[tb]
    \centering
@@
 
-\begin{figure*}[tb]
+\begin{figure*}[tp]
 \centering

### 2017-10-18 eg6-letters/NIM/review-1/review-1.tex
more updated to the NIM paper

@@
    \textcolor{blue}{This is a schematic to illustrate the definitions of 
-   $T_{min}$ and $T_{max}$ for a chain hits. The figure can be modified if 
+   $T_{min}$ and $T_{max}$ in a chain of hits. The figure can be modified if 
 needed.}
@@
    first reading\\
-\textcolor{blue}{Cleared}
+\textcolor{blue}{The text is cleared}
 
@@
    field variation if the radius have some mm of uncertainty?\\
-\textcolor{blue}{We did not study this case.}
+\textcolor{blue}{We did not study this case. }
 
@@
    to simulate the electronics?\\
-\textcolor{blue}{ }
+\textcolor{blue}{Only GEANT4 simulation was used in performing the gain 
+   calibration, where the drift paths are updated in the simulation. The 
+   electrons avalanche formation and the gas diffusion are performed though 
+GEANT4. We did not implement a detailed description to simulate the 
+electronics, but we did apply similar conditions to match the real DAQ, such as 
+the rejection of the signals from bad pads and conditions to ensure that each 
+pad must have at least 3 consecutive time bins, with ADC values above the 
+threshold, 35 ADCs, in order to be recorded. The text is cleared with more 
+details. }
 
@@
    good tracks been used for calibration? Lack of statistics?\\
-\textcolor{blue}{ }
+\textcolor{blue}{Correction factor on the extracted gain for each pad. We used 
+the elastic $^4$He tracks as we could calculate the recoil $^4$He kinematics 
+from the scattered electron in CLAS to avoid any discrepancy from the RTPC.}
 
@@
    please write it. \\
-\textcolor{blue}{ }
+\textcolor{blue}{The gain extraction is following this order: \\
+- pass 1: the gain of each pad is defined as the ratio between the mean 
+recorded experimental ADCs to the mean simulated ADCs in the same track. Then 
+for each pad, the gain ratios were collected from all the identified elastic 
+tracks and these gains were fitted by a Landau function to give a
+  first pass gain for each pad as the most probable value of the fit.\\
+ - pass2: to make sure that the recorded ADCs by a given pad are similar to the 
+ recorded ADCs by other pads in the same track, we refined this calibration 
+ after the extracted gains were applied to the experimental data. At this step, 
+ we compared the mean ADCs of each pad to the mean ADCs of the whole track. 
+ This ratio is collected from all the elastic events and a gain correction 
+ factor is extracted and applied giving a final gain for each pad.
+  }
 
@@
    questions, but I could not understand the figure.\\
-\textcolor{blue}{ }
+   \textcolor{blue}{- It is for only one track (written in the caption).
+   - We dont understand your second question. A pad is a channel. Do you mean 
+how many pads are fired for a single track? Figure \ref{npd_track} shows the 
+number of active pads as a function of the momentum for the collected elastic 
+$^4$He tracks.\\
+- dE is calculated from the ADCs of the individual pads that read out hits 
+  corresponding to the same track. One needed to know the individual step size 
+  very precisely to put dEdx from the individual pads, which is not available.  
+  - Last question is addressed by figure \ref{npd_track}. The mean value is 
+    around 10 pads. }
 
-\item Figure 12 - please, put if after figure 11. Moreover, please change dEdx 
+\begin{figure}[h!]
+   \centering
+   \includegraphics[scale=0.45]{npd_p_elastic.png}
+   \caption{The number of active pads versus the measured momentum of the 
+   elastic $^4$He tracks. } \label{fig:npd_track}
+\end{figure}
+
+\item Figure 12 - please, put it after figure 11. Moreover, please change dEdx 
    to dE/dx on y axis. Why are the left and right pictures so different?  
@@
    the smear on the top part of the right picture. \\
-\textcolor{blue}{ }
+\textcolor{red}{- The figures layout will be updated.\\}
+
+\textcolor{blue}{- The y-axis label on figure 12 is updated.\\}
+\textcolor{blue}{- Regarding the lower peak in the left module of the RTPC, 
+   these events pass all the elastic requirements but for some reasons they 
+   have lower ADC values.  They represent around 7\% of all the elastic events.  
+   After extended studies, the nature of these particles is not identified yet.  
+   We note that this is a global phenomenon in the left module as 94\% of the 
+   left module's pads are involved in both some low and high dEdx events. For 
+   the calibration procedures, the events with low dEdx were excluded as we do 
+not fully understand their nature.}
 
@@
    times. Sum $dE_{i}$/Sum $dx_{i}$ is not equal to Sum ($dE_{i}/dx_{i}$).\\
-\textcolor{blue}{ }
+\textcolor{blue}{Maybe this would improve our calculations for dEdx by few 
+percent, but a precise hits ordering is needed to compute dEdx as you suggest, 
+which is not available in our setting.}
 

### 2017-11-06 eg6-letters/NIM/EG6_RTPC_NIM.tex
Starting on the review of NIM

@@
 up to 6 GeV energy and 100$\%$ duty factor to three experimental Halls (A, B, C) 
-simultaneously. The CLAS spectrometer~\cite{Mecking:2003zu}, located
+simultaneously. The CEBAF Large
+Acceptance Spectrometer (CLAS)~\cite{Mecking:2003zu}, located
 in Hall-B, was based on a superconducting toroidal magnet and composed of 
@@
 RTPC was designed to be as close as possible to the target and fit inside the 
-230~mm diameter shell and cryostat wall of the solenoid magnet bore.
+230~mm diameter shell and cryostat wall of the solenoid magnet bore of the 
+CLAS.
 
@@
 
-One of the important challenges in developing the RTPC was to obtain a good 
-support structure for the GEM foils to allow a tractable installation of the 
-GEMs. At the same time, we wanted to keep the material budget small in the 
-forward region where we detect other particles in subsequent detectors. We 
-successfully realized these prerequisites by using fiber glass rings glued to 
-each end of the GEM foils to form self supporting cylinders that could be 
+The main structural improvement compared to the 2005 RTPC~\cite{Fenker:2008zz} 
+was to obtain a better support structure for the GEM foils. In the previous version,
+the RTPC was essencially composed of two independent half-cylinder separated
+by their own structures. In these, the installation of the GEM was not very practical
+and wrinkles were visibles on the GEM surfaces. To allow for a better installation 
+and, at the same time, keep the mechanical structure out of the drift volume, 
+the present design is based on GEM cylinder. This improves the acceptance of the
+overall detector and reduces the material budget in the 
+forward region, where we detect other particles in CLAS. We 
+realized these cylinders by using fiber glass rings glued to 
+each ends of the GEM foils to form self supporting pieces that could be 
 installed independently in the RTPC after gluing and soldering operations. The 

### 2017-11-06 eg6-letters/NIM/review-1/review-1.tex
Starting on the review of NIM

@@
-%\documentclass[a4paper,11pt,twoside]{ThesisStyle}
 \documentclass[a4paper,11pt,twoside]{article}
@@
    when speaking the first time about GEM in the text.\\
-\textcolor{blue}{cylinderical GEMs-> semi-cylinderical. The reference has been added.}
+\textcolor{blue}{cylindrical GEMs-> semi-cylindrical. The reference has been added.}
 
@@
    maybe in a table, to make them evident.\\
-\textcolor{red}{To the group: Do we have such a comparison? }
+\textcolor{blue}{The main difference is in the design of the structure, this has 
+been made clearer in this chapter.}
 
@@
    GEM.\\
-\textcolor{blue}{- The target tube is the central z-axis of the detector. The 
-text is modified to make it clean.\\}
+\textcolor{red}{- The target tube is the central z-axis of the detector. The 
+text is modified to make it clean. Raph: He understands that, he asks what is the z position.\\}
 \textcolor{red}{- Regarding the electric field, it was 2.8 kV/cm in BoNuS, does 
-anyone know our exact field in this gap?\\}
-\textcolor{blue}{- The gain of such GEM configuration has been studied by 
-   CERN's Gas Detector Development Group (Fabio Sauli, Progress with the Gas 
-   Electron Multiplier, 2nd Workshop on Advanced Transition Radiation Detectors 
-   for Accelerator and Space Applications (Bari, Sept. 4-7, 2003), Nucl. Instr. 
-   and Meth. A522(2004)93). The results, see the reference, demonstrate that 
-one should not simply add gains to each other for multilayer GEM 
-amplifications.  We did not evaluate precisely the overall gain in our chamber, 
-so we do not have a value for our RTPC GEM system at this point.}
+anyone know our exact field in this gap? Raph: This is indicated already, I am not sure what he
+means by "induction gap"\\}
+\textcolor{red}{We did not evaluate precisely the overall gain in our chamber.
+Can we quote a value from comparison with Bethe-Heitler or GEANT4?}
 
@@
 \textcolor{red}{To the group: We do have radial and azimuthal drift velocities, 
-but we measure the average of their sum. }
+but we measure the average of their sum. Raph: What is the link with the question?}
 
@@
 the simulations?\\
-\textcolor{blue}{ }
+\textcolor{red}{Raph: I will modify the text for this.}
 
@@
    extremities?\\
-   \textcolor{blue}{This is a schematic to illustrate the definitions of 
+   \textcolor{red}{This is a schematic to illustrate the definitions of 
    $T_{min}$ and $T_{max}$ in a chain of hits. The figure can be modified if 
-needed.}
+needed. Raph: Are you asking him if he insists? We need to fix the figure.}
 

### 2017-11-07 eg6-letters/NIM/EG6_RTPC_NIM.tex
more updated to figure 6 and 7 and the target z position

--- 2017-10-18 eg6-letters/NIM/EG6_RTPC_NIM.tex
@@
 reduced the amount of material in the path of the outgoing particles. The enhanced design, 
-used in the 2009 DVCS experiment, is described in section \ref{sec_design} 
-of this paper. The 
-data acquisition system described in section \ref{sec_readout} was reconfigured 
-to increase the event readout rate. The calibration methods 
+used in the 2009 DVCS experiment, is described in section \ref{sec_design} of 
+this paper. The data acquisition system described in section \ref{sec_readout} 
+was reconfigured to increase the event readout rate. The calibration methods 
 are discussed in section \ref{sec_calib} and the tracking algorithm in section
@@
 \begin{itemize}
-  \item The 6~atm $^4$He target forms the detector central z-axis which is 
-     along the beamline ; it is a 284~mm long, 6~mm diameter Kapton straw with 
-     a 27~$\mu$m wall.
+  \item The 6~atm $^4$He target extends from -146~mm to 146~mm in z-direction 
+     with respect to the center of the detector forming the detector central 
+     axis. It is a 6~mm diameter Kapton straw with a 27~$\mu$m wall.
    \item The first gas gap covers the radial range from 3~mm to 20~mm. It is 

### 2017-11-07 eg6-letters/NIM/review-1/review-1.tex
more updated to figure 6 and 7 and the target z position

--- 2017-10-18 eg6-letters/NIM/review-1/review-1.tex
@@
    GEM.\\
-\textcolor{blue}{- The target tube is the central z-axis of the detector. The 
-text is modified to make it clean.\\}
+\textcolor{blue}{ The text has been modified to clarify the z position of the 
+target with respect to the detector.\\}
 \textcolor{red}{- Regarding the electric field, it was 2.8 kV/cm in BoNuS, does 
@@
    extremities?\\
-   \textcolor{blue}{This is a schematic to illustrate the definitions of 
-   $T_{min}$ and $T_{max}$ in a chain of hits. The figure can be modified if 
-needed.}
+   \textcolor{blue}{The figure is updated.}
 

### 2017-11-08 eg6-letters/NIM/EG6_RTPC_NIM.tex
edit the z position of the target

--- 2017-10-18 eg6-letters/NIM/EG6_RTPC_NIM.tex
@@
 \begin{itemize}
-  \item The 6~atm $^4$He target forms the detector central z-axis which is 
-     along the beamline ; it is a 284~mm long, 6~mm diameter Kapton straw with 
-     a 27~$\mu$m wall.
+  \item The 6~atm $^4$He target extends along the beamline forming the detector 
+     central axis; it is a 292~mm~long, 6~mm diameter Kapton straw with a 
+     27~$\mu$m wall. The detector and the target are centered at 64~cm to the 
+     left of CLAS's center.
    \item The first gas gap covers the radial range from 3~mm to 20~mm. It is 

### 2017-11-16 eg6-letters/NIM/review-1/review-1.tex
update the response to questions 18 and 21

@@
    is passed then a noise level is subtracted? If so, how is it calculated?\\
-\textcolor{red}{Nathan, Can you work on it. }
+\textcolor{blue}{The oscillatory noise was removed just by rejecting all hits 
+from a channel if too many of its hits fall on the noise curve in a given 
+event. No threshold/pedestal concept, just hit rejection if it looks like 
+noise. }
 
@@
    times. Sum $dE_{i}$/Sum $dx_{i}$ is not equal to Sum ($dE_{i}/dx_{i}$).\\
-\textcolor{blue}{Maybe this would improve our calculations for dEdx by few 
-percent, but a precise hits ordering is needed to compute dEdx as you suggest, 
-which is not available in our setting.}
+\textcolor{blue}{We actually did compute dEdx with  path-length and ADC- 
+truncations, and a linear fit to ADC vs path-length to get slope and fit 
+quality and dedx from fit. Unfortunately, it never seemed to give us much 
+improvement compared to Sum $dE_{i}$/Sum $dx_{i}$. }
 

### 2017-12-07 eg6-letters/NIM/review-1/review-1.tex
update the response to the NIM review

@@
 \textcolor{blue}{ The text has been modified to clarify the z position of the 
-target with respect to the detector.\\}
-\textcolor{red}{- Regarding the electric field, it was 2.8 kV/cm in BoNuS, does 
-anyone know our exact field in this gap?\\}
+target and the RTPC with respect to CLAS sectrometer.\\}
+\textcolor{red}{- Regarding the electric field in the induction gap, it was 2.8 
+kV/cm in BoNuS, does anyone know our exact field in this gap?\\}
 \textcolor{blue}{- The gain of such GEM configuration has been studied by 

### 2017-12-07 1st_round_comments/1st_round_comments_final/Jan31_2016_comments.tex
added the 1st round comments for the analysis note

This review is based on your 'First version of the Note'. Please put a date on 
successive versions (on the web page as well as on the Note cover page). You 
will find hereafter the comments from the three reviewers (after a round of 
discussions among us). There are some overlapping comments. We left them as 
such on purpose to reinforce the idea, but you may refer to an earlier answer 
in your answer to another reviewer.\\

There are many points to be addressed, but most of them should not take too 
much time. In short, what seems of particular importance to us is:\\
- A better explanation of the RTPC drift speed calibration and track 
reconstruction, and this may entail some rewriting.\\
- Explain from the start what the RTPC gain calibration is or is not used for 
and remove the first method which is not used in the end (or just allude to 
it).\\
- In several instances raised by the three reviewers, check results with 
tighter cuts. It does not necessarily mean that the end results should use 
tighter cuts (e.g. in z-vertex), but that this is a way to study systematic 
effects.\\
- The validity of some 'early' pid cuts (Cerenkov, z-vertex, ...) should be 
checked after exclusivity cuts (for both coherent and incoherent).\\
- The question of accidentals (especially in e-4He coincidences) needs to be 
addressed.\\
- The question of physical background other than exclusive pi0 should be 
discussed, at least qualitatively.\\
This is not to say that the other points are to be dismissed ....

\section*{\centering{$1^{st}$ reviewer}}

~~~~I first have to say that this is of course an unusually complicated and 
difficult analysis (even by CLAS standards) because of the many idiosyncrasies 
concerning the RTPC. Many students and other members of the EG6 collaboration 
have spent an enormous amount of time trying out all kinds of improvements and 
analysis methods, so it would seem like double jeopardy to also insist on an 
equally voluminous tome to describe the analysis. However, I do feel that the 
present version is missing quite a few details that are important for us to 
fully understand what was done, to assess whether it was done 'well enough' and 
to give our green light to the analysis.\\

1) Eq. 2.1, p.16: The second row is missing the charge, q, in front of Bz. This 
is not trivial, as the next 3 lines contain numerical examples that seem to be 
wrong. For instance, the range in $r_{0}$ quoted for DVCS is 20 - 45 mm - but I 
find a radius of 100 mm for 260 MeV/c 4He nuclei going radially (q = 2e). Even 
at some angle, 20 mm is impossible - such a track would never make it through 
the drift region. (Fig. 2.7 shows a minuscule pedestal below $r_{0}$ = 25 mm, but 
this must be due to some spurious effect - I don't see how you can reconstruct 
any tracks with $r_{0}$ < 30 mm). Is this mistake in your software as well (see 
horizontal scale in Fig. 2.7)?\\
\textcolor{blue}{
   In equation 2.1, the charge of the particle (q) is missed. Regarding the 
numerical calculations of $r_0$ for the elastic and the DVCS $^4$He, the 0.3 
factor is missed only in these calculations while the charge issue is taken 
into account. In the reconstruction software, both issues are properly 
implemented.  (For example, In a magnetic field of 4.5 T, the recoil 4He nuclei 
from DVCS (elastic) reaction have kinetic energies in the range [10, 25] ([17, 
35]) MeV, from momenta of [260, 450] ([360, 550]) MeV and $r_0$ [70, 150] 
([130,180]) mm.) }\\

2) Section 2.2: The RTPC calibration procedure is described in 2 steps: Event 
selection (2.2.1) and actual calibration (2.2.2 - 2.2.4) plus noise rejection 
(2.2.5). However, the event selection contains cuts on $r_0$, chi2, z etc.  
which in turn presuppose some initial calibration already. In other words, the 
process MUST be iterative - but I couldn't find a clear summary how this 
iteration was executed (i.e., what was used for the first iteration, how many 
iterations total, etc.). There is a short mention at the bottom of p. 27, but 
no details.\\
\textcolor{blue}{The drift paths and drift speed were first extracted using the 
MAGBOLTZ Monte Carlo simulation. One can find the detailed procedure of 
this first extraction in the BoNuS analysis note 
(https://www.jlab.org/Hall-B/secure/bonus/publication/BonusAnal110117.pdf).  
Then, we proceeded to derive empirical improvements with many iterations after 
each change that would affect the drift paths, such as the beam-offset
 and gain calibrations of the RTPC. Moreover after each pass, the number of
elastic events used for calibration increased. Overall, this was a long 
process that evolved and improved over the years and we concentrated in the 
note on the description of the final iteration.}\\

3) 2.2.1.1 It would be helpful to have some more background information: What 
is the longest drift time (from the inner radius) for a good track? What kind 
of momentum gives you only 4 hits, and are those events important? (see further 
down, under Fig. 3.19) What is the timing offset between the trigger and the 
shortest drift time (outer radius RTPC)? What is the average drift velocity and 
Lorentz angle? Conversion TDC-> time is given p. 15, but it would be much more 
helpful to have all these basic parameters collected in a single place: 2.1.1 - 
2.1.3 are all good places to summarize these parameters.\\
\textcolor{blue}{
  The longest drift time depend on $z$ but is typically around 6.6 $\mu$s. 
  Four is the number of the fired pads for each track, not the number of hits.  
  This value has been found to be reasonable from simulation, it mainly help 
  clean the sample and play very little role after other cuts. The time offset 
  is 15 TDCs (1 TDC= 114 ns), the average drift velocity is 6.14 $\mu$m/ns and 
  we did not extract the Lorentz angle, but MAGBOLTZ indicated about 20 
  degrees.}\\

4) 3rd bullet: There should also be an upper limit on $r_0$, since it is 
actually $r_0$ = +infinity that is indistinguishable from $r_0$ = -infinity 
(i.e., charge will be unknown). For the same reason, it would be nice to have a 
plot of $1/r_0$ instead of or in addition to Fig. 2.7 \\
\textcolor{blue}{Figure \ref{fig:1overr0} shows the 1/$r_0$
   distribution for a sample of the 1.2 GeV data for all the reconstructed 
   tracks without any requirement. Figure \ref{fig:good_r0} presents the same 
   distribution after requiring reading from at least 4 pads, $sdist$ and 
   $edist$ cuts. We see in figure \ref{fig:good_r0} that selecting 
   $r_0>0$ is already cutting the tail of the distribution. Applying a cut for 
   large $r_0$ would correspond to applying a cut at a larger $1/r_0$. Based on this
   distribution, we do not see any motivation for this. In particular since exclusivity
   cut will eventually clean all unphysical results.}\\
%  \textcolor{red}{Raph: Follow up on p49 bullet 4 of the note, you speak about 
   %  "the  mechanical supports between the two model of the RTPC". Beyond the 
   %  English, I remind you that there is not mechanical structure inside the 
   %  drift region in the eg6 RTPC. Please correct!} \\

\begin{figure}[tbp]
\hspace{-1cm}
\begin{minipage}[c]{.46\linewidth}
\includegraphics[height=6.5cm]{fig/rtpc_1overr0_all_before.png}
\caption{1/$r_{0}$ for all the reconstructed tracks in the RTPC using 1.2 GeV 
electron beam.}
\label{fig:1overr0}
\end{minipage} \hfill
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.1in}\includegraphics[height=6.5cm]{fig/rtpc_1overr0_all.png}
\caption{1/$r_{0}$ for tracks that passed the requirements: reading from at 
least 4 pads, $sdist$ and $edist$.}
\label{fig:good_r0}
\end{minipage}
\end{figure}

5) 4th bullet: How are the points $r^{helix}$, $\phi^{helix}$ and $z^{helix}$ 
determined?  Somehow, you have to identify points on a continuous line that are 
closest to (perhaps) the hits? How are the uncertainties (sigmas) in  
$\chi^{2}$ determined?  Are those the final values AFTER calibration? If so, 
how do you select your sample initially? (See above - it must be an iterative 
process).  \\
\textcolor{blue}{$(r^{helix},\phi^{helix},z^{helix})$ is the point
on the helix that is closest to the reconstructed hit position.
The values of the uncertainties are intrinsic detector properties depending
primarily on the size and configuration of the readout pads. These 
uncertainties, $(\sigma_{r}, \sigma_{\phi}, \sigma_{z}) = (0.53 mm, 2^{\circ}, 
1.2 mm)$, were not derived from our data and were held fixed.} \\

\textcolor{blue}{Equation 2.2 needs the beam-spot constraint added in
quadrature $\left(\frac{DOCA}{\sigma_r}\right)^2$ and the denominator adjusted
accordingly $(N_{pts}-5)$. It has to be written in full form as: (changed in 
the note as well).  }\\

\textcolor{blue}{
\begin{equation}
   \chi^{2} = \frac{\displaystyle \left(\frac{DOCA}{\sigma_r}\right)^2 
       + \sum_{i = 1}^{ N_{pts}} \left(\frac{r^{pt}_{i} 
      - r^{helix}_{i} }{\sigma_{r}}\right)^{2}  + \left( \frac{\phi^{pt}_{i} - 
      \phi^{helix}_{i} }{\sigma_{\phi}}\right)^{2} + \left( \frac{z^{pt}_{i} - 
      z^{helix}_{i} }{\sigma_{z} } \right)^{2}}{N_{pts} - 5}
\end{equation}
}\\
%  \textcolor{green}{Raph: I did a minor change in the equation, to clarify 
%  that the beam spot term is not in the sum. To use in the note if you are 
%  ok.} \\

6) 5th bullet: Again, $sdist$ and $edist$ already pre-suppose a timing 
calibration.  For assessing possible accidental coincidences (see more below), 
it would be useful to know what time spans correspond to the limits chosen on 
them.\\
\textcolor{blue}{ $sdist$ limits span a drift time equal to 0.68 $\mu s$, while 
$edist$ limits span 1.03 $\mu s$.}\\

7) Finally, I'm puzzled by the large positive limit on $edist$ - supposedly this 
quantity is easier to measure (shortest 'drift' time), yet there is clearly a 
tail towards positive $edist$ (towards smaller radii??) superimposed on an 
otherwise sharp peak. Wouldn't you want to cut that tail at least for the 
purpose of calibration, to make sure you only look at 'golden tracks'? Is it 
specific to higher momenta? \\
 \textcolor{blue}{
The positive long tail on $edist$ distribution is made of hits out of time 
mostly due to electronic noise. However, if we do not apply any constraint on 
$edist$ and $sdist$ variables and select the elastic He-4 tracks with the other 
cuts, we observe that most of the tails are removed as can be seen in the 
figure~\ref{fig:sdist} and \ref{fig:edist}. Therefore, making tighter cuts 
would not cause changes in the calibration as the tracks in the tail regions 
are cleaned by the other cuts.  No correlations was observed between the tails 
and the momentum, as can be seen in figure~\ref{fig:edistp}.}\\

\begin{figure}[!h]
\begin{minipage}[c]{.46\linewidth}
\includegraphics[height=6.5cm]{fig/sdist_elastic_1p2GeV.png}
\caption{sdist distribution for the selected elastic $^{4}$He tracks.}
\label{fig:sdist}
\end{minipage} \hfill
\begin{minipage}[c]{.46\linewidth}
\hspace{-0.1in}\includegraphics[height=6.5cm]{fig/edist_elastic_1p2GeV.png}
\caption{edist distribution for the selected elastic $^{4}$He tracks.}
\label{fig:edist}
\end{minipage}
\end{figure}

\begin{figure}[!h]
\centering
\includegraphics[height=6.2cm]{fig/edist_poverq_elastic_1p2GeV.png}
\caption{edist as a function of the measured p/q for the selected elastic 
tracks.}
\label{fig:edistp}
\end{figure}

8) Last bullet: Again, what are the initial choices on this cut to select 
calibration tracks? What do you use for the $z_0$ of the simulated track?  \\
\textcolor{blue}{
   We used similar cuts for all the calibration iterations. $z_0$ of the 
simulated $^{4}$He is set to be the z-vertex of the scattered electron. The 
2$\sigma$ cut corresponding to $\approx$ 20 mm.  }\\

9) 2.2.1.2 Again, these cuts already pre-suppose (good enough) initial tracks.  \\
\textcolor{blue}{Yes}\\

 10) Fig. 2.11: Do we understand why $\Delta z$ is not constant? Is this before 
or after the RTPC alignment (alluded to but not explained)? Is the resolution 
shown the final result after optimizing the calibration? The exact same 
questions also arise for Fig. 2.12. \\
\textcolor{blue}{
  The presented $\Delta z$ and $\Delta\phi$ distributions are after all the 
calibration and detector alignments (RTPC alignment is described in CLAS-NOTE-2013-008).
The observed remaining dependences are not fully understood and probably arise
from field misalignement and variations in the electric and magnetic fields
within the chamber.} \\

11) Eq. 2.4: It is much better to use a cut on the reconstructed beam energy 
from the measured angles $\theta_e$ and $\theta_{He}$, since momenta are less 
precisely measured by CLAS than angles. Peter Bosted has used this method very 
effectively. Indeed, Fig. 2.13 shows a rather broad distribution, with a cut 
that barely has any effect. (This is a side comment, not meant to require 
additional work).\\
\textcolor{blue}{We are indeed aware of this, this is why we do use theta cut
as our main selection. Note also that $\delta\phi$ and $\delta z$ cuts have already
been applied in Figure 2.13's $\delta\theta$.}\\

12) Fig. 2.14: It's curious that the W distribution 'for the right RTPC module' 
is wider than on the lhs, given that nothing measured by the RTPC enters this 
quantity. However, it might be that the corresponding sectors in CLAS have 
different resolution, as well.\\
\textcolor{blue}{
Yes, this is related to the different resolutions of the corresponding CLAS sectors. 
This effect is large because, the reaction products are produced back to back 
results in small regions of overlapping acceptances of the RTPC and CLAS.  
In figure \ref{fig:W_sec}, we plot $W$ distributions corresponding to the 
different sectors in CLAS, one can immediately see the differences of resolution. }\\

\begin{figure}[!h]
   \centering
   \includegraphics[height=10.5cm]{fig/W_dis_sectors.png}
   \caption{W distributions for the identified good tracks (in blue) and 
   elastic events (in shaded brown) where the electron scattered in the 
different sectors of CLAS.}
   \label{fig:W_sec}
\end{figure}

- 2.2.2 2nd paragraph: Due to the varying B(z) and therefore the varying 
Lorentz angle, the drift path is NOT the same for all electrons at all z.  
(Corrected in the 3rd paragraph.)
More importantly, all times are given in TDC units instead of $\mu$s- we must 
know the conversion factor and the offset! (Is it the same for all TDC 
channels?)\\
\textcolor{blue}{1 TDC = 114 ns, the time offset is TDCmin (= 15 TDCs) and is 
the same for all the readout channels.}\\

13) Fig. 2.19: I can't figure out what exactly is plotted here (in particular 
on the z-axis). If I understand Eq. 2.8 correctly, then R is simply deduce from 
TDC for the real data - so no surprise to see a straight line. How is this then 
linked to the simulated track?\\
\textcolor{blue}{Here R is from simulation and TDC is from real data. This 
figure is indeed here only to illustrate the Eq 2.8 and allows to associate
simulated hits with measured ones. The text is modified to clarify this 
point.}\\

14) Figs. 2.20-22: Again, more detail needed to understand what's plotted and 
how it is calculated. Why is Delta-phi not zero for TDC = 15 (which corresponds 
to the outer radius of the drift region)?- Eq. 2.9: A (brief) derivation would 
help a lot here.\\
\textcolor{blue}{
$\Delta \phi$ at the anode (TDC = 15) is not equal to zero because there is a 
drift in phi between the anode (the first GEM layer at radial distance equal to 
60 mm) and the readout pads (at radial distance equal to 69mm). Regarding the 
derivation, figure \ref{fig:drift_derive} shows a simple drawing explaining how 
Eq. 2.9 has been derived.}\\
\textcolor{green}{Raph: Equations in the drawing need to be replaced by text.}

\begin{figure}[!h]
   \centering
   \includegraphics[height=12.5cm]{fig/drift_draw.png}
   \caption{Schematic drawing shows how the radius of emmision (R) at each 
   ionization point is calculated from the drift paths ($\Delta \phi$) and the 
drift speed ($DS$).}
   \label{fig:drift_derive}
\end{figure}

15) 2.2.4: Eq. 2.12 is differential, while Eq. 2.14 is integrated over the 
whole track. Do you integrate Eq. 2.12? Otherwise, it probably doesn't work all 
that well. Maybe this is the reason why the bands visible in Fig. 2.29 are not 
well represented by the superimposed curves? BTW, what is the vertical scale on 
Fig. 2.29?\\
\textcolor{blue}{Eq. 2.14 represents the average energy loss per unit of length in the 
track, $vtl$ being the visible track length. Assuming the energy loss in the 
drift region small, the two can be easily compared. Indeed at the lowest energy 
this assumption is not true anymore. But the difference between instantaneous 
and average $\frac{dE}{dx}$ is expected to be small compared to our 
resolution except very close to threshold (see right panel of Figure 
\ref{fig:energylosscorrection}).}
\textcolor{blue}{In Fig. 2.29 the bands are just there to guide the eye. Since the
vertical scale has never been carefully calibrated, we always present it in
arbitrary units. To have a feeling of the units, we have extracted an over all 
conversions from comparing real data to simulation, where 1 ADC is equal to 17 eV 
(21 eV) deposited in the left (right) module of the RTPC.} \\

16) p. 29, 2nd to last paragraph: I THINK I understand the Landau fit (over 
many tracks, no?) for each channel. But I don't understand the last step - why 
is it needed? What does it accomplish? For sure more details (and a plot) are 
needed.\\
\textcolor{blue}{
Yes, the gain ratio of each readout pad is calculated from comparing all the 
experimental elastic tracks to their corresponding tracks obtained from 
simulation. These ratios give us a first gain for each readout pad. However, 
we noticed that some pads record lower ADCs than expected (issue shown in 
figure 2.28) and noise. For these reasons, we wanted to make sure that the recorded 
ADCs by a given pad are similar to the recorded ADCs recorded by another pad in 
the same track. In figure~\ref{fig:dedxre}, one can see improvements obtained
by using this method to fine tune the gains obtained previously.} \\

\begin{figure}[!h]
\hspace{-0.5 cm}
\includegraphics[height=11.5cm]{fig/dedx_ratio_elastic.png}
\caption{The ratio between experimental dEdx and 
the simulated ones for different regions along $z$ of the RTPC. The blue lines 
are using the first method of extracting the gains (comparing the experimental 
recorded dEdx to the expected values calculated from the Bethe-Block formula), 
the violet lines are using the second method with a small fraction of our 
elastic events, the green lines are using the 1st pass of the second method 
(comparing simulation to data only) with all the elastic event sample and the 
brown lines are using the gains extracted from the second method (both steps).}
\label{fig:dedxre}
\end{figure}

17) p.31, last paragraph: Could it be that the low-signal tracks are due to 
protons (maybe elastically scattered out of the Kapton target enclosure)? There 
could be some beam halo interacting with the straw tube. Last sentence (top 
p.32): HOW are 'events from the low-region' excluded from the analysis (for 
NON-elastic events)? Do you use a cut on dE/dx? Describe the cut! (It's not 
mention in Section 3.1.4 - but why bother with gain calibration if you don't 
use the ADC values?)\\
\textcolor{blue}{More work is needed to understand the nature of these 
low-signal tracks, but they cannot be protons as their dedx would be much smaller,
and they are only present in one half of the RTPC.  We looked hard but found no
correlation between these tracks and any other experimental quantities.
A possible explanation is that the gain might have been periodically
lowered by high rates of events. For this DVCS analysis we do 
not use $\frac{dE}{dx}$ to select $^4$He, instead we only use the DVCS 
exclusivity cuts.
Figure \ref{fig:dedx_good_6gev} shows dEdx as a function of $p/q$ 
for the good tracks from 6 GeV beam energy runs, while Figure 
\ref{fig:dedx_dvcs_6gev} shows the same for identified coherent DVCS He-4 
nuclei. One can see that the selected He4 nuclei have on average high dEdx 
trend that matches with the theoretical line, 
but the band seem too wide to apply a significative cut.} \\

\begin{figure}[tbp]
\hspace{-1.0cm}
\includegraphics[height=6.2cm]{fig/dedx_p_Coh_l_good.png}
\includegraphics[height=6.2cm]{fig/dedx_p_Coh_r_good.png}
\caption{dEdx verus $p/q$ distribution for the good tracks collected at 6 GeV 
beam energy.}
\label{fig:dedx_good_6gev}
\end{figure}

\begin{figure}[tbp]
\hspace{-0.1cm}
\includegraphics[height=6.2cm]{fig/dedx_p_Coh_l_dvcs.png}
\includegraphics[height=6.2cm]{fig/dedx_p_Coh_r_dvcs.png}
\caption{dEdx verus $p/q$ distribution for the identified He4 DVCS nuclei at 6 
GeV beam energy.}
\label{fig:dedx_dvcs_6gev}
\end{figure}

18) 2.2.5: 3rd line, the claim is made that elastic 4He produce too small a 
signal because of their small Tkin. This is strange, since low Tkin actually 
means LOTS of energy LOSS - which is also born out by Fig. 2.29. Overall, it 
would be good to get a quantitative feeling for the amplitude of the noise (in 
mV and in equivalent dE/dx relative to good 4He tracks). It would be even 
better if we had any inkling about the source of the noise (electronics 
malfunction? cross-talk? antenna pick-up?), but of course that's not a 
requirement for the analysis to be approved. \\
\textcolor{blue}{
The statement about too small Tkin is misleading and has been changed.
The fact is that readout thresholds were set low to avoid efficiency problems,
with the effect of recording more electronic noise. We do not know where the noise is
coming from, only speculation. As for getting a feeling of the
amplitude of the noise, one option is to compare Figures 2.30 with 2.25 and/or
2.28 top. This shows that the amplitude of the oscillatory noise is not much
smaller than the typical hits from a $^4$He track.}\\

19) Fig. 2.30: What is plotted on the z-axis? (Occupancy?) Is this plot 
integrated over all 'good tracks', or only for tracks that actually traversed 
the selected pad (or a nearby pad)? If the former, what does a signal for a 
good track that crosses this pad look like?\\
  \textcolor{blue}{The color scale on the $z$-axis is a hit yield. The
hits included are only those recorded by one example noisy pad and only when
those hits were also included in a good track.} \\

20) 2.3: 5th line p. 37: No, the z-vertex resolution for an extended target in 
the presence of the DVCS solenoid is a lot worse than 1 mm - see Fig. 3.1 So in 
fact the z-resolution of the RTPC is not that bad.\\
 \textcolor{blue}{Indeed the indicated value is without solenoid. In the presence of 
the solenoid, the z-vertex resolution of 
CLAS is about 3 mm, which we measured from the downstream target 
window, as can be seen from figure \ref{fig:z_electron_res}.}\\

\begin{figure}[tbp]
\centering
\includegraphics[height=6.2cm]{fig/clas_z_resolution.png}
\caption{ z-vertex of scattered electrons at 6 GeV beam energy from the 
downstream window of the target. The z-vetex resolution of CLAS here is about 3 
mm.}
\label{fig:z_electron_res}
\end{figure}

21) Fig. 2.37: Clearly, momenta are shifted 10$\%$ lower on average. This is 
not surprising, since at low momentum, energy loss will reduce the 
reconstructed radius of the helix. However, since the 4He momentum enters 
various cuts, we need a better understanding of Deltap/p as a function of p and 
theta, e.g. through 2D plots like Figs. 2.11-2.13. Of course it would be even 
better to CORRECT p for energy loss and other effects - but Section 3.3 doesn't 
mention any kinematic corrections for 4He. (I don't insist on this, but the 
effect on the 'true exclusivity' of the final cuts should be discussed.\\  
\textcolor{blue}{We do in fact correct for energy loss. The correction is 
calculated from energy loss in GEANT between the primary electron vertex and
the midpoint of the drift region. This correction was parameterized in terms 
of $(p,\theta)$ and particle type, it was validated by hand-integrating 
Bethe-Bloch formula. The left panel of Figure \ref{fig:energylosscorrection} 
shows our energy correction for a few polar angles. 
The following plots, \ref{fig:delta_p_p} and \ref{fig:delta_p_theta}, 
show that the momentum shift after the energy correction 
as a function of the measured momentum is still present. One could deduce
that our energy loss correction is not strong enough however 
no correlation is observed with the measured polar angle, which
should be expected if the mismatch was due to energy loss. Different
unidentified issues are probably at the origin of this problem.}\\
\textcolor{blue}{We decided to test corrections based on the z-dependence shown
in figure \ref{fig:delta_p_z}. Figure \ref{fig:P_diff_z_correction} shows the 
difference between the elastic 4He momentum the values from electron scattering 
angle. A second test was performed by doubling the energy loss, which gives 
correct momentum.  When applied on He4 DVCS, as shown in figure 
\ref{fig:dvcs_mom_corr}, we see a deterioration of the missing transverse 
momentum. We conclude that the momentum shift comes from more complicated 
effects linked to angles and possibly other experimental conditions and cannot 
be simply corrected
by a scale factor.}\\

\begin{figure}[tbp]
   \centering
   \includegraphics[height=6.2cm]{fig/eg6eloss_4He_rot.png}
   \includegraphics[height=6.2cm]{fig/Biasbb_alpha.png}
   \caption{On the left is the energy loss correction (in terms of momentum)
   derived from full simulation for $^4$He and a few relevant polar angles, where
   the $x$-axis is momentum at the primary vertex.  On the right is the relative
   difference between the instantaneous $^4$He $\frac{dE}{dx}$ at the midpoint of the
   drift region and averaged over the drift region, where the $x$-axis is the average
   momentum in the drift region.  The maximum path length at 40$^\circ$ is about 50 mm.}
   \label{fig:energylosscorrection}
\end{figure}

\begin{figure}[tbp]
\includegraphics[height=6.2cm]{fig/delta_p_p_elastic_l.png}
\includegraphics[height=6.2cm]{fig/delta_p_p_elastic_r.png}
\caption{$\Delta$p/p as a function of the p for the identified elastic He4 at 
1.2 GeV electron beam.   }
\label{fig:delta_p_p}
\end{figure}

\begin{figure}[tbp]
\includegraphics[height=6.2cm]{fig/delta_p_theta_elastic_l.png}
\includegraphics[height=6.2cm]{fig/delta_p_theta_elastic_r.png}
\caption{$\Delta$p/p as a function of $\theta$ for the identified elastic He4.}
\label{fig:delta_p_theta}
\end{figure}

\begin{figure}[tbp]
\includegraphics[height=6.2cm]{fig/delta_p_z_elastic_l.png}
\includegraphics[height=6.2cm]{fig/delta_p_z_elastic_r.png}
\caption{$\Delta$p/p as a function of z-vertex for the identified elastic He4.}
\label{fig:delta_p_z}
\end{figure}

\begin{figure}[tbp]
   \centering
   \includegraphics[height=6.2cm]{fig/P_diff_z_correction.png}
   \caption{$\Delta$p/p without any corrections (in black), after energy loss 
   corrections (in blue), from simulation (in green), and after the corrections 
extracted based on the z-dependence (in red) on top of the energy loss 
corrections.}
   \label{fig:P_diff_z_correction}
\end{figure}

\begin{figure}[tbp]
   \centering
   \includegraphics[height=6.2cm]{fig/Coh_e4Hegamma_PT_Mis.png}
   \caption{The missing transverse momentum for the identified coherent DVCS 
      events, after applying only the energy loss corrections (in blue), 
      doubling the energy loss corrections (in black), and after applaying the 
   extracted momentum correction form the z-dependence.}
   \label{fig:dvcs_mom_corr}
\end{figure}

22) Section 3.1: p. 40, 1st bullet: In DIS and SIDIS, the pe cut is supposed to 
remove events with large radiative effects due to photon radiation followed by 
elastic scattering. Here, this is actually part of the signal (interference of 
BH and DVCS). So, the cut should instead be chosen to lie just above the 
hardware trigger threshold of the EC, to avoid fluctuating values for this 
threshold to influence the electron sample.\\
\textcolor{blue}{The explanation in the note is wrong. This cut is applied to 
   eliminate low momentum electrons because during the data acquisition, the EC 
   threshold was set to 200 mV corresponding to electrons having a minimum 
momentum of about 0.7 GeV/c. In this analysis, we applied a conservative cut of 
0.8 GeV/c to be above this threshold.}\\

23) Fig. 3.8: Any explanation for the second 'bump' right above 2 nphe? 
Similarly, the 'green curve' which is really red shows a steep edge, again at 
nphe=2. Are there any other cuts applied before this plot, e.g. exclusivity or 
Osipenko?\\
  \textcolor{blue}{The ``peak'' visible in Figure \ref{fig:nphe_1} above 2 
nphe is the tail of the single photo-electron peak. 
The supression at 1.5 nphe is just an effect of the trigger and creates the 
artificial appearance of a peak just above 2 nphe when only loose cuts are 
applied.}\\

\begin{figure}[tbp]
\centering
\includegraphics[height=9.2cm]{fig/nphe_1_sectors.png}
\caption{Distribution of nphe emitted by electrons in the six sector of CLAS 
before the CLAS trigger change at run 61732.}
\label{fig:nphe_1}
\end{figure}

24) Fig. 3.9: Seems superfluous - it doesn't show anything new and doesn't 
contain all the fiducial cuts.\\
 \textcolor{blue}{Removed.}\\

25) p. 45 bottom: Are there any fiducial cuts to remove dead regions? Why 
not?\\
\textcolor{blue}{They are not implemented in this analysis as we deemed them
insignificant for this low statistics asymmetry measurement, particularly since
RTPC efficiency already shows a good agreement between LEFT/RIGHT in elastic scattering even
without removing dead regions (see answer to R1Q28 below and Figure~\ref{fig:tpceff}).}\\

26) Fig. 3.15: This may be my ignorance, but it looks like there is a 
secondary 'bump' between beta =0.9 and 1. What could it be? If it's neutrons, 
wouldn't that contribute to your background?\\
\textcolor{blue}{We seem to disagree there is a significant bump. However, if 
   there are some neutrons, they will be well removed by the following 
   exclusivity requirements. Also we want to point out the energy of the 
   neutral particle we use are greater than 2 GeV.  At such energies the time 
   of flight measurement from the EC is not good enough to separate neutrons 
   from photons anyway (see Fig.  \ref{fig:sim_coh} and 
\ref{fig:sim_incoh}).}\\

27) Bottom p.47: Indicate that the threshold on IC discris towards TDC has been 
too high to be useful and/or the flight path is too short to apply a beta cut 
as in EC.\\
\textcolor{blue}{
 The timing of the IC has is not functionning properly for certain channels. Therefore, 
 applying a timing cut would add inefficient regions in the detector that we 
 wanted to avoid. Moreover, the comment from previous answer applies as well,
such a cut would be very little help to reduce backgrounds at such high particle energies.}\\

28) Fig. 3.19:  The lhs of the RTPC apparently has only 1/2 the efficiency of the 
rhs. Is there any good explanation (at least qualitatively)? This could 
potentially distort phi-distributions, no? \\
\textcolor{blue}{This plot contains no good
   track cuts and so say very little about the efficiency. In more details, 
   This difference in the yield should not be linked to a different performance 
   of the RTPC.  They are due to the complicated convolution of CLAS and the 
   RTPC acceptance.  We measured the efficiency of RTPC using elastic 
scattering, and found that the left/right halves have similar efficiencies 
except near the upstream and downstream ends, as shown in 
Figure~\ref{fig:tpceff}.} \\

\begin{figure}[tbp]\centering
  \includegraphics[width=8cm]{fig/tpceffyields.png}
  \includegraphics[width=8cm]{fig/tpceff.png}
  \caption{On left is the inclusive and exclusive elastic yields separated into 
     the two RTPC halves (LEFT/RIGHT).  Here the inclusive yields are the 
     number of electrons in the elastic W-peak (e.g.\ Fig.~\ref{fig:W_sec}) 
     whose corresponding elastically scattered $^4$He would have been in the 
     acceptance of the RTPC, and the exclusive yields require the additional 
     detection of the $^4$He.  The large LEFT/RIGHT differences in CLAS 
     acceptance for elastic kinematics are clear in the inclusive yields.  On 
     right is the RTPC $^4$He efficiency calculated from the ratio of exclusive 
     and inclusive elastic yields.  (Here LEFT/RIGHT is from the beam's 
     perspective, i.e.  beam-LEFT/beam-RIGHT)\label{fig:tpceff}}
\end{figure}

29) bulleted list p. 48-49, Bullet 2: Would be nice to see a distribution of 
number of active pads vs. p (but not necessary).\\
\textcolor{blue}{It is added and shown here in Fig. \ref{fig:padnb} as well.}\\

\begin{figure}[tbp]
\centering
\includegraphics[height=6.2cm]{fig/npd_p_elastic.png}
\caption{The number of active pads versus the measured p/q for the good tracks 
collected using 1.2 GeV electron beam.}
\label{fig:padnb}
\end{figure}

30) As asked before: Why is there no PID cut at all? (E.g. Signal height vs.  
p)\\
\textcolor{blue}{We claim that kinematic exclusivity cuts are sufficient to
cleanly select coherent $^4$He DVCS events without the need for $\frac{dE}{dx}$ 
cuts. We performed few checks regarding applying a PID cut, where the full data 
was analyzed in the following three sets:\\
1. Processing all the reconstructed tracks in each event with the exclusivity 
cuts.\\
2. Processing events with only one good track in the RTPC being 
reconstructed.\\
3. Processing events with only one track that passes a dedx cut.\\
The results are shown in figure \ref{fig:all_incoh_exc_cuts} in terms of the 
exclusive variables for the identified coherent DVCS events. One can see that 
applying a PID cut would only change the statistics and not the width of 
distributions. On the other hand, figure 
\ref{fig:coh_alu_PID} shows a comparison between the reconstructed beam-spin 
asymmetries with and without applying a PID cut. The two sets 
of asymmetries are compatible within the given statistical error bars.
From these two observations, we deduce that a PID cut on the Helium would
not reduce any background contribution.}\\

\begin{figure}[tbp]
   \hspace{-0.5cm}
\includegraphics[height=14.2cm]{fig/all_incoh_exc_cuts.png}
\caption{Distributions of the exclusive variable for the identified DVCS events 
with only one track in the RTPC (blue), one track and PID1 is equal to 47 
(red), and processing all the tracks in each event with the exclusivity 
variables (black).}
\label{fig:all_incoh_exc_cuts}
\end{figure}

\begin{figure}[tbp]
   \centering
\includegraphics[height=8.2cm]{fig/Coh_ALU_W_out_PID.png}
\caption{The integrated coherent beam-spin asymmetries as a function of 
$\phi$ with (red) and without (blue) applying a PID cut on Helium tracks.}
\label{fig:coh_alu_PID}
\end{figure}

31) Also asked before: What coincidence time window do the $edist$ and $sdist$ 
cuts translate into? This is relevant for accidental coincidences. Fig. 3.23 
indicates clearly that there is an uncorrelated (in z) background from those!  
Yet, there seems to be no discussion of accidental coincidences at all.\\
\textcolor{blue}{For $edist$ and $sdist$ part, it is answered previously in 
comment 6.}\\

\textcolor{blue}{ Regarding the background, figure 
\ref{fig:delta_z_after_exclusitivty} shows $\Delta z$ distributions of the 
identified Coherent DVCS events after applying the exclusivity cuts without any 
initial constrain on $\Delta z$.}\\

\begin{figure}[tbp]
\centering
\includegraphics[height=6.2cm]{fig/rtpc_delta_z.png}
\caption{The z-vertex correspondence between the scattered electron and the 
recoil He4 for the identified coherent DVCS events after the exclusivity cuts 
in the two modules of the RTPC separately. Table \ref{table:Events_numbers} 
summarizes the cut numerically. }
\label{fig:delta_z_after_exclusitivty}
 \end{figure}

\begin{table}[!h]
   \centering
   \begin{center}
      \begin{tabular}{|l|l|l|}
         \hline
         \multicolumn{3}{ |c| }{Number of coherent DVCS events} \\
         \hline
         $\Delta z$ [mm] & Left module & Right module\\
         \hline
         [-50:-20] & 165 & 132 \\
         \hline
         [-20:20]  & 2736 & 2828\\
         \hline
         [20:50]   & 78 &  166 \\
         \hline
         Total     & 2979  & 3126 \\
         \hline 
      \end{tabular}
      \caption{The numbers of the identified coherent DVCS events in the 
      different regions in $\Delta z$ for the two modules of the RTPC.}
      \label{table:Events_numbers}
   \end{center}
\end{table}

32) 3.2: Does the generator contain any kind of implementation for the spectral 
function ('Fermi motion') of the proton in 4He? \\
 \textcolor{blue}{ Yes, the 
Fermi motion is implemented based on the parameterization of  C.~Ciofi~degli 
Atti and S.~Simula (PRC 53 (1996) 1689). Figure \ref{fig:fermi_motion} shows 
the proton initial momentum we used. We cut the high-momentum tail 
at 300 MeV/c, higher momentum should not contribute to the final sample 
because of our exclusivity cuts.} \\

\begin{figure}[tbp]
\centering
\includegraphics[height=6.2cm]{fig/fermi_momentum_dis.png}
\caption{Fermi momentum distribution for nucleons inside $^{4}$He in GeV/c.}
\label{fig:fermi_motion}
 \end{figure}

33) You mention, in 3.2.5, that the RTPC is not implemented in GSIM. Does this 
include the materials as well? If those are not in GSIM, you might 
underestimate multiple scattering and energy loss of electrons and, 
particularly, outgoing protons.\\
\textcolor{blue}{No the material of the RTPC is implemented in GSIM,
however it is only considered as dead material and the detection 
simulation is not implemented. The description is clarified in the
note.} \\

34) Also in 3.2.5, I would like a little more detail on the fastmc: How does it 
calculate the energy loss of the 4He? Is multiple scattering included? Could 
you show comparisons between measured and simulated distributions?\\
\textcolor{blue}{We do not specifically apply energy loss and multiple 
scattering in our fastmc, but we apply resolution effects based on 
experimental data that include both effects. The plots in Fig.~\ref{fig:comp_He} 
show the comparison between data and simulation in terms of theta, phi and 
momentum of the He-4 DVCS nuclei.}\\

\begin{figure}[!h]
\includegraphics[height=5.0cm]{fig/He_theta.png}
\includegraphics[height=5.0cm]{fig/He_phi.png}
\centering
\includegraphics[height=5.0cm]{fig/He_mom.png}
\caption{Comparison between experimental and simulated DVCS $^{4}$He nuclei in 
terms of polar angle, azimuthal angle and momentum.}
\label{fig:comp_He}
\end{figure}

35) 3.3.: The kinematic corrections you mention are based on simulation only and 
mostly take care of energy loss by the protons. Most other CLAS analyses 
require additional, EMPIRICAL kinematic corrections (see, e.g. the BONuS 
experiment). Can you give a justification for leaving them out?
It may be obvious, but you don't show or say it: Are the corrections explained 
in 3.3.1-3.3.3 applied to the real data as well?\\
\textcolor{blue}{For electrons and protons, the presented corrections in 
sections 3.3.1 and 3.3.2, respectively, are applied for experimental data and 
simulation. We did not find the need for additional kinematic corrections on 
protons and electron as we found good enough match already.
In the case of the of the IC photons, the corrections 
for data and for simulation are different and presented in the following two 
sections, sections 3.3.3 and 3.3.4. In the latter case
these where empirical corrections.  Additional corrections are not pursued
for the data since data and simulation already agree reasonably well regarding
the quantities that are involved in event selection and asymmetry 
extraction.}\\

36) 3.3.4: The 3 corrections you describe for IC photons are somewhat 
correlated, since they all are checked by optimizing $m_{\pi^0}$. Did you try a 
simultaneous fit of all parameters (or at least several ones) that enter the 
various corrections?\\
\textcolor{blue}{The position correction (3.3.4.2) is derived based on minimizing
$z$-dependence of $m_{\pi^0}$, and is highly uncorrelated with energy 
corrections. The run-dependence (3.3.4.1) is also uncorrelated with energy, as
can be seen in the top panel of Fig 3.35, but is primarily a run-dependent global
scale factor on energy. Finally the radial- and energy- dependent energy correction
(3.3.4.3) are indeed correlated and therefore treated multidimensionally ($R,E$).}\\
\textcolor{green}{Rpahael: I believe Nathan will provide answer more detailed 
for this.  If not need to be clarified.} \\

37) Fig. 3.39, I am a bit troubled by the huge shift in missing energy - on 
average several 100 MeV - after applying the corrections. This contrasts to  
Figs. 3.34-3.38, where most deviations from the true pi0 mass appear to be less  
than a couple $\%$.\\
\textcolor{blue}{Most pi0 are found at low energy, while the correction affects
2 to 6.0 GeV photons. This is the reason the correction has such an important 
impact. See later reply to question 31 ii from reviewer 2 for more details.}\\
\textcolor{green}{Raphael: Same as previous.} \\

38) Sec.4.1, Fig. 4.1 and 4.2, Fig. 4.5: In addition to looking at He4/e and 
p/e, why don't you also look at e/FC to eliminate unstable runs?\\
\textcolor{blue}{We did not use the Faraday cup reading in the analysis. We
feel it is an unecessary cut for an assymetry measurement.}\\

Do we have an idea why the RTPC lost nearly 50$\%$ of its efficiency over the 
course of the experiment?\\
\textcolor{blue}{
 This is mainly related to experimental changes in the RTPC. In particular, we 
had leaks in our gas system that appeared during the run. This probably
caused gas contamination, changing the properties of the detector.}\\

39) Eq. 4.1: It would be nice to know the typical value (or range) for tmin.\\
\textcolor{blue}{We show in figure \ref{fig:tmin_both}, for both DVCS 
channels, $t_{min}$ distributions for our DVCS events.}\\

\begin{figure}[tbp]
\includegraphics[height=5.0cm]{fig/tmin_coh.png}
\includegraphics[height=5.0cm]{fig/tmin_incoh.png}
\caption{Coherent (left) and incoherent (right) tmin distributions calculated 
for the experimentally selected DVCS events. We use the experimental $Q^{2}$ 
and $x_{B}$ of the individual events. }
\label{fig:tmin_both}
 \end{figure}

40) Fig. 4.2: I'm bothered by the wide distribution in Emiss (top middle), and 
don't understand why you use such wide cuts. Surely, anything above Emiss = 0.4 
must have additional particles in it, and even if not, why not cut this tail?  
Note that the same tail is absent for the p (FIg. 4.6) where you use indeed a 
tighter cut, although you don't even account for the proton's initial 
momentum.\\
\textcolor{blue}{ We applied 3$\sigma$ guided by the comparison between data 
and simulation, see figure 4.4 in the note. In the following, figure 
\ref{fig:coherent_ME_bins}, we performed bins in the missing energy 
distribution and we watch the reconstructed beam-spin asymmetries. As a 
conclusion, we see that the reconstructed asymmetries are compatible within the 
given error bars.} \\

\begin{figure}[h!]
   \includegraphics[height=5.0cm]{fig/coh_ME_bins.png}
   \includegraphics[height=5.0cm]{fig/incoh_ME_bins.png}
   \includegraphics[height=5.5cm]{fig/BSA_coherent_ME.png}
   \includegraphics[height=5.5cm]{fig/BSA_incoherent_ME.png}
   \includegraphics[height=5.5cm]{fig/coh_ME_alpha.png}
   \hspace{+0.7cm}
   \includegraphics[height=5.5cm]{fig/incoh_ME_alpha.png}

   \caption{Coherent (left) and incoherent (right) missing energy distributions 
   (top), the reconstructed beam-spin asymmetries as a function of $\phi$ 
(middle), and the extracted asymmetry at $\phi = 90 ^{\circ}$ from fitting the 
asymmetries as a function of the missing energy in each bin. }
   \label{fig:coherent_ME_bins}
    \end{figure}

41) Fig. 4.6: Here you could cut deeper on the ep missing mass. Can be done.
Why is it so lopsided? Because the fact that we do not take into account the 
proton's initial momentum. Didn't you correct the IC photons to avoid that? \\
\textcolor{blue}{We can always cut deeper. We choose not to cut by eye, but 
   using 3 $\sigma$ in order to avoid biassed choices. Moreover, most 
   contamination eventually remaining is pi0 and is treated by a specific 
correction. We do not understand how IC correction can possibly affect the epX 
system.}\\

42) Fig. 4.8: Again, the missing energy from epgamma is lopsided, as is the 
missing egamma mass. Looks like Egamma is still not properly calibrated; but 
then why are the corresponding plots for the coherent channel spot-on? \\
\textcolor{blue}{The assymetry effects are due to the background of the pi0
contributing only on one side of distributions. The peaks are indeed all 
slightly shifted, this is probably due to a complex mix of misalinements and 
miscalibrations. Any attempt to correct with a simple function for one 
variable makes the other worse. In particular, we want to point out that both 
epX and e$\gamma$X missing mass are slightly off but ep$\gamma$ missing mass 
is peaked at 0. These problem do not appear for the coherent channel because
of the larger mass term that reduce the relative impact of some of the
measurement errors. Equation \ref{eq:egamma.} shows that the precision on the 
calculated missing mass squared of $e\gamma X$ depends on the mass of the 
initial state hadron in each DVCS channel.}\\
   \begin{equation}
      \frac{\partial MM^2_{e\gamma X}}{\partial E_{\gamma}}
      = 2*(E_{\gamma^{*}}-M_{target} - E_{\gamma})
      \label{eq:egamma}
   \end{equation}

43) 4.5: You discuss the pi0 background. Am I correct to assume that Eq. 4.11 
is applied separately for each beam helicity? (I assume you use the same R, but 
of course the reconstructed pi0 events could - probably will - have an 
asymmetry).   \\
\textcolor{blue}{ Yes, the subtraction is done separately for each helicity 
   direction. We modified the text to include that information. As can be seen 
   from figure \ref{fig:pi0yield}, the $\pi^0$-background yield with respect to 
   the coherent DVCS events is around 2-4$\%$.}\\
\begin{figure}[h!]
   \centering
   \includegraphics[height=5.5cm]{fig/t_ratio_coh_t.png}
   \caption{The coherent $pi0$-background yield.}
   \label{fig:pi0yield}
\end{figure}

   \textcolor{blue}{
   Figure \ref{fig:coh_dvcs_pi0_Alu} shows the reconstructed coherent 
   asymmetries in t-bins as a function of phi, where the red shaded point are 
   the DVCS asymmetries after the background subtraction, the blue points are 
   the DVCS raw asymmetries without background subtraction and the black points 
   are the $\pi^0$-asymmetries ($e^{4}He\pi^{0}$ events).  }\\
\begin{figure}[h!]
   \centering
   \includegraphics[height=7.5cm]{fig/coherent_AlU_pi0.png}
   \caption{In black, measured coherent $\pi^{0}$ asymmetries. In blue, the 
   coherent DVCS asymmetries without background subtraction. In red: the 
coherent DVCS asymmetries after the background subtraction.}
   \label{fig:coh_dvcs_pi0_Alu}
    \end{figure}

\textcolor{blue}{This leads us to conclude that:\\
- The  $\pi^{0}$-asymmetries are consistent with zero.\\
- 2-4$\%$ background yield does not affect much our DVCS asymmetries.\\
Therefore, assuming that the two helicity configuration have the same 
acceptance ratio R is very good approximation.}\\

44)Unfortunately, no other backgrounds are discussed (not even dismissed): 
scattering from other target components (Kapton? windows?), events with more 
particles in the final state (especially since you allow such a large Emiss), 
and accidental coincidences (particular for the coherent channel), plus perhaps 
photon misidentification. The various strange 'bumps' I've pointed out along 
the way show that those backgrounds may not be totally negligible. \\
\textcolor{blue}{The procedure follows the same guidelines as for other DVCS 
analysis on the nucleon. The neutral pion production occurs "without threshold" 
as seen from the eHegamma sample, meaning that the contamination from 
$eHe\pi^0$ with one photon lost is distributed all the way down to the DVCS 
threshold, in the limit where the second photon energy becomes negligible in 
the lab. Single charged pion production occurs with a small threshold but is 
inconsistent with the already detected particles (e and He). Two pion 
production is entirely cleaned up by the exclusivity cuts. Scattering from the 
windows is excluded by the vertex cuts. As far as accidental coincidences, we 
neglected that possibility since it is already rare with CLAS luminosities and 
the coincidence would have to fall inside narrow exclusivity cuts. This was 
also neglected in the DVCS analysis on the nucleon, which have higher 
luminosities. See also the answers to:\\
- Comment 31, figure 23, from the first reviewer.\\
- Comment 46, figure 30, from the first reviewer.\\
- Comment 7, figure 47, from the third reviewer.\\
- comment 14, figure 52, from the third reviewer.}\\

45) Fig. 4.11: For the final correction, do you produce the phi-dependence of R 
for each of the individual bins in xB, Q2 or t that you use? \\
 \textcolor{blue}{Yes we do.}\\

46) 4.7: I admit to being biased and a pain in the butt about this, but I NEVER 
understand why more or less arbitrarily varying a cut (and, in this case, even 
a rather meaningless cut in my mind) gives you a QUANTITATIVE estimate of 
background uncertainties. For one, you are mixing systematic effects from the 
tails with statistics (since you change the sample size). Plus, how do you know 
that there isn't even sizable background for your smallest (2.0 sigma) 
variation? I'd much rather see a sequential, quantitative discussion of 
possible background sources and direct estimates of their magnitude INSIDE all 
cuts (e.g., by selecting background events on purpose and looking at their 
distribution in the variables that you cut on). See above for a list of such 
backgrounds.\\
 \textcolor{blue}{Cuts are arbitrary, we could choose 2.32 sigma or 2.74 and 
there is no strong argument for either. It is therefore necessary to associate
an error with this choice. The chosen variable (missing mass of ep$\gamma$) is 
neither meaningless nor arbitrary, it is the one with the larger tails even 
after applying all other cuts. From these, it seems clear that such a study 
indicates a clear source of systematic errors linked to background. It can of 
course be argued that this test does not account for the full background error, 
but we never claimed this, so we are unsure what is the source of the critic. In 
fact, we claim the opposite since we treat pi0 background independently and 
associate another systematic error to it.}\\

 \textcolor{blue}{
 Regarding the window effect inside the exclusive distributions, the data
 has been processed with NO constraints on the z-vertex of the electron nor
 the $^{4}$He, and as a result no single event from outside the target has 
 passed the exclusive cuts. Even more, requiring that each event has three 
 particles (e, $\gamma$, $^{4}$He) in the final state and applying the $Q^{2}$ 
 and W cuts are enough to reject all the events generated from outside the 
 target. In figure \ref{fig:exclusive_z}, we show the exclusive variables in 
 figure 4.2 (in the note) as a function of z-vertex of the electron.  The scale 
 on Y-axis is kept the same as in figure 4.2. The target extends from -74 cm to 
 -54 cm with respect to the center of CLAS. As a conclusion, this source of the 
 background has no magnitude inside the exclusive distributions. }\\

 \begin{figure}[h!]
 \centering
 \includegraphics[height=14.5cm]{fig/exclusivity_zele.png}
 \caption{The distributions of the exclusive variables as a function of 
    z-vertex of the scattered electron, after applying $Q^{2}>1$ and $W>2.0$ 
 and before all the exclusivity cuts.}
 \label{fig:exclusive_z}
 \end{figure}

47) p. 80: I believe that one-loop corrections aren't a big worry. However, one 
contribution I can think of is the radiation of a second photon, e.g. right 
before the actual DVCS event (and not connected to a pi0). It's not clear to me 
that this is a priori a small effect, again especially given the wide Emiss 
cuts. \\
\textcolor{blue}{It has been shown that such effects are small for asymmetries
on free proton and we see no argument to claim otherwise. Regarding the 
one-loop contributions, we are in contact with Andrei V. Afanasev who started 
to do the calculations for our specific DVCS channels, and this part will be 
updated as soon as we get the results.}\\

48) Fig. 5.2: 'red error bars' aren't visible - use shaded bands instead.
    To do, unbinned fit and separate the systematic errors. \\
    \textcolor{blue}{In figures \ref{fig:coh_alu_sep} and 
       \ref{fig:incoh_alu_sep} we show the coherent and the incoherent 
       beam-spin asymmetries respectively. In blue only the statistical error 
       are added, in red the statistical and the systematic errors (except beam 
    polarization uncertainty) are quadratically summed, and in shaded brown on 
 the systematic errors are shown. } \\
 \begin{figure}[h!]
 \centering
 \includegraphics[height=7.0cm]{fig/BSA_Coherent_Q2.png}
 \includegraphics[height=7.0cm]{fig/BSA_Coherent_xB.png}
 \includegraphics[height=7.0cm]{fig/BSA_Coherent_t.png}
 \caption{Coherent beam-spin asymmetries}
 \label{fig:coh_alu_sep}
 \end{figure}

 \begin{figure}[h!]
 \centering
 \includegraphics[height=5.5cm]{fig/BSA_InCoherent_Q2.png}
 \includegraphics[height=5.5cm]{fig/BSA_InCoherent_xB.png}
 \includegraphics[height=5.5cm]{fig/BSA_InCoherent_t.png}
 \caption{Incoherent beam-spin asymmetries}
 \label{fig:incoh_alu_sep}
 \end{figure}

49) Fig. 5.3: Why the weird vertical ticks and tick labels? At least 0 should 
be clearly marked. Also, indicate the averages of the 2 other variables in the 
same way in the 3 plots, indicating that it is an average? \\
\textcolor{red}{Mohammad: To do with the final results.} \\

50) Fig. 5.5: Are the curves integrated over the experimental acceptance? 
Again, showing averages for all 3 variables (preferably for each data point) 
would help interpret the applicability of the curves.
- No matter what, you must supply tables for all your ALU(90deg) results with 
averages of all kinematic variables for each data point - after all, there 
aren't so many. \\

\textcolor{blue}{ The theoretical curves are not integrated over the 
   experimental acceptance. For example, they are calculated at fixed xb, Q2 
   and phi when looking to the dependence on t. Tables for all the two 
   dimensional bins are added to the note for the coherent and the incoherent 
   and shown here in tables \ref{table:Coh_Q2_BSA} to \ref{table:InCoh_t_BSA}.  
} \\

51) Fig. 5.6: It would be nice to superimpose the incoherent p results from 4He 
on the same graphs.\\
\textcolor{blue}{ Figures 5.4 and 5.6 are superimposed in figure
\ref{fig:incoh_free_ALU}}
\begin{figure}[h!]

   \includegraphics[height=5.5cm]{fig/Q2_dep.png}
   \includegraphics[height=5.5cm]{fig/xB_dep.png}
   \includegraphics[height=5.5cm]{fig/t_dep.png}
   \caption{The blue (black) points are the incoherent (free) proton $A_{LU}$ 
   as a function of $\phi$ in $Q^{2}$, $x_{B}$ and $-t$ bins.}
   \label{fig:incoh_free_ALU}
\end{figure}
\\

52) Fig. 5.7: I'm confused why Im(HA) is rising with Q2 but falling with xB.  
These 2 are pretty tightly correlated! Any explanation?\\
\textcolor{red}{Mohammad: need to be checked with the new extractions.} \\

53) 5.4: 3rd paragraph: Be careful not to over interpret the meaning of your 
results. For one, your xB is more closely related to xi, not x in DIS. Also, 
there are other possibilities to explain the smaller asymmetries for bound 
protons than the EMC effect - e.g., FSI. \\

\textcolor{red}{We are not sure what you are referring to. We clarified a 
little the paragraph in order to alleviate any issues.} \\

\textcolor{blue}{Regarding the FSI effect, this can be investigated by 
construction bins in missing transverse momentum. Figure 
\ref{fig:bins_pt_incoh} shows three bins in missing pt, while figure 
\ref{fig:incoh_Alu_pt}. Figure \ref{fig:alu_alpha_bins_pt} shows the extracted 
$A_{LU}$ at 90$^{\circ}$ from fitting the asymmetry signals. As a conclusion 
one can see that the incoherent asymmetries are consistent and so the FSI has 
no big effects on the measured asymmetries.  }\\
 \begin{figure}[h!]
  \centering
  \includegraphics[height=5.5cm]{fig/incoh_bins_pt.png}
  \caption{ Three reconstructed bins in the missing transverse momentum.}
  \label{fig:bins_pt_incoh}
 \end{figure}

 \begin{figure}[h!]
  \centering
  \includegraphics[height=6.5cm]{fig/BSA_incoherent_PT.png}
  \caption{The reconstructed beam-spin asymmetries as a function of phi in the 
  for the bins shown in figure \ref{fig:bins_pt_incoh}.}
  \label{fig:incoh_Alu_pt}
 \end{figure}

 \begin{figure}[h!]
  \centering
  \includegraphics[height=6.5cm]{fig/incoh_PT_alpha.png}
  \caption{The incoherent beam-spin asymmetries at $\phi = 90 ^{\circ}$, from 
  fitting the signals, as a function of the missing pt.}
  \label{fig:alu_alpha_bins_pt}
 \end{figure}

54) 4th paragraph: I am not sure what you are saying with 'in the same coherent 
domains of ...'. Can you specify exactly which range in x, t and Q2 either data 
set is integrated over?\\
\textcolor{blue}{We modified the text to include that information. }\\

55) Fig. 5.9: Certainly interesting, but maybe careful with the interpretation.  
Once again, I don't understand the very different behavior with xB and with Q2.  
Also, the x-dependence might be affected by the very different SHAPE of the 
coherent results vs. phi - indicating that the denominator may play a role. Of 
course, there is no expectation that coherent 4He should agree with free p - 
for one, all the nucleons are moving inside, and there are neutrons as well as 
protons.  Your disagreement with HERMES is also interesting - any comment on 
the possible source? Did they also use their own free p data? Of course, they 
have much less stringent cuts, in particular on exclusivity ... \\
\textcolor{blue}{HERMES data are selected for very small $-t$ and just assume 
they are in the coherent regime from this cut. The large difference between the 
measurement shows that the detection of the recoil has a strong impact on the 
final result. However, we do not want to comment more than necessary on the 
quality of HERMES result, it is not the place.}\\

\section*{\centering{2$^{nd}$ reviewer}}

1) p. 5-6: define ksi and t and indicate how they will be calculated in this 
analysis.\\
   \textcolor{blue}{ (Added). Experimentally, only  $\xi$ and $t$ are 
      measurable in the DVCS reaction. At twist-2 order, $\xi$ can be 
      calculated as $xB/(2-xB)$, where $xB$ is the Bjorken variable $(= 
      Q^{2}/(2M_{N}(E-E')$ where $Q^2$ is the vertuality of the exchanged 
      photon, $M_{N}$ is the mass of the nucleon and $E (E')$ is the energy of 
      the incident (scattered) electron. The squared
 momentum transfer $t$  is equal to $(p'- p)^{2}$, where $p' (p)$ is the nergy 
 momentum four-vector of the final-state (initial) hadron target. }\\

2) Eq. 1.7: define $\xi_{A}$ and $\xi_{N}$ in function of measured quantities.
\textcolor{blue}{   (Added)
  $ \xi_{A}= x_{A}/(2-x_{A})$ and  $\xi_{N}= xB/(2-xB)$.
}\\

3) Eq. 1.11: not of any consequence for the CAN, but should be corrected:  this 
is taken from Eq. 29 of ref. 2, but there, it is zeta, and not $\xi$. The 
relation between the 2 variables is in their Eq. 3d.
\textcolor{blue}{   Done.}\\

4) p. 11: 'The exclusivity of the selected DVCS events WAS APPROXIMATELY 
insured by a cut ... egX (resolution on this variable = ... GeV)'.
\textcolor{blue}{Done.}\\

5) Need to insert a short chapter (1 to 2 pages) before the one on RTPC with all 
running conditions and analysis conditions: very short description of set-up, 
positioning of RTPC, solenoid and IC wrt to CLAS center, beam intensity and 
polarization (including the Moller measurements), current in solenoid, magnetic 
field intensity and direction in solenoid, current in torus, inbending ... Date 
of data taking. Then cooking pass number and date (for reference in case 
another one is made in the future), and for each calibration, name of person in 
charge.
\textcolor{red}{Mohammad: written and Will be added.}\\

6) p. 14: I am confused by the description of the second gap, which does not 
correspond with the indications on Figs 2.2 and 2.5. Fig. 2.2 indicates it is 
filled with He, while the text says it is with the drift gas.
\textcolor{blue}{This gap is filled with the drift gas. I used different colors 
in figure 2.2 to indicate different gases. The $^{4}He$ label in figures 2.2 
and 2.5 is for the green line representing a track not for the gas. } \\

7) p. 11: Is the overall gain really 10$^6$ (100 per layer)? Any experimental 
indication?
\textcolor{blue}{
     The gain of such TPC has been studied by CERN's Gas Detector Development 
Group (Fabio Sauli, Progress with the Gas Electron Multiplier, 2nd Workshop on 
Advanced Transition Radiation Detectors for Accelerator and Space Applications 
(Bari, Sept. 4-7, 2003), Nucl. Instr. and Meth. A522(2004)93). The results 
shown in figure \ref{fig:gem_gains} demonstrate that one should not simply add 
gains to each other for multilayer GEM amplifications. We did not evaluate 
precisely the overall gain in our chamber, so we do not have a value for the 
eg6 RTPC at this point.}\\

\begin{figure}[h!]
\centering
\includegraphics[height=7.2cm]{fig/GEM_gains.png}
\caption{ The effective gain as a function of the voltage across the GEM foils 
of Single-GEM (SGEM), Double-GEM (DGEM) and Triple-GEM configurations.}
\label{fig:gem_gains}
\end{figure}

8) p. 16 track fitting: is it really a 5-parameter fit? why not imposing that the 
circle goes through x=y=0; that would be a 4-parameter fit. In fact Eq. 2.2 
further down indicates that there are indeed 4 degrees of freedom.
    x0, y0, R, slope and constant !!!!!.\\
   \textcolor{blue}{We do use a beamline constraint. See the answer to comment 
   15 of the first reviewer.}\\

9) p. 17-18 + fig. 2.7 caption: $r_{0}$ is the radius of curvature, not the curvature. 
Also the He4 travels in a clockwise direction if one looks into the beam, not 
in the direction of the beam (if B is in the direction of the beam).\\
\textcolor{blue}{  Corrected.}\\

10) p. 18: I suppose the resolutions mentioned 2 lines below Eq. 2.2 come from the 
vertical widths of graphs such as Figs 2.21 and 2.22. I can read also the 
resolutions in phi and z in section 2.3. Correct?\\
 \textcolor{blue}{ Answered in comment 5 from the first reviewer.  }\\

All this should be mentioned here.  No variations observed (or expected from 
simulation) depending on He4 energies and angles? Also may be worth adding at 
the end of the first line after Eq. 2.2: 'each hit 'i', determined from the TDC 
information as described in Section 2.2.3'.\\
  \textcolor{blue}{
     - This is very good comment. Regarding the dependence on the azimuthal 
     angle ($\phi$), the drift paths were extracted for each half of the RTPC 
     and as a result we have seen the two sets of drift paths overlap with no 
     variations. For the dependence on the momentum and the polar angle, we 
     used the identified elastic events for our calibration where the domains 
     of the momentum and $\theta$ are limited. Therefore, we assumed that there 
     is no dependence on these two variables. \\
  - The sentence is added.}\\

11) Fig. 2.10: why not centered at 0 like $sdist$?
\textcolor{blue}{ Answered previously in comment 7 of the first reviewer.}\\

12) Fig. 2.11 2.12 and 2.13: did you check for any dependence of Delta-z and other 
Delta's on CLAS sector? If yes, should be mentioned and described. If not, 
would like to see it.\\
\textcolor{blue}{In figures \ref{fig:delta_z_sec},\ref{fig:delta_phi_sec}, and 
\ref{fig:delta_theta_sec} we show the corresponding distributions in the 
different sectors of CLAS for the identified good tracks at 1.2 GeV beam 
energy.}\\

\begin{figure}[h!]
\centering
\includegraphics[height=6.7cm]{fig/delta_z_sec.png}
\caption{$\Delta z$ distributions between the scattered electron in the 
different sectors of CLAS and the recoil particle in the RTPC for the 
identified good tracks at 1.2 GeV beam energy.}
\label{fig:delta_z_sec}
 \end{figure}

\begin{figure}[h!]
\centering
\includegraphics[height=6.7cm]{fig/delta_phi_sec.png}
\caption{ $\Delta \phi$ between the scattered electron in the different sectors 
of CLAS and the recoil particle in the RTPC for the identified good tracks at 
1.2 GeV beam energy.}
\label{fig:delta_phi_sec}
 \end{figure}

\begin{figure}[h!]
\centering
\includegraphics[height=6.7cm]{fig/delta_theta_sec.png}
\caption{$\Delta theta$ distributions between the scattered electron in the 
different sectors of CLAS and the recoil particle in the RTPC for the 
identified good tracks at 1.2 GeV beam energy.}
\label{fig:delta_theta_sec}
 \end{figure}

13) Are Figs 2.6 to 2.11 for elastic He4 or for coherent DVCS events? any 
difference between the distributions for these two types of events?\\

\textcolor{blue}{ The figures are for the good tracks collected during the 1.2 
GeV runs. Yes, one can see different level of performance of the RTPC during 
the experimental data taking period is due to some known experimental setting 
changes, indicated in figure 4.1.}\\

\textcolor{blue}{ In comment 7 of the first reviewer, we have shown the sdist 
   and edist distributions for the identified elastic events without applying 
   any requirements on sdist and edist. Figure \ref{fig:dvcs_coh_sdis_edist} 
   shows the equivalent distributions of the identified coherent 4He DVCS 
   nuclei using the presented exclusivity cuts, where larger cuts were applied 
to clean the initial dataset. -3 mm < sdist < 2 mm and -2mm < edist < 3 mm are 
considered in the second round of the analysis. }\\

\begin{figure}[h!]
   \hspace{-1.0cm}
   \includegraphics[height=6.7cm]{fig/coh_rtpc_sdist.png}
\includegraphics[height=6.7cm]{fig/coh_rtpc_edist.png}
\caption{sdist (left) and edist (right) of the identified 4He DVCS nuclei via 
the exclusivity cuts.}
\label{fig:dvcs_coh_sdist_edist}
 \end{figure}

14) p. 23, 2nd paragraph: you write TDCmax = DPL/DS. Is not it (TDCmax - 
15)*114 ns = DPL/DS?\\
\textcolor{blue}{ We show it in this form to simplify the correlation between 
these variables.  Indeed it is  TDCmax-15 without the conversion unit as our 
drift speed in TDC units. } \\

15) p. 23: can you show the dependence of TDCmax/2 on z for a given run? \\ 
\textcolor{blue}{ The shown figure in p.24 (figure 2.16) is for a single 
experimental run.} \\

16) 'Figure 2.18 \textcolor{blue}{ALSO} shows the percentage increase in good 
tracks (GT) ...' \textcolor{blue}{ Added.}\\

17) Eq. 2.8: is not it TDCmax instead of a fixed 75?\\
\textcolor{blue}{Typically, it has to be TDCmax instead of 75, while this 
   change has no effects on the final extracted drift paths as it comes as a 
selection cut in the first pass to get an initial set of the paths. In the 
second pass, all the hits are processed and R is calculated more precisely from 
the drift paths (equation 2.9 in the analysis note). More checks were performed 
using TDCmax and as a result, the previously extracted drift paths overlap on 
the new ones, using TDCmax, without and variations. The plots of the new drift 
paths with the old fits can be provided for the 20 bins along the RTPC in case 
requested.}\\

18) Eq. 2.9 does not have the right dimensions. Should not the second term be 
multiplied by 114 ns?
\textcolor{blue}{ Corrected. The sum is multiplied by a TDC unit.}\\

19) p. 29, 3rd paragraph: remove 'The results are shown in figure 2.26' as the 
method should be described first, the figure appears later and the results are 
commented at the bottom of the page.
\textcolor{blue}{  Done.}\\

20) p. 32 bottom: 'large' -> 'wide'. More importantly, give in conclusion in which 
data sets the ADC information will be used, since it is not so clear later that 
it is used for elastic events selection, but not for DVCS events selection.
\textcolor{blue}{  Done.}\\

21) p. 37: 'The CLAS detector NOMINALLY provides electron detection ...'. Also 
in Table 1 caption, add '(neglecting the contributions from the CLAS 
resolutions).'
\textcolor{blue}{  Done.}\\

22) Chapter 3 intro: should prepare (for the publication) an argumentation to 
neglect other possible source of background (e.g. e He4 pi0 gamma).
\textcolor{blue}{ Answered previously in comments 44 and 46 of the first 
reviewer.}\\

23) Chapter 3: the effect of some of the early pid cuts should be looked at after 
exclusivity cuts (for both samples of coherent and incoherent events). Ideally 
without the pid cut in question, but if this is not practical, with this cut 
included. For example, the z-vertex of Fig. 3.1, if looked at with the DVCS 
exclusivity cuts, could persuade us that there are no window contributions 
there, especially in the incoherent channel. If the z-cut cannot be removed in 
this exercise, it is still useful to see if there is or not an increase towards 
the ends of the cut. So I am thinking not only of fig. 3.1, but also fig. 3.8.
\textcolor{blue}{ Answered previously in comments 44 and 46 of the first 
reviewer.}\\

24) p. 42: section??
\textcolor{blue}{ Removed.}\\

25) p. 48, 2nd line of 3.1.4: chapter and section numbers to be fixed. Same p. 55 
in 3.2.5.
 Done.

26) Figs 3.21 and 3.22: would (part of) the tails of these distributions be 
attributed to random coincidences? If yes, what about a subtraction?
\textcolor{blue}{Yes, this is true and justified by distributions previously in 
comment 7 from the first reviewer and comment 13 of the second reviewer.}\\

27) Fig. 3.39: More than a factor 2 gain in statistics between pass1 and pass2 in 
eHe4g events or are these arbitrary subsets of the total sample? More 
worrisome, why a 40$\%$ loss in statistics between pass1 and pass2 in epg 
events or are these arbitrary subsets of the total sample?\\
\textcolor{blue}{
The full data set was included in pass1 and pass2 distributions. The 35$\%$ 
loss in the incoherent DVCS events is because we were not seeing real 
indications about the peaks in the exclusivity distributions. So the 3 sigma 
cuts were very wide to adapt to very broad distributions. }\\
\textcolor{green}{Nathan wants to clean this answer more.}

28) p.65: (optional addition) Since I noticed many people do not have a good 
sense of (the kinematical dependences of) tmin, it would be instructive to add 
2 plots of lines of constant tmin in the Q2-xB plane within the acceptance 
locus limited by beam energy and W cut, both for He4 and for proton.\\
\textcolor{blue}{
   The plots in figure \ref{fig:Q2_xB} show the coherent and the incoherent 
-tmin distributions distributions with the W and -tmin cuts. }\\

\begin{figure}[h!]
\includegraphics[height=6.2cm]{fig/coh_Q2_xB.png}
\includegraphics[height=6.2cm]{fig/incoh_Q2_xB.png}
\caption{The coherent (left) and incoherent (right) $Q^{2}$ versus $x_{B}$ 
   distributions for the identified DVCS events, with the W and -tmin (0.01 
GeV$^{2}$ cuts in the $Q^{2}$-$x_{B}$ plane.}
\label{fig:Q2_xB}
 \end{figure}

29) p.65: Eg cut: should add that the simulation indicates that no DVCS events 
are expected (in IC) with photon energy less than 2 GeV.
\textcolor{blue}{ Added. Figures \ref{fig:sim_coh} and \ref{fig:sim_incoh} show 
the energy of the simulated coherent and incoherent DVCS photons, respectively.  
}\\

\begin{figure}[h!]
\centering
\includegraphics[height=6.2cm]{fig/photon_energy_coh_sim.png}
\caption{The energy of the simulated coherent DVCS photons}
\label{fig:sim_coh}
 \end{figure}

\begin{figure}[h!]
\centering
\includegraphics[height=7.2cm]{fig/photon_energy_incoh_sim.png}
\caption{The energy of the simulated incoherent DVCS photons.}
\label{fig:sim_incoh}
 \end{figure}

30) p. 67: specify/explain what is an equivalent set of DVCS exclusivity cuts 
or the simulated events.\\
\textcolor{blue}{ We apply similar exclusivity cuts as presented for the 
experimental coherent DVCS events. Then, each exclusive distribution is fitted 
by a Gaussian and a 3$\sigma$ cut is applied. So the cut are not
identical, but obtained with the same method. This is done to avoid issues on 
variables where the peak is not in the exact same place in simulation and in 
data. }\\

31) Fig. 4.8: \\
i) the experimental widths are similar to the simulated ones: can we conclude 
from this that the Fermi motion has negligible effects (which I am ready to 
believe considering the beam energy). 
 \textcolor{blue}{
   Not actually, because the simulation also includes the Fermi motion effect 
as shown previously. See the answer to comment 32 of the first reviewer.  }\\

ii) any comment on the significant shifts in 2 of the distributions?\\
\textcolor{blue}{ The large shift in missing energy is due to the correction in
3.3.4.3.  That correction is measured in the range of $E_\gamma$ available in
the IC from $\pi^0\to\gamma\gamma$ decays, which is about 0.8 to 2.5 GeV.
The correction takes the form of Equation 3.14, which contains a linear scale
factor on the energy and an offset, both parameterized as a function of radius
as shown in Figure 3.38.  To apply the correction on a photon, its radius is
used to get the linear energy dependence, and then that is extrapolated to
the measured energy of the photon.  For DVCS, this goes well above the measured
range of photon energies used to derive this correction.  It should be noted
that previously accepted corrections for photon energies included parameterizing
a similar, but 1-dimensional, radial-dependent energy scaling based on the
reaction of physical interest (DVCS), effectively to fix the missing mass or
energy in DVCS to the zero just by adjusting the photon energy.  Here we derive
the photon energy correction based on an independent decay ($\pi^0$) and assume
an extrapolation to the energies of interest.  Figure \ref{fig:exprepostcorr}
illustrates the size of the correction at high energy and its effect on DVCS.
This relates to question \#37 from the first reviewer also. }\\

\begin{figure}[htbp]\centering
  \includegraphics[width=10cm]{fig/exprepostcorr.png}
  \caption{The histogram is the coherent DVCS event selection before the photon 
     energy corrections in 3.3.4.3.  The red curve is the correction of 3.3.4.3 
  for 4 GeV photons, our average DVCS photon energy.\label{fig:exprepostcorr}}
\end{figure}

32) p.73: remove 'in figure??' \textcolor{blue}{ Corrected. Figure 4.7 in the 
place of ??}\\

33) p.74: remove ', as expressed in equation??,' and refer to eqs 1.4 to 1.6 
for ALU.\\
\textcolor{blue}{ Done.}\\

34) Conclude section 4.4 by a table of bin values for all variables in the two 
topologies.\\
\textcolor{blue}{ See tables \ref{table:Coh_Q2_BSA} to \ref{table:InCoh_t_BSA} 
at the end of this document. }\\

35) Section 4.5: I have a potential issue with the way you use the acceptance 
ratio. Since, even after integration, one can see some kinematical dependences, 
I would expect that a 2D subtraction using an integrated R is not rigorous. 
Mathematically, if I call ijkl the bin indices of the 4 variables:
N(ij) = sum(over kl) [Nexp(ijkl) - R(ijkl)NexpPi0(ijkl)] is what you want and 
is different from sum(over kl)[Nexp(ijkl)] -  sum(over kl)[NexpPi0(ijkl)] which 
you are using. In the end, the difference might be small, but maybe not 
negligible compared to systematic uncertainties.\\
\textcolor{blue}{We are not sure to understand fully the argument here. You 
   probably forgot a R term in the second formula. In any case, in the 2D 
   correction, we are indeed dependent on the reproduction of the integrated 
   variables. The figures 4.3, 4.4, 4.7 and 4.8 are here to show that we have a 
   good reproduction of the variables and should not be sensitive to such 
problems. }\\

36) Section 4.7: should distinguish from the start in the text down to Table 
4.1 between overall normalization error (beam polarization) and bin to bin 
systematic errors. \\
\textcolor{blue}{All the systematic errors are added bin by bin except the beam 
polarization, which added to the value of the asymmetry at 90$^{\circ}$ after 
fitting the signal. I Will change the text to include this information.}\\

37) p. 77 last sentence: it is ALU(90°) here and you should mention that it is 
extracted from the ALU(phi) distribution from a fit to be discussed in section 
5.1.\\
\textcolor{blue}{Yes, it is ALU(90°) from the fit. The text is modified to 
detail this information.}\\

38) p. 77: When you change the missing mass cut, do you do a similar change in 
the numerator of R? \\
\textcolor{blue}{We used the same acceptance R. The analysis is refined using 
different acceptance R. The details with the new results can be found in the 
answers to comments 20 of the third reviewer.  }\\

I read on Fig. 4.13 Coherent ALU(3sigma) - ALU(2sigma) = 0.02; for a mean value 
of .32, that makes 6.2$\%$, not 4. Incoherent OK.\\
\textcolor{blue}{ Indeed it is 0.018 resulting in 5.7$\%$. Corrected.}\\

39) Fig. 4.13 coherent again: I worry that ALU increases with a tighter cut.  
For an asymmetry, a tight cut might be closer to the real value. Comment?  Do 
you see this on all bins? Is this figure integrated on all bins?\\
\textcolor{blue}{ This came from applying the same acceptance R. See the answer 
to comment 20 from the third reviewer, where the analysis is refined and the 
results are flat withing the given error bars. It is integrated over all the 
bins.  }\\

40) p. 79: change 83.67$\%$ to 0.8367 to distinguish from the following 
percentage value 3.5$\%$ which is really a ratio DeltaP/P.\\
\textcolor{blue}{ Done.}\\

41) Radiative corrections: the conclusion could be that we neglect this effect in 
the end result and table. By the way, I am not aware of any asymmetry for any 
exclusive channel (elastic, DVCS,...) where the radiative effects are not 
negligible. If you know a counter example, please let me know.
\textcolor{blue}{ All the previous studies have assumed that the radiative 
corrections have no interest effects to the asymmetry ratios comparing to the 
other systematic sources. }\\

42) p. 83: Belitsky and Muller (PRD 79 014017) updated earlier DVCS 
calculations, getting rid of some approximations in their formulae. I know that 
it makes a difference in the case of a spin 1/2 target (indeed Hall A is using 
the new formulae from PRD 82 while some CLAS publications still refer to the 
old ones), but what about a scalar target? Could you please check from this PRD 
79 if you have to change the expressions of your $\alpha_{i}$'s?\\
\textcolor{blue}{
The used parameterization  (http://arxiv.org/pdf/hep-ph/0302007v2.pdf)\\
The refined parameterization (http://arxiv.org/pdf/0809.2890.pdf)\\
  If we take only the twist-2 terms:\\
  - The coefficients of the squared DVCS amplitude remain the same. In our 
preliminary CFF extraction, we assume the pure DVCS is negligible. \\
  - The interference coefficients change.\\
  - The squared BH amplitude, that come in the $\alpha_{1}$ which functions as 
  a scaling factor for other $\alpha$'s, is the same in both calculations.\\
For instance the following plot, \ref{fig:alpha_zero} shows the $\alpha_{0}$ as 
a function of $\phi$ using the two models of calculation. As a result, the 
extracted CFF will be changed.\\
We updated all fits in the note with the most recent formulas.} \\

\begin{figure}[h!]
\centering
\includegraphics[height=7.5cm]{fig/alpha_0_two_models.png}
\caption{$\alpha_0$ as a function of $\phi$ using the old (black) and the new 
(red) KM parametrizations.}
\label{fig:alpha_zero}
 \end{figure}

43) Eqs 5.2 to 5.5: should not they be the same as A.18 to A.21? 
    They are exactly the same, I wrote them in simplified way in equations 5.2 to 5.5. 
In any case 5.2 and A.15 would lead to Im(HA) squared in the numerator !! All this is very 
confusing. Please check/correct your formulae and tell us which one you really 
used in the CFF extraction.\\
\textcolor{blue}{ The are exactly the same. We will include all the terms in 
the second version of the analysis note with the refined parametrization. The 
fitting form for the asymmetries will be changed such that the real and the 
imaginary parts of the CFF $H_A$ will be the free parameters in the fit.} \\

44) p. 84: the last paragraph of section 5.1 is confusing. I would altogether 
replace it by :
'This two-parameter fit allows us to extract ALU(90 $^{\circ}$) already used in 
Section 4.7 and hereafter in this chapter for comparison with the HERMES data 
and with model calculations. We checked that adding a cos(2phi) term in the 
denominator does not change the extracted values of ALU(90$^{\circ}$), within 
the quoted statistical uncertainties. Furthermore, alpha and beta are linear 
functions of the imaginary part and real parts of the Compton form factors 
(single He4 CFF in the coherent case, proton CFF's in the incoherent case).  
Then, in the coherent case, this two-parameter fit can equivalently be replaced 
by a fit in function of Im(HA) and Re(HA) treated as free parameters, see 
Section 5.3.'
\textcolor{blue}{ The paragraph is changed.}\\

45) When adding the systematic and statistical uncertainties in quadrature, should 
not include the error on beam polarization.
\textcolor{blue}{This is what we do, we add the beam polarization error as a 
normalization to the extracted asymmetries from fitting the signals.}\\

46) It seems your phi values are at the middle of each phi-bin. The phi values in 
each bin should be event weighted (in the same way as Q2, xB, t). Once you do 
that, you'll have to redo all your fits.
\textcolor{blue}{ It is not the middle, it is the mean value of phi in each phi 
bin.}\\

47) Fig. 5.2 top left: value of <-t> missing. Added.  Section 5.2.1: the drop 
at high t is 'suggested', not 'observed' by HERMES. \textcolor{blue}{ 
Corrected.}\\

48) Fig 5.5 caption: 'top left' -> 'top'; 'top right' -> 'middle'; 
\textcolor{blue}{Changed.}\\
The kinematics of the CLAS results are not the same as on the figures.  
\textcolor{blue}{  The ones in figure 5.4 are showing the mean Q2, xB and -t 
for each bin. In Figure 5.5, I show the mean values over the full data. For 
example, in the Q2 dependence plot, xB= 0.267 and -t =0.506 are the mean values 
over all the bins.}\\

49) Section 5.2.3: in order to convince us (and others) that the proton BSA you 
analyzed are compatible with the published results, could you reproduce figure 
4 of ref 34 (ask FX if need be) and place on it the results from your fits of 
Fig. 5.6 (the kinematics will differ slightly, but the closest match for each 
point)\\
\textcolor{red}{Mohammad: I need to implement the binning of e1dvcs1 in my 
analysis codes for e1dvcs data.}\\

50) Section 5.3: do you really get Im(HA) and Re(HA) from alpha and beta or do 
you redo the fit? I would favor the latter.  \\
\textcolor{blue}{ The fitting function is changed by a fit in function of
Im(HA) and Re(HA) treated as free parameters.}

Also at this stage, it does not cost you anything to put the whole expression 
5.1 in the fit, including the cos(2phi) term in c2BH and the apha3 term, since 
all the coefficients are known and it does not add any parameter. The end 
result might not be significantly different, but it is a more convincing 
procedure. \textcolor{blue}{ In the process.}\\

51) Overall, the physics discussion of the results may not be up to the level of a 
publication, but this is beyond the scope of the present review. It is not 
enough to say that we agree or disagree with a given calculation, one may want 
to give tentative explanations. The most significant deviation from model 
expectations is R{incoh} at small xB. Are we then at too small Q2 for validity 
of leading-twist approximation (but the sin(phi) dominance is what is expected 
from leading twist)? If we suppose leading twist OK, what would that mean for 
the bound proton? Etc ...

p. 97: 3.23 -> 2.11 
\textcolor{blue}{ Corrected.}\\

\section*{\centering{3$^{rd}$ reviewer}}

1) Page 5, 2nd paragraph
'..., such as confinement size of the bound nucleons ...' - '..., the quark 
confinement size of the bound nucleons ...'
\textcolor{blue}{ Changed.}\\

2) Page 6, in Figure 1.2 it looks like beta = b+b' rather than b-b'.
\textcolor{blue}{ The figure is corrected.}\\

3) Page 9, Fig caption 1.5, last sentence  '...-t,0.2 and 0.4  2 
GeV$^{2}$/c$^{2}$ ...'.  Is -t= 0.42?
\textcolor{blue}{ It is -t= 0.4 GeV$^{2}$/c$^{2}$. Corrected.}\\

4) Page 10, A strange introduction into the need of an RTPC, section 2.1. No 
logical conclusion about the lack of exclusivity in the HERMES results, for 
example, to justify the RTPC. First paragraph talks directly about the momentum 
per charge of the He4 needing an RTPC.\\
\textcolor{blue}{I will write a brief chapter about CLAS, IC, solenoid and beam 
before the chapter of the RTPC.}\\

5) Page 13, Chapter 2,  2.1 ,  'mechanical'  in Fig. 2.2 is misspelled in the mechanical support (green boxes).
\textcolor{blue}{ Corrected.}\\

6) 2.2.1.1 Why not choose a region that is relatively flat in the vertex cuts. I 
understand we lose events but why not choose a region with less steep 
variations for example, -50,+50mm for $z_{RTPC}$ and then as part of the 
systematic studies see what effects if any are introduced by the upstream and 
downstream regions to recover more statistics. See also reviewer 2 request to 
see this distribution after exclusivity cuts: this may be a clearer way to look 
in the end regions. \\

7) Page 17, 2.2.1.1 RTPC good track requirements, bullet 2, I understand that 
the z cut of -80,+80 mm is well within the physical dimension of the RTPC,  
however the z  acceptance of the RTPC is changing rapidly between -80 to -50 
and +50 to +80, therefore why not have a  tighter cut first. It can be opened 
later to increase the statistics when it is shown that there are no systematic 
effects of the edge regions. \\
\textcolor{blue}{
 Both 6+7: Regarding the calibration, the z cut is meaningless since we make 
 the calibration in z bins anyway. If we want calibration for the outer z as 
 well we need to keep it. Regarding the data analysis, for the elastic events 
 at 1.2 GeV data, if we remove both z-vertex cuts and apply the other quality 
 cuts on selecting the electron and the recoiled 4He, we obtain figure 
 \ref{fig:elastic_z_vertex} for the z-vertex distributions of the elastic 
 events: (where both vertices are taken with respect to the center of the 
 RTPC).  As a conclusion, the -[80:+80] mm cuts on the helium z-vertex appear 
 to be the suitable cuts to ensure that the reconstructed tracks are within the 
 physical volume of the RTPC from one side, and to reduce the background 
 effects on the other presented variables in section 2.2.1.1.  Also, one can 
 see the almost symmetric trends between [-80:-50] and [+50, 80].  }\\
\begin{figure}[h!]
\centering
\includegraphics[height=7.5cm]{fig/elastic_z_vertex.png}
\caption{z-vertex distribution for the electrons of the identified elastic 
events in the two modules of the RTPC.}
\label{fig:elastic_z_vertex}
 \end{figure}

8) 2.1.3, 1st paragraph, 3rd sentence'... spatial reconstructing ...' should be 
'...  spatial reconstruction ...' \textcolor{blue}{ Done.}

9) Page 17, 2.2.1.1 RTPC good track requirements, bullet 5, why is $sdist$  
(-2.0,2.0 mm) with better number of digits compared to $edist$ (-1,5 mm).  Is 
there a resolution difference?\\
\textcolor{blue}{
  In addition to the answer of comment 7 from the 1st reviewer, the probability 
that a noise signal produced close to the anode to reach the readout pads and 
being recorder is higher than the probability the of the same noise released 
close near the cathode to cross the full drift region and recorder as a signal.  
Therefore, the noise contribution at the end of each chain of hits is bigger 
than the contribution at the beginning, resulting in more precise reconstructed 
$sdist$ than $edist$. The noise effect at low TDC can be seen from figure 2.30, 
section 2.2.5.1}\\

10) Page 19,  in Figures 2.7, 2.8, 2.9 and 2.10 when comparing the left and right 
RTPC modules the total number of events is similar even though the shapes are 
not the same . However, when elastic tracks are used the left and right samples 
are dramatically different in size. Is this due to electron efficiencies in the 
CLAS detector between left side and right side? This difference is again seen 
later in Fig. 3.19 for example and 3.23.\\
 \textcolor{blue}{ Answered previously in comment 12 of the 1st reviewer.  }\\

11) Page 24, Figure 2.16, do we understand why at z=0 $TDC_{max}/2$ is the 
largest.\\
  \textcolor{blue}{
Because of the generated electromagnetic field where:\\
- One can see from figure 2.4 that the magnetic field at the sides of the RTPC 
is slightly deviated from the direction of the beam line and weaker.
- The generated electric field between the two cylinders (cathode and anode) 
produces small gradient components at the sides. We added field cages at both 
ends of the RTPC to adapt for these gradient components, but they were 
disconnected soon in the run because of HV trips. The electric field might 
therefore be significantly off on the sides. }\\

If there is a small region around the center that is most stable one should 
perhaps again analyze the data with a z cut that is narrower from what has been 
taken in the analysis to check systematic effects.\\
  \textcolor{blue}{ We performed an additional iteration of the analysis where 
  the events with the scattered electrons being originate within 6 cm from the 
  center of the RTPC, and compared it to the case where the full length of the 
  RTPC is considered. The results are presented in figures 
  \ref{fig:coh_exc_cuts_z} and \ref{fig:incoh_exc_cuts_z} for the coherent and 
  the incoherent channel respectively. As a conclusion, one can see that 
  cutting in the flat region around the center of the RTPC has no direct impact 
  on the exclusive distributions. }\\

\begin{figure}[h!]
\centering
\includegraphics[height=14.5cm]{fig/coh_exc_cuts_z.png}
\caption{The coherent exclusive distributions in case of taking events 
originate along the full length of the RTPC (in blue) and in case of analyzing 
events with the scattered electrons being originate within 6 cm from the center 
of the RTPC.}
\label{fig:coh_exc_cuts_z}
 \end{figure}

\begin{figure}[h!]
\centering
\includegraphics[height=14.5cm]{fig/incoh_exc_cuts_z.png}
\caption{The incoherent exclusive distributions in case of taking events 
originate along the full length of the RTPC (in blue) and in case of analyzing 
events with the scattered electrons being originate within 6 cm from the center 
of the RTPC.}
\label{fig:incoh_exc_cuts_z}
 \end{figure}

Is run 61510 typical? 
\textcolor{blue}{
   Yes, it is one of the good runs.  }\\

It would be important to check systematic effects on the results as a function 
of groups of runs with roughly common position of the maximum of 
$TDC_{max}/2$.\\
\textcolor{blue}{ Figure \ref{fig:coh_alu_run} presents the reconstructed 
coherent $A_{LU}$ as a function for different groups of run numbers. Within the 
given statistics, the asymmetries are compatible. }\\
\begin{figure}[h!]
\centering
\includegraphics[height=7.5cm]{fig/bsa_coherent_runs.png}
\caption{The reconstructed coherent beam-spin asymmetries as a function of the 
run number.}
\label{fig:coh_alu_run}
 \end{figure}

12) Page 24, in Fig. 2.18, it is not clear at what z the $TDC_{max}/2$ was 
plotted.\\
\textcolor{blue}{ It is integrated over the full z range of the RTPC to show 
the variation with time during the experimental data taking period.}\\

13) Page 44, figure 3.8 indicates a Cherenkov detector response of the sum of all 
sectors. It would be helpful to show the response per sector and how well the 
phototubes of each sector are calibrated with each other. The spectrum as shown 
seems to indicate an average performance with a mean of 7 to 8 photoelectrons. 
However, the shape on the low number of photoelectrons hints at a mismatch of 
performance between different sectors.  The cut of the number of photoelectrons 
to define a good electron track could be optimized per sector and not on the 
total spectrum as shown. In the end, I would like to see this figure after 
exclusivity cuts.
\textcolor{blue}{ See the answer to comment 23 from the first reviewer. The 
   sector-dependent distributions after the exclusivity cuts are shown in 
figures \ref{fig:nphe_after_excl_cuts_coh} and 
\ref{fig:nphe_after_excl_cuts_incoh} for the coherent and the incoherent 
channels respectively without any initial cut on the number of photo-electrons.  
. In figure \ref{fig:nphe_coh_incoh_alu} we show the reconstructed integrated 
coherent and incoherent $A_{LU}$ as a function of $\phi$ using nphe>20 and 
nphe>40. This leads us to conclude that the small contribution that remains 
from the single photo-electron peaks has no significant effect on the 
reconstructed asymmetries.}\\

\begin{figure}[h!]
   \hspace{-1.0 cm}
\includegraphics[height=12.5cm]{fig/e_nphe_coh.png}
\caption{The sector-dependent distributions of the number photoelectrons 
produced by the electrons of the identified coherent DVCS events. }
\label{fig:nphe_after_excl_cuts_coh}
\end{figure}

\begin{figure}[h!]
   \hspace{-1.0 cm}
   \includegraphics[height=12.5cm]{fig/e_nphe_incoh.png}
\caption{The sector-dependent distributions of the photoelectrons produced by 
the electrons of the identified incoherent DVCS events via the exclusivity 
cuts.  }
\label{fig:nphe_after_excl_cuts_incoh}
\end{figure}

\begin{figure}[h!]
   \hspace{-1.0 cm}
\includegraphics[height=7.5cm]{fig/nphe_BSA_Coherent.png}
   \hspace{-1.0 cm}
\includegraphics[height=7.5cm]{fig/nphe_BSA_InCoherent.png}
\caption{The Coheren (left) and incoherent (right) measured beam-spin 
asymmetries using the cuts nphe > 20 (blue) and nphe > 40 (red). }
\label{fig:nphe_coh_incoh_alu}
\end{figure}

14) Page 49, the RTPC track requirement $z_{RTPC}$ cut in Fig. 2.6 of page 19 
is set to be within the RTPC volume according to  2.1.1.1 bullet number 2. Then 
in page 49, Fig. 3.19, when RTPC events are correlated with the electrons 
detected in CLAS, it is set all the way to the edges of the RTPC. Aren't the 
proponents worried about edges and inconsistencies with earlier cuts?

\textcolor{blue}{
  It is justified for the case of the elastic events in the answer of comment 7 
  from the 3rd reviewer. For the case of the DVCS events, figure 
  \ref{fig:coh_z_vertex} shows the distribution of the He4 DVCS events after 
  the exclusivity cuts without applying any PID cuts on the He4 selection.  
  Therefore, the cut will be tuned to be as the one for the elastic selection 
  as we saw that no contributions from the target's windows was observed.}\\

\begin{figure}[h!]
\centering
\includegraphics[height=7.5cm]{fig/dvcs_z_vertex.png}
\caption{$^{4}$He z-vertex distribution for the identified DVCS events in the 
two modules of the RTPC. The events are selected by applying the exclusivity 
cuts with no cut on the PID nor the z-vertex.}
\label{fig:coh_z_vertex}
 \end{figure}

15) Page 50, figure 3.23 the left side is showing half as many events as the 
right side of the RTPC. Although a priori that should not affect the phi 
distributions of the results, like for instance in figure 4.10, page 74, I 
would like to see separate phi distributions of the He4 asymmetries for the two 
halves of the RTPC and check that they are compatible.\\

\textcolor{blue}{Figure \ref{fig:coherent_alu_sides} shows the integrated (over 
Q2, xB and t) beam-spin asymmetries for the two halves of the RTPC separately 
and the integrated asymmetries over the whole RTPC.  }\\
\begin{figure}[h!]
\centering
\includegraphics[height=8.5cm]{fig/BSA_Coherent_sides.png}
\caption{The reconstructed beam-spin asymmetries as a function of the hadronic 
angle $\phi$ in the two modules of the RTPC separately and the integrated 
signal over the whole RTPC.}
\label{fig:coherent_alu_sides}
 \end{figure}

16) Page 68, figure 4.4, the experimental coplanarity angle is significantly 
shifted compared to the simulated one. Is this understood? Also, do you know 
why the experimental missing pT distribution looks much more smeared out than 
the simulated one for 4He but not for the proton. Is the He4 multiple 
scattering and fluctuations in energy loss taken in to account in the 
simulation?  \textcolor{blue}{
   The coplanarity and the pT distributions are both linked to the azimuthal 
   angle of the recoiled 4He. Regarding the multiple scattering and the energy 
   loss, we do not apply them individually, but we apply an overall smearing to 
   the kinematics of the Helium nuclei based on the real data. One can see from 
   the comparison between the simulated and the experimental 4He (comment 34 of 
   the 1st reviewer) that there is slight difference in terms of phi that is 
   reflected on the coplanaratiy and pT distributions. The difference in phi 
   comes from the fact that experimentally there are some dead regions in the 
   azimuthal range of the RTPC (the locations can be figured out from figure 
   2.27) where the 4He is not reconstructed if it passes these regions.  These 
   dead regions are not implemented in the fastmc for the moment. Of course 
   implementing these regions is very important if we look for measuring the 
   cross sections as our observables, while most of such acceptance issues 
   cancel in the case of the asymmetries.}\\

17) Page 69, first paragraph:  Is the timing information between the electron 
and the proton included? Are there any timing cuts between the electron and 
proton?
\textcolor{blue}{ We do apply a timing cut between the electron and the proton 
   through $\Delta \beta$ cut which is defined in equation 3.4. There the 
   $t_{TOF}$ is the difference between the time at the vertex of the electron 
and the time of the proton.}\\

18) Page 72, figure 4.8: Why is there such a big discrepancy between the 
experimental and simulated data for e'p gamma: missing E  and  e'gamma: missing 
$M^{2}$ in the case of the proton?  There is no similar discrepancy in the 
coherent case for He4, see figure 4.4?

\textcolor{blue}{ See the answer to comment \#31 of the second reviewer.}\\

19) Page 77-78, (Systematic: DVCS selection cuts): You are barely changing your 
statistics moving out from a 2 sigma cut. To truly show that your cuts are 
sufficient and don't influence the results, you should do something more 
drastic. It would be much more convincing if , for example, you would compare 
the results within a 1 sigma range (inner ~66$\%$ of events) with the results 
between 1 sigma and 3 sigma (outer ~33$\%$ of events).\\
 \textcolor{blue}{Included in the answer of the next question.}\\

20) Page 86:\\
  a) It would be nice if you could give the chi2 and error on the fit.\\
  b) Have you tried fitting the spectra including the cos(2phi) term? How 
strongly does the minimizer prefer using the simple 2-parameter form from 
equation 5.6?\\

\textcolor{blue}{ Referring to comment 38 of the 2nd reviewer. We were taking 
the same acceptance R for the different cuts. In the following we show the 
corresponding R for each cut width, where similar changes in the cut width are 
applied in the dominator and the numerator of R. Regarding comment 19 of the 
3rd reviewer, we take cuts from 1 to 5 $\sigma$.  The cuts are shown in figure 
\ref{fig:MM2_sys_cuts} and the corresponding acceptance ratios are shown in 
figure \ref{fig:R_sys_plot}. We also turn to fit our beam-spin asymmetry 
signals with the full expression ($\frac{\alpha sin(\phi)}{1 + \beta cos(\phi) 
+ \eta cos(2\phi)}$). Figure \ref{fig:alu_phi_sigmas} shows the reconstructed 
bean-spin asymmetries as a function of $\phi$ integrated over Q2, xB , and -t 
for the coherent and the incoherent DVCS channels. In Figures 
\ref{fig:sys_fit_alpha}, \ref{fig:sys_fit_beta}, \ref{fig:sys_fit_eta}, and 
\ref{fig:sys_fit_chi2} we show $\alpha$, $\beta$, $\eta$, and $\chi^{2}$ of the 
fits as a function of the cut width for the coherent and the incoherent 
channels. The beam-spin asymmetry at $\phi = 90 ^{\circ}$ ($= 
\frac{\alpha}{1-eta}$) is shown as a function of the cut size for both DVCS 
channels in figure \ref{fig:sys_fit_Alu}. }

\begin{figure}[h!]
\hspace{-1.0cm}
   \includegraphics[height=7.2cm]{fig/e4Hegamma_M2_Mis_sig.png}
   \includegraphics[height=7.2cm]{fig/epgamma_M2_Mis_sig.png}
   \caption{The applied cuts on the missing mass squared  of the coherent 
(right) and the incoherent DVCS channels in order to estimate the systematic 
uncertainties stemming from the DVCS selection cuts. }
\label{fig:MM2_sys_cuts}
\end{figure}

\begin{figure}[h!]
   \includegraphics[height=6.2cm]{fig/e4Hegamma_e4Hepi0_Phi_2.png}
   \includegraphics[height=6.2cm]{fig/epgamma_eppi0_Phi.png}
   \caption{Coherent (right) and incoherent (left) acceptance ratios 
corresponding to the different cuts shown in figure \ref{fig:MM2_sys_cuts}. }
\label{fig:R_sys_plot}
\end{figure}

\begin{figure}[h!]
   \includegraphics[height=7.2cm]{fig/BSA_Coherent_sigmas.png}
   \includegraphics[height=7.2cm]{fig/BSA_InCoherent_sigmas.png}
   \caption{ Integrated coherent (right) and incoherent (left) beam-spin 
asymmetry signals as a function of the angle $\phi$. The different colored 
points indicate the different cuts shown in figure \ref{fig:MM2_sys_cuts}. The 
colored lines are fits to the data points of the form $\frac{\alpha 
sin(\phi)}{1 + \beta cos(\phi) + \eta cos(2\phi)}$. }
\label{fig:alu_phi_sigmas}
\end{figure}

\begin{figure}[h!]
   \includegraphics[height=6.2cm]{fig/coh_alpha_Nsig.png}
   \includegraphics[height=6.2cm]{fig/incoh_alpha_Nsig.png}
   \caption{The coherent (left) and incoherent (right) $\alpha$ parameter of 
the fits as a function of cut width.  }
\label{fig:sys_fit_alpha}
\end{figure}

\begin{figure}[h!]
   \includegraphics[height=6.2cm]{fig/coh_beta_Nsig.png}
   \includegraphics[height=6.2cm]{fig/incoh_beta_Nsig.png}
   \caption{The coherent (left) and incoherent (right) $\beta$ parameter of the 
fits as a function of cut width.  }
\label{fig:sys_fit_beta}
\end{figure}

\begin{figure}[h!]
   \includegraphics[height=6.2cm]{fig/coh_eta_Nsig.png}
   \includegraphics[height=6.2cm]{fig/incoh_eta_Nsig.png}
   \caption{The coherent (left) and incoherent (right) $\eta$ parameter of the 
fits as a function of cut width.  }
\label{fig:sys_fit_eta}
\end{figure}

\begin{figure}[h!]
   \includegraphics[height=6.2cm]{fig/coh_chi2_Nsig.png}
   \includegraphics[height=6.2cm]{fig/incoh_chi2_Nsig.png}
   \caption{The coherent (left) and incoherent (right) $\chi^{2}$ parameter of 
the fits as a function of cut width.}
\label{fig:sys_fit_chi2}
\end{figure}

\begin{figure}[h!]
   \includegraphics[height=6.2cm]{fig/coh_Alu_Nsig.png}
   \includegraphics[height=6.2cm]{fig/incoh_Alu_Nsig.png}
   \caption{The coherent (left) and incoherent (right) beam-spin asymmetry at 
$\phi = 90 ^{\circ}$. }
\label{fig:sys_fit_Alu}
\end{figure}

  c) How sensitive are the fit results to your binning? You could investigate 
by e.g., adding/removing a bin in phi, or  by shifting the bin edges. (Or you 
could remove any bias introduced by the choice of binning by doing an unbinned 
fit...)\\

21) Page 91: you do need to quantify 'significant trends'. For example by 
showing how much better a fit with a simple A1 + A2*x works as compared to just 
a fit of a constant.\\
\textcolor{red}{To do at the very end.}

22) Page 92, third paragraph, last sentence: not true, within errors the values 
are compatible with each other!\\
\textcolor{red}{To modify at the very end.}

23) In summary, the analysis seems sound and clearly a lot of work has gone 
into it, but to be fully convincing more checks are needed in my opinion.  The 
key observables presented here are beam spin asymmetries which are more 
forgiving given that many of the systematic errors cancel.  However, I have yet 
to see solid systematic studies performed on the stability of the final results 
with respect to selection cuts and exclusivity cuts.

 a) A systematic study of the phi dependence of the He4 asymmetry seen by the 
 left side and the right side of the RTPC need to be carried out.\\
\textcolor{blue}{ The reconstructed asymmetries in each module of the RTPC are 
shown in figure \ref{fig:coherent_alu_sides}. In terms of the exclusivity 
distributions, see figure \ref{fig:sides_rtpc_exclusivity}, the performance of 
the two sides of the RTPC are almost similar.}\\

\begin{figure}[h!]
   \centering 
\includegraphics[height=14.2cm]{fig/all_coh_exc_cuts_final_sides.png} 
\caption{The distributions of the exclusive variables of the identified 
coherent DVCS events in the individual modules of the RTPC.}                                    
\label{fig:sides_rtpc_exclusivity}                                   
\end{figure}

 b) A good justification of the cuts ranges used is not always provided. The 
rejection efficiency of the cuts is not determined systematically. Of course, 
the statistical and systematic errors will depend on these cuts and the change 
of the physics results needs to be tested against the range of these cuts. \\
\textcolor{blue}{ Point raised and answered in Q47 of Reviewer 1. }\\

c) The stability of the physics results needs to be tested more meaningfully 
(see above comment at page 77-78).\\
\textcolor{blue}{ Point raised and answered in Q19.}\\

d) I have no comments on the physics interpretation discussed in this note 
until I am confident about the stability of the results.\\
\textcolor{blue} { To be updated at the very end}.\\

\newpage
\newpage
\newpage
\newpage
\newpage
\section*{ALU tables}
\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
         \hline
         1.143 & 0.136 & 0.096 & 23.23927  & 0.1247296  $\pm$  0.08549987 $\pm$ 
0.005198194 \\
         1.143 & 0.136 & 0.096 & 59.48556  & 0.3459717  $\pm$  0.07314284 $\pm$   
0.01733864  \\
         1.143 & 0.136 & 0.096 & 98.24482  & 0.3662185  $\pm$  0.09123816 $\pm$   
0.02086274  \\
         1.143 & 0.136 & 0.096 & 139.8573  & 0.123654   $\pm$  0.1369718  $\pm$   
0.007644888 \\
         1.143 & 0.136 & 0.096 & 177.6156  & 0.1881762  $\pm$  0.1425249  $\pm$   
0.01204172  \\
         1.143 & 0.136 & 0.096 & 219.9521  & -0.1284634 $\pm$  0.1201698  $\pm$   
0.008207119 \\
         1.143 & 0.136 & 0.096 & 263.1257  & -0.3533904 $\pm$  0.09727483  
$\pm$   0.02156403  \\
         1.143 & 0.136 & 0.096 & 302.3684  & -0.1883949 $\pm$  0.07858033  $\pm$   0.01054965  \\
         1.143 & 0.136 & 0.096 & 338.4607  & -0.3627951 $\pm$  0.0780912   $\pm$   0.01790232  \\
         \hline

         1.423 & 0.172 & 0.099 & 19.93889  & 0.1760962  $\pm$ 0.06994611  $\pm$ 
0.007186426   \\
         1.423 & 0.172 & 0.099 & 57.30933  & 0.3273063  $\pm$ 0.07332903  $\pm$ 0.01625548    \\
         1.423 & 0.172 & 0.099 & 95.76019  & 0.3951926  $\pm$ 0.1072231   $\pm$ 0.02236637    \\
         1.423 & 0.172 & 0.099 & 138.3863   & 0.1724817  $\pm$ 0.1474493   
$\pm$ 0.01064165    \\
         1.423 & 0.172 & 0.099 & 180.1999  & 0.3134116  $\pm$ 0.174575    $\pm$ 
0.02007781\\
         1.423 & 0.172 & 0.099 & 219.4606  & -0.2137216 $\pm$ 0.1650798   $\pm$ 0.01365754    \\
         1.423 & 0.172 & 0.099 & 262.8408  & -0.3995619 $\pm$ 0.1171428   $\pm$ 0.02439264    \\
         1.423 & 0.172 & 0.099 & 302.7633  & -0.3371412 $\pm$ 0.07239325  $\pm$ 0.01885809    \\
         1.423 & 0.172 & 0.099 & 337.9644  & -0.1104303 $\pm$ 0.07089989  $\pm$ 0.005460803   \\

         \hline
         1.902 & 0.224 & 0.107 &    20.63179 &  0.1234387 $\pm$   0.06716204 
$\pm$   0.005060101   \\
         1.902 & 0.224 & 0.107 &    56.56459 &  0.3228563 $\pm$   0.06874834 $\pm$   0.01598409    \\
         1.902 & 0.224 & 0.107 &    96.48    &  0.2124576 $\pm$   0.1092699  $\pm$    0.01204736   \\
         1.902 & 0.224 & 0.107 &    139.5199 &  0.1641143 $\pm$   0.1786647  $\pm$    0.01014158   \\
         1.902 & 0.224 & 0.107 &    179.4707 & -0.1374314 $\pm$   0.2300651  $\pm$    0.008801557  \\
         1.902 & 0.224 & 0.107 &    221.9652 & -0.1313449 $\pm$   0.1867839  $\pm$    0.008381788  \\
         1.902 & 0.224 & 0.107 &    262.5326 & -0.2970555 $\pm$   0.1203578  $\pm$    0.01814375   \\
         1.902 & 0.224 & 0.107 &    303.679  & -0.1723132 $\pm$   0.0794609  $\pm$    0.009613363  \\
         1.902 & 0.224 & 0.107 &    339.1609 & -0.1499256 $\pm$   0.06416965 $\pm$   0.007375924   \\

      \hline 
      \hline
      \end{tabular}
      \caption{ Coherent ALU in Q2 bins}
      \label{table:Coh_Q2_BSA}
   \end{center}
\end{table}

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
        1.164 & 0.132 & 0.095 & 25.00918 & -0.01089098 $\pm$ 0.1093718   $\pm$   
         0.000458874        \\
        1.164 & 0.132 & 0.095 & 60.37537 & 0.3737458   $\pm$ 0.07030024  $\pm$   0.01879876       \\
        1.164 & 0.132 & 0.095 & 98.36012 & 0.4043316   $\pm$ 0.08467823  $\pm$   0.02304085       \\
        1.164 & 0.132 & 0.095 & 140.2482 & 0.2465853   $\pm$ 0.1273109   $\pm$   0.01525331       \\
        1.164 & 0.132 & 0.095 & 177.0902 & 0.2375646   $\pm$ 0.1356063   $\pm$   0.01519848       \\
        1.164 & 0.132 & 0.095 & 218.9657 & -0.1073686  $\pm$ 0.1144325   $\pm$   0.006862974      \\
        1.164 & 0.132 & 0.095 & 262.7748 & -0.3805058  $\pm$ 0.08938742  $\pm$   0.02323176       \\
        1.164 & 0.132 & 0.095 & 301.4627 & -0.14755    $\pm$ 0.07265177  $\pm$   0.008283367      \\
        1.164 & 0.132 & 0.095 & 336.3236 & -0.3183937  $\pm$ 0.09471679  $\pm$   0.01585399       \\

         \hline
        1.439 & 0.17 & 0.099 &  21.27081  & 0.2034567  $\pm$  0.06758651  $\pm$  
0.008374507     \\
        1.439 & 0.17 & 0.099 &  56.76747  & 0.2169678  $\pm$  0.07229423  $\pm$  0.01075096      \\
        1.439 & 0.17 & 0.099 &  96.06215  & 0.249271   $\pm$  0.1107664   $\pm$  0.01411916      \\
        1.439 & 0.17 & 0.099 &  137.9266  & 0.1647911  $\pm$  0.1437837   $\pm$  0.01016048      \\
        1.439 & 0.17 & 0.099 &  180.9459  & 0.04356753 $\pm$  0.1729548   $\pm$  0.002791833     \\
        1.439 & 0.17 & 0.099 &  221.1382  & -0.2181618 $\pm$  0.1698173   $\pm$  0.01392861      \\
        1.439 & 0.17 & 0.099 &  264.1321  & -0.2657665 $\pm$  0.1185378   $\pm$  0.01619059      \\
        1.439 & 0.17 & 0.099 &  302.8373  & -0.3964279 $\pm$  0.07400956  $\pm$  0.02216967      \\
        1.439 & 0.17 & 0.099 &  337.9737  & -0.2096681 $\pm$  0.06842138  $\pm$  0.01036772      \\

         \hline
        1.844 & 0.225 & 0.107 & 19.58073  & 0.1554335   $\pm$   0.0628847   
$\pm$   0.006328427  \\
        1.844 & 0.225 & 0.107 &   56.29838  & 0.4152198   $\pm$   0.07433955  $\pm$   0.02053361 \\
        1.844 & 0.225 & 0.107 &   95.70361  & 0.2737049   $\pm$   0.1221503   $\pm$   0.01548828 \\
        1.844 & 0.225 & 0.107 &  139.5136  & -0.1539183  $\pm$   0.2139162   $\pm$   0.009511429 \\
        1.844 & 0.225 & 0.107 &   180.1244  & 0.1652893   $\pm$   0.2879629   $\pm$   0.01058847 \\
        1.844 & 0.225 & 0.107 &  222.8838  & -0.2355333  $\pm$   0.2105884   $\pm$   0.0150224   \\
        1.844 & 0.225 & 0.107 &  261.1443  & -0.3851749  $\pm$   0.1436202   $\pm$   0.0235777   \\
        1.844 & 0.225 & 0.107 &  304.757  -& 0.1531414   $\pm$   0.08530942  $\pm$   0.008517339 \\
        1.844 & 0.225 & 0.107 &  339.9749  & -0.09807582 $\pm$   0.06178372  $\pm$   0.00480806  \\

         \hline  
         \hline
      \end{tabular}
      \caption{Coherent ALU in xB bins}
      \label{table:Coh_xB_BSA}
   \end{center}
\end{table}

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\

         \hline
           1.36 & 0.160 & 0.080 & 21.65936  & 0.191738   $\pm$ 0.07672737  
$\pm$  0.007911716  \\
           1.36 & 0.160 & 0.080 &  57.55693  & 0.3027442  $\pm$ 0.06844172  $\pm$  0.01505127  \\
           1.36 & 0.160 & 0.080 &  96.99456  & 0.386873   $\pm$ 0.09974605  $\pm$  0.02196743  \\
           1.36 & 0.160 & 0.080 &  138.0931  & 0.1068763  $\pm$ 0.1481201   $\pm$  0.006591219 \\
           1.36 & 0.160 & 0.080 &  178.9474  & 0.3560828  $\pm$ 0.1622455   $\pm$  0.02279972  \\
           1.36 & 0.160 & 0.080 &  221.7811  & -0.1575038 $\pm$ 0.1428135   $\pm$  0.01005219  \\
           1.36 & 0.160 & 0.080 &  265.1648  & -0.4574556 $\pm$ 0.1123913   $\pm$  0.02782067  \\
           1.36 & 0.160 & 0.080 &  300.928   & -0.2462821 $\pm$  0.08067071 $\pm$   0.01384662 \\
           1.36 & 0.160 & 0.080 &  340.2102  & -0.1938488 $\pm$ 0.06732494  $\pm$  0.009493476 \\

         \hline
           1.507 & 0.179 & 0.094 & 20.86336 &  0.1670261  $\pm$ 0.07457232  
$\pm$  0.006857072 \\
           1.507 & 0.179 & 0.094 &  56.0533  & 0.3557391   $\pm$ 0.07177428  $\pm$  0.01757378 \\
           1.507 & 0.179 & 0.094 &  96.89244 &  0.180321   $\pm$ 0.1052948   $\pm$  0.01023623 \\
           1.507 & 0.179 & 0.094 &  141.685  & 0.05132467  $\pm$ 0.1618232   $\pm$  0.003181041\\
           1.507 & 0.179 & 0.094 &  177.7203 &  -0.2658653 $\pm$ 0.1840261   $\pm$  0.01701399 \\
           1.507 & 0.179 & 0.094 &  221.0472 &  -0.1237617 $\pm$ 0.1692357   $\pm$  0.007902008\\
           1.507 & 0.179 & 0.094 &  262.4797 &  -0.173583  $\pm$ 0.111135    $\pm$  0.01060312 \\
           1.507 & 0.179 & 0.094 & 303.5025 &  -0.2042846 $\pm$ 0.0814908   $\pm$  0.01140279  \\
           1.507 & 0.179 & 0.094 & 337.9422 &  -0.1527353 $\pm$ 0.07303888  $\pm$  0.007553509 \\

         \hline

           1.610 & 0.193 & 0.127 & 20.94824 &  0.04717589 $\pm$ 0.07199532 
         $\pm$ i0.001937809   \\
           1.610 & 0.193 & 0.127 &59.5986  & 0.3470424   $\pm$ 0.07684609 $\pm$ 0.01740037     \\
           1.610 & 0.193 & 0.127 &96.79543 &  0.3991681  $\pm$ 0.102308   $\pm$ 0.02265366     \\
           1.610 & 0.193 & 0.127 &138.4498 &  0.2740809  $\pm$ 0.1495366  $\pm$ 0.01691157     \\
           1.610 & 0.193 & 0.127 &179.5052 &  0.3297299  $\pm$ 0.1629695  $\pm$ 0.02111728     \\
           1.610 & 0.193 & 0.127 &218.6472 &  -0.1422435 $\pm$ 0.1447941  $\pm$ 0.009093639    \\
           1.610 & 0.193 & 0.127 &261.193  & -0.4233491  $\pm$ 0.1116738  $\pm$ 0.02591248     \\
           1.610 & 0.193 & 0.127 &303.6351 &  -0.2608586 $\pm$ 0.07153079 $\pm$ 0.01455514     \\
           1.610 & 0.193 & 0.127 &337.479  & -0.2039268  $\pm$ 0.07466683 $\pm$ 0.01010503     \\

         \hline                   
         \hline
      \end{tabular}
      \caption{Coherent ALU in -t bins}
      \label{table:Coh_t_BSA}
   \end{center}
\end{table}

% incoherent channel

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
         \hline

 1.395 & 0.166 & 0.407  & 20.99582 & 0.05948851  $\pm$ 0.04387614  $\pm$ 
0.002545615    \\
 1.395 & 0.166 & 0.407  & 61.74789 & 0.05987977  $\pm$ 0.04714287  $\pm$ 
0.004040185    \\
 1.395 & 0.166 & 0.407  & 95.61221 & 0.1799428   $\pm$ 0.04880652  $\pm$ 0.0147708      \\
 1.395 & 0.166 & 0.407  & 139.5363 & 0.08171111  $\pm$ 0.06090302  $\pm$ 0.007605015    \\
 1.395 & 0.166 & 0.407  & 182.201  &0.08009554   $\pm$ 0.07427192  $\pm$ 0.007619131    \\
 1.395 & 0.166 & 0.407  & 219.8818 & -0.01298693 $\pm$ 0.06771097  $\pm$ 0.00116723     \\
 1.395 & 0.166 & 0.407  & 258.5257 & -0.13608    $\pm$ 0.04652703  $\pm$ 0.01056183     \\
 1.395 & 0.166 & 0.407  & 303.4791 & -0.1156886  $\pm$ 0.03632167  $\pm$ 0.006314795    \\
 1.395 & 0.166 & 0.407  & 337.5902 & -0.03337033 $\pm$ 0.0466729   $\pm$ 0.001028396    \\

         \hline
  1.886 & 0.233 & 0.499 & 20.36902 & -0.00550785  $\pm$ 0.03554479  $\pm$  
0.0002332663   \\
  1.886 & 0.233 & 0.499 & 59.51454 & 0.0865409    $\pm$ 0.04730011  $\pm$  0.00573937     \\
  1.886 & 0.233 & 0.499 & 96.27168 & 0.1056762    $\pm$ 0.05415594  $\pm$  0.008699009    \\
  1.886 & 0.233 & 0.499 & 140.2293 & 0.2104464    $\pm$ 0.08284055  $\pm$  0.01960796     \\
  1.886 & 0.233 & 0.499 & 179.6974 & -0.006023816 $\pm$ 0.1001192   $\pm$  0.0005737056   \\
  1.886 & 0.233 & 0.499 & 221.8638 & -0.3006683   $\pm$ 0.09505653  $\pm$  0.02688511     \\
  1.886 & 0.233 & 0.499 & 260.5396 & -0.08288381  $\pm$ 0.0676998   $\pm$  0.006364218    \\
  1.886 & 0.233 & 0.499 & 303.6075 & -0.1980294   $\pm$ 0.0489431   $\pm$  0.01079362     \\
  1.886 & 0.233 & 0.499 & 338.5772 & -0.02449678  $\pm$ 0.05217832  $\pm$  0.0007361083   \\

         \hline
  2.338 & 0.29 & 0.521  & 20.54167 & 0.07520706  $\pm$   0.03409327  $\pm$ 
0.003194271   \\
  2.338 & 0.29 & 0.521  & 57.56577 & 0.1583533   $\pm$   0.04763939  $\pm$ 0.01033978    \\
  2.338 & 0.29 & 0.521  & 95.08678 & 0.07038454  $\pm$   0.06116666  $\pm$ 0.005764509   \\
  2.338 & 0.29 & 0.521  & 140.4598 & 0.061577    $\pm$   0.1034334   $\pm$ 0.005739368   \\
  2.338 & 0.29 & 0.521  & 182.4113 & -0.06731816 $\pm$   0.1393835   $\pm$ 0.006402942   \\
  2.338 & 0.29 & 0.521  & 225.0168 & -0.006314793$\pm$   0.1269017   $\pm$ 0.0005598014  \\
  2.338 & 0.29 & 0.521  & 260.9166 & -0.249064   $\pm$   0.07753102  $\pm$ 0.01908511    \\
  2.338 & 0.29 & 0.521  & 303.3817 & -0.2126162  $\pm$   0.05908072  $\pm$ 0.01161831    \\
  2.338 & 0.29 & 0.521  & 339.1649 & -0.06832607 $\pm$   0.0593668   $\pm$ 0.002021729   \\

         \hline
  3.098 &0.379 & 0.65  & 20.00771 & 0.1066541  $\pm$   0.03223103  $\pm$   
0.004489826   \\
  3.098 &0.379 & 0.65  & 57.14716 & 0.0941076  $\pm$   0.04804565  $\pm$   0.006123894   \\
  3.098 &0.379 & 0.65  & 94.59164 & 0.1305121  $\pm$   0.06923002  $\pm$   0.01066595    \\
  3.098 &0.379 & 0.65  & 137.7186 & 0.05354516 $\pm$   0.1440831   $\pm$   0.00496877    \\
  3.098 &0.379 & 0.65  & 180.4945 & -0.3925136 $\pm$   0.2078121   $\pm$   0.03736982    \\
  3.098 &0.379 & 0.65  & 227.2433 & 0.0826614  $\pm$   0.1787858   $\pm$   0.007280692   \\
  3.098 &0.379 & 0.65  & 263.6608 & -0.1950766 $\pm$   0.07945851  $\pm$   0.01472067    \\
  3.098 &0.379 & 0.65  & 303.4889 & -0.1567501 $\pm$   0.03740481  $\pm$   0.008555163   \\
  3.098 &0.379 & 0.65  & 340.4058 & -0.0524533 $\pm$   0.03117202  $\pm$   0.001500876   \\

         \hline
         \hline
      \end{tabular}
      \caption{Incoherent ALU in Q2 bins}
      \label{table:InCoh_Q2_BSA}
   \end{center}
\end{table}

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
         \hline 
 1.425 & 0.162 & 0.397 & 20.97013 & 0.08626376   $\pm$   0.04639585  $\pm$ 
0.003689821  \\
 1.425 & 0.162 & 0.397 & 62.6421  &0.04930313    $\pm$   0.04597865  $\pm$ 0.003348979  \\
 1.425 & 0.162 & 0.397 & 95.82162 & 0.1224201    $\pm$   0.04586875  $\pm$ 0.01005802   \\
 1.425 & 0.162 & 0.397 & 139.6892 & 0.08754554   $\pm$   0.05613428  $\pm$ 0.008150009  \\
 1.425 & 0.162 & 0.397 & 181.2826 & 0.08689862   $\pm$   0.06698238  $\pm$ 0.008270208  \\
 1.425 & 0.162 & 0.397 & 219.4891 & -0.0375365   $\pm$   0.06384645  $\pm$ 0.003377014  \\
 1.425 & 0.162 & 0.397 & 258.6045 & -0.1130657   $\pm$   0.04491125  $\pm$ 0.008771949  \\
 1.425 & 0.162 & 0.397 & 303.3676 & -0.08717632  $\pm$   0.03808702  $\pm$ 0.004764464  \\
 1.425 & 0.162 & 0.397 & 337.2495 & -0.001292913 $\pm$   0.05197389  $\pm$ 4.018625e-05 \\

         \hline
  1.922 & 0.227 & 0.418 & 21.57308 & -0.008430847 $\pm$  0.03822631  $\pm$ 
0.0003641738  \\
  1.922 & 0.227 & 0.418 & 59.16565 & 0.111757     $\pm$  0.04526789  $\pm$ 0.007391354   \\
  1.922 & 0.227 & 0.418 & 96.43508 & 0.1141028    $\pm$  0.05198208  $\pm$ 0.009399181   \\
  1.922 & 0.227 & 0.418 & 140.9017 & 0.1548699    $\pm$  0.08123609  $\pm$ 0.0144446     \\
  1.922 & 0.227 & 0.418 & 181.8854 & -0.0481868   $\pm$  0.1001495   $\pm$ 0.004584565   \\
  1.922 & 0.227 & 0.418 & 222.8398 & -0.2544383   $\pm$  0.0893361   $\pm$ 0.02269204    \\
  1.922 & 0.227 & 0.418 & 260.2223 & -0.1167433   $\pm$  0.05887855  $\pm$ 0.008979522   \\
  1.922 & 0.227 & 0.418 & 303.2291 & -0.2337499   $\pm$  0.04409228  $\pm$ 0.01279513    \\
  1.922 & 0.227 & 0.418 & 337.305  &-0.04801249   $\pm$  0.05092665  $\pm$ 0.001490256   \\

         \hline
   2.354 & 0.287 & 0.492 & 20.72653 & 0.04639471  $\pm$    0.00197654  $\pm$  
0.03368072   \\
   2.354 & 0.287 & 0.492 & 58.45404 & 0.1237376   $\pm$    0.00813755  $\pm$  0.04677291   \\
   2.354 & 0.287 & 0.492 & 94.51698 & 0.1315813   $\pm$    0.01074982  $\pm$  0.06113826   \\
   2.354 & 0.287 & 0.492 & 138.9117 & 0.1560256   $\pm$    0.01450708  $\pm$  0.1093031    \\
   2.354 & 0.287 & 0.492 & 180.8249 & -0.2729523  $\pm$    0.02598283  $\pm$  0.1502588    \\
   2.354 & 0.287 & 0.492 & 226.2591 & 0.1262439   $\pm$    0.01115158  $\pm$  0.1231889    \\
   2.354 & 0.287 & 0.492 & 261.4329 & -0.3136316  $\pm$    0.02396477  $\pm$  0.07142533   \\
   2.354 & 0.287 & 0.492 & 303.6894 & -0.1473891  $\pm$    0.00802600  $\pm$  0.04010664   \\
   2.354 & 0.287 & 0.492 & 338.8274 & -0.03638465 $\pm$    0.00108621  $\pm$  0.04154249   \\

         \hline
   2.987 & 0.390 & 0.714 & 19.37729 & 0.1023275  $\pm$   0.004262096  $\pm$   
0.03068386   \\
   2.987 & 0.390 & 0.714 & 55.29714 & 0.1178224  $\pm$   0.007550191  $\pm$   0.0549492    \\
   2.987 & 0.390 & 0.714 & 93.98511 & 0.1667466  $\pm$   0.01359089   $\pm$   0.09110539   \\
   2.987 & 0.390 & 0.714 & 134.9596 & -0.139577  $\pm$   0.01288957   $\pm$   0.2491587    \\
   2.987 & 0.390 & 0.714 & 181.8623 & -1.873885  $\pm$   0.1782864    $\pm$   2.72237      \\
   2.987 & 0.390 & 0.714 & 230.3936 & -0.3244869 $\pm$   0.02830547   $\pm$   0.3535998    \\
   2.987 & 0.390 & 0.714 & 265.493  &-0.1138915  $\pm$   0.008503447  $\pm$   0.09607017   \\
   2.987 & 0.390 & 0.714 & 303.6668 & -0.1628255 $\pm$   0.008868856  $\pm$   0.03647585   \\
   2.987 & 0.390 & 0.714 & 341.0907 & -0.0611224 $\pm$   0.001715804  $\pm$   0.02745835   \\

         \hline
         \hline
      \end{tabular}
      \caption{Incoherent ALU in xB bins}
      \label{table:InCoh_xB_BSA}
   \end{center}
\end{table}

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\

         \hline
  1.823 & 0.213 & 0.145 & 21.76232 & 0.05295778   $\pm$  0.002294523  $\pm$  
0.04069827  \\
   1.823 & 0.213 & 0.145 & 58.58495 & 0.1219361    $\pm$  0.008027474  $\pm$  0.04764173  \\
   1.823 & 0.213 & 0.145 & 96.96136 & 0.1173358    $\pm$  0.009686957  $\pm$  0.04541699  \\
   1.823 & 0.213 & 0.145 & 140.7066 & 0.1817539    $\pm$  0.01694703   $\pm$  0.06006007  \\
   1.823 & 0.213 & 0.145 & 181.0183 & -0.001970789 $\pm$  0.0001875857 $\pm$  0.07600509  \\
   1.823 & 0.213 & 0.145 & 220.405  &-0.04819504   $\pm$  0.004325879  $\pm$  0.06647841  \\
   1.823 & 0.213 & 0.145 & 260.7167 & -0.1293622   $\pm$  0.009923488  $\pm$  0.04629438  \\
   1.823 & 0.213 & 0.145 & 303.2256 & -0.1248732   $\pm$  0.006835643  $\pm$  0.03973616  \\
   1.823 & 0.213 & 0.145 & 337.1253 & -0.0568979   $\pm$  0.001773968  $\pm$  0.04461593  \\

         \hline
 2.127 & 0.255 & 0.282  & 21.13741 & 0.05676917  $\pm$   0.002434879  $\pm$  
0.03872277 \\
  2.127 & 0.255 & 0.282  & 59.88266 & 0.04066772  $\pm$   0.002704859  $\pm$  0.04482714 \\
  2.127 & 0.255 & 0.282  & 95.47925 & 0.1736134   $\pm$   0.0142431    $\pm$  0.052589   \\
  2.127 & 0.255 & 0.282  & 140.3364 & 0.05497469  $\pm$   0.005123015  $\pm$  0.07245594 \\
  2.127 & 0.255 & 0.282  & 181.9189 & -0.103328   $\pm$   0.009830611  $\pm$  0.08641265 \\
  2.127 & 0.255 & 0.282  & 221.125  &-0.08229461  $\pm$   0.007372876  $\pm$  0.08294356 \\
  2.127 & 0.255 & 0.282  & 259.4795 & -0.1175477  $\pm$   0.009077516  $\pm$  0.05100342 \\
  2.127 & 0.255 & 0.282  & 303.6039 & -0.1683549  $\pm$   0.009176586  $\pm$  0.03529877 \\
  2.127 & 0.255 & 0.282  & 338.8501 & -0.06212176 $\pm$   0.001853458  $\pm$  0.04171552 \\

         \hline
   2.308 & 0.284 & 0.490 & 20.40386 & 0.1444039   $\pm$    0.006119278   $\pm$  
0.03725259 \\
   2.308 & 0.284 & 0.490 & 59.94014 & 0.1145024   $\pm$    0.007619109   $\pm$  0.04516257 \\
   2.308 & 0.284 & 0.490 & 94.51028 & 0.1042987   $\pm$    0.008520657   $\pm$  0.05770054 \\
   2.308 & 0.284 & 0.490 & 137.4529 & 0.05629055  $\pm$    0.005221187   $\pm$  0.1013111  \\
   2.308 & 0.284 & 0.490 & 181.6079 & 0.2913442   $\pm$    0.02772291    $\pm$  0.1200124  \\
   2.308 & 0.284 & 0.490 & 225.4196 & -0.1115956  $\pm$    0.009881524   $\pm$  0.09789392 \\
   2.308 & 0.284 & 0.490 & 259.6316 & -0.2224212  $\pm$    0.01716233    $\pm$  0.05517074 \\
   2.308 & 0.284 & 0.490 & 302.5122 & -0.1288317  $\pm$    0.007108798   $\pm$  0.03097601 \\
   2.308 & 0.284 & 0.490 & 338.7144 & -0.03035411 $\pm$    0.0009088618  $\pm$  0.03626738 \\

         \hline
   2.406 & 0.308 & 0.90 & 20.23392 & 0.03616055   $\pm$   0.001528019  $\pm$   
0.03177921  \\
   2.406 & 0.308 & 0.90 & 57.19179 & 0.1434394    $\pm$   0.009337483  $\pm$   0.05685747  \\
   2.406 & 0.308 & 0.90 & 93.08909 & 0.08508241   $\pm$   0.006907134  $\pm$   0.1091959   \\
   2.406 & 0.308 & 0.90 & 131.5139 & -0.275777    $\pm$   0.02529905   $\pm$   0.4348743   \\
   2.406 & 0.308 & 0.90 & 177.2893 & 1.936221     $\pm$   0.1845638    $\pm$   0.6244698   \\ 
   2.406 & 0.308 & 0.90 & 226.5454 & -4.94355     $\pm$   0.4363171    $\pm$   10.50945    \\
   2.406 & 0.308 & 0.90 & 263.2745 & -0.1005967   $\pm$   0.007607858  $\pm$   0.1138163   \\
   2.406 & 0.308 & 0.90 & 304.5626 & -0.1565288   $\pm$   0.008438927  $\pm$   0.04279407  \\
   2.406 & 0.308 & 0.90 & 339.8646 & -0.0230393   $\pm$   0.0006690608 $\pm$   0.03586971  \\

         \hline
         \hline
      \end{tabular}
      \caption{Incoherent ALU in -t bins}
      \label{table:InCoh_t_BSA}
   \end{center}
\end{table}

### 2017-12-08 eg6-letters/NIM/EG6_RTPC_NIM.tex
more updates to the nim paper

@@
 
-After the ionization, the released electrons 
-drift to the cylindrical detection plane under the effect of the electric field. The 
-electrons released close to the cathode take the most time to reach the readout 
-pads, the cylindrical symmetry insures that this maximum drift distance is the 
-same for all tracks. We illustrate this in Figure~\ref{fig:RTPC_signals}, where 
-we depict a typical $^{4}$He track. By measuring the maximum time ($T_{Max}$), 
-we can therefore infer the drift speed of the electrons in the RTPC.\\
+After the ionization, the released electrons drift to the cylindrical detection 
+plane under the effect of the electric field. The electrons released close to 
+the cathode take the most time to reach the readout pads, and the cylindrical 
+symmetry ensures that this maximum drift distance is the same for all tracks.  
+We illustrate this in Figure~\ref{fig:RTPC_signals}, where we depict a typical 
+$^{4}$He track. Due to the non-perfect experimental conditions, in particular 
+possible contamination of our gas mixture, the drift speed changed during the 
+three months long experimental run\footnote{We had to increase the gas flow 
+   during the experiment due to a small leak in the RTPC, which concurred to 
+   the large shift of drift time observed around run number 61600. While our 
+   gas system was kept slightly over atmospheric pressure to limit 
+contamination from air or other external gases, it is likely that this leak was 
+the source of modification of the drift speed.}. This can be calibrated by 
+finding drift speed as function of experimental run-number. By measuring a 
+reference time, we can therefore infer the drift speed of the electrons in the 
+RTPC, by: $\textnormal{drift time} = \frac{\textnormal{drift path 
+length}}{\textnormal{drift speed}}$.
 
@@
 
-To measure the maximum drift time, we used the time profile of hits from 
-identified tracks shown in Figure~\ref{fig:TDC_profile}. We can clearly observe 
-the dropping edge expected from geometrical considerations. We define a value 
-$T_{Max/2}$ at which the dropping edge passes half the maximum number of hits 
+Figure~\ref{fig:TDC_profile} presents the time profile of hits from identified 
+tracks in one z-bin along the detector in one experimental run. We can clearly 
+observe the dropping edge expected from geometrical considerations. In order to 
+avoid the statistical fluctuations on finding the maximum drift time 
+($T_{max}$) from the time profile, we define a more stable value, i.e., 
+$T_{max/2}$, at which the dropping edge passes half the maximum number of hits 
 in the histogram. This value was measured in bins along the 200~mm RTPC's 
@@
 \includegraphics[scale=0.42]{hits_time_profile.pdf}
-\caption[]{Time distribution of the hits associated with a track in one 
+\caption[]{Time distribution of the hits in one z-bin along the RTPC in one 
 experimental run. Trigger time is defined as T=15, the time unit is the ALTRO 
-sampling time of 100~ns.} 
-\label{fig:TDC_profile}
+sampling time of 100~ns.} \label{fig:TDC_profile}
 \end{figure}
@@
 
-Due to the non perfect experimental conditions, in particular possible contamination 
-of our gas mixture, the drift speed changed during the three months long experimental 
-run\footnote{We had to increase the gas flow during the experiment due to a small leak 
-in the RTPC, which concurred to the large shift of drift time observed around 
-run number 61600. While our gas system was kept slightly over atmospheric 
-pressure to limit contamination from air or other external gases, it is likely 
-that this leak was the source of modification of the drift speed.}.  
-Figure~\ref{fig:Drift_run_number_1} shows the $T_{Max/2}$ values for individual 
+Figure~\ref{fig:Drift_run_number_1} shows the $T_{max/2}$ values for individual 
 runs (approximately 2 hours long). We observe significant change in the drift 
@@
 shown in Figure~\ref{fig:EVENT_adc_tdc}. The gain for each pad was calculated 
-as the ratio of the measured ADCs to the simulated deposited energy. Then, This 
+as the ratio of the measured ADCs to the simulated deposited energy. Then, this 
 set of the gains was applied to the experimental data. We noticed that some 

### 2017-12-08 eg6-letters/NIM/review-1/review-1.tex
more updates to the nim paper

@@
    make a quick calculation and use $T_{max}$ ~ 65 * 100ns and a drift length 
-   of ~ 3cm /cos(23°) ~ 7.5 cm I get a $v_{drift}$ ~ 1.15 cm/microsec << 5 
-   cm/microsec which is the average value of drift velocity in drift 
+   of ~ 3cm /cos(23$^{\circ}$) ~ 7.5 cm I get a $v_{drift}$ ~ 1.15 cm/microsec 
+   << 5 cm/microsec which is the average value of drift velocity in drift 
    chambers.\\
@@
 the simulations?\\
-\textcolor{blue}{ }
+\textcolor{red}{- The text has been updated to clarify the procedures.\\
+                - With T = 65*100~ns and drift length equal to 3cm/ 
+             cos(23$^{\circ}$, $v_{drift}$ = 0.501 cm/microsec which is 
+          consistent with our 0.61 cm/microsec from simulation. \\
+               - In deed, we use $delta_{t} = T_{max/2} - T_{min}$ in our 
+            reconstruction code.}
 

### 2017-12-08 eg6-letters/NIM/EG6_RTPC_NIM.tex
update the nim paper with Stepan's comments.

@@
 \linenumbers
+\usepackage{dblfloatfix}    % To enable figures at the bottom of page
 \begin{document}
@@
      central axis; it is a 292~mm~long, 6~mm diameter Kapton straw with a 
-     27~$\mu$m wall. The detector and the target are centered at 64~cm to the 
-     left of CLAS's center.
+     27~$\mu$m wall. The detector and the target are centered at 64~cm upstream 
+     of the CLAS center.
    \item The first gas gap covers the radial range from 3~mm to 20~mm. It is 
@@
 measured samples from active channels are reported, together with a channel 
-identifier and a timestamp, to the ROC application, that in turns sends them on 
+identifier and a timestamp, to the ROC application, that in turn sends them on 
 the main event builder. Readout from FECs occurs in ``block-transfer'' mode, 
@@
 system\footnote{In the original BoNuS system, the U2F readout controller had no 
-multi-event capability and used a USB connection rather than fiber optics for 
-readout. These factors limited the maximum readout rate from the BoNuS detector 
-to about 500 Hz.}. In order to read all the detector readout pads, four FEC 
-crates were used, each equipped with 6 boards, plus a ROC. A schematic of the 
-readout system, for a single crate, is reported in 
+   multi-event capability and used a USB connection rather than fiber optics 
+   for readout. These factors limited the maximum readout rate from the BoNuS 
+detector to about 500 Hz.}. In order to read all the detector readout pads, 
+four FEC crates were used, each equipped with 6 boards, plus a ROC. A schematic 
+of the readout system, for a single crate, is reported in 
 Figure~\ref{fig:ReadoutScheme}. This configuration permitted to reduce the dead 
@@
 of emission of the charge and its time of detection, and then refined our 
-result. Indeed, because of the magnetic field, the drift paths are not linear 
-in the RTPC, but the curvature was minimal and this process converged already 
-on the second iteration.
+result. Because of the magnetic field, the drift paths in RTPC are not linear 
+but the curvature is small and the refining  process converged already on the 
+second iteration.
 
@@
 \centering
-\includegraphics[scale=0.42]{FitResult_p2_11.pdf}
+\includegraphics[scale=0.46]{FitResult_p2_11.pdf}
 \caption{$\Delta \phi$ versus T distribution for tracks
@@
 1.269 GeV data from the end of the run period (shown in blue on 
-Figure~\ref{fig:Drift_run_number_1}). Interestingly, we found very similar 
-drift paths for the two data sets and concluded that any changes in the system 
-only significantly affected the drift speed.
+Figure~\ref{fig:Drift_run_number_1}). We found very similar drift paths for the 
+two data sets and concluded that any changes in the system only significantly 
+affected the drift speed.
 
@@
 
-\begin{figure}[tb]
+\begin{figure}[!t]
    \centering
@@
 
-\begin{figure*}[tp]
+\begin{figure*}[!h]
 \centering
@@
 
-\begin{figure}[tb!]\centering
+\begin{figure}[tb]
+   \centering
 \includegraphics[scale=0.25]{noisy_pad_before_rejection2.png}

### 2018-01-08 eg6-letters/NIM/EG6_RTPC_NIM.tex

--- 2017-11-08 eg6-letters/NIM/EG6_RTPC_NIM.tex
@@
 \begin{itemize}
-  \item The 6~atm $^4$He target extends along the beamline forming the detector 
-     central axis; it is a 292~mm~long, 6~mm diameter Kapton straw with a 
-     27~$\mu$m wall. The detector and the target are centered at 64~cm to the 
-     left of CLAS's center.
+  \item The 6~atm $^4$He target extends from -146~mm to 146~mm in z-direction 
+     with respect to the center of the detector forming the detector central 
+     axis. It is a 6~mm diameter Kapton straw with a 27~$\mu$m wall.
    \item The first gas gap covers the radial range from 3~mm to 20~mm. It is 

### 2018-01-08 eg6-letters/NIM/review-1/review-1.tex

--- 2017-11-16 eg6-letters/NIM/review-1/review-1.tex
@@
 \textcolor{red}{- Regarding the electric field, it was 2.8 kV/cm in BoNuS, does 
-anyone know our exact field in this gap?\\}
-\textcolor{blue}{- The gain of such GEM configuration has been studied by 
-   CERN's Gas Detector Development Group (Fabio Sauli, Progress with the Gas 
-   Electron Multiplier, 2nd Workshop on Advanced Transition Radiation Detectors 
-   for Accelerator and Space Applications (Bari, Sept. 4-7, 2003), Nucl. Instr. 
-   and Meth. A522(2004)93). The results, see the reference, demonstrate that 
-one should not simply add gains to each other for multilayer GEM 
-amplifications.  We did not evaluate precisely the overall gain in our chamber, 
-so we do not have a value for our RTPC GEM system at this point.}
+anyone know our exact field in this gap? Raph: This is indicated already, I am not sure what he
+means by "induction gap"\\}
+\textcolor{red}{We did not evaluate precisely the overall gain in our chamber.
+Can we quote a value from comparison with Bethe-Heitler or GEANT4?}
 
@@
    is passed then a noise level is subtracted? If so, how is it calculated?\\
-\textcolor{blue}{The oscillatory noise was removed just by rejecting all hits 
-from a channel if too many of its hits fall on the noise curve in a given 
-event. No threshold/pedestal concept, just hit rejection if it looks like 
-noise. }
+\textcolor{red}{Nathan, Can you work on it. }
 
@@
    times. Sum $dE_{i}$/Sum $dx_{i}$ is not equal to Sum ($dE_{i}/dx_{i}$).\\
-\textcolor{blue}{We actually did compute dEdx with  path-length and ADC- 
-truncations, and a linear fit to ADC vs path-length to get slope and fit 
-quality and dedx from fit. Unfortunately, it never seemed to give us much 
-improvement compared to Sum $dE_{i}$/Sum $dx_{i}$. }
+\textcolor{blue}{Maybe this would improve our calculations for dEdx by few 
+percent, but a precise hits ordering is needed to compute dEdx as you suggest, 
+which is not available in our setting.}
 

### 2018-01-08 1st_round_comments/1st_round_comments_final/comments.tex

--- 2017-12-07 1st_round_comments/1st_round_comments_final/Jan31_2016_comments.tex
@@
 \textcolor{blue}{
-   In equation 2.1, the charge of the particle (q) is missed. Regarding the 
+   In equation 2.1, the charge of the particle (q) is indeed missing. Regarding the 
 numerical calculations of $r_0$ for the elastic and the DVCS $^4$He, the 0.3 
-factor is missed only in these calculations while the charge issue is taken 
+factor is missing only in these calculations while the charge issue is taken 
 into account. In the reconstruction software, both issues are properly 
@@
 MAGBOLTZ Monte Carlo simulation. One can find the detailed procedure of 
-this first extraction in the BoNuS analysis note 
+a similar extraction in the BoNuS analysis note 
 (https://www.jlab.org/Hall-B/secure/bonus/publication/BonusAnal110117.pdf).  
@@
   The longest drift time depend on $z$ but is typically around 6.6 $\mu$s. 
-  Four is the number of the fired pads for each track, not the number of hits.  
+  Four is the number of the active pads for a track, not the number of hits.  
   This value has been found to be reasonable from simulation, it mainly help 
-  clean the sample and play very little role after other cuts. The time offset 
+  clean the sample and plays very little role after other cuts. The time offset 
   is 15 TDCs (1 TDC= 114 ns), the average drift velocity is 6.14 $\mu$m/ns and 
@@
    cut will eventually clean all unphysical results.}\\
-%  \textcolor{red}{Raph: Follow up on p49 bullet 4 of the note, you speak about 
-   %  "the  mechanical supports between the two model of the RTPC". Beyond the 
-   %  English, I remind you that there is not mechanical structure inside the 
-   %  drift region in the eg6 RTPC. Please correct!} \\
 
@@
 uncertainties, $(\sigma_{r}, \sigma_{\phi}, \sigma_{z}) = (0.53 mm, 2^{\circ}, 
-1.2 mm)$, were not derived from our data and were held fixed.} \\
-
+1.2 mm)$, were not derived from our data and were held fixed over all 
+calibration itterations.} \\
 \textcolor{blue}{Equation 2.2 needs the beam-spot constraint added in
-quadrature $\left(\frac{DOCA}{\sigma_r}\right)^2$ and the denominator adjusted
-accordingly $(N_{pts}-5)$. It has to be written in full form as: (changed in 
-the note as well).  }\\
+quadrature $\left(\frac{DOCA}{\sigma_r}\right)^2$ as follows (changed in 
+the note as well): }\\
 
@@
       \phi^{helix}_{i} }{\sigma_{\phi}}\right)^{2} + \left( \frac{z^{pt}_{i} - 
-      z^{helix}_{i} }{\sigma_{z} } \right)^{2}}{N_{pts} - 5}
+   z^{helix}_{i} }{\sigma_{z} } \right)^{2}}{N_{pts} - 4}
 \end{equation}
 }\\
-%  \textcolor{green}{Raph: I did a minor change in the equation, to clarify 
-%  that the beam spot term is not in the sum. To use in the note if you are 
-%  ok.} \\
 
@@
 additional work).\\
-\textcolor{blue}{We are indeed aware of this, this is why we do use theta cut
-as our main selection. Note also that $\delta\phi$ and $\delta z$ cuts have already
-been applied in Figure 2.13's $\delta\theta$.}\\
+\textcolor{blue}{We are indeed aware of this and we do use a $\Delta \theta$ cut
+as our main selection for this reason, which we believe is equivalent to your
+proposition. Note also that $\Delta\phi$ and 
+$\Delta z$ cuts have already been applied in Figure 2.13's $\Delta\theta$.}\\
 
@@
 Yes, this is related to the different resolutions of the corresponding CLAS sectors. 
-This effect is large because, the reaction products are produced back to back 
-results in small regions of overlapping acceptances of the RTPC and CLAS.  
+This effect is large because, the reaction products are emitted back to back 
+resulting in small regions of overlapping acceptances of the RTPC and CLAS.  
 In figure \ref{fig:W_sec}, we plot $W$ distributions corresponding to the 
-different sectors in CLAS, one can immediately see the differences of resolution. }\\
+different sectors in CLAS, one can immediately see the differences of resolution.}\\
 
@@
 $\Delta \phi$ at the anode (TDC = 15) is not equal to zero because there is a 
-drift in phi between the anode (the first GEM layer at radial distance equal to 
+drift in $\phi$ between the anode (the first GEM layer at radial distance equal to 
 60 mm) and the readout pads (at radial distance equal to 69mm). Regarding the 
 derivation, figure \ref{fig:drift_derive} shows a simple drawing explaining how 
-Eq. 2.9 has been derived.}\\
-\textcolor{green}{Raph: Equations in the drawing need to be replaced by text.}
+Eq. 2.9 can be derived.}\\
 
@@
    \centering
-   \includegraphics[height=12.5cm]{fig/drift_draw.png}
+   \includegraphics[height=6.5cm]{fig/deriv_R_drift.png}
    \caption{Schematic drawing shows how the radius of emmision (R) at each 
@@
 \end{figure}
+\textcolor{blue}{In figure \ref{fig:drift_derive}, the radial distance of the 
+   ionization point $k$, $R(TDC_{k})$, is equal to to the radial distance from 
+   the target to the cathode, $R_{Min}$, plus the radial distances ($\sum 
+   r_{i}$) that are caused by the drift from the first point of ionization at 
+   $TDC_{max}$ to the point $k$. In each TDC bin, the radial drift distance 
+($r_{i}$) is calculated as:}
+
+   \begin{equation}
+      r_{i} = \sqrt{DS^{2} - r_{i-1}  \bigg(\frac{\partial \Delta \phi} 
+      {\partial TDC}(TDC_i) \bigg)^{2} }
+\end{equation}
+\textcolor{blue}{Adding all the terms, $R(TDC_{k})$ is formulated as:}
+\begin{equation}
+   R (TDC_{k}) = R_{min} + \sum\limits_{i=TDC_{Max}}^{TDC_{k}} r_{i}
+\end{equation}
 
@@
 resolution except very close to threshold (see right panel of Figure 
-\ref{fig:energylosscorrection}).}
-\textcolor{blue}{In Fig. 2.29 the bands are just there to guide the eye. Since the
+\ref{fig:energylosscorrection}).} \\
+\textcolor{blue}{In Fig. 2.29 the lines are just there to guide the eye. Since the
 vertical scale has never been carefully calibrated, we always present it in
@@
 we noticed that some pads record lower ADCs than expected (issue shown in 
-figure 2.28) and noise. For these reasons, we wanted to make sure that the recorded 
+figure 2.28) and sometime noise. For these reasons, we wanted to make sure that the recorded 
 ADCs by a given pad are similar to the recorded ADCs recorded by another pad in 
@@
 \hspace{-0.5 cm}
-\includegraphics[height=11.5cm]{fig/dedx_ratio_elastic.png}
-\caption{The ratio between experimental dEdx and 
-the simulated ones for different regions along $z$ of the RTPC. The blue lines 
-are using the first method of extracting the gains (comparing the experimental 
-recorded dEdx to the expected values calculated from the Bethe-Block formula), 
-the violet lines are using the second method with a small fraction of our 
-elastic events, the green lines are using the 1st pass of the second method 
-(comparing simulation to data only) with all the elastic event sample and the 
-brown lines are using the gains extracted from the second method (both steps).}
+\includegraphics[height=11.5cm]{fig/dedx_ratio_elastic_NAB.png}
+\caption{The ratio between the experimental dEdx and the simulated ones for 
+   different regions along $z$ of the RTPC. The blue lines are using the first 
+   method of extracting the gains (comparing the experimental recorded dEdx to 
+   the expected values calculated from the Bethe-Block formula), the green 
+lines are using the 1st pass of the second method (comparing simulation to data 
+only) with all the elastic event sample and the brown lines are using the gains 
+extracted from the second method (both steps).}
 \label{fig:dedxre}
@@
 hits included are only those recorded by one example noisy pad and only when
-those hits were also included in a good track.} \\
+those hits were used in a good track.} \\
 
@@
 in figure \ref{fig:delta_p_z}. Figure \ref{fig:P_diff_z_correction} shows the 
-difference between the elastic 4He momentum the values from electron scattering 
+difference between the elastic 4He momentum and its calculated value 
+from the electron scattering 
 angle. A second test was performed by doubling the energy loss, which gives 
@@
 \includegraphics[height=9.2cm]{fig/nphe_1_sectors.png}
-\caption{Distribution of nphe emitted by electrons in the six sector of CLAS 
-before the CLAS trigger change at run 61732.}
+\caption{Distribution of nphe emitted by electrons in the six sector of CLAS.}
 \label{fig:nphe_1}
@@
 \textcolor{blue}{They are not implemented in this analysis as we deemed them
-insignificant for this low statistics asymmetry measurement, particularly since
-RTPC efficiency already shows a good agreement between LEFT/RIGHT in elastic scattering even
-without removing dead regions (see answer to R1Q28 below and Figure~\ref{fig:tpceff}).}\\
+insignificant for this low statistics asymmetry measurement.}\\
 
@@
 \textcolor{blue}{We seem to disagree there is a significant bump. However, if 
-   there are some neutrons, they will be well removed by the following 
-   exclusivity requirements. Also we want to point out the energy of the 
-   neutral particle we use are greater than 2 GeV.  At such energies the time 
+   there are some neutrons, they will be highly suppressed by the DVCS
+   exclusivity requirements. In particular we want to point out the energy of the 
+   neutral particle is always greater than 2 GeV. At such energies the time 
    of flight measurement from the EC is not good enough to separate neutrons 
-   from photons anyway (see Fig.  \ref{fig:sim_coh} and 
-\ref{fig:sim_incoh}).}\\
+   from photons anyway (see Fig. \ref{fig:sim_coh} and \ref{fig:sim_incoh}).}\\
 
@@
 \textcolor{blue}{
- The timing of the IC has is not functionning properly for certain channels. Therefore, 
+ The timing of the IC is not functionning properly for certain channels. Therefore, 
  applying a timing cut would add inefficient regions in the detector that we 
@@
 rhs. Is there any good explanation (at least qualitatively)? This could 
-potentially distort phi-distributions, no? \\
-\textcolor{blue}{This plot contains no good
-   track cuts and so say very little about the efficiency. In more details, 
+potentially distort $phi$-distributions, no? \\
+\textcolor{blue}{ 
    This difference in the yield should not be linked to a different performance 
@@
 \includegraphics[height=6.2cm]{fig/npd_p_elastic.png}
-\caption{The number of active pads versus the measured p/q for the good tracks 
-collected using 1.2 GeV electron beam.}
+\caption{The number of active pads versus the measured p for the good tracks 
+collected using 6 GeV electron beam.}
 \label{fig:padnb}
@@
 identified Coherent DVCS events after applying the exclusivity cuts without any 
-initial constrain on $\Delta z$.}\\
+initial constrain on $\Delta z$.  This guides us to correct for these 
+accidentals in our asymmetries in the form: $ A_{LU~~corr.} = \frac{1}{1 - 
+contamination} A_{LU}$, with a 4.1$\%$ global accidental contamination.} \\
 
@@
 recoil He4 for the identified coherent DVCS events after the exclusivity cuts 
-in the two modules of the RTPC separately. Table \ref{table:Events_numbers} 
-summarizes the cut numerically. }
+in the two modules of the RTPC separately without any initial constrains on 
+z-vertices of the individual particles.  Table \ref{table:Events_numbers} 
+summarizes the cut numerically.}
+
 \label{fig:delta_z_after_exclusitivty}
@@
          \hline
-         [-50:-20] & 165 & 132 \\
-         \hline
-         [-20:20]  & 2736 & 2828\\
-         \hline
-         [20:50]   & 78 &  166 \\
-         \hline
-         Total     & 2979  & 3126 \\
+         [-50:-30] & 42 & 77 \\
+         \hline
+         [-20:20]  & 2741 & 2856\\
+         \hline
+         [30:50]   & 34 &  78 \\
+         \hline
+         Contamination percentage  & 2.7$\%$  & 5.4$\%$ \\
          \hline 
@@
 experimental data that include both effects. The plots in Fig.~\ref{fig:comp_He} 
-show the comparison between data and simulation in terms of theta, phi and 
+show the comparison between data and simulation in terms of theta, $phi$ and 
 momentum of the He-4 DVCS nuclei.}\\
@@
 protons and electron as we found good enough match already.
-In the case of the of the IC photons, the corrections 
+In the case of the energy of the IC photons, the corrections 
 for data and for simulation are different and presented in the following two 
@@
 (3.3.4.3) are indeed correlated and therefore treated multidimensionally ($R,E$).}\\
-\textcolor{green}{Rpahael: I believe Nathan will provide answer more detailed 
-for this.  If not need to be clarified.} \\
 
@@
 than a couple $\%$.\\
-\textcolor{blue}{Most pi0 are found at low energy, while the correction affects
+\textcolor{blue}{Most $\pi^0$ are found at low energy, while the correction affects
 2 to 6.0 GeV photons. This is the reason the correction has such an important 
 impact. See later reply to question 31 ii from reviewer 2 for more details.}\\
-\textcolor{green}{Raphael: Same as previous.} \\
 
@@
 momentum.\\
-\textcolor{blue}{ We applied 3$\sigma$ guided by the comparison between data 
+\textcolor{blue}{ We applied 3$\sigma$ based on the comparison between data 
 and simulation, see figure 4.4 in the note. In the following, figure 
@@
 
-\begin{figure}[h!]
+\begin{figure}[tbp]
    \includegraphics[height=5.0cm]{fig/coh_ME_bins.png}
@@
 
-41) Fig. 4.6: Here you could cut deeper on the ep missing mass. Can be done.
-Why is it so lopsided? Because the fact that we do not take into account the 
-proton's initial momentum. Didn't you correct the IC photons to avoid that? \\
+41) Fig. 4.6: Here you could cut deeper on the ep missing mass.
+Why is it so lopsided? Didn't you correct the IC photons to avoid that?  \\
 \textcolor{blue}{We can always cut deeper. We choose not to cut by eye, but 
@@
 of the larger mass term that reduce the relative impact of some of the
-measurement errors. Equation \ref{eq:egamma.} shows that the precision on the 
+measurement errors. Equation \ref{eq:egamma} shows that the precision on the 
 calculated missing mass squared of $e\gamma X$ depends on the mass of the 
@@
 asymmetry).   \\
-\textcolor{blue}{ Yes, the subtraction is done separately for each helicity 
+\textcolor{blue}{Yes, the subtraction is done separately for each helicity 
    direction. We modified the text to include that information. As can be seen 
@@
    the coherent DVCS events is around 2-4$\%$.}\\
-\begin{figure}[h!]
+   \textcolor{blue}{
+   Figure \ref{fig:coh_dvcs_pi0_Alu} shows the reconstructed coherent 
+   asymmetries in t-bins as a function of $phi$, where the red shaded point are 
+   the DVCS asymmetries after the background subtraction, the blue points are 
+   the DVCS raw asymmetries without background subtraction and the black points 
+   are the $\pi^0$-asymmetries ($e^{4}He\pi^{0}$ events).  }\\
+\textcolor{blue}{This leads us to conclude that:\\
+- The  $\pi^{0}$-asymmetries are consistent with zero.\\
+- 2-4$\%$ background yield does not affect much our DVCS asymmetries.\\
+Therefore, assuming that the two helicity configuration have the same 
+acceptance ratio R is a good approximation.}\\
+
+\begin{figure}[tbp]
    \centering
@@
 
-   \textcolor{blue}{
-   Figure \ref{fig:coh_dvcs_pi0_Alu} shows the reconstructed coherent 
-   asymmetries in t-bins as a function of phi, where the red shaded point are 
-   the DVCS asymmetries after the background subtraction, the blue points are 
-   the DVCS raw asymmetries without background subtraction and the black points 
-   are the $\pi^0$-asymmetries ($e^{4}He\pi^{0}$ events).  }\\
-\begin{figure}[h!]
+\begin{figure}[tbp]
    \centering
@@
     \end{figure}
-
-\textcolor{blue}{This leads us to conclude that:\\
-- The  $\pi^{0}$-asymmetries are consistent with zero.\\
-- 2-4$\%$ background yield does not affect much our DVCS asymmetries.\\
-Therefore, assuming that the two helicity configuration have the same 
-acceptance ratio R is very good approximation.}\\
 
@@
 the way show that those backgrounds may not be totally negligible. \\
-\textcolor{blue}{The procedure follows the same guidelines as for other DVCS 
+\textcolor{blue}{The procedure follows the same guidelines as for DVCS 
 analysis on the nucleon. The neutral pion production occurs "without threshold" 
-as seen from the eHegamma sample, meaning that the contamination from 
-$eHe\pi^0$ with one photon lost is distributed all the way down to the DVCS 
-threshold, in the limit where the second photon energy becomes negligible in 
+as seen from the $eHe\gamma$ sample, meaning that the contamination from 
+$eHe\pi^0$ with one photon lost is distributed all the way down to the DVCS, 
+in the limit where the second photon energy becomes negligible in 
 the lab. Single charged pion production occurs with a small threshold but is 
@@
 production is entirely cleaned up by the exclusivity cuts. Scattering from the 
-windows is excluded by the vertex cuts. As far as accidental coincidences, we 
-neglected that possibility since it is already rare with CLAS luminosities and 
-the coincidence would have to fall inside narrow exclusivity cuts. This was 
-also neglected in the DVCS analysis on the nucleon, which have higher 
-luminosities. See also the answers to:\\
-- Comment 31, figure 23, from the first reviewer.\\
+windows is excluded by the vertex cuts. As far as accidental, we correct for 
+that as presented in comment \#31 from the first reviewer. For discussions of 
+other background sources see also the answers to:\\
 - Comment 46, figure 30, from the first reviewer.\\
@@
 
-45) Fig. 4.11: For the final correction, do you produce the phi-dependence of R 
+45) Fig. 4.11: For the final correction, do you produce the $phi$-dependence of R 
 for each of the individual bins in xB, Q2 or t that you use? \\
@@
 but we never claimed this, so we are unsure what is the source of the critic. In 
-fact, we claim the opposite since we treat pi0 background independently and 
+fact, we claim the opposite since we treat $\pi^0$ background independently and 
 associate another systematic error to it.}\\
 
- \textcolor{blue}{
- Regarding the window effect inside the exclusive distributions, the data
- has been processed with NO constraints on the z-vertex of the electron nor
- the $^{4}$He, and as a result no single event from outside the target has 
- passed the exclusive cuts. Even more, requiring that each event has three 
- particles (e, $\gamma$, $^{4}$He) in the final state and applying the $Q^{2}$ 
- and W cuts are enough to reject all the events generated from outside the 
- target. In figure \ref{fig:exclusive_z}, we show the exclusive variables in 
- figure 4.2 (in the note) as a function of z-vertex of the electron.  The scale 
- on Y-axis is kept the same as in figure 4.2. The target extends from -74 cm to 
- -54 cm with respect to the center of CLAS. As a conclusion, this source of the 
- background has no magnitude inside the exclusive distributions. }\\
-
- \begin{figure}[h!]
+ \textcolor{blue}{ Regarding the windows effect inside the exclusive 
+    distributions, the data has been processed with NO constraints on the 
+    z-vertex of the electron nor the $^{4}$He. Figure \ref{fig:exclusive_z} 
+    shows the exclusive variables as a function of z-vertex of the electron for 
+ the identified coherent DVCS events. The target extends from -74 cm to -54 cm 
+ with respect to the center of CLAS. As a conclusion, our vertex cut, shown in 
+ figure 3.1 in the note, remove most of the windows effect. For the remaining 
+ contamination, we correct for it as presented in comment 44 from the first 
+ reviewer. }\\
+
+ \begin{figure}[tbp]
  \centering
@@
  \caption{The distributions of the exclusive variables as a function of 
-    z-vertex of the scattered electron, after applying $Q^{2}>1$ and $W>2.0$ 
- and before all the exclusivity cuts.}
+ z-vertex of the scattered electron after applying all the exclusivity cuts 
+ without any initial constrains on $\Delta z$ nor the z-vertices of the 
+ individual particles.}
  \label{fig:exclusive_z}
@@
 \textcolor{blue}{It has been shown that such effects are small for asymmetries
-on free proton and we see no argument to claim otherwise. Regarding the 
-one-loop contributions, we are in contact with Andrei V. Afanasev who started 
-to do the calculations for our specific DVCS channels, and this part will be 
-updated as soon as we get the results.}\\
+on free proton and we see no argument to claim otherwise. Actually reviewer 2
+in its question 41 is supporting this point.}\\
 
@@
        \ref{fig:incoh_alu_sep} we show the coherent and the incoherent 
-       beam-spin asymmetries respectively. In blue only the statistical error 
-       are added, in red the statistical and the systematic errors (except beam 
-    polarization uncertainty) are quadratically summed, and in shaded brown on 
- the systematic errors are shown. } \\
- \begin{figure}[h!]
- \centering
- \includegraphics[height=7.0cm]{fig/BSA_Coherent_Q2.png}
- \includegraphics[height=7.0cm]{fig/BSA_Coherent_xB.png}
- \includegraphics[height=7.0cm]{fig/BSA_Coherent_t.png}
+    beam-spin asymmetries respectively. In blue the statistical and the 
+ systematic errors are added quadratically, in green the statistical errors and 
+ brown bands present the full systematic uncertainties. The red lines are fits 
+ to the data and presented in chapter 5 of the note. } \\
+ \begin{figure}[tbp]
+ \centering
+ \includegraphics[height=7.0cm]{fig/coh_Q2_phi.png}
+ \includegraphics[height=7.0cm]{fig/coh_xB_phi.png}
+ \includegraphics[height=7.0cm]{fig/coh_t_phi.png}
  \caption{Coherent beam-spin asymmetries}
@@
 
- \begin{figure}[h!]
- \centering
- \includegraphics[height=5.5cm]{fig/BSA_InCoherent_Q2.png}
- \includegraphics[height=5.5cm]{fig/BSA_InCoherent_xB.png}
- \includegraphics[height=5.5cm]{fig/BSA_InCoherent_t.png}
+ \begin{figure}[tbp]
+ \centering
+ \includegraphics[height=5.5cm]{fig/incoh_Q2_phi.png}
+ \includegraphics[height=5.5cm]{fig/incoh_xB_phi.png}
+ \includegraphics[height=5.5cm]{fig/incoh_t_phi.png}
  \caption{Incoherent beam-spin asymmetries}
@@
 same way in the 3 plots, indicating that it is an average? \\
-\textcolor{red}{Mohammad: To do with the final results.} \\
+\textcolor{blue}{It is corrected in the second version of the analysis note, 
+see figures 5.2 and 5.4.} \\
 
@@
 aren't so many. \\
-
-\textcolor{blue}{ The theoretical curves are not integrated over the 
+\textcolor{blue}{The theoretical curves are not integrated over the 
    experimental acceptance. For example, they are calculated at fixed xb, Q2 
-   and phi when looking to the dependence on t. Tables for all the two 
-   dimensional bins are added to the note for the coherent and the incoherent 
-   and shown here in tables \ref{table:Coh_Q2_BSA} to \ref{table:InCoh_t_BSA}.  
+   and $phi$ when looking to the dependence on t. Tables for all the two 
+   dimensional bins are added to the note for both the coherent and the 
+   incoherent channel as well as at the end of this document in tables 
+   \ref{table:Coh_Q2_BSA} to \ref{table:InCoh_t_BSA}.  
 } \\
@@
 \ref{fig:incoh_free_ALU}}
-\begin{figure}[h!]
+\begin{figure}[tbp]
 
@@
 These 2 are pretty tightly correlated! Any explanation?\\
-\textcolor{red}{Mohammad: need to be checked with the new extractions.} \\
+\textcolor{blue}{The new extraction of the GPDs show almost the same trend in 
+   $Q^2$ and $x_B$, where the data is fitted with a form in which the real and 
+   the imaginaries parts of the CFF $H_A$ are the free parameters. The previous 
+   observation might come for the neglecting some parts of the full formula 
+that we thought would be negligible. } \\
 
@@
 protons than the EMC effect - e.g., FSI. \\
-
-\textcolor{red}{We are not sure what you are referring to. We clarified a 
+\textcolor{blue}{We are not sure what you are referring to. We clarified a 
 little the paragraph in order to alleviate any issues.} \\
-
 \textcolor{blue}{Regarding the FSI effect, this can be investigated by 
 construction bins in missing transverse momentum. Figure 
-\ref{fig:bins_pt_incoh} shows three bins in missing pt, while figure 
-\ref{fig:incoh_Alu_pt}. Figure \ref{fig:alu_alpha_bins_pt} shows the extracted 
-$A_{LU}$ at 90$^{\circ}$ from fitting the asymmetry signals. As a conclusion 
-one can see that the incoherent asymmetries are consistent and so the FSI has 
-no big effects on the measured asymmetries.  }\\
- \begin{figure}[h!]
-  \centering
-  \includegraphics[height=5.5cm]{fig/incoh_bins_pt.png}
-  \caption{ Three reconstructed bins in the missing transverse momentum.}
-  \label{fig:bins_pt_incoh}
- \end{figure}
-
- \begin{figure}[h!]
-  \centering
-  \includegraphics[height=6.5cm]{fig/BSA_incoherent_PT.png}
-  \caption{The reconstructed beam-spin asymmetries as a function of phi in the 
-  for the bins shown in figure \ref{fig:bins_pt_incoh}.}
-  \label{fig:incoh_Alu_pt}
- \end{figure}
-
- \begin{figure}[h!]
+\ref{fig:alu_alpha_bins_pt} shows the extracted $A_{LU}$ at 90$^{\circ}$ from 
+fitting the asymmetry signals for different $p_t$ bins. As a conclusion one 
+can see that the incoherent asymmetries are consistent and so the FSI seem to 
+have no big effects on the measured asymmetries. This question of course is to 
+be discussed in more detail in the paper, rather than in the analysis note.}\\
+
+%\begin{figure}[tbp]
+% \centering
+% \includegraphics[height=5.5cm]{fig/incoh_bins_pt.png}
+% \caption{ Three reconstructed bins in the missing transverse momentum.}
+% \label{fig:bins_pt_incoh}
+%\end{figure}
+
+%\begin{figure}[tbp]
+% \centering
+% \includegraphics[height=6.5cm]{fig/BSA_incoherent_PT.png}
+% \caption{The reconstructed beam-spin asymmetries as a function of $phi$ in the 
+% for the bins shown in figure \ref{fig:bins_pt_incoh}.}
+% \label{fig:incoh_Alu_pt}
+%\end{figure}
+
+ \begin{figure}[tbp]
   \centering
@@
 Also, the x-dependence might be affected by the very different SHAPE of the 
-coherent results vs. phi - indicating that the denominator may play a role. Of 
+coherent results vs. $phi$ - indicating that the denominator may play a role. Of 
 course, there is no expectation that coherent 4He should agree with free p - 
@@
 have much less stringent cuts, in particular on exclusivity ... \\
-\textcolor{blue}{HERMES data are selected for very small $-t$ and just assume 
-they are in the coherent regime from this cut. The large difference between the 
+\textcolor{blue}{HERMES data are selected for very small $-t$ and then assumed
+to be in the coherent regime from this cut. The large difference between the 
 measurement shows that the detection of the recoil has a strong impact on the 
@@
 analysis.\\
-   \textcolor{blue}{ (Added). Experimentally, only  $\xi$ and $t$ are 
+   \textcolor{blue}{ Experimentally, only  $\xi$ and $t$ are 
       measurable in the DVCS reaction. At twist-2 order, $\xi$ can be 
@@
 
-2) Eq. 1.7: define $\xi_{A}$ and $\xi_{N}$ in function of measured quantities.
-\textcolor{blue}{   (Added)
-  $ \xi_{A}= x_{A}/(2-x_{A})$ and  $\xi_{N}= xB/(2-xB)$.
+2) Eq. 1.7: define $\xi_{A}$ and $\xi_{N}$ in function of measured quantities. \\
+\textcolor{blue}{ $ \xi_{A}= x_{A}/(2-x_{A})$ and  $\xi_{N}= xB/(2-xB)$.
 }\\
@@
 is taken from Eq. 29 of ref. 2, but there, it is zeta, and not $\xi$. The 
-relation between the 2 variables is in their Eq. 3d.
+relation between the 2 variables is in their Eq. 3d. \\
 \textcolor{blue}{   Done.}\\
@@
 4) p. 11: 'The exclusivity of the selected DVCS events WAS APPROXIMATELY 
-insured by a cut ... egX (resolution on this variable = ... GeV)'.
+insured by a cut ... egX (resolution on this variable = ... GeV)'. \\
 \textcolor{blue}{Done.}\\
@@
 charge.
-\textcolor{red}{Mohammad: written and Will be added.}\\
+\textcolor{blue}{Done.}\\
 
@@
 correspond with the indications on Figs 2.2 and 2.5. Fig. 2.2 indicates it is 
-filled with He, while the text says it is with the drift gas.
+filled with He, while the text says it is with the drift gas.\\
 \textcolor{blue}{This gap is filled with the drift gas. I used different colors 
@@
 7) p. 11: Is the overall gain really 10$^6$ (100 per layer)? Any experimental 
-indication?
+indication?\\
 \textcolor{blue}{
@@
 
-\begin{figure}[h!]
+\begin{figure}[tbp]
 \centering
@@
     x0, y0, R, slope and constant !!!!!.\\
-   \textcolor{blue}{We do use a beamline constraint. See the answer to comment 
-   15 of the first reviewer.}\\
+   \textcolor{blue}{See answer to question \#5 of reviewer 1 about the use of
+   the beam position in the fit. However, this is not used as an absolut constrain
+   so the number of degrees of freedom remains 5. Eq. 2.2 has a $-4$ factor 
+only because of the accounting for the beam position information ($N_{dof} = 
+N_{pts} +1 -5$).}\\
 
@@
 vertical widths of graphs such as Figs 2.21 and 2.22. I can read also the 
-resolutions in phi and z in section 2.3. Correct?\\
+resolutions in $phi$ and z in section 2.3. Correct?\\
  \textcolor{blue}{ Answered in comment 5 from the first reviewer.  }\\
@@
   \textcolor{blue}{
-     - This is very good comment. Regarding the dependence on the azimuthal 
+     - Regarding the dependence on the azimuthal 
      angle ($\phi$), the drift paths were extracted for each half of the RTPC 
@@
      used the identified elastic events for our calibration where the domains 
-     of the momentum and $\theta$ are limited. Therefore, we assumed that there 
-     is no dependence on these two variables. \\
+     of the momentum and $\theta$ are limited. However, we do not expect any 
+     dependence on these two variables. \\
   - The sentence is added.}\\
 
-11) Fig. 2.10: why not centered at 0 like $sdist$?
+11) Fig. 2.10: why not centered at 0 like $sdist$?\\
 \textcolor{blue}{ Answered previously in comment 7 of the first reviewer.}\\
@@
 would like to see it.\\
-\textcolor{blue}{In figures \ref{fig:delta_z_sec},\ref{fig:delta_phi_sec}, and 
-\ref{fig:delta_theta_sec} we show the corresponding distributions in the 
+\textcolor{blue}{In figures \ref{fig:delta_z_sec}, \ref{fig:delta_phi_sec} and 
+\ref{fig:delta_theta_sec}, we show the corresponding distributions in the 
 different sectors of CLAS for the identified good tracks at 1.2 GeV beam 
@@
 difference between the distributions for these two types of events?\\
-
 \textcolor{blue}{ The figures are for the good tracks collected during the 1.2 
@@
 changes, indicated in figure 4.1.}\\
-
 \textcolor{blue}{ In comment 7 of the first reviewer, we have shown the sdist 
    and edist distributions for the identified elastic events without applying 
-   any requirements on sdist and edist. Figure \ref{fig:dvcs_coh_sdis_edist} 
+   any requirements on sdist and edist. Figure \ref{fig:dvcs_coh_sdist_edist} 
    shows the equivalent distributions of the identified coherent 4He DVCS 
-   nuclei using the presented exclusivity cuts, where larger cuts were applied 
-to clean the initial dataset. -3 mm < sdist < 2 mm and -2mm < edist < 3 mm are 
-considered in the second round of the analysis. }\\
-
-\begin{figure}[h!]
+   nuclei using the cuts based on the first version of the note.
+   Following your comments, we now tighten these and use: -3 mm < sdist < 2 mm 
+   and -2mm < edist < 3 mm are for the second round of the analysis. }\\
+
+\begin{figure}[tbp]
    \hspace{-1.0cm}
@@
 
-14) p. 23, 2nd paragraph: you write TDCmax = DPL/DS. Is not it (TDCmax - 
-15)*114 ns = DPL/DS?\\
+14) p. 23, 2nd paragraph: you write TDCmax = DPL/DS. Is not it 
+(TDCmax - 15)*114 ns = DPL/DS?\\
 \textcolor{blue}{ We show it in this form to simplify the correlation between 
 these variables.  Indeed it is  TDCmax-15 without the conversion unit as our 
-drift speed in TDC units. } \\
+drift speed is in TDC units. } \\
 
 15) p. 23: can you show the dependence of TDCmax/2 on z for a given run? \\ 
-\textcolor{blue}{ The shown figure in p.24 (figure 2.16) is for a single 
+\textcolor{blue}{ The figure in p.24 (figure 2.16) is for a single 
 experimental run.} \\
 
-16) 'Figure 2.18 \textcolor{blue}{ALSO} shows the percentage increase in good 
-tracks (GT) ...' \textcolor{blue}{ Added.}\\
+16) 'Figure 2.18 ALSO shows the percentage increase in good 
+tracks (GT) ...' \\
+\textcolor{blue}{ Added.}\\
 
@@
 using TDCmax and as a result, the previously extracted drift paths overlap on 
-the new ones, using TDCmax, without and variations. The plots of the new drift 
-paths with the old fits can be provided for the 20 bins along the RTPC in case 
-requested.}\\
+the new ones.}\\
 
 18) Eq. 2.9 does not have the right dimensions. Should not the second term be 
-multiplied by 114 ns?
+multiplied by 114 ns? \\
 \textcolor{blue}{ Corrected. The sum is multiplied by a TDC unit.}\\
@@
 method should be described first, the figure appears later and the results are 
-commented at the bottom of the page.
+commented at the bottom of the page. \\
 \textcolor{blue}{  Done.}\\
@@
 data sets the ADC information will be used, since it is not so clear later that 
-it is used for elastic events selection, but not for DVCS events selection.
+it is used for elastic events selection, but not for DVCS events selection. \\
 \textcolor{blue}{  Done.}\\
@@
 in Table 1 caption, add '(neglecting the contributions from the CLAS 
-resolutions).'
+resolutions).'\\
 \textcolor{blue}{  Done.}\\
@@
 22) Chapter 3 intro: should prepare (for the publication) an argumentation to 
-neglect other possible source of background (e.g. e He4 pi0 gamma).
+neglect other possible source of background (e.g. e He4 pi0 gamma). \\
 \textcolor{blue}{ Answered previously in comments 44 and 46 of the first 
@@
 this exercise, it is still useful to see if there is or not an increase towards 
-the ends of the cut. So I am thinking not only of fig. 3.1, but also fig. 3.8.
+the ends of the cut. So I am thinking not only of fig. 3.1, but also fig. 3.8. \\
 \textcolor{blue}{ Answered previously in comments 44 and 46 of the first 
@@
 
-24) p. 42: section??
+24) p. 42: section?? \\
 \textcolor{blue}{ Removed.}\\
@@
 25) p. 48, 2nd line of 3.1.4: chapter and section numbers to be fixed. Same p. 55 
-in 3.2.5.
- Done.
+in 3.2.5. \\
+\textcolor{blue}{Done.}\\
 
 26) Figs 3.21 and 3.22: would (part of) the tails of these distributions be 
-attributed to random coincidences? If yes, what about a subtraction?
-\textcolor{blue}{Yes, this is true and justified by distributions previously in 
+attributed to random coincidences? If yes, what about a subtraction? \\
+\textcolor{blue}{Yes, this is true and discussed in 
 comment 7 from the first reviewer and comment 13 of the second reviewer.}\\
@@
 cuts were very wide to adapt to very broad distributions. }\\
-\textcolor{green}{Nathan wants to clean this answer more.}
 
@@
 \textcolor{blue}{
-   The plots in figure \ref{fig:Q2_xB} show the coherent and the incoherent 
--tmin distributions distributions with the W and -tmin cuts. }\\
-
-\begin{figure}[h!]
+   The plots in figure \ref{fig:Q2_xB} show the $Q^2$ as a function of $x_B$ 
+for the identified coherent and the incoherent DVCS events, with $Q^2$($x_B$) 
+at fixed -tmin values and the W cut.  }\\
+
+\begin{figure}[tbp]
 \includegraphics[height=6.2cm]{fig/coh_Q2_xB.png}
@@
 \caption{The coherent (left) and incoherent (right) $Q^{2}$ versus $x_{B}$ 
-   distributions for the identified DVCS events, with the W and -tmin (0.01 
-GeV$^{2}$ cuts in the $Q^{2}$-$x_{B}$ plane.}
+distributions of the identified DVCS events, with W and -tmin cuts, at 
+different values, in the $Q^{2}$-$x_{B}$ plane.}
 \label{fig:Q2_xB}
@@
 29) p.65: Eg cut: should add that the simulation indicates that no DVCS events 
-are expected (in IC) with photon energy less than 2 GeV.
+are expected (in IC) with photon energy less than 2 GeV. \\
 \textcolor{blue}{ Added. Figures \ref{fig:sim_coh} and \ref{fig:sim_incoh} show 
@@
 \textcolor{blue}{ We apply similar exclusivity cuts as presented for the 
-experimental coherent DVCS events. Then, each exclusive distribution is fitted 
+experimental coherent DVCS events. That is each exclusive distribution is fitted 
 by a Gaussian and a 3$\sigma$ cut is applied. So the cut are not
@@
 from this that the Fermi motion has negligible effects (which I am ready to 
-believe considering the beam energy). 
+believe considering the beam energy). \\
  \textcolor{blue}{
@@
 
-32) p.73: remove 'in figure??' \textcolor{blue}{ Corrected. Figure 4.7 in the 
+32) p.73: remove 'in figure??' \\
+\textcolor{blue}{ Corrected. Figure 4.7 in the 
 place of ??}\\
@@
 at the end of this document. }\\
+\newpage
 
@@
 negligible compared to systematic uncertainties.\\
-\textcolor{blue}{We are not sure to understand fully the argument here. You 
-   probably forgot a R term in the second formula. In any case, in the 2D 
-   correction, we are indeed dependent on the reproduction of the integrated 
-   variables. The figures 4.3, 4.4, 4.7 and 4.8 are here to show that we have a 
-   good reproduction of the variables and should not be sensitive to such 
-problems. }\\
+\textcolor{blue}{ You probably forgot a R term in the second formula. Rewriting 
+the formulas: The 4-dimensional background subtraction takes this form:}
+
+\begin{equation}
+   N_{DVCS}^{true}(Q^2, x_B, t, \phi)=   N_{DVCS}^{Exp.}(Q^2, x_B, t, \phi)  - 
+R^{Sim.}(Q^2, x_B, t, \phi)* N_{\pi^{0}}^{Exp.}(Q^2, x_B, t, \phi) 
+\end{equation}
+\textcolor{blue}{ In order to get the 2-dimensional binning, for instance the 
+$Q^2-\phi$, we integrate over the other two variable, here are $x_B$ and $t$ 
+like:}
+\begin{equation}
+   N_{DVCS}^{true}(Q^2, \phi)=   \sum\limits_{x_B, t} N_{DVCS}^{Exp.}(Q^2, 
+\phi)  - \sum\limits_{x_B, t} ( R^{Sim.}(Q^2, x_B, t, \phi)* 
+N_{\pi^{0}}^{Exp.}(Q^2, x_B, t, \phi)) \end{equation}
+\textcolor{blue}{ What we do in our analysis is:}
+\begin{equation}
+      N_{DVCS}^{true}(Q^2, \phi)=   \sum\limits_{x_B, t} N_{DVCS}^{Exp.}(Q^2, 
+      \phi)  - \sum\limits_{x_B, t} R^{Sim.}(Q^2, x_B, t, \phi)* 
+      \sum\limits_{x_B, t}
+N_{\pi^{0}}^{Exp.}(Q^2, x_B, t, \phi) \end{equation}
+
+   \textcolor{blue}{We carried out our analysis in this way and we assume that 
+      it is a good approximation based on:\\
+      - Figure \ref{fig:coh_back_yield} shows that the background yield is 
+      really very small.\\
+      - R is alomst constant in $Q2$, $x_B$ and $t$. See the one-dimensional 
+      dependences of R in section 4.5.1.\\
+      - In any case, in the 2D correction, we are indeed dependent on the 
+      reproduction of the integrated variables.  The figures 4.3, 4.4, 4.7 and 
+      4.8 are here to show that we have a good reproduction of the variables 
+      and should not be sensitive to such problems.\\
+      - We carry out a full procedures to add the slight deviations in R that 
+      comes from this assumption as a systematic uncertainty on the 
+      reconstructed asymmetries. See section 4.7 in the analysis note.
+}\\
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[height=4.5cm]{fig/coh_back_yield.png}
+\caption{In -t bins; the coherent acceptance ratio (left) is multiplied by the 
+coherent yield of $\pi^{0}$ production (middle) resulting in the backgroud 
+yield (right).}
+\label{fig:coh_back_yield}
+ \end{figure}
+
+%\begin{figure}[tbp]
+%\centering
+%\includegraphics[height=5.5cm]{fig/coh_alu_t_back_sub.png}
+%\caption{The coherent reconstructed beam-spin asymmetries with (in red) and 
+ %without (in blue) background subtraction in -t bins as a function of $\phi$.}
+%\label{fig:coh_alu_back_comp}
+% \end{figure}
 
@@
 \textcolor{blue}{All the systematic errors are added bin by bin except the beam 
-polarization, which added to the value of the asymmetry at 90$^{\circ}$ after 
-fitting the signal. I Will change the text to include this information.}\\
-
-37) p. 77 last sentence: it is ALU(90°) here and you should mention that it is 
+polarization, which is added to the value of the asymmetry at 90$^{\circ}$ after 
+fitting the signal.}\\
+
+37) p. 77 last sentence: it is ALU(90$^{\circ}$) here and you should mention that it is 
 extracted from the ALU(phi) distribution from a fit to be discussed in section 
 5.1.\\
-\textcolor{blue}{Yes, it is ALU(90°) from the fit. The text is modified to 
+\textcolor{blue}{Yes, it is ALU(90$^{\circ}$) from the fit. The text is modified to 
 detail this information.}\\
@@
 to comment 20 from the third reviewer, where the analysis is refined and the 
-results are flat withing the given error bars. It is integrated over all the 
+results are flat within the error bars. And, yes the figure is integrated over all the 
 bins.  }\\
@@
 exclusive channel (elastic, DVCS,...) where the radiative effects are not 
-negligible. If you know a counter example, please let me know.
-\textcolor{blue}{ All the previous studies have assumed that the radiative 
-corrections have no interest effects to the asymmetry ratios comparing to the 
+negligible. If you know a counter example, please let me know. \\
+\textcolor{blue}{ Indeed, all the previous studies have concluded that the radiative 
+corrections have no sizeable effect to the asymmetry ratios comparing to the 
 other systematic sources. }\\
@@
 \textcolor{blue}{
-The used parameterization  (http://arxiv.org/pdf/hep-ph/0302007v2.pdf)\\
-The refined parameterization (http://arxiv.org/pdf/0809.2890.pdf)\\
-  If we take only the twist-2 terms:\\
-  - The coefficients of the squared DVCS amplitude remain the same. In our 
-preliminary CFF extraction, we assume the pure DVCS is negligible. \\
+We now use the  refined parameterization (http://arxiv.org/pdf/0809.2890.pdf)
+in opposition to the old parameterization (http://arxiv.org/pdf/hep-ph/0302007v2.pdf).
+  Using only the twist-2 terms, we note that:\\
+  - The coefficients of the squared DVCS amplitude remain the same. However, in our 
+preliminary CFF extraction, we assumed the pure DVCS to be negligible. \\
   - The interference coefficients change.\\
-  - The squared BH amplitude, that come in the $\alpha_{1}$ which functions as 
-  a scaling factor for other $\alpha$'s, is the same in both calculations.\\
+  - The squared BH amplitude is the same in both calculations.\\
 For instance the following plot, \ref{fig:alpha_zero} shows the $\alpha_{0}$ as 
-a function of $\phi$ using the two models of calculation. As a result, the 
-extracted CFF will be changed.\\
+a function of $\phi$ using the two models of calculation.
 We updated all fits in the note with the most recent formulas.} \\
 
-\begin{figure}[h!]
+\begin{figure}[tbp]
 \centering
@@
 
-43) Eqs 5.2 to 5.5: should not they be the same as A.18 to A.21? 
-    They are exactly the same, I wrote them in simplified way in equations 5.2 to 5.5. 
-In any case 5.2 and A.15 would lead to Im(HA) squared in the numerator !! All this is very 
-confusing. Please check/correct your formulae and tell us which one you really 
-used in the CFF extraction.\\
-\textcolor{blue}{ The are exactly the same. We will include all the terms in 
+43) Eqs 5.2 to 5.5: should not they be the same as A.18 to A.21? \\
+\textcolor{blue}{ They are actually the same, only notations vary. In any case, 
+we will include all the terms in 
 the second version of the analysis note with the refined parametrization. The 
@@
 by a fit in function of Im(HA) and Re(HA) treated as free parameters, see 
-Section 5.3.'
+Section 5.3.'\\
 \textcolor{blue}{ The paragraph is changed.}\\
@@
 45) When adding the systematic and statistical uncertainties in quadrature, should 
-not include the error on beam polarization.
+not include the error on beam polarization.\\
 \textcolor{blue}{This is what we do, we add the beam polarization error as a 
@@
 
-46) It seems your phi values are at the middle of each phi-bin. The phi values in 
+46) It seems your $phi$ values are at the middle of each phi-bin. The phi values in 
 each bin should be event weighted (in the same way as Q2, xB, t). Once you do 
-that, you'll have to redo all your fits.
-\textcolor{blue}{ It is not the middle, it is the mean value of phi in each phi 
+that, you'll have to redo all your fits.\\
+\textcolor{blue}{ It is not the middle, it is the mean value of $phi$ in each phi 
 bin.}\\
@@
 47) Fig. 5.2 top left: value of <-t> missing. Added.  Section 5.2.1: the drop 
-at high t is 'suggested', not 'observed' by HERMES. \textcolor{blue}{ 
-Corrected.}\\
-
-48) Fig 5.5 caption: 'top left' -> 'top'; 'top right' -> 'middle'; 
+at high t is 'suggested', not 'observed' by HERMES. \\
+\textcolor{blue}{ Corrected.}\\
+
+48) Fig 5.5 caption: 'top left' -> 'top'; 'top right' -> 'middle'; \\
 \textcolor{blue}{Changed.}\\
@@
 \textcolor{blue}{  The ones in figure 5.4 are showing the mean Q2, xB and -t 
-for each bin. In Figure 5.5, I show the mean values over the full data. For 
+for each bin. In Figure 5.5, we show the mean values over the full data. For 
 example, in the Q2 dependence plot, xB= 0.267 and -t =0.506 are the mean values 
@@
 point)\\
-\textcolor{red}{Mohammad: I need to implement the binning of e1dvcs1 in my 
-analysis codes for e1dvcs data.}\\
+\textcolor{blue}{We will use the published results to construct the asymmetry 
+ratios.}\\
 
@@
 you redo the fit? I would favor the latter.  \\
-\textcolor{blue}{ The fitting function is changed by a fit in function of
-Im(HA) and Re(HA) treated as free parameters.}
+\textcolor{blue}{ The fitting function is now changed and is function of
+Im(HA) and Re(HA) only.}
 
@@
 result might not be significantly different, but it is a more convincing 
-procedure. \textcolor{blue}{ In the process.}\\
+procedure. \\
+\textcolor{blue}{Done.}\\
 
@@
 to give tentative explanations. The most significant deviation from model 
-expectations is R{incoh} at small xB. Are we then at too small Q2 for validity 
-of leading-twist approximation (but the sin(phi) dominance is what is expected 
-from leading twist)? If we suppose leading twist OK, what would that mean for 
-the bound proton? Etc ...
-
-p. 97: 3.23 -> 2.11 
+expectations is $R_{incoh}$ at small xB. Are we then at too small Q2 for 
+validity of leading-twist approximation (but the sin(phi) dominance is what is 
+expected from leading twist)? If we suppose leading twist OK, what would that 
+mean for the bound proton? Etc ...
+\textcolor{blue}{Physics discussion will be developed in the paper.}\\
+
+52) p. 97: 3.23 -> 2.11 \\
 \textcolor{blue}{ Corrected.}\\
@@
 '..., such as confinement size of the bound nucleons ...' - '..., the quark 
-confinement size of the bound nucleons ...'
+confinement size of the bound nucleons ...' \\
 \textcolor{blue}{ Changed.}\\
 
-2) Page 6, in Figure 1.2 it looks like beta = b+b' rather than b-b'.
+2) Page 6, in Figure 1.2 it looks like beta = b+b' rather than b-b'. \\
 \textcolor{blue}{ The figure is corrected.}\\
@@
 3) Page 9, Fig caption 1.5, last sentence  '...-t,0.2 and 0.4  2 
-GeV$^{2}$/c$^{2}$ ...'.  Is -t= 0.42?
+GeV$^{2}$/c$^{2}$ ...'.  Is -t= 0.42? \\
 \textcolor{blue}{ It is -t= 0.4 GeV$^{2}$/c$^{2}$. Corrected.}\\
@@
 per charge of the He4 needing an RTPC.\\
-\textcolor{blue}{I will write a brief chapter about CLAS, IC, solenoid and beam 
-before the chapter of the RTPC.}\\
+\textcolor{blue}{We have added a longer and hopefully clearer introduction.}\\
 
@@
  events: (where both vertices are taken with respect to the center of the 
- RTPC).  As a conclusion, the -[80:+80] mm cuts on the helium z-vertex appear 
+ RTPC).  As a conclusion, the [-80:+80] mm cuts on the helium z-vertex appear 
  to be the suitable cuts to ensure that the reconstructed tracks are within the 
- physical volume of the RTPC from one side, and to reduce the background 
- effects on the other presented variables in section 2.2.1.1.  Also, one can 
- see the almost symmetric trends between [-80:-50] and [+50, 80].  }\\
-\begin{figure}[h!]
+ physical volume of the RTPC.}\\
+\begin{figure}[tbp]
 \centering
@@
 8) 2.1.3, 1st paragraph, 3rd sentence'... spatial reconstructing ...' should be 
-'...  spatial reconstruction ...' \textcolor{blue}{ Done.}
+'...  spatial reconstruction ...' \\
+\textcolor{blue}{ Done.} \\
 
@@
 there a resolution difference?\\
-\textcolor{blue}{
-  In addition to the answer of comment 7 from the 1st reviewer, the probability 
-that a noise signal produced close to the anode to reach the readout pads and 
-being recorder is higher than the probability the of the same noise released 
-close near the cathode to cross the full drift region and recorder as a signal.  
-Therefore, the noise contribution at the end of each chain of hits is bigger 
-than the contribution at the beginning, resulting in more precise reconstructed 
-$sdist$ than $edist$. The noise effect at low TDC can be seen from figure 2.30, 
-section 2.2.5.1}\\
+\textcolor{blue}{ This is answered in our answer to question \#7 from the 1st 
+reviewer. } \\
 
@@
 - One can see from figure 2.4 that the magnetic field at the sides of the RTPC 
-is slightly deviated from the direction of the beam line and weaker.
+is slightly deviated from the direction of the beam line and weaker. \\
 - The generated electric field between the two cylinders (cathode and anode) 
@@
 disconnected soon in the run because of HV trips. The electric field might 
-therefore be significantly off on the sides. }\\
+therefore be significantly off on the sides. \\
+However since the TDCmax are extracted directly from data, we are unable to 
+assess which effect is stronger.}\\
 
@@
 
-\begin{figure}[h!]
+\begin{figure}[tbp]
 \centering
 \includegraphics[height=14.5cm]{fig/coh_exc_cuts_z.png}
-\caption{The coherent exclusive distributions in case of taking events 
-originate along the full length of the RTPC (in blue) and in case of analyzing 
-events with the scattered electrons being originate within 6 cm from the center 
+\caption{The coherent exclusive distributions for events 
+originating from the full length of the RTPC (in blue) and for 
+eventsoriginating within 6 cm from the center 
 of the RTPC.}
@@
 
-\begin{figure}[h!]
+\begin{figure}[tbp]
 \centering
 \includegraphics[height=14.5cm]{fig/incoh_exc_cuts_z.png}
-\caption{The incoherent exclusive distributions in case of taking events 
-originate along the full length of the RTPC (in blue) and in case of analyzing 
-events with the scattered electrons being originate within 6 cm from the center 
+\caption{The incoherent exclusive distributions for events 
+originating from the full length of the RTPC (in blue) and for 
+eventsoriginating within 6 cm from the center 
 of the RTPC.}
@@
 
-Is run 61510 typical? 
+Is run 61510 typical? \\
 \textcolor{blue}{
@@
 \textcolor{blue}{ Figure \ref{fig:coh_alu_run} presents the reconstructed
-coherent $A_{LU}$ as a function for different groups of run numbers. Within the 
-given statistics, the asymmetries are compatible. }\\
-\begin{figure}[h!]
+   coherent $A_{LU}$ as a function of $\phi$ for different groups of run 
+numbers. Within the given statistics, the asymmetries are compatible. }\\
+\begin{figure}[tbp]
    \centering
    \includegraphics[height=7.5cm]{fig/bsa_coherent_runs.png}
-\caption{The reconstructed coherent beam-spin asymmetries as a function of the 
-run number.}
+   \caption{The reconstructed coherent beam-spin asymmetries as a function of 
+   $\phi$ for different groups of runs that exhibit similar trends in the drift 
+speed based on figure 2.18 in the analysis note.  }
    \label{fig:coh_alu_run}
@@
 channels respectively without any initial cut on the number of photo-electrons.  
-. In figure \ref{fig:nphe_coh_incoh_alu} we show the reconstructed integrated 
+In figure \ref{fig:nphe_coh_incoh_alu} we show the integrated 
 coherent and incoherent $A_{LU}$ as a function of $\phi$ using nphe>20 and 
-nphe>40. This leads us to conclude that the small contribution that remains 
+nphe>40 cuts. This leads us to conclude that the small contribution that remains 
 from the single photo-electron peaks has no significant effect on the 
@@
 
-\begin{figure}[h!]
+\begin{figure}[tbp]
    \hspace{-1.0 cm}
-\includegraphics[height=12.5cm]{fig/e_nphe_coh.png}
-\caption{The sector-dependent distributions of the number photoelectrons 
-produced by the electrons of the identified coherent DVCS events. }
+\includegraphics[height=11cm]{fig/e_nphe_coh.png}
+\caption{The sector-dependent distributions of the number of photoelectrons 
+produced by the electrons of identified coherent DVCS events. }
 \label{fig:nphe_after_excl_cuts_coh}
@@
 
-\begin{figure}[h!]
+\begin{figure}[tbp]
    \hspace{-1.0 cm}
-   \includegraphics[height=12.5cm]{fig/e_nphe_incoh.png}
-\caption{The sector-dependent distributions of the photoelectrons produced by 
-the electrons of the identified incoherent DVCS events via the exclusivity 
-cuts.  }
+   \includegraphics[height=11cm]{fig/e_nphe_incoh.png}
+\caption{The sector-dependent distributions of the number of photoelectrons 
+produced by the electrons of identified incoherent DVCS events.  }
 \label{fig:nphe_after_excl_cuts_incoh}
@@
 
-\begin{figure}[h!]
+\begin{figure}[tbp]
    \hspace{-1.0 cm}
@@
 \includegraphics[height=7.5cm]{fig/nphe_BSA_InCoherent.png}
-\caption{The Coheren (left) and incoherent (right) measured beam-spin 
+\caption{The Coherent (left) and incoherent (right) beam-spin 
 asymmetries using the cuts nphe > 20 (blue) and nphe > 40 (red). }
@@
 \textcolor{blue}{
-  It is justified for the case of the elastic events in the answer of comment 7 
-  from the 3rd reviewer. For the case of the DVCS events, figure 
+  For the DVCS events, figure 
   \ref{fig:coh_z_vertex} shows the distribution of the He4 DVCS events after 
   the exclusivity cuts without applying any PID cuts on the He4 selection.  
-  Therefore, the cut will be tuned to be as the one for the elastic selection 
-  as we saw that no contributions from the target's windows was observed.}\\
-
-\begin{figure}[h!]
+  Following your observation, we set the cut at -80 and 80 as for elastics.}\\
+
+\begin{figure}[tbp]
 \centering
@@
 two modules of the RTPC. The events are selected by applying the exclusivity 
-cuts with no cut on the PID nor the z-vertex.}
+cuts with no cut on the helium PID nor the z-vertex.}
 \label{fig:coh_z_vertex}
@@
 15) Page 50, figure 3.23 the left side is showing half as many events as the 
-right side of the RTPC. Although a priori that should not affect the phi 
+right side of the RTPC. Although a priori that should not affect the $phi$ 
 distributions of the results, like for instance in figure 4.10, page 74, I 
-would like to see separate phi distributions of the He4 asymmetries for the two 
+would like to see separate $phi$ distributions of the He4 asymmetries for the two 
 halves of the RTPC and check that they are compatible.\\
-
 \textcolor{blue}{Figure \ref{fig:coherent_alu_sides} shows the integrated (over 
 Q2, xB and t) beam-spin asymmetries for the two halves of the RTPC separately 
-and the integrated asymmetries over the whole RTPC.  }\\
-\begin{figure}[h!]
+and the integrated asymmetries over the whole RTPC.}\\
+
+\begin{figure}[tbp]
 \centering
@@
 scattering and fluctuations in energy loss taken in to account in the 
-simulation?  \textcolor{blue}{
-   The coplanarity and the pT distributions are both linked to the azimuthal 
-   angle of the recoiled 4He. Regarding the multiple scattering and the energy 
-   loss, we do not apply them individually, but we apply an overall smearing to 
-   the kinematics of the Helium nuclei based on the real data. One can see from 
-   the comparison between the simulated and the experimental 4He (comment 34 of 
-   the 1st reviewer) that there is slight difference in terms of phi that is 
-   reflected on the coplanaratiy and pT distributions. The difference in phi 
-   comes from the fact that experimentally there are some dead regions in the 
-   azimuthal range of the RTPC (the locations can be figured out from figure 
-   2.27) where the 4He is not reconstructed if it passes these regions.  These 
-   dead regions are not implemented in the fastmc for the moment. Of course 
-   implementing these regions is very important if we look for measuring the 
-   cross sections as our observables, while most of such acceptance issues 
-   cancel in the case of the asymmetries.}\\
+simulation?  \\
+\textcolor{blue}{ The difference in phi comes from the fact that experimentally 
+there are some dead regions in the azimuthal range of the RTPC (the locations 
+can be figured out from figure 2.27 in the analysis note). These dead regions 
+are not implemented in the fastmc and might affect slightly efficencies. We 
+consider that most of such acceptance issues cancel for the measurement of 
+asymmetries.
+The incoherent missing-pT is highly smeared by Fermi motion, while the coherent 
+one is not, and this is visible by comparing the two channels' missing-pT in 
+the figures.  This makes its agreement between experiment and simulation less 
+sensitive to resolution for the incoherent channel, and probably related to the 
+worse agreement for the coherent channel.
+However, this does not play a significant role in the asymmetry
+measurement, as can be seen in the asymmetry extracted for different
+missing-pT ranges shown in figure \ref{fig:alu_alpha_bins_pt}.  Regarding the 
+multiple scattering and the energy loss, we do not apply them individually, but 
+we apply an overall smearing to the kinematics of the Helium nuclei based on 
+the real data.} \\
 
@@
 and the proton included? Are there any timing cuts between the electron and 
-proton?
+proton? \\
 \textcolor{blue}{ We do apply a timing cut between the electron and the proton 
@@
 $M^{2}$ in the case of the proton?  There is no similar discrepancy in the 
-coherent case for He4, see figure 4.4?
-
+coherent case for He4, see figure 4.4?  \\
 \textcolor{blue}{ See the answer to comment \#31 of the second reviewer.}\\
@@
 equation 5.6?\\
-
 \textcolor{blue}{ Referring to comment 38 of the 2nd reviewer. We were taking 
@@
 \ref{fig:MM2_sys_cuts} and the corresponding acceptance ratios are shown in 
-figure \ref{fig:R_sys_plot}. We also turn to fit our beam-spin asymmetry 
+figure \ref{fig:R_sys_plot}. We fit here our beam-spin asymmetry 
 signals with the full expression ($\frac{\alpha sin(\phi)}{1 + \beta cos(\phi) 
@@
 
-\begin{figure}[h!]
+\begin{figure}[tbp]
 \hspace{-1.0cm}
@@
    \includegraphics[height=7.2cm]{fig/epgamma_M2_Mis_sig.png}
-   \caption{The applied cuts on the missing mass squared  of the coherent 
+   \caption{The cuts applied on the missing mass squared of the coherent 
 (right) and the incoherent DVCS channels in order to estimate the systematic 
@@
 
-\begin{figure}[h!]
+\begin{figure}[tbp]
    \includegraphics[height=6.2cm]{fig/e4Hegamma_e4Hepi0_Phi_2.png}
@@
 
-\begin{figure}[h!]
+\begin{figure}[tbp]
    \includegraphics[height=7.2cm]{fig/BSA_Coherent_sigmas.png}
@@
 
-\begin{figure}[h!]
+\begin{figure}[tbp]
    \includegraphics[height=6.2cm]{fig/coh_alpha_Nsig.png}
@@
 
-\begin{figure}[h!]
+\begin{figure}[tbp]
    \includegraphics[height=6.2cm]{fig/coh_beta_Nsig.png}
@@
 
-\begin{figure}[h!]
+\begin{figure}[tbp]
    \includegraphics[height=6.2cm]{fig/coh_eta_Nsig.png}
@@
 
-\begin{figure}[h!]
+\begin{figure}[tbp]
    \includegraphics[height=6.2cm]{fig/coh_chi2_Nsig.png}
@@
 
-\begin{figure}[h!]
+\begin{figure}[tbp]
    \includegraphics[height=6.2cm]{fig/coh_Alu_Nsig.png}
@@
   c) How sensitive are the fit results to your binning? You could investigate 
-by e.g., adding/removing a bin in phi, or  by shifting the bin edges. (Or you 
+by e.g., adding/removing a bin in $phi$, or  by shifting the bin edges. (Or you 
 could remove any bias introduced by the choice of binning by doing an unbinned 
 fit...)\\
+\textcolor{blue}{ In order to evaluate this uncertainty we binned the data into 
+   11 bins in phi and we compared the reconstructed asymmetries to the results 
+from our old binning.  Figure \ref{fig:coh_bins_phi_9_11} shows the coherent 
+reconstructed $A_{LU}$ as a function of $\phi$ in $Q^{2}$, $x_B$ and $-t$ bins.  
+The coherent, figure \ref{fig:coh_BSA_9_11}, and the incoherent, figure 
+\ref{fig:incoh_BSA_9_11}, measured $A_{LU}$ at $\phi = 90 ^{\circ}$ are showing 
+5$\%$ to 10$\%$ systematic uncertainties, which will be added to our estimated 
+uncertainties for the extracted asymmetries at $\phi = 90^{\circ}$.  }\\
+\begin{figure}[tbp]
+   \centering
+      \includegraphics[height=7.2cm]{fig/sBSA_Coherent_Q2.png}
+      \includegraphics[height=7.2cm]{fig/sBSA_Coherent_xB.png}
+      \includegraphics[height=7.2cm]{fig/sBSA_Coherent_t.png}
+     \caption{The measured coherent beam-spin asymmetry as
+     a function of $\phi$ in $Q^{2}$, $x_B$ and $-t$ bins, using two binning 
+  sets in $\phi$: 9 bins (in blue) and 11 bins (in red).}
+      \label{fig:coh_bins_phi_9_11}
+    \end{figure}
+
+\begin{figure}[tbp]
+   \centering
+      \includegraphics[height=9.2cm]{fig/BSA_Coherent_9_11.png}
+      \caption{The coherent $A_{LU}$($\phi = 90 ^{\circ}$), from the fit, as a 
+      function of $Q^{2}$, $x_B$ and $-t$, using 9 (in blue) and 11 (in red) 
+   bins in $\phi$.}
+      \label{fig:coh_BSA_9_11}
+    \end{figure}
+
+\begin{figure}[tbp]
+   \centering
+      \includegraphics[height=9.2cm]{fig/BSA_InCoherent_9_11.png}
+      \caption{The incoherent $A_{LU}$($\phi = 90 ^{\circ}$), from the fit, as 
+         a function of $Q^{2}$, $x_B$ and $-t$, using 9 (in blue) and 11 (in 
+      red) bins in $\phi$. }
+      \label{fig:incoh_BSA_9_11}
+    \end{figure}
 
@@
 a fit of a constant.\\
-\textcolor{red}{To do at the very end.}
+\textcolor{blue}{Physics discussion to be developed in the paper.  }
 
@@
 are compatible with each other!\\
-\textcolor{red}{To modify at the very end.}
+\textcolor{blue}{Modified.}
 
@@
 
- a) A systematic study of the phi dependence of the He4 asymmetry seen by the 
+ a) A systematic study of the $phi$ dependence of the He4 asymmetry seen by the 
  left side and the right side of the RTPC need to be carried out.\\
@@
 distributions, see figure \ref{fig:sides_rtpc_exclusivity}, the performance of 
-the two sides of the RTPC are almost similar.}\\
-
-\begin{figure}[h!]
+the two sides of the RTPC are very similar.}\\
+
+\begin{figure}[tbp]
    \centering 
@@
 until I am confident about the stability of the results.\\
-\textcolor{blue} { To be updated at the very end}.\\
+
+- External question: what W > 2 $GeV^22$ cut, where the target is assumed to be 
+a nucleon, does for the case of the coherent channel?\\
+\textcolor{blue}{
+To investigate this effect, we removed W cut and identify the coherent DVCS 
+events via the exclusivity cuts presented in chapter 4 of the analysis note.  
+The results are presented in figure \ref{fig:W_coh_DVCS}. As a conclusion, this 
+cut has no effect on the coherent channel and is removed.}\\
+
+\begin{figure}[tbp]
+\includegraphics[height=6.2cm]{fig/W_coh_p.png}             
+\includegraphics[height=6.2cm]{fig/W_coh_He.png} \caption{W distributions of 
+   the identified coherent DVCS events. On the left: $W_p$ is calculated 
+   assuming the target is a nucleon. On the right $W_{^4He}$ is by using the 
+real mass of He4.}
+\label{fig:W_coh_DVCS}
+\end{figure}
 
@@
          \hline
-         1.143 & 0.136 & 0.096 & 23.23927  & 0.1247296  $\pm$  0.08549987 $\pm$ 
-0.005198194 \\
-         1.143 & 0.136 & 0.096 & 59.48556  & 0.3459717  $\pm$  0.07314284 $\pm$   
-0.01733864  \\
-         1.143 & 0.136 & 0.096 & 98.24482  & 0.3662185  $\pm$  0.09123816 $\pm$   
-0.02086274  \\
-         1.143 & 0.136 & 0.096 & 139.8573  & 0.123654   $\pm$  0.1369718  $\pm$   
-0.007644888 \\
-         1.143 & 0.136 & 0.096 & 177.6156  & 0.1881762  $\pm$  0.1425249  $\pm$   
-0.01204172  \\
-         1.143 & 0.136 & 0.096 & 219.9521  & -0.1284634 $\pm$  0.1201698  $\pm$   
-0.008207119 \\
-         1.143 & 0.136 & 0.096 & 263.1257  & -0.3533904 $\pm$  0.09727483  
-$\pm$   0.02156403  \\
-         1.143 & 0.136 & 0.096 & 302.3684  & -0.1883949 $\pm$  0.07858033  $\pm$   0.01054965  \\
-         1.143 & 0.136 & 0.096 & 338.4607  & -0.3627951 $\pm$  0.0780912   $\pm$   0.01790232  \\
-         \hline
-
-         1.423 & 0.172 & 0.099 & 19.93889  & 0.1760962  $\pm$ 0.06994611  $\pm$ 
-0.007186426   \\
-         1.423 & 0.172 & 0.099 & 57.30933  & 0.3273063  $\pm$ 0.07332903  $\pm$ 0.01625548    \\
-         1.423 & 0.172 & 0.099 & 95.76019  & 0.3951926  $\pm$ 0.1072231   $\pm$ 0.02236637    \\
-         1.423 & 0.172 & 0.099 & 138.3863   & 0.1724817  $\pm$ 0.1474493   
-$\pm$ 0.01064165    \\
-         1.423 & 0.172 & 0.099 & 180.1999  & 0.3134116  $\pm$ 0.174575    $\pm$ 
-0.02007781\\
-         1.423 & 0.172 & 0.099 & 219.4606  & -0.2137216 $\pm$ 0.1650798   $\pm$ 0.01365754    \\
-         1.423 & 0.172 & 0.099 & 262.8408  & -0.3995619 $\pm$ 0.1171428   $\pm$ 0.02439264    \\
-         1.423 & 0.172 & 0.099 & 302.7633  & -0.3371412 $\pm$ 0.07239325  $\pm$ 0.01885809    \\
-         1.423 & 0.172 & 0.099 & 337.9644  & -0.1104303 $\pm$ 0.07089989  $\pm$ 0.005460803   \\
-
-         \hline
-         1.902 & 0.224 & 0.107 &    20.63179 &  0.1234387 $\pm$   0.06716204 
-$\pm$   0.005060101   \\
-         1.902 & 0.224 & 0.107 &    56.56459 &  0.3228563 $\pm$   0.06874834 $\pm$   0.01598409    \\
-         1.902 & 0.224 & 0.107 &    96.48    &  0.2124576 $\pm$   0.1092699  $\pm$    0.01204736   \\
-         1.902 & 0.224 & 0.107 &    139.5199 &  0.1641143 $\pm$   0.1786647  $\pm$    0.01014158   \\
-         1.902 & 0.224 & 0.107 &    179.4707 & -0.1374314 $\pm$   0.2300651  $\pm$    0.008801557  \\
-         1.902 & 0.224 & 0.107 &    221.9652 & -0.1313449 $\pm$   0.1867839  $\pm$    0.008381788  \\
-         1.902 & 0.224 & 0.107 &    262.5326 & -0.2970555 $\pm$   0.1203578  $\pm$    0.01814375   \\
-         1.902 & 0.224 & 0.107 &    303.679  & -0.1723132 $\pm$   0.0794609  $\pm$    0.009613363  \\
-         1.902 & 0.224 & 0.107 &    339.1609 & -0.1499256 $\pm$   0.06416965 $\pm$   0.007375924   \\
-
+         1.143 & 0.136 & 0.096 &  23.32563   &    0.1370716  $\pm$   0.08373948  $\pm$   0.02571563 \\
+         1.143 & 0.136 & 0.096 &  59.81847   &    0.3758095  $\pm$   0.07101178  $\pm$   0.01885969 \\
+         1.143 & 0.136 & 0.096 &  97.78493   &    0.4125528  $\pm$   0.08798407  $\pm$   0.04038886 \\
+         1.143 & 0.136 & 0.096 &  140.0018   &    0.159693   $\pm$   0.1366452   $\pm$   0.02678967 \\
+         1.143 & 0.136 & 0.096 &  179.0882   &    0.1714253  $\pm$   0.1398893   $\pm$   0.02789155 \\
+         1.143 & 0.136 & 0.096 &  219.1279   &   -0.1240822  $\pm$   0.1156237   $\pm$   0.02484531 \\
+         1.143 & 0.136 & 0.096 &  263.7259   &   -0.3608519  $\pm$   0.09411095  $\pm$   0.03891253 \\
+         1.143 & 0.136 & 0.096 &  302.9283   &   -0.1683747  $\pm$   0.07604881  $\pm$   0.02632836 \\
+         1.143 & 0.136 & 0.096 &  337.3336   &   -0.3508557  $\pm$   0.07680001  $\pm$   0.03431105 \\
+         \hline                                                                          
+         1.423 & 0.172 & 0.099 &  19.94307   &    0.1650792  $\pm$   0.067211    $\pm$   0.02673700 \\
+         1.423 & 0.172 & 0.099 &  57.17185   &    0.3028724  $\pm$   0.068908    $\pm$   0.02503328 \\
+         1.423 & 0.172 & 0.099 &  95.77216   &    0.4372785  $\pm$   0.099537    $\pm$   0.04267748 \\
+         1.423 & 0.172 & 0.099 &  137.9543   &    0.1147926  $\pm$   0.142932    $\pm$   0.02500644 \\
+         1.423 & 0.172 & 0.099 &  180.9498   &    0.1924395  $\pm$   0.1806951   $\pm$   0.03026008 \\
+         1.423 & 0.172 & 0.099 &  220.1671   &   -0.2589808  $\pm$   0.1611112   $\pm$   0.03447198 \\
+         1.423 & 0.172 & 0.099 &  263.1496   &   -0.3065283  $\pm$   0.1158366   $\pm$   0.03663218 \\
+         1.423 & 0.172 & 0.099 &  302.3187   &   -0.3646641  $\pm$   0.069707    $\pm$   0.03835156 \\
+         1.423 & 0.172 & 0.099 &  338.0674   &   -0.1660148  $\pm$   0.069482    $\pm$   0.02613428 \\
+         \hline                                                                        
+         1.902 & 0.224 & 0.107 &  20.96588   &    0.0841330  $\pm$   0.06370723  $\pm$   0.02345626 \\
+         1.902 & 0.224 & 0.107 &  56.59966   &    0.3739804  $\pm$   0.06574343  $\pm$   0.01851792 \\
+         1.902 & 0.224 & 0.107 &  95.79632   &    0.1779531  $\pm$   0.1058264   $\pm$   0.0173685  \\
+         1.902 & 0.224 & 0.107 &  139.5123   &    0.1574064  $\pm$   0.1713567   $\pm$   0.01702304 \\
+         1.902 & 0.224 & 0.107 &  179.5613   &   -0.0837227  $\pm$   0.2119008   $\pm$   0.01265815 \\
+         1.902 & 0.224 & 0.107 &  221.6768   &   -0.1251566  $\pm$   0.1783256   $\pm$   0.01528429 \\
+         1.902 & 0.224 & 0.107 &  263.0872   &   -0.3069055  $\pm$   0.1173135   $\pm$   0.02602474 \\
+         1.902 & 0.224 & 0.107 &  303.6431   &   -0.2404473  $\pm$   0.07568278  $\pm$   0.02071202 \\
+         1.902 & 0.224 & 0.107 &  339.2973   &   -0.184311   $\pm$   0.06150122  $\pm$   0.01635832 \\
       \hline 
@@
  $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\ 
-        1.164 & 0.132 & 0.095 & 25.00918 & -0.01089098 $\pm$ 0.1093718   $\pm$   
-         0.000458874        \\
-        1.164 & 0.132 & 0.095 & 60.37537 & 0.3737458   $\pm$ 0.07030024  $\pm$   0.01879876       \\
-        1.164 & 0.132 & 0.095 & 98.36012 & 0.4043316   $\pm$ 0.08467823  $\pm$   0.02304085       \\
-        1.164 & 0.132 & 0.095 & 140.2482 & 0.2465853   $\pm$ 0.1273109   $\pm$   0.01525331       \\
-        1.164 & 0.132 & 0.095 & 177.0902 & 0.2375646   $\pm$ 0.1356063   $\pm$   0.01519848       \\
-        1.164 & 0.132 & 0.095 & 218.9657 & -0.1073686  $\pm$ 0.1144325   $\pm$   0.006862974      \\
-        1.164 & 0.132 & 0.095 & 262.7748 & -0.3805058  $\pm$ 0.08938742  $\pm$   0.02323176       \\
-        1.164 & 0.132 & 0.095 & 301.4627 & -0.14755    $\pm$ 0.07265177  $\pm$   0.008283367      \\
-        1.164 & 0.132 & 0.095 & 336.3236 & -0.3183937  $\pm$ 0.09471679  $\pm$   0.01585399       \\
-
-         \hline
-        1.439 & 0.17 & 0.099 &  21.27081  & 0.2034567  $\pm$  0.06758651  $\pm$  
-0.008374507     \\
-        1.439 & 0.17 & 0.099 &  56.76747  & 0.2169678  $\pm$  0.07229423  $\pm$  0.01075096      \\
-        1.439 & 0.17 & 0.099 &  96.06215  & 0.249271   $\pm$  0.1107664   $\pm$  0.01411916      \\
-        1.439 & 0.17 & 0.099 &  137.9266  & 0.1647911  $\pm$  0.1437837   $\pm$  0.01016048      \\
-        1.439 & 0.17 & 0.099 &  180.9459  & 0.04356753 $\pm$  0.1729548   $\pm$  0.002791833     \\
-        1.439 & 0.17 & 0.099 &  221.1382  & -0.2181618 $\pm$  0.1698173   $\pm$  0.01392861      \\
-        1.439 & 0.17 & 0.099 &  264.1321  & -0.2657665 $\pm$  0.1185378   $\pm$  0.01619059      \\
-        1.439 & 0.17 & 0.099 &  302.8373  & -0.3964279 $\pm$  0.07400956  $\pm$  0.02216967      \\
-        1.439 & 0.17 & 0.099 &  337.9737  & -0.2096681 $\pm$  0.06842138  $\pm$  0.01036772      \\
-
-         \hline
-        1.844 & 0.225 & 0.107 & 19.58073  & 0.1554335   $\pm$   0.0628847   
-$\pm$   0.006328427  \\
-        1.844 & 0.225 & 0.107 &   56.29838  & 0.4152198   $\pm$   0.07433955  $\pm$   0.02053361 \\
-        1.844 & 0.225 & 0.107 &   95.70361  & 0.2737049   $\pm$   0.1221503   $\pm$   0.01548828 \\
-        1.844 & 0.225 & 0.107 &  139.5136  & -0.1539183  $\pm$   0.2139162   $\pm$   0.009511429 \\
-        1.844 & 0.225 & 0.107 &   180.1244  & 0.1652893   $\pm$   0.2879629   $\pm$   0.01058847 \\
-        1.844 & 0.225 & 0.107 &  222.8838  & -0.2355333  $\pm$   0.2105884   $\pm$   0.0150224   \\
-        1.844 & 0.225 & 0.107 &  261.1443  & -0.3851749  $\pm$   0.1436202   $\pm$   0.0235777   \\
-        1.844 & 0.225 & 0.107 &  304.757  -& 0.1531414   $\pm$   0.08530942  $\pm$   0.008517339 \\
-        1.844 & 0.225 & 0.107 &  339.9749  & -0.09807582 $\pm$   0.06178372  $\pm$   0.00480806  \\
-
+         \hline
+        1.164 & 0.132 & 0.095 &   24.70837  &    -0.0009864  $\pm$   0.1023417     $\pm$   0.02214862    \\
+        1.164 & 0.132 & 0.095 &   60.38457  &     0.394491   $\pm$   0.06742577    $\pm$   0.01984295    \\
+        1.164 & 0.132 & 0.095 &   98.05482  &     0.4169974  $\pm$   0.0822727     $\pm$   0.04084068    \\
+        1.164 & 0.132 & 0.095 &   140.4849  &     0.2629772  $\pm$   0.1287244     $\pm$   0.03336946    \\
+        1.164 & 0.132 & 0.095 &   178.7877  &     0.1917519  $\pm$   0.133959      $\pm$   0.02937379    \\
+        1.164 & 0.132 & 0.095 &   218.4067  &    -0.1139352  $\pm$   0.1099316     $\pm$   0.02438166    \\
+        1.164 & 0.132 & 0.095 &   263.7104  &    -0.3303477  $\pm$   0.08687361    $\pm$   0.0372357     \\
+        1.164 & 0.132 & 0.095 &   302.0021  &    -0.158615   $\pm$   0.06873616    $\pm$   0.02598807    \\
+        1.164 & 0.132 & 0.095 &   335.3734  &    -0.2978278  $\pm$   0.09144179    $\pm$   0.03198552    \\
+         \hline                                                                         
+        1.439 & 0.17 & 0.099 &    21.20114   &    0.1944966  $\pm$   0.06481715    $\pm$   0.023002136   \\
+        1.439 & 0.17 & 0.099 &    57.05011   &    0.2135007  $\pm$   0.0688628     $\pm$   0.01959182    \\
+        1.439 & 0.17 & 0.099 &    95.32827   &    0.3033697  $\pm$   0.1028014     $\pm$   0.0295878     \\
+        1.439 & 0.17 & 0.099 &    137.6747   &    0.1027237  $\pm$   0.134283      $\pm$   0.01876947    \\
+        1.439 & 0.17 & 0.099 &    180.8816   &   -0.0055032  $\pm$   0.1730991     $\pm$   0.0197908     \\
+        1.439 & 0.17 & 0.099 &    220.8371   &   -0.2294214  $\pm$   0.1615644     $\pm$   0.0270881     \\
+        1.439 & 0.17 & 0.099 &    264.4366   &   -0.2758285  $\pm$   0.1156173     $\pm$   0.02923329    \\
+        1.439 & 0.17 & 0.099 &    302.6414   &   -0.3697083  $\pm$   0.07362371    $\pm$   0.03312501    \\
+        1.439 & 0.17 & 0.099 &    337.925    &   -0.2626907  $\pm$   0.06672689    $\pm$   0.02543044    \\              
+         \hline                                                                         
+        1.844 & 0.225 & 0.107 &   19.94412   &    0.1199148  $\pm$   0.0610976     $\pm$   0.024893846   \\
+        1.844 & 0.225 & 0.107 &   56.1033    &    0.4535308  $\pm$   0.07056983    $\pm$   0.02240954    \\
+        1.844 & 0.225 & 0.107 &   95.56723   &    0.2782661  $\pm$   0.1178502     $\pm$   0.02714954    \\
+        1.844 & 0.225 & 0.107 &   139.3193   &   -0.0854730  $\pm$   0.2144445     $\pm$   0.01668931    \\
+        1.844 & 0.225 & 0.107 &   180.6025   &    0.1409771  $\pm$   0.2599303     $\pm$   0.02044162    \\
+        1.844 & 0.225 & 0.107 &   223.7917   &   -0.2456453  $\pm$   0.2105987     $\pm$   0.02706752    \\
+        1.844 & 0.225 & 0.107 &   260.904    &   -0.3907139  $\pm$   0.1417117     $\pm$   0.03533464    \\
+        1.844 & 0.225 & 0.107 &   304.3742   &   -0.2674945  $\pm$   0.08101173    $\pm$   0.02630272    \\
+        1.844 & 0.225 & 0.107 &   340.0658   &   -0.125335   $\pm$   0.06016415    $\pm$   0.01755089    \\
          \hline  
@@
          \hline
-           1.36 & 0.160 & 0.080 & 21.65936  & 0.191738   $\pm$ 0.07672737  
-$\pm$  0.007911716  \\
-           1.36 & 0.160 & 0.080 &  57.55693  & 0.3027442  $\pm$ 0.06844172  $\pm$  0.01505127  \\
-           1.36 & 0.160 & 0.080 &  96.99456  & 0.386873   $\pm$ 0.09974605  $\pm$  0.02196743  \\
-           1.36 & 0.160 & 0.080 &  138.0931  & 0.1068763  $\pm$ 0.1481201   $\pm$  0.006591219 \\
-           1.36 & 0.160 & 0.080 &  178.9474  & 0.3560828  $\pm$ 0.1622455   $\pm$  0.02279972  \\
-           1.36 & 0.160 & 0.080 &  221.7811  & -0.1575038 $\pm$ 0.1428135   $\pm$  0.01005219  \\
-           1.36 & 0.160 & 0.080 &  265.1648  & -0.4574556 $\pm$ 0.1123913   $\pm$  0.02782067  \\
-           1.36 & 0.160 & 0.080 &  300.928   & -0.2462821 $\pm$  0.08067071 $\pm$   0.01384662 \\
-           1.36 & 0.160 & 0.080 &  340.2102  & -0.1938488 $\pm$ 0.06732494  $\pm$  0.009493476 \\
-
-         \hline
-           1.507 & 0.179 & 0.094 & 20.86336 &  0.1670261  $\pm$ 0.07457232  
-$\pm$  0.006857072 \\
-           1.507 & 0.179 & 0.094 &  56.0533  & 0.3557391   $\pm$ 0.07177428  $\pm$  0.01757378 \\
-           1.507 & 0.179 & 0.094 &  96.89244 &  0.180321   $\pm$ 0.1052948   $\pm$  0.01023623 \\
-           1.507 & 0.179 & 0.094 &  141.685  & 0.05132467  $\pm$ 0.1618232   $\pm$  0.003181041\\
-           1.507 & 0.179 & 0.094 &  177.7203 &  -0.2658653 $\pm$ 0.1840261   $\pm$  0.01701399 \\
-           1.507 & 0.179 & 0.094 &  221.0472 &  -0.1237617 $\pm$ 0.1692357   $\pm$  0.007902008\\
-           1.507 & 0.179 & 0.094 &  262.4797 &  -0.173583  $\pm$ 0.111135    $\pm$  0.01060312 \\
-           1.507 & 0.179 & 0.094 & 303.5025 &  -0.2042846 $\pm$ 0.0814908   $\pm$  0.01140279  \\
-           1.507 & 0.179 & 0.094 & 337.9422 &  -0.1527353 $\pm$ 0.07303888  $\pm$  0.007553509 \\
-
-         \hline
-
-           1.610 & 0.193 & 0.127 & 20.94824 &  0.04717589 $\pm$ 0.07199532 
-         $\pm$ i0.001937809   \\
-           1.610 & 0.193 & 0.127 &59.5986  & 0.3470424   $\pm$ 0.07684609 $\pm$ 0.01740037     \\
-           1.610 & 0.193 & 0.127 &96.79543 &  0.3991681  $\pm$ 0.102308   $\pm$ 0.02265366     \\
-           1.610 & 0.193 & 0.127 &138.4498 &  0.2740809  $\pm$ 0.1495366  $\pm$ 0.01691157     \\
-           1.610 & 0.193 & 0.127 &179.5052 &  0.3297299  $\pm$ 0.1629695  $\pm$ 0.02111728     \\
-           1.610 & 0.193 & 0.127 &218.6472 &  -0.1422435 $\pm$ 0.1447941  $\pm$ 0.009093639    \\
-           1.610 & 0.193 & 0.127 &261.193  & -0.4233491  $\pm$ 0.1116738  $\pm$ 0.02591248     \\
-           1.610 & 0.193 & 0.127 &303.6351 &  -0.2608586 $\pm$ 0.07153079 $\pm$ 0.01455514     \\
-           1.610 & 0.193 & 0.127 &337.479  & -0.2039268  $\pm$ 0.07466683 $\pm$ 0.01010503     \\
-
+           1.36 & 0.160 & 0.080 &   21.30242  &  0.1531553   $\pm$  0.07225752   $\pm$  0.026305318    \\
+           1.36 & 0.160 & 0.080 &   57.11194  &  0.2900274   $\pm$  0.06585235   $\pm$  0.02439207     \\
+           1.36 & 0.160 & 0.080 &   96.15277  &  0.4041914   $\pm$  0.09641501   $\pm$  0.03947151     \\
+           1.36 & 0.160 & 0.080 &   137.9588  &  0.1402594   $\pm$  0.1434757    $\pm$  0.02522018     \\
+           1.36 & 0.160 & 0.080 &   179.2052  &  0.3218006   $\pm$  0.1641379    $\pm$  0.03717874     \\
+           1.36 & 0.160 & 0.080 &   221.4243  &  -0.3213178  $\pm$  0.1356342    $\pm$  0.03708316     \\
+           1.36 & 0.160 & 0.080 &   265.92    &  -0.392002   $\pm$  0.1066914    $\pm$  0.04038161     \\
+           1.36 & 0.160 & 0.080 &   301.3226  &  -0.2284983  $\pm$  0.07726413   $\pm$  0.02940459     \\
+           1.36 & 0.160 & 0.080 &   339.661   &  -0.2348847  $\pm$  0.06494273   $\pm$  0.02810254     \\
+         \hline                                                                         
+           1.507 & 0.179 & 0.094 &  21.17746   & 0.1631617   $\pm$  0.07120653   $\pm$  0.026711914     \\
+           1.507 & 0.179 & 0.094 &  56.92214   & 0.3715996   $\pm$  0.06870001   $\pm$  0.02842517      \\
+           1.507 & 0.179 & 0.094 &  97.24788   & 0.3145243   $\pm$  0.09659388   $\pm$  0.03076673      \\
+           1.507 & 0.179 & 0.094 &  141.6889   & 0.1388844   $\pm$  0.1607593    $\pm$  0.02150343      \\
+           1.507 & 0.179 & 0.094 &  179.6762   & -0.3612444  $\pm$  0.1723714    $\pm$  0.03603272      \\
+           1.507 & 0.179 & 0.094 &  220.3783   & -0.029479   $\pm$  0.1576259    $\pm$  0.01477838      \\
+           1.507 & 0.179 & 0.094 &  262.64     & -0.2524102  $\pm$  0.1096333    $\pm$  0.02830972      \\
+           1.507 & 0.179 & 0.094 &  303.6787   & -0.282367   $\pm$  0.07599572   $\pm$  0.02864878      \\
+           1.507 & 0.179 & 0.094 &  338.2113   & -0.1464348  $\pm$  0.07113145   $\pm$  0.02012911      \\
+         \hline                                                                       
+           1.610 & 0.193 & 0.127 &  21.08428   & 0.0341355   $\pm$  0.07013161   $\pm$   0.021403381     \\
+           1.610 & 0.193 & 0.127 &  59.38832   & 0.4083206   $\pm$  0.07247885   $\pm$   0.02045513      \\
+           1.610 & 0.193 & 0.127 &  96.08225   & 0.3209038   $\pm$  0.1013991    $\pm$   0.0313346       \\
+           1.610 & 0.193 & 0.127 &  138.5581   & 0.1170443   $\pm$  0.146122     $\pm$   0.02038013      \\
+           1.610 & 0.193 & 0.127 &  180.2608   & 0.3477719   $\pm$  0.1581127    $\pm$   0.0354366       \\
+           1.610 & 0.193 & 0.127 &  218.4883   & -0.091217   $\pm$  0.142311     $\pm$   0.01898904      \\
+           1.610 & 0.193 & 0.127 &  261.3985   & -0.320382   $\pm$  0.1108918    $\pm$   0.0327608       \\
+           1.610 & 0.193 & 0.127 &  303.3648   & -0.266328   $\pm$  0.07080153   $\pm$   0.02802882      \\
+           1.610 & 0.193 & 0.127 &  337.2208   & -0.261976   $\pm$  0.07224138   $\pm$   0.02615273      \\
          \hline
@@
  \hline  
-
- 1.395 & 0.166 & 0.407  & 20.99582 & 0.05948851  $\pm$ 0.04387614  $\pm$ 
-0.002545615    \\
- 1.395 & 0.166 & 0.407  & 61.74789 & 0.05987977  $\pm$ 0.04714287  $\pm$ 
-0.004040185    \\
- 1.395 & 0.166 & 0.407  & 95.61221 & 0.1799428   $\pm$ 0.04880652  $\pm$ 0.0147708      \\
- 1.395 & 0.166 & 0.407  & 139.5363 & 0.08171111  $\pm$ 0.06090302  $\pm$ 0.007605015    \\
- 1.395 & 0.166 & 0.407  & 182.201  &0.08009554   $\pm$ 0.07427192  $\pm$ 0.007619131    \\
- 1.395 & 0.166 & 0.407  & 219.8818 & -0.01298693 $\pm$ 0.06771097  $\pm$ 0.00116723     \\
- 1.395 & 0.166 & 0.407  & 258.5257 & -0.13608    $\pm$ 0.04652703  $\pm$ 0.01056183     \\
- 1.395 & 0.166 & 0.407  & 303.4791 & -0.1156886  $\pm$ 0.03632167  $\pm$ 0.006314795    \\
- 1.395 & 0.166 & 0.407  & 337.5902 & -0.03337033 $\pm$ 0.0466729   $\pm$ 0.001028396    \\
-
-         \hline
-  1.886 & 0.233 & 0.499 & 20.36902 & -0.00550785  $\pm$ 0.03554479  $\pm$  
-0.0002332663   \\
-  1.886 & 0.233 & 0.499 & 59.51454 & 0.0865409    $\pm$ 0.04730011  $\pm$  0.00573937     \\
-  1.886 & 0.233 & 0.499 & 96.27168 & 0.1056762    $\pm$ 0.05415594  $\pm$  0.008699009    \\
-  1.886 & 0.233 & 0.499 & 140.2293 & 0.2104464    $\pm$ 0.08284055  $\pm$  0.01960796     \\
-  1.886 & 0.233 & 0.499 & 179.6974 & -0.006023816 $\pm$ 0.1001192   $\pm$  0.0005737056   \\
-  1.886 & 0.233 & 0.499 & 221.8638 & -0.3006683   $\pm$ 0.09505653  $\pm$  0.02688511     \\
-  1.886 & 0.233 & 0.499 & 260.5396 & -0.08288381  $\pm$ 0.0676998   $\pm$  0.006364218    \\
-  1.886 & 0.233 & 0.499 & 303.6075 & -0.1980294   $\pm$ 0.0489431   $\pm$  0.01079362     \\
-  1.886 & 0.233 & 0.499 & 338.5772 & -0.02449678  $\pm$ 0.05217832  $\pm$  0.0007361083   \\
-
-         \hline
-  2.338 & 0.29 & 0.521  & 20.54167 & 0.07520706  $\pm$   0.03409327  $\pm$ 
-0.003194271   \\
-  2.338 & 0.29 & 0.521  & 57.56577 & 0.1583533   $\pm$   0.04763939  $\pm$ 0.01033978    \\
-  2.338 & 0.29 & 0.521  & 95.08678 & 0.07038454  $\pm$   0.06116666  $\pm$ 0.005764509   \\
-  2.338 & 0.29 & 0.521  & 140.4598 & 0.061577    $\pm$   0.1034334   $\pm$ 0.005739368   \\
-  2.338 & 0.29 & 0.521  & 182.4113 & -0.06731816 $\pm$   0.1393835   $\pm$ 0.006402942   \\
-  2.338 & 0.29 & 0.521  & 225.0168 & -0.006314793$\pm$   0.1269017   $\pm$ 0.0005598014  \\
-  2.338 & 0.29 & 0.521  & 260.9166 & -0.249064   $\pm$   0.07753102  $\pm$ 0.01908511    \\
-  2.338 & 0.29 & 0.521  & 303.3817 & -0.2126162  $\pm$   0.05908072  $\pm$ 0.01161831    \\
-  2.338 & 0.29 & 0.521  & 339.1649 & -0.06832607 $\pm$   0.0593668   $\pm$ 0.002021729   \\
-
-         \hline
-  3.098 &0.379 & 0.65  & 20.00771 & 0.1066541  $\pm$   0.03223103  $\pm$   
-0.004489826   \\
-  3.098 &0.379 & 0.65  & 57.14716 & 0.0941076  $\pm$   0.04804565  $\pm$   0.006123894   \\
-  3.098 &0.379 & 0.65  & 94.59164 & 0.1305121  $\pm$   0.06923002  $\pm$   0.01066595    \\
-  3.098 &0.379 & 0.65  & 137.7186 & 0.05354516 $\pm$   0.1440831   $\pm$   0.00496877    \\
-  3.098 &0.379 & 0.65  & 180.4945 & -0.3925136 $\pm$   0.2078121   $\pm$   0.03736982    \\
-  3.098 &0.379 & 0.65  & 227.2433 & 0.0826614  $\pm$   0.1787858   $\pm$   0.007280692   \\
-  3.098 &0.379 & 0.65  & 263.6608 & -0.1950766 $\pm$   0.07945851  $\pm$   0.01472067    \\
-  3.098 &0.379 & 0.65  & 303.4889 & -0.1567501 $\pm$   0.03740481  $\pm$   0.008555163   \\
-  3.098 &0.379 & 0.65  & 340.4058 & -0.0524533 $\pm$   0.03117202  $\pm$   0.001500876   \\
-
+  1.395 & 0.166 & 0.407  &   21.10406  &  0.04811468 $\pm$  0.04658231  $\pm$  0.012062557     \\
+  1.395 & 0.166 & 0.407  &   61.33965  &  0.0836005  $\pm$  0.0531715   $\pm$  0.015623204     \\
+  1.395 & 0.166 & 0.407  &   95.84617  &  0.1792438  $\pm$  0.05315892  $\pm$  0.02637904      \\
+  1.395 & 0.166 & 0.407  &   140.0124  &  0.04524659 $\pm$  0.07010027  $\pm$  0.0158652       \\
+  1.395 & 0.166 & 0.407  &   181.9726  &  0.1242038  $\pm$  0.08510458  $\pm$  0.02346724      \\
+  1.395 & 0.166 & 0.407  &   219.0216  &  0.03828423 $\pm$  0.07649991  $\pm$  0.01509915      \\
+  1.395 & 0.166 & 0.407  &   259.0493  &  -0.1422473 $\pm$  0.0495869   $\pm$  0.02266091      \\
+  1.395 & 0.166 & 0.407  &   303.8597  &  -0.1478417 $\pm$  0.03942399  $\pm$  0.01968592      \\
+  1.395 & 0.166 & 0.407  &   337.5399  &  -0.0844819 $\pm$  0.04879445  $\pm$  0.01425768      \\
+ \hline                                                                      
+  1.886 & 0.233 & 0.499 &    20.62881  &  -0.0058365 $\pm$  0.03877985  $\pm$  0.012482536     \\
+  1.886 & 0.233 & 0.499 &    58.90961  &  0.1058029  $\pm$  0.05262749  $\pm$  0.016983385     \\
+  1.886 & 0.233 & 0.499 &    95.93819  &  0.1373368  $\pm$  0.06176916  $\pm$  0.02021609      \\
+  1.886 & 0.233 & 0.499 &    141.0758  &  0.2106814  $\pm$  0.09877572  $\pm$  0.02858216      \\
+  1.886 & 0.233 & 0.499 &    179.8328  &  0.06009099 $\pm$  0.1188988   $\pm$  0.01464961      \\
+  1.886 & 0.233 & 0.499 &    220.9095  &  -0.03806458 $\pm$  0.1066278   $\pm$  
+ 0.04304848      \\
+  1.886 & 0.233 & 0.499 &    260.608   &  -0.1192977 $\pm$  0.07428519  $\pm$  0.01808374      \\
+  1.886 & 0.233 & 0.499 &    304.2599  &  -0.2011292 $\pm$  0.05552498  $\pm$  0.0198082       \\
+  1.886 & 0.233 & 0.499 &    338.4649  &  -0.0815212 $\pm$  0.0567802   $\pm$  0.01138369      \\
+ \hline                                                                      
+  2.338 & 0.29 & 0.521  &    20.72956  &  0.08229175 $\pm$  0.03744839  $\pm$  0.013506039    \\ 
+  2.338 & 0.29 & 0.521  &    56.90895  &  0.155593   $\pm$  0.05379751  $\pm$  0.01010521     \\ 
+  2.338 & 0.29 & 0.521  &    94.91647  &  0.05217237 $\pm$  0.0715696   $\pm$  0.017660975    \\ 
+  2.338 & 0.29 & 0.521  &    141.1955  &  0.1371172  $\pm$  0.1260972   $\pm$  0.01618568     \\ 
+  2.338 & 0.29 & 0.521  &    181.6533  &  -0.2127209 $\pm$  0.1556657   $\pm$  0.02363223     \\ 
+  2.338 & 0.29 & 0.521  &    224.0629  &  0.2006703  $\pm$  0.1501709   $\pm$  0.02122811     \\ 
+  2.338 & 0.29 & 0.521  &    261.0354  &  -0.2716077 $\pm$  0.09343596  $\pm$  0.02419026     \\ 
+  2.338 & 0.29 & 0.521  &    303.8146  &  -0.2199163 $\pm$  0.06880397  $\pm$  0.01534961     \\ 
+  2.338 & 0.29 & 0.521  &    339.3798  &  -0.0379564 $\pm$  0.06803362  $\pm$  0.014507918    \\ 
+ \hline                                                                      
+  3.098 &0.379 & 0.65  &     20.11158  &  0.1124871  $\pm$  0.03615842  $\pm$  0.014743619    \\ 
+  3.098 &0.379 & 0.65  &     56.98647  &  0.0725830  $\pm$  0.0555646   $\pm$  0.014717011    \\ 
+  3.098 &0.379 & 0.65  &     95.74599  &  0.1911079  $\pm$  0.07990027  $\pm$  0.02811833     \\ 
+  3.098 &0.379 & 0.65  &     137.8186  &  -0.005798  $\pm$  0.1509773   $\pm$  0.01296021     \\ 
+  3.098 &0.379 & 0.65  &     179.3002  &  -0.605363  $\pm$  0.2490573   $\pm$  0.027008585    \\ 
+  3.098 &0.379 & 0.65  &     227.8571  &  0.1695245  $\pm$  0.1915087   $\pm$  0.02732611     \\ 
+  3.098 &0.379 & 0.65  &     263.4649  &  -0.120036  $\pm$  0.09407594  $\pm$  0.02149023     \\ 
+  3.098 &0.379 & 0.65  &     303.8994  &  -0.178453  $\pm$  0.04217566  $\pm$  0.02211641     \\ 
+  3.098 &0.379 & 0.65  &     340.4588  &  -0.059749  $\pm$  0.03455414  $\pm$  0.01412915     \\ 
  \hline
@@
          \hline 
- 1.425 & 0.162 & 0.397 & 20.97013 & 0.08626376   $\pm$   0.04639585  $\pm$ 
-0.003689821  \\
- 1.425 & 0.162 & 0.397 & 62.6421  &0.04930313    $\pm$   0.04597865  $\pm$ 0.003348979  \\
- 1.425 & 0.162 & 0.397 & 95.82162 & 0.1224201    $\pm$   0.04586875  $\pm$ 0.01005802   \\
- 1.425 & 0.162 & 0.397 & 139.6892 & 0.08754554   $\pm$   0.05613428  $\pm$ 0.008150009  \\
- 1.425 & 0.162 & 0.397 & 181.2826 & 0.08689862   $\pm$   0.06698238  $\pm$ 0.008270208  \\
- 1.425 & 0.162 & 0.397 & 219.4891 & -0.0375365   $\pm$   0.06384645  $\pm$ 0.003377014  \\
- 1.425 & 0.162 & 0.397 & 258.6045 & -0.1130657   $\pm$   0.04491125  $\pm$ 0.008771949  \\
- 1.425 & 0.162 & 0.397 & 303.3676 & -0.08717632  $\pm$   0.03808702  $\pm$ 0.004764464  \\
- 1.425 & 0.162 & 0.397 & 337.2495 & -0.001292913 $\pm$   0.05197389  $\pm$ 4.018625e-05 \\
-
-         \hline
-  1.922 & 0.227 & 0.418 & 21.57308 & -0.008430847 $\pm$  0.03822631  $\pm$ 
-0.0003641738  \\
-  1.922 & 0.227 & 0.418 & 59.16565 & 0.111757     $\pm$  0.04526789  $\pm$ 0.007391354   \\
-  1.922 & 0.227 & 0.418 & 96.43508 & 0.1141028    $\pm$  0.05198208  $\pm$ 0.009399181   \\
-  1.922 & 0.227 & 0.418 & 140.9017 & 0.1548699    $\pm$  0.08123609  $\pm$ 0.0144446     \\
-  1.922 & 0.227 & 0.418 & 181.8854 & -0.0481868   $\pm$  0.1001495   $\pm$ 0.004584565   \\
-  1.922 & 0.227 & 0.418 & 222.8398 & -0.2544383   $\pm$  0.0893361   $\pm$ 0.02269204    \\
-  1.922 & 0.227 & 0.418 & 260.2223 & -0.1167433   $\pm$  0.05887855  $\pm$ 0.008979522   \\
-  1.922 & 0.227 & 0.418 & 303.2291 & -0.2337499   $\pm$  0.04409228  $\pm$ 0.01279513    \\
-  1.922 & 0.227 & 0.418 & 337.305  &-0.04801249   $\pm$  0.05092665  $\pm$ 0.001490256   \\
-
-         \hline
-   2.354 & 0.287 & 0.492 & 20.72653 & 0.04639471  $\pm$    0.00197654  $\pm$  
-0.03368072   \\
-   2.354 & 0.287 & 0.492 & 58.45404 & 0.1237376   $\pm$    0.00813755  $\pm$  0.04677291   \\
-   2.354 & 0.287 & 0.492 & 94.51698 & 0.1315813   $\pm$    0.01074982  $\pm$  0.06113826   \\
-   2.354 & 0.287 & 0.492 & 138.9117 & 0.1560256   $\pm$    0.01450708  $\pm$  0.1093031    \\
-   2.354 & 0.287 & 0.492 & 180.8249 & -0.2729523  $\pm$    0.02598283  $\pm$  0.1502588    \\
-   2.354 & 0.287 & 0.492 & 226.2591 & 0.1262439   $\pm$    0.01115158  $\pm$  0.1231889    \\
-   2.354 & 0.287 & 0.492 & 261.4329 & -0.3136316  $\pm$    0.02396477  $\pm$  0.07142533   \\
-   2.354 & 0.287 & 0.492 & 303.6894 & -0.1473891  $\pm$    0.00802600  $\pm$  0.04010664   \\
-   2.354 & 0.287 & 0.492 & 338.8274 & -0.03638465 $\pm$    0.00108621  $\pm$  0.04154249   \\
-
-         \hline
-   2.987 & 0.390 & 0.714 & 19.37729 & 0.1023275  $\pm$   0.004262096  $\pm$   
-0.03068386   \\
-   2.987 & 0.390 & 0.714 & 55.29714 & 0.1178224  $\pm$   0.007550191  $\pm$   0.0549492    \\
-   2.987 & 0.390 & 0.714 & 93.98511 & 0.1667466  $\pm$   0.01359089   $\pm$   0.09110539   \\
-   2.987 & 0.390 & 0.714 & 134.9596 & -0.139577  $\pm$   0.01288957   $\pm$   0.2491587    \\
-   2.987 & 0.390 & 0.714 & 181.8623 & -1.873885  $\pm$   0.1782864    $\pm$   2.72237      \\
-   2.987 & 0.390 & 0.714 & 230.3936 & -0.3244869 $\pm$   0.02830547   $\pm$   0.3535998    \\
-   2.987 & 0.390 & 0.714 & 265.493  &-0.1138915  $\pm$   0.008503447  $\pm$   0.09607017   \\
-   2.987 & 0.390 & 0.714 & 303.6668 & -0.1628255 $\pm$   0.008868856  $\pm$   0.03647585   \\
-   2.987 & 0.390 & 0.714 & 341.0907 & -0.0611224 $\pm$   0.001715804  $\pm$   0.02745835   \\
-
+  1.425 & 0.162 & 0.397 &   21.03589  &  0.08658236   $\pm$  0.04970597   $\pm$  0.013707438    \\
+  1.425 & 0.162 & 0.397 &   62.13969  &  0.09617981   $\pm$  0.0520029    $\pm$  0.016508612    \\
+  1.425 & 0.162 & 0.397 &   95.88097  &  0.1468384    $\pm$  0.05007717   $\pm$  0.02161179     \\
+  1.425 & 0.162 & 0.397 &   140.2158  &  0.05840751   $\pm$  0.06522249   $\pm$  0.0149864      \\
+  1.425 & 0.162 & 0.397 &   181.147   &  0.1472116    $\pm$  0.07694323   $\pm$  0.02355567     \\
+  1.425 & 0.162 & 0.397 &   218.8907  &  -0.0045843   $\pm$  0.07180578   $\pm$  0.01995755     \\
+  1.425 & 0.162 & 0.397 &   259.1392  &  -0.1140192   $\pm$  0.04807579   $\pm$  0.01836548     \\
+  1.425 & 0.162 & 0.397 &   303.893   &  -0.1078614   $\pm$  0.04183492   $\pm$  0.01540446     \\
+  1.425 & 0.162 & 0.397 &   337.0219  &  -0.0313563   $\pm$  0.05506042   $\pm$  0.01052464     \\
+  \hline                                                                       
+  1.922 & 0.227 & 0.418 &   22.06063  &  -0.0071624   $\pm$  0.04158333   $\pm$  0.013118195    \\
+  1.922 & 0.227 & 0.418 &   58.5659   &  0.09277118   $\pm$  0.05070619   $\pm$  0.016106517    \\
+  1.922 & 0.227 & 0.418 &   96.23033  &  0.1248119    $\pm$  0.05973952   $\pm$  0.01838518     \\
+  1.922 & 0.227 & 0.418 &   141.4482  &  0.1767175    $\pm$  0.09500723   $\pm$  0.0246086      \\
+  1.922 & 0.227 & 0.418 &   181.8282  &  -0.0887164   $\pm$  0.1180524    $\pm$  0.01655364     \\
+  1.922 & 0.227 & 0.418 &   221.2517  &  -0.2925814   $\pm$  0.102211     $\pm$  0.03431685     \\
+  1.922 & 0.227 & 0.418 &   260.3485  &  -0.1909171   $\pm$  0.06539497   $\pm$  0.02278749     \\
+  1.922 & 0.227 & 0.418 &   303.5284  &  -0.2302893   $\pm$  0.05094602   $\pm$  0.02067598     \\
+  1.922 & 0.227 & 0.418 &   337.3474  &  -0.0637682   $\pm$  0.05413252   $\pm$  0.01008997     \\
+  \hline                                                                       
+  2.354 & 0.287 & 0.492 &   20.85891  &  0.04657884   $\pm$  0.036766     $\pm$  0.01988718     \\
+  2.354 & 0.287 & 0.492 &   57.91331  &  0.1459641    $\pm$  0.0526584    $\pm$  0.019557668    \\
+  2.354 & 0.287 & 0.492 &   94.69206  &  0.128379     $\pm$  0.07104001   $\pm$  0.01884086     \\
+  2.354 & 0.287 & 0.492 &   139.8528  &  0.1707919    $\pm$  0.1258279    $\pm$  0.02424851     \\
+  2.354 & 0.287 & 0.492 &   179.8321  &  -0.3851509   $\pm$  0.1628791    $\pm$  0.014502416    \\
+  2.354 & 0.287 & 0.492 &   225.9931  &  0.359824     $\pm$  0.1375561    $\pm$  0.014015373    \\
+  2.354 & 0.287 & 0.492 &   261.519   &  -0.2473872   $\pm$  0.08518201   $\pm$  0.02723866     \\
+  2.354 & 0.287 & 0.492 &   304.2744  &  -0.1756475   $\pm$  0.04527543   $\pm$  0.01784578     \\
+  2.354 & 0.287 & 0.492 &   338.8707  &  -0.0591266   $\pm$  0.04527858   $\pm$  0.01010778     \\
+ \hline                                                                        
+  2.987 & 0.390 & 0.714 &   19.433    &  0.1032664    $\pm$  0.03435814   $\pm$  0.014305278    \\
+  2.987 & 0.390 & 0.714 &   55.24427  &  0.07535726   $\pm$  0.06348906   $\pm$  0.014826822    \\
+  2.987 & 0.390 & 0.714 &   95.27441  &  0.21340720   $\pm$  0.1066241    $\pm$  0.03136377     \\
+  2.987 & 0.390 & 0.714 &   134.3823  &  -0.2684007   $\pm$  0.2723481    $\pm$  0.03863117     \\
+  2.987 & 0.390 & 0.714 &   182.475   &  3.6842530    $\pm$  5.592241     $\pm$  0.03642855     \\
+  2.987 & 0.390 & 0.714 &   232.2045  &  -0.3810377   $\pm$  0.426418     $\pm$  0.04691644     \\
+  2.987 & 0.390 & 0.714 &   264.8367  &  -0.0853021   $\pm$  0.1126019    $\pm$  0.02026491     \\
+  2.987 & 0.390 & 0.714 &   304.1341  &  -0.1678875   $\pm$  0.04062397   $\pm$  0.02296748     \\
+  2.987 & 0.390 & 0.714 &   341.2705  &  -0.0649467   $\pm$  0.03014188   $\pm$  0.01568537     \\
  \hline
@@
  $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
-
-         \hline
-  1.823 & 0.213 & 0.145 & 21.76232 & 0.05295778   $\pm$  0.002294523  $\pm$  
-0.04069827  \\
-   1.823 & 0.213 & 0.145 & 58.58495 & 0.1219361    $\pm$  0.008027474  $\pm$  0.04764173  \\
-   1.823 & 0.213 & 0.145 & 96.96136 & 0.1173358    $\pm$  0.009686957  $\pm$  0.04541699  \\
-   1.823 & 0.213 & 0.145 & 140.7066 & 0.1817539    $\pm$  0.01694703   $\pm$  0.06006007  \\
-   1.823 & 0.213 & 0.145 & 181.0183 & -0.001970789 $\pm$  0.0001875857 $\pm$  0.07600509  \\
-   1.823 & 0.213 & 0.145 & 220.405  &-0.04819504   $\pm$  0.004325879  $\pm$  0.06647841  \\
-   1.823 & 0.213 & 0.145 & 260.7167 & -0.1293622   $\pm$  0.009923488  $\pm$  0.04629438  \\
-   1.823 & 0.213 & 0.145 & 303.2256 & -0.1248732   $\pm$  0.006835643  $\pm$  0.03973616  \\
-   1.823 & 0.213 & 0.145 & 337.1253 & -0.0568979   $\pm$  0.001773968  $\pm$  0.04461593  \\
-
-         \hline
- 2.127 & 0.255 & 0.282  & 21.13741 & 0.05676917  $\pm$   0.002434879  $\pm$  
-0.03872277 \\
-  2.127 & 0.255 & 0.282  & 59.88266 & 0.04066772  $\pm$   0.002704859  $\pm$  0.04482714 \\
-  2.127 & 0.255 & 0.282  & 95.47925 & 0.1736134   $\pm$   0.0142431    $\pm$  0.052589   \\
-  2.127 & 0.255 & 0.282  & 140.3364 & 0.05497469  $\pm$   0.005123015  $\pm$  0.07245594 \\
-  2.127 & 0.255 & 0.282  & 181.9189 & -0.103328   $\pm$   0.009830611  $\pm$  0.08641265 \\
-  2.127 & 0.255 & 0.282  & 221.125  &-0.08229461  $\pm$   0.007372876  $\pm$  0.08294356 \\
-  2.127 & 0.255 & 0.282  & 259.4795 & -0.1175477  $\pm$   0.009077516  $\pm$  0.05100342 \\
-  2.127 & 0.255 & 0.282  & 303.6039 & -0.1683549  $\pm$   0.009176586  $\pm$  0.03529877 \\
-  2.127 & 0.255 & 0.282  & 338.8501 & -0.06212176 $\pm$   0.001853458  $\pm$  0.04171552 \\
-
-         \hline
-   2.308 & 0.284 & 0.490 & 20.40386 & 0.1444039   $\pm$    0.006119278   $\pm$  
-0.03725259 \\
-   2.308 & 0.284 & 0.490 & 59.94014 & 0.1145024   $\pm$    0.007619109   $\pm$  0.04516257 \\
-   2.308 & 0.284 & 0.490 & 94.51028 & 0.1042987   $\pm$    0.008520657   $\pm$  0.05770054 \\
-   2.308 & 0.284 & 0.490 & 137.4529 & 0.05629055  $\pm$    0.005221187   $\pm$  0.1013111  \\
-   2.308 & 0.284 & 0.490 & 181.6079 & 0.2913442   $\pm$    0.02772291    $\pm$  0.1200124  \\
-   2.308 & 0.284 & 0.490 & 225.4196 & -0.1115956  $\pm$    0.009881524   $\pm$  0.09789392 \\
-   2.308 & 0.284 & 0.490 & 259.6316 & -0.2224212  $\pm$    0.01716233    $\pm$  0.05517074 \\
-   2.308 & 0.284 & 0.490 & 302.5122 & -0.1288317  $\pm$    0.007108798   $\pm$  0.03097601 \\
-   2.308 & 0.284 & 0.490 & 338.7144 & -0.03035411 $\pm$    0.0009088618  $\pm$  0.03626738 \\
-
-         \hline
-   2.406 & 0.308 & 0.90 & 20.23392 & 0.03616055   $\pm$   0.001528019  $\pm$   
-0.03177921  \\
-   2.406 & 0.308 & 0.90 & 57.19179 & 0.1434394    $\pm$   0.009337483  $\pm$   0.05685747  \\
-   2.406 & 0.308 & 0.90 & 93.08909 & 0.08508241   $\pm$   0.006907134  $\pm$   0.1091959   \\
-   2.406 & 0.308 & 0.90 & 131.5139 & -0.275777    $\pm$   0.02529905   $\pm$   0.4348743   \\
-   2.406 & 0.308 & 0.90 & 177.2893 & 1.936221     $\pm$   0.1845638    $\pm$   0.6244698   \\ 
-   2.406 & 0.308 & 0.90 & 226.5454 & -4.94355     $\pm$   0.4363171    $\pm$   10.50945    \\
-   2.406 & 0.308 & 0.90 & 263.2745 & -0.1005967   $\pm$   0.007607858  $\pm$   0.1138163   \\
-   2.406 & 0.308 & 0.90 & 304.5626 & -0.1565288   $\pm$   0.008438927  $\pm$   0.04279407  \\
-   2.406 & 0.308 & 0.90 & 339.8646 & -0.0230393   $\pm$   0.0006690608 $\pm$   0.03586971  \\
-
+  \hline
+   1.823 & 0.213 & 0.145 &   22.36456  &   0.08044984  $\pm$  0.044171     $\pm$  0.013519389    \\
+   1.823 & 0.213 & 0.145 &   57.76681  &   0.139094    $\pm$  0.05252524   $\pm$  0.019097037    \\
+   1.823 & 0.213 & 0.145 &   97.34826  &   0.1215345   $\pm$  0.05070444   $\pm$  0.01794958     \\
+   1.823 & 0.213 & 0.145 &   141.6077  &   0.1973951   $\pm$  0.07158507   $\pm$  0.0263301      \\
+   1.823 & 0.213 & 0.145 &   180.9132  &   0.03301465  $\pm$  0.087735     $\pm$  0.01504234     \\
+   1.823 & 0.213 & 0.145 &   219.6382  &   0.00344467  $\pm$  0.07526837   $\pm$  0.018209534    \\
+   1.823 & 0.213 & 0.145 &   261.1274  &  -0.1527359   $\pm$  0.05030086   $\pm$  0.01958999     \\
+   1.823 & 0.213 & 0.145 &   303.674   &  -0.1071745   $\pm$  0.04406731   $\pm$  0.0137369      \\
+   1.823 & 0.213 & 0.145 &   337.0581  &  -0.06869941  $\pm$  0.04715184   $\pm$  0.01004524     \\
+ \hline                                                                        
+  2.127 & 0.255 & 0.282  &   21.36259  &  0.07262895   $\pm$ 0.04230211    $\pm$  0.013126559   \\
+  2.127 & 0.255 & 0.282  &   59.22203  &  0.03806518   $\pm$ 0.04905662    $\pm$  0.012518665   \\
+  2.127 & 0.255 & 0.282  &   95.55563  &  0.22988040   $\pm$ 0.05867932    $\pm$  0.03380763    \\
+  2.127 & 0.255 & 0.282  &   140.5704  &  -0.03154477  $\pm$ 0.08162287    $\pm$  0.0178829     \\
+  2.127 & 0.255 & 0.282  &   181.2953  &  -0.1565047   $\pm$ 0.10092       $\pm$  0.0298368     \\
+  2.127 & 0.255 & 0.282  &   219.844   &  -0.03787627  $\pm$ 0.09359193    $\pm$  0.01834677    \\
+  2.127 & 0.255 & 0.282  &   259.6599  &  -0.1349929   $\pm$ 0.05604338    $\pm$  0.02535689    \\
+  2.127 & 0.255 & 0.282  &   304.1345  &  -0.1822338   $\pm$ 0.03916768    $\pm$  0.02481545    \\
+  2.127 & 0.255 & 0.282  &   338.5113  &  -0.07208852  $\pm$ 0.04495988    $\pm$  0.01711214    \\
+ \hline                                                                          
+  2.308 & 0.284 & 0.490 &    20.67062  &  0.129165     $\pm$ 0.0415758     $\pm$  0.015497728  \\
+  2.308 & 0.284 & 0.490 &    59.71279  &  0.113594     $\pm$ 0.05196332    $\pm$  0.017545246  \\
+  2.308 & 0.284 & 0.490 &    94.41645  &  0.1003674    $\pm$ 0.06511375    $\pm$  0.01472001   \\
+  2.308 & 0.284 & 0.490 &    137.7611  &  0.1088956    $\pm$ 0.1159367     $\pm$  0.01662967   \\
+  2.308 & 0.284 & 0.490 &    181.8561  &  0.3436873    $\pm$ 0.1353462     $\pm$  0.03922332   \\
+  2.308 & 0.284 & 0.490 &    225.1743  &  -0.06749131  $\pm$ 0.1106012     $\pm$  0.01250426   \\
+  2.308 & 0.284 & 0.490 &    259.4171  &  -0.2186645   $\pm$ 0.06202168    $\pm$  0.02341567   \\
+  2.308 & 0.284 & 0.490 &    302.9163  &  -0.1778958   $\pm$ 0.03422616    $\pm$  0.01629588   \\
+  2.308 & 0.284 & 0.490 &    338.8539  &  -0.04591294  $\pm$ 0.03922611    $\pm$  0.017893601  \\
+ \hline                         
+   2.406 & 0.308 & 0.90 &    20.16669  &  0.01851554   $\pm$ 0.03466921    $\pm$ 0.017815254  \\
+   2.406 & 0.308 & 0.90 &    57.08842  &  0.167122     $\pm$ 0.06853916    $\pm$ 0.01086996   \\
+   2.406 & 0.308 & 0.90 &    93.11341  &  0.07585309   $\pm$ 0.140148      $\pm$ 0.01108901   \\
+   2.406 & 0.308 & 0.90 &    132.8371  &  -0.1390574   $\pm$ 0.4839775     $\pm$ 0.01772069   \\
+   2.406 & 0.308 & 0.90 &    177.344   &  1.854154     $\pm$ 0.5453675     $\pm$ 0.01816686   \\ 
+   2.406 & 0.308 & 0.90 &    228.2105  &  5.778605     $\pm$ 10.58589      $\pm$ 0.01512427   \\
+   2.406 & 0.308 & 0.90 &    263.1194  &  0.02895751   $\pm$ 0.1390042     $\pm$ 0.017122356  \\
+   2.406 & 0.308 & 0.90 &    305.0914  &  -0.1501369   $\pm$ 0.04840413    $\pm$ 0.01297528   \\
+   2.406 & 0.308 & 0.90 &    340.095   &  -0.05253375  $\pm$ 0.03990596    $\pm$ 0.016446498  \\
  \hline

### 2018-01-08 1st_round_comments/1st_round_comments_final/feb02_comments.tex

--- 2017-12-07 1st_round_comments/1st_round_comments_final/Jan31_2016_comments.tex
@@
 uncertainties, $(\sigma_{r}, \sigma_{\phi}, \sigma_{z}) = (0.53 mm, 2^{\circ}, 
-1.2 mm)$, were not derived from our data and were held fixed.} \\
+1.2 mm)$, were not derived from our data and were held fixed over all 
+calibration itterations.} \\
 
@@
 quadrature $\left(\frac{DOCA}{\sigma_r}\right)^2$ and the denominator adjusted
-accordingly $(N_{pts}-5)$. It has to be written in full form as: (changed in 
+accordingly $(N_{pts}-4)$. It has to be written in full form as: (changed in 
 the note as well).  }\\
@@
       \phi^{helix}_{i} }{\sigma_{\phi}}\right)^{2} + \left( \frac{z^{pt}_{i} - 
-      z^{helix}_{i} }{\sigma_{z} } \right)^{2}}{N_{pts} - 5}
+   z^{helix}_{i} }{\sigma_{z} } \right)^{2}}{N_{pts} - 4}
 \end{equation}
@@
 $\Delta \phi$ at the anode (TDC = 15) is not equal to zero because there is a 
-drift in phi between the anode (the first GEM layer at radial distance equal to 
+drift in $\phi$ between the anode (the first GEM layer at radial distance equal to 
 60 mm) and the readout pads (at radial distance equal to 69mm). Regarding the 
@@
 identified Coherent DVCS events after applying the exclusivity cuts without any 
-initial constrain on $\Delta z$.}\\
+initial constrain on $\Delta z$.  This guides us to correct for these 
+accidentals in our asymmetries in the form: $ A_{LU~~corr.} = \frac{1}{1 - 
+contamination} A_{LU}$ }\\
 
@@
 also neglected in the DVCS analysis on the nucleon, which have higher 
-luminosities. See also the answers to:\\
+luminosities. For discussion of other background sources see also the answers to:\\
 - Comment 31, figure 23, from the first reviewer.\\
@@
  the systematic errors are shown. } \\
- \begin{figure}[h!]
+ \begin{figure}[tbp]
  \centering
@@
 
- \begin{figure}[h!]
+ \begin{figure}[tbp]
  \centering
@@
     x0, y0, R, slope and constant !!!!!.\\
-   \textcolor{blue}{We do use a beamline constraint. See the answer to comment 
-   15 of the first reviewer.}\\
+   \textcolor{blue}{This is true and corrected. See the answer to comment 15 of 
+   the first reviewer.}\\
 
@@
    The plots in figure \ref{fig:Q2_xB} show the coherent and the incoherent 
--tmin distributions distributions with the W and -tmin cuts. }\\
-
-\begin{figure}[h!]
+-tmin distributions with the W and -tmin cuts. }\\
+
+\begin{figure}[tbp]
 \includegraphics[height=6.2cm]{fig/coh_Q2_xB.png}
@@
 
-p. 97: 3.23 -> 2.11 
+52) p. 97: 3.23 -> 2.11 \\
 \textcolor{blue}{ Corrected.}\\
@@
  to be the suitable cuts to ensure that the reconstructed tracks are within the 
- physical volume of the RTPC from one side, and to reduce the background 
- effects on the other presented variables in section 2.2.1.1.  Also, one can 
- see the almost symmetric trends between [-80:-50] and [+50, 80].  }\\
-\begin{figure}[h!]
+ physical volume of the RTPC.}\\
+\begin{figure}[tbp]
 \centering
@@
 scattering and fluctuations in energy loss taken in to account in the 
-simulation?  \textcolor{blue}{
+simulation?  \\
+\textcolor{blue}{
    The coplanarity and the pT distributions are both linked to the azimuthal 
@@
    the comparison between the simulated and the experimental 4He (comment 34 of 
-   the 1st reviewer) that there is slight difference in terms of phi that is 
-   reflected on the coplanaratiy and pT distributions. The difference in phi 
+   the 1st reviewer) that there is slight difference in terms of $phi$ that is 
+   reflected on the coplanaratiy and pT distributions. The difference in $phi$ 
    comes from the fact that experimentally there are some dead regions in the 
    azimuthal range of the RTPC (the locations can be figured out from figure 
-   2.27) where the 4He is not reconstructed if it passes these regions.  These 
-   dead regions are not implemented in the fastmc for the moment. Of course 
-   implementing these regions is very important if we look for measuring the 
-   cross sections as our observables, while most of such acceptance issues 
-   cancel in the case of the asymmetries.}\\
+   2.27). These dead regions are not implemented in the fastmc and might affect 
+   slightly efficencies. We consider that most of such acceptance issues 
+   cancel for the measurement of asymmetries.}\\
 
@@
   c) How sensitive are the fit results to your binning? You could investigate 
-by e.g., adding/removing a bin in phi, or  by shifting the bin edges. (Or you 
+by e.g., adding/removing a bin in $phi$, or  by shifting the bin edges. (Or you 
 could remove any bias introduced by the choice of binning by doing an unbinned 
 fit...)\\
+\textcolor{blue}{ In order to evaluate this uncertainty we binned the data into 
+   11 bins in phi and we compared the reconstructed asymmetries to the results 
+from our old binning.  Figure \ref{fig:coh_bins_phi_9_11} shows the coherent 
+reconstructed $A_{LU}$ as a function of $\phi$ in $Q^{2}$, $x_B$ and $-t$ bins.  
+The coherent, figure \ref{fig:coh_BSA_9_11}, and the incoherent, figure 
+\ref{fig:incoh_BSA_9_11}, measured $A_{LU}$ at $\phi = 90 ^{\circ}$ are showing 
+5$\%$ to 10$\%$ systematic uncertainties that will be included in to our 
+estimated uncertainties. }\\
+\begin{figure}[tbp]
+   \centering
+      \includegraphics[height=7.2cm]{fig/sBSA_Coherent_Q2.png}
+      \includegraphics[height=7.2cm]{fig/sBSA_Coherent_xB.png}
+      \includegraphics[height=7.2cm]{fig/sBSA_Coherent_t.png}
+     \caption{The measured coherent beam-spin asymmetry as
+     a function of $\phi$ in $Q^{2}$, $x_B$ and $-t$ bins, using two binning 
+  sets in $\phi$: 9 bins (in blue) and 11 bins (in red).}
+      \label{fig:coh_bins_phi_9_11}
+    \end{figure}
+
+\begin{figure}[tbp]
+   \centering
+      \includegraphics[height=9.2cm]{fig/BSA_Coherent_9_11.png}
+      \caption{The coherent $A_{LU}$($\phi = 90 ^{\circ}$), from the fit, as a 
+      function of $Q^{2}$, $x_B$ and $-t$, using 9 (in blue) and 11 (in red) 
+   bins in $\phi$.}
+      \label{fig:coh_BSA_9_11}
+    \end{figure}
+
+\begin{figure}[tbp]
+   \centering
+      \includegraphics[height=9.2cm]{fig/BSA_InCoherent_9_11.png}
+      \caption{The incoherent $A_{LU}$($\phi = 90 ^{\circ}$), from the fit, as 
+         a function of $Q^{2}$, $x_B$ and $-t$, using 9 (in blue) and 11 (in 
+      red) bins in $\phi$. }
+      \label{fig:incoh_BSA_9_11}
+    \end{figure}
 
@@
 until I am confident about the stability of the results.\\
-\textcolor{blue} { To be updated at the very end}.\\
 

### 2018-01-08 eg6-letters/NIM/review-1/review-1.tex

--- 2017-12-08 eg6-letters/NIM/review-1/review-1.tex
@@
 so we do not have a value for our RTPC GEM system at this point.}
+>>>>>>> 10849ae3d4920c417e2d8b634ec1b3e86ec0ad03
 
@@
             reconstruction code.} 
+>>>>>>> 10849ae3d4920c417e2d8b634ec1b3e86ec0ad03
 

### 2018-01-08 eg6-letters/coherent/dvcs_he4_prl.tex

@@
 %\documentclass[preprint,nofootinbib,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
-\documentclass[twocolumn,nofootinbib,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
+\documentclass[twocolumn,nofootinbib,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
 \usepackage{graphicx}
@@
 %
-\date{\today}
+%\date{\today}
+
 \begin{abstract}
@@
 process of coherent deeply virtual Compton scattering off a nucleus. The 
-experiment used the 6 GeV electron beam from the CEBAF accelerator at Jefferson 
-Lab incident on a pressurized $^4$He gaseous target placed in front of the CEBAF Large Acceptance 
-Spectrometer (CLAS). The scattered electron was detected by CLAS and the photon 
+experiment uses the 6 GeV electron beam from the Continuous Electron Beam 
+Accelerator Facility (CEBAF) accelerator at Jefferson Lab incident on a 
+pressurized $^4$He gaseous target placed in front of the CEBAF Large Acceptance 
+Spectrometer (CLAS). The scattered electron is detected by CLAS and the photon 
 by a dedicated electromagnetic calorimeter at forward angles. To ensure the 
 exclusivity of the process, a specially designed radial time projection chamber 
-was used to detect the recoiling $^4$He nuclei. We measured beam-spin 
+is used to detect the recoiling $^4$He nuclei.  We measure beam-spin 
 asymmetries larger than those observed on the free proton in the same kinematic 
-domain. From these, we were able to extract, in a model-independent way, the 
+domain.  From these, we are able to extract, in a model-independent way, the 
 real and imaginary parts of the only $^4$He Compton form factor, $\cal H_A$.  
-This first measurement of coherent deeply virtual Compton scattering on 
-the $^4$He nucleus, with a fully exclusive final state via nuclear recoil 
-tagging, leads the way toward 3D imaging of the partonic structure of nuclei.
+This first measurement of coherent deeply virtual Compton scattering on the 
+$^4$He nucleus, with a fully exclusive final state via nuclear recoil tagging, 
+leads the way toward 3D imaging of the partonic structure of nuclei.
 \end{abstract}
-\pacs{Valid PACS appear here}
+%\pacs{Valid PACS appear here}
 
@@
 promising way to access GPDs experimentally is through the measurement of 
-deeply virtual Compton scattering (DVCS), \textit{i.e.}, the hard exclusive 
-electroproduction of a real photon on a hadron. While other processes are also known 
-to be sensitive to GPDs, the measurement of DVCS is considered the cleanest 
-probe and has been the focus of efforts at Jefferson Lab, HERA, and CERN 
+deeply virtual Compton scattering (DVCS), i.e., the hard exclusive 
+electroproduction of a real photon on a hadron. While other processes are also 
+known to be sensitive to GPDs, the measurement of DVCS is considered the 
+cleanest probe and has been the focus of efforts at Jefferson Lab, HERA, and 
+CERN 
 \cite{Stepanyan:2001sm,Airapetian,Airapetian:2010nu,Chekanov:2003ya,Adloff:2001cn,Aktas:2005ty,Chen:2006na,
@@
 functions~\cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}. The results 
-presented in this letter demonstrate the feasibility of such an approach and 
+presented in this Letter demonstrate the feasibility of such an approach and 
 constitute the first step toward a tomography of nuclei.
@@
 Figure~\ref{fig:diags} illustrates the handbag diagram for coherent DVCS on 
-$^4$He, where the four-vectors of the electrons, photons, and $^4$He are denoted 
-by $k/k^\prime$, $q/q^\prime$, and $p/p^\prime$ respectively. For large 
-virtual photon 4-momentum squared, $Q^2=-(k-k')^{2}$, and small squared 
-momentum transfer, $t=(p-p')^{2}$, the DVCS handbag 
-diagram can be factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The 
-hard part includes the photon-quark interaction and is calculable in 
-perturbative QED. The non-perturbative part is parametrized in terms of GPDs, 
-which embed the partonic structure of the hadron. The GPDs depend on the three 
-variables $x$, $\xi$, and $t$. $\xi$ relates to the Bjorken variable 
-$x_{A}$: $\xi\approx {{x_A}\over{2-x_A}}$, where $x_A=\frac{Q^2}{2M_A\nu}$, 
-$\nu$ is the energy of the virtual photon, and 
-$M_A$ is the nuclei mass. $x$ is the quark's internal loop momentum 
-fraction and cannot be accessed experimentally in DVCS. We in fact measure 
-Compton form factors (CFF), which are complex quantities defined as:
+$^4$He, where the four-vectors of the electrons, photons, and $^4$He are 
+denoted by $k/k^\prime$, $q/q^\prime$, and $p/p^\prime$, respectively. For 
+large virtual photon 4-momentum squared, $Q^2=-(k-k')^{2}$, and small squared 
+momentum transfer, $t=(p-p')^{2}$, the DVCS handbag diagram can be factorized 
+into two parts \cite{Freund_Collins,Ji_Osborne}. The hard part includes the 
+photon-quark interaction and is calculable in perturbative QED. The 
+nonperturbative part is parametrized in terms of GPDs, which embed the partonic 
+structure of the hadron. The GPDs depend on the three variables $x$, $\xi$, and 
+$t$. $\xi$ relates to the Bjorken variable $x_{A}$: $\xi\approx 
+{{x_A}\over{2-x_A}}$, where $x_A=\frac{Q^2}{2M_A\nu}$, $\nu$ is the energy of 
+the virtual photon, and $M_A$ is the nuclei mass. $x$ is the quark's internal 
+loop momentum fraction and cannot be accessed experimentally in DVCS.  We in 
+fact measure Compton form factors (CFFs), which are complex quantities defined 
+as
 \begin{align}
 \begin{split}
-\Re e(&\mathcal{H}_{A}) = \\
-    &\mathcal{P} 
-\int_{0}^{1}dx[H_A(x,\xi,t)-H_A(-x,\xi,t)] \, C^{+}(x,\xi), 
+\Re(&\mathcal{H}_{A}) = \\
+    &\mathcal{P} \int_{0}^{1}dx[H_A(x,\xi,t)-H_A(-x,\xi,t)] \, C^{+}(x,\xi), 
 \end{split} \\
-\Im m(&\mathcal{H}_{A}) = - \pi ( H_A(\xi,\xi,t)-H_A(-\xi,\xi,t)),
+\Im(&\mathcal{H}_{A}) = - \pi [H_A(\xi,\xi,t)-H_A(-\xi,\xi,t)],
 \end{align}
-with $H_A$ a GPD, $\mathcal{P}$ 
-the Cauchy principal value integral, and a coefficient function $C^{+}= 
-\frac{1}{x-\xi} + \frac{1}{x+\xi}$.
+with $H_A$ a GPD, $\mathcal{P}$ the Cauchy principal value integral, and a 
+coefficient function $C^{+}= 1/(x-\xi) + 1/(x+\xi)$.
 
@@
 scattered electron and real photon. This measurement was performed on a large 
-set of nuclei ($^4$He, $^{14}$N, $^{20}$Ne, $^{85}$Kr and $^{131}$Xe), 
-but contamination from incoherent processes can be suspected to influence the results 
-significantly~\cite{Guzey:2003jh}. The direct detection of the recoil nucleus 
-can however guarantee that the nucleus remains intact.
+set of nuclei ($^4$He, $^{14}$N, $^{20}$Ne, $^{85}$Kr, and $^{131}$Xe), but 
+contamination from incoherent processes can be suspected to influence the 
+results significantly~\cite{Guzey:2003jh}. The direct detection of the recoil 
+nucleus can, however, guarantee that the nucleus remains intact.
 
@@
 important simplification, as a spin-zero hadron is parametrized by only one 
-chiral even GPD ($H_{A}(x,\xi,t)$) at leading-twist, while four GPDs arise for 
-the spin-$\frac{1}{2}$ nucleon. This significantly simplifies the interpretation of the 
-data and allows a model independent extraction of the $^4$He CFF 
-($\mathcal{H}_{A}$) presented at the end of this letter.
+chiral even GPD [$H_{A}(x,\xi,t)$] at leading twist, while four GPDs arise for 
+the spin-$\frac{1}{2}$ nucleon. This significantly simplifies the 
+interpretation of the data and allows a model-independent extraction of the 
+$^4$He CFF ($\mathcal{H}_{A}$) presented at the end of this Letter.
 
-The CEBAF Large Acceptance Spectrometer (CLAS) in Hall B at Jefferson 
-Lab~\cite{Mecking:2003zu} has been previously supplemented with an inner 
-calorimeter (IC) and a solenoid magnet to measure DVCS observables on the nucleon
+The Continuous Electron Beam Accelerator Facility (CEBAF) Large Acceptance 
+Spectrometer (CLAS) in Hall B at Jefferson Lab~\cite{Mecking:2003zu} has been 
+previously supplemented with an inner calorimeter (IC) and a solenoid magnet to 
+measure DVCS observables on the nucleon
 \cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}. The IC 
@@
 In the kinematic range of the present experiment, the recoil $^4$He nuclei 
-have low momentum, averaging 300 MeV. CLAS could not detect such low-energy $\alpha$ 
-particles, so in order to ensure the exclusivity of the measurement, we built a 
-small and light radial time projection chamber (RTPC). The 
-RTPC was a $20$-cm-long cylinder with a diameter of $15$ cm, positioned in the 
-solenoid magnet. In the center of the RTPC was the target cell, a $25$-cm-long 
-and $6$-mm-diameter Kapton tube with $27$-$\mu$m-thick walls filled with 
-gaseous $^4$He at 6~atm (see~\cite{Dupre:2017upj} for a detailed description of 
-the RTPC and its performances). The experiment (E08-024)~\cite{Hafidi:2008pr} collected
-data over 40 days at the end of 2009 using a 
-nearly 100\% duty factor, longitudinally polarized electron beam (83.7$\pm 3.5 \%$ 
-polarization~\cite{Perrin:thesis}) at an energy of 6.064 GeV. The RTPC was calibrated specifically 
-for the detection of $^4$He nuclei using elastic scattering 
-($e^4$He $\to e^\prime$$^4$He$'$) with a 1.2~GeV electron beam.
+have low momentum, averaging 300 MeV. CLAS could not detect such low-energy 
+$\alpha$ particles, so, in order to ensure the exclusivity of the measurement, 
+we built a small and light radial time projection chamber (RTPC). The RTPC was 
+a $20$-cm-long cylinder with a diameter of $15$ cm, positioned in the solenoid 
+magnet. In the center of the RTPC was the target cell, a $25$-cm-long and 
+$6$-mm-diameter Kapton tube with $27$-$\mu$m-thick walls filled with gaseous 
+$^4$He at 6~atm (see~\cite{Dupre:2017upj} for a detailed description of the 
+RTPC and its performances). The experiment (E08-024)~\cite{Hafidi:2008pr} 
+collected data over 40 days at the end of 2009 using a nearly 100\% duty 
+factor, longitudinally polarized electron beam (83.7$\pm 3.5 \%$ 
+polarization~\cite{Perrin:thesis}) at an energy of 6.064 GeV. The RTPC was 
+calibrated specifically for the detection of $^4$He nuclei using elastic 
+scattering ($e^4$He $\to e^\prime$$^4$He$'$) with a 1.2~GeV electron beam.
 
@@
 were identified in the RTPC using time and energy-loss cuts for tracks in the 
-fiducial region~\cite{Hattawy:thesis}. In addition, we applied a vertex-matching 
-cut to ensure that the 
-electron and helium nucleus originated from a common reaction vertex in the 
-target cell. The photons were 
-detected in either the IC or the CLAS electromagnetic calorimeters. Note that 
-even though the DVCS reaction has only one real photon in the final state, 
-events with more than one good photon were not discarded at this stage. These
+fiducial region~\cite{Hattawy:thesis}. In addition, we applied a 
+vertex-matching cut to ensure that the electron and helium nucleus originated 
+from a common reaction vertex in the target cell. The photons were detected in 
+either the IC or the CLAS electromagnetic calorimeters. Note that even though 
+the DVCS reaction has only one real photon in the final state, events with more 
+than one good photon were not discarded at this stage. These
 were mainly caused by accidental coincidences of soft photons and did not directly
-affect this measurement, as only the most energetic photon of an 
-event was considered a DVCS photon candidate.
-This prescription however slightly increased the corrections associated with
-the $\pi^0$ and the accidental backgrounds discussed below.
+affect this measurement, as only the most energetic photon of an event was 
+considered a DVCS photon candidate. This prescription, however, slightly 
+increased the corrections associated with the $\pi^0$ and the accidental 
+backgrounds discussed below.
 
@@
 and ($\gamma^*$,$^4$He$'$) planes, the missing energy, mass, and transverse
-momentum of the $e'^4$He$'\gamma$ system, the missing mass squared of 
-the $e'^4$He$'$ system, and the angle $\theta$
-between the measured photon and the missing momentum of the $e'^4$He$'$ system.  
-The experimental data for the most relevant exclusivity variables and applied
-cuts are shown in Fig.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for 
-additional details). We also 
-rejected events where a $\pi^0$ was identified by the invariant mass of 
-two photons. About 3200 events passed all these requirements, their kinematic 
-distributions\footnote{We use here and for other results 
-$x_B =\frac{Q^2}{2M_N\nu}$ with $M_N$ the proton mass instead of $x_A$.
-This makes it easier to compare these results with the proton DVCS data
-available in the literature.} are shown in Fig.~\ref{fig:kin-coverage}.
+momentum of the $e'^4$He$'\gamma$ system, the missing mass squared of the 
+$e'^4$He$'$ system, and the angle $\theta$ between the measured photon and the 
+missing momentum of the $e'^4$He$'$ system. The experimental data for the most 
+relevant exclusivity variables and applied cuts are shown in 
+Fig.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for additional details). We 
+also rejected events where a $\pi^0$ was identified by the invariant mass of 
+two photons. About 3200 events passed all these requirements; their kinematic 
+distributions are shown in Fig.~\ref{fig:kin-coverage}. (We use here and for 
+other results $x_B =\frac{Q^2}{2M_N\nu}$ with $M_N$ the proton mass instead of 
+$x_A$. This makes it easier to compare these results with the proton DVCS data
+available in the literature.)
 
@@
 the quantity plotted. The vertical red lines represent the applied cuts.
-The distributions from left to right and from top to bottom are: coplanarity 
-angle $\Delta \phi$, missing energy $E_X$, missing-mass-squared $M_X^2$, and 
-the cone angle $\theta$ between the measured photon and the missing momentum 
-of the $e^\prime{^4}$He$^\prime$ system.}
+The distributions from left to right and from top to bottom are coplanarity 
+angle $\Delta \phi$, missing energy $E_X$, missing mass squared $M_X^2$, and 
+the cone angle $\theta$ between the measured photon and the missing momentum of 
+the $e^\prime{^4}$He$^\prime$ system.}
 \label{fig:kin-cuts}
@@
 
-We identified two main backgrounds, accidental coincidences and exclusive coherent
-$\pi^0$ production. The accidentals have particles originating from different events,
-and we estimated their contribution to be 4.1\% of the data sample. We evaluated this 
-contribution by selecting events passing all the cuts but with the scattered electron and 
-$^4$He originating from different vertices. The $\pi^0$ production can
-be mistaken for DVCS when one of the two photons from the $\pi^0$ 
-decay is produced at low-energy in the laboratory frame and remains undetected.  
-To estimate the effect of this contamination, we developed an event generator 
-tuned on the experimental yield of exclusive $\pi^0$ with two photons measured. 
-We used this generator together with a GEANT3 simulation of our 
-detectors to estimate the ratio of the number of $\pi^0$ events where the 
-two photons are detected to those that are misidentified as DVCS events. This 
-ratio is then multiplied by the measured yield of exclusive $\pi^0$ events to 
-correct the DVCS data. Depending on the kinematics, we found contaminations of 
-2 to 4\%.
+We identified two main backgrounds: accidental coincidences and exclusive 
+coherent $\pi^0$ production. The accidentals have particles originating from 
+different events, and we estimated their contribution to be 4.1\% of the data 
+sample. We evaluated this contribution by selecting events passing all the cuts 
+but with the scattered electron and $^4$He originating from different vertices.  
+The $\pi^0$ production can be mistaken for DVCS when one of the two photons 
+from the $\pi^0$ decay is produced at low energy in the laboratory frame and 
+remains undetected.  To estimate the effect of this contamination, we developed 
+an event generator tuned on the experimental yield of exclusive $\pi^0$ with 
+two photons measured.  We used this generator together with a GEANT3 simulation 
+of our detectors to estimate the ratio of the number of $\pi^0$ events where 
+the two photons are detected to those that are misidentified as DVCS events.  
+This ratio is then multiplied by the measured yield of exclusive $\pi^0$ events 
+to correct the DVCS data. Depending on the kinematics, we found contaminations 
+of 2-4\%.
 
@@
 In this work, the physics observable extracted using coherent DVCS events is
-the beam-spin asymmetry, $A_{LU}$. On an unpolarized target, $A_{LU}$ is 
-defined as the difference of cross sections for the reaction with opposite beam 
+the beam-spin asymmetry $A_{LU}$. On an unpolarized target, $A_{LU}$ is defined 
+as the difference of cross sections for the reaction with opposite beam 
 helicities normalized to the total cross section:
@@
   \end{equation}
-where $d^{4}\sigma^{\pm}$ is the DVCS differential cross 
-section for positive (negative) beam helicity.
+where $d^{4}\sigma^{\pm}$ is the DVCS differential cross section for positive 
+(negative) beam helicity.
 
-In this ratio, luminosity normalization and
-detector efficiencies largely cancel and $A_{LU}$ can be 
-extracted from the reaction yields for the two helicities ($N^{\pm}$):
+In this ratio, luminosity normalization and detector efficiencies largely 
+cancel, and $A_{LU}$ can be extracted from the reaction yields for the two 
+helicities ($N^{\pm}$):
 \begin{equation}
@@
 emitted by the incoming or the outgoing lepton. The DVCS and BH processes are 
-indistinguishable experimentally and the amplitude of the electroproduction of 
+indistinguishable experimentally, and the amplitude of the electroproduction of 
 a real photon includes a sum of the amplitudes of these two processes. The BH 
@@
 kinematics, the cross section of the real photon electroproduction is dominated 
-by BH contribution, which varies strongly with $\phi$, the azimuthal angle 
+by the BH contribution, which varies strongly with $\phi$, the azimuthal angle 
 between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes. The DVCS 
-contribution is smaller by about a factor of two, but independent of $\phi$ at twist-2~%
-\cite{Belitsky:2001ns}, and thus it is possible to separate these contributions 
-with a cross section measurement. However, the DVCS-BH interference term offers 
-an easier experimental access by generating spin asymmetries. We have, in 
-particular, for a spin-zero target the beam spin asymmetry, $A_{LU}$, which 
-can be expressed at leading-order and leading-twist~\cite{Kirchner:2003wt,
-Belitsky:2008bz} as
+contribution is smaller by about a factor of 2 but independent of $\phi$ at 
+twist-2~% \cite{Belitsky:2001ns}, and thus it is possible to separate these 
+contributions with a cross section measurement. However, the DVCS-BH 
+interference term offers an easier experimental access by generating spin 
+asymmetries. We have, in particular, for a spin-zero target the beam spin 
+asymmetry $A_{LU}$, which can be expressed at leading order and leading 
+twist~\cite{Kirchner:2003wt,Belitsky:2008bz} as
 \begin{equation}
@@
 &A_{LU}(\phi) = \\
-&\frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
-{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
-\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}.
+&\frac{\alpha_{0}(\phi) \, \Im (\mathcal{H}_{A})}
+   {\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re (\mathcal{H}_{A}) + 
+   \alpha_{3}(\phi) \, \big[ \Re (\mathcal{H}_{A})^{2} + \Im 
+(\mathcal{H}_{A})^{2} \big]}.
 \end{split}
@@
 \begin{split}
-&\alpha_0 (\phi)  = \frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi) \\
-&\alpha_1 (\phi)  =  c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi) \\
-&\alpha_2 (\phi)  =  \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
-C_{++}(1) cos(\phi) \right) \\
+&\alpha_0 (\phi)  = \frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi), \\
+&\alpha_1 (\phi)  =  c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi), \\
+&\alpha_2 (\phi)  =  \frac{x_{A}(1+\epsilon^2)^2}{y}  \left[ C_{++}(0) +  
+C_{++}(1) \cos(\phi) \right], \\
 &\alpha_3 (\phi) = \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
@@
 where $S_{++}(1)$ and $C_{++}(0,1)$ are the Fourier harmonics of the 
-interference amplitude in the leptonic tensor, $c_{0,1,2}^{BH}$ 
-the Fourier harmonics of the BH amplitude, and
-finally ${\mathcal P}_{1,2}(\phi)$ the BH
-propagators, which include $\cos(\phi)$ dependencies\footnote{The explicit 
-expression of all these terms can be found in Appendix~A of \cite{Armstrong:2017wfw}.}.
-We observe that using the different $\sin(\phi)$, $\cos(\phi)$ and $\cos(2\phi)$ contributions, 
-one can extract unambiguously both the imaginary and real parts of $\mathcal{H}_{A}$
-with a fit of the $A_{LU}(\phi)$ distribution.
+interference amplitude in the leptonic tensor, $c_{0,1,2}^{BH}$ the Fourier 
+harmonics of the BH amplitude, and finally ${\mathcal P}_{1,2}(\phi)$ the BH
+propagators, which include $\cos(\phi)$ dependencies. (The explicit expression 
+of all these terms can be found in Appendix~A of Ref.  
+\cite{Armstrong:2017wfw}.). We observe that, using the different $\sin(\phi)$, 
+$\cos(\phi)$, and $\cos(2\phi)$ contributions, one can extract unambiguously 
+both the imaginary and real parts of $\mathcal{H}_{A}$ with a fit of the 
+$A_{LU}(\phi)$ distribution.
 
 We present in Fig.~\ref{fig:alu} $A_{LU}$ as a function of azimuthal angle 
-$\phi$ and the kinematical variables $Q^2$, $x_B$, and $t$. Due to limited 
-statistics, these latter variables are studied separately with a two-dimensional 
-data binning. The curves on 
-the plots are fits using the function presented in Eq.~(\ref{eq:A_LU-coh}), 
-where the real and imaginary parts of the CFF $\mathcal{H}_{A}$ are the only 
-free parameters. 
+$\phi$ and the kinematical variables $Q^2$, $x_B$, and $t$. Because of limited 
+statistics, these latter variables are studied separately with a 
+two-dimensional data binning. The curves on the plots are fits using the 
+function presented in Eq.~(\ref{eq:A_LU-coh}), where the real and imaginary 
+parts of the CFF $\mathcal{H}_{A}$ are the only free parameters. 
 %Could add a sentence to mention that it is sin phi dominated as expected 
@@
    bins (bottom panel).  The error bars represent the statistical 
-   uncertainties. The grey bands represent the systematic uncertainties, 
-   including the normalization uncertainties. The red curves are the results of 
-   fits with Eq.~(\ref{eq:A_LU-coh}).}
+uncertainties. The gray bands represent the systematic uncertainties, including 
+the normalization uncertainties. The red curves are the results of fits with 
+Eq.~(\ref{eq:A_LU-coh}).}
 \label{fig:alu}
@@
 
-In Fig.~\ref{fig:alu90}, the $Q^2$, $x_{B}$, and $t$-dependencies of the fitted 
+In Fig.~\ref{fig:alu90}, the $Q^2$, $x_{B}$, and $t$ dependencies of the fitted 
 $A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The comparison to HERMES data
 shows that we obtain the same sign, but the size of the error bars and the difference
-of kinematics do not permit to say much more. The $x_{B}$ and $t$-dependencies 
-are also compared to theoretical calculations by S.~Liuti and K.~Taneja 
+of kinematics do not permit us to say much more. The $x_{B}$ and $t$ 
+dependencies are also compared to theoretical calculations by Liuti and Taneja 
 \cite{simonetta_2}. The model accounts for the effect of the nucleon virtuality 
 (off-shellness) on the quark distribution. The calculations are at slightly 
-different kinematics than the data but still allow us to draw some conclusions. The 
-model appear to predict smaller asymmetries than observed. 
-The difference may arise from the theoretical uncertainty in the determination 
-of the crossing point where the parton nuclear distribution becomes larger than the 
-nucleon one, and reverses the sign of the nuclear effect.
+different kinematics than the data but still allow us to draw some conclusions.  
+The model appears to predict smaller asymmetries than observed. The difference 
+may arise from the theoretical uncertainty in the determination of the crossing 
+point where the parton nuclear distribution becomes larger than the nucleon one 
+and reverses the sign of the nuclear effect.
 
@@
 \includegraphics[width=16cm]{F_Coherent_ALU_phi_90.pdf}
-\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $t$-dependencies (right) of
-   $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
-   middle plot: the full-red and the dashed-blue curves are theoretical 
-   calculations from \cite{simonetta_2}. On the right: the green circles are 
-   the HERMES $-A_{LU}$ (a positron beam was used) inclusive measurements 
-   \cite{Airapetian:2010nu}, and the curve is the theoretical calculation 
-   from \cite{simonetta_2}. The grey bands represent the systematic errors.}
+\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $t$ dependencies (right) of
+   $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). In the middle plot, the 
+   full red and the dashed blue curves are theoretical calculations from Ref.  
+   \cite{simonetta_2}. On the right, the green circles are the HERMES $-A_{LU}$ 
+(a positron beam was used) inclusive measurements \cite{Airapetian:2010nu}, and 
+the curve is the theoretical calculation from Ref. \cite{simonetta_2}. The gray 
+bands represent the systematic errors.}
 \label{fig:alu90}
@@
 curves are the calculations based on the convolution model from Ref.~\cite{Vadim_priv}.
-The black-dashed curves are calculations from the same 
-model using different GPDs for the nucleons (VGG model~\cite{Guidal:2004nd}). The 
-blue long-dashed curve on the top-right plot is from
-the off-shell model as described in Ref.~\cite{GonzalezHernandez:2012jv}.}
+The black dashed curves are calculations from the same model using different 
+GPDs for the nucleons [Vanderhaeghen-Guichon-Guidal (VGG) 
+model~\cite{Guidal:2004nd}]. The blue long-dashed curve on the top-right plot 
+is from the off-shell model as described in 
+Ref.~\cite{GonzalezHernandez:2012jv}.}
 \label{fig:CFF_HA}
@@
 {\it convolution} and {\it off-shell}. In the convolution model 
-\cite{Vadim_priv}, the nucleus is assumed to be composed of non-relativistic 
-nucleons, each interacting independently with the probe. The Convolution-Dual 
-model is based on nucleon GPDs from the dual parametrization~\cite{Guzey:2006xi}, 
-where the Convolution-VGG uses nucleon GPDs from the VGG model~\cite{Guidal:2004nd} 
-and is based on the double distributions ansatz \cite{DD_model}. The 
-off-shell model is the same as in Fig.~\ref{fig:alu90} using a more recent
+\cite{Vadim_priv}, the nucleus is assumed to be composed of nonrelativistic 
+nucleons, each interacting independently with the probe. The convolution-dual 
+model is based on nucleon GPDs from the dual 
+parametrization~\cite{Guzey:2006xi}, where the convolution-VGG uses nucleon 
+GPDs from the VGG model~\cite{Guidal:2004nd} and is based on the double 
+distributions ansatz \cite{DD_model}. The off-shell model is the same as in 
+Fig.~\ref{fig:alu90} using a more recent
 GPD model for the nucleon \cite{GonzalezHernandez:2012jv}.
@@
 Recherche Scientifique, the French Commissariat \`a l'Energie Atomique, the 
-U.S. Department of Energy under contract number DE-AC02-06CH11357, the UK 
-Science and Technology Facilities Council (STFC), the Scottish Universities 
-Physics Alliance (SUPA), the National Research Foundation of Korea, and the 
-Office of Research and Economic 
-Development at Mississippi State University. The author (M.~Hattawy) also 
-acknowledges the support of the Consulat G\'en\'eral de France \`a J\'erusalem.  
-The Southeastern Universities Research Association operates the Thomas 
-Jefferson National Accelerator Facility for the United States Department of 
-Energy under contract DE-AC05-06OR23177.
+U.S. Department of Energy under Contract No. DE-AC02-06CH11357, the United 
+Kingdom Science and Technology Facilities Council (STFC), the Scottish 
+Universities Physics Alliance (SUPA), the National Research Foundation of 
+Korea, and the Office of Research and Economic Development at Mississippi State 
+University. M.~Hattawy also acknowledges the support of the Consulat 
+G\'en\'eral de France \`a J\'erusalem.  The Southeastern Universities Research 
+Association operates the Thomas Jefferson National Accelerator Facility for the 
+United States Department of Energy under Contract No. DE-AC05-06OR23177.
 
@@
 D. Mueller, D. Robaschik, B. Geyer, F.M. Dittes and J.~Horejsi,
-Fortsch.\ Phys. {\bf 42}, 101 (1994).
+Fortschr.\ Phys. {\bf 42}, 101 (1994).
 
@@
   M.~Burkardt,
-  Phys.\ Rev.\ D {\bf 62}, 071503 (2000);
-  Erratum: Phys.\ Rev.\ D {\bf 66}, 119903(E) (2002).
+  Phys.\ Rev.\ D {\bf 62}, 071503 (2000); {\bf 66}, 119903(E) (2002).
 
@@
   M.~Diehl,
-  Eur.\ Phys.\ J.\ C {\bf 25}, 223 (2002);
-  Erratum: Eur.\ Phys.\ J.\ C {\bf 31}, 277 (2003).
+  Eur.\ Phys.\ J.\ C {\bf 25}, 223 (2002); {\bf 31}, 277(E) (2003).
 
@@
 \bibitem{Stepanyan:2001sm}
-S.~Stepanyan {\it et al.} [CLAS Collaboration],
+   S.~Stepanyan {\it et al.} (CLAS Collaboration),
 Phys.\ Rev.\ Lett. {\bf 87}, 182002 (2001).
@@
 \bibitem{Airapetian}
-A. Airapetian {\it et al.} [HERMES Collaboration],
+   A. Airapetian {\it et al.} (HERMES Collaboration),
 Phys.\ Rev.\ Lett. {\bf 87}, 182001 (2001);
 Phys.\ Rev.\  D {\bf 75}, 011103 (2007);
-JHEP {\bf 0806}, 066 (2008);
-JHEP {\bf 0911}, 083 (2009);
-JHEP {\bf 1006}, 019 (2010);
+J. High Energy Phys. 06 (2008), 066; 11 (2009) 083;
+06 (2010) 019;
 Phys.\ Lett.\ B {\bf 704}, 15 (2011);
-JHEP {\bf 1207}, 032 (2012);
-JHEP {\bf 1210}, 042 (2012).
+J. High Energy Phys. 07 (2012) 032; 10 (2012) 042.
 
 \bibitem{Airapetian:2010nu}
-A. Airapetian {\it et al.} [HERMES Collaboration],
+   A. Airapetian {\it et al.} (HERMES Collaboration),
 Phys.\ Rev.\ C {\bf 81}, 035202 (2010).
 
-\bibitem{Adloff:2001cn} 
-  C.~Adloff {\it et al.} [H1 Collaboration],
+\bibitem{Adloff:2001cn} C.~Adloff {\it et al.} (H1 Collaboration),
   Phys.\ Lett.\ B {\bf 517}, 47 (2001)
@@
 \bibitem{Chekanov:2003ya}
-S. Chekanov {\it et al.} [ZEUS Collaboration],
+   S. Chekanov {\it et al.} (ZEUS Collaboration),
 Phys.\ Lett.\  B {\bf 573}, 46 (2003).
@@
 \bibitem{Aktas:2005ty}
-A. Aktas {\it et al.} [H1 Collaboration],
+   A. Aktas {\it et al.} (H1 Collaboration),
 Eur.\ Phys.\ J.\ C {\bf 44}, 1 (2005).
 
-\bibitem{Chen:2006na} 
-S.~Chen {\it et al.} [CLAS Collaboration],
+\bibitem{Chen:2006na} S.~Chen {\it et al.} (CLAS Collaboration),
 Phys.\ Rev.\ Lett.\ {\bf 97}, 072002 (2006).
 
-\bibitem{MunozCamacho:2006hx} 
-C. Mu\~noz Camacho {\it et al.} [Jefferson Lab Hall A Collaboration],
+\bibitem{MunozCamacho:2006hx} C. Mu\~noz Camacho {\it et al.} (Jefferson Lab 
+   Hall A Collaboration),
 Phys.\ Rev.\ Lett. {\bf 97}, 262002 (2006).
 
-\bibitem{Girod:2007aa} 
-F.X. Girod {\it et al.} [CLAS Collaboration],
+\bibitem{Girod:2007aa} F.X. Girod {\it et al.} (CLAS Collaboration),
 Phys.\ Rev.\ Lett. {\bf 100}, 162002 (2008).
 
-\bibitem{Mazouz:2007aa} 
-   M.~Mazouz {\it et al.} [Jefferson Lab Hall A Collaboration],
+\bibitem{Mazouz:2007aa} M.~Mazouz {\it et al.} (Jefferson Lab Hall A 
+   Collaboration),
    Phys.\ Rev.\ Lett.\  {\bf 99}, 242501 (2007).
 
-\bibitem{Gavalian:2009} 
-G. Gavalian {\it et al.} [CLAS Collaboration],
+\bibitem{Gavalian:2009} G. Gavalian {\it et al.} (CLAS Collaboration),
 Phys.\ Rev.\ C {\bf 80}, 035206 (2009).
 
-\bibitem{Seder:2015} 
-E. Seder {\it et al.} [CLAS Collaboration],
+\bibitem{Seder:2015} E. Seder {\it et al.} (CLAS Collaboration),
 Phys.\ Rev.\ Lett. {\bf 114}, 032001 (2015).
 
-\bibitem{Defurne:2015kxq} 
-  M.~Defurne {\it et al.} [Jefferson Lab Hall A Collaboration],
-  Phys.\ Rev.\ C {\bf 92}, no. 5, 055202 (2015).
+\bibitem{Defurne:2015kxq} M.~Defurne {\it et al.} (Jefferson Lab Hall A 
+   Collaboration),
+  Phys.\ Rev.\ C {\bf 92}, 055202 (2015).
 
-\bibitem{Pisano:2015} 
-S.~Pisano {\it et al.} [CLAS Collaboration],
+\bibitem{Pisano:2015} S.~Pisano {\it et al.} (CLAS Collaboration),
 Phys.\ Rev.\ D {\bf 91}, 052014 (2015).
@@
 \bibitem{Jo:2015ema}
-H.~S.~Jo {\it et al.} [CLAS Collaboration],
-  Phys.\ Rev.\ Lett.\  {\bf 115}, no. 21, 212003 (2015).
+   H.~S.~Jo {\it et al.} (CLAS Collaboration),
+  Phys.\ Rev.\ Lett.\  {\bf 115}, 212003 (2015).
 
-\bibitem{Joerg:2016hhs} 
-  P.~Joerg [COMPASS Collaboration],
-  PoS DIS {\bf 2016}, 235 (2016).
+\bibitem{Joerg:2016hhs} P.~Joerg (COMPASS Collaboration),
+  Proc. Sci. DIS2016, 235 (2016).
 
@@
 M. Diehl,
-Phys.\ Rept.  {\bf 388}, 41 (2003).
+Phys.\ Rep. {\bf 388}, 41 (2003).
 
@@
 X.D. Ji,
-Ann.\ Rev.\ Nucl.\ Part.\ Sci. {\bf 54}, 413 (2004).
+Annu.\ Rev.\ Nucl.\ Part.\ Sci. {\bf 54}, 413 (2004).
 
@@
 A.V. Belitsky and A.V. Radyushkin,
-Phys.\ Rept. {\bf 418}, 1 (2005).
+Phys.\ Rep. {\bf 418}, 1 (2005).
 
 \bibitem{Boffi:2007yc} S. Boffi and B. Pasquini,
-Riv.\ Nuovo Cim. {\bf 30}, 387 (2007).
+Riv.\ Nuovo Cimento Soc. Ital. Fis. {\bf 30}, 387 (2007).
 
-\bibitem{Guidal:2013rya} 
-M.~Guidal, H.~Moutarde and M.~Vanderhaeghen,
-Rept.\ Prog.\ Phys.\  {\bf 76}, 066202 (2013).
+\bibitem{Guidal:2013rya} M.~Guidal, H.~Moutarde, and M.~Vanderhaeghen,
+Rep.\ Prog.\ Phys.\  {\bf 76}, 066202 (2013).
 
-\bibitem{Berger:2001zb} 
-  E.~R.~Berger, F.~Cano, M.~Diehl and B.~Pire,
-  Phys.\ Rev.\ Lett.\  {\bf 87}, 142302 (2001)
-  [hep-ph/0106192].
+\bibitem{Berger:2001zb} E.~R.~Berger, F.~Cano, M.~Diehl, and B.~Pire,
+  Phys.\ Rev.\ Lett.\  {\bf 87}, 142302 (2001).
 
@@
   F.~Cano and B.~Pire,
-  Eur.\ Phys.\ J.\ A {\bf 19}, 423 (2004)
-  [hep-ph/0307231].
+  Eur.\ Phys.\ J.\ A {\bf 19}, 423 (2004).
 
@@
   V.~Guzey and M.~Siddikov,
-  J.\ Phys.\ G {\bf 32}, 251 (2006)
-  [hep-ph/0509158].
+  J.\ Phys.\ G {\bf 32}, 251 (2006).
 
@@
   R.~Dupr\'e and S.~Scopetta,
-  Eur.\ Phys.\ J.\ A {\bf 52}, no. 6, 159 (2016).
+  Eur.\ Phys.\ J.\ A {\bf 52}, 159 (2016).
 
-\bibitem{Hen:2016kwk} 
-  O.~Hen, G.~A.~Miller, E.~Piasetzky and L.~B.~Weinstein,
-  arXiv:1611.09748 [nucl-ex].
+\bibitem{Hen:2016kwk} O.~Hen, G.~A.~Miller, E.~Piasetzky, and L.~B.~Weinstein,
+  arXiv:1611.09748 [Rev. Mod. Phys. (to be published)].
 
@@
   P.~R.~Norton,
-  Rept.\ Prog.\ Phys.\  {\bf 66}, 1253 (2003).
+  Rep.\ Prog.\ Phys.\  {\bf 66}, 1253 (2003).
 
@@
   D.~F.~Geesaman, K.~Saito and A.~W.~Thomas,
-  Ann.\ Rev.\ Nucl.\ Part.\ Sci.\  {\bf 45}, 337 (1995).
+  Annu.\ Rev.\ Nucl.\ Part.\ Sci.\  {\bf 45}, 337 (1995).
 
@@
 \bibitem{JSeely}
-J. Seely {\it et al.} 
-Phys.\ Rev.\ Lett.\ {\bf 103}, 202301 (2009).
+J. Seely {\it et al.}, Phys.\ Rev.\ Lett.\ {\bf 103}, 202301 (2009).
 
-\bibitem{Mecking:2003zu} 
-B.~A.~Mecking {\it et al.} [CLAS Collaboration],
-   Nucl.\ Instrum.\ Meth.\ A {\bf 503}, 513 (2003).
+\bibitem{Mecking:2003zu} B.~A.~Mecking {\it et al.} (CLAS Collaboration),
+   Nucl.\ Instrum.\ Methods Phys. Res. Sect.\ A {\bf 503}, 513 (2003).
 
@@
   R.~Dupr\'e {\it et al.},
-  arXiv:1706.10160 [physics.ins-det].
-  (submitted to Nucl.\ Instrum.\ Meth.\ A)
+  arXiv:1706.10160.
 
@@
    K.~Hafidi {\it et al.},
-   Proposal PR-08-024 to JLab PAC33.
+   proposal PR-08-024 to JLab PAC33 (unpublished).
 
 \bibitem{Perrin:thesis}
-Y.~Perrin, Ph.D. thesis (2012), Universit{\'e} de Grenoble, France
+Y.~Perrin, Ph.D. thesis, Universit{\'e} de Grenoble, France, 2012
 [Institution Report No. 2012GRENY092].
@@
 \bibitem{Hattawy:thesis}
-M.~Hattawy, Ph.D. thesis (2015), Universit{\'e} Paris Sud - Paris XI, France 
+M.~Hattawy, Ph.D. thesis, Universit{\'e} Paris Sud - Paris XI, France, 2015 
 [Institution Report No. 2015PA112161].
@@
 \bibitem{Belitsky:2001ns}
-A.~V.~Belitsky, D.~Mueller and A.~Kirchner,
+A.~V.~Belitsky, D.~Mueller, and A.~Kirchner,
 Nucl.\ Phys.\ B {\bf 629}, 323 (2002).
@@
   W.~Armstrong {\it et al.},
-  arXiv:1708.00888 [nucl-ex].
+  arXiv:1708.00888.
 
@@
 \bibitem{Vadim_priv}
-Private communications with V.~Guzey based on: 
-V.~Guzey, Phys.\ Rev.\ C {\bf 78}, 025211 (2008).
+   V.~Guzey (private communication); Phys.\ Rev.\ C {\bf 78}, 025211 (2008).
 
@@
 \bibitem{Guidal:2004nd}
-M.~Vanderhaeghen, P.A.M.~Guichon and M.~Guidal, Phys.Rev.Lett.{\bf 80} 5064 (1998), 
-Phys.Rev. D {\bf 60}, 094017 (1999);
-K.~Goeke, M.V.~Polyakov and M.~Vanderhaeghen, Prog.Part. Nucl. Phys. {\bf 47}, 401 (2001);
-M.~Guidal, M.V.~Polyakov, A.V.~Radyushkin and M.~Vanderhaeghen, Phys.\ Rev.\ D {\bf 72}, 054013 (2005).
+M.~Vanderhaeghen, P.A.M.~Guichon, and M.~Guidal, Phys. Rev. Lett.{\bf 80} 5064 
+(1998); Phys. Rev. D {\bf 60}, 094017 (1999);
+K.~Goeke, M.V.~Polyakov, and M.~Vanderhaeghen, Prog.Part. Nucl. Phys. {\bf 47}, 
+401 (2001);
+M.~Guidal, M.V.~Polyakov, A.V.~Radyushkin, and M.~Vanderhaeghen, Phys.\ Rev.\ D 
+{\bf 72}, 054013 (2005).
 
@@
 \bibitem{GonzalezHernandez:2012jv}
-J.~O.~Gonzalez-Hernandez, S.~Liuti, G.~R.~Goldstein and K.~Kathuria,
-Phys.\ Rev.\ C {\bf 88}, no. 6, 065206, (2013).
+J.~O.~Gonzalez-Hernandez, S.~Liuti, G.~R.~Goldstein, and K.~Kathuria,
+Phys.\ Rev.\ C {\bf 88}, 065206 (2013).
 

### 2018-01-12 eg6-letters/NIM/EG6_RTPC_NIM.tex
review of readout session

@@
 
-\begin{figure*}[tb]
-   \centering
-   \includegraphics[width=.75\textwidth]{ReadoutScheme.png}
-   \caption[]{Schematic representation of the RTPC readout system, showing
-   the different elements of the front end electronics.} 
-   \label{fig:ReadoutScheme}
-\end{figure*}
+%\begin{figure*}[tb]
+%   \centering
+%   \includegraphics[width=.75\textwidth]{ReadoutScheme.png}
+%   \caption[]{Schematic representation of the RTPC readout system, showing
+%   the different elements of the front end electronics.} 
+%   \label{fig:ReadoutScheme}
+%\end{figure*}
 
-The readout system, similar to the original BoNuS RTPC system~\cite{Fenker:2008zz}, 
-was based on the front end electronic boards originally developed for the ALICE 
-TPC readout system at CERN~\cite{ALICE-FEE}. The Front End Card (FEC) hosted 
-the analogue receiver circuit and the subsequent amplification and digitization 
-stages, based on the PASA~\cite{Soltveit:2012jp} and 
-ALTRO~\cite{EsteveBosch:2003bj} ASICS. A Readout Control Unit (RCU) board was 
-used to distribute the trigger signal to FECs and for data readout, with each 
-RCU handling up to 25 FECs. Communication between readout controller 
-application (ROC) and FECs was performed trough a custom backplane, 
-implementing a low-voltage signal bus. The RCU communicated with the CLAS DAQ 
-system trough a 200 MB/s optical link, connected to a data acquisition PC 
-hosting a readout receiver card. This PC hosted the ROC used to interface with 
-the CLAS DAQ system. An Ethernet link was also present, for slow-controls and 
-monitoring.
+The readout system was an upgraded version of the original BoNuS RTPC system~\cite{Fenker:2008zz}, 
+based ALICE-TPC front end electronic boards (FECs)~\cite{ALICE-FEE}. 
+Each FEC hosted 128 channels, providing amplification and digitization of the input signals.
+For each event, 100 samples/channel were digitized by the ALTRO ASIC~\cite{EsteveBosch:2003bj}, operated at 10 MHz sampling frequency.
+In order to reduce the data size, the system was operated in zero-suppression mode, keeping data from $N_{PRE}=3$ samples before threshold crossing on the rising edge to $N_{POST}=3$ samples after threshold crossing on the falling edge.
+The theshold level was set on each channel just above the noise level.
 
-The standard CLAS electron trigger was used to initiate the RTPC readout. For each 
-event, 100 samples/channel were digitized and processed by the ALTRO ASIC. In order 
-to reduce the data size, ALTRO was operated in zero-suppression mode, keeping only 
-samples from channels above a programmable threshold set just above the noise level. 
-Samples were pre-processed 
-by a glitch-filter to reject noise and spurious pulses. To properly reconstruct the 
-signal shape, $N_{PRE}=3$ samples before threshold-crossing and $N_{POST}=3$ samples 
-after the signal returns below threshold were saved.
-
-The trigger signal also initiates RCU readout operation from FEC boards. All the 
-measured samples from active channels are reported, together with a channel 
-identifier and a timestamp, to the ROC application, that in turn sends them on 
-the main event builder. Readout from FECs occurs in ``block-transfer'' mode, 
-making use of the ALTRO internal multi-event buffer. This feature could be 
-exploited thanks to the new RCU boards developed for the RTPC readout 
-system\footnote{In the original BoNuS system, the U2F readout controller had no 
-   multi-event capability and used a USB connection rather than fiber optics 
-   for readout. These factors limited the maximum readout rate from the BoNuS 
-detector to about 500 Hz.}. In order to read all the detector readout pads, 
-four FEC crates were used, each equipped with 6 boards, plus a ROC. A schematic 
-of the readout system, for a single crate, is reported in 
-Figure~\ref{fig:ReadoutScheme}. This configuration permitted to reduce the dead 
-time associated to FEC readout operations, which is scaling linearly with the 
-number of boards in the crate. During the 2009 run, the system was successfully 
+A new custom backplane was developed to connect FECs to the Readout Control Unit (RCU)~\cite{RCU}, allowing fast (200 MB/s) communication between the boards.
+The RCU board, used to distribute the trigger signal to different FECs and read data, was equipped with a fast optical link for data transferring to the main event builder.
+These features, together with the ``block-transfer'' readout mode making use of the FECs multi-event buffer, allowed to reach a signifantly higher readout-rate compared to the original BoNuS system.
+During the 2009 run, the system was successfully
 operated with a DAQ rate of 3.1 kHz and a live time of $70 \%$, for a 
 luminosity of about $10^{34}$~cm$^{-2}\cdot$s$^{-1}$ and a beam energy of 
-6.064~GeV.
+6.064~GeV, to be compared with the 500 Hz obtained with the first BoNuS detector at similar run conditions.
 
-Finally, during data reconstruction, the acquired samples were processed to obtain, 
+During data reconstruction, the acquired samples were processed to obtain, 
 for each readout pad, the accumulated charge (ADC) and the pulse time (T). Since 
 pulse time was obtained as the time-stamp of the first sample above threshold, 
-referred to the trigger time, the resolution is equivalent to the ALTRO 
-sampling time, 100~ns.
+referred to the trigger time, the resolution was equivalent to the ALTRO 
+sampling time of 100~ns.
 
@@
  \bibitem{ALICE-FEE}
- L. Musa et al., The ALICE TPC front end Electronics Nuclear Science Symposium 
+ L. Musa et al., The ALICE TPC front end Electronics, Nuclear Science Symposium 
  Conference Record, 2003 IEEE, 5 3647-3651 Vol.5, Oct (2003).
 
-\bibitem{Soltveit:2012jp} 
-   H.~K.~Soltveit {\it et al.},
-  The Preamplifier shaper for the ALICE TPC-Detector,
-  Nucl.\ Instrum.\ Meth.\ A {\bf 676}, 106 (2012).
+%\bibitem{Soltveit:2012jp} 
+%   H.~K.~Soltveit {\it et al.},
+%  The Preamplifier shaper for the ALICE TPC-Detector,
+%  Nucl.\ Instrum.\ Meth.\ A {\bf 676}, 106 (2012).
   %doi:10.1016/j.nima.2012.02.012
@@
   %doi:10.1109/TNS.2003.820629
+\bibitem{RCU}
+    C.~G.~Gutierrez et al., The ALICE TPC Readout Control Unit, IEEE Nuclear Science Symposium Conference Record, 1, 575
 

### 2018-01-12 eg6-letters/NIM/review-1/review-1.tex
Updating comments for review

@@
    maybe in a table, to make them evident.\\
-\textcolor{blue}{The main difference is in the design of the structure, this has 
-been made clearer in this chapter.}
+\textcolor{blue}{The main difference is in the design of the structure and in the
+firmware of the electronics, this has been made clearer.}
 
@@
 \textcolor{blue}{ The text has been modified to clarify the z position of the 
-target and the RTPC with respect to CLAS sectrometer.\\}
-\textcolor{red}{- Regarding the electric field in the induction gap, it was 2.8 
-kV/cm in BoNuS, does anyone know our exact field in this gap?\\}
-\textcolor{blue}{- The gain of such GEM configuration has been studied by 
+target and the RTPC with respect to CLAS sectrometer.\\
+Regarding the electric field it is unclear what you call the induction gap. We
+provide these fields for the drift region and the inter-GEM regions which we 
+find most relevant. If extra information is needed, please let us know.\\}
+The gain of such triple GEM configuration has been studied by 
 CERN's Gas Detector Development Group (Fabio Sauli, Progress with the Gas 
@@
 for Accelerator and Space Applications (Bari, Sept. 4-7, 2003), Nucl. Instr. 
-   and Meth. A522(2004)93). The results, see the reference, demonstrate that 
-one should not simply add gains to each other for multilayer GEM 
-amplifications.  We did not evaluate precisely the overall gain in our chamber, 
-so we do not have a value for our RTPC GEM system at this point.}
->>>>>>> 10849ae3d4920c417e2d8b634ec1b3e86ec0ad03
+and Meth. A522(2004)93). We evaluated only the overall gain in our chamber, 
+the lack of calibration of some electronics elements makes it impossible for 
+us to extract a gain specific to the GEM system at this point.}
 
@@
    acquisition rate was increased (footnote 2).\\
-\textcolor{red}{Raphael, Can you check here?}
+\textcolor{blue}{This section has been completely reworked.}
 
@@
 - why L1 and L2 (trigger levels?) \\
-\textcolor{red}{Raphael, Can you check here? }
+\textcolor{blue}{Based on previous comment, we shortened the discussion and 
+droped this figure. }
 

### 2018-01-12 eg6-letters/NIM/review-1/review-1.tex
Advancing answers.

@@
    "speed"\\
-\textcolor{red}{To the group: We do have radial and azimuthal drift velocities, 
-but we measure the average of their sum. Raph: What is the link with the question?}
+\textcolor{blue}{What is calibrated here is mainly a speed, as we are just looking 
+how fast electrons are going without regard at there direction, which is looked into 
+in the following paragraph.}
 
@@
 the simulations?\\
-\textcolor{red}{- The text has been updated to clarify the procedures.\\
-                - With T = 65*100~ns and drift length equal to 3cm/ 
-             cos(23$^{\circ}$, $v_{drift}$ = 0.501 cm/microsec which is 
-          consistent with our 0.61 cm/microsec from simulation. \\
-               - In deed, we use $delta_{t} = T_{max/2} - T_{min}$ in our 
-            reconstruction code.} 
->>>>>>> 10849ae3d4920c417e2d8b634ec1b3e86ec0ad03
+\textcolor{blue}{The text has been updated to simplify and clarify the procedure 
+(in particular, some of the variable were not necessary). What we are doing is pretty 
+similar to what you describe, but we might have overlooked some informations in the
+original description. Hopefully it is now better.\\
+Trigger time is at time bin 15, so T = 50*100~ns = 5$\mu$s.
+The drift length is equal to 3cm/ cos(23$^{\circ}$ = 3.26 cm (I assume the 7.5 is a typo).
+Giving $v_{drift}$ = 0.65 cm/$\mu$s. These values are exactly what was anticipated by
+our early comparison of gaz mixtures based on MAGBOLTZ, so we assume there is no 
+problem there.\\} 
+\textcolor{red}{Actually the text still needs some work}
 
@@
    first reading\\
-\textcolor{blue}{The text is cleared}
+\textcolor{blue}{The text is cleared.}
 

### 2018-01-16 eg6-letters/NIM/review-1/review-1.tex
Minor fix to compile NIM review

@@
 provide these fields for the drift region and the inter-GEM regions which we 
-find most relevant. If extra information is needed, please let us know.\\}
+find most relevant. If extra information is needed, please let us know.\\
 The gain of such triple GEM configuration has been studied by 

### 2018-01-16 eg6-letters/NIM/EG6_RTPC_NIM.tex
Advancing answers.
Advancing the review comments on NIM

@@
 (using the same elastic events as for the drift paths calibration). This 
-requires a very good GEANT4 simulation including drift paths and the spread of 
-the charge along the path before reaching the pad, so that the simulated hits 
-match the experimental ones. Moreover, the simulation has to match the DAQ 
-features that can lead to cutting out some hits. After setting the simulation 
-properly, we compared simulation to experiment on an event by event basis as 
+requires a detailed simulation, including the drift paths and the diffusion of 
+the charges along the path before reaching the pad to 
+match the experimental data. We implemented in the GEANT4 simulation the
+drift path we obtained from the calibration described above and implemented an ad 
+hoc diffusion to match the average number of hits recorded in the simulation with
+the one from experimental data. To perform this step properly, we implemented in
+the simulation the details of the DAQ process to record hits.
+
+We then compared this simulation to experiment on an event by event basis as 
 shown in Figure~\ref{fig:EVENT_adc_tdc}. The gain for each pad was calculated 
-as the ratio of the measured ADCs to the simulated deposited energy. Then, this 
-set of the gains was applied to the experimental data. We noticed that some 
-pads record lower ADCs than expected. For this reason, we wanted to make sure 
-that the recorded ADCs by a given pad are similar to the ADCs recorded by other 
-pads in the same track. At this step, we compared the mean ADCs of each
-pad to the mean ADCs of the whole track. This ratio is collected for each pad 
-from a sample of elastic events and a gain correction factor is extracted and 
-applied to the first extracted gain ratio giving a final gain for each readout 
-pad. Final results are shown in Figure~\ref{fig:dedx_p_exp_2nd}, where energy 
+as the ratio of the measured ADCs to the simulated deposited energy. This 
+provided our initial set of gains for each pads and it was applied to the 
+experimental data. However, after this calibration some pads recorded lower ADCs 
+than expected. So, we added a correction factor obtained by comparing  
+the energy deposit on a given pad to its neighbours. To do so, we compared, for 
+each track, the energy deposit on a pad to the energy deposit in the whole track. 
+The gain correction factors are extracted by averaging this ratio for a sample 
+of elastic events. Final results are shown in Figure~\ref{fig:dedx_p_exp_2nd}, where energy 
 loss of particles is plotted against momentum over charge ratio. One can 
-clearly see the band for $^4$He in its expected position.
+clearly see the band for $^4$He in its expected position\footnote{The lower peak 
+   in the left module of the RTPC comes from an unidentified problem in this half 
+   of the detector that concerns 7\% of all the elastic events. 
+   Our best guess is that these events are linked with a high voltage supply 
+   issue, that would sometimes bring the GEM gain down. These events pass all 
+   the elastic requirements and we found nothing that differenciates them 
+   from other events but their low recorded ADCs. For 
+   the calibration procedures, these events were therefore excluded.}.
 
@@
 \caption{Simulated (upper) and experimental (lower) ADC and T distributions 
-of a track. The colors indicate the pads, same color in top and bottom indicate 
-that they are the same pad.}
+of a single track. The different colors indicate the signals from different pads, 
+the same color in the top and bottom figure indicate that the signal was registered
+on the same pad.}
 \label{fig:EVENT_adc_tdc}
@@
 channel. Its amplitude is similar to those of real tracks. About 18\% of the 
-readout channels exhibit large contributions from this noise characteristic.  
-Due to its unique time-energy correlation for the given channels, the noise 
-could be removed on an event by event and channel by channel basis without 
-significant loss of good signals. The result of the
+readout channels exhibit large contributions from this noise.  
+Due to its unique time-energy correlation, we use a patern
+recognition algorithm and discard the hits coming from the channels that display 
+this behavior on an event by event basis. The result of the
 procedure is illustrated in the bottom panel of Figure~\ref{fig:noise}.
@@
 pre-amplifiers boards, when simultaneous hits in most of the 16 channels of the
-board were recorded. An event-based technique to identify and remove this noise was developed based 
+board were recorded. An event-based technique to identify and remove this noise 
+was developed based 
 on counting simultaneous hits in each pre-amplifier group, and, if sufficiently large, 
@@
 $\theta$- and $z$-resolutions are highly correlated.
+
 \begin{table}[htbp]
@@
 \end{tabular}
-\caption{The resolutions of the two modules of the RTPC for $z$-vertex, polar and azimuthal angles, and momentum.}
+\caption{The resolutions of the two modules of the RTPC for $z$-vertex, 
+polar and azimuthal angles, and momentum.}
 \label{tab:reso}

### 2018-01-16 eg6-letters/NIM/review-1/review-1.tex
Advancing the review comments on NIM

@@
    "speed"\\
-\textcolor{blue}{What is calibrated here is mainly a speed, as we are just looking 
-how fast electrons are going without regard at there direction, which is looked into 
-in the following paragraph.}
+\textcolor{blue}{What is calibrated here is mainly the drift time, based 
+on your next question as well, we clarified the text about these.} 
+\textcolor{red}{To be implemented}
 
@@
    to simulate the electronics?\\
-\textcolor{blue}{Only GEANT4 simulation was used in performing the gain 
-   calibration, where the drift paths are updated in the simulation. The 
-   electrons avalanche formation and the gas diffusion are performed though 
-GEANT4. We did not implement a detailed description to simulate the 
-electronics, but we did apply similar conditions to match the real DAQ, such as 
-the rejection of the signals from bad pads and conditions to ensure that each 
-pad must have at least 3 consecutive time bins, with ADC values above the 
-threshold, 35 ADCs, in order to be recorded. The text is cleared with more 
-details. }
+\textcolor{blue}{The section has been extended to provide more details. We 
+implemented specific codes in our GEANT4 simulation to have a realistic 
+description of the electron drifts and of the DAQ process.}
 
@@
    good tracks been used for calibration? Lack of statistics?\\
-\textcolor{blue}{Correction factor on the extracted gain for each pad. We used 
-the elastic $^4$He tracks as we could calculate the recoil $^4$He kinematics 
-from the scattered electron in CLAS to avoid any discrepancy from the RTPC.}
+\textcolor{blue}{We improved the gains by using a method based only on data,
+the text has been clarified on the topic. All these calibration procedures
+are performed with good tracks only.}
 
@@
  - pass2: to make sure that the recorded ADCs by a given pad are similar to the 
- recorded ADCs by other pads in the same track, we refined this calibration 
- after the extracted gains were applied to the experimental data. At this step, 
+ recorded ADCs by other pads in the same track, we refined this calibration. For this, 
  we compared the mean ADCs of each pad to the mean ADCs of the whole track. 
@@
    questions, but I could not understand the figure.\\
-   \textcolor{blue}{- It is for only one track (written in the caption).
-   - We dont understand your second question. A pad is a channel. Do you mean 
-how many pads are fired for a single track? Figure \ref{npd_track} shows the 
-number of active pads as a function of the momentum for the collected elastic 
-$^4$He tracks.\\
-- dE is calculated from the ADCs of the individual pads that read out hits 
-  corresponding to the same track. One needed to know the individual step size 
-  very precisely to put dEdx from the individual pads, which is not available.  
-  - Last question is addressed by figure \ref{npd_track}. The mean value is 
-    around 10 pads. }
-
-\begin{figure}[h!]
-   \centering
-   \includegraphics[scale=0.45]{npd_p_elastic.png}
-   \caption{The number of active pads versus the measured momentum of the 
-   elastic $^4$He tracks. } \label{fig:npd_track}
-\end{figure}
+   \textcolor{blue}{This figure only displays one track. Pads are single channels, 
+the bins correspond to time (100 ns per bin). The dE is calculated overall in general,
+we use this pad by pad method only for calibration. The average number of pad per 
+track is 9, with most of the good tracks between 6 and 14.}
 
@@
    the smear on the top part of the right picture. \\
-\textcolor{red}{- The figures layout will be updated.\\}
+\textcolor{red}{The figures layout will be updated.\\}
 
-\textcolor{blue}{- The y-axis label on figure 12 is updated.\\}
-\textcolor{blue}{- Regarding the lower peak in the left module of the RTPC, 
-   these events pass all the elastic requirements but for some reasons they 
-   have lower ADC values.  They represent around 7\% of all the elastic events.  
-   After extended studies, the nature of these particles is not identified yet.  
-   We note that this is a global phenomenon in the left module as 94\% of the 
-   left module's pads are involved in both some low and high dEdx events. For 
-   the calibration procedures, the events with low dEdx were excluded as we do 
-not fully understand their nature.}
+\textcolor{blue}{The y-axis label on figure 12 is updated. Regarding the lower 
+   peak in the left module of the RTPC, it is likely not deuterons. We added
+   a footnote to clarify the question.}
 
@@
 \textcolor{blue}{The oscillatory noise was removed just by rejecting all hits 
-from a channel if too many of its hits fall on the noise curve in a given 
-event. No threshold/pedestal concept, just hit rejection if it looks like 
-noise. }
+from a channel if too many of these hits fall on the noise curve in a given 
+event. We did not use a threshold or pedestal concept, just a pad rejection 
+if we observe the oscillating noise in the event, the text was clarified.}
 
@@
 \textcolor{blue}{The distance between hits are calculated in 3D. This cut has 
-been chosen because it enables us to jump longer gaps from dead areas of the 
-readout pads without increasing the level of spurious tracks.}
+been chosen because it enables to jump a one pad gap in case of a dead 
+channel.}
 
@@
    ionization in this gas mixture?\\
-   \textcolor{blue}{Figure \ref{fig:nb_hits} shows the number of hits 
-   distribution for the collected elastic $^4$He tracks from the 1.2 GeV 
-dataset. The mean number of hits is around 135 and the 10 hits cut at the 
-reconstruction level is a loose cut to reduce the level of the spurious 
-tracks.}
-
-\begin{figure}[h!]
-   \centering
-   \includegraphics[scale=0.45]{nb_hits.png}
-   \caption{the number of hits distribution for the collected elastic $^4$He 
-   tracks from the 1.2 GeV dataset.} \label{fig:nb_hits}
-\end{figure}
+   \textcolor{blue}{This cut is set to avoid tracks made out of random noise and
+to limit computing time. The number of hits in good tracks at the end of the 
+analysis is always above 30, with a mean around 135, so this cut has no impact 
+on the good track selection.}
 
@@
    times. Sum $dE_{i}$/Sum $dx_{i}$ is not equal to Sum ($dE_{i}/dx_{i}$).\\
-\textcolor{blue}{We actually did compute dEdx with  path-length and ADC- 
+\textcolor{blue}{We compute dEdx with path-length and ADC- 
 truncations, and a linear fit to ADC vs path-length to get slope and fit 
 quality and dedx from fit. Unfortunately, it never seemed to give us much 
-improvement compared to Sum $dE_{i}$/Sum $dx_{i}$. }
+improvement compared to Sum $dE_{i}$/Sum $dx_{i}$. Note that, by the nature of 
+the FADC electronics used, our hits always correspond to 100 ns time bins such that
+each measured ADCs are almost dE/dx measurements already.}
 
@@
    to compute the mean efficiency? If I misunderstood, please comment.\\
-\textcolor{red}{Nathan, do you still have the individual integrals? }
+\textcolor{blue}{This study has been performed by a student a long time
+ago and we do not have all the individual fits anymore.}
 
@@
    but what is the rate the RTPC underwent during data taking?\\
-\textcolor{red}{Can we find such information in the logbook?}
+\textcolor{red}{The rate of protons is of MHz in the chamber with a readout of
+about 3kHz, so one could argue that it is both. Our point here is to emphasis
+the high rate however, as these slow protons deposit a lot of energy in the 
+chamber.}
 
@@
    performances in that case?\\
-\textcolor{blue}{Typically, the elastic reaction is used for such performance 
-evaluation. But the elastic cross sections is really small at 6 GeV beam 
-energy.}
+\textcolor{blue}{It is not possible to do such studies with the 6 GeV beam, because 
+of the lack of an exclusive process to use as elastic cross sections drops dramatically 
+in our acceptance at such high energy. We would have loved to and tried many alternate
+channels, but none was detectable with reasonnable statistics.}
 
@@
 
+\textcolor{blue}{We would like to thank the reviewer for the detailed remark that
+helped improving the manuscript significantly.}
+
 \end{document}

### 2018-01-18 eg6-letters/NIM/EG6_RTPC_NIM.tex
Improving the NIM paper

@@
 \usepackage{bm}  
+\usepackage{textcomp}  
 \usepackage{amssymb}  
@@
 structure and fabrication technique that both increased the acceptance and 
-reduced the amount of material in the path of the outgoing particles. The enhanced design, 
+reduced the amount of material in the path of the outgoing particles. 
+Moreover, the data aquisition electronic was improved to increase the event 
+readout rate. The enhanced design, 
 used in the 2009 DVCS experiment, is described in section \ref{sec_design} of 
-this paper. The data acquisition system described in section \ref{sec_readout} 
-was reconfigured to increase the event readout rate. The calibration methods 
-are discussed in section \ref{sec_calib} and the tracking algorithm in section
-\ref{sec_tracking}. Finally, the overall performance
-of the RTPC is described in section \ref{sec_perfor}.
+this paper. The data acquisition system is described in section \ref{sec_readout}, 
+the calibration methods in section \ref{sec_calib} and the tracking algorithm in section
+\ref{sec_tracking}. Finally, the overall performances
+of the RTPC are described in section \ref{sec_perfor}.
 
@@
   \item The 6~atm $^4$He target extends along the beamline forming the detector 
-     central axis; it is a 292~mm~long, 6~mm diameter Kapton straw with a 
-     27~$\mu$m wall. The detector and the target are centered at 64~cm upstream 
-     of the CLAS center.
+     central axis. It is a 6~mm diameter Kapton straw with a 27~\textmu{}m wall 
+     of 292~mm length such that its entrance and exit 15~\textmu{}m aluminum windows 
+     are placed outside of the detector volume. The detector and the target are 
+     placed in the center of the solenoid, 64~cm upstream of the CLAS center.
    \item The first gas gap covers the radial range from 3~mm to 20~mm. It is 
@@
       M\o{}ller electrons scattered by the beam. This region is surrounded by 
-      a 4 $\mu$m thick window made of grounded aluminized Mylar.
+      a 4 \textmu{}m thick window made of grounded aluminized Mylar.
    \item The second gas gap region extends between 20~mm and 30~mm and is 
       filled with the gas mixture of 80$\%$ neon (Ne) and 20$\%$ dimethyl ether 
-      (DME).  This region is surrounded by a 4~$\mu$m thick window made of 
+      (DME).  This region is surrounded by a 4~\textmu{}m thick window made of 
       aluminized Mylar set at $-4260$~V to serve as the cathode.
@@
 amount of energy. The GEMs for this RTPC are made from a Kapton insulator 
-layer, 50~$\mu$m thick, sandwiched between two 5~$\mu$m copper 
+layer, 50~\textmu{}m thick, sandwiched between two 5~\textmu{}m copper 
 layers\footnote{The GEM foils were produced by Tech-Etch, Inc.}. The mesh of 
-each GEM layer is chemically etched with 50~$\mu$m diameter holes with 
+each GEM layer is chemically etched with 50~\textmu{}m diameter holes with 
 double-conical shapes as illustrated in Figure~\ref{fig:GEMs}. The potential 
@@
 the RTPC was essencially composed of two independent half-cylinder separated
-by their own structures. In these, the installation of the GEM was not very practical
+by their own structures. In this design, the installation of the GEMs was not very practical
 and wrinkles were visibles on the GEM surfaces. To allow for a better installation 
 and, at the same time, keep the mechanical structure out of the drift volume, 
-the present design is based on GEM cylinder. This improves the acceptance of the
-overall detector and reduces the material budget in the 
-forward region, where we detect other particles in CLAS. We 
+the present design is based on self supporting GEM cylinder. We 
 realized these cylinders by using fiber glass rings glued to 
-each ends of the GEM foils to form self supporting pieces that could be 
-installed independently in the RTPC after gluing and soldering operations. The 
+each ends of the GEM foils in order to 
+instal them independently in the RTPC after gluing and soldering operations. The 
 rigidity of the GEM foils was enough for the structure to be self-supporting 
@@
 
-%\begin{figure*}[tb]
-%   \centering
-%   \includegraphics[width=.75\textwidth]{ReadoutScheme.png}
-%   \caption[]{Schematic representation of the RTPC readout system, showing
-%   the different elements of the front end electronics.} 
-%   \label{fig:ReadoutScheme}
-%\end{figure*}
-
 The readout system was an upgraded version of the original BoNuS RTPC system~\cite{Fenker:2008zz}, 
 based ALICE-TPC front end electronic boards (FECs)~\cite{ALICE-FEE}. 
-Each FEC hosted 128 channels, providing amplification and digitization of the input signals.
-For each event, 100 samples/channel were digitized by the ALTRO ASIC~\cite{EsteveBosch:2003bj}, operated at 10 MHz sampling frequency.
-In order to reduce the data size, the system was operated in zero-suppression mode, keeping data from $N_{PRE}=3$ samples before threshold crossing on the rising edge to $N_{POST}=3$ samples after threshold crossing on the falling edge.
-The theshold level was set on each channel just above the noise level.
+Each FEC hosted 128 channels, providing amplification and digitization of the 
+input signals. For each event, 100 samples/channel were digitized by the ALTRO 
+ASIC~\cite{EsteveBosch:2003bj}, operated at 10 MHz sampling frequency. In order 
+to reduce the data size, the system was operated in zero-suppression mode, 
+keeping data from $N_{PRE}=3$ samples before threshold crossing on the rising 
+edge to $N_{POST}=3$ samples after threshold crossing on the falling edge. 
+The threshold level was set on each channel just above the noise level.
 
-A new custom backplane was developed to connect FECs to the Readout Control Unit (RCU)~\cite{RCU}, allowing fast (200 MB/s) communication between the boards.
-The RCU board, used to distribute the trigger signal to different FECs and read data, was equipped with a fast optical link for data transferring to the main event builder.
-These features, together with the ``block-transfer'' readout mode making use of the FECs multi-event buffer, allowed to reach a signifantly higher readout-rate compared to the original BoNuS system.
-During the 2009 run, the system was successfully
-operated with a DAQ rate of 3.1 kHz and a live time of $70 \%$, for a 
+A new custom backplane was developed to connect FECs to the Readout Control 
+Unit (RCU)~\cite{RCU}, allowing fast (200 MB/s) communication between the 
+boards. The RCU board, used to distribute the trigger signal to different FECs 
+and read data, was equipped with a fast optical link for data transferring to 
+the main event builder. These features, together with the ``block-transfer'' 
+readout mode making use of the FECs multi-event buffer, allowed to reach a 
+signifantly higher readout-rate compared to the original BoNuS system. During 
+the 2009 run, the system was successfully 
+operated with a DAQ rate of 3.1 kHz and a live time of 70~\%, for a 
 luminosity of about $10^{34}$~cm$^{-2}\cdot$s$^{-1}$ and a beam energy of 
@@
 
-In this section we will detail the methods used to calibrate the drift speed,
-drift paths and gains of the detector. Drift speed and paths were initially
+In this section we will detail the methods used to calibrate the drift time,
+drift paths and gains of the detector. Drift time and paths were initially
 calculated using the MAGBOLTZ~\cite{Biagi:1999nwa} program, then refined using
-data to account for variations of the run conditions. We always assume 
-cylindrical symmetry in the chamber for the calibration, such that none of
-the parameters depend on the azimuthal angle $\phi$. The initial MAGBOLTZ
+data to account for variations of the run conditions. We assume 
+cylindrical symmetry in the chamber for the calibration of the drift parameters, 
+such that do not depend on the azimuthal angle $\phi$. The initial MAGBOLTZ
 calibration was improved through several iterations of the
-process described below, with each time an increasing number of tracks 
+data driven process described below, with each time an increasing number of tracks 
 reconstructed in the RTPC. The figures presented in this section
@@
 
-\subsection{Drift Speed Parametrization}
+\subsection{Maximum Drift Time Parametrization}
 
+%To be rewritten!!!
 After the ionization, the released electrons drift to the cylindrical detection 
 plane under the effect of the electric field. The electrons released close to 
-the cathode take the most time to reach the readout pads, and the cylindrical 
-symmetry ensures that this maximum drift distance is the same for all tracks.  
+the cathode take the most time to reach the readout pads, the cylindrical 
+symmetry indicates that this maximum drift distance is the same for all tracks.  
 We illustrate this in Figure~\ref{fig:RTPC_signals}, where we depict a typical 
@@
 first calibration, but, as can be seen with the drift speed, conditions in the 
-chamber were changing over time. Moreover, the 4 $\mu$m foil used as a cathode 
+chamber were changing over time. Moreover, the 4 \textmu{}m foil used as a cathode 
 is easily deformed, such that we expect the geometrical accuracy to be of few 
@@
 necessitated a correction for optimal momentum reconstruction at the primary 
-interaction vertex.  The dominant loss was in the 27~$\mu$m thick Kapton target 
+interaction vertex.  The dominant loss was in the 27~\textmu{}m thick Kapton target 
 wall, with significant contributions also from the pressurized target gas and 

### 2018-01-18 eg6-letters/NIM/review-1/review-1.tex
Updated the review answers of NIM

@@
 Regarding the electric field it is unclear what you call the induction gap. We
-provide these fields for the drift region and the inter-GEM regions which we 
+provide the fields for the drift region and the inter-GEM regions which we 
 find most relevant. If extra information is needed, please let us know.\\
@@
 the lack of calibration of some electronics elements makes it impossible for 
-us to extract a gain specific to the GEM system at this point.}
+us to extract a gain specific to our GEM system at this point.}
 
@@
    very high fields.\\
-\textcolor{blue}{Sorry typo. It is 50 $mu$m}
+\textcolor{blue}{Sorry typo. It is 50 $\mu$m}
 
@@
 on your next question as well, we clarified the text about these.}
-\textcolor{red}{To be implemented}
 
@@
 problem there.\\}
-\textcolor{red}{Actually the text still needs some work}
 
@@
    field variation if the radius have some mm of uncertainty?\\
-\textcolor{blue}{We did not study this case. }
+\textcolor{blue}{No, we did not study this. Field variation of several \% is
+   possible, but note that our data driven calibration does not depend on
+   the electric field.}
 
@@
    please write it. \\
-\textcolor{blue}{The gain extraction is following this order: \\
-- pass 1: the gain of each pad is defined as the ratio between the mean 
-recorded experimental ADCs to the mean simulated ADCs in the same track. Then 
-for each pad, the gain ratios were collected from all the identified elastic 
-tracks and these gains were fitted by a Landau function to give a
-  first pass gain for each pad as the most probable value of the fit.\\
- - pass2: to make sure that the recorded ADCs by a given pad are similar to the 
- recorded ADCs by other pads in the same track, we refined this calibration. For this, 
- we compared the mean ADCs of each pad to the mean ADCs of the whole track. 
- This ratio is collected from all the elastic events and a gain correction 
- factor is extracted and applied giving a final gain for each pad.
+\textcolor{blue}{ 
+ The ratio is collected from all the elastic events and a gain correction 
+ factor is extracted and applied giving a final gain for each pad. \\
+ The noise reduction process is completely independent of the calibration
+ and is performed before all other steps. We clarified the text in the article. 
   }
@@
    the smear on the top part of the right picture. \\
-\textcolor{red}{The figures layout will be updated.\\}
-
-\textcolor{blue}{The y-axis label on figure 12 is updated. Regarding the lower 
+\textcolor{blue}{The figures layout is updated. The y-axis label on figure 12 
+   is also updated. Regarding the lower 
    peak in the left module of the RTPC, it is likely not deuterons. We added
@@
 analysis is always above 30, with a mean around 135, so this cut has no impact 
-on the good track selection.}
+on the good track selection. We did not study the number of primary ionization, 
+since we are looking at low energy $\alpha$s, we assumed it is very large. }
 
@@
    but what is the rate the RTPC underwent during data taking?\\
-\textcolor{red}{The rate of protons is of MHz in the chamber with a readout of
-about 3kHz, so one could argue that it is both. Our point here is to emphasis
-the high rate however, as these slow protons deposit a lot of energy in the 
-chamber.}
+\textcolor{blue}{The rate of slow protons is of MHz in the chamber with a readout of
+about 3kHz, so one could argue that it is both. However, our point there is to emphasis
+the high rate, as these slow protons deposit a lot of energy in the chamber.}
 

### 2018-01-18 eg6-letters/NIM/review-1/review-1.tex
Update more on NIM review

@@
 \textcolor{blue}{It is not possible to do such studies with the 6 GeV beam, because 
-of the lack of an exclusive process to use as elastic cross sections drops dramatically 
-in our acceptance at such high energy. We would have loved to and tried many alternate
-channels, but none was detectable with reasonnable statistics.}
+of the lack of an exclusive process to use. Elastic cross sections drops dramatically 
+in our acceptance at higher energy and we could not find any suitable replacement. We 
+have tried many alternate channels, but none was detectable with reasonnable statistics
+in the 6~GeV data.}
 

### 2018-01-19 eg6-letters/NIM/EG6_RTPC_NIM.tex
Last (?) edits on the NIM paper

@@
 
-The timing information collected for each signal above threshold
-was used to infer the origin of the ionization electrons and 
-then the trajectory of the detected particle. The recorded ADCs were used to reconstruct 
+The timing information collected from each signal is used 
+to infer the origin of the ionization electrons, from which we
+reconstruct the trajectory of the initial particle. The strength of these 
+signals, recorded in ADC units, is then used to reconstruct 
 the deposited energy per unit of length ($\small{\frac{dE}{dX}}$) which, 
@@
 In this section we will detail the methods used to calibrate the drift time,
-drift paths and gains of the detector. Drift time and paths were initially
+drift paths and gains of the detector. The drift paths were initially
 calculated using the MAGBOLTZ~\cite{Biagi:1999nwa} program, then refined using
-data to account for variations of the run conditions. We assume 
-cylindrical symmetry in the chamber for the calibration of the drift parameters, 
-such that do not depend on the azimuthal angle $\phi$. The initial MAGBOLTZ
+data to account for variations of the run conditions. The initial MAGBOLTZ
 calibration was improved through several iterations of the
 data driven process described below, with each time an increasing number of tracks 
-reconstructed in the RTPC. The figures presented in this section
+reconstructed in the RTPC justifying a new iteration. The figures presented in this section
 are the ones obtained while performing the last iteration of this
-calibration process.
+calibration process. We assume 
+cylindrical symmetry in the chamber for the calibration of the drift parameters, 
+such that do not depend on the azimuthal angle $\phi$.
 
@@
 
-%To be rewritten!!!
-After the ionization, the released electrons drift to the cylindrical detection 
-plane under the effect of the electric field. The electrons released close to 
-the cathode take the most time to reach the readout pads, the cylindrical 
-symmetry indicates that this maximum drift distance is the same for all tracks.  
-We illustrate this in Figure~\ref{fig:RTPC_signals}, where we depict a typical 
-$^{4}$He track. Due to the non-perfect experimental conditions, in particular 
-possible contamination of our gas mixture, the drift speed changed during the 
-three months long experimental run\footnote{We had to increase the gas flow 
-during the experiment due to a small leak in the RTPC, which concurred to 
-the large shift of drift time observed around run number 61600. While our 
-gas system was kept slightly over atmospheric pressure to limit 
-contamination from air or other external gases, it is likely that this leak was 
-the source of modification of the drift speed.}. This can be calibrated by 
-finding drift speed as function of experimental run-number. By measuring a 
-reference time, we can therefore infer the drift speed of the electrons in the 
-RTPC, by: $\textnormal{drift time} = \frac{\textnormal{drift path 
-length}}{\textnormal{drift speed}}$.
+The first step in the calibration is to fix the maximum drift time ($T_{max}$) that an
+electron can arrive on the detection plane. This value is highly dependent on the gas 
+mixture composition, the electric and the magnetic field experienced by the drift 
+electrons. This time correspond to the electrons released close to 
+the cathode, which take the most time to reach the readout pads as illustrated in 
+Figure~\ref{fig:RTPC_signals}. Note that the minimum time is not calibrated, as we
+use the trigger time is defined ($T_{min}=15$), and that the time unit is the ALTRO 
+sampling time of 100~ns.
 
@@
 
-Figure~\ref{fig:TDC_profile} presents the time profile of hits from identified 
-tracks in one z-bin along the detector in one experimental run. We can clearly 
-observe the dropping edge expected from geometrical considerations. In order to 
-avoid the statistical fluctuations on finding the maximum drift time 
-($T_{max}$) from the time profile, we define a more stable value, i.e., 
-$T_{max/2}$, at which the dropping edge passes half the maximum number of hits 
-in the histogram. This value was measured in bins along the 200~mm RTPC's 
+In order to experimentally determine the value of $T_{max}$, we analyse the
+time profile of hits from identified good tracks, as presented in 
+Figure~\ref{fig:TDC_profile}. We can clearly observe the expected dropping 
+edge and define $T_{max}$, as the time at which the distribution passes 
+below half the maximum number of hits in the histogram. This value was 
+measured in bins along the 200~mm RTPC's 
 length to take into account variations in the electric and magnetic field in 
-the RTPC (see Figure~\ref{fig:RunNumber_61551_TDCmax_Zslice}).
+the RTPC. We show this result for one experimental run in 
+Figure~\ref{fig:RunNumber_61551_TDCmax_Zslice}.
 
@@
 \includegraphics[scale=0.42]{hits_time_profile.pdf}
-\caption[]{Time distribution of the hits in one z-bin along the RTPC in one 
-experimental run. Trigger time is defined as T=15, the time unit is the ALTRO 
-sampling time of 100~ns.} \label{fig:TDC_profile}
+\caption{Time distribution of the hits in one z-bin along the RTPC in one 
+experimental run. } \label{fig:TDC_profile}
 \end{figure}
@@
 Figure~\ref{fig:Drift_run_number_1} shows the $T_{max/2}$ values for individual 
-runs (approximately 2 hours long). We observe significant change in the drift 
-speed before and after run 61600, while variations within these periods are 
-around 2\%.
+runs (approximately 2 hours long). We observe significant change of $T_{max}$
+before and after run 61600, while variations within these periods are 
+around 2\%. This is likely due to non-perfect experimental conditions, in 
+particular possible contamination of our gas mixture. We indeed increase the gas flow 
+around that time due to a small leak in the RTPC. While our 
+gas system was kept slightly over atmospheric pressure to limit 
+contamination from air or other external gases, it is likely that this leak was 
+the source of modification of the drift velocity.
 
@@
 
-In summary, we obtain from our calibration a parametrization of the drift speed 
-as a function of both position along the beam axis and the run number.  These 
-functions were extracted for our entire data set and implemented in the track 
-reconstruction code.
+To take this effects into account, we parametrized the maximum drift time 
+as a function of both the position along the beam axis and the run number. These 
+functions were extracted for the entire data set and implemented in the track 
+reconstruction code for the next steps of calibration and track reconstruction.
 
@@
 The drift path is the trajectory followed by the electrons released through 
-ionization in the gas. We calculated them with
-MAGBOLTZ~\cite{Biagi:1999nwa}, but it requires knowledge of the detector's 
-geometry, gas mixture composition, and of course the electric and magnetic 
-fields over the whole volume of the detector. We used this calculation as a 
-first calibration, but, as can be seen with the drift speed, conditions in the 
+ionization in the gas. We initially calculated them with
+MAGBOLTZ~\cite{Biagi:1999nwa}, but this calculation requires knowledge of the detector's 
+geometry, of the gas mixture composition, and of the electric and magnetic 
+fields over the whole volume of the detector. As we seen in the previous section, 
+the conditions in the 
 chamber were changing over time. Moreover, the 4 \textmu{}m foil used as a cathode 
-is easily deformed, such that we expect the geometrical accuracy to be of few 
-millimeters, directly impacting our knowledge of the electric field. These 
+is easily deformed, such that we expect the geometrical accuracy to be only of a few 
+millimeters, also impacting our knowledge of the electric field. These 
 problems, already encountered for the BoNuS RTPC 
@@
 ($e^{4}$He$\rightarrow e^{4}$He). In this process, the measurement of
-the electron kinematics allows to calculate directly the kinematics of the Helium nucleus. 
+the electron kinematics allows to calculate the kinematics of the Helium nucleus. 
 By comparing the calculated momentum and angle of the recoil alpha particle to the 
@@
 we compared the calculated GEANT4 trajectory of the Helium nuclei to 
-the hits measured in the chamber. To perform this drift path extraction, 
+the hits measured in the chamber. To perform the drift path extraction, 
 we made a first approximation assuming a linear dependence between the radius 
 of emission of the charge and its time of detection, and then refined our 
-result. Because of the magnetic field, the drift paths in RTPC are not linear 
-but the curvature is small and the refining  process converged already on the 
+result. Because of the magnetic field, the drift paths in the RTPC are not linear 
+but the curvature is small and the process converged already on the 
 second iteration.
@@
 two data sets and concluded that any changes in the system only significantly 
-affected the drift speed.
+affected the drift speed and thus the measured maximum time.
 
@@
 match the experimental data. We implemented in the GEANT4 simulation the
-drift path we obtained from the calibration described above and implemented an ad 
-hoc diffusion to match the average number of hits recorded in the simulation with
-the one from experimental data. To perform this step properly, we implemented in
+drift path we obtained from the calibration described above and implemented an {\it ad 
+hoc} diffusion function to match the average number of hits recorded in the simulation with
+the one from experimental data. To perform this step properly, we also implemented in
 the simulation the details of the DAQ process to record hits.
@@
 than expected. So, we added a correction factor obtained by comparing  
-the energy deposit on a given pad to its neighbours. To do so, we compared, for 
+the energy deposit on the pads within individual tracks. To do so, we compared, for 
 each track, the energy deposit on a pad to the energy deposit in the whole track. 
 The gain correction factors are extracted by averaging this ratio for a sample 
-of elastic events. Final results are shown in Figure~\ref{fig:dedx_p_exp_2nd}, where energy 
+of elastic events and are thus completely independent from simulation.
+
+The results after calibration are shown in Figure~\ref{fig:dedx_p_exp_2nd}, where energy 
 loss of particles is plotted against momentum over charge ratio. One can 
-clearly see the band for $^4$He in its expected position\footnote{The lower peak 
+clearly see there the band for $^4$He in its expected position\footnote{The lower peak 
    in the left module of the RTPC comes from an unidentified problem in this half 
@@
    the elastic requirements and we found nothing that differenciates them 
-   from other events but their low recorded ADCs. For 
-   the calibration procedures, these events were therefore excluded.}.
+   from other events but their low recorded ADCs. In particular, 94\% of pads
+   are involved with these tracks such that we are sure they do not come from 
+   a miscalibration of a part of the detector. Finally, we decided to discard
+   these events for the calibration procedures.}.
 

### 2018-01-19 eg6-letters/NIM/fig/hits_time_profile.C
update the source file for hit profile plot

@@ -421,7 +421,7 @@ void hits_time_profile()
             l2->SetTextColor(kBlue); 
             //l2->Draw("same");
 
-    TLatex *l3= new TLatex(65.0,-500.0,"T_{max/2}");
+    TLatex *l3= new TLatex(65.0,-500.0,"T_{max}");
             l3->SetTextSize(0.07);
             l3->SetTextColor(kBlue); 
             l3->Draw("same");

### 2018-01-19 eg6-letters/NIM/fig/RunNumber_61452.00_TDCmax_Zslice.C
update figures 6, 7 and 8 and adding the source files in the directory "fig"

@@ -91,10 +91,10 @@
    Graph_Graph5->GetXaxis()->SetLabelSize(0.055);
    Graph_Graph5->GetXaxis()->SetTitleSize(0.07);
    Graph_Graph5->GetXaxis()->CenterTitle(true);
-   Graph_Graph5->GetYaxis()->SetTitle("T_{max/2}");
+   Graph_Graph5->GetYaxis()->SetTitle("T_{max}");
    Graph_Graph5->GetYaxis()->SetLabelSize(0.055);
    Graph_Graph5->GetYaxis()->SetTitleSize(0.07);
-   Graph_Graph5->GetYaxis()->SetTitleOffset(0.9);
+   Graph_Graph5->GetYaxis()->SetTitleOffset(1.0);
    Graph_Graph5->GetYaxis()->CenterTitle(true);
    gre->SetHistogram(Graph_Graph5);
  

### 2018-01-19 eg6-letters/NIM/EG6_RTPC_NIM.tex
update figures 6, 7 and 8 and adding the source files in the directory "fig"
editing typos, changing the layout of the figures to fit and be ordered with their numbers

--- 2018-01-18 eg6-letters/NIM/EG6_RTPC_NIM.tex
@@
 Time projection chamber, gas electron multipliers, alpha particles, DVCS, 
-Nuclear physics
+Nuclear physics.
 \end{keywords}
@@
 15$^{\circ}$~\cite{Hyon-suk}. To protect the CLAS detector and the IC from the 
-large flux of low energy M{\o}ller electrons, a 5~T solenoid magnet was placed 
-around the target to shield the detectors.  To detect recoiling $\alpha$ 
+large flux of the low energy M{\o}ller electrons, a 5~T solenoid magnet was 
+placed around the target to shield the detectors.  To detect recoiling $\alpha$ 
 particles from the coherent DVCS on Helium, a new radial time projection 
@@
 RTPC was designed to be as close as possible to the target and fit inside the 
-230~mm diameter shell and cryostat wall of the solenoid magnet bore of the 
-CLAS.
+230~mm diameter shell and cryostat wall of the solenoid magnet bore of CLAS.
 
@@
 was to obtain a better support structure for the GEM foils. In the previous version,
-the RTPC was essencially composed of two independent half-cylinder separated
-by their own structures. In this design, the installation of the GEMs was not very practical
-and wrinkles were visibles on the GEM surfaces. To allow for a better installation 
-and, at the same time, keep the mechanical structure out of the drift volume, 
-the present design is based on self supporting GEM cylinder. We 
-realized these cylinders by using fiber glass rings glued to 
-each ends of the GEM foils in order to 
-instal them independently in the RTPC after gluing and soldering operations. The 
-rigidity of the GEM foils was enough for the structure to be self-supporting 
-and only the upstream end of the cylinder was fixed to the main mechanical 
-support structure. This design only left a light fiberglass ring in the 
-downstream end, reducing to a minimum secondary interactions.
+the RTPC was essentially composed of two independent half-cylinder separated
+by their own structures. In this design, the installation of the GEMs was not 
+very practical and wrinkles were visible on the GEM surfaces. To allow for a 
+better installation and, at the same time, keep the mechanical structure out of 
+the drift volume, the present design is based on self supporting GEM cylinder.  
+We realized these cylinders by using fiber glass rings glued to each end of the 
+GEM foils in order to install them independently in the RTPC after gluing and 
+soldering operations. The rigidity of the GEM foils was enough for the 
+structure to be self-supporting and only the upstream end of the cylinder was 
+fixed to the main mechanical support structure. This design only left a light 
+fiberglass ring in the downstream end, reducing to a minimum secondary 
+interactions.
 
@@
 signifantly higher readout-rate compared to the original BoNuS system. During 
-the 2009 run, the system was successfully 
-operated with a DAQ rate of 3.1 kHz and a live time of 70~\%, for a 
-luminosity of about $10^{34}$~cm$^{-2}\cdot$s$^{-1}$ and a beam energy of 
-6.064~GeV, to be compared with the 500 Hz obtained with the first BoNuS detector at similar run conditions.
+the 2009 run, the system was successfully operated with a DAQ rate of 3.1 kHz 
+and a live time of 70~\%, for a luminosity of about 
+$10^{34}$~cm$^{-2}\cdot$s$^{-1}$ and a beam energy of 6.064~GeV, to be compared 
+with the 500 Hz obtained with the first BoNuS detector at similar run 
+conditions.
 
@@
 
-%To be rewritten!!!
 After the ionization, the released electrons drift to the cylindrical detection 
@@
    gas system was kept slightly over atmospheric pressure to limit 
-contamination from air or other external gases, it is likely that this leak was 
-the source of modification of the drift speed.}. This can be calibrated by 
-finding drift speed as function of experimental run-number. By measuring a 
-reference time, we can therefore infer the drift speed of the electrons in the 
-RTPC, by: $\textnormal{drift time} = \frac{\textnormal{drift path 
+   contamination from air or other external gases, it is likely that this leak 
+   was the source of modification of the drift speed.}. This can be calibrated 
+   by finding drift speed as function of experimental run-number. By measuring 
+   a reference time, we can therefore infer the drift speed of the electrons in 
+   the RTPC, by: $\textnormal{drift time} = \frac{\textnormal{drift path 
    length}}{\textnormal{drift speed}}$.
@@
 \caption[]{A schematic drawing of a $^{4}$He track (in green) traversing the 
-drift region, with the drift paths followed by the electrons (in black). } 
+drift region, with the drift paths followed by the electrons (in blue). } 
 \label{fig:RTPC_signals}
@@
 avoid the statistical fluctuations on finding the maximum drift time 
-($T_{max}$) from the time profile, we define a more stable value, i.e., 
-$T_{max/2}$, at which the dropping edge passes half the maximum number of hits 
-in the histogram. This value was measured in bins along the 200~mm RTPC's 
-length to take into account variations in the electric and magnetic field in 
-the RTPC (see Figure~\ref{fig:RunNumber_61551_TDCmax_Zslice}).
+($T_{max}$) from the time profile, we define it in a more stable value, i.e., 
+at which the dropping edge passes half the maximum number of hits in the 
+histogram. This value was measured in bins along the 200~mm RTPC's length to 
+take into account variations in the electric and magnetic field in the RTPC 
+(see Figure~\ref{fig:RunNumber_61551_TDCmax_Zslice}).
 
-\begin{figure}[tb]
+\begin{figure}[t]
 \centering
@@
 
-\begin{figure}[tb]
+\begin{figure}[t]
 \centering
@@
 
-Figure~\ref{fig:Drift_run_number_1} shows the $T_{max/2}$ values for individual 
+Figure~\ref{fig:Drift_run_number_1} shows the $T_{max}$ values for individual 
 runs (approximately 2 hours long). We observe significant change in the drift 
@@
 
-\begin{figure*}[tb]
+\begin{figure*}[t!]
 \centering
-\includegraphics[width=15.5cm]{Drift_run_number.pdf}
-\caption{$T_{max/2}$ versus the experimental run numbers.} 
+\includegraphics[width=17.5cm]{Drift_run_number.pdf}
+\caption{$T_{max}$ versus the experimental run numbers.} 
 \label{fig:Drift_run_number_1}
@@
 
-\begin{figure}[tb]
+To verify the stability of the drift paths, this procedure was carried out 
+using both the 1.204 GeV data from the beginning of the run period and the 
+1.269 GeV data from the end of the run period (shown in blue on 
+Figure~\ref{fig:Drift_run_number_1}). We found very similar drift paths for the 
+two data sets and concluded that any changes in the system only significantly 
+affected the drift speed.
+
+\begin{figure}[t]
 \centering
@@
 \end{figure}
-
-To verify the stability of the drift paths, this procedure was carried out 
-using both the 1.204 GeV data from the beginning of the run period and the 
-1.269 GeV data from the end of the run period (shown in blue on 
-Figure~\ref{fig:Drift_run_number_1}). We found very similar drift paths for the 
-two data sets and concluded that any changes in the system only significantly 
-affected the drift speed.
 
@@
 The gain correction factors are extracted by averaging this ratio for a sample 
-of elastic events. Final results are shown in Figure~\ref{fig:dedx_p_exp_2nd}, where energy 
-loss of particles is plotted against momentum over charge ratio. One can 
-clearly see the band for $^4$He in its expected position\footnote{The lower peak 
-   in the left module of the RTPC comes from an unidentified problem in this half 
-   of the detector that concerns 7\% of all the elastic events. 
+of elastic events. Final results are shown in Figure~\ref{fig:dedx_p_exp_2nd}, 
+where energy loss of particles is plotted against momentum over charge ratio. 
+One can clearly see the band for $^4$He in its expected position\footnote{The 
+   lower peak in the left module of the RTPC comes from an unidentified problem 
+   in this half of the detector that concerns 7\% of all the elastic events.  
    Our best guess is that these events are linked with a high voltage supply 
    issue, that would sometimes bring the GEM gain down. These events pass all 
-   the elastic requirements and we found nothing that differenciates them 
-   from other events but their low recorded ADCs. For 
-   the calibration procedures, these events were therefore excluded.}.
+the elastic requirements and we found nothing that differentiates them from 
+other events but their low recorded ADCs. For the calibration procedures, these 
+events were therefore excluded.}.
 
@@
 channel. Its amplitude is similar to those of real tracks. About 18\% of the 
-readout channels exhibit large contributions from this noise.  
-Due to its unique time-energy correlation, we use a patern
-recognition algorithm and discard the hits coming from the channels that display 
-this behavior on an event by event basis. The result of the
-procedure is illustrated in the bottom panel of Figure~\ref{fig:noise}.
+readout channels exhibit large contributions from this noise.  Due to its 
+unique time-energy correlation, we use a pattern recognition algorithm and 
+discard the hits coming from the channels that display this behavior on an 
+event by event basis. The result of the procedure is illustrated in the bottom 
+panel of Figure~\ref{fig:noise}.
 
@@
 board were recorded. An event-based technique to identify and remove this noise 
-was developed based 
-on counting simultaneous hits in each pre-amplifier group, and, if sufficiently large, 
-perform a dynamic pedestal subtraction based on the average ADC of neighboring 
-channels within this group.
+was developed based on counting simultaneous hits in each pre-amplifier group, 
+and, if sufficiently large, perform a dynamic pedestal subtraction based on the 
+average ADC of neighboring channels within this group.
 
 The sources of these effects were not determined, but rejection techniques 
-allowed to reconstruct 10\% more good tracks and 
-recover 70 channels that were previously ignored due to excessive noise levels.
+allowed to reconstruct 10\% more good tracks and recover 70 channels that were 
+previously ignored due to excessive noise levels.
 
@@
 
-The tracking starts with reconstructing the spacial origin of the hits using the extracted drift speed and drift path 
-parameters. For each registered hit, we calculate a position of emission from 
-the signal time and the pad position. The third step 
-is to create chains of hits. The maximum distance between two close adjacent 
-hits has to be less than 10.5 mm to chain them, which roughly corresponds to 
-neighbors and next to neighbors. We fit the chains with a helix if they have a minimum of 
-10 hits. We then eliminate from the chain the hits that are 5 mm or farther from the fit,
-as they are not likely part of the same track.
-This new reduced chain is used for a second and final helix fit.
+The tracking starts with reconstructing the spacial origin of the hits using 
+the extracted drift speed and drift path parameters. For each registered hit, 
+we calculate a position of emission from the signal time and the pad position.  
+The third step is to create chains of hits. The maximum distance between two 
+close adjacent hits has to be less than 10.5 mm to chain them, which roughly 
+corresponds to neighbors and next to neighbors. We fit the chains with a helix 
+if they have a minimum of 10 hits. We then eliminate from the chain the hits 
+that are 5 mm or farther from the fit, as they are not likely part of the same 
+track. This new reduced chain is used for a second and final helix fit.
 
@@
 on GEANT4 simulations with the full RTPC geometry and parameterized in terms of 
-recoil curvature in the drift region and polar angle, separetely for all recoil 
+recoil curvature in the drift region and polar angle, separately for all recoil 
 hypotheses ($p$, $d$, $^3$H, $^3$He, $^4$He).  At our average coherent $^4$He 

### 2018-01-22 eg6-letters/NIM/EG6_RTPC_NIM.tex

--- 2018-01-19 eg6-letters/NIM/EG6_RTPC_NIM.tex
@@
 
-For certain experiments the base CLAS system was complimented with ancillary 
+For certain experiments the base CLAS system was complemented with ancillary 
 detectors. For example, the measurement of the Deeply Virtual Compton 
@@
 solenoid field was used to bend tracks and measure momentum of particles in the 
-RTPC. The CLAS detector supplemented with both IC and RTPC was used during a 
+RTPC. The CLAS detector supplemented with both IC and RTPC was used in 2009 during a 
 three months experimental run~\cite{proposal1,proposal2}
-in 2009 with a longitudinally polarized electron beam of 130~nA 
-and energy of 6.064 GeV incident on a gaseous $^{4}$He target.
+with a longitudinally polarized, 130~nA and 6.064 GeV electron beam
+incident on a gaseous $^{4}$He target.
 
@@
 used in the 2009 DVCS experiment, is described in section \ref{sec_design} of 
-this paper. The data acquisition system is described in section \ref{sec_readout}, 
+this article. The data acquisition system is described in section \ref{sec_readout}, 
 the calibration methods in section \ref{sec_calib} and the tracking algorithm in section
@@
       The average electric field in this region is perpendicular to the beam 
-      and about 550~V/cm.
+      and average around 550~V/cm.
    \item The electron amplification system is composed of three GEMs located at 
@@
 was to obtain a better support structure for the GEM foils. In the previous version,
-the RTPC was essencially composed of two independent half-cylinder separated
-by their own structures. In this design, the installation of the GEMs was not very practical
-and wrinkles were visibles on the GEM surfaces. To allow for a better installation 
-and, at the same time, keep the mechanical structure out of the drift volume, 
-the present design is based on self supporting GEM cylinder. We 
-realized these cylinders by using fiber glass rings glued to 
-each ends of the GEM foils in order to 
-instal them independently in the RTPC after gluing and soldering operations. The 
-rigidity of the GEM foils was enough for the structure to be self-supporting 
-and only the upstream end of the cylinder was fixed to the main mechanical 
-support structure. This design only left a light fiberglass ring in the 
-downstream end, reducing to a minimum secondary interactions.
+the RTPC was essentially composed of two independent half-cylinder separated
+by their own structures. In this design, the installation of the GEMs was not 
+very practical and wrinkles were visible on the GEM surfaces. To allow for a 
+better installation and, at the same time, keep the mechanical structure out of 
+the drift volume, the present design is based on self supporting GEM cylinder.  
+We realized these cylinders by using fiber glass rings glued to each end of the 
+GEM foils in order to install them independently in the RTPC after gluing and 
+soldering operations. The rigidity of the GEM foils was enough for the 
+structure to be self-supporting and only the upstream end of the cylinder was 
+fixed to the mechanical support structure. This design only left a light 
+fiberglass ring in the downstream end, reducing to a minimum secondary 
+interactions.
 
@@
 input signals. For each event, 100 samples/channel were digitized by the ALTRO 
-ASIC~\cite{EsteveBosch:2003bj}, operated at 10 MHz sampling frequency. In order 
+ASIC~\cite{EsteveBosch:2003bj}, operated at 10~MHz sampling frequency. In order 
 to reduce the data size, the system was operated in zero-suppression mode, 
@@
 electron can arrive on the detection plane. This value is highly dependent on the gas 
-mixture composition, the electric and the magnetic field experienced by the drift 
-electrons. This time correspond to the electrons released close to 
-the cathode, which take the most time to reach the readout pads as illustrated in 
+mixture composition, as well as the electric and magnetic field experienced by the drift 
+electrons. The maximum time corresponds to electrons released close to 
+the cathode, which are the furthest from the readout pads as illustrated in 
 Figure~\ref{fig:RTPC_signals}. Note that the minimum time is not calibrated, as we
-use the trigger time is defined ($T_{min}=15$), and that the time unit is the ALTRO 
+use the trigger time for it ($T_{min}=15$), and that the time unit is the ALTRO 
 sampling time of 100~ns.
@@
 below half the maximum number of hits in the histogram. This value was 
-measured in bins along the 200~mm RTPC's 
-length to take into account variations in the electric and magnetic field in 
-the RTPC. We show this result for one experimental run in 
-Figure~\ref{fig:RunNumber_61551_TDCmax_Zslice}.
+measured in bins along the 200~mm RTPC's length to take into account 
+variations in the electric and magnetic field. We show this result for one 
+experimental run in Figure~\ref{fig:RunNumber_61551_TDCmax_Zslice}.
 
-\begin{figure}[tb]
+\begin{figure}[t]
 \centering
@@
 
-Figure~\ref{fig:Drift_run_number_1} shows the $T_{max/2}$ values for individual 
+Figure~\ref{fig:Drift_run_number_1} shows the $T_{max}$ values for individual 
 runs (approximately 2 hours long). We observe significant change of $T_{max}$
@@
 of emission of the charge and its time of detection, and then refined our 
-result. Because of the magnetic field, the drift paths in the RTPC are not linear 
-but the curvature is small and the process converged already on the 
-second iteration.
+result accounting for the curvature of the drift path. The curvature was small 
+enough, such that the process converged already on the second iteration.
 
@@
 
-\begin{figure}[tb]
+To verify the stability of the drift paths, this procedure was carried out 
+using both the 1.204 GeV data from the beginning of the run period and the 
+1.269 GeV data from the end of the run period (shown in blue on 
+Figure~\ref{fig:Drift_run_number_1}). We found very similar drift paths for the 
+two data sets and concluded that any changes in the system only significantly 
+affected the drift speed.
+
+\begin{figure}[t]
 \centering
-\includegraphics[scale=0.46]{FitResult_p2_11.pdf}
+\includegraphics[scale=0.48]{FitResult_p2_11.pdf}
 \caption{$\Delta \phi$ versus T distribution for tracks
 from one bin in longitudinal position along the RTPC. The black line represents 
-the final drift paths in this bin.}
+our firt of the drift path in this bin.}
 \label{fig:DELTA_PHI_TDC}

### 2018-01-29 eg6-letters/NIM/EG6_RTPC_NIM.tex
implenemet the comments from stepan

@@
       extends from the cathode to the first GEM, 60~mm away from the beam axis.  
-      The average electric field in this region is perpendicular to the beam 
-      and average around 550~V/cm.
+      The electric field in this region is perpendicular to the beam and 
+      average around 550~V/cm.
    \item The electron amplification system is composed of three GEMs located at 
@@
 
-The drift gas used in the experiment is a 80-20\% Ne-DME mixture. This choice 
+The drift gas used in the experiment is a 80\%-20\% Ne-DME mixture. This choice 
 has been made in order to balance the energy deposit, which is critical
@@
 polarity -- from negative to positive -- to match the requirements of the 
-subsequent readout system, and driving the 6~m long ribbon cable that connects 
-to it.
+subsequent readout system, and driving signals through the 6~m long ribbon 
+cable that connects to the readout system.
 
-The readout system was an upgraded version of the original BoNuS RTPC system~\cite{Fenker:2008zz}, 
-based ALICE-TPC front end electronic boards (FECs)~\cite{ALICE-FEE}. 
-Each FEC hosted 128 channels, providing amplification and digitization of the 
-input signals. For each event, 100 samples/channel were digitized by the ALTRO 
-ASIC~\cite{EsteveBosch:2003bj}, operated at 10~MHz sampling frequency. In order 
-to reduce the data size, the system was operated in zero-suppression mode, 
-keeping data from $N_{PRE}=3$ samples before threshold crossing on the rising 
-edge to $N_{POST}=3$ samples after threshold crossing on the falling edge. 
-The threshold level was set on each channel just above the noise level.
+The readout system was an upgraded version of the original BoNuS RTPC 
+system~\cite{Fenker:2008zz}, based on ALICE-TPC front end electronic boards 
+(FECs)~\cite{ALICE-FEE}.  Each FEC hosted 128 channels, providing amplification 
+and digitization of the input signals. For each event, 100 samples/channel were 
+digitized by the ALTRO ASIC~\cite{EsteveBosch:2003bj}, operated at 10~MHz 
+sampling frequency. In order to reduce the data size, the system was operated 
+in zero-suppression mode, keeping data from $N_{PRE}=3$ samples before 
+threshold crossing on the rising edge to $N_{POST}=3$ samples after threshold 
+crossing on the falling edge.  The threshold level was set on each channel just 
+above the noise level.
 
@@
 
-To verify the stability of the drift paths, this procedure was carried out 
-using both the 1.204 GeV data from the beginning of the run period and the 
-1.269 GeV data from the end of the run period (shown in blue on 
-Figure~\ref{fig:Drift_run_number_1}). We found very similar drift paths for the 
-two data sets and concluded that any changes in the system only significantly 
-affected the drift speed.
-
 \begin{figure}[t]
@@
 from one bin in longitudinal position along the RTPC. The black line represents 
-our firt of the drift path in this bin.}
+our fit of the drift path in this bin.}
 \label{fig:DELTA_PHI_TDC}
@@
 the extracted drift speed and drift path parameters. For each registered hit, 
-we calculate a position of emission from the signal time and the pad position.  
-The third step is to create chains of hits. The maximum distance between two 
+we calculate the position of emission from the signal time and the pad 
+position. Then, chains of hits are created. The maximum distance between two 
 close adjacent hits has to be less than 10.5 mm to chain them, which roughly 
@@
   \includegraphics[width=8cm]{fit_W_distribution_l.png}
-  \caption{The recoil mass $W$ distribution calculated from electron kinematics 
-  before (``inclusive'') and after (``exclusive'') requiring a matching track 
-  in the RTPC.\label{fig:w}}
+  \caption{The recoil mass, $W$, distribution calculated from electron 
+  kinematics before (``inclusive'') and after (``exclusive'') requiring a 
+  matching track in the RTPC.\label{fig:w}}
 \end{figure}

### 2018-01-29 eg6-letters/NIM/EG6_RTPC_NIM.tex
correct some typos

@@
       The electric field in this region is perpendicular to the beam and 
-      average around 550~V/cm.
+      averages around 550~V/cm.
    \item The electron amplification system is composed of three GEMs located at 
@@
 readout mode making use of the FECs multi-event buffer, allowed to reach a 
-signifantly higher readout-rate compared to the original BoNuS system. During 
+significantly higher readout-rate compared to the original BoNuS system. During 
 the 2009 run, the system was successfully operated with a DAQ rate of 3.1 kHz 
@@
    issue, that would sometimes bring the GEM gain down. These events pass all 
-   the elastic requirements and we found nothing that differenciates them 
-   from other events but their low recorded ADCs. In particular, 94\% of pads
+   the elastic requirements and we found nothing that differentiates them from 
+   other events but their low recorded ADCs. In particular, 94\% of pads
    are involved with these tracks such that we are sure they do not come from 

### 2018-01-29 eg6-letters/NIM/EG6_RTPC_NIM.tex
update line 112 from stepan

@@
    \item The electron amplification system is composed of three GEMs located at 
-      radii of 60, 63 and 66~mm. In this configuration, the first GEM layer 
-      serves as the anode and each subsequent GEM is set at a lower voltage to
-      obtain a strong ($\sim$1600~V/cm) electric field between the GEM foils. A 
-      275~V bias is applied across each GEM for amplification.
+      radii of 60, 63 and 66~mm. In this configuration, the first GEM layer is 
+      set to $\Delta V=1650$~V relative to the cathode foil and each subsequent 
+      layer is set to a lower voltage relative to the previous to obtain a 
+      strong (~1600~V/cm) electric field between the GEM foils. A 275~V bias is 
+      applied across each GEM for amplification.
    \item The readout board has an internal radius of 69~mm and collects charges 

### 2018-01-30 eg6-letters/NIM/EG6_RTPC_NIM.tex
Minor fixes on NIM for resubmission

--- 2018-01-29 eg6-letters/NIM/EG6_RTPC_NIM.tex
@@
 reduced the amount of material in the path of the outgoing particles. 
-Moreover, the data aquisition electronic was improved to increase the event 
+Moreover, the data acquisition electronic was improved to increase the event 
 readout rate. The enhanced design, 
@@
    \item The electron amplification system is composed of three GEMs located at 
-      radii of 60, 63 and 66~mm. In this configuration, the first GEM layer 
-      serves as the anode and each subsequent GEM is set at a lower voltage to
-      obtain a strong ($\sim$1600~V/cm) electric field between the GEM foils. A 
-      275~V bias is applied across each GEM for amplification.
+      radii of 60, 63 and 66~mm. The first GEM layer is 
+      set to $\Delta V=1620$~V relative to the cathode foil and then each subsequent 
+      layer is set to a lower voltage relative to the previous to obtain a 
+      strong (~1600~V/cm) electric field between the GEM foils. A 275~V bias is 
+      applied across each GEM for amplification.
    \item The readout board has an internal radius of 69~mm and collects charges 
@@
 
-In order to experimentally determine the value of $T_{max}$, we analyse the
+In order to experimentally determine the value of $T_{max}$, we analyze the
 time profile of hits from identified good tracks, as presented in 
@@
 the foils before reaching the drift region.  Corrections were developed based 
-on GEANT4 simulations with the full RTPC geometry and parameterized in terms of 
+on GEANT4 simulations with the full RTPC geometry and parametrized in terms of 
 recoil curvature in the drift region and polar angle, separately for all recoil 

### 2018-01-30 eg6-letters/NIM/EG6_RTPC_NIM.tex
Correct typo in NIM paper

@@
       layer is set to a lower voltage relative to the previous to obtain a 
-      strong (~1600~V/cm) electric field between the GEM foils. A 275~V bias is 
+      strong ($\sim$1600~V/cm) electric field between the GEM foils. A 275~V bias is 
       applied across each GEM for amplification.

### 2018-01-30 eg6-letters/NIM/review-1/review-1.tex
Changes for submission of NIM on Arxiv and NIM

@@
    when speaking the first time about GEM in the text.\\
-\textcolor{blue}{cylindrical GEMs-> semi-cylindrical. The reference has been added.}
+{ \bf cylindrical GEMs-> semi-cylindrical. The reference has been added.}
 
@@
    maybe in a table, to make them evident.\\
-\textcolor{blue}{The main difference is in the design of the structure and in the
+{ \bf The main difference is in the design of the structure and in the
 firmware of the electronics, this has been made clearer.}
@@
    GEM.\\
-\textcolor{blue}{ The text has been modified to clarify the z position of the 
+{ \bf  The text has been modified to clarify the z position of the 
 target and the RTPC with respect to CLAS sectrometer.\\
@@
    Bachmann et al.\\
-\textcolor{blue}{Thanks. It has been replaced.}
+{ \bf Thanks. It has been replaced.}
 
@@
    very high fields.\\
-\textcolor{blue}{Sorry typo. It is 50 $\mu$m}
+{ \bf Sorry typo. It is 50 $\mu$m}
 
@@
    acquisition rate was increased (footnote 2).\\
-\textcolor{blue}{This section has been completely reworked.}
+{ \bf This section has been completely reworked.}
 
@@
 - why L1 and L2 (trigger levels?) \\
-\textcolor{blue}{Based on previous comment, we shortened the discussion and 
+{ \bf Based on previous comment, we shortened the discussion and 
 droped this figure. }
@@
    "speed"\\
-\textcolor{blue}{What is calibrated here is mainly the drift time, based 
+{ \bf What is calibrated here is mainly the drift time, based 
 on your next question as well, we clarified the text about these.}
@@
 the simulations?\\
-\textcolor{blue}{The text has been updated to simplify and clarify the procedure 
+{ \bf The text has been updated to simplify and clarify the procedure 
 (in particular, some of the variable were not necessary). What we are doing is pretty 
@@
    extremities?\\
-   \textcolor{blue}{The figure is updated.}
+   { \bf The figure is updated.}
 
@@
    first reading\\
-\textcolor{blue}{The text is cleared.}
+{ \bf The text is cleared.}
 
@@
    field variation if the radius have some mm of uncertainty?\\
-\textcolor{blue}{No, we did not study this. Field variation of several \% is
+{ \bf No, we did not study this. Field variation of several \% is
    possible, but note that our data driven calibration does not depend on
@@
    to simulate the electronics?\\
-\textcolor{blue}{The section has been extended to provide more details. We 
+{ \bf The section has been extended to provide more details. We 
 implemented specific codes in our GEANT4 simulation to have a realistic 
@@
    good tracks been used for calibration? Lack of statistics?\\
-\textcolor{blue}{We improved the gains by using a method based only on data,
+{ \bf We improved the gains by using a method based only on data,
 the text has been clarified on the topic. All these calibration procedures
@@
    please write it. \\
-\textcolor{blue}{ 
+{ \bf  
  The ratio is collected from all the elastic events and a gain correction 
@@
    questions, but I could not understand the figure.\\
-   \textcolor{blue}{This figure only displays one track. Pads are single channels, 
+   { \bf This figure only displays one track. Pads are single channels, 
 the bins correspond to time (100 ns per bin). The dE is calculated overall in general,
@@
    the smear on the top part of the right picture. \\
-\textcolor{blue}{The figures layout is updated. The y-axis label on figure 12 
+{ \bf The figures layout is updated. The y-axis label on figure 12 
    is also updated. Regarding the lower 
@@
    is passed then a noise level is subtracted? If so, how is it calculated?\\
-\textcolor{blue}{The oscillatory noise was removed just by rejecting all hits 
+{ \bf The oscillatory noise was removed just by rejecting all hits 
 from a channel if too many of these hits fall on the noise curve in a given 
@@
 \item How was "10.5 mm" cut chosen? is it in xy plane or in 3-dimensions?\\
-\textcolor{blue}{The distance between hits are calculated in 3D. This cut has 
+{ \bf The distance between hits are calculated in 3D. This cut has 
 been chosen because it enables to jump a one pad gap in case of a dead 
@@
    ionization in this gas mixture?\\
-   \textcolor{blue}{This cut is set to avoid tracks made out of random noise and
+   { \bf This cut is set to avoid tracks made out of random noise and
 to limit computing time. The number of hits in good tracks at the end of the 
@@
    times. Sum $dE_{i}$/Sum $dx_{i}$ is not equal to Sum ($dE_{i}/dx_{i}$).\\
-\textcolor{blue}{We compute dEdx with path-length and ADC- 
+{ \bf We compute dEdx with path-length and ADC- 
 truncations, and a linear fit to ADC vs path-length to get slope and fit 
@@
    to compute the mean efficiency? If I misunderstood, please comment.\\
-\textcolor{blue}{This study has been performed by a student a long time
+{ \bf This study has been performed by a student a long time
 ago and we do not have all the individual fits anymore.}
@@
    but what is the rate the RTPC underwent during data taking?\\
-\textcolor{blue}{The rate of slow protons is of MHz in the chamber with a readout of
+{ \bf The rate of slow protons is of MHz in the chamber with a readout of
 about 3kHz, so one could argue that it is both. However, our point there is to emphasis
@@
    performances in that case?\\
-\textcolor{blue}{It is not possible to do such studies with the 6 GeV beam, because 
+{ \bf It is not possible to do such studies with the 6 GeV beam, because 
 of the lack of an exclusive process to use. Elastic cross sections drops dramatically 
@@
    pattern gas detectors (it depends on what is available).\\
-\textcolor{blue}{Updated}
+{ \bf Updated}
 
@@
    the text.\\
-\textcolor{blue}{ }
+{ \bf  }
 
@@
    there are more in the text).\\
-\textcolor{blue}{Updated everywhere}
+{ \bf Updated everywhere}
 
@@
    BoNus. Please uniform this to the correct one, which I think is BoNuS.\\
-\textcolor{blue}{Updated to BoNuS everywhere}
+{ \bf Updated to BoNuS everywhere}
 
@@
    with the same layout.\\
-\textcolor{blue}{Updated}
+{ \bf Updated}
 
@@
 \item line 17: "GeV" --> "GeV/c"\\
-\textcolor{blue}{Corrected}
+{ \bf Corrected}
 
 \item line 26: "nuclei" --> "nucleus"\\
-\textcolor{blue}{Corrected}
+{ \bf Corrected}
 
@@
    bends the track and then the detector tracks them)\\
-\textcolor{blue}{Added}
+{ \bf Added}
 
 \item line 91: "second gap" --> "second gas gap"\\
-\textcolor{blue}{Added}
+{ \bf Added}
 
@@
    the amplification system.\\
-\textcolor{blue}{Added}
+{ \bf Added}
 
 \item line 131: "axial magnetic field" --> "solenoidal magnetic field"\\
-\textcolor{blue}{Replaced}
+{ \bf Replaced}
 
 \item line 133: "challenge" --> "challenges"\\
-\textcolor{blue}{Added}
+{ \bf Added}
 
@@
    it in the whole text (like, "RTPC")\\
-\textcolor{blue}{Uniformed}
+{ \bf Uniformed}
 
 \item line 167: "stage" --> "stages"\\
-\textcolor{blue}{Corrected}
+{ \bf Corrected}
 
@@
    articles\\
-\textcolor{blue}{Uniformed}
+{ \bf Uniformed}
 
@@
    not in the center vertically)\\
-\textcolor{blue}{Corrected}
+{ \bf Corrected}
 
 \item line 208 again: "6.067" before it said "6.064", please fix the wrong one
-\textcolor{blue}{Corrected. It is 6.064} \\
+{ \bf Corrected. It is 6.064} \\
 
 \item line 263: "2\%" --> I would put "around 2\%"\\
-\textcolor{blue}{Added}
+{ \bf Added}
 
 \item line 268: "reconstructions" --> "reconstruction"\\
-\textcolor{blue}{Corrected }
+{ \bf Corrected }
 
 \item line 269: "Paths" --> "Path"\\
-\textcolor{blue}{Corrected}
+{ \bf Corrected}
 
 \item line 308: "codes" --> "code"\\
-\textcolor{blue}{Corrected}
+{ \bf Corrected}
 
 \item line 405: "electron's" --> "electron"\\
-\textcolor{blue}{Corrected}
+{ \bf Corrected}
 
@@
    distribution"\\
-\textcolor{blue}{Added}
+{ \bf Added}
 
@@
    percentage\\
-\textcolor{blue}{Yes it is. Corrected }
+{ \bf Yes it is. Corrected }
 
 \item line 432: "Helium-4" --> "4He" (for uniformity, as was written before)\\
-\textcolor{blue}{Changed to $^4$He}
+{ \bf Changed to $^4$He}
 
 \item line 488: There is an extra "," at the beginning of the item\\
-\textcolor{blue}{Cleaned}\\
+{ \bf Cleaned}\\
 ~\\
@@
 
-\textcolor{blue}{We would like to thank the reviewer for the detailed remark that
+{ \bf We would like to thank the reviewer for the detailed remark that
 helped improving the manuscript significantly.}

### 2018-02-02 eg6-letters/incoherent/incoherent_prl.tex
update the incoherent plots
added the updated figure 2 and 3 in the incoherent channel with the source files
start writing the incoherent prl

@@
 
-\title{Incoherent Deep Virtual Compton Scattering off $^4$He using CLAS 
-spectrometer}
+\title{Revealing the Bound Nucleon 3D Partonic Structure through Incoherent 
+Deeply Virtual Compton Scattering off $^4$He}
 
-\newcommand*{\ANL}{Argonne National Laboratory, Argonne, Illinois 60439}
-\newcommand*{\ANLindex}{1}
-\affiliation{\ANL}
-\newcommand*{\ORSAY}{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}
-\newcommand*{\ORSAYindex}{2}
-\affiliation{\ORSAY}
-\newcommand*{\JLAB}{Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606}
-\newcommand*{\JLABindex}{3}
-\affiliation{\JLAB}
-
-\newcommand*{\NOWJLAB}{Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606}
-\newcommand*{\NOWODU}{Old Dominion University, Norfolk, Virginia 23529}
- %%%%%%%%%%%%%%% END OF Latex Macros for institute addresses  %%%%%%%%%%%%%%%%%%%%%%%%%
-
-\author {M.~Hattawy}
-\affiliation{\ANL}
-\affiliation{\ORSAY}
-\author {R.~Dupr\'{e}} 
-\affiliation{\ANL}
-\affiliation{\ORSAY}
-\author {N.A.~Baltzell} 
-\affiliation{\ANL}
-\affiliation{\JLAB}
-\author {K.~Hafidi} 
-\email[corresponding author: ]{kawtar@anl.gov}
-\affiliation{\ANL}
-
-\collaboration{The CLAS Collaboration}
-\noaffiliation
+\input author_list.tex
 
@@
 \begin{abstract}
-We report the incoherent beam-spin asymmetry measurement of deeply virtual 
-Compton scattering (DVCS) off $^4$He. The experiment used the 6 GeV electron 
-beam from Jefferson Lab projected onto a $^4$He target in the center of the 
-CEBAF Large Acceptance Spectrometer (CLAS).
+The three-dimensional imaging of the nucleon's fundamental partons, i.e, quarks 
+and gluons, is set to be revealed through the generalized parton distributions 
+(GPDs). While the majority of our knowledge about the nucleons' partonic 
+structure has come from the elsatic and deep-inelastic lepton scatterings,
+
+they have not resolved the question of how partons share the nucleon’s spin and 
+build up its intrinsic properties, such as the mass and the electromagnetic 
+properties. Understanding the correlations between the momentum and spatial 
+degrees of freedom of the partons inside the nucleons is a powerful way to 
+characterize the nucleons’ structure and resolve theses crucial open
+questions. These correlations are accessible via the study of generalized 
+parton distributions
+(GPDs), which we probe with hard exclusive scattering reactions, such as 
+deeply-virtual
+Compton scattering (DVCS)
+
+We report on the beam-spin asymmetry measurement associated with incoherent 
+deeply virtual Compton scattering off $^4$He in the valence quark region.  The 
+data has been accumulated using a 6 GeV longitudinally-polarized electron beam 
+incident on a pressurized $^4$He gaseous target placed in front of CLAS 
+spectrometer at Thomas Jefferson National Accelerator Facility. The base setup 
+of CLAS detected the scattered electrons and the recoil protons, while the 
+final-state real photons are detected by a supplementary electromagnetic 
+calorimeter at very forward angles.  The measured incoherent beam-spin 
+asymmetries indicate a suppression compared to those on free proton, indicating 
+possible medium modifications on the nucleon's quark distributions and opening 
+new opportunities to explore the origin of the EMC effect within the 
+generalized parton distributions framework.
+
 \end{abstract}
@@
 \begin{figure}[tb]
-\includegraphics[width=8.9cm]{figs/ALU_phi_p_Q2.pdf}
-\includegraphics[width=8.9cm]{figs/ALU_phi_p_x.pdf}
-\includegraphics[width=8.9cm]{figs/ALU_phi_p_t.pdf}
+\includegraphics[width=8.9cm]{figs/incoherent_ALU_phi.pdf}
 \caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented

### 2018-02-14 eg6-letters/incoherent/incoherent_prl.tex
pushing the first draft of the incoherent prl

--- 2017-03-23 eg6-letters/incoherent/incoherent_prl.tex
@@
 \begin{abstract}
-We report the incoherent beam-spin asymmetry measurement of deeply virtual 
-Compton scattering (DVCS) off $^4$He. The experiment used the 6 GeV electron 
-beam from Jefferson Lab projected onto a $^4$He target in the center of the 
-CEBAF Large Acceptance Spectrometer (CLAS).
+We report on the beam-spin asymmetries associated with incoherent deeply 
+   virtual Compton scattering off $^4$He in the valence quark region.  The data 
+   have been accumulated using a 6 GeV longitudinally-polarized electron beam 
+   incident on a pressurized $^4$He gaseous target placed in front of the CLAS 
+   spectrometer in Hall-B at Thomas Jefferson National Accelerator Facility.  
+   The baseline detection sub-systems of CLAS detected the scattered electrons 
+   and the recoil protons, while the final-state real photons are detected by a 
+   supplementary electromagnetic calorimeter at very forward angles. The 
+   measured beam-spin asymmetries on bound-protons exhibit a suppression 
+   compared to those on free proton, indicating possible medium modifications 
+   on the nucleon's quark distributions and opening new opportunities to 
+   explore the origin of the EMC effect within the framework of the generalized 
+   parton distributions.
+
 \end{abstract}
@@
 
-The main access to GPDs is through the measurement of deep virtual Compton 
-scattering (DVCS), i.e. the hard exclusive electroproduction of a real photon.  
-While other processes are known to be sensitive to GPDs, the measurement of
-DVCS is considered the cleanest probe and has been the focus of a worldwide effort 
+Electromagnetic probes have played a major role in advancing our knowledge 
+about the structure of nucleons, which are the origin of almost all the
+Universe visible matter. While the elastic lepton-nucleon measurements have 
+taught us about the spatial charge and magnetization distributions 
+\cite{Hofstadter:1955ae,Perdrisat:2006hj}, the deep-inelastic scattering (DIS) 
+experiments have uncovered the features of momentum sharing between the 
+constituents partons, i.e., quarks and gluons \cite{Dokshitzer:1977sg,pdg}. 
+With nuclear targets, the DIS measurements have revealed the fact that the 
+distribution of quarks in a fast moving nucleus is not a simple convolution of 
+their distributions within nucleons, known as the ``EMC 
+effect''\cite{EMC_first} (for reviews on the extensive investigations, see  
+\cite{EMC_CERN,EMC_SLAC,EMC_HERMES,EMC_JLab,EMC_John,EMC_mdeium_1,EMC_medium_2}).
+
+A wealth of information on the structure of matter lies in the correlations 
+between the momentum and spatial degrees of freedom of the partons. These 
+correlations are set to be revealed through deeply virtual Compton scattering 
+(DVCS), i.e., the hard exclusive lepto-production of a real photon, which 
+provide access to a three-dimensional imaging of partons within the generalized 
+parton distributions (GPDs) framework 
+\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.   
+The free proton DVCS measurement has been the focus of a worldwide effort 
 \cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
@@
 involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
-CERN. The vast majority of these measurements focused on the study of proton 
-structure and allowed extraction of the tomography of the nucleon (for details 
-on the formalism, see 
-\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
+CERN. Combining these measurements has enabled the first tomography extraction 
+of the free proton \cite{Dupre:2016mai}. New groundbreaking measurements of 
+exclusive DVCS from the $^{4}$He nucleus are a critical step towards providing 
+similar 3D pictures of the quark structure of the nucleus as a whole, via the 
+coherent channel \cite{Hattawy:2017woc}, and provide a new approach to 
+understanding the partonic modifications of the bound nucleons via the 
+incoherent DVCS channel \cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}. The 
+$^{4}$He nucleus is an ideal experimental target for these purposes as it has 
+only one chiral-even GPD that parametrizes its partonic structure, is 
+characterized by a strong binding energy, and has a relatively high nuclear 
+core density. The inclusive scattering off $^{4}$He has shown a large EMC 
+effect \cite{JSeely}, making this nucleus a golden target for investigating the 
+medium partonic modifications.
 
@@
 \caption{Representation of the leading-order, twist-2, handbag diagram of the 
-incoherent DVCS process off $^4$He.}
+   incoherent DVCS process off $^4$He, where the four-vectors of the electrons, 
+   photons, and protons are denoted by $k/k^\prime$, $q/q^\prime$, and 
+   $p/p^\prime$, respectively. $x+\xi$ is the nucleon’s longitudinal momentum 
+   fraction carried by the struck quark, 2$\xi$ is the longitudinal momentum 
+   fraction of the momentum transfer $\Delta$ ($= p - p^\prime$), and 
+   $t$~($=\Delta^2$) is the squared momentum transfer between the initial and
+   the final state nucleon.}
 \label{fig:diags}
@@
 
+FIG.~\ref{fig:diags} illustrates a schematic representation of the 
+leading-twist handbag diagram for the incoherent DVCS off $^{4}$He. In the 
+Bjorken region, i.e, large virtual photon four-momentum squared 
+($Q^{2}=-(k-k^\prime)^2$), and at small invariant momentum transfer ($t$), the 
+DVCS handbag diagram can be factorized, leaving the non-perturbative structure 
+of the nucleon to be parametrized in terms of four chirally-even GPDs: $H$, 
+$E$, $\widetilde{H}$, and $\widetilde{E}$, representing the four helicity-spin 
+combinations of the quark-nucleon states \cite{Freund_Collins,Ji_Osborne}.
+
+In this Letter, we present the beam-spin asymmetries associated with the photon 
+electroproduction on bound-proton off $^{4}$He. While the experimentally 
+measured cross section amplitude is the sum of the DVCS, BH (i.e., the final 
+state real photon is emitted by the incident or the scattered electron), and 
+their interference, the beam-spin asymmetry observable is sensitive to the 
+amplitudes that contain information on the GPDs, i.e., DVCS and interference 
+amplitudes. The beam-spin asymmetry observable is measurable using a polarized 
+lepton beam on unpolarized target (U) and defined in terms of the cross 
+sections as
+\begin{equation}
+  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
+                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
+    \label{BSA_equation}
+  \end{equation}
+where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the photon electroproduction 
+differential cross section for a positive (negative) beam helicity.
+
+Following the cross section decomposition suggested by \cite{Belitsky:2001ns}, 
+the different amplitudes can be expressed in terms of Fourier coefficients 
+associated with $\phi$-harmonics, where $\phi$ is the angle between the 
+leptonic and the hadronic planes of the reaction. At leading-twist, the 
+beam-spin asymmetry can be simplified as \begin{equation}
+   A_{LU}(\phi) = \frac{a_{0}\sin(\phi)}{1+a_{1}\cos(\phi)+a_{2}\cos(2\phi)}
+   \label{eq:alu-simp}
+\end{equation}
+with the parameters $a_{0,1,2}$ are combinations of the above mentioned Fourier 
+coefficients. The first sine harmonic of the beam-spin asymmetry is dominant 
+and proportional to the following combination of Compton form factors (CFF) 
+\cite{Guidal:2013rya}
+\begin{equation}
+   A_{LU}^{\sin\phi} \propto \operatorname{Im}( F_1 \mathcal{H}- \frac{t}{4M^2} 
+   F_2 \mathcal{E}+ \frac{x_B}{2}(F_1+F_2)\tilde{\mathcal{H}})
+\end{equation}
+where $F_1$ and $F_2$ are the Dirac and Pauli form factors with $x_B$ as the 
+Bjorken scaling variable. The real and the imaginary parts of the CFF 
+$\mathcal{H}$ are corresponding to the GPD $H$ by  \begin{align}
+   \Re(&\mathcal{H}) = \mathcal{P} \int_{0}^{1}dx[H(x,\xi,t)-H(-x,\xi,t)] \, 
+   C^{+}(x,\xi) \\
+   \Im(&\mathcal{H}) = - \pi [H(\xi,\xi,t)-H(-\xi,\xi,t)],
+\end{align}
+with $\mathcal{P}$ is the Cauchy principal value integral and $C^{+}$ is a 
+coefficient function defined as $(1/(x-\xi) + 1/(x+\xi))$ with $\xi$ being 
+related to $x_B$ by $\xi\approx {{x_B}\over{2-x_B}}$. Similar expressions apply 
+for the GPDs $E$, $\widetilde{H}$, and $\widetilde{E}$.
+
 %experimental setup
 
-The experiment E08-024 took place in Hall-B at JLab
-in 2009 using the nearly 100\% duty factor, longitudinally 
-polarized electron beam (83$\%$ polarization) at its full energy of 6.064 
-GeV. The data were collected over three months using a 6 atm gaseous $^4$He 
-target placed in the center of CLAS. For DVCS experiments, the CLAS baseline 
-design \cite{Mecking:2003zu} is supplemented with an inner calorimeter (IC) and 
-a solenoid. The IC extends the photon detection acceptance of CLAS, which was 
-originally from 15$^{\circ}$ to 45$^{\circ}$, to polar angles as low as 
-4$^{\circ}$. At these small angles the low-energy M\o{}ller electrons produced 
-in the target form a very high rate background that is
-suppressed by a 5 Tesla solenoid placed around the target.
+The experiment (E08-024~\cite{Hafidi:2008pr}) took place in Hall-B of Jefferson 
+Lab using the nearly 100\% duty factor, longitudinally-polarized electron beam 
+(83$\%$ polarization) from the Continuous Electron Beam Accelerator Facility 
+(CEBAF) accelerator at its full energy of 6.064 GeV. The data were accumulated 
+over 40 days using a 6-atm-pressure, 292-mm-long, and 6-mm-diameter gaseous 
+$^4$He target centered at 64~cm upstream of the CEBAF Large Acceptance 
+Spectrometer (CLAS) center. For similar DVCS experiments on free-proton target
+\cite{Girod:2007aa,Jo:2015ema}, the CLAS baseline design \cite{Mecking:2003zu} 
+is supplemented with an inner calorimeter (IC) and a solenoid. The IC extends 
+the photon detection acceptance of CLAS, which was originally from 15$^{\circ}$ 
+to 45$^{\circ}$, to polar angles as low as 4$^{\circ}$. As the coherent DVCS 
+off $^4$He, where the nucleus remain intact, was one of the proposed 
+measurements of our experiment and since CLAS cannot detect such low-energy 
+recoil nuclei, we built a small radial time projection chamber (RTPC) around 
+the target cell. (See~\cite{Dupre:2017upj} for a detailed description of the 
+RTPC and its performances and \cite{Hattawy:2017woc} for the coherent DVCS 
+measurements). In this setup, the 5-Tesla solenoid (that surrounds the target 
+and the RTPC) enabled the detection of the low-energy charged ions in the RTPC 
+and prevented the high-rate low-energy M\o{}ller electrons from reaching CLAS 
+sub-detectors by guiding these electrons towards a heavy shield placed around 
+the beam line.
 
-%DVCS selection
-To identify incoherent DVCS events, we first select events where one electron, 
-one proton, and at least one photon are detected in the final state. Electrons 
-are identified by using fiducial cuts and requiring appropriate signals in all 
-the sub-detectors of the baseline CLAS (drift chambers, Cherenkov counters, 
-electromagnetic calorimeter, and time of flight scintillators). Protons were 
-identified with fiducial and timing cuts using the CLAS drift chambers and time 
-of flight scintillators. In addition, we apply a vertex matching cut to ensure 
-the electron and the proton originate from the same position. The photons are 
-detected in either the IC or the CLAS electromagnetic calorimeter.  Note that 
-even though the DVCS reaction has only one real photon in the final state, 
-events with more than one good photon are not discarded at this stage. This is 
-motivated by the fact that, while soft photons are likely to be produced in 
-random coincidence, they cannot be mistaken for the large energy DVCS photons 
-($>2$ GeV). The most energetic photon is always considered as the DVCS photon 
-candidate.
+% DVCS selection
+Incoherent DVCS events were selected if an electron, a proton, and at least one 
+photon were detected in the final state. Electrons were identified by having 
+appropriate deposited energy in the electromagnetic calorimeter and proper 
+light yield in the Cherenkov counters in addition to having a negative 
+track-curvature in the drift chambers that corresponds to a momentum greater 
+than 800 MeV. The protons were distinguished from other positive particles by 
+timing cuts established using the time-of-flight measured by the scintillators 
+and the reconstructed track information from the drift chambers. Also, the 
+selected proton was required to be originating from the electron's vertex by 
+applying a vertex matching cut. The photons were detected in either the IC or 
+the CLAS electromagnetic calorimeter. All the signals within IC fiducial region 
+were assumed to be photons, while a timing cut is used to clean the EC photons 
+from neutrons. Note that even though the DVCS reaction has only one real photon 
+in the final state, events with more than one good photon are not discarded at 
+this stage. It was observed by the DVCS exclusivity cuts, discussed below, that 
+most of these photons are soft ones produced in random coincidence. In the 
+following selection stage, the most energetic photon is considered as the DVCS 
+photon candidate (see \cite{Hattawy:thesis} for additional details on the 
+particles identification).
 
-The main background in the measurement of DVCS is incoherent $\pi^{0}$ 
-production. Therefore, we remove events where a $\pi^{0}$ can be identified by 
-invariant mass reconstruction of two photons. To ensure the interaction occurs 
-at the partonic level and the DVCS handbag diagram is dominant, we select 
-events with $Q^{2}>1~[GeV^{2}/c^{2}]$. The exclusivity of the events is 
-obtained by applying a set of cuts on the following kinematic variables: the 
-co-planarity angle ($\Delta \phi$), the missing energy, the missing mass 
-squared, the missing transverse momentum, the missing mass squared of the 
-$e'^4He'$ system, and the angle ($\theta$) between the measured photon and the 
-missing momentum of the $e'^4He'$ system. The cuts are presented in 
-Figure~\ref{fig:kin-cuts}, which shows 3$\sigma$ cuts except for the missing.  
-After these requirements, we have about 20k events left, and Figure 
-\ref{fig:kin-coverage} presents their
-kinematic distributions in ($Q^{2}$,$x_{B}$) and ($Q^{2}$,$-t$).
+Further requirements were applied to clean the identified initial set of 
+incoherent DVCS events from backgrounds and other channels. Events were 
+selected with $Q^{2}$ greater the 1 GeV$^2$ to ensure that the interaction 
+occurs at the partonic level and the applicability of the factorization on the 
+DVCS handbag diagram, $\gamma^{*}p$ invariant mass (W) greater than 2 GeV to 
+avoid the nucleon region of excitation to resonances, and the transferred 
+momentum squared to the recoil proton has to be greater than a
+minimum value defined by the kinematics of the beam and the scattered electron 
+($-t~>~-t_{min}$). Then, the exclusivity of the incoherent DVCS events was 
+ensured by imposing constraints on the kinematical variables resulting from 
+conserving the four-momentum in the reaction $ep\rightarrow e'p'\gamma$. These 
+kinematical variables are: the coplanarity angle $\Delta\phi$ between the 
+($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) planes, the missing energy, mass, and 
+transverse momentum of the $e'\gamma$ and $e'p'\gamma$ system, the missing mass 
+squared of the $e'p'$ system, and the angle $\theta$ between the measured 
+photon and the missing momentum of the $e'p'$ system. The experimental data for 
+the most relevant exclusivity variables and applied cuts are shown in 
+FIG.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for additional details). We 
+also rejected events where a $\pi^0$ was identified by the invariant mass of 
+two photons. About 30k events passed all these requirements; their kinematic 
+distributions are shown in FIG.~\ref{fig:kin-coverage}.
 
@@
 \caption{The incoherent DVCS exclusivity cuts. The black distributions 
-   represent the coherent DVCS events candidate. The shaded distributions 
-   represent the events which passed all the exclusivity cuts except the 
-   quantity plotted. The vertical red lines represent the applied exclusivity 
-cuts. The distributions from left to right and from top to bottoms are: $\Delta 
-\phi$, missing energy, missing masses squared and the cone angle ($\theta$) 
-between the measured and the calculated photons.}
+   represent the incoherent DVCS events candidate before all the exclusive 
+   cuts. The shaded distributions represent the incoherent DVCS events which 
+   passed all the exclusivity cuts except the quantity plotted. The vertical 
+   red lines represent the applied exclusivity cuts. The distributions from 
+   left to right and from top to bottoms are: $\Delta \phi$, missing energy,
+   missing masses squared and the cone angle ($\theta$) between the measured 
+   and the calculated photons in the $e'p'$ final-state system. }
 \label{fig:kin-cuts}
+
 \end{figure}
-
-\begin{figure}[tb]
+\begin{figure}[h!]
 \hspace{-0.45cm}
@@
 
-%We identified two main backgrounds to our measurement, accidental coincidences 
-%and exclusive $\pi^0$ production. The accidental events have particles coming 
-%from different events, and we estimate their  contribution
-%to be 4.1\% of our sample. We evaluated this contribution by selecting events 
-%passing all our cuts but with an electron and an helium originating from 
-%different vertices. Regarding the $\pi^0$ production, it can easily be 
-%mistaken for DVCS when one of the two photons of the $\pi^0$ decay is produced 
-%at low energy in the laboratory frame and remains undetected. To estimate the 
-%importance of this background, we developed an event generator calibrated on 
-%the experimental yield of exclusive $\pi^0$ measured by our experiment. We 
-%used this generator together with a GEANT3 simulation of our detection system 
-%to estimate the ratio between
-%the number of $\pi^0$ events where the two photons are detected and those that 
-%would be mistaken for DVCS. This ratio is then multiplied by the measured 
-%yield of exclusive $\pi^0$ events to correct the DVCS data. Depending on the 
-%kinematics, we
-%found contaminations of 2 to 4\%. The study of systematics errors showed that 
-%the main contributions come from the choice of the DVCS exclusivity cuts (8\%) 
-%and the large binning size (5.1\%) [Is that right to add it here?]. However, 
-%added quadratically, these errors sum up to about 10\%, which always remain 
-%significantly smaller than the statistical errors.
+%background
+In spite of our selection requirements, two main backgrounds were observed to 
+contaminate our incoherent DVCS sample; accidental coincidences and exclusive 
+$\pi^0$ production. For the accidental events, i.e., $e'p'\gamma$ collection 
+with particles originated from different events, their contribution of 6.5\% 
+was evaluated by selecting events passing all our cuts but originating from 
+different vertices. Regarding the $\pi^0$ contamination, i.e., $ep\rightarrow 
+e'p'\pi^0$ events where one of the two photons of the $\pi^0$ decay is produced 
+below the energy threshold or outside the detection acceptance, we evaluated 
+this contribution by using data and simulation. From the simulation, we 
+calculated the ratio ($R$) between the number of $\pi^0$ events where the two 
+photons are detected and those that would be mistaken for DVCS ($R = 
+N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$). Then in each kinematical bin and for 
+each beam-helicity state, the $\pi^0$-subtracted experimental DVCS events is 
+calculated as $N = N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow 
+e'p'\pi^0}_{exp}$, where $N^{ep\rightarrow e'p'\gamma}_{exp}$ is the 
+experimentally identified number of $ep\rightarrow e'p'\gamma$ and 
+$N^{ep\rightarrow e'p'\pi^0}_{exp}$ is the experimentally identified 
+$ep\rightarrow e'p'\pi^0$ with the two photons were detected. Depending on the 
+kinematics, we found contaminations of 8\%-10\%.
 
 %asymmetries
-Several observables related to DVCS are of interest, but in this work we focus only 
-on the beam-spin asymmetry. This  observable is measurable using a polarized 
-lepton beam on an unpolarized target (U). It is convenient to use the beam-spin 
-asymmetry because most of the experimental normalization and acceptance issues 
-cancel out in the asymmetry ratio. It is defined in terms of the cross sections 
-as:
-  \begin{equation}
-  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
-                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
-    \label{BSA_equation}
-  \end{equation}
-where $d^{5}\sigma^{+(-)}$ is the DVCS differential cross 
-section for a positive (negative) beam helicity. Experimentally, $A_{LU}$ 
-can be expressed in terms of the measured number of events in each 
-beam-helicity state ($N^{+}$, $N^{-}$) as:
+It is convenient to use the beam-spin asymmetry as a DVCS observable because  
+the cross sections luminosity normalization and detector efficiencies cancel 
+out in the asymmetry ratio.  Experimentally, $A_{LU}$ can be simplified in 
+terms of the reaction yield in each beam-helicity state ($N^{\pm}$) as
 \begin{equation}
@@
 \end{equation}
-where $P_{B}$ is the beam polarization, and $N^{+}$ and $N^{-}$ are the number 
-of DVCS events detected with positive and negative electron helicity with 
-respect to the beam direction.
+where $P_{B}$ is the longitudinal beam polarization.
 
-To interpret DVCS, one has to keep in mind that this reaction is 
-indistinguishable from the Bethe-Heitler (BH) process, where the final photon 
-is emitted either from the incoming or the outgoing leptons. At leading twist 
-and leading order, the deeply virtual photon production cross section is 
-composed of BH, DVCS, and interference terms. The amplitudes of the 
-three terms can be approximated as a finite sum of Fourier harmonics, as shown 
-for the nucleon in \cite{Belitsky:2001ns}.
+Following the model guidance of \cite{Guidal:2013rya}, the GPD $H$ dominants 
+the other three GPDs within the accessible phase-phase of using the 6 GeV 
+electron beam from CEBAF and CLAS spectrometer. Therefore, measuring $A_{LU}$ 
+gives access to the real and imaginary part of the CFF $\mathcal{H}$ through 
+the parameters $a_0$, $a_1$, and $a_2$ of equation \ref{eq:alu-simp}.  
+Moreover, the free proton $A_{LU}$ measurements, \cite{Girod:2007aa}, have 
+shown that the $cos(2\phi)$ term, which is corresponding to the pure DVCS 
+amplitude, is suppressed and compatible with zero.
 
-Due to limited statistics, we only bin  our data two-dimensionally 
- in the azimuthal angle ($\phi$) and one of the kinemtical variables 
-$Q^{2}$, $x_{B}$ and $t$. Figure \ref{fig:alu} presents $A_{LU}$ for the three
-sets of binning. The asymmetries are fitted with the form of $\frac{\alpha 
-sin(\phi)}{1+ \beta cos(\phi)}$.  Figure \ref{fig:alu90} shows the $Q^2$, 
-$x_{B}$, and $-t$-dependencies of the fitted $A_{LU}$ signals at 
-$\phi$~=~90$^{\circ}$. The $x_{B}$ and $-t$-dependencies are compared to 
-theoretical calculations performed by S.~Liuti and K.~Taneja 
-\cite{simonetta_2}. Their model relies on the impulse approximation and uses 
-advanced spectral functions of nuclei.  The calculations are at slightly 
-different kinematics than our data but still provide some guidance. The 
-experimental results appear to have larger asymmetries than the calculations.  
-These differences may arise from nuclear effects which are not taken into 
-account in the model, such as long-range interactions.
+Due to limited statistics, the data were binned two-dimensionally into 36 bins.  
+That is, four statistically-equivalent bins in each of the kinematical 
+variables ($Q^{2}$, $x_{B}$, $t$) were constructed one at a time. Then, each 
+bin is divided into nine bins in the azimuthal angle ($\phi$).  
+FIG.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
+$\phi$ in bins in $Q^{2}$, $x_{B}$, and $t$. The curves on the plots are fits 
+of the approximated form $\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$. The 
+study of systematic uncertainties showed that the main contributions come from 
+the choice of the DVCS exclusivity cuts (6\%) and the large binning size (7\%).  
+However, added quadratically, these uncertainties sum up to about 10\%, which 
+always remains significantly smaller than the statistical errors.
 
 \begin{figure}[tb]
-\includegraphics[width=8.9cm]{figs/ALU_phi_p_Q2.pdf}
-\includegraphics[width=8.9cm]{figs/ALU_phi_p_x.pdf}
-\includegraphics[width=8.9cm]{figs/ALU_phi_p_t.pdf}
+\includegraphics[width=8.9cm]{figs/incoherent_ALU_phi.pdf}
 \caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
@@
    $-t$ bins (bottom panel). The error bars represent the statistical 
-uncertainties. The gray bands represent the systematic uncertainties, including 
-the normalisation uncertainties. The red curves are the results of our fits 
-with the form $\frac{\alpha sin(\phi)}{1+ \beta cos(\phi)}$.}
+   uncertainties. The gray bands represent the systematic uncertainties, 
+   including the normalisation uncertainties. The black curves are the results 
+   of our fits with the form $\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$.}
 \label{fig:alu}
 \end{figure}
+
+We present in FIG.~\ref{fig:alu90} the dependence of the fitted $A_{LU}$ 
+signals at $\phi$~=~90$^{\circ}$ on the kinematical variables $Q^2$, $x_{B}$, 
+and $t$. Within the given uncertainties, $A_{LU}$ does not indicate a strong 
+dependence on $Q^2$. The $x_{B}$ and $t$ dependencies are compared to 
+theoretical calculations performed by S.~Liuti and K.~Taneja 
+\cite{simonetta_2}. Their model uses a realistic spectral function and 
+considers off-shell effects. The calculations are carried out at slightly 
+different kinematics than our data but still provide some guidance. The 
+experimental results appear to have smaller asymmetries than the calculations.  
+These differences may arise from nuclear effects which are not taken into 
+account in the model, such as long-range interactions.
 
@@
 \includegraphics[width=6.9cm]{figs/ALU_90_p_vs_t_shortscenrario.pdf}
-\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $-t$-dependencies (right) of
-   the $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
-   middle plot: the full-red and the dashed-blue curves are theoretical 
-   calculations from \cite{simonetta_2}. On the right: the green circles are 
+\caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $t$ dependencies (bottom) of
+   the fitted $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). The error bars 
+   represent the statistical uncertainties, while the gray bands represent the 
+   systematic uncertainties. On the middle plot: the curves are theoretical 
+   calculations from \cite{simonetta_2}. On the bottom: the green circles are 
    the HERMES $-A_{LU}$ (positron beam was used) inclusive measurements 
-\cite{Airapetian}, the colored curves represent theoretical calculations from 
-\cite{simonetta_2}.}
-\label{fig:alu90}
+   \cite{Airapetian}, the curves represent theoretical calculations from 
+   \cite{simonetta_2}. } \label{fig:alu90}
 \end{figure}
 
-\begin{figure}[tp]
+In this work we carried out the first step towards measuring the 
+``generalized'' EMC effect in order to understand the potential sources of 
+nuclear effects at the partonic level within the GPDs framework. We construct 
+the ratio of $A_{LU}$ for bound protons to that on free proton target measured 
+using similar electron-beam energy and experimental setup.  
+FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the dependence of the 
+beam-spin asymmetry ratio at $\phi$~=~90$^{\circ}$ on the kinematical variables 
+$Q^2$, $x_B$, and $t$. The free proton asymmetries were interpolated from the 
+published results \cite{Girod:2007aa}.
+
+\begin{figure}[tb]
 \centering
@@
 \includegraphics[width=6.9cm]{figs/ALU_ratioInc_t_shortscenrario.pdf}
-\caption{ The $A_{LU}$ ratio between the bound and the free proton at 
-   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
-   middle), and $t$ (on the bottom). The black squares are our results, the 
-   green circles are the HERMES inclusive measurement \cite{Airapetian} 
-   results.  The blue and red curves are from an on-shell calculations from S.  
-   Liuti and K.  Taneja \cite{simonetta_2}. The solid and dashed black curves 
-are from the off-shell calculations \cite{Guzey:2008fe}.} 
+\caption{ The $A_{LU}$ ratio of the bound to the free proton at 
+   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (top), $x_B$ (middle), and $t$ 
+   (bottom). The black squares are from this work, the green circles are the 
+   HERMES inclusive measurement \cite{Airapetian}. The blue and red curves are 
+   results of off-shell calculations \cite{simonetta_2}. The solid and dashed 
+   black curves are from on-shell calculations \cite{Guzey:2008fe}.} 
    \label{fig:incoh_EMC_ratio_ALU_proton}
@@
 
+The $A_{LU}$ ratios show a 20\%-40\% suppression in the bound protons compared 
+to the free protons. These measurements disagree with the enhancement predicted 
+by the on-shell calculations that use the medium modified GPDs as caluclated 
+from the quark-meson coupling model \cite{Guzey:2008fe}. The off-shell 
+calculations overshoot the data indicating a trend \cite{simonetta_2}. In
+particular, the anti-shadowing region seems to be absent in terms of the 
+$A_{LU}$ ratio, while it was predicted by the calculation. Within the given 
+uncertainties, our measured ratios are compatible with the previous measured 
+single point from HERMES \cite{Airapetian}.
+
+These data, while limited in statistics, proved the experimental feasibility of 
+measuring DVCS of bound-nucleons in addition to the EMC effect within the GPDs 
+framework and led the way to the approval of a next generation nuclear 
+measurements \cite{Armstrong:2017wfw}. The future measurements will be carried 
+out using the new CLAS12 spectrometer and the upgraded CEBAF 12 GeV electron 
+beam at an electron-nucleon luminosity of 10$^{35}$cm$^{-2}$s$^{-1}$. The wider 
+accessible phase-space and the higher luminosity will enable us to study 
+nuclear effects and their manifestations on GPDs including the effect of final 
+state interactions.
+
 %conclusion
+In summary, we have presented the first exclusive beam-spin asymmetries 
+associated with incoherent DVCS off $^4$He using an upgraded setup of CLAS 
+spectrometer at Jefferson Lab. Our results were compared to some model 
+calculations based on different assumptions of the nuclear medium effects at 
+the partonic level and allowed us to draw some conclusions. The bound-proton 
+beam-spin asymmetries indicate a suppression compared to the free proton 
+results measured in similar phase-space. While the data are limited in 
+statistics, they opened new insights for extensive future measurements.
 
@@
 
-We acknowledge the staff of the Accelerator and Physics Divisions at Jefferson 
-Lab for making this experiment possible. This work is supported by the U.S.  
-Department of Energy, Office of Science, Office of Nuclear Physics contract 
-DE-AC05-06OR23177.
+The authors acknowledge the staff of the Accelerator and Physics Divisions at 
+the Thomas Jefferson National Accelerator Facility who made this experiment 
+possible. This work was supported in part by the Chilean Comisi\'on Nacional de 
+Investigaci\'on Cient\'ifica y Tecnol\'ogica (CONICYT), the Italian Instituto 
+Nazionale di Fisica Nucleare, the French Centre National de la Recherche 
+Scientifique, the French Commissariat \`a l'Energie Atomique, the U.S.  
+Department of Energy under Contract No. DE-AC02-06CH11357, the United Kingdom 
+Science and Technology Facilities Council (STFC), the Scottish Universities 
+Physics Alliance (SUPA), the National Research Foundation of Korea, and the 
+Office of Research and Economic Development at Mississippi State University.  
+M.~Hattawy also acknowledges the support of the Consulat G\'en\'eral de France 
+\`a J\'erusalem.  The Southeastern Universities Research Association operates 
+the Thomas Jefferson National Accelerator Facility for the United States 
+Department of Energy under Contract No. DE-AC05-06OR23177.
 
 \begin{thebibliography}{99}
-\bibitem{Mueller:1998fv} 
-D. Mueller, D. Robaschik, B. Geyer, F.M. Dittes and J. Horejsi,
+
+%\cite{Hofstadter:1955ae}
+\bibitem{Hofstadter:1955ae} R.~Hofstadter and R.~W.~McAllister,
+%``Electron Scattering From the Proton,''
+Phys.\ Rev.\  {\bf 98}, 217 (1955).
+%doi:10.1103/PhysRev.98.217
+
+%\cite{Perdrisat:2006hj}
+\bibitem{Perdrisat:2006hj} C.~F.~Perdrisat, V.~Punjabi and M.~Vanderhaeghen,
+%``Nucleon Electromagnetic Form Factors,''
+Prog.\ Part.\ Nucl.\ Phys.\  {\bf 59}, 694 (2007)
+%doi:10.1016/j.ppnp.2007.05.001
+%[hep-ph/0612014].
+
+%\cite{Dokshitzer:1977sg}
+\bibitem{Dokshitzer:1977sg} Y.~L.~Dokshitzer,
+%``Calculation of the Structure Functions for Deep Inelastic Scattering and e+ 
+   %e- Annihilation by Perturbation Theory in Quantum Chromodynamics.,''
+Sov.\ Phys.\ JETP {\bf 46}, 641 (1977)
+[Zh.\ Eksp.\ Teor.\ Fiz.\  {\bf 73}, 1216 (1977)].
+
+%\cite{pdg}
+\bibitem{pdg} J.~Beringer {\it et al.} (Particle Data Group), Phys.\ Rev.\ D 
+   {\bf 86}, 010001 (2012).
+
+\bibitem{EMC_first}
+   J.~J.~Aubert {\it et al.}, 
+      %“The ratio of the nucleon structure functions F 2 n for iron and
+      %deuterium,” 
+      Phys.\ Lett.\, vol.\ B { \bf 123}, pp. 275–278 (1983).
+
+\bibitem{EMC_CERN}
+J. Ashman et al. (EMC Collaboration), 
+      %Measurement of the ratios of deep inelastic muon-nucleus cross sections 
+%on various nuclei compared to deuterium, 
+      Phys.\ Lett.\ B\ {\bf 202}, 603 1988.
+
+\bibitem{EMC_SLAC}
+J. Gomez et al. (SLAC-E139), 
+      %Measurement of the A dependence of deep-inelastic electron scattering, 
+      Phys.\ Rev.\ D\ {\bf 49}, 4348 (1994).
+
+\bibitem{EMC_HERMES}
+A. Airapetian et al. (HERMES Collaboration), 
+      %Nuclear effects on R = $\sigma_{L}/\sigma_{T}$ in deep-inelastic 
+%scattering, 
+      Phys.\ Lett.\ B\ {\bf 567}, 339 (2003).
+
+\bibitem{EMC_JLab}
+J. Seely et al., 
+      %New Measurements of the European Muon Collaboration Effect in Very Light 
+%Nuclei, 
+      Phys.\ Rev.\ Lett.\ {\bf 103}, 202301 (2009).
+
+\bibitem{EMC_John}
+J. Arrington et al., 
+%A detailed study of the nuclear dependence of the EMC effect and short-range 
+%correlations, 
+      Phys.\ Rev.\ C\ {\bf 86}, 065204 (2012).
+
+\bibitem{EMC_mdeium_1}
+I. Clo\"et et al., 
+%Isovector EMC effect explains the NuTeV anomaly, 
+Phys.\ Rev.\ Lett.\ {\bf 102}, 252301 (2009).
+
+\bibitem{EMC_medium_2}
+I. Clo\"et et al., %Parity-violating DIS and the flavour dependence of the EMC 
+%effect, 
+Phys.\ Rev.\ Lett.\ {\bf 109}, 182301 (2012).
+
+\bibitem{Mueller:1998fv} D. Mueller, D. Robaschik, B. Geyer, F.M. Dittes, and 
+   J.  Horejsi,
 Fortsch.\ Phys. {\bf 42}, 101 (1994).
@@
 Phys.\ Rev.\ D {\bf 56}, 5524 (1997).
-
-\bibitem{Burkardt:2000za} 
-  M.~Burkardt,
-  Phys.\ Rev.\ D {\bf 62}, 071503 (2000)
-  Erratum: Phys.\ Rev.\ D {\bf 66}, 119903 (2002)
-
-\bibitem{Diehl:2002he} 
-  M.~Diehl,
-  Eur.\ Phys.\ J.\ C {\bf 25}, 223 (2002)
-  Erratum: Eur.\ Phys.\ J.\ C {\bf 31}, 277 (2003)
-
-\bibitem{Belitsky:2002ep} 
-  A.~V.~Belitsky and D.~Mueller,
-  Nucl.\ Phys.\ A {\bf 711}, 118 (2002)
-
-\bibitem{Burkardt:2005hp} 
-  M.~Burkardt,
-  Phys.\ Rev.\ D {\bf 72}, 094020 (2005)
 
@@
 
-\bibitem{Goeke:2001tz}
-K. Goeke, M.V. Polyakov and M. Vanderhaeghen,
-Prog.\ Part.\ Nucl.\ Phys. {\bf 47}, 401 (2001).
+\bibitem{JSeely}
+J. Seely {\it et al.}, Phys.\ Rev.\ Lett.\ {\bf 103}, 202301 (2009).
 
-\bibitem{Diehl:2003ny}
-M. Diehl,
-Phys.\ Rept.  {\bf 388}, 41 (2003).
+\bibitem{Dupre:2016mai} R.~Dupre, M.~Guidal and M.~Vanderhaeghen,
+ %``Tomographic image of the proton,''
+ Phys.\ Rev.\ D {\bf 95}, no. 1, 011501 (2017)
 
-\bibitem{Ji:2004gf}
-X.D. Ji,
-Ann.\ Rev.\ Nucl.\ Part.\ Sci. {\bf 54}, 413 (2004).
+\bibitem{Hattawy:2017woc} 
+   M.~Hattawy {\it et al.} [CLAS Collaboration],
+   Phys.\ Rev.\ Lett.\  {\bf 119}, no. 20, 202004 (2017)
 
-\bibitem{Belitsky:2005qn}
-A.V. Belitsky and A.V. Radyushkin,
-Phys.\ Rept. {\bf 418}, 1 (2005).
+\bibitem{simonetta_2}
+S.~Liuti and K.~Taneja, Phys.\ Rev.\ C {\bf 72}, 032201 (2005)
 
-\bibitem{Boffi:2007yc} S. Boffi and B. Pasquini,
-Riv.\ Nuovo Cim. {\bf 30}, 387 (2007).
+\bibitem{Guzey:2006xi} V.~Guzey and T.~Teckentrup, Phys.\ Rev.\ D {\bf 74}, 
+   054027 (2006)
 
-\bibitem{Guidal:2013rya} 
-M.~Guidal, H.~Moutarde and M.~Vanderhaeghen,
-Rept.\ Prog.\ Phys.\  {\bf 76}, 066202 (2013).
-
-\bibitem{Dupre:2015jha} 
-  R.~Dupr\'e and S.~Scopetta,
-  Eur.\ Phys.\ J.\ A {\bf 52}, no. 6, 159 (2016)
-
-\bibitem{Hen:2016kwk} 
-  O.~Hen, G.~A.~Miller, E.~Piasetzky and L.~B.~Weinstein,
-  arXiv:1611.09748 [nucl-ex].
-
-\bibitem{Norton:2003cb} 
-  P.~R.~Norton,
-  Rept.\ Prog.\ Phys.\  {\bf 66}, 1253 (2003).
-
-\bibitem{Geesaman:1995yd} 
-  D.~F.~Geesaman, K.~Saito and A.~W.~Thomas,
-  Ann.\ Rev.\ Nucl.\ Part.\ Sci.\  {\bf 45}, 337 (1995).
+\bibitem{Guzey:2008fe} V.~Guzey, A.~W.~Thomas and K.~Tsushima,
+  Phys.\ Lett.\ B {\bf 673}, 9 (2009)
 
 \bibitem{Freund_Collins}
-A.~Freund and J.C.~Collins, 
-Phys.\ Rev.\ D {\bf 59}, 074009 (1998)
+J.C.~Collins and A.~Freund, Phys.\ Rev.\ D {\bf 59}, 074009 (1999).
 
 \bibitem{Ji_Osborne}
-X.-D.~Ji and J.~Osborne, 
-Phys.\ Rev.\ D {\bf 58}, 094018 (1998)
-
-\bibitem{Ellinghaus:2002zw}
-F.~Ellinghaus {\it et al.} [HERMES Collaboration],
-AIP Conf.\ Proc.\  {\bf 675}, 303 (2003)
-
-\bibitem{Guzey:2003jh} 
-  V.~Guzey and M.~Strikman,
-  Phys.\ Rev.\ C {\bf 68}, 015204 (2003)
-
-\bibitem{JSeely}
-J. Seely {\it et al.} 
-Phys.\ Rev.\ Lett.\ {\bf 103}, 202301 (2009)
-
-\bibitem{Mecking:2003zu} 
-   B.~A.~Mecking {\it et al.} [CLAS Collaboration],
-   Nucl.\ Instrum.\ Meth.\ A {\bf 503}, 513 (2003).
+   X.-D.~Ji and J.~Osborne, Phys.\ Rev.\ D {\bf 58}, 094018 (1998).
 
@@
 
-\bibitem{Kirchner:2003wt}
-A.~Kirchner and D.~Mueller, 
-Eur.\ Phys.\ J.\ C {\bf 32}, 347 (2003)
+\bibitem{Guidal:2013rya} M.~Guidal, H.~Moutarde, and M.~Vanderhaeghen,
+Rep.\ Prog.\ Phys.\  {\bf 76}, 066202 (2013).
 
-\bibitem{Belitsky:2008bz}
-A.~V.~Belitsky and D.~Mueller,
-Phys.\ Rev.\ D {\bf 79}, 014017 (2009)
+\bibitem{Hafidi:2008pr} K.~Hafidi {\it et al.},
+   proposal PR-08-024 to JLab PAC33 (unpublished).
 
-%\bibitem{eg6_note}
-%M. Hattawy {\it et al.} (CLAS-EG6 Working Group), CLAS internal analysis note, 
-%2016.
+\bibitem{Mecking:2003zu} B.~A.~Mecking {\it et al.} [CLAS Collaboration],
+   Nucl.\ Instrum.\ Meth.\ A {\bf 503}, 513 (2003).
 
-\bibitem{simonetta_2}
-S.~Liuti and K.~Taneja, 
-Phys.\ Rev.\ C {\bf 72}, 032201 (2005)
+\bibitem{Dupre:2017upj} R.~Dupr\'e {\it et al.},
+  arXiv:1706.10160.
 
-\bibitem{Guzey:2006xi}
-V.~Guzey and T.~Teckentrup,
-Phys.\ Rev.\ D {\bf 74}, 054027 (2006)
+\bibitem{Hattawy:thesis}
+M.~Hattawy, Ph.D. thesis, Universit{\'e} Paris Sud - Paris XI, France, 2015 
+[Institution Report No. 2015PA112161].
 
-%\cite{Guzey:2008fe}
-\bibitem{Guzey:2008fe} 
-   V.~Guzey, A.~W.~Thomas and K.~Tsushima,
-  Phys.\ Lett.\ B {\bf 673}, 9 (2009)
-
-\bibitem{DD_model}
-I.~V.~Musatov and A.~V.~Radyushkin, 
-Phys.\ Rev.\ D {\bf 61}, 074027 (2000).
+%\cite{Armstrong:2017wfw}
+\bibitem{Armstrong:2017wfw} W.~Armstrong {\it et al.},
+     %``Partonic Structure of Light Nuclei,''
+     arXiv:1708.00888 [nucl-ex].
+       %%CITATION = ARXIV:1708.00888;%%
+         %2 citations counted in INSPIRE as of 13 Feb 2018
+     %\cite{Armstrong:2017zqr}
+%\bibitem{Armstrong:2017zqr} W.~Armstrong {\it et al.},
+       %``Tagged EMC Measurements on Light Nuclei,''
+       arXiv:1708.00891 [nucl-ex].
+         %%CITATION = ARXIV:1708.00891;%%
+           %1 citations counted in INSPIRE as of 13 Feb 2018
+       %\cite{Armstrong:2017zcm}
+%    \bibitem{Armstrong:2017zcm} W.~R.~Armstrong {\it et al.},
+         %``Spectator-Tagged Deeply Virtual Compton Scattering on Light 
+       %Nuclei,''
+         arXiv:1708.00835 [nucl-ex].
+           %%CITATION = ARXIV:1708.00835;%%
 

### 2018-02-19 eg6-letters/incoherent/incoherent_prl.tex
1st set of implementing the comments from Stepan

@@
 \begin{document}
-%\linenumbers
+\linenumbers
 
-\title{Revealing the Bound Nucleon 3D Partonic Structure through Incoherent 
-Deeply Virtual Compton Scattering off $^4$He}
+\title{First exclusive DVCS measurement off bound nucleon in $^4$He}
+%\title{Revealing the Bound Nucleon 3D Partonic Structure through Incoherent Deeply Virtual Compton Scattering off $^4$He}
 
@@
    virtual Compton scattering off $^4$He in the valence quark region. The data 
-   have been accumulated using a 6 GeV longitudinally-polarized electron beam 
+   were accumulated using a 6 GeV longitudinally-polarized electron beam 
    incident on a pressurized $^4$He gaseous target placed in front of the CLAS 
-   spectrometer in Hall-B at Thomas Jefferson National Accelerator Facility.  
-   The baseline detection sub-systems of CLAS detected the scattered electrons 
-   and the recoil protons, while the final-state real photons are detected by a 
-   supplementary electromagnetic calorimeter at very forward angles. The 
-   measured beam-spin asymmetries on bound-protons exhibit a suppression 
-   compared to those on free proton, indicating possible medium modifications 
-   on the nucleon's quark distributions and opening new opportunities to 
-   explore the origin of the EMC effect within the framework of the generalized 
-   parton distributions.
+   spectrometer in Hall-B at the Thomas Jefferson National Accelerator 
+   Facility.  The baseline detection sub-systems of CLAS detected the scattered 
+   electrons and the recoil protons, while the final-state real photons are 
+   detected by a supplementary electromagnetic calorimeter at very forward 
+   angles. The measured beam-spin asymmetries on bound-protons exhibit a 
+   suppression compared to those on free proton, indicating possible medium 
+   modifications on the nucleon's quark distributions and opening new 
+   opportunities to explore the origin of the EMC effect within the framework 
+   of the generalized parton distributions.
 
@@
 about the structure of nucleons, which are the origin of almost all the
-Universe visible matter. While the elastic lepton-nucleon measurements have 
+Universe's visible matter. While elastic lepton-nucleon measurements have 
 taught us about the spatial charge and magnetization distributions 
-\cite{Hofstadter:1955ae,Perdrisat:2006hj}, the deep-inelastic scattering (DIS) 
+\cite{Hofstadter:1955ae,Perdrisat:2006hj}, deep-inelastic scattering (DIS) 
 experiments have uncovered the features of momentum sharing between the 
@@
 distribution of quarks in a fast moving nucleus is not a simple convolution of 
-their distributions within nucleons, known as the ``EMC 
+their distributions within nucleons, an observation known as the ``EMC 
 effect''\cite{EMC_first} (for reviews on the extensive investigations, see  
@@
 (DVCS), i.e., the hard exclusive lepto-production of a real photon, which 
-provide access to a three-dimensional imaging of partons within the generalized 
-parton distributions (GPDs) framework 
+provides access to a three-dimensional imaging of partons within the 
+generalized parton distributions (GPDs) framework 
 \cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.   
 The free proton DVCS measurement has been the focus of a worldwide effort 
-\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
+\cite{Stepanyan:2001sm,Airapetian:2001yk,Airapetian:2006zr,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
 Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}
-involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
-CERN. Combining these measurements has enabled the first tomography extraction 
-of the free proton \cite{Dupre:2016mai}. New groundbreaking measurements of 
-exclusive DVCS from the $^{4}$He nucleus are a critical step towards providing 
-similar 3D pictures of the quark structure of the nucleus as a whole, via the 
-coherent channel \cite{Hattawy:2017woc}, and provide a new approach to 
-understanding the partonic modifications of the bound nucleons via the 
-incoherent DVCS channel \cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}. The 
+involving several accelerator facilities such as Jefferson Lab, HERA and  
+CERN. Combining these measurements has enabled the first extractions of GPDs 
+and a 3-D tomography of the free proton \cite{Guidal:2013rya,Dupre:2016mai}.  
+New measurements of exclusive DVCS from the $^{4}$He nucleus are a critical 
+step towards providing similar 3-D pictures of the quark structure of the 
+nucleus as a whole, via the coherent channel 
+\cite{Airapetian:2009cga,Hattawy:2017woc}, and provide a new approach for 
+understanding modifications of the partonic structure of the bound nucleons via 
+the incoherent DVCS channel \cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}. The 
 $^{4}$He nucleus is an ideal experimental target for these purposes as it has 
@@
 effect \cite{JSeely}, making this nucleus a golden target for investigating the 
-medium partonic modifications.
+medium modifications of the nucleon's partonic structure.
 
@@
 
-FIG.~\ref{fig:diags} illustrates a schematic representation of the 
+FIG.~\ref{fig:diags} illustrates the 
 leading-twist handbag diagram for the incoherent DVCS off $^{4}$He. In the 
-Bjorken region, i.e, large virtual photon four-momentum squared 
-($Q^{2}=-(k-k^\prime)^2$), and at small invariant momentum transfer ($t$), the 
-DVCS handbag diagram can be factorized, leaving the non-perturbative structure 
+Bjorken regime, i.e, large virtual photon four-momentum squared 
+($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small invariant momentum transfer ($t=(p-p^\prime)^2$), the 
+DVCS scattering process can be factorized, leaving the non-perturbative structure 
 of the nucleon to be parametrized in terms of four chirally-even GPDs: $H$, 
@@
 
-In this Letter, we present the beam-spin asymmetries associated with the photon 
-electroproduction on bound-proton off $^{4}$He. While the experimentally 
-measured cross section amplitude is the sum of the DVCS, BH (i.e., the final 
-state real photon is emitted by the incident or the scattered electron), and 
-their interference, the beam-spin asymmetry observable is sensitive to the 
-amplitudes that contain information on the GPDs, i.e., DVCS and interference 
-amplitudes. The beam-spin asymmetry observable is measurable using a polarized 
-lepton beam on unpolarized target (U) and defined in terms of the cross 
-sections as
+In this Letter, we present the first exclusive measurement of the beam-spin asymmetry in deeply virtual electroproduction of a real photon off bound-proton in $^{4}$He.
+Experimentally we measure squared sum of the Bethe-Heitler (BH) and DVCS amplitudes, with BH process where real photon is emitted by the incident or the scattered electron dominating the cross section in our kinematics.
+%While the experimentally measured cross section amplitude is the sum of the DVCS, BH (i.e., the final state real photon is emitted by the incident or the scattered electron), and their interference, 
+The beam-spin asymmetry, in other hand, is sensitive to the DVCS amplitude and the interference term that contain information on the GPDs. 
+The beam-spin asymmetry observable with a longitudinally polarized electron beam (L) and unpolarized target (U) is defined as:
 \begin{equation}
@@
 
-Following the cross section decomposition suggested by \cite{Belitsky:2001ns}, 
-the different amplitudes can be expressed in terms of Fourier coefficients 
+Following the cross section decomposition provided in \cite{Belitsky:2001ns}, 
+the different components can be expressed in terms of Fourier coefficients 
 associated with $\phi$-harmonics, where $\phi$ is the angle between the 
 leptonic and the hadronic planes of the reaction. At leading-twist, the 
-beam-spin asymmetry can be simplified as \begin{equation}
+beam-spin asymmetry can be simplified as: 
+\begin{equation}
    A_{LU}(\phi) = \frac{a_{0}\sin(\phi)}{1+a_{1}\cos(\phi)+a_{2}\cos(2\phi)}
@@
 \end{equation}
-with the parameters $a_{0,1,2}$ are combinations of the above mentioned Fourier 
-coefficients. The first sine harmonic of the beam-spin asymmetry is dominant 
-and proportional to the following combination of Compton form factors (CFF) 
+where the parameters $a_{0,1,2}$ are combinations of the above mentioned Fourier 
+coefficients. The $\sin(\phi)$ harmonic is dominant in $A_{LU}$ 
+and is proportional to the following combination of Compton form factors (CFF) 
 \cite{Guidal:2013rya}
@@
 Bjorken scaling variable. The real and the imaginary parts of the CFF 
-$\mathcal{H}$ are corresponding to the GPD $H$ by  \begin{align}
+$\mathcal{H}$ relate to the GPD $H$ as  
+\begin{align}
    \Re(&\mathcal{H}) = \mathcal{P} \int_{0}^{1}dx[H(x,\xi,t)-H(-x,\xi,t)] \, 
@@
 (83$\%$ polarization) from the Continuous Electron Beam Accelerator Facility 
-(CEBAF) accelerator at its full energy of 6.064 GeV. The data were accumulated 
+(CEBAF) accelerator at energy of 6.064 GeV. The data were accumulated 
 over 40 days using a 6-atm-pressure, 292-mm-long, and 6-mm-diameter gaseous 
 $^4$He target centered at 64~cm upstream of the CEBAF Large Acceptance 
-Spectrometer (CLAS) center. For similar DVCS experiments on free-proton target
+Spectrometer (CLAS) coordinate center. For similar DVCS experiments on free-proton target
 \cite{Girod:2007aa,Jo:2015ema}, the CLAS baseline design \cite{Mecking:2003zu} 
-is supplemented with an inner calorimeter (IC) and a solenoid. The IC extends 
-the photon detection acceptance of CLAS, which was originally from 15$^{\circ}$ 
-to 45$^{\circ}$, to polar angles as low as 4$^{\circ}$. As the coherent DVCS 
-off $^4$He, where the nucleus remain intact, was one of the proposed 
-measurements of our experiment and since CLAS cannot detect such low-energy 
-recoil nuclei, we built a small radial time projection chamber (RTPC) around 
-the target cell. (See~\cite{Dupre:2017upj} for a detailed description of the 
-RTPC and its performances and \cite{Hattawy:2017woc} for the coherent DVCS 
-measurements). In this setup, the 5-Tesla solenoid (that surrounds the target 
-and the RTPC) enabled the detection of the low-energy charged ions in the RTPC 
-and prevented the high-rate low-energy M\o{}ller electrons from reaching CLAS 
-sub-detectors by guiding these electrons towards a heavy shield placed around 
-the beam line.
+is supplemented with an inner calorimeter (IC) and a solenoid magnet. The IC extends 
+the photon detection acceptance of CLAS to very small polar angles, 4$^{\circ}$. 
+%As the coherent DVCS off $^4$He, where the nucleus remain intact, was one of the proposed measurements of our experiment and since CLAS cannot detect such low-energy recoil nuclei, we built a small radial time projection chamber (RTPC) around the target cell.
+(See~\cite{Dupre:2017upj} for a detailed description of the RTPC and its performances and \cite{Hattawy:2017woc} for the coherent DVCS measurements).
+In this setup,
+The 5-Tesla solenoid magnet in the center of which target was located 
+%(that surrounds the target and the RTPC) enabled the detection of the low-energy charged ions in the RTPC and 
+prevented the high-rate low-energy M{\o}ller electrons from reaching the CLAS drift chambers by guiding them electrons insde a tungsten shield placed around the beam line.
 
@@
 Incoherent DVCS events were selected if an electron, a proton, and at least one 
-photon were detected in the final state. Electrons were identified by having 
-appropriate deposited energy in the electromagnetic calorimeter and proper 
-light yield in the Cherenkov counters in addition to having a negative 
-track-curvature in the drift chambers that corresponds to a momentum greater 
-than 800 MeV. The protons were distinguished from other positive particles by 
-timing cuts established using the time-of-flight measured by the scintillators 
-and the reconstructed track information from the drift chambers. Also, the 
-selected proton was required to be originating from the electron's vertex by 
-applying a vertex matching cut. The photons were detected in either the IC or 
-the CLAS electromagnetic calorimeter. All the signals within IC fiducial region 
+photon were detected in the final state.
+Electrons were identified as negatively charged tracks reconstructed in drift chambers with an appropriate energy deposition in the electromagnetic calorimeters (EC) and a proper
+light yield in the Cherenkov counters. The protons were identified from positively charged tracks by 
+timing analysis using the time-of-flight measured by the scintillator counters. 
+In addition, it was required that both the electron and the proton in the event originated from the same vertex at the target within CLAS tracking vertex resolution.
+The photons were detected in either the IC or
+the CLAS electromagnetic calorimeters. All the clusters within the IC fiducial region 
 were assumed to be photons, while a timing cut is used to clean the EC photons 
 from neutrons. Note that even though the DVCS reaction has only one real photon 
-in the final state, events with more than one good photon are not discarded at 
-this stage. It was observed by the DVCS exclusivity cuts, discussed below, that 
-most of these photons are soft ones produced in random coincidence. In the 
-following selection stage, the most energetic photon is considered as the DVCS 
-photon candidate (see \cite{Hattawy:thesis} for additional details on the 
-particles identification).
+in the final state, events with more than one photon were not discarded at 
+this stage.
+As will be discussed below, the DVCS exclusivity cuts allow identification of the correct photon in the event, discarding accidental, mostly soft photons.
+In the following selection stage, the most energetic photon is considered as the DVCS
+photon candidate (see \cite{Hattawy:thesis} for additional details on the particles identification).
 
 Further requirements were applied to clean the identified initial set of 
-incoherent DVCS events from backgrounds and other channels. Events were 
-selected with $Q^{2}$ greater the 1 GeV$^2$ to ensure that the interaction 
-occurs at the partonic level and the applicability of the factorization on the 
-DVCS handbag diagram, $\gamma^{*}p$ invariant mass (W) greater than 2 GeV to 
-avoid the nucleon region of excitation to resonances, and the transferred 
-momentum squared to the recoil proton has to be greater than a
-minimum value defined by the kinematics of the beam and the scattered electron 
-($-t~>~-t_{min}$). Then, the exclusivity of the incoherent DVCS events was 
+incoherent DVCS events from accidental and physics background events. First, events were 
+selected with Q$^{2}$ greater the 1 GeV$^2$ to ensure the applicability of the 
+DVCS handbag diagram, and with $\gamma^{*}p$ invariant mass (W$=(q+p)^2$) greater than 2 GeV to 
+avoid the nucleon resonance region. The transferred momentum squared to the recoil proton was required to be greater than a
+minimum allowed value at given Q$^2$ and W ($t~>~t_{min}$). Then, the exclusivity of the incoherent DVCS events was 
 ensured by imposing constraints on the kinematical variables resulting from 
@@
 ($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) planes, the missing energy, mass, and 
-transverse momentum of the $e'\gamma$ and $e'p'\gamma$ system, the missing mass 
+transverse momentum of the $e'\gamma$ and $e'p'\gamma$ systems, the missing mass 
 squared of the $e'p'$ system, and the angle $\theta$ between the measured 
@@
 %background
-In spite of our selection requirements, two main backgrounds were observed to 
-contaminate our incoherent DVCS sample; accidental coincidences and exclusive 
-$\pi^0$ production. For the accidental events, i.e., $e'p'\gamma$ collection 
-with particles originated from different events, their contribution of 6.5\% 
+The two main backgrounds that contribute to the event sample after the exclusivity cuts are  
+events due to accidental coincidences and exclusive $\pi^0$ production where one of photons from $\pi^0$ decay escape the detection. For the accidental events, i.e., $e'p'\gamma$ collection 
+with particles originated from different electron scattering events, their contribution of 6.5\% 
 was evaluated by selecting events passing all our cuts but originating from 
-different vertices. Regarding the $\pi^0$ contamination, i.e., $ep\rightarrow 
-e'p'\pi^0$ events where one of the two photons of the $\pi^0$ decay is produced 
-below the energy threshold or outside the detection acceptance, we evaluated 
-this contribution by using data and simulation. From the simulation, we 
-calculated the ratio ($R$) between the number of $\pi^0$ events where the two 
-photons are detected and those that would be mistaken for DVCS ($R = 
-N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$). Then in each kinematical bin and for 
+different vertices. The $\pi^0$ contamination 
+%, i.e., $ep\rightarrow e'p'\pi^0$ events where one of the two photons of the $\pi^0$ decay is produced below the energy threshold or outside the detection acceptance, we
+was estimated 
+%this contribution by 
+using the data and simulation. From simulation, we 
+calculated the ratio ($R$) of the number of $\pi^0$ events that are identified as $ep\rightarrow e'p'\gamma$ events after our selection cuts to the number of identified $\pi^0$ events, $R = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$.
+Then in each kinematical bin and for
 each beam-helicity state, the $\pi^0$-subtracted experimental DVCS events is 
@@
 %asymmetries
-It is convenient to use the beam-spin asymmetry as a DVCS observable because  
-the cross sections luminosity normalization and detector efficiencies cancel 
-out in the asymmetry ratio.  Experimentally, $A_{LU}$ can be simplified in 
-terms of the reaction yield in each beam-helicity state ($N^{\pm}$) as
+%It is convenient to use the beam-spin asymmetry as a DVCS observable because  the cross sections luminosity normalization and detector efficiencies cancel out in the asymmetry ratio.  
+Experimentally, $A_{LU}$ 
+%can be simplified in terms of the reaction yield in each beam-helicity state ($N^{\pm}$) 
+is defined as
 \begin{equation}
@@
 \end{equation}
-where $P_{B}$ is the longitudinal beam polarization.
+where $N^{+}$ and $N^{-}$ are the number of DVCS events for positive and negative  beam-helicity state, and $P_{B}$ is the longitudinal beam polarization.
 
-Following the model guidance of \cite{Guidal:2013rya}, the GPD $H$ dominants 
-the other three GPDs within the accessible phase-phase of using the 6 GeV 
-electron beam from CEBAF and CLAS spectrometer. Therefore, measuring $A_{LU}$ 
-gives access to the real and imaginary part of the CFF $\mathcal{H}$ through 
-the parameters $a_0$, $a_1$, and $a_2$ of equation \ref{eq:alu-simp}.  
-Moreover, the free proton $A_{LU}$ measurements, \cite{Girod:2007aa}, have 
-shown that the $cos(2\phi)$ term, which is corresponding to the pure DVCS 
-amplitude, is suppressed and compatible with zero.
+In the kinematical domain of our experiment, the dominant contribution to the beam-spin asymmetry comes from GPD H \cite{Guidal:2013rya} and
+%Following the model guidance of \cite{Guidal:2013rya}, the GPD $H$ dominants the other three GPDs within the accessible phase-phase of using the 6 GeV electron beam from CEBAF and CLAS spectrometer.
+Therefore,
+therefore $\phi$ dependence of $A_{LU}$ gives access to the real and imaginary part of the CFF $\mathcal{H}$ through 
+the parameters $a_0$, $a_1$, and $a_2$ of equation \ref{eq:alu-simp}. The studies of  
+the free proton $A_{LU}$ measurements, \cite{Girod:2007aa}, have 
+shown that the the pure DVCS contribution, $cos(2\phi)$ term ($a_2$), is suppressed and compatible with zero.
 
@@
 FIG.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
-$\phi$ in bins in $Q^{2}$, $x_{B}$, and $t$. The curves on the plots are fits 
+$\phi$ in bins of $Q^{2}$, $x_{B}$, and $t$. The curves on the plots are fits 
 of the approximated form $\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$. The 
@@
 the choice of the DVCS exclusivity cuts (6\%) and the large binning size (7\%).  
-However, added quadratically, these uncertainties sum up to about 10\%, which 
-always remains significantly smaller than the statistical errors.
+Added quadratically, these uncertainties sum up to less than 10\% for all data points and are significantly smaller than the statistical errors.
 
@@
 considers off-shell effects. The calculations are carried out at slightly 
-different kinematics than our data but still provide some guidance. The 
+different kinematics than our data but still provide important guidance. The 
 experimental results appear to have smaller asymmetries than the calculations.  
@@
 account in the model, such as long-range interactions.
+On the graph for $t$ dependence we show previous measurements by  the HERMES collaboration  \cite{Airapetian} using inclusive final state, ($e^\prime\gamma$).
+Due to large experimental uncertainties of HERMES points, the only conclusion is that the two measurements do not disagree.
 
@@
 
-The $A_{LU}$ ratios show a 20\%-40\% suppression in the bound protons compared 
-to the free protons. These measurements disagree with the enhancement predicted 
-by the on-shell calculations that use the medium modified GPDs as caluclated 
-from the quark-meson coupling model \cite{Guzey:2008fe}. The off-shell 
-calculations overshoot the data indicating a trend \cite{simonetta_2}. In
-particular, the anti-shadowing region seems to be absent in terms of the 
-$A_{LU}$ ratio, while it was predicted by the calculation. Within the given 
-uncertainties, our measured ratios are compatible with the previous measured 
+The $A_{LU}$ ratios show a 20\%-40\% lower asymmetries for a bound proton compared 
+to the free proton.
+The measurements disagree with the off-shell \cite{simonetta_2} and the on-shell calculations that use the medium modified GPDs as calculated from the quark-meson coupling model \cite{Guzey:2008fe}.
+%the enhancement predicted by the on-shell calculations that use the medium modified GPDs as calculated from the quark-meson coupling model \cite{Guzey:2008fe}.
+The off-shell calculations overshoot the data indicating a trend \cite{simonetta_2}.
+In particular, the anti-shadowing region where off-shell model expects enhancement of the ratio experiment shows a sharp drop. Within the given 
+uncertainties, our measured ratios are compatible with the previously measured 
 single point from HERMES \cite{Airapetian}.
 
-These data, while limited in statistics, proved the experimental feasibility of 
-measuring DVCS of bound-nucleons in addition to the EMC effect within the GPDs 
-framework and led the way to the approval of a next generation nuclear 
-measurements \cite{Armstrong:2017wfw}. The future measurements will be carried 
-out using the new CLAS12 spectrometer and the upgraded CEBAF 12 GeV electron 
-beam at an electron-nucleon luminosity of 10$^{35}$cm$^{-2}$s$^{-1}$. The wider 
-accessible phase-space and the higher luminosity will enable us to study 
-nuclear effects and their manifestations on GPDs including the effect of final 
-state interactions.
+%These data, while limited in statistics, proved the experimental feasibility of measuring DVCS of bound-nucleons in addition to the EMC effect within the GPDs framework and led the way to the approval of a next generation nuclear measurements \cite{Armstrong:2017wfw}.
+The future measurements will be carried out using the new CLAS12 spectrometer and the upgraded CEBAF 12 GeV electron beam at an electron-nucleon luminosity of 10$^{35}$cm$^{-2}$s$^{-1}$.
+The wider accessible phase-space and the higher luminosity will enable us to study nuclear effects and their manifestations on GPDs including the effect of final state interactions.
 
 %conclusion
-In summary, we have presented the first exclusive beam-spin asymmetries 
-associated with incoherent DVCS off $^4$He using an upgraded setup of CLAS 
-spectrometer at Jefferson Lab. Our results were compared to some model 
+In summary, we have presented the first exclusive beam-spin asymmetry measurements 
+associated with incoherent DVCS off $^4$He using an upgraded setup of the CLAS 
+spectrometer at Jefferson Lab. Our results were compared to model 
 calculations based on different assumptions of the nuclear medium effects at 
-the partonic level and allowed us to draw some conclusions. The bound-proton 
+the partonic level.
+% and allowed us to draw some conclusions. 
+The bound-proton 
 beam-spin asymmetries indicate a suppression compared to the free proton 
 results measured in similar phase-space. While the data are limited in 
-statistics, they opened new insights for extensive future measurements.
+statistics, they opened new avenue for future measurements. This study lead to the approval of a next generation nuclear 
+DVCS measurements \cite{Armstrong:2017wfw} using the new CLAS12 spectrometer and the upgraded CEBAF 12 GeV electron 
+beam.
 
@@
 
-\bibitem{Airapetian}
-A. Airapetian {\it et al.} [HERMES Collaboration],
-Phys.\ Rev.\ Lett. {\bf 87}, 182001 (2001);
-JHEP {\bf 1207}, 032 (2012);
-JHEP {\bf 1006}, 019 (2010);
-JHEP {\bf 0806}, 066 (2008);
-Phys.\ Lett.\ B {\bf 704}, 15 (2011);
-Phys.\ Rev.\  D {\bf 75}, 011103 (2007);
-JHEP {\bf 0911}, 083 (2009);
-Phys.\ Rev.\ C {\bf 81}, 035202 (2010);
-JHEP {\bf 1210}, 042 (2012).
+%\cite{Airapetian:2001yk}
+\bibitem{Airapetian:2001yk} A.~Airapetian {\it et al.} [HERMES Collaboration],
+%``Measurement of the beam spin azimuthal asymmetry associated with deeply 
+   %virtual Compton scattering,''
+ Phys.\ Rev.\ Lett.\  {\bf 87}, 182001 (2001)
+%doi:10.1103/PhysRevLett.87.182001
+%[hep-ex/0106068].
+
+%\cite{Airapetian:2006zr}
+\bibitem{Airapetian:2006zr} A.~Airapetian {\it et al.} [HERMES Collaboration],
+ %``The Beam-charge azimuthal asymmetry and deeply virtual compton 
+   %scattering,''
+Phys.\ Rev.\ D {\bf 75}, 011103 (2007)
+%doi:10.1103/PhysRevD.75.011103
+%[hep-ex/0605108].
+
+%\bibitem{Airapetian}
+%A. Airapetian {\it et al.} [HERMES Collaboration],
+%Phys.\ Rev.\ Lett. {\bf 87}, 182001 (2001);
+%JHEP {\bf 1207}, 032 (2012);
+%JHEP {\bf 1006}, 019 (2010);
+%JHEP {\bf 0806}, 066 (2008);
+%Phys.\ Lett.\ B {\bf 704}, 15 (2011);
+%Phys.\ Rev.\  D {\bf 75}, 011103 (2007);
+%JHEP {\bf 0911}, 083 (2009);
+%Phys.\ Rev.\ C {\bf 81}, 035202 (2010);
+%JHEP {\bf 1210}, 042 (2012).
 
@@
 
-\bibitem{JSeely}
-J. Seely {\it et al.}, Phys.\ Rev.\ Lett.\ {\bf 103}, 202301 (2009).
+\bibitem{Guidal:2013rya} M.~Guidal, H.~Moutarde, and M.~Vanderhaeghen,
+Rep.\ Prog.\ Phys.\  {\bf 76}, 066202 (2013).
 
@@
  Phys.\ Rev.\ D {\bf 95}, no. 1, 011501 (2017)
+
+%\cite{Airapetian:2009cga}
+\bibitem{Airapetian:2009cga} A.~Airapetian {\it et al.} [HERMES Collaboration],
+     %``Nuclear-mass dependence of azimuthal beam-helicity and beam-charge 
+   %asymmetries in deeply virtual Compton scattering,''
+Phys.\ Rev.\ C {\bf 81}, 035202 (2010)
+%doi:10.1103/PhysRevC.81.035202
+%[arXiv:0911.0091 [hep-ex]].
 
@@
 
+\bibitem{JSeely}
+J. Seely {\it et al.}, Phys.\ Rev.\ Lett.\ {\bf 103}, 202301 (2009).
+
 \bibitem{Freund_Collins}
@@
 Nucl.\ Phys.\ B {\bf 629}, 323 (2002)
-
-\bibitem{Guidal:2013rya} M.~Guidal, H.~Moutarde, and M.~Vanderhaeghen,
-Rep.\ Prog.\ Phys.\  {\bf 76}, 066202 (2013).
 

### 2018-02-19 eg6-letters/incoherent/incoherent_prl.tex
edit figure 5 by including the coherent points

@@
    systematic uncertainties. On the middle plot: the curves are theoretical 
-   calculations from \cite{simonetta_2}. On the bottom: the green circles are 
-   the HERMES $-A_{LU}$ (positron beam was used) inclusive measurements 
-   \cite{Airapetian}, the curves represent theoretical calculations from 
+   calculations from \cite{simonetta_2}. On the bottom: the solid (empty) green 
+   circles are the HERMES $-A_{LU}$ (positron beam was used) inclusive 
+measurements for the incoherent (coherent) enriched region 
+\cite{Airapetian:2009cga}, the curves represent theoretical calculations from 
 \cite{simonetta_2}.  } \label{fig:alu90}
@@
    (bottom). The black squares are from this work, the green circles are the 
-   HERMES inclusive measurement \cite{Airapetian}. The blue and red curves are 
-   results of off-shell calculations \cite{simonetta_2}. The solid and dashed 
+HERMES inclusive measurement \cite{Airapetian:2009cga}. The blue and red curves 
+are results of off-shell calculations \cite{simonetta_2}. The solid and dashed 
 black curves are from on-shell calculations \cite{Guzey:2008fe}.} 

### 2018-02-20 eg6-letters/incoherent/incoherent_prl.tex
update the abstract from stepan

@@
 \begin{abstract}
-We report on the beam-spin asymmetries associated with incoherent deeply 
-   virtual Compton scattering off $^4$He in the valence quark region. The data 
-   were accumulated using a 6 GeV longitudinally-polarized electron beam 
-   incident on a pressurized $^4$He gaseous target placed in front of the CLAS 
-   spectrometer in Hall-B at the Thomas Jefferson National Accelerator 
-   Facility.  The baseline detection sub-systems of CLAS detected the scattered 
-   electrons and the recoil protons, while the final-state real photons are 
-   detected by a supplementary electromagnetic calorimeter at very forward 
-   angles. The measured beam-spin asymmetries on bound-protons exhibit a 
-   suppression compared to those on free proton, indicating possible medium 
-   modifications on the nucleon's quark distributions and opening new 
-   opportunities to explore the origin of the EMC effect within the framework 
-   of the generalized parton distributions.
+%We report on the beam-spin asymmetries associated with incoherent deeply 
+%virtual Compton scattering off $^4$He in the valence quark region. The data 
+%were accumulated using a 6 GeV longitudinally-polarized electron beam incident 
+%on a pressurized $^4$He gaseous target placed in front of the CLAS 
+%spectrometer in Hall-B at the Thomas Jefferson National Accelerator Facility.  
+%The baseline detection sub-systems of CLAS detected the scattered electrons 
+%and the recoil protons, while the final-state real photons are detected by a 
+%supplementary electromagnetic calorimeter at very forward angles. The measured 
+%beam-spin asymmetries on bound-protons exhibit a suppression compared to those 
+%on free proton, indicating possible medium modifications on the nucleon's 
+%quark distributions and opening new opportunities to explore the origin of the 
+%EMC effect within the framework of the generalized parton distributions.
+
+ We report the first beam spin asymmetry (BSA) measurements in incoherent 
+ deeply virtual Compton scattering (DVCS) off $^4$He using the fully exclusive 
+ final state. The data were accumulated using a 6 GeV longitudinally polarized 
+ electron beam incident on a pressurized $^4$He gaseous target placed in front 
+ of the CLAS spectrometer in Hall-B at the Thomas Jefferson National 
+ Accelerator Facility. The azimuthal angular ($\phi$) dependence of BSA is 
+ studied in wide range of the virtual photon and the scattered proton 
+ kinematics. The Q$^2$, $x_B$, and $t$ dependencies of BSA on bound nucleon has 
+ been compared with one on free proton. In the whole kinematical region of our 
+ measurements BSA on bound nucleon is by about $20\%$ to $30\%$ smaller, 
+ indicating possible medium modification on the nucleon's partonic structure.  
+ This measurement opens a new opportunity to explore the origin of the EMC 
+ effect within the framework of the generalized parton distributions.
 

### 2018-03-09 eg6-letters/incoherent/incoherent_prl.tex
Corrections to the incoherent letter

--- 2018-02-19 eg6-letters/incoherent/incoherent_prl.tex
@@
 
-%
 \begin{document}
@@
 
-\title{First exclusive DVCS measurement off bound nucleon in $^4$He}
-%\title{Revealing the Bound Nucleon 3D Partonic Structure through Incoherent Deeply Virtual Compton Scattering off $^4$He}
+\title{First exclusive Deeply Virtual Compton Scattering measurement off bound nucleon in $^4$He}
 
@@
 
-%
 \date{\today}
 \begin{abstract}
-We report on the beam-spin asymmetries associated with incoherent deeply 
-   virtual Compton scattering off $^4$He in the valence quark region. The data 
-   were accumulated using a 6 GeV longitudinally-polarized electron beam 
-   incident on a pressurized $^4$He gaseous target placed in front of the CLAS 
-   spectrometer in Hall-B at the Thomas Jefferson National Accelerator 
-   Facility.  The baseline detection sub-systems of CLAS detected the scattered 
-   electrons and the recoil protons, while the final-state real photons are 
-   detected by a supplementary electromagnetic calorimeter at very forward 
-   angles. The measured beam-spin asymmetries on bound-protons exhibit a 
-   suppression compared to those on free proton, indicating possible medium 
-   modifications on the nucleon's quark distributions and opening new 
-   opportunities to explore the origin of the EMC effect within the framework 
-   of the generalized parton distributions.
+ We report the first beam spin asymmetry (BSA) measurements in incoherent 
+ deeply virtual Compton scattering (DVCS) off $^4$He using the fully exclusive 
+ final state. The data were accumulated using a 6 GeV longitudinally polarized 
+ electron beam incident on a pressurized $^4$He gaseous target placed in front 
+ of the CLAS spectrometer in Hall-B at the Thomas Jefferson National 
+ Accelerator Facility. The azimuthal angular ($\phi$) dependence of the BSA is 
+ studied in a wide range of virtual photon and scattered proton 
+ kinematics. The Q$^2$, $x_B$, and $t$ dependencies of the BSA on the bound nucleon has 
+ been compared with the one on the free proton. In the whole kinematical region of our 
+ measurements, the BSA on the bound nucleon is smaller by about $20\%$ to $30\%$, 
+ indicating possible medium modification on the nucleon's partonic structure.  
+ This measurement opens a new opportunity to explore the origin of the EMC 
+ effect within the framework of the generalized parton distributions.
 
@@
 Electromagnetic probes have played a major role in advancing our knowledge 
-about the structure of nucleons, which are the origin of almost all the
-Universe's visible matter. While elastic lepton-nucleon measurements have 
+about the structure of the nucleon, which is at the origin of almost all the
+universe's visible matter. While elastic lepton-nucleon measurements have 
 taught us about the spatial charge and magnetization distributions 
-\cite{Hofstadter:1955ae,Perdrisat:2006hj}, deep-inelastic scattering (DIS) 
+\cite{Hofstadter:1955ae,Perdrisat:2006hj}, deep-inelastic scattering 
 experiments have uncovered the features of momentum sharing between the 
 constituents partons, i.e., quarks and gluons \cite{Dokshitzer:1977sg,pdg}.  
-With nuclear targets, the DIS measurements have revealed the fact that the 
-distribution of quarks in a fast moving nucleus is not a simple convolution of 
+With nuclear targets, these measurements have revealed the fact that the 
+distribution of quarks in a nucleus is not a simple convolution of 
 their distributions within nucleons, an observation known as the ``EMC 
-effect''\cite{EMC_first} (for reviews on the extensive investigations, see  
+effect''\cite{EMC_first} (for reviews on the topic, see  
 \cite{EMC_CERN,EMC_SLAC,EMC_HERMES,EMC_JLab,EMC_John,EMC_mdeium_1,EMC_medium_2}).
 
-A wealth of information on the structure of matter lies in the correlations 
+A wealth of information on the structure of hadrons lies in the correlations 
 between the momentum and spatial degrees of freedom of the partons. These 
@@
 Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}
-involving several accelerator facilities such as Jefferson Lab, HERA and  
+involving several accelerator facilities such as Jefferson Lab, DESY and  
 CERN. Combining these measurements has enabled the first extractions of GPDs 
@@
 the incoherent DVCS channel \cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}. The 
-$^{4}$He nucleus is an ideal experimental target for these purposes as it has 
-only one chiral-even GPD that parametrizes its partonic structure, is 
-characterized by a strong binding energy, and has a relatively high nuclear 
-core density. The inclusive scattering off $^{4}$He has shown a large EMC 
-effect \cite{JSeely}, making this nucleus a golden target for investigating the 
+$^{4}$He nucleus is an ideal experimental target for these purposes as it is 
+characterized by a strong binding energy, a relatively high nuclear 
+core density, and a large EMC effect~\cite{JSeely}. However, it remains simple 
+enough that exact calculation of its structure 
+can be performed, making this nucleus the perfect target for our investigation of the 
 medium modifications of the nucleon's partonic structure.
@@
 
-In this Letter, we present the first exclusive measurement of the beam-spin asymmetry in deeply virtual electroproduction of a real photon off bound-proton in $^{4}$He.
-Experimentally we measure squared sum of the Bethe-Heitler (BH) and DVCS amplitudes, with BH process where real photon is emitted by the incident or the scattered electron dominating the cross section in our kinematics.
-%While the experimentally measured cross section amplitude is the sum of the DVCS, BH (i.e., the final state real photon is emitted by the incident or the scattered electron), and their interference, 
-The beam-spin asymmetry, in other hand, is sensitive to the DVCS amplitude and the interference term that contain information on the GPDs. 
-The beam-spin asymmetry observable with a longitudinally polarized electron beam (L) and unpolarized target (U) is defined as:
+In this Letter, we present the first exclusive measurement of the beam-spin asymmetry 
+in deeply virtual electroproduction of a real photon off bound-proton in $^{4}$He. 
+Experimentally, we measure the squared sum of the Bethe-Heitler (BH) and the DVCS 
+amplitudes, with the BH process the process where the real photon is emitted by 
+the incident or the scattered electron rather than the nucleon. The beam-spin 
+asymmetry arises from the interference of these two terms and is directly 
+sensitive to the DVCS amplitude that contain the information on the GPDs. 
+Using a longitudinally polarized electron beam (L) and an unpolarized target 
+(U), this beam-spin asymmetry observable is defined as:
 \begin{equation}
@@
 \end{equation}
-where $F_1$ and $F_2$ are the Dirac and Pauli form factors with $x_B$ as the 
+where $F_1$ and $F_2$ are the Dirac and Pauli form factors and $x_B$ the 
 Bjorken scaling variable. The real and the imaginary parts of the CFF 
@@
 \end{align}
-with $\mathcal{P}$ is the Cauchy principal value integral and $C^{+}$ is a 
-coefficient function defined as $(1/(x-\xi) + 1/(x+\xi))$ with $\xi$ being 
+with $\mathcal{P}$ the Cauchy principal value integral and $C^{+}$ a 
+coefficient function defined as $(1/(x-\xi) + 1/(x+\xi))$, there $\xi$ is the 
+skewing factor and can be
 related to $x_B$ by $\xi\approx {{x_B}\over{2-x_B}}$. Similar expressions apply 
@@
 $^4$He target centered at 64~cm upstream of the CEBAF Large Acceptance 
-Spectrometer (CLAS) coordinate center. For similar DVCS experiments on free-proton target
-\cite{Girod:2007aa,Jo:2015ema}, the CLAS baseline design \cite{Mecking:2003zu} 
+Spectrometer (CLAS) coordinate center. For DVCS experiments, the CLAS baseline 
+design \cite{Mecking:2003zu} 
 is supplemented with an inner calorimeter (IC) and a solenoid magnet. The IC extends 
 the photon detection acceptance of CLAS to very small polar angles, 4$^{\circ}$. 
-%As the coherent DVCS off $^4$He, where the nucleus remain intact, was one of the proposed measurements of our experiment and since CLAS cannot detect such low-energy recoil nuclei, we built a small radial time projection chamber (RTPC) around the target cell.
-(See~\cite{Dupre:2017upj} for a detailed description of the RTPC and its performances and \cite{Hattawy:2017woc} for the coherent DVCS measurements).
-In this setup,
-The 5-Tesla solenoid magnet in the center of which target was located 
-%(that surrounds the target and the RTPC) enabled the detection of the low-energy charged ions in the RTPC and 
-prevented the high-rate low-energy M{\o}ller electrons from reaching the CLAS drift chambers by guiding them electrons insde a tungsten shield placed around the beam line.
+The 5-Tesla solenoid magnet in the center of which the target was located 
+prevented the high-rate low-energy M{\o}ller electrons from reaching the CLAS 
+drift chambers by guiding these electrons inside a tungsten shield placed around the beam line.
 
@@
 Incoherent DVCS events were selected if an electron, a proton, and at least one 
-photon were detected in the final state.
-Electrons were identified as negatively charged tracks reconstructed in drift chambers with an appropriate energy deposition in the electromagnetic calorimeters (EC) and a proper
-light yield in the Cherenkov counters. The protons were identified from positively charged tracks by 
+photon were detected in the final state. Electrons were identified as negatively 
+charged tracks reconstructed in drift chambers with an appropriate energy 
+deposition in the electromagnetic calorimeter (EC) and a proper light yield in 
+the Cherenkov counters. The protons were identified from positively charged tracks by 
 timing analysis using the time-of-flight measured by the scintillator counters. 
-In addition, it was required that both the electron and the proton in the event originated from the same vertex at the target within CLAS tracking vertex resolution.
-The photons were detected in either the IC or
-the CLAS electromagnetic calorimeters. All the clusters within the IC fiducial region 
+In addition, it was required that both the electron and the proton in the event 
+originated from the same vertex at the target within CLAS tracking vertex 
+resolution. The photons were detected in either the IC or 
+the CLAS electromagnetic calorimeter. All the clusters within the IC fiducial region 
 were assumed to be photons, while a timing cut is used to clean the EC photons 
@@
 in the final state, events with more than one photon were not discarded at 
-this stage.
-As will be discussed below, the DVCS exclusivity cuts allow identification of the correct photon in the event, discarding accidental, mostly soft photons.
-In the following selection stage, the most energetic photon is considered as the DVCS
-photon candidate (see \cite{Hattawy:thesis} for additional details on the particles identification).
+this stage. These are mostly soft photons from accidental coincidence which, 
+as will be discussed below, the DVCS exclusivity cuts eliminate easily. In the 
+following selection stage, the most energetic photon is considered as the DVCS 
+photon candidate (see \cite{Hattawy:thesis} for additional details on the 
+particles identification).
 
@@
 The two main backgrounds that contribute to the event sample after the exclusivity cuts are  
-events due to accidental coincidences and exclusive $\pi^0$ production where one of photons from $\pi^0$ decay escape the detection. For the accidental events, i.e., $e'p'\gamma$ collection 
-with particles originated from different electron scattering events, their contribution of 6.5\% 
-was evaluated by selecting events passing all our cuts but originating from 
-different vertices. The $\pi^0$ contamination 
-%, i.e., $ep\rightarrow e'p'\pi^0$ events where one of the two photons of the $\pi^0$ decay is produced below the energy threshold or outside the detection acceptance, we
-was estimated 
-%this contribution by 
-using the data and simulation. From simulation, we 
-calculated the ratio ($R$) of the number of $\pi^0$ events that are identified as $ep\rightarrow e'p'\gamma$ events after our selection cuts to the number of identified $\pi^0$ events, $R = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$.
-Then in each kinematical bin and for
+events due to accidental coincidences and exclusive $\pi^0$ production where one of the photons 
+from the $\pi^0$ decay escapes the detection. For the accidental events, i.e., $e'p'\gamma$ collection 
+with particles originated from different electron scattering events, their contribution 
+was evaluated to be of 6.5\% by selecting events passing all our cuts but originating from 
+different vertices. The $\pi^0$ contamination was estimated using the data and 
+simulation. From simulation, we calculated the ratio ($R$) of the number of $\pi^0$ 
+events that are identified as $ep\rightarrow e'p'\gamma$ events after our selection 
+cuts to the number of identified $\pi^0$ events, 
+$R = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$. Then in each kinematical bin and for 
 each beam-helicity state, the $\pi^0$-subtracted experimental DVCS events is 
@@
 $N^{ep\rightarrow e'p'\pi^0}_{exp}$ is the experimentally identified 
-$ep\rightarrow e'p'\pi^0$ with the two photons were detected. Depending on the 
-kinematics, we found contaminations of 8\%-10\%.
+$ep\rightarrow e'p'\pi^0$ with the two photons detected. Depending on the 
+kinematics, we found this contamination to be of 8\% to 10\%.
 
 %asymmetries
-%It is convenient to use the beam-spin asymmetry as a DVCS observable because  the cross sections luminosity normalization and detector efficiencies cancel out in the asymmetry ratio.  
-Experimentally, $A_{LU}$ 
-%can be simplified in terms of the reaction yield in each beam-helicity state ($N^{\pm}$) 
-is defined as
+Experimentally, $A_{LU}$ is defined as
 \begin{equation}
@@
 \end{equation}
-where $N^{+}$ and $N^{-}$ are the number of DVCS events for positive and negative  beam-helicity state, and $P_{B}$ is the longitudinal beam polarization.
+where $N^{+}$ and $N^{-}$ are the number of DVCS events for positive and negative 
+beam-helicity state, and $P_{B}$ is the longitudinal beam polarization.
 
-In the kinematical domain of our experiment, the dominant contribution to the beam-spin asymmetry comes from GPD H \cite{Guidal:2013rya} and
-%Following the model guidance of \cite{Guidal:2013rya}, the GPD $H$ dominants the other three GPDs within the accessible phase-phase of using the 6 GeV electron beam from CEBAF and CLAS spectrometer.
-Therefore,
-therefore $\phi$ dependence of $A_{LU}$ gives access to the real and imaginary part of the CFF $\mathcal{H}$ through 
-the parameters $a_0$, $a_1$, and $a_2$ of equation \ref{eq:alu-simp}. The studies of  
+In the kinematical domain of our experiment, the dominant contribution to the 
+beam-spin asymmetry comes from the GPD $H$ \cite{Guidal:2013rya} as the $\phi$ 
+dependence of $A_{LU}$ gives access to the real and imaginary part of the CFF 
+$\mathcal{H}$ through the parameters $a_0$, $a_1$, and $a_2$ of equation \ref{eq:alu-simp}. The studies of  
 the free proton $A_{LU}$ measurements, \cite{Girod:2007aa}, have 
 shown that the the pure DVCS contribution, $cos(2\phi)$ term ($a_2$), is suppressed and compatible with zero.  
+{\bf Raphael: This paragraph is very confusing, is it true that a1 and a2 are 
+dominated by H? Do we have equivalents of eq. 3 for those? I actually did not find
+it in ref 31, which we are referring and we are also not using the same definition
+of Im(H)...}
 
 Due to limited statistics, the data were binned two-dimensionally into 36 bins.  
-That is, four statistically-equivalent bins in each of the kinematical 
-variables ($Q^{2}$, $x_{B}$, $t$) were constructed one at a time. Then, each 
+That is, four statistically-equivalent bins in one of the kinematical 
+variable of interest -- $Q^{2}$, $x_{B}$ or $t$ -- were constructed, then each 
 bin is divided into nine bins in the azimuthal angle ($\phi$).  
@@
 $\phi$ in bins of $Q^{2}$, $x_{B}$, and $t$. The curves on the plots are fits 
-of the approximated form $\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$. The 
-study of systematic uncertainties showed that the main contributions come from 
-the choice of the DVCS exclusivity cuts (6\%) and the large binning size (7\%).  
-Added quadratically, these uncertainties sum up to less than 10\% for all data points and are significantly smaller than the statistical errors.
+of the form $\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$. The main contributions 
+to systematic uncertainties on these fits are from the choice of the DVCS 
+exclusivity cuts (6\%) and the large binning size (7\%). Added quadratically, 
+these uncertainties sum up to less than 10\% for all data points and remain 
+significantly smaller than the statistical errors.
 
@@
    uncertainties. The gray bands represent the systematic uncertainties, 
-   including the normalisation uncertainties. The black curves are the results 
+   including the normalization uncertainties. The black curves are the results 
    of our fits with the form $\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$.}
@@
 These differences may arise from nuclear effects which are not taken into 
-account in the model, such as long-range interactions.
-On the graph for $t$ dependence we show previous measurements by  the HERMES collaboration  \cite{Airapetian} using inclusive final state, ($e^\prime\gamma$).
-Due to large experimental uncertainties of HERMES points, the only conclusion is that the two measurements do not disagree.
+account in the model, such as long-range interactions. On the graph for $-t$ 
+dependence, we show previous measurements by the HERMES collaboration
+\cite{Airapetian:2009cga} using inclusive final state, ($e^\prime\gamma$). Due 
+to large experimental uncertainties of HERMES points, the two measurements 
+do not disagree, but we can also see that their high $-t$ results were 
+smaller than expected by models.
 
@@
 The $A_{LU}$ ratios show a 20\%-40\% lower asymmetries for a bound proton compared 
-to the free proton.
-The measurements disagree with the off-shell \cite{simonetta_2} and the on-shell calculations that use the medium modified GPDs as calculated from the quark-meson coupling model \cite{Guzey:2008fe}.
-%the enhancement predicted by the on-shell calculations that use the medium modified GPDs as calculated from the quark-meson coupling model \cite{Guzey:2008fe}.
-The off-shell calculations overshoot the data indicating a trend \cite{simonetta_2}.
-In particular, the anti-shadowing region where off-shell model expects enhancement of the ratio experiment shows a sharp drop. Within the given 
-uncertainties, our measured ratios are compatible with the previously measured 
-single point from HERMES \cite{Airapetian}.
-
-%These data, while limited in statistics, proved the experimental feasibility of measuring DVCS of bound-nucleons in addition to the EMC effect within the GPDs framework and led the way to the approval of a next generation nuclear measurements \cite{Armstrong:2017wfw}.
-The future measurements will be carried out using the new CLAS12 spectrometer and the upgraded CEBAF 12 GeV electron beam at an electron-nucleon luminosity of 10$^{35}$cm$^{-2}$s$^{-1}$.
-The wider accessible phase-space and the higher luminosity will enable us to study nuclear effects and their manifestations on GPDs including the effect of final state interactions.
+to the free proton. The measurements disagree with the off-shell \cite{simonetta_2} 
+and the on-shell calculations that use the medium modified GPDs as calculated from 
+the quark-meson coupling model \cite{Guzey:2008fe}. In particular, at lower $x_B$, 
+where the off-shell model predicts an enhancement of the ratio, our experiment 
+shows a sharp drop. This measurement shows that an important nuclear effect is
+missing from the existing models in order to explain this strong quenching of
+the beam-spin asymmetry.
 
@@
 calculations based on different assumptions of the nuclear medium effects at 
-the partonic level.
-% and allowed us to draw some conclusions. 
-The bound-proton 
-beam-spin asymmetries indicate a suppression compared to the free proton 
-results measured in similar phase-space. While the data are limited in 
-statistics, they opened new avenue for future measurements. This study lead to the approval of a next generation nuclear 
-DVCS measurements \cite{Armstrong:2017wfw} using the new CLAS12 spectrometer and the upgraded CEBAF 12 GeV electron 
-beam.
+the partonic level.  The bound-proton 
+beam-spin asymmetries is largely suppressed compared to the free proton 
+results measured in a similar phase-space. This surprising result opens a new avenue 
+for progress in the understanding of the quarks and gluons behavior in the
+nuclear medium.
 

### 2018-03-28 eg6-letters/incoherent/incoherent_prl.tex
cleaning the paper after updating the incoherent ratio plot

@@
 \centering
-\includegraphics[width=6.9cm]{figs/ALU_ratioInc_Q2_shortscenrario.pdf}\\
-\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}\\
-\includegraphics[width=6.9cm]{figs/ALU_ratioInc_t_shortscenrario.pdf}
+%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_Q2_shortscenrario.pdf}\\
+%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}\\
+\includegraphics[width=8.5cm]{figs/ALU_ratioInc_t_shortscenrario.pdf}
 \caption{ The $A_{LU}$ ratio of the bound to the free proton at 
-   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (top), $x_B$ (middle), and $t$ 
-   (bottom). The black squares are from this work, the green circles are the 
-HERMES inclusive measurement \cite{Airapetian:2009cga}. The blue and red curves 
-are results of off-shell calculations \cite{simonetta_2}. The solid and dashed 
-black curves are from on-shell calculations \cite{Guzey:2008fe}.} 
+   $\phi$~=~90$^{\circ}$ as a function of $t$. The black squares are from this 
+   work, the green circles are the HERMES inclusive measurement 
+   \cite{Airapetian:2009cga}. The blue and red curves are results of off-shell 
+   calculations \cite{simonetta_2}. The solid and dashed black curves are from 
+   on-shell calculations \cite{Guzey:2008fe}.} 
    \label{fig:incoh_EMC_ratio_ALU_proton}

### 2018-06-26 eg6-letters/NIM/EG6_RTPC_NIM.tex
Changes for submission of NIM on Arxiv and NIM
Modification asked by reviewer
some cleaning

@@
 \usepackage[displaymath]{lineno}
-\linenumbers
+%\linenumbers
 \usepackage{dblfloatfix}    % To enable figures at the bottom of page
@@
 \begin{figure}[tbp]
-\centering \includegraphics[scale=0.3]{test_clas.png}
+\centering \includegraphics[scale=0.18]{test_clas.png}
 \caption{A three dimensional representation of the baseline CLAS setup. The
@@
 \centering
-\includegraphics[scale=0.70]{GEM_photo.jpg}
+\includegraphics[scale=0.17]{GEM_photo.jpg}
 \caption{Image of a typical GEM foil similar to the one used for our RTPC 
@@
    \centering
-   \includegraphics[scale=0.55]{PADs.png}
+   \includegraphics[scale=0.21]{PADs.png}
    \caption[]{A schematic representation of the readout pads. The 
@@
 
-The first step in the calibration is to fix the maximum drift time ($T_{max}$) that an
+The first step in the calibration is to determine the maximum drift time ($T_{max}$) at which an
 electron can arrive on the detection plane. This value is highly dependent on the gas 
@@
    \centering
-\includegraphics[scale=0.25]{noisy_pad_before_rejection2.png}
-\includegraphics[scale=0.25]{noisy_pad_after_rejection2.png}
+\includegraphics[scale=0.20]{noisy_pad_before_rejection2.png}
+\includegraphics[scale=0.20]{noisy_pad_after_rejection2.png}
 \caption{The ADC vs. T spectrum for an example noisy channel before (top) and 

### 2018-06-26 eg6-letters/incoherent/incoherent_prl.tex
more cleaning

@@
 \begin{equation}
-   A_{LU}^{\sin\phi} \propto \operatorname{Im}( F_1 \mathcal{H}- \frac{t}{4M^2} 
-   F_2 \mathcal{E}+ \frac{x_B}{2}(F_1+F_2)\tilde{\mathcal{H}})
+   a_{0} \propto \operatorname{Im}( F_1 \mathcal{H}- \frac{t}{4M^2} F_2 
+   \mathcal{E}+ \frac{x_B}{2}(F_1+F_2)\tilde{\mathcal{H}})
 \end{equation}
@@
 
-In the kinematical domain of our experiment, the dominant contribution to the 
-beam-spin asymmetry comes from the GPD $H$ \cite{Guidal:2013rya} as the $\phi$ 
-dependence of $A_{LU}$ gives access to the real and imaginary part of the CFF 
-$\mathcal{H}$ through the parameters $a_0$, $a_1$, and $a_2$ of equation \ref{eq:alu-simp}. The studies of  
-the free proton $A_{LU}$ measurements, \cite{Girod:2007aa}, have 
-shown that the the pure DVCS contribution, $cos(2\phi)$ term ($a_2$), is suppressed and compatible with zero.  
-{\bf Raphael: This paragraph is very confusing, is it true that a1 and a2 are 
-dominated by H? Do we have equivalents of eq. 3 for those? I actually did not find
-it in ref 31, which we are referring and we are also not using the same definition
-of Im(H)...}
+In the kinematical phase-space of our experiment, the GPD $H$ dominants the 
+contribution in the beam-spin asymmetry over the other three GPDs. Therefore, 
+the $\phi$ dependence of $A_{LU}$ gives a direct access to the real and 
+imaginary part of the CFF $\mathcal{H}$ through the parameters $a_0$, $a_1$, 
+and $a_2$ of equation \ref{eq:alu-simp}. The studies of  the free proton 
+$A_{LU}$ measurements, \cite{Girod:2007aa}, have shown that the the pure DVCS 
+contribution, $cos(2\phi)$ term ($a_2$), is suppressed and compatible with 
+zero.
+
+%{\bf Raphael: This paragraph is very confusing, is it true that a1 and a2 are 
+%dominated by H? Do we have equivalents of eq. 3 for those? I actually did 
+%notfind it in ref 31, which we are referring and we are also not using the 
+%same definition of Im(H)...}
 

### 2018-06-27 eg6-letters/incoherent/incoherent_prl.tex
more cleaning

@@
  We report the first beam spin asymmetry (BSA) measurements in incoherent 
- deeply virtual Compton scattering (DVCS) off $^4$He using the fully exclusive 
- final state. The data were accumulated using a 6 GeV longitudinally polarized 
- electron beam incident on a pressurized $^4$He gaseous target placed in front 
- of the CLAS spectrometer in Hall-B at the Thomas Jefferson National 
- Accelerator Facility. The azimuthal angular ($\phi$) dependence of the BSA is 
- studied in a wide range of virtual photon and scattered proton 
- kinematics. The Q$^2$, $x_B$, and $t$ dependencies of the BSA on the bound nucleon has 
- been compared with the one on the free proton. In the whole kinematical region of our 
- measurements, the BSA on the bound nucleon is smaller by about $20\%$ to $30\%$, 
- indicating possible medium modification on the nucleon's partonic structure.  
- This measurement opens a new opportunity to explore the origin of the EMC 
- effect within the framework of the generalized parton distributions.
+   deeply virtual Compton scattering (DVCS) off $^4$He using the exclusive 
+   final state. The data were accumulated using a 6 GeV longitudinally 
+   polarized electron beam incident on a pressurized $^4$He gaseous target 
+   placed in front of the CLAS spectrometer in Hall-B at the Thomas Jefferson 
+   National Accelerator Facility. The azimuthal angular ($\phi$) dependence of 
+   the BSA is studied in a wide range of virtual photon and scattered proton 
+   kinematics. The Q$^2$, $x_B$, and $t$ dependencies of the BSA on the bound 
+   nucleon have been compared with the one on the free proton. In the whole 
+   kinematical region of our measurements, the BSA on the bound nucleon is 
+   smaller by about $20\%$ to $30\%$, indicating possible medium modification 
+   on the nucleon's partonic structure.  This measurement opens a new 
+   opportunity to explore the origin of the EMC effect within the framework of 
+   the generalized parton distributions.
 
@@
 
-In this Letter, we present the first exclusive measurement of the beam-spin asymmetry 
-in deeply virtual electroproduction of a real photon off bound-proton in $^{4}$He. 
-Experimentally, we measure the squared sum of the Bethe-Heitler (BH) and the DVCS 
-amplitudes, with the BH process the process where the real photon is emitted by 
-the incident or the scattered electron rather than the nucleon. The beam-spin 
-asymmetry arises from the interference of these two terms and is directly 
-sensitive to the DVCS amplitude that contain the information on the GPDs. 
-Using a longitudinally polarized electron beam (L) and an unpolarized target 
-(U), this beam-spin asymmetry observable is defined as:
+In this Letter, we present the first exclusive measurement of the beam-spin 
+asymmetry in deeply virtual electroproduction of a real photon off a bound 
+proton in $^{4}$He. Experimentally, we measure the squared sum of the 
+Bethe-Heitler (BH) and the DVCS amplitudes, with the former is the process 
+where the real photon is emitted by the incident or the scattered electron 
+rather than the nucleon. The beam-spin asymmetry arises from the interference 
+of these two terms and is directly sensitive to the DVCS amplitude that contain 
+the information on the GPDs.  Using a longitudinally polarized electron beam 
+(L) and an unpolarized target (U), this beam-spin asymmetry observable is 
+defined as:
 \begin{equation}
@@
 (83$\%$ polarization) from the Continuous Electron Beam Accelerator Facility 
-(CEBAF) accelerator at energy of 6.064 GeV. The data were accumulated 
-over 40 days using a 6-atm-pressure, 292-mm-long, and 6-mm-diameter gaseous 
-$^4$He target centered at 64~cm upstream of the CEBAF Large Acceptance 
-Spectrometer (CLAS) coordinate center. For DVCS experiments, the CLAS baseline 
-design \cite{Mecking:2003zu} 
-is supplemented with an inner calorimeter (IC) and a solenoid magnet. The IC extends 
-the photon detection acceptance of CLAS to very small polar angles, 4$^{\circ}$. 
-The 5-Tesla solenoid magnet in the center of which the target was located 
-prevented the high-rate low-energy M{\o}ller electrons from reaching the CLAS 
-drift chambers by guiding these electrons inside a tungsten shield placed around the beam line.
+(CEBAF) accelerator at an energy of 6.064 GeV. The data were accumulated over 
+40 days using a 6-atm-pressure, 292-mm-long, and 6-mm-diameter gaseous $^4$He 
+target centered at 64~cm upstream of the CEBAF Large Acceptance Spectrometer 
+(CLAS) coordinate center. For DVCS experiments, the CLAS baseline design 
+\cite{Mecking:2003zu} is supplemented with an inner calorimeter (IC) and a 
+solenoid magnet. The IC extends the photon detection acceptance of CLAS to very 
+small polar angles, 4$^{\circ}$.  The 5-Tesla solenoid magnet in the center of 
+which the target was located prevented the high-rate low-energy M{\o}ller 
+electrons from reaching the CLAS drift chambers by guiding these electrons 
+inside a tungsten shield placed around the beam line.
 
 % DVCS selection
-Incoherent DVCS events were selected if an electron, a proton, and at least one 
-photon were detected in the final state. Electrons were identified as negatively 
-charged tracks reconstructed in drift chambers with an appropriate energy 
-deposition in the electromagnetic calorimeter (EC) and a proper light yield in 
-the Cherenkov counters. The protons were identified from positively charged tracks by 
-timing analysis using the time-of-flight measured by the scintillator counters. 
-In addition, it was required that both the electron and the proton in the event 
-originated from the same vertex at the target within CLAS tracking vertex 
-resolution. The photons were detected in either the IC or 
-the CLAS electromagnetic calorimeter. All the clusters within the IC fiducial region 
-were assumed to be photons, while a timing cut is used to clean the EC photons 
-from neutrons. Note that even though the DVCS reaction has only one real photon 
-in the final state, events with more than one photon were not discarded at 
-this stage. These are mostly soft photons from accidental coincidence which, 
-as will be discussed below, the DVCS exclusivity cuts eliminate easily. In the 
-following selection stage, the most energetic photon is considered as the DVCS 
-photon candidate (see \cite{Hattawy:thesis} for additional details on the 
-particles identification).
+Incoherent DVCS events were selected by requiring an electron, a proton, and at 
+least one photon in the final state. Electrons were identified as negatively 
+charged tracks reconstructed in the drift chambers with an appropriate energy 
+deposition in the electromagnetic calorimeter (EC) and a light yield above the 
+threshold in the Cherenkov counters. The protons were identified from 
+positively charged tracks by timing analysis using the time-of-flight measured 
+by the scintillator counters.  In addition, it was required that both the 
+electron and the proton in the event originated from the same vertex at the 
+target within CLAS tracking vertex resolution. The photons were detected in 
+either the IC or the CLAS electromagnetic calorimeter. All the clusters within 
+the IC fiducial region were assumed to be photons, while a timing cut is used 
+to clean the EC photons from neutrons. Note that even though the DVCS reaction 
+has only one real photon in the final state, events with more than one photon 
+were not discarded at this stage. These are mostly soft photons from accidental 
+coincidence which, as will be discussed below, the DVCS exclusivity cuts 
+eliminate easily. In the following selection stage, the most energetic photon 
+is considered as the DVCS photon candidate (see \cite{Hattawy:thesis} for 
+additional details on the particles identification).
 
 Further requirements were applied to clean the identified initial set of 
-incoherent DVCS events from accidental and physics background events. First, events were 
-selected with Q$^{2}$ greater the 1 GeV$^2$ to ensure the applicability of the 
-DVCS handbag diagram, and with $\gamma^{*}p$ invariant mass (W$=(q+p)^2$) greater than 2 GeV to 
-avoid the nucleon resonance region. The transferred momentum squared to the recoil proton was required to be greater than a
-minimum allowed value at given Q$^2$ and W ($t~>~t_{min}$). Then, the exclusivity of the incoherent DVCS events was 
-ensured by imposing constraints on the kinematical variables resulting from 
-conserving the four-momentum in the reaction $ep\rightarrow e'p'\gamma$. These 
-kinematical variables are: the coplanarity angle $\Delta\phi$ between the 
-($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) planes, the missing energy, mass, and 
-transverse momentum of the $e'\gamma$ and $e'p'\gamma$ systems, the missing mass 
-squared of the $e'p'$ system, and the angle $\theta$ between the measured 
-photon and the missing momentum of the $e'p'$ system. The experimental data for 
-the most relevant exclusivity variables and applied cuts are shown in 
-FIG.~\ref{fig:kin-cuts} (see \cite{Hattawy:thesis} for additional details). We 
-also rejected events where a $\pi^0$ was identified by the invariant mass of 
-two photons. About 30k events passed all these requirements; their kinematic 
-distributions are shown in FIG.~\ref{fig:kin-coverage}.
+incoherent DVCS events from accidental and physics background events. First, 
+events were selected with Q$^{2}$ greater the 1 GeV$^2$ to ensure the 
+applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
+mass (W$=(q+p)^2$) greater than 2 GeV to avoid the nucleon resonance region.  
+The $t$, transferred momentum squared to the recoil proton by assuming an 
+on-shell proton at rest, was required to be greater than a minimum allowed 
+value at given Q$^2$ and W ($t~>~t_{min}$).  Then, the exclusivity of the 
+incoherent DVCS events was ensured by imposing constraints on the kinematical 
+variables resulting from conserving the four-momentum in the reaction 
+$ep\rightarrow e'p'\gamma$. These kinematical variables are: the coplanarity 
+angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) 
+planes, the missing energy, mass, and transverse momentum of the $e'\gamma$ and 
+$e'p'\gamma$ systems, the missing mass squared of the $e'p'$ system, and the 
+angle $\theta$ between the measured photon and the missing momentum of the 
+$e'p'$ system. The experimental data for the most relevant exclusivity 
+variables and applied cuts are shown in FIG.~\ref{fig:kin-cuts} (see 
+\cite{Hattawy:thesis} for additional details). We also rejected events where a 
+$\pi^0$ was identified by the invariant mass of two photons. About 30k events 
+passed all these requirements; their kinematic distributions are shown in 
+FIG.~\ref{fig:kin-coverage}.
 
@@
    passed all the exclusivity cuts except the quantity plotted. The vertical 
-   red lines represent the applied exclusivity cuts. The distributions from 
-   left to right and from top to bottoms are: $\Delta \phi$, missing energy,
-   missing masses squared and the cone angle ($\theta$) between the measured 
-   and the calculated photons in the $e'p'$ final-state system. }
+   red-dashed lines represent the applied exclusivity cuts. The distributions 
+   from left to right and from top to bottoms are: $\Delta \phi$, missing 
+   energy, missing masses squared and the cone angle ($\theta$) between the 
+   measured and the calculated photons in the $e'p'$ final-state system. }
 \label{fig:kin-cuts}
@@
 e'p'\pi^0}_{exp}$, where $N^{ep\rightarrow e'p'\gamma}_{exp}$ is the 
-experimentally identified number of $ep\rightarrow e'p'\gamma$ and 
+experimentally identified number of yield of $ep\rightarrow e'p'\gamma$ and 
 $N^{ep\rightarrow e'p'\pi^0}_{exp}$ is the experimentally identified 
@@
 different kinematics than our data but still provide important guidance. The 
-experimental results appear to have smaller asymmetries than the calculations.  
-These differences may arise from nuclear effects which are not taken into 
-account in the model, such as long-range interactions. On the graph for $-t$ 
-dependence, we show previous measurements by the HERMES collaboration
-\cite{Airapetian:2009cga} using inclusive final state, ($e^\prime\gamma$). Due 
-to large experimental uncertainties of HERMES points, the two measurements 
-do not disagree, but we can also see that their high $-t$ results were 
-smaller than expected by models.
+experimental results appear to have smaller asymmetries especially at low 
+$x_{B}$ than the calculations.  These differences may arise from nuclear 
+effects which are not taken into account in the model, such as long-range 
+interactions.  On the graph for $-t$ dependence, we show previous measurements 
+by the HERMES collaboration \cite{Airapetian:2009cga} using inclusive final 
+state, ($e^\prime\gamma$). Due to large experimental uncertainties of HERMES 
+points, the two measurements do not disagree, but we can also see that their 
+high $-t$ results were smaller than expected by models.
 

### 2018-07-04 eg6-letters/incoherent/incoherent_prl.tex
Some edits on the incoherent paper

@@
  We report the first beam spin asymmetry (BSA) measurements in incoherent 
-   deeply virtual Compton scattering (DVCS) off $^4$He using the exclusive 
-   final state. The data were accumulated using a 6 GeV longitudinally 
+   deeply virtual Compton scattering (DVCS) off $^4$He. The data were 
+   accumulated using a 6 GeV longitudinally 
    polarized electron beam incident on a pressurized $^4$He gaseous target 
@@
    kinematical region of our measurements, the BSA on the bound nucleon is 
-   smaller by about $20\%$ to $30\%$, indicating possible medium modification 
+   smaller by $20\%$ to $40\%$, indicating possible medium modification 
    on the nucleon's partonic structure. This measurement opens a new 
@@
 Electromagnetic probes have played a major role in advancing our knowledge 
-about the structure of the nucleon, which is at the origin of almost all the
-universe's visible matter. While elastic lepton-nucleon measurements have 
+about the structure of the nucleon. While elastic lepton-nucleon measurements have 
 taught us about the spatial charge and magnetization distributions 
@@
 and a 3-D tomography of the free proton \cite{Guidal:2013rya,Dupre:2016mai}.  
-New measurements of exclusive DVCS from the $^{4}$He nucleus are a critical 
-step towards providing similar 3-D pictures of the quark structure of the 
-nucleus as a whole, via the coherent channel 
-\cite{Airapetian:2009cga,Hattawy:2017woc}, and provide a new approach for 
-understanding modifications of the partonic structure of the bound nucleons via 
-the incoherent DVCS channel \cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}. The 
-$^{4}$He nucleus is an ideal experimental target for these purposes as it is 
+New measurements of DVCS from the $^{4}$He nucleus are a critical 
+step towards providing a similar 3-D pictures of the quark structure of the 
+nucleus~\cite{Dupre:2015jha}. In the nuclear case however, two channels are available,
+the coherent channel where the nucleus is left intact \cite{Airapetian:2009cga,
+Hattawy:2017woc}, and the incoherent channel where the DVCS happens on a nucleon.
+The latter, which is the focus of this letter, provides a unique access to the 
+modification of the partonic structure of the bound nucleons 
+\cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}. The 
+$^{4}$He nucleus is an ideal experimental target for this measurement as it is 
 characterized by a strong binding energy, a relatively high nuclear 
-core density, and a large EMC effect~\cite{JSeely}. However, it remains simple 
-enough that exact calculation of its structure 
+core density, and a large EMC effect~\cite{JSeely}. Moreover, it remains simple 
+enough that precise calculation of its structure 
 can be performed, making this nucleus the perfect target for our investigation of the 
@@
 In this Letter, we present the first exclusive measurement of the beam-spin 
-asymmetry in deeply virtual electroproduction of a real photon off a bound 
+asymmetry (BSA) in deeply virtual electroproduction of a real photon off a bound 
 proton in $^{4}$He. Experimentally, we measure the squared sum of the 
-Bethe-Heitler (BH) and the DVCS amplitudes, with the former is the process 
+Bethe-Heitler (BH) and the DVCS amplitudes, with the BH the process 
 where the real photon is emitted by the incident or the scattered electron 
-rather than the nucleon. The beam-spin asymmetry arises from the interference 
+rather than the nucleon. The BSA arises from the interference 
 of these two terms and is directly sensitive to the DVCS amplitude that contain 
 the information on the GPDs.  Using a longitudinally polarized electron beam 
-(L) and an unpolarized target (U), this beam-spin asymmetry observable is 
-defined as:
+(L) and an unpolarized target (U), the BSA is defined as:
 \begin{equation}
@@
 leptonic and the hadronic planes of the reaction. At leading-twist, the 
-beam-spin asymmetry can be simplified as: 
+BSA can be simplified as: 
 \begin{equation}
@@
 \cite{Mecking:2003zu} is supplemented with an inner calorimeter (IC) and a 
-solenoid magnet. The IC extends the photon detection acceptance of CLAS to very 
-small polar angles, 4$^{\circ}$.  The 5-Tesla solenoid magnet in the center of 
+solenoid magnet. The IC extends the photon detection acceptance of CLAS down 
+to a polar angle of 4$^{\circ}$. The 5-Tesla solenoid magnet in the center of 
 which the target was located prevented the high-rate low-energy M{\o}ller 
@@
 threshold in the Cherenkov counters. The protons were identified from 
-positively charged tracks by timing analysis using the time-of-flight measured 
+positively charged tracks based on their time-of-flight measured 
 by the scintillator counters.  In addition, it was required that both the 
@@
 has only one real photon in the final state, events with more than one photon 
-were not discarded at this stage. These are mostly soft photons from accidental 
+were not discarded at this stage. These extra photons are mostly soft photons from accidental 
 coincidence which, as will be discussed below, the DVCS exclusivity cuts 
@@
 \cite{Hattawy:thesis} for additional details). We also rejected events where a 
-$\pi^0$ was identified by the invariant mass of two photons. About 30k events 
-passed all these requirements; their kinematic distributions are shown in 
+$\pi^0$ was identified by the invariant mass of two photons. At the end of
+this selection process, about 30k events 
+passed all the requirements; their kinematic distributions are shown in 
 FIG.~\ref{fig:kin-coverage}.
@@
 The two main backgrounds that contribute to the event sample after the exclusivity cuts are  
-events due to accidental coincidences and exclusive $\pi^0$ production where one of the photons 
-from the $\pi^0$ decay escapes the detection. For the accidental events, i.e., $e'p'\gamma$ collection 
-with particles originated from different electron scattering events, their contribution 
-was evaluated to be of 6.5\% by selecting events passing all our cuts but originating from 
-different vertices. The $\pi^0$ contamination was estimated using the data and 
-simulation. From simulation, we calculated the ratio ($R$) of the number of $\pi^0$ 
-events that are identified as $ep\rightarrow e'p'\gamma$ events after our selection 
-cuts to the number of identified $\pi^0$ events, 
+due to accidental coincidences and exclusive $\pi^0$ production where one of the photons 
+from the $\pi^0$ decay escapes the detection. The contribution from accidental events, i.e., $e'p'\gamma$ collections 
+with particles originating from different electron scatterings,
+was evaluated to be of 6.5\% by selecting events passing all our selection cuts but originating from 
+different vertices. The $\pi^0$ contamination was estimated using detector simulation and experimental 
+data. From simulation, we calculated the ratio ($R$) of the number of $\pi^0$ 
+events that are wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the 
+number of events correcltly identified as exclusive $ep\rightarrow e'p'\pi^0$, 
 $R = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$. Then in each kinematical bin and for 
@@
 e'p'\pi^0}_{exp}$, where $N^{ep\rightarrow e'p'\gamma}_{exp}$ is the 
-experimentally identified number of yield of $ep\rightarrow e'p'\gamma$ and 
+experimentally identified number of $ep\rightarrow e'p'\gamma$ and 
 $N^{ep\rightarrow e'p'\pi^0}_{exp}$ is the experimentally identified 
-$ep\rightarrow e'p'\pi^0$ with the two photons detected. Depending on the 
-kinematics, we found this contamination to be of 8\% to 10\%.
+$ep\rightarrow e'p'\pi^0$. Depending on the 
+kinematics, we found this contamination to be of 8 to 10\%.
 
@@
 
-In the kinematical phase-space of our experiment, the GPD $H$ dominants the 
-contribution in the beam-spin asymmetry over the other three GPDs. Therefore, 
+In the kinematical phase-space of our experiment, the GPD $H$ dominates the 
+contribution in the BSA over the other three GPDs. Therefore, 
 the $\phi$ dependence of $A_{LU}$ gives a direct access to the real and 
@@
 FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the dependence of the 
-beam-spin asymmetry ratio at $\phi$~=~90$^{\circ}$ on the kinematical variables 
+BSA ratio at $\phi$~=~90$^{\circ}$ on the kinematical variables 
 $Q^2$, $x_B$, and $t$. The free proton asymmetries were interpolated from the 
@@
 missing from the existing models in order to explain this strong quenching of
-the beam-spin asymmetry.
+the BSA.
 
 %conclusion
-In summary, we have presented the first exclusive beam-spin asymmetry measurements 
+In summary, we have presented our BSA measurements 
 associated with incoherent DVCS off $^4$He using an upgraded setup of the CLAS 
@@
 the partonic level.  The bound-proton 
-beam-spin asymmetries is largely suppressed compared to the free proton 
+BSA is largely suppressed compared to the free proton 
 results measured in a similar phase-space. This surprising result opens a new avenue 
@@
 
+\bibitem{Dupre:2015jha} 
+  R.~Dupré and S.~Scopetta,
+  Eur.\ Phys.\ J.\ A {\bf 52}, no. 6, 159 (2016)
+
 %\cite{Airapetian:2009cga}
@@
 
-\bibitem{Dupre:2017upj} R.~Dupr\'e {\it et al.},
-  arXiv:1706.10160.
+\bibitem{Dupre:2017upj} 
+  R.~Dupr\'e {\it et al.},
+  Nucl.\ Instrum.\ Meth.\ A {\bf 898}, 90 (2018)
 

### 2018-07-05 eg6-letters/incoherent/incoherent_prl.tex
Final edits for RD

@@
 electron and the proton in the event originated from the same vertex at the 
-target within CLAS tracking vertex resolution. The photons were detected in 
+target. The photons were detected in 
 either the IC or the CLAS electromagnetic calorimeter. All the clusters within 
@@
 mass (W$=(q+p)^2$) greater than 2 GeV to avoid the nucleon resonance region.  
-The $t$, transferred momentum squared to the recoil proton by assuming an 
+The $t$, transferred momentum squared to the recoil proton assuming an 
 on-shell proton at rest, was required to be greater than a minimum allowed 
@@
 $e'p'$ system. The experimental data for the most relevant exclusivity 
-variables and applied cuts are shown in FIG.~\ref{fig:kin-cuts} (see 
-\cite{Hattawy:thesis} for additional details). We also rejected events where a 
+variables are shown in FIG.~\ref{fig:kin-cuts}. We also rejected events where a 
 $\pi^0$ was identified by the invariant mass of two photons. At the end of
@@
 \includegraphics[width=8.9cm]{figs/incoh_exc_cuts_final.pdf}
-\caption{The incoherent DVCS exclusivity cuts. The black distributions 
-   represent the incoherent DVCS events candidate before all the exclusive 
-   cuts. The shaded distributions represent the incoherent DVCS events which 
-   passed all the exclusivity cuts except the quantity plotted. The vertical 
-   red-dashed lines represent the applied exclusivity cuts. The distributions 
+\caption{The distributions 
    from left to right and from top to bottoms are: $\Delta \phi$, missing 
    energy, missing masses squared and the cone angle ($\theta$) between the 
-   measured and the calculated photons in the $e'p'$ final-state system. }
+   measured and the calculated photons in the $e'p'$ final-state system.
+   The incoherent DVCS exclusivity cuts are represented by the vertical 
+   red-dashed lines. The black distributions 
+   represent the incoherent DVCS events candidate before the exclusivity 
+   cuts. The shaded distributions represent the incoherent DVCS events which 
+   passed all these cuts except the quantity plotted.}
 \label{fig:kin-cuts}
@@
 events that are wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the 
-number of events correcltly identified as exclusive $ep\rightarrow e'p'\pi^0$, 
+number of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$, 
 $R = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$. Then in each kinematical bin and for 
@@
 calculated as $N = N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow 
-e'p'\pi^0}_{exp}$, where $N^{ep\rightarrow e'p'\gamma}_{exp}$ is the 
-experimentally identified number of $ep\rightarrow e'p'\gamma$ and 
-$N^{ep\rightarrow e'p'\pi^0}_{exp}$ is the experimentally identified 
-$ep\rightarrow e'p'\pi^0$. Depending on the 
+e'p'\pi^0}_{exp}$, where $N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is the 
+number of $ep\rightarrow e'p'\gamma$ ($ep\rightarrow e'p'\pi^0$) experimentally identified. Depending on the 
 kinematics, we found this contamination to be of 8 to 10\%.
@@
 
-In the kinematical phase-space of our experiment, the GPD $H$ dominates the 
-contribution in the BSA over the other three GPDs. Therefore, 
-the $\phi$ dependence of $A_{LU}$ gives a direct access to the real and 
-imaginary part of the CFF $\mathcal{H}$ through the parameters $a_0$, $a_1$, 
-and $a_2$ of equation \ref{eq:alu-simp}. The studies of  the free proton 
-$A_{LU}$ measurements, \cite{Girod:2007aa}, have shown that the the pure DVCS 
-contribution, $cos(2\phi)$ term ($a_2$), is suppressed and compatible with 
-zero.
-
-%{\bf Raphael: This paragraph is very confusing, is it true that a1 and a2 are 
-%dominated by H? Do we have equivalents of eq. 3 for those? I actually did 
-%notfind it in ref 31, which we are referring and we are also not using the 
-%same definition of Im(H)...}
+In the kinematical phase-space of our experiment, the GPD $H$ is
+expected to dominate the 
+contribution in the BSA over the other three GPDs. There, 
+the $\phi$ dependence of $A_{LU}$ is mostly sensitive to the  
+imaginary part of the CFF $\mathcal{H}$ through the parameters $a_0$ of 
+equation~\ref{eq:alu-simp}. The measurement of the free proton 
+$A_{LU}$ \cite{Girod:2007aa} has confirmed that the $a_0$ term is 
+dominating the shape of the distribution.
 
 Due to limited statistics, the data were binned two-dimensionally into 36 bins.  
-That is, four statistically-equivalent bins in one of the kinematical 
-variable of interest -- $Q^{2}$, $x_{B}$ or $t$ -- were constructed, then each 
-bin is divided into nine bins in the azimuthal angle ($\phi$).  
+That is, four bins in one of the kinematical variable of interest ($Q^{2}$, 
+$x_{B}$ or $t$) and nine bins in the azimuthal angle ($\phi$).  
 FIG.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
@@
 to systematic uncertainties on these fits are from the choice of the DVCS 
-exclusivity cuts (6\%) and the large binning size (7\%). Added quadratically, 
-these uncertainties sum up to less than 10\% for all data points and remain 
-significantly smaller than the statistical errors.
+exclusivity cuts (6\%) and the large binning size (7\%). The systematic uncertainties
+sum up to less than 10\% for all data points and thus always remain significantly 
+smaller than the statistical errors.
 
@@
 theoretical calculations performed by S.~Liuti and K.~Taneja 
-\cite{simonetta_2}. Their model uses a realistic spectral function and 
-considers off-shell effects. The calculations are carried out at slightly 
+\cite{simonetta_2}. Their model uses nuclear spectral function and 
+considers mainly off-shell effects. The calculations are carried out at slightly 
 different kinematics than our data but still provide important guidance. The 
@@
 interactions. On the graph for $-t$ dependence, we show previous measurements 
-by the HERMES collaboration \cite{Airapetian:2009cga} using inclusive final 
-state, ($e^\prime\gamma$). Due to large experimental uncertainties of HERMES 
-points, the two measurements do not disagree, but we can also see that their 
-high $-t$ results were smaller than expected by models.
+by the HERMES collaboration \cite{Airapetian:2009cga}, in which only electrons
+and photons were measured. Due to the large experimental uncertainties of the HERMES 
+points, the two measurements are completely compatible.
 
@@
 
-In this work we carried out the first step towards measuring the 
-``generalized'' EMC effect in order to understand the potential sources of 
-nuclear effects at the partonic level within the GPDs framework. We construct 
-the ratio of $A_{LU}$ for bound protons to that on free proton target measured 
-using similar electron-beam energy and experimental setup.  
-FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the dependence of the 
-BSA ratio at $\phi$~=~90$^{\circ}$ on the kinematical variables 
-$Q^2$, $x_B$, and $t$. The free proton asymmetries were interpolated from the 
-published results \cite{Girod:2007aa}.
+One can use the nuclear DVCS to measure a ``generalized'' EMC effect in order 
+to see if significant nuclear effects are also visible within the GPD framework. 
+To explore this idea, we construct 
+the ratio of $A_{LU}$ for bound protons to that on free proton target.  
+FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the 
+BSA ratio based on interpolation of the free proton asymmetries from  
+CLAS \cite{Girod:2007aa} as a function of the kinematical variable
+$x_B$. The $A_{LU}$ ratios show a 20\%-40\% lower asymmetries for a bound proton compared 
+to the free proton mirroring a form of EMC effect but with a surprising 
+large effect, in particular at low $x_B$. The measurements disagree with the off-shell \cite{simonetta_2} 
+and the on-shell calculations that use the medium modified GPDs as calculated from 
+the quark-meson coupling model \cite{Guzey:2008fe}. In particular, the difference becomes
+large at lower $x_B$, 
+where the off-shell model predicts an enhancement of the ratio, where our experiment 
+shows a sharp drop. This measurement shows that an important nuclear effect is
+missing from the existing models in order to explain this strong quenching of
+the BSA.
 
@@
 %\includegraphics[width=6.9cm]{figs/ALU_ratioInc_Q2_shortscenrario.pdf}\\
-%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}\\
-\includegraphics[width=8.5cm]{figs/ALU_ratioInc_t_shortscenrario.pdf}
+\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}
+%\includegraphics[width=8.5cm]{figs/ALU_ratioInc_t_shortscenrario.pdf}
 \caption{ The $A_{LU}$ ratio of the bound to the free proton at 
-   $\phi$~=~90$^{\circ}$ as a function of $t$. The black squares are from this 
-   work, the green circles are the HERMES inclusive measurement 
+   $\phi$~=~90$^{\circ}$ as a function of $x_B$. The black squares are from this 
+   work, the green circle is the HERMES measurement 
    \cite{Airapetian:2009cga}. The blue and red curves are results of off-shell 
@@
 
-The $A_{LU}$ ratios show a 20\%-40\% lower asymmetries for a bound proton compared 
-to the free proton. The measurements disagree with the off-shell \cite{simonetta_2} 
-and the on-shell calculations that use the medium modified GPDs as calculated from 
-the quark-meson coupling model \cite{Guzey:2008fe}. In particular, at lower $x_B$, 
-where the off-shell model predicts an enhancement of the ratio, our experiment 
-shows a sharp drop. This measurement shows that an important nuclear effect is
-missing from the existing models in order to explain this strong quenching of
-the BSA.
-
 %conclusion
@@
 calculations based on different assumptions of the nuclear medium effects at 
-the partonic level.  The bound-proton 
-BSA is largely suppressed compared to the free proton 
-results measured in a similar phase-space. This surprising result opens a new avenue 
+the partonic level. The bound-proton BSA is largely suppressed compared to 
+the free proton BSA. This surprising result opens a new avenue 
 for progress in the understanding of the quarks and gluons behavior in the
@@
 
-\bibitem{Hattawy:thesis}
-M.~Hattawy, Ph.D. thesis, Universit{\'e} Paris Sud - Paris XI, France, 2015 
-[Institution Report No. 2015PA112161].
-
 %\cite{Armstrong:2017wfw}

### 2018-07-05 eg6-letters/incoherent/incoherent_prl.tex
Add Stepan's comments

@@
 
-\title{First exclusive Deeply Virtual Compton Scattering measurement off bound nucleon in $^4$He}
+\title{Deeply Virtual Compton Scattering measurement off bound proton}
 
@@
    kinematics. The Q$^2$, $x_B$, and $t$ dependencies of the BSA on the bound 
-   nucleon have been compared with the one on the free proton. In the whole 
-   kinematical region of our measurements, the BSA on the bound nucleon is 
+   proton have been compared with the one on the free proton. In the whole 
+   kinematical region of our measurements, the BSA on the bound proton is 
    smaller by $20\%$ to $40\%$, indicating possible medium modification 
-   on the nucleon's partonic structure. This measurement opens a new 
-   opportunity to explore the origin of the EMC effect within the framework of 
-   the generalized parton distributions.
+   of its partonic structure. This measurement opens a new avenue for 
+   studying structure of the bound nucleon and explore the origin of the EMC 
+   effect using the framework of the generalized parton distributions.
 
@@
 Electromagnetic probes have played a major role in advancing our knowledge 
-about the structure of the nucleon. While elastic lepton-nucleon measurements have 
+about the structure of the nucleon. While lepton-nucleon elastic scattering 
+measurements have 
 taught us about the spatial charge and magnetization distributions 
 \cite{Hofstadter:1955ae,Perdrisat:2006hj}, deep-inelastic scattering 
-experiments have uncovered the features of momentum sharing between the 
-constituents partons, i.e., quarks and gluons \cite{Dokshitzer:1977sg,pdg}.  
-With nuclear targets, these measurements have revealed the fact that the 
+experiments have uncovered the partonic structure of the nucleon and 
+the longitudinal momentum distributions of the 
+constituents partons, i.e., quarks and gluons \cite{pdg}.  
+With nuclear targets, deeply inelastic lepton scattering measurements 
+have revealed the fact that the 
 distribution of quarks in a nucleus is not a simple convolution of 
@@
 effect''\cite{EMC_first} (for reviews on the topic, see  
-\cite{EMC_CERN,EMC_SLAC,EMC_HERMES,EMC_JLab,EMC_John,EMC_mdeium_1,EMC_medium_2}).
+\cite{Arneodo:1992wf,Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}).
 
@@
 involving several accelerator facilities such as Jefferson Lab, DESY and  
-CERN. Combining these measurements has enabled the first extractions of GPDs 
+CERN. These measurements now enable the extractions of GPDs 
 and a 3-D tomography of the free proton \cite{Guidal:2013rya,Dupre:2016mai}.  
@@
 
+In the 
+Bjorken regime, i.e, large virtual photon four-momentum squared 
+($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small invariant momentum transfer ($t=(p-p^\prime)^2$), the 
+DVCS scattering process can be factorized, leaving the non-perturbative structure 
+of the nucleon to be parametrized in terms of four chirally-even GPDs: $H$, 
+$E$, $\widetilde{H}$, and $\widetilde{E}$, representing the four helicity-spin 
+combinations of the quark-nucleon states \cite{Freund_Collins,Ji_Osborne}.
+
 \begin{figure}[tb]
@@
 
-FIG.~\ref{fig:diags} illustrates the 
-leading-twist handbag diagram for the incoherent DVCS off $^{4}$He. In the 
-Bjorken regime, i.e, large virtual photon four-momentum squared 
-($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small invariant momentum transfer ($t=(p-p^\prime)^2$), the 
-DVCS scattering process can be factorized, leaving the non-perturbative structure 
-of the nucleon to be parametrized in terms of four chirally-even GPDs: $H$, 
-$E$, $\widetilde{H}$, and $\widetilde{E}$, representing the four helicity-spin 
-combinations of the quark-nucleon states \cite{Freund_Collins,Ji_Osborne}.
-
 In this Letter, we present the first exclusive measurement of the beam-spin 
 asymmetry (BSA) in deeply virtual electroproduction of a real photon off a bound 
-proton in $^{4}$He. Experimentally, we measure the squared sum of the 
-Bethe-Heitler (BH) and the DVCS amplitudes, with the BH the process 
+proton in $^{4}$He. FIG.~\ref{fig:diags} illustrates the 
+leading-twist handbag diagram for this process. Experimentally, we measure the squared sum of the 
+Bethe-Heitler (BH) and the DVCS amplitudes. The BH process, 
 where the real photon is emitted by the incident or the scattered electron 
-rather than the nucleon. The BSA arises from the interference 
+rather than the nucleon, dominates the cross section at our kinematics. The BSA arises from the interference 
 of these two terms and is directly sensitive to the DVCS amplitude that contain 
@@
 (83$\%$ polarization) from the Continuous Electron Beam Accelerator Facility 
-(CEBAF) accelerator at an energy of 6.064 GeV. The data were accumulated over 
+(CEBAF) at an energy of 6.064 GeV. The data were accumulated over 
 40 days using a 6-atm-pressure, 292-mm-long, and 6-mm-diameter gaseous $^4$He 
@@
 due to accidental coincidences and exclusive $\pi^0$ production where one of the photons 
-from the $\pi^0$ decay escapes the detection. The contribution from accidental events, i.e., $e'p'\gamma$ collections 
+from the $\pi^0$ decay escapes the detection. The contribution from accidental 
+events, i.e., $e'p'\gamma$ collections 
 with particles originating from different electron scatterings,
@@
 different vertices. The $\pi^0$ contamination was estimated using detector simulation and experimental 
-data. From simulation, we calculated the ratio ($R$) of the number of $\pi^0$ 
+data. From simulation, we calculated the ratio ($R = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) 
+of the number of $\pi^0$ 
 events that are wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the 
-number of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$, 
-$R = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$. Then in each kinematical bin and for 
+number of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$. Then 
+in each kinematical bin and for 
 each beam-helicity state, the $\pi^0$-subtracted experimental DVCS events is 
@@
 to systematic uncertainties on these fits are from the choice of the DVCS 
-exclusivity cuts (6\%) and the large binning size (7\%). The systematic uncertainties
+exclusivity cuts (6\%) and the large bin size (7\%). The systematic uncertainties
 sum up to less than 10\% for all data points and thus always remain significantly 
@@
 We present in FIG.~\ref{fig:alu90} the dependence of the fitted $A_{LU}$ 
-signals at $\phi$~=~90$^{\circ}$ on the kinematical variables $Q^2$, $x_{B}$, 
+values at $\phi$~=~90$^{\circ}$ on the kinematical variables $Q^2$, $x_{B}$, 
 and $t$. Within the given uncertainties, $A_{LU}$ does not indicate a strong 
@@
 
-%\cite{Hofstadter:1955ae}
 \bibitem{Hofstadter:1955ae} R.~Hofstadter and R.~W.~McAllister,
@@
 Phys.\ Rev.\  {\bf 98}, 217 (1955).
-%doi:10.1103/PhysRev.98.217
 
-%\cite{Perdrisat:2006hj}
 \bibitem{Perdrisat:2006hj} C.~F.~Perdrisat, V.~Punjabi and M.~Vanderhaeghen,
@@
 Prog.\ Part.\ Nucl.\ Phys.\  {\bf 59}, 694 (2007)
-%doi:10.1016/j.ppnp.2007.05.001
-%[hep-ph/0612014].
 
-%\cite{Dokshitzer:1977sg}
-\bibitem{Dokshitzer:1977sg} Y.~L.~Dokshitzer,
-%``Calculation of the Structure Functions for Deep Inelastic Scattering and e+ 
-   %e- Annihilation by Perturbation Theory in Quantum Chromodynamics.,''
-Sov.\ Phys.\ JETP {\bf 46}, 641 (1977)
-[Zh.\ Eksp.\ Teor.\ Fiz.\  {\bf 73}, 1216 (1977)].
-
-%\cite{pdg}
 \bibitem{pdg} J.~Beringer {\it et al.} (Particle Data Group), Phys.\ Rev.\ D 
@@
 
-\bibitem{EMC_CERN}
-J. Ashman et al. (EMC Collaboration), 
-      %Measurement of the ratios of deep inelastic muon-nucleus cross sections 
-%on various nuclei compared to deuterium, 
-      Phys.\ Lett.\ B\ {\bf 202}, 603 1988.
+\bibitem{Arneodo:1992wf} 
+  M.~Arneodo,
+  %``Nuclear effects in structure functions,''
+  Phys.\ Rept.\  {\bf 240}, 301 (1994).
 
-\bibitem{EMC_SLAC}
-J. Gomez et al. (SLAC-E139), 
-      %Measurement of the A dependence of deep-inelastic electron scattering, 
-      Phys.\ Rev.\ D\ {\bf 49}, 4348 (1994).
+\bibitem{Geesaman:1995yd} 
+  D.~F.~Geesaman, K.~Saito and A.~W.~Thomas,
+  %``The nuclear EMC effect,''
+  Ann.\ Rev.\ Nucl.\ Part.\ Sci.\  {\bf 45}, 337 (1995).
+  %doi:10.1146/annurev.ns.45.120195.002005
 
-\bibitem{EMC_HERMES}
-A. Airapetian et al. (HERMES Collaboration), 
-      %Nuclear effects on R = $\sigma_{L}/\sigma_{T}$ in deep-inelastic 
-%scattering, 
-      Phys.\ Lett.\ B\ {\bf 567}, 339 (2003).
+\bibitem{Norton:2003cb} 
+  P.~R.~Norton,
+  %``The EMC effect,''
+  Rept.\ Prog.\ Phys.\  {\bf 66}, 1253 (2003).
+  %doi:10.1088/0034-4885/66/8/201
 
-\bibitem{EMC_JLab}
-J. Seely et al., 
-      %New Measurements of the European Muon Collaboration Effect in Very Light 
-%Nuclei, 
-      Phys.\ Rev.\ Lett.\ {\bf 103}, 202301 (2009).
-
-\bibitem{EMC_John}
-J. Arrington et al., 
-%A detailed study of the nuclear dependence of the EMC effect and short-range 
-%correlations, 
-      Phys.\ Rev.\ C\ {\bf 86}, 065204 (2012).
-
-\bibitem{EMC_mdeium_1}
-I. Clo\"et et al., 
-%Isovector EMC effect explains the NuTeV anomaly, 
-Phys.\ Rev.\ Lett.\ {\bf 102}, 252301 (2009).
-
-\bibitem{EMC_medium_2}
-I. Clo\"et et al., %Parity-violating DIS and the flavour dependence of the EMC 
-%effect, 
-Phys.\ Rev.\ Lett.\ {\bf 109}, 182301 (2012).
+\bibitem{Hen:2016kwk} 
+  O.~Hen {\it et al.},
+  %``Nucleon-Nucleon Correlations, Short-lived Excitations, and the Quarks Within,''
+  Rev.\ Mod.\ Phys.\  {\bf 89}, no. 4, 045002 (2017).
 
@@
 
-%\cite{Airapetian:2001yk}
 \bibitem{Airapetian:2001yk} A.~Airapetian {\it et al.} [HERMES Collaboration],
@@
 %[hep-ex/0605108].
-
-%\bibitem{Airapetian}
-%A. Airapetian {\it et al.} [HERMES Collaboration],
-%Phys.\ Rev.\ Lett. {\bf 87}, 182001 (2001);
-%JHEP {\bf 1207}, 032 (2012);
-%JHEP {\bf 1006}, 019 (2010);
-%JHEP {\bf 0806}, 066 (2008);
-%Phys.\ Lett.\ B {\bf 704}, 15 (2011);
-%Phys.\ Rev.\  D {\bf 75}, 011103 (2007);
-%JHEP {\bf 0911}, 083 (2009);
-%Phys.\ Rev.\ C {\bf 81}, 035202 (2010);
-%JHEP {\bf 1210}, 042 (2012).
 

### 2018-07-09 eg6-letters/incoherent/incoherent_prl.tex
Implement the last corrections from stepan

@@
 experiments have uncovered the partonic structure of the nucleon and 
-the longitudinal momentum distributions of the 
-constituents partons, i.e., quarks and gluons \cite{pdg}.  
-With nuclear targets, deeply inelastic lepton scattering measurements 
-have revealed the fact that the 
-distribution of quarks in a nucleus is not a simple convolution of 
-their distributions within nucleons, an observation known as the ``EMC 
-effect''\cite{EMC_first} (for reviews on the topic, see  
+the longitudinal momentum distributions of the constituent partons, i.e., 
+quarks and gluons \cite{pdg}.  With nuclear targets, deeply inelastic lepton 
+scattering measurements have revealed the fact that the distribution of quarks 
+in a nucleus is not a simple convolution of their distributions within 
+nucleons, an observation known as the ``EMC effect''\cite{EMC_first} (for 
+reviews on the topic, see  
 \cite{Arneodo:1992wf,Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}).
@@
 
-In the 
-Bjorken regime, i.e, large virtual photon four-momentum squared 
-($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small invariant momentum transfer ($t=(p-p^\prime)^2$), the 
-DVCS scattering process can be factorized, leaving the non-perturbative structure 
-of the nucleon to be parametrized in terms of four chirally-even GPDs: $H$, 
-$E$, $\widetilde{H}$, and $\widetilde{E}$, representing the four helicity-spin 
-combinations of the quark-nucleon states \cite{Freund_Collins,Ji_Osborne}.
-
 \begin{figure}[tb]
@@
 asymmetry (BSA) in deeply virtual electroproduction of a real photon off a bound 
-proton in $^{4}$He. FIG.~\ref{fig:diags} illustrates the 
-leading-twist handbag diagram for this process. Experimentally, we measure the squared sum of the 
-Bethe-Heitler (BH) and the DVCS amplitudes. The BH process, 
-where the real photon is emitted by the incident or the scattered electron 
-rather than the nucleon, dominates the cross section at our kinematics. The BSA arises from the interference 
-of these two terms and is directly sensitive to the DVCS amplitude that contain 
-the information on the GPDs. Using a longitudinally polarized electron beam 
-(L) and an unpolarized target (U), the BSA is defined as:
+proton in $^{4}$He. FIG.~\ref{fig:diags} illustrates the leading-twist handbag 
+diagram for this process. In the Bjorken regime, i.e, large virtual photon 
+four-momentum squared ($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small invariant 
+momentum transfer ($t=(p-p^\prime)^2$), the DVCS scattering process can be 
+factorized, leaving the non-perturbative structure of the nucleon to be 
+parametrized in terms of four chirally-even GPDs: $H$, $E$, $\widetilde{H}$, 
+and $\widetilde{E}$, representing the four helicity-spin combinations of the 
+quark-nucleon states \cite{Freund_Collins,Ji_Osborne}. Experimentally, we 
+measure the squared sum of the Bethe-Heitler (BH) and the DVCS amplitudes. The 
+BH process, where the real photon is emitted by the incident or the scattered 
+electron rather than the nucleon, dominates the cross section at our 
+kinematics. The BSA arises from the interference of these two terms and is 
+directly sensitive to the DVCS amplitude that contain the information on the 
+GPDs. Using a longitudinally polarized electron beam (L) and an unpolarized 
+target (U), the BSA is defined as:
 \begin{equation}
@@
 was evaluated to be of 6.5\% by selecting events passing all our selection cuts but originating from 
-different vertices. The $\pi^0$ contamination was estimated using detector simulation and experimental 
-data. From simulation, we calculated the ratio ($R = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) 
-of the number of $\pi^0$ 
-events that are wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the 
-number of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$. Then 
-in each kinematical bin and for 
-each beam-helicity state, the $\pi^0$-subtracted experimental DVCS events is 
-calculated as $N = N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow 
-e'p'\pi^0}_{exp}$, where $N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is the 
-number of $ep\rightarrow e'p'\gamma$ ($ep\rightarrow e'p'\pi^0$) experimentally identified. Depending on the 
-kinematics, we found this contamination to be of 8 to 10\%.
+different vertices. The $\pi^0$ contamination was estimated using detector 
+simulation and experimental data. From simulation, we calculated the ratio ($R 
+= N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ events that 
+are wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the 
+number of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$.  
+Then in each kinematical bin and for each beam-helicity state, the 
+$\pi^0$-subtracted experimental DVCS events is calculated as $N = 
+N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow e'p'\pi^0}_{exp}$, where 
+$N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is 
+the number of the experimentally identified $ep\rightarrow e'p'\gamma$ 
+($ep\rightarrow e'p'\pi^0$). Depending on the kinematics, we found this 
+contamination to be of 8 to 10\%.
 
@@
 
+\bibitem{Hattawy:thesis}
+M.~Hattawy, Ph.D. thesis, Universit{\'e} Paris Sud - Paris XI, France, 2015 
+[Institution Report No. 2015PA112161].
+
 \bibitem{Dupre:2017upj} 

### 2018-07-09 eg6-letters/incoherent/incoherent_prl.tex
minor correction

@@
 the number of the experimentally identified $ep\rightarrow e'p'\gamma$ 
-($ep\rightarrow e'p'\pi^0$). Depending on the kinematics, we found this 
+($ep\rightarrow e'p'\pi^0$) events. Depending on the kinematics, we found this 
 contamination to be of 8 to 10\%.

### 2018-07-12 eg6-letters/incoherent/incoherent_prl.tex
edit the acknowledgment for ahmed's institution

@@
 possible. This work was supported in part by the Chilean Comisi\'on Nacional de 
-Investigaci\'on Cient\'ifica y Tecnol\'ogica (CONICYT), the Italian Instituto 
-Nazionale di Fisica Nucleare, the French Centre National de la Recherche 
-Scientifique, the French Commissariat \`a l'Energie Atomique, the U.S.  
-Department of Energy under Contract No. DE-AC02-06CH11357, the United Kingdom 
-Science and Technology Facilities Council (STFC), the Scottish Universities 
-Physics Alliance (SUPA), the National Research Foundation of Korea, and the 
-Office of Research and Economic Development at Mississippi State University.  
-M.~Hattawy also acknowledges the support of the Consulat G\'en\'eral de France 
-\`a J\'erusalem.  The Southeastern Universities Research Association operates 
-the Thomas Jefferson National Accelerator Facility for the United States 
-Department of Energy under Contract No. DE-AC05-06OR23177.
+Investigaci\'on Cient\'ifica y Tecnol\'ogica (CONICYT), by CONICYT PIA grant 
+ACT1413, the Italian Instituto Nazionale di Fisica Nucleare, the French Centre 
+National de la Recherche Scientifique, the French Commissariat \`a l'Energie 
+Atomique, the U.S.  Department of Energy under Contract No. DE-AC02-06CH11357, 
+the United Kingdom Science and Technology Facilities Council (STFC), the 
+Scottish Universities Physics Alliance (SUPA), the National Research Foundation 
+of Korea, and the Office of Research and Economic Development at Mississippi 
+State University.  M.~Hattawy also acknowledges the support of the Consulat 
+G\'en\'eral de France \`a J\'erusalem.  The Southeastern Universities Research 
+Association operates the Thomas Jefferson National Accelerator Facility for the 
+United States Department of Energy under Contract No. DE-AC05-06OR23177.
 

### 2018-08-09 eg6-letters/incoherent/adhocreview/1st_adhoc_comments.tex
push the adhoc comments

%\documentclass[a4paper,11pt,twoside]{ThesisStyle}
\documentclass[a4paper,11pt,twoside]{article}

\title{First round comments from the Ad-hoc rewiew committee \\
 (Maurik Holtrop , Kevin Giovankl, and Zein-Eddine Meziani)}

\date{\today}
\include{formatAndDefs}

\begin{document}

\maketitle

\section*{}

Dear Mohammad Hattawy,

We have reviewed your paper, "First exclusive Deeply Virtual Compton Scattering measurement off bound nucleon in $^4$He", and have compiled an initial set of comments.\\

First, we think these are interesting results, and we think that the paper is fairly well written.\\

We would like to ask for some clarification on several points, and suggest that these are addressed in the paper. The following list is loosely arranged in order of importance: \\

\begin{enumerate}

\item    For figure 6, you state that "our experiment shows a sharp drop" (line 
   250), in the incoherent $A_{LU}$/proton $A_{LU}$. You do indeed have a 
      single point, at the lowest $x_B$, that is lower than the other three, 
      but it seems that I can draw a straight horizontal line through all 4 
      error bars. It seems too strong a statement to speak of a sharp drop 
      here, and subsequently conclude that there is "strong quenching of the 
      BSA" (line 253). If I contrast this graph with figure 5, where you state 
      that "$A_{LU}$ does not indicate a strong dependence on $Q^2$", I agree 
      with you. The variation between the point in figure 5 is however similar 
      to that in figure 6, except the order of the variation is different.\\ 
      \textcolor{blue}{ }

\item    To further consider this statement, I looked up ref. 21, which 
   contains the proton data that you divide by. This data is not, however, 
      shown as a function of $x_B$, but in a set of tiles, with variation in -t 
      shown for different $x_B$ and $Q^2$ average values. It is then not quite 
      clear how you used this data to get the data points to divide out the 
      proton $A_{LU}$. How closely do the kinematics agree? How does this 
      procedure affect the systematic uncertainties? This is important 
      information to make a judgement on the validity of your figure6.\\
   \textcolor{blue}{ }

\item  The paper makes no mention of the initial momentum of the struck 
   nucleon, which I would expect to smear out the kinematics. It would be 
      useful for the reader to get an impression on how large this effect would 
      be. Does this explain the widths of the distributions in figure 2, or are 
      these widths dominated by detector resolution?\\
   \textcolor{blue}{ }

\item    There is also no mention of final state interactions in the paper. It 
   is not obvious to me that the FSA should be zero for a beam spin asymmetry 
      on 4He. If you have a calculation that shows this is the case, it would 
      be good to mention it.\\
   \textcolor{blue}{ }

\end{enumerate}

There are also number of minor initial edits and stylistic suggestions that we 
would like you to consider. This list is in chronological order:

\begin{enumerate}

\item    In the title, add an "a":  "Deeply Virtual Compton Scattering off a bound proton", or make proton plural (protons).\\
   \textcolor{blue}{ }

\item    First sentence of abstract, does "measurement of incoherent deeply 
   virtual..." work better?\\
   \textcolor{blue}{ }

\item    Third sentence, replace "have been compared" with the more active "are compared"\\
   \textcolor{blue}{ }

\item    Line27: leave out "the fact"\\
   \textcolor{blue}{ }

\item    Rephrase line 34. Perhaps:  "correlations can be revealed"\\
   \textcolor{blue}{ }

\item    Line 46 - 49: Perhaps make it more clear that in the coherent case the scattering is off the entire nucleus, and that for the incoherent case the nucleon is ejected? Is that a correct interpretation of what is going on?\\
   \textcolor{blue}{ }

\item    Line 78: "amplitude that contains", or make amplitude plural.\\
   \textcolor{blue}{ }

\item    Line 154, you do not define what was used for $t_min$, and how it was 
   determined.\\
   \textcolor{blue}{ }

\item    Line 206: To make it more clear to the reader what you are doing with 
   the data, you should explicitly state that you make a fit of the $\phi$ 
      distributions, and then extract the $a_0$ value as $A_{LU}$(90). You 
      should also explicitly state that when plotting versus one kinematic 
      variable, you integrate over all the other kinematic variables. This 
      relates to comment \#2 above.\\
   \textcolor{blue}{ }

\item    Line 207: "Fig 4 presents ..." and line 215: "We present in Fig 5". 
   One is passive, the other active. It is probably better to choose one or the 
      other, but not mix them.\\
   \textcolor{blue}{ }

\item    Line 221: Either "Their model uses a nuclear spectral function" or 
   "Their model uses nuclear spectral functions".\\
   \textcolor{blue}{ }

\item    Line 238: -> "on a free proton target".\\
   \textcolor{blue}{ }

\item    Line 241: "ratios show 20\%-40\% lower asymmetries" (drop "a")\\
   \textcolor{blue}{ }

\item    Line 243: rewrite to not have "effect" twice in the sentence so close together.\\
   \textcolor{blue}{ }

\item    Line 260: Rewrite your last sentence. Suggestion: "This surprising 
   result opens a new avenue for progress in understanding quarks and gluons in 
      the nuclear medium."\\
   \textcolor{blue}{ }

\end{enumerate}

\end{document}

### 2018-08-09 eg6-letters/incoherent/incoherent_prl.tex
implementing some of the suggestions

@@
 
-\title{Deeply Virtual Compton Scattering measurement off bound proton}
+\title{Deeply Virtual Compton Scattering measurement off bound protons}
 
@@
 \begin{abstract}
- We report the first beam spin asymmetry (BSA) measurements in incoherent 
-   deeply virtual Compton scattering (DVCS) off $^4$He. The data were 
-   accumulated using a 6 GeV longitudinally 
-   polarized electron beam incident on a pressurized $^4$He gaseous target 
-   placed in front of the CLAS spectrometer in Hall-B at the Thomas Jefferson 
-   National Accelerator Facility. The azimuthal angular ($\phi$) dependence of 
-   the BSA is studied in a wide range of virtual photon and scattered proton 
-   kinematics. The Q$^2$, $x_B$, and $t$ dependencies of the BSA on the bound 
-   proton have been compared with the one on the free proton. In the whole 
-   kinematical region of our measurements, the BSA on the bound proton is 
-   smaller by $20\%$ to $40\%$, indicating possible medium modification 
-   of its partonic structure. This measurement opens a new avenue for 
-   studying structure of the bound nucleon and explore the origin of the EMC 
-   effect using the framework of the generalized parton distributions.
+ We report the first beam spin asymmetry (BSA) measurement of incoherent deeply 
+   virtual Compton scattering (DVCS) off $^4$He. The data were accumulated 
+   using a 6 GeV longitudinally polarized electron beam incident on a 
+   pressurized $^4$He gaseous target placed in front of the CLAS spectrometer 
+   in Hall-B at the Thomas Jefferson National Accelerator Facility. The 
+   azimuthal angular ($\phi$) dependence of the BSA is studied in a wide range 
+   of virtual photon and scattered proton kinematics. The Q$^2$, $x_B$, and $t$ 
+   dependencies of the BSA on the bound proton are compared with the one on the 
+   free proton. In the whole kinematical region of our measurements, the BSA on 
+   the bound proton is smaller by $20\%$ to $40\%$, indicating possible medium 
+   modification of its partonic structure. This measurement opens a new avenue 
+   for studying structure of the bound nucleon and explore the origin of the 
+   EMC effect using the framework of the generalized parton distributions.
 
@@
 quarks and gluons \cite{pdg}.  With nuclear targets, deeply inelastic lepton 
-scattering measurements have revealed the fact that the distribution of quarks 
-in a nucleus is not a simple convolution of their distributions within 
-nucleons, an observation known as the ``EMC effect''\cite{EMC_first} (for 
-reviews on the topic, see  
-\cite{Arneodo:1992wf,Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}).
+scattering measurements have revealed that the distribution of quarks in a 
+nucleus is not a simple convolution of their distributions within nucleons, an 
+observation known as the ``EMC effect''\cite{EMC_first} (for reviews on the 
+topic, see  \cite{Arneodo:1992wf,Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}).
 
@@
 between the momentum and spatial degrees of freedom of the partons. These 
-correlations are set to be revealed through deeply virtual Compton scattering 
-(DVCS), i.e., the hard exclusive lepto-production of a real photon, which 
-provides access to a three-dimensional imaging of partons within the 
-generalized parton distributions (GPDs) framework 
+correlations can be revealed through deeply virtual Compton scattering (DVCS), 
+i.e., the hard exclusive lepto-production of a real photon, which provides 
+access to a three-dimensional imaging of partons within the generalized parton 
+distributions (GPDs) framework 
 \cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.   
@@
 nucleus~\cite{Dupre:2015jha}. In the nuclear case however, two channels are available,
-the coherent channel where the nucleus is left intact \cite{Airapetian:2009cga,
-Hattawy:2017woc}, and the incoherent channel where the DVCS happens on a nucleon.
+the coherent channel where the scattering is off the entire nucleus, which is 
+left intact in the final state \cite{Airapetian:2009cga,
+Hattawy:2017woc}, and the incoherent channel where the DVCS happens on a 
+nucleon, which is ejected from the nucleus.
 The latter, which is the focus of this letter, provides a unique access to the 
@@
 kinematics. The BSA arises from the interference of these two terms and is 
-directly sensitive to the DVCS amplitude that contain the information on the 
+directly sensitive to the DVCS amplitude that contains the information on the 
 GPDs. Using a longitudinally polarized electron beam (L) and an unpolarized 

### 2018-08-10 eg6-letters/incoherent/adhocreview/1st_adhoc_comments.tex
implementing some of the suggestions
implement all the minor corrections

@@
 \title{First round comments from the Ad-hoc rewiew committee \\
- (Maurik Holtrop , Kevin Giovankl, and Zein-Eddine Meziani)}
+ (Maurik Holtrop, Kevin Giovankl, Zein-Eddine Meziani)}
 
@@
 \item    In the title, add an "a":  "Deeply Virtual Compton Scattering off a bound proton", or make proton plural (protons).\\
-   \textcolor{blue}{ }
+   \textcolor{blue}{Updated. "protons"}
 
@@
    virtual..." work better?\\
-   \textcolor{blue}{ }
+   \textcolor{blue}{Updated. }
 
 \item    Third sentence, replace "have been compared" with the more active "are compared"\\
-   \textcolor{blue}{ }
+   \textcolor{blue}{Replaced. }
 
 \item    Line27: leave out "the fact"\\
-   \textcolor{blue}{ }
+   \textcolor{blue}{Cleaned. }
 
 \item    Rephrase line 34. Perhaps:  "correlations can be revealed"\\
-   \textcolor{blue}{ }
+   \textcolor{blue}{Cleaned. }
 
@@
 Is that a correct interpretation of what is going on?\\
-   \textcolor{blue}{ }
+   \textcolor{blue}{Updated.}
 
 \item    Line 78: "amplitude that contains", or make amplitude plural.\\
-   \textcolor{blue}{ }
+   \textcolor{blue}{Cleaned.}
 
-\item    Line 154, you do not define what was used for $t_min$, and how it was 
-   determined.\\
-   \textcolor{blue}{ }
+\item    Line 154, you do not define what was used for $t_{min}$, and how it 
+   was determined.\\
+   \textcolor{blue}{The definitions is added.}
 
@@
       relates to comment \#2 above.\\
-   \textcolor{blue}{ }
+      \textcolor{red}{Cleaned. ( I am not sure this is needed as it is 
+      mentioned at the beginning of the paragraph).}
 
@@
       other, but not mix them.\\
-   \textcolor{blue}{ }
+   \textcolor{blue}{Cleaned.}
 
@@
    "Their model uses nuclear spectral functions".\\
-   \textcolor{blue}{ }
+   \textcolor{blue}{Cleaned.}
 
 \item    Line 238: -> "on a free proton target".\\
-   \textcolor{blue}{ }
+   \textcolor{blue}{Corrected. }
 
 \item    Line 241: "ratios show 20\%-40\% lower asymmetries" (drop "a")\\
-   \textcolor{blue}{ }
+   \textcolor{blue}{Corrected.}
 
 \item    Line 243: rewrite to not have "effect" twice in the sentence so close together.\\
-   \textcolor{blue}{ }
+   \textcolor{blue}{Cleaned.}
 
@@
       the nuclear medium."\\
-   \textcolor{blue}{ }
+   \textcolor{blue}{Added.}
 

### 2018-08-10 eg6-letters/incoherent/incoherent_prl.tex
implement all the minor corrections

@@
 electron and the proton in the event originated from the same vertex at the 
-target. The photons were detected in 
-either the IC or the CLAS electromagnetic calorimeter. All the clusters within 
-the IC fiducial region were assumed to be photons, while a timing cut is used 
-to clean the EC photons from neutrons. Note that even though the DVCS reaction 
-has only one real photon in the final state, events with more than one photon 
-were not discarded at this stage. These extra photons are mostly soft photons from accidental 
-coincidence which, as will be discussed below, the DVCS exclusivity cuts 
-eliminate easily. In the following selection stage, the most energetic photon 
-is considered as the DVCS photon candidate (see \cite{Hattawy:thesis} for 
-additional details on the particles identification).
+target. The photons were detected in either the IC or the CLAS electromagnetic 
+calorimeter. All the clusters within the IC fiducial region were assumed to be 
+photons, while a timing cut is used to clean the EC photons from neutrons. Note 
+that even though the DVCS reaction has only one real photon in the final state, 
+events with more than one photon were not discarded at this stage. These extra 
+photons are mostly soft photons from accidental coincidence which, as will be 
+discussed below, the DVCS exclusivity cuts eliminate easily. In the following 
+selection stage, the most energetic photon is considered as the DVCS photon 
+candidate (see \cite{Hattawy:thesis} for additional details on the particles 
+identification).
 
@@
 mass (W$=(q+p)^2$) greater than 2 GeV to avoid the nucleon resonance region. 
-The $t$, transferred momentum squared to the recoil proton assuming an 
-on-shell proton at rest, was required to be greater than a minimum allowed 
-value at given Q$^2$ and W ($t~>~t_{min}$).  Then, the exclusivity of the 
-incoherent DVCS events was ensured by imposing constraints on the kinematical 
-variables resulting from conserving the four-momentum in the reaction 
-$ep\rightarrow e'p'\gamma$. These kinematical variables are: the coplanarity 
-angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) 
-planes, the missing energy, mass, and transverse momentum of the $e'\gamma$ and 
-$e'p'\gamma$ systems, the missing mass squared of the $e'p'$ system, and the 
-angle $\theta$ between the measured photon and the missing momentum of the 
-$e'p'$ system. The experimental data for the most relevant exclusivity 
-variables are shown in FIG.~\ref{fig:kin-cuts}. We also rejected events where a 
-$\pi^0$ was identified by the invariant mass of two photons. At the end of
+The $t$, transferred momentum squared to the recoil proton assuming an on-shell 
+proton at rest, was required to be greater than a minimum allowed value at 
+given Q$^2$ and W ($t>~t_{min}(=~- Q^{2}~\frac{2(1- x_{B})(1~-~\sqrt{1 
++~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$,
+where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
+proton mass). Then, the exclusivity of the incoherent DVCS events was ensured 
+by imposing constraints on the kinematical variables resulting from conserving 
+the four-momentum in the reaction $ep\rightarrow e'p'\gamma$.  These 
+kinematical variables are: the coplanarity angle $\Delta\phi$ between the 
+($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) planes, the missing energy, mass, and 
+transverse momentum of the $e'\gamma$ and $e'p'\gamma$ systems, the missing 
+mass squared of the $e'p'$ system, and the angle $\theta$ between the measured 
+photon and the missing momentum of the $e'p'$ system. The experimental data for 
+the most relevant exclusivity variables are shown in FIG.~\ref{fig:kin-cuts}.  
+We also rejected events where a $\pi^0$ was identified by the invariant mass of 
+two photons. At the end of
 this selection process, about 30k events 
@@
 That is, four bins in one of the kinematical variable of interest ($Q^{2}$, 
-$x_{B}$ or $t$) and nine bins in the azimuthal angle ($\phi$).  
+$x_{B}$, or $t$) and then nine bins in the azimuthal angle ($\phi$).   
 FIG.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
-$\phi$ in bins of $Q^{2}$, $x_{B}$, and $t$. The curves on the plots are fits 
-of the form $\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$. The main contributions 
-to systematic uncertainties on these fits are from the choice of the DVCS 
-exclusivity cuts (6\%) and the large bin size (7\%). The systematic uncertainties
-sum up to less than 10\% for all data points and thus always remain significantly 
-smaller than the statistical errors.
+$\phi$ in bins of $Q^{2}$ (integarted over full $x_{B}$ and $t$ ranges), 
+$x_{B}$ (integarted over full $Q^{2}$ and $t$ ranges), and $t$ (integarted over 
+full $Q^{2}$ and $x_{B}$ ranges). The curves on the plots are fits of the form 
+$\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$.  The main contributions to 
+systematic uncertainties on these fits are from the choice of the DVCS 
+exclusivity cuts (6\%) and the large bin size (7\%). The systematic 
+uncertainties sum up to less than 10\% for all data points and thus always 
+remain significantly smaller than the statistical errors.
 
@@
 
-We present in FIG.~\ref{fig:alu90} the dependence of the fitted $A_{LU}$ 
-values at $\phi$~=~90$^{\circ}$ on the kinematical variables $Q^2$, $x_{B}$, 
-and $t$. Within the given uncertainties, $A_{LU}$ does not indicate a strong 
-dependence on $Q^2$. The $x_{B}$ and $t$ dependencies are compared to 
-theoretical calculations performed by S.~Liuti and K.~Taneja 
-\cite{simonetta_2}. Their model uses nuclear spectral function and 
-considers mainly off-shell effects. The calculations are carried out at slightly 
-different kinematics than our data but still provide important guidance. The 
-experimental results appear to have smaller asymmetries especially at low 
-$x_{B}$ than the calculations. These differences may arise from nuclear 
-effects which are not taken into account in the model, such as long-range 
-interactions. On the graph for $-t$ dependence, we show previous measurements 
-by the HERMES collaboration \cite{Airapetian:2009cga}, in which only electrons
+FIG.~\ref{fig:alu90} presents the dependence of the fitted $A_{LU}$ values at 
+$\phi$~=~90$^{\circ}$ ($a_{0}$ parameter from the individual fits in 
+FIG.~\ref{fig:alu}) on the kinematical variables $Q^2$, $x_{B}$, and $t$.  
+Within the given uncertainties, $A_{LU}$ does not indicate a strong dependence 
+on $Q^2$.  The $x_{B}$ and $t$ dependencies are compared to theoretical 
+calculations performed by S.~Liuti and K.~Taneja \cite{simonetta_2}. Their 
+model uses a nuclear spectral function and considers mainly off-shell effects.  
+The calculations are carried out at slightly different kinematics than our data 
+but still provide important guidance. The experimental results appear to have 
+smaller asymmetries especially at low $x_{B}$ than the calculations. These 
+differences may arise from nuclear effects which are not taken into account in 
+the model, such as long-range interactions.  On the graph for $-t$ dependence, 
+we show previous measurements by the HERMES collaboration 
+\cite{Airapetian:2009cga}, in which only electrons
 and photons were measured. Due to the large experimental uncertainties of the HERMES 
@@
 One can use the nuclear DVCS to measure a ``generalized'' EMC effect in order 
-to see if significant nuclear effects are also visible within the GPD framework. 
-To explore this idea, we construct 
-the ratio of $A_{LU}$ for bound protons to that on free proton target.  
-FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the 
-BSA ratio based on interpolation of the free proton asymmetries from  
-CLAS \cite{Girod:2007aa} as a function of the kinematical variable
-$x_B$. The $A_{LU}$ ratios show a 20\%-40\% lower asymmetries for a bound proton compared 
-to the free proton mirroring a form of EMC effect but with a surprising 
-large effect, in particular at low $x_B$. The measurements disagree with the off-shell \cite{simonetta_2} 
-and the on-shell calculations that use the medium modified GPDs as calculated from 
-the quark-meson coupling model \cite{Guzey:2008fe}. In particular, the difference becomes
-large at lower $x_B$, 
-where the off-shell model predicts an enhancement of the ratio, where our experiment 
-shows a sharp drop. This measurement shows that an important nuclear effect is
-missing from the existing models in order to explain this strong quenching of
-the BSA.
+to see if significant nuclear effects are also visible within the GPD 
+framework.  To explore this idea, we construct the ratio of $A_{LU}$ for bound 
+protons to that on a free proton target. 
+FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the BSA ratio based on 
+interpolation of the free proton asymmetries from  CLAS \cite{Girod:2007aa} as 
+a function of the kinematical variable $x_B$. The $A_{LU}$ ratios show 
+20\%-40\% lower asymmetries for a bound proton compared to the free proton 
+mirroring a form of EMC effect but with a surprising large modification, in 
+particular at low $x_B$. The measurements disagree with the off-shell 
+\cite{simonetta_2} and the on-shell calculations that use the medium modified 
+GPDs as calculated from the quark-meson coupling model \cite{Guzey:2008fe}. In 
+particular, the difference becomes large at lower $x_B$, where the off-shell 
+model predicts an enhancement of the ratio, where our experiment shows a sharp 
+drop. This measurement shows that an important nuclear effect is missing from 
+the existing models in order to explain this strong quenching of the BSA.
 
@@
 the partonic level. The bound-proton BSA is largely suppressed compared to 
-the free proton BSA. This surprising result opens a new avenue 
-for progress in the understanding of the quarks and gluons behavior in the
-nuclear medium.
+the free proton BSA. This surprising result opens a new avenue for progress in 
+the understanding quarks and gluons in the nuclear medium.
 

### 2018-08-10 eg6-letters/incoherent/adhocreview/1st_adhoc_comments.tex
first response to the adhon comments

@@
       to that in figure 6, except the order of the variation is different.\\ 
-      \textcolor{blue}{ }
+      \textcolor{red}{Should we keep it then? }
 
@@
       information to make a judgement on the validity of your figure6.\\
-   \textcolor{blue}{ }
+   \textcolor{blue}{For this specific purpose, we applied four dimensional 
+      binning to our incoherent DVCS data to get kinematical mean values close 
+      to the published free proton results. The review committee members are 
+      invited to check our kinematical distributions in 
+      fig.~\ref{fig:incoh-kin} for the shown bins in FIG.~6 in the PRL and the 
+      free proton data highlighted in figure \ref{fig:free-p}. }
+
+\begin{figure}[h!]
+   \includegraphics[width=14.9cm]{t_InCoh_bins.pdf}
+   \caption{The t, $Q^2$ and $x_{B}$ distributions for the incoherent DVCS bins 
+   shown in figure 6 in the prl.}
+\label{fig:incoh-kin}
+\end{figure}
+
+\begin{figure}[h!]
+\includegraphics[width=14.9cm]{e1dvcs1_free_proton_alu.pdf}
+   \caption{The free proton published beam-spin asymmetries. The highlighted 
+   data points are the ones used to construct the beam-spin asymmetry rations 
+   in FIG.~6 in the PRL.}
+\label{fig:free-p}
+\end{figure}
 
@@
       these widths dominated by detector resolution?\\
-   \textcolor{blue}{ }
+   \textcolor{blue}{We have studied this effect in details. The review 
+      committee members are invited to check appendix H in the analysis note 
+      \url{ 
+      https://www.jlab.org/Hall-B/shifts/index.php?display=admin&task=paper_review&rid=7619165&operation=view}.}
 
-\item    There is also no mention of final state interactions in the paper. It 
-   is not obvious to me that the FSA should be zero for a beam spin asymmetry 
-      on 4He. If you have a calculation that shows this is the case, it would 
-      be good to mention it.\\
-   \textcolor{blue}{ }
+\item  There is also no mention of final state interactions in the paper. It is 
+   not obvious to me that the FSA should be zero for a beam spin asymmetry on 
+      4He. If you have a calculation that shows this is the case, it would be 
+      good to mention it.\\
+   \textcolor{blue}{There are no such theoretical calculations of the FSI on 
+      the incoherent DVCS asymmetries on the $^4$He. }
 
 \end{enumerate}
+
+\newpage
+\newpage
+\newpage
+\newpage
 

### 2018-08-13 eg6-letters/incoherent/incoherent_prl.tex
implement Stepan's comments

@@
 particular, the difference becomes large at lower $x_B$, where the off-shell 
-model predicts an enhancement of the ratio, where our experiment shows a sharp 
-drop. This measurement shows that an important nuclear effect is missing from 
-the existing models in order to explain this strong quenching of the BSA.
+model predicts an enhancement of the ratio, while our experiment shows no sign 
+of an increase of ratios. This measurement shows that an important nuclear 
+effect is missing from the existing models in order to explain this strong 
+quenching of the BSA.
 

### 2018-08-13 eg6-letters/incoherent/adhocreview/1st_adhoc_comments.tex
implement Stepan's comments
Advance adhoc response for incoherent

@@
       to that in figure 6, except the order of the variation is different.\\ 
-      \textcolor{red}{Should we keep it then? }
+      \textcolor{blue}{The text is updated.}
 
@@
       free proton data highlighted in figure \ref{fig:free-p}. }
+      \textcolor{red}{Figure provided are not corresponding. Moreover, we talk 
+      about extrapolating free proton data in the paper. Yet, it appears 
+      that we are rather rebinning the eg6 data. We should update figures
+      (including in the analysis note) and rephrase the statement in the 
+      paper.}
 
@@
       these widths dominated by detector resolution?\\
-   \textcolor{blue}{We have studied this effect in details. The review 
+   \textcolor{blue}{We have studied this effect, we updated the paper to
+      address the question. The review 
       committee members are invited to check appendix H in the analysis note 
+      for more details
       \url{ 
       https://www.jlab.org/Hall-B/shifts/index.php?display=admin&task=paper_review&rid=7619165&operation=view}.}
+   \textcolor{red}{Please Mohammad check what I added in the paper on this topic.}
 
@@
    \textcolor{blue}{There are no such theoretical calculations of the FSI on 
-      the incoherent DVCS asymmetries on the $^4$He. }
+      the incoherent DVCS asymmetries on the $^4$He. A statement has been added
+      toward the end to address this point.}
 

### 2018-08-13 eg6-letters/incoherent/incoherent_prl.tex
Advance adhoc response for incoherent

@@
 nucleon, which is ejected from the nucleus.
-The latter, which is the focus of this letter, provides a unique access to the 
+The latter is the focus of this letter and provides a unique access to the 
 modification of the partonic structure of the bound nucleons 
@@
 the most relevant exclusivity variables are shown in FIG.~\ref{fig:kin-cuts}.  
-We also rejected events where a $\pi^0$ was identified by the invariant mass of 
-two photons. At the end of
-this selection process, about 30k events 
+Because of the Fermi motion of the nucleons in the helium nucleus, these cuts
+are slightly wider than those previously used for free proton experiments~%
+\cite{Girod:2007aa}. After the corrections discussed below, the assymetries 
+appear to be stable as a function of cut width and we see no sizeable effect 
+that can be related to the initial momentum of the nucleons. We also rejected 
+events where a $\pi^0$ was identified by the invariant mass of 
+two photons. At the end of this selection process, about 30k events 
 passed all the requirements; their kinematic distributions are shown in 
@@
 20\%-40\% lower asymmetries for a bound proton compared to the free proton 
-mirroring a form of EMC effect but with a surprising large modification, in 
+mirroring the EMC effect but with a surprising large modification, in 
 particular at low $x_B$. The measurements disagree with the off-shell 
@@
 effect is missing from the existing models in order to explain this strong 
-quenching of the BSA.
+quenching of the BSA. More theoretical developments will be needed to identify 
+the origin of this quenching, in particular it will be key to differenciate 
+initial from final state effects and how they can affect the DVCS assymetries.
 

### 2018-08-22 analysis-note-vf/Appendix.tex
clean the appendix with the right A.16 equation
add the incoherent 4D binning

@@
 \frac{1-xA+\frac{\sqrt{1+\epsilon^2}-1}{2}}{1+\epsilon^2} 
-\frac{t-t_{min}}{Q^{2}} \right) \cdot F_{A}(t) \label{eq:s1I}
+\frac{t-t_{min}}{Q^{2}} \right) \label{eq:s1I}
 \end{eqnarray}
@@
 unless a major objections appear.
+
+\chapter{Binning the incoherent DVCS data to match the free proton DVCS 
+published data}
+
+\begin{figure}[h!]
+   \centering
+   \includegraphics[height=17.0cm]{4D-incoh-bin/4D-Q2_InCoh_bins.pdf}
+   \caption{First row: the four bins in $Q^2$ of the incoherent DVCS events.  
+   Second row: the associated distributions of $t$ for the bins in $Q^2$.  
+   Third row: the associated distributions of $x_B$ for the bins in $Q^2$.}
+\label{fig:incoh_Q2-bins-freep}
+\end{figure}
+
+\begin{figure}[h!]
+   \centering
+   \includegraphics[height=17.0cm]{4D-incoh-bin/4D-xB_InCoh_bins.pdf}
+   \caption{ First row: the four bins in $x_B$ of the incoherent DVCS events.  
+   Second row: the associated distributions of $t$ for the bins in $x_B$.    
+   Third row: the associated distributions of $Q^2$ for the bins in $x_B$.}
+\label{fig:incoh_xB-bins-freep}
+\end{figure}
+
+\begin {table}[!h]
+\begin{center}
+\begin{tabular}{|l|l|l|l|l|l|l|l|}
+\hline
+<$x_{B}$> & <$Q^2$> & <-t> & $\alpha$ & $\Delta \alpha$ &  $\beta$ & $\Delta 
+   \beta$ & $\chi^{2}$\\
+\hline
+0.238  & 1.89 & 0.14 & 0.243 & 0.013 & -0.02 & 0.09 & 1.0\\
+\hline
+0.249  & 1.95 & 0.28 & 0.275 & 0.014 & -0.06 & 0.09 & 1.3\\
+\hline
+0.249  & 1.95 & 0.49 & 0.200 & 0.026 & -0.36 & 0.15 & 1.3\\
+\hline
+0.248  & 1.94 & 0.77 & 0.172 & 0.035 & 0.01 &  0.31 & 0.3\\
+\hline
+\end{tabular}
+   \caption{free proton DVCS $Q^{2}$ and $x_{B}$ bins
+   \ref{fig:ic_alpha_beta_fitting}.}
+\label{Table:freeproton-t_bins}
+\end{center}
+\end{table}
+
+\begin{figure}[h!]
+   \centering
+   \includegraphics[height=17.0cm]{4D-incoh-bin/4D-t_InCoh_bins.pdf}
+   \caption{ First row: the four bins in $t$ of the incoherent DVCS events.  
+   Second row: the associated distributions of $Q^2$ for the bins in $t$.  
+   Third row: the associated distributions of $x_B$ for the bins in $t$.}
+\label{fig:incoh_xB-bins-freep}
+\end{figure}
+
+\begin {table}[!h]
+\begin{center}
+\begin{tabular}{|l|l|l|l|l|l|l|l|}
+\hline
+<$x_{B}$> & <$Q^2$> & <-t> & $\alpha$ & $\Delta \alpha$ &  $\beta$ & $\Delta 
+   \beta$ & $\chi^{2}$\\
+\hline
+0.177 & 1.56 & 0.14 & 0.19 & 0.009 & -0.03 & 0.12  & 2.3\\
+\hline
+0.249 & 1.95 & 0.28 & 0.275 & 0.014 & -0.06 & 0.09  & 1.3\\
+\hline
+0.345 & 2.64 & 0.30 & 0.269 & 0.019 & 0.29 & 0.15  & 0.3\\
+\hline
+0.471 & 3.34 & 0.78 & 0.262 & 0.052 & -0.23 & 0.25  & 0.9\\
+\hline
+\end{tabular}
+   \caption{free proton DVCS $Q^{2}$ and $x_{B}$ bins
+   \ref{fig:ic_alpha_beta_fitting}.}
+\label{Table:freeproton-x_Q2_bins}
+\end{center}
+\end{table}

### 2018-08-22 analysis-note-vf/4D-incoh-bin/BSA_InCoherent_Q2.C

@@ -1,0 +1,640 @@
+void BSA_InCoherent_Q2()
+{
+//=========Macro generated from canvas: c15/Incoherent channel
+//=========  (Tue Aug 21 12:00:25 2018) by ROOT version6.09/01
+   TCanvas *c15 = new TCanvas("c15", "Incoherent channel",0,0,1200,400);
+   gStyle->SetOptFit(1);
+   c15->Range(0,0,1,1);
+   c15->SetFillColor(0);
+   c15->SetBorderMode(0);
+   c15->SetBorderSize(2);
+   c15->SetLeftMargin(0.025);
+   c15->SetRightMargin(0.02325581);
+   c15->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: c15_1
+   TPad *c15_1 = new TPad("c15_1", "Incoherent channel_1",0,0,0.262936,0.9);
+   c15_1->Draw();
+   c15_1->cd();
+   c15_1->Range(-31.0033,-0.4888889,351.075,0.4);
+   c15_1->SetFillColor(0);
+   c15_1->SetBorderMode(0);
+   c15_1->SetBorderSize(2);
+   c15_1->SetGridx();
+   c15_1->SetGridy();
+   c15_1->SetRightMargin(0);
+   c15_1->SetTopMargin(0);
+   c15_1->SetFrameBorderMode(0);
+   c15_1->SetFrameBorderMode(0);
+   
+   TMultiGraph *multigraph = new TMultiGraph();
+   multigraph->SetName("");
+   multigraph->SetTitle("1.15<Q^{2}<1.89 [GeV^{2}/c^{2}]");
+   
+   Double_t Graph_fx1114[9] = {
+   22.83501,
+   62.34,
+   96.47249,
+   141.5276,
+   181.1347,
+   220.5213,
+   258.6931,
+   303.53,
+   335.4445};
+   Double_t Graph_fy1114[9] = {
+   0.1170777,
+   -0.01461722,
+   0.1838749,
+   0.202231,
+   0.008111727,
+   -0.1379145,
+   -0.1290101,
+   -0.2362785,
+   -0.003709615};
+   Double_t Graph_fex1114[9] = {
+   0,
+   0,
+   0,
+   0,
+   0,
+   0,
+   0,
+   0,
+   0};
+   Double_t Graph_fey1114[9] = {
+   0.06288827,
+   0.06411342,
+   0.05587873,
+   0.06378475,
+   0.07967556,
[…]

### 2018-08-24 analysis-note-vf/Appendix.tex
push the results for the 4D binning of the incoherent dvcs
more updates to the appendix

@@
 \end{tabular}
-   \caption{free proton DVCS $Q^{2}$ and $x_{B}$ bins
-   \ref{fig:ic_alpha_beta_fitting}.}
+   \caption{Free proton DVCS published asymmetries associated with the 
+   incoherent -t bins.}
 \label{Table:freeproton-t_bins}
@@
 \hline
-0.177 & 1.56 & 0.14 & 0.19 & 0.009 & -0.03 & 0.12  & 2.3\\
+0.177 & 1.56 & 0.14 & 0.190 & 0.009 & -0.03 & 0.12  & 2.3\\
 \hline
@@
 \end{tabular}
-   \caption{free proton DVCS $Q^{2}$ and $x_{B}$ bins
-   \ref{fig:ic_alpha_beta_fitting}.}
+   \caption{Free proton DVCS published asymmetries associated with the 1250 
+   incoherent $Q^{2}$ and $x_{B}$ bins.}
 \label{Table:freeproton-x_Q2_bins}
@@
 \end{table}
+
+\begin{figure}[tp]
+\centering
+\includegraphics[scale=0.52]{4D-incoh-bin/comp_ALU_ratioInc_Q2_shortscenrario.pdf}\\
+\includegraphics[scale=0.52]{4D-incoh-bin/comp_ALU_ratioInc_x_shortscenrario.pdf}\\
+\includegraphics[scale=0.52]{4D-incoh-bin/comp_ALU_ratioInc_t_shortscenrario.pdf}
+\caption{ The $A_{LU}$ ratio between the bound and the free proton at 
+   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
+   middle), and $t$ (on the bottom). The black squares are our results using 
+   the interpolation method to get the free proton asymmetries at our kinematic 
+   , the red squares are our results using the method of tuning our kinematics 
+   to get kinematics similar to the published free proton from E1DVCS1 
+   experiment. The gray band stands for the systematic errors calculated as the 
+   difference between the two extraction methods. The green circles are the 
+   HERMES inclusive measurement \cite{HERMES_BSA} results. The blue and red 
+   curves are from an on-shell calculations from S.  Liuti and K.  Taneja 
+   \cite{simonetta_2}. The solid and dashed black curves are from the off-shell 
+   calculations \cite{EMC_vadim_2}.} \label{fig:incoh_EMC_ratio_ALU_proton}
+\end{figure}

### 2018-08-24 eg6-letters/incoherent/incoherent_prl.tex
update the asymmetry ratio plot in the incoherent paper

@@
 %\includegraphics[width=6.9cm]{figs/ALU_ratioInc_Q2_shortscenrario.pdf}\\
-\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}
-%\includegraphics[width=8.5cm]{figs/ALU_ratioInc_t_shortscenrario.pdf}
+%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}
+\includegraphics[width=8.5cm]{figs/ALU_ratioInc_t_shortscenrario.pdf}
 \caption{ The $A_{LU}$ ratio of the bound to the free proton at 
-   $\phi$~=~90$^{\circ}$ as a function of $x_B$. The black squares are from this 
-   work, the green circle is the HERMES measurement 
-   \cite{Airapetian:2009cga}. The blue and red curves are results of off-shell 
-   calculations \cite{simonetta_2}. The solid and dashed black curves are from 
-   on-shell calculations \cite{Guzey:2008fe}.} 
+   $\phi$~=~90$^{\circ}$ as a function of $t$. The black squares are from this 
+   work, the green circle is the HERMES measurement \cite{Airapetian:2009cga}.  
+   The error bars represent the statistical uncertainties, while the gray bands 
+   represent the systematic uncertainties. The blue and red curves are results 
+   of off-shell calculations \cite{simonetta_2}. The solid and dashed black 
+   curves are from on-shell calculations \cite{Guzey:2008fe}.} 
    \label{fig:incoh_EMC_ratio_ALU_proton}

### 2018-08-27 eg6-letters/incoherent/incoherent_prl.tex
minor correction
some cleaning after stepans comments

@@
 FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the BSA ratio based on 
-interpolation of the free proton asymmetries from CLAS \cite{Girod:2007aa} as 
-a function of the kinematical variable $x_B$. The $A_{LU}$ ratios show 
-20\%-40\% lower asymmetries for a bound proton compared to the free proton 
-mirroring the EMC effect but with a surprising large modification, in 
-particular at low $x_B$. The measurements disagree with the off-shell 
-\cite{simonetta_2} and the on-shell calculations that use the medium modified 
-GPDs as calculated from the quark-meson coupling model \cite{Guzey:2008fe}. In 
-particular, the difference becomes large at lower $x_B$, where the off-shell 
-model predicts an enhancement of the ratio, while our experiment shows no sign 
-of an increase of ratios. This measurement shows that an important nuclear 
-effect is missing from the existing models in order to explain this strong 
-quenching of the BSA. More theoretical developments will be needed to identify 
-the origin of this quenching, in particular it will be key to differenciate 
-initial from final state effects and how they can affect the DVCS assymetries.
+interpolation of the free proton asymmetries from CLAS \cite{Girod:2007aa} as a 
+function of the kinematical variable $t$. The $A_{LU}$ ratios show 25\%-40\% 
+lower asymmetries and independent of $t$ for a bound proton compared to the 
+free proton. The measurements disagree with the off-shell \cite{simonetta_2} 
+and the on-shell calculations that use the medium modified GPDs as calculated 
+from the quark-meson coupling model \cite{Guzey:2008fe}. In particular, the 
+difference becomes large at lower $x_B$, where the off-shell model predicts an 
+enhancement of the ratio, while our experiment shows no sign of an increase of 
+ratios. This measurement shows that an important nuclear effect is missing from 
+the existing models in order to explain this strong quenching of the BSA. More 
+theoretical developments will be needed to identify the origin of this 
+quenching, in particular it will be key to differenciate initial from final 
+state effects and how they can affect the DVCS assymetries.
 
@@
    work, the green circle is the HERMES measurement \cite{Airapetian:2009cga}.  
-   The error bars represent the statistical uncertainties, while the gray bands 
-   represent the systematic uncertainties. The blue and red curves are results 
+   The error bars represent the statistical uncertainties, while the gray band 
+   represents the systematic uncertainties. The blue and red curves are results 
    of off-shell calculations \cite{simonetta_2}. The solid and dashed black 

### 2018-08-27 eg6-letters/incoherent/incoherent_prl.tex
some more cleaning

@@
 and the on-shell calculations that use the medium modified GPDs as calculated 
-from the quark-meson coupling model \cite{Guzey:2008fe}. In particular, the 
-difference becomes large at lower $x_B$, where the off-shell model predicts an 
-enhancement of the ratio, while our experiment shows no sign of an increase of 
-ratios. This measurement shows that an important nuclear effect is missing from 
-the existing models in order to explain this strong quenching of the BSA. More 
-theoretical developments will be needed to identify the origin of this 
-quenching, in particular it will be key to differenciate initial from final 
-state effects and how they can affect the DVCS assymetries.
+from the quark-meson coupling model \cite{Guzey:2008fe}. Our results show that 
+an important nuclear effect is missing from the existing models in order to 
+explain this strong quenching of the BSA.  More theoretical developments will 
+be needed to identify the origin of this quenching, in particular it will be 
+key to differenciate initial from final state effects and how they can affect 
+the DVCS assymetries.
 

### 2018-08-27 analysis-note-vf/Appendix.tex
add a chapter in the appendix for the nucleon dvcs theory

@@
 
+\chapter{ Angular dependence of the nucleon DVCS beam-spin asymmetry}
+
+Note: All the formulas have been derived from A.~V.~Belitsky, D.~Mueller and 
+A.~Kirchner,
+  %``Theory of deeply virtual Compton scattering on the nucleon,''
+Nucl.\ Phys.\ B {\bf 629}, 323 (2002).
+[hep-ph/0112108].
+%%CITATION = hep-ph/0112108%%
+
+The four-fold cross section for the process $e (k) h (P_1) \to e (k^\prime) h 
+(P_2) \gamma (q_2)$,
+
+\begin{eqnarray}
+\label{WQ}
+\frac{d\sigma}{d\Bx dy d|\Delta^2| d\phi }
+=
+\frac{\alpha^3  \Bx y } {16 \, \pi^2 \,  {\cal Q}^2 \sqrt{1 + \epsilon^2}}
+   \frac{ |{\cal T}_{\rm BH}|^2 + |{\cal T}_{\rm DVCS}|^2 + {\cal I} }{e^6} \, 
+   .
+   \eqname{eq.22\&23 in ref}
+\end{eqnarray}
+This cross section depends on the Bjorken variable $\Bx$, the squared
+momentum transfer $\Delta^2 = (P_2 - P_1)^2$, the lepton energy fraction $y
+= P_1\cdot q_1/P_1\cdot k$, with $q_1 = k - k'$, $\phi$ is the angle between 
+the lepton and hadron scattering planes, and $epsilon$ is defined as
+$\epsilon \equiv 2 \Bx \frac{M}{{\cal Q}}$
+
+The BH term $|{\cal T}_{\rm BH}|^2$, squared DVCS amplitude
+$|{\cal T}_{\rm DVCS}|^2$, and  interference term ${\cal I}$ read
+\begin{eqnarray}
+\label{Par-BH}
+&&|{\cal T}_{\rm BH}|^2
+= \frac{e^6}
+{\Bx^2 y^2 (1 + \epsilon^2)^2 \Delta^2\, {\cal P}_1 (\phi) {\cal P}_2 (\phi)}
+\left\{
+c^{\rm BH}_0
++  \sum_{n = 1}^2
+c^{\rm BH}_n \, \cos{(n\phi)} + s^{\rm BH}_1 \, \sin{(\phi)}
+\right\} \, ,
+   \eqname{eq.25 in ref}
+\\
+\label{AmplitudesSquared}
+&& |{\cal T}_{\rm DVCS}|^2
+=
+\frac{e^6}{y^2 {\cal Q}^2}\left\{
+c^{\rm DVCS}_0
++ \sum_{n=1}^2
+\left[
+c^{\rm DVCS}_n \cos (n\phi) + s^{\rm DVCS}_n \sin (n \phi)
+\right]
+\right\} \, ,
+   \eqname{eq.26 in ref}
+\\
+\label{InterferenceTerm}
+&&{\cal I}
+= \frac{\pm e^6}{\Bx y^3 \Delta^2 {\cal P}_1 (\phi) {\cal P}_2 (\phi)}
+\left\{
+c_0^{\cal I}
++ \sum_{n = 1}^3
+\left[
+c_n^{\cal I} \cos(n \phi) +  s_n^{\cal I} \sin(n \phi)
+\right]
+\right\} \, ,
+   \eqname{eq.27 in ref}
+\end{eqnarray}
+where the $+$ ($-$) sign in the interference stands for the negatively
+(positively) charged lepton.
+
+\section{Definition of some variables}
+
+The lepton BH propagators,
+
+\begin{eqnarray}
+\label{Par-BH-Pro}
+{\cal P}_1
+   &=&- \frac{1}{y (1 + \epsilon^2)} \left\{ J + 2 K \cos(\phi) \right\}
+\,\,
+   \eqname{eq.32 in ref}
+   \\
+{\cal P}_2
+   &=&
+1 + \frac{\Delta^2}{\cQ^2} +
+\frac{1}{y (1 + \epsilon^2)}\left\{J   + 2 K \cos(\phi)
+\right\}
+   \eqname{eq.32 in ref}
+\, ,
+\end{eqnarray}
+
+where
+\begin{eqnarray*}
+J =
+\left( 1 - y - \frac{y \epsilon^2}{2} \right)
+\left( 1 + \frac{\Delta^2}{\cQ^2} \right)
+-
+(1 - x) (2 - y) \frac{\Delta^2}{\cQ^2} \, .
+   \eqname{eq.32 in ref}
+\end{eqnarray*}
+
+\begin{equation}
+K^2 = -\frac{\Delta^2}{{\cal Q}^2} (1 - \Bx)
+\left( 1 - y - \frac{y^2\epsilon^2}{4} \right)
+\left( 1 - \frac{\Delta^2_{\rm min}}{\Delta^2} \right)
+\left\{
+\sqrt{1 + \epsilon^2}
++ \frac{4\Bx (1 - \Bx) + \epsilon^2}{4(1 - \Bx)}
+\frac{\Delta^2 - \Delta^2_{\rm min}}{{\cal Q}^2}
+\right\} \, ,
+   \eqname{eq.30 in ref}
+\end{equation}
+
+\begin{eqnarray}
+\label{Def-tmin}
+-\Delta_{\rm min}^2
+=  {\cal Q}^2
+\frac{2(1 - \Bx) \left(1 - \sqrt{1 + \epsilon^2}\right) + \epsilon^2}
+{4\Bx (1 - \Bx) + \epsilon^2}
+\approx \frac{M^2 \Bx^2}{1 - \Bx + \Bx M^2/{\cQ}^2}
+\, ,
+   \eqname{eq.31 in ref}
+\end{eqnarray}
+
+\begin{eqnarray}
+y(x,\cQ^2)
+=
+2 \frac{\sqrt{1 + \epsilon^2} - 1}{\epsilon^2}
+\approx
+1 - \frac{M^2 \Bx^2}{\cQ^2} \, .
+\end{eqnarray}
+
+\section{Beam-spin asymmetry}
+ At leading twist, the beam-spin asymmetry ($A_{LU}$) with two opposite 
+ helicities of a  longitudinally-polarized electron beam (L) on an unpolarized 
+ target (U) can be written as:
+
+ \begin{eqnarray}
+    \label{eq:coh_BSA}
+    \eqname{eq.176 in ref}
+A_{LU}& =& \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
+                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}\\
+    \eqname{}
+      & =& \frac{x_A(1+\epsilon^2)^2}{y} \, s_1^{\cal I} \sin(\phi) \, \bigg/ 
+      \, \bigg[ \, \sum_{n=0}^{n=2}c_n^{BH}\cos{(n\phi)} +  \\
+    & & \frac{x_A^2 t {(1+\epsilon^2)}^2}{Q^2} {\cal P}_1(\phi) {\cal 
+    P}_2(\phi) \, c_0^{DVCS} + \frac{x_A (1+\epsilon^2)^2}{y} \sum_{n=0}^{n=1} 
+    c_n^{\cal I} \cos{(n\phi)} \bigg].  
+ \nonumber 
+ \end{eqnarray}
+
+\subsection{Rewriting $A_{LU}$ in term of $\phi$ harmonics}
+$A_{LU}$ can be expressed as following
+
+ \begin{eqnarray}
+A_{LU}& =& \frac{\alpha_0 \sin(\phi)}
+                {\alpha_1 +  \alpha_2 \cos(\phi) + \alpha_3 \cos(2\phi) }   
+                \label{eq:coh_BSA_2}
+\end{eqnarray}
+with the kinematical variables $\alpha_{0,1,2,3}$ as
+
+ \begin{eqnarray}
+\alpha_{0}& =& \frac{x_A(1+\epsilon^2)^2}{y} \, {\color{blue} s_1^{\cal I}},
+\nonumber\\
+\alpha_{1}& =& {\color{blue} c_0^{BH}} - \frac{x_A^2 t {(1+\epsilon^2)}^2}{Q^2}  \frac{1}{y (1 + \epsilon^2)}
+\left( (J+K) (1 + \frac{\Delta^2}{\cQ^2}) + \frac{J^2 + 2K^2}{y (1 + \epsilon^2)} \right) {\color{blue} c_0^{DVCS}} + \frac{x_A (1+\epsilon^2)^2}{y} {\color{blue} c_0^{\cal I}},\\
+\nonumber\\
+\alpha_{2}& =& {\color{blue} c_1^{BH}} + \frac{x_A (1+\epsilon^2)^2}{y} {\color{blue} c_1^{\cal I}},
+\nonumber\\
+\alpha_{3}& =& {\color{blue} c_2^{BH}} - \frac{x_A^2 t {(1+\epsilon^2)}^2}{Q^2}  \frac{K}{y (1 + \epsilon^2)}
+\left( 1 + \frac{\Delta^2}{\cQ^2} + \frac{2K}{y (1 + \epsilon^2)} \right) {\color{blue} c_0^{DVCS} }
+\nonumber\\
+%\alpha_{4}& =& - \frac{x_A^2 t {(1+\epsilon^2)}^2}{Q^2}  \frac{2K}{y (1 + \epsilon^2)}
+%\left( 1 + \frac{\Delta^2}{\cQ^2} + \frac{2K}{y (1 + \epsilon^2)} \right) {\color{blue} c_0^{DVCS} }.
+%\nonumber\\
+ \label{eq:alphas_}
+\end{eqnarray}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Leading twist Fourier coefficients for unpolarized nucleon target}
+
+\begin{itemize}
+\item Bethe-Heitler coefficients
+\label{BHcrosssection}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+This part of the leptoproduction cross section is expressed solely in
+terms of $F_1(\Delta^2)$ and $F_2(\Delta^2)$, the known Dirac and Pauli
+form factors of the nucleon. For unpolarized target the Fourier
+coefficients are:
+
+\begin{eqnarray}
+\label{Def-FC-BH-unp0}
+    \eqname{eq.35 in ref}
+c^{\rm BH}_{0,{\rm unp}}
+\!\!\!&=&\!\!\!
+8 K^2
+\left\{
+\left( 2 + 3 \epsilon^2 \right)
+\frac{{\cal Q}^2}{\Delta^2}
+\left( F_1^2 - \frac{\Delta^2}{4 M^2} F_2^2 \right)
++ 2 \Bx^2 \left( F_1 + F_2 \right)^2
+\right\}
+\\
+&+&\!\!\! (2 - y)^2
+\Bigg\{
+\left( 2 + \epsilon^2 \right)
+\Bigg[
+\frac{4 \Bx^2 M^2}{\Delta^2}
+\left( 1 + \frac{\Delta^2}{{\cal Q}^2} \right)^2
++ 4 (1 - \Bx)
+\left( 1 + \Bx  \frac{\Delta^2}{{\cal Q}^2} \right)
+\Bigg]
+\left( F_1^2 - \frac{\Delta^2}{4 M^2} F_2^2 \right)
+\nonumber\\
+&+&\!\!\!
+4 \Bx^2
+\Bigg[
+\Bx + \left(1 - \Bx + \frac{\epsilon^2}{2} \right)
+\left(1 -  \frac{\Delta^2}{Q^2} \right)^2
+- \Bx (1 - 2 \Bx) \frac{\Delta^4}{Q^4}
+\Bigg]
+\left( F_1 + F_2 \right)^2
+\Bigg\}
+\nonumber\\
+&+&\!\!\! 8 \left( 1 + \epsilon^2 \right)
+\left(1 - y - \frac{\epsilon^2 y^2}{4} \right)
+\Bigg\{
+2 \epsilon^2
+\left( 1 - \frac{\Delta^2}{4 M^2} \right)
+\left( F_1^2 - \frac{\Delta^2}{4 M^2} F_2^2 \right)
+\nonumber\\
+&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad
+- \Bx^2
+\left( 1 -  \frac{\Delta^2}{Q^2} \right)^2
+\left( F_1 + F_2 \right)^2
+\Bigg\} \, ,
+\nonumber\\
+\label{Def-FC-BH-unp1}
+    \eqname{eq.36 in ref}
+c^{\rm BH}_{1,{\rm unp}}
+\!\!\!&=&\!\!\!
+8 K (2 - y)
+\Bigg\{
+\left(
+\frac{4\Bx^2 M^2}{\Delta^2} - 2\Bx - \epsilon^2
+\right)
+\left(
+F_1^2 - \frac{\Delta^2}{4 M^2} F_2^2
+\right)
+\\
+&&\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad\qquad
++ \, 2 \, \Bx^2
+\left( 1 - (1 - 2\Bx) \frac{\Delta^2}{{\cal Q}^2} \right)
+\left( F_1 + F_2 \right)^2
+\Bigg\},
+\nonumber\\
+\label{Def-FC-BH-unp2}
+    \eqname{eq.37 in ref}
+c^{\rm BH}_{2,{\rm unp}} \!\!\!&=&\!\!\!
+8 \Bx^2 K^2  \left\{ \frac{4 M^2}{\Delta^2}
+\left(F_1^2 - \frac{\Delta^2}{4 M^2} F_2^2\right) + 2 \left(F_1 +
+F_2\right)^2 \right\} \, .
+\end{eqnarray}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\item DVCS coefficients
+\label{SubSec-AziAngDep-DVCS}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+$|{\cal T}_{\rm DVCS}|^2$ is bilinear in the CFFs, and its coefficients read
+at leading twist and leading order for unpolarized target:
+
+\begin{eqnarray}
+\label{Def-C-DVCS-unp}
+    \eqname{eq.43\&66 in ref}
+c^{\rm DVCS}_{0,{\rm unp}}
+\!\!\!&=&\!\!\!
+   \frac{2 ( 2 - 2 y + y^2 )}{(2 - \Bx)^2}
+\Bigg\{
+4 (1 - \Bx)
+\left(
+{\cal H} {\cal H}^\ast
++
+\widetilde{\cal H} \widetilde {\cal H}^\ast
+\right)- \Bx^2
+\bigg(
+{\cal H} {\cal E}^\ast
++ {\cal E} {\cal H}^\ast
++ \widetilde{{\cal H}} \widetilde{{\cal E}}^\ast
++ \widetilde{{\cal E}} \widetilde{{\cal H}}^\ast
+\bigg)
+\nonumber\\
+&&\qquad\qquad\;
+-
+\left( \Bx^2 + (2 - \Bx)^2 \frac{\Delta^2}{4M^2} \right)
+{\cal E} {\cal E}^\ast
+- \Bx^2 \frac{\Delta^2}{4M^2}
+\widetilde{{\cal E}} \widetilde{{\cal E}}^\ast
+\Bigg\},
+\end{eqnarray}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\item Interference coefficients
+\label{SubSec-AziAngDep-INT}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+For the phenomenology of GPDs, ${\cal I}$ is the most interesting quantity
+since it is linear in CFFs. This simplifies their disentanglement from
+experimental measurements. At leading twist and leading order, the Fourier 
+harmonics have the following form for unpolarized target:
+
+\begin{eqnarray}
+    \eqname{eq.53 in ref}
+   c^{\cal I}_{0,\rm{unp}}
+   \!\!\!&=&\!\!\!
+   - 8  (2 - y)
+   \Re{\rm e}
+   \Bigg\{
+      \frac{(2 - y)^2}{1-y} K^2 {\cal C}^{\cal I}_{\rm unp} \left({\cal 
+      F}\right)
+      +
+      \frac{\Delta^2}{{\cal Q}^2}  (1-y)(2 - \Bx)
+      \left(
+      {\cal C}^{\cal I}_{\rm unp} + \Delta {\cal C}^{\cal I}_{\rm unp}
+      \right)
+      \left( {\cal F} \right)
+      \Bigg\} \, ,
+    \end{eqnarray}
+
+\begin{eqnarray}
+   \label{Res-IntTer-unp_c}
+    \eqname{eq.54 in ref}
+   c^{\cal I}_{1, \rm unp} &\!\!\!=\!\!\!&
+   -8 K (2 - 2y + y^2)~\Re{\rm e}\left\{
+       {\cal C}^{\cal I}_{\rm unp}\left({\cal F} \right) \right\}
+    \end{eqnarray}
+
+\begin{eqnarray}
+   \label{Res-IntTer-unp_s}
+    \eqname{eq.54 in ref}
+    s^{\cal I}_{1, \rm unp}
+   &\!\!\!=\!\!\!&
+   8 K \lambda y (2-y)~\Im{\rm m} \left\{
+      {\cal C}^{\cal I}_{\rm unp}\left({\cal F} \right) \right\} \end{eqnarray}
+
+In the lowest twist approximation, ${\cal C}^{\cal I}_{\rm unp}\left({\cal F} 
+\right)$ reads
+
+\begin{eqnarray}
+   \label{Def-C-Int-unp}
+    \eqname{eq.69 in ref}
+   {\cal C}^{\cal I}_{\rm unp}
+   \!\!\!&=&\!\!\!
+   F_1 {\cal H} + \frac{\Bx}{2 - \Bx}
+   (F_1 + F_2) \widetilde {\cal H}
+   -
+   \frac{\Delta^2}{4M^2} F_2 {\cal E} \, ,
+\end{eqnarray}
+
+The addenda arising in power-suppressed contribution is defined as
+
+\begin{eqnarray}
+   \label{Def-C-IntAdd-unp}
+    \eqname{eq.72 in ref}
+   \Delta {\cal C}^{\cal I}_{{\rm unp}}
+   \!\!\!&=&\!\!\!
+   - \frac{\Bx}{2-\Bx}  (F_1 + F_2)
+   \left\{
+      \frac{\Bx}{2 - \Bx} ({\cal H} + {\cal E})
+      + \widetilde {\cal H}
+      \right\} \, ,
+\end{eqnarray}
+
+\end{itemize}
+
+\subsection{Definition of the CFFs}
+The Compton form factors (CFFs), $\mathcal{F = \{ H, E, \widetilde{H}, 
+\widetilde{E}}\}$, are defined in terms of the GPDs, $F = \{H, E, 
+\widetilde{H}, \widetilde{E}\}$ ,as:
+
+\begin{align}
+\begin{split}
+    \eqname{}
+\Re(&\mathcal{F}) = \mathcal{P} \int_{0}^{1}dx[F(x,\xi,t)-F(-x,\xi,t)] \, 
+C^{\pm}(x,\xi), \end{split} \\
+\Im(&\mathcal{F}) = - \pi [F(\xi,\xi,t)-F(-\xi,\xi,t)],
+\end{align}
+
+\subsection{Definition of $\phi$}
+The angle between the leptonic and the hadronic planes, $\phi$, is defined as:
+
+\begin{equation}
+  \cos(\phi) = \frac{\vec{k} \times \vec{k'}}{| \vec{k} \times \vec{k'} |} 
+   \cdot \frac{\vec{q} \times \vec{p'}}{| \vec{q} \times \vec{p'} |}
+\end{equation}
+and $\phi \in [0,\phi] iff (\vec{k} \times \vec{k'}).\vec{q'} \geq 0$.
+
+Where $\vec{k}/\vec{k'}$, $\vec{q}/\vec{q'}$, $\vec{p}/\vec{p'}$ are the 
+four-vectors of the incident/scatter electrons, virtual/real photons, 
+initial/final protons.
+
 \normalsize

### 2018-08-27 eg6-letters/incoherent/incoherent_prl.tex
clean the summary

@@
 %conclusion
-In summary, we have presented our BSA measurements 
-associated with incoherent DVCS off $^4$He using an upgraded setup of the CLAS 
-spectrometer at Jefferson Lab. Our results were compared to model 
-calculations based on different assumptions of the nuclear medium effects at 
-the partonic level. The bound-proton BSA is largely suppressed compared to 
-the free proton BSA. This surprising result opens a new avenue for progress in 
-the understanding quarks and gluons in the nuclear medium.
+In summary, we have presented the first BSA measurment associated with bound 
+proton DVCS off $^4$He using an upgraded setup of the CLAS spectrometer at 
+Jefferson Lab. Our results were compared to model calculations based on 
+different assumptions of the nuclear medium effects at the partonic level. The 
+bound-proton BSA is largely suppressed compared to the free proton BSA. This 
+surprising result opens a new avenue for progress in the understanding quarks 
+and gluons in the nuclear medium.
 

### 2018-08-27 eg6-letters/incoherent/figs-sources/ALU_90_p_vs_Q2_shortscenrario.C
clean the directory

@@ -1,167 +1,0 @@
-void ALU_90_p_vs_Q2_shortscenrario()
-{
-//=========Macro generated from canvas: Can_p_Q2/DVCS Helium BoNuS
-//=========  (Thu Jul  6 14:04:33 2017) by ROOT version6.09/01
-   TCanvas *Can_p_Q2 = new TCanvas("Can_p_Q2", "DVCS Helium BoNuS",0,0,600,450);
-   gStyle->SetOptFit(1);
-   Can_p_Q2->SetHighLightColor(2);
-   Can_p_Q2->Range(-0.2792208,-0.2168831,4.915584,0.5623377);
-   Can_p_Q2->SetFillColor(0);
-   Can_p_Q2->SetBorderMode(0);
-   Can_p_Q2->SetBorderSize(2);
-   Can_p_Q2->SetLeftMargin(0.15);
-   Can_p_Q2->SetRightMargin(0.08);
-   Can_p_Q2->SetTopMargin(0.08);
-   Can_p_Q2->SetBottomMargin(0.15);
-   Can_p_Q2->SetFrameBorderMode(0);
-   Can_p_Q2->SetFrameBorderMode(0);
-   
-   TH2F *HALU_p_vs_Q2__1 = new TH2F("HALU_p_vs_Q2__1","",100,0.5,4.5,100,-0.1,0.5);
-   HALU_p_vs_Q2__1->SetStats(0);
-
-   Int_t ci;      // for color index setting
-   TColor *color; // for color definition with alpha
-   ci = TColor::GetColor("#000099");
-   HALU_p_vs_Q2__1->SetLineColor(ci);
-   HALU_p_vs_Q2__1->GetXaxis()->SetTitle("Q^{2} [GeV^{2}]");
-   HALU_p_vs_Q2__1->GetXaxis()->CenterTitle(true);
-   HALU_p_vs_Q2__1->GetXaxis()->SetNdivisions(605);
-   HALU_p_vs_Q2__1->GetXaxis()->SetLabelFont(22);
-   HALU_p_vs_Q2__1->GetXaxis()->SetLabelSize(0.05);
-   HALU_p_vs_Q2__1->GetXaxis()->SetTitleSize(0.07);
-   HALU_p_vs_Q2__1->GetXaxis()->SetTitleFont(22);
-   HALU_p_vs_Q2__1->GetYaxis()->SetTitle("A_{LU}^{Incoh}(90#circ)");
-   HALU_p_vs_Q2__1->GetYaxis()->CenterTitle(true);
[…]

### 2018-08-27 eg6-letters/incoherent/figs-sources/ALU_90_p_vs_t_shortscenrario.C

@@ -1,407 +1,0 @@
-void ALU_90_p_vs_t_shortscenrario()
-{
-//=========Macro generated from canvas: Can_p_t/DVCS Helium BoNuS
-//=========  (Thu Jul  6 14:04:34 2017) by ROOT version6.09/01
-   TCanvas *Can_p_t = new TCanvas("Can_p_t", "DVCS Helium BoNuS",0,0,600,450);
-   gStyle->SetOptFit(1);
-   Can_p_t->SetHighLightColor(2);
-   Can_p_t->Range(-0.2337662,-0.2168831,1.324675,0.5623377);
-   Can_p_t->SetFillColor(0);
-   Can_p_t->SetBorderMode(0);
-   Can_p_t->SetBorderSize(2);
-   Can_p_t->SetLeftMargin(0.15);
-   Can_p_t->SetRightMargin(0.08);
-   Can_p_t->SetTopMargin(0.08);
-   Can_p_t->SetBottomMargin(0.15);
-   Can_p_t->SetFrameBorderMode(0);
-   Can_p_t->SetFrameBorderMode(0);
-   
-   TH2F *HALU_p_vs_t__5 = new TH2F("HALU_p_vs_t__5","",100,0,1.2,100,-0.1,0.5);
-   HALU_p_vs_t__5->SetStats(0);
-
-   Int_t ci;      // for color index setting
-   TColor *color; // for color definition with alpha
-   ci = TColor::GetColor("#000099");
-   HALU_p_vs_t__5->SetLineColor(ci);
-   HALU_p_vs_t__5->GetXaxis()->SetTitle("-t [GeV^{2}]");
-   HALU_p_vs_t__5->GetXaxis()->CenterTitle(true);
-   HALU_p_vs_t__5->GetXaxis()->SetNdivisions(605);
-   HALU_p_vs_t__5->GetXaxis()->SetLabelFont(22);
-   HALU_p_vs_t__5->GetXaxis()->SetLabelSize(0.05);
-   HALU_p_vs_t__5->GetXaxis()->SetTitleSize(0.07);
-   HALU_p_vs_t__5->GetXaxis()->SetTitleFont(22);
-   HALU_p_vs_t__5->GetYaxis()->SetTitle("A_{LU}^{Incoh}(90#circ)");
-   HALU_p_vs_t__5->GetYaxis()->CenterTitle(true);
-   HALU_p_vs_t__5->GetYaxis()->SetNdivisions(605);
[…]

### 2018-08-27 eg6-letters/incoherent/figs-sources/ALU_90_p_vs_x_shortscenrario.C

@@ -1,313 +1,0 @@
-void ALU_90_p_vs_x_shortscenrario()
-{
-//=========Macro generated from canvas: Can_p_x/DVCS Helium BoNuS
-//=========  (Thu Jul  6 14:04:33 2017) by ROOT version6.09/01
-   TCanvas *Can_p_x = new TCanvas("Can_p_x", "DVCS Helium BoNuS",0,0,600,450);
-   gStyle->SetOptFit(1);
-   Can_p_x->SetHighLightColor(2);
-   Can_p_x->Range(-0.1363636,-0.2168831,0.7727273,0.5623377);
-   Can_p_x->SetFillColor(0);
-   Can_p_x->SetBorderMode(0);
-   Can_p_x->SetBorderSize(2);
-   Can_p_x->SetLeftMargin(0.15);
-   Can_p_x->SetRightMargin(0.08);
-   Can_p_x->SetTopMargin(0.08);
-   Can_p_x->SetBottomMargin(0.15);
-   Can_p_x->SetFrameBorderMode(0);
-   Can_p_x->SetFrameBorderMode(0);
-   
-   TH2F *HALU_p_vs_x__3 = new TH2F("HALU_p_vs_x__3","",100,0,0.7,100,-0.1,0.5);
-   HALU_p_vs_x__3->SetStats(0);
-
-   Int_t ci;      // for color index setting
-   TColor *color; // for color definition with alpha
-   ci = TColor::GetColor("#000099");
-   HALU_p_vs_x__3->SetLineColor(ci);
-   HALU_p_vs_x__3->GetXaxis()->SetTitle("x_{B}");
-   HALU_p_vs_x__3->GetXaxis()->CenterTitle(true);
-   HALU_p_vs_x__3->GetXaxis()->SetNdivisions(605);
-   HALU_p_vs_x__3->GetXaxis()->SetLabelFont(22);
-   HALU_p_vs_x__3->GetXaxis()->SetLabelSize(0.05);
-   HALU_p_vs_x__3->GetXaxis()->SetTitleSize(0.07);
-   HALU_p_vs_x__3->GetXaxis()->SetTitleFont(22);
-   HALU_p_vs_x__3->GetYaxis()->SetTitle("A_{LU}^{Incoh}(90#circ)");
-   HALU_p_vs_x__3->GetYaxis()->CenterTitle(true);
-   HALU_p_vs_x__3->GetYaxis()->SetNdivisions(605);
[…]

### 2018-08-27 eg6-letters/incoherent/figs-sources/ALU_ratioInc_Q2_shortscenrario.C

@@ -1,117 +1,0 @@
-void ALU_ratioInc_Q2_shortscenrario()
-{
-//=========Macro generated from canvas: Can/DVCS Helium BoNuS
-//=========  (Thu Jul  6 14:04:33 2017) by ROOT version6.09/01
-   TCanvas *Can = new TCanvas("Can", "DVCS Helium BoNuS",0,0,600,450);
-   gStyle->SetOptFit(1);
-   Can->SetHighLightColor(2);
-   Can->Range(-0.1818182,-0.09220779,4.363636,1.855844);
-   Can->SetFillColor(0);
-   Can->SetBorderMode(0);
-   Can->SetBorderSize(2);
-   Can->SetLeftMargin(0.15);
-   Can->SetRightMargin(0.08);
-   Can->SetTopMargin(0.08);
-   Can->SetBottomMargin(0.15);
-   Can->SetFrameBorderMode(0);
-   Can->SetFrameBorderMode(0);
-   
-   TH2F *HALU_RATIO_Q2__2 = new TH2F("HALU_RATIO_Q2__2","",100,0.5,4,100,0.2,1.7);
-   HALU_RATIO_Q2__2->SetStats(0);
-
-   Int_t ci;      // for color index setting
-   TColor *color; // for color definition with alpha
-   ci = TColor::GetColor("#000099");
-   HALU_RATIO_Q2__2->SetLineColor(ci);
-   HALU_RATIO_Q2__2->GetXaxis()->SetTitle("Q^{2} [GeV^{2}]");
-   HALU_RATIO_Q2__2->GetXaxis()->CenterTitle(true);
-   HALU_RATIO_Q2__2->GetXaxis()->SetNdivisions(605);
-   HALU_RATIO_Q2__2->GetXaxis()->SetLabelFont(22);
-   HALU_RATIO_Q2__2->GetXaxis()->SetLabelSize(0.05);
-   HALU_RATIO_Q2__2->GetXaxis()->SetTitleSize(0.07);
-   HALU_RATIO_Q2__2->GetXaxis()->SetTitleFont(22);
-   HALU_RATIO_Q2__2->GetYaxis()->SetTitle("A_{LU}^{Incoh}/A_{LU}^{p}(90#circ)");
-   HALU_RATIO_Q2__2->GetYaxis()->CenterTitle(true);
[…]

### 2018-08-27 eg6-letters/incoherent/figs-sources/ALU_ratioInc_t_shortscenrario.C

@@ -1,489 +1,0 @@
-void ALU_ratioInc_t_shortscenrario()
-{
-//=========Macro generated from canvas: Can_R_t/
-//=========  (Thu Jul  6 14:04:34 2017) by ROOT version6.09/01
-   TCanvas *Can_R_t = new TCanvas("Can_R_t", "",0,0,600,450);
-   gStyle->SetOptFit(1);
-   Can_R_t->SetHighLightColor(2);
-   Can_R_t->Range(-0.2337662,0.1467533,1.324675,1.835065);
-   Can_R_t->SetFillColor(0);
-   Can_R_t->SetBorderMode(0);
-   Can_R_t->SetBorderSize(2);
-   Can_R_t->SetLeftMargin(0.15);
-   Can_R_t->SetRightMargin(0.08);
-   Can_R_t->SetTopMargin(0.08);
-   Can_R_t->SetBottomMargin(0.15);
-   Can_R_t->SetFrameBorderMode(0);
-   Can_R_t->SetFrameBorderMode(0);
-   
-   TH2F *HALU_RATIO_t__6 = new TH2F("HALU_RATIO_t__6","",100,0,1.2,100,0.4,1.7);
-   HALU_RATIO_t__6->SetStats(0);
-
-   Int_t ci;      // for color index setting
-   TColor *color; // for color definition with alpha
-   ci = TColor::GetColor("#000099");
-   HALU_RATIO_t__6->SetLineColor(ci);
-   HALU_RATIO_t__6->GetXaxis()->SetTitle("-t [GeV^{2}]");
-   HALU_RATIO_t__6->GetXaxis()->CenterTitle(true);
-   HALU_RATIO_t__6->GetXaxis()->SetNdivisions(605);
-   HALU_RATIO_t__6->GetXaxis()->SetLabelFont(22);
-   HALU_RATIO_t__6->GetXaxis()->SetLabelSize(0.05);
-   HALU_RATIO_t__6->GetXaxis()->SetTitleSize(0.07);
-   HALU_RATIO_t__6->GetXaxis()->SetTitleFont(22);
-   HALU_RATIO_t__6->GetYaxis()->SetTitle("A_{LU}^{Incoh}/A_{LU}^{p} (90#circ)");
-   HALU_RATIO_t__6->GetYaxis()->CenterTitle(true);
-   HALU_RATIO_t__6->GetYaxis()->SetNdivisions(605);
-   HALU_RATIO_t__6->GetYaxis()->SetLabelFont(22);
[…]

### 2018-08-27 eg6-letters/incoherent/figs-sources/ALU_ratioInc_x_shortscenrario.C

@@ -1,418 +1,0 @@
-void ALU_ratioInc_x_shortscenrario()
-{
-//=========Macro generated from canvas: Can_R_x/DVCS Helium BoNuS
-//=========  (Thu Jul  6 14:04:34 2017) by ROOT version6.09/01
-   TCanvas *Can_R_x = new TCanvas("Can_R_x", "DVCS Helium BoNuS",0,0,600,450);
-   gStyle->SetOptFit(1);
-   Can_R_x->SetHighLightColor(2);
-   Can_R_x->Range(-0.1558442,0.02727273,0.8831169,1.845455);
-   Can_R_x->SetFillColor(0);
-   Can_R_x->SetBorderMode(0);
-   Can_R_x->SetBorderSize(2);
-   Can_R_x->SetLeftMargin(0.15);
-   Can_R_x->SetRightMargin(0.08);
-   Can_R_x->SetTopMargin(0.08);
-   Can_R_x->SetBottomMargin(0.15);
-   Can_R_x->SetFrameBorderMode(0);
-   Can_R_x->SetFrameBorderMode(0);
-   
-   TH2F *HALU_RATIO_x__4 = new TH2F("HALU_RATIO_x__4","",100,0,0.8,100,0.3,1.7);
-   HALU_RATIO_x__4->SetStats(0);
-
-   Int_t ci;      // for color index setting
-   TColor *color; // for color definition with alpha
-   ci = TColor::GetColor("#000099");
-   HALU_RATIO_x__4->SetLineColor(ci);
-   HALU_RATIO_x__4->GetXaxis()->SetTitle("x_{B}");
-   HALU_RATIO_x__4->GetXaxis()->CenterTitle(true);
-   HALU_RATIO_x__4->GetXaxis()->SetNdivisions(605);
-   HALU_RATIO_x__4->GetXaxis()->SetLabelFont(22);
-   HALU_RATIO_x__4->GetXaxis()->SetLabelSize(0.05);
-   HALU_RATIO_x__4->GetXaxis()->SetTitleSize(0.07);
-   HALU_RATIO_x__4->GetXaxis()->SetTitleFont(22);
-   HALU_RATIO_x__4->GetYaxis()->SetTitle("A_{LU}^{Incoh}/A_{LU}^{p} (90#circ)");
-   HALU_RATIO_x__4->GetYaxis()->CenterTitle(true);
[…]

### 2018-08-27 eg6-letters/incoherent/figs-sources/incoh_exc_cuts_final.C

@@ -1,3585 +1,0 @@
-void incoh_exc_cuts_final()
-{
-//=========Macro generated from canvas: aall_cuts/
-//=========  (Thu Jul  6 16:33:57 2017) by ROOT version6.09/01
-   TCanvas *aall_cuts = new TCanvas("aall_cuts", "",1,1,900,1176);
-   gStyle->SetOptStat(0);
-   aall_cuts->Range(0,0,1,1);
-   aall_cuts->SetFillColor(0);
-   aall_cuts->SetBorderMode(0);
-   aall_cuts->SetBorderSize(0);
-   aall_cuts->SetTopMargin(0.01);
-   aall_cuts->SetBottomMargin(0.2);
-   aall_cuts->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: aall_cuts_1
-   TPad *aall_cuts_1 = new TPad("aall_cuts_1", "aall_cuts_1",0.01,0.6766667,0.49,0.99);
-   aall_cuts_1->Draw();
-   aall_cuts_1->cd();
-   aall_cuts_1->Range(-10,-223.0633,10,892.2532);
-   aall_cuts_1->SetFillColor(0);
-   aall_cuts_1->SetBorderMode(0);
-   aall_cuts_1->SetBorderSize(2);
-   aall_cuts_1->SetTopMargin(0.01);
-   aall_cuts_1->SetBottomMargin(0.2);
-   aall_cuts_1->SetFrameBorderMode(0);
-   aall_cuts_1->SetFrameBorderMode(0);
-   
-   TH1D *h2_delta_phi_InCoh__249 = new TH1D("h2_delta_phi_InCoh__249"," ",300,-8,8);
-   h2_delta_phi_InCoh__249->SetBinContent(3,3);
-   h2_delta_phi_InCoh__249->SetBinContent(4,1);
-   h2_delta_phi_InCoh__249->SetBinContent(5,1);
-   h2_delta_phi_InCoh__249->SetBinContent(6,1);
-   h2_delta_phi_InCoh__249->SetBinContent(7,1);
-   h2_delta_phi_InCoh__249->SetBinContent(8,1);
-   h2_delta_phi_InCoh__249->SetBinContent(9,2);
-   h2_delta_phi_InCoh__249->SetBinContent(10,2);
-   h2_delta_phi_InCoh__249->SetBinContent(12,2);
-   h2_delta_phi_InCoh__249->SetBinContent(13,3);
-   h2_delta_phi_InCoh__249->SetBinContent(14,3);
[…]

### 2018-08-27 eg6-letters/incoherent/figs-sources/incoherent_ALU_phi.C

@@ -1,4209 +1,0 @@
-void incoherent_ALU_phi()
-{
-//=========Macro generated from canvas: c15/
-//=========  (Thu Jul  6 14:04:35 2017) by ROOT version6.09/01
-   TCanvas *c15 = new TCanvas("c15", "",0,0,1200,900);
-   gStyle->SetOptFit(1);
-   c15->Range(0,0,1,1);
-   c15->SetFillColor(0);
-   c15->SetBorderMode(0);
-   c15->SetBorderSize(2);
-   c15->SetLeftMargin(0.06395349);
-   c15->SetRightMargin(0.01968414);
-   c15->SetTopMargin(0.02680798);
-   c15->SetBottomMargin(0.08527131);
-   c15->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: c15_1
-   TPad *c15_1 = new TPad("c15_1", "_1",0,0.6772185,0.2930441,0.973192);
-   c15_1->Draw();
-   c15_1->cd();
-   c15_1->Range(-135.625,-0.35,375,0.35);
-   c15_1->SetFillColor(0);
-   c15_1->SetBorderMode(0);
-   c15_1->SetBorderSize(2);
-   c15_1->SetLeftMargin(0.255814);
-   c15_1->SetRightMargin(0);
-   c15_1->SetTopMargin(0);
-   c15_1->SetBottomMargin(0);
-   c15_1->SetFrameBorderMode(0);
-   c15_1->SetFrameBorderMode(0);
-   
-   TMultiGraph *multigraph = new TMultiGraph();
-   multigraph->SetName("");
-   multigraph->SetTitle("");
-   
-   Double_t Graph_fx1011[9] = {
-   21.0166,
-   62.924,
-   95.4492,
-   140.122,
-   182.321,
-   220.463,
-   258.455,
-   303.145,
-   337.42};
-   Double_t Graph_fy1011[9] = {
-   0.0541395,
-   0.0771959,
-   0.191317,
-   0.107603,
-   0.0448121,
-   -0.0294133,
-   -0.126129,
-   -0.12384,
-   -0.0122601};
-   Double_t Graph_fex1011[9] = {
-   0,
-   0,
-   0,
-   0,
-   0,
-   0,
-   0,
-   0,
-   0};
-   Double_t Graph_fey1011[9] = {
-   0.04257746,
-   0.04345303,
-   0.03915796,
-   0.0538811,
[…]

### 2018-08-28 analysis-note-vf/Appendix.tex
update the analysis note

@@
 
+\chapter{Investigating the Fermi motion effects on the incoherent DVCS channel}
+
+In our DVCS analysis, we considered the initial proton of the incoherent 
+channel to be at rest, while this is not totally true because of the Fermi 
+motion. Does this assumption is a good approximation? What other options can be 
+used to minimize this effect on the calculated exclusive quantities?\\
+
+Figure \ref{fig:handbag} presents the leading order handbag diagram of the 
+incoherent DVCS channel off $^4$He, where the nucleus breaks and the DVCS 
+occurs on a bound nucleon. Ideally, the transferred momentum squared ($t$) is 
+defined using the initial and the final nucleons' 4-vectors as $(p-p')^{2}$.  
+Then as a DVCS requirement, $t$ has to be greater than a certain value 
+($t_{min}$), that is defined using the kinematics of the incoming and the 
+scattered electrons. Due to the knowledge lack of the initial proton's 
+momentum, this cut maybe inaccurate causes loosing some good DVCS events. In 
+this work, we try to tackle this issue and check the stability of the 
+reconstructed beam-spin asymmetry, as being our DVCS observable.\\
+
+\begin{figure}[h!]
+   \centering
+\includegraphics[height=10.0cm]{fig-incoh/handbag_incoherent.pdf}
+\caption{Representation of the leading order handbag diagram of the incoherent 
+DVCS process off $^4$He}
+\label{fig:handbag}
+\end{figure}
+
+Typically, the transferred momentum squared $t$ is equal to the transferred 
+momentum squared ($t'$) defined between the virtual photon and the final-state 
+real photon, as shown in Figure \ref{fig:handbag}.  While defining the momentum 
+transferred as $t'$ is a good way to pass the Fermi motion effect on the 
+initial bound proton, it is more smeared than than $t$ due to bigger energy 
+resolutions of the photons. Figure \ref{fig:tprime} shows the distributions of 
+the coherent and the incoherent relative difference between $t$ and $t'$. One 
+can see that the coherent DVCS channel, the distributions is symmetric and 
+centered at zero as expected due to our good knowledge on the initial $^4$He 
+target, while it is not exactly the case for the incoherent case due to the 
+Fermi motion.\\
+
+\begin{figure}[h!]
+\includegraphics[height=5.0cm]{fig-incoh/T_tprime_Coh.png}
+\includegraphics[height=5.0cm]{fig-incoh/T_tprime_InCoh.png}
+\caption{On the left: the coherent relative difference between $t$ and $t'$.  
+On the right: the incoherent relative difference.}
+\label{fig:tprime}
+\end{figure}
+
+In the following, we check the effects of defining the transferred momentum 
+squared as $t$ and $t'$ on the exclusive distributions and on the reconstructed 
+beam-spin asymmetries. Figure \ref{fig:cuts_t} presents the exclusive 
+distributions of the incoherent DVCS events where the transferred momentum
+squared is defined as $t$, while it is define as $t'$ in figure 
+\ref{fig:cuts_tprime}. To minimize the smearing effects of $t'$ on the 
+exclusive distributions, 2$\sigma$ exclusive cuts were optimized compared to 
+3$\sigma$ cuts which were applied in the $t$ case. In terms of collected 
+statistics, the 2$\sigma$ cuts using $t'$ gave almost the same statistics using 
+$t$. From comparing the exclusive distributions, especially the $ep\gamma$ 
+missing energy and the missing mass squared, one sees that using $t'$ gives 
+more Gaussian missing energy distributions and cleaner missing mass squared 
+distribution.\\
+
+\begin{figure}[h!]
+\includegraphics[height=15.0cm]{fig-incoh/old_all_incoh_exc_cuts.pdf}
+\caption{The old set of exclusive cuts with $t$>$t_{min}$. The black
+   distributions represent the incoherent DVCS events candidate. The shaded
+   distributions represent the events which passed all the exclusivity cuts
+   except the quantity plotted. The vertical red lines represent the applied
+exclusivity, 3$\sigma$ cuts.}
+\label{fig:cuts_t}
+\end{figure}
+
+\begin{figure}[h!]
+   \includegraphics[height=15.0cm]{fig-incoh/all_incoh_exc_cuts_test.pdf}
+   \caption{New set of exclusive cuts with $t'$>$t_{min}$. The black
+      distributions represent the incoherent DVCS events candidate. The shaded
+      distributions represent the events which passed all the exclusivity cuts
+      except the quantity plotted. The vertical red lines represent the applied 
+   exclusivity, 2$\sigma$ cuts.}
+\label{fig:cuts_tprime}
+\end{figure}
+
+\begin{figure}[h!]
+   \includegraphics[height=6.0cm]{fig-incoh/ALU_phi_p_Q2.pdf}
+   \includegraphics[height=6.0cm]{fig-incoh/ALU_phi_p_x.pdf}
+   \includegraphics[height=6.0cm]{fig-incoh/ALU_phi_p_t.pdf}
+\caption{The reconstructed incoherent $A_{LU}$ as a function of the angle 
+   $\phi$ in $Q^2$, $x_B$, and $-t$ bins, respectively from top to bottom using 
+$t$>$t_{min}$ in black squares, and $t'$>$t_{min}$ in red squares.}
+   \label{fig:bsa_incoh_bins}
+\end{figure}
+
+\begin{figure}[h!]
+   \centering
+   \includegraphics[height=6.0cm]{fig-incoh/ALU_90_p_vs_Q2_shortscenrario.pdf}\\
+   \includegraphics[height=6.0cm]{fig-incoh/ALU_90_p_vs_x_shortscenrario.pdf}\\
+   \includegraphics[height=6.0cm]{fig-incoh/ALU_90_p_vs_t_shortscenrario.pdf}
+   \caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $-t$-dependencies (bottom) 
+      of the incoherent $A_{LU}$ at $\phi$~=~90$^{\circ}$, using the 
+   $t$>$t_{min}$ cut and the corresponding exclusive cuts in black squares, and 
+in red squares using the $t'$>$t_{min}$ and it's exclusive cuts.  The curves 
+are theoretical calculations. On the bottom: the green circles are the HERMES 
+$-A_{LU}$ (positron beam was used) inclusive measurements.}
+\label{fig:incoh_Q2_xB_t_ALU}
+\end{figure}
+
+\section*{Conclusions}
+In summary, we have studied the effects of Fermi motion on the measured 
+incoherent beam-spin asymmetries by defining the transferred momentum squared 
+through the nucleons in one case and through the photons in the other case. In 
+terms of collected statistics, 2$\sigma$ exclusive cuts using the photons 
+produced the same statistics as 3$\sigma$ cuts. The exclusive distributions 
+using $t'$, through the photons, have shown more acceptable distributions in 
+terms of being more symmetric in some cases and cleaner on others. The 
+reconstructed asymmetries in the two cases of defining the transferred momentum 
+squared are compatible and while the given error bars. As a suggestion, we 
+would like to consider the $t'$ analysis as the final set for publications 
+unless a major objections appear.
+
 \chapter{Free proton beam-spin asymmetry interpolation} 
@@
 
-\chapter{Investigating the Fermi motion effects on the incoherent DVCS channel}
-
-In our DVCS analysis, we considered the initial proton of the incoherent 
-channel to be at rest, while this is not totally true because of the Fermi 
-motion. Does this assumption is a good approximation? What other options can be 
-used to minimize this effect on the calculated exclusive quantities?\\
-
-Figure \ref{fig:handbag} presents the leading order handbag diagram of the 
-incoherent DVCS channel off $^4$He, where the nucleus breaks and the DVCS 
-occurs on a bound nucleon. Ideally, the transferred momentum squared ($t$) is 
-defined using the initial and the final nucleons' 4-vectors as $(p-p')^{2}$.  
-Then as a DVCS requirement, $t$ has to be greater than a certain value 
-($t_{min}$), that is defined using the kinematics of the incoming and the 
-scattered electrons. Due to the knowledge lack of the initial proton's 
-momentum, this cut maybe inaccurate causes loosing some good DVCS events. In 
-this work, we try to tackle this issue and check the stability of the 
-reconstructed beam-spin asymmetry, as being our DVCS observable.\\
-
-\begin{figure}[h!]
-   \centering
-\includegraphics[height=10.0cm]{fig-incoh/handbag_incoherent.pdf}
-\caption{Representation of the leading order handbag diagram of the incoherent 
-DVCS process off $^4$He}
-\label{fig:handbag}
-\end{figure}
-
-Typically, the transferred momentum squared $t$ is equal to the transferred 
-momentum squared ($t'$) defined between the virtual photon and the final-state 
-real photon, as shown in Figure \ref{fig:handbag}.  While defining the momentum 
-transferred as $t'$ is a good way to pass the Fermi motion effect on the 
-initial bound proton, it is more smeared than than $t$ due to bigger energy 
-resolutions of the photons. Figure \ref{fig:tprime} shows the distributions of 
-the coherent and the incoherent relative difference between $t$ and $t'$. One 
-can see that the coherent DVCS channel, the distributions is symmetric and 
-centered at zero as expected due to our good knowledge on the initial $^4$He 
-target, while it is not exactly the case for the incoherent case due to the 
-Fermi motion.\\
-
-\begin{figure}[h!]
-\includegraphics[height=5.0cm]{fig-incoh/T_tprime_Coh.png}
-\includegraphics[height=5.0cm]{fig-incoh/T_tprime_InCoh.png}
-\caption{On the left: the coherent relative difference between $t$ and $t'$.  
-On the right: the incoherent relative difference.}
-\label{fig:tprime}
-\end{figure}
-
-In the following, we check the effects of defining the transferred momentum 
-squared as $t$ and $t'$ on the exclusive distributions and on the reconstructed 
-beam-spin asymmetries. Figure \ref{fig:cuts_t} presents the exclusive 
-distributions of the incoherent DVCS events where the transferred momentum
-squared is defined as $t$, while it is define as $t'$ in figure 
-\ref{fig:cuts_tprime}. To minimize the smearing effects of $t'$ on the 
-exclusive distributions, 2$\sigma$ exclusive cuts were optimized compared to 
-3$\sigma$ cuts which were applied in the $t$ case. In terms of collected 
-statistics, the 2$\sigma$ cuts using $t'$ gave almost the same statistics using 
-$t$. From comparing the exclusive distributions, especially the $ep\gamma$ 
-missing energy and the missing mass squared, one sees that using $t'$ gives 
-more Gaussian missing energy distributions and cleaner missing mass squared 
-distribution.\\
-
-\begin{figure}[h!]
-\includegraphics[height=15.0cm]{fig-incoh/old_all_incoh_exc_cuts.pdf}
-\caption{The old set of exclusive cuts with $t$>$t_{min}$. The black
-   distributions represent the incoherent DVCS events candidate. The shaded
-   distributions represent the events which passed all the exclusivity cuts
-   except the quantity plotted. The vertical red lines represent the applied
-exclusivity, 3$\sigma$ cuts.}
-\label{fig:cuts_t}
-\end{figure}
-
-\begin{figure}[h!]
-   \includegraphics[height=15.0cm]{fig-incoh/all_incoh_exc_cuts_test.pdf}
-   \caption{New set of exclusive cuts with $t'$>$t_{min}$. The black
-      distributions represent the incoherent DVCS events candidate. The shaded
-      distributions represent the events which passed all the exclusivity cuts
-      except the quantity plotted. The vertical red lines represent the applied 
-   exclusivity, 2$\sigma$ cuts.}
-\label{fig:cuts_tprime}
-\end{figure}
-
-\begin{figure}[h!]
-   \includegraphics[height=6.0cm]{fig-incoh/ALU_phi_p_Q2.pdf}
-   \includegraphics[height=6.0cm]{fig-incoh/ALU_phi_p_x.pdf}
-   \includegraphics[height=6.0cm]{fig-incoh/ALU_phi_p_t.pdf}
-\caption{The reconstructed incoherent $A_{LU}$ as a function of the angle 
-   $\phi$ in $Q^2$, $x_B$, and $-t$ bins, respectively from top to bottom using 
-$t$>$t_{min}$ in black squares, and $t'$>$t_{min}$ in red squares.}
-   \label{fig:bsa_incoh_bins}
-\end{figure}
-
-\begin{figure}[h!]
-   \centering
-   \includegraphics[height=6.0cm]{fig-incoh/ALU_90_p_vs_Q2_shortscenrario.pdf}\\
-   \includegraphics[height=6.0cm]{fig-incoh/ALU_90_p_vs_x_shortscenrario.pdf}\\
-   \includegraphics[height=6.0cm]{fig-incoh/ALU_90_p_vs_t_shortscenrario.pdf}
-   \caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $-t$-dependencies (bottom) 
-      of the incoherent $A_{LU}$ at $\phi$~=~90$^{\circ}$, using the 
-   $t$>$t_{min}$ cut and the corresponding exclusive cuts in black squares, and 
-in red squares using the $t'$>$t_{min}$ and it's exclusive cuts.  The curves 
-are theoretical calculations. On the bottom: the green circles are the HERMES 
-$-A_{LU}$ (positron beam was used) inclusive measurements.}
-\label{fig:incoh_Q2_xB_t_ALU}
-\end{figure}
-
-\section*{Conclusions}
-In summary, we have studied the effects of Fermi motion on the measured 
-incoherent beam-spin asymmetries by defining the transferred momentum squared 
-through the nucleons in one case and through the photons in the other case. In 
-terms of collected statistics, 2$\sigma$ exclusive cuts using the photons 
-produced the same statistics as 3$\sigma$ cuts. The exclusive distributions 
-using $t'$, through the photons, have shown more acceptable distributions in 
-terms of being more symmetric in some cases and cleaner on others. The 
-reconstructed asymmetries in the two cases of defining the transferred momentum 
-squared are compatible and while the given error bars. As a suggestion, we 
-would like to consider the $t'$ analysis as the final set for publications 
-unless a major objections appear.
-
 \chapter{Binning the incoherent DVCS data to match the free proton DVCS 
 published data}
+ \label{app_free_proton_4D}
+
+Following the discussion in section \ref{sec:Generalized_EMC} and the 
+interpolation technique for the free proton DVCS asymmetries in 
+Appendix~\ref{app:free-proton-alu}, here we carry out a different technique to 
+validate the calculated incoherent DVCS asymmetry ratios. We apply tuning cuts 
+on the kinematical distributions to get similar mean values close to the 
+published free proton kinematics published in \ref{fig:FXfree-proton-alu}. For 
+instance, regarding the binning in $Q^2$, we start binning our incoherent DVCS 
+data into four bins in $Q^2$ with mean values similar to the published free 
+proton values, then we apply tuning cuts on the associated distributions in 
+$x_B$ and $t$. Figure \ref{fig:incoh_Q2-bins-freep} shows the resulting 
+kinematical distributions for the $Q^2$ bins, which are compared to the 
+published free proton bins shown in table~\ref{Table:freeproton-x_Q2_bins}.  
+Similarly, we apply tuning cuts to the binning in $x_B$ and $-t$ dependence.  
+Figure \ref{fig:incoh_xB-bins-freep} shows the resulting kinematical 
+distributions for the $x_B$ bins, which are compared to the published free 
+proton bins shown in table~\ref{Table:freeproton-x_Q2_bins}. Figure 
+\ref{fig:incoh_t-bins-freep} shows the resulting kinematical distributions for 
+the $t$ bins, which are compared to the published free proton bins shown in 
+table~\ref{Table:freeproton-t_bins}.
+
+The beam-spin asymmetry dependence on $Q^2$, $x_B$, and $t$ bins is constructed 
+as a function of the azimuthal angle $\phi$ and fitted for the incoherent DVCS 
+data. The $A_{LU}$ ratios at $\phi$~=~90$^{\circ}$ are calculated using the two 
+methods; interpolating the free proton data and tunning the incoherent DVCS 
+data. The results are presented in 
+Figure~\ref{fig:incoh_EMC_ratio_ALU_proton_two}. To conclude, the second method 
+provides us with the adequate validation of the extracted asymmetry ratios 
+using the interpolation technique. The difference between the two calculated 
+asymmetry ratios will be considered as a systematic uncertainty to the first 
+method.
 
@@
 
-\begin {table}[!h]
-\begin{center}
-\begin{tabular}{|l|l|l|l|l|l|l|l|}
-\hline
-<$x_{B}$> & <$Q^2$> & <-t> & $\alpha$ & $\Delta \alpha$ &  $\beta$ & $\Delta 
-   \beta$ & $\chi^{2}$\\
-\hline
-0.238  & 1.89 & 0.14 & 0.243 & 0.013 & -0.02 & 0.09 & 1.0\\
-\hline
-0.249  & 1.95 & 0.28 & 0.275 & 0.014 & -0.06 & 0.09 & 1.3\\
-\hline
-0.249  & 1.95 & 0.49 & 0.200 & 0.026 & -0.36 & 0.15 & 1.3\\
-\hline
-0.248  & 1.94 & 0.77 & 0.172 & 0.035 & 0.01 &  0.31 & 0.3\\
-\hline
-\end{tabular}
-   \caption{Free proton DVCS published asymmetries associated with the 
-   incoherent -t bins.}
-\label{Table:freeproton-t_bins}
-\end{center}
-\end{table}
-
 \begin{figure}[h!]
@@
    Third row: the associated distributions of $x_B$ for the bins in $t$.}
-\label{fig:incoh_xB-bins-freep}
+\label{fig:incoh_t-bins-freep}
 \end{figure}
@@
 \end{tabular}
-   \caption{Free proton DVCS published asymmetries associated with the 1250 
+   \caption{Free proton DVCS published asymmetries associated with the 
    incoherent $Q^{2}$ and $x_{B}$ bins.}
 \label{Table:freeproton-x_Q2_bins}
+\end{center}
+\end{table}
+
+\begin {table}[!h]
+\begin{center}
+\begin{tabular}{|l|l|l|l|l|l|l|l|}
+\hline
+<$x_{B}$> & <$Q^2$> & <-t> & $\alpha$ & $\Delta \alpha$ &  $\beta$ & $\Delta 
+   \beta$ & $\chi^{2}$\\
+\hline
+0.238  & 1.89 & 0.14 & 0.243 & 0.013 & -0.02 & 0.09 & 1.0\\
+\hline
+0.249  & 1.95 & 0.28 & 0.275 & 0.014 & -0.06 & 0.09 & 1.3\\
+\hline
+0.249  & 1.95 & 0.49 & 0.200 & 0.026 & -0.36 & 0.15 & 1.3\\
+\hline
+0.248  & 1.94 & 0.77 & 0.172 & 0.035 & 0.01 &  0.31 & 0.3\\
+\hline
+\end{tabular}
+   \caption{Free proton DVCS published asymmetries associated with the 
+   incoherent $t$ bins.}
+\label{Table:freeproton-t_bins}
 \end{center}
@@
    \cite{simonetta_2}. The solid and dashed black curves are from the off-shell 
-   calculations \cite{EMC_vadim_2}.} \label{fig:incoh_EMC_ratio_ALU_proton}
-\end{figure}
+   calculations \cite{EMC_vadim_2}.} \label{fig:incoh_EMC_ratio_ALU_proton_two}
+\end{figure}

### 2018-08-28 analysis-note-vf/results.tex
update the analysis note

@@
 data are similar to the ones of the incoherent channel, and the two data sets 
-were recorded using similar electron-beam energies and experimental setup.  
-Therefore, we construct $A_{LU}$ ratios based on choosing the free proton bins 
-which have similar $Q^2$, $x_{B}$ and $-t$ values as our bins. The incoherent 
-$A_{LU}$ ratios at $\phi$~=~90$^{\circ}$ are shown in figure 
+were recorded using similar electron-beam energies and experimental setup. Due 
+to the different binning that has been performed over the published free proton 
+data, we performed an interpolation to extract the free proton asymmetries at 
+the kinematics of our incoherent DVCS bins. In Appendix 
+\ref{app:free-proton-alu} we detail this extraction procedure. Additionally, In 
+Appendix \ref{app_free_proton_4D} we carried out a different binning procedure 
+to our incoherent DVCS binning in order to get an overall validation of the 
+interpolated free proton DVCS asymmetries. In each extraction method, the 
+$A_{LU}$ ratios have been calculated, and the difference between the two 
+methods has been associated as systematic errors to the calculated $A_{LU}$ 
+ratios using the interpolation technique. The measured incoherent $A_{LU}$ 
+ratios at $\phi$~=~90$^{\circ}$ are shown in figure 
 \ref{fig:incoh_EMC_ratio_ALU_proton} as functions of $Q^{2}$, $x_{B}$, and 

### 2018-08-28 eg6-letters/incoherent/adhocreview/1st_adhoc_comments.tex
update the response to the adhoc comments

--- 2018-08-10 eg6-letters/incoherent/adhocreview/1st_adhoc_comments.tex
@@
       to that in figure 6, except the order of the variation is different.\\ 
-      \textcolor{blue}{ }
+      \textcolor{blue}{The text is updated. We show the dependence on $t$ as it 
+      is mostly related to the modifications of the GPDs.}
 
@@
       information to make a judgement on the validity of your figure6.\\
-   \textcolor{blue}{ }
+   \textcolor{blue}{For this specific purpose, we applied four dimensional 
+      binning to our incoherent DVCS data to get kinematical mean values close 
+      to the published free proton results. The review committee members are 
+      invited to check Appendix J in the analysis note. }
 
@@
       these widths dominated by detector resolution?\\
-   \textcolor{blue}{ }
+   \textcolor{blue}{We have studied this effect, we updated the paper to
+      address the question. The review 
+      committee members are invited to check appendix H in the analysis note 
+      for more details.}
 
-\item    There is also no mention of final state interactions in the paper. It 
-   is not obvious to me that the FSA should be zero for a beam spin asymmetry 
-      on 4He. If you have a calculation that shows this is the case, it would 
-      be good to mention it.\\
-   \textcolor{blue}{ }
+\item  There is also no mention of final state interactions in the paper. It is 
+   not obvious to me that the FSA should be zero for a beam spin asymmetry on 
+      4He. If you have a calculation that shows this is the case, it would be 
+      good to mention it.\\
+   \textcolor{blue}{There are no such theoretical calculations of the FSI on 
+      the incoherent DVCS asymmetries on the $^4$He. A statement has been added
+      toward the end to address this point.}
 
 \end{enumerate}
+
+\newpage
+\newpage
+\newpage
+\newpage
 

### 2018-09-06 eg6-letters/incoherent/adhocreview/1st_adhoc_comments.tex
some cleaning

@@
       to that in figure 6, except the order of the variation is different.\\ 
-      \textcolor{blue}{The text is updated. We show the dependence on $t$ as it 
-      is mostly related to the modifications of the GPDs.}
+      \textcolor{blue}{We replaced the figure with the t-dependence, and 
+      changed the wording in the text accordingly. We believe t-dependence 
+      better reflects difference between the free and bound nucleon structures, 
+      and shows clear difference with existing theoretical models.}
 
@@
       procedure affect the systematic uncertainties? This is important 
-      information to make a judgement on the validity of your figure6.\\
-   \textcolor{blue}{For this specific purpose, we applied four dimensional 
-      binning to our incoherent DVCS data to get kinematical mean values close 
-      to the published free proton results. The review committee members are 
-      invited to check Appendix J in the analysis note. }
+      information to make a judgement on the validity of your figure~6.\\
+   \textcolor{blue}{The ratio of $A_{LU}$s were derived in two ways, in the  
+      first method we studied and parameterized $x_B$, $Q^2$, and t-dependences 
+      of free proton $A_{LU}$ from ref~[21]. Then using this parametrizations 
+      we calculated $A_{LU}$s for free proton at kinematic points of our data.  
+      In the second method we selected events in our analysis such that 
+      kinematics of selected events matched kinematics of the free proton 
+      points for the t-dependence of the ratio. In the figure we use results of 
+      the first method since statistics is higher for our data. The difference 
+      in ratios calculated with these two methods was taken as systematic error 
+      for the ratio. The details can be found in the analysis note (appendix 
+      J).  }
 
@@
       relates to comment \#2 above.\\
-      \textcolor{red}{Cleaned. ( I am not sure this is needed as it is 
-      mentioned at the beginning of the paragraph).}
+      \textcolor{blue}{Cleaned. }
 

### 2018-09-08 eg6-letters/incoherent/adhocreview/1st_adhoc_comments.tex
Minor updates on incoherent

@@
    \textcolor{blue}{We have studied this effect, we updated the paper to
-      address the question. The review 
-      committee members are invited to check appendix H in the analysis note 
-      for more details.}
+      address the question. Of relevance to this question, the appendix H in the analysis note 
+      looks in more details into alternative kinematics to solve the issue. However,
+      final results did not appear to be affected by any of the alternate choices,
+      confirming the small impact of the Fermi momentum smearing.}
 

### 2018-10-01 eg6-letters/incoherent/incoherent_prl.tex
Minor updates on incoherent
Implement the English typos from the second round comments from the adhoc review

@@
    of virtual photon and scattered proton kinematics. The Q$^2$, $x_B$, and $t$ 
-   dependencies of the BSA on the bound proton are compared with the one on the 
+   dependencies of the BSA on the bound proton are compared with those on the 
    free proton. In the whole kinematical region of our measurements, the BSA on 
@@
 proton in $^{4}$He. FIG.~\ref{fig:diags} illustrates the leading-twist handbag 
-diagram for this process. In the Bjorken regime, i.e, large virtual photon 
+diagram for the DVCS process. In the Bjorken regime, i.e, large virtual photon 
 four-momentum squared ($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small invariant 
@@
 incoherent DVCS events from accidental and physics background events. First, 
-events were selected with Q$^{2}$ greater the 1 GeV$^2$ to ensure the 
+events were selected with Q$^{2}$ greater than 1 GeV$^2$ to ensure the 
 applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
-mass (W$=(q+p)^2$) greater than 2 GeV to avoid the nucleon resonance region. 
-The $t$, transferred momentum squared to the recoil proton assuming an on-shell 
-proton at rest, was required to be greater than a minimum allowed value at 
-given Q$^2$ and W ($t>~t_{min}(=~- Q^{2}~\frac{2(1- x_{B})(1~-~\sqrt{1 
+mass (W$=\sqrt{(q+p)^2}$) greater than 2 GeV to avoid the nucleon resonance 
+region.  The $t$, transferred momentum squared to the recoil proton assuming an 
+on-shell proton at rest, was required to be greater than a minimum allowed 
+value at given Q$^2$ and W ($t>~t_{min}(=~- Q^{2}~\frac{2(1- x_{B})(1~-~\sqrt{1 
 +~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$,
@@
 FIG.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
-$\phi$ in bins of $Q^{2}$ (integarted over full $x_{B}$ and $t$ ranges), 
-$x_{B}$ (integarted over full $Q^{2}$ and $t$ ranges), and $t$ (integarted over 
+$\phi$ in bins of $Q^{2}$ (integrated over full $x_{B}$ and $t$ ranges), 
+$x_{B}$ (integrated over full $Q^{2}$ and $t$ ranges), and $t$ (integrated over 
 full $Q^{2}$ and $x_{B}$ ranges). The curves on the plots are fits of the form 
@@
 Within the given uncertainties, $A_{LU}$ does not indicate a strong dependence 
-on $Q^2$.  The $x_{B}$ and $t$ dependencies are compared to theoretical 
+on $Q^2$.  The $x_{B}$ and $t$ dependency are compared to theoretical 
 calculations performed by S.~Liuti and K.~Taneja \cite{simonetta_2}. Their 
@@
 differences may arise from nuclear effects which are not taken into account in 
-the model, such as long-range interactions.  On the graph for $-t$ dependence, 
-we show previous measurements by the HERMES collaboration 
-\cite{Airapetian:2009cga}, in which only electrons
-and photons were measured. Due to the large experimental uncertainties of the HERMES 
-points, the two measurements are completely compatible.
+the model, such as long-range interactions and final state interactions of the 
+knock-out proton. On the graph for $-t$ dependence, we show previous 
+measurements by the HERMES collaboration \cite{Airapetian:2009cga}, in which 
+only electrons and photons were measured. Due to the large experimental 
+uncertainties of the HERMES points, the two measurements are completely 
+compatible.
 
@@
    systematic uncertainties. On the middle plot: the curves are theoretical 
-   calculations from \cite{simonetta_2}. On the bottom: the solid (empty) green 
-   circles are the HERMES $-A_{LU}$ (positron beam was used) inclusive 
+   calculations from \cite{simonetta_2}. On the bottom plot: the solid (empty) 
+   green circles are the HERMES $-A_{LU}$ (a positron beam was used) inclusive 
    measurements for the incoherent (coherent) enriched region 
-\cite{Airapetian:2009cga}, the curves represent theoretical calculations from 
-\cite{simonetta_2}.  } \label{fig:alu90}
+   \cite{Airapetian:2009cga}, the curves represent theoretical calculations 
+   from \cite{simonetta_2}.  } \label{fig:alu90}
 \end{figure}
@@
 bound-proton BSA is largely suppressed compared to the free proton BSA. This 
-surprising result opens a new avenue for progress in the understanding quarks 
-and gluons in the nuclear medium.
+surprising result opens a new avenue for progress in understanding the 
+properties of quarks and gluons in the nuclear medium.
 
@@
 
-\bibitem{Dupre:2016mai} R.~Dupre, M.~Guidal and M.~Vanderhaeghen,
+\bibitem{Dupre:2016mai} R.~Dupr\'{e}, M.~Guidal and M.~Vanderhaeghen,
  %``Tomographic image of the proton,''

### 2018-10-02 eg6-letters/incoherent/2nd-adhocreview/2nd_adhoc_comments.tex
add the 2nd round comments

%\documentclass[a4paper,11pt,twoside]{ThesisStyle}
\documentclass[a4paper,11pt,twoside]{article}

\title{Second round comments from the Ad-hoc rewiew committee \\
 (Maurik Holtrop, Kevin Giovankl, Zein-Eddine Meziani)}

\date{\today}
\include{formatAndDefs}

\begin{document}

\maketitle

\section*{}

Dear Mohammad Hattawy,

We have read the updated version of the paper and find it significantly 
improved over the first version we read. There are still some comments we think 
you should address:

The new plot of the data versus t shows far more clearly the point you are 
trying to make about possible modification of the struck proton in 4He. We are 
a bit concerned however that it would not be clear to the reader that there is 
significant expected smearing of the t variable due to the Fermi motion of the 
initial proton. The question we have is whether horizontal error bars on your 
plot, which would include the bin width effects and the smearing of the t 
variable, could be added to make this explicitly clear to the reader.\\
   \textcolor{blue}{Updated.}\\

There are still a number of English language issues in the paper:\\

\begin{enumerate}

\item  Abstract: "The $Q^2$, $x_b$ and t dependencies .... are compared with 
   the one on the free proton": Since dependencies is plural, replace "the one"
      with "those".\\
   \textcolor{blue}{Corrected.}

\item  Line 150: greater the 1 GeV -> greater than 1 GeV.\\
   \textcolor{blue}{Corrected.}

\item  Line 152: formula would be $W^2 = (q+p)^2$, or else take square root.\\
   \textcolor{blue}{Corrected.}

\item  Line 218,219:  Three times misspelling of "integrated"\\
   \textcolor{blue}{Corrected.}

\item  Line 231: dependencies -> dependency\\
   \textcolor{blue}{Corrected.}

\item  Line 240: such as long-range interactions -> such as long-range 
   interactions and final state interactions of the knock-out proton.\\
   \textcolor{blue}{Corrected.}

\item  line 273: Sentence should be rewritten. Minimal suggesion:
"This surprising result opens a new avenue for progress in understanding the 
      properties of quarks and gluons in the nuclear medium.\\
   \textcolor{blue}{Corrected.}

\item  Caption to Figure 5: On the bottom -> On the bottom plot:
(positron beam was used) -> (a positron beam was used)\\
   \textcolor{blue}{Corrected.}

\item  References: line 343:  Accent on name:  R. Dupr\'{e}.\\
   \textcolor{blue}{Corrected.}

\end{enumerate}

\end{document}

### 2018-10-04 incoh_fermi_investigation/Incoh_fermi.tex
added documenation for fermi motion effect on incoherent dvcs

--- 2017-03-23 for_eg6_group/incoh_t_EG6_E1DVCS1_2/Incoh.tex
@@
 \documentclass[a4paper,11pt,twoside]{article}
-\author{M. Hattawy}
+
 \date{\today}
@@
 
-\title{\centering{Follow up on the incoherent t, t'}}
+\title{\centering{Investigating the Fermi motion smearing on the incoherent 
+DVCS channel}}
 \maketitle
 
-\section{Overview}
-In our DVCS analysis, we considered the initial proton of the incoherent 
-channel to be at rest, while this is not totally true because of the Fermi 
-motion. Does this assumption is a good approximation? What other options can be 
-used to minimize this effect on the calculated exclusive quantities?\\
-
-Figure \ref{fig:handbag} presents the leading order handbag diagram of the 
-incoherent DVCS channel off $^4$He. Ideally, the transferred momentum squared 
-($t$) is defined using the initial and the final nucleons' 4-vectors as 
-$(p-p')^{2}$. Then as a DVCS requirement, $t$ has to be greater than a certain 
-value ($t_{min}$), which is defined using the kinematics of the incoming and 
-the scattered electrons. Due to the knowledge lack of the initial proton's 
-momentum, this cut maybe inaccurate, causes loosing some good DVCS events and 
-leading to inaccurate determination of the exclusivity cuts.\\
-
 \begin{figure}[h!]
-\centering
-   \includegraphics[height=8.0cm]{fig/handbag_incoherent.pdf}
-\caption{Representation of the leading order handbag diagram of the incoherent 
-DVCS process off $^4$He}
-\label{fig:handbag}
-\end{figure}
-
-\section{Investigating the free proton DVCS data}
-
-Typically, the transferred momentum squared $t$ is equal to the transferred 
-momentum squared ($t'$) defined between the virtual photon and the final-state 
-real photon, as shown in Figure \ref{fig:handbag}.  While defining the momentum 
-transferred as $t'$ is a good way to pass the Fermi motion effect on the 
-initial bound proton, $t'$ suffers from the radiative effects. In this work, we 
-study the radiative effects on $t'$ using the CLAS available free proton DVCS 
-data sets, E1-DVCS1 and E1-DVCS2.
-
-Figure \ref{fig:tprime_eg6} presents the collected incoherent DVCS events from 
-EG6 data binned into four bins in $t$. In order to evaluate the radiative 
-effects on $t'$ we carried out a full analysis on E1-DVCS1 and E1-DVCS2 data 
-sets (free proton data). The collected free proton DVCS events in the two data 
-sets were binned into similar bins as our incoherent DVCS events. The results 
-are presented in figure \ref{fig:tprime_e1dvcs2}.  While the EG6 incoherent 
-DVCS events show a relatively more smeared $\frac{t'-t}{t}$ distributions than 
-the free proton data sets, the free proton sets show a significant shifts 
-specially at low $t$ values.
-
-\begin{figure}[h!]
-\centering
-\includegraphics[height=19.0cm]{fig/t_tprime_Incoh.pdf}
-\caption{The EG6 incoherent DVCS sample. The first row presents the four bins 
-in $t$. The second row shows the distribution of $t'$ for the DVCS events in 
-each bin in $t$ in the first row plots. The third row shows $\frac{t'-t}{t}$.  
-The 4$^{th}$ shows $\frac{t-t'}{t'}$, and the 5$^{th}$ shows $t-t'$.}
-\label{fig:tprime_eg6}
-\end{figure}
-
-%\begin{figure}[h!]
-%\centering
-%\includegraphics[height=19.0cm]{fig/E1-dvcs1-t_tprime_Incoh.pdf}
-%\caption{The E1-DVCS1 free proton DVCS sample. See the caption of figure 
-%\ref{fig:tprime_eg6} for plots description.}
-%\label{fig:tprime_e1dvcs1}
-%\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[height=19.0cm]{fig/before_corrections_E1-dvcs2-t_tprime_Incoh.pdf}
-\caption{The E1-DVCS2 free proton DVCS sample BEFORE correcting $t'$. See the 
-caption of figure \ref{fig:tprime_eg6} for plots description.}
-\label{fig:tprime_e1dvcs2}
-\end{figure}
-
-\section{$t'$ correction}
-One can see from the free proton DVCS sample, figure \ref{fig:tprime_e1dvcs2}, 
-that $t'$ is slightly shifted compared to $t$, which is considered as the true 
-value in the free proton case. This shift in $t'$ is mainly induced by the 
-radiative effects on the leptons. Before considering $t'$ in the incoherent EG6 
-analysis, $t'$ has to be corrected and the reconstructed free proton 
-asymmetries have to be verified in order to estimate the associated systematic 
-uncertainties. Figure \ref{fig:corrections_tprime_e1dvcs2} presents the 
-distributions of $t-t'$ as a function of $t'$ for the free proton DVCS sample 
-from E1-DVCS2 data before and after correcting $t'$. In figure 
-\ref{fig:after_tprime_e1dvcs2}, the distributions of figure 
-\ref{fig:tprime_e1dvcs2} are shown after the $t'$ corrections.
-
-\begin{figure}[h!]
-\centering
-\includegraphics[height=10.0cm]{fig/before_corrections_tprimet_t_InCoh.pdf}
-\includegraphics[height=10.0cm]{fig/after_corrections_tprimet_t_InCoh.pdf}
-\caption{On top: $t-t'$ as a function of $t'$ for the E1-DVCS2 free proton DVCS 
-sample BEFORE correcting $t'$. The red line is the extracted correction for 
-$t'$. On bottom: $t-t'$ as a function of $t'$ after correcting $t'$.}
-\label{fig:corrections_tprime_e1dvcs2}
+\includegraphics[height=10.0cm]{figs/t_n_Incoh.pdf}
+\caption{}
+\label{fig:exp}
 \end{figure}
@@
 \begin{figure}[h!]
-\centering
-\includegraphics[height=19.0cm]{fig/after_corrections_E1-dvcs2-t_tprime_Incoh.pdf}
-\caption{The E1-DVCS2 free proton DVCS sample AFTER correcting $t'$. See the 
-caption of figure \ref{fig:tprime_eg6} for plots description.}
-\label{fig:after_tprime_e1dvcs2}
-\end{figure}
-
-\section{Comparing the $t$ and the corrected $t'$ asymmetries in the E1-DVCS2 
-data set}
-Here we compare the E1-DVCS2 free proton DVCS beam-spin asymmetries using $t$ 
-and the corrected $t'$ to estimate the associated systematic uncertainties.  
-Figure \ref{t_tprime_ALU_phi} presents the reconstructed $A_{LU}$ as a function 
-of $\phi$ in the same binning as the incoherent EG6 DVCS channel. The binning 
-in $t$ and the corrected $t'$ are the same. Figure \ref{fig:t_tprime_ALU_90} 
-presents the $A_{LU}$ at $\phi = 90^{\circ}$ from the fits in figure 
-\ref{fig:t_tprime_ALU_phi}, as a function of $t$ and the corrected $t'$ showing 
-the estimated systematic uncertainties. No induced systematic uncertainties are 
-observed on the $Q^{2}$ and $x_B$, while some appear on $t$, which will be 
-added to the EG6 incoherent asymmetries.
-
-\begin{figure}[h!]
-\centering
-\includegraphics[height=6.0cm]{fig/E1DVCS2-ALU_phi_p_Q2.pdf}
-\includegraphics[height=6.0cm]{fig/E1DVCS2-ALU_phi_p_x.pdf}
-\includegraphics[height=6.0cm]{fig/E1DVCS2-ALU_phi_p_t.pdf}
-\caption{The reconstructed $A_{LU}$ as a function of $\phi$ for the collected 
-E1-DVCS2 free proton DVCS sample using $t$ in black points and using the 
-corrected $t'$ in red points. The lines represent fits in the form of 
-$\frac{\alpha sin(\phi)}{1+\beta cos(\phi)}$ for the two sets of analysis.}
-\label{fig:t_tprime_ALU_phi}
+\includegraphics[height=10.0cm]{figs/sim_Fermi_mom.png}
+\caption{}
+\label{fig:fermi}
 \end{figure}
@@
 \begin{figure}[h!]
-\centering
-\includegraphics[height=7.0cm]{fig/E1DVCS2-ALU_90_p_vs_Q2_shortscenrario.pdf}
-\includegraphics[height=7.0cm]{fig/E1DVCS2-ALU_90_p_vs_x_shortscenrario.pdf}
-\includegraphics[height=7.0cm]{fig/E1DVCS2-ALU_90_p_vs_t_shortscenrario.pdf}
-\caption{$A_{LU}$ at $\phi = 90^{\circ}$ from the fits in figure 
-\ref{fig:t_tprime_ALU_phi} as a function of $t$ in black points and as a 
-function of the corrected $t'$ in red points.}
-\label{fig:t_tprime_ALU_90}
+\includegraphics[height=10.0cm]{figs/sim_t_n_Incoh.pdf}
+\caption{}
+\label{fig:fermi}
 \end{figure}
 
-\section{EG6 Incoherent DVCS channel}
-Here we apply the $t'$ corrections that were extracted from the free proton 
-asymmetries  to the EG6 incoherent DVCS channel. Then, the asymmetries using 
-$t$ are compared to the ones reconstructed using the corrected $t'$. The 
-results are presented in figures \ref{fig:alu} and \ref{fig:alu90}.
-
-\begin{figure}[tb]
-   \centering
-\includegraphics[width=15cm]{fig/ALU_phi_p_Q2.pdf}
-\includegraphics[width=15cm]{fig/ALU_phi_p_x.pdf}
-\includegraphics[width=15cm]{fig/ALU_phi_p_t.pdf}
-\caption{The EG6 incoherent $A_{LU}$ as a function of $\phi$. Results are 
-   presented for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle 
-panel), and $t$ bins (bottom panel) using $t$ in black points and using the 
-corrected $t'$ in red points.  The red curves are the results of our fits with 
-the form $\frac{\alpha sin(\phi)}{1+ \beta cos(\phi)}$.}
-\label{fig:alu}
-\end{figure}
-
-\begin{figure}[tb]
-   \centering
-\includegraphics[width=12cm]{fig/ALU_90_p_vs_Q2_shortscenrario.pdf}
-\includegraphics[width=12cm]{fig/ALU_90_p_vs_x_shortscenrario.pdf}
-\includegraphics[width=12cm]{fig/ALU_90_p_vs_t_shortscenrario.pdf}
-\caption{The EG6 incoherent $Q^{2}$ (left), $x_{B}$ (middle), and 
-$t$-dependencies (right) of the $A_{LU}$ at $\phi$~=~90$^{\circ}$ using $t$ in 
-black points and using the corrected $t'$ in red points. }
-\label{fig:alu90}
-\end{figure}
-
-\section{Conclusions}
-We improved the EG6 incoherent DVCS channel via the $t'$ that is calculated 
-using the virtual and the final state real photons with corrections based on 
-similar analysis on the free proton DVCS sample using the same setup of CLAS 
-detector. The $Q^{2}$ and $x_B$ dependences of the asymmetries have shown 
-slight changes using $t'$ rather than $t$, while the effect is bigger on the 
-t-dependence, with overall changes are compatible with the statistical error 
-bars.  Based on the free proton DVCS data, no induced systematic uncertainties 
-are observed on the $Q^{2}$ and $x_B$, while some appear on $t$, which will be 
-added to the EG6 incoherent asymmetries.
-
 \end{document}

### 2018-10-04 eg6-letters/incoherent/incoh_fermi_investigation/Incoh_fermi.tex
updated the fermi motion investigation

%\documentclass[a4paper,11pt,twoside]{ThesisStyle}
\documentclass[a4paper,11pt,twoside]{article}

\date{\today}
\include{formatAndDefs}
\begin{document}

\title{\centering{Investigating the Fermi motion smearing on the incoherent 
DVCS channel}}
\maketitle

Following our emails on investigating the Fermi motion effect on smearing our 
t-bin values in the incoherent DVCS channel, here in figure \ref{fig:exp} I 
show the $t$ distributions of our binning in $t$. On the simulation side, 
figure \ref{fig:fermi} shows the initial proton's Fermi momentum distribution 
of the simulated incoherent DVCS. To estimate the smearing of Fermi motion on 
$t$ values, in figure \ref{fig:sim} I calculated $t$ by assuming that the 
initial proton is at rest (first row of plots) and using the exact generated 
initial proton kinematics (second row of plots). In the third row of figure 
\ref{fig:sim}, I show the difference between the two calculated $t$ values for 
the different bins.

\begin{figure}[h!]
   \centering
\includegraphics[height=6.0cm]{figs/t_n_Incoh.pdf}
\caption{$t$ distributions for our experimental four bins in $t$.}
\label{fig:exp}
\end{figure}

\begin{figure}[h!]
   \centering
\includegraphics[height=5.0cm]{figs/sim_Fermi_mom.png}
\caption{The Fermi momentum distribution of the initial proton in the simulated 
   incoherent DVCS events.
   }
\label{fig:fermi}
\end{figure}

\begin{figure}[h!]
   \centering
\includegraphics[height=14.0cm]{figs/sim_t_n_Incoh.pdf}
\caption{$t$ distributions for the simulated incoherent DVCS events. From left 
   to right are our four bins in $t$. In the first row of plots, $t$ is 
   calculated assuming the initial proton is on-shell. In the second row plots, 
   $t$ is calculated using the true generated momentum of the initial proton .  
   In the third raw, I show the difference between the two calculated $t$ 
   values.}
   \label{fig:sim}
\end{figure}

\end{document}

### 2018-10-09 eg6-letters/incoherent/figs/incoherent_Handbag.C
add the source file for the incoherent handbag diagram

@@ -1,0 +1,167 @@
+void incoherent_Handbag(void){
+ TCanvas *c1 = new TCanvas("c1", "A canvas", 20,20, 1000, 800);
+          c1->Range(-30, -65, 90, 140);
+
+          Int_t linsav = gStyle->GetLineWidth();
+ gStyle->SetLineWidth(3);
+
+ TArrow *arr;
+ TLatex t;
+ t.SetTextAlign(22);
+ t.SetTextSize(0.04);
+
+ TLatex tt;
+ tt.SetTextAlign(22);
+ tt.SetTextSize(0.045);
+ tt.SetTextColor(4);
+
+
+ // target 
+ TLine * l;
+         l = new TLine(20, -3, 35, 25); l->SetLineWidth(10); l->Draw();
+         l = new TLine(78, 5, 58, 25); l->SetLineWidth(10); l->Draw();
+
+         arr = new TArrow(20, -3, 28, 12, 0.05,"|>");  arr->SetAngle(40);  arr->Draw();
+         arr = new TArrow(58, 25, 72, 11, 0.05,"|>");  arr->SetAngle(40);  arr->Draw();
+
+        // incoming lines  
+        l = new TLine(-28, -15, 0, -15);l->Draw();
+        l = new TLine(-28, -20, 0, -20);l->Draw();
+        l = new TLine(-28, -25, 0, -25);l->Draw();
+        l = new TLine(-28, -30, 0, -30);l->Draw();
+
+        arr = new TArrow(-28, -15, -17, -15, 0.03,">"); arr->SetAngle(40);  arr->Draw();
+        arr = new TArrow(-28, -20, -17, -20, 0.03,">"); arr->SetAngle(40);  arr->Draw();
+        arr = new TArrow(-28, -25, -17, -25, 0.03,">"); arr->SetAngle(40);  arr->Draw();
+        arr = new TArrow(-28, -30, -17, -30, 0.03,">"); arr->SetAngle(40);  arr->Draw();
+
+      
+         // out going line 
+        l = new TLine(20, -20, 60, -35);l->Draw();
+        l = new TLine(20, -25, 60, -40);l->Draw();
+        l = new TLine(20, -30, 60, -45);l->Draw();
+ 
[…]

### 2018-10-09 eg6-letters/incoherent/figs/incoherent_Handbag.C
update the incoherent handbag diagram

@@ -74,7 +74,7 @@ void incoherent_Handbag(void){
         l = new TLine(35, 65, 55, 65);l->Draw();
         l = new TLine(57, 38, 55, 65);l->Draw();
 
-        //arr = new TArrow(33, 38, 34.3, 55, 0.02,"|>"); arr->SetAngle(40);  arr->Draw();
+        arr = new TArrow(33, 38, 34.3, 55, 0.02,"|>"); arr->SetAngle(40);  arr->Draw();
         arr = new TArrow(35, 65, 45, 65, 0.02,"|>"); arr->SetAngle(40);  arr->Draw();
         arr = new TArrow(55, 65, 56.3, 48, 0.02,"|>"); arr->SetAngle(40);  arr->Draw();
 
@@ -92,7 +92,7 @@ void incoherent_Handbag(void){
        arcarrow->SetLineStyle(2);
        //arcarrow->Draw();
 
-       arr = new TArrow(51.0, 10, 52.0, 10, 0.03); arr->SetAngle(40);  arr->Draw();
+       //arr = new TArrow(51.0, 10, 52.0, 10, 0.03); arr->SetAngle(40);  arr->Draw();
 
        arcarrow = new TArc(45,115,35,240,315);
        arcarrow->SetNoEdges();

### 2018-10-09 eg6-letters/incoherent/incoherent_prl.tex
some cleaning

@@
    fraction carried by the struck quark, 2$\xi$ is the longitudinal momentum 
-   fraction of the momentum transfer $\Delta$ ($= p - p^\prime$), and 
+   fraction of the momentum transfer $\Delta$ ($= q - q^\prime$), and 
    $t$~($=\Delta^2$) is the squared momentum transfer between the initial and
@@
 four-momentum squared ($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small invariant 
-momentum transfer ($t=(p-p^\prime)^2$), the DVCS scattering process can be 
+momentum transfer ($t=(q-q^\prime)^2$), the DVCS scattering process can be 
 factorized, leaving the non-perturbative structure of the nucleon to be 
@@
 mass (W$=\sqrt{(q+p)^2}$) greater than 2 GeV to avoid the nucleon resonance 
-region.  The $t$, transferred momentum squared to the recoil proton assuming an 
-on-shell proton at rest, was required to be greater than a minimum allowed 
-value at given Q$^2$ and W ($t>~t_{min}(=~- Q^{2}~\frac{2(1- x_{B})(1~-~\sqrt{1 
-+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$,
+region.  The $t$, transferred momentum squared to the recoil proton, calculated 
+from 4-momentum vectors of incoming and outgoing photons, was required to be 
+greater than a minimum allowed value at given Q$^2$ and 
+W~($t>t_{min}(~=-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$,
 where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
-proton mass). Then, the exclusivity of the incoherent DVCS events was ensured 
-by imposing constraints on the kinematical variables resulting from conserving 
-the four-momentum in the reaction $ep\rightarrow e'p'\gamma$.  These 
-kinematical variables are: the coplanarity angle $\Delta\phi$ between the 
+proton mass). We used kinematics of the photons for determining the $t$ to 
+avoid uncertainty of the initial proton kinematics due to Fermi motion. Then, 
+the exclusivity of the incoherent DVCS events was ensured by imposing 
+constraints on the kinematical variables resulting from conserving the 
+four-momentum in the reaction $ep\rightarrow e'p'\gamma$. These kinematical 
+variables are: the coplanarity angle $\Delta\phi$ between the 
 ($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) planes, the missing energy, mass, and 
@@
 %\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}
-\includegraphics[width=8.5cm]{figs/ALU_ratioInc_t_shortscenrario.pdf}
+\includegraphics[width=8.5cm]{figs/ALU_ratioInc_t_shortscenrario-without-error-onX.pdf}
 \caption{ The $A_{LU}$ ratio of the bound to the free proton at 

### 2018-10-10 eg6-letters/incoherent/incoherent_prl.tex
implement the corrections from Stepan

@@
 associated with $\phi$-harmonics, where $\phi$ is the angle between the 
-leptonic and the hadronic planes of the reaction. At leading-twist, the 
-BSA can be simplified as: 
+leptonic and the hadronic planes of the reaction. At leading-twist, the BSA can 
+be parametrized as: 
 \begin{equation}
@@
 \end{equation}
-where $F_1$ and $F_2$ are the Dirac and Pauli form factors and $x_B$ the 
-Bjorken scaling variable. The real and the imaginary parts of the CFF 
-$\mathcal{H}$ relate to the GPD $H$ as  
-\begin{align}
+where $F_1$ and $F_2$ are the Dirac and Pauli form factors, respectively, and 
+$x_B$ the Bjorken scaling variable. The real and the imaginary parts of the CFF 
+$\mathcal{H}$ relate to the GPD $H$ as  \begin{align}
    \Re(&\mathcal{H}) = \mathcal{P} \int_{0}^{1}dx[H(x,\xi,t)-H(-x,\xi,t)] \, 
@@
 In the kinematical phase-space of our experiment, the GPD $H$ is
-expected to dominate the 
-contribution in the BSA over the other three GPDs. There, 
-the $\phi$ dependence of $A_{LU}$ is mostly sensitive to the  
-imaginary part of the CFF $\mathcal{H}$ through the parameters $a_0$ of 
-equation~\ref{eq:alu-simp}. The measurement of the free proton 
-$A_{LU}$ \cite{Girod:2007aa} has confirmed that the $a_0$ term is 
-dominating the shape of the distribution.
+expected to dominate the contribution in the BSA over the other three GPDs.  
+There, the $\phi$ dependence of $A_{LU}$ is mostly sensitive to the  imaginary 
+part of the CFF $\mathcal{H}$ through the parameter $a_0$ of 
+equation~\ref{eq:alu-simp}. The measurement of the free proton $A_{LU}$ 
+\cite{Girod:2007aa} has confirmed that the $a_0$ term is dominating the shape 
+of the distribution.
 
@@
 Within the given uncertainties, $A_{LU}$ does not indicate a strong dependence 
-on $Q^2$.  The $x_{B}$ and $t$ dependency are compared to theoretical 
+on $Q^2$.  The $x_{B}$ and $t$ dependencies are compared to theoretical 
 calculations performed by S.~Liuti and K.~Taneja \cite{simonetta_2}. Their 
@@
 but still provide important guidance. The experimental results appear to have 
-smaller asymmetries especially at low $x_{B}$ than the calculations. These 
+smaller asymmetries especially at small $x_{B}$ than the calculations. These 
 differences may arise from nuclear effects which are not taken into account in 

### 2018-10-15 eg6-letters/incoherent/2nd-adhocreview/2nd_adhoc_comments.tex
some cleaning
Modif on Incoherent for ad hoc

@@
 \title{Second round comments from the Ad-hoc rewiew committee \\
- (Maurik Holtrop, Kevin Giovankl, Zein-Eddine Meziani)}
+ (Maurik Holtrop, Kevin Giovanetti, Zein-Eddine Meziani)}
 
@@
 variable, could be added to make this explicitly clear to the reader.\\
-   \textcolor{blue}{Updated.}\\
+   \textcolor{blue}{We used the kinematics of the photons to determine $t$ specifically
+   in order to avoid such uncertainty linked to the initial proton kinematics (see 
+   Appendix H of the analysis note for details). However, the paper was unclear on 
+   the topic, we have changed Fig 1 and added a statement line 160-163 to clarify 
+   this in the new version.}\\
 

### 2018-10-15 eg6-letters/incoherent/incoherent_prl.tex
Modif on Incoherent for ad hoc

@@
 where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
-proton mass). We used kinematics of the photons for determining the $t$ to 
-avoid uncertainty of the initial proton kinematics due to Fermi motion. Then, 
-the exclusivity of the incoherent DVCS events was ensured by imposing 
-constraints on the kinematical variables resulting from conserving the 
-four-momentum in the reaction $ep\rightarrow e'p'\gamma$. These kinematical 
+proton mass). We specifically use the kinematics of the photons to determine 
+$t$ because the initial proton kinematics is unknown due to Fermi motion. Then, 
+we ensured the exclusivity of the incoherent DVCS events by imposing 
+a series of constraints based on the four-momentum conservation 
+in the reaction $ep\rightarrow e'p'\gamma$. These kinematical 
 variables are: the coplanarity angle $\Delta\phi$ between the 

### 2018-11-05 eg6-letters/incoherent/incoherent_prl.tex
Minor accent issue
the third round comments from the adhoc committee

@@
 coefficient function defined as $(1/(x-\xi) + 1/(x+\xi))$, there $\xi$ is the 
-skewing factor and can be
-related to $x_B$ by $\xi\approx {{x_B}\over{2-x_B}}$. Similar expressions apply 
-for the GPDs $E$, $\widetilde{H}$, and $\widetilde{E}$.
+skewing factor and can be related to $x_B$ by $\xi\approx {{x_B}\over{2-x_B}}$.  
+Similar expressions apply for the GPDs $E$, $\widetilde{H}$, and 
+$\widetilde{E}$.
 
@@
 applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
-mass (W$=\sqrt{(q+p)^2}$) greater than 2 GeV to avoid the nucleon resonance 
-region.  The $t$, transferred momentum squared to the recoil proton, calculated 
-from 4-momentum vectors of incoming and outgoing photons, was required to be 
-greater than a minimum allowed value at given Q$^2$ and 
+mass (W$=\sqrt{(q+p)^2}$ assuming the initial proton is at rest) greater than 2 
+GeV to avoid the nucleon resonance region.  The $t$, transferred momentum 
+squared to the recoil proton, calculated from 4-momentum vectors of incoming 
+and outgoing photons, was required to be greater than a minimum allowed value 
+at given Q$^2$ and 
 W~($t>t_{min}(~=-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$,
@@
 are slightly wider than those previously used for free proton experiments~%
-\cite{Girod:2007aa}. After the corrections discussed below, the assymetries 
+\cite{Girod:2007aa}. After the corrections discussed below, the asymmetries 
 appear to be stable as a function of cut width and we see no sizeable effect 
 that can be related to the initial momentum of the nucleons. We also rejected 
-events where a $\pi^0$ was identified by the invariant mass of 
-two photons. At the end of this selection process, about 30k events 
-passed all the requirements; their kinematic distributions are shown in 
+events where a $\pi^0$ was identified by the invariant mass of two photons. At 
+the end of this selection process, about 30k events passed all the 
+requirements; their kinematic distributions are shown in 
 FIG.~\ref{fig:kin-coverage}.
@@
 %background
-The two main backgrounds that contribute to the event sample after the exclusivity cuts are  
-due to accidental coincidences and exclusive $\pi^0$ production where one of the photons 
-from the $\pi^0$ decay escapes the detection. The contribution from accidental 
-events, i.e., $e'p'\gamma$ collections 
-with particles originating from different electron scatterings,
-was evaluated to be of 6.5\% by selecting events passing all our selection cuts but originating from 
-different vertices. The $\pi^0$ contamination was estimated using detector 
-simulation and experimental data. From simulation, we calculated the ratio ($R 
-= N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ events that 
-are wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the 
-number of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$.  
-Then in each kinematical bin and for each beam-helicity state, the 
+The two main backgrounds that contribute to the event sample after the 
+exclusivity cuts are due to accidental coincidences and exclusive $\pi^0$ 
+production where one of the photons from the $\pi^0$ decay escapes the 
+detection. The contribution from accidental events, i.e., $e'p'\gamma$ 
+collections with particles originating from different electron scatterings, was 
+evaluated to be of 6.5\% by selecting events passing all our selection cuts but 
+originating from different vertices. The $\pi^0$ contamination was estimated 
+using detector simulation and experimental data. From simulation, we calculated 
+the ratio ($R = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ 
+events that are wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ 
+events to the number of events correctly identified as exclusive $ep\rightarrow 
+e'p'\pi^0$.  Then in each kinematical bin and for each beam-helicity state, the 
 $\pi^0$-subtracted experimental DVCS events is calculated as $N = 
@@
 an important nuclear effect is missing from the existing models in order to 
-explain this strong quenching of the BSA.  More theoretical developments will 
-be needed to identify the origin of this quenching, in particular it will be 
-key to differenciate initial from final state effects and how they can affect 
-the DVCS assymetries.
+explain this strong quenching of the BSA. More theoretical developments will be 
+needed to identify the origin of this quenching, in particular it will be key 
+to differentiate initial from final state effects and how they can affect the 
+DVCS asymmetries.
 
@@
 bound-proton BSA is largely suppressed compared to the free proton BSA. This 
-surprising result opens a new avenue for progress in understanding the 
-properties of quarks and gluons in the nuclear medium.
+result is a first step in using an exciting novel experimental method of 
+understanding the properties of bound nucleons directly from the basic degrees 
+of freedom of QCD, quarks and gluons.
 
@@
 \bibitem{Dupre:2015jha} 
-  R.~Dupré and S.~Scopetta,
+  R.~Dupr\'e and S.~Scopetta,
   Eur.\ Phys.\ J.\ A {\bf 52}, no. 6, 159 (2016)

### 2018-11-05 eg6-letters/incoherent/incoherent_prl.tex
final version

@@
 applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
-mass (W$=\sqrt{(q+p)^2}$ assuming the initial proton is at rest) greater than 2 
-GeV to avoid the nucleon resonance region.  The $t$, transferred momentum 
-squared to the recoil proton, calculated from 4-momentum vectors of incoming 
-and outgoing photons, was required to be greater than a minimum allowed value 
-at given Q$^2$ and 
+mass (W$=\sqrt{(q+p)^2}$, assuming that the initial proton is at rest) greater 
+than 2 GeV to avoid the nucleon resonance region.  The $t$, transferred 
+momentum squared to the recoil proton, calculated from 4-momentum vectors of 
+incoming and outgoing photons, was required to be greater than a minimum 
+allowed value at given Q$^2$ and 
 W~($t>t_{min}(~=-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$,

### 2018-11-06 eg6-letters/incoherent/incoherent_prl.tex
Passed through auto corrector

@@
 factorized, leaving the non-perturbative structure of the nucleon to be 
-parametrized in terms of four chirally-even GPDs: $H$, $E$, $\widetilde{H}$, 
+parameterized in terms of four chirally-even GPDs: $H$, $E$, $\widetilde{H}$, 
 and $\widetilde{E}$, representing the four helicity-spin combinations of the 
@@
 leptonic and the hadronic planes of the reaction. At leading-twist, the BSA can 
-be parametrized as: 
+be parameterized as: 
 \begin{equation}
@@
 \cite{Girod:2007aa}. After the corrections discussed below, the asymmetries 
-appear to be stable as a function of cut width and we see no sizeable effect 
+appear to be stable as a function of cut width and we see no sizable effect 
 that can be related to the initial momentum of the nucleons. We also rejected 
@@
 %conclusion
-In summary, we have presented the first BSA measurment associated with bound 
+In summary, we have presented the first BSA measurement associated with bound 
 proton DVCS off $^4$He using an upgraded setup of the CLAS spectrometer at 

### 2018-11-27 eg6-letters/incoherent/collaboration_comments/clas_comments.tex
implement the comment from the clas collaboration review

%\documentclass[a4paper,11pt,twoside]{ThesisStyle}
\documentclass[a4paper,11pt,twoside]{article}

\date{\today}
\include{formatAndDefs}
\begin{document}

\section{Comments from Daniel Carman}

\begin{enumerate}

\item Page 1:\\
 - Abstract:\\
   - Line 4. Use "... azimuthal angle ...".
   \textcolor{blue}{Done}

   - Line 5. Use "... of the beam spin asymmetry (BSA) was ..."
   \textcolor{blue}{is -> was, corrected!}

   - Line 6. Use "$Q^2$".
   \textcolor{blue}{Done}

   - Line 9. Use "... and for exploring the origin ...".
   \textcolor{blue}{Done.}

 - Line 36. Use "... a three-dimensional (3-D) ..."
   \textcolor{blue}{Added.}

 - Line 38. Use "The measurement of free proton DVCS has been ...".
   \textcolor{blue}{Modified.}

 - Line 45. Use "... similar 3-D picture of the ...".
   \textcolor{blue}{Corrected}

 - Line 46. Use "... case, however, two ...".
   \textcolor{blue}{Done}

 - Line 65. Use "Fig. 1".
   \textcolor{blue}{Kept as FIG.1. We show it in the text as shown in the 
      caption.}

 - Line 67. Use "i.e.".
   \textcolor{blue}{Done}
~\\
\item Page 2:\\
 - Fig. 1 caption.\\
   - Line 5. Use "... is the nucleon longitudinal ...".
   \textcolor{blue}{Done}

 - Line 72. Use "chirally even".
   \textcolor{blue}{Done}

 - Eq. (1). Use comma after equation, not a period.
   \textcolor{blue}{Done}

 - Line 84. Use "... is the virtual photoproduction differential cross section 
      ...".
   \textcolor{red}{We do not agree here.}

 - Eq. (2). Add a comma after the equation.
   \textcolor{blue}{Done}

 - Line 93. Use "abovementioned".
   \textcolor{blue}{Done}

 - Eq. (3). Add a comma after the equation.
   \textcolor{blue}{Done}

 - Line 103. Use "... where $\xi$ is the ...".
    \textcolor{blue}{Done}

 - Line 105. Use "Similar expressions apply for the GPDs ...". Provide a 
   reference here.
     \textcolor{blue}{Done}

 - Line 108. Use "longitudinally polarized".
      \textcolor{blue}{Done}

- Line 113. Use "... centered 64~cm upstream ...".
      \textcolor{blue}{Done}

- Line 115. Use "... [40] was supplemented ...".
      \textcolor{blue}{Done}

- Line 117. Use "The IC extended ...".
      \textcolor{blue}{Done}

- Line 123. Use "beamline".
      \textcolor{blue}{Done}

- Line 138. Use "... timing cut was used to separate the EC ...".
      \textcolor{blue}{Done}

- Line 142. Use "... photons were mostly soft ..."
     \textcolor{blue}{Done}
~\\
  \item Page 3:\\
 - Line 144. Use "... cuts easily eliminated.".
    \textcolor{blue}{Done}

- Line 145. Use "... photon was considered ...".
     \textcolor{blue}{Done }

- Line 146. Use "... on the particle identification."
     \textcolor{blue}{Done }

- Line 151. Use "$Q^2$".
     \textcolor{blue}{Done}

- Line 153. Use "$W$".
     \textcolor{blue}{Done }

- Line 155. Use "The squared transferred momentum to the recoil proton $t$, 
  calculated from the four-momentum vectors of the incoming ...".
     \textcolor{blue}{Done }

- Line 158. Use "... at a given $Q^2$ and $W$ ...".
     \textcolor{blue}{Done}

- Line 161. Use "specifically used the ...".
     \textcolor{blue}{Done}

- Line 173. Use "Fig. 2".
     \textcolor{blue}{We keep it as in the caption.}

- Line 178. Use "... and we saw no sizable effect that could be ...".
     \textcolor{blue}{Done}

- Line 183. Use "Fig. 3".
     \textcolor{blue}{We keep it as in the caption.}

- Line 184. Use "... that contributed ...".
     \textcolor{blue}{Done}

- Line 187. Use "... escapes detection.".
     \textcolor{blue}{Done }

- Line 190. Use "... to be 6.5\% by ...".
     \textcolor{blue}{Done }

- Line 195. Use "... that were wrongly identified ...".
     \textcolor{blue}{Done}

- Fig. 2 caption.\\
   a- Line 2. Use "... to bottom are: ...".
    \textcolor{blue}{Done}\\
   b- Line 7. Use "... event candidates ..."
    \textcolor{blue}{Done}\\
   c- Line 8. Use "... events that passed ...".
    \textcolor{blue}{Done}\\
   d- Line 9. Use "... all of these cuts ...".
    \textcolor{blue}{Done}

 - Line 199. Use "... events were calculated as ...".
    \textcolor{blue}{Done}
~\\
\item Page 4:\\
 - Line 203. Use "... to be 8 to 10\%".
     \textcolor{blue}{Done}

- Eq. (6). Equation should end with a comma, not a period.
      \textcolor{blue}{Done}

- Line 206. Use "... DVCS events for the positive ...".
      \textcolor{blue}{Done}

- Line 207. Use "... beam-helicity states, ...".
      \textcolor{blue}{Done.}

- Line 215. Use "... $a_0$ term dominates the shape ...".
      \textcolor{blue}{Done}

- Line 220. Use "Fig. 4".
      \textcolor{blue}{We prefer to keep it as in the caption.}

- Line 222. Use "... integrated over the full ...".
      \textcolor{blue}{Done}

- Line 223. Use "... integrated over the full  ... integrated over the full 
  ...".
      \textcolor{blue}{Done}

- Line 225. Use "sin" and "cos" should be in rm font. In latex use "$\sin$" and 
  "$\cos$" in math mode.
      \textcolor{blue}{Done}

- Line 230. Use "statistical uncertainties".
      \textcolor{blue}{Done}

- Line 231. Use "Fig. 5".
      \textcolor{blue}{We prefer to keep it as in the caption.}

- Line 233. Use "Fig. 4".
      \textcolor{blue}{We prefer to keep it as in the caption.}

- Line 234. Use "... does not show a strong ...".
      \textcolor{blue}{Done}

- Line 236. Use "... are compared to the theoretical ...".
      \textcolor{blue}{Done}

- Line 238. Use "Their model used a nuclear spectral function and considers 
   mainly off-shell effects." This is a statement of jargon that is not 
   appropriate for the general PRL audience.  Please reconsider.
      \textcolor{red}{We kept it as it is.}

- Line 243. Use "... effects that are not taken ...".
      \textcolor{blue}{Done}

- Line 245. Use "... knocked-out proton ...".
      \textcolor{blue}{Done}

- Line 246. Use "On the graph for the $-t$ ...".
      \textcolor{blue}{Done}

- Line 247. Use "HERMES Collaboration".
      \textcolor{blue}{Done}

- Line 254. Use "... we constructed ...".
      \textcolor{blue}{Done}

- Fig. 4. The labels are all too small on this plot (axis labels, titles, plot 
  kinematic labels)
      \textcolor{red}{Will be revised.}

- Fig. 4 caption.\\
   a- Line 2. Use "(top row)".
      \textcolor{blue}{Done}\\
   b- Line 3. Use "(middle row)" and "(bottom row)".
      \textcolor{blue}{Done}\\
   c- Line 7. "sin" and "cos" should be in rm font. In latex use "$\sin$" and 
   "$\cos$" in math mode.
      \textcolor{blue}{Done}

- Line 255. Use "Fig. 6".
      \textcolor{blue}{We prefer to keep it as in the caption.}

- Line 259. Use "... lower asymmetries that are independent of ...".
      \textcolor{blue}{Done}

- Line 262. Use "medium-modified".
      \textcolor{blue}{Done}

- Line 268. Use "... will be important to differentiate ...".
      \textcolor{blue}{Done}

- Line 273. Use "Our results are compared ...".
     \textcolor{blue}{Done}
~\\
\item Page 5:\\
 - Fig. 5 caption.\\
   - Line 5. Use "On the middle plot the curves ...".
     \textcolor{blue}{Done}\\
   - Line 6. Use "On the bottom plot the solid ...".
     \textcolor{blue}{Done}\\
   - Line 8. It is not clear what you mean by "enriched region".  
     \textcolor{blue}{They were not detecting the final state hadron and the 
     were separating the coherent from the incoherent DVCS events based on the 
     assumption that the coherent dominates the low $t$ region and the 
     incoherent dominate the high $t$ region, and they avoided calling it pure 
     coherent or incoherent by labeling them as coherent or incoherent enriched 
     regions. }\\
   - Line 8. Use "... [30]; the curves represent ...".
     \textcolor{blue}{Done}
~\\
References:\\
 - End the following references with a period: [2], [28], [29], [30], [31], 
   [32], [33], [34], [38].
     \textcolor{blue}{Done. All the references have been double checked for 
     this.}

 - Ref. [40] is not a CLAS Collaboration paper.
     \textcolor{blue}{Cleaned}

 - Refs. [42] and [43] are not cited in the paper.
     \textcolor{blue}{Cleaned.}

\end{enumerate}

\section{Comments from Michel Gar\c{c}on}

\begin{enumerate}

\item Since HERMES already measured DVCS BSA on "coherent enriched" and "
   incoherent enriched" event samples off He4, one has to be more careful i) in 
      the use of ''first'' in the abstract and on lines 62 and 270, ii) on the 
      way to quote or qualify ref. [30]. In any case, the way it is done now is 
      not OK if only because Figs 5 and 6 show that there were previous 
      measurements, and this is contradictory with the use of "first". My 
      suggestion would be to keep the word "first" (at the risk of having 
      problems with a referee), except maybe in line 62, to remove the ref 30 
      in line 49 and to add at the end of the paragraph in line 61 the 
      sentence: "The previous (or pioneering?) measurements of DVCS off nuclei, 
      and in particular off 4He, performed at HERMES [30] yielded results with 
      both "coherent enriched" and "incoherent enriched" event samples, hence 
      not fully exclusive, but significant enough to be compared with our 
      results below".
\textcolor{blue}{}

   \item Abstract line 3: "within" or "close to the center of" instead of "in 
      front of".
\textcolor{blue}{in front of -> within.}

   \item Abstract next to last line: "for studying the structure of bound 
      nucleons".
\textcolor{blue}{Done.}

   \item Line 50: happens -> occurs.
\textcolor{blue}{Done.}

   \item Fig. 1 caption: is not it -2ksi, and not 2ksi ?
\textcolor{blue}{Done.}

   \item Line 158: ... minimum kinematically allowed ...
\textcolor{blue}{Done.}

   \item Line 188-192: one wonders what is done with this 6.5\%. If nothing is 
      done, should be stated explicitly and/or justified
\textcolor{blue}{We have corrected our asymmetries for these accidentals.
      }\\
       \textcolor{blue}{This sentence has been added to the paper: Our final 
       asymmetries have been corrected for this contamination in the form
      $A_{LU~corrected}~=~\frac{1}{1-contamination~percentage}~A_{LU~measured}$ 
      }

   \item Figs 2, 3 and 4: tick labels too small.
\textcolor{red}{will be revised.}

   \item Line 277: I would drop "exciting"; "novel" is enough.
\textcolor{blue}{Done.}

   \item Ref. [3]: why not quote the latest 2018 issue? It also contains a 
      section on DIS.
\textcolor{blue}{Done.}

   \item Ref. [20]: this work was superseded by PRC92, 055202 (2015), a 
      reanalysis of the same data. I would either replace Munoz Camacho et al.  
      by Defurne et al, or add to CMC: updated in ....
      \textcolor{blue}{Replaced by: M. Defurne et al. (Jefferson Lab Hall A 
      Collaboration). Phys. Rev. C 92, 055202 (2015).}

   \item Ref[38]: add B+M, PRD82, 0704010 (2010).
\textcolor{blue}{Added.}

   \item Ref.[39]: why not give the publicly accessible link to the proposal?
   \textcolor{blue}{Added.}

\end{enumerate}

\section{Comments from David Irland}

\begin{enumerate}

\item Page 2, Equation 3: I don't see the definition of epsilon (or is it a 
   curly E?)
\textcolor{blue}{It is the Compton form factor associated with the GPD E.}

\item Page 3, line 154: Is a lower limit of 2 GeV enough to avoid the nucleon 
   resonance region? There are several known resonances in the range between 2 
      and 3 GeV. Perhaps you can argue that the effect of these is negligible.
\textcolor{blue}{Right, all the free nucleon DVCS analysis have made this 
      assumption.}

\item Page 3, line 159-160: the equations are quite hard to follow, 
   particularly with the braces. It may look better as a displaymath equation.
\textcolor{blue}{Tested. It is not looking much better.}

\item Page 4, figure 4: the font size is way too small!  \textcolor{red}{Will 
   be revised.}

\end{enumerate}

\end{document}

### 2018-11-27 eg6-letters/incoherent/incoherent_prl.tex
implement the comment from the clas collaboration review

@@
    using a 6 GeV longitudinally polarized electron beam incident on a 
-   pressurized $^4$He gaseous target placed in front of the CLAS spectrometer 
-   in Hall-B at the Thomas Jefferson National Accelerator Facility. The 
-   azimuthal angular ($\phi$) dependence of the BSA is studied in a wide range 
-   of virtual photon and scattered proton kinematics. The Q$^2$, $x_B$, and $t$ 
+   pressurized $^4$He gaseous target placed within the CLAS spectrometer in 
+   Hall-B at the Thomas Jefferson National Accelerator Facility. The azimuthal 
+   angle ($\phi$) dependence of the BSA was studied in a wide range of virtual 
+   photon and scattered proton kinematics. The $Q^2$, $x_B$, and $t$ 
    dependencies of the BSA on the bound proton are compared with those on the 
@@
    modification of its partonic structure. This measurement opens a new avenue 
-   for studying structure of the bound nucleon and explore the origin of the 
-   EMC effect using the framework of the generalized parton distributions.
+   for studying the structure of bound nucleons and for exploring the origin of 
+   the EMC effect using the framework of the generalized parton distributions.
 
@@
 i.e., the hard exclusive lepto-production of a real photon, which provides 
-access to a three-dimensional imaging of partons within the generalized parton 
-distributions (GPDs) framework 
+access to a three-dimensional (3-D) imaging of partons within the generalized 
+parton distributions (GPDs) framework 
 \cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.   
-The free proton DVCS measurement has been the focus of a worldwide effort 
-\cite{Stepanyan:2001sm,Airapetian:2001yk,Airapetian:2006zr,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
-Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}
+The measurement of free proton DVCS has been the focus of a worldwide effort 
+\cite{Stepanyan:2001sm,Airapetian:2001yk,Airapetian:2006zr,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Defurne:2015kxq,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}
 involving several accelerator facilities such as Jefferson Lab, DESY and  
@@
 and a 3-D tomography of the free proton \cite{Guidal:2013rya,Dupre:2016mai}.  
-New measurements of DVCS from the $^{4}$He nucleus are a critical 
-step towards providing a similar 3-D pictures of the quark structure of the 
-nucleus~\cite{Dupre:2015jha}. In the nuclear case however, two channels are available,
-the coherent channel where the scattering is off the entire nucleus, which is 
-left intact in the final state \cite{Airapetian:2009cga,
-Hattawy:2017woc}, and the incoherent channel where the DVCS happens on a 
-nucleon, which is ejected from the nucleus.
-The latter is the focus of this letter and provides a unique access to the 
-modification of the partonic structure of the bound nucleons 
-\cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}. The 
-$^{4}$He nucleus is an ideal experimental target for this measurement as it is 
-characterized by a strong binding energy, a relatively high nuclear 
-core density, and a large EMC effect~\cite{JSeely}. Moreover, it remains simple 
-enough that precise calculation of its structure 
-can be performed, making this nucleus the perfect target for our investigation of the 
-medium modifications of the nucleon's partonic structure.
+New measurements of DVCS from the $^{4}$He nucleus are a critical step towards 
+providing a similar 3-D picture of the quark structure of the 
+nucleus~\cite{Dupre:2015jha}. In the nuclear case, however, two channels are 
+available, the coherent channel where the scattering is off the entire nucleus, 
+which is left intact in the final state \cite{Airapetian:2009cga,
+Hattawy:2017woc}, and the incoherent channel where the DVCS occurs on a 
+nucleon, which is ejected from the nucleus. The latter is the focus of this 
+letter and provides a unique access to the modification of the partonic 
+structure of the bound nucleons \cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}.  
+The $^{4}$He nucleus is an ideal experimental target for this measurement as it 
+is characterized by a strong binding energy, a relatively high nuclear core 
+density, and a large EMC effect~\cite{JSeely}. Moreover, it remains simple 
+enough that precise calculation of its structure can be performed, making this 
+nucleus the perfect target for our investigation of the medium modifications of 
+the nucleon's partonic structure.
 
@@
    photons, and protons are denoted by $k/k^\prime$, $q/q^\prime$, and 
-   $p/p^\prime$, respectively. $x+\xi$ is the nucleon’s longitudinal momentum 
-   fraction carried by the struck quark, 2$\xi$ is the longitudinal momentum 
+   $p/p^\prime$, respectively. $x+\xi$ is the nucleon longitudinal momentum 
+   fraction carried by the struck quark, -2$\xi$ is the longitudinal momentum 
    fraction of the momentum transfer $\Delta$ ($= q - q^\prime$), and 
@@
 proton in $^{4}$He. FIG.~\ref{fig:diags} illustrates the leading-twist handbag 
-diagram for the DVCS process. In the Bjorken regime, i.e, large virtual photon 
+diagram for the DVCS process. In the Bjorken regime, i.e. large virtual photon 
 four-momentum squared ($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small invariant 
@@
 factorized, leaving the non-perturbative structure of the nucleon to be 
-parameterized in terms of four chirally-even GPDs: $H$, $E$, $\widetilde{H}$, 
+parameterized in terms of four chirally even GPDs: $H$, $E$, $\widetilde{H}$, 
 and $\widetilde{E}$, representing the four helicity-spin combinations of the 
@@
 \begin{equation}
-   A_{LU}(\phi) = \frac{a_{0}\sin(\phi)}{1+a_{1}\cos(\phi)+a_{2}\cos(2\phi)}
+   A_{LU}(\phi) = \frac{a_{0}\sin(\phi)}{1+a_{1}\cos(\phi)+a_{2}\cos(2\phi)},
    \label{eq:alu-simp}
 \end{equation}
-where the parameters $a_{0,1,2}$ are combinations of the above mentioned Fourier 
-coefficients. The $\sin(\phi)$ harmonic is dominant in $A_{LU}$ 
-and is proportional to the following combination of Compton form factors (CFF) 
+where the parameters $a_{0,1,2}$ are combinations of the abovementioned Fourier 
+coefficients. The $\sin(\phi)$ harmonic is dominant in $A_{LU}$ and is 
+proportional to the following combination of Compton form factors (CFF) 
 \cite{Guidal:2013rya}
@@
    a_{0} \propto \operatorname{Im}( F_1 \mathcal{H}- \frac{t}{4M^2} F_2 
-   \mathcal{E}+ \frac{x_B}{2}(F_1+F_2)\tilde{\mathcal{H}})
+   \mathcal{E}+ \frac{x_B}{2}(F_1+F_2)\tilde{\mathcal{H}}),
 \end{equation}
@@
    \Re(&\mathcal{H}) = \mathcal{P} \int_{0}^{1}dx[H(x,\xi,t)-H(-x,\xi,t)] \, 
-   C^{+}(x,\xi) \\
+   C^{+}(x,\xi), \\
    \Im(&\mathcal{H}) = - \pi [H(\xi,\xi,t)-H(-\xi,\xi,t)],
@@
 with $\mathcal{P}$ the Cauchy principal value integral and $C^{+}$ a 
-coefficient function defined as $(1/(x-\xi) + 1/(x+\xi))$, there $\xi$ is the 
+coefficient function defined as $(1/(x-\xi) + 1/(x+\xi))$, where $\xi$ is the 
 skewing factor and can be related to $x_B$ by $\xi\approx {{x_B}\over{2-x_B}}$.  
 Similar expressions apply for the GPDs $E$, $\widetilde{H}$, and 
-$\widetilde{E}$.
+$\widetilde{E}$ \cite{Guidal:2013rya}.
 
@@
 The experiment (E08-024~\cite{Hafidi:2008pr}) took place in Hall-B of Jefferson 
-Lab using the nearly 100\% duty factor, longitudinally-polarized electron beam 
+Lab using the nearly 100\% duty factor, longitudinally polarized electron beam 
 (83$\%$ polarization) from the Continuous Electron Beam Accelerator Facility 
-(CEBAF) at an energy of 6.064 GeV. The data were accumulated over 
-40 days using a 6-atm-pressure, 292-mm-long, and 6-mm-diameter gaseous $^4$He 
-target centered at 64~cm upstream of the CEBAF Large Acceptance Spectrometer 
-(CLAS) coordinate center. For DVCS experiments, the CLAS baseline design 
-\cite{Mecking:2003zu} is supplemented with an inner calorimeter (IC) and a 
-solenoid magnet. The IC extends the photon detection acceptance of CLAS down 
-to a polar angle of 4$^{\circ}$. The 5-Tesla solenoid magnet in the center of 
-which the target was located prevented the high-rate low-energy M{\o}ller 
-electrons from reaching the CLAS drift chambers by guiding these electrons 
-inside a tungsten shield placed around the beam line.
+(CEBAF) at an energy of 6.064 GeV. The data were accumulated over 40 days using 
+a 6-atm-pressure, 292-mm-long, and 6-mm-diameter gaseous $^4$He target centered 
+64~cm upstream of the CEBAF Large Acceptance Spectrometer (CLAS) coordinate 
+center. For DVCS experiments, the CLAS baseline design \cite{Mecking:2003zu} 
+was supplemented with an inner calorimeter (IC) and a solenoid magnet. The IC 
+extended the photon detection acceptance of CLAS down to a polar angle of 
+4$^{\circ}$. The 5-Tesla solenoid magnet in the center of which the target was 
+located prevented the high-rate low-energy M{\o}ller electrons from reaching 
+the CLAS drift chambers by guiding these electrons inside a tungsten shield 
+placed around the beamline.
 
@@
 calorimeter. All the clusters within the IC fiducial region were assumed to be 
-photons, while a timing cut is used to clean the EC photons from neutrons. Note 
-that even though the DVCS reaction has only one real photon in the final state, 
-events with more than one photon were not discarded at this stage. These extra 
-photons are mostly soft photons from accidental coincidence which, as will be 
-discussed below, the DVCS exclusivity cuts eliminate easily. In the following 
-selection stage, the most energetic photon is considered as the DVCS photon 
-candidate (see \cite{Hattawy:thesis} for additional details on the particles 
-identification).
+photons, while a timing cut was used to clean the EC photons from neutrons.  
+Note that even though the DVCS reaction has only one real photon in the final 
+state, events with more than one photon were not discarded at this stage. These 
+extra photons were mostly soft photons from accidental coincidence which, as 
+will be discussed below, the DVCS exclusivity cuts easily eliminated. In the 
+following selection stage, the most energetic photon was considered as the DVCS 
+photon candidate (see \cite{Hattawy:thesis} for additional details on the 
+particle identification).
 
@@
 incoherent DVCS events from accidental and physics background events. First, 
-events were selected with Q$^{2}$ greater than 1 GeV$^2$ to ensure the 
+events were selected with $Q^{2}$ greater than 1 GeV$^2$ to ensure the 
 applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
-mass (W$=\sqrt{(q+p)^2}$, assuming that the initial proton is at rest) greater 
-than 2 GeV to avoid the nucleon resonance region.  The $t$, transferred 
-momentum squared to the recoil proton, calculated from 4-momentum vectors of 
-incoming and outgoing photons, was required to be greater than a minimum 
-allowed value at given Q$^2$ and 
-W~($t>t_{min}(~=-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$,
+mass ($W=\sqrt{(q+p)^2}$, assuming that the initial proton is at rest) greater 
+than 2 GeV to avoid the nucleon resonance region. The squared transferred 
+momentum to the recoil proton $t$, calculated from the four-momentum vectors of 
+the incoming and outgoing photons, was required to be greater than a minimum 
+kinematically allowed value at given $Q^2$ and 
+$W$~($t>t_{min}(~=-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$, 
 where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
-proton mass). We specifically use the kinematics of the photons to determine 
+proton mass). We specifically used the kinematics of the photons to determine 
 $t$ because the initial proton kinematics is unknown due to Fermi motion. Then, 
-we ensured the exclusivity of the incoherent DVCS events by imposing 
-a series of constraints based on the four-momentum conservation 
-in the reaction $ep\rightarrow e'p'\gamma$. These kinematical 
-variables are: the coplanarity angle $\Delta\phi$ between the 
-($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) planes, the missing energy, mass, and 
-transverse momentum of the $e'\gamma$ and $e'p'\gamma$ systems, the missing 
-mass squared of the $e'p'$ system, and the angle $\theta$ between the measured 
-photon and the missing momentum of the $e'p'$ system. The experimental data for 
-the most relevant exclusivity variables are shown in FIG.~\ref{fig:kin-cuts}.  
-Because of the Fermi motion of the nucleons in the helium nucleus, these cuts
+we ensured the exclusivity of the incoherent DVCS events by imposing a series 
+of constraints based on the four-momentum conservation in the reaction 
+$ep\rightarrow e'p'\gamma$. These kinematical variables are: the coplanarity 
+angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) 
+planes, the missing energy, mass, and transverse momentum of the $e'\gamma$ and 
+$e'p'\gamma$ systems, the missing mass squared of the $e'p'$ system, and the 
+angle $\theta$ between the measured photon and the missing momentum of the 
+$e'p'$ system. The experimental data for the most relevant exclusivity 
+variables are shown in FIG.~\ref{fig:kin-cuts}. Because of the Fermi motion of 
+the nucleons in the helium nucleus, these cuts
 are slightly wider than those previously used for free proton experiments~%
 \cite{Girod:2007aa}. After the corrections discussed below, the asymmetries 
-appear to be stable as a function of cut width and we see no sizable effect 
-that can be related to the initial momentum of the nucleons. We also rejected 
+appear to be stable as a function of cut width and we saw no sizable effect 
+that could be related to the initial momentum of the nucleons. We also rejected 
 events where a $\pi^0$ was identified by the invariant mass of two photons. At 
@@
 \includegraphics[width=8.9cm]{figs/incoh_exc_cuts_final.pdf}
-\caption{The distributions 
-   from left to right and from top to bottoms are: $\Delta \phi$, missing 
-   energy, missing masses squared and the cone angle ($\theta$) between the 
-   measured and the calculated photons in the $e'p'$ final-state system.
-   The incoherent DVCS exclusivity cuts are represented by the vertical 
-   red-dashed lines. The black distributions 
-   represent the incoherent DVCS events candidate before the exclusivity 
-   cuts. The shaded distributions represent the incoherent DVCS events which 
-   passed all these cuts except the quantity plotted.}
+\caption{The distributions from left to right and from top to bottom are: 
+   $\Delta \phi$, missing energy, missing masses squared and the cone angle 
+   ($\theta$) between the measured and the calculated photons in the $e'p'$ 
+   final-state system. The incoherent DVCS exclusivity cuts are represented by 
+   the vertical red-dashed lines. The black distributions represent the 
+   incoherent DVCS event candidates before the exclusivity cuts. The shaded 
+   distributions represent the incoherent DVCS events that passed all of these 
+   cuts except the quantity plotted.}
 \label{fig:kin-cuts}
@@
 %background
-The two main backgrounds that contribute to the event sample after the 
+The two main backgrounds that contributed to the event sample after the 
 exclusivity cuts are due to accidental coincidences and exclusive $\pi^0$ 
-production where one of the photons from the $\pi^0$ decay escapes the 
-detection. The contribution from accidental events, i.e., $e'p'\gamma$ 
-collections with particles originating from different electron scatterings, was 
-evaluated to be of 6.5\% by selecting events passing all our selection cuts but 
-originating from different vertices. The $\pi^0$ contamination was estimated 
-using detector simulation and experimental data. From simulation, we calculated 
-the ratio ($R = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ 
-events that are wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ 
-events to the number of events correctly identified as exclusive $ep\rightarrow 
-e'p'\pi^0$.  Then in each kinematical bin and for each beam-helicity state, the 
-$\pi^0$-subtracted experimental DVCS events is calculated as $N = 
-N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow e'p'\pi^0}_{exp}$, where 
+production where one of the photons from the $\pi^0$ decay escapes detection.  
+The contribution from accidental events, i.e., $e'p'\gamma$ collections with 
+particles originating from different electron scatterings, was evaluated to be 
+6.5\% by selecting events passing all our selection cuts but originating from 
+different vertices. Our final asymmetries have been corrected for this 
+contamination in the form of
+$A_{LU~\text{corrected}}~=~\frac{1}{1~-~\text{contamination~percentage}}~A_{LU~\text{measured}}$. 
+The $\pi^0$ contamination was estimated using detector simulation and 
+experimental data. From simulation, we calculated the ratio ($R = 
+N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ events that were 
+wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the number 
+of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$.  Then in 
+each kinematical bin and for each beam-helicity state, the $\pi^0$-subtracted 
+experimental DVCS events were calculated as $N = N^{ep\rightarrow 
+e'p'\gamma}_{exp}- R~N^{ep\rightarrow e'p'\pi^0}_{exp}$, where 
 $N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is 
@@
 ($ep\rightarrow e'p'\pi^0$) events.  Depending on the kinematics, we found this 
-contamination to be of 8 to 10\%.
+contamination to be 8 to 10\%.
 
@@
 \begin{equation}
-A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} }.
+A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} },
 \end{equation}
-where $N^{+}$ and $N^{-}$ are the number of DVCS events for positive and negative 
-beam-helicity state, and $P_{B}$ is the longitudinal beam polarization.
+where $N^{+}$ and $N^{-}$ are the number of DVCS events for the positive and 
+negative beam-helicity states, and $P_{B}$ is the longitudinal beam 
+polarization.
 
@@
 equation~\ref{eq:alu-simp}. The measurement of the free proton $A_{LU}$ 
-\cite{Girod:2007aa} has confirmed that the $a_0$ term is dominating the shape 
-of the distribution.
+\cite{Girod:2007aa} has confirmed that the $a_0$ term dominates the shape of 
+the distribution.
 
@@
 FIG.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
-$\phi$ in bins of $Q^{2}$ (integrated over full $x_{B}$ and $t$ ranges), 
-$x_{B}$ (integrated over full $Q^{2}$ and $t$ ranges), and $t$ (integrated over 
-full $Q^{2}$ and $x_{B}$ ranges). The curves on the plots are fits of the form 
-$\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$.  The main contributions to 
-systematic uncertainties on these fits are from the choice of the DVCS 
-exclusivity cuts (6\%) and the large bin size (7\%). The systematic 
+$\phi$ in bins of $Q^{2}$ (integrated over the full $x_{B}$ and $t$ ranges), 
+$x_{B}$ (integrated over the full $Q^{2}$ and $t$ ranges), and $t$ (integrated 
+over the full $Q^{2}$ and $x_{B}$ ranges). The curves on the plots are fits of 
+the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.  The main 
+contributions to systematic uncertainties on these fits are from the choice of 
+the DVCS exclusivity cuts (6\%) and the large bin size (7\%). The systematic 
 uncertainties sum up to less than 10\% for all data points and thus always 
-remain significantly smaller than the statistical errors.
+remain significantly smaller than the statistical uncertainities.
 
@@
 \caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
-   for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle panel), and 
-   $-t$ bins (bottom panel). The error bars represent the statistical 
-   uncertainties. The gray bands represent the systematic uncertainties, 
-   including the normalization uncertainties. The black curves are the results 
-   of our fits with the form $\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$.}
+   for different $Q^{2}$ bins (top row), $x_{B}$ bins (middle row), and $-t$ 
+   bins (bottom row). The error bars represent the statistical uncertainties.  
+   The gray bands represent the systematic uncertainties, including the 
+   normalization uncertainties. The black curves are the results of our fits 
+   with the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.}
 \label{fig:alu}
@@
 FIG.~\ref{fig:alu}) on the kinematical variables $Q^2$, $x_{B}$, and $t$.  
-Within the given uncertainties, $A_{LU}$ does not indicate a strong dependence 
-on $Q^2$.  The $x_{B}$ and $t$ dependencies are compared to theoretical 
+Within the given uncertainties, $A_{LU}$ does not show a strong dependence on 
+$Q^2$.  The $x_{B}$ and $t$ dependencies are compared to the theoretical 
 calculations performed by S.~Liuti and K.~Taneja \cite{simonetta_2}. Their 
@@
 smaller asymmetries especially at small $x_{B}$ than the calculations. These 
-differences may arise from nuclear effects which are not taken into account in 
+differences may arise from nuclear effects that are not taken into account in 
 the model, such as long-range interactions and final state interactions of the 
-knock-out proton. On the graph for $-t$ dependence, we show previous 
-measurements by the HERMES collaboration \cite{Airapetian:2009cga}, in which 
-only electrons and photons were measured. Due to the large experimental 
+knocked-out proton. On the graph for the $-t$ dependence, we show previous 
+measurements by HERMES collaboration \cite{Airapetian:2009cga}, in which only 
+electrons and photons were measured. Due to the large experimental 
 uncertainties of the HERMES points, the two measurements are completely 
@@
    represent the statistical uncertainties, while the gray bands represent the 
-   systematic uncertainties. On the middle plot: the curves are theoretical 
-   calculations from \cite{simonetta_2}. On the bottom plot: the solid (empty) 
+   systematic uncertainties. On the middle plot the curves are theoretical 
+   calculations from \cite{simonetta_2}. On the bottom plot the solid (empty) 
    green circles are the HERMES $-A_{LU}$ (a positron beam was used) inclusive 
    measurements for the incoherent (coherent) enriched region 
-   \cite{Airapetian:2009cga}, the curves represent theoretical calculations 
+   \cite{Airapetian:2009cga}; the curves represent theoretical calculations 
    from \cite{simonetta_2}.  } \label{fig:alu90}
@@
 to see if significant nuclear effects are also visible within the GPD 
-framework.  To explore this idea, we construct the ratio of $A_{LU}$ for bound 
+framework. To explore this idea, we constructed the ratio of $A_{LU}$ for bound 
 protons to that on a free proton target.  
@@
 function of the kinematical variable $t$. The $A_{LU}$ ratios show 25\%-40\% 
-lower asymmetries and independent of $t$ for a bound proton compared to the 
-free proton. The measurements disagree with the off-shell \cite{simonetta_2} 
-and the on-shell calculations that use the medium modified GPDs as calculated 
-from the quark-meson coupling model \cite{Guzey:2008fe}. Our results show that 
-an important nuclear effect is missing from the existing models in order to 
-explain this strong quenching of the BSA. More theoretical developments will be 
-needed to identify the origin of this quenching, in particular it will be key 
-to differentiate initial from final state effects and how they can affect the 
-DVCS asymmetries.
+lower asymmetries that are independent of $t$ for a bound proton compared to 
+the free proton. The measurements disagree with the off-shell 
+\cite{simonetta_2} and the on-shell calculations that use the medium-modified 
+GPDs as calculated from the quark-meson coupling model \cite{Guzey:2008fe}. Our 
+results show that an important nuclear effect is missing from the existing 
+models in order to explain this strong quenching of the BSA. More theoretical 
+developments will be needed to identify the origin of this quenching, in 
+particular it will be important to differentiate initial from final state 
+effects and how they can affect the DVCS asymmetries.
 
@@
 proton DVCS off $^4$He using an upgraded setup of the CLAS spectrometer at 
-Jefferson Lab. Our results were compared to model calculations based on 
+Jefferson Lab. Our results are compared to model calculations based on 
 different assumptions of the nuclear medium effects at the partonic level. The 
 bound-proton BSA is largely suppressed compared to the free proton BSA. This 
-result is a first step in using an exciting novel experimental method of 
-understanding the properties of bound nucleons directly from the basic degrees 
-of freedom of QCD, quarks and gluons.
+result is a first step in using a novel experimental method of understanding 
+the properties of bound nucleons directly from the basic degrees of freedom of 
+QCD, quarks and gluons.
 
@@
 %``Nucleon Electromagnetic Form Factors,''
-Prog.\ Part.\ Nucl.\ Phys.\  {\bf 59}, 694 (2007)
+Prog.\ Part.\ Nucl.\ Phys.\  {\bf 59}, 694 (2007).
 
-\bibitem{pdg} J.~Beringer {\it et al.} (Particle Data Group), Phys.\ Rev.\ D 
-   {\bf 86}, 010001 (2012).
+\bibitem{pdg} M.~Tanabashi {\it et al.} (Particle Data Group), Phys.\ Rev.\ D 
+   {\bf 98}, 030001 (2018).
 
@@
    %virtual Compton scattering,''
- Phys.\ Rev.\ Lett.\  {\bf 87}, 182001 (2001)
+ Phys.\ Rev.\ Lett.\  {\bf 87}, 182001 (2001).
 %doi:10.1103/PhysRevLett.87.182001
@@
    %scattering,''
-Phys.\ Rev.\ D {\bf 75}, 011103 (2007)
+Phys.\ Rev.\ D {\bf 75}, 011103 (2007).
 %doi:10.1103/PhysRevD.75.011103
@@
 
-\bibitem{Munoz Camacho:2006hx} 
-C. Mu\~noz Camacho {\it et al.} [Jefferson Lab Hall A Collaboration],
-Phys.\ Rev.\ Lett. {\bf 97}, 262002 (2006).
+\bibitem{Defurne:2015kxq}
+M.~Defurne {\it et al.} [Jefferson Lab Hall A Collaboration],
+  Phys.\ Rev.\ C {\bf 92}, no. 5, 055202 (2015).
 
@@
 \bibitem{Jo:2015ema} H.~S.~Jo {\it et al.} [CLAS Collaboration],
-  Phys.\ Rev.\ Lett.\  {\bf 115}, no. 21, 212003 (2015)
+  Phys.\ Rev.\ Lett.\  {\bf 115}, no. 21, 212003 (2015).
 
@@
  %``Tomographic image of the proton,''
- Phys.\ Rev.\ D {\bf 95}, no. 1, 011501 (2017)
+ Phys.\ Rev.\ D {\bf 95}, no. 1, 011501 (2017).
 
@@
    %asymmetries in deeply virtual Compton scattering,''
-Phys.\ Rev.\ C {\bf 81}, 035202 (2010)
+Phys.\ Rev.\ C {\bf 81}, 035202 (2010).
 %doi:10.1103/PhysRevC.81.035202
@@
    M.~Hattawy {\it et al.} [CLAS Collaboration],
-   Phys.\ Rev.\ Lett.\  {\bf 119}, no. 20, 202004 (2017)
+   Phys.\ Rev.\ Lett.\  {\bf 119}, no. 20, 202004 (2017).
 
 \bibitem{simonetta_2}
-S.~Liuti and K.~Taneja, Phys.\ Rev.\ C {\bf 72}, 032201 (2005)
+S.~Liuti and K.~Taneja, Phys.\ Rev.\ C {\bf 72}, 032201 (2005).
 
@@
 \bibitem{Guzey:2008fe} V.~Guzey, A.~W.~Thomas and K.~Tsushima,
-  Phys.\ Lett.\ B {\bf 673}, 9 (2009)
+  Phys.\ Lett.\ B {\bf 673}, 9 (2009).
 
@@
 \bibitem{Belitsky:2001ns}
-A.~V.~Belitsky, D.~Mueller and A.~Kirchner,
-Nucl.\ Phys.\ B {\bf 629}, 323 (2002)
+A.~V.~Belitsky, D.~Mueller and A.~Kirchner, Nucl.\ Phys.\ B {\bf 629}, 323 
+(2002). Updated in: A.~V.~Belitsky and D.~Mueller, Phys.\ Rev.\ D {\bf 82}, 
+074010 (2010).
 
 \bibitem{Hafidi:2008pr} K.~Hafidi {\it et al.},
-   proposal PR-08-024 to JLab PAC33 (unpublished).
+   proposal PR-08-024 to JLab PAC33 
+   (\url{https://www.jlab.org/exp_prog/proposals/08/PR-08-024.pdf}).
 
-\bibitem{Mecking:2003zu} B.~A.~Mecking {\it et al.} [CLAS Collaboration],
+\bibitem{Mecking:2003zu} B.~A.~Mecking {\it et al.},
    Nucl.\ Instrum.\ Meth.\ A {\bf 503}, 513 (2003).
@@
 
-\bibitem{Dupre:2017upj} 
-  R.~Dupr\'e {\it et al.},
-  Nucl.\ Instrum.\ Meth.\ A {\bf 898}, 90 (2018)
-
-%\cite{Armstrong:2017wfw}
-\bibitem{Armstrong:2017wfw} W.~Armstrong {\it et al.},
-     %``Partonic Structure of Light Nuclei,''
-     arXiv:1708.00888 [nucl-ex].
-       %%CITATION = ARXIV:1708.00888;%%
-         %2 citations counted in INSPIRE as of 13 Feb 2018
-     %\cite{Armstrong:2017zqr}
-%\bibitem{Armstrong:2017zqr} W.~Armstrong {\it et al.},
-       %``Tagged EMC Measurements on Light Nuclei,''
-       arXiv:1708.00891 [nucl-ex].
-         %%CITATION = ARXIV:1708.00891;%%
-           %1 citations counted in INSPIRE as of 13 Feb 2018
-       %\cite{Armstrong:2017zcm}
-%    \bibitem{Armstrong:2017zcm} W.~R.~Armstrong {\it et al.},
-         %``Spectator-Tagged Deeply Virtual Compton Scattering on Light 
-       %Nuclei,''
-         arXiv:1708.00835 [nucl-ex].
-           %%CITATION = ARXIV:1708.00835;%%
-
 \end{thebibliography}

### 2018-11-27 eg6-letters/incoherent/figs/incoh_exc_cuts_final.C
added the source file for fig.2

@@ -1,0 +1,3639 @@
+void incoh_exc_cuts_final()
+{
+//=========Macro generated from canvas: aall_cuts/
+//=========  (Wed Oct  3 12:12:48 2018) by ROOT version6.09/01
+   TCanvas *aall_cuts = new TCanvas("aall_cuts", "",0,0,900,1200);
+   gStyle->SetOptFit(1);
+   aall_cuts->Range(0,0,1,1);
+   aall_cuts->SetFillColor(0);
+   aall_cuts->SetBorderMode(0);
+   aall_cuts->SetBorderSize(2);
+   aall_cuts->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: aall_cuts_1
+   TPad *aall_cuts_1 = new TPad("aall_cuts_1", "aall_cuts_1",0.01,0.6766667,0.49,0.99);
+   aall_cuts_1->Draw();
+   aall_cuts_1->cd();
+   aall_cuts_1->Range(-10,-116.7375,10,1050.638);
+   aall_cuts_1->SetFillColor(0);
+   aall_cuts_1->SetBorderMode(0);
+   aall_cuts_1->SetBorderSize(2);
+   aall_cuts_1->SetFrameBorderMode(0);
+   aall_cuts_1->SetFrameBorderMode(0);
+   
+   TH1D *h2_delta_phi_InCoh__3 = new TH1D("h2_delta_phi_InCoh__3"," ",300,-8,8);
+   h2_delta_phi_InCoh__3->SetBinContent(3,3);
+   h2_delta_phi_InCoh__3->SetBinContent(4,1);
+   h2_delta_phi_InCoh__3->SetBinContent(5,1);
+   h2_delta_phi_InCoh__3->SetBinContent(6,1);
+   h2_delta_phi_InCoh__3->SetBinContent(7,1);
+   h2_delta_phi_InCoh__3->SetBinContent(8,1);
+   h2_delta_phi_InCoh__3->SetBinContent(9,2);
+   h2_delta_phi_InCoh__3->SetBinContent(10,2);
+   h2_delta_phi_InCoh__3->SetBinContent(12,2);
+   h2_delta_phi_InCoh__3->SetBinContent(13,3);
+   h2_delta_phi_InCoh__3->SetBinContent(14,3);
+   h2_delta_phi_InCoh__3->SetBinContent(15,1);
+   h2_delta_phi_InCoh__3->SetBinContent(16,2);
+   h2_delta_phi_InCoh__3->SetBinContent(17,3);
[…]

### 2018-11-27 eg6-letters/incoherent/incoherent_prl.tex

@@
 %asymmetries
+\begin{figure*}[t!]
+\includegraphics[width=13.9cm]{figs/incoherent_ALU_phi.pdf}
+\caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
+   for different $Q^{2}$ bins (top row), $x_{B}$ bins (middle row), and $-t$ 
+   bins (bottom row). The error bars represent the statistical uncertainties.  
+   The gray bands represent the systematic uncertainties, including the 
+   normalization uncertainties. The black curves are the results of our fits 
+   with the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.}
+\label{fig:alu}
+\end{figure*}
+
 Experimentally, $A_{LU}$ is defined as
@@
 
-\begin{figure}[tb]
-\includegraphics[width=8.9cm]{figs/incoherent_ALU_phi.pdf}
-\caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
-   for different $Q^{2}$ bins (top row), $x_{B}$ bins (middle row), and $-t$ 
-   bins (bottom row). The error bars represent the statistical uncertainties.  
-   The gray bands represent the systematic uncertainties, including the 
-   normalization uncertainties. The black curves are the results of our fits 
-   with the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.}
-\label{fig:alu}
-\end{figure}
-
 FIG.~\ref{fig:alu90} presents the dependence of the fitted $A_{LU}$ values at 
@@
 \begin{figure}[tb]
-\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_Q2_shortscenrario.pdf}
-\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_x_shortscenrario.pdf}
-\includegraphics[width=6.9cm]{figs/ALU_90_p_vs_t_shortscenrario.pdf}
+\includegraphics[width=7.8cm]{figs/ALU_90_p_vs_Q2_shortscenrario.pdf}
+\includegraphics[width=7.8cm]{figs/ALU_90_p_vs_x_shortscenrario.pdf}
+\includegraphics[width=7.8cm]{figs/ALU_90_p_vs_t_shortscenrario.pdf}
 \caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $t$ dependencies (bottom) of

### 2018-11-27 eg6-letters/incoherent/incoherent_prl.tex
more implementation of clas comments

@@
 available, the coherent channel where the scattering is off the entire nucleus, 
-which is left intact in the final state \cite{Airapetian:2009cga,
-Hattawy:2017woc}, and the incoherent channel where the DVCS occurs on a 
-nucleon, which is ejected from the nucleus. The latter is the focus of this 
-letter and provides a unique access to the modification of the partonic 
-structure of the bound nucleons \cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}.  
-The $^{4}$He nucleus is an ideal experimental target for this measurement as it 
-is characterized by a strong binding energy, a relatively high nuclear core 
-density, and a large EMC effect~\cite{JSeely}. Moreover, it remains simple 
-enough that precise calculation of its structure can be performed, making this 
-nucleus the perfect target for our investigation of the medium modifications of 
-the nucleon's partonic structure.
+which is left intact in the final state \cite{Hattawy:2017woc}, and the 
+incoherent channel where the DVCS occurs on a nucleon, which is ejected from 
+the nucleus. The latter is the focus of this letter and provides a unique 
+access to the modification of the partonic structure of the bound nucleons 
+\cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}.  The $^{4}$He nucleus is an ideal 
+experimental target for this measurement as it is characterized by a strong 
+binding energy, a relatively high nuclear core density, and a large EMC 
+effect~\cite{JSeely}. Moreover, it remains simple enough that precise 
+calculation of its structure can be performed, making this nucleus the perfect 
+target for our investigation of the medium modifications of the nucleon's 
+partonic structure. The previous measurements of DVCS off nuclei, and in 
+particular off $^4$He, performed at HERMES \cite{Airapetian:2009cga} yielded 
+results with both "coherent enriched" and "incoherent enriched" event samples, 
+hence not fully exclusive, but significant enough to be compared with our 
+results below.
 
@@
 %background
+\begin{figure*}[t!]
+\includegraphics[width=13.9cm]{figs/incoherent_ALU_phi.pdf}
+\caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
+   for different $Q^{2}$ bins (top row), $x_{B}$ bins (middle row), and $-t$ 
+   bins (bottom row). The error bars represent the statistical uncertainties.  
+   The gray bands represent the systematic uncertainties, including the 
+   normalization uncertainties. The black curves are the results of our fits 
+   with the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.}
+\label{fig:alu}
+\end{figure*}
+
 The two main backgrounds that contributed to the event sample after the 
@@
 %asymmetries
-\begin{figure*}[t!]
-\includegraphics[width=13.9cm]{figs/incoherent_ALU_phi.pdf}
-\caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
-   for different $Q^{2}$ bins (top row), $x_{B}$ bins (middle row), and $-t$ 
-   bins (bottom row). The error bars represent the statistical uncertainties.  
-   The gray bands represent the systematic uncertainties, including the 
-   normalization uncertainties. The black curves are the results of our fits 
-   with the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.}
-\label{fig:alu}
-\end{figure*}
 
@@
 %\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}
-\includegraphics[width=8.5cm]{figs/ALU_ratioInc_t_shortscenrario-without-error-onX.pdf}
+\includegraphics[width=7.8cm]{figs/ALU_ratioInc_t_shortscenrario-without-error-onX.pdf}
 \caption{ The $A_{LU}$ ratio of the bound to the free proton at 
@@
 
-%\cite{Airapetian:2009cga}
-\bibitem{Airapetian:2009cga} A.~Airapetian {\it et al.} [HERMES Collaboration],
-     %``Nuclear-mass dependence of azimuthal beam-helicity and beam-charge 
-   %asymmetries in deeply virtual Compton scattering,''
-Phys.\ Rev.\ C {\bf 81}, 035202 (2010).
-%doi:10.1103/PhysRevC.81.035202
-%[arXiv:0911.0091 [hep-ex]].
-
-\bibitem{Hattawy:2017woc} 
-   M.~Hattawy {\it et al.} [CLAS Collaboration],
+\bibitem{Hattawy:2017woc} M.~Hattawy {\it et al.} [CLAS Collaboration],
    Phys.\ Rev.\ Lett.\  {\bf 119}, no. 20, 202004 (2017).
@@
 J. Seely {\it et al.}, Phys.\ Rev.\ Lett.\ {\bf 103}, 202301 (2009).
+
+%\cite{Airapetian:2009cga}
+\bibitem{Airapetian:2009cga} A.~Airapetian {\it et al.} [HERMES Collaboration],
+     %``Nuclear-mass dependence of azimuthal beam-helicity and beam-charge 
+   %asymmetries in deeply virtual Compton scattering,''
+Phys.\ Rev.\ C {\bf 81}, 035202 (2010).
+%doi:10.1103/PhysRevC.81.035202
+%[arXiv:0911.0091 [hep-ex]].
 

### 2018-11-27 eg6-letters/incoherent/incoherent_prl.tex
latest correction after the clas comments

@@
 proton mass). We specifically used the kinematics of the photons to determine 
-$t$ because the initial proton kinematics is unknown due to Fermi motion. Then, 
-we ensured the exclusivity of the incoherent DVCS events by imposing a series 
-of constraints based on the four-momentum conservation in the reaction 
+$t$ because the initial proton kinematics is unknown due to Fermi motion. We 
+ensured the exclusivity of the incoherent DVCS events by imposing a series of 
+constraints based on the four-momentum conservation in the reaction 
 $ep\rightarrow e'p'\gamma$. These kinematical variables are: the coplanarity 
@@
 contamination in the form of
-$A_{LU~\text{corrected}}~=~\frac{1}{1~-~\text{contamination~percentage}}~A_{LU~\text{measured}}$. 
+$A_{LU~\text{corrected}}~=~\frac{A_{LU~\text{measured}}}{1~-~\text{contamination~percentage}}$.  
 The $\pi^0$ contamination was estimated using detector simulation and 
@@
 particular it will be important to differentiate initial from final state 
-effects and how they can affect the DVCS asymmetries.
+effects and how they affect the DVCS asymmetries.
 

### 2018-11-27 eg6-letters/incoherent/figs/Q2_xB_t_InCoh.C

@@ -2446,6 +2446,7 @@ palette->SetTitleSize(0.075);
    h_Q2_xB_InCoh->GetXaxis()->SetTitle("x_{B}");
    h_Q2_xB_InCoh->GetXaxis()->CenterTitle(true);
    h_Q2_xB_InCoh->GetXaxis()->SetNdivisions(205);
+   h_Q2_xB_InCoh->GetYaxis()->SetNdivisions(205);
    h_Q2_xB_InCoh->GetXaxis()->SetLabelFont(22);
    h_Q2_xB_InCoh->GetXaxis()->SetLabelSize(0.085);
    h_Q2_xB_InCoh->GetXaxis()->SetTitleSize(0.085);
@@ -7910,6 +7911,8 @@ palette->SetTitleSize(0.075);
    h_t_Q2_InCoh->SetLineColor(ci);
    h_t_Q2_InCoh->GetXaxis()->SetTitle("-t [GeV^{2}/c^{2}]");
    h_t_Q2_InCoh->GetXaxis()->CenterTitle(true);
+   h_t_Q2_InCoh->GetXaxis()->SetNdivisions(205);
+   h_t_Q2_InCoh->GetYaxis()->SetNdivisions(205);
    h_t_Q2_InCoh->GetXaxis()->SetLabelFont(22);
    h_t_Q2_InCoh->GetXaxis()->SetLabelSize(0.085);
    h_t_Q2_InCoh->GetXaxis()->SetTitleSize(0.085);

### 2018-11-29 eg6-letters/incoherent/collaboration_comments/clas_comments.tex
more implementation of clas comments
latest correction after the clas comments
minor edit
update the paper after Raphael's suggestions

@@
  - Line 65. Use "Fig. 1".
-   \textcolor{blue}{Kept as FIG.1. We show it in the text as shown in the 
-      caption.}
+   \textcolor{blue}{Done}
 
@@
       ...".
-   \textcolor{red}{We do not agree here.}
+   \textcolor{blue}{Done}
 
@@
 - Line 173. Use "Fig. 2".
-     \textcolor{blue}{We keep it as in the caption.}
+     \textcolor{blue}{Done}
 
@@
 - Line 183. Use "Fig. 3".
-     \textcolor{blue}{We keep it as in the caption.}
+     \textcolor{blue}{Done}
 
@@
 - Line 220. Use "Fig. 4".
-      \textcolor{blue}{We prefer to keep it as in the caption.}
+      \textcolor{blue}{Done}
 
@@
 - Line 231. Use "Fig. 5".
-      \textcolor{blue}{We prefer to keep it as in the caption.}
+      \textcolor{blue}{Done}
 
 - Line 233. Use "Fig. 4".
-      \textcolor{blue}{We prefer to keep it as in the caption.}
+      \textcolor{blue}{Done}
 
@@
    appropriate for the general PRL audience.  Please reconsider.
-      \textcolor{red}{We kept it as it is.}
+      \textcolor{blue}{Done}
 
@@
   kinematic labels)
-      \textcolor{red}{Will be revised.}
+      \textcolor{blue}{Done.}
 
@@
 - Line 255. Use "Fig. 6".
-      \textcolor{blue}{We prefer to keep it as in the caption.}
+      \textcolor{blue}{Done}
 
@@
    - Line 8. It is not clear what you mean by "enriched region".  
-     \textcolor{blue}{They were not detecting the final state hadron and the 
-     were separating the coherent from the incoherent DVCS events based on the 
-     assumption that the coherent dominates the low $t$ region and the 
-     incoherent dominate the high $t$ region, and they avoided calling it pure 
-     coherent or incoherent by labeling them as coherent or incoherent enriched 
-     regions. }\\
+     \textcolor{blue}{This is jargon introduced in their paper. They were not 
+     detecting the final state hadron and were separating the coherent from the 
+     incoherent DVCS events based on the assumption that the coherent dominates 
+     the low $t$ region and the incoherent dominate the high $t$ region, and 
+     they avoided calling it pure coherent or incoherent by labeling them as 
+     coherent or incoherent enriched regions. }\\
    - Line 8. Use "... [30]; the curves represent ...".
@@
       results below".
-\textcolor{blue}{}
+\textcolor{blue}{We took your suggestion. Modified.}
 
@@
 \textcolor{blue}{We have corrected our asymmetries for these accidentals.
-      }\\
-       \textcolor{blue}{This sentence has been added to the paper: Our final 
-       asymmetries have been corrected for this contamination in the form
-      $A_{LU~corrected}~=~\frac{1}{1-contamination~percentage}~A_{LU~measured}$ 
-      }
+      equation 6 has been updated to state that.}\\
 
    \item Figs 2, 3 and 4: tick labels too small.
-\textcolor{red}{will be revised.}
+\textcolor{blue}{Done.}
 
@@
    particularly with the braces. It may look better as a displaymath equation.
-\textcolor{blue}{Tested. It is not looking much better.}
+\textcolor{blue}{Updated.}
 
-\item Page 4, figure 4: the font size is way too small!  \textcolor{red}{Will 
-   be revised.}
+\item Page 4, figure 4: the font size is way too small!  \textcolor{blue}{Done
+   .}
 

### 2018-11-29 eg6-letters/incoherent/incoherent_prl.tex
update the paper after Raphael's suggestions

@@
 In this Letter, we present the first exclusive measurement of the beam-spin 
-asymmetry (BSA) in deeply virtual electroproduction of a real photon off a bound 
-proton in $^{4}$He. FIG.~\ref{fig:diags} illustrates the leading-twist handbag 
-diagram for the DVCS process. In the Bjorken regime, i.e. large virtual photon 
-four-momentum squared ($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small invariant 
-momentum transfer ($t=(q-q^\prime)^2$), the DVCS scattering process can be 
-factorized, leaving the non-perturbative structure of the nucleon to be 
+asymmetry (BSA) in deeply virtual electroproduction of a real photon off a 
+bound proton in $^{4}$He. Fig.~\ref{fig:diags} illustrates the leading-twist 
+handbag diagram for the DVCS process. In the Bjorken regime, i.e. large virtual 
+photon four-momentum squared ($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small 
+invariant momentum transfer ($t=(q-q^\prime)^2$), the DVCS scattering process 
+can be factorized, leaving the non-perturbative structure of the nucleon to be 
 parameterized in terms of four chirally even GPDs: $H$, $E$, $\widetilde{H}$, 
@@
   \end{equation}
-where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the photon electroproduction 
+where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the virtual photoproduction 
 differential cross section for a positive (negative) beam helicity.
@@
 the incoming and outgoing photons, was required to be greater than a minimum 
-kinematically allowed value at given $Q^2$ and 
-$W$~($t>t_{min}(~=-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}}$, 
+kinematically allowed value ($t_{min}$) at given $Q^2$ and $W$ defined as: 
+\begin{equation}
+t_{min} 
+   =-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}},
+\end{equation}
 where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
@@
 $e'p'$ system. The experimental data for the most relevant exclusivity 
-variables are shown in FIG.~\ref{fig:kin-cuts}. Because of the Fermi motion of 
+variables are shown in Fig.~\ref{fig:kin-cuts}. Because of the Fermi motion of 
 the nucleons in the helium nucleus, these cuts
@@
 requirements; their kinematic distributions are shown in 
-FIG.~\ref{fig:kin-coverage}.
+Fig.~\ref{fig:kin-coverage}.
 
@@
 6.5\% by selecting events passing all our selection cuts but originating from 
-different vertices. Our final asymmetries have been corrected for this 
-contamination in the form of
-$A_{LU~\text{corrected}}~=~\frac{A_{LU~\text{measured}}}{1~-~\text{contamination~percentage}}$.  
-The $\pi^0$ contamination was estimated using detector simulation and 
-experimental data.  From simulation, we calculated the ratio ($R = 
-N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ events that were 
-wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the number 
-of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$. Then in 
-each kinematical bin and for each beam-helicity state, the $\pi^0$-subtracted 
-experimental DVCS events were calculated as $N = N^{ep\rightarrow 
-e'p'\gamma}_{exp}- R~N^{ep\rightarrow e'p'\pi^0}_{exp}$, where 
+different vertices. The $\pi^0$ contamination was estimated using detector 
+simulation and experimental data. From simulation, we calculated the ratio ($R 
+= N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ events that 
+were wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the 
+number of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$.  
+Then in each kinematical bin and for each beam-helicity state, the 
+$\pi^0$-subtracted experimental DVCS events were calculated as $N = 
+N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow e'p'\pi^0}_{exp}$, where 
 $N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is 
@@
 \begin{equation}
-A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} },
+   A_{LU} = \frac{1}{P_{B}(1-C)} \frac{N^{+} - N^{-}}{N^{+} + N^{-} },
 \end{equation}
 where $N^{+}$ and $N^{-}$ are the number of DVCS events for the positive and 
-negative beam-helicity states, and $P_{B}$ is the longitudinal beam 
-polarization.
+negative beam-helicity states, $P_{B}$ is the longitudinal beam polarization, 
+and C stands for the contamination percentage of the accidental coincidences.
 
@@
 $x_{B}$, or $t$) and then nine bins in the azimuthal angle ($\phi$).   
-FIG.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
+Fig.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
 $\phi$ in bins of $Q^{2}$ (integrated over the full $x_{B}$ and $t$ ranges), 
@@
 
-FIG.~\ref{fig:alu90} presents the dependence of the fitted $A_{LU}$ values at 
+Fig.~\ref{fig:alu90} presents the dependence of the fitted $A_{LU}$ values at 
 $\phi$~=~90$^{\circ}$ ($a_{0}$ parameter from the individual fits in 
-FIG.~\ref{fig:alu}) on the kinematical variables $Q^2$, $x_{B}$, and $t$.  
+Fig.~\ref{fig:alu}) on the kinematical variables $Q^2$, $x_{B}$, and $t$.  
 Within the given uncertainties, $A_{LU}$ does not show a strong dependence on 
@@
 calculations performed by S.~Liuti and K.~Taneja \cite{simonetta_2}. Their 
-model uses a nuclear spectral function and considers mainly off-shell effects.  
-The calculations are carried out at slightly different kinematics than our data 
-but still provide important guidance. The experimental results appear to have 
-smaller asymmetries especially at small $x_{B}$ than the calculations. These 
-differences may arise from nuclear effects that are not taken into account in 
-the model, such as long-range interactions and final state interactions of the 
-knocked-out proton. On the graph for the $-t$ dependence, we show previous 
-measurements by HERMES collaboration \cite{Airapetian:2009cga}, in which only 
-electrons and photons were measured. Due to the large experimental 
-uncertainties of the HERMES points, the two measurements are completely 
-compatible.
+model uses a nuclear spectral function and considers mainly the effect of the 
+nucleon off-shellness. The calculations are carried out at slightly different 
+kinematics than our data but still provide important guidance. The experimental 
+results appear to have smaller asymmetries especially at small $x_{B}$ than the 
+calculations.  These differences may arise from nuclear effects that are not 
+taken into account in the model, such as long-range interactions and final 
+state interactions of the knocked-out proton. On the graph for the $-t$ 
+dependence, we show previous measurements by HERMES collaboration 
+\cite{Airapetian:2009cga}, in which only electrons and photons were measured.  
+Due to the large experimental uncertainties of the HERMES points, the two 
+measurements are completely compatible.
 
@@
 protons to that on a free proton target.  
-FIG.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the BSA ratio based on 
+Fig.~\ref{fig:incoh_EMC_ratio_ALU_proton} presents the BSA ratio based on 
 interpolation of the free proton asymmetries from CLAS \cite{Girod:2007aa} as a 

### 2018-12-13 eg6-letters/incoherent/incoherent_prl.tex
update the author list

@@
 proportional to the following combination of Compton form factors (CFF) 
+$\mathcal{H}$, $\mathcal{E}$, and $\tilde{\mathcal{H}}$ as  
 \cite{Guidal:2013rya}

### 2018-12-21 eg6-letters/incoherent/publication_version/edit_author_list.tex
add version of the paper that fits the publication procedures

M. Hattawy, N.A. Baltzell, R. Dupr\'{e}, S. B\"{u}ltmann, R. De Vita, A. El Alaoui, L. El Fassi, H. Egiyan, F.X. Girod, M. Guidal, K. Hafidi, D. Jenkins, S. Liuti, Y. Perrin, S. Stepanyan, B. Torayev, E. Voutier, S. Adhikari, Giovanni Angelini, C. Ayerbe Gayoso, L. Barion, M. Battaglieri, I. Bedlinskiy, A.S. Biselli, F. Boss\`u, W. Brooks, F. Cao, D.S. Carman, A. Celentano, P. Chatagnon, T. Chetry, G. Ciullo, L. Clark, P.L. Cole, M. Contalbrigo, V. Crede, A. D'Angelo, N. Dashyan, E. De Sanctis, M. Defurne, A. Deur, S. Diehl, C. Djalali, M. Ehrhart, P. Eugenio, S. Fegan, A. Filippi, T.A.Forest, A. Fradi, M. Gar\c{c}on, G. Gavalian, N. Gevorgyan, G.P. Gilfoyle, K.L. Giovanetti, E. Golovatch, R.W. Gothe, K.A. Griffioen, N. Harrison, F. Hauenstein, T.B. Hayward, D. Heddle, K. Hicks, M. Holtrop, Y. Ilieva, D.G. Ireland, E.L. Isupov, S. Johnston, D. Keller, G. Khachatryan, M. Khachatryan, A. Khanal, M. Khandaker, C.W. Kim, W. Kim, F.J. Klein, V. Kubarovsky, S.E. Kuhn, L. Lanza, M.L. Kabir, P. Lenisa, K. Livingston, I.J.D. MacGregor, D. Marchand, N. Markov, M. Mayer, B. McKinnon, Z.E. Meziani, T. Mineeva, M. Mirazita, R.A. Montgomery, C. Munoz Camacho, P. Nadel-Turonski, S. Niccolai, A.I. Ostrovidov, L.L. Pappalardo, R. Paremuzyan, E. Pasyuk, O. Pogorelko, J. Poudel, Y. Prok, D. Protopopescu, M. Ripani, D. Riser, A. Rizzo, G. Rosner, P. Rossi, F. Sabati\'e, C. Salgado, R.A. Schumacher, Y.G. Sharabian, Iu. Skorodumina, D. Sokhan, O. Soto, N. Sparveris, S. Strauch, M. Taiuti, J.A. Tan, N. Tyler, M. Ungaro, H. Voskanyan, R. Wang, D.P. Watts, X. Wei, L.B. Weinstein, M.H. Wood, N. Zachariou, J. Zhang, Z.W. Zhao (The CLAS Collaboration)

### 2018-12-21 eg6-letters/incoherent/publication_version/incoherent_prl.tex
add version of the paper that fits the publication procedures

--- 2018-12-13 eg6-letters/incoherent/incoherent_prl.tex
@@
 \RequirePackage{lineno}
-\documentclass[twocolumn,nofootinbib,showpacs,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
+\documentclass[twocolumn,nofootinbib,prl,superscriptaddress,secnumarabic,amssymb,nobibnotes,aps,floatfix]{revtex4}
 \usepackage{graphicx}
@@
 \begin{document}
-\linenumbers
+%\linenumbers
 
@@
 \end{abstract}
-\pacs{Valid PACS appear here}
+%\pacs{Valid PACS appear here}
 
@@
 \begin{figure}[tb]
-\includegraphics[width=7.5cm]{figs/handbag_incoherent.pdf}
+\includegraphics[width=7.5cm]{handbag_incoherent.pdf}
 \caption{Representation of the leading-order, twist-2, handbag diagram of the 
@@
 the end of this selection process, about 30k events passed all the 
-requirements; their kinematic distributions are shown in 
-Fig.~\ref{fig:kin-coverage}.
+requirements.
 
 \begin{figure}[tb]
-\includegraphics[width=8.9cm]{figs/incoh_exc_cuts_final.pdf}
+\includegraphics[width=8.9cm]{incoh_exc_cuts_final.pdf}
 \caption{The distributions from left to right and from top to bottom are: 
@@
 \label{fig:kin-cuts}
-
-\end{figure}
-\begin{figure}[h!]
-\hspace{-0.45cm}
-\includegraphics[width=9.0cm]{figs/Q2_xB_t_InCoh.pdf}
-\caption{Incoherent DVCS event distributions for $Q^{2}$ as a function of 
-$x_{B}$ (left) and $Q^{2}$ as a function of $-t$ (right) after the exclusivity 
-cuts.}
-\label{fig:kin-coverage}
 \end{figure}
@@
 \begin{figure*}[t!]
-\includegraphics[width=13.9cm]{figs/incoherent_ALU_phi.pdf}
+\includegraphics[width=13.9cm]{incoherent_ALU_phi.pdf}
 \caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
@@
 \begin{figure}[tb]
-\includegraphics[width=7.8cm]{figs/ALU_90_p_vs_Q2_shortscenrario.pdf}
-\includegraphics[width=7.8cm]{figs/ALU_90_p_vs_x_shortscenrario.pdf}
-\includegraphics[width=7.8cm]{figs/ALU_90_p_vs_t_shortscenrario.pdf}
+\includegraphics[width=7.8cm]{ALU_90_p_vs_Q2_shortscenrario.pdf}
+\includegraphics[width=7.8cm]{ALU_90_p_vs_x_shortscenrario.pdf}
+\includegraphics[width=7.8cm]{ALU_90_p_vs_t_shortscenrario.pdf}
 \caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $t$ dependencies (bottom) of
@@
 \centering
-%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_Q2_shortscenrario.pdf}\\
-%\includegraphics[width=6.9cm]{figs/ALU_ratioInc_x_shortscenrario.pdf}
-\includegraphics[width=7.8cm]{figs/ALU_ratioInc_t_shortscenrario-without-error-onX.pdf}
+\includegraphics[width=7.8cm]{ALU_ratioInc_t_shortscenrario-without-error-onX.pdf}
 \caption{ The $A_{LU}$ ratio of the bound to the free proton at 

### 2018-12-21 eg6-letters/incoherent/publication_version/incoherent_prl.tex
update the paper after editing the figures

@@
 variables are shown in Fig.~\ref{fig:kin-cuts}. Because of the Fermi motion of 
-the nucleons in the helium nucleus, these cuts
-are slightly wider than those previously used for free proton experiments~%
-\cite{Girod:2007aa}. After the corrections discussed below, the asymmetries 
-appear to be stable as a function of cut width and we saw no sizable effect 
-that could be related to the initial momentum of the nucleons. We also rejected 
-events where a $\pi^0$ was identified by the invariant mass of two photons. At 
-the end of this selection process, about 30k events passed all the 
-requirements.
+the nucleons in the helium nucleus, these cuts are slightly wider than those 
+previously used for free proton experiments~\cite{Girod:2007aa}. After the 
+corrections discussed below, the asymmetries appear to be stable as a function 
+of cut width and we saw no sizable effect that could be related to the initial 
+momentum of the nucleons. We also rejected events where a $\pi^0$ was 
+identified by the invariant mass of two photons. At the end of this selection 
+process, about 30k events passed all the requirements.
 
@@
 \caption{The distributions from left to right and from top to bottom are: 
-   $\Delta \phi$, missing energy, missing masses squared and the cone angle 
+   $\Delta \phi$, missing energy, missing mass squared and the cone angle 
    ($\theta$) between the measured and the calculated photons in the $e'p'$ 
@@
 \begin{figure*}[t!]
-\includegraphics[width=13.9cm]{incoherent_ALU_phi.pdf}
-\caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
-   for different $Q^{2}$ bins (top row), $x_{B}$ bins (middle row), and $-t$ 
-   bins (bottom row). The error bars represent the statistical uncertainties.  
-   The gray bands represent the systematic uncertainties, including the 
-   normalization uncertainties. The black curves are the results of our fits 
-   with the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.}
+\includegraphics[width=13.9cm]{incoherent_ALU_phi_t.pdf}
+\caption{The incoherent $A_{LU}$ as a function of $\phi$ for different $t$ 
+   bins.  The error bars represent the statistical uncertainties. The gray 
+   bands represent the systematic uncertainties, including the normalization 
+   uncertainties. The black curves are the results of our fits with the form 
+   $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.}
 \label{fig:alu}
@@
 Fig.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
-$\phi$ in bins of $Q^{2}$ (integrated over the full $x_{B}$ and $t$ ranges), 
-$x_{B}$ (integrated over the full $Q^{2}$ and $t$ ranges), and $t$ (integrated 
-over the full $Q^{2}$ and $x_{B}$ ranges). The curves on the plots are fits of 
-the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.  The main 
-contributions to systematic uncertainties on these fits are from the choice of 
-the DVCS exclusivity cuts (6\%) and the large bin size (7\%). The systematic 
-uncertainties sum up to less than 10\% for all data points and thus always 
-remain significantly smaller than the statistical uncertainities.
+$\phi$ in bins of $t$ (integrated over the full $Q^{2}$ and $x_{B}$ ranges).  
+The curves on the plots are fits of the form $\frac{a_{0}~\sin(\phi)}{1+ 
+a_{1}~\cos(\phi)}$.  The main contributions to systematic uncertainties on 
+these fits are from the choice of the DVCS exclusivity cuts (6\%) and the large 
+bin size (7\%). The systematic uncertainties sum up to less than 10\% for all 
+data points and thus always remain significantly smaller than the statistical 
+uncertainities.
 

### 2019-02-21 eg6-letters/incoherent/incoherent_prl.tex
minor cleaning for publication
Add notes from Stepan and Raphael

@@
 \begin{document}
-\linenumbers
+%\linenumbers
 
-\title{Deeply Virtual Compton Scattering measurement off bound protons}
+\title{Exploring the structure of the bound proton with Deeply Virtual Compton Scattering}
 
@@
 \begin{abstract}
- We report the first beam spin asymmetry (BSA) measurement of incoherent deeply 
-   virtual Compton scattering (DVCS) off $^4$He. The data were accumulated 
-   using a 6 GeV longitudinally polarized electron beam incident on a 
-   pressurized $^4$He gaseous target placed within the CLAS spectrometer in 
-   Hall-B at the Thomas Jefferson National Accelerator Facility. The azimuthal 
-   angle ($\phi$) dependence of the BSA was studied in a wide range of virtual 
-   photon and scattered proton kinematics. The $Q^2$, $x_B$, and $t$ 
-   dependencies of the BSA on the bound proton are compared with those on the 
-   free proton. In the whole kinematical region of our measurements, the BSA on 
-   the bound proton is smaller by $20\%$ to $40\%$, indicating possible medium 
-   modification of its partonic structure. This measurement opens a new avenue 
-   for studying the structure of bound nucleons and for exploring the origin of 
-   the EMC effect using the framework of the generalized parton distributions.
-
+In the past two decades, deeply virtual Compton scattering of electrons has been successfully 
+used to advance our knowledge of the partonic structure of the free proton and investigate 
+correlations between the transverse position and the longitudinal momentum of quarks inside 
+the nucleon. In this work, we report the first beam spin asymmetry (BSA) measurement of deeply 
+virtual Compton scattering (DVCS) off a proton bound in $^4$He. The structure of the bound 
+nucleons in nuclei has been studied in inclusive deep-inelastic lepton scattering experiments 
+off nuclear targets only, showing a significant difference in longitudinal momentum distribution 
+of quarks inside the bound nucleon, known as the EMC effect and still eluding our understanding. 
+The data used here were accumulated using a $6$ GeV longitudinally polarized electron beam 
+incident on a pressurized $^4$He gaseous target placed within the CLAS spectrometer in Hall-B 
+at the Thomas Jefferson National Accelerator Facility. The azimuthal angle ($\phi$) dependence 
+of the BSA was studied in a wide range of virtual photon and scattered proton kinematics. The 
+Q$^2$, x$_B$, and t dependencies of the BSA on the bound proton are compared with those on the 
+free proton. In the whole kinematical region of our measurements, the BSA on the bound proton 
+is smaller by 20\% to 40\%, indicating possible medium modification of its partonic structure.
 \end{abstract}
-\pacs{Valid PACS appear here}
+%\pacs{Valid PACS appear here}
 
@@
 6.5\% by selecting events passing all our selection cuts but originating from 
-different vertices. The $\pi^0$ contamination was estimated using detector 
+different vertices. The $\pi^0$ contamination was estimated and substracted using detector 
 simulation and experimental data. From simulation, we calculated the ratio ($R 
 = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ events that 
-were wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the 
-number of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$.  
+were wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events ($N^{1\gamma}_{sim}$) to the 
+number of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$ ($N^{2\gamma}_{sim}$).  
 Then in each kinematical bin and for each beam-helicity state, the 
@@
 the number of the experimentally identified $ep\rightarrow e'p'\gamma$ 
-($ep\rightarrow e'p'\pi^0$) events. Depending on the kinematics, we found this 
-contamination to be 8 to 10\%.
+($ep\rightarrow e'p'\pi^0$) events. Depending on the kinematics, we substracted
+between 8 and 10\% of the data due to the $\pi^0$ contamination.
 
@@
 the properties of bound nucleons directly from the basic degrees of freedom of 
-QCD, quarks and gluons.
+QCD, quarks and gluons. Planned experiments at Jefferson Lab will continue 
+and extend these studies of the bound nucleon structure using DVCS. We have 
+an experimental program using the CLAS12 detector in the experimental Hall-B, 
+called ALERT, to improve the DVCS measurements with the detection of nuclear
+fragments to control better the final state interactions and the initial state
+kinematic.
 

### 2019-02-27 eg6-letters/incoherent/incoherent_prl.tex
fix grammar

@@
 called ALERT, to improve the DVCS measurements with the detection of nuclear
-fragments to control better the final state interactions and the initial state
+fragments to better control the final state interactions and the initial state
 kinematic.

### 2019-02-27 eg6-letters/incoherent/incoherent_prl.tex
cleanup abstract

@@
 correlations between the transverse position and the longitudinal momentum of quarks inside 
-the nucleon. In this work, we report the first beam spin asymmetry (BSA) measurement of deeply 
-virtual Compton scattering (DVCS) off a proton bound in $^4$He. The structure of the bound 
-nucleons in nuclei has been studied in inclusive deep-inelastic lepton scattering experiments 
-off nuclear targets only, showing a significant difference in longitudinal momentum distribution 
-of quarks inside the bound nucleon, known as the EMC effect and still eluding our understanding. 
-The data used here were accumulated using a $6$ GeV longitudinally polarized electron beam 
-incident on a pressurized $^4$He gaseous target placed within the CLAS spectrometer in Hall-B 
-at the Thomas Jefferson National Accelerator Facility. The azimuthal angle ($\phi$) dependence 
-of the BSA was studied in a wide range of virtual photon and scattered proton kinematics. The 
-Q$^2$, x$_B$, and t dependencies of the BSA on the bound proton are compared with those on the 
-free proton. In the whole kinematical region of our measurements, the BSA on the bound proton 
-is smaller by 20\% to 40\%, indicating possible medium modification of its partonic structure.
+the nucleon.  The structure of bound nucleons in nuclei has only been studied in inclusive
+deep-inelastic lepton scattering experiments off nuclear targets, showing a significant
+difference in longitudinal momentum distribution of quarks inside the bound nucleon, known as
+the EMC effect.  In this work, we report the first beam spin asymmetry (BSA) measurement of
+exclusive deeply virtual Compton scattering (DVCS) off a proton bound in $^4$He.  The data
+used here were accumulated using a $6$ GeV longitudinally polarized electron beamincident on
+a pressurized $^4$He gaseous target placed within the CLAS spectrometer in Hall-B at the Thomas
+Jefferson National Accelerator Facility. The azimuthal angle ($\phi$) dependence of the BSA was
+studied in a wide range of virtual photon and scattered proton kinematics. The Q$^2$, x$_B$,
+and t dependencies of the BSA on the bound proton are compared with those on the free proton.
+In the whole kinematical region of our measurements, the BSA on the bound proton is smaller by
+20\% to 40\%, indicating possible medium modification of its partonic structure.
 \end{abstract}

### 2019-02-27 eg6-letters/incoherent/incoherent_prl.tex
fix spelling mistake

@@
 6.5\% by selecting events passing all our selection cuts but originating from 
-different vertices. The $\pi^0$ contamination was estimated and substracted using detector 
+different vertices. The $\pi^0$ contamination was estimated and subtracted using detector 
 simulation and experimental data. From simulation, we calculated the ratio ($R 
@@
 the number of the experimentally identified $ep\rightarrow e'p'\gamma$ 
-($ep\rightarrow e'p'\pi^0$) events. Depending on the kinematics, we substracted
+($ep\rightarrow e'p'\pi^0$) events. Depending on the kinematics, we subtracted
 between 8 and 10\% of the data due to the $\pi^0$ contamination.

### 2019-02-28 eg6-letters/incoherent/incoherent_prl.tex
implement the recent comments from stepan

@@
 Incoherent DVCS events were selected by requiring an electron, a proton, and at 
-least one photon in the final state. Electrons were identified as negatively 
-charged tracks reconstructed in the drift chambers with an appropriate energy 
-deposition in the electromagnetic calorimeter (EC) and a light yield above the 
-threshold in the Cherenkov counters. The protons were identified from 
-positively charged tracks based on their time-of-flight measured 
-by the scintillator counters.  In addition, it was required that both the 
-electron and the proton in the event originated from the same vertex at the 
-target. The photons were detected in either the IC or the CLAS electromagnetic 
-calorimeter. All the clusters within the IC fiducial region were assumed to be 
-photons, while a timing cut was used to clean the EC photons from neutrons.  
+least one photon in the final state using the standard particle identification 
 Note that even though the DVCS reaction has only one real photon in the final 
@@
 following selection stage, the most energetic photon was considered as the DVCS 
-photon candidate (see \cite{Hattawy:thesis} for additional details on the 
-particle identification).
+photon candidate.
 
 Further requirements were applied to clean the identified initial set of 
-incoherent DVCS events from accidental and physics background events. First, 
-events were selected with $Q^{2}$ greater than 1 GeV$^2$ to ensure the 
-applicability of the DVCS handbag diagram, and with $\gamma^{*}p$ invariant 
-mass ($W=\sqrt{(q+p)^2}$, assuming that the initial proton is at rest) greater 
-than 2 GeV to avoid the nucleon resonance region. The squared transferred 
-momentum to the recoil proton $t$, calculated from the four-momentum vectors of 
-the incoming and outgoing photons, was required to be greater than a minimum 
-kinematically allowed value ($t_{min}$) at given $Q^2$ and $W$ defined as: 
-\begin{equation}
+incoherent DVCS events from accidental and physics background events. 
+First, events were selected with $Q^2$ grater than $1$ GeV$^2$ and the 
+$\gamma^*p$ invariant mass ($W=\sqrt{(q+p)^2}$, assuming that the initial 
+nucleon is at rest) greater than $2$ GeV. This is a commonly accepted region of 
+kinematics used by the previous DVCS experiments to ensure the applicability of 
+the DVCS handbag diagram and avoid the nucleon resonance region. The squared 
+transferred momentum to the recoil proton $t$, calculated from the 
+four-momentum vectors of the incoming and outgoing photons, was required to be 
+greater than a minimum kinematically allowed value ($t_{min}$) at given $Q^2$ 
+and $W$ defined as: \begin{equation}
 t_{min} 
@@
 where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
-proton mass). We specifically used the kinematics of the photons to determine 
-$t$ because the initial proton kinematics is unknown due to Fermi motion. We 
-ensured the exclusivity of the incoherent DVCS events by imposing a series of 
-constraints based on the four-momentum conservation in the reaction 
-$ep\rightarrow e'p'\gamma$. These kinematical variables are: the coplanarity 
-angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and ($\gamma^*$,$p'$) 
-planes, the missing energy, mass, and transverse momentum of the $e'\gamma$ and 
-$e'p'\gamma$ systems, the missing mass squared of the $e'p'$ system, and the 
-angle $\theta$ between the measured photon and the missing momentum of the 
-$e'p'$ system. The experimental data for the most relevant exclusivity 
-variables are shown in Fig.~\ref{fig:kin-cuts}. Because of the Fermi motion of 
-the nucleons in the helium nucleus, these cuts
+proton mass. This cut was applied to avoid accepting events in unphysical 
+regions of kinematics due to the radiative effects. We specifically used the 
+kinematics of the photons to determine $t$ because the initial proton 
+kinematics is unknown due to Fermi motion.
+
+In the final sample, the exclusivity of the incoherent DVCS events was ensured 
+by imposing a series of constraints based on the four-momentum conservation in 
+the reaction $ep\rightarrow e'p'\gamma$.  These kinematical variables are: the 
+coplanarity angle $\Delta\phi$ between the ($\gamma,\gamma^*$) and 
+($\gamma^*$,$p'$) planes, the missing energy, mass, and transverse momentum of 
+the $e'\gamma$ and $e'p'\gamma$ systems, the missing mass squared of the $e'p'$ 
+system, and the angle $\theta$ between the measured photon and the missing 
+momentum of the $e'p'$ system. The experimental data for the most relevant 
+exclusivity variables are shown in Fig.~\ref{fig:kin-cuts}.  Because of the 
+Fermi motion of the nucleons in the helium nucleus, these cuts
 are slightly wider than those previously used for free proton experiments~%

### 2019-02-28 eg6-letters/incoherent/incoherent_prl.tex
minor edit to fix implementing the first suggestion from stepan regarding the PID paragraph

@@
 least one photon in the final state using the standard particle identification 
-Note that even though the DVCS reaction has only one real photon in the final 
-state, events with more than one photon were not discarded at this stage. These 
-extra photons were mostly soft photons from accidental coincidence which, as 
-will be discussed below, the DVCS exclusivity cuts easily eliminated.  In the 
-following selection stage, the most energetic photon was considered as the DVCS 
-photon candidate.
+framework of the CLAS event reconstruction (see \cite{Hattawy:thesis} for 
+additional details on the particle identification). Note that even though the 
+DVCS reaction has only one real photon in the final state, events with more 
+than one photon were not discarded at this stage. These extra photons were 
+mostly soft photons from accidental coincidence which, as will be discussed 
+below, the DVCS exclusivity cuts easily eliminated.  In the following selection 
+stage, the most energetic photon was considered as the DVCS photon candidate.
 

### 2019-03-07 eg6-letters/incoherent/incoherent_prl.tex
Minor edits

@@
 exclusive deeply virtual Compton scattering (DVCS) off a proton bound in $^4$He.  The data
-used here were accumulated using a $6$ GeV longitudinally polarized electron beamincident on
+used here were accumulated using a $6$ GeV longitudinally polarized electron beam incident on
 a pressurized $^4$He gaseous target placed within the CLAS spectrometer in Hall-B at the Thomas
@@
 \end{equation}
-where the parameters $a_{0,1,2}$ are combinations of the abovementioned Fourier 
+where the parameters $a_{0,1,2}$ are combinations of the aforementioned Fourier 
 coefficients. The $\sin(\phi)$ harmonic is dominant in $A_{LU}$ and is 
@@
 proton mass. This cut was applied to avoid accepting events in unphysical 
-regions of kinematics due to the radiative effects. We specifically used the 
+regions of kinematics for which it is not possible to calculate the radiative 
+effects. We specifically use the 
 kinematics of the photons to determine $t$ because the initial proton 
@@
 uncertainties sum up to less than 10\% for all data points and thus always 
-remain significantly smaller than the statistical uncertainities.
+remain significantly smaller than the statistical uncertainties.
 
@@
 fragments to better control the final state interactions and the initial state
-kinematic.
+kinematic of the bound nucleon.
 

### 2019-03-07 eg6-letters/incoherent/responsereferee.tex
More edits and addition of referee response

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{LZ15969:  Authors' Reply}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle

\section{Summary of Changes}

The title and abstracted were rewritten completely, the summary was appended with the future plans, and we also clarified the content in several places. However, we would like to refute the claims regarding the invalidity of the $Q^2$ selection and factorization assumptions, particularly regarding this letter's relationship to a large history of published research in this field.

\section{Responses to Referees}

\subsection{Referee A}

{\em The title needs work, to try to grab the attention of the reader.
At present it reads like the title of an internal collaboration
report. Here is one suggestion, "Medium Modification of Nucleon 
Properties, Explored with Deeply Virtual Compton Scattering" but 
I am sure the many senior people in the author list can come up
with something even better.

Similar comments apply to the abstract; the motivation for the
experiment is buried at the end. Bring it to the front. Start the
abstract with something like "Deeply virtual Compton scattering of
electrons from protons not only affords a view into the internal
structure of protons but also provides a method of exploring the
modification of that structure when the proton is bound within a
nucleus." Again, I am sure you can come up with something better than
that.

If you have any plans for additional uses of this technique, it
would be a good idea to mention them in your final summary paragraph.}

\noindent \\
Answer: Following the comments from the Referee A, we revisited the title and abstract completely. We
also made an addition to the summary paragraph to document future related plans, the approved ALERT experiment at JLab.

\subsection{Referee B}

{\em I do not support publication of this manuscript in Physical Review Letters. Both the introduction and experimental aspects are well described, but the article does lack in general accessibility in its science description, and oversimplifies in its physics interpretation. The data are worthwhile to publish and of interest, but I fail to see the portrayed science conclusions at this time.

My criticism related to general accessibility is that no clear meaning or physics insights are attributed to the Compton form factor H, it is simply postulated. Similarly, that the $a_0$ term dominates the shape of the distribution is derived from an earlier publication, but its relevance not explained. An 8 to 10\% contamination of the $\pi^0$ channel is reported, but its impact on the results or systematics is never further elucidated. To interpret some of the figures and textual description, the reader needs to fold in the $t$-dependence. Perhaps more critical, the results and the conclusions drawn are oversimplified and it is unclear if they are correct. First, it is certainly not true that selection of events with $Q^2>1$  GeV$^2$ suffices to ensure the applicability of the DVCS handbag diagram. Even in the inclusive DIS case the argument is still out if $Q^2>1$ GeV$^2$ suffices for a (leading-twist) partonic interpretation. There are no experimental data that cleanly indicate such low $Q^2$ cut would suffice for a pure handbag diagram description. It is further stated that t was required to be greater than a minimum kinematically allowed value, which seems an empty statement without further clarification.  A further serious objection I have is that it seems the authors assumed an Impulse Approximation, and draw their main conclusions from that assumption.

The authors assume a factorization of their measured process as a DVCS process on a single quasi-free proton and a nuclear spectral function, and then compare with an inclusive EMC effect and with a QMC calculation, and conclude that they find medium-modified GPDs beyond these. But there is no one-to-one comparison possible, as the nuclear ratio they measure is (at best!) a convolution of electron-quark scattering with the handbag mechanism, embedded in a nuclear medium, at $Q^2 > 1 $ GeV$^2$. It is certainly not a given that this at these scales is separable in a quasi-free DVCS-like process convoluted with a nuclear spectral function. The conclusion that the measured BSA is quenched and that nuclear effects exist is fair, but to link those at such low-$Q^2$ scales to possible medium modifications of the bound-proton’s partonic structure or, separately, to a new avenue to explore the origin of the EMC effect is a stretch. It reminds of initial $(e,e’p)$ experiments where quenching was also postulated to be related to bound-nucleon EMC-like effects. It is just too early to draw such conclusions, even more if it is not clear if one can interpret the data in this low-$Q^2$ region with a leading-twist handbag mechanism, and if this changes in the nuclear medium.}

\noindent \\
Answer:

We clarified the letter to make it clearer to the general reader where it is possible without adding too much material. Particularly, the physics behind the H GPD is clarified, the resoning behind the minimum t cut, as well as the $\pi^0$ contamination and how we accounted for it (i.e. it is measured and subtracted at each kinematic). It is unclear what the referee is pointing at when mentioning that we assume impulse approximation for our conclusion. We do not draw any strong conclusion in favor of a particular interpretation of the result, beyond the fact that the result is at odds with existing models. Actually, as would be expected from any surprising first measurement, we point that this result should lead to further exploration of the question both on the theoretical and experimental levels.

We strongly disagree with the suggestion that the cut $Q^2 > 1$ GeV$^2$ is unjustified and improper. While some of the criticisms raised by the referee are sound, they may be forgetting that a significant aspect of this work involves comparing our results to previous experimental DVCS results from the past decade. Those results have systematically used such a cut, and a different choice for us would defeat the purpose of our comparison. Moreover, this cut is widely used in previously published results cited in the letter that are all consistent with the handbag diagram description: PRL 87, 182001; 97, 072002; 100, 162002; 114, 032001; 115, 212003; 119, 202004 just to quote PRL references. Such extended literature strongly establish this cut as the standard of the field, we fail to see how this letter could possibly be a reasonnable place to revisit this standard.

About the publication in PRL, we still feel strongly that such a large deviation (20 to 40\%) from the predictions of theoretical models, whatever its source, is worth communicating to a large audience of physicists, thus our choice of PRL to publish this work.

\end{document}

### 2019-03-07 eg6-letters/incoherent/incoherent_prl.tex
More edits and addition of referee response

@@
 
-In the kinematical phase-space of our experiment, the GPD $H$ is
+In the kinematical phase-space of our experiment, the GPD $H$, which encodes
+the unpolarized density of partons, is
 expected to dominate the contribution in the BSA over the other three GPDs.  

### 2019-03-08 eg6-letters/incoherent/incoherent_prl.tex
latest comments from Stepan

--- 2019-03-07 eg6-letters/incoherent/incoherent_prl.tex
@@
 \begin{abstract}
-In the past two decades, deeply virtual Compton scattering of electrons has been successfully 
-used to advance our knowledge of the partonic structure of the free proton and investigate 
-correlations between the transverse position and the longitudinal momentum of quarks inside 
-the nucleon.  The structure of bound nucleons in nuclei has only been studied in inclusive
-deep-inelastic lepton scattering experiments off nuclear targets, showing a significant
-difference in longitudinal momentum distribution of quarks inside the bound nucleon, known as
-the EMC effect.  In this work, we report the first beam spin asymmetry (BSA) measurement of
-exclusive deeply virtual Compton scattering (DVCS) off a proton bound in $^4$He.  The data
-used here were accumulated using a $6$ GeV longitudinally polarized electron beam incident on
+In the past two decades, deeply virtual Compton scattering of electrons has 
+   been successfully used to advance our knowledge of the partonic structure of 
+   the free proton and investigate correlations between the transverse position 
+   and the longitudinal momentum of quarks inside the nucleon. Meanwhile, the 
+   structure of bound nucleons in nuclei has only been studied in inclusive 
+   deep-inelastic lepton scattering experiments off nuclear targets, showing a 
+   significant difference in longitudinal momentum distribution of quarks 
+   inside the bound nucleon, known as
+the EMC effect. In this work, we report the first beam spin asymmetry (BSA) 
+   measurement of exclusive deeply virtual Compton scattering (DVCS) off a 
+   proton bound in $^4$He.  The data used here were accumulated using a $6$ GeV 
+   longitudinally polarized electron beam incident on
 a pressurized $^4$He gaseous target placed within the CLAS spectrometer in Hall-B at the Thomas
 Jefferson National Accelerator Facility. The azimuthal angle ($\phi$) dependence of the BSA was
-studied in a wide range of virtual photon and scattered proton kinematics. The Q$^2$, x$_B$,
+studied in a wide range of virtual photon and scattered proton kinematics. The 
+   $Q^2$, $x_B$,
 and t dependencies of the BSA on the bound proton are compared with those on the free proton.
@@
    \mathcal{E}+ \frac{x_B}{2}(F_1+F_2)\tilde{\mathcal{H}}),
+   \label{a0_cff}
 \end{equation}
@@
 Similar expressions apply for the GPDs $E$, $\widetilde{H}$, and 
-$\widetilde{E}$ \cite{Guidal:2013rya}.
+$\widetilde{E}$ \cite{Guidal:2013rya}. At forward limit, $\xi\to 0$ and $t \to 0$, the GPD H reduces to quark anti-quark PDFs and its 0th moment in $x$ represents the elastic Dirac form-factor F$_1$.
 
@@
 where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
-proton mass. This cut was applied to avoid accepting events in unphysical 
-regions of kinematics for which it is not possible to calculate the radiative 
-effects. We specifically use the 
-kinematics of the photons to determine $t$ because the initial proton 
-kinematics is unknown due to Fermi motion.
+proton mass. This cut was applied to avoid accepting events that appear in  
+unphysical regions of kinematics due to detector resolution and radiative 
+effects.  We specifically use the kinematics of the photons to determine $t$ 
+because the initial proton kinematics is unknown due to Fermi motion.
 
@@
 
-In the kinematical phase-space of our experiment, the GPD $H$ is
-expected to dominate the contribution in the BSA over the other three GPDs.  
-There, the $\phi$ dependence of $A_{LU}$ is mostly sensitive to the  imaginary 
-part of the CFF $\mathcal{H}$ through the parameter $a_0$ of 
-equation~\ref{eq:alu-simp}. The measurement of the free proton $A_{LU}$ 
-\cite{Girod:2007aa} has confirmed that the $a_0$ term dominates the shape of 
-the distribution.
+In the kinematical phase-space of our experiment, the $\phi$ dependence of 
+$A_{LU}$ is most sensitive to the imaginary part of the CFFs through the $a_0$ 
+term of Eq.~\ref{eq:alu-simp}, as confirmed by high statistics measurements on 
+the free proton \cite{Girod:2007aa,Jo:2015ema}. In the determination of $a_0$ 
+in Eq.~\ref{a0_cff}, the CFF $\mathcal{E}$ and $\mathcal{\tilde {H}}$ are 
+suppressed due to form-factors and the smallness of the coefficients.  
+Therefore, the dominant contribution to the BSA comes from the CFF 
+$\mathcal{H}$ and hence the GPD $H$.
 
@@
 QCD, quarks and gluons. Planned experiments at Jefferson Lab will continue 
-and extend these studies of the bound nucleon structure using DVCS. We have 
-an experimental program using the CLAS12 detector in the experimental Hall-B, 
-called ALERT, to improve the DVCS measurements with the detection of nuclear
-fragments to better control the final state interactions and the initial state
-kinematic of the bound nucleon.
+and extend these studies of the bound nucleon structure using DVCS. We have an 
+experimental program called ALERT using the CLAS12 detector in the Hall-B of 
+Jefferson Lab. These experiments will improve the DVCS measurements with the 
+detection of nuclear fragments to better control the final state interactions 
+and the initial state kinematics of the bound nucleon.
 

### 2019-03-10 eg6-letters/incoherent/incoherent_prl.tex
fix spelling

@@
 incoherent DVCS events from accidental and physics background events. 
-First, events were selected with $Q^2$ grater than $1$ GeV$^2$ and the 
+First, events were selected with $Q^2$ greater than $1$ GeV$^2$ and the 
 $\gamma^*p$ invariant mass ($W=\sqrt{(q+p)^2}$, assuming that the initial 

### 2019-03-10 eg6-letters/incoherent/incoherent_prl.tex
fix inconsistent GPD H instead of $H$

@@
 Similar expressions apply for the GPDs $E$, $\widetilde{H}$, and 
-$\widetilde{E}$ \cite{Guidal:2013rya}. At forward limit, $\xi\to 0$ and $t \to 0$, the GPD H reduces to quark anti-quark PDFs and its 0th moment in $x$ represents the elastic Dirac form-factor F$_1$.
+$\widetilde{E}$ \cite{Guidal:2013rya}.
+At forward limit, $\xi\to 0$ and $t \to 0$, the GPD $H$ reduces to quark anti-quark PDFs and its 0th moment in $x$ represents the elastic Dirac form-factor F$_1$.
 

### 2019-03-10 eg6-letters/incoherent/incoherent_prl.tex
fix screwed up sentence on forward limit

--- 2019-03-10 eg6-letters/incoherent/incoherent_prl.tex
@@
 Similar expressions apply for the GPDs $E$, $\widetilde{H}$, and 
-$\widetilde{E}$ \cite{Guidal:2013rya}. At forward limit, $\xi\to 0$ and $t \to 0$, the GPD H reduces to quark anti-quark PDFs and its 0th moment in $x$ represents the elastic Dirac form-factor F$_1$.
+$\widetilde{E}$ \cite{Guidal:2013rya}.
+At the forward limit, $\xi\to 0$ and $t \to 0$, the GPD $H$ reduces to quark, anti-quark PDFs, and its zeroth moment in $x$ represents the elastic Dirac form-factor F$_1$.
 

### 2019-03-10 eg6-letters/incoherent/responsereferee.tex
add more explicit summary list of changes

@@
 \section{Summary of Changes}
+Below is a summary list of the changes to the paper and their location in the text.
+The following sections contain responses to the referees, where we feel we have largely addressed the expressed concerns.
+Note, we would like to refute the claims regarding the invalidity of the $Q^2$ selection and factorization assumptions, particularly regarding this letter's relationship to a large history of published research in this field.
 
-The title and abstracted were rewritten completely, the summary was appended with the future plans, and we also clarified the content in several places.
-However, we would like to refute the claims regarding the invalidity of the $Q^2$ selection and factorization assumptions, particularly regarding this letter's relationship to a large history of published research in this field.
+\begin{itemize}
+    \item{The title and abstract were completely rewritten.}
+    \item{The summary was updated with future plans inclluding an upcoming experiment.}
+    \item{Removed some unnecesary experimental details that are standard to CLAS analyses, and added a corresponding reference, in the right column of page 3.}
+    \item{Added a sentence on the relationship between the GPD $H$ and PDFs, after equation 5.}
+    \item{Explicitly mentioned the standard nature and justification of the $Q^2>2$ GeV selection, at the beginning of page 4.}
+    \item{Motivation for the $t>t_{min}$ selection was clarified, in the left coulmn of page 4.}
+    \item{Treatment of $\pi^0$ contamination and subtraction was clarified, in the paragraph starting at the end of page 4.}
+    \item{The dominance of $a_0$, the Compton Form Factor, and the GPD $H$, was clarified and supported with references, in the left column of page 5.}
+    \item{Minor grammar and style updates.}
+\end{itemize}
 

### 2019-03-10 eg6-letters/incoherent/responsereferee.tex
minor language
fix spelling mistakes in response to referees

@@
 Below is a summary list of the changes to the paper and their location in the text.
-The following sections contain responses to the referees, where we feel we have largely addressed the expressed concerns.
+The following sections contain responses to the referees, where we feel we have addressed the expressed concerns.
 Note, we would like to refute the claims regarding the invalidity of the $Q^2$ selection and factorization assumptions, particularly regarding this letter's relationship to a large history of published research in this field.
@@
     \item{The title and abstract were completely rewritten.}
-    \item{The summary was updated with future plans inclluding an upcoming experiment.}
-    \item{Removed some unnecesary experimental details that are standard to CLAS analyses, and added a corresponding reference, in the right column of page 3.}
+    \item{The summary was updated with future plans including an upcoming experiment.}
+    \item{Removed some unnecessary experimental details that are standard to CLAS analyses, and added a corresponding reference, in the right column of page 3.}
     \item{Added a sentence on the relationship between the GPD $H$ and PDFs, after equation 5.}
     \item{Explicitly mentioned the standard nature and justification of the $Q^2>2$ GeV selection, at the beginning of page 4.}
-    \item{Motivation for the $t>t_{min}$ selection was clarified, in the left coulmn of page 4.}
+    \item{Motivation for the $t>t_{min}$ selection was clarified, in the left column of page 4.}
     \item{Treatment of $\pi^0$ contamination and subtraction was clarified, in the paragraph starting at the end of page 4.}
@@
 We clarified the letter to make it clearer to the general reader where it is possible without adding too much material.
-Particularly, the physics behind the H GPD is clarified, the resoning behind the minimum t cut, as well as the $\pi^0$ contamination and how we accounted for it (i.e.
+Particularly, the physics behind the H GPD is clarified, the reasoning behind the minimum t cut, as well as the $\pi^0$ contamination and how we accounted for it (i.e.
 it is measured and subtracted at each kinematic).
@@
 Moreover, this cut is widely used in previously published results cited in the letter that are all consistent with the handbag diagram description: PRL 87, 182001; 97, 072002; 100, 162002; 114, 032001; 115, 212003; 119, 202004 just to quote PRL references.
-Such extended literature strongly establish this cut as the standard of the field, we fail to see how this letter could possibly be a reasonnable place to revisit this standard.
+Such extended literature strongly establish this cut as the standard of the field, we fail to see how this letter could possibly be a reasonable place to revisit this standard.
 

### 2019-03-11 eg6-letters/incoherent/incoherent_prl.tex
*final* comments from Stepan

@@
 mostly soft photons from accidental coincidence which, as will be discussed 
-below, the DVCS exclusivity cuts easily eliminated.  In the following selection 
+below, the DVCS exclusivity cuts easily eliminated.  In the following 
 stage, the most energetic photon was considered as the DVCS photon candidate.
@@
 system, and the angle $\theta$ between the measured photon and the missing 
-momentum of the $e'p'$ system. The experimental data for the most relevant 
+momentum of the $e'p'$ system. The experimental distributions for the most relevant 
 exclusivity variables are shown in Fig.~\ref{fig:kin-cuts}.  Because of the 
-Fermi motion of the nucleons in the helium nucleus, these cuts
+Fermi motion of the nucleons in the helium nucleus, the cuts indicated by the dashed lines
 are slightly wider than those previously used for free proton experiments~%

### 2019-03-25 eg6-letters/incoherent/March2019_Updated_docs_for_LZ15969_Hattawy/publication_version/incoherent_prl.tex
some cleaning for the directory after being re-submitted

--- 2019-03-11 eg6-letters/incoherent/incoherent_prl.tex
@@
    significant difference in longitudinal momentum distribution of quarks 
-   inside the bound nucleon, known as
-the EMC effect. In this work, we report the first beam spin asymmetry (BSA) 
+   inside the bound nucleon, known as the EMC effect. In this work, we report the first beam spin asymmetry (BSA) 
    measurement of exclusive deeply virtual Compton scattering (DVCS) off a 
@@
 that could be related to the initial momentum of the nucleons. We also rejected 
-events where a $\pi^0$ was identified by the invariant mass of two photons. At 
-the end of this selection process, about 30k events passed all the 
-requirements; their kinematic distributions are shown in 
-Fig.~\ref{fig:kin-coverage}.
+events where a $\pi^0$ was identified by the invariant mass of two photons. At the end of this selection 
+process, about 30k events passed all the requirements.
 
 \begin{figure}[tb]
-\includegraphics[width=8.9cm]{figs/incoh_exc_cuts_final.pdf}
+\includegraphics[width=8.9cm]{incoh_exc_cuts_final.pdf}
 \caption{The distributions from left to right and from top to bottom are: 
-   $\Delta \phi$, missing energy, missing masses squared and the cone angle 
+   $\Delta \phi$, missing energy, missing mass squared and the cone angle 
    ($\theta$) between the measured and the calculated photons in the $e'p'$ 
@@
 \begin{figure*}[t!]
-\includegraphics[width=13.9cm]{figs/incoherent_ALU_phi.pdf}
-\caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
-   for different $Q^{2}$ bins (top row), $x_{B}$ bins (middle row), and $-t$ 
-   bins (bottom row). The error bars represent the statistical uncertainties.  
-   The gray bands represent the systematic uncertainties, including the 
-   normalization uncertainties. The black curves are the results of our fits 
-   with the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.}
+\includegraphics[width=13.9cm]{incoherent_ALU_phi_t.pdf}
+\caption{The incoherent $A_{LU}$ as a function of $\phi$ for different $t$ 
+   bins. The error bars represent the statistical uncertainties. The gray 
+   bands represent the systematic uncertainties, including the normalization 
+   uncertainties. The black curves are the results of our fits with the form 
+   $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.}
 \label{fig:alu}
@@
 Fig.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
-$\phi$ in bins of $Q^{2}$ (integrated over the full $x_{B}$ and $t$ ranges), 
-$x_{B}$ (integrated over the full $Q^{2}$ and $t$ ranges), and $t$ (integrated 
-over the full $Q^{2}$ and $x_{B}$ ranges). The curves on the plots are fits of 
-the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.  The main 
-contributions to systematic uncertainties on these fits are from the choice of 
+$\phi$ in bins of $t$ (integrated over the full $Q^{2}$ and $x_{B}$ ranges).  
+The curves on the plots are fits of the form $\frac{a_{0}~\sin(\phi)}{1+ 
+a_{1}~\cos(\phi)}$. The main contributions to systematic uncertainties on these fits are from the choice of 
 the DVCS exclusivity cuts (6\%) and the large bin size (7\%). The systematic 
 uncertainties sum up to less than 10\% for all data points and thus always 
-remain significantly smaller than the statistical uncertainties.
+remain significantly smaller than the statistical uncertainities.
 

### 2019-05-10 eg6-letters/incoherent/incoherent_prl.tex
shrink figures

@@
 \begin{figure}[tb]
-\includegraphics[width=7.5cm]{figs/handbag_incoherent.pdf}
+\includegraphics[width=6.5cm]{handbag_incoherent.pdf}
 \caption{Representation of the leading-order, twist-2, handbag diagram of the 
@@
 that could be related to the initial momentum of the nucleons. We also rejected 
-events where a $\pi^0$ was identified by the invariant mass of two photons. At 
-the end of this selection process, about 30k events passed all the 
-requirements; their kinematic distributions are shown in 
-Fig.~\ref{fig:kin-coverage}.
+events where a $\pi^0$ was identified by the invariant mass of two photons. At the end of this selection 
+process, about 30k events passed all the requirements.
 
 \begin{figure}[tb]
-\includegraphics[width=8.9cm]{figs/incoh_exc_cuts_final.pdf}
+\includegraphics[width=8.9cm,height=7.8cm]{incoh_exc_cuts_final.pdf}
 \caption{The distributions from left to right and from top to bottom are: 
-   $\Delta \phi$, missing energy, missing masses squared and the cone angle 
+   $\Delta \phi$, missing energy, missing mass squared and the cone angle 
    ($\theta$) between the measured and the calculated photons in the $e'p'$ 
@@
 \begin{figure*}[t!]
-\includegraphics[width=13.9cm]{figs/incoherent_ALU_phi.pdf}
-\caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
-   for different $Q^{2}$ bins (top row), $x_{B}$ bins (middle row), and $-t$ 
-   bins (bottom row). The error bars represent the statistical uncertainties.  
-   The gray bands represent the systematic uncertainties, including the 
-   normalization uncertainties. The black curves are the results of our fits 
-   with the form $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.}
+\includegraphics[width=13cm]{incoherent_ALU_phi_t.pdf}
+\caption{The incoherent $A_{LU}$ as a function of $\phi$ for different $t$ 
+   bins. The error bars represent the statistical uncertainties. The gray 
+   bands represent the systematic uncertainties, including the normalization 
+   uncertainties. The black curves are the results of our fits with the form 
+   $\frac{a_{0}~\sin(\phi)}{1+ a_{1}~\cos(\phi)}$.}
 \label{fig:alu}
@@
 
-\begin{figure}[tb]
-\includegraphics[width=7.8cm]{figs/ALU_90_p_vs_Q2_shortscenrario.pdf}
-\includegraphics[width=7.8cm]{figs/ALU_90_p_vs_x_shortscenrario.pdf}
-\includegraphics[width=7.8cm]{figs/ALU_90_p_vs_t_shortscenrario.pdf}
+%\begin{figure}[tb]
+%\includegraphics[width=7cm]{ALU_90_p_vs_Q2_shortscenrario.pdf}
+%\includegraphics[width=7cm]{ALU_90_p_vs_x_shortscenrario.pdf}
+%\includegraphics[width=7cm]{ALU_90_p_vs_t_shortscenrario.pdf}
+%\caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $t$ dependencies (bottom) of
+%   the fitted $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). The error bars 
+%   represent the statistical uncertainties, while the gray bands represent the 
+%   systematic uncertainties. On the middle plot the curves are theoretical 
+%   calculations from \cite{simonetta_2}. On the bottom plot the solid (empty) 
+%   green circles are the HERMES $-A_{LU}$ (a positron beam was used) inclusive 
+%   measurements for the incoherent (coherent) enriched region 
+%   \cite{Airapetian:2009cga}; the curves represent theoretical calculations 
+%   from \cite{simonetta_2}.  } \label{fig:alu90}
+%\end{figure}
+
+\begin{figure*}[t!]
+\includegraphics[height=4.2cm,trim={0 0 1.59cm 0},clip]{ALU_90_p_vs_Q2_shortscenrario.pdf}
+\includegraphics[height=4.2cm,trim={3cm 0 1.6cm 0},clip]{ALU_90_p_vs_x_shortscenrario.pdf}
+\includegraphics[height=4.2cm,trim={3cm 0 1.6cm 0},clip]{ALU_90_p_vs_t_shortscenrario.pdf}
 \caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $t$ dependencies (bottom) of
@@
    \cite{Airapetian:2009cga}; the curves represent theoretical calculations 
-   from \cite{simonetta_2}.  } \label{fig:alu90}
-\end{figure}
+   from \cite{simonetta_2}.}
+\label{fig:alu90}
+\end{figure*}
 

### 2019-05-10 eg6-letters/incoherent/incoherent_prl.tex
2 referee text changes

@@
    and the longitudinal momentum of quarks inside the nucleon. Meanwhile, the 
-   structure of bound nucleons in nuclei has only been studied in inclusive 
+   structure of bound nucleons in nuclei has been studied in inclusive 
    deep-inelastic lepton scattering experiments off nuclear targets, showing a 
@@
 nucleon is at rest) greater than $2$ GeV. This is a commonly accepted region of 
-kinematics used by the previous DVCS experiments to ensure the applicability of 
-the DVCS handbag diagram and avoid the nucleon resonance region. The squared 
+kinematics used by the previous DVCS experiments 
+%to ensure the applicability of the DVCS handbag diagram and avoid
+and avoids the nucleon resonance region. The squared 
 transferred momentum to the recoil proton $t$, calculated from the 

### 2019-05-11 eg6-letters/incoherent/incoherent_prl.tex
change top/middle/bottom to left/middle/right in Figure 4 caption

@@
 \includegraphics[height=4.2cm,trim={3cm 0 1.6cm 0},clip]{ALU_90_p_vs_t_shortscenrario.pdf}
-\caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $t$ dependencies (bottom) of
+\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $t$ dependencies (right) of
    the fitted $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). The error bars 
@@
    systematic uncertainties. On the middle plot the curves are theoretical 
-   calculations from \cite{simonetta_2}. On the bottom plot the solid (empty) 
+   calculations from \cite{simonetta_2}. On the right plot the solid (empty) 
    green circles are the HERMES $-A_{LU}$ (a positron beam was used) inclusive 

### 2019-05-23 eg6-letters/incoherent/incoherent_prl.tex
some cleaning

--- 2019-05-10 eg6-letters/incoherent/incoherent_prl.tex
@@
 \begin{figure}[tb]
-\includegraphics[width=6.5cm]{handbag_incoherent.pdf}
+\includegraphics[width=7.5cm]{handbag_incoherent.pdf}
 \caption{Representation of the leading-order, twist-2, handbag diagram of the 
@@
 \begin{figure}[tb]
-\includegraphics[width=8.9cm,height=7.8cm]{incoh_exc_cuts_final.pdf}
+\includegraphics[width=8.9cm]{incoh_exc_cuts_final.pdf}
 \caption{The distributions from left to right and from top to bottom are: 
@@
 \begin{figure*}[t!]
-\includegraphics[width=13cm]{incoherent_ALU_phi_t.pdf}
+\includegraphics[width=13.9cm]{incoherent_ALU_phi_t.pdf}
 \caption{The incoherent $A_{LU}$ as a function of $\phi$ for different $t$ 
@@
 = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) of the number of $\pi^0$ events that 
-were wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events ($N^{1\gamma}_{sim}$) to the 
-number of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$ ($N^{2\gamma}_{sim}$).  
-Then in each kinematical bin and for each beam-helicity state, the 
-$\pi^0$-subtracted experimental DVCS events were calculated as $N = 
-N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow e'p'\pi^0}_{exp}$, where 
-$N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is 
-the number of the experimentally identified $ep\rightarrow e'p'\gamma$ 
-($ep\rightarrow e'p'\pi^0$) events. Depending on the kinematics, we subtracted
+were wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events 
+($N^{1\gamma}_{sim}$) to the number of events correctly identified as exclusive 
+$ep\rightarrow e'p'\pi^0$ ($N^{2\gamma}_{sim}$).  Then in each kinematical bin 
+and for each beam-helicity state, the $\pi^0$-subtracted experimental DVCS 
+events were calculated as $N = N^{ep\rightarrow e'p'\gamma}_{exp}- 
+R~N^{ep\rightarrow e'p'\pi^0}_{exp}$, where $N^{ep\rightarrow 
+e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is the number of the 
+experimentally identified $ep\rightarrow e'p'\gamma$ ($ep\rightarrow 
+e'p'\pi^0$) events. Depending on the kinematics, we subtracted
 between 8 and 10\% of the data due to the $\pi^0$ contamination.
@@
 
-Experimentally, $A_{LU}$ is defined as
+experimentally, $a_{lu}$ is defined as
 \begin{equation}
-   A_{LU} = \frac{1}{P_{B}(1-C)} \frac{N^{+} - N^{-}}{N^{+} + N^{-} },
+   a_{lu} = \frac{1}{p_{b}(1-c)} \frac{n^{+} - n^{-}}{n^{+} + n^{-} },
 \end{equation}
-where $N^{+}$ and $N^{-}$ are the number of DVCS events for the positive and 
-negative beam-helicity states, $P_{B}$ is the longitudinal beam polarization, 
+where $n^{+}$ and $n^{-}$ are the number of dvcs events for the positive and 
+negative beam-helicity states, $p_{b}$ is the longitudinal beam polarization, 
 and C stands for the contamination percentage of the accidental coincidences.
@@
 
-%\begin{figure}[tb]
-%\includegraphics[width=7cm]{ALU_90_p_vs_Q2_shortscenrario.pdf}
-%\includegraphics[width=7cm]{ALU_90_p_vs_x_shortscenrario.pdf}
-%\includegraphics[width=7cm]{ALU_90_p_vs_t_shortscenrario.pdf}
-%\caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $t$ dependencies (bottom) of
-%   the fitted $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). The error bars 
-%   represent the statistical uncertainties, while the gray bands represent the 
-%   systematic uncertainties. On the middle plot the curves are theoretical 
-%   calculations from \cite{simonetta_2}. On the bottom plot the solid (empty) 
-%   green circles are the HERMES $-A_{LU}$ (a positron beam was used) inclusive 
-%   measurements for the incoherent (coherent) enriched region 
-%   \cite{Airapetian:2009cga}; the curves represent theoretical calculations 
-%   from \cite{simonetta_2}.  } \label{fig:alu90}
-%\end{figure}
-
-\begin{figure*}[t!]
-\includegraphics[height=4.2cm,trim={0 0 1.59cm 0},clip]{ALU_90_p_vs_Q2_shortscenrario.pdf}
-\includegraphics[height=4.2cm,trim={3cm 0 1.6cm 0},clip]{ALU_90_p_vs_x_shortscenrario.pdf}
-\includegraphics[height=4.2cm,trim={3cm 0 1.6cm 0},clip]{ALU_90_p_vs_t_shortscenrario.pdf}
+\begin{figure}[tb]
+\includegraphics[width=7.8cm]{ALU_90_p_vs_Q2_shortscenrario.pdf}
+\includegraphics[width=7.8cm]{ALU_90_p_vs_x_shortscenrario.pdf}
+\includegraphics[width=7.8cm]{ALU_90_p_vs_t_shortscenrario.pdf}
 \caption{The $Q^{2}$ (top), $x_{B}$ (middle), and $t$ dependencies (bottom) of
@@
    \cite{Airapetian:2009cga}; the curves represent theoretical calculations 
-   from \cite{simonetta_2}.}
-\label{fig:alu90}
-\end{figure*}
+   from \cite{simonetta_2}.  } \label{fig:alu90}
+\end{figure}
 

### 2019-05-23 eg6-letters/incoherent/incoherent_prl.tex
fixing typos

@@
 
-experimentally, $a_{lu}$ is defined as
+Experimentally, $A_{LU}$ is defined as
 \begin{equation}
-   a_{lu} = \frac{1}{p_{b}(1-c)} \frac{n^{+} - n^{-}}{n^{+} + n^{-} },
+   A_{LU} = \frac{1}{P_{B}(1-C)} \frac{N^{+} - N^{-}}{N^{+} + N^{-} },
 \end{equation}
-where $n^{+}$ and $n^{-}$ are the number of dvcs events for the positive and 
-negative beam-helicity states, $p_{b}$ is the longitudinal beam polarization, 
+where $N^{+}$ and $N^{-}$ are the number of DVCS events for the positive and 
+negative beam-helicity states, $P_{B}$ is the longitudinal beam polarization, 
 and C stands for the contamination percentage of the accidental coincidences.

### 2019-05-23 eg6-letters/incoherent/LZ15969_Hattawy_SummaryOfChanges_May23_2019.tex
add updated figure 4 and response to the referees

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{LZ15969:  Authors' Reply}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle

\section{Summary of Changes}
Below is a summary list of the changes to the paper:

\begin{itemize}
   \item{ In response to Referee A (remove ``only''): it has been removed.}
   \item{ In response to Referee B (remove ``to ensure
the applicability of the DVCS handbag diagram''): it has been removed.}
   \item{ In response to Referee B (change ``avoid'' to ``avoids''): it has 
      been replaced.}
   \item { The figures has been edited to be within the maximum allowed length 
      3750.}

\end{itemize}

\end{document}

### 2019-05-23 eg6-letters/incoherent/incoherent_prl.tex
add updated figure 4 and response to the referees

--- 2019-05-11 eg6-letters/incoherent/incoherent_prl.tex
@@
 \begin{figure*}[t!]
-\includegraphics[height=4.2cm,trim={0 0 1.59cm 0},clip]{ALU_90_p_vs_Q2_shortscenrario.pdf}
-\includegraphics[height=4.2cm,trim={3cm 0 1.6cm 0},clip]{ALU_90_p_vs_x_shortscenrario.pdf}
-\includegraphics[height=4.2cm,trim={3cm 0 1.6cm 0},clip]{ALU_90_p_vs_t_shortscenrario.pdf}
+\includegraphics[height=5.2cm,trim={0 0 0cm 
+   0},clip]{ALU_90_p_shortscenrario.pdf}
 \caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $t$ dependencies (right) of

### 2019-05-23 eg6-letters/incoherent/ALU_90_p_shortscenrario.C

@@ -1,0 +1,970 @@
+void ALU_90_p_shortscenrario()
+{
+//=========Macro generated from canvas: Cann/
+//=========  (Thu May 23 15:02:43 2019) by ROOT version 6.14/04
+   TCanvas *Cann = new TCanvas("Cann", "",0,0,1000,400);
+   gStyle->SetOptFit(1);
+   Cann->Range(0,0,1,1);
+   Cann->SetFillColor(0);
+   Cann->SetBorderMode(0);
+   Cann->SetBorderSize(2);
+   Cann->SetLeftMargin(0.08527131);
+   Cann->SetRightMargin(0.02680798);
+   Cann->SetBottomMargin(0.255814);
+   Cann->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: Cann_1
+   TPad *Cann_1 = new TPad("Cann_1", "_1",0,0,0.3812449,0.9029345);
+   Cann_1->Draw();
+   Cann_1->cd();
+   Cann_1->Range(-0.875,-0.30625,4.5,0.5);
+   Cann_1->SetFillColor(0);
+   Cann_1->SetBorderMode(0);
+   Cann_1->SetBorderSize(2);
+   Cann_1->SetLeftMargin(0.255814);
+   Cann_1->SetRightMargin(0);
+   Cann_1->SetTopMargin(0);
+   Cann_1->SetBottomMargin(0.255814);
+   Cann_1->SetFrameBorderMode(0);
+   Cann_1->SetFrameBorderMode(0);
+   
+   TH2F *HALU_p_vs_Q2__3 = new TH2F("HALU_p_vs_Q2__3","",100,0.5,4.5,100,-0.1,0.5);
+   HALU_p_vs_Q2__3->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   HALU_p_vs_Q2__3->SetLineColor(ci);
+   HALU_p_vs_Q2__3->GetXaxis()->SetTitle("Q^{2} [GeV^{2}]");
+   HALU_p_vs_Q2__3->GetXaxis()->CenterTitle(true);
+   HALU_p_vs_Q2__3->GetXaxis()->SetNdivisions(605);
+   HALU_p_vs_Q2__3->GetXaxis()->SetLabelFont(22);
[…]

### 2019-05-24 eg6-letters/incoherent/LZ15969_Hattawy_SummaryOfChanges_May23_2019.tex
update reply

@@
 \section{Summary of Changes}
-Below is a summary list of the changes to the paper:
+We agree with the referees' suggestions and implemented the changes to the paper:
 
 \begin{itemize}
-   \item{ In response to Referee A (remove ``only''): it has been removed.}
-   \item{ In response to Referee B (remove ``to ensure
-the applicability of the DVCS handbag diagram''): it has been removed.}
-   \item{ In response to Referee B (change ``avoid'' to ``avoids''): it has 
-      been replaced.}
-   \item { The figures has been edited to be within the maximum allowed length 
-      3750.}
-
+   \item{ Per the recommendation of Referee A, we removed the ``only'' in the abstract.}
+   \item{ Per the recommendation of Referee B, we removed ``to ensure the applicability of the DVCS handbag diagram'' and changed ``avoid'' to ``avoids'' at the end of page 3.}
+   \item{ The figures have been adjusted to meet the maximum allowed length requirement.}   
 \end{itemize}

### 2019-06-19 eg6-letters/incoherent/journal-proof/proof_cover1/journal_proof1.tex
add journal proof 1

%\documentclass[a4paper,11pt,twoside]{ThesisStyle}
\documentclass[a4paper,11pt,twoside]{article}

\title{First Journal proof on Article LZ15969)}

\date{\today}
\include{formatAndDefs}

\begin{document}

\maketitle

\begin{enumerate}
   \item  PRL prefers to refer to the current article as ``Letter.'' Please 
      indicate when terms such as ``study'' and/or ``work'' can be changed to 
      ``Letter'' throughout the article or when the terms ``study'' and 
      ``work'' refer to the larger body of research behind the Letter.

   \item Journal style dictates that acronyms not appear in the abstract unless 
   they occur more than once.

\item Copyediting changes have been made to your article to conform to APS 
   style and improve readability. Please check to make sure changes have not 
      altered your intended meaning.

\item Please supply a definition for ``EMC'' as it is not on our list of 
   acronyms not needing definition. Journal style dictates that acronyms be 
      defined at their first occurrence in the body of the article.

   \item Please check the sentence beginning ``The previous measurements of 
      DVCS...'' to be sure your meaning has not been changed.

\item Please note the change to outer square brackets throughout the article to 
   avoid nested fences of the same size and type per PRL style.

      \item Please check all equations carefully to be sure errors were not 
         introduced during conversion.

      \item Please supply a definition for ``PDF'' as it is not on our list of 
         acronyms not needing to be defined and there is more than one possible 
         definition. Journal style dictates that acronyms used only once in the 
         body of the article be spelled out and the acronym deleted.

\item Journal style dictates that full words, abbreviations, and acronyms with 
   more than one letter appearing in the inferior or superior positions be set 
      roman.

\item PRL prefers italic font for single-letter acronyms and single-letter 
   variables and abbreviations in text and in math.

\item Please review the funding information section of the proof's cover letter 
   and respond as appropriate. We must receive confirmation that the funding 
      agencies have been properly identified before the article can publish.

\item This query was generated by an automatic reference checking system.  
   Reference [18] could not be located in the databases used by the system.  
      While the references may be correct, we ask that you check them so we can 
      provide as many links to the referenced articles as possible.

\item NOTE: External links, which appear as blue text in the reference section, 
   are created for any reference where a Digital Object Identifier (DOI) can be 
      found. Please confirm that the links created in this PDF proof, which can 
      be checked by clicking on the blue text, direct the reader to the correct 
      references online. If there is an error, correct the information in the 
      reference or supply the correct DOI for the reference. If no correction 
      can be made or the correct DOI cannot be supplied, the link will be 
      removed.

   \item  APS now requires that journal references with authors numbering 10 or 
      fewer display all author names. Please verify author names in expanded 
      author list for Ref. [8].

\item Please provide publication information for Ref. [41] if available.

\end{enumerate}

\end{document}

### 2019-06-19 eg6-letters/incoherent/journal-proof/proof_cover1/journal_proof1.tex
added the response to the 1st proof

@@
 
-\title{First Journal proof on Article LZ15969)}
+\title{First Journal proof on Article LZ15969}
 
@@
       ``Letter'' throughout the article or when the terms ``study'' and 
-      ``work'' refer to the larger body of research behind the Letter.
+      ``work'' refer to the larger body of research behind the Letter.\\
+      \textcolor{blue}{Response: the word ``work'' can be changed to ``Letter'' 
+      in Line 73. We prefere to keep the word ``work'' as it is in F5:2. }
 
    \item Journal style dictates that acronyms not appear in the abstract unless 
-   they occur more than once.
+      they occur more than once.\\
+      \textcolor{blue}{Response: We are fine with this edit, i.e., removing 
+      ``DVCS'' acronym. }
 
@@
    style and improve readability. Please check to make sure changes have not 
-      altered your intended meaning.
+      altered your intended meaning.\\
+      \textcolor{blue}{Response: Everything looks good. }
 
@@
    acronyms not needing definition. Journal style dictates that acronyms be 
-      defined at their first occurrence in the body of the article.
+      defined at their first occurrence in the body of the article.\\
+      \textcolor{blue}{Response: ``EMC'' stands for ``European Muon 
+      Collaboration'' }
 
    \item Please check the sentence beginning ``The previous measurements of 
-      DVCS...'' to be sure your meaning has not been changed.
+      DVCS...'' to be sure your meaning has not been changed.\\
+      \textcolor{blue}{Response: your edit of adding ``they are'' to this 
+      sentence is fine for us. Nothing has been changed in terms of the 
+      meaning. }
 
 \item Please note the change to outer square brackets throughout the article to 
-   avoid nested fences of the same size and type per PRL style.
+   avoid nested fences of the same size and type per PRL style.\\
+      \textcolor{blue}{Response: Everything looks good on this aspect. }
 
       \item Please check all equations carefully to be sure errors were not 
-         introduced during conversion.
+         introduced during conversion.\\
+      \textcolor{blue}{Response: The equations are fine.}
 
@@
          definition. Journal style dictates that acronyms used only once in the 
-         body of the article be spelled out and the acronym deleted.
+         body of the article be spelled out and the acronym deleted.\\
+      \textcolor{blue}{Response: ``PDFs'' stands for ``parton distribution 
+      functions'' }
 
@@
    more than one letter appearing in the inferior or superior positions be set 
-      roman.
+      roman.\\
+      \textcolor{blue}{Response: We are fine with this modification of 
+      $t_{min}$.}
 
 \item PRL prefers italic font for single-letter acronyms and single-letter 
-   variables and abbreviations in text and in math.
+   variables and abbreviations in text and in math.\\
+      \textcolor{blue}{Response: We are find with this change of ``k'' }
 
@@
    and respond as appropriate. We must receive confirmation that the funding 
-      agencies have been properly identified before the article can publish.
+      agencies have been properly identified before the article can publish.\\
+      \textcolor{blue}{Response: The funding agencies are properly identified.  
+      }
 
@@
       While the references may be correct, we ask that you check them so we can 
-      provide as many links to the referenced articles as possible.
+      provide as many links to the referenced articles as possible.\\  
+      \textcolor{blue}{Response: These are some links to the paper:\\
+     DOI:10.1140/epjc/s2005-02345-3\\        arXiv:hep-ex/0505061}
 
@@
       can be made or the correct DOI cannot be supplied, the link will be 
-      removed.
+      removed.\\
+      \textcolor{blue}{Response: All the links are working fine. }
 
@@
       fewer display all author names. Please verify author names in expanded 
-      author list for Ref. [8].
+      author list for Ref. [8].\\
+      \textcolor{blue}{Response: The full author list is correct.}
 
-\item Please provide publication information for Ref. [41] if available.
+\item Please provide publication information for Ref. [41] if available.\\
+      \textcolor{blue}{Response: We can provide this direct link to this 
+      reference \url{https://tel.archives-ouvertes.fr/tel-01218756/document}}
 

### 2019-06-25 eg6-letters/incoherent/journal-proof/proof_cover2/authors_response_journal_proof2.tex
add the response to the second proof

%\documentclass[a4paper,11pt,twoside]{ThesisStyle}
\documentclass[a4paper,11pt,twoside]{article}

\title{Second Journal proof on Article LZ15969}

\date{\today}
\include{formatAndDefs}

\begin{document}

\maketitle

\begin{enumerate}

\item Second Proof: Please check and confirm the edit made in the sentence 
   ``With nuclear targets, deeply inelastic lepton scattering
...''\\
   \textcolor{blue}{Response: We are fine with adding ``European Muon 
      Collaboration (EMC) effect'' at the end of the sentence.}

\item  Second Proof: Please carefully confirm that all first-proof corrections 
   were addressed and that changes were made accurately. \\
   \textcolor{blue}{Response: Everything is well implemented.    }

\item Second Proof: Please confirm the paper is now ready to be published in 
   its current form.\\  \textcolor{blue}{Response: Everything looks fine except 
      reference 41. Right click on the link somehow does not open the link 
      right away. We confirm that the link 
      \url{https://tel.archives-ouvertes.fr/tel-01218756/document} is right.  }

\end{enumerate}

\end{document}

### 2019-07-09 eg6-letters/incoherent/journal-proof/proof_cover3/authors_response_journal_proof3.tex
Add the third proofs for the incoherent paper

%\documentclass[a4paper,11pt,twoside]{ThesisStyle}
\documentclass[a4paper,11pt,twoside]{article}

\title{Third Journal proof on Article LZ15969}

\date{\today}
\include{formatAndDefs}

\begin{document}

\maketitle

\begin{enumerate}

\item Third proof: Please check very closely to confirm all of the corrections have been incorporated properly throughout this
Letter and also approve the Letter is ready to be published in its current form.\\
   \textcolor{blue}{Response: See next.}

\item Third proof: Kindly check and confirm whether the URL is now working. \\
   \textcolor{blue}{Response: The link does not appear to be working.}

\end{enumerate}

\end{document}

### 2019-10-10 eg6-letters/long-paper/prc-dvcshelium.tex
updated the acknowledgments of the NIM paper
Long paper is in. Needs clean up and latex compatibility

@@
 \documentclass[aps,prc,preprint,superscriptaddress]{revtex4}
+%\usepackage{amsmath,amssymb}             % AMS Math
+%\usepackage[francais]{babel}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage{lmodern,textcomp}
+%\usepackage[left=3.5cm,right=2.5cm,top=2cm,bottom=2cm,includefoot,includehead,headheight=15pt]{geometry}
+\usepackage{setspace}
+\usepackage{microtype}
+\usepackage{epigraph}
+\usepackage{lineno}
+%\usepackage[scaled]{helvet}
+%\usepackage[pagebackref,hyperindex=true]{hyperref}
+%\usepackage{pdfpages}
+\usepackage{graphicx}
+\usepackage{array}
 
@@
 H_A$, leading the way toward 3D imaging of the partonic structure of nuclei.
-
 \end{abstract}
@@
 
-  \subsection{Incoherent Nuclear DVCS}
+\subsection{Coherent nuclear DVCS}
 
-  \subsection{Coherent Nuclear DVCS}
+The reaction measured in the experiment is the coherent electro-production of a photon on helium
+$e+^4\!\!He \rightarrow e+\gamma+^4\!\!He$ at high 4-momentum transfer squared ($Q^2$). The leading order diagrams
+of this reaction are the coherent DVCS and BH processes. The nuclear coherent DVCS is 
+represented in Fig. \ref{fig:CohDiag}. As was detailed in the Chap. \ref{chap:pheno}, 
+the two processes interfere at the amplitude level, which give rise to sizable spin asymmetries.
+In our experiment, we focused on the measurement of the beam-spin asymmetry (BSA) noted $A_{LU}$ with 
+$L$ for the longitudinally-polarized electron beam and $U$ the unpolarized target and defined as:  
+\begin{equation}
+A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
+              {d^{5}\sigma^{+} + d^{5}\sigma^{-}},
+  \label{eq:BSA}
+\end{equation}
+where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the differential cross section for a positive 
+(negative) beam helicity. At leading order and leading twist, the BSA can be expressed as:        
+\begin{eqnarray}
+A_{LU}& =& \frac{x_A(1+\epsilon^2)^2}{y} \, s_1^{INT} \sin(\phi) \, 
+\bigg/ \, \bigg[ \, \sum_{n=0}^{n=2}c_n^{BH}\cos{(n\phi)} +  \\
+& & \frac{x_A^2 t {(1+\epsilon^2)}^2}{Q^2} P_1(\phi) P_2(\phi) \, c_0^{DVCS} + 
+\frac{x_A (1+\epsilon^2)^2}{y} \sum_{n=0}^{n=1} c_n^{INT} \cos{(n\phi)} \bigg].  \nonumber 
+\label{eq:coh_BSA}
+\end{eqnarray}
+where $\mathcal{P}_1(\phi)$ and $\mathcal {P}_2(\phi)$ are the BH 
+propagators. The factors: $c_{0,1,2}^{BH}$, $c_0^{DVCS}$, $c_{0,1}^{INT}$ and 
+$s_1^{INT}$ are the Fourier coefficients of the BH, the DVCS and the 
+interference amplitudes for a spin-zero target \cite{Kirchner:2003wt}. %The explicit 
+%expressions of these coefficients can be found in Appendix 
+%\ref{app:Helium_cross_section}.
 
-\section{The E08-024 Experiment}
+\begin{figure}[tbp!]
+\center
+\includegraphics[width=9cm]{fig3/DVCS_diagram.pdf}
+\caption{Diagram representing the coherent nuclear DVCS.}
+\label{fig:CohDiag}
+\end{figure}
+%TODO fix delta
 
-  \subsection{The CLAS DVCS Setting}
+This formula can be expressed in a simplified manner for a spin-0 target as \cite{Belitsky:2008bz}:
+\begin{equation}
+A_{LU}(\phi) = \frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
+{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
+\big( 
+\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
+\label{eq:A_LU-coh}
+\end{equation}
+where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
+and real parts of the CFF $\mathcal{H}_{A}$ associated to the GPD $H_A$ of the 
+spin-0 nucleus. The 
+$\alpha_{i}$ factors are $\phi$-dependent kinematical terms that depend on the 
+nuclear form factor $F_A$ and the independent variables $Q^2$, $x$ and $t$.  
+These factors have the following simplified expressions:
+%\small
+\begin{eqnarray}
+	\label{eq:alpha1}
+   \alpha_0 (\phi) & = &\frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi)\\
+    \alpha_1 (\phi) & = & c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi)\\ 
+   \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
+C_{++}(1) cos(\phi) \right)\\
+\alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
+{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
+\epsilon^2},
+	\label{eq:alpha4}
+\end{eqnarray}
+%\normalsize
+where $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
+leptonic tensor \cite{Belitsky:2008bz} and $x_{A} = \frac{M_{p}\cdot x}{M_{^4\!He}}$. 
+%Their explicit expressions can be found in Appendix 
+%\ref{app:Helium_cross_section}.
 
-  \subsection{The Radial Time Projection Chamber}
+The Eq. \ref{eq:A_LU-coh} is particularly convenient to perform an extraction of 
+the $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ through a fit of the BSA as 
+a function of $\phi$. As can be seen in Fig. \ref{fig:alphas}, the form of each 
+$\alpha$ coefficient is known and characteristic, such that a fit is easy. The only caveat
+is the large difference of magnitude between the $\alpha$ factors, which will lead to 
+rather different error propagation for the two parts of the CFF.
 
-\section{Data Analysis}
+\begin{figure}[tbp!]
+\center
+\includegraphics[width=8cm]{fig3/AlphaCoefs.png}
+	\caption{Coefficients presented in Eq. \ref{eq:alpha1} to \ref{eq:alpha4}.
+	Note the prescaling factors used for $\alpha_0$, $\alpha_2$ and $\alpha_3$.}
+\label{fig:alphas}
+\end{figure}
 
-  \subsection{Particle Identification}
+\subsection{Incoherent nuclear DVCS}
 
-  \subsection{Monte-Carlo Simulation}
+The incoherent nuclear DVCS process, is the DVCS off a bound nucleon in a nucleus
+as represented in Fig. \ref{fig:InCohDiag} for an helium-4 target. The remnants of 
+the nucleus ($X$) contain only the missing three nucleons. 
+The theory for incoherent DVCS on the nucleon is largely based on the free proton theory
+already reviewed in Chap. \ref{chap:pheno}. Two important differences in the 
+reaction need to be accounted however, the different initial state and the addition of 
+final state effects. In the initial state, the intrinsic Fermi motion of the nucleons in the nucleus 
+lead to an uncertainty on the exact kinematic of the reaction. Moreover, in general the nucleon 
+is in an off-shell state that is not exactly identical to its final state. In the final state, 
+interactions between the outgoing nucleon from the DVCS reaction and remnants of the nuclear 
+target are possible, including possible charge exchange. The latter
+leading to contamination from other channels, in particular charge exchange can lead to
+large differences in this background.
 
-  \subsection{Kinematic Corrections}
+\begin{figure}[tbp!]
+\center
+\includegraphics[width=10cm]{fig3/handbag_incoherent.pdf}
+\caption{Diagram representing the incoherent nuclear DVCS.}
+\label{fig:InCohDiag}
+\end{figure}
 
-  \subsection{Background Reduction}
+Since, DVCS is a 
+process selected using tight exclusivity constrains, some of the initial and final-state effects are
+automatically mitigated. Selection criterion on missing energy and momentum are performed,
+constraining the range of initial Fermi motion and final interactions possible. However, no theoretical
+calculation is available to correct for the reminder of these effects yet. Since, modern calculations exist 
+for such effects in DIS \cite{Cosyn:2017ekf}, we can expect them to be extended to the DVCS 
+process as more data becomes available. Another avenue of progress
+on this topic will be the use of experimental techniques like tagging to control them. This process
+and how it can help with these issues will be discussed
+in details at the end of the present chapter.
 
-\section{Incoherent DVCS}
+\subsection{The HERMES nuclear DVCS measurements}
 
-  \subsection{Event Selection}
+The first measurement of nuclear DVCS has been performed by the HERMES collaboration 
+\cite{Airapetian:2009cga}.
+This experiment covered an array of nuclear target and looked at the $A$ dependence of the
+BSA signal. The results, presented in Fig. \ref{fig:HERMES1} and \ref{fig:HERMES2}, suffer
+from large error bars, which makes them consistent with the free proton data and prevents us to
+reach strong conclusions about the nuclear effect. Yet, in the coherent DVCS case a rather
+strong effect was expected, leading to a conflict between the HERMES results and theoretical
+expectations.
 
-  \subsection{Systematic Errors}
+\begin{figure}[tbp!]
+\center
+	\includegraphics[width=10.5cm]{fig3/HERMES_BSA.png}
+	\caption{The sinus moment of the BSA as a function of $-t$ measured by HERMES
+	on a series of nuclei \cite{Airapetian:2009cga}.}
+\label{fig:HERMES1}
+\end{figure}
 
-\section{Coherent DVCS}
+\begin{figure}[tbp!]
+\center
+\includegraphics[width=10cm]{fig3/HERMES_BSA_2.png}
+\caption{The sinus moment of the BSA at low and high $-t$ as a function of $A$ measured by HERMES
+	\cite{Airapetian:2009cga}.}
+\label{fig:HERMES2}
+\end{figure}
 
-  \subsection{Event Selection}
+An issue with the HERMES measurement and how it is obtained from data has been raised in
+\cite{Guzey:2003jh} to explain the discrepancy with theoretical expectations.
+The main concern is that the DVCS process is not fully detected and the scattered target
+is instead reconstructed through a missing mass measurement of the other reaction products. The 
+issue with this method is that the detector resolution is not good enough to separate the 
+coherent and incoherent channels. 
+Instead, the results are labeled "coherent enriched" and "incoherent enriched" at low and high 
+$-t$, respectively. This label is based on the assumption that the very different behavior of the
+cross sections of the two channels in $t$ will lead to a clear differentiation. However, the
+results in Fig. \ref{fig:HERMES2} show similar behaviors in both sectors of $t$, which is 
+challenging this assumption and could explain the tension between theory and experiment.
 
-  \subsection{Systematic Errors}
+Altogether, the large error bars and the impossibility to properly separate the coherent and 
+incoherent channels have strongly impaired the measurement and any conclusions that could be
+obtained from it. The CLAS experiment presented here has profited largely from this
+result and was designed specifically to solve these two issues of low statistics and exclusivity.
+
+\section{The CLAS nuclear DVCS experimental setup}
+
+The CLAS experiment had for main objective to explore the coherent DVCS on helium-4 and assess if
+the predicted BSA increase could be observed and if GPDs could be extracted from it. In order to
+perform this measurement however, several instrumentation challenges need to be passed. First, to
+measure the scattered electron and the low angle photon of the DVCS, for which we used CLAS in its 
+DVCS setup, $i.e.$ with the addition of a low angle calorimeter and a solenoid magnet. Second, the
+helium recoil need to be measured to ensure the exclusivity of the reaction. In this section, we 
+will rapidly describe the particular detector setup used in our experiment.
+
+\subsection{The CLAS detector}
+
+CLAS is installed in the hall B of the JLab main accelerator. It has for main objective to study the 
+multi-particles final states
+that cannot be reconstructed with arm spectrometers. Its historic use to measure DVCS in many different 
+configurations made it an ideal place for this new DVCS measurement.
+
+The CLAS spectrometer \cite{Mecking:2003zu} is composed of six identical radial 
+sectors separated by a toroidal magnet and each sector is made of four detectors 
+as shown in Fig. \ref{fig:CLAS}.  Three regions of drift chambers \cite{Mestayer:2000we} 
+are placed in the solenoid area to reconstruct the charge particle's tracks and 
+calculate their momentum. Then, an array of scintillators is placed to measure 
+a precise time for each track and perform time-of-flight measurement 
+\cite{Smith:1999ii}. These detectors cover the polar angle from 8 to 142 degrees. 
+This is completed by two important forward detectors, from 8 
+to 45 degrees for electron identification, a Cerenkov counter 
+\cite{Adams:2001kk} and an electromagnetic calorimeter \cite{Amarian:2001zs}.
+
+\begin{figure}[tbp!]
+\center
+\includegraphics[width=8cm]{fig3/CLAS_geantview-PS.jpg}
+	\caption{View of the CLAS detector setup.}
+\label{fig:CLAS}
+\end{figure}
+
+Altogether, CLAS provides a large acceptance of about $\pi$ steradians for momentums 
+starting at 200 MeV/c. During the nuclear DVCS experiment,
+the beam energy was maximal for CLAS with 6.064 GeV, while the beam intensity varied
+between 120 and 150 nA. Such beam on our helium-4 target pressurized between 5 and 6 atm,
+corresponds to luminosities in the range of $1$ to $1.2 \times 10^{34}$ cm$^{-2}$.s$^{-1}$.
+During the experiment, the data acquisition rate ran around 3 kHz with about 70\% live-time
+using an inclusive electron trigger.
+
+\subsection{Adaptations for DVCS}
+
+The CLAS collaboration has established a specific setup to measure the typically 
+low angle photons of the DVCS process. This setup is composed of an inner 
+calorimeter and a solenoid and has lead to numerous DVCS measurements on proton 
+targets \cite{Seder:2014cdc,Jo:2015ema,HirlingerSaylor:2018bnu}.
+
+The inner calorimeter, illustrated in Fig. \ref{fig:IC} is a homogeneous 
+calorimeter composed 424 lead tungstate 
+(PbWO) crystals read out by $5 \times 5$ mm$^2$ avalanche photo-diodes (APDs). 
+It covers angles from 4 to 15 degrees. However, placing a detector at such low angles makes it 
+particularly sensitive to the Moller electrons scattered at low angles.
+
+\begin{figure}[tbp!]
+\center
+\includegraphics[width=8cm]{fig3/IC-CLAS.png}
+	\caption{Representation of the inner calorimeter (IC) of CLAS. The crystals that compose the
+	sensitive part of the detector are represented in purple.}
+\label{fig:IC}
+\end{figure}
+
+To protect the calorimeter from the low energy background a 5~T solenoid is 
+placed around the target to form
+a magnetic shield. Thanks to this field, low energy charged particles (particularly 
+electrons) curl around the beam line 
+and never make it to the calorimeter or other CLAS detectors as illustrated 
+by simulation results presented 
+in Fig. \ref{fig:Solenoid}. This allows to run much higher luminosity experiments,
+a necessity for low rates processes like DVCS.
+
+\begin{figure}[tbp!]
+\center
+\includegraphics[width=14cm]{fig3/solenoid.png}
+\caption{Representation of the center of CLAS with the beam background in red with and without
+	the solenoid field activated, right and left, respectively.}
+\label{fig:Solenoid}
+\end{figure}
+
+\subsection{The Radial time projection chamber}
+
+The recoil helium nuclei from coherent DVCS are mostly emitted between 150 
+and 200 MeV/c at our beam energy. Therefore, a specific detector was 
+needed to detect them. To design the present setup, large inspiration was drawn from the 
+Bonus setup that also used a GEM based RTPC \cite{Fenker:2008zz}, installed in CLAS to 
+detect slow protons out of a deuterium target \cite{Baillie:2011za}. In such an RTPC the 
+charges are projected toward large radii 
+rather than towards the endcaps, as is more traditional in time 
+projection chambers. This design allows to reduce significantly the drift time and reduce the 
+amount of pile-up from accidental events. The RTPC has been described in more 
+details elsewhere \cite{Dupre:2017upj}, here is a summary of key elements.
+
+In order to detect the recoil helium nuclei from a DVCS reaction, we first need 
+to ensure that it will come out of the target. For this, we used a light straw 
+target made of a thin kapton wall of 27 $\mu$m filled with up to 6 atm of 
+helium. The entrance and exit windows are thin aluminum foils and an helium 
+bag is placed downstream of the target to avoid interaction with air in the gap 
+between the target and the beamline vacuum. The cylindrical 
+chamber surrounds the target as illustrated in Fig. \ref{fig:RTPCGlobal}, we 
+list the elements composing it based on their radii:
+\begin{itemize}
+	\item Up to a radius of 3 mm the pressurized helium target.
+	\item From 3 to 20 mm a keep-out zone filled with 1 atm of helium to 
+		minimize the production of secondaries. 
+	\item At 20 mm a grounded foil made of 4 $\mu$m aluminized Mylar to 
+		isolate the chamber from the beam line 
+		region and collect charges. It also serves to separate gas regions.
+	\item From 20 to 30 mm a dead zone to separate the ground from the cathode
+		filled with the drift gas, a mix of neon and dimethyl ether (DME) in 
+		80/20 proportions.
+	\item At 30 mm the cathode foil made of 4 $\mu$m aluminized Mylar.
+	\item From 30 to 60 mm the drift region filled with the drift gas.
+	\item From 60 to 69 mm the amplification regions, filled with drift gas, 
+		with GEM foils placed at 60, 63 and 66 mm.
+	\item At 69 mm the collection pads connected to the preamplifers placed 
+		directly outside the chamber.
+\end{itemize}
+
+\begin{figure}[tbp!]
+\center
+\includegraphics[width=10cm]{fig3/RTPC_new_1.png}
+\caption{Cut view of the RTPC.}
+\label{fig:RTPCGlobal}
+\end{figure}
+
+The calibration of the detector has been performed with a 
+dependence on $z$, the position along the beam line axis, due to 
+variations in the magnetic fields. To perform this calibration we took  
+dedicated data at 1.2 GeV beam energy. In 
+this data set, we were able to select elastic events, for which the kinematic 
+of the helium recoil can be calculated from the electron kinematic and 
+directly compared to the measurement in the RTPC. This comparison helped to 
+map the correspondence between time and position in the chamber and determine 
+the drift path of electrons. A more detailed description of the calibration process 
+is available in \cite{Dupre:2017upj}.
+
+\section{DVCS event selection}
+
+\subsection{Particle identification}
+
+The electrons are detected with the baseline CLAS detectors, the drift chamber measures the kinematic 
+of the electron and the large signal in both the Cerenkov counter and electromagnetic calorimeter
+provide the identification. A signal of good quality is also required in the 
+time-of-flight system, which serves as a time reference for other detectors. In particular, it 
+serves for the identification of the protons, which is based on a 
+time-of-flight measurement. Several 
+fiducial cuts are applied to ensure that particles did not go through part of the inner calorimeter 
+or the solenoid, as well as to reject the edges of the detectors, where efficiency is rapidly 
+decreasing. Kinematic corrections are also applied to the electrons and protons to correct for energy loss
+and biases in calibration, they are at subpercent level except for protons below 500 MeV/c for which they
+go up to 10\% at the detection limit of 200 MeV/c.
+
+The photons from DVCS are mainly detected with the inner calorimeter. No specific 
+identification cuts are used in this detector as large energy deposit are dominantly 
+from electrons and photons, which cannot be separated reliably. However, the detection 
+of an electron at larger angle in CLAS 
+highly suppresses the number of electrons in the calorimeter, moreover
+the exclusivity cuts used later in the analysis further this suppression. Left over accidentals, will be
+accounted for in the background subtraction. The inner calorimeter was calibrated through a series
+of steps, involving the reconstruction of $\pi^0$ from their two photons decay. Calibration was obtained 
+with an iterative process to adjust each crystal gain to obtain the most accurate $\pi^0$ mass. A
+global calibration of the calorimeter was also performed to account for incident angle, energy and 
+time dependent effects.
+
+Finally, we select events that contain a single electron, a high energy photon ($E>2$ GeV) and
+either a helium or a proton. We perform a vertex selection cut on the two charged particles 
+to ensure they originate from the same vertex, inside the target, thus rejecting target windows.
+Moreover, since we are aiming to study deep processes occurring at the partonic level, we select
+$Q^2>1$ GeV$^2$. Also, the transferred momentum squared to the recoil $^{4}He$ is bound by
+   a minimum value based on basic energy momentum conservation:
+\begin{equation}
+   t_{min} = - Q^{2} \frac{2(1- x_{A})(1 - \sqrt{1 + \epsilon ^{2}}) + \epsilon 
+   ^{2}}{4 x_{A}(1-x_{A})+ \epsilon ^{2}},\\
+\end{equation}
+where $\epsilon ^{2} = \frac{4M^{2}_{^4\!He}x^{2}_{A}}{Q^{2}}$. For incoherent DVCS, 
+$x_A$ is replaced by $x$ and $M_{^4\!He}$ by $M_{p}$.
+
+\subsection{Exclusive photo-production selection}
+
+To select exclusive events and suppress the backgrounds, we define several 
+exclusivity cuts based on energy and momentum conservation. In principle, 
+a selection based on two or three variables can be used to guaranty the 
+exclusivity of the process. However, in such experiment, where particles 
+are detected at very different energies and with very different detector 
+precision, we chose to over constrain the selection by using seven 
+variables. The seven variables are defined as follow for the coherent 
+DVCS (replace helium by proton for the incoherent case):
+\begin{itemize}
+	\item Co-planarity ($\Delta \phi$) of the virtual photon, the real photon and
+		the recoil helium, defined as the angle between the helium, virtual photon
+		plane and the virtual photon, real photon plane;
+	\item Missing energy of the full system;
+	\item Missing mass of the full system;
+	\item Missing transverse momentum of the full system;
+	\item Missing mass of the system electron-helium, ignoring the photon;
+	\item Missing mass of the system electron-photon, ignoring the recoil helium;
+	\item Co-linearity ($\theta$) of the measured photon with the missing momentum of the 
+		electron-helium system.
+\end{itemize}
+
+In the analysis, we apply selection cuts based on a fit of the exclusive peak at 3$\sigma$ around 
+the mean value for each variable. This automatic method helps to avoid any bias 
+in the selection of the events. The selection of coherent DVCS with these variables is illustrated in 
+Fig. \ref{fig:CohExcCuts}. We note on these distributions only few minor anomalies, where the 
+distribution have some asymmetries. These are linked with the detector resolutions, that impact
+differently the kinematic variables. The selection of incoherent DVCS is presented in 
+Fig. \ref{fig:IncExcCuts}, with two main differences: larger distributions overall and more
+offset distributions. The former is largely due to Fermi motion, but simulations have shown
+that this effect is not strong enough to reproduce these distribution widths and final 
+state interactions must play a role as well. The later is caused by slight detector 
+misalignment between CLAS sectors and are within the levels obtained with free proton 
+targets to which they can be directly compared (see \cite{HirlingerSaylor:2018bnu} for instance).
+
+\begin{figure}[tbp!]
+\center
+\includegraphics[trim=20 10 20 5,clip,width=15cm]{fig3/all_coh_exc_cuts.pdf}
+	\caption{Overlay of the events distributions before (black) and after (blue line filled
+	in Grey) the exclusivity cuts used to select coherent DVCS represented by the 
+	red dashed lines. The histograms are for the seven variables described in the text, 
+	plus the missing $P_x$ and $P_y$, in order left to right and top to bottom.}
+\label{fig:CohExcCuts}
+\end{figure}
+
+\begin{figure}[tbp!]
+\center
+\includegraphics[trim=20 10 20 5,clip,width=15cm]{fig3/all_incoh_exc_cuts.pdf}
+\caption{Overlay of the events distributions before (black) and after (blue line filled
+	in Grey) the exclusivity cuts used to select incoherent DVCS represented by the 
+	red dashed lines. The histograms are for the seven variables described in the text, 
+	plus the missing $P_x$ and $P_y$, in order left to right and top to bottom.}
+\label{fig:IncExcCuts}
+\end{figure}
+
+\subsection{Background subtraction}
+
+The final sample of events selected is still not free of backgrounds. The main contamination is 
+from the exclusive production of a $\pi^0$, the final state of which is very similar to DVCS with 
+only an extra photon. Therefore, if one of the photon is produced 
+at low energy, it is easy to confuse the two processes. In order to estimate the contribution from
+this channel, we detect it in the same way as DVCS, with a series of similar exclusivity cuts, completed
+by a selection on the invariant mass of the two photons. The events obtained for the coherent and incoherent
+channels are respectively shown in Fig. \ref{fig:CohPi0Simul} and \ref{fig:InCohPi0Simul}. From 
+this sample, we elaborated an event generator, which after being processed
+in the simulation of our detectors output the red histograms of Fig. \ref{fig:CohPi0Simul} and 
+\ref{fig:InCohPi0Simul}. To correct the experimental data, we estimate the number of single photon 
+events coming from DVCS with:
+\begin{equation}
+	N_{1\gamma,\pi^0}^{Exp} = \frac{N_{1\gamma,\pi^0}^{Sim}}{N_{2\gamma,\pi^0}^{Sim}} \times N_{2\gamma,\pi^0}^{Exp},\\
+\end{equation}
+where $N_{1\gamma,\pi^0}^{Sim}$ is the number of simulated exclusive $\pi^0$ mistaken for DVCS events,
+$N_{2\gamma,\pi^0}^{Sim}$ the number of simulated exclusive $\pi^0$ fully reconstructed and $N_{2\gamma,\pi^0}^{Exp}$
+the number of experimentally measured exclusive $\pi^0$. This number can then be subtracted to
+the experimental measurement of DVCS events ($N_{DVCS}^{Exp}$) to get the corrected result: 
+\begin{equation}
+	N_{DVCS}^{Corr} = N_{DVCS}^{Exp} - N_{1\gamma,\pi^0}^{Exp}.\\
+\end{equation}
+
+\begin{figure}[p]
+\center
+\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/xB_Coh_pi0.png}
+\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/Q2_Coh_pi0.png}
+\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/t_Coh_pi0.png}
+\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/phi_h_Coh_pi0.png}
+	\caption{The measured (filled blue) and simulated (red) distributions of
+	coherent exclusive $\pi^0$ production as a function of $x$, $Q^2$, $-t$ and $\phi$.}
+\label{fig:CohPi0Simul}
+\end{figure}
+
+\begin{figure}[p]
+\center
+\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/xB_InCoh_pi0.png}
+\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/Q2_InCoh_pi0.png}
+\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/t_InCoh_pi0.png}
+\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/phi_h_InCoh_pi0.png}
+	\caption{The measured (filled blue) and simulated (red) distributions of
+	incoherent exclusive $\pi^0$ production as a function of $x$, $Q^2$, $-t$ and $\phi$.}
+\label{fig:InCohPi0Simul}
+\end{figure}
+
+The $\pi^0$ contamination was found to be 2 to 4\% in the coherent channel and 3 to 17\% in the incoherent
+channel (with variations between bins). To make the correction on the DVCS BSA, we assume that
+the exclusive $\pi^0$ production has no such asymmetry. This has been checked with the exclusive 
+$\pi^0$ production data, for which no significant level of BSA has been measured.
+
+The second important source of background comes from accidentals. Despite the many exclusivity cuts, it is 
+possible to have particles from different events getting combining and pass all the cuts and get 
+into the data sample. To evaluate the number of such events, we invert the vertex selection 
+of the two charged 
+particles of the process, electron and helium (or proton in the incoherent case), and request that they
+are separate. We find 4.1\% of the coherent and 6.5\% of the incoherent samples are accidentals.
+
+\subsection{Systematic errors}
+
+To evaluate the systematic error of the measurement, we performed several specific studies. We 
+evaluated the impact of changing the exclusivity selection cuts by varying them from 1 to 5 $\sigma$. 
+We evaluated the impact of changing the binning in $\phi$ on the extraction of the beam-spin asymmetry
+at 90°. We used the spread of the beam polarization measurements during the run period to evaluate their 
+precision. We checked different methods to make the simulation of the exclusive $\pi^0$
+production to evaluate the 
+possible bias introduced by this correction. As radiative corrections are expected to be small
+for our process, we did not apply them, but associated an error of their expected size.
+These errors are summarized in Tab. \ref{Table:systematic_uncertainties}, with their respective 
+evaluated sizes. They are added quadratically for the total systematic error presented in the results.
+
+\begin{table}[tbp]
+\begin{center}
+	\begin{tabular}{|m{4cm}|m{2cm}<{\centering}|m{2.3cm}<{\centering}|m{3.7cm}<{\centering}|}
+\hline
+\bf Systematic source & \bf  Coherent channel  & \bf Incoherent channel & \bf Type of systematic 
+error\\
+\hline
+DVCS cuts & 8 $\%$ &  6 $\%$ & bin to bin\\
+\hline
+Data binning & 5.1$\%$ & 7.1$\%$ &bin to bin\\
+\hline
+Beam polarization &  3.5$\%$ &  3.5$\%$& Normalization\\
+\hline
+$\pi^0$ subtraction &  0.6$\%$ &  2.0$\%$ &bin to bin\\
+\hline
+%Beam charge asymmetry &  ~~~~~1.1$\%$&  ~~~~~1.1$\%$\\
+%\hline
+Radiative corrections &  0.1$\%$ & 0.1$\%$ & bin to bin\\
+\hline
+\textbf{Total} &  \textbf{10.1}$\%$ &   \textbf{10.1}$\%$ &bin to 
+bin\\
+\hline
+\end{tabular}
+\caption{The systematic uncertainties on the measured coherent and incoherent 
+beam-spin asymmetries at $\phi = 90^{\circ}$.}
+\label{Table:systematic_uncertainties}
+\end{center}
+\end{table}
+
+%TODO MAke sure acceptance ratio is indeed pi0
+
+As discussed above, the best way to define $t$ in the incoherent channel is not completely
+straightforward. As can be seen in the Fig. \ref{fig:InCohDiag}, 
+we can either use $t$ or $t^\prime$ ($= (p - p^\prime)^2$). In principle, the two are 
+identical, but experimentally we face some issues. The measurement of $t$ is less precise than
+$t^\prime$ because it involves the photon rather than charged particles. However, the 
+exact measurement of $t^\prime$ is impossible and one needs to assume a proton at rest
+in the initial state to calculate $t^\prime$. As it is not obvious which solution is best,
+we studied the difference between them by analyzing the data independently using the two 
+definitions. We found no significant difference between them, as is 
+illustrated in Fig. \ref{fig:ttpComp}. We use in our final results $t$,
+which is the correct definition.
+
+\begin{figure}[tbp!]
+\center
+\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_Q2_shortscenrario.pdf}
+\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_t_shortscenrario.pdf}
+%\includegraphics[width=7cm]{fig3/ALU_90_p_vs_x_shortscenrario.pdf}
+	\caption{The BSA at 90° ($A_{LU}^{Incoh} (90^\circ)$) as a
+	function of $Q^2$ and $-t$, using the photon based $t$ definition (empty red)
+	and the proton based $t^\prime$ definition (full black).}
+	%TODO we could remove HERMES and the models on these
+\label{fig:ttpComp}
+\end{figure}
 
@@
 
+\subsection{Coherent DVCS}
+
+In Fig. \ref{fig:CohALUphi}, we present the results for the BSA in the coherent DVCS channel. We 
+observe the dominant sinusoidal component typical of the DVCS BSA, but note also the large size 
+of the asymmetry, almost double than the one measured for the free proton \cite{Jo:2015ema}. This 
+predicted feature of nuclear DVCS \cite{Guzey:2003jh} is observed here for the first time, we
+can conclude that this measurement cleanly isolates the coherent DVCS process. The absence of 
+this feature in HERMES data and its clear observation here indicates that the recoil 
+detection is a strong help to isolate the effects of the coherent DVCS process from backgrounds.
+
+\begin{figure}[bp!]
+\center
+\includegraphics[width=12cm]{fig3/Coherent_ALU_phi.pdf}
+	\caption{The BSA in the coherent exclusive photo-production off helium-4 as a 
+	function of $\phi$ and $Q^2$ 
+	(top panels), $x$ (middle panels) and $-t$ (lower panels). Error bars are  
+	statistical, Grey bands represent the systematic errors. The data is fitted with Eq. 
+	\ref{eq:A_LU-coh}, the results of these fits are drawn with red full lines.}
+\label{fig:CohALUphi}
+\end{figure}
+
+\begin{figure}[tbp]
+\center
+\includegraphics[width=10cm]{fig3/Coherent_ALU_phi_90.pdf}
+\caption{The BSA at 90° as a function of $Q^2$ (top panel), $x$ (middle panel) and $-t$ (lower panel).
+	Our results are shown with black squares, HERMES results 
+	with green circles \cite{Airapetian:2009cga} and theoretical predictions 
+	from \cite{Liuti:2005gi} with full and dashed lines.}
+\label{fig:CohALU90}
+\end{figure}
+
+In order to compare to models, we extract the BSA at 90° in Fig. \ref{fig:CohALU90}. The model 
+compared to the data \cite{Liuti:2005gi} is based on the idea that the main nuclear effects are 
+included by accounting for the nucleon off-shellness and kinematics in nuclei with a nuclear
+spectral function. It appears that the model undershoot our results systematically. However, 
+a more recent calculation, using similar principles but with a more advanced nuclear spectral 
+function \cite{Fucini:2018gso} has been able to reproduce the data very well. This 
+sort of theoretical model, also able to describe the EMC effect, is the only one which has 
+been confronted to this data yet. We observe that reproducing these data is not 
+straightforward and necessitates an advanced nuclear model.
+
+% TODO add footnote
+%\footnote{We actually show here the opposite of HERMES results, as the HERMES 
+%experiment ran with a positron beam, which lead to opposite BSAs.}
+%TODO Add Sergio's results there
+
+One of the promise of the helium-4 DVCS was the expected ease to extract the CFF $\mathcal{H}_A$ from
+data. To do so, we used the form from Eq. \ref{eq:A_LU-coh} to fit the data from Fig. 
+\ref{fig:CohALUphi}. We obtained the real and imaginary parts of the unique helium-4
+CFF presented in Fig. \ref{fig:CohCFF}. The results are rather encouraging, the two parts
+of the CFF are constrained by data without need of any model. This capacity to obtain a
+model independent result with such a limited data set offers a striking contrast with the
+situation of the free proton fits described in Chap. \ref{chap:pheno}.
+
+\begin{figure}[tbp!]
+\center
+\includegraphics[width=14cm]{fig3/Coherent_CFF.pdf}
+	\caption{The imaginary (top panels) and real (bottom panels) parts of the helium-4
+	CFF $\mathcal{H}_A$ as a function of $Q^2$ (left panels), $x$ (middle panels) and 
+	$-t$ (right panels). The red full line red is the theoretical calculation from 
+	\cite{Guzey:2003jh,Guzey:2008th}, the black dashed line is the same calculation 
+	using the VGG model as input \cite{Vanderhaeghen:1999xj,Guidal:2004nd}, and
+	the blue dashed line is a calculation from \cite{GonzalezHernandez:2012jv}.} 
+	%TODO change model names description
+\label{fig:CohCFF}
+\end{figure}
+
+The CFF extraction allows us to compare the results to other theoretical calculations.
+The calculation within the impulse approximation from \cite{Guzey:2003jh,Guzey:2008th} 
+gives the nuclear GPD directly
+from the proton and neutron GPDs, such that it allows to test the effect of different 
+nucleon's GPD models. In Fig. \ref{fig:CohCFF}, we can see that the effect of such a change of 
+GPD model is of similar size or larger than the difference with another nuclear 
+model \cite{GonzalezHernandez:2012jv}. However, at the level of precision of the present data,
+it is not possible to resolve which variant is best. This feature still highlights the 
+importance to try different nucleon models when evaluating a feature of the data.
+
+This measurement of the BSA in the deeply virtual coherent exclusive photo-production on a nucleus
+is the first to clearly isolate the effect of coherent nuclear DVCS and of nuclear GPDs. While, the
+statistical precision and the kinematic coverage are still far behind the experimental results on
+proton target, the results appear to match very well the predictions using the GPD framework. It 
+validates the relevance of the nuclear DVCS to study the nucleus globally in terms of quarks and 
+gluons, bypassing any intermediate degree of freedom like the nucleons.
+
 \subsection{Incoherent DVCS}
 
-  \subsection{Coherent DVCS}
+\begin{figure}[bp!]
+\center
+\includegraphics[width=15cm]{fig3/incoherent_ALU_phi.pdf}
+	\caption{The BSA in the incoherent exclusive photo-production off a proton bound in
+	helium-4 as a function of $\phi$ and $Q^2$ 
+	(top panels), $x$ (middle panels) and $-t$ (lower panels). Error bars are  
+	statistical, Grey bands represent the systematic errors. The data is fitted with the 
+	form $\frac{\alpha \sin(\phi)}{1+\beta \cos(\phi)}$; the results of the 
+	fits are drawn with black full lines.}
+\label{fig:InCohALUphi}
+\end{figure}
+
+The results for the measurement of the BSA in the incoherent DVCS channel are presented in
+Fig. \ref{fig:InCohALUphi}. They display patterns rather similar to the one observed with the 
+free proton, with a clear domination of their sinusoidal component. To compare the data to 
+models, we extract the BSA at 90° with a fit of the form $\frac{\alpha \sin(\phi)}{1+\beta \cos(\phi)}$.
+
+The asymmetries at 90° are presented in Fig. \ref{fig:IncALU} together with the theoretical
+calculation presented also in Fig. \ref{fig:CohALU90}. The results are much more precise than 
+the existing HERMES data and offer a strong constraint on the model presented. As in the
+coherent case, the calculation appears to have issues to reproduce the shape of the data.
+However, this time the calculation overshoots the data, sometimes by a significant amount.
+An interesting way to look into this issue is to show the result on incoherent DVCS compared 
+with the free proton. We can for instance make a ratio, in a fashion similar to the EMC 
+effect, which allows to cancel out
+the effects from the nucleon structure and highlight nuclear effects. Such ratio is presented
+in Fig. \ref{fig:IncRatios}, where we observe again that most models overshoot the data.
+
+\begin{figure}[tbp!]
+\center
+\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_Q2_shortscenrario.png}
+\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_t_shortscenrario.png}
+\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_x_shortscenrario.png}
+	\caption{The BSA at 90° as a function of  $Q^2$ (top left), $x$ (top right) and 
+	$-t$ (bottom). Our measurement is represented with black squares, HERMES 
+	measurement \cite{Airapetian:2009cga} with green circles and the theoretical 
+	calculation from \cite{Liuti:2005gi} with full lines.}
+\label{fig:IncALU}
+\end{figure}
+
+\begin{figure}[tbp!]
+\center
+\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_Q2_shortscenrario.png}
+\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_t_shortscenrario.png}
+\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_x_shortscenrario.png}
+	\caption{DVCS BSA ratio of the bound proton to the free proton as a function of 
+	$Q^2$ (top left), $x$ (top right) and $-t$ (bottom). The present measurement is 
+	represented with black squares, HERMES 
+	measurement \cite{Airapetian:2009cga} with green circles, the theoretical 
+	calculation from \cite{Liuti:2005gi} with blue and red full lines and the
+	calculation from \cite{Guzey:2008fe} with full and dashed black lines.}
+\label{fig:IncRatios}
+\end{figure}
+
+This measurement of the incoherent DVCS BSA shows a global tendency of the experimental data 
+to be smaller than expected from theoretical calculations. We observe the incoherent DVCS 
+BSA to go as low as 60\% of the size of the BSA observed
+on the free proton. This drastic reduction is still unexplained, though some theoretical 
+work has been recently published to prolong the calculation from \cite{Fucini:2018gso} to the incoherent 
+channel \cite{Fucini:2019xlc}. The explanation for this surprising behavior can come from different sources
+both in the initial state and the final state.
 

### 2020-01-05 eg6-letters/long-paper/prc-dvcshelium.tex

@@
 
+The theory of GPDs has been already reviewed in details in various 
+publications~\cite{Diehl:2003ny,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya},
+we summarized here only necessary elements to discuss our experimental results.
+we obtain real structure functions 
+$F^{q}(x,\xi,t)$, where $x+\xi$ and $x-\xi$ are the incoming and outgoing quark momenta 
+respectively and $t=\Delta^2$ the squared transferred momentum to the target as illustrated in 
+Fig. \ref{fig:GPD}.
+
+\begin{figure}[tbp!]
+\center
+\includegraphics[width=10.0cm]{fig1/GPD.png}
+\caption{General representation for the GPDs of a nucleon represented by the triple lines and noted $N$.
+	Single lines can represent quarks or anti-quarks probed in the nucleon.}
+\label{fig:GPD}
+\end{figure}
+
+The different spin states possible lead to several independent GPDs for 
+any given hadron. The proper accounting of 
+the number of GPDs must be done with regard to the symmetries of the system.
+At leading order and leading twist, we find that there are $2(2J+1)^2$ GPDs for a particle of spin $J$, 
+$i.e.$ for a spin-0 hadron, like the helium-4 nucleus, we will
+have two GPDs, for a spin-1/2 hadron, like the proton, eight GPDs. Half of these involve a 
+parton helicity flip, they are called transversity GPDs and do not intervene 
+in the DVCS process.
+
+As mentioned above, DVCS is the main experimental access to GPDs. However, this process does not offer
+a full access to the GPDs and we only access them integrated over $x$, in the following form:
+\begin{equation}
+	\int^1 _{-1} dx F^{q}(x,\xi,t) \left [ {1 \over x - \xi - i \epsilon} 
+	                                   \mp {1 \over x + \xi - i \epsilon} \right]. 
+\end{equation}
+To account for this and simplify equations, we define the complex Compton form factors (CFF,
+noted with curved $\mathcal{F}$ for a given GPD $F$) for each GPD as follows:
+\begin{equation}
+	\Re e (\mathcal{F}(\xi,t)) = \sum _q e^2_q \mathcal{P} \int^1_{-1} dx F^{q}(x,\xi,t)
+	      \left [ {1 \over x - \xi} \mp {1 \over x + \xi} \right], 
+\end{equation}
+\begin{equation}
+	\Im m (\mathcal{F}(\xi,t)) = - \pi \sum _q e^2_q \left [ F^{q}(\xi,\xi,t) \mp F^{q}(-\xi,\xi,t) \right]. 
+\end{equation} 
+These are the quantities directly present in the DVCS cross sections. We note that they are summed over
+the different quark flavors present in the hadron, as the electromagnetic probe do not differentiate
+quark flavors. A similar situation exists for TCS and DVMP giving only a partial access to the GPDs. 
+The double DVCS is a special case and it retains the full
+dependence of the GPDs in three independent variables.
+
+Experimentally, another process is indistinguishable from the DVCS. This is the Bethe-Heitler (BH) 
+process in which % TODO add BH figure
+the final state photon is emitted by the scattering lepton rather than the hadron. In this case the 
+photon-hadron interaction is the same as in elastic scattering and therefore such process depends on the
+target FFs rather than its GPDs. The DVCS and BH processes are experimentally indistinguishable as they
+have identical final states, such that they interfere in the squared photo-production amplitude of the
+exclusive photo-production process:
+\begin{equation}
+	|T|^2 = |T_{DVCS}|^2 + |T_{BH}|^2 + T_{DVCS}^* T_{BH} + T_{DVCS}T_{BH}^*. 
+\end{equation}
+The interference terms increase significantly the cross section in specific parts of the phase space
+and lead to significant charge and spin asymmetries.
+
+Finally, we need to define our kinematics properly. We use the 
+conventions from Fig. \ref{fig:PhiAngle}. 
+In experiments, we generally use slightly different kinematic variables : 
+$-t = -(p_p-p_p^\prime)^2 = \Delta^2$ and 
+$x = {2\xi \over 1+\xi}$.
+
+\begin{figure}[tbp!]
+\center
+\includegraphics[width=9cm]{fig1/finalplane.png}
+	\caption{Illustration of the scattering (or leptonic) and production (or hadronic) planes
+	in the DVCS process.} %TODO upgrade to a figure with phi_S
+\label{fig:PhiAngle}
+\end{figure}
+
 \subsection{Coherent nuclear DVCS}
@@
 The reaction measured in the experiment is the coherent electro-production of a photon on helium
-$e+^4\!\!He \rightarrow e+\gamma+^4\!\!He$ at high 4-momentum transfer squared ($Q^2$). The leading order diagrams
+$e+^4\!\!He \rightarrow e+\gamma+^4\!\!He$ at high 4-momentum transfer squared ($Q^2$). The 
+leading order diagrams
 of this reaction are the coherent DVCS and BH processes. The nuclear coherent DVCS is 
-represented in Fig. \ref{fig:CohDiag}. As was detailed in the Chap. \ref{chap:pheno}, 
+represented in Fig. \ref{fig:CohDiag}. As  
 the two processes interfere at the amplitude level, which give rise to sizable spin asymmetries.

### 2020-01-08 eg6-letters/long-paper/prc-dvcshelium.tex
Add intro and refs (with an unresolved issue)

@@
 \section{Introduction}
+
+The developpement of the three dimensional structure functions to study the nucleon 
+in the past decades is the opportunity to revisit the quark structure of the nucleus
+with this new perspective. This new approach to the structure of the nucleus in terms 
+of quarks and gluons is particularly needed as it remains today the subject of numerous
+controvercies. Indeed, while much progress has been made in measuring the nuclear
+parton distribution functions (PDFs) and in particular the EMC effect \cite{}. The 
+observed shape of the distribution remains fundamentaly unexplained, in particular
+in the intermediate $x$ range, where are observed the anti-shadowing and the EMC 
+effects \cite{}.
+
+In particular, the generalized parton distributions (GPDs) can be probed through
+spin assymetries in the deeply virtual Compton scattering (DVCS) process in a very 
+convenient way. Moreover, on nuclear targets of spin-0, the extraction can be 
+simplified with the reduction of the number of GPDs. The measurement of the nuclear
+DVCS is however a challenging task, first attempts from the HERMES collaboration 
+\cite{} did not lead to important progress, but more recent measurements from the
+CLAS collaboration \cite{} have been much more promising. We extend in this article 
+the description of the nuclear DVCS CLAS experiment, detail the methods used for the
+measurement and publish for the first time the full results for each channel measured.
 
@@
 \begin{acknowledgments}
+	% Add Sergio and ERC!
  Put your acknowledgments here.
@@
 % Create the reference section using BibTeX:
-\bibliography{basename of .bib file}
+\bibliography{hadro.bib}
 

### 2020-01-08 eg6-letters/long-paper/source_files/InCoh/ALU_ratioInc_Q2_shortscenrario.C
add the source files for the incoherent/free protons asy ratios

@@ -1,0 +1,173 @@
+void ALU_ratioInc_Q2_shortscenrario()
+{
+//=========Macro generated from canvas: Can/DVCS Helium BoNuS
+//=========  (Fri Jul 19 14:29:28 2019) by ROOT version 6.14/04
+   TCanvas *Can = new TCanvas("Can", "DVCS Helium BoNuS",63,57,600,450);
+   gStyle->SetOptFit(1);
+   Can->SetHighLightColor(2);
+   Can->Range(-0.1818182,-0.4506493,4.363636,1.887013);
+   Can->SetFillColor(0);
+   Can->SetBorderMode(0);
+   Can->SetBorderSize(2);
+   Can->SetLeftMargin(0.15);
+   Can->SetRightMargin(0.08);
+   Can->SetTopMargin(0.08);
+   Can->SetBottomMargin(0.15);
+   Can->SetFrameBorderMode(0);
+   Can->SetFrameBorderMode(0);
+   
+   TH2F *HALU_RATIO_Q2__1 = new TH2F("HALU_RATIO_Q2__1","",100,0.5,4,100,-0.1,1.7);
+   HALU_RATIO_Q2__1->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   HALU_RATIO_Q2__1->SetLineColor(ci);
+   HALU_RATIO_Q2__1->GetXaxis()->SetTitle("Q^{2} [GeV^{2}]");
+   HALU_RATIO_Q2__1->GetXaxis()->CenterTitle(true);
+   HALU_RATIO_Q2__1->GetXaxis()->SetNdivisions(605);
+   HALU_RATIO_Q2__1->GetXaxis()->SetLabelFont(22);
+   HALU_RATIO_Q2__1->GetXaxis()->SetLabelSize(0.05);
+   HALU_RATIO_Q2__1->GetXaxis()->SetTitleSize(0.07);
+   HALU_RATIO_Q2__1->GetXaxis()->SetTitleFont(22);
+   HALU_RATIO_Q2__1->GetYaxis()->SetTitle("A_{LU}^{Incoh}/A_{LU}^{p}(90#circ)");
+   HALU_RATIO_Q2__1->GetYaxis()->CenterTitle(true);
+   HALU_RATIO_Q2__1->GetYaxis()->SetNdivisions(605);
[…]

### 2020-01-08 eg6-letters/long-paper/source_files/InCoh/ALU_ratioInc_t_shortscenrario.C

@@ -1,0 +1,500 @@
+void ALU_ratioInc_t_shortscenrario()
+{
+//=========Macro generated from canvas: Can_R_t/
+//=========  (Fri Jul 19 14:29:29 2019) by ROOT version 6.14/04
+   TCanvas *Can_R_t = new TCanvas("Can_R_t", "",63,57,600,450);
+   gStyle->SetOptFit(1);
+   Can_R_t->SetHighLightColor(2);
+   Can_R_t->Range(-0.2337662,-0.512987,1.324675,2.24026);
+   Can_R_t->SetFillColor(0);
+   Can_R_t->SetBorderMode(0);
+   Can_R_t->SetBorderSize(2);
+   Can_R_t->SetLeftMargin(0.15);
+   Can_R_t->SetRightMargin(0.08);
+   Can_R_t->SetTopMargin(0.08);
+   Can_R_t->SetBottomMargin(0.15);
+   Can_R_t->SetFrameBorderMode(0);
+   Can_R_t->SetFrameBorderMode(0);
+   
+   TH2F *HALU_RATIO_t__6 = new TH2F("HALU_RATIO_t__6","",100,0,1.2,100,-0.1,2.02);
+   HALU_RATIO_t__6->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   HALU_RATIO_t__6->SetLineColor(ci);
+   HALU_RATIO_t__6->GetXaxis()->SetTitle("-t [GeV^{2}]");
+   HALU_RATIO_t__6->GetXaxis()->CenterTitle(true);
+   HALU_RATIO_t__6->GetXaxis()->SetNdivisions(605);
+   HALU_RATIO_t__6->GetXaxis()->SetLabelFont(22);
+   HALU_RATIO_t__6->GetXaxis()->SetLabelSize(0.05);
+   HALU_RATIO_t__6->GetXaxis()->SetTitleSize(0.07);
+   HALU_RATIO_t__6->GetXaxis()->SetTitleFont(22);
+   HALU_RATIO_t__6->GetYaxis()->SetTitle("A_{LU}^{Incoh}/A_{LU}^{p} (90#circ)");
+   HALU_RATIO_t__6->GetYaxis()->CenterTitle(true);
+   HALU_RATIO_t__6->GetYaxis()->SetNdivisions(605);
+   HALU_RATIO_t__6->GetYaxis()->SetLabelFont(22);
[…]

### 2020-01-08 eg6-letters/long-paper/source_files/InCoh/ALU_ratioInc_x_shortscenrario.C

@@ -1,0 +1,484 @@
+void ALU_ratioInc_x_shortscenrario()
+{
+//=========Macro generated from canvas: Can_R_x/DVCS Helium BoNuS
+//=========  (Fri Jul 19 14:29:28 2019) by ROOT version 6.14/04
+   TCanvas *Can_R_x = new TCanvas("Can_R_x", "DVCS Helium BoNuS",63,57,600,450);
+   gStyle->SetOptFit(1);
+   Can_R_x->SetHighLightColor(2);
+   Can_R_x->Range(-0.1558442,-0.4506493,0.8831169,1.887013);
+   Can_R_x->SetFillColor(0);
+   Can_R_x->SetBorderMode(0);
+   Can_R_x->SetBorderSize(2);
+   Can_R_x->SetLeftMargin(0.15);
+   Can_R_x->SetRightMargin(0.08);
+   Can_R_x->SetTopMargin(0.08);
+   Can_R_x->SetBottomMargin(0.15);
+   Can_R_x->SetFrameBorderMode(0);
+   Can_R_x->SetFrameBorderMode(0);
+   
+   TH2F *HALU_RATIO_x__2 = new TH2F("HALU_RATIO_x__2","",100,0,0.8,100,-0.1,1.7);
+   HALU_RATIO_x__2->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   HALU_RATIO_x__2->SetLineColor(ci);
+   HALU_RATIO_x__2->GetXaxis()->SetTitle("x_{B}");
+   HALU_RATIO_x__2->GetXaxis()->CenterTitle(true);
+   HALU_RATIO_x__2->GetXaxis()->SetNdivisions(605);
+   HALU_RATIO_x__2->GetXaxis()->SetLabelFont(22);
+   HALU_RATIO_x__2->GetXaxis()->SetLabelSize(0.05);
+   HALU_RATIO_x__2->GetXaxis()->SetTitleSize(0.07);
+   HALU_RATIO_x__2->GetXaxis()->SetTitleFont(22);
+   HALU_RATIO_x__2->GetYaxis()->SetTitle("A_{LU}^{Incoh}/A_{LU}^{p} (90#circ)");
+   HALU_RATIO_x__2->GetYaxis()->CenterTitle(true);
+   HALU_RATIO_x__2->GetYaxis()->SetNdivisions(605);
[…]

### 2020-01-08 eg6-letters/long-paper/source_files/InCoh/ALU_90_p_vs_x_shortscenrario.C
add the incoherent 90 asy figures source files

@@ -1,0 +1,321 @@
+void ALU_90_p_vs_x_shortscenrario()
+{
+//=========Macro generated from canvas: Can_p_x/DVCS Helium BoNuS
+//=========  (Thu May 23 14:35:04 2019) by ROOT version 6.14/04
+   TCanvas *Can_p_x = new TCanvas("Can_p_x", "DVCS Helium BoNuS",63,57,600,450);
+   gStyle->SetOptFit(1);
+   Can_p_x->SetHighLightColor(2);
+   Can_p_x->Range(-0.1363636,-0.2168831,0.7727273,0.5623377);
+   Can_p_x->SetFillColor(0);
+   Can_p_x->SetBorderMode(0);
+   Can_p_x->SetBorderSize(2);
+   Can_p_x->SetLeftMargin(0.15);
+   Can_p_x->SetRightMargin(0.08);
+   Can_p_x->SetTopMargin(0.08);
+   Can_p_x->SetBottomMargin(0.15);
+   Can_p_x->SetFrameBorderMode(0);
+   Can_p_x->SetFrameBorderMode(0);
+   
+   TH2F *HALU_p_vs_x__3 = new TH2F("HALU_p_vs_x__3","",100,0,0.7,100,-0.1,0.5);
+   HALU_p_vs_x__3->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   HALU_p_vs_x__3->SetLineColor(ci);
+   HALU_p_vs_x__3->GetXaxis()->SetTitle("x_{B}");
+   HALU_p_vs_x__3->GetXaxis()->CenterTitle(true);
+   HALU_p_vs_x__3->GetXaxis()->SetNdivisions(605);
+   HALU_p_vs_x__3->GetXaxis()->SetLabelFont(22);
+   HALU_p_vs_x__3->GetXaxis()->SetLabelSize(0.05);
+   HALU_p_vs_x__3->GetXaxis()->SetTitleSize(0.07);
+   HALU_p_vs_x__3->GetXaxis()->SetTitleFont(22);
+   HALU_p_vs_x__3->GetYaxis()->SetTitle("A_{LU}^{Incoh}(90#circ)");
+   HALU_p_vs_x__3->GetYaxis()->CenterTitle(true);
+   HALU_p_vs_x__3->GetYaxis()->SetNdivisions(605);
[…]

### 2020-01-08 eg6-letters/long-paper/source_files/Coh/Coherent_ALU_phi.C
add the coherent results source files, these need some work

@@ -1,0 +1,5407 @@
+void Coherent_ALU_phi()
+{
+//=========Macro generated from canvas: c12/
+//=========  (Wed Jan  8 16:10:15 2020) by ROOT version 6.14/04
+   TCanvas *c12 = new TCanvas("c12", "",63,57,1000,900);
+   gStyle->SetOptFit(1);
+   c12->Range(0,0,1,1);
+   c12->SetFillColor(0);
+   c12->SetBorderMode(0);
+   c12->SetBorderSize(2);
+   c12->SetLeftMargin(0.08333334);
+   c12->SetRightMargin(0.03278689);
+   c12->SetTopMargin(0.007102027);
+   c12->SetBottomMargin(0.08130082);
+   c12->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: c12_1
+   TPad *c12_1 = new TPad("c12_1", "_1",0,0.6890323,0.3779599,0.992898);
+   c12_1->Draw();
+   c12_1->cd();
+   c12_1->Range(-131.6667,-0.65,375,0.65);
+   c12_1->SetFillColor(0);
+   c12_1->SetBorderMode(0);
+   c12_1->SetBorderSize(2);
+   c12_1->SetLeftMargin(0.25);
+   c12_1->SetRightMargin(0);
+   c12_1->SetTopMargin(0);
+   c12_1->SetBottomMargin(0);
+   c12_1->SetFrameBorderMode(0);
+   c12_1->SetFrameBorderMode(0);
+   
+   TMultiGraph *multigraph = new TMultiGraph();
+   multigraph->SetName("");
+   multigraph->SetTitle("");
+   
+   Double_t Graph_fx1001[9] = {
+   24.3146,
+   61.16264,
+   98.9465,
+   140.9271,
+   178.4282,
+   219.1438,
+   262.95,
+   301.9212,
+   337.7335};
+   Double_t Graph_fy1001[9] = {
+   0.1327475,
+   0.3210551,
+   0.3709448,
+   0.2452102,
+   0.02256708,
+   -0.0526485,
+   -0.2642824,
+   -0.1761262,
+   -0.2791955};
+   Double_t Graph_fex1001[9] = {
+   0,
+   0,
+   0,
+   0,
+   0,
+   0,
+   0,
+   0,
+   0};
+   Double_t Graph_fey1001[9] = {
+   0.105757,
+   0.09132477,
+   0.09435479,
[…]

### 2020-01-08 eg6-letters/long-paper/source_files/Coh/Coherent_ALU_phi_90.C

@@ -1,0 +1,783 @@
+void Coherent_ALU_phi_90()
+{
+//=========Macro generated from canvas: Can/Helium DVCS
+//=========  (Wed Jan  8 16:10:15 2020) by ROOT version 6.14/04
+   TCanvas *Can = new TCanvas("Can", "Helium DVCS",63,57,1200,400);
+   gStyle->SetOptFit(1);
+   Can->Range(0,0,1,1);
+   Can->SetFillColor(0);
+   Can->SetBorderMode(0);
+   Can->SetBorderSize(2);
+   Can->SetLeftMargin(0.08333334);
+   Can->SetRightMargin(0.03278689);
+   Can->SetTopMargin(0.02576996);
+   Can->SetBottomMargin(0.2439024);
+   Can->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: Can_1
+   TPad *Can_1 = new TPad("Can_1", "Helium DVCS_1",0,0,0.3779599,0.97423);
+   Can_1->Draw();
+   Can_1->cd();
+   Can_1->Range(0.2666667,-0.3645161,2.6,0.72);
+   Can_1->SetFillColor(0);
+   Can_1->SetBorderMode(0);
+   Can_1->SetBorderSize(2);
+   Can_1->SetLeftMargin(0.25);
+   Can_1->SetRightMargin(0);
+   Can_1->SetTopMargin(0);
+   Can_1->SetBottomMargin(0.2439024);
+   Can_1->SetFrameBorderMode(0);
+   Can_1->SetFrameBorderMode(0);
+   
+   TH2F *HALU_He_vs_Q2__1 = new TH2F("HALU_He_vs_Q2__1","",100,0.85,2.6,100,-0.1,0.72);
+   HALU_He_vs_Q2__1->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   HALU_He_vs_Q2__1->SetLineColor(ci);
+   HALU_He_vs_Q2__1->GetXaxis()->SetTitle("Q^{2} [GeV^{2}]");
+   HALU_He_vs_Q2__1->GetXaxis()->CenterTitle(true);
+   HALU_He_vs_Q2__1->GetXaxis()->SetNdivisions(205);
+   HALU_He_vs_Q2__1->GetXaxis()->SetLabelFont(22);
[…]

### 2020-01-08 eg6-letters/long-paper/source_files/Coh/Coherent_ALU_ratio.C

@@ -1,0 +1,1219 @@
+void Coherent_ALU_ratio()
+{
+//=========Macro generated from canvas: Can_r/Helium DVCS
+//=========  (Wed Jan  8 16:10:15 2020) by ROOT version 6.14/04
+   TCanvas *Can_r = new TCanvas("Can_r", "Helium DVCS",63,57,1200,450);
+   gStyle->SetOptFit(1);
+   Can_r->Range(0,0,1,1);
+   Can_r->SetFillColor(0);
+   Can_r->SetBorderMode(0);
+   Can_r->SetBorderSize(2);
+   Can_r->SetLeftMargin(0.22);
+   Can_r->SetTopMargin(0.02);
+   Can_r->SetBottomMargin(0.2);
+   Can_r->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: Can_r_1
+   TPad *Can_r_1 = new TPad("Can_r_1", "Can_r_1",0.01,0.01,0.3233333,0.99);
+   Can_r_1->Draw();
+   Can_r_1->cd();
+   Can_r_1->Range(-0.3411765,-0.7487179,3.482353,3.994872);
+   Can_r_1->SetFillColor(0);
+   Can_r_1->SetBorderMode(0);
+   Can_r_1->SetBorderSize(2);
+   Can_r_1->SetLeftMargin(0.22);
+   Can_r_1->SetTopMargin(0.02);
+   Can_r_1->SetBottomMargin(0.2);
+   Can_r_1->SetFrameBorderMode(0);
+   Can_r_1->SetFrameBorderMode(0);
+   
+   TH2F *HALU_RATIO_Q2__4 = new TH2F("HALU_RATIO_Q2__4","",100,0.5,3.1,100,0.2,3.9);
+   HALU_RATIO_Q2__4->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   HALU_RATIO_Q2__4->SetLineColor(ci);
+   HALU_RATIO_Q2__4->GetXaxis()->SetTitle("Q^{2} [GeV^{2}]");
+   HALU_RATIO_Q2__4->GetXaxis()->CenterTitle(true);
+   HALU_RATIO_Q2__4->GetXaxis()->SetNdivisions(205);
[…]

### 2020-01-08 eg6-letters/long-paper/source_files/Coh/Coherent_CFF.C

@@ -1,0 +1,1352 @@
+void Coherent_CFF()
+{
+//=========Macro generated from canvas: cc/
+//=========  (Wed Jan  8 16:10:15 2020) by ROOT version 6.14/04
+   TCanvas *cc = new TCanvas("cc", "",63,81,1050,850);
+   gStyle->SetOptFit(1);
+   cc->Range(0,0,1,1);
+   cc->SetFillColor(0);
+   cc->SetBorderMode(0);
+   cc->SetBorderSize(2);
+   cc->SetLeftMargin(0.08333334);
+   cc->SetRightMargin(0.03278689);
+   cc->SetTopMargin(0.01113525);
+   cc->SetBottomMargin(0.1219512);
+   cc->SetFrameBorderMode(0);
+  
+// ------------>Primitives in pad: cc_1
+   TPad *cc_1 = new TPad("cc_1", "_1",0,0.555408,0.3779599,0.9888647);
+   cc_1->Draw();
+   cc_1->cd();
+   cc_1->Range(0.2666667,-2,2.6,78);
+   cc_1->SetFillColor(0);
+   cc_1->SetBorderMode(0);
+   cc_1->SetBorderSize(2);
+   cc_1->SetLeftMargin(0.25);
+   cc_1->SetRightMargin(0);
+   cc_1->SetTopMargin(0);
+   cc_1->SetBottomMargin(0);
+   cc_1->SetFrameBorderMode(0);
+   cc_1->SetFrameBorderMode(0);
+   
+   TMultiGraph *multigraph = new TMultiGraph();
+   multigraph->SetName("");
+   multigraph->SetTitle("");
+   
+   Double_t Graph_fx1082[3] = {
+   1.143,
+   1.423,
+   1.902};
+   Double_t Graph_fy1082[3] = {
+   30.21691,
+   25.13263,
+   13.14901};
+   Double_t Graph_fex1082[3] = {
+   0,
+   0,
+   0};
+   Double_t Graph_fey1082[3] = {
+   11.00217,
+   7.474222,
+   5.586008};
+   TGraphErrors *gre = new TGraphErrors(3,Graph_fx1082,Graph_fy1082,Graph_fex1082,Graph_fey1082);
+   gre->SetName("Graph");
+   gre->SetTitle("Graph");
+   gre->SetFillColor(1);
+   gre->SetFillStyle(1000);
+   gre->SetLineWidth(2);
[…]

### 2020-01-09 eg6-letters/long-paper/source_files/Coh/Coherent_ALU_phi.C
all the coherent plots source files are ready to be used for Raphael

@@ -1,5407 +1,0 @@
-void Coherent_ALU_phi()
-{
-//=========Macro generated from canvas: c12/
-//=========  (Wed Jan  8 16:10:15 2020) by ROOT version 6.14/04
-   TCanvas *c12 = new TCanvas("c12", "",63,57,1000,900);
-   gStyle->SetOptFit(1);
-   c12->Range(0,0,1,1);
-   c12->SetFillColor(0);
-   c12->SetBorderMode(0);
-   c12->SetBorderSize(2);
-   c12->SetLeftMargin(0.08333334);
-   c12->SetRightMargin(0.03278689);
-   c12->SetTopMargin(0.007102027);
-   c12->SetBottomMargin(0.08130082);
-   c12->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: c12_1
-   TPad *c12_1 = new TPad("c12_1", "_1",0,0.6890323,0.3779599,0.992898);
-   c12_1->Draw();
-   c12_1->cd();
-   c12_1->Range(-131.6667,-0.65,375,0.65);
-   c12_1->SetFillColor(0);
-   c12_1->SetBorderMode(0);
-   c12_1->SetBorderSize(2);
-   c12_1->SetLeftMargin(0.25);
-   c12_1->SetRightMargin(0);
-   c12_1->SetTopMargin(0);
-   c12_1->SetBottomMargin(0);
-   c12_1->SetFrameBorderMode(0);
-   c12_1->SetFrameBorderMode(0);
-   
-   TMultiGraph *multigraph = new TMultiGraph();
-   multigraph->SetName("");
-   multigraph->SetTitle("");
-   
-   Double_t Graph_fx1001[9] = {
-   24.3146,
-   61.16264,
-   98.9465,
-   140.9271,
-   178.4282,
-   219.1438,
-   262.95,
-   301.9212,
-   337.7335};
-   Double_t Graph_fy1001[9] = {
-   0.1327475,
-   0.3210551,
-   0.3709448,
-   0.2452102,
-   0.02256708,
-   -0.0526485,
-   -0.2642824,
-   -0.1761262,
-   -0.2791955};
-   Double_t Graph_fex1001[9] = {
-   0,
-   0,
-   0,
-   0,
-   0,
-   0,
-   0,
-   0,
-   0};
-   Double_t Graph_fey1001[9] = {
-   0.105757,
-   0.09132477,
-   0.09435479,
[…]

### 2020-01-09 eg6-letters/long-paper/source_files/Coh/Coherent_ALU_ratio.C

@@ -21,9 +21,10 @@ void Coherent_ALU_ratio()
    Can_r_1->SetFillColor(0);
    Can_r_1->SetBorderMode(0);
    Can_r_1->SetBorderSize(2);
-   Can_r_1->SetLeftMargin(0.22);
-   Can_r_1->SetTopMargin(0.02);
-   Can_r_1->SetBottomMargin(0.2);
+   Can_r_1->SetLeftMargin(0.18);
+   Can_r_1->SetRightMargin(0.04);
+   Can_r_1->SetTopMargin(0.0);
+   Can_r_1->SetBottomMargin(0.18);
    Can_r_1->SetFrameBorderMode(0);
    Can_r_1->SetFrameBorderMode(0);
    
@@ -39,16 +40,16 @@ void Coherent_ALU_ratio()
    HALU_RATIO_Q2__4->GetXaxis()->SetNdivisions(205);
    HALU_RATIO_Q2__4->GetXaxis()->SetLabelFont(22);
    HALU_RATIO_Q2__4->GetXaxis()->SetLabelSize(0.05);
-   HALU_RATIO_Q2__4->GetXaxis()->SetTitleSize(0.14);
-   HALU_RATIO_Q2__4->GetXaxis()->SetTitleOffset(1.5);
+   HALU_RATIO_Q2__4->GetXaxis()->SetTitleSize(0.07);
+   HALU_RATIO_Q2__4->GetXaxis()->SetTitleOffset(1.0);
    HALU_RATIO_Q2__4->GetXaxis()->SetTitleFont(22);
    HALU_RATIO_Q2__4->GetYaxis()->SetTitle("A_{LU}^{^{4}He}/A_{LU}^{p}(90^{#circ})");
    HALU_RATIO_Q2__4->GetYaxis()->CenterTitle(true);
    HALU_RATIO_Q2__4->GetYaxis()->SetNdivisions(511);
    HALU_RATIO_Q2__4->GetYaxis()->SetLabelFont(22);
    HALU_RATIO_Q2__4->GetYaxis()->SetLabelSize(0.05);
-   HALU_RATIO_Q2__4->GetYaxis()->SetTitleSize(0.14);
-   HALU_RATIO_Q2__4->GetYaxis()->SetTitleOffset(1.5);
+   HALU_RATIO_Q2__4->GetYaxis()->SetTitleSize(0.07);
[…]

### 2020-01-09 eg6-letters/long-paper/source_files/Coh/Coherent_CFF.C

@@ -89,16 +89,18 @@ void Coherent_CFF()
    multigraph->GetXaxis()->CenterTitle(true);
    multigraph->GetXaxis()->SetNdivisions(605);
    multigraph->GetXaxis()->SetLabelFont(22);
-   multigraph->GetXaxis()->SetLabelSize(0.07);
-   multigraph->GetXaxis()->SetTitleSize(0.128);
+   multigraph->GetXaxis()->SetLabelSize(0.08);
+   multigraph->GetXaxis()->SetTitleSize(0.14);
    multigraph->GetXaxis()->SetTitleFont(22);
    multigraph->GetYaxis()->SetTitle("#Jgothic(H_{A})");
    multigraph->GetYaxis()->CenterTitle(true);
    multigraph->GetYaxis()->SetLabelFont(22);
-   multigraph->GetYaxis()->SetLabelSize(0.07);
-   multigraph->GetYaxis()->SetTitleSize(0.128);
+   multigraph->GetYaxis()->SetLabelSize(0.08);
+   multigraph->GetYaxis()->SetTitleSize(0.14);
    multigraph->GetYaxis()->SetTitleOffset(0.8);
    multigraph->GetYaxis()->SetTitleFont(22);
+   multigraph->GetXaxis()->SetLimits(0.85,2.6);
+   multigraph->GetYaxis()->SetRangeUser(-2.0, 78.0);
    
    Double_t Graph0_fx10[21] = {
    1,
@@ -252,8 +254,8 @@ void Coherent_CFF()
    multigraph->GetXaxis()->CenterTitle(true);
    multigraph->GetXaxis()->SetNdivisions(605);
    multigraph->GetXaxis()->SetLabelFont(22);
-   multigraph->GetXaxis()->SetLabelSize(0.07);
-   multigraph->GetXaxis()->SetTitleSize(0.123);
+   multigraph->GetXaxis()->SetLabelSize(0.08);
+   multigraph->GetXaxis()->SetTitleSize(0.1);
    multigraph->GetXaxis()->SetTitleOffset(0.8);
    multigraph->GetXaxis()->SetTitleFont(22);
    multigraph->GetYaxis()->SetTitle("#Rgothic(H_{A})");
@@ -263,7 +265,10 @@ void Coherent_CFF()
    multigraph->GetYaxis()->SetTitleSize(0.123);
    multigraph->GetYaxis()->SetTitleOffset(0.8);
[…]

### 2020-01-09 eg6-letters/long-paper/source_files/Coh/Coherent_ALU_phi_90.C
Improve figs and add Fucini et al points

@@ -18,7 +18,7 @@ void Coherent_ALU_phi_90()
    TPad *Can_1 = new TPad("Can_1", "Helium DVCS_1",0,0,0.3779599,0.97423);
    Can_1->Draw();
    Can_1->cd();
-   Can_1->Range(0.2666667,-0.3645161,2.6,0.72);
+   Can_1->Range(0.2666667,-0.3645161,2.6,0.75);
    Can_1->SetFillColor(0);
    Can_1->SetBorderMode(0);
    Can_1->SetBorderSize(2);
@@ -29,7 +29,7 @@ void Coherent_ALU_phi_90()
    Can_1->SetFrameBorderMode(0);
    Can_1->SetFrameBorderMode(0);
    
-   TH2F *HALU_He_vs_Q2__1 = new TH2F("HALU_He_vs_Q2__1","",100,0.85,2.6,100,-0.1,0.72);
+   TH2F *HALU_He_vs_Q2__1 = new TH2F("HALU_He_vs_Q2__1","",100,0.94,2.2,100,-0.05,0.75);
    HALU_He_vs_Q2__1->SetStats(0);
 
    Int_t ci;      // for color index setting
@@ -78,7 +78,7 @@ void Coherent_ALU_phi_90()
    gre->SetTitle("This Work (<x_{B}>= 0.177, <-t> = 0.100)");
    gre->SetFillColor(1);
    gre->SetFillStyle(1000);
-   gre->SetLineWidth(3);
+   gre->SetLineWidth(2);
    gre->SetMarkerStyle(21);
    gre->SetMarkerSize(1.5);
    
@@ -107,6 +107,26 @@ void Coherent_ALU_phi_90()
    
    gre->Draw("p");
    
+   Double_t _sx21[3] = {
+   1.15,
+   1.42,
+   1.87};
+   Double_t _sy21[3] = {
+   0.279,
+   0.278,
+   0.275};
+
+   TGraph *graphS = new TGraph(3,_sx21,_sy21);
+   graphS->SetName("");
+   graphS->SetTitle("");
+   graphS->SetMarkerStyle(34);
+   graphS->SetMarkerSize(1.5);
+   graphS->SetMarkerColor(6);
+   graphS->SetLineStyle(9);
+   graphS->SetLineWidth(2);
+   graphS->SetLineColor(6);
+   graphS->Draw("l");
+
    Double_t _fx21[7] = {
    1,
    1,
@@ -154,7 +174,7 @@ void Coherent_ALU_phi_90()
    
[…]

### 2020-01-09 eg6-letters/long-paper/source_files/Coh/Coherent_CFF.C

@@ -2,7 +2,7 @@ void Coherent_CFF()
 {
 //=========Macro generated from canvas: cc/
 //=========  (Wed Jan  8 16:10:15 2020) by ROOT version 6.14/04
-   TCanvas *cc = new TCanvas("cc", "",63,81,1050,850);
+   TCanvas *cc = new TCanvas("cc", "",63,81,1050,600);
    gStyle->SetOptFit(1);
    cc->Range(0,0,1,1);
    cc->SetFillColor(0);
@@ -18,7 +18,7 @@ void Coherent_CFF()
    TPad *cc_1 = new TPad("cc_1", "_1",0,0.555408,0.3779599,0.9888647);
    cc_1->Draw();
    cc_1->cd();
-   cc_1->Range(0.2666667,-2,2.6,78);
+   cc_1->Range(0.2666667,-3,2.6,68);
    cc_1->SetFillColor(0);
    cc_1->SetBorderMode(0);
    cc_1->SetBorderSize(2);
@@ -96,11 +96,11 @@ void Coherent_CFF()
    multigraph->GetYaxis()->CenterTitle(true);
    multigraph->GetYaxis()->SetLabelFont(22);
    multigraph->GetYaxis()->SetLabelSize(0.08);
-   multigraph->GetYaxis()->SetTitleSize(0.14);
+   multigraph->GetYaxis()->SetTitleSize(0.13);
    multigraph->GetYaxis()->SetTitleOffset(0.8);
    multigraph->GetYaxis()->SetTitleFont(22);
    multigraph->GetXaxis()->SetLimits(0.85,2.6);
-   multigraph->GetYaxis()->SetRangeUser(-2.0, 78.0);
+   multigraph->GetYaxis()->SetRangeUser(-3.0, 68.0);
    
    Double_t Graph0_fx10[21] = {
    1,
@@ -152,7 +152,7 @@ void Coherent_CFF()
    graph->SetFillColor(1);
    graph->SetFillStyle(1000);
    graph->SetLineColor(2);
-   graph->SetLineWidth(4);
+   graph->SetLineWidth(2);
    
    TH1F *Graph_Graph010 = new TH1F("Graph_Graph010","Graph",100,0.84,2.76);
    Graph_Graph010->SetMinimum(15.01272);
@@ -222,7 +222,7 @@ void Coherent_CFF()
    gre->SetFillColor(1);
    gre->SetFillStyle(1000);
    gre->SetLineWidth(2);
[…]

### 2020-02-13 eg6-letters/long-paper/prc-dvcshelium.tex
Several minor edits, fix compile

--- 2020-01-05 eg6-letters/long-paper/prc-dvcshelium.tex
@@
 \usepackage{lineno}
+\usepackage{natbib}
 %\usepackage[scaled]{helvet}
@@
 \section{Introduction}
+
+In the past few decades, the study of the proton structure has made significant progress
+thanks to the theoretical and experimental developpements with three dimensional 
+structure functions \cite{Anselmino:2015uka}. These studies can be generalized to the
+nucleus and offer a unique opportunity to revisit the quark structure of the nucleus
+with an original perspective. This new approach is particularly needed as the quark
+structure of the nucleus remains today the subject of numerous
+controvercies. Indeed, while much progress has been made in measuring the nuclear
+parton distribution functions (PDFs), the observed shape of the PDF ratio, known as
+EMC effect, remains fundamentaly unexplained \cite{Norton:2003cb,Malace:2014uea,Hen:2016kwk}.
+
+In nuclei, the generalized parton distributions (GPDs) can be probed conveniently through
+spin assymetries in the deeply virtual Compton scattering (DVCS) 
+process~\cite{Diehl:2003ny,Belitsky:2005qn,Guidal:2013rya}. Indeed, the exclusive
+production of a photon limits the possibilities of final state interactions in the nuclear 
+medium. Moreover, with a nuclear targets of spin-0 the extraction of the GPD from the DVCS data 
+is significantly simplified with the reduction to a single GPD intervening in the process. The 
+measurement of the nuclear DVCS is however challenging experimentally, first attempts from 
+the HERMES collaboration \cite{Airapetian:2009cga} lead to imprecise results. We present here
+more recent and detailed measurements from the CLAS collaboration already partially presented
+in previous letters \cite{Hattawy:2017woc,Hattawy:2018liu}. We extend in this article 
+the description of the nuclear DVCS CLAS experiment, detail the methods used for the
+data analysis and produce the full experimental results for each channel measured.
 
@@
 where $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
-leptonic tensor \cite{Belitsky:2008bz} and $x_{A} = \frac{M_{p}\cdot x}{M_{^4\!He}}$. 
+leptonic tensor \cite{Belitsky:2008bz}, their explicit expression can be found in 
+appendix \ref{sec:eq}, and $x_{A} = \frac{M_{p}\cdot x}{M_{^4\!He}}$.
+
 %Their explicit expressions can be found in Appendix 
@@
 a function of $\phi$. As can be seen in Fig. \ref{fig:alphas}, the form of each 
-$\alpha$ coefficient is known and characteristic, such that a fit is easy. The only caveat
-is the large difference of magnitude between the $\alpha$ factors, which will lead to 
+$\alpha$ coefficient has a characteristic $\phi$ dependence, such that a fit can
+easily separate their respective contributions. The only caveat
+is the large difference of magnitude between the $\alpha$ factors, which can lead to 
 rather different error propagation for the two parts of the CFF.
@@
 
+An important issue with the use of this theoretical framework is the large mass of the 
+helium nuclei. In principle, this could lead to significant target mass corrections...
+REF? \cite{Braun:2012bg}
+
 \subsection{Incoherent nuclear DVCS}
@@
 The theory for incoherent DVCS on the nucleon is largely based on the free proton theory
-already reviewed in Chap. \ref{chap:pheno}. Two important differences in the 
-reaction need to be accounted however, the different initial state and the addition of 
+already reviewed many times in the litterature~\cite{Diehl:2003ny,Belitsky:2005qn,Guidal:2013rya}. 
+Two important differences need to be accounted for however, the different initial state and the addition of 
 final state effects. In the initial state, the intrinsic Fermi motion of the nucleons in the nucleus 
@@
 leading to contamination from other channels, in particular charge exchange can lead to
-large differences in this background.
+a large contribution from such background reaction.
 
@@
 process as more data becomes available. Another avenue of progress
-on this topic will be the use of experimental techniques like tagging to control them. This process
-and how it can help with these issues will be discussed
-in details at the end of the present chapter.
+on this topic will be the use of experimental techniques like tagging. This process
+can help to control both initial and final state effects by detecting the nuclear remnant.
+In the tagged process the target breaks in two providing directly the initial state
+of the struck nucleon, while a measured backward nuclear fragment limits significantly the
+impact of final state effects.
 
-\subsection{The HERMES nuclear DVCS measurements}
+\section{Past nuclear DVCS measurements}
 
@@
 This experiment covered an array of nuclear target and looked at the $A$ dependence of the
-BSA signal. The results, presented in Fig. \ref{fig:HERMES1} and \ref{fig:HERMES2}, suffer
+BSA signal. Thier results, presented in Fig. \ref{fig:HERMES1} and \ref{fig:HERMES2}, suffer
 from large error bars, which makes them consistent with the free proton data and prevents us to
-reach strong conclusions about the nuclear effect. Yet, in the coherent DVCS case a rather
+reach strong conclusions about any nuclear effect. Yet, in the coherent DVCS case a rather
 strong effect was expected, leading to a conflict between the HERMES results and theoretical
@@
 
-An issue with the HERMES measurement and how it is obtained from data has been raised in
+An important issue with the HERMES measurement and how it is obtained from data has been raised in
 \cite{Guzey:2003jh} to explain the discrepancy with theoretical expectations.
@@
 is instead reconstructed through a missing mass measurement of the other reaction products. The 
-issue with this method is that the detector resolution is not good enough to separate the 
-coherent and incoherent channels. 
+issue with this method is that the detector resolution may not be good enough to separate the 
+coherent and incoherent channels properly. 
 Instead, the results are labeled "coherent enriched" and "incoherent enriched" at low and high 
@@
 perform this measurement however, several instrumentation challenges need to be passed. First, to
-measure the scattered electron and the low angle photon of the DVCS, for which we used CLAS in its 
+measure the scattered electron and the low angle photon of the DVCS, we used CLAS in its 
 DVCS setup, $i.e.$ with the addition of a low angle calorimeter and a solenoid magnet. Second, the
-helium recoil need to be measured to ensure the exclusivity of the reaction. In this section, we 
+helium recoil need to be measured to ensure the exclusivity in the coherent channel. In this section, we 
 will rapidly describe the particular detector setup used in our experiment.
@@
 
-CLAS is installed in the hall B of the JLab main accelerator. It has for main objective to study the 
-multi-particles final states
+The CLAS spectrometer \cite{Mecking:2003zu} is installed in the hall-B of the JLab main 
+accelerator. It has for main objective to study the multi-particles final states
 that cannot be reconstructed with arm spectrometers. Its historic use to measure DVCS in many different 
 configurations made it an ideal place for this new DVCS measurement.  
-
-The CLAS spectrometer \cite{Mecking:2003zu} is composed of six identical radial 
+CLAS is composed of six identical radial 
 sectors separated by a toroidal magnet and each sector is made of four detectors 
@@
 It covers angles from 4 to 15 degrees. However, placing a detector at such low angles makes it 
-particularly sensitive to the Moller electrons scattered at low angles.
+particularly sensitive to the Moller electrons scattered from the target at small angles.
 
@@
 projection chambers. This design allows to reduce significantly the drift time and reduce the 
-amount of pile-up from accidental events. The RTPC has been described in more 
+amount of pile-up from accidental events. The RTPC design, its operation, calibration and 
+the track reconstruction have been described in more 
 details elsewhere \cite{Dupre:2017upj}, here is a summary of key elements.
@@
 time-of-flight system, which serves as a time reference for other detectors. In particular, it 
-serves for the identification of the protons, which is based on a 
-time-of-flight measurement. Several 
+serves for the identification of the protons. Several 
 fiducial cuts are applied to ensure that particles did not go through part of the inner calorimeter 
@@
 The second important source of background comes from accidentals. Despite the many exclusivity cuts, it is 
-possible to have particles from different events getting combining and pass all the cuts and get 
+possible to have particles from different events getting combined and pass all the cuts and get 
 into the data sample. To evaluate the number of such events, we invert the vertex selection 
@@
 illustrated in Fig. \ref{fig:ttpComp}. We use in our final results $t$,
-which is the correct definition.
+which is the correct definition with the slightly poorer resolution.
 
@@
 
-In order to compare to models, we extract the BSA at 90° in Fig. \ref{fig:CohALU90}. The model 
+We extract the BSA at 90° in Fig. \ref{fig:CohALU90}, the model 
 compared to the data \cite{Liuti:2005gi} is based on the idea that the main nuclear effects are 
@@
 
+\appendix
+\section{Detailed equations}
+\label{sec:eq}
+ tests
+
 % Create the reference section using BibTeX:
-\bibliography{basename of .bib file}
+\bibliography{hadro.bib}
 

### 2020-03-19 eg6-letters/long-paper/prc-dvcshelium.tex
Reread of long paper part 1

@@
 \usepackage{epigraph}
-\usepackage{lineno}
 \usepackage{natbib}
@@
 \usepackage{array}
+\usepackage{amsmath}
 
@@
 %Title of paper
-\title{Measurement of deeply virtual Compton scattering off Helium-4}
+\title{Measurement of deeply virtual Compton scattering off Helium-4 with CLAS at Jefferson Lab}
 
@@
 low-energy recoiling $^4$He nuclei and an inner calorimeter to extend the 
-photon detection acceptance to very forward angles. Our results confirm the 
+photon detection acceptance at forward angles. Our results confirm the 
 theoretically predicted enhancement of the coherent 
@@
 thanks to the theoretical and experimental developpements with three dimensional 
-structure functions \cite{Anselmino:2015uka}. These studies can be generalized to the
-nucleus and offer a unique opportunity to revisit the quark structure of the nucleus
-with an original perspective. This new approach is particularly needed as the quark
-structure of the nucleus remains today the subject of numerous
+structure functions \cite{Anselmino:2015uka}. These studies, which have focused on generalized
+parton distributions (GPD) and transverse momentum dependent parton distribution functions (PDF)
+can be generalized to the nucleus and offer a unique opportunity to revisit the quark structure 
+of the nucleus with an original perspective~\cite{Dupre:2015jha}. This new approach is 
+particularly needed as the quark structure of the nucleus remains today the subject of numerous
 controvercies. Indeed, while much progress has been made in measuring the nuclear
-parton distribution functions (PDFs), the observed shape of the PDF ratio, known as
-EMC effect, remains fundamentaly unexplained \cite{Norton:2003cb,Malace:2014uea,Hen:2016kwk}.
+PDFs, their shape remains fundamentaly unexplained \cite{Norton:2003cb,Malace:2014uea,Hen:2016kwk}.
 
-In nuclei, the generalized parton distributions (GPDs) can be probed conveniently through
-spin assymetries in the deeply virtual Compton scattering (DVCS) 
-process~\cite{Diehl:2003ny,Belitsky:2005qn,Guidal:2013rya}. Indeed, the exclusive
+In nuclei, the GPDs can be probed conveniently through the measurement of the
+spin assymetries generated by the deeply virtual Compton scattering (DVCS) 
+process~\cite{Diehl:2003ny,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}. The measurement of the exclusive
 production of a photon limits the possibilities of final state interactions in the nuclear 
-medium. Moreover, with a nuclear targets of spin-0 the extraction of the GPD from the DVCS data 
-is significantly simplified with the reduction to a single GPD intervening in the process. The 
+medium and offers a unique opportunity to make a measurement free of final state interactions 
+(FSI). Moreover, with a nuclear targets of spin-0 the extraction of the GPD from the DVCS data 
+is significantly simplified with the reduction to a single GPD intervening in the process at leading order. The 
 measurement of the nuclear DVCS is however challenging experimentally, first attempts from 
-the HERMES collaboration \cite{Airapetian:2009cga} lead to imprecise results. We present here
-more recent and detailed measurements from the CLAS collaboration already partially presented
-in previous letters \cite{Hattawy:2017woc,Hattawy:2018liu}. We extend in this article 
+the HERMES collaboration \cite{Airapetian:2009cga} lead to controversial conclusions. We present here
+in detail the more recent measurements from the CLAS collaboration, which has been already partially presented
+in two short letters \cite{Hattawy:2017woc,Hattawy:2018liu}. We extend in this article 
 the description of the nuclear DVCS CLAS experiment, detail the methods used for the
-data analysis and produce the full experimental results for each channel measured.
+data analysis and produce the complete experimental results for each channel measured.
 
@@
 we summarized here only necessary elements to discuss our experimental results.
-we obtain real structure functions 
-$F^{q}(x,\xi,t)$, where $x+\xi$ and $x-\xi$ are the incoming and outgoing quark momenta 
-respectively and $t=\Delta^2$ the squared transferred momentum to the target as illustrated in 
+The GPDs are real structure functions $F^{q}(x,\xi,t)$, where $x+\xi$ and $x-\xi$ are incoming and outgoing quark momenta 
+respectively and $t=\Delta^2$ the squared transferred momentum to the target in this exchange of quarks as illustrated in 
 Fig. \ref{fig:GPD}.
@@
 
-The different spin states possible lead to several independent GPDs for 
-any given hadron. The proper accounting of 
-the number of GPDs must be done with regard to the symmetries of the system.
-At leading order and leading twist, we find that there are $2(2J+1)^2$ GPDs for a particle of spin $J$, 
-$i.e.$ for a spin-0 hadron, like the helium-4 nucleus, we will
-have two GPDs, for a spin-1/2 hadron, like the proton, eight GPDs. Half of these involve a 
+The different spin states possible lead to several independent GPDs for any 
+given hadron. The proper accounting of the number of GPDs must be done with 
+regard to the symmetries of the system. At leading order and leading twist, we 
+find that there are $2(2J+1)^2$ GPDs for a particle of spin $J$, 
+$i.e.$ for a spin-0 hadron, like the helium-4 nucleus, we will have two GPDs, 
+for a spin-1/2 hadron, like the proton, eight GPDs. Half of these involve a 
 parton helicity flip, they are called transversity GPDs and do not intervene 
@@
 
-As mentioned above, DVCS is the main experimental access to GPDs. However, this process does not offer
+DVCS is the main experimental access to GPDs. However, this process does not offer
 a full access to the GPDs and we only access them integrated over $x$, in the following form:
@@
 the different quark flavors present in the hadron, as the electromagnetic probe do not differentiate
-quark flavors. A similar situation exists for TCS and DVMP giving only a partial access to the GPDs. 
-The double DVCS is a special case and it retains the full
-dependence of the GPDs in three independent variables.
+quark flavors.
 
-Experimentally, another process is indistinguishable from the DVCS. This is the Bethe-Heitler (BH) 
-process in which % TODO add BH figure
-the final state photon is emitted by the scattering lepton rather than the hadron. In this case the 
-photon-hadron interaction is the same as in elastic scattering and therefore such process depends on the
+Experimentally, another process is indistinguishable from the DVCS, the Bethe-Heitler (BH) 
+process in which % TODO add BH figure ?
+the final state photon is emitted by the scattering lepton rather than the hadron. In this case, the 
+photon-hadron interaction is the same as in elastic scattering and depends on the
 target FFs rather than its GPDs. The DVCS and BH processes are experimentally indistinguishable as they
-have identical final states, such that they interfere in the squared photo-production amplitude of the
+have identical final states, such that they interfere in the squared amplitude of the
 exclusive photo-production process:
@@
 The interference terms increase significantly the cross section in specific parts of the phase space
-and lead to significant charge and spin asymmetries.
+and lead to significant beam spin asymmetries (BSA), which are the focus of the measurements presented 
+here.
 
 Finally, we need to define our kinematics properly. We use the 
-conventions from Fig. \ref{fig:PhiAngle}. 
-In experiments, we generally use slightly different kinematic variables : 
+conventions from Fig. \ref{fig:PhiAngle} for angles and the experimental kinematic variables
+used here are defined as: 
 $-t = -(p_p-p_p^\prime)^2 = \Delta^2$ and 
-$x = {2\xi \over 1+\xi}$.
+$x_B = {Q^2 \over 2 M_N \nu}\sim {2\xi \over 1+\xi}$, with $M_N$ the nucleon mass and $\nu$ the
+energy transfer to the target $\nu = {E -E^\prime} $.
 
@@
 
-The reaction measured in the experiment is the coherent electro-production of a photon on helium
+The first reaction measured in the experiment is the coherent electro-production of a photon on helium
 $e+^4\!\!He \rightarrow e+\gamma+^4\!\!He$ at high 4-momentum transfer squared ($Q^2$). The 
-leading order diagrams
-of this reaction are the coherent DVCS and BH processes. The nuclear coherent DVCS is 
-represented in Fig. \ref{fig:CohDiag}. As  
-the two processes interfere at the amplitude level, which give rise to sizable spin asymmetries.
+leading order diagram of the nuclear coherent DVCS is represented in Fig. \ref{fig:CohDiag}.
 In our experiment, we focused on the measurement of the beam-spin asymmetry (BSA) noted $A_{LU}$ with 
@@
 where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the differential cross section for a positive 
-(negative) beam helicity. At leading order and leading twist, the BSA can be expressed as:        
+(negative) beam helicity. At leading order and leading twist, the BSA can be expressed as \cite{Kirchner:2003wt}:        
 \begin{eqnarray}
@@
 $s_1^{INT}$ are the Fourier coefficients of the BH, the DVCS and the 
-interference amplitudes for a spin-zero target \cite{Kirchner:2003wt}. %The explicit 
-%expressions of these coefficients can be found in Appendix 
-%\ref{app:Helium_cross_section}.
+interference amplitudes for a spin-zero target. The explicit 
+expressions of these coefficients, which have been derived based on the work of 
+Kirchner and Müller \cite{Kirchner:2003wt}, can be found in Appendix \ref{app:Helium_cross_section}.
 
@@
 \end{figure}
-%TODO fix delta
 
@@
 
-%Their explicit expressions can be found in Appendix 
-%\ref{app:Helium_cross_section}.
-
 The Eq. \ref{eq:A_LU-coh} is particularly convenient to perform an extraction of 
@@
 An important issue with the use of this theoretical framework is the large mass of the 
-helium nuclei. In principle, this could lead to significant target mass corrections...
-REF? \cite{Braun:2012bg}
+helium nuclei. Recent work indicate that the effect of this correction is moderate 
+\cite{Braun:2012bg}, however the applicability to such a large mass remains to be
+fully explored from the theoretical point of view.
 
@@
 interactions between the outgoing nucleon from the DVCS reaction and remnants of the nuclear 
-target are possible, including possible charge exchange. The latter
-leading to contamination from other channels, in particular charge exchange can lead to
-a large contribution from such background reaction.
+target are possible. The latter leading to contamination from other channels, in particular 
+charge exchange processes can lead to a large contribution from such background reaction.
 
@@
 
-The first measurement of nuclear DVCS has been performed by the HERMES collaboration 
-\cite{Airapetian:2009cga}.
-This experiment covered an array of nuclear target and looked at the $A$ dependence of the
-BSA signal. Thier results, presented in Fig. \ref{fig:HERMES1} and \ref{fig:HERMES2}, suffer
+The first measurement of nuclear DVCS has been performed by the HERMES 
+collaboration~\cite{Airapetian:2009cga}. This experiment covered an array of 
+nuclear targets and looked at the $A$ dependence of the
+BSA signal. Their main results, reproduced in Fig. \ref{fig:HERMES1} and \ref{fig:HERMES2}, suffer
 from large error bars, which makes them consistent with the free proton data and prevents us to
-reach strong conclusions about any nuclear effect. Yet, in the coherent DVCS case a rather
+reach strong conclusions about possible nuclear effects. Yet, in the coherent DVCS case a rather
 strong effect was expected, leading to a conflict between the HERMES results and theoretical
@@
 is instead reconstructed through a missing mass measurement of the other reaction products. The 
-issue with this method is that the detector resolution may not be good enough to separate the 
+issue with this method is that the detector resolution is not good enough to separate the 
 coherent and incoherent channels properly. 
@@
 \appendix
-\section{Detailed equations}
+\section{Expressions for the BSA of the coherent DVCS}
 \label{sec:eq}
+
+ The differential cross section for a longitudinally-polarized electron beam ($\lambda$) and an unpolarized $^4$He target can written as:
+\small
+\begin{equation}
+\frac{d^{5}\sigma_{\lambda}}{dx_{A} dQ^{2} dt d\phi_{e} d\phi} = 
+\frac{\alpha^{3}}{16 \pi^{2}} \frac{x_{A} \, y^{2}}{Q^{4} \sqrt{1 + \epsilon ^{2}}} 
+\frac{
+|\mathcal{T}_{BH}|^{2} + |{\mathcal{T}}_{DVCS}^{\lambda}|^{2} + {\mathcal{I}}_{BH*DVCS}^{\lambda}}{e^{6}}
+\label{eq:sigdiff}
+\end{equation}
+\normalsize
+where $y = \frac{p \cdot q}{p \cdot k}$, $\epsilon  =  \frac{2 x_{A} M_{A}}{Q}$ 
+and $x_A  =  \frac{Q^2}{2 p \cdot q}$. The different amplitudes can be written 
+as \cite{BM_2009}:
+\small
+\begin{equation}
+|\mathcal{T}_{BH}|^{2} =  
+\frac{e^{6} (1 + \epsilon^{2})^{-2}}{x^{2}_{A} y^{2} t \mathcal{P}_{1}(\phi) \mathcal{P}_{2}(\phi)} \left[ c_{0}^{BH} + c_{1}^{BH} \cos(\phi) + c_{2}^{BH} \cos(2\phi)\right] 
+\label{TTBH}
+\end{equation}
+
+\begin{equation}
+|\mathcal{T}_{DVCS}|^{2} =  \frac{e^{6}}{y^{2} Q^{2}} \left[ c_{0}^{DVCS} + \sum_{n=1}^{2} \Bigg( c_{n}^{DVCS} \cos(n \phi) + \lambda s_{n}^{DVCS} \sin(n \phi)\Bigg) \right] 
+\label{TTDVCS}
+\end{equation}
+
+\begin{equation}
+\mathcal{I}_{BH*DVCS} =  \frac{\pm e^{6}}{x_A y^{3} t \, \mathcal{P}_{1}(\phi) 
+\mathcal{P}_{2}(\phi)} \left[ c_{0}^{I} + \sum_{n=0}^{3} \Bigg( c_{n}^{I} \cos(n \phi) + \lambda s_{n}^{I} \sin(n \phi) \Bigg) \right] 
+\label{TTinter} 
+\end{equation}
+\\
+\normalsize
+where $\mathcal{P}_{1}(\phi)$ and $\mathcal{P}_{2}(\phi)$ are BH propagators and defined as:
+\small
+\begin{align}
+&\mathcal{P}_{1}(\phi) = \frac{(k - q')^{2}}{Q^{2}} = - \frac{1}{y (1 + \epsilon^{2})} 
+\big[ J + 2 K \cos(\phi) \big] \\
+&\mathcal{P}_{2}(\phi) = \frac{(k - \Delta)^{2}}{Q^{2}} = 1 + \frac{t}{Q^{2}} + 
+\frac{1}{y (1 + \epsilon^{2})} \big[ J + 2 K \cos(\phi) \big]
+\end{align}
+~~~~~~~~~~~with,
+\begin{align}
+& J = \bigg( 1 - y - \frac{y \epsilon^{2}}{2} \bigg) \bigg(1 + \frac{t}{Q^{2}} \bigg) - 
+(1 - x_{A})(2 - y) \frac{t}{Q^{2}} \\
+& K^{2} = - \delta t \, (1 - x_{A}) \bigg( 1 - y - \frac{y^{2} \epsilon^{2}}{4} \bigg) 
+\bigg\{ \sqrt{1 + \epsilon^{2}} + \frac{4 x_{A} (1-x_{A}) + \epsilon^{2}}{4 (1 - x_{A})}
+\delta t \bigg\} \\
+& \delta t = \frac{t - t_{min}}{Q^{2}} = \frac{t}{Q^{2}} + \frac{2(1-x_{A}) \left(1- \sqrt{1 + 
+\epsilon^{2}} \right) + \epsilon^{2}}{4 x_{A} (1- x_{A}) + \epsilon^{2}}
+\end{align}
+\normalsize
+where $t_{min}$ represents the kinematic boundary of the process and defined as:
+\small
+\begin{equation}
+t_{min} = Q^2 \frac{2(1-x_A)(1 - \sqrt{1+\epsilon^2}) + \epsilon^2}{4 x_A(1-x_A) + \epsilon^2}
+\end{equation}
+\normalsize
+The Fourier coefficients, in equations \ref{TTBH}, \ref{TTDVCS} and \ref{TTinter}, of a spin-0 target are defined as:
+\small
+\begin{eqnarray}
+c_0^{BH} = & \bigg[ & \left\{ {(2-y)}^2 + y^2{(1+\epsilon^2)}^2 \right\} 
+\left\{ \frac{\epsilon^2 Q^2}{t} + 4 (1-x_A) + (4x_A+\epsilon^2) \frac{t}{Q^2} 
+\right\} \nonumber \\
+& \phantom{\bigg[} & + 2 \epsilon^2 \left\{ 4(1-y)(3+2\epsilon^2) + y^2(2-\epsilon^4) 
+\right\} - 4 x_A^2{(2-y)}^2 (2+\epsilon^2) \frac{t}{Q^2} \nonumber \\
+& \phantom{\bigg[} & + 8 K^2 \frac{\epsilon^2 Q^2}{t} \,\,\,\,\,\,\, \bigg] F_A^2(t)  \\
+c_1^{BH} = & \phantom{\bigg[} & -8 (2-y) K \left\{ 2 x_A + \epsilon^2 - 
+\frac{\epsilon^2 Q^2}{t} \right\} F_A^2(t)  \\
+c_2^{BH} = & \phantom{\bigg[} & 8 K^2 \frac{\epsilon^2 Q^2}{t} F_A^2(t) 
+\end{eqnarray} 
+\normalsize
+where $F_A(t)$ is the electromagnetic form factor of the $^4$He. At leading twist, the $|\mathcal{T}_{DVCS}|^{2}$ writes as a function of only one CFF according to
+\small
+\begin{equation}
+%c_0^{DVCS} = 2 (2-2y+y^2) \, {\mathcal H}_A {\mathcal H}^{\star}_A 
+   c_0^{DVCS}= 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + \epsilon^2} \, 
+   {\mathcal H}_A {\mathcal H}^{\star}_A 
+   \label{eq:c0DVCS}
+\end{equation}
+\normalsize
+and the interference amplitude coefficients are written as:
+\small
+\begin{equation}
+s_{1}^{INT} = F_{A}(t) \Im m(\mathcal{H}_{A}) S_{++}(1),
+\end{equation}
+with
+\begin{eqnarray}
+   S_{++}(1) &=& \frac{-8K(2-y)y}{1+\epsilon^2} \left( 1 + 
+\frac{1-xA+\frac{\sqrt{1+\epsilon^2}-1}{2}}{1+\epsilon^2} 
+\frac{t-t_{min}}{Q^{2}} \right) \label{eq:s1I}
+\end{eqnarray}
+
+%c_0^{INT} & = & - 8 (2 - y) \frac{t}{Q^2} F_A \, \Re e \{{\mathcal H}_A\} 
+%\label{eq:c0I} \\
+% & \times & \left\{ (2-x_A)(1-y) - (1-x_A){(2-y)}^2 \left( 1 - 
+% \frac{t_{min}}{Q^2} \right) \right\} \nonumber \\
+
+%c_1^{INT} & = & 8 K (2y-y^2-2) F_A \, \Re e \{{\mathcal H}_A\} \label{eq:c1I}
+
+\begin{eqnarray}
+\small
+c_0^{INT} &=& F_A(t) \Re e(\mathcal{H}_{A}) C_{++}(0),
+\end{eqnarray}
+with \begin{eqnarray}  C_{++}(0) &=&
+\frac{-4(2-y)(1+\sqrt{1+\epsilon^{2}})}{(1+\epsilon^{2})^2}  \bigg\{ 
+   \frac{\widetilde{K}^2}{Q^2}  \frac{(2-y)^2}{\sqrt{1+\epsilon^{2}}} \, \\
+   &+& \frac{t}{Q^2}  \left( 1 - y - \frac{\epsilon^2}{4} y^2 \right)  
+(2-x_{A}) \left(  1 + \frac{2x_A(2-x_A + \frac{\sqrt{1+\epsilon^{2}}-1}{2} + 
+\frac{\epsilon^{2}}{2x_A})\frac{t}{Q^2} + \epsilon^{2}}{(2-x_A) 
+(1+\sqrt{1+\epsilon^{2}})}  \right)  \bigg\} \nonumber
+ \label{eq:c0I} 
+ \end{eqnarray}
+
+\begin{eqnarray}
+   c_1^{INT} &=&  F_A(t) \Re e(\mathcal{H}_{A}) C_{++}(1),
+\end{eqnarray}
+with
+
+   \begin{eqnarray}
+   C_{++}(1) &=&
+   \frac{-16K(1-y+\frac{\epsilon^{2}}{4}y^2)}{(1+\epsilon^{2})^{5/2}}\bigg\{\left(1+(1-x_A)\frac{\sqrt{1+\epsilon^{2}}-1}{2x_A} 
+   + \frac{\epsilon^{2}}{4x_A}\right) 
+\frac{x_At}{Q^2}-\frac{3\epsilon^{2}}{4.0} \bigg\} \nonumber \\&-& 4K \left( 
+2-2y+y^2+\frac{\epsilon^{2}}{2}y^2\right)\frac{1+\sqrt{1+\epsilon^{2}}-\epsilon^{2}}{(1+e2)^{5/2}}\bigg\{1-(1-3x_A)\frac{t}{Q^2}\nonumber\\&\,\,\,\,&\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,+\frac{1-\sqrt{1+\epsilon^{2}}+3\epsilon^{2}}{1+\sqrt{1+\epsilon^{2}}-\epsilon^{2}}
+\frac{x_A*t}{Q^2}\bigg\} \label{eq:c1I}
+\end{eqnarray}
+
+\section{Table of results with information on full kinematics}
+\label{sec:fullresults}
  tests

### 2020-03-25 eg6-letters/long-paper/prc-dvcshelium.tex
Add corrections to long paper

@@
 In the past few decades, the study of the proton structure has made significant progress
-thanks to the theoretical and experimental developpements with three dimensional 
+thanks to the theoretical and experimental developments with three dimensional 
 structure functions \cite{Anselmino:2015uka}. These studies, which have focused on generalized
@@
 particularly needed as the quark structure of the nucleus remains today the subject of numerous
-controvercies. Indeed, while much progress has been made in measuring the nuclear
-PDFs, their shape remains fundamentaly unexplained \cite{Norton:2003cb,Malace:2014uea,Hen:2016kwk}.
+controversies. Indeed, while much progress has been made in measuring the nuclear
+PDFs, their shape remains fundamentally unexplained \cite{Norton:2003cb,Malace:2014uea,Hen:2016kwk}.
 
 In nuclei, the GPDs can be probed conveniently through the measurement of the
-spin assymetries generated by the deeply virtual Compton scattering (DVCS) 
+spin asymmetries generated by the deeply virtual Compton scattering (DVCS) 
 process~\cite{Diehl:2003ny,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}. The measurement of the exclusive
@@
 Experimentally, another process is indistinguishable from the DVCS, the Bethe-Heitler (BH) 
-process in which % TODO add BH figure ?
+process in which 
 the final state photon is emitted by the scattering lepton rather than the hadron. In this case, the 
@@
 	\caption{Illustration of the scattering (or leptonic) and production (or hadronic) planes
-	in the DVCS process.} %TODO upgrade to a figure with phi_S
+	in the DVCS process.} 
 \label{fig:PhiAngle}
@@
 \begin{eqnarray}
+\label{eq:coh_BSA}
 A_{LU}& =& \frac{x_A(1+\epsilon^2)^2}{y} \, s_1^{INT} \sin(\phi) \, 
@@
 \frac{x_A (1+\epsilon^2)^2}{y} \sum_{n=0}^{n=1} c_n^{INT} \cos{(n\phi)} \bigg].  \nonumber 
-\label{eq:coh_BSA}
 \end{eqnarray}
@@
 These factors have the following simplified expressions:
-%\small
 \begin{eqnarray}
@@
 \end{eqnarray}
-%\normalsize
 where $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
@@
 The theory for incoherent DVCS on the nucleon is largely based on the free proton theory
-already reviewed many times in the litterature~\cite{Diehl:2003ny,Belitsky:2005qn,Guidal:2013rya}. 
+already reviewed many times in the literature~\cite{Diehl:2003ny,Belitsky:2005qn,Guidal:2013rya}. 
 Two important differences need to be accounted for however, the different initial state and the addition of 
@@
 	\caption{The sinus moment of the BSA as a function of $-t$ measured by HERMES
-	on a series of nuclei \cite{Airapetian:2009cga}.}
+	for a series of nuclei \cite{Airapetian:2009cga}.}
 \label{fig:HERMES1}
@@
 the predicted BSA increase could be observed and if GPDs could be extracted from it. In order to
-perform this measurement however, several instrumentation challenges need to be passed. First, to
+perform this measurement however, several instrumentation challenges needed to be resolved. First, to
 measure the scattered electron and the low angle photon of the DVCS, we used CLAS in its 
-DVCS setup, $i.e.$ with the addition of a low angle calorimeter and a solenoid magnet. Second, the
-helium recoil need to be measured to ensure the exclusivity in the coherent channel. In this section, we 
-will rapidly describe the particular detector setup used in our experiment.
-
-\subsection{The CLAS detector}
-
-The CLAS spectrometer \cite{Mecking:2003zu} is installed in the hall-B of the JLab main 
-accelerator. It has for main objective to study the multi-particles final states
-that cannot be reconstructed with arm spectrometers. Its historic use to measure DVCS in many different 
-configurations made it an ideal place for this new DVCS measurement.  
-CLAS is composed of six identical radial 
-sectors separated by a toroidal magnet and each sector is made of four detectors 
+DVCS setup, $i.e.$ with the addition of a low angle calorimeter and a 5-T solenoid magnet. Second, a
+radial time projection chamber (RTPC) was installed to measure the
+helium recoils and thus ensure the exclusivity of the process in the coherent channel. In this section, we 
+will review the important elements of this detection setup.
+
+\subsection{The CEBAF Large Acceptance Spectrometer (CLAS)}
+
+The CLAS \cite{Mecking:2003zu} is installed in the hall-B of the JLab continuous electron beam 
+accelerator facility (CEBAF). CLAS is specifically designed to study the multi-particles final states
+that cannot be observed conveniently with arm spectrometers. Its historic use to measure DVCS in many different 
+configurations made it an ideal place for this new DVCS measurement. CLAS is composed of six identical radial 
+sectors separated by toroidal magnets, with each sector made of four detectors 
 as shown in Fig. \ref{fig:CLAS}.  Three regions of drift chambers \cite{Mestayer:2000we} 
@@
 \cite{Smith:1999ii}. These detectors cover the polar angle from 8 to 142 degrees. 
-This is completed by two important forward detectors, from 8 
-to 45 degrees for electron identification, a Cerenkov counter 
+They are completed by two important forward detectors, covering the polar angle from 8 
+to 45 degrees, a Cerenkov counter 
 \cite{Adams:2001kk} and an electromagnetic calorimeter \cite{Amarian:2001zs}.
@@
 It covers angles from 4 to 15 degrees. However, placing a detector at such low angles makes it 
-particularly sensitive to the Moller electrons scattered from the target at small angles.
-
-\begin{figure}[tbp!]
-\center
-\includegraphics[width=8cm]{fig3/IC-CLAS.png}
-	\caption{Representation of the inner calorimeter (IC) of CLAS. The crystals that compose the
-	sensitive part of the detector are represented in purple.}
-\label{fig:IC}
-\end{figure}
-
-To protect the calorimeter from the low energy background a 5~T solenoid is 
+particularly sensitive to the low energy Moller electrons scattered from the target.
+To protect the calorimeter from this background, a 5~T solenoid is 
 placed around the target to form
@@
 \center
+\includegraphics[width=8cm]{fig3/IC-CLAS.png}
+	\caption{Representation of the inner calorimeter (IC) of CLAS. The crystals that compose the
+	sensitive part of the detector are represented in purple.}
+\label{fig:IC}
+\end{figure}
+
+\begin{figure}[tbp!]
+\center
 \includegraphics[width=14cm]{fig3/solenoid.png}
@@
 needed to detect them. To design the present setup, large inspiration was drawn from the 
-Bonus setup that also used a GEM based RTPC \cite{Fenker:2008zz}, installed in CLAS to 
-detect slow protons out of a deuterium target \cite{Baillie:2011za}. In such an RTPC the 
+Bonus setup that also used a GEM based RTPC~\cite{Fenker:2008zz} in CLAS to 
+detect slow protons out of a deuterium target~\cite{Baillie:2011za}. In such an RTPC the 
 charges are projected toward large radii 
@@
 the track reconstruction have been described in more 
-details elsewhere \cite{Dupre:2017upj}, here is a summary of key elements.
+details elsewhere~\cite{Dupre:2017upj}, here is a summary of key elements.
 
@@
 to ensure that it will come out of the target. For this, we used a light straw 
-target made of a thin kapton wall of 27 $\mu$m filled with up to 6 atm of 
-helium. The entrance and exit windows are thin aluminum foils and an helium 
+target made of a thin kapton wall of 27 $\mu$m filled with helium at 6 atm 
+pressure. The entrance and exit windows are thin aluminum foils and an helium 
 bag is placed downstream of the target to avoid interaction with air in the gap 
 between the target and the beamline vacuum. The cylindrical 
-chamber surrounds the target as illustrated in Fig. \ref{fig:RTPCGlobal}, we 
+chamber surrounds the target as illustrated in Fig.~\ref{fig:RTPCGlobal}, we 
 list the elements composing it based on their radii:
@@
 the drift path of electrons. A more detailed description of the calibration process 
-is available in \cite{Dupre:2017upj}.
+is available in~\cite{Dupre:2017upj}.
 
@@
 The electrons are detected with the baseline CLAS detectors, the drift chamber measures the kinematic 
-of the electron and the large signal in both the Cerenkov counter and electromagnetic calorimeter
+of the electron and the signal measured in both the Cerenkov counter and electromagnetic calorimeter
 provide the identification. A signal of good quality is also required in the 
@@
 Finally, we select events that contain a single electron, a high energy photon ($E>2$ GeV) and
-either a helium or a proton. We perform a vertex selection cut on the two charged particles 
-to ensure they originate from the same vertex, inside the target, thus rejecting target windows.
+either a helium or a proton. We apply a selection cut on the two charged particles 
+to ensure they originate from the same vertex inside the target, thus rejecting accidentals and
+events from the target windows.
 Moreover, since we are aiming to study deep processes occurring at the partonic level, we select
@@
 where $\epsilon ^{2} = \frac{4M^{2}_{^4\!He}x^{2}_{A}}{Q^{2}}$. For incoherent DVCS, 
-$x_A$ is replaced by $x$ and $M_{^4\!He}$ by $M_{p}$.
+we use a similar cut where $x_A$ is replaced by $x$ and $M_{^4\!He}$ by $M_{p}$.
 
@@
 are detected at very different energies and with very different detector 
-precision, we chose to over constrain the selection by using seven 
+resolutions, we chose to over constrain the selection by using seven 
 variables. The seven variables are defined as follow for the coherent 
@@
 In the analysis, we apply selection cuts based on a fit of the exclusive peak at 3$\sigma$ around 
-the mean value for each variable. This automatic method helps to avoid any bias 
+the mean value for each variable. This systematic method helps to avoid any bias 
 in the selection of the events. The selection of coherent DVCS with these variables is illustrated in 
@@
 distribution have some asymmetries. These are linked with the detector resolutions, that impact
-differently the kinematic variables. The selection of incoherent DVCS is presented in 
+some of the kinematic variables non linearly. The selection of incoherent DVCS is presented in 
 Fig. \ref{fig:IncExcCuts}, with two main differences: larger distributions overall and more
@@
 misalignment between CLAS sectors and are within the levels obtained with free proton 
-targets to which they can be directly compared (see \cite{HirlingerSaylor:2018bnu} for instance).
+targets~\cite{HirlingerSaylor:2018bnu} to which they can be directly compared.
 
@@
 \includegraphics[trim=20 10 20 5,clip,width=15cm]{fig3/all_coh_exc_cuts.pdf}
-	\caption{Overlay of the events distributions before (black) and after (blue line filled
+	\caption{Distributions of the coherent photon production events before 
+	(black) and after (blue line filled
 	in Grey) the exclusivity cuts used to select coherent DVCS represented by the 
-	red dashed lines. The histograms are for the seven variables described in the text, 
-	plus the missing $P_x$ and $P_y$, in order left to right and top to bottom.}
+	red dashed lines. The histograms are shown as a function of the 
+	seven variables used for the exclusivity selection described in the text, 
+	plus the missing $P_x$ and $P_y$, in order left to right and top to bottom. 
+	}
 \label{fig:CohExcCuts}
@@
 \includegraphics[trim=20 10 20 5,clip,width=15cm]{fig3/all_incoh_exc_cuts.pdf}
-\caption{Overlay of the events distributions before (black) and after (blue line filled
-	in Grey) the exclusivity cuts used to select incoherent DVCS represented by the 
-	red dashed lines. The histograms are for the seven variables described in the text, 
+\caption{Distributions of the incoherent photon production events before 
+	(black) and after (blue line filled
+	in Grey) the exclusivity cuts used to select coherent DVCS represented by the 
+	red dashed lines. The histograms are shown as a function of the 
+	seven variables used for the exclusivity selection described in the text, 
 	plus the missing $P_x$ and $P_y$, in order left to right and top to bottom.}
@@
 
-The final sample of events selected is still not free of backgrounds. The main contamination is 
+The main contamination is expected to be 
 from the exclusive production of a $\pi^0$, the final state of which is very similar to DVCS with 
-only an extra photon. Therefore, if one of the photon is produced 
-at low energy, it is easy to confuse the two processes. In order to estimate the contribution from
-this channel, we detect it in the same way as DVCS, with a series of similar exclusivity cuts, completed
-by a selection on the invariant mass of the two photons. The events obtained for the coherent and incoherent
-channels are respectively shown in Fig. \ref{fig:CohPi0Simul} and \ref{fig:InCohPi0Simul}. From 
+only an extra photon. In such an event, if one of the photon is produced at low energy, it is 
+easy to confuse this process with single photon production. In order to estimate the contribution from
+this channel in our data, we measure the exclusive $\pi^0$ production in the same way as DVCS, with 
+a series of exclusivity cuts, completed by a selection cut on the invariant mass of the two photons
+to match the $\pi^0$ mass. The events obtained for the coherent and incoherent
+channels are shown in Fig. \ref{fig:CohPi0Simul} and \ref{fig:InCohPi0Simul}, respectively. From 
 this sample, we elaborated an event generator, which after being processed
@@
 The second important source of background comes from accidentals. Despite the many exclusivity cuts, it is 
-possible to have particles from different events getting combined and pass all the cuts and get 
+possible to have particles from different events being combined and pass all the cuts to get 
 into the data sample. To evaluate the number of such events, we invert the vertex selection 
@@
 
-To evaluate the systematic error of the measurement, we performed several specific studies. We 
+To evaluate the systematic error of the measurement, we performed several specialized studies. We 
 evaluated the impact of changing the exclusivity selection cuts by varying them from 1 to 5 $\sigma$. 
 We evaluated the impact of changing the binning in $\phi$ on the extraction of the beam-spin asymmetry
-at 90°. We used the spread of the beam polarization measurements during the run period to evaluate their 
-precision. We checked different methods to make the simulation of the exclusive $\pi^0$
-production to evaluate the 
+at 90°. The precision with which we know the beam polarization is estimated based on the spread 
+of its measurements during the complete run period. We also checked different methods to make the 
+simulation of the exclusive $\pi^0$ production to evaluate the 
 possible bias introduced by this correction. As radiative corrections are expected to be small
@@
 
-%TODO MAke sure acceptance ratio is indeed pi0
-
 As discussed above, the best way to define $t$ in the incoherent channel is not completely
@@
 in the initial state to calculate $t^\prime$. As it is not obvious which solution is best,
-we studied the difference between them by analyzing the data independently using the two 
+we studied the difference between the two results by analyzing the data independently using the two 
 definitions. We found no significant difference between them, as is 
@@
 In Fig. \ref{fig:CohALUphi}, we present the results for the BSA in the coherent DVCS channel. We 
-observe the dominant sinusoidal component typical of the DVCS BSA, but note also the large size 
-of the asymmetry, almost double than the one measured for the free proton \cite{Jo:2015ema}. This 
+observe the dominant sinusoidal component typical of the DVCS BSA, with an amplitude almost 
+double than the one measured for the free proton \cite{Jo:2015ema}. This 
 predicted feature of nuclear DVCS \cite{Guzey:2003jh} is observed here for the first time, we
 can conclude that this measurement cleanly isolates the coherent DVCS process. The absence of 
-this feature in HERMES data and its clear observation here indicates that the recoil 
-detection is a strong help to isolate the effects of the coherent DVCS process from backgrounds.
+this feature in the previous measurement from HERMES \cite{Airapetian:2009cga} and its clear observation here indicates that the recoil 
+detection is a necessity to isolate the effects of the coherent DVCS process from backgrounds.
 
@@
 	function of $\phi$ and $Q^2$ 
-	(top panels), $x$ (middle panels) and $-t$ (lower panels). Error bars are  
-	statistical, Grey bands represent the systematic errors. The data is fitted with Eq. 
-	\ref{eq:A_LU-coh}, the results of these fits are drawn with red full lines.}
+	(top panels), $x$ (middle panels) or $-t$ (lower panels). Error bars are  
+	statistical, Grey bands represent the systematic errors. The full red lines show
+	the fit of the data with the form of Eq.~\ref{eq:A_LU-coh}.}
+	%TODO Add the chi2 somewhere
 \label{fig:CohALUphi}
@@
 \center
-\includegraphics[width=10cm]{fig3/Coherent_ALU_phi_90.pdf}
+\includegraphics[width=15cm]{fig3/Coherent_ALU_phi_90.pdf}
 \caption{The BSA at 90° as a function of $Q^2$ (top panel), $x$ (middle panel) and $-t$ (lower panel).
@@
 
-We extract the BSA at 90° in Fig. \ref{fig:CohALU90}, the model 
-compared to the data \cite{Liuti:2005gi} is based on the idea that the main nuclear effects are 
-included by accounting for the nucleon off-shellness and kinematics in nuclei with a nuclear
-spectral function. It appears that the model undershoot our results systematically. However, 
-a more recent calculation, using similar principles but with a more advanced nuclear spectral 
-function \cite{Fucini:2018gso} has been able to reproduce the data very well. This 
-sort of theoretical model, also able to describe the EMC effect, is the only one which has 
-been confronted to this data yet. We observe that reproducing these data is not 
-straightforward and necessitates an advanced nuclear model.
-
-% TODO add footnote
-%\footnote{We actually show here the opposite of HERMES results, as the HERMES 
-%experiment ran with a positron beam, which lead to opposite BSAs.}
-%TODO Add Sergio's results there
-
-One of the promise of the helium-4 DVCS was the expected ease to extract the CFF $\mathcal{H}_A$ from
+We extract the BSA at 90° in Fig. \ref{fig:CohALU90}, the model compared to the 
+data~\cite{Liuti:2005gi} is based on the hypothesis that the main nuclear effects are 
+included by accounting for the nucleon off-shellness and kinematics in nuclei. It 
+appears that this model undershoots our results systematically. However, a new independent 
+calculation \cite{Fucini:2018gso}, using similar principles but with a more recent nuclear spectral 
+function, has been able to reproduce the data very well. Since these results are from independent 
+groups, it remains unclear at this point if the difference between them is manly due to the nuclear
+spectral function or to its precise implementation. Another factor in the difference is that the
+recent calculation from Fucini {\it et al.}~\cite{Fucini:2018gso} benefited from using the precise 
+kinematic of each points. This feature appears to have a significant impact on some points, for 
+instance the $-t$ distribution appears to have a peculiar structure well reproduced by the 
+calculation. For this reason, we provide the detailed kinematic of each result presented in
+appendix \ref{sec:fullresults}.
+
+One of the promise of the helium-4 coherent DVCS was the ease to extract the CFF $\mathcal{H}_A$ from
 data. To do so, we used the form from Eq. \ref{eq:A_LU-coh} to fit the data from Fig. 
@@
 CFF presented in Fig. \ref{fig:CohCFF}. The results are rather encouraging, the two parts
-of the CFF are constrained by data without need of any model. This capacity to obtain a
+of the CFF are constrained by data without need of any constraint beyond our data points. This 
+capacity to obtain a
 model independent result with such a limited data set offers a striking contrast with the
-situation of the free proton fits described in Chap. \ref{chap:pheno}.
+situation of the free proton fits \cite{Dupre:2016mai,Dupre:2017hfs}.
 
@@
 	$-t$ (right panels). The red full line red is the theoretical calculation from 
-	\cite{Guzey:2003jh,Guzey:2008th}, the black dashed line is the same calculation 
+	Guzey {\it et al.}~\cite{Guzey:2003jh,Guzey:2008th}, the black dashed line is the same calculation 
 	using the VGG model as input \cite{Vanderhaeghen:1999xj,Guidal:2004nd}, and
-	the blue dashed line is a calculation from \cite{GonzalezHernandez:2012jv}.} 
-	%TODO change model names description
+	the blue dashed line is a calculation from Liuti {\it et 
+	al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv}.} 
 \label{fig:CohCFF}
@@
 The CFF extraction allows us to compare the results to other theoretical calculations.
-The calculation within the impulse approximation from \cite{Guzey:2003jh,Guzey:2008th} 
-gives the nuclear GPD directly
-from the proton and neutron GPDs, such that it allows to test the effect of different 
-nucleon's GPD models. In Fig. \ref{fig:CohCFF}, we can see that the effect of such a change of 
-GPD model is of similar size or larger than the difference with another nuclear 
-model \cite{GonzalezHernandez:2012jv}. However, at the level of precision of the present data,
-it is not possible to resolve which variant is best. This feature still highlights the 
-importance to try different nucleon models when evaluating a feature of the data.
-
-This measurement of the BSA in the deeply virtual coherent exclusive photo-production on a nucleus
-is the first to clearly isolate the effect of coherent nuclear DVCS and of nuclear GPDs. While, the
-statistical precision and the kinematic coverage are still far behind the experimental results on
-proton target, the results appear to match very well the predictions using the GPD framework. It 
-validates the relevance of the nuclear DVCS to study the nucleus globally in terms of quarks and 
-gluons, bypassing any intermediate degree of freedom like the nucleons.
+These are performed within the impulse approximation \cite{Guzey:2003jh,Guzey:2008th} 
+and give the nuclear GPD directly from the proton and neutron GPDs. In 
+Fig. \ref{fig:CohCFF}, we show two versions of this calculation, where two different nucleon GPD
+models are used as input, compared with the calculation previously shown from Liuti 
+{\it et al.}~\cite{Liuti:2005gi} with an updated nucleon model \cite{GonzalezHernandez:2012jv}.
+We can see that the effect of changing the input nucleon GPD model
+is of similar size or larger than the difference between nuclear 
+models. However, at the level of precision of the present data,
+it is not possible to resolve which variant is best. This feature highlights the 
+importance of the choice of nucleon model to study nuclear effects with this data.
+
+In summary, this measurement of the BSA in the deeply virtual coherent exclusive 
+photo-production on a nucleus is the first to clearly isolate the effect of 
+coherent nuclear DVCS and of nuclear GPDs. While, the statistical precision and 
+the kinematic coverage are still far behind the experimental results on
+proton target, the results appear to match very well the predictions using the GPD 
+framework. Moreover, the extraction of the CFF appears to be very convenient based
+on the BSA measurement only. Together, these findings  validate the relevance of the 
+coherent nuclear DVCS to study the nucleus globally in terms of quarks and 
+gluons.
 
@@
 	helium-4 as a function of $\phi$ and $Q^2$ 
-	(top panels), $x$ (middle panels) and $-t$ (lower panels). Error bars are  
+	(top panels), $x$ (middle panels) or $-t$ (lower panels). Error bars are  
 	statistical, Grey bands represent the systematic errors. The data is fitted with the 
@@
 the effects from the nucleon structure and highlight nuclear effects. Such ratio is presented
-in Fig. \ref{fig:IncRatios}, where we observe again that most models overshoot the data.
+in Fig. \ref{fig:IncRatios}, where we observe again that most models significantly overshoot the data.
 
@@
 BSA to go as low as 60\% of the size of the BSA observed
-on the free proton. This drastic reduction is still unexplained, though some theoretical 
+on the free proton at $x_B \sim 0.15$. This drastic reduction is still unexplained, though some theoretical 
 work has been recently published to prolong the calculation from \cite{Fucini:2018gso} to the incoherent 
@@
 
+Further work is needed to fully comprehend this newly discovered nuclear effect. On the 
+experimental side, the use of tagging methods, where the nuclear fragments are measured
+appear to offer the best option forward. Indeed, tagging offers the best chance to understand better
+this result by offering better control over both the initial and the final state 
+effects~\cite{Dupre:2015jha}.
+
 \section{Summary}
+
+We report the measurement of the coherent and incoherent DVCS processes off helium-4 with
+CLAS at JLab. To properly isolate the coherent channel, the experiment used a specially 
+designed RTPC to detect the scattered helium-4. While statistically limited, this coherent 
+DVCS measurement reveals the large BSA ($\sim 35$\%) expected by theoretical calculations
+made in the impulse approximation. Moreover, we showed that the CFF extraction can be 
+immediately performed using these data without any model prescription. The incoherent DVCS measurement 
+however reveals relatively small asymmetries in comparison to previous free proton 
+measurements. It remains unclear what is the source of the suppression of the BSA as both 
+initial and final state effect contributions could lead to such outcome.
 
@@
 \begin{acknowledgments}
-	% Add Sergio and ERC!
- Put your acknowledgments here.
+	%TODO Add Sergio and ERC!
+ The authors acknowledge the staff of the Accelerator and Physics Divisions at 
+the Thomas Jefferson National Accelerator Facility who made this experiment 
+possible. This work was supported in part by the Chilean Comisi\'on Nacional de 
+Investigaci\'on Cient\'ifica y Tecnol\'ogica (CONICYT), by CONICYT PIA grant 
+ACT1413, the Italian Instituto Nazionale di Fisica Nucleare, the French Centre 
+National de la Recherche Scientifique, the French Commissariat \`a l'Energie 
+Atomique, the U.S. Department of Energy under Contract No. DE-AC02-06CH11357, 
+the United Kingdom Science and Technology Facilities Council (STFC), the 
+Scottish Universities Physics Alliance (SUPA), the National Research Foundation 
+of Korea, and the Office of Research and Economic Development at Mississippi 
+State University.  M.~Hattawy also acknowledges the support of the Consulat 
+G\'en\'eral de France \`a J\'erusalem.  The Southeastern Universities Research 
+Association operates the Thomas Jefferson National Accelerator Facility for the 
+United States Department of Energy under Contract No. DE-AC05-06OR23177.
 \end{acknowledgments}
@@
 
- The differential cross section for a longitudinally-polarized electron beam ($\lambda$) and an unpolarized $^4$He target can written as:
-\small
-\begin{equation}
-\frac{d^{5}\sigma_{\lambda}}{dx_{A} dQ^{2} dt d\phi_{e} d\phi} = 
-\frac{\alpha^{3}}{16 \pi^{2}} \frac{x_{A} \, y^{2}}{Q^{4} \sqrt{1 + \epsilon ^{2}}} 
-\frac{
-|\mathcal{T}_{BH}|^{2} + |{\mathcal{T}}_{DVCS}^{\lambda}|^{2} + {\mathcal{I}}_{BH*DVCS}^{\lambda}}{e^{6}}
-\label{eq:sigdiff}
-\end{equation}
-\normalsize
-where $y = \frac{p \cdot q}{p \cdot k}$, $\epsilon  =  \frac{2 x_{A} M_{A}}{Q}$ 
-and $x_A  =  \frac{Q^2}{2 p \cdot q}$. The different amplitudes can be written 
-as \cite{BM_2009}:
-\small
-\begin{equation}
-|\mathcal{T}_{BH}|^{2} =  
-\frac{e^{6} (1 + \epsilon^{2})^{-2}}{x^{2}_{A} y^{2} t \mathcal{P}_{1}(\phi) \mathcal{P}_{2}(\phi)} \left[ c_{0}^{BH} + c_{1}^{BH} \cos(\phi) + c_{2}^{BH} \cos(2\phi)\right] 
-\label{TTBH}
-\end{equation}
-
-\begin{equation}
-|\mathcal{T}_{DVCS}|^{2} =  \frac{e^{6}}{y^{2} Q^{2}} \left[ c_{0}^{DVCS} + \sum_{n=1}^{2} \Bigg( c_{n}^{DVCS} \cos(n \phi) + \lambda s_{n}^{DVCS} \sin(n \phi)\Bigg) \right] 
-\label{TTDVCS}
-\end{equation}
-
-\begin{equation}
-\mathcal{I}_{BH*DVCS} =  \frac{\pm e^{6}}{x_A y^{3} t \, \mathcal{P}_{1}(\phi) 
-\mathcal{P}_{2}(\phi)} \left[ c_{0}^{I} + \sum_{n=0}^{3} \Bigg( c_{n}^{I} \cos(n \phi) + \lambda s_{n}^{I} \sin(n \phi) \Bigg) \right] 
-\label{TTinter} 
-\end{equation}
-\\
-\normalsize
-where $\mathcal{P}_{1}(\phi)$ and $\mathcal{P}_{2}(\phi)$ are BH propagators and defined as:
-\small
+We present in this appendix the detailed expressions used for Eq. \ref{eq:coh_BSA} 
+and Eq. \ref{eq:alpha1} to \ref{eq:alpha4}. These are adapted from the work of 
+Kirchner and Müller \cite{Kirchner:2003wt} to match the notations and conventions used
+in this work.
+
+First, $\mathcal{P}_{1}(\phi)$ and $\mathcal{P}_{2}(\phi)$ are BH propagators and defined as:
 \begin{align}
@@
 \end{align}
-~~~~~~~~~~~with,
+with,
 \begin{align}
@@
 & \delta t = \frac{t - t_{min}}{Q^{2}} = \frac{t}{Q^{2}} + \frac{2(1-x_{A}) \left(1- \sqrt{1 + 
-\epsilon^{2}} \right) + \epsilon^{2}}{4 x_{A} (1- x_{A}) + \epsilon^{2}}
+\epsilon^{2}} \right) + \epsilon^{2}}{4 x_{A} (1- x_{A}) + \epsilon^{2}}.
 \end{align}
-\normalsize
-where $t_{min}$ represents the kinematic boundary of the process and defined as:
-\small
-\begin{equation}
-t_{min} = Q^2 \frac{2(1-x_A)(1 - \sqrt{1+\epsilon^2}) + \epsilon^2}{4 x_A(1-x_A) + \epsilon^2}
-\end{equation}
-\normalsize
-The Fourier coefficients, in equations \ref{TTBH}, \ref{TTDVCS} and \ref{TTinter}, of a spin-0 target are defined as:
-\small
+
+The Fourier coefficients for BH contributions are defined as:
 \begin{eqnarray}
@@
 \end{eqnarray} 
-\normalsize
-where $F_A(t)$ is the electromagnetic form factor of the $^4$He. At leading twist, the $|\mathcal{T}_{DVCS}|^{2}$ writes as a function of only one CFF according to
-\small
+where $F_A(t)$ is the electromagnetic form factor of the $^4$He. 
+The coefficient for the DVCS contribution is given by: 
 \begin{equation}
-%c_0^{DVCS} = 2 (2-2y+y^2) \, {\mathcal H}_A {\mathcal H}^{\star}_A 
    c_0^{DVCS}= 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + \epsilon^2} \, 
@@
 \end{equation}
-\normalsize
-and the interference amplitude coefficients are written as:
-\small
+
+Finally, the interference amplitude coefficients are written as:
 \begin{equation}
@@
 
-%c_0^{INT} & = & - 8 (2 - y) \frac{t}{Q^2} F_A \, \Re e \{{\mathcal H}_A\} 
-%\label{eq:c0I} \\
-% & \times & \left\{ (2-x_A)(1-y) - (1-x_A){(2-y)}^2 \left( 1 - 
-% \frac{t_{min}}{Q^2} \right) \right\} \nonumber \\
-
-%c_1^{INT} & = & 8 K (2y-y^2-2) F_A \, \Re e \{{\mathcal H}_A\} \label{eq:c1I}
-
 \begin{eqnarray}
-\small
 c_0^{INT} &=& F_A(t) \Re e(\mathcal{H}_{A}) C_{++}(0),
@@
 with  
-
    \begin{eqnarray}

### 2020-03-26 eg6-letters/long-paper/prc-dvcshelium.tex
Update figures

@@
 \center
-\includegraphics[width=15cm]{fig3/Coherent_ALU_phi_90.pdf}
+\includegraphics[width=17cm]{fig3/Coherent_ALU_phi_90.pdf}
 \caption{The BSA at 90° as a function of $Q^2$ (top panel), $x$ (middle panel) and $-t$ (lower panel).
 	Our results are shown with black squares, HERMES results 
-	with green circles \cite{Airapetian:2009cga} and theoretical predictions 
-	from \cite{Liuti:2005gi} with full and dashed lines.}
+	with green circles \cite{Airapetian:2009cga}. Theoretical predictions 
+	from Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
+	with red full line and dashed blue, while the calculation from Fucini 
+	{\it et al.}~\cite{Fucini:2018gso} is shown with a magenta long dash line.}
 \label{fig:CohALU90}
@@
 	using the VGG model as input \cite{Vanderhaeghen:1999xj,Guidal:2004nd}, and
-	the blue dashed line is a calculation from Liuti {\it et 
+	the blue long dash line shows the predictions from Liuti {\it et 
 	al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv}.} 
@@
 The asymmetries at 90° are presented in Fig. \ref{fig:IncALU} together with the theoretical
-calculation presented also in Fig. \ref{fig:CohALU90}. The results are much more precise than 
-the existing HERMES data and offer a strong constraint on the model presented. As in the
+calculation presented also in Fig. \ref{fig:CohALU90}. We observe an important improvement
+on the precisision compared to 
+the HERMES data, which offers a strong constraint on the model presented. As in the
 coherent case, the calculation appears to have issues to reproduce the shape of the data.
@@
 \center
-\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_Q2_shortscenrario.png}
-\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_t_shortscenrario.png}
-\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_x_shortscenrario.png}
+\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_Q2_shortscenrario.pdf}
+\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_t_shortscenrario.pdf}
+\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_x_shortscenrario.pdf}
 	\caption{The BSA at 90° as a function of  $Q^2$ (top left), $x$ (top right) and 
-	$-t$ (bottom). Our measurement is represented with black squares, HERMES 
-	measurement \cite{Airapetian:2009cga} with green circles and the theoretical 
-	calculation from \cite{Liuti:2005gi} with full lines.}
+	$-t$ (bottom). Our measurement is represented with black squares and the HERMES 
+	measurement \cite{Airapetian:2009cga} with green circles. Theoretical predictions 
+	from Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
+	with red full line and dashed blue, while the calculation from Fucini 
+	{\it et al.}~\cite{Fucini:2019xlc} is shown with a magenta long dash line.}
 \label{fig:IncALU}
@@
 \center
-\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_Q2_shortscenrario.png}
-\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_t_shortscenrario.png}
-\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_x_shortscenrario.png}
+\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_Q2_shortscenrario.pdf}
+\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_t_shortscenrario.pdf}
+\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_x_shortscenrario.pdf}
 	\caption{DVCS BSA ratio of the bound proton to the free proton as a function of 
 	$Q^2$ (top left), $x$ (top right) and $-t$ (bottom). The present measurement is 
-	represented with black squares, HERMES 
-	measurement \cite{Airapetian:2009cga} with green circles, the theoretical 
-	calculation from \cite{Liuti:2005gi} with blue and red full lines and the
-	calculation from \cite{Guzey:2008fe} with full and dashed black lines.}
+	represented with black squares and the HERMES 
+	measurement \cite{Airapetian:2009cga} with green circles. Theoretical predictions 
+	from Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
+	with red full line and dashed blue, the calculation from Fucini 
+	{\it et al.}~\cite{Fucini:2019xlc} is shown with a magenta long dash line and the
+	the black dot-dash line is the calculation from Guzey {\it et al.}~\cite{Guzey:2008th}.}
 \label{fig:IncRatios}
@@
 \begin{acknowledgments}
-	%TODO Add Sergio and ERC!
 The authors acknowledge the staff of the Accelerator and Physics Divisions at 

### 2020-03-26 eg6-letters/long-paper/source_files/Coh/Coherent_ALU_phi_90.C

@@ -138,7 +138,7 @@ void Coherent_ALU_phi_90()
    entry->SetMarkerStyle(21);
    entry->SetMarkerSize(1.5);
    entry->SetTextFont(42);
-   TLegendEntry *entry2=leg->AddEntry("graphS","Fucini et al. [x]","L");
+   TLegendEntry *entry2=leg->AddEntry("graphS","Fucini et al. [31]","L");
    entry2->SetLineStyle(9);
    entry2->SetLineWidth(2);
    entry2->SetLineColor(6);
@@ -349,7 +349,7 @@ void Coherent_ALU_phi_90()
    line->SetLineStyle(7);
    line->Draw();
    
-   leg = new TLegend(0.14,0.76,0.98,1,NULL,"brNDC");
+   leg = new TLegend(0.29,0.76,0.98,1,NULL,"brNDC");
    leg->SetBorderSize(1);
    leg->SetTextSize(0.05);
    leg->SetLineColor(1);
@@ -365,7 +365,7 @@ void Coherent_ALU_phi_90()
    entry->SetMarkerStyle(21);
    entry->SetMarkerSize(1.5);
    entry->SetTextFont(42);
-   entry=leg->AddEntry("LT (-t=0.100)","Gonzalez-H. et al. (low -t) [x]","L");
+   entry=leg->AddEntry("LT (-t=0.100)","Liuti et al. (low -t) [29]","L");
    entry->SetLineColor(2);
    entry->SetLineStyle(1);
    entry->SetLineWidth(2);
@@ -373,7 +373,7 @@ void Coherent_ALU_phi_90()
    entry->SetMarkerStyle(21);
    entry->SetMarkerSize(1);
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Graph1","Gonzalez-H. et al. (high -t) [x]","L");
+   entry=leg->AddEntry("Graph1","Liuti et al. (high -t) [29]","L");
    entry->SetLineColor(4);
    entry->SetLineStyle(7);
    entry->SetLineWidth(2);
@@ -381,7 +381,7 @@ void Coherent_ALU_phi_90()
    entry->SetMarkerStyle(21);
    entry->SetMarkerSize(1);
    entry->SetTextFont(42);
-   entry2=leg->AddEntry("graphS","Fucini et al. [x]","L");
+   entry2=leg->AddEntry("graphS","Fucini et al. [31]","L");
    entry2->SetLineStyle(9);
[…]

### 2020-03-26 eg6-letters/long-paper/source_files/Coh/Coherent_CFF.C

@@ -755,7 +755,7 @@ void Coherent_CFF()
    entry->SetMarkerStyle(21);
    entry->SetMarkerSize(1.5);
    entry->SetTextFont(42);
-   entry=leg->AddEntry("graphCFF","Convolution-Dual [x]","L");
+   entry=leg->AddEntry("graphCFF","Guzey et al. [17]","L");
    entry->SetLineColor(2);
    entry->SetLineStyle(1);
    entry->SetLineWidth(2);
@@ -913,12 +913,12 @@ void Coherent_CFF()
    leg->SetLineWidth(1);
    leg->SetFillColor(0);
    leg->SetFillStyle(1001);
-   entry=leg->AddEntry("Graph0","Convolution-VGG [x]","L");
+   entry=leg->AddEntry("Graph0","Guzey et al. [17]","L");
    entry->SetLineColor(1);
    entry->SetLineStyle(7);
    entry->SetLineWidth(2);
    entry->SetTextFont(42);
-   TLegendEntry *entry2=leg->AddEntry("graph","Off-shell model [x]","L");
+   TLegendEntry *entry2=leg->AddEntry("graph","Liuti et al. [29]","L");
    entry2->SetLineStyle(9);
    entry2->SetLineWidth(2);
    entry2->SetTextFont(42);

### 2020-03-26 eg6-letters/long-paper/source_files/InCoh/ALU_90_p_vs_Q2_shortscenrario.C

@@ -94,10 +94,10 @@ void ALU_90_p_vs_Q2_shortscenrario()
    2.34,
    3.10};
    Double_t _sy1[4] = {
-   0.233,
-   0.198,
-   0.174,
-   0.136};
+   0.2477,
+   0.2241,
+   0.1918,
+   0.1463};
    TGraph *graphS = new TGraph(4,_sx1,_sy1);
    graphS->SetLineStyle(9);
    graphS->SetLineWidth(2);
@@ -114,7 +114,7 @@ void ALU_90_p_vs_Q2_shortscenrario()
    TLegendEntry *entry;
    entry=leg->AddEntry("clas","CLAS (this work)","p");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Scope","Fucini et al. [x]","l");
+   entry=leg->AddEntry("Scope","Fucini et al. [37]","l");
    entry->SetLineStyle(9);
    entry->SetLineWidth(2);
    entry->SetLineColor(6);

### 2020-03-26 eg6-letters/long-paper/source_files/InCoh/ALU_90_p_vs_t_shortscenrario.C

@@ -92,15 +92,19 @@ void ALU_90_p_vs_t_shortscenrario()
    graph->Draw("f");
    
    Double_t _sx1[4] = {
-   0.136,
-   0.281,
-   0.492,
-   1.09 };
+   0.145,
+   0.282,
+   0.490,
+   1.11 };
    Double_t _sy1[4] = {
-   0.137,
-   0.154,
-   0.169,
-   0.186};
+   0.1455,
+   0.1644,
+   0.1902,
+   0.1728};
+// 0.140,
+// 0.155,
+// 0.173,
+// 0.165};
    TGraph *graphS = new TGraph(4,_sx1,_sy1);
    graphS->SetLineStyle(9);
    graphS->SetLineWidth(2);
@@ -286,7 +290,7 @@ void ALU_90_p_vs_t_shortscenrario()
    line->SetLineStyle(7);
    line->Draw();
    
-   TLegend *leg = new TLegend(0.47,0.64,0.92,0.92,NULL,"brNDC");
+   TLegend *leg = new TLegend(0.46,0.64,0.92,0.92,NULL,"brNDC");
    leg->SetBorderSize(1);
    leg->SetLineColor(1);
    leg->SetLineStyle(1);
@@ -295,10 +299,10 @@ void ALU_90_p_vs_t_shortscenrario()
    leg->SetFillStyle(1001);
    TLegendEntry *entry=leg->AddEntry("Graph0","CLAS (This work)","P");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Graph1","HERMES [x]","P");
-   entry=leg->AddEntry("Graph3","Liuti et al. (low x_{B}) [x]","L");
-   entry=leg->AddEntry("Graph4","Liuti et al. (high x_{B}) [x]","L");
-   entry=leg->AddEntry("GraphS","Fucini et al. [x]","L");
+   entry=leg->AddEntry("Graph1","HERMES [10]","P");
+   entry=leg->AddEntry("Graph3","Liuti et al. (low x_{B}) [29]","L");
+   entry=leg->AddEntry("Graph4","Liuti et al. (high x_{B}) [29]","L");
+   entry=leg->AddEntry("GraphS","Fucini et al. [37]","L");
    entry->SetLineStyle(9);
    entry->SetLineWidth(2);
    entry->SetLineColor(6);

### 2020-03-26 eg6-letters/long-paper/source_files/InCoh/ALU_90_p_vs_x_shortscenrario.C

@@ -137,15 +137,19 @@ void ALU_90_p_vs_x_shortscenrario()
    graph->Draw("c");
    
    Double_t _sx1[4] = {
-   0.163,
-   0.225,
-   0.283,
-   0.389};
+   0.162,
+   0.227,
+   0.287,
+   0.390};
    Double_t _sy1[4] = {
-   0.199,
-   0.178,
-   0.169,
-   0.149};
+   0.2084,
+   0.2003,
+   0.1847,
+   0.1625};
+// 0.192,
+// 0.185,
+// 0.169,
+// 0.147};
    TGraph *graphS = new TGraph(4,_sx1,_sy1);
    graphS->SetLineStyle(9);
    graphS->SetLineWidth(2);
@@ -206,11 +210,11 @@ void ALU_90_p_vs_x_shortscenrario()
    leg->SetFillStyle(1001);
    TLegendEntry *entry=leg->AddEntry("Graph0","CLAS (This work)","P");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Graph1","Liuti et al. (low -t) [x]","L");
+   entry=leg->AddEntry("Graph1","Liuti et al. (low -t) [29]","L");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Graph2","Liuti et al. (high -t) [x]","L");
+   entry=leg->AddEntry("Graph2","Liuti et al. (high -t) [29]","L");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("GraphS","Fucini et al. [x]","L");
+   entry=leg->AddEntry("GraphS","Fucini et al. [37]","L");
    entry->SetLineStyle(9);
    entry->SetLineWidth(2);
    entry->SetLineColor(6);

### 2020-03-26 eg6-letters/long-paper/source_files/InCoh/ALU_ratioInc_Q2_shortscenrario.C

@@ -78,12 +78,12 @@ void ALU_ratioInc_Q2_shortscenrario()
    1.40,
    1.89,
    2.34,
-   3.09};
+   3.10};
    Double_t _sy1[4] = {
-   0.980,
-   0.989,
-   0.988,
-   0.973};
+   0.9038,
+   0.9687,
+   0.9904,
+   0.9759};
    TGraph *graphS = new TGraph(4,_sx1,_sy1);
    graphS->SetLineStyle(9);
    graphS->SetLineWidth(2);
@@ -130,7 +130,7 @@ void ALU_ratioInc_Q2_shortscenrario()
    leg->SetFillStyle(1001);
    TLegendEntry *entry=leg->AddEntry("gre","CLAS (This work)","P");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("graphS","Fucini et al. [x]","L");
+   entry=leg->AddEntry("graphS","Fucini et al. [37]","L");
    entry->SetLineStyle(9);
    entry->SetLineWidth(2);
    entry->SetLineColor(6);

### 2020-03-26 eg6-letters/long-paper/source_files/InCoh/ALU_ratioInc_t_shortscenrario.C

@@ -95,10 +95,10 @@ void ALU_ratioInc_t_shortscenrario()
    0.492,
    1.09};
    Double_t _sy1[4] = {
-   1.03,
-   1.00,
-   0.987,
-   0.987};
+   1.0328,
+   1.0006,
+   0.9959,
+   0.8344};
    TGraph *graphS = new TGraph(4,_sx1,_sy1);
    graphS->SetName("GraphS");
    graphS->SetLineStyle(9);
@@ -243,15 +243,15 @@ void ALU_ratioInc_t_shortscenrario()
    leg->SetBorderSize(1);
    TLegendEntry *entry=leg->AddEntry("Graph0","CLAS (This work)","P");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("GraphH","HERMES [x]","P");
+   entry=leg->AddEntry("GraphH","HERMES [10]","P");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Graph2","Liuti et al. (low -t) [x]","L");
+   entry=leg->AddEntry("Graph2","Liuti et al. (low -t) [29]","L");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Graph4","Guzey et al. [x]","L");
+   entry=leg->AddEntry("Graph4","Guzey et al. [34]","L");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Graph3","Liuti et al. (high -t) [x]","L");
+   entry=leg->AddEntry("Graph3","Liuti et al. (high -t) [29]","L");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("GraphS","Fucini et al. [x]","L");
+   entry=leg->AddEntry("GraphS","Fucini et al. [37]","L");
    entry->SetLineStyle(9);
    entry->SetLineWidth(2);
    entry->SetLineColor(6);

### 2020-03-26 eg6-letters/long-paper/source_files/InCoh/ALU_ratioInc_x_shortscenrario.C

@@ -95,10 +95,10 @@ void ALU_ratioInc_x_shortscenrario()
    0.283,
    0.388};
    Double_t _sy1[4] = {
-   0.972,
-   0.994,
-   0.989,
-   0.971};
+   0.8430,
+   0.9967,
+   0.9937,
+   0.9742};
    TGraph *graphS = new TGraph(4,_sx1,_sy1);
    graphS->SetName("GraphS");
    graphS->SetLineStyle(9);
@@ -231,15 +231,15 @@ void ALU_ratioInc_x_shortscenrario()
    leg->SetBorderSize(1);
    TLegendEntry *entry=leg->AddEntry("Graph0","CLAS (This work)","P");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("GraphH","HERMES [x]","P");
+   entry=leg->AddEntry("GraphH","HERMES [10]","P");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Graph2","Liuti et al. (low -t) [x]","L");
+   entry=leg->AddEntry("Graph2","Liuti et al. (low -t) [29]","L");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Graph4","Guzey et al. [x]","L");
+   entry=leg->AddEntry("Graph4","Guzey et al. [34]","L");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Graph3","Liuti et al. (high -t) [x]","L");
+   entry=leg->AddEntry("Graph3","Liuti et al. (high -t) [29]","L");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("GraphS","Fucini et al. [x]","L");
+   entry=leg->AddEntry("GraphS","Fucini et al. [37]","L");
    entry->SetLineStyle(9);
    entry->SetLineWidth(2);
    entry->SetLineColor(6);

### 2020-03-26 eg6-letters/long-paper/prc-dvcshelium.tex
Update result discussion based on Fucini updated calculation

@@
 The asymmetries at 90° are presented in Fig. \ref{fig:IncALU} together with the theoretical
-calculation presented also in Fig. \ref{fig:CohALU90}. We observe an important improvement
-on the precisision compared to 
+calculation presented previously in Fig. \ref{fig:CohALU90}. We observe an important improvement
+on the precision compared to 
 the HERMES data, which offers a strong constraint on the model presented. As in the
-coherent case, the calculation appears to have issues to reproduce the shape of the data.
-However, this time the calculation overshoots the data, sometimes by a significant amount.
-An interesting way to look into this issue is to show the result on incoherent DVCS compared 
-with the free proton. We can for instance make a ratio, in a fashion similar to the EMC 
+coherent case, the calculation appears to have issues to reproduce the shape of the data,
+with Fucini {\it et al.}~\cite{Fucini:2019xlc} doing better than the others.
+However, this time the calculations overshoot the data, sometimes by a significant amount.
+
+An interesting way to look into this data is to show the result on incoherent nuclear DVCS compared 
+with the free proton one. We can for instance make a ratio, in a fashion similar to the EMC 
 effect, which allows to cancel out
 the effects from the nucleon structure and highlight nuclear effects. Such ratio is presented
-in Fig. \ref{fig:IncRatios}, where we observe again that most models significantly overshoot the data.
+in Fig. \ref{fig:IncRatios}.
+Notably, the calculation from Fucini {\it et al.}~\cite{Fucini:2019xlc} appears closer to the
+others, hinting that maybe the better results with the raw asymmetries was linked to the
+input model they used for the free nucleon GPD. Also, they appear to somewhat reproduce the 
+shape of the $x_B$ distribution, which would indicate that it is linked to kinematic effects.
+Altogether, this result confirms that most models significantly overshoot the data and that 
+the BSA in the incoherent DVCS channel is suppressed by 20 to 30 \%.
 
@@
 
-This measurement of the incoherent DVCS BSA shows a global tendency of the experimental data 
-to be smaller than expected from theoretical calculations. We observe the incoherent DVCS 
-BSA to go as low as 60\% of the size of the BSA observed
-on the free proton at $x_B \sim 0.15$. This drastic reduction is still unexplained, though some theoretical 
-work has been recently published to prolong the calculation from \cite{Fucini:2018gso} to the incoherent 
-channel \cite{Fucini:2019xlc}. The explanation for this surprising behavior can come from different sources
-both in the initial state and the final state.
-
+The explanation for this surprising behavior can come from different sources
+both in the initial state and in the final state. 
 Further work is needed to fully comprehend this newly discovered nuclear effect. On the 

### 2020-03-26 eg6-letters/long-paper/prc-dvcshelium.tex
Minor link fix

@@
 expressions of these coefficients, which have been derived based on the work of 
-Kirchner and Müller \cite{Kirchner:2003wt}, can be found in Appendix \ref{app:Helium_cross_section}.
+Kirchner and Müller \cite{Kirchner:2003wt}, can be found in Appendix \ref{sec:eq}.
 
@@
 leptonic tensor \cite{Belitsky:2008bz}, their explicit expression can be found in 
-appendix \ref{sec:eq}, and $x_{A} = \frac{M_{p}\cdot x}{M_{^4\!He}}$.
+Appendix \ref{sec:eq}, and $x_{A} = \frac{M_{p}\cdot x}{M_{^4\!He}}$.
 

### 2020-03-30 eg6-letters/long-paper/prc-dvcshelium.tex
edit figure 3, 12, 13 and adding the source files

@@
 \center
-\includegraphics[trim=20 10 20 5,clip,width=15cm]{fig3/all_coh_exc_cuts.pdf}
+\includegraphics[trim=10 10 10 5,clip,width=16.5cm]{fig3/all_coh_exc_cuts.png}
         \caption{Distributions of the coherent photon production events before 
-	(black) and after (blue line filled
+        (blue) and after (black line filled
 	in Grey) the exclusivity cuts used to select coherent DVCS represented by the 
@@
 \center
-\includegraphics[trim=20 10 20 5,clip,width=15cm]{fig3/all_incoh_exc_cuts.pdf}
-\caption{Distributions of the incoherent photon production events before 
-	(black) and after (blue line filled
+\includegraphics[trim=10 10 10 
+   5,clip,width=16.5cm]{fig3/all_incoh_exc_cuts.png}
+\caption{Distributions of the incoherent photon production events before (blue) 
+   and after (black line filled
 	in Grey) the exclusivity cuts used to select coherent DVCS represented by the 

### 2020-03-31 eg6-letters/long-paper/source_files/ALU_90_p_vs_Q2_shortscenrario.C
add the source files for figure 16

@@ -1,0 +1,171 @@
+void ALU_90_p_vs_Q2_shortscenrario()
+{
+//=========Macro generated from canvas: Can_p_Q2/DVCS Helium BoNuS
+//=========  (Thu May 23 14:35:03 2019) by ROOT version 6.14/04
+   TCanvas *Can_p_Q2 = new TCanvas("Can_p_Q2", "DVCS Helium BoNuS",63,57,600,450);
+   gStyle->SetOptFit(1);
+   Can_p_Q2->SetHighLightColor(2);
+   Can_p_Q2->Range(-0.2792208,-0.2168831,4.915584,0.5623377);
+   Can_p_Q2->SetFillColor(0);
+   Can_p_Q2->SetBorderMode(0);
+   Can_p_Q2->SetBorderSize(2);
+   Can_p_Q2->SetLeftMargin(0.15);
+   Can_p_Q2->SetRightMargin(0.08);
+   Can_p_Q2->SetTopMargin(0.08);
+   Can_p_Q2->SetBottomMargin(0.15);
+   Can_p_Q2->SetFrameBorderMode(0);
+   Can_p_Q2->SetFrameBorderMode(0);
+   
+   TH2F *HALU_p_vs_Q2__1 = new TH2F("HALU_p_vs_Q2__1","",100,0.5,4.5,100,-0.1,0.5);
+   HALU_p_vs_Q2__1->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   HALU_p_vs_Q2__1->SetLineColor(ci);
+   HALU_p_vs_Q2__1->GetXaxis()->SetTitle("Q^{2} [GeV^{2}]");
+   HALU_p_vs_Q2__1->GetXaxis()->CenterTitle(true);
+   HALU_p_vs_Q2__1->GetXaxis()->SetNdivisions(605);
+   HALU_p_vs_Q2__1->GetXaxis()->SetLabelFont(22);
+   HALU_p_vs_Q2__1->GetXaxis()->SetLabelSize(0.05);
+   HALU_p_vs_Q2__1->GetXaxis()->SetTitleSize(0.07);
+   HALU_p_vs_Q2__1->GetXaxis()->SetTitleFont(22);
+   HALU_p_vs_Q2__1->GetYaxis()->SetTitle("A_{LU}^{Incoh}(90#circ)");
+   HALU_p_vs_Q2__1->GetYaxis()->CenterTitle(true);
[…]

### 2020-03-31 eg6-letters/long-paper/source_files/ALU_90_p_vs_t_shortscenrario.C

@@ -1,0 +1,473 @@
+void ALU_90_p_vs_t_shortscenrario()
+{
+//=========Macro generated from canvas: Can_p_t/DVCS Helium BoNuS
+//=========  (Thu May 23 14:35:04 2019) by ROOT version 6.14/04
+   TCanvas *Can_p_t = new TCanvas("Can_p_t", "DVCS Helium BoNuS",63,57,600,450);
+   gStyle->SetOptFit(1);
+   Can_p_t->SetHighLightColor(2);
+   Can_p_t->Range(-0.2337662,-0.2168831,1.324675,0.5623377);
+   Can_p_t->SetFillColor(0);
+   Can_p_t->SetBorderMode(0);
+   Can_p_t->SetBorderSize(2);
+   Can_p_t->SetLeftMargin(0.15);
+   Can_p_t->SetRightMargin(0.08);
+   Can_p_t->SetTopMargin(0.08);
+   Can_p_t->SetBottomMargin(0.15);
+   Can_p_t->SetFrameBorderMode(0);
+   Can_p_t->SetFrameBorderMode(0);
+   
+   TH2F *HALU_p_vs_t__5 = new TH2F("HALU_p_vs_t__5","",100,0,1.2,100,-0.1,0.5);
+   HALU_p_vs_t__5->SetStats(0);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#000099");
+   HALU_p_vs_t__5->SetLineColor(ci);
+   HALU_p_vs_t__5->GetXaxis()->SetTitle("-t [GeV^{2}]");
+   HALU_p_vs_t__5->GetXaxis()->CenterTitle(true);
+   HALU_p_vs_t__5->GetXaxis()->SetNdivisions(605);
+   HALU_p_vs_t__5->GetXaxis()->SetLabelFont(22);
+   HALU_p_vs_t__5->GetXaxis()->SetLabelSize(0.05);
+   HALU_p_vs_t__5->GetXaxis()->SetTitleSize(0.07);
+   HALU_p_vs_t__5->GetXaxis()->SetTitleFont(22);
+   HALU_p_vs_t__5->GetYaxis()->SetTitle("A_{LU}^{Incoh}(90#circ)");
+   HALU_p_vs_t__5->GetYaxis()->CenterTitle(true);
[…]

### 2020-04-22 eg6-letters/long-paper/prc-dvcshelium.tex
Add Stepan's comment and some fig rework

@@
 in two short letters \cite{Hattawy:2017woc,Hattawy:2018liu}. We extend in this article 
-the description of the nuclear DVCS CLAS experiment, detail the methods used for the
+the description of the CLAS nuclear DVCS experiment, detail the methods used for the
 data analysis and produce the complete experimental results for each channel measured.
@@
 publications~\cite{Diehl:2003ny,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya},
-we summarized here only necessary elements to discuss our experimental results.
+we summarized here only necessary elements to discuss the present experimental results.
 The GPDs are real structure functions $F^{q}(x,\xi,t)$, where $x+\xi$ and $x-\xi$ are incoming and outgoing quark momenta 
@@
 
-DVCS is the main experimental access to GPDs. However, this process does not offer
-a full access to the GPDs and we only access them integrated over $x$, in the following form:
+DVCS is the main experimental probe of the GPDs. However, this process does not allow
+for an extraction of the GPDs in full phase space parameters. Instead, DVCS gives access
+to the GPDs integrated over $x$, in the following form:
 \begin{equation}
@@
 photon-hadron interaction is the same as in elastic scattering and depends on the
-target FFs rather than its GPDs. The DVCS and BH processes are experimentally indistinguishable as they
+target form factors rather than its GPDs. The DVCS and BH processes are experimentally 
+indistinguishable as they
 have identical final states, such that they interfere in the squared amplitude of the
@@
 
-Finally, we need to define our kinematics properly. We use the 
+Finally, we need to define the kinematics. We use the 
 conventions from Fig. \ref{fig:PhiAngle} for angles and the experimental kinematic variables
@@
 The first reaction measured in the experiment is the coherent electro-production of a photon on helium
-$e+^4\!\!He \rightarrow e+\gamma+^4\!\!He$ at high 4-momentum transfer squared ($Q^2$). The 
+$e+^4\!\!He \rightarrow e+\gamma+^4\!\!He$ at large 4-momentum transfer squared ($Q^2$). The 
 leading order diagram of the nuclear coherent DVCS is represented in Fig. \ref{fig:CohDiag}.
-In our experiment, we focused on the measurement of the beam-spin asymmetry (BSA) noted $A_{LU}$ with 
-$L$ for the longitudinally-polarized electron beam and $U$ the unpolarized target and defined as:  
+In the present experiment, we focused on the measurement of the beam-spin asymmetry (BSA) 
+noted $A_{LU}$ with 
+$L$ for the longitudinally-polarized electron beam and $U$ the unpolarized target and is defined as:  
 \begin{equation}
@@
 The theory for incoherent DVCS on the nucleon is largely based on the free proton theory
-already reviewed many times in the literature~\cite{Diehl:2003ny,Belitsky:2005qn,Guidal:2013rya}. 
+already reviewed widely in the literature~\cite{Diehl:2003ny,Belitsky:2005qn,Guidal:2013rya}. 
 Two important differences need to be accounted for however, the different initial state and the addition of 
@@
 In the tagged process the target breaks in two providing directly the initial state
-of the struck nucleon, while a measured backward nuclear fragment limits significantly the
+of the struck nucleon, while measured backward nuclear fragments limit significantly the
 impact of final state effects.
@@
 cross sections of the two channels in $t$ will lead to a clear differentiation. However, the
-results in Fig. \ref{fig:HERMES2} show similar behaviors in both sectors of $t$, which is 
-challenging this assumption and could explain the tension between theory and experiment.
-
-Altogether, the large error bars and the impossibility to properly separate the coherent and 
+results in Fig. \ref{fig:HERMES2} show similar behaviors in both sectors of $t$, which  
+challenges this assumption and could explain the tension between theory and experiment.
+
+Altogether, large error bars and the failure to properly separate the coherent and 
 incoherent channels have strongly impaired the measurement and any conclusions that could be
@@
 perform this measurement however, several instrumentation challenges needed to be resolved. First, to
-measure the scattered electron and the low angle photon of the DVCS, we used CLAS in its 
-DVCS setup, $i.e.$ with the addition of a low angle calorimeter and a 5-T solenoid magnet. Second, a
+measure the scattered electron and the small angle photon of the DVCS, we used CLAS in its 
+DVCS setup, $i.e.$ with the addition of a forward angle calorimeter and a 5-T solenoid magnet. Second, a
 radial time projection chamber (RTPC) was installed to measure the
@@
 configurations made it an ideal place for this new DVCS measurement. CLAS is composed of six identical radial 
-sectors separated by toroidal magnets, with each sector made of four detectors 
+sectors separated by coils of toroidal magnets, with each sector made of four detectors 
 as shown in Fig. \ref{fig:CLAS}.  Three regions of drift chambers \cite{Mestayer:2000we} 
-are placed in the solenoid area to reconstruct the charge particle's tracks and 
-calculate their momentum. Then, an array of scintillators is placed to measure 
+are placed between the torus magnet to reconstruct the charge particle's tracks and 
+calculate their momentum. An array of scintillators is placed behind drift chambers to measure 
 a precise time for each track and perform time-of-flight measurement 
 \cite{Smith:1999ii}. These detectors cover the polar angle from 8 to 142 degrees. 
-They are completed by two important forward detectors, covering the polar angle from 8 
-to 45 degrees, a Cerenkov counter 
-\cite{Adams:2001kk} and an electromagnetic calorimeter \cite{Amarian:2001zs}.
+In forward region, from 8 to 45 degree, these two detectors are complimented with 
+Cerenkov counters \cite{Adams:2001kk} and electromagnetic calorimeters \cite{Amarian:2001zs},
+important for electron identification.
 
@@
 
-Altogether, CLAS provides a large acceptance of about $\pi$ steradians for momentums 
+Altogether, CLAS provides a large acceptance of about $2\pi$ steradians for momenta 
 starting at 200 MeV/c. During the nuclear DVCS experiment,
-the beam energy was maximal for CLAS with 6.064 GeV, while the beam intensity varied
-between 120 and 150 nA. Such beam on our helium-4 target pressurized between 5 and 6 atm,
+the beam energy was highest for CLAS with 6.064 GeV, while the beam intensity varied
+between 120 and 150 nA. Such beam on the helium-4 target pressurized between 5 and 6 atm,
 corresponds to luminosities in the range of $1$ to $1.2 \times 10^{34}$ cm$^{-2}$.s$^{-1}$.
@@
 The CLAS collaboration has established a specific setup to measure the typically 
-low angle photons of the DVCS process. This setup is composed of an inner 
+small angle photons of the DVCS process. This setup is composed of an inner 
 calorimeter and a solenoid and has lead to numerous DVCS measurements on proton 
@@
 (PbWO) crystals read out by $5 \times 5$ mm$^2$ avalanche photo-diodes (APDs). 
-It covers angles from 4 to 15 degrees. However, placing a detector at such low angles makes it 
+It covers angles from 4 to 15 degrees. However, placing a detector at such small angles makes it 
 particularly sensitive to the low energy Moller electrons scattered from the target.
@@
 The recoil helium nuclei from coherent DVCS are mostly emitted between 150 
-and 200 MeV/c at our beam energy. Therefore, a specific detector was 
+and 200 MeV/c at the beam energy of 6~GeV. Therefore, a specific detector was 
 needed to detect them. To design the present setup, large inspiration was drawn from the 
@@
 	\item Missing transverse momentum of the full system;
-	\item Missing mass of the system electron-helium, ignoring the photon;
-	\item Missing mass of the system electron-photon, ignoring the recoil helium;
+	\item Missing mass of the system electron-helium;
+	\item Missing mass of the system electron-photon;
 	\item Co-linearity ($\theta$) of the measured photon with the missing momentum of the 
@@
 Fig. \ref{fig:IncExcCuts}, with two main differences: larger distributions overall and more
-offset distributions. The former is largely due to Fermi motion, but simulations have shown
-that this effect is not strong enough to reproduce these distribution widths and final 
-state interactions must play a role as well. The later is caused by slight detector 
+offset distributions. The larger distributions are largely attributed to the effect of 
+Fermi motion, but simulations have shown that this effect is not strong enough to fully 
+reproduce the distribution widths and final state interactions must play a role as well. 
+The offsets of some distributions is caused by slight detector 
 misalignment between CLAS sectors and are within the levels obtained with free proton 
@@
 from the exclusive production of a $\pi^0$, the final state of which is very similar to DVCS with 
-only an extra photon. In such an event, if one of the photon is produced at low energy, it is 
+only an extra photon. In such an event, if one of the photons is produced at low energy, it is 
 easy to confuse this process with single photon production. In order to estimate the contribution from
-this channel in our data, we measure the exclusive $\pi^0$ production in the same way as DVCS, with 
+this channel in the data, we measure the exclusive $\pi^0$ production in the same way as DVCS, with 
 a series of exclusivity cuts, completed by a selection cut on the invariant mass of the two photons
@@
 this sample, we elaborated an event generator, which after being processed
-in the simulation of our detectors output the red histograms of Fig. \ref{fig:CohPi0Simul} and 
+in the simulation of the detectors gives the red histograms of Fig. \ref{fig:CohPi0Simul} and 
 \ref{fig:InCohPi0Simul}. To correct the experimental data, we estimate the number of single photon 
-events coming from DVCS with:
+events coming from the exclusive $\pi^0$ production as:
 \begin{equation}
@@
 $N_{2\gamma,\pi^0}^{Sim}$ the number of simulated exclusive $\pi^0$ fully reconstructed and $N_{2\gamma,\pi^0}^{Exp}$
-the number of experimentally measured exclusive $\pi^0$. This number can then be subtracted to
-the experimental measurement of DVCS events ($N_{DVCS}^{Exp}$) to get the corrected result: 
+the number of experimentally measured exclusive $\pi^0$. This number can then be subtracted from
+the experimentally measured number of DVCS events ($N_{DVCS}^{Exp}$) to get the corrected result: 
 \begin{equation}
@@
 The $\pi^0$ contamination was found to be 2 to 4\% in the coherent channel and 3 to 17\% in the incoherent
-channel (with variations between bins). To make the correction on the DVCS BSA, we assume that
+channel (with variations between kinematic bins). To make the correction on the DVCS BSA, we assume that
 the exclusive $\pi^0$ production has no such asymmetry. This has been checked with the exclusive 
@@
 
-\subsection{Systematic errors}
+\subsection{Systematic uncertainties}
 
@@
 possible bias introduced by this correction. As radiative corrections are expected to be small
-for our process, we did not apply them, but associated an error of their expected size.
-These errors are summarized in Tab. \ref{Table:systematic_uncertainties}, with their respective 
-evaluated sizes. They are added quadratically for the total systematic error presented in the results.
+for this process, we did not apply them, but associated an error of their expected value.
+These uncertainties are summarized in Tab. \ref{Table:systematic_uncertainties}, with their respective 
+evaluated values. They are added quadratically for the total systematic error presented in the results.
 
@@
 we studied the difference between the two results by analyzing the data independently using the two 
-definitions. We found no significant difference between them, as is 
-illustrated in Fig. \ref{fig:ttpComp}. We use in our final results $t$,
+definitions. We found no significant difference between them, as it is 
+illustrated in Fig. \ref{fig:ttpComp}. We use in the final results $t$,
 which is the correct definition with the slightly poorer resolution.
@@
 \center
-\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_Q2_shortscenrario.pdf}
-\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_t_shortscenrario.pdf}
+\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_Q2_tcomp.pdf}
+\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_t_tcomp.pdf}
 %\includegraphics[width=7cm]{fig3/ALU_90_p_vs_x_shortscenrario.pdf}
@@
 	(top panels), $x$ (middle panels) or $-t$ (lower panels). Error bars are  
-	statistical, Grey bands represent the systematic errors. The full red lines show
+	statistical, Grey bands represent the systematic uncertainties. The full red lines show
 	the fit of the data with the form of Eq.~\ref{eq:A_LU-coh}.}
@@
 included by accounting for the nucleon off-shellness and kinematics in nuclei. It 
-appears that this model undershoots our results systematically. However, a new independent 
+appears that this model undershoots the results systematically. However, a new independent 
 calculation \cite{Fucini:2018gso}, using similar principles but with a more recent nuclear spectral 
-function, has been able to reproduce the data very well. Since these results are from independent 
-groups, it remains unclear at this point if the difference between them is manly due to the nuclear
-spectral function or to its precise implementation. Another factor in the difference is that the
+function, has been able to reproduce the data very well. Another factor in the difference is that the
 recent calculation from Fucini {\it et al.}~\cite{Fucini:2018gso} benefited from using the precise 
@@
 One of the promise of the helium-4 coherent DVCS was the ease to extract the CFF $\mathcal{H}_A$ from
-data. To do so, we used the form from Eq. \ref{eq:A_LU-coh} to fit the data from Fig. 
-\ref{fig:CohALUphi}. We obtained the real and imaginary parts of the unique helium-4
-CFF presented in Fig. \ref{fig:CohCFF}. The results are rather encouraging, the two parts
-of the CFF are constrained by data without need of any constraint beyond our data points. This 
-capacity to obtain a
+data. To do so, we used the form from Eq. \ref{eq:A_LU-coh} to fit the data in Fig. 
+\ref{fig:CohALUphi}. We presente in Fig. \ref{fig:CohCFF} the real and imaginary parts 
+of the single CFF of the helium-4 nucleus. The results are rather encouraging, the two parts
+of the CFF are constrained by data without the need of any model assumption. This capacity to obtain a
 model independent result with such a limited data set offers a striking contrast with the
@@
 	CFF $\mathcal{H}_A$ as a function of $Q^2$ (left panels), $x$ (middle panels) and 
-	$-t$ (right panels). The red full line red is the theoretical calculation from 
+	$-t$ (right panels). The red full line is the theoretical calculation from 
 	Guzey {\it et al.}~\cite{Guzey:2003jh,Guzey:2008th}, the black dashed line is the same calculation 
@@
 	(top panels), $x$ (middle panels) or $-t$ (lower panels). Error bars are  
-	statistical, Grey bands represent the systematic errors. The data is fitted with the 
+	statistical, Grey bands represent the systematic uncertainties. The data is fitted with the 
 	form $\frac{\alpha \sin(\phi)}{1+\beta \cos(\phi)}$; the results of the 
@@
 Altogether, this result confirms that most models significantly overshoot the data and that 
-the BSA in the incoherent DVCS channel is suppressed by 20 to 30 \%.
+the BSA in the incoherent DVCS channel is suppressed by 20 to 30 \% compared to the free proton.
 
@@
 initial and final state effect contributions could lead to such outcome.
+
+%TODO add sentence on recent theory and one on ALERT
 

### 2020-04-22 eg6-letters/long-paper/source_files/Coh/all_coh_exc_cuts.C

@@ -4,13 +4,14 @@ void all_coh_exc_cuts()
 //=========  (Mon Mar 30 18:54:02 2020) by ROOT version 6.14/04
    TCanvas *all_cus = new TCanvas("all_cus", "",1,1,1200,976);
    gStyle->SetOptFit(1);
+   gStyle->SetOptStat(0);
    all_cus->Range(0,0,1,1);
    all_cus->SetFillColor(0);
    all_cus->SetBorderMode(0);
    all_cus->SetBorderSize(0);
-   all_cus->SetLeftMargin(0.2);
-   all_cus->SetRightMargin(0.05);
-   all_cus->SetBottomMargin(0.2);
+   all_cus->SetLeftMargin(0.1);
+   all_cus->SetRightMargin(0.04);
+   all_cus->SetBottomMargin(0.18);
    all_cus->SetFrameBorderMode(0);
   
 // ------------>Primitives in pad: all_cus_1
@@ -21,9 +22,10 @@ void all_coh_exc_cuts()
    all_cus_1->SetFillColor(0);
    all_cus_1->SetBorderMode(0);
    all_cus_1->SetBorderSize(2);
-   all_cus_1->SetLeftMargin(0.2);
-   all_cus_1->SetRightMargin(0.05);
-   all_cus_1->SetBottomMargin(0.2);
+   all_cus_1->SetLeftMargin(0.1);
+   all_cus_1->SetRightMargin(0.04);
+   all_cus_1->SetBottomMargin(0.18);
+   all_cus_1->SetTopMargin(0.015);
    all_cus_1->SetFrameBorderMode(0);
    all_cus_1->SetFrameBorderMode(0);
    
@@ -122,20 +124,6 @@ void all_coh_exc_cuts()
    h2_delta_phi_Coh__904->SetMaximum(402.6);
    h2_delta_phi_Coh__904->SetEntries(3509);
    
-   TPaveStats *ptstats = new TPaveStats(0.55,0.65,0.9,0.9,"brNDC");
-   ptstats->SetName("stats");
-   ptstats->SetBorderSize(1);
-   ptstats->SetFillColor(0);
-   ptstats->SetTextAlign(12);
-   ptstats->SetTextFont(42);
-   TText *ptstats_LaTex = ptstats->AddText("Entries = 3509   ");
[…]

### 2020-04-22 eg6-letters/long-paper/source_files/InCoh/all_incoh_exc_cuts.C

@@ -9,11 +9,12 @@ void all_incoh_exc_cuts()
    all_cus->SetFillColor(0);
    all_cus->SetBorderMode(0);
    all_cus->SetBorderSize(0);
-   all_cus->SetLeftMargin(0.05);
-   all_cus->SetRightMargin(0.05);
+   all_cus->SetLeftMargin(0.02);
+   all_cus->SetRightMargin(0.02);
    all_cus->SetBottomMargin(0.2);
    all_cus->SetFrameBorderMode(0);
   
+   float L(0.10),R(0.04),T(0.015),B(0.18);
 // ------------>Primitives in pad: all_cus_1
    TPad *all_cus_1 = new TPad("all_cus_1", "all_cus_1",0.01,0.6766667,0.3233333,0.99);
    all_cus_1->Draw();
@@ -21,10 +22,11 @@ void all_incoh_exc_cuts()
    all_cus_1->Range(-12.26667,-263.3714,9.066667,1053.486);
    all_cus_1->SetFillColor(0);
    all_cus_1->SetBorderMode(0);
-   all_cus_1->SetBorderSize(2);
-   all_cus_1->SetLeftMargin(0.12);
-   all_cus_1->SetRightMargin(0.05);
-   all_cus_1->SetBottomMargin(0.2);
+   all_cus_1->SetBorderSize(1);
+   all_cus_1->SetLeftMargin(L);
+   all_cus_1->SetRightMargin(R);
+   all_cus_1->SetTopMargin(T);
+   all_cus_1->SetBottomMargin(B);
    all_cus_1->SetFrameBorderMode(0);
    all_cus_1->SetFrameBorderMode(0);
    
@@ -336,11 +338,11 @@ void all_incoh_exc_cuts()
    h2_delta_phi_InCoh__839->GetXaxis()->SetNdivisions(505);
    h2_delta_phi_InCoh__839->GetYaxis()->SetNdivisions(505);
    h2_delta_phi_InCoh__839->GetXaxis()->SetLabelFont(22);
-   h2_delta_phi_InCoh__839->GetXaxis()->SetLabelSize(0.075);
-   h2_delta_phi_InCoh__839->GetXaxis()->SetTitleSize(0.09);
+   h2_delta_phi_InCoh__839->GetXaxis()->SetLabelSize(0.070);
[…]

### 2020-04-22 eg6-letters/long-paper/source_files/InCoh/ALU_90_p_vs_Q2_shortscenrario.C
Recover files erased by error

@@ -16,7 +16,7 @@ void ALU_90_p_vs_Q2_shortscenrario()
    Can_p_Q2->SetFrameBorderMode(0);
    Can_p_Q2->SetFrameBorderMode(0);
    
-   TH2F *HALU_p_vs_Q2__1 = new TH2F("HALU_p_vs_Q2__1","",100,0.5,4.5,100,-0.1,0.5);
+   TH2F *HALU_p_vs_Q2__1 = new TH2F("HALU_p_vs_Q2__1","",100,0.8,3.8,100,-0.1,0.45);
    HALU_p_vs_Q2__1->SetStats(0);
 
    Int_t ci;      // for color index setting
@@ -25,23 +25,18 @@ void ALU_90_p_vs_Q2_shortscenrario()
    HALU_p_vs_Q2__1->SetLineColor(ci);
    HALU_p_vs_Q2__1->GetXaxis()->SetTitle("Q^{2} [GeV^{2}]");
    HALU_p_vs_Q2__1->GetXaxis()->CenterTitle(true);
-   HALU_p_vs_Q2__1->GetXaxis()->SetNdivisions(605);
-   HALU_p_vs_Q2__1->GetXaxis()->SetLabelFont(22);
-   HALU_p_vs_Q2__1->GetXaxis()->SetLabelSize(0.05);
-   HALU_p_vs_Q2__1->GetXaxis()->SetTitleSize(0.07);
-   HALU_p_vs_Q2__1->GetXaxis()->SetTitleFont(22);
+   HALU_p_vs_Q2__1->GetXaxis()->SetLabelFont(42);
+   HALU_p_vs_Q2__1->GetXaxis()->SetLabelSize(0.045);
+   HALU_p_vs_Q2__1->GetXaxis()->SetTitleSize(0.06);
+   HALU_p_vs_Q2__1->GetXaxis()->SetTitleFont(42);
+   HALU_p_vs_Q2__1->GetXaxis()->SetTitleOffset(0.9);
    HALU_p_vs_Q2__1->GetYaxis()->SetTitle("A_{LU}^{Incoh}(90#circ)");
    HALU_p_vs_Q2__1->GetYaxis()->CenterTitle(true);
-   HALU_p_vs_Q2__1->GetYaxis()->SetNdivisions(605);
-   HALU_p_vs_Q2__1->GetYaxis()->SetLabelFont(22);
[…]

### 2020-04-22 eg6-letters/long-paper/source_files/InCoh/ALU_90_p_vs_t_shortscenrario.C

@@ -16,7 +16,7 @@ void ALU_90_p_vs_t_shortscenrario()
    Can_p_t->SetFrameBorderMode(0);
    Can_p_t->SetFrameBorderMode(0);
    
-   TH2F *HALU_p_vs_t__5 = new TH2F("HALU_p_vs_t__5","",100,0,1.2,100,-0.1,0.5);
+   TH2F *HALU_p_vs_t__5 = new TH2F("HALU_p_vs_t__5","",100,0,1.3,100,-0.1,0.45);
    HALU_p_vs_t__5->SetStats(0);
 
    Int_t ci;      // for color index setting
@@ -26,22 +26,19 @@ void ALU_90_p_vs_t_shortscenrario()
    HALU_p_vs_t__5->GetXaxis()->SetTitle("-t [GeV^{2}]");
    HALU_p_vs_t__5->GetXaxis()->CenterTitle(true);
    HALU_p_vs_t__5->GetXaxis()->SetNdivisions(605);
-   HALU_p_vs_t__5->GetXaxis()->SetLabelFont(22);
-   HALU_p_vs_t__5->GetXaxis()->SetLabelSize(0.05);
-   HALU_p_vs_t__5->GetXaxis()->SetTitleSize(0.07);
-   HALU_p_vs_t__5->GetXaxis()->SetTitleFont(22);
+   HALU_p_vs_t__5->GetXaxis()->SetLabelFont(42);
+   HALU_p_vs_t__5->GetXaxis()->SetLabelSize(0.045);
+   HALU_p_vs_t__5->GetXaxis()->SetTitleSize(0.06);
+   HALU_p_vs_t__5->GetXaxis()->SetTitleFont(42);
+   HALU_p_vs_t__5->GetXaxis()->SetTitleOffset(.9);
    HALU_p_vs_t__5->GetYaxis()->SetTitle("A_{LU}^{Incoh}(90#circ)");
    HALU_p_vs_t__5->GetYaxis()->CenterTitle(true);
    HALU_p_vs_t__5->GetYaxis()->SetNdivisions(605);
-   HALU_p_vs_t__5->GetYaxis()->SetLabelFont(22);
-   HALU_p_vs_t__5->GetYaxis()->SetLabelSize(0.05);
-   HALU_p_vs_t__5->GetYaxis()->SetTitleSize(0.07);
-   HALU_p_vs_t__5->GetYaxis()->SetTitleOffset(0);
[…]

### 2020-04-22 eg6-letters/long-paper/prc-dvcshelium.tex
Small addition to summary

@@
 CLAS at JLab. To properly isolate the coherent channel, the experiment used a specially 
-designed RTPC to detect the scattered helium-4. While statistically limited, this coherent 
+designed RTPC to detect the scattered helium-4. This coherent 
 DVCS measurement reveals the large BSA ($\sim 35$\%) expected by theoretical calculations
@@
 measurements. It remains unclear what is the source of the suppression of the BSA as both 
-initial and final state effect contributions could lead to such outcome.
+initial and final state effect contributions could lead to such outcome. We presented 
+various models for both channels, while old and recent work agree nicely with the data
+from the coherent channel, it appears more difficult to reproduce the incoherent ones.
+A future experimental program using tagging at the upgraded CLAS12 detector is 
+planned to address this question in the coming years by using a new recoil detector 
+design~\cite{Armstrong:2017zcm}.
 
 %TODO add sentence on recent theory and one on ALERT
-
-% \begin{figure}
-% \includegraphics{}%
-% \caption{\label{}}
-% \end{figure}
-
-% Surround figure environment with turnpage environment for landscape
-% figure
-% \begin{turnpage}
-% \begin{figure}
-% \includegraphics{}%
-% \caption{\label{}}
-% \end{figure}
-% \end{turnpage}
-
-% tables should appear as floats within the text
-%
-% Here is an example of the general form of a table:
-% Fill in the caption in the braces of the \caption{} command. Put the label
-% that you will use with \ref{} command in the braces of the \label{} command.
-% Insert the column specifiers (l, r, c, d, etc.) in the empty braces of the
-% \begin{tabular}{} command.
-% The ruledtabular enviroment adds doubled rules to table and sets a
-% reasonable default table settings.
-% Use the table* environment to get a full-width table in two-column
-% Add \usepackage{longtable} and the longtable (or longtable*}
-% environment for nicely formatted long tables. Or use the the [H]
-% placement option to break a long table (with less control than 
-% in longtable).
-% \begin{table}%[H] add [H] placement to break table across pages
-% \caption{\label{}}
-% \begin{ruledtabular}
-% \begin{tabular}{}
-% Lines of table here ending with \\
-% \end{tabular}
-% \end{ruledtabular}
-% \end{table}
-
-% Specify following sections are appendices. Use \appendix* if there
-% only one appendix.
-%\appendix
-%\section{}
-
-% Surround table environment with turnpage environment for landscape
-% table
-% \begin{turnpage}
-% \begin{table}
-% \caption{\label{}}
-% \begin{ruledtabular}
-% \begin{tabular}{}
-% \end{tabular}
-% \end{ruledtabular}
-% \end{table}
-% \end{turnpage}
 
@@
 
-\section{Table of results with information on full kinematics}
+\section{Table of results with kinematic information}
 \label{sec:fullresults}
- tests
+
+\begin{table}[!h]
+   \begin{center}
+      \begin{tabular}{||l|l|l|l|l||}
+         \hline
+ $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
+         \hline
+  1.143 & 0.136 & 0.096 & 24.3  &  0.1327 $\pm$ 0.1088 $\pm$ 0.0257 \\ 
+  1.143 & 0.136 & 0.096 & 61.1  &  0.3210 $\pm$ 0.0932 $\pm$ 0.0188 \\ 
+  1.143 & 0.136 & 0.096 & 98.9  &  0.3709 $\pm$ 0.1026 $\pm$ 0.0403 \\ 
+  1.143 & 0.136 & 0.096 & 140.9 &  0.2452 $\pm$ 0.1517 $\pm$ 0.0267 \\ 
+  1.143 & 0.136 & 0.096 & 178.4 &  0.0225 $\pm$ 0.1632 $\pm$ 0.0278 \\ 
+  1.143 & 0.136 & 0.096 & 219.1 & -0.0526 $\pm$ 0.1475 $\pm$ 0.0248 \\ 
+  1.143 & 0.136 & 0.096 & 262.9 & -0.2642 $\pm$ 0.1196 $\pm$ 0.0389 \\ 
+  1.143 & 0.136 & 0.096 & 301.9 & -0.1761 $\pm$ 0.0968 $\pm$ 0.0263 \\ 
+  1.143 & 0.136 & 0.096 & 337.7 & -0.2791 $\pm$ 0.1047 $\pm$ 0.0343 \\ 
+  \hline                                                                                                           
+  1.423 & 0.172 & 0.099 & 21.1  &  0.1917 $\pm$ 0.0892 $\pm$ 0.0267 \\ 
+  1.423 & 0.172 & 0.099 & 56.6  &  0.2819 $\pm$ 0.0866 $\pm$ 0.0250 \\ 
+  1.423 & 0.172 & 0.099 & 96.9  &  0.4855 $\pm$ 0.1291 $\pm$ 0.0426 \\ 
+  1.423 & 0.172 & 0.099 & 139.9 &  0.0996 $\pm$ 0.1679 $\pm$ 0.0250 \\ 
+  1.423 & 0.172 & 0.099 & 180.3 &  0.1458 $\pm$ 0.1906 $\pm$ 0.0302 \\ 
+  1.423 & 0.172 & 0.099 & 218.7 & -0.1109 $\pm$ 0.1853 $\pm$ 0.0344 \\ 
+  1.423 & 0.172 & 0.099 & 263.1 & -0.3516 $\pm$ 0.1371 $\pm$ 0.0366 \\ 
+  1.423 & 0.172 & 0.099 & 302.2 & -0.4141 $\pm$ 0.0842 $\pm$ 0.0383 \\ 
+  1.423 & 0.172 & 0.099 & 338.2 & -0.2786 $\pm$ 0.0836 $\pm$ 0.0261 \\ 
+  \hline                                                                                                           
+  1.902 & 0.224 & 0.107 & 21.4  &  0.1803 $\pm$ 0.0805 $\pm$ 0.0234 \\ 
+  1.902 & 0.224 & 0.107 & 57.2  &  0.3501 $\pm$ 0.0824 $\pm$ 0.0185 \\ 
+  1.902 & 0.224 & 0.107 & 96.2  &  0.2701 $\pm$ 0.1230 $\pm$ 0.0173 \\ 
+  1.902 & 0.224 & 0.107 & 139.5 &  0.3053 $\pm$ 0.2390 $\pm$ 0.0170 \\ 
+  1.902 & 0.224 & 0.107 & 178.2 &  0.1028 $\pm$ 0.2670 $\pm$ 0.0126 \\ 
+  1.902 & 0.224 & 0.107 & 221.4 & -0.2118 $\pm$ 0.2147 $\pm$ 0.0152 \\ 
+  1.902 & 0.224 & 0.107 & 263.3 & -0.3060 $\pm$ 0.1306 $\pm$ 0.0260 \\ 
+  1.902 & 0.224 & 0.107 & 303.3 & -0.1384 $\pm$ 0.0944 $\pm$ 0.0207 \\ 
+  1.902 & 0.224 & 0.107 & 338.5 & -0.1633 $\pm$ 0.0791 $\pm$ 0.0163 \\ 
+         \hline \hline
+      \end{tabular}
+      \caption{Values of the coherent $A_{LU}$ in $Q^2$ bins from Fig. \ref{fig:CohALUphi}.}
+      \label{table:Coh_Q2_BSA}
+   \end{center}
+\end{table}
+
+\begin{table}[!h]
+   \begin{center}
+      \begin{tabular}{||l|l|l|l|l||}
+         \hline
+ $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
+         \hline
+
+  1.164 & 0.132 & 0.095 & 25.6  &  0.0174 $\pm$ 0.1440 $\pm$ 0.0221 \\
+  1.164 & 0.132 & 0.095 & 61.6  &  0.3478 $\pm$ 0.0867 $\pm$ 0.0198 \\
+  1.164 & 0.132 & 0.095 & 99.0  &  0.3808 $\pm$ 0.0948 $\pm$ 0.0408 \\
+  1.164 & 0.132 & 0.095 & 141.7 &  0.2943 $\pm$ 0.1379 $\pm$ 0.0333 \\
+  1.164 & 0.132 & 0.095 & 178.1 &  0.0433 $\pm$ 0.1519 $\pm$ 0.0293 \\
+  1.164 & 0.132 & 0.095 & 218.5 & -0.0352 $\pm$ 0.1316 $\pm$ 0.0243 \\
+  1.164 & 0.132 & 0.095 & 262.7 & -0.2771 $\pm$ 0.1050 $\pm$ 0.0372 \\
+  1.164 & 0.132 & 0.095 & 300.7 & -0.2138 $\pm$ 0.0836 $\pm$ 0.0259 \\
+  1.164 & 0.132 & 0.095 & 335.2 & -0.2339 $\pm$ 0.1221 $\pm$ 0.0319 \\
+   \hline                                                                                                         
+  1.439 & 0.17 & 0.099 &  22.9  &  0.1579 $\pm$ 0.0853 $\pm$ 0.0230 \\
+  1.439 & 0.17 & 0.099 &  57.1  &  0.1733 $\pm$ 0.0880 $\pm$ 0.0195 \\
+  1.439 & 0.17 & 0.099 &  96.3  &  0.2259 $\pm$ 0.1331 $\pm$ 0.0295 \\
+  1.439 & 0.17 & 0.099 &  139.1 &  0.2454 $\pm$ 0.1758 $\pm$ 0.0187 \\
+  1.439 & 0.17 & 0.099 &  180.1 & -0.1021 $\pm$ 0.1918 $\pm$ 0.0197 \\
+  1.439 & 0.17 & 0.099 &  218.9 & -0.2876 $\pm$ 0.1909 $\pm$ 0.0270 \\
+  1.439 & 0.17 & 0.099 &  263.9 & -0.2943 $\pm$ 0.1360 $\pm$ 0.0292 \\
+  1.439 & 0.17 & 0.099 &  302.5 & -0.3979 $\pm$ 0.0921 $\pm$ 0.0331 \\
+  1.439 & 0.17 & 0.099 &  338.1 & -0.2692 $\pm$ 0.0834 $\pm$ 0.0254 \\
+   \hline                                                                                                         
+  1.844 & 0.225 & 0.107 & 20.1  &  0.2626 $\pm$ 0.0755 $\pm$ 0.0248 \\
+  1.844 & 0.225 & 0.107 & 55.9  &  0.4281 $\pm$ 0.0887 $\pm$ 0.0224 \\
+  1.844 & 0.225 & 0.107 & 96.4  &  0.4925 $\pm$ 0.1390 $\pm$ 0.0271 \\
+  1.844 & 0.225 & 0.107 & 137.7 & -0.2736 $\pm$ 0.2804 $\pm$ 0.0166 \\
+  1.844 & 0.225 & 0.107 & 179.8 &  0.8470 $\pm$ 0.2497 $\pm$ 0.0204 \\
+  1.844 & 0.225 & 0.107 & 224.7 & -0.0513 $\pm$ 0.2811 $\pm$ 0.0270 \\
+  1.844 & 0.225 & 0.107 & 262.8 & -0.3416 $\pm$ 0.1694 $\pm$ 0.0353 \\
+  1.844 & 0.225 & 0.107 & 304.5 & -0.1359 $\pm$ 0.1025 $\pm$ 0.0263 \\
+  1.844 & 0.225 & 0.107 & 339.8 & -0.1658 $\pm$ 0.0770 $\pm$ 0.0175 \\
+
+         \hline 
+         \hline
+      \end{tabular}
+      \caption{Values of the coherent $A_{LU}$ in $x_B$ bins from Fig. \ref{fig:CohALUphi}.}
+      \label{table:Coh_xB_BSA}
+   \end{center}
+\end{table}
+
+\begin{table}[!h]
+   \begin{center}
+      \begin{tabular}{||l|l|l|l|l||}
+         \hline
+ $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
+  \hline
+  1.36 & 0.160 & 0.080  & 22.8  &  0.2378 $\pm$ 0.0928 $\pm$ 0.0263 \\
+  1.36 & 0.160 & 0.080  & 57.6  &  0.3014 $\pm$ 0.0874 $\pm$ 0.0243 \\
+  1.36 & 0.160 & 0.080  & 98.1  &  0.4896 $\pm$ 0.1118 $\pm$ 0.0394 \\
+  1.36 & 0.160 & 0.080  & 139.3 &  0.1965 $\pm$ 0.1595 $\pm$ 0.0252 \\
+  1.36 & 0.160 & 0.080  & 178.8 &  0.0577 $\pm$ 0.1923 $\pm$ 0.0371 \\
+  1.36 & 0.160 & 0.080  & 222.6 & -0.1651 $\pm$ 0.1640 $\pm$ 0.0370 \\
+  1.36 & 0.160 & 0.080  & 265.6 & -0.3467 $\pm$ 0.1339 $\pm$ 0.0403 \\
+  1.36 & 0.160 & 0.080  & 300.0 & -0.2891 $\pm$ 0.0928 $\pm$ 0.0294 \\
+  1.36 & 0.160 & 0.080  & 339.3 & -0.1849 $\pm$ 0.0856 $\pm$ 0.0281 \\
+  \hline                                                                
+  1.507 & 0.179 & 0.094 & 21.1  &  0.2481 $\pm$ 0.0931 $\pm$ 0.0267 \\ 
+  1.507 & 0.179 & 0.094 & 56.4  &  0.3386 $\pm$ 0.0828 $\pm$ 0.0284 \\ 
+  1.507 & 0.179 & 0.094 & 97.5  &  0.3467 $\pm$ 0.1156 $\pm$ 0.0307 \\ 
+  1.507 & 0.179 & 0.094 & 141.9 &  0.1464 $\pm$ 0.1887 $\pm$ 0.0215 \\ 
+  1.507 & 0.179 & 0.094 & 179.5 & -0.2814 $\pm$ 0.1864 $\pm$ 0.0360 \\ 
+  1.507 & 0.179 & 0.094 & 218.5 &  0.2104 $\pm$ 0.1998 $\pm$ 0.0147 \\ 
+  1.507 & 0.179 & 0.094 & 262.8 & -0.2399 $\pm$ 0.1280 $\pm$ 0.0283 \\ 
+  1.507 & 0.179 & 0.094 & 303.5 & -0.1989 $\pm$ 0.0955 $\pm$ 0.0286 \\ 
+  1.507 & 0.179 & 0.094 & 338.5 & -0.2098 $\pm$ 0.0875 $\pm$ 0.0201 \\ 
+  \hline                                                                                                                 
+  1.610 & 0.193 & 0.127 & 22.3  &  0.0280 $\pm$ 0.0909 $\pm$ 0.0214 \\
+  1.610 & 0.193 & 0.127 & 60.7  &  0.3582 $\pm$ 0.0932 $\pm$ 0.0204 \\
+  1.610 & 0.193 & 0.127 & 96.8  &  0.2559 $\pm$ 0.1269 $\pm$ 0.0313 \\
+  1.610 & 0.193 & 0.127 & 139.9 &  0.2207 $\pm$ 0.1930 $\pm$ 0.0203 \\
+  1.610 & 0.193 & 0.127 & 178.5 &  0.5138 $\pm$ 0.1832 $\pm$ 0.0354 \\
+  1.610 & 0.193 & 0.127 & 217.5 & -0.2473 $\pm$ 0.1664 $\pm$ 0.0189 \\
+  1.610 & 0.193 & 0.127 & 260.9 & -0.2919 $\pm$ 0.1295 $\pm$ 0.0327 \\
+  1.610 & 0.193 & 0.127 & 303.4 & -0.2488 $\pm$ 0.0892 $\pm$ 0.0280 \\
+  1.610 & 0.193 & 0.127 & 336.8 & -0.2825 $\pm$ 0.0901 $\pm$ 0.0261 \\
+         \hline
+         \hline
+      \end{tabular}
+      \caption{Values of the coherent $A_{LU}$ in $-t$ bins from Fig. \ref{fig:CohALUphi}.}
+      \label{table:Coh_t_BSA}
+   \end{center}
+\end{table}
+
+% incoherent channel
+
+\begin{table}[!h]
+   \begin{center}
+      \begin{tabular}{||l|l|l|l|l||}
+         \hline
+ $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
+ \hline 
+  1.404 & 0.166 & 0.376  &   21.0 &   0.0541 $\pm$  0.0442  $\pm$ 0.0120 \\
+  1.404 & 0.166 & 0.376  &   62.9 &   0.0771 $\pm$  0.0461  $\pm$ 0.0156 \\
+  1.404 & 0.166 & 0.376  &   95.4 &   0.1913 $\pm$  0.0472  $\pm$ 0.0263 \\
+  1.404 & 0.166 & 0.376  &  140.1 &   0.1076 $\pm$  0.0561  $\pm$ 0.0158 \\
+  1.404 & 0.166 & 0.376  &  182.3 &   0.0448 $\pm$  0.0693  $\pm$ 0.0234 \\
+  1.404 & 0.166 & 0.376  &  220.4 &  -0.0294 $\pm$  0.0675  $\pm$ 0.0150 \\
+  1.404 & 0.166 & 0.376  &  258.4 &  -0.1261 $\pm$  0.0459  $\pm$ 0.0226 \\
+  1.404 & 0.166 & 0.376  &  303.1 &  -0.1238 $\pm$  0.0401  $\pm$ 0.0196 \\
+  1.404 & 0.166 & 0.376  &  337.4 &  -0.0122 $\pm$  0.0537  $\pm$ 0.0142 \\
+  \hline                                                              
+  1.889 & 0.232 & 0.415  &   20.3 &   0.0143 $\pm$  0.0355  $\pm$ 0.0124 \\
+  1.889 & 0.232 & 0.415  &   60.5 &   0.0668 $\pm$  0.0464  $\pm$ 0.0169 \\
+  1.889 & 0.232 & 0.415  &   95.8 &   0.1297 $\pm$  0.0521  $\pm$ 0.0202 \\
+  1.889 & 0.232 & 0.415  &  140.9 &   0.1651 $\pm$  0.0771  $\pm$ 0.0285 \\
+  1.889 & 0.232 & 0.415  &  179.7 &   0.1589 $\pm$  0.0894  $\pm$ 0.0146 \\
+  1.889 & 0.232 & 0.415  &  221.5 &  -0.2594 $\pm$  0.0808  $\pm$ 0.0430 \\
+  1.889 & 0.232 & 0.415  &  260.3 &  -0.1280 $\pm$  0.0559  $\pm$ 0.0180 \\
+  1.889 & 0.232 & 0.415  &  303.5 &  -0.1762 $\pm$  0.0386  $\pm$ 0.0198 \\
+  1.889 & 0.232 & 0.415  &  338.2 &  -0.0303 $\pm$  0.0447  $\pm$ 0.0113 \\
+  \hline                                                              
+  2.339 & 0.288 & 0.497  &  20.8  &  0.0740  $\pm$  0.0330  $\pm$ 0.0135 \\
+  2.339 & 0.288 & 0.497  &  58.2  &  0.1359  $\pm$  0.0458  $\pm$ 0.0101 \\
+  2.339 & 0.288 & 0.497  &  94.7  &  0.1836  $\pm$  0.0567  $\pm$ 0.0176 \\
+  2.339 & 0.288 & 0.497  & 140.9  & -0.0178  $\pm$  0.1008  $\pm$ 0.0161 \\
+  2.339 & 0.288 & 0.497  & 181.8  &  0.0922  $\pm$  0.1329  $\pm$ 0.0236 \\
+  2.339 & 0.288 & 0.497  & 225.0  & -0.0751  $\pm$  0.1066  $\pm$ 0.0212 \\
+  2.339 & 0.288 & 0.497  & 261.0  & -0.2439  $\pm$  0.0596  $\pm$ 0.0241 \\
+  2.339 & 0.288 & 0.497  & 303.0  & -0.1977  $\pm$  0.0384  $\pm$ 0.0153 \\
+  2.339 & 0.288 & 0.497  & 338.7  & -0.0889  $\pm$  0.0397  $\pm$ 0.0145 \\
+  \hline                                                              
+  3.098 & 0.379 & 0.641  & 20.1   & 0.0959   $\pm$  0.0305  $\pm$ 0.0147 \\ 
+  3.098 & 0.379 & 0.641  & 57.1   & 0.0817   $\pm$  0.0478  $\pm$ 0.0147 \\
+  3.098 & 0.379 & 0.641  & 94.2   & 0.1632   $\pm$  0.0684  $\pm$ 0.0281 \\
+  3.098 & 0.379 & 0.641  &137.7   & 0.0930   $\pm$  0.1412  $\pm$ 0.0129 \\
+  3.098 & 0.379 & 0.641  &180.2   &-0.2272   $\pm$  0.1918  $\pm$ 0.0270 \\
+  3.098 & 0.379 & 0.641  &226.0   &-0.0333   $\pm$  0.1599  $\pm$ 0.0273 \\
+  3.098 & 0.379 & 0.641  &263.9   &-0.1630   $\pm$  0.0802  $\pm$ 0.0214 \\
+  3.098 & 0.379 & 0.641  &303.2   &-0.1644   $\pm$  0.0405  $\pm$ 0.0221 \\
+  3.098 & 0.379 & 0.641  &340.5   &-0.0914   $\pm$  0.0368  $\pm$ 0.0141 \\
+ \hline
+ \hline
+      \end{tabular}
+      \caption{Values of the incoherent $A_{LU}$ in $Q^2$ bins from Fig. \ref{fig:InCohALUphi}.}
+      \label{table:InCoh_Q2_BSA}
+   \end{center}
+\end{table}
+
+\begin{table}[!h]
+   \begin{center}
+      \begin{tabular}{||l|l|l|l|l||}
+         \hline
+ $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
+         \hline
+ 1.449 & 0.163 & 0.374 &  21.0  &  0.0935 $\pm$ 0.0463  $\pm$  0.0137 \\ 
+  1.449 & 0.163 & 0.374 &  63.4  &  0.0690 $\pm$ 0.0442  $\pm$  0.0165 \\ 
+  1.449 & 0.163 & 0.374 &  95.6  &  0.1469 $\pm$ 0.0439  $\pm$  0.0216 \\ 
+  1.449 & 0.163 & 0.374 & 140.3  &  0.1017 $\pm$ 0.0519  $\pm$  0.0149 \\ 
+  1.449 & 0.163 & 0.374 & 181.3  &  0.0707 $\pm$ 0.0619  $\pm$  0.0235 \\ 
+  1.449 & 0.163 & 0.374 & 220.0  & -0.0446 $\pm$ 0.0616  $\pm$  0.0199 \\ 
+  1.449 & 0.163 & 0.374 & 258.5  & -0.1145 $\pm$ 0.0433  $\pm$  0.0183 \\ 
+  1.449 & 0.163 & 0.374 & 303.0  & -0.0977 $\pm$ 0.0394  $\pm$  0.0154 \\ 
+  1.449 & 0.163 & 0.374 & 336.9  &  0.0329 $\pm$ 0.0565  $\pm$  0.0105 \\ 
+  \hline
+  1.929 & 0.225 & 0.381 &  21.5  &  0.0016 $\pm$ 0.0383  $\pm$  0.0131 \\
+  1.929 & 0.225 & 0.381 &  60.3  &  0.0556 $\pm$ 0.0441  $\pm$  0.0161 \\
+  1.929 & 0.225 & 0.381 &  96.0  &  0.1681 $\pm$ 0.0495  $\pm$  0.0183 \\
+  1.929 & 0.225 & 0.381 & 141.2  &  0.1422 $\pm$ 0.0788  $\pm$  0.0246 \\
+  1.929 & 0.225 & 0.381 & 181.5  &  0.1672 $\pm$ 0.0957  $\pm$  0.0165 \\
+  1.929 & 0.225 & 0.381 & 223.1  & -0.2619 $\pm$ 0.0828  $\pm$  0.0343 \\
+  1.929 & 0.225 & 0.381 & 260.2  & -0.1845 $\pm$ 0.0517  $\pm$  0.0227 \\
+  1.929 & 0.225 & 0.381 & 303.0  & -0.1962 $\pm$ 0.0367  $\pm$  0.0206 \\
+  1.929 & 0.225 & 0.381 & 336.8  & -0.0410 $\pm$ 0.0455  $\pm$  0.0100 \\
+  \hline
+  2.334 & 0.283 & 0.468 &  20.9  &  0.0687 $\pm$ 0.0327  $\pm$  0.0198 \\
+  2.334 & 0.283 & 0.468 &  59.2  &  0.1242 $\pm$ 0.0456  $\pm$  0.0195 \\
+  2.334 & 0.283 & 0.468 &  94.1  &  0.1648 $\pm$ 0.0583  $\pm$  0.0188 \\
+  2.334 & 0.283 & 0.468 & 139.3  &  0.1118 $\pm$ 0.1102  $\pm$  0.0242 \\
+  2.334 & 0.283 & 0.468 & 180.7  & -0.1943 $\pm$ 0.1545  $\pm$  0.0145 \\
+  2.334 & 0.283 & 0.468 & 225.2  &  0.0081 $\pm$ 0.1109  $\pm$  0.0140 \\
+  2.334 & 0.283 & 0.468 & 261.4  & -0.2416 $\pm$ 0.0660  $\pm$  0.0272 \\
+  2.334 & 0.283 & 0.468 & 303.3  & -0.1712 $\pm$ 0.0375  $\pm$  0.0178 \\
+  2.334 & 0.283 & 0.468 & 338.4  & -0.0649 $\pm$ 0.0406  $\pm$  0.0101 \\
+  \hline
+  2.975 & 0.389 & 0.688 &   19.6 &   0.0809$\pm$  0.0289 $\pm$  0.0143 \\
+  2.975 & 0.389 & 0.688 &   55.1 &   0.1214$\pm$  0.0539 $\pm$  0.0148 \\
+  2.975 & 0.389 & 0.688 &   93.4 &   0.2530$\pm$  0.0899 $\pm$  0.0313 \\
+  2.975 & 0.389 & 0.688 &  135.1 &  -0.2304$\pm$  0.2247 $\pm$  0.0386 \\
+  2.975 & 0.389 & 0.688 &  179.9 &  -0.0522$\pm$  0.4248 $\pm$  0.0364 \\
+  2.975 & 0.389 & 0.688 &  230.5 &  -0.3766$\pm$  0.3336 $\pm$  0.0469 \\
+  2.975 & 0.389 & 0.688 &  265.5 &  -0.0929$\pm$  0.1030 $\pm$  0.0202 \\
+  2.975 & 0.389 & 0.688 &  303.4 &  -0.1977$\pm$  0.0453 $\pm$  0.0229 \\
+  2.975 & 0.389 & 0.688 &  341.2 &  -0.1084$\pm$  0.0352 $\pm$  0.0156 \\
+ \hline
+ \hline
+ \end{tabular}
+ \caption{Values of the incoherent $A_{LU}$ in $x_B$ bins from Fig. \ref{fig:InCohALUphi}.}
+ \label{table:InCoh_xB_BSA}
+ \end{center}
+\end{table}
+
+\begin{table}[!h]
+   \begin{center}
+      \begin{tabular}{||l|l|l|l|l||}
+         \hline
+ $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
+  \hline
+  1.842 & 0.215 & 0.135  &   21.6  &  0.1197  $\pm$  0.0369 $\pm$ 0.0135 \\ 
+  1.842 & 0.215 & 0.135  &   60.6  &  0.0273  $\pm$  0.0416 $\pm$ 0.0190 \\ 
+  1.842 & 0.215 & 0.135  &   96.3  &  0.2189  $\pm$  0.0409 $\pm$ 0.0179 \\ 
+  1.842 & 0.215 & 0.135  &  141.9  &  0.1502  $\pm$  0.0542 $\pm$ 0.0263 \\ 
+  1.842 & 0.215 & 0.135  &  179.8  &  0.0083  $\pm$  0.0670 $\pm$ 0.0150 \\ 
+  1.842 & 0.215 & 0.135  &  220.7  & -0.1185  $\pm$  0.0653 $\pm$ 0.0182 \\ 
+  1.842 & 0.215 & 0.135  &  259.6  & -0.2041  $\pm$  0.0430 $\pm$ 0.0195 \\ 
+  1.842 & 0.215 & 0.135  &  303.3  & -0.1605  $\pm$  0.0369 $\pm$ 0.0137 \\ 
+  1.842 & 0.215 & 0.135  &  337.5  & -0.0493  $\pm$  0.0469 $\pm$ 0.0100 \\ 
+  \hline
+
+  2.149 & 0.257 & 0.281  &  21.4   & 0.0356   $\pm$ 0.0400  $\pm$ 0.0131 \\
+  2.149 & 0.257 & 0.281  &  60.9   & 0.0927   $\pm$ 0.0454  $\pm$ 0.0125 \\
+  2.149 & 0.257 & 0.281  &  95.7   & 0.1488   $\pm$ 0.0510  $\pm$ 0.0338 \\
+  2.149 & 0.257 & 0.281  & 139.3   & 0.1112   $\pm$ 0.0732  $\pm$ 0.0178 \\
+  2.149 & 0.257 & 0.281  & 183.3   & 0.1052   $\pm$ 0.0933  $\pm$ 0.0298 \\
+  2.149 & 0.257 & 0.281  & 222.8   &-0.0744   $\pm$ 0.0760  $\pm$ 0.0183 \\
+  2.149 & 0.257 & 0.281  & 259.3   &-0.0912   $\pm$ 0.0549  $\pm$ 0.0253 \\
+  2.149 & 0.257 & 0.281  & 302.2   &-0.2004   $\pm$ 0.0390  $\pm$ 0.0248 \\
+  2.149 & 0.257 & 0.281  & 337.8   &-0.1041   $\pm$ 0.0468  $\pm$ 0.0171 \\
+  \hline
+
+  2.366 & 0.291 & 0.492  &   20.8  &  0.1113  $\pm$ 0.0371  $\pm$ 0.0154 \\
+  2.366 & 0.291 & 0.492  &   59.9  &  0.1542  $\pm$ 0.0449  $\pm$ 0.0175 \\
+  2.366 & 0.291 & 0.492  &   94.1  &  0.0957  $\pm$ 0.0598  $\pm$ 0.0147 \\
+  2.366 & 0.291 & 0.492  &  137.7  & -0.1066  $\pm$ 0.1051  $\pm$ 0.0166 \\
+  2.366 & 0.291 & 0.492  &  182.9  &  0.2483  $\pm$ 0.1187  $\pm$ 0.0392 \\
+  2.366 & 0.291 & 0.492  &  223.6  & -0.0691  $\pm$ 0.1101  $\pm$ 0.0125 \\
+  2.366 & 0.291 & 0.492  &  261.1  & -0.1898  $\pm$ 0.0616  $\pm$ 0.0234 \\
+  2.366 & 0.291 & 0.492  &  302.7  & -0.1744  $\pm$ 0.0363  $\pm$ 0.0162 \\
+  2.366 & 0.291 & 0.492  &  337.8  & -0.0666  $\pm$ 0.0466  $\pm$ 0.0178 \\
+  \hline
+
+  2.447 & 0.312 & 1.089  &  19.7   & 0.0317   $\pm$ 0.0304  $\pm$ 0.0178 \\
+  2.447 & 0.312 & 1.089  &  56.7   & 0.0910   $\pm$ 0.0584  $\pm$ 0.0108 \\
+  2.447 & 0.312 & 1.089  &  90.6   & 0.1629   $\pm$ 0.1117  $\pm$ 0.0110 \\
+  2.447 & 0.312 & 1.089  & 131.2   & 0.0424   $\pm$ 0.3072  $\pm$ 0.0177 \\
+  2.447 & 0.312 & 1.089  & 175.3   &-0.9355   $\pm$ 0.3971  $\pm$ 0.0181 \\
+  2.447 & 0.312 & 1.089  & 230.5   &-1.1889   $\pm$ 0.5170  $\pm$ 0.0151 \\
+  2.447 & 0.312 & 1.089  & 264.3   &-0.0721   $\pm$ 0.1091  $\pm$ 0.0171 \\
+  2.447 & 0.312 & 1.089  & 304.8   &-0.1190   $\pm$ 0.0475  $\pm$ 0.0129 \\
+  2.447 & 0.312 & 1.089  & 340.5   &-0.0442   $\pm$ 0.0364  $\pm$ 0.0164 \\
+
+ \hline
+ \hline
+ \end{tabular}
+ \caption{Values of the incoherent $A_{LU}$ in $-t$ bins from Fig. \ref{fig:InCohALUphi}.}
+ \label{table:InCoh_t_BSA}
+ \end{center}
+\end{table}
 

### 2020-04-24 eg6-letters/long-paper/prc-dvcshelium.tex
Update Fucini's results with authors comments

@@
 appears that this model undershoots the results systematically. However, a new independent 
-calculation \cite{Fucini:2018gso}, using similar principles but with a more recent nuclear spectral 
-function, has been able to reproduce the data very well. Another factor in the difference is that the
-recent calculation from Fucini {\it et al.}~\cite{Fucini:2018gso} benefited from using the precise 
-kinematic of each points. This feature appears to have a significant impact on some points, for 
-instance the $-t$ distribution appears to have a peculiar structure well reproduced by the 
-calculation. For this reason, we provide the detailed kinematic of each result presented in
-appendix \ref{sec:fullresults}.
+calculation \cite{Fucini:2018gso}, using similar principles but with a non diagonal nuclear spectral 
+function \cite{Viviani:2001wu} based on the Av18 nucleon-nucleon potential \cite{Wiringa:1994wb} 
+and the UIV three-body forces \cite{Pudliner:1995wk}, has been able to reproduce the data very 
+well. Another factor in the difference is that the recent calculation from Fucini {\it et 
+al.}~\cite{Fucini:2018gso} benefited from using the precise kinematic of each points presented 
+in appendix \ref{sec:fullresults}. Including this information appears to have a significant 
+impact on some points, for instance the $-t$ distribution appears to have a peculiar structure 
+which is well reproduced when using this information.
 
@@
 Notably, the calculation from Fucini {\it et al.}~\cite{Fucini:2019xlc} appears closer to the
-others, hinting that maybe the better results with the raw asymmetries was linked to the
-input model they used for the free nucleon GPD. Also, they appear to somewhat reproduce the 
+other with this observable, hinting that maybe the different results with the raw asymmetries 
+was linked to the input model they used for the free nucleon GPD rather than the nuclear model. 
+Also, they appear to reproduce the 
 shape of the $x_B$ distribution, which would indicate that it is linked to kinematic effects.
@@
 	from Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
-	with red full line and dashed blue, the calculation from Fucini 
+	with red full line and dashed blue, a calculation adapted from Fucini 
 	{\it et al.}~\cite{Fucini:2019xlc} is shown with a magenta long dash line and the

### 2020-04-24 eg6-letters/long-paper/source_files/InCoh/ALU_90_p_vs_Q2_shortscenrario.C

@@ -94,10 +94,10 @@ void ALU_90_p_vs_Q2_shortscenrario()
    2.34,
    3.10};
    Double_t _sy1[4] = {
-   0.2477,
-   0.2241,
-   0.1918,
-   0.1463};
+   0.233,
+   0.205,
+   0.175,
+   0.134};
    TGraph *graphS = new TGraph(4,_sx1,_sy1);
    graphS->SetLineStyle(9);
    graphS->SetLineWidth(2);
@@ -114,7 +114,7 @@ void ALU_90_p_vs_Q2_shortscenrario()
    TLegendEntry *entry;
    entry=leg->AddEntry("clas","CLAS (this work)","p");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Scope","Fucini et al. [37]","l");
+   entry=leg->AddEntry("Scope","Fucini et al. [40]","l");
    entry->SetLineStyle(9);
    entry->SetLineWidth(2);
    entry->SetLineColor(6);

### 2020-04-24 eg6-letters/long-paper/source_files/InCoh/ALU_90_p_vs_t_shortscenrario.C

@@ -97,14 +97,14 @@ void ALU_90_p_vs_t_shortscenrario()
    0.490,
    1.11 };
    Double_t _sy1[4] = {
-   0.1455,
-   0.1644,
-   0.1902,
-   0.1728};
-// 0.140,
-// 0.155,
-// 0.173,
-// 0.165};
+// 0.1455,
+// 0.1644,
+// 0.1902,
+// 0.1728};
+   0.140,
+   0.155,
+   0.173,
+   0.165};
    TGraph *graphS = new TGraph(4,_sx1,_sy1);
    graphS->SetLineStyle(9);
    graphS->SetLineWidth(2);
@@ -181,7 +181,11 @@ void ALU_90_p_vs_t_shortscenrario()
    0.0997915,
    0.1352,
    0.199169,
-   0.243986,
+   0.243986,  
+  
+  
+  
+
    0.273819,
    0.29121,
    0.298917,
@@ -302,7 +306,7 @@ void ALU_90_p_vs_t_shortscenrario()
    entry=leg->AddEntry("Graph1","HERMES [10]","P");
    entry=leg->AddEntry("Graph3","Liuti et al. (low x_{B}) [29]","L");
    entry=leg->AddEntry("Graph4","Liuti et al. (high x_{B}) [29]","L");
-   entry=leg->AddEntry("GraphS","Fucini et al. [37]","L");
+   entry=leg->AddEntry("GraphS","Fucini et al. [40]","L");
    entry->SetLineStyle(9);
    entry->SetLineWidth(2);
    entry->SetLineColor(6);

### 2020-04-24 eg6-letters/long-paper/source_files/InCoh/ALU_90_p_vs_x_shortscenrario.C

@@ -142,14 +142,14 @@ void ALU_90_p_vs_x_shortscenrario()
    0.287,
    0.390};
    Double_t _sy1[4] = {
-   0.2084,
-   0.2003,
-   0.1847,
-   0.1625};
-// 0.192,
-// 0.185,
-// 0.169,
-// 0.147};
+// 0.2084,
+// 0.2003,
+// 0.1847,
+// 0.1625};
+   0.192,
+   0.185,
+   0.169,
+   0.147};
    TGraph *graphS = new TGraph(4,_sx1,_sy1);
    graphS->SetLineStyle(9);
    graphS->SetLineWidth(2);
@@ -214,7 +214,7 @@ void ALU_90_p_vs_x_shortscenrario()
    entry->SetTextFont(42);
    entry=leg->AddEntry("Graph2","Liuti et al. (high -t) [29]","L");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("GraphS","Fucini et al. [37]","L");
+   entry=leg->AddEntry("GraphS","Fucini et al. [40]","L");
    entry->SetLineStyle(9);
    entry->SetLineWidth(2);
    entry->SetLineColor(6);

### 2020-04-24 eg6-letters/long-paper/source_files/InCoh/ALU_ratioInc_Q2_shortscenrario.C

@@ -130,7 +130,7 @@ void ALU_ratioInc_Q2_shortscenrario()
    leg->SetFillStyle(1001);
    TLegendEntry *entry=leg->AddEntry("gre","CLAS (This work)","P");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("graphS","Fucini et al. [37]","L");
+   entry=leg->AddEntry("graphS","Fucini et al. [40]","L");
    entry->SetLineStyle(9);
    entry->SetLineWidth(2);
    entry->SetLineColor(6);

### 2020-04-24 eg6-letters/long-paper/source_files/InCoh/ALU_ratioInc_t_shortscenrario.C

@@ -247,11 +247,11 @@ void ALU_ratioInc_t_shortscenrario()
    entry->SetTextFont(42);
    entry=leg->AddEntry("Graph2","Liuti et al. (low -t) [29]","L");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Graph4","Guzey et al. [34]","L");
+   entry=leg->AddEntry("Graph4","Guzey et al. [37]","L");
    entry->SetTextFont(42);
    entry=leg->AddEntry("Graph3","Liuti et al. (high -t) [29]","L");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("GraphS","Fucini et al. [37]","L");
+   entry=leg->AddEntry("GraphS","Fucini et al. [40]","L");
    entry->SetLineStyle(9);
    entry->SetLineWidth(2);
    entry->SetLineColor(6);

### 2020-04-24 eg6-letters/long-paper/source_files/InCoh/ALU_ratioInc_x_shortscenrario.C

@@ -235,11 +235,11 @@ void ALU_ratioInc_x_shortscenrario()
    entry->SetTextFont(42);
    entry=leg->AddEntry("Graph2","Liuti et al. (low -t) [29]","L");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Graph4","Guzey et al. [34]","L");
+   entry=leg->AddEntry("Graph4","Guzey et al. [37]","L");
    entry->SetTextFont(42);
    entry=leg->AddEntry("Graph3","Liuti et al. (high -t) [29]","L");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("GraphS","Fucini et al. [37]","L");
+   entry=leg->AddEntry("GraphS","Fucini et al. [40]","L");
    entry->SetLineStyle(9);
    entry->SetLineWidth(2);
    entry->SetLineColor(6);

### 2020-04-24 eg6-letters/long-paper/prc-dvcshelium.tex
Add pi0 contamination figures.

@@
 
-The $\pi^0$ contamination was found to be 2 to 4\% in the coherent channel and 3 to 17\% in the incoherent
-channel (with variations between kinematic bins). To make the correction on the DVCS BSA, we assume that
+We show in Fig.~\ref{fig:cont_yield} the $\pi^0$ contamination for the $-t$ bins, where it varies
+the most from one bin to another. The study
+shows 2 to 4\% contamination in the coherent channel and 3 to 17\% in the incoherent
+channel. To make the correction on the DVCS BSA, we assume that
 the exclusive $\pi^0$ production has no such asymmetry. This has been checked with the exclusive 
-$\pi^0$ production data, for which no significant level of BSA has been measured.
+$\pi^0$ production data, for which no significant level of BSA was measured.
+
+\begin{figure}[tbp]
+\includegraphics[width=8cm]{fig3/T_ratio_pi0_dvcs_Coh_t.pdf}
+\includegraphics[width=8cm]{fig3/T_ratio_pi0_dvcs_InCoh_t.pdf}
+\caption{The coherent (left) and incoherent (right) $\pi^{0}$ 
+contamination estimated in the DVCS events as a function of the 
+transfered momentum squared -$t$ and integrated over the kinematical 
+variables $Q^2$, $x_B$, and $\phi$.}
+\label{fig:cont_yield}
+\end{figure}
 
@@
 	the fit of the data with the form of Eq.~\ref{eq:A_LU-coh}.}
-	%TODO Add the chi2 somewhere
 \label{fig:CohALUphi}
@@
 
-%TODO add sentence on recent theory and one on ALERT
-
 \begin{acknowledgments}
@@
 State University. M.~Hattawy also acknowledges the support of the Consulat 
-G\'en\'eral de France \`a J\'erusalem.  The Southeastern Universities Research 
+G\'en\'eral de France \`a J\'erusalem. This work has received funding from 
+the European Research Council (ERC) under the European Union’s Horizon 2020 
+research and innovation programme (Grant agreement No. 804480). The Southeastern Universities Research 
 Association operates the Thomas Jefferson National Accelerator Facility for the 
@@
 \label{sec:fullresults}
+%TODO Tables to be checked
 

### 2020-05-11 eg6-letters/long-paper/t-tprime_incoh/t_tprime_ALU_90_p_shortscenrario.C
Update figures t comparison

@@ -20,14 +20,14 @@ void t_tprime_ALU_90_p_shortscenrario()
    Cann_1->SetFillColor(0);
    Cann_1->SetBorderMode(0);
    Cann_1->SetBorderSize(2);
-   Cann_1->SetLeftMargin(0.3012048);
+   Cann_1->SetLeftMargin(0.2012048);
    Cann_1->SetRightMargin(0);
    Cann_1->SetTopMargin(0);
    Cann_1->SetBottomMargin(0.255814);
    Cann_1->SetFrameBorderMode(0);
    Cann_1->SetFrameBorderMode(0);
    
-   TH2F *HALU_p_vs_Q2__1 = new TH2F("HALU_p_vs_Q2__1","",100,0.5,4.5,100,-0.1,0.5);
+   TH2F *HALU_p_vs_Q2__1 = new TH2F("HALU_p_vs_Q2__1","",100,0.8,3.8,100,-0.05,0.35);
    HALU_p_vs_Q2__1->SetStats(0);
 
    Int_t ci;      // for color index setting
@@ -217,7 +217,7 @@ void t_tprime_ALU_90_p_shortscenrario()
    
    graph->Draw("f");
    
-   TLegend *leg = new TLegend(0.7,0.85,0.99,0.99,NULL,"brNDC");
+   TLegend *leg = new TLegend(0.65,0.82,0.99,0.99,NULL,"brNDC");
    leg->SetBorderSize(1);
    leg->SetTextSize(0.05);
    leg->SetLineColor(1);
@@ -225,7 +225,7 @@ void t_tprime_ALU_90_p_shortscenrario()
    leg->SetLineWidth(1);
    leg->SetFillColor(0);
    leg->SetFillStyle(1001);
-   TLegendEntry *entry=leg->AddEntry("Graph0","bins in t","P");
+   TLegendEntry *entry=leg->AddEntry("Graph0","t definition","P");
    entry->SetLineColor(1);
    entry->SetLineStyle(1);
    entry->SetLineWidth(1);
@@ -235,7 +235,7 @@ void t_tprime_ALU_90_p_shortscenrario()
    entry->SetMarkerStyle(21);
    entry->SetMarkerSize(1.5);
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Graph1","bins in t'","P");
+   entry=leg->AddEntry("Graph1","t' definition","P");
    entry->SetLineColor(1);
    entry->SetLineStyle(1);
[…]

### 2020-05-11 eg6-letters/long-paper/prc-dvcshelium.tex
Update fig 17 and add line numbers for review

@@
-\documentclass[aps,prc,preprint,superscriptaddress]{revtex4}
+\documentclass{article}
+\usepackage[left=3.5cm,right=2.5cm,top=2cm,bottom=2cm,includefoot,includehead,headheight=15pt]{geometry}
+\usepackage{lineno}
+%\documentclass[aps,prc,preprint,superscriptaddress]{revtex4}
 %\usepackage{amsmath,amssymb}             % AMS Math
@@
 \usepackage{lmodern,textcomp}
-%\usepackage[left=3.5cm,right=2.5cm,top=2cm,bottom=2cm,includefoot,includehead,headheight=15pt]{geometry}
 \usepackage{setspace}
@@
 
+%TODO
+\let\oldequation\equation
+\let\oldendequation\endequation
+
+\renewenvironment{equation}
+  {\linenomathNonumbers\oldequation}
+  {\oldendequation\endlinenomath}
+
 \begin{document}
@@
 
-\input author_list.tex
+%\input author_list.tex
 
 \date{\today}
+%TODO
+\maketitle
+\linenumbers
 
@@
 % insert suggested PACS numbers in braces on next line
-\pacs{}
-
-\maketitle
+%\pacs{}
+
+%\maketitle
 
@@
 \center
-\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_Q2_tcomp.pdf}
-\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_t_tcomp.pdf}
-%\includegraphics[width=7cm]{fig3/ALU_90_p_vs_x_shortscenrario.pdf}
+\includegraphics[width=15cm]{fig3/t_tprime_ALU_90_p_shortscenrario.pdf}
 	\caption{The BSA at 90° ($A_{LU}^{Incoh} (90^\circ)$) as a
-	function of $Q^2$ and $-t$, using the photon based $t$ definition (empty red)
-	and the proton based $t^\prime$ definition (full black).}
-	%TODO we could remove HERMES and the models on these
+	function of $Q^2$, $x_{B}$ and $-t$, using the photon based $t$ definition (red)
+	and the proton based $t^\prime$ definition (black).}
 \label{fig:ttpComp}
@@
 
-\begin{acknowledgments}
+%TODO
+\section{Acknowledgments}
+%\begin{acknowledgments}
 The authors acknowledge the staff of the Accelerator and Physics Divisions at 
@@
 United States Department of Energy under Contract No. DE-AC05-06OR23177.
-\end{acknowledgments}
+%\end{acknowledgments}
 
@@
 \right\} - 4 x_A^2{(2-y)}^2 (2+\epsilon^2) \frac{t}{Q^2} \nonumber \\
+pdflatex prc-dvcshelium.tex
 & \phantom{\bigg[} & + 8 K^2 \frac{\epsilon^2 Q^2}{t} \,\,\,\,\,\,\, \bigg] F_A^2(t)  \\
@@
 % Create the reference section using BibTeX:
+%TODO
+\bibliographystyle{unsrt}
 \bibliography{hadro.bib}

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_Q2[0]_Phi.C
add the incoherent DVCS and pi0 tables

@@ -1,0 +1,103 @@
+{
+//=========Macro generated from canvas: c1/
+//=========  (Fri Dec 18 09:59:46 2015) by ROOT version5.34/34
+   TCanvas *c1 = new TCanvas("c1", "",0,0,700,500);
+   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
+   c1->SetFillColor(0);
+   c1->SetBorderMode(0);
+   c1->SetBorderSize(0);
+   c1->SetGridx();
+   c1->SetGridy();
+   c1->SetLeftMargin(0.16);
+   c1->SetRightMargin(0.08);
+   c1->SetTopMargin(0.08);
+   c1->SetBottomMargin(0.16);
+   c1->SetFrameBorderMode(0);
+   c1->SetFrameBorderMode(0);
+   
+   TGraphErrors *gre = new TGraphErrors(18);
+   gre->SetName("Graph0");
+   gre->SetTitle("Graph");
+   gre->SetFillColor(1);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#0000ff");
+   gre->SetMarkerColor(ci);
+   gre->SetMarkerStyle(21);
+   gre->SetPoint(0,10,0.2173649);
+   gre->SetPointError(0,0,0.01684412);
+   gre->SetPoint(1,30,0.2118398);
+   gre->SetPointError(1,0,0.01619167);
+   gre->SetPoint(2,50,0.1866126);
+   gre->SetPointError(2,0,0.01970022);
+   gre->SetPoint(3,70,0.1717172);
+   gre->SetPointError(3,0,0.01472644);
+   gre->SetPoint(4,90,0.2051282);
+   gre->SetPointError(4,0,0.01781088);
+   gre->SetPoint(5,110,0.1922428);
+   gre->SetPointError(5,0,0.02589966);
+   gre->SetPoint(6,130,0.1504132);
+   gre->SetPointError(6,0,0.02188276);
+   gre->SetPoint(7,150,0.2006221);
+   gre->SetPointError(7,0,0.02557555);
+   gre->SetPoint(8,170,0.180602);
+   gre->SetPointError(8,0,0.03502131);
+   gre->SetPoint(9,190,0.2097458);
+   gre->SetPointError(9,0,0.03073457);
[…]

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_Q2[1]_Phi.C

@@ -1,0 +1,103 @@
+{
+//=========Macro generated from canvas: c1/
+//=========  (Fri Dec 18 09:59:46 2015) by ROOT version5.34/34
+   TCanvas *c1 = new TCanvas("c1", "",1,1,700,476);
+   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
+   c1->SetFillColor(0);
+   c1->SetBorderMode(0);
+   c1->SetBorderSize(0);
+   c1->SetGridx();
+   c1->SetGridy();
+   c1->SetLeftMargin(0.16);
+   c1->SetRightMargin(0.08);
+   c1->SetTopMargin(0.08);
+   c1->SetBottomMargin(0.16);
+   c1->SetFrameBorderMode(0);
+   c1->SetFrameBorderMode(0);
+   
+   TGraphErrors *gre = new TGraphErrors(18);
+   gre->SetName("Graph0");
+   gre->SetTitle("Graph");
+   gre->SetFillColor(1);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#0000ff");
+   gre->SetMarkerColor(ci);
+   gre->SetMarkerStyle(21);
+   gre->SetPoint(0,10,0.270282);
+   gre->SetPointError(0,0,0.01645827);
+   gre->SetPoint(1,30,0.2719864);
+   gre->SetPointError(1,0,0.01462209);
+   gre->SetPoint(2,50,0.2261245);
+   gre->SetPointError(2,0,0.01741651);
+   gre->SetPoint(3,70,0.2302709);
+   gre->SetPointError(3,0,0.01723348);
+   gre->SetPoint(4,90,0.1935691);
+   gre->SetPointError(4,0,0.01606589);
+   gre->SetPoint(5,110,0.2240117);
+   gre->SetPointError(5,0,0.02668184);
+   gre->SetPoint(6,130,0.1945032);
+   gre->SetPointError(6,0,0.02922162);
+   gre->SetPoint(7,150,0.2055336);
+   gre->SetPointError(7,0,0.02929131);
+   gre->SetPoint(8,170,0.1498258);
+   gre->SetPointError(8,0,0.03169215);
+   gre->SetPoint(9,190,0.2072539);
+   gre->SetPointError(9,0,0.03372063);
[…]

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_Q2[2]_Phi.C

@@ -1,0 +1,103 @@
+{
+//=========Macro generated from canvas: c1/
+//=========  (Fri Dec 18 09:59:47 2015) by ROOT version5.34/34
+   TCanvas *c1 = new TCanvas("c1", "",1,1,700,476);
+   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
+   c1->SetFillColor(0);
+   c1->SetBorderMode(0);
+   c1->SetBorderSize(0);
+   c1->SetGridx();
+   c1->SetGridy();
+   c1->SetLeftMargin(0.16);
+   c1->SetRightMargin(0.08);
+   c1->SetTopMargin(0.08);
+   c1->SetBottomMargin(0.16);
+   c1->SetFrameBorderMode(0);
+   c1->SetFrameBorderMode(0);
+   
+   TGraphErrors *gre = new TGraphErrors(18);
+   gre->SetName("Graph0");
+   gre->SetTitle("Graph");
+   gre->SetFillColor(1);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#0000ff");
+   gre->SetMarkerColor(ci);
+   gre->SetMarkerStyle(21);
+   gre->SetPoint(0,10,0.2528931);
+   gre->SetPointError(0,0,0.01394339);
+   gre->SetPoint(1,30,0.2661026);
+   gre->SetPointError(1,0,0.01291824);
+   gre->SetPoint(2,50,0.2378329);
+   gre->SetPointError(2,0,0.01554594);
+   gre->SetPoint(3,70,0.21303);
+   gre->SetPointError(3,0,0.01533933);
+   gre->SetPoint(4,90,0.2175549);
+   gre->SetPointError(4,0,0.01712635);
+   gre->SetPoint(5,110,0.2097625);
+   gre->SetPointError(5,0,0.02425417);
+   gre->SetPoint(6,130,0.2126789);
+   gre->SetPointError(6,0,0.03047256);
+   gre->SetPoint(7,150,0.2344398);
+   gre->SetPointError(7,0,0.03273268);
+   gre->SetPoint(8,170,0.2);
+   gre->SetPointError(8,0,0.04177746);
+   gre->SetPoint(9,190,0.2204969);
+   gre->SetPointError(9,0,0.03845598);
[…]

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_Q2[3]_Phi.C

@@ -1,0 +1,103 @@
+{
+//=========Macro generated from canvas: c1/
+//=========  (Fri Dec 18 09:59:47 2015) by ROOT version5.34/34
+   TCanvas *c1 = new TCanvas("c1", "",1,1,700,476);
+   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
+   c1->SetFillColor(0);
+   c1->SetBorderMode(0);
+   c1->SetBorderSize(0);
+   c1->SetGridx();
+   c1->SetGridy();
+   c1->SetLeftMargin(0.16);
+   c1->SetRightMargin(0.08);
+   c1->SetTopMargin(0.08);
+   c1->SetBottomMargin(0.16);
+   c1->SetFrameBorderMode(0);
+   c1->SetFrameBorderMode(0);
+   
+   TGraphErrors *gre = new TGraphErrors(18);
+   gre->SetName("Graph0");
+   gre->SetTitle("Graph");
+   gre->SetFillColor(1);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#0000ff");
+   gre->SetMarkerColor(ci);
+   gre->SetMarkerStyle(21);
+   gre->SetPoint(0,10,0.2620474);
+   gre->SetPointError(0,0,0.01249124);
+   gre->SetPoint(1,30,0.2338724);
+   gre->SetPointError(1,0,0.009671807);
+   gre->SetPoint(2,50,0.2185522);
+   gre->SetPointError(2,0,0.01138208);
+   gre->SetPoint(3,70,0.2140152);
+   gre->SetPointError(3,0,0.01316895);
+   gre->SetPoint(4,90,0.2124378);
+   gre->SetPointError(4,0,0.01501901);
+   gre->SetPoint(5,110,0.2120452);
+   gre->SetPointError(5,0,0.02382219);
+   gre->SetPoint(6,130,0.1842105);
+   gre->SetPointError(6,0,0.02872546);
+   gre->SetPoint(7,150,0.1983914);
+   gre->SetPointError(7,0,0.03333485);
+   gre->SetPoint(8,170,0.2159091);
+   gre->SetPointError(8,0,0.05129984);
+   gre->SetPoint(9,190,0.1782609);
+   gre->SetPointError(9,0,0.03959385);
[…]

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_t[0]_Phi.C

@@ -1,0 +1,103 @@
+{
+//=========Macro generated from canvas: c1/
+//=========  (Fri Dec 18 09:59:46 2015) by ROOT version5.34/34
+   TCanvas *c1 = new TCanvas("c1", "",1,1,700,476);
+   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
+   c1->SetFillColor(0);
+   c1->SetBorderMode(0);
+   c1->SetBorderSize(0);
+   c1->SetGridx();
+   c1->SetGridy();
+   c1->SetLeftMargin(0.16);
+   c1->SetRightMargin(0.08);
+   c1->SetTopMargin(0.08);
+   c1->SetBottomMargin(0.16);
+   c1->SetFrameBorderMode(0);
+   c1->SetFrameBorderMode(0);
+   
+   TGraphErrors *gre = new TGraphErrors(18);
+   gre->SetName("Graph0");
+   gre->SetTitle("Graph");
+   gre->SetFillColor(1);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#0000ff");
+   gre->SetMarkerColor(ci);
+   gre->SetMarkerStyle(21);
+   gre->SetPoint(0,10,0.1827161);
+   gre->SetPointError(0,0,0.02143916);
+   gre->SetPoint(1,30,0.173384);
+   gre->SetPointError(1,0,0.01626394);
+   gre->SetPoint(2,50,0.1726685);
+   gre->SetPointError(2,0,0.01787363);
+   gre->SetPoint(3,70,0.1706161);
+   gre->SetPointError(3,0,0.02009086);
+   gre->SetPoint(4,90,0.1664122);
+   gre->SetPointError(4,0,0.01586865);
+   gre->SetPoint(5,110,0.1774809);
+   gre->SetPointError(5,0,0.01849594);
+   gre->SetPoint(6,130,0.1329212);
+   gre->SetPointError(6,0,0.01955893);
+   gre->SetPoint(7,150,0.1713961);
+   gre->SetPointError(7,0,0.0197225);
+   gre->SetPoint(8,170,0.1566731);
+   gre->SetPointError(8,0,0.0242986);
+   gre->SetPoint(9,190,0.1849315);
+   gre->SetPointError(9,0,0.02544756);
[…]

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_t[1]_Phi.C

@@ -1,0 +1,103 @@
+{
+//=========Macro generated from canvas: c1/
+//=========  (Fri Dec 18 09:59:47 2015) by ROOT version5.34/34
+   TCanvas *c1 = new TCanvas("c1", "",1,1,700,476);
+   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
+   c1->SetFillColor(0);
+   c1->SetBorderMode(0);
+   c1->SetBorderSize(0);
+   c1->SetGridx();
+   c1->SetGridy();
+   c1->SetLeftMargin(0.16);
+   c1->SetRightMargin(0.08);
+   c1->SetTopMargin(0.08);
+   c1->SetBottomMargin(0.16);
+   c1->SetFrameBorderMode(0);
+   c1->SetFrameBorderMode(0);
+   
+   TGraphErrors *gre = new TGraphErrors(18);
+   gre->SetName("Graph0");
+   gre->SetTitle("Graph");
+   gre->SetFillColor(1);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#0000ff");
+   gre->SetMarkerColor(ci);
+   gre->SetMarkerStyle(21);
+   gre->SetPoint(0,10,0.2207131);
+   gre->SetPointError(0,0,0.0201187);
+   gre->SetPoint(1,30,0.2226322);
+   gre->SetPointError(1,0,0.01722242);
+   gre->SetPoint(2,50,0.2054196);
+   gre->SetPointError(2,0,0.01947345);
+   gre->SetPoint(3,70,0.1802011);
+   gre->SetPointError(3,0,0.01681675);
+   gre->SetPoint(4,90,0.1810345);
+   gre->SetPointError(4,0,0.01505044);
+   gre->SetPoint(5,110,0.2074264);
+   gre->SetPointError(5,0,0.02371925);
+   gre->SetPoint(6,130,0.1729894);
+   gre->SetPointError(6,0,0.02294065);
+   gre->SetPoint(7,150,0.211288);
+   gre->SetPointError(7,0,0.02552409);
+   gre->SetPoint(8,170,0.2013201);
+   gre->SetPointError(8,0,0.03734194);
+   gre->SetPoint(9,190,0.1943888);
+   gre->SetPointError(9,0,0.02843923);
[…]

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_t[2]_Phi.C

@@ -1,0 +1,103 @@
+{
+//=========Macro generated from canvas: c1/
+//=========  (Fri Dec 18 09:59:47 2015) by ROOT version5.34/34
+   TCanvas *c1 = new TCanvas("c1", "",1,1,700,476);
+   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
+   c1->SetFillColor(0);
+   c1->SetBorderMode(0);
+   c1->SetBorderSize(0);
+   c1->SetGridx();
+   c1->SetGridy();
+   c1->SetLeftMargin(0.16);
+   c1->SetRightMargin(0.08);
+   c1->SetTopMargin(0.08);
+   c1->SetBottomMargin(0.16);
+   c1->SetFrameBorderMode(0);
+   c1->SetFrameBorderMode(0);
+   
+   TGraphErrors *gre = new TGraphErrors(18);
+   gre->SetName("Graph0");
+   gre->SetTitle("Graph");
+   gre->SetFillColor(1);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#0000ff");
+   gre->SetMarkerColor(ci);
+   gre->SetMarkerStyle(21);
+   gre->SetPoint(0,10,0.2595137);
+   gre->SetPointError(0,0,0.01767792);
+   gre->SetPoint(1,30,0.2453035);
+   gre->SetPointError(1,0,0.0140764);
+   gre->SetPoint(2,50,0.2141393);
+   gre->SetPointError(2,0,0.01532071);
+   gre->SetPoint(3,70,0.1806061);
+   gre->SetPointError(3,0,0.01217269);
+   gre->SetPoint(4,90,0.2111212);
+   gre->SetPointError(4,0,0.01425841);
+   gre->SetPoint(5,110,0.2352168);
+   gre->SetPointError(5,0,0.02610753);
+   gre->SetPoint(6,130,0.2112903);
+   gre->SetPointError(6,0,0.02694614);
+   gre->SetPoint(7,150,0.2794872);
+   gre->SetPointError(7,0,0.0409224);
+   gre->SetPoint(8,170,0.2242424);
+   gre->SetPointError(8,0,0.05432248);
+   gre->SetPoint(9,190,0.2633333);
+   gre->SetPointError(9,0,0.04483087);
[…]

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_t[3]_Phi.C

@@ -1,0 +1,103 @@
+{
+//=========Macro generated from canvas: c1/
+//=========  (Fri Dec 18 09:59:48 2015) by ROOT version5.34/34
+   TCanvas *c1 = new TCanvas("c1", "",1,1,700,476);
+   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
+   c1->SetFillColor(0);
+   c1->SetBorderMode(0);
+   c1->SetBorderSize(0);
+   c1->SetGridx();
+   c1->SetGridy();
+   c1->SetLeftMargin(0.16);
+   c1->SetRightMargin(0.08);
+   c1->SetTopMargin(0.08);
+   c1->SetBottomMargin(0.16);
+   c1->SetFrameBorderMode(0);
+   c1->SetFrameBorderMode(0);
+   
+   TGraphErrors *gre = new TGraphErrors(18);
+   gre->SetName("Graph0");
+   gre->SetTitle("Graph");
+   gre->SetFillColor(1);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#0000ff");
+   gre->SetMarkerColor(ci);
+   gre->SetMarkerStyle(21);
+   gre->SetPoint(0,10,0.2676135);
+   gre->SetPointError(0,0,0.0107303);
+   gre->SetPoint(1,30,0.2622631);
+   gre->SetPointError(1,0,0.009141398);
+   gre->SetPoint(2,50,0.2334912);
+   gre->SetPointError(2,0,0.01131366);
+   gre->SetPoint(3,70,0.251633);
+   gre->SetPointError(3,0,0.01328484);
+   gre->SetPoint(4,90,0.2753623);
+   gre->SetPointError(4,0,0.02153829);
+   gre->SetPoint(5,110,0.2798354);
+   gre->SetPointError(5,0,0.05188648);
+   gre->SetPoint(6,130,0.4081633);
+   gre->SetPointError(6,0,0.105767);
+   gre->SetPoint(7,150,0.3333333);
+   gre->SetPointError(7,0,0.1405215);
+   gre->SetPoint(8,170,0.2352941);
+   gre->SetPointError(8,0,0.1747143);
+   gre->SetPoint(9,190,0.2592593);
+   gre->SetPointError(9,0,0.1478852);
+   gre->SetPoint(10,210,0.25);
[…]

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_xB[0]_Phi.C

@@ -1,0 +1,103 @@
+{
+//=========Macro generated from canvas: c1/
+//=========  (Fri Dec 18 09:59:46 2015) by ROOT version5.34/34
+   TCanvas *c1 = new TCanvas("c1", "",1,1,700,476);
+   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
+   c1->SetFillColor(0);
+   c1->SetBorderMode(0);
+   c1->SetBorderSize(0);
+   c1->SetGridx();
+   c1->SetGridy();
+   c1->SetLeftMargin(0.16);
+   c1->SetRightMargin(0.08);
+   c1->SetTopMargin(0.08);
+   c1->SetBottomMargin(0.16);
+   c1->SetFrameBorderMode(0);
+   c1->SetFrameBorderMode(0);
+   
+   TGraphErrors *gre = new TGraphErrors(18);
+   gre->SetName("Graph0");
+   gre->SetTitle("Graph");
+   gre->SetFillColor(1);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#0000ff");
+   gre->SetMarkerColor(ci);
+   gre->SetMarkerStyle(21);
+   gre->SetPoint(0,10,0.1918736);
+   gre->SetPointError(0,0,0.01727882);
+   gre->SetPoint(1,30,0.1835967);
+   gre->SetPointError(1,0,0.01678977);
+   gre->SetPoint(2,50,0.1408935);
+   gre->SetPointError(2,0,0.01747246);
+   gre->SetPoint(3,70,0.1540388);
+   gre->SetPointError(3,0,0.01367574);
+   gre->SetPoint(4,90,0.1745058);
+   gre->SetPointError(4,0,0.01546273);
+   gre->SetPoint(5,110,0.1646707);
+   gre->SetPointError(5,0,0.02207203);
+   gre->SetPoint(6,130,0.1486111);
+   gre->SetPointError(6,0,0.01990519);
+   gre->SetPoint(7,150,0.1757656);
+   gre->SetPointError(7,0,0.02171222);
+   gre->SetPoint(8,170,0.1626667);
+   gre->SetPointError(8,0,0.0292274);
+   gre->SetPoint(9,190,0.1964912);
+   gre->SetPointError(9,0,0.02679679);
[…]

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_xB[1]_Phi.C

@@ -1,0 +1,103 @@
+{
+//=========Macro generated from canvas: c1/
+//=========  (Fri Dec 18 09:59:46 2015) by ROOT version5.34/34
+   TCanvas *c1 = new TCanvas("c1", "",1,1,700,476);
+   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
+   c1->SetFillColor(0);
+   c1->SetBorderMode(0);
+   c1->SetBorderSize(0);
+   c1->SetGridx();
+   c1->SetGridy();
+   c1->SetLeftMargin(0.16);
+   c1->SetRightMargin(0.08);
+   c1->SetTopMargin(0.08);
+   c1->SetBottomMargin(0.16);
+   c1->SetFrameBorderMode(0);
+   c1->SetFrameBorderMode(0);
+   
+   TGraphErrors *gre = new TGraphErrors(18);
+   gre->SetName("Graph0");
+   gre->SetTitle("Graph");
+   gre->SetFillColor(1);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#0000ff");
+   gre->SetMarkerColor(ci);
+   gre->SetMarkerStyle(21);
+   gre->SetPoint(0,10,0.21498);
+   gre->SetPointError(0,0,0.01622722);
+   gre->SetPoint(1,30,0.2105505);
+   gre->SetPointError(1,0,0.01433715);
+   gre->SetPoint(2,50,0.1911197);
+   gre->SetPointError(2,0,0.01593808);
+   gre->SetPoint(3,70,0.2005277);
+   gre->SetPointError(3,0,0.01489334);
+   gre->SetPoint(4,90,0.1842984);
+   gre->SetPointError(4,0,0.01447875);
+   gre->SetPoint(5,110,0.2059524);
+   gre->SetPointError(5,0,0.0227643);
+   gre->SetPoint(6,130,0.1775862);
+   gre->SetPointError(6,0,0.02487195);
+   gre->SetPoint(7,150,0.2347973);
+   gre->SetPointError(7,0,0.02956535);
+   gre->SetPoint(8,170,0.1495327);
+   gre->SetPointError(8,0,0.02992929);
+   gre->SetPoint(9,190,0.2191781);
+   gre->SetPointError(9,0,0.0328425);
[…]

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_xB[2]_Phi.C

@@ -1,0 +1,103 @@
+{
+//=========Macro generated from canvas: c1/
+//=========  (Fri Dec 18 09:59:47 2015) by ROOT version5.34/34
+   TCanvas *c1 = new TCanvas("c1", "",1,1,700,476);
+   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
+   c1->SetFillColor(0);
+   c1->SetBorderMode(0);
+   c1->SetBorderSize(0);
+   c1->SetGridx();
+   c1->SetGridy();
+   c1->SetLeftMargin(0.16);
+   c1->SetRightMargin(0.08);
+   c1->SetTopMargin(0.08);
+   c1->SetBottomMargin(0.16);
+   c1->SetFrameBorderMode(0);
+   c1->SetFrameBorderMode(0);
+   
+   TGraphErrors *gre = new TGraphErrors(18);
+   gre->SetName("Graph0");
+   gre->SetTitle("Graph");
+   gre->SetFillColor(1);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#0000ff");
+   gre->SetMarkerColor(ci);
+   gre->SetMarkerStyle(21);
+   gre->SetPoint(0,10,0.2463387);
+   gre->SetPointError(0,0,0.01439152);
+   gre->SetPoint(1,30,0.2362288);
+   gre->SetPointError(1,0,0.01175382);
+   gre->SetPoint(2,50,0.2195821);
+   gre->SetPointError(2,0,0.0139289);
+   gre->SetPoint(3,70,0.206772);
+   gre->SetPointError(3,0,0.01405526);
+   gre->SetPoint(4,90,0.2208219);
+   gre->SetPointError(4,0,0.01616897);
+   gre->SetPoint(5,110,0.2210012);
+   gre->SetPointError(5,0,0.0241493);
+   gre->SetPoint(6,130,0.2178423);
+   gre->SetPointError(6,0,0.03118168);
+   gre->SetPoint(7,150,0.2483801);
+   gre->SetPointError(7,0,0.03470477);
+   gre->SetPoint(8,170,0.2378855);
+   gre->SetPointError(8,0,0.04816112);
+   gre->SetPoint(9,190,0.184466);
+   gre->SetPointError(9,0,0.03492703);
[…]

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_xB[3]_Phi.C

@@ -1,0 +1,103 @@
+{
+//=========Macro generated from canvas: c1/
+//=========  (Fri Dec 18 09:59:48 2015) by ROOT version5.34/34
+   TCanvas *c1 = new TCanvas("c1", "",1,1,700,476);
+   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
+   c1->SetFillColor(0);
+   c1->SetBorderMode(0);
+   c1->SetBorderSize(0);
+   c1->SetGridx();
+   c1->SetGridy();
+   c1->SetLeftMargin(0.16);
+   c1->SetRightMargin(0.08);
+   c1->SetTopMargin(0.08);
+   c1->SetBottomMargin(0.16);
+   c1->SetFrameBorderMode(0);
+   c1->SetFrameBorderMode(0);
+   
+   TGraphErrors *gre = new TGraphErrors(18);
+   gre->SetName("Graph0");
+   gre->SetTitle("Graph");
+   gre->SetFillColor(1);
+
+   Int_t ci;      // for color index setting
+   TColor *color; // for color definition with alpha
+   ci = TColor::GetColor("#0000ff");
+   gre->SetMarkerColor(ci);
+   gre->SetMarkerStyle(21);
+   gre->SetPoint(0,10,0.2886309);
+   gre->SetPointError(0,0,0.01168431);
+   gre->SetPoint(1,30,0.2797864);
+   gre->SetPointError(1,0,0.009988949);
+   gre->SetPoint(2,50,0.2544893);
+   gre->SetPointError(2,0,0.01271304);
+   gre->SetPoint(3,70,0.2610107);
+   gre->SetPointError(3,0,0.01662025);
+   gre->SetPoint(4,90,0.2564281);
+   gre->SetPointError(4,0,0.02010893);
+   gre->SetPoint(5,110,0.2588933);
+   gre->SetPointError(5,0,0.03412882);
+   gre->SetPoint(6,130,0.231405);
+   gre->SetPointError(6,0,0.04579806);
+   gre->SetPoint(7,150,0.1717172);
+   gre->SetPointError(7,0,0.04165266);
+   gre->SetPoint(8,170,0.2531646);
+   gre->SetPointError(8,0,0.08509255);
+   gre->SetPoint(9,190,0.2795699);
+   gre->SetPointError(9,0,0.08381821);
[…]

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_Q2[0]_Phi.C
eclean the title

@@ -1,103 +1,0 @@
-{
-//=========Macro generated from canvas: c1/
-//=========  (Fri Dec 18 09:59:46 2015) by ROOT version5.34/34
-   TCanvas *c1 = new TCanvas("c1", "",0,0,700,500);
-   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
-   c1->SetFillColor(0);
-   c1->SetBorderMode(0);
-   c1->SetBorderSize(0);
-   c1->SetGridx();
-   c1->SetGridy();
-   c1->SetLeftMargin(0.16);
-   c1->SetRightMargin(0.08);
-   c1->SetTopMargin(0.08);
-   c1->SetBottomMargin(0.16);
-   c1->SetFrameBorderMode(0);
-   c1->SetFrameBorderMode(0);
-   
-   TGraphErrors *gre = new TGraphErrors(18);
-   gre->SetName("Graph0");
-   gre->SetTitle("Graph");
-   gre->SetFillColor(1);
-
-   Int_t ci;      // for color index setting
-   TColor *color; // for color definition with alpha
-   ci = TColor::GetColor("#0000ff");
-   gre->SetMarkerColor(ci);
-   gre->SetMarkerStyle(21);
-   gre->SetPoint(0,10,0.2173649);
-   gre->SetPointError(0,0,0.01684412);
-   gre->SetPoint(1,30,0.2118398);
-   gre->SetPointError(1,0,0.01619167);
-   gre->SetPoint(2,50,0.1866126);
-   gre->SetPointError(2,0,0.01970022);
-   gre->SetPoint(3,70,0.1717172);
-   gre->SetPointError(3,0,0.01472644);
-   gre->SetPoint(4,90,0.2051282);
-   gre->SetPointError(4,0,0.01781088);
-   gre->SetPoint(5,110,0.1922428);
-   gre->SetPointError(5,0,0.02589966);
-   gre->SetPoint(6,130,0.1504132);
-   gre->SetPointError(6,0,0.02188276);
-   gre->SetPoint(7,150,0.2006221);
-   gre->SetPointError(7,0,0.02557555);
-   gre->SetPoint(8,170,0.180602);
-   gre->SetPointError(8,0,0.03502131);
-   gre->SetPoint(9,190,0.2097458);
-   gre->SetPointError(9,0,0.03073457);
[…]

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_Q2[1]_Phi.C

@@ -1,103 +1,0 @@
-{
-//=========Macro generated from canvas: c1/
-//=========  (Fri Dec 18 09:59:46 2015) by ROOT version5.34/34
-   TCanvas *c1 = new TCanvas("c1", "",1,1,700,476);
-   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
-   c1->SetFillColor(0);
-   c1->SetBorderMode(0);
-   c1->SetBorderSize(0);
-   c1->SetGridx();
-   c1->SetGridy();
-   c1->SetLeftMargin(0.16);
-   c1->SetRightMargin(0.08);
-   c1->SetTopMargin(0.08);
-   c1->SetBottomMargin(0.16);
-   c1->SetFrameBorderMode(0);
-   c1->SetFrameBorderMode(0);
-   
-   TGraphErrors *gre = new TGraphErrors(18);
-   gre->SetName("Graph0");
-   gre->SetTitle("Graph");
-   gre->SetFillColor(1);
-
-   Int_t ci;      // for color index setting
-   TColor *color; // for color definition with alpha
-   ci = TColor::GetColor("#0000ff");
-   gre->SetMarkerColor(ci);
-   gre->SetMarkerStyle(21);
-   gre->SetPoint(0,10,0.270282);
-   gre->SetPointError(0,0,0.01645827);
-   gre->SetPoint(1,30,0.2719864);
-   gre->SetPointError(1,0,0.01462209);
-   gre->SetPoint(2,50,0.2261245);
-   gre->SetPointError(2,0,0.01741651);
-   gre->SetPoint(3,70,0.2302709);
-   gre->SetPointError(3,0,0.01723348);
-   gre->SetPoint(4,90,0.1935691);
-   gre->SetPointError(4,0,0.01606589);
-   gre->SetPoint(5,110,0.2240117);
-   gre->SetPointError(5,0,0.02668184);
-   gre->SetPoint(6,130,0.1945032);
-   gre->SetPointError(6,0,0.02922162);
-   gre->SetPoint(7,150,0.2055336);
-   gre->SetPointError(7,0,0.02929131);
-   gre->SetPoint(8,170,0.1498258);
-   gre->SetPointError(8,0,0.03169215);
-   gre->SetPoint(9,190,0.2072539);
-   gre->SetPointError(9,0,0.03372063);
[…]

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_Q2[2]_Phi.C

@@ -1,103 +1,0 @@
-{
-//=========Macro generated from canvas: c1/
-//=========  (Fri Dec 18 09:59:47 2015) by ROOT version5.34/34
-   TCanvas *c1 = new TCanvas("c1", "",1,1,700,476);
-   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
-   c1->SetFillColor(0);
-   c1->SetBorderMode(0);
-   c1->SetBorderSize(0);
-   c1->SetGridx();
-   c1->SetGridy();
-   c1->SetLeftMargin(0.16);
-   c1->SetRightMargin(0.08);
-   c1->SetTopMargin(0.08);
-   c1->SetBottomMargin(0.16);
-   c1->SetFrameBorderMode(0);
-   c1->SetFrameBorderMode(0);
-   
-   TGraphErrors *gre = new TGraphErrors(18);
-   gre->SetName("Graph0");
-   gre->SetTitle("Graph");
-   gre->SetFillColor(1);
-
-   Int_t ci;      // for color index setting
-   TColor *color; // for color definition with alpha
-   ci = TColor::GetColor("#0000ff");
-   gre->SetMarkerColor(ci);
-   gre->SetMarkerStyle(21);
-   gre->SetPoint(0,10,0.2528931);
-   gre->SetPointError(0,0,0.01394339);
-   gre->SetPoint(1,30,0.2661026);
-   gre->SetPointError(1,0,0.01291824);
-   gre->SetPoint(2,50,0.2378329);
-   gre->SetPointError(2,0,0.01554594);
-   gre->SetPoint(3,70,0.21303);
-   gre->SetPointError(3,0,0.01533933);
-   gre->SetPoint(4,90,0.2175549);
-   gre->SetPointError(4,0,0.01712635);
-   gre->SetPoint(5,110,0.2097625);
-   gre->SetPointError(5,0,0.02425417);
-   gre->SetPoint(6,130,0.2126789);
-   gre->SetPointError(6,0,0.03047256);
-   gre->SetPoint(7,150,0.2344398);
-   gre->SetPointError(7,0,0.03273268);
-   gre->SetPoint(8,170,0.2);
-   gre->SetPointError(8,0,0.04177746);
-   gre->SetPoint(9,190,0.2204969);
-   gre->SetPointError(9,0,0.03845598);
[…]

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_Q2[3]_Phi.C

@@ -1,103 +1,0 @@
-{
-//=========Macro generated from canvas: c1/
-//=========  (Fri Dec 18 09:59:47 2015) by ROOT version5.34/34
-   TCanvas *c1 = new TCanvas("c1", "",1,1,700,476);
-   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
-   c1->SetFillColor(0);
-   c1->SetBorderMode(0);
-   c1->SetBorderSize(0);
-   c1->SetGridx();
-   c1->SetGridy();
-   c1->SetLeftMargin(0.16);
-   c1->SetRightMargin(0.08);
-   c1->SetTopMargin(0.08);
-   c1->SetBottomMargin(0.16);
-   c1->SetFrameBorderMode(0);
-   c1->SetFrameBorderMode(0);
-   
-   TGraphErrors *gre = new TGraphErrors(18);
-   gre->SetName("Graph0");
-   gre->SetTitle("Graph");
-   gre->SetFillColor(1);
-
-   Int_t ci;      // for color index setting
-   TColor *color; // for color definition with alpha
-   ci = TColor::GetColor("#0000ff");
-   gre->SetMarkerColor(ci);
-   gre->SetMarkerStyle(21);
-   gre->SetPoint(0,10,0.2620474);
-   gre->SetPointError(0,0,0.01249124);
-   gre->SetPoint(1,30,0.2338724);
-   gre->SetPointError(1,0,0.009671807);
-   gre->SetPoint(2,50,0.2185522);
-   gre->SetPointError(2,0,0.01138208);
-   gre->SetPoint(3,70,0.2140152);
-   gre->SetPointError(3,0,0.01316895);
-   gre->SetPoint(4,90,0.2124378);
-   gre->SetPointError(4,0,0.01501901);
-   gre->SetPoint(5,110,0.2120452);
-   gre->SetPointError(5,0,0.02382219);
-   gre->SetPoint(6,130,0.1842105);
-   gre->SetPointError(6,0,0.02872546);
-   gre->SetPoint(7,150,0.1983914);
-   gre->SetPointError(7,0,0.03333485);
-   gre->SetPoint(8,170,0.2159091);
-   gre->SetPointError(8,0,0.05129984);
-   gre->SetPoint(9,190,0.1782609);
-   gre->SetPointError(9,0,0.03959385);
[…]

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_t[0]_Phi.C

@@ -1,103 +1,0 @@
-{
-//=========Macro generated from canvas: c1/
-//=========  (Fri Dec 18 09:59:46 2015) by ROOT version5.34/34
-   TCanvas *c1 = new TCanvas("c1", "",1,1,700,476);
-   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
-   c1->SetFillColor(0);
-   c1->SetBorderMode(0);
-   c1->SetBorderSize(0);
-   c1->SetGridx();
-   c1->SetGridy();
-   c1->SetLeftMargin(0.16);
-   c1->SetRightMargin(0.08);
-   c1->SetTopMargin(0.08);
-   c1->SetBottomMargin(0.16);
-   c1->SetFrameBorderMode(0);
-   c1->SetFrameBorderMode(0);
-   
-   TGraphErrors *gre = new TGraphErrors(18);
-   gre->SetName("Graph0");
-   gre->SetTitle("Graph");
-   gre->SetFillColor(1);
-
-   Int_t ci;      // for color index setting
-   TColor *color; // for color definition with alpha
-   ci = TColor::GetColor("#0000ff");
-   gre->SetMarkerColor(ci);
-   gre->SetMarkerStyle(21);
-   gre->SetPoint(0,10,0.1827161);
-   gre->SetPointError(0,0,0.02143916);
-   gre->SetPoint(1,30,0.173384);
-   gre->SetPointError(1,0,0.01626394);
-   gre->SetPoint(2,50,0.1726685);
-   gre->SetPointError(2,0,0.01787363);
-   gre->SetPoint(3,70,0.1706161);
-   gre->SetPointError(3,0,0.02009086);
-   gre->SetPoint(4,90,0.1664122);
-   gre->SetPointError(4,0,0.01586865);
-   gre->SetPoint(5,110,0.1774809);
-   gre->SetPointError(5,0,0.01849594);
-   gre->SetPoint(6,130,0.1329212);
-   gre->SetPointError(6,0,0.01955893);
-   gre->SetPoint(7,150,0.1713961);
-   gre->SetPointError(7,0,0.0197225);
-   gre->SetPoint(8,170,0.1566731);
-   gre->SetPointError(8,0,0.0242986);
-   gre->SetPoint(9,190,0.1849315);
-   gre->SetPointError(9,0,0.02544756);
[…]

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_t[1]_Phi.C

@@ -1,103 +1,0 @@
-{
-//=========Macro generated from canvas: c1/
-//=========  (Fri Dec 18 09:59:47 2015) by ROOT version5.34/34
-   TCanvas *c1 = new TCanvas("c1", "",1,1,700,476);
-   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
-   c1->SetFillColor(0);
-   c1->SetBorderMode(0);
-   c1->SetBorderSize(0);
-   c1->SetGridx();
-   c1->SetGridy();
-   c1->SetLeftMargin(0.16);
-   c1->SetRightMargin(0.08);
-   c1->SetTopMargin(0.08);
-   c1->SetBottomMargin(0.16);
-   c1->SetFrameBorderMode(0);
-   c1->SetFrameBorderMode(0);
-   
-   TGraphErrors *gre = new TGraphErrors(18);
-   gre->SetName("Graph0");
-   gre->SetTitle("Graph");
-   gre->SetFillColor(1);
-
-   Int_t ci;      // for color index setting
-   TColor *color; // for color definition with alpha
-   ci = TColor::GetColor("#0000ff");
-   gre->SetMarkerColor(ci);
-   gre->SetMarkerStyle(21);
-   gre->SetPoint(0,10,0.2207131);
-   gre->SetPointError(0,0,0.0201187);
-   gre->SetPoint(1,30,0.2226322);
-   gre->SetPointError(1,0,0.01722242);
-   gre->SetPoint(2,50,0.2054196);
-   gre->SetPointError(2,0,0.01947345);
-   gre->SetPoint(3,70,0.1802011);
-   gre->SetPointError(3,0,0.01681675);
-   gre->SetPoint(4,90,0.1810345);
-   gre->SetPointError(4,0,0.01505044);
-   gre->SetPoint(5,110,0.2074264);
-   gre->SetPointError(5,0,0.02371925);
-   gre->SetPoint(6,130,0.1729894);
-   gre->SetPointError(6,0,0.02294065);
-   gre->SetPoint(7,150,0.211288);
-   gre->SetPointError(7,0,0.02552409);
-   gre->SetPoint(8,170,0.2013201);
-   gre->SetPointError(8,0,0.03734194);
-   gre->SetPoint(9,190,0.1943888);
-   gre->SetPointError(9,0,0.02843923);
[…]

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_t[2]_Phi.C

@@ -1,103 +1,0 @@
-{
-//=========Macro generated from canvas: c1/
-//=========  (Fri Dec 18 09:59:47 2015) by ROOT version5.34/34
-   TCanvas *c1 = new TCanvas("c1", "",1,1,700,476);
-   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
-   c1->SetFillColor(0);
-   c1->SetBorderMode(0);
-   c1->SetBorderSize(0);
-   c1->SetGridx();
-   c1->SetGridy();
-   c1->SetLeftMargin(0.16);
-   c1->SetRightMargin(0.08);
-   c1->SetTopMargin(0.08);
-   c1->SetBottomMargin(0.16);
-   c1->SetFrameBorderMode(0);
-   c1->SetFrameBorderMode(0);
-   
-   TGraphErrors *gre = new TGraphErrors(18);
-   gre->SetName("Graph0");
-   gre->SetTitle("Graph");
-   gre->SetFillColor(1);
-
-   Int_t ci;      // for color index setting
-   TColor *color; // for color definition with alpha
-   ci = TColor::GetColor("#0000ff");
-   gre->SetMarkerColor(ci);
-   gre->SetMarkerStyle(21);
-   gre->SetPoint(0,10,0.2595137);
-   gre->SetPointError(0,0,0.01767792);
-   gre->SetPoint(1,30,0.2453035);
-   gre->SetPointError(1,0,0.0140764);
-   gre->SetPoint(2,50,0.2141393);
-   gre->SetPointError(2,0,0.01532071);
-   gre->SetPoint(3,70,0.1806061);
-   gre->SetPointError(3,0,0.01217269);
-   gre->SetPoint(4,90,0.2111212);
-   gre->SetPointError(4,0,0.01425841);
-   gre->SetPoint(5,110,0.2352168);
-   gre->SetPointError(5,0,0.02610753);
-   gre->SetPoint(6,130,0.2112903);
-   gre->SetPointError(6,0,0.02694614);
-   gre->SetPoint(7,150,0.2794872);
-   gre->SetPointError(7,0,0.0409224);
-   gre->SetPoint(8,170,0.2242424);
-   gre->SetPointError(8,0,0.05432248);
-   gre->SetPoint(9,190,0.2633333);
-   gre->SetPointError(9,0,0.04483087);
[…]

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_t[3]_Phi.C

@@ -1,103 +1,0 @@
-{
-//=========Macro generated from canvas: c1/
-//=========  (Fri Dec 18 09:59:48 2015) by ROOT version5.34/34
-   TCanvas *c1 = new TCanvas("c1", "",1,1,700,476);
-   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
-   c1->SetFillColor(0);
-   c1->SetBorderMode(0);
-   c1->SetBorderSize(0);
-   c1->SetGridx();
-   c1->SetGridy();
-   c1->SetLeftMargin(0.16);
-   c1->SetRightMargin(0.08);
-   c1->SetTopMargin(0.08);
-   c1->SetBottomMargin(0.16);
-   c1->SetFrameBorderMode(0);
-   c1->SetFrameBorderMode(0);
-   
-   TGraphErrors *gre = new TGraphErrors(18);
-   gre->SetName("Graph0");
-   gre->SetTitle("Graph");
-   gre->SetFillColor(1);
-
-   Int_t ci;      // for color index setting
-   TColor *color; // for color definition with alpha
-   ci = TColor::GetColor("#0000ff");
-   gre->SetMarkerColor(ci);
-   gre->SetMarkerStyle(21);
-   gre->SetPoint(0,10,0.2676135);
-   gre->SetPointError(0,0,0.0107303);
-   gre->SetPoint(1,30,0.2622631);
-   gre->SetPointError(1,0,0.009141398);
-   gre->SetPoint(2,50,0.2334912);
-   gre->SetPointError(2,0,0.01131366);
-   gre->SetPoint(3,70,0.251633);
-   gre->SetPointError(3,0,0.01328484);
-   gre->SetPoint(4,90,0.2753623);
-   gre->SetPointError(4,0,0.02153829);
-   gre->SetPoint(5,110,0.2798354);
-   gre->SetPointError(5,0,0.05188648);
-   gre->SetPoint(6,130,0.4081633);
-   gre->SetPointError(6,0,0.105767);
-   gre->SetPoint(7,150,0.3333333);
-   gre->SetPointError(7,0,0.1405215);
-   gre->SetPoint(8,170,0.2352941);
-   gre->SetPointError(8,0,0.1747143);
-   gre->SetPoint(9,190,0.2592593);
-   gre->SetPointError(9,0,0.1478852);
-   gre->SetPoint(10,210,0.25);
[…]

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_xB[0]_Phi.C

@@ -1,103 +1,0 @@
-{
-//=========Macro generated from canvas: c1/
-//=========  (Fri Dec 18 09:59:46 2015) by ROOT version5.34/34
-   TCanvas *c1 = new TCanvas("c1", "",1,1,700,476);
-   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
-   c1->SetFillColor(0);
-   c1->SetBorderMode(0);
-   c1->SetBorderSize(0);
-   c1->SetGridx();
-   c1->SetGridy();
-   c1->SetLeftMargin(0.16);
-   c1->SetRightMargin(0.08);
-   c1->SetTopMargin(0.08);
-   c1->SetBottomMargin(0.16);
-   c1->SetFrameBorderMode(0);
-   c1->SetFrameBorderMode(0);
-   
-   TGraphErrors *gre = new TGraphErrors(18);
-   gre->SetName("Graph0");
-   gre->SetTitle("Graph");
-   gre->SetFillColor(1);
-
-   Int_t ci;      // for color index setting
-   TColor *color; // for color definition with alpha
-   ci = TColor::GetColor("#0000ff");
-   gre->SetMarkerColor(ci);
-   gre->SetMarkerStyle(21);
-   gre->SetPoint(0,10,0.1918736);
-   gre->SetPointError(0,0,0.01727882);
-   gre->SetPoint(1,30,0.1835967);
-   gre->SetPointError(1,0,0.01678977);
-   gre->SetPoint(2,50,0.1408935);
-   gre->SetPointError(2,0,0.01747246);
-   gre->SetPoint(3,70,0.1540388);
-   gre->SetPointError(3,0,0.01367574);
-   gre->SetPoint(4,90,0.1745058);
-   gre->SetPointError(4,0,0.01546273);
-   gre->SetPoint(5,110,0.1646707);
-   gre->SetPointError(5,0,0.02207203);
-   gre->SetPoint(6,130,0.1486111);
-   gre->SetPointError(6,0,0.01990519);
-   gre->SetPoint(7,150,0.1757656);
-   gre->SetPointError(7,0,0.02171222);
-   gre->SetPoint(8,170,0.1626667);
-   gre->SetPointError(8,0,0.0292274);
-   gre->SetPoint(9,190,0.1964912);
-   gre->SetPointError(9,0,0.02679679);
[…]

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_xB[1]_Phi.C

@@ -1,103 +1,0 @@
-{
-//=========Macro generated from canvas: c1/
-//=========  (Fri Dec 18 09:59:46 2015) by ROOT version5.34/34
-   TCanvas *c1 = new TCanvas("c1", "",1,1,700,476);
-   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
-   c1->SetFillColor(0);
-   c1->SetBorderMode(0);
-   c1->SetBorderSize(0);
-   c1->SetGridx();
-   c1->SetGridy();
-   c1->SetLeftMargin(0.16);
-   c1->SetRightMargin(0.08);
-   c1->SetTopMargin(0.08);
-   c1->SetBottomMargin(0.16);
-   c1->SetFrameBorderMode(0);
-   c1->SetFrameBorderMode(0);
-   
-   TGraphErrors *gre = new TGraphErrors(18);
-   gre->SetName("Graph0");
-   gre->SetTitle("Graph");
-   gre->SetFillColor(1);
-
-   Int_t ci;      // for color index setting
-   TColor *color; // for color definition with alpha
-   ci = TColor::GetColor("#0000ff");
-   gre->SetMarkerColor(ci);
-   gre->SetMarkerStyle(21);
-   gre->SetPoint(0,10,0.21498);
-   gre->SetPointError(0,0,0.01622722);
-   gre->SetPoint(1,30,0.2105505);
-   gre->SetPointError(1,0,0.01433715);
-   gre->SetPoint(2,50,0.1911197);
-   gre->SetPointError(2,0,0.01593808);
-   gre->SetPoint(3,70,0.2005277);
-   gre->SetPointError(3,0,0.01489334);
-   gre->SetPoint(4,90,0.1842984);
-   gre->SetPointError(4,0,0.01447875);
-   gre->SetPoint(5,110,0.2059524);
-   gre->SetPointError(5,0,0.0227643);
-   gre->SetPoint(6,130,0.1775862);
-   gre->SetPointError(6,0,0.02487195);
-   gre->SetPoint(7,150,0.2347973);
-   gre->SetPointError(7,0,0.02956535);
-   gre->SetPoint(8,170,0.1495327);
-   gre->SetPointError(8,0,0.02992929);
-   gre->SetPoint(9,190,0.2191781);
-   gre->SetPointError(9,0,0.0328425);
[…]

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_xB[2]_Phi.C

@@ -1,103 +1,0 @@
-{
-//=========Macro generated from canvas: c1/
-//=========  (Fri Dec 18 09:59:47 2015) by ROOT version5.34/34
-   TCanvas *c1 = new TCanvas("c1", "",1,1,700,476);
-   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
-   c1->SetFillColor(0);
-   c1->SetBorderMode(0);
-   c1->SetBorderSize(0);
-   c1->SetGridx();
-   c1->SetGridy();
-   c1->SetLeftMargin(0.16);
-   c1->SetRightMargin(0.08);
-   c1->SetTopMargin(0.08);
-   c1->SetBottomMargin(0.16);
-   c1->SetFrameBorderMode(0);
-   c1->SetFrameBorderMode(0);
-   
-   TGraphErrors *gre = new TGraphErrors(18);
-   gre->SetName("Graph0");
-   gre->SetTitle("Graph");
-   gre->SetFillColor(1);
-
-   Int_t ci;      // for color index setting
-   TColor *color; // for color definition with alpha
-   ci = TColor::GetColor("#0000ff");
-   gre->SetMarkerColor(ci);
-   gre->SetMarkerStyle(21);
-   gre->SetPoint(0,10,0.2463387);
-   gre->SetPointError(0,0,0.01439152);
-   gre->SetPoint(1,30,0.2362288);
-   gre->SetPointError(1,0,0.01175382);
-   gre->SetPoint(2,50,0.2195821);
-   gre->SetPointError(2,0,0.0139289);
-   gre->SetPoint(3,70,0.206772);
-   gre->SetPointError(3,0,0.01405526);
-   gre->SetPoint(4,90,0.2208219);
-   gre->SetPointError(4,0,0.01616897);
-   gre->SetPoint(5,110,0.2210012);
-   gre->SetPointError(5,0,0.0241493);
-   gre->SetPoint(6,130,0.2178423);
-   gre->SetPointError(6,0,0.03118168);
-   gre->SetPoint(7,150,0.2483801);
-   gre->SetPointError(7,0,0.03470477);
-   gre->SetPoint(8,170,0.2378855);
-   gre->SetPointError(8,0,0.04816112);
-   gre->SetPoint(9,190,0.184466);
-   gre->SetPointError(9,0,0.03492703);
[…]

### 2020-06-24 incoherent_pi0_subtraction/fig_R_fit/epgamma_eppi0_xB[3]_Phi.C

@@ -1,103 +1,0 @@
-{
-//=========Macro generated from canvas: c1/
-//=========  (Fri Dec 18 09:59:48 2015) by ROOT version5.34/34
-   TCanvas *c1 = new TCanvas("c1", "",1,1,700,476);
-   c1->Range(-80.8421,0.01578948,424.421,0.5421053);
-   c1->SetFillColor(0);
-   c1->SetBorderMode(0);
-   c1->SetBorderSize(0);
-   c1->SetGridx();
-   c1->SetGridy();
-   c1->SetLeftMargin(0.16);
-   c1->SetRightMargin(0.08);
-   c1->SetTopMargin(0.08);
-   c1->SetBottomMargin(0.16);
-   c1->SetFrameBorderMode(0);
-   c1->SetFrameBorderMode(0);
-   
-   TGraphErrors *gre = new TGraphErrors(18);
-   gre->SetName("Graph0");
-   gre->SetTitle("Graph");
-   gre->SetFillColor(1);
-
-   Int_t ci;      // for color index setting
-   TColor *color; // for color definition with alpha
-   ci = TColor::GetColor("#0000ff");
-   gre->SetMarkerColor(ci);
-   gre->SetMarkerStyle(21);
-   gre->SetPoint(0,10,0.2886309);
-   gre->SetPointError(0,0,0.01168431);
-   gre->SetPoint(1,30,0.2797864);
-   gre->SetPointError(1,0,0.009988949);
-   gre->SetPoint(2,50,0.2544893);
-   gre->SetPointError(2,0,0.01271304);
-   gre->SetPoint(3,70,0.2610107);
-   gre->SetPointError(3,0,0.01662025);
-   gre->SetPoint(4,90,0.2564281);
-   gre->SetPointError(4,0,0.02010893);
-   gre->SetPoint(5,110,0.2588933);
-   gre->SetPointError(5,0,0.03412882);
-   gre->SetPoint(6,130,0.231405);
-   gre->SetPointError(6,0,0.04579806);
-   gre->SetPoint(7,150,0.1717172);
-   gre->SetPointError(7,0,0.04165266);
-   gre->SetPoint(8,170,0.2531646);
-   gre->SetPointError(8,0,0.08509255);
-   gre->SetPoint(9,190,0.2795699);
-   gre->SetPointError(9,0,0.08381821);
[…]

### 2020-07-07 eg6-letters/long-paper/prc-dvcshelium.tex
add tables for the coherent and incoherent alu (90)
Implement all minor changes

@@
 \begin{abstract}
-Measurements of the beam-spin asymmetry in the deeply virtual Compton 
-scattering off $^4$He using the CEBAF Large Acceptance Spectrometer (CLAS) are 
-reported. A 6 GeV longitudinally polarized electron beam was incident on a 
-pressurized $^4$He gaseous target to study the partonic structure of the 
-nucleus and the bound nucleons. To ensure the exclusivity of the reactions, 
-CLAS was upgraded with a radial time projection chamber to detect the 
+We report on the measurement of the beam-spin asymmetry in the deeply virtual Compton 
+scattering off $^4$He using the CEBAF Large Acceptance Spectrometer (CLAS) at
+Jefferson Lab using a 6 GeV longitudinally polarized electron beam incident on a 
+pressurized $^4$He gaseous target. We detail the method used to ensure the exclusivity 
+of the measured reactions, in particular the upgrade of CLAS with a radial time 
+projection chamber to detect the 
 low-energy recoiling $^4$He nuclei and an inner calorimeter to extend the 
@@
 structure functions \cite{Anselmino:2015uka}. These studies, which have focused on generalized
-parton distributions (GPD) and transverse momentum dependent parton distribution functions (PDF)
+parton distributions (GPD) and transverse momentum dependent parton distribution functions (TMD)
 can be generalized to the nucleus and offer a unique opportunity to revisit the quark structure 
@@
 controversies. Indeed, while much progress has been made in measuring the nuclear
-PDFs, their shape remains fundamentally unexplained \cite{Norton:2003cb,Malace:2014uea,Hen:2016kwk}.
+parton distribution functions, their shape remains fundamentally 
+unexplained \cite{Norton:2003cb,Malace:2014uea,Hen:2016kwk}.
 
@@
 medium and offers a unique opportunity to make a measurement free of final state interactions 
-(FSI). Moreover, with a nuclear targets of spin-0 the extraction of the GPD from the DVCS data 
-is significantly simplified with the reduction to a single GPD intervening in the process at leading order. The 
-measurement of the nuclear DVCS is however challenging experimentally, first attempts from 
-the HERMES collaboration \cite{Airapetian:2009cga} lead to controversial conclusions. We present here
-in detail the more recent measurements from the CLAS collaboration, which has been already partially presented
+(FSI). Moreover, with a spin-0 nuclear target, the extraction of the GPD from the DVCS data 
+is significantly simplified since a single GPD is occurring in the process at leading order. However, the 
+measurement of the nuclear DVCS is challenging experimentally and the first attempts by 
+the HERMES collaboration \cite{Airapetian:2009cga} led to controversial conclusions. We present here
+in detail the more recent measurements by the CLAS collaboration, which has been already partially presented
 in two short letters \cite{Hattawy:2017woc,Hattawy:2018liu}. We extend in this article 
@@
 
-The different spin states possible lead to several independent GPDs for any 
+The different possible spin states lead to several independent GPDs for any 
 given hadron. The proper accounting of the number of GPDs must be done with 
@@
 DVCS is the main experimental probe of the GPDs. However, this process does not allow
-for an extraction of the GPDs in full phase space parameters. Instead, DVCS gives access
-to the GPDs integrated over $x$, in the following form:
-\begin{equation}
-	\int^1 _{-1} dx F^{q}(x,\xi,t) \left [ {1 \over x - \xi - i \epsilon} 
-	                                   \mp {1 \over x + \xi - i \epsilon} \right]. 
-\end{equation}
+for an extraction of the GPDs in the full phase space of parameters. Instead, DVCS gives access
+to the GPDs integrated over $x$. 
 To account for this and simplify equations, we define the complex Compton form factors (CFF,
@@
 These are the quantities directly present in the DVCS cross sections. We note that they are summed over
-the different quark flavors present in the hadron, as the electromagnetic probe do not differentiate
+the different quark flavors present in the hadron, as the electromagnetic probe does not differentiate
 quark flavors.
 
-Experimentally, another process is indistinguishable from the DVCS, the Bethe-Heitler (BH) 
+Experimentally, another process is indistinguishable from DVCS, the Bethe-Heitler (BH) 
 process in which 
@@
 where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
-and real parts of the CFF $\mathcal{H}_{A}$ associated to the GPD $H_A$ of the 
+and real parts of the CFF $\mathcal{H}_{A}$ associated with the GPD $H_A$ of the 
 spin-0 nucleus. The 
@@
 An important issue with the use of this theoretical framework is the large mass of the 
-helium nuclei. Recent work indicate that the effect of this correction is moderate 
+helium nucleus. Recent work indicate that the effect of this correction is moderate 
 \cite{Braun:2012bg}, however the applicability to such a large mass remains to be
@@
 BSA signal. Their main results, reproduced in Fig. \ref{fig:HERMES1} and \ref{fig:HERMES2}, suffer
-from large error bars, which makes them consistent with the free proton data and prevents us to
+from large uncertainties, which makes them consistent with the free proton data and prevents us to
 reach strong conclusions about possible nuclear effects. Yet, in the coherent DVCS case a rather
@@
 	\caption{The sinus moment of the BSA as a function of $-t$ measured by HERMES
-	for a series of nuclei \cite{Airapetian:2009cga}.}
+	for a series of nuclei \cite{Airapetian:2009cga}, gray bands represent the systematic 
+        uncertainties.}
 \label{fig:HERMES1}
@@
 \caption{The sinus moment of the BSA at low and high $-t$ as a function of $A$ measured by HERMES
-	\cite{Airapetian:2009cga}.}
+	\cite{Airapetian:2009cga}. The inner error bars represent the statistical uncertainty, while 
+the outer represent the quadratic sum of the statistical and systematic uncertainties.}
 \label{fig:HERMES2}
@@
 Altogether, large error bars and the failure to properly separate the coherent and 
-incoherent channels have strongly impaired the measurement and any conclusions that could be
+incoherent channels have strongly impaired the interpretation of the measurement 
+and the conclusions that could be
 obtained from it. The CLAS experiment presented here has profited largely from this
@@
 
-The CLAS experiment had for main objective to explore the coherent DVCS on helium-4 and assess if
-the predicted BSA increase could be observed and if GPDs could be extracted from it. In order to
+The CLAS experiment had for main objectives to explore the coherent DVCS on helium-4, to assess if
+the predicted BSA increase could be observed, and to extract the helium-4 GPD. In order to
 perform this measurement however, several instrumentation challenges needed to be resolved. First, to
@@
 
-The CLAS \cite{Mecking:2003zu} is installed in the hall-B of the JLab continuous electron beam 
+CLAS \cite{Mecking:2003zu} is installed in the hall-B of the JLab continuous electron beam 
 accelerator facility (CEBAF). CLAS is specifically designed to study the multi-particles final states
@@
 as shown in Fig. \ref{fig:CLAS}.  Three regions of drift chambers \cite{Mestayer:2000we} 
-are placed between the torus magnet to reconstruct the charge particle's tracks and 
-calculate their momentum. An array of scintillators is placed behind drift chambers to measure 
+are placed between the torus magnet to reconstruct the charged particles' tracks and 
+calculate their momentum. An array of scintillators is placed behind the drift chambers to measure 
 a precise time for each track and perform time-of-flight measurement 
 \cite{Smith:1999ii}. These detectors cover the polar angle from 8 to 142 degrees. 
-In forward region, from 8 to 45 degree, these two detectors are complimented with 
+In forward region, from 8 to 45 degree, these two detectors are complemented with 
 Cerenkov counters \cite{Adams:2001kk} and electromagnetic calorimeters \cite{Amarian:2001zs},
@@
 corresponds to luminosities in the range of $1$ to $1.2 \times 10^{34}$ cm$^{-2}$.s$^{-1}$.
-During the experiment, the data acquisition rate ran around 3 kHz with about 70\% live-time
+During the experiment, the data acquisition operated at a rate of about 3 kHz with about 70\% live-time
 using an inclusive electron trigger.
@@
 small angle photons of the DVCS process. This setup is composed of an inner 
-calorimeter and a solenoid and has lead to numerous DVCS measurements on proton 
+calorimeter and a solenoid and has been employed for numerous DVCS measurements on proton 
 targets \cite{Seder:2014cdc,Jo:2015ema,HirlingerSaylor:2018bnu}.
@@
 from electrons and photons, which cannot be separated reliably. However, the detection 
-of an electron at larger angle in CLAS 
-highly suppresses the number of electrons in the calorimeter, moreover
-the exclusivity cuts used later in the analysis further this suppression. Left over accidentals, will be
-accounted for in the background subtraction. The inner calorimeter was calibrated through a series
-of steps, involving the reconstruction of $\pi^0$ from their two photons decay. Calibration was obtained 
+of an electron at larger angle in CLAS highly suppresses the number of electrons 
+in the calorimeter, moreover the exclusivity cuts used later in the analysis further 
+this suppression. Left over accidentals are accounted for in the background subtraction 
+described below. The inner calorimeter was calibrated through a series of steps, 
+involving the reconstruction of $\pi^0$ from their decay into two photons. Calibration was obtained 
 with an iterative process to adjust each crystal gain to obtain the most accurate $\pi^0$ mass. A
@@
 exclusivity cuts based on energy and momentum conservation. In principle, 
-a selection based on two or three variables can be used to guaranty the 
+a selection based on two or three variables can be used to guarantee the 
 exclusivity of the process. However, in such experiment, where particles 
@@
 	\item Missing transverse momentum of the full system;
-	\item Missing mass of the system electron-helium;
-	\item Missing mass of the system electron-photon;
+	\item Missing mass of the electron-helium system;
+	\item Missing mass of the electron-photon system;
 	\item Co-linearity ($\theta$) of the measured photon with the missing momentum of the 
@@
 Fig. \ref{fig:IncExcCuts}, with two main differences: larger distributions overall and more
-offset distributions. The larger distributions are largely attributed to the effect of 
+offset distributions. The larger distributions are mainly attributed to the effect of 
 Fermi motion, but simulations have shown that this effect is not strong enough to fully 
@@
 As discussed above, the best way to define $t$ in the incoherent channel is not completely
-straightforward. As can be seen in the Fig. \ref{fig:InCohDiag}, 
+straightforward. As can be seen in Fig. \ref{fig:InCohDiag}, 
 we can either use $t$ or $t^\prime$ ($= (p - p^\prime)^2$). In principle, the two are 
@@
 can conclude that this measurement cleanly isolates the coherent DVCS process. The absence of 
-this feature in the previous measurement from HERMES \cite{Airapetian:2009cga} and its clear observation here indicates that the recoil 
-detection is a necessity to isolate the effects of the coherent DVCS process from backgrounds.
+this feature in the previous measurement by HERMES \cite{Airapetian:2009cga} and its clear observation here indicates that the recoil 
+detection is necessary to isolate the effects of the coherent DVCS process from backgrounds.
 
@@
 	with green circles \cite{Airapetian:2009cga}. Theoretical predictions 
-	from Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
-	with red full line and dashed blue, while the calculation from Fucini 
+	by Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
+	with red full line and dashed blue, while the calculation by Fucini 
 	{\it et al.}~\cite{Fucini:2018gso} is shown with a magenta long dash line.}
@@
 and the UIV three-body forces \cite{Pudliner:1995wk}, has been able to reproduce the data very 
-well. Another factor in the difference is that the recent calculation from Fucini {\it et 
+well. Another factor in the difference is that the recent calculation by Fucini {\it et 
 al.}~\cite{Fucini:2018gso} benefited from using the precise kinematic of each points presented 
@@
 
-One of the promise of the helium-4 coherent DVCS was the ease to extract the CFF $\mathcal{H}_A$ from
-data. To do so, we used the form from Eq. \ref{eq:A_LU-coh} to fit the data in Fig. 
-\ref{fig:CohALUphi}. We presente in Fig. \ref{fig:CohCFF} the real and imaginary parts 
-of the single CFF of the helium-4 nucleus. The results are rather encouraging, the two parts
+One of the motivation for the choice of helium-4 for the coherent DVCS measurement was
+a simplified extraction of the CFF $\mathcal{H}_A$ from
+data. To perform this step, we used the form from Eq. \ref{eq:A_LU-coh} to fit the data in Fig. 
+\ref{fig:CohALUphi}. We present in Fig. \ref{fig:CohCFF} the real and imaginary parts 
+of the single CFF of the helium-4 nucleus extracted. The results are rather encouraging, the two parts
 of the CFF are constrained by data without the need of any model assumption. This capacity to obtain a
@@
 	CFF $\mathcal{H}_A$ as a function of $Q^2$ (left panels), $x$ (middle panels) and 
-	$-t$ (right panels). The red full line is the theoretical calculation from 
+	$-t$ (right panels). The red full line is the theoretical calculation by 
 	Guzey {\it et al.}~\cite{Guzey:2003jh,Guzey:2008th}, the black dashed line is the same calculation 
 	using the VGG model as input \cite{Vanderhaeghen:1999xj,Guidal:2004nd}, and
-	the blue long dash line shows the predictions from Liuti {\it et 
+	the blue long dash line shows the predictions by Liuti {\it et 
 	al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv}.} 
@@
 Fig. \ref{fig:CohCFF}, we show two versions of this calculation, where two different nucleon GPD
-models are used as input, compared with the calculation previously shown from Liuti 
+models are used as input, compared with the calculation previously shown by Liuti 
 {\it et al.}~\cite{Liuti:2005gi} with an updated nucleon model \cite{GonzalezHernandez:2012jv}.
@@
 coherent nuclear DVCS and of nuclear GPDs. While, the statistical precision and 
-the kinematic coverage are still far behind the experimental results on
-proton target, the results appear to match very well the predictions using the GPD 
+the kinematic coverage are still behind the experimental results of
+the proton, the results appear to match very well the predictions using the GPD 
 framework. Moreover, the extraction of the CFF appears to be very convenient based
@@
 the HERMES data, which offers a strong constraint on the model presented. As in the
-coherent case, the calculation appears to have issues to reproduce the shape of the data,
+coherent case, the calculation appears to have issues reproducing the shape of the data,
 with Fucini {\it et al.}~\cite{Fucini:2019xlc} doing better than the others.
@@
 in Fig. \ref{fig:IncRatios}.
-Notably, the calculation from Fucini {\it et al.}~\cite{Fucini:2019xlc} appears closer to the
-other with this observable, hinting that maybe the different results with the raw asymmetries 
-was linked to the input model they used for the free nucleon GPD rather than the nuclear model. 
-Also, they appear to reproduce the 
+Notably, the calculation by Fucini {\it et al.}~\cite{Fucini:2019xlc} appears closer than the
+others with this observable. This feature indicates that the different raw asymmetry results might be 
+linked to the different input model used for the free nucleon GPD rather than to differences in the 
+treatment of the nuclear effects. Also, Fucini {\it et al.} appear to reproduce the 
 shape of the $x_B$ distribution, which would indicate that it is linked to kinematic effects.
@@
 	measurement \cite{Airapetian:2009cga} with green circles. Theoretical predictions 
-	from Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
-	with red full line and dashed blue, while the calculation from Fucini 
+	by Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
+	with red full line and dashed blue, while the calculation by Fucini 
 	{\it et al.}~\cite{Fucini:2019xlc} is shown with a magenta long dash line.}
@@
 	measurement \cite{Airapetian:2009cga} with green circles. Theoretical predictions 
-	from Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
-	with red full line and dashed blue, a calculation adapted from Fucini 
+	by Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
+	with red full line and dashed blue, a calculation adapted by Fucini 
 	{\it et al.}~\cite{Fucini:2019xlc} is shown with a magenta long dash line and the
-	the black dot-dash line is the calculation from Guzey {\it et al.}~\cite{Guzey:2008th}.}
+	the black dot-dash line is the calculation by Guzey {\it et al.}~\cite{Guzey:2008th}.}
 \label{fig:IncRatios}
@@
 
+\begin{table}[!h]
+   \begin{center}
+      \begin{tabular}{||l|l|l|l||}
+         \hline
+ $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $A_{LU}$(90$^{\circ}$) $\pm$ stat. $\pm$ syst.\\
+  \hline
+  1.143 & 0.136 & 0.096 &  0.3036 $\pm$ 0.0513 $\pm$ 0.0321\\
+  1.423 & 0.172 & 0.099 &  0.3641 $\pm$ 0.0594 $\pm$ 0.0374\\
+  1.902 & 0.224 & 0.107 &  0.2946 $\pm$ 0.0605 $\pm$ 0.0275\\
+  \hline                   
+  1.164 & 0.132 & 0.095 &  0.3196 $\pm$ 0.0446 $\pm$ 0.0376\\
+  1.439 & 0.17  & 0.099 &  0.2780 $\pm$ 0.0788 $\pm$ 0.0269\\
+  1.844 & 0.225 & 0.107 &  0.3196 $\pm$ 0.1612 $\pm$ 0.0366\\
+  \hline                   
+  1.36  & 0.160 & 0.080 &  0.3760 $\pm$ 0.0416 $\pm$ 0.0326\\
+  1.507 & 0.179 & 0.094 &  0.2452 $\pm$ 0.0720 $\pm$ 0.0309\\
+  1.610 & 0.193 & 0.127 &  0.3182 $\pm$ 0.0948 $\pm$ 0.0345\\
+  \hline
+  \end{tabular}
+  \caption{Values of the coherent $A_{LU}$(90$^{\circ}$) in $Q^2$ (top block), $x_B$ (middle block), and $-t$ (bottom block) bins. }
+  \label{table:Coh_BSA_90}
+  \end{center}
+\end{table}
+
+% incoherent channel
+
+\begin{table}[!h]
+\begin{center}
+\begin{tabular}{||l|l|l|l||}
+\hline
+ $<Q^{2}>$ & $<x_{B}>$ & $<-t>$  & $A_{LU}$(90$^{\circ}$) $\pm$ stat. $\pm$ syst.\\
+ \hline 
+  1.404 & 0.166 & 0.376 & 0.1369 $\pm$ 0.0223 $\pm$ 0.0136\\   
+  1.889 & 0.232 & 0.415 & 0.1529 $\pm$ 0.0266 $\pm$ 0.0169\\   
+  2.339 & 0.288 & 0.497 & 0.1902 $\pm$ 0.0299 $\pm$ 0.0169\\   
+  3.098 & 0.379 & 0.641 & 0.1297 $\pm$ 0.0413 $\pm$ 0.0155\\   
+ \hline                   
+  1.449 & 0.163 & 0.374 & 0.1173 $\pm$ 0.0211 $\pm$ 0.0118\\   
+  1.929 & 0.225 & 0.381 & 0.1772 $\pm$ 0.0237 $\pm$ 0.0183\\   
+  2.334 & 0.283 & 0.468 & 0.1777 $\pm$ 0.0308 $\pm$ 0.0153\\   
+  2.975 & 0.389 & 0.688 & 0.1603 $\pm$ 0.0480 $\pm$ 0.0144\\   
+ \hline                   
+  1.842 & 0.215 & 0.135 & 0.1828 $\pm$ 0.0205 $\pm$ 0.0143\\   
+  2.149 & 0.257 & 0.281 & 0.1408 $\pm$ 0.0272 $\pm$ 0.0200\\   
+  2.366 & 0.291 & 0.492 & 0.1371 $\pm$ 0.0290 $\pm$ 0.0244\\   
+  2.447 & 0.312 & 1.089 & 0.1389 $\pm$ 0.0618 $\pm$ 0.0239\\
+
+ \hline
+ \hline
+ \end{tabular}
+ \caption{Values of the incoherent $A_{LU}$(90$^{\circ}$) in $Q^2$ (top block), $x_B$ (middle block), and $-t$ (bottom block) bins.}
+ \label{table:InCoh_BSA_90}
+ \end{center}
+\end{table}
+
 % Create the reference section using BibTeX:

### 2020-08-17 eg6-letters/long-paper/AdHoc/AnswerAdHoc.tex
Start answer AdHoc last paper

%\documentclass[a4paper,11pt,twoside]{ThesisStyle}
\documentclass[a4paper,11pt,twoside]{article}

\title{Answer to comments from the Ad-hoc rewiew committee \\
 Measurement of deeply virtual Compton
scattering off Helium-4 with CLAS at Jefferson Lab}

\date{\today}
\include{formatAndDefs}

\begin{document}

\maketitle

\section*{}

The committee met on July 2, 2020, to discuss our concerns about the manuscript. We are separating out
our comments on English, wording, typographical errors, etc., as helpful suggestions for you, which do not need
any reponse. However, there are a few areas concern where we would like a response before we can approve the
manuscript. In some cases, we would appreciate a direct answer or some clarifying information. In others, we
recommend changes to the manuscript to make it more clear and easier to read. In any case, please note your
reponse and any manuscript changes in a written document in addition to any discussion between the committee
and the authors by e-mail, so that the response can be preserved in the official record.

\begin{enumerate}
\item  As this is a long paper, giving more details about two published letters, we'd appreciate some statement as
to whether or not anything in the analysis has changed between this paper and the two previous papers? Did
the systematic error decrease? Did the central values of the results move in any case more than 1$\sigma$ of their
former error. Perhaps it would be good to state the changes/improvements achieved in this new publication.

   \textcolor{blue}{There was no change to the results. The statement at the end of the second paragraph
clearly states that we are giving more details and do not mention any change or new analysis.}

\item  We have concerns about how you describe your approach to the $\pi^0$ contamination, especially in the incoherent
channel.
\begin{enumerate}
\item In Figs. 14 and 15, bottom right panels, what is the definition of the $\phi$ angle? Is this the $\phi$ angle of the
$\pi^0$ ?

   \textcolor{blue}{Yes.}

\item What kind of input distributions went into the $\pi^0$ generation to produce the $\phi$-dependence of Figs. 14
and 15.

   \textcolor{blue}{This is given in eq. 3.6 and tab. 3.1 of the analysis note, we decided not to go to this level 
   of details.}

\item We feel that it would be more useful to see the $\phi$ distribution calculated (from simulation) from the
single detected photons, i.e., what the $\phi$-distribution of your actual background looks like.

   \textcolor{blue}{the intent of this figure is comparing the simulation to the real data. What you propose is 
different and would show the shape of the background. We do not have a way to show this background from experimental 
data. We provided some of this information by email, but are not convinced it is a useful addition. The document is
already going into a lot of technical details already.}

\item In lines 280-282, you write "To make the correction on the DVCS BSA, we assume that the exclusive $\pi^0$
production has no such asymmetry. This has been checked with the exclusive $\pi^0$ production data, for
which no significant level of BSA was measured."
There are couple of issues here. First, this claim is contradicted by CLAS data on protons, for example
https://arxiv.org/pdf/0711.4736.pdf, which observed 5-10\% BSA over a wide kinematic range.
Second, even if you check with your own exclusive $\pi^0$ data and see no BSA, this claim is only so good as
the precision of your check, and there must be some systematic uncertainty associated with the possibility
of a BSA below your ability to detect. This needs to be explained in the paper.

   \textcolor{blue}{The results are not contradictory, our target is half proton half neutron and will experience,
at least, some smearings from nuclear effects. There is clearly no solid ground to build a correction from the 
existing data. Moreover, our own measurement shows results consistent with 0, so if we were to make a correction
it would be very small. On your second point, there is indeed
a systematic error associated with the $\pi^0$ substraction as specified in the Tab. 1. We clarified in the text that 
this correction includes a possible undetected asymmetry in the exclusive $\pi^0$ data.}

\item It would be helpful for you to write a few words explaining the differences in the assumed $\pi^0$ distributions
for the coherent and incoherent cases.

   \textcolor{blue}{There are no assumptions on this, we adjusted the parameters to fit the measured distributions.
We clarify this point in the text of the paper.}

\end{enumerate}

\item  Regarding the final state interaction discussion starting at approximately line 100, the issue is a nucleonic
final state interaction issue, and we are not sure why DIS is mentioned here as a reference. There must be
people who spent their time investigating the A(e, e 0 p)X nucleonic final state calculations, for example, that
might inform us on these effects. Perhaps adding a more relevant reference would help.
   \textcolor{blue}{...}

\item  In Section 4.1, your choice to use the present tense here is quite jarring, especially since you don't make a
distinction between the original CLAS, the upgraded CLAS-12 detector. Please consider switching to past
tense here and making that distinction explicit. Furthermore, it would be good to state that these data came
from the EG6 run period, and give the year that they were collected.
   \textcolor{blue}{...}

5. Line 147: "Its historic use to measure DVCS in many different configurations made it an ideal place for this
new DVCS measurement."
This is not an informative claim. CLAS can be ideal for DVCS for many reasons, but you're pretty much
giving a tautology here.
   \textcolor{blue}{The information is that CLAS has been used for other DVCS measurements in the past. It seems
rather relevant when showing results for a new DVCS channel.}

\item  Section 5.1: "In particular, it serves for the identification of the protons."
Are you referring to the time-of-flight detection of the electron or the proton? Perhaps separate sections for
electron ID and proton ID are warranted. Furthermore, you have no section on the ID of 4 He in the RTPC.
We know that this is covered in the RTPC NIM, but a paragraph would be nice.
   \textcolor{blue}{...}

\item  Line 238: "In principle, a selection based on two or three variables can be used to guaranty the exclusivity of
the process."
In exclusive DVCS, you measure the momentum vectors of 3 particles of known ID, i.e. 9 quantities. Exclu-
sivity requires both energy and momentum conservation, i.e. 4 constraints. Where do "2 or 3" come from?
That is a vague statement.
   \textcolor{blue}{This is incorrect, 1 constraint is enough, you can ensure exclusivity by only cutting on missing 
energy, if it is 0 the process is exclusive. Due to the effects of resolution this is usually never a good solution
and 2-3 variables are used, often mass and missing momentum for instance. However, we agree the statement was a bit 
vague and we changed this sentence.}

\item  Line 302: "As it is not obvious which solution is best. . ."
What is obvious is that this is not an issue of correct or incorrect, but one of possible bias introduced to your
BSA from your poor t resolution. Please rephrase the paragraph in these terms, and state what systematic
uncertainty is introduced from the limitations in your ability to reconstruct t. If this effect introduces negligible
uncertainty on the BSA, that's fine, but make that argument clear.
   \textcolor{blue}{...}

\item  Table 1 is mildly misleading, simply because the beam polarization is a relative uncertainty, while the others
are absolute uncertainties (if we understand correctly). Perhaps it is better to pull beam polarization out of
the middle of the table and put it somewhere else so it can be understood as distinct.
That 3.5\% is a multiplicative factor, right?
   \textcolor{blue}{...}

\item  Eq. 25 appears to have a mis-print. xA should be $x_A$.
   \textcolor{blue}{Done.}

\item  English and Typographical suggestions.
   \textcolor{blue}{All done.}

\end{enumerate}

\end{document}

### 2020-08-17 eg6-letters/long-paper/prc-dvcshelium.tex
Start answer AdHoc last paper

@@
 
-To select exclusive events and suppress the backgrounds, we define several 
-exclusivity cuts based on energy and momentum conservation. In principle, 
-a selection based on two or three variables can be used to guarantee the 
-exclusivity of the process. However, in such experiment, where particles 
+In principle, 
+a selection based only on the missing energy of the system would be
+enough to guarantee the 
+exclusivity of the process. However, in our experiment, where particles 
 are detected at very different energies and with very different detector 
-resolutions, we chose to over constrain the selection by using seven 
-variables. The seven variables are defined as follow for the coherent 
+resolutions, this method would not be optimal. For instance the momentum 
+of the helium nuclei is negligible in the missing energy observable, thus
+this valuable information has no impact on a selection using this observable only.
+To circumvent this issue, we constrain the selection of our exclusive events by using seven 
+variables selected to optimize the use of all the detector information available. 
+The seven variables are defined as follow for the coherent 
 DVCS (replace helium by proton for the incoherent case):
@@
 to match the $\pi^0$ mass. The events obtained for the coherent and incoherent
-channels are shown in Fig. \ref{fig:CohPi0Simul} and \ref{fig:InCohPi0Simul}, respectively. From 
-this sample, we elaborated an event generator, which after being processed
-in the simulation of the detectors gives the red histograms of Fig. \ref{fig:CohPi0Simul} and 
+channels are shown in Fig. \ref{fig:CohPi0Simul} and \ref{fig:InCohPi0Simul}, respectively. Using 
+this sample, we elaborated an event generator by adjusting it to the data after being processed
+in the simulation of the detectors. the result of this process is shown with the red histograms 
+of Fig. \ref{fig:CohPi0Simul} and 
 \ref{fig:InCohPi0Simul}. To correct the experimental data, we estimate the number of single photon 
@@
 of its measurements during the complete run period. We also checked different methods to make the 
-simulation of the exclusive $\pi^0$ production to evaluate the 
+simulation of the exclusive $\pi^0$ production and accounted for a possible undetected 
+asymmetry in its signal to evaluate the 
 possible bias introduced by this correction. As radiative corrections are expected to be small
@@
    S_{++}(1) &=& \frac{-8K(2-y)y}{1+\epsilon^2} \left( 1 + 
-\frac{1-xA+\frac{\sqrt{1+\epsilon^2}-1}{2}}{1+\epsilon^2} 
+\frac{1-x_A+\frac{\sqrt{1+\epsilon^2}-1}{2}}{1+\epsilon^2} 
 \frac{t-t_{min}}{Q^{2}} \right) \label{eq:s1I}

### 2020-09-23 eg6-letters/long-paper/AdHoc/AnswerAdHoc.tex
Further answers to comments for long paper

@@
 
-   \textcolor{blue}{This is given in eq. 3.6 and tab. 3.1 of the analysis note, we decided not to go to this level 
-   of details.}
+   \textcolor{blue}{This is given in eq. 3.6 and tab. 3.1 of the analysis note, there is no $\phi$-dependence 
+   in the generation. We decided not to go to this level 
+   of details in this paper as the parameters have no relevant physics signification.}
 
@@
 
-   \textcolor{blue}{the intent of this figure is comparing the simulation to the real data. What you propose is 
-different and would show the shape of the background. We do not have a way to show this background from experimental 
-data. We provided some of this information by email, but are not convinced it is a useful addition. The document is
-already going into a lot of technical details already.}
+   \textcolor{blue}{The intent of this figure is to compare the simulation to the real data, to assess the 
+quality of the simulation. What you propose would not be more useful, it would serve a different purpose:
+showing the shape of the background. We do not have a way to show this background from experimental 
+data so it would not allow to assess the same information. We provided some of the numbers by email, 
+but are not convinced it highlights anything important about the analysis. The document is
+already going into a lot of technical details, probably more than most comparable long paper and prefer not 
+to go to that extend.}
 
@@
 existing data. Moreover, our own measurement shows results consistent with 0, so if we were to make a correction
-it would be very small. On your second point, there is indeed
-a systematic error associated with the $\pi^0$ substraction as specified in the Tab. 1. We clarified in the text that 
+it would be very small. On your second point, there is indeed a systematic error associated with the $\pi^0$ 
+substraction as specified in the Tab. 1. We clarified in the text that 
 this correction includes a possible undetected asymmetry in the exclusive $\pi^0$ data.}
@@
 
-   \textcolor{blue}{There are no assumptions on this, we adjusted the parameters to fit the measured distributions.
-We clarify this point in the text of the paper.}
+   \textcolor{blue}{There are no assumptions on this, we adjusted the parameters to fit the measured 
+distributions. We clarify this point in the text of the paper.}
 
@@
 from the EG6 run period, and give the year that they were collected.
-   \textcolor{blue}{...}
+   \textcolor{blue}{This section has been modified.}
 
@@
    \textcolor{blue}{The information is that CLAS has been used for other DVCS measurements in the past. It seems
-rather relevant when showing results for a new DVCS channel.}
+to be a relevant information when showing results for DVCS on a new target.}
 
@@
 We know that this is covered in the RTPC NIM, but a paragraph would be nice.
-   \textcolor{blue}{...}
+   \textcolor{blue}{We made the change and clarified the detection of protons and helium nuclei.}
 
@@
 energy, if it is 0 the process is exclusive. Due to the effects of resolution this is usually never a good solution
-and 2-3 variables are used, often mass and missing momentum for instance. However, we agree the statement was a bit 
-vague and we changed this sentence.}
+and 2-3 variables are used, often missing mass and missing momentum for instance. However, we agree the statement was 
+vague and not very useful, we changed this sentence completely.}
 
@@
 uncertainty on the BSA, that's fine, but make that argument clear.
-   \textcolor{blue}{...}
+   \textcolor{blue}{We added a sentence about the fact that no error is associated to 
+this study.}
 
@@
 That 3.5\% is a multiplicative factor, right?
-   \textcolor{blue}{...}
+   \textcolor{blue}{We changed the order of the lines and the presentation in the table to make it clearer.}
 

### 2020-09-23 eg6-letters/long-paper/prc-dvcshelium.tex
Further answers to comments for long paper

@@
 
-The CLAS experiment had for main objectives to explore the coherent DVCS on helium-4, to assess if
+The CLAS nuclear DVCS experiment had for main objectives to explore the coherent DVCS on helium-4, to assess if
 the predicted BSA increase could be observed, and to extract the helium-4 GPD. In order to
@@
 
-CLAS \cite{Mecking:2003zu} is installed in the hall-B of the JLab continuous electron beam 
-accelerator facility (CEBAF). CLAS is specifically designed to study the multi-particles final states
+CLAS \cite{Mecking:2003zu} was installed in the hall-B of the JLab continuous electron beam 
+accelerator facility (CEBAF). CLAS was specifically designed to study the multi-particles final states
 that cannot be observed conveniently with arm spectrometers. Its historic use to measure DVCS in many different 
-configurations made it an ideal place for this new DVCS measurement. CLAS is composed of six identical radial 
+configurations made it an ideal place for this new DVCS measurement. CLAS was composed of six identical radial 
 sectors separated by coils of toroidal magnets, with each sector made of four detectors 
 as shown in Fig. \ref{fig:CLAS}. Three regions of drift chambers \cite{Mestayer:2000we} 
-are placed between the torus magnet to reconstruct the charged particles' tracks and 
-calculate their momentum. An array of scintillators is placed behind the drift chambers to measure 
+were placed between the torus magnet to reconstruct the charged particles' tracks and 
+calculate their momentum. An array of scintillators was placed behind the drift chambers to measure 
 a precise time for each track and perform time-of-flight measurement 
-\cite{Smith:1999ii}. These detectors cover the polar angle from 8 to 142 degrees. 
-In forward region, from 8 to 45 degree, these two detectors are complemented with 
+\cite{Smith:1999ii}. These detectors covered the polar angle from 8 to 142 degrees. 
+In the forward region, from 8 to 45 degree, these two detectors were complemented with 
 Cerenkov counters \cite{Adams:2001kk} and electromagnetic calorimeters \cite{Amarian:2001zs},
-important for electron identification.
+important for electron identification and photon detection.
 
@@
 
-Altogether, CLAS provides a large acceptance of about $2\pi$ steradians for momenta 
-starting at 200 MeV/c. During the nuclear DVCS experiment,
-the beam energy was highest for CLAS with 6.064 GeV, while the beam intensity varied
+Altogether, CLAS provided a large acceptance for momenta 
+starting at 200 MeV/c. The nuclear DVCS experiment took place from October to December 2009,
+the beam energy was 6.064 GeV, while the beam intensity varied
 between 120 and 150 nA. Such beam on the helium-4 target pressurized between 5 and 6 atm,
@@
 provide the identification. A signal of good quality is also required in the 
-time-of-flight system, which serves as a time reference for other detectors. In particular, it 
-serves for the identification of the protons. Several 
+time-of-flight system, which serves as a time reference for all detectors. 
+Protons are detected with the baseline CLAS detectors as well, the drift chamber measures the kinematic 
+of the proton and the time-of-flight system ensure its identification.
+Several 
 fiducial cuts are applied to ensure that particles did not go through part of the inner calorimeter 
@@
 time dependent effects.
+
+The helium-4 nuclei are detected with the RTPC using a series of constraints on the quality
+of the track reconstruction. As the chamber was operated at low gain and had very low efficiency 
+for protons, we did not apply further identification cuts for the helium-4 nuclei 
+detection~\cite{Dupre:2017upj}.
 
@@
 \hline
-DVCS cuts & 8 $\%$ &  6 $\%$ & bin to bin\\
-\hline
-Data binning & 5.1$\%$ & 7.1$\%$ &bin to bin\\
-\hline
 Beam polarization &  3.5$\%$ &  3.5$\%$& Normalization\\
 \hline
-$\pi^0$ subtraction &  0.6$\%$ &  2.0$\%$ &bin to bin\\
-\hline
-%Beam charge asymmetry &  ~~~~~1.1$\%$&  ~~~~~1.1$\%$\\
-%\hline
-Radiative corrections &  0.1$\%$ & 0.1$\%$ & bin to bin\\
-\hline
-\textbf{Total} &  \textbf{10.1}$\%$ &   \textbf{10.1}$\%$ &bin to 
+\hline
+DVCS cuts & 8 $\%$ &  6 $\%$ & Bin to bin\\
+\hline
+Data binning & 5.1$\%$ & 7.1$\%$ & Bin to bin\\
+\hline
+$\pi^0$ subtraction &  0.6$\%$ &  2.0$\%$ & Bin to bin\\
+\hline
+Radiative corrections &  0.1$\%$ & 0.1$\%$ & Bin to bin\\
+\hline
+\hline
+\textbf{Total bin to bin} &  \textbf{10.1}$\%$ &   \textbf{10.1}$\%$ & Bin to 
 bin\\
@@
 
-As discussed above, the best way to define $t$ in the incoherent channel is not completely
-straightforward. As can be seen in Fig. \ref{fig:InCohDiag}, 
+An extra problem that was studied is the best way to define $t$ in the incoherent channel, 
+which is not completely straightforward. As can be seen in Fig. \ref{fig:InCohDiag}, 
 we can either use $t$ or $t^\prime$ ($= (p - p^\prime)^2$). In principle, the two are 
@@
 definitions. We found no significant difference between them, as it is 
-illustrated in Fig. \ref{fig:ttpComp}. We use in the final results $t$,
-which is the correct definition with the slightly poorer resolution.
+illustrated in Fig. \ref{fig:ttpComp}. We use in the final results $t$ as it is based on the 
+rigorous definition. Since the effect of resolution appears small and is partly accounted for
+in the systematic error associated to the DVCS cuts, we decided not to associate an extra
+systematic error based on this study.
 

### 2020-10-09 eg6-letters/long-paper/AdHoc/AnswerAdHoc.tex
Finish material for Ad Hoc answer on long paper

@@
 data so it would not allow to assess the same information. We provided some of the numbers by email, 
-but are not convinced it highlights anything important about the analysis. The document is
-already going into a lot of technical details, probably more than most comparable long paper and prefer not 
+but are not convinced it highlights anything important about the analysis. The article is
+already going into a lot of technical details, probably more than most comparable long paper. So we prefer not 
 to go to that extend.}
@@
 \textcolor{blue}{The results are not contradictory, our target is half proton half neutron and will experience,
-at least, some smearings from nuclear effects. There is clearly no solid ground to build a correction from the 
-existing data. Moreover, our own measurement shows results consistent with 0, so if we were to make a correction
+at least, some nuclear effects. There is clearly no solid ground to build a correction from the 
+existing data. Moreover, our CLAS measurement shows results consistent with 0, so if we were to make a correction
 it would be very small. On your second point, there is indeed a systematic error associated with the $\pi^0$ 
@@
 might inform us on these effects. Perhaps adding a more relevant reference would help.
-   \textcolor{blue}{...}
+
+   \textcolor{blue}{We added a modern reference about quasi-elastic FSI. We welcome suggestions if you know 
+of more relevant publications on the topic.}
 
@@
 from the EG6 run period, and give the year that they were collected.
+
    \textcolor{blue}{This section has been modified.}
@@
 giving a tautology here.
+
    \textcolor{blue}{The information is that CLAS has been used for other DVCS measurements in the past. It seems
@@
 We know that this is covered in the RTPC NIM, but a paragraph would be nice.
+
    \textcolor{blue}{We made the change and clarified the detection of protons and helium nuclei.}
@@
 That is a vague statement.
-   \textcolor{blue}{This is incorrect, 1 constraint is enough, you can ensure exclusivity by only cutting on missing 
-energy, if it is 0 the process is exclusive. Due to the effects of resolution this is usually never a good solution
-and 2-3 variables are used, often missing mass and missing momentum for instance. However, we agree the statement was 
+
+   \textcolor{blue}{This is incorrect, one constraint is enough, you can ensure exclusivity by only cutting on missing 
+energy, if it is 0 the process is exclusive. Due to the effects of resolution, this is usually never a good solution
+and 2, 3 or more variables are used, often missing mass and missing momentum for instance. Anyway, we agree the statement was 
 vague and not very useful, we changed this sentence completely.}
@@
 uncertainty on the BSA, that's fine, but make that argument clear.
+
    \textcolor{blue}{We added a sentence about the fact that no error is associated to 
@@
 That 3.5\% is a multiplicative factor, right?
+
    \textcolor{blue}{We changed the order of the lines and the presentation in the table to make it clearer.}
@@
 \item  Eq. 25 appears to have a mis-print. xA should be $x_A$.
+
    \textcolor{blue}{Done.}
@@
 \item  English and Typographical suggestions.
+
    \textcolor{blue}{All done.}

### 2020-10-09 eg6-letters/long-paper/prc-dvcshelium.tex
Finish material for Ad Hoc answer on long paper

@@
 \usepackage{amsmath} 
+\usepackage{multirow}
 
@@
 constraining the range of initial Fermi motion and final interactions possible. However, no theoretical
-calculation is available to correct for the reminder of these effects yet. Since, modern calculations exist 
-for such effects in DIS \cite{Cosyn:2017ekf}, we can expect them to be extended to the DVCS 
+calculation is available to correct for the reminder of these effects yet. Modern calculations exist 
+for such effects in DIS \cite{Cosyn:2017ekf} and quasi-elastic \cite{Ethier:2014bua}
+and we can expect them to be extended to the DVCS 
 process as more data becomes available. Another avenue of progress
@@
 
+\bibliographystyle{unsrt}
+\bibliography{hadro.bib}
+
 \appendix
@@
 
-\section{Table of results with kinematic information}
+\section{Tables of results with kinematic information}
 \label{sec:fullresults}
-%TODO Tables to be checked
 
@@
    \begin{center}
-      \begin{tabular}{||l|l|l|l|l||}
-         \hline
- $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
-         \hline
-  1.143 & 0.136 & 0.096 & 24.3  &  0.1327 $\pm$ 0.1088 $\pm$ 0.0257 \\ 
-  1.143 & 0.136 & 0.096 & 61.1  &  0.3210 $\pm$ 0.0932 $\pm$ 0.0188 \\ 
-  1.143 & 0.136 & 0.096 & 98.9  &  0.3709 $\pm$ 0.1026 $\pm$ 0.0403 \\ 
-  1.143 & 0.136 & 0.096 & 140.9 &  0.2452 $\pm$ 0.1517 $\pm$ 0.0267 \\ 
-  1.143 & 0.136 & 0.096 & 178.4 &  0.0225 $\pm$ 0.1632 $\pm$ 0.0278 \\ 
-  1.143 & 0.136 & 0.096 & 219.1 & -0.0526 $\pm$ 0.1475 $\pm$ 0.0248 \\ 
-  1.143 & 0.136 & 0.096 & 262.9 & -0.2642 $\pm$ 0.1196 $\pm$ 0.0389 \\ 
-  1.143 & 0.136 & 0.096 & 301.9 & -0.1761 $\pm$ 0.0968 $\pm$ 0.0263 \\ 
-  1.143 & 0.136 & 0.096 & 337.7 & -0.2791 $\pm$ 0.1047 $\pm$ 0.0343 \\ 
-  \hline                                                                                                           
-  1.423 & 0.172 & 0.099 & 21.1  &  0.1917 $\pm$ 0.0892 $\pm$ 0.0267 \\ 
-  1.423 & 0.172 & 0.099 & 56.6  &  0.2819 $\pm$ 0.0866 $\pm$ 0.0250 \\ 
-  1.423 & 0.172 & 0.099 & 96.9  &  0.4855 $\pm$ 0.1291 $\pm$ 0.0426 \\ 
-  1.423 & 0.172 & 0.099 & 139.9 &  0.0996 $\pm$ 0.1679 $\pm$ 0.0250 \\ 
-  1.423 & 0.172 & 0.099 & 180.3 &  0.1458 $\pm$ 0.1906 $\pm$ 0.0302 \\ 
-  1.423 & 0.172 & 0.099 & 218.7 & -0.1109 $\pm$ 0.1853 $\pm$ 0.0344 \\ 
-  1.423 & 0.172 & 0.099 & 263.1 & -0.3516 $\pm$ 0.1371 $\pm$ 0.0366 \\ 
-  1.423 & 0.172 & 0.099 & 302.2 & -0.4141 $\pm$ 0.0842 $\pm$ 0.0383 \\ 
-  1.423 & 0.172 & 0.099 & 338.2 & -0.2786 $\pm$ 0.0836 $\pm$ 0.0261 \\ 
-  \hline                                                                                                           
-  1.902 & 0.224 & 0.107 & 21.4  &  0.1803 $\pm$ 0.0805 $\pm$ 0.0234 \\ 
-  1.902 & 0.224 & 0.107 & 57.2  &  0.3501 $\pm$ 0.0824 $\pm$ 0.0185 \\ 
-  1.902 & 0.224 & 0.107 & 96.2  &  0.2701 $\pm$ 0.1230 $\pm$ 0.0173 \\ 
-  1.902 & 0.224 & 0.107 & 139.5 &  0.3053 $\pm$ 0.2390 $\pm$ 0.0170 \\ 
-  1.902 & 0.224 & 0.107 & 178.2 &  0.1028 $\pm$ 0.2670 $\pm$ 0.0126 \\ 
-  1.902 & 0.224 & 0.107 & 221.4 & -0.2118 $\pm$ 0.2147 $\pm$ 0.0152 \\ 
-  1.902 & 0.224 & 0.107 & 263.3 & -0.3060 $\pm$ 0.1306 $\pm$ 0.0260 \\ 
-  1.902 & 0.224 & 0.107 & 303.3 & -0.1384 $\pm$ 0.0944 $\pm$ 0.0207 \\ 
-  1.902 & 0.224 & 0.107 & 338.5 & -0.1633 $\pm$ 0.0791 $\pm$ 0.0163 \\ 
-         \hline \hline
+      \begin{tabular}{|c|c|c|c|c|}
+         \hline
+ $\langle Q^{2} \rangle$ & $\langle x_{B} \rangle$ & $\langle -t \rangle$ & $\langle \phi \rangle$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
+ (GeV$^{2}$) &           & (GeV$^{2}$) & (degree) &  \\
+         \hline
+        &       &       & 24    &  0.133  $\pm$ 0.109  $\pm$ 0.026  \\ 
+        &       &       & 61    &  0.321  $\pm$ 0.093  $\pm$ 0.019  \\ 
+        &       &       & 99    &  0.371  $\pm$ 0.103  $\pm$ 0.040  \\ 
+        &       &       & 141   &  0.245  $\pm$ 0.152  $\pm$ 0.027  \\ 
+  1.14  & 0.136 & 0.096 & 178   &  0.023  $\pm$ 0.163  $\pm$ 0.028  \\ 
+        &       &       & 219   & -0.053  $\pm$ 0.148  $\pm$ 0.025  \\ 
+        &       &       & 263   & -0.264  $\pm$ 0.120  $\pm$ 0.039  \\ 
+        &       &       & 302   & -0.176  $\pm$ 0.097  $\pm$ 0.026  \\ 
+        &       &       & 338   & -0.279  $\pm$ 0.105  $\pm$ 0.034  \\ 
+  \hline 
+        &       &       &  21   &  0.192  $\pm$ 0.089  $\pm$ 0.027  \\ 
+        &       &       &  57   &  0.282  $\pm$ 0.087  $\pm$ 0.025  \\ 
+        &       &       &  97   &  0.486  $\pm$ 0.129  $\pm$ 0.043  \\ 
+        &       &       & 140   &  0.100  $\pm$ 0.168  $\pm$ 0.025  \\ 
+  1.42  & 0.172 & 0.099 & 180   &  0.146  $\pm$ 0.191  $\pm$ 0.030  \\ 
+        &       &       & 219   & -0.111  $\pm$ 0.185  $\pm$ 0.034  \\ 
+        &       &       & 263   & -0.352  $\pm$ 0.137  $\pm$ 0.037  \\ 
+        &       &       & 302   & -0.414  $\pm$ 0.084  $\pm$ 0.038  \\ 
+        &       &       & 338   & -0.279  $\pm$ 0.084  $\pm$ 0.026  \\ 
+  \hline 
+        &       &       &  21.4 &  0.180  $\pm$ 0.081  $\pm$ 0.023  \\ 
+        &       &       &  57.2 &  0.350  $\pm$ 0.082  $\pm$ 0.019  \\ 
+        &       &       &  96.2 &  0.270  $\pm$ 0.123  $\pm$ 0.017  \\ 
+        &       &       & 139.5 &  0.305  $\pm$ 0.239  $\pm$ 0.017  \\ 
+  1.90  & 0.224 & 0.107 & 178.2 &  0.103  $\pm$ 0.267  $\pm$ 0.013  \\ 
+        &       &       & 221.4 & -0.212  $\pm$ 0.215  $\pm$ 0.015  \\ 
+        &       &       & 263.3 & -0.306  $\pm$ 0.131  $\pm$ 0.026  \\ 
+        &       &       & 303.3 & -0.138  $\pm$ 0.094  $\pm$ 0.021  \\ 
+        &       &       & 338.5 & -0.163  $\pm$ 0.079  $\pm$ 0.016  \\ 
+         \hline 
       \end{tabular}
@@
    \begin{center}
-      \begin{tabular}{||l|l|l|l|l||}
-         \hline
- $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
-         \hline
-
-  1.164 & 0.132 & 0.095 & 25.6  &  0.0174 $\pm$ 0.1440 $\pm$ 0.0221 \\
-  1.164 & 0.132 & 0.095 & 61.6  &  0.3478 $\pm$ 0.0867 $\pm$ 0.0198 \\
-  1.164 & 0.132 & 0.095 & 99.0  &  0.3808 $\pm$ 0.0948 $\pm$ 0.0408 \\
-  1.164 & 0.132 & 0.095 & 141.7 &  0.2943 $\pm$ 0.1379 $\pm$ 0.0333 \\
-  1.164 & 0.132 & 0.095 & 178.1 &  0.0433 $\pm$ 0.1519 $\pm$ 0.0293 \\
-  1.164 & 0.132 & 0.095 & 218.5 & -0.0352 $\pm$ 0.1316 $\pm$ 0.0243 \\
-  1.164 & 0.132 & 0.095 & 262.7 & -0.2771 $\pm$ 0.1050 $\pm$ 0.0372 \\
-  1.164 & 0.132 & 0.095 & 300.7 & -0.2138 $\pm$ 0.0836 $\pm$ 0.0259 \\
-  1.164 & 0.132 & 0.095 & 335.2 & -0.2339 $\pm$ 0.1221 $\pm$ 0.0319 \\
-   \hline                                                                                                         
-  1.439 & 0.17 & 0.099 &  22.9  &  0.1579 $\pm$ 0.0853 $\pm$ 0.0230 \\
-  1.439 & 0.17 & 0.099 &  57.1  &  0.1733 $\pm$ 0.0880 $\pm$ 0.0195 \\
-  1.439 & 0.17 & 0.099 &  96.3  &  0.2259 $\pm$ 0.1331 $\pm$ 0.0295 \\
-  1.439 & 0.17 & 0.099 &  139.1 &  0.2454 $\pm$ 0.1758 $\pm$ 0.0187 \\
-  1.439 & 0.17 & 0.099 &  180.1 & -0.1021 $\pm$ 0.1918 $\pm$ 0.0197 \\
-  1.439 & 0.17 & 0.099 &  218.9 & -0.2876 $\pm$ 0.1909 $\pm$ 0.0270 \\
-  1.439 & 0.17 & 0.099 &  263.9 & -0.2943 $\pm$ 0.1360 $\pm$ 0.0292 \\
-  1.439 & 0.17 & 0.099 &  302.5 & -0.3979 $\pm$ 0.0921 $\pm$ 0.0331 \\
-  1.439 & 0.17 & 0.099 &  338.1 & -0.2692 $\pm$ 0.0834 $\pm$ 0.0254 \\
-   \hline                                                                                                         
-  1.844 & 0.225 & 0.107 & 20.1  &  0.2626 $\pm$ 0.0755 $\pm$ 0.0248 \\
-  1.844 & 0.225 & 0.107 & 55.9  &  0.4281 $\pm$ 0.0887 $\pm$ 0.0224 \\
-  1.844 & 0.225 & 0.107 & 96.4  &  0.4925 $\pm$ 0.1390 $\pm$ 0.0271 \\
-  1.844 & 0.225 & 0.107 & 137.7 & -0.2736 $\pm$ 0.2804 $\pm$ 0.0166 \\
-  1.844 & 0.225 & 0.107 & 179.8 &  0.8470 $\pm$ 0.2497 $\pm$ 0.0204 \\
-  1.844 & 0.225 & 0.107 & 224.7 & -0.0513 $\pm$ 0.2811 $\pm$ 0.0270 \\
-  1.844 & 0.225 & 0.107 & 262.8 & -0.3416 $\pm$ 0.1694 $\pm$ 0.0353 \\
-  1.844 & 0.225 & 0.107 & 304.5 & -0.1359 $\pm$ 0.1025 $\pm$ 0.0263 \\
-  1.844 & 0.225 & 0.107 & 339.8 & -0.1658 $\pm$ 0.0770 $\pm$ 0.0175 \\
-
-         \hline 
+      \begin{tabular}{|c|c|c|c|c|}
+         \hline
+ $\langle Q^{2} \rangle$ & $\langle x_{B} \rangle$ & $\langle -t \rangle$ & $\langle \phi \rangle$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
+ (GeV$^{2}$) &           & (GeV$^{2}$) & (degree) &  \\
+         \hline
+
+        &       &       &  26   &  0.017  $\pm$ 0.144  $\pm$ 0.022  \\
+        &       &       &  62   &  0.348  $\pm$ 0.087  $\pm$ 0.020  \\
+        &       &       &  99   &  0.381  $\pm$ 0.095  $\pm$ 0.041  \\
+        &       &       & 142   &  0.294  $\pm$ 0.138  $\pm$ 0.033  \\
+  1.16  & 0.132 & 0.095 & 178   &  0.043  $\pm$ 0.152  $\pm$ 0.029  \\
+        &       &       & 219   & -0.035  $\pm$ 0.132  $\pm$ 0.024  \\
+        &       &       & 263   & -0.277  $\pm$ 0.105  $\pm$ 0.037  \\
+        &       &       & 301   & -0.214  $\pm$ 0.084  $\pm$ 0.026  \\
+        &       &       & 335   & -0.234  $\pm$ 0.122  $\pm$ 0.032  \\
+   \hline 
+        &       &       &   23  &  0.158  $\pm$ 0.085  $\pm$ 0.023  \\
+        &       &       &   57  &  0.173  $\pm$ 0.088  $\pm$ 0.020  \\
+        &       &       &   96  &  0.226  $\pm$ 0.133  $\pm$ 0.030  \\
+        &       &       &  139  &  0.245  $\pm$ 0.176  $\pm$ 0.019  \\
+  1.44  & 0.170 & 0.099 &  180  & -0.102  $\pm$ 0.192  $\pm$ 0.020  \\
+        &       &       &  219  & -0.288  $\pm$ 0.191  $\pm$ 0.027  \\
+        &       &       &  264  & -0.294  $\pm$ 0.136  $\pm$ 0.029  \\
+        &       &       &  303  & -0.398  $\pm$ 0.092  $\pm$ 0.033  \\
+        &       &       &  338  & -0.269  $\pm$ 0.083  $\pm$ 0.025  \\
+   \hline 
+        &       &       &  20   &  0.263  $\pm$ 0.076  $\pm$ 0.025  \\
+        &       &       &  56   &  0.428  $\pm$ 0.089  $\pm$ 0.022  \\
+        &       &       &  96   &  0.493  $\pm$ 0.139  $\pm$ 0.027  \\
+        &       &       & 138   & -0.274  $\pm$ 0.280  $\pm$ 0.017  \\
+  1.84  & 0.225 & 0.107 & 180   &  0.847  $\pm$ 0.250  $\pm$ 0.020  \\
+        &       &       & 225   & -0.051  $\pm$ 0.281  $\pm$ 0.027  \\
+        &       &       & 263   & -0.342  $\pm$ 0.169  $\pm$ 0.035  \\
+        &       &       & 305   & -0.136  $\pm$ 0.103  $\pm$ 0.026  \\
+        &       &       & 340   & -0.166  $\pm$ 0.077  $\pm$ 0.018  \\
          \hline
@@
    \begin{center}
-      \begin{tabular}{||l|l|l|l|l||}
-         \hline
- $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
-  \hline
-  1.36 & 0.160 & 0.080  & 22.8  &  0.2378 $\pm$ 0.0928 $\pm$ 0.0263 \\
-  1.36 & 0.160 & 0.080  & 57.6  &  0.3014 $\pm$ 0.0874 $\pm$ 0.0243 \\
-  1.36 & 0.160 & 0.080  & 98.1  &  0.4896 $\pm$ 0.1118 $\pm$ 0.0394 \\
-  1.36 & 0.160 & 0.080  & 139.3 &  0.1965 $\pm$ 0.1595 $\pm$ 0.0252 \\
-  1.36 & 0.160 & 0.080  & 178.8 &  0.0577 $\pm$ 0.1923 $\pm$ 0.0371 \\
-  1.36 & 0.160 & 0.080  & 222.6 & -0.1651 $\pm$ 0.1640 $\pm$ 0.0370 \\
-  1.36 & 0.160 & 0.080  & 265.6 & -0.3467 $\pm$ 0.1339 $\pm$ 0.0403 \\
-  1.36 & 0.160 & 0.080  & 300.0 & -0.2891 $\pm$ 0.0928 $\pm$ 0.0294 \\
-  1.36 & 0.160 & 0.080  & 339.3 & -0.1849 $\pm$ 0.0856 $\pm$ 0.0281 \\
-  \hline                                                                
-  1.507 & 0.179 & 0.094 & 21.1  &  0.2481 $\pm$ 0.0931 $\pm$ 0.0267 \\ 
-  1.507 & 0.179 & 0.094 & 56.4  &  0.3386 $\pm$ 0.0828 $\pm$ 0.0284 \\ 
-  1.507 & 0.179 & 0.094 & 97.5  &  0.3467 $\pm$ 0.1156 $\pm$ 0.0307 \\ 
-  1.507 & 0.179 & 0.094 & 141.9 &  0.1464 $\pm$ 0.1887 $\pm$ 0.0215 \\ 
-  1.507 & 0.179 & 0.094 & 179.5 & -0.2814 $\pm$ 0.1864 $\pm$ 0.0360 \\ 
-  1.507 & 0.179 & 0.094 & 218.5 &  0.2104 $\pm$ 0.1998 $\pm$ 0.0147 \\ 
-  1.507 & 0.179 & 0.094 & 262.8 & -0.2399 $\pm$ 0.1280 $\pm$ 0.0283 \\ 
-  1.507 & 0.179 & 0.094 & 303.5 & -0.1989 $\pm$ 0.0955 $\pm$ 0.0286 \\ 
-  1.507 & 0.179 & 0.094 & 338.5 & -0.2098 $\pm$ 0.0875 $\pm$ 0.0201 \\ 
-  \hline                                                                                                                 
-  1.610 & 0.193 & 0.127 & 22.3  &  0.0280 $\pm$ 0.0909 $\pm$ 0.0214 \\
-  1.610 & 0.193 & 0.127 & 60.7  &  0.3582 $\pm$ 0.0932 $\pm$ 0.0204 \\
-  1.610 & 0.193 & 0.127 & 96.8  &  0.2559 $\pm$ 0.1269 $\pm$ 0.0313 \\
-  1.610 & 0.193 & 0.127 & 139.9 &  0.2207 $\pm$ 0.1930 $\pm$ 0.0203 \\
-  1.610 & 0.193 & 0.127 & 178.5 &  0.5138 $\pm$ 0.1832 $\pm$ 0.0354 \\
-  1.610 & 0.193 & 0.127 & 217.5 & -0.2473 $\pm$ 0.1664 $\pm$ 0.0189 \\
-  1.610 & 0.193 & 0.127 & 260.9 & -0.2919 $\pm$ 0.1295 $\pm$ 0.0327 \\
-  1.610 & 0.193 & 0.127 & 303.4 & -0.2488 $\pm$ 0.0892 $\pm$ 0.0280 \\
-  1.610 & 0.193 & 0.127 & 336.8 & -0.2825 $\pm$ 0.0901 $\pm$ 0.0261 \\
-         \hline
+      \begin{tabular}{|c|c|c|c|c|}
+         \hline
+ $\langle Q^{2} \rangle$ & $\langle x_{B} \rangle$ & $\langle -t \rangle$ & $\langle \phi \rangle$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
+ (GeV$^{2}$) &           & (GeV$^{2}$) & (degree) &  \\
+  \hline
+        &       &       &  23   &  0.238  $\pm$ 0.093  $\pm$ 0.026  \\
+        &       &       &  58   &  0.301  $\pm$ 0.087  $\pm$ 0.024  \\
+        &       &       &  98   &  0.490  $\pm$ 0.112  $\pm$ 0.039  \\
+        &       &       & 139   &  0.197  $\pm$ 0.160  $\pm$ 0.025  \\
+  1.36  & 0.160 & 0.080 & 179   &  0.058  $\pm$ 0.192  $\pm$ 0.037  \\
+        &       &       & 223   & -0.165  $\pm$ 0.164  $\pm$ 0.037  \\
+        &       &       & 266   & -0.347  $\pm$ 0.134  $\pm$ 0.040  \\
+        &       &       & 300   & -0.289  $\pm$ 0.093  $\pm$ 0.029  \\
+        &       &       & 339   & -0.185  $\pm$ 0.086  $\pm$ 0.028  \\
+  \hline 
+        &       &       &  21   &  0.248  $\pm$ 0.093  $\pm$ 0.027  \\ 
+        &       &       &  56   &  0.339  $\pm$ 0.083  $\pm$ 0.028  \\ 
+        &       &       &  98   &  0.347  $\pm$ 0.116  $\pm$ 0.031  \\ 
+        &       &       & 142   &  0.146  $\pm$ 0.189  $\pm$ 0.022  \\ 
+  1.51  & 0.179 & 0.094 & 180   & -0.281  $\pm$ 0.186  $\pm$ 0.036  \\ 
+        &       &       & 219   &  0.210  $\pm$ 0.200  $\pm$ 0.015  \\ 
+        &       &       & 263   & -0.240  $\pm$ 0.128  $\pm$ 0.028  \\ 
+        &       &       & 304   & -0.199  $\pm$ 0.096  $\pm$ 0.029  \\ 
+        &       &       & 339   & -0.210  $\pm$ 0.088  $\pm$ 0.020  \\ 
+  \hline
+        &       &       &  22   &  0.028  $\pm$ 0.091  $\pm$ 0.021  \\
+        &       &       &  61   &  0.358  $\pm$ 0.093  $\pm$ 0.020  \\
+        &       &       &  97   &  0.256  $\pm$ 0.127  $\pm$ 0.031  \\
+        &       &       & 140   &  0.221  $\pm$ 0.193  $\pm$ 0.020  \\
+  1.61  & 0.193 & 0.127 & 179   &  0.514  $\pm$ 0.183  $\pm$ 0.035  \\
+        &       &       & 218   & -0.247  $\pm$ 0.166  $\pm$ 0.019  \\
+        &       &       & 261   & -0.292  $\pm$ 0.130  $\pm$ 0.033  \\
+        &       &       & 303   & -0.249  $\pm$ 0.089  $\pm$ 0.028  \\
+        &       &       & 337   & -0.283  $\pm$ 0.090  $\pm$ 0.026  \\
          \hline
@@
    \begin{center}
-      \begin{tabular}{||l|l|l|l|l||}
-         \hline
- $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
- \hline 
-  1.404 & 0.166 & 0.376  &   21.0 &   0.0541 $\pm$  0.0442  $\pm$ 0.0120 \\
-  1.404 & 0.166 & 0.376  &   62.9 &   0.0771 $\pm$  0.0461  $\pm$ 0.0156 \\
-  1.404 & 0.166 & 0.376  &   95.4 &   0.1913 $\pm$  0.0472  $\pm$ 0.0263 \\
-  1.404 & 0.166 & 0.376  &  140.1 &   0.1076 $\pm$  0.0561  $\pm$ 0.0158 \\
-  1.404 & 0.166 & 0.376  &  182.3 &   0.0448 $\pm$  0.0693  $\pm$ 0.0234 \\
-  1.404 & 0.166 & 0.376  &  220.4 &  -0.0294 $\pm$  0.0675  $\pm$ 0.0150 \\
-  1.404 & 0.166 & 0.376  &  258.4 &  -0.1261 $\pm$  0.0459  $\pm$ 0.0226 \\
-  1.404 & 0.166 & 0.376  &  303.1 &  -0.1238 $\pm$  0.0401  $\pm$ 0.0196 \\
-  1.404 & 0.166 & 0.376  &  337.4 &  -0.0122 $\pm$  0.0537  $\pm$ 0.0142 \\
-  \hline                                                              
-  1.889 & 0.232 & 0.415  &   20.3 &   0.0143 $\pm$  0.0355  $\pm$ 0.0124 \\
-  1.889 & 0.232 & 0.415  &   60.5 &   0.0668 $\pm$  0.0464  $\pm$ 0.0169 \\
-  1.889 & 0.232 & 0.415  &   95.8 &   0.1297 $\pm$  0.0521  $\pm$ 0.0202 \\
-  1.889 & 0.232 & 0.415  &  140.9 &   0.1651 $\pm$  0.0771  $\pm$ 0.0285 \\
-  1.889 & 0.232 & 0.415  &  179.7 &   0.1589 $\pm$  0.0894  $\pm$ 0.0146 \\
-  1.889 & 0.232 & 0.415  &  221.5 &  -0.2594 $\pm$  0.0808  $\pm$ 0.0430 \\
-  1.889 & 0.232 & 0.415  &  260.3 &  -0.1280 $\pm$  0.0559  $\pm$ 0.0180 \\
-  1.889 & 0.232 & 0.415  &  303.5 &  -0.1762 $\pm$  0.0386  $\pm$ 0.0198 \\
-  1.889 & 0.232 & 0.415  &  338.2 &  -0.0303 $\pm$  0.0447  $\pm$ 0.0113 \\
-  \hline                                                              
-  2.339 & 0.288 & 0.497  &  20.8  &  0.0740  $\pm$  0.0330  $\pm$ 0.0135 \\
-  2.339 & 0.288 & 0.497  &  58.2  &  0.1359  $\pm$  0.0458  $\pm$ 0.0101 \\
-  2.339 & 0.288 & 0.497  &  94.7  &  0.1836  $\pm$  0.0567  $\pm$ 0.0176 \\
-  2.339 & 0.288 & 0.497  & 140.9  & -0.0178  $\pm$  0.1008  $\pm$ 0.0161 \\
-  2.339 & 0.288 & 0.497  & 181.8  &  0.0922  $\pm$  0.1329  $\pm$ 0.0236 \\
-  2.339 & 0.288 & 0.497  & 225.0  & -0.0751  $\pm$  0.1066  $\pm$ 0.0212 \\
-  2.339 & 0.288 & 0.497  & 261.0  & -0.2439  $\pm$  0.0596  $\pm$ 0.0241 \\
-  2.339 & 0.288 & 0.497  & 303.0  & -0.1977  $\pm$  0.0384  $\pm$ 0.0153 \\
-  2.339 & 0.288 & 0.497  & 338.7  & -0.0889  $\pm$  0.0397  $\pm$ 0.0145 \\
-  \hline                                                              
-  3.098 & 0.379 & 0.641  & 20.1   & 0.0959   $\pm$  0.0305  $\pm$ 0.0147 \\ 
-  3.098 & 0.379 & 0.641  & 57.1   & 0.0817   $\pm$  0.0478  $\pm$ 0.0147 \\
-  3.098 & 0.379 & 0.641  & 94.2   & 0.1632   $\pm$  0.0684  $\pm$ 0.0281 \\
-  3.098 & 0.379 & 0.641  &137.7   & 0.0930   $\pm$  0.1412  $\pm$ 0.0129 \\
-  3.098 & 0.379 & 0.641  &180.2   &-0.2272   $\pm$  0.1918  $\pm$ 0.0270 \\
-  3.098 & 0.379 & 0.641  &226.0   &-0.0333   $\pm$  0.1599  $\pm$ 0.0273 \\
-  3.098 & 0.379 & 0.641  &263.9   &-0.1630   $\pm$  0.0802  $\pm$ 0.0214 \\
-  3.098 & 0.379 & 0.641  &303.2   &-0.1644   $\pm$  0.0405  $\pm$ 0.0221 \\
-  3.098 & 0.379 & 0.641  &340.5   &-0.0914   $\pm$  0.0368  $\pm$ 0.0141 \\
- \hline
+      \begin{tabular}{|c|c|c|c|c|}
+         \hline
+ $\langle Q^{2} \rangle$ & $\langle x_{B} \rangle$ & $\langle -t \rangle$ & $\langle \phi \rangle$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
+ (GeV$^{2}$) &           & (GeV$^{2}$) & (degree) &  \\
+ \hline 
+        &       &        &   21   &   0.054  $\pm$  0.044   $\pm$ 0.012  \\
+        &       &        &   63   &   0.077  $\pm$  0.046   $\pm$ 0.016  \\
+        &       &        &   95   &   0.191  $\pm$  0.047   $\pm$ 0.026  \\
+        &       &        &  140   &   0.108  $\pm$  0.056   $\pm$ 0.016  \\
+  1.40  & 0.166 & 0.376  &  182   &   0.045  $\pm$  0.069   $\pm$ 0.023  \\
+        &       &        &  220   &  -0.029  $\pm$  0.068   $\pm$ 0.015  \\
+        &       &        &  258   &  -0.126  $\pm$  0.046   $\pm$ 0.023  \\
+        &       &        &  303   &  -0.124  $\pm$  0.040   $\pm$ 0.020  \\
+        &       &        &  337   &  -0.012  $\pm$  0.054   $\pm$ 0.014  \\
+  \hline 
+        &       &        &   20   &   0.014  $\pm$  0.036   $\pm$ 0.012  \\
+        &       &        &   61   &   0.067  $\pm$  0.046   $\pm$ 0.017  \\
+        &       &        &   96   &   0.130  $\pm$  0.052   $\pm$ 0.020  \\
+        &       &        &  141   &   0.165  $\pm$  0.077   $\pm$ 0.029  \\
+  1.89  & 0.232 & 0.415  &  180   &   0.159  $\pm$  0.089   $\pm$ 0.015  \\
+        &       &        &  222   &  -0.259  $\pm$  0.081   $\pm$ 0.043  \\
+        &       &        &  260   &  -0.128  $\pm$  0.056   $\pm$ 0.018  \\
+        &       &        &  304   &  -0.176  $\pm$  0.039   $\pm$ 0.020  \\
+        &       &        &  338   &  -0.030  $\pm$  0.045   $\pm$ 0.011  \\
+  \hline 
+        &       &        &   21   &   0.074  $\pm$  0.033   $\pm$ 0.014  \\
+        &       &        &   58   &   0.136  $\pm$  0.046   $\pm$ 0.010  \\
+        &       &        &   95   &   0.184  $\pm$  0.057   $\pm$ 0.018  \\
+        &       &        &  141   &  -0.018  $\pm$  0.101   $\pm$ 0.016  \\
+  2.34  & 0.288 & 0.497  &  182   &   0.092  $\pm$  0.133   $\pm$ 0.024  \\
+        &       &        &  225   &  -0.075  $\pm$  0.107   $\pm$ 0.021  \\
+        &       &        &  261   &  -0.244  $\pm$  0.060   $\pm$ 0.024  \\
+        &       &        &  303   &  -0.198  $\pm$  0.038   $\pm$ 0.015  \\
+        &       &        &  339   &  -0.089  $\pm$  0.040   $\pm$ 0.015  \\
+  \hline 
+        &       &        &   20   &   0.096  $\pm$  0.030   $\pm$ 0.015  \\ 
+        &       &        &   57   &   0.082  $\pm$  0.048   $\pm$ 0.015  \\
+        &       &        &   94   &   0.163  $\pm$  0.069   $\pm$ 0.028  \\
+        &       &        &  138   &   0.093  $\pm$  0.141   $\pm$ 0.013  \\
+  3.10  & 0.379 & 0.641  &  180   &  -0.227  $\pm$  0.192   $\pm$ 0.027  \\
+        &       &        &  226   &  -0.033  $\pm$  0.160   $\pm$ 0.027  \\
+        &       &        &  264   &  -0.163  $\pm$  0.080   $\pm$ 0.021  \\
+        &       &        &  303   &  -0.164  $\pm$  0.041   $\pm$ 0.022  \\
+        &       &        &  341   &  -0.091  $\pm$  0.037   $\pm$ 0.014  \\
  \hline
@@
    \begin{center}
-      \begin{tabular}{||l|l|l|l|l||}
-         \hline
- $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
-         \hline
- 1.449 & 0.163 & 0.374 &  21.0  &  0.0935 $\pm$ 0.0463  $\pm$  0.0137 \\ 
-  1.449 & 0.163 & 0.374 &  63.4  &  0.0690 $\pm$ 0.0442  $\pm$  0.0165 \\ 
-  1.449 & 0.163 & 0.374 &  95.6  &  0.1469 $\pm$ 0.0439  $\pm$  0.0216 \\ 
-  1.449 & 0.163 & 0.374 & 140.3  &  0.1017 $\pm$ 0.0519  $\pm$  0.0149 \\ 
-  1.449 & 0.163 & 0.374 & 181.3  &  0.0707 $\pm$ 0.0619  $\pm$  0.0235 \\ 
-  1.449 & 0.163 & 0.374 & 220.0  & -0.0446 $\pm$ 0.0616  $\pm$  0.0199 \\ 
-  1.449 & 0.163 & 0.374 & 258.5  & -0.1145 $\pm$ 0.0433  $\pm$  0.0183 \\ 
-  1.449 & 0.163 & 0.374 & 303.0  & -0.0977 $\pm$ 0.0394  $\pm$  0.0154 \\ 
-  1.449 & 0.163 & 0.374 & 336.9  &  0.0329 $\pm$ 0.0565  $\pm$  0.0105 \\ 
-  \hline
-  1.929 & 0.225 & 0.381 &  21.5  &  0.0016 $\pm$ 0.0383  $\pm$  0.0131 \\
-  1.929 & 0.225 & 0.381 &  60.3  &  0.0556 $\pm$ 0.0441  $\pm$  0.0161 \\
-  1.929 & 0.225 & 0.381 &  96.0  &  0.1681 $\pm$ 0.0495  $\pm$  0.0183 \\
-  1.929 & 0.225 & 0.381 & 141.2  &  0.1422 $\pm$ 0.0788  $\pm$  0.0246 \\
-  1.929 & 0.225 & 0.381 & 181.5  &  0.1672 $\pm$ 0.0957  $\pm$  0.0165 \\
-  1.929 & 0.225 & 0.381 & 223.1  & -0.2619 $\pm$ 0.0828  $\pm$  0.0343 \\
-  1.929 & 0.225 & 0.381 & 260.2  & -0.1845 $\pm$ 0.0517  $\pm$  0.0227 \\
-  1.929 & 0.225 & 0.381 & 303.0  & -0.1962 $\pm$ 0.0367  $\pm$  0.0206 \\
-  1.929 & 0.225 & 0.381 & 336.8  & -0.0410 $\pm$ 0.0455  $\pm$  0.0100 \\
-  \hline
-  2.334 & 0.283 & 0.468 &  20.9  &  0.0687 $\pm$ 0.0327  $\pm$  0.0198 \\
-  2.334 & 0.283 & 0.468 &  59.2  &  0.1242 $\pm$ 0.0456  $\pm$  0.0195 \\
-  2.334 & 0.283 & 0.468 &  94.1  &  0.1648 $\pm$ 0.0583  $\pm$  0.0188 \\
-  2.334 & 0.283 & 0.468 & 139.3  &  0.1118 $\pm$ 0.1102  $\pm$  0.0242 \\
-  2.334 & 0.283 & 0.468 & 180.7  & -0.1943 $\pm$ 0.1545  $\pm$  0.0145 \\
-  2.334 & 0.283 & 0.468 & 225.2  &  0.0081 $\pm$ 0.1109  $\pm$  0.0140 \\
-  2.334 & 0.283 & 0.468 & 261.4  & -0.2416 $\pm$ 0.0660  $\pm$  0.0272 \\
-  2.334 & 0.283 & 0.468 & 303.3  & -0.1712 $\pm$ 0.0375  $\pm$  0.0178 \\
-  2.334 & 0.283 & 0.468 & 338.4  & -0.0649 $\pm$ 0.0406  $\pm$  0.0101 \\
-  \hline
-  2.975 & 0.389 & 0.688 &   19.6 &   0.0809$\pm$  0.0289 $\pm$  0.0143 \\
-  2.975 & 0.389 & 0.688 &   55.1 &   0.1214$\pm$  0.0539 $\pm$  0.0148 \\
-  2.975 & 0.389 & 0.688 &   93.4 &   0.2530$\pm$  0.0899 $\pm$  0.0313 \\
-  2.975 & 0.389 & 0.688 &  135.1 &  -0.2304$\pm$  0.2247 $\pm$  0.0386 \\
-  2.975 & 0.389 & 0.688 &  179.9 &  -0.0522$\pm$  0.4248 $\pm$  0.0364 \\
-  2.975 & 0.389 & 0.688 &  230.5 &  -0.3766$\pm$  0.3336 $\pm$  0.0469 \\
-  2.975 & 0.389 & 0.688 &  265.5 &  -0.0929$\pm$  0.1030 $\pm$  0.0202 \\
-  2.975 & 0.389 & 0.688 &  303.4 &  -0.1977$\pm$  0.0453 $\pm$  0.0229 \\
-  2.975 & 0.389 & 0.688 &  341.2 &  -0.1084$\pm$  0.0352 $\pm$  0.0156 \\
- \hline
+      \begin{tabular}{|c|c|c|c|c|}
+         \hline
+ $\langle Q^{2} \rangle$ & $\langle x_{B} \rangle$ & $\langle -t \rangle$ & $\langle \phi \rangle$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
+ (GeV$^{2}$) &           & (GeV$^{2}$) & (degree) &  \\
+         \hline
+        &       &       &  21    &  0.094  $\pm$ 0.046   $\pm$  0.014  \\ 
+        &       &       &  63    &  0.069  $\pm$ 0.044   $\pm$  0.017  \\ 
+        &       &       &  96    &  0.147  $\pm$ 0.044   $\pm$  0.022  \\ 
+        &       &       & 140    &  0.102  $\pm$ 0.052   $\pm$  0.015  \\ 
+  1.45  & 0.163 & 0.374 & 181    &  0.071  $\pm$ 0.062   $\pm$  0.024  \\ 
+        &       &       & 220    & -0.045  $\pm$ 0.062   $\pm$  0.020  \\ 
+        &       &       & 259    & -0.115  $\pm$ 0.043   $\pm$  0.018  \\ 
+        &       &       & 303    & -0.098  $\pm$ 0.039   $\pm$  0.015  \\ 
+        &       &       & 337    &  0.033  $\pm$ 0.057   $\pm$  0.011  \\ 
+  \hline
+        &       &       &  22    &  0.002  $\pm$ 0.038   $\pm$  0.013  \\
+        &       &       &  60    &  0.056  $\pm$ 0.044   $\pm$  0.016  \\
+        &       &       &  96    &  0.168  $\pm$ 0.050   $\pm$  0.018  \\
+        &       &       & 141    &  0.142  $\pm$ 0.079   $\pm$  0.025  \\
+  1.93  & 0.225 & 0.381 & 182    &  0.167  $\pm$ 0.096   $\pm$  0.017  \\
+        &       &       & 223    & -0.262  $\pm$ 0.083   $\pm$  0.034  \\
+        &       &       & 260    & -0.185  $\pm$ 0.052   $\pm$  0.023  \\
+        &       &       & 303    & -0.196  $\pm$ 0.037   $\pm$  0.021  \\
+        &       &       & 337    & -0.041  $\pm$ 0.046   $\pm$  0.010  \\
+  \hline
+        &       &       &  21    &  0.069  $\pm$ 0.033   $\pm$  0.020  \\
+        &       &       &  59    &  0.124  $\pm$ 0.046   $\pm$  0.020  \\
+        &       &       &  94    &  0.165  $\pm$ 0.058   $\pm$  0.019  \\
+        &       &       & 139    &  0.111  $\pm$ 0.110   $\pm$  0.024  \\
+  2.33  & 0.283 & 0.468 & 181    & -0.194  $\pm$ 0.155   $\pm$  0.015  \\
+        &       &       & 225    &  0.008  $\pm$ 0.111   $\pm$  0.014  \\
+        &       &       & 261    & -0.242  $\pm$ 0.066   $\pm$  0.027  \\
+        &       &       & 303    & -0.171  $\pm$ 0.038   $\pm$  0.018  \\
+        &       &       & 338    & -0.065  $\pm$ 0.041   $\pm$  0.010  \\
+  \hline
+        &       &       &  20    &  0.081  $\pm$ 0.029   $\pm$  0.014  \\
+        &       &       &  55    &  0.121  $\pm$ 0.054   $\pm$  0.015  \\
+        &       &       &  93    &  0.253  $\pm$ 0.090   $\pm$  0.031  \\
+        &       &       & 135    & -0.230  $\pm$ 0.225   $\pm$  0.039  \\
+  2.98  & 0.389 & 0.688 & 180    & -0.052  $\pm$ 0.425   $\pm$  0.036  \\
+        &       &       & 231    & -0.377  $\pm$ 0.334   $\pm$  0.047  \\
+        &       &       & 266    & -0.093  $\pm$ 0.103   $\pm$  0.020  \\
+        &       &       & 303    & -0.198  $\pm$ 0.045   $\pm$  0.023  \\
+        &       &       & 341    & -0.108  $\pm$ 0.035   $\pm$  0.016  \\
  \hline
@@
    \begin{center}
-      \begin{tabular}{||l|l|l|l|l||}
-         \hline
- $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
-  \hline
-  1.842 & 0.215 & 0.135  &   21.6  &  0.1197  $\pm$  0.0369 $\pm$ 0.0135 \\ 
-  1.842 & 0.215 & 0.135  &   60.6  &  0.0273  $\pm$  0.0416 $\pm$ 0.0190 \\ 
-  1.842 & 0.215 & 0.135  &   96.3  &  0.2189  $\pm$  0.0409 $\pm$ 0.0179 \\ 
-  1.842 & 0.215 & 0.135  &  141.9  &  0.1502  $\pm$  0.0542 $\pm$ 0.0263 \\ 
-  1.842 & 0.215 & 0.135  &  179.8  &  0.0083  $\pm$  0.0670 $\pm$ 0.0150 \\ 
-  1.842 & 0.215 & 0.135  &  220.7  & -0.1185  $\pm$  0.0653 $\pm$ 0.0182 \\ 
-  1.842 & 0.215 & 0.135  &  259.6  & -0.2041  $\pm$  0.0430 $\pm$ 0.0195 \\ 
-  1.842 & 0.215 & 0.135  &  303.3  & -0.1605  $\pm$  0.0369 $\pm$ 0.0137 \\ 
-  1.842 & 0.215 & 0.135  &  337.5  & -0.0493  $\pm$  0.0469 $\pm$ 0.0100 \\ 
-  \hline
-
-  2.149 & 0.257 & 0.281  &  21.4   & 0.0356   $\pm$ 0.0400  $\pm$ 0.0131 \\
-  2.149 & 0.257 & 0.281  &  60.9   & 0.0927   $\pm$ 0.0454  $\pm$ 0.0125 \\
-  2.149 & 0.257 & 0.281  &  95.7   & 0.1488   $\pm$ 0.0510  $\pm$ 0.0338 \\
-  2.149 & 0.257 & 0.281  & 139.3   & 0.1112   $\pm$ 0.0732  $\pm$ 0.0178 \\
-  2.149 & 0.257 & 0.281  & 183.3   & 0.1052   $\pm$ 0.0933  $\pm$ 0.0298 \\
-  2.149 & 0.257 & 0.281  & 222.8   &-0.0744   $\pm$ 0.0760  $\pm$ 0.0183 \\
-  2.149 & 0.257 & 0.281  & 259.3   &-0.0912   $\pm$ 0.0549  $\pm$ 0.0253 \\
-  2.149 & 0.257 & 0.281  & 302.2   &-0.2004   $\pm$ 0.0390  $\pm$ 0.0248 \\
-  2.149 & 0.257 & 0.281  & 337.8   &-0.1041   $\pm$ 0.0468  $\pm$ 0.0171 \\
-  \hline
-
-  2.366 & 0.291 & 0.492  &   20.8  &  0.1113  $\pm$ 0.0371  $\pm$ 0.0154 \\
-  2.366 & 0.291 & 0.492  &   59.9  &  0.1542  $\pm$ 0.0449  $\pm$ 0.0175 \\
-  2.366 & 0.291 & 0.492  &   94.1  &  0.0957  $\pm$ 0.0598  $\pm$ 0.0147 \\
-  2.366 & 0.291 & 0.492  &  137.7  & -0.1066  $\pm$ 0.1051  $\pm$ 0.0166 \\
-  2.366 & 0.291 & 0.492  &  182.9  &  0.2483  $\pm$ 0.1187  $\pm$ 0.0392 \\
-  2.366 & 0.291 & 0.492  &  223.6  & -0.0691  $\pm$ 0.1101  $\pm$ 0.0125 \\
-  2.366 & 0.291 & 0.492  &  261.1  & -0.1898  $\pm$ 0.0616  $\pm$ 0.0234 \\
-  2.366 & 0.291 & 0.492  &  302.7  & -0.1744  $\pm$ 0.0363  $\pm$ 0.0162 \\
-  2.366 & 0.291 & 0.492  &  337.8  & -0.0666  $\pm$ 0.0466  $\pm$ 0.0178 \\
-  \hline
-
-  2.447 & 0.312 & 1.089  &  19.7   & 0.0317   $\pm$ 0.0304  $\pm$ 0.0178 \\
-  2.447 & 0.312 & 1.089  &  56.7   & 0.0910   $\pm$ 0.0584  $\pm$ 0.0108 \\
-  2.447 & 0.312 & 1.089  &  90.6   & 0.1629   $\pm$ 0.1117  $\pm$ 0.0110 \\
-  2.447 & 0.312 & 1.089  & 131.2   & 0.0424   $\pm$ 0.3072  $\pm$ 0.0177 \\
-  2.447 & 0.312 & 1.089  & 175.3   &-0.9355   $\pm$ 0.3971  $\pm$ 0.0181 \\
-  2.447 & 0.312 & 1.089  & 230.5   &-1.1889   $\pm$ 0.5170  $\pm$ 0.0151 \\
-  2.447 & 0.312 & 1.089  & 264.3   &-0.0721   $\pm$ 0.1091  $\pm$ 0.0171 \\
-  2.447 & 0.312 & 1.089  & 304.8   &-0.1190   $\pm$ 0.0475  $\pm$ 0.0129 \\
-  2.447 & 0.312 & 1.089  & 340.5   &-0.0442   $\pm$ 0.0364  $\pm$ 0.0164 \\
-
- \hline
+      \begin{tabular}{|c|c|c|c|c|}
+         \hline
+ $\langle Q^{2} \rangle$ & $\langle x_{B} \rangle$ & $\langle -t \rangle$ & $\langle \phi \rangle$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
+ (GeV$^{2}$) &           & (GeV$^{2}$) & (degree) &  \\
+  \hline
+        &       &        &   22    &  0.120   $\pm$  0.037  $\pm$ 0.014  \\ 
+        &       &        &   61    &  0.027   $\pm$  0.042  $\pm$ 0.019  \\ 
+        &       &        &   96    &  0.219   $\pm$  0.041  $\pm$ 0.018  \\ 
+        &       &        &  142    &  0.150   $\pm$  0.054  $\pm$ 0.026  \\ 
+  1.84  & 0.215 & 0.135  &  180    &  0.008   $\pm$  0.067  $\pm$ 0.015  \\ 
+        &       &        &  221    & -0.119   $\pm$  0.065  $\pm$ 0.018  \\ 
+        &       &        &  260    & -0.204   $\pm$  0.043  $\pm$ 0.020  \\ 
+        &       &        &  303    & -0.160   $\pm$  0.037  $\pm$ 0.014  \\ 
+        &       &        &  338    & -0.049   $\pm$  0.047  $\pm$ 0.010  \\ 
+  \hline 
+        &       &        &   21    &  0.036   $\pm$  0.040  $\pm$ 0.013  \\
+        &       &        &   61    &  0.093   $\pm$  0.045  $\pm$ 0.013  \\
+        &       &        &   96    &  0.149   $\pm$  0.051  $\pm$ 0.034  \\
+        &       &        &  139    &  0.111   $\pm$  0.073  $\pm$ 0.018  \\
+  2.15  & 0.257 & 0.281  &  183    &  0.105   $\pm$  0.093  $\pm$ 0.030  \\
+        &       &        &  223    & -0.074   $\pm$  0.076  $\pm$ 0.018  \\
+        &       &        &  259    & -0.091   $\pm$  0.055  $\pm$ 0.025  \\
+        &       &        &  302    & -0.200   $\pm$  0.039  $\pm$ 0.025  \\
+        &       &        &  338    & -0.104   $\pm$  0.047  $\pm$ 0.017  \\
+  \hline 
+        &       &        &   21    &  0.111   $\pm$  0.037  $\pm$ 0.015  \\
+        &       &        &   60    &  0.154   $\pm$  0.045  $\pm$ 0.018  \\
+        &       &        &   94    &  0.096   $\pm$  0.060  $\pm$ 0.015  \\
+        &       &        &  138    & -0.107   $\pm$  0.105  $\pm$ 0.017  \\
+  2.37  & 0.291 & 0.492  &  183    &  0.248   $\pm$  0.119  $\pm$ 0.039  \\
+        &       &        &  224    & -0.069   $\pm$  0.110  $\pm$ 0.013  \\
+        &       &        &  261    & -0.190   $\pm$  0.062  $\pm$ 0.023  \\
+        &       &        &  303    & -0.174   $\pm$  0.036  $\pm$ 0.016  \\
+        &       &        &  338    & -0.067   $\pm$  0.047  $\pm$ 0.018  \\
+  \hline 
+        &       &        &   20    &  0.032   $\pm$  0.030  $\pm$ 0.018  \\
+        &       &        &   57    &  0.091   $\pm$  0.058  $\pm$ 0.011  \\
+        &       &        &   91    &  0.163   $\pm$  0.112  $\pm$ 0.011  \\
+        &       &        &  131    &  0.042   $\pm$  0.307  $\pm$ 0.018  \\
+  2.45  & 0.312 & 1.089  &  175    & -0.936   $\pm$  0.397  $\pm$ 0.018  \\
+        &       &        &  231    & -1.189   $\pm$  0.517  $\pm$ 0.015  \\
+        &       &        &  264    & -0.072   $\pm$  0.109  $\pm$ 0.017  \\
+        &       &        &  305    & -0.119   $\pm$  0.048  $\pm$ 0.013  \\
+        &       &        &  341    & -0.044   $\pm$  0.036  $\pm$ 0.016  \\
  \hline
@@
    \begin{center}
-      \begin{tabular}{||l|l|l|l||}
-         \hline
- $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $A_{LU}$(90$^{\circ}$) $\pm$ stat. $\pm$ syst.\\
-  \hline
-  1.143 & 0.136 & 0.096 &  0.3036 $\pm$ 0.0513 $\pm$ 0.0321\\
-  1.423 & 0.172 & 0.099 &  0.3641 $\pm$ 0.0594 $\pm$ 0.0374\\
-  1.902 & 0.224 & 0.107 &  0.2946 $\pm$ 0.0605 $\pm$ 0.0275\\
-  \hline                   
-  1.164 & 0.132 & 0.095 &  0.3196 $\pm$ 0.0446 $\pm$ 0.0376\\
-  1.439 & 0.17  & 0.099 &  0.2780 $\pm$ 0.0788 $\pm$ 0.0269\\
-  1.844 & 0.225 & 0.107 &  0.3196 $\pm$ 0.1612 $\pm$ 0.0366\\
-  \hline                   
-  1.36  & 0.160 & 0.080 &  0.3760 $\pm$ 0.0416 $\pm$ 0.0326\\
-  1.507 & 0.179 & 0.094 &  0.2452 $\pm$ 0.0720 $\pm$ 0.0309\\
-  1.610 & 0.193 & 0.127 &  0.3182 $\pm$ 0.0948 $\pm$ 0.0345\\
+      \begin{tabular}{|c|c|c|c|}
+         \hline
+ $\langle Q^{2} \rangle$ & $\langle x_{B} \rangle$ & $\langle -t \rangle$  & $A_{LU}$(90$^{\circ}$) $\pm$ stat. $\pm$ syst.\\
+ (GeV$^{2}$) &           & (GeV$^{2}$) &  \\
+  \hline
+  1.14  & 0.136 & 0.096 &  0.304  $\pm$ 0.051  $\pm$ 0.032 \\
+  1.42  & 0.172 & 0.099 &  0.364  $\pm$ 0.059  $\pm$ 0.037 \\
+  1.90  & 0.224 & 0.107 &  0.295  $\pm$ 0.061  $\pm$ 0.028 \\
+  \hline 
+  1.16  & 0.132 & 0.095 &  0.320  $\pm$ 0.045  $\pm$ 0.038 \\
+  1.44  & 0.17  & 0.099 &  0.278  $\pm$ 0.079  $\pm$ 0.027 \\
+  1.84  & 0.225 & 0.107 &  0.320  $\pm$ 0.161  $\pm$ 0.037 \\
+  \hline 
+  1.36  & 0.160 & 0.080 &  0.376  $\pm$ 0.042  $\pm$ 0.033 \\
+  1.51  & 0.179 & 0.094 &  0.245  $\pm$ 0.072  $\pm$ 0.031 \\
+  1.61  & 0.193 & 0.127 &  0.318  $\pm$ 0.095  $\pm$ 0.035 \\
   \hline
@@
 \begin{center}
-\begin{tabular}{||l|l|l|l||}
-\hline
- $<Q^{2}>$ & $<x_{B}>$ & $<-t>$  & $A_{LU}$(90$^{\circ}$) $\pm$ stat. $\pm$ syst.\\
- \hline 
-  1.404 & 0.166 & 0.376 & 0.1369 $\pm$ 0.0223 $\pm$ 0.0136\\   
-  1.889 & 0.232 & 0.415 & 0.1529 $\pm$ 0.0266 $\pm$ 0.0169\\   
-  2.339 & 0.288 & 0.497 & 0.1902 $\pm$ 0.0299 $\pm$ 0.0169\\   
-  3.098 & 0.379 & 0.641 & 0.1297 $\pm$ 0.0413 $\pm$ 0.0155\\   
- \hline                   
-  1.449 & 0.163 & 0.374 & 0.1173 $\pm$ 0.0211 $\pm$ 0.0118\\   
-  1.929 & 0.225 & 0.381 & 0.1772 $\pm$ 0.0237 $\pm$ 0.0183\\   
-  2.334 & 0.283 & 0.468 & 0.1777 $\pm$ 0.0308 $\pm$ 0.0153\\   
-  2.975 & 0.389 & 0.688 & 0.1603 $\pm$ 0.0480 $\pm$ 0.0144\\   
- \hline                   
-  1.842 & 0.215 & 0.135 & 0.1828 $\pm$ 0.0205 $\pm$ 0.0143\\   
-  2.149 & 0.257 & 0.281 & 0.1408 $\pm$ 0.0272 $\pm$ 0.0200\\   
-  2.366 & 0.291 & 0.492 & 0.1371 $\pm$ 0.0290 $\pm$ 0.0244\\   
-  2.447 & 0.312 & 1.089 & 0.1389 $\pm$ 0.0618 $\pm$ 0.0239\\
-
- \hline
+\begin{tabular}{|c|c|c|c|}
+\hline
+ $\langle Q^{2} \rangle$ & $\langle x_{B} \rangle$ & $\langle -t \rangle$  & $A_{LU}$(90$^{\circ}$) $\pm$ stat. $\pm$ syst.\\
+ (GeV$^{2}$) &           & (GeV$^{2}$) &  \\
+ \hline 
+  1.40  & 0.166 & 0.376 & 0.137  $\pm$ 0.022  $\pm$ 0.014 \\   
+  1.89  & 0.232 & 0.415 & 0.153  $\pm$ 0.027  $\pm$ 0.017 \\   
+  2.34  & 0.288 & 0.497 & 0.190  $\pm$ 0.030  $\pm$ 0.017 \\   
+  3.10  & 0.379 & 0.641 & 0.130  $\pm$ 0.041  $\pm$ 0.016 \\   
+ \hline 
+  1.45  & 0.163 & 0.374 & 0.117  $\pm$ 0.021  $\pm$ 0.012 \\   
+  1.93  & 0.225 & 0.381 & 0.177  $\pm$ 0.024  $\pm$ 0.018 \\   
+  2.33  & 0.283 & 0.468 & 0.178  $\pm$ 0.031  $\pm$ 0.015 \\   
+  2.98  & 0.389 & 0.688 & 0.160  $\pm$ 0.048  $\pm$ 0.014 \\   
+ \hline 
+  1.84  & 0.215 & 0.135 & 0.183  $\pm$ 0.021  $\pm$ 0.014 \\   
+  2.15  & 0.257 & 0.281 & 0.141  $\pm$ 0.027  $\pm$ 0.020 \\   
+  2.37  & 0.291 & 0.492 & 0.137  $\pm$ 0.029  $\pm$ 0.024 \\   
+  2.45  & 0.312 & 1.089 & 0.139  $\pm$ 0.062  $\pm$ 0.024 \\   
  \hline
@@
 
-% Create the reference section using BibTeX:
-%TODO
-\bibliographystyle{unsrt}
-\bibliography{hadro.bib}
-
 \end{document}

### 2020-10-20 eg6-letters/long-paper/prc-dvcshelium.tex
Small changes

@@
 \caption{General representation for the GPDs of a nucleon represented by the triple lines and noted $N$.
-	Single lines can represent quarks or anti-quarks probed in the nucleon.}
+	Single lines can represent quarks or anti-quarks probed in the nucleon shown by the triple lines.}
 \label{fig:GPD}
@@
 calculation is available to correct for the reminder of these effects yet. Modern calculations exist 
-for such effects in DIS \cite{Cosyn:2017ekf} and quasi-elastic \cite{Ethier:2014bua}
+for such effects in DIS \cite{Cosyn:2017ekf} and quasi-elastic scattering \cite{Ethier:2014bua}
 and we can expect them to be extended to the DVCS 
@@
 
-An important issue with the HERMES measurement and how it is obtained from data has been raised in
+An issue with the HERMES measurement and how it is obtained from data has been raised in
 \cite{Guzey:2003jh} to explain the discrepancy with theoretical expectations.
@@
 are detected at very different energies and with very different detector 
-resolutions, this method would not be optimal. For instance the momentum 
+resolutions, this method would not be sufficient. For instance the momentum 
 of the helium nuclei is negligible in the missing energy observable, thus
@@
 contamination estimated in the DVCS events as a function of the 
-transfered momentum squared -$t$ and integrated over the kinematical 
+transferred momentum squared -$t$ and integrated over the kinematical 
 variables $Q^2$, $x_B$, and $\phi$.}

### 2020-11-24 eg6-letters/long-paper/AdHoc/AnswerAdHoc.tex
Add the 2nd round of AdHoc for long paper

@@
 
-\title{Answer to comments from the Ad-hoc rewiew committee \\
+\title{Answer to comments from the Ad-hoc review committee \\
  Measurement of deeply virtual Compton

### 2020-11-24 eg6-letters/long-paper/AdHoc/AnswerAdHoc_2.tex
Add the 2nd round of AdHoc for long paper

%\documentclass[a4paper,11pt,twoside]{ThesisStyle}
\documentclass[a4paper,11pt,twoside]{article}

\title{Answer to the second round of comments from the Ad-hoc review committee \\
 Measurement of deeply virtual Compton
scattering off Helium-4 with CLAS at Jefferson Lab}

\date{\today}
\include{formatAndDefs}

\begin{document}

\maketitle

\section*{}
Having discussed your second draft and replies to our comments, we are satisfied on all points except 2 and 5.
We'll start with the minor quibble. \\

\textbf{Point 5} \\
You have left the sentence: \textit{"Its historic use to measure DVCS in many different configurations made it an ideal
place for this new DVCS measurement."} Our objection is mostly focused on the word "ideal," which connotes
"perfection." (Also historic is not quite the word you want.) You have explained what you mean to communicate,
and so we urge you to write: \textit{"It was naturally well-suited for measuring DVCS, and several DVCS experiments
were successfully conducted using multiple different configurations."} \\
   \textcolor{blue}{Text has been changed.}

\textbf{Point 2:} \\
Our remaining concern is still on the subtraction of background coming from exclusive $\pi^0$ s with a missing photon.
Your response was helpful in correcting some of our misunderstandings. We think this is a complicated point
because the problem is nested.
\begin{enumerate}
\item There is the BSA in the $\pi^0$ production itself.
\item There is the possibility of an apparent BSA in the $\phi$ distribution that you reconstruct from the single detected
photon, when you are forced to (incorrectly) assume that the process is DVCS.
\item There is the change in BSA that happens as a part of the subtraction of the $\pi^0$ background.
\end{enumerate}
Let us address each.
\begin{enumerate}
\item The use of a $\pi^0$ generator with no BSA is an interesting analysis choice. I don't think it's our committee's job
to critique that choice. It's clear that the MC does a good job of reproducing incoherent exclusive $\pi^0$ data
(your Fig. 15) so the choice is well-motivated. It's interesting that this contrasts with a measured BSA in
exclusive $\pi^0$ production on a proton. You haven't given us enough to understand whether your data could
see 5-10\% BSA. We think it's your choice how deep you want to go when discussing that in the paper. We'd
prefer more discussion, but that's your choice to make. \\
   \textcolor{blue}{The very thorough analysis of F. Cao on the coherent $\pi^0$ channel (with the same data) indicates that no BSA is detectable in the coherent channel. It also shows we could probably resolve a BSA if it was around 10\% or more, but not around 5\%. We can assume these error levels are similar in the incoherent channel even though no detailed analysis exists there. We had some discussions with the group behind this other analysis and they want to make an independent paper, so we do not want to "steal" their figures. However, if the committee feels we should clarify some of the text, we are happy to add some sentences on the topic. But, we would need clearer guidance on what information you would like us to add.}
\item You have pointed out that Figs. 14 and 15 show good agreement between the $\pi^0$ simulation and the measured
$\pi^0$ data. But this doesn't answer our concern about what the distribution of $\pi^0$ single photon events looks
like when binned according to the $\phi$ you would use when you assume the event is DVCS. Your simulation
can answer that question. It seems like that distribution is what really matters when assessing a false BSA
coming from $\pi^0$ s. Are we being naive in asking that? Is guaranteed to be flat for some reason that we don't
understand? \\
   \textcolor{blue}{Previously, we understood your question to be about the generated $\pi^0$, these are flat in $\phi$ and thus, the photons from their decay as well. However, the single photons from $\pi^0$ making it into the DVCS sample are modified by the acceptance of CLAS and follow a different distribution. We do not have a figure for this, but it can be easily reconstructed from the two plots in Fig. \ref{fig}. One can multiply the histogram on the left with the ratio on the right to get the detected single photons from $\pi^0$. As we can see things are almost flat on the right and the distribution will be very similar to the one from fully reconstructed $\pi^0$.}
\item It's not clear what (if any) correction you are making to your reported BSA. You write:
\textit{"to make the correction on the DVCS BSA, . . .} \\
 $[$implying you are making a correction$]$ \\
   \textcolor{blue}{We have to disagree here, we do not imply we make a correction, we are saying it.} \\
\textit{. . . we assume that the exclusive $\pi^0$ production has no such asymmetry. . . .} \\
 $[$fine, but that's not the relevant $\phi$ angle!$]$ \\
   \textcolor{blue}{If there is no BSA in the  $\pi^0$ production, we do not see how changing angle could generate some BSA. Our impression is that this would only be relevant if we used a non-0 BSA.} \\
\textit{. . . This has been checked with the exclusive $\pi^0$ production data for which no significant level of BSA was
measured."} \\
\end{enumerate}
This still leaves questions un-answered for the reader. For the committee to be happy to approve this paper, we
would like:
\begin{itemize}
\item The sentence about the BSA to be made more clear. Are you making a correction for $\pi^0$ contamination? Are
you not making a correction? How big is the correction to the BSA you extract? \\
  \textcolor{blue}{We do not see how this text is ambiguous as to the fact that we apply a correction. The correction is described over about 20 lines, 3 figures and 2 equations. It is unclear to us what could make the reader think that we do not apply the correction described. The size of the correction is given in the figure 16, we are unsure what more you are asking.}
\item Some response (doesn't have to go in the paper) about what the simulated distribution of $\pi^0$ events with a
missing photon looks like, when binned in the $\phi$ that you calculate assuming DVCS. Is it flat? Is there a fake
BSA? Is there some reason why we are naive to think that this is important? We need to know more to assess
whether or not what you have written is clear and accurate. \\
  \textcolor{blue}{The first part of this question is answered above and illustrated with Fig. \ref{fig}. On the second part of the question, we do not see how a fake BSA can be generated from a process without any BSA in the first place. It is very difficult to answer this question as you ask to know more, but you are not saying about what. If you want to know more about the correction, you can read the text in the analysis note on this topic. If that is still unclear we are happy to discuss in a meeting or to answer questions as above that point at specific issues that are unclear.}
\end{itemize}
A $\phi$ distribution of the A LU before and after the correction for the $N_{1\gamma,\pi^0}$ contamination would go a long way
to satisfy everyone on the issue of $\pi^0$ background in the incoherent case.\\
 \textcolor{blue}{ We do not have this figure at hand and it would take a while to produce. However, it can be again more or less estimated thanks to existing figures that this correction has very little $\phi$ dependence as DVCS and $\pi^0$ have similar distributions (illustrated in Fig. \ref{fig}). } \\

 \textcolor{blue}{Some final comments on this question of the $\pi^0$ correction. The bin with the largest $\pi^0$ contamination is 17\%, so assuming a 10\% BSA from free proton data, that would lead to a 1.7\% change on our DVCS BSA result in this bin (much less elsewhere). A few comments on this: (i) this is accounted for in our systematic errors and falls well within our error bars; (ii) both nuclear effects and the fact that we measure only a single photon would reduce the size of the BSA actually getting in our measurement compared to a free proton target, so a 1.7\% effect is even an exaggerated figure; (iii) this change would be reducing the $\pi^0$ correction we apply as it would make the $\pi^0$ events more like the DVCS events; (iv) therefore, such change in the analysis would reduce our final DVCS BSA; (v) our main conclusion on the incoherent is that the incoherent DVCS asymmetries are unexpectedly low already, so the discussed change if implemented would not weaken our conclusions it would reinforce them (by a fraction of $\sigma$). For all these reasons, we do think this correction does not necessitate an in depth reanalysis as we are performing now or a much more detailed description in the paper.}

\begin{figure}[htbp!]
\center
\includegraphics[width=8.2cm]{../../../analysis-note-vf/fig_dvcs/comp/phi_h_InCoh_pi0.png}
\includegraphics[width=8.2cm]{../../../analysis-note-vf/fig_dvcs/epgamma_eppi0_Phi.png}
\caption{Left, the distribution of $\pi^0$ measured (blue) and simulated (red). Right, the ratio of DVCS like single photon events from $\pi^0$ to detectable 2 photons $\pi^0$ events.}
\label{fig}
\end{figure}

\end{document}

### 2021-01-11 eg6-letters/long-paper/prc-dvcshelium.tex
Add the 2nd round of AdHoc for long paper
Changes from last round of ad hoc committee comments

@@
 CLAS \cite{Mecking:2003zu} was installed in the hall-B of the JLab continuous electron beam 
-accelerator facility (CEBAF). CLAS was specifically designed to study the multi-particles final states
-that cannot be observed conveniently with arm spectrometers. Its historic use to measure DVCS in many different 
-configurations made it an ideal place for this new DVCS measurement. CLAS was composed of six identical radial 
+accelerator facility (CEBAF). CLAS was specifically designed to study the multi-particles 
+final states that cannot be observed conveniently with arm spectrometers. It was naturally 
+well-suited for measuring DVCS, and several DVCS experiments were successfully conducted 
+before this experiment using multiple different configurations. CLAS was composed of six identical radial 
 sectors separated by coils of toroidal magnets, with each sector made of four detectors 
@@
 shows 2 to 4\% contamination in the coherent channel and 3 to 17\% in the incoherent
-channel. To make the correction on the DVCS BSA, we assume that
-the exclusive $\pi^0$ production has no such asymmetry. This has been checked with the exclusive 
-$\pi^0$ production data, for which no significant level of BSA was measured.
+channel. After subtracting this contamination, we make no further correction to 
+the DVCS BSA, \textit{i.e}., we assume the exclusive $\pi^0$ production has no such 
+asymmetry in either the coherent or incoherent channels. Our own exclusive $\pi^0$ 
+data rules out any BSA above approximately 10\%, a level which would have an 
+insignificant effect on our results given the small amount of contamination.
 
@@
 \includegraphics[width=8cm]{fig3/T_ratio_pi0_dvcs_InCoh_t.pdf}
-\caption{The coherent (left) and incoherent (right) $\pi^{0}$ 
-contamination estimated in the DVCS events as a function of the 
+\caption{The estimated coherent (left) and incoherent (right) $\pi^{0}$ 
+contamination fraction in the DVCS events as a function of the 
 transferred momentum squared -$t$ and integrated over the kinematical 
@@
 at 90°. The precision with which we know the beam polarization is estimated based on the spread 
-of its measurements during the complete run period. We also checked different methods to make the 
-simulation of the exclusive $\pi^0$ production and accounted for a possible undetected 
-asymmetry in its signal to evaluate the 
-possible bias introduced by this correction. As radiative corrections are expected to be small
+of its measurements during the complete run period. We studied how different methods of
+simulating the exclusive $\pi^0$ production affected the single-photon background and
+further estimated how much bias could arise from an undetected BSA in the process. As 
+radiative corrections are expected to be small
 for this process, we did not apply them, but associated an error of their expected value.

### 2021-01-30 eg6-letters/long-paper/prc-dvcshelium.tex
Add comments from Dan and Sebastian to long P

@@
 \usepackage[left=3.5cm,right=2.5cm,top=2cm,bottom=2cm,includefoot,includehead,headheight=15pt]{geometry}
-\usepackage{lineno}
+%\usepackage{lineno}
 %\documentclass[aps,prc,preprint,superscriptaddress]{revtex4}
@@
 
-\renewenvironment{equation}
-  {\linenomathNonumbers\oldequation}
-  {\oldendequation\endlinenomath}
+%\renewenvironment{equation}
+%  {\linenomathNonumbers\oldequation}
+%  {\oldendequation\endlinenomath}
 
@@
 \maketitle
-\linenumbers
 
 \begin{abstract}
-We report on the measurement of the beam-spin asymmetry in the deeply virtual Compton 
+We report on the measurement of the beam spin asymmetry in the deeply virtual Compton 
 scattering off $^4$He using the CEBAF Large Acceptance Spectrometer (CLAS) at
@@
 theoretically predicted enhancement of the coherent 
-($e^4$He~$\to~e'$$^4$He$'\gamma'$) beam-spin asymmetries compared to those 
+($e^4$He~$\to~e'$$^4$He$'\gamma'$) beam spin asymmetries compared to those 
 observed on the free proton, while the incoherent 
@@
 In the past few decades, the study of the proton structure has made significant progress
-thanks to the theoretical and experimental developments with three dimensional 
+thanks to the theoretical and experimental developments of three dimensional 
 structure functions \cite{Anselmino:2015uka}. These studies, which have focused on generalized
-parton distributions (GPD) and transverse momentum dependent parton distribution functions (TMD)
+parton distributions (GPDs) and transverse momentum dependent parton distribution functions (TMDs)
 can be generalized to the nucleus and offer a unique opportunity to revisit the quark structure 
@@
 controversies. Indeed, while much progress has been made in measuring the nuclear
-parton distribution functions, their shape remains fundamentally 
-unexplained \cite{Norton:2003cb,Malace:2014uea,Hen:2016kwk}.
+parton distribution functions, their shape can be explained with very different model 
+assumptions~\cite{Norton:2003cb,Malace:2014uea,Hen:2016kwk}.
 
@@
 process~\cite{Diehl:2003ny,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}. The measurement of the exclusive
-production of a photon limits the possibilities of final state interactions in the nuclear 
-medium and offers a unique opportunity to make a measurement free of final state interactions 
-(FSI). Moreover, with a spin-0 nuclear target, the extraction of the GPD from the DVCS data 
-is significantly simplified since a single GPD is occurring in the process at leading order. However, the 
+production of a photon limits the possibilities of final state interactions (FSIs) in the nuclear 
+medium and offers a unique opportunity to make a measurement free of them. 
+Moreover, with a spin-0 nuclear target, the extraction of the GPD from the DVCS data 
+is significantly simplified since a single GPD is involved in the process at leading order. However, the 
 measurement of the nuclear DVCS is challenging experimentally and the first attempts by 
-the HERMES collaboration \cite{Airapetian:2009cga} led to controversial conclusions. We present here
-in detail the more recent measurements by the CLAS collaboration, which has been already partially presented
+the HERMES Collaboration \cite{Airapetian:2009cga} led to controversial conclusions. We present here
+in detail the more recent measurements by the CLAS Collaboration, which has been already partially presented
 in two short letters \cite{Hattawy:2017woc,Hattawy:2018liu}. We extend in this article 
@@
 
-The theory of GPDs has been already reviewed in details in various 
+The theory of GPDs has been already reviewed in detail in various 
 publications~\cite{Diehl:2003ny,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya},
-we summarized here only necessary elements to discuss the present experimental results.
-The GPDs are real structure functions $F^{q}(x,\xi,t)$, where $x+\xi$ and $x-\xi$ are incoming and outgoing quark momenta 
-respectively and $t=\Delta^2$ the squared transferred momentum to the target in this exchange of quarks as illustrated in 
-Fig. \ref{fig:GPD}.
+and we summarize here only the necessary elements to discuss the present 
+experimental results. The GPDs are real structure functions $F^{q}(x,\xi,t)$, 
+where $x+\xi$ and $x-\xi$ are the incoming and outgoing quark momenta respectively 
+and $t=\Delta^2$ is the squared transferred four momentum to the target, as 
+illustrated in Fig.~\ref{fig:GPD}.
 
@@
 regard to the symmetries of the system. At leading order and leading twist, we 
-find that there are $2(2J+1)^2$ GPDs for a particle of spin $J$, 
-$i.e.$ for a spin-0 hadron, like the helium-4 nucleus, we will have two GPDs, 
-for a spin-1/2 hadron, like the proton, eight GPDs. Half of these involve a 
-parton helicity flip, they are called transversity GPDs and do not intervene 
-in the DVCS process.
+find that there are $2(2J+1)^2$ GPDs for a particle of spin $J$. 
+Therefore for a spin-0 hadron like the helium-4 nucleus, we will have two GPDs, and 
+for a spin-1/2 hadron like the proton, eight GPDs. Half of these involve a 
+parton helicity flip, they are called transversity GPDs and do not contribute to 
+the DVCS process.
 
 DVCS is the main experimental probe of the GPDs. However, this process does not allow
-for an extraction of the GPDs in the full phase space of parameters. Instead, DVCS gives access
-to the GPDs integrated over $x$. 
-To account for this and simplify equations, we define the complex Compton form factors (CFF,
+for an extraction of the GPDs in the full phase space of the parameters. Instead, 
+DVCS gives access to the GPDs integrated over $x$. 
+To account for this and simplify the notation, we define the complex Compton form factors (CFF,
 noted with curved $\mathcal{F}$ for a given GPD $F$) for each GPD as follows:
@@
 \end{equation}
-The interference terms increase significantly the cross section in specific parts of the phase space
-and lead to significant beam spin asymmetries (BSA), which are the focus of the measurements presented 
+The interference terms significantly increase the cross section in specific parts of the phase space
+and lead to significant beam spin asymmetries (BSAs), which are the focus of the measurements presented 
 here.
@@
 $x_B = {Q^2 \over 2 M_N \nu}\sim {2\xi \over 1+\xi}$, with $M_N$ the nucleon mass and $\nu$ the
-energy transfer to the target $\nu = {E -E^\prime} $.
+energy transfer to the target, $\nu = {E -E^\prime} $.
 
@@
 
-\subsection{Coherent nuclear DVCS}
+\subsection{Coherent Nuclear DVCS}
 
 The first reaction measured in the experiment is the coherent electro-production of a photon on helium
-$e+^4\!\!He \rightarrow e+\gamma+^4\!\!He$ at large 4-momentum transfer squared ($Q^2$). The 
+$e+^4\!\!He \rightarrow e^\prime+\gamma+^4\!\!He^\prime$ at large 4-momentum transfer squared ($Q^2$). The 
 leading order diagram of the nuclear coherent DVCS is represented in Fig. \ref{fig:CohDiag}.
-In the present experiment, we focused on the measurement of the beam-spin asymmetry (BSA) 
+In the present experiment, we focused on the measurement of the BSA 
 noted $A_{LU}$ with 
-$L$ for the longitudinally-polarized electron beam and $U$ the unpolarized target and is defined as:  
+$L$ for the longitudinally polarized electron beam and $U$ the unpolarized target, which is defined as:  
 \begin{equation}
@@
 & & \frac{x_A^2 t {(1+\epsilon^2)}^2}{Q^2} P_1(\phi) P_2(\phi) \, c_0^{DVCS} + 
-\frac{x_A (1+\epsilon^2)^2}{y} \sum_{n=0}^{n=1} c_n^{INT} \cos{(n\phi)} \bigg].  \nonumber 
+\frac{x_A (1+\epsilon^2)^2}{y} \sum_{n=0}^{n=1} c_n^{INT} \cos{(n\phi)} \bigg],  \nonumber 
 \end{eqnarray}
-where $\mathcal{P}_1(\phi)$ and $\mathcal {P}_2(\phi)$ are the BH 
-propagators. The factors: $c_{0,1,2}^{BH}$, $c_0^{DVCS}$, $c_{0,1}^{INT}$ and 
+where $\mathcal{P}_1(\phi)$ and $\mathcal {P}_2(\phi)$ are the BH propagators, 
+and $x_{A} = \frac{M_{p}\cdot x}{M_{^4\!He}}$. The factors: $c_{0,1,2}^{BH}$, 
+$c_0^{DVCS}$, $c_{0,1}^{INT}$ and 
 $s_1^{INT}$ are the Fourier coefficients of the BH, the DVCS and the 
-interference amplitudes for a spin-zero target. The explicit 
+interference amplitudes for a spin-zero target, respectively. The explicit 
 expressions of these coefficients, which have been derived based on the work of 
@@
 \includegraphics[width=9cm]{fig3/DVCS_diagram.pdf}
-\caption{Diagram representing the coherent nuclear DVCS.}
+\caption{Diagram representing the coherent nuclear DVCS, where we 
+indicate the limit between the hard and the soft components with the dot-dashed factorization line.}
 \label{fig:CohDiag}
@@
 \big( 
-\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}
+\Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)},
 \label{eq:A_LU-coh}
@@
 where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
-and real parts of the CFF $\mathcal{H}_{A}$ associated with the GPD $H_A$ of the 
-spin-0 nucleus. The 
+and real parts,respectively, of the CFF $\mathcal{H}_{A}$ associated with 
+the GPD $H_A$ of the spin-0 nucleus. The 
 $\alpha_{i}$ factors are $\phi$-dependent kinematical terms that depend on the 
@@
    \alpha_2 (\phi) & = & \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
-C_{++}(1) cos(\phi) \right)\\
+C_{++}(1) \cos(\phi) \right)\\
 \alpha_3 (\phi) &=& \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
@@
 \end{eqnarray}
-where $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics in the 
-leptonic tensor \cite{Belitsky:2008bz}, their explicit expression can be found in 
-Appendix \ref{sec:eq}, and $x_{A} = \frac{M_{p}\cdot x}{M_{^4\!He}}$.
-
-The Eq. \ref{eq:A_LU-coh} is particularly convenient to perform an extraction of 
-the $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ through a fit of the BSA as 
+where $S_{++}(1)$, $C_{++}(0)$, and $C_{++}(1)$ are the Fourier harmonics found in the 
+leptonic tensor \cite{Belitsky:2008bz}. Their explicit expression are provided in 
+Appendix \ref{sec:eq}.
+
+Eq. \ref{eq:A_LU-coh} is particularly convenient to perform an extraction of 
+$\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ through a fit of the BSA as 
 a function of $\phi$. As can be seen in Fig. \ref{fig:alphas}, the form of each 
@@
 \includegraphics[width=8cm]{fig3/AlphaCoefs.png}
-	\caption{Coefficients presented in Eq. \ref{eq:alpha1} to \ref{eq:alpha4}.
+	\caption{Coefficients presented in Eqs. \ref{eq:alpha1} to \ref{eq:alpha4}.
 	Note the prescaling factors used for $\alpha_0$, $\alpha_2$ and $\alpha_3$.}
@@
 An important issue with the use of this theoretical framework is the large mass of the 
-helium nucleus. Recent work indicate that the effect of this correction is moderate 
+helium nucleus. Recent work indicates that the effect of this correction is moderate 
 \cite{Braun:2012bg}, however the applicability to such a large mass remains to be
@@
 
-\subsection{Incoherent nuclear DVCS}
+\subsection{Incoherent Nuclear DVCS}
 
@@
 already reviewed widely in the literature~\cite{Diehl:2003ny,Belitsky:2005qn,Guidal:2013rya}. 
-Two important differences need to be accounted for however, the different initial state and the addition of 
-final state effects. In the initial state, the intrinsic Fermi motion of the nucleons in the nucleus 
-lead to an uncertainty on the exact kinematic of the reaction. Moreover, in general the nucleon 
+Two important differences need to be accounted for however: the different initial state and the addition of 
+FSIs. In the initial state, the intrinsic Fermi motion of the nucleons in the nucleus 
+leads to an uncertainty on the exact kinematics of the reaction. Moreover, in general, the nucleon 
 is in an off-shell state that is not exactly identical to its final state. In the final state, 
-interactions between the outgoing nucleon from the DVCS reaction and remnants of the nuclear 
-target are possible. The latter leading to contamination from other channels, in particular 
-charge exchange processes can lead to a large contribution from such background reaction.
+interactions between the outgoing nucleon from the DVCS reaction and the remnants of the nuclear 
+target are possible. The latter leads to contamination from other channels; in particular, 
+charge exchange processes can lead to a large contribution from such background reactions.
 
@@
 
-Since, DVCS is a 
-process selected using tight exclusivity constrains, some of the initial and final-state effects are
+Since DVCS is a 
+process selected using tight exclusivity constraints, some of the initial and final-state effects are
 automatically mitigated. Selection criterion on missing energy and momentum are performed,
-constraining the range of initial Fermi motion and final interactions possible. However, no theoretical
+constraining the range of initial Fermi motion and FSIs possible. However, no theoretical
 calculation is available to correct for the reminder of these effects yet. Modern calculations exist 
-for such effects in DIS \cite{Cosyn:2017ekf} and quasi-elastic scattering \cite{Ethier:2014bua}
-and we can expect them to be extended to the DVCS 
-process as more data becomes available. Another avenue of progress
+for such effects in deep inelastic scattering \cite{Cosyn:2017ekf} and quasi-elastic 
+scattering \cite{Ethier:2014bua}, and we can expect them to be extended to the DVCS 
+process as more data become available. Another avenue of progress
 on this topic will be the use of experimental techniques like tagging. This process
 can help to control both initial and final state effects by detecting the nuclear remnant.
-In the tagged process the target breaks in two providing directly the initial state
-of the struck nucleon, while measured backward nuclear fragments limit significantly the
-impact of final state effects.
-
-\section{Past nuclear DVCS measurements}
-
-The first measurement of nuclear DVCS has been performed by the HERMES 
-collaboration~\cite{Airapetian:2009cga}. This experiment covered an array of 
+In the tagged process the target breaks in two, thus measuring the nuclear remnant provides 
+information about the initial state of the struck nucleon, while a backward fragment also 
+limits significantly the probability of FSIs.
+
+\section{Past Nuclear DVCS Measurements}
+
+The first measurement of nuclear DVCS was performed by the HERMES 
+Collaboration~\cite{Airapetian:2009cga}. This experiment covered an array of 
 nuclear targets and looked at the $A$ dependence of the
-BSA signal. Their main results, reproduced in Fig. \ref{fig:HERMES1} and \ref{fig:HERMES2}, suffer
+BSA signal. Their main results, reproduced in Figs. \ref{fig:HERMES1} and \ref{fig:HERMES2}, suffer
 from large uncertainties, which makes them consistent with the free proton data and prevents us to
@@
 	\includegraphics[width=10.5cm]{fig3/HERMES_BSA.png}
-	\caption{The sinus moment of the BSA as a function of $-t$ measured by HERMES
-	for a series of nuclei \cite{Airapetian:2009cga}, gray bands represent the systematic 
+	\caption{The $\sin(\phi)$ moment of the BSA as a function of $-t$ measured by HERMES
+	for a series of nuclei \cite{Airapetian:2009cga}. The gray bands represent the systematic 
         uncertainties.}
@@
 \includegraphics[width=10cm]{fig3/HERMES_BSA_2.png}
-\caption{The sinus moment of the BSA at low and high $-t$ as a function of $A$ measured by HERMES
+\caption{The $\sin(\phi)$ moment of the BSA at low and high $-t$ as a function of $A$ measured by HERMES
 	\cite{Airapetian:2009cga}. The inner error bars represent the statistical uncertainty, while 
@@
 An issue with the HERMES measurement and how it is obtained from data has been raised in
-\cite{Guzey:2003jh} to explain the discrepancy with theoretical expectations.
+Ref. \cite{Guzey:2003jh} to explain the discrepancy with theoretical expectations.
 The main concern is that the DVCS process is not fully detected and the scattered target
@@
 incoherent channels have strongly impaired the interpretation of the measurement 
-and the conclusions that could be
+and the conclusions that can be
 obtained from it. The CLAS experiment presented here has profited largely from this
@@
 
-\section{The CLAS nuclear DVCS experimental setup}
-
-The CLAS nuclear DVCS experiment had for main objectives to explore the coherent DVCS on helium-4, to assess if
+\section{The CLAS Nuclear DVCS Experimental Setup}
+
+The CLAS nuclear DVCS experiment had as its main objectives to explore coherent DVCS on helium-4, to assess if
 the predicted BSA increase could be observed, and to extract the helium-4 GPD. In order to
 perform this measurement however, several instrumentation challenges needed to be resolved. First, to
-measure the scattered electron and the small angle photon of the DVCS, we used CLAS in its 
+measure the scattered electron and the small angle photon from DVCS, we used CLAS in its 
 DVCS setup, $i.e.$ with the addition of a forward angle calorimeter and a 5-T solenoid magnet. Second, a
@@
 
-CLAS \cite{Mecking:2003zu} was installed in the hall-B of the JLab continuous electron beam 
-accelerator facility (CEBAF). CLAS was specifically designed to study the multi-particles 
-final states that cannot be observed conveniently with arm spectrometers. It was naturally 
+The CLAS \cite{Mecking:2003zu} spectrometer was installed in Hall~B of Jefferson Lab (JLab) continuous electron beam 
+accelerator facility (CEBAF). This detector was specifically designed to study the multi-particles 
+final states that cannot be observed conveniently with multi-arm spectrometers. It was naturally 
 well-suited for measuring DVCS, and several DVCS experiments were successfully conducted 
-before this experiment using multiple different configurations. CLAS was composed of six identical radial 
-sectors separated by coils of toroidal magnets, with each sector made of four detectors 
+before this experiment using multiple different configurations. CLAS was composed of six identical 
+sectors separated by the coils of a toroidal magnet, with each sector made of four detectors 
 as shown in Fig. \ref{fig:CLAS}. Three regions of drift chambers \cite{Mestayer:2000we} 
@@
 calculate their momentum. An array of scintillators was placed behind the drift chambers to measure 
-a precise time for each track and perform time-of-flight measurement 
+the precise time-of-flight for each track
 \cite{Smith:1999ii}. These detectors covered the polar angle from 8 to 142 degrees. 
-In the forward region, from 8 to 45 degree, these two detectors were complemented with 
+In the forward region, from 8 to 45 degrees, these detectors were complemented with 
 Cerenkov counters \cite{Adams:2001kk} and electromagnetic calorimeters \cite{Amarian:2001zs},
@@
 Altogether, CLAS provided a large acceptance for momenta 
-starting at 200 MeV/c. The nuclear DVCS experiment took place from October to December 2009,
-the beam energy was 6.064 GeV, while the beam intensity varied
-between 120 and 150 nA. Such beam on the helium-4 target pressurized between 5 and 6 atm,
-corresponds to luminosities in the range of $1$ to $1.2 \times 10^{34}$ cm$^{-2}$.s$^{-1}$.
+starting at 200 MeV. The nuclear DVCS experiment took place from October to December 2009
+at an electron beam energy of 6.064 GeV, with the beam intensity varying
+between 120 and 150 nA. This beam, on the helium-4 target pressurized between 5 and 6 atm,
+corresponds to luminosities in the range of $1$ to $1.2 \times 10^{34}$ cm$^{-2}$s$^{-1}$.
 During the experiment, the data acquisition operated at a rate of about 3 kHz with about 70\% live-time
@@
 
-The CLAS collaboration has established a specific setup to measure the typically 
+The CLAS Collaboration has established a specific setup to measure the typically 
 small angle photons of the DVCS process. This setup is composed of an inner 
@@
 
-The inner calorimeter, illustrated in Fig. \ref{fig:IC} is a homogeneous 
-calorimeter composed 424 lead tungstate 
+The inner calorimeter, illustrated in Fig. \ref{fig:IC}, is a homogeneous 
+calorimeter composed of 424 lead tungstate 
 (PbWO) crystals read out by $5 \times 5$ mm$^2$ avalanche photo-diodes (APDs). 
@@
 particularly sensitive to the low energy Moller electrons scattered from the target.
-To protect the calorimeter from this background, a 5~T solenoid is 
+To protect the calorimeter from this background, a 5~T solenoid was 
 placed around the target to form
 a magnetic shield. Thanks to this field, low energy charged particles (particularly 
-electrons) curl around the beam line 
-and never make it to the calorimeter or other CLAS detectors as illustrated 
-by simulation results presented 
+electrons) curled around the beamline 
+and never made it to the calorimeter or other CLAS detectors as illustrated 
+by the simulation results presented 
 in Fig. \ref{fig:Solenoid}. This allows to run much higher luminosity experiments,
-a necessity for low rates processes like DVCS.
+a necessity for low rate processes like DVCS.
 
@@
 
-\subsection{The Radial time projection chamber}
+\subsection{The Radial Time Projection Chamber}
 
 The recoil helium nuclei from coherent DVCS are mostly emitted between 150 
-and 200 MeV/c at the beam energy of 6~GeV. Therefore, a specific detector was 
-needed to detect them. To design the present setup, large inspiration was drawn from the 
-Bonus setup that also used a GEM based RTPC~\cite{Fenker:2008zz} in CLAS to 
-detect slow protons out of a deuterium target~\cite{Baillie:2011za}. In such an RTPC the 
-charges are projected toward large radii 
-rather than towards the endcaps, as is more traditional in time 
+and 200 MeV at the beam energy of 6~GeV. Therefore, a specific detector was 
+needed to detect them. To design the present setup, inspiration was drawn from the 
+BONUS setup that also used a GEM-based RTPC~\cite{Fenker:2008zz} in CLAS to 
+detect slow protons coming out of a deuterium target~\cite{Baillie:2011za}. In such an RTPC the 
+ionization electrons drift toward large radii 
+rather than toward the endcaps, as is more traditional in time 
 projection chambers. This design allows to reduce significantly the drift time and reduce the 
@@
 the track reconstruction have been described in more 
-details elsewhere~\cite{Dupre:2017upj}, here is a summary of key elements.
+details elsewhere~\cite{Dupre:2017upj}. Here a summary of key elements is provided.
 
@@
 pressure. The entrance and exit windows are thin aluminum foils and an helium 
-bag is placed downstream of the target to avoid interaction with air in the gap 
+bag was placed downstream of the target to avoid interaction with air in the gap 
 between the target and the beamline vacuum. The cylindrical 
-chamber surrounds the target as illustrated in Fig.~\ref{fig:RTPCGlobal}, we 
+chamber surrounds the target as illustrated in Fig.~\ref{fig:RTPCGlobal}. Here we 
 list the elements composing it based on their radii:
@@
 	\item At 20 mm a grounded foil made of 4 $\mu$m aluminized Mylar to 
-		isolate the chamber from the beam line 
-		region and collect charges. It also serves to separate gas regions.
-	\item From 20 to 30 mm a dead zone to separate the ground from the cathode
-		filled with the drift gas, a mix of neon and dimethyl ether (DME) in 
-		80/20 proportions.
+		isolate the chamber from the beamline 
+		region and collect charges. It also serves to separate the gas regions.
+	\item From 20 to 30 mm a dead zone
+		filled with the drift gas to separate the ground from the cathode.
 	\item At 30 mm the cathode foil made of 4 $\mu$m aluminized Mylar.
-	\item From 30 to 60 mm the drift region filled with the drift gas.
+	\item From 30 to 60 mm the drift region filled with the drift gas, a mix of 
+                neon and dimethyl ether (DME) in an 80/20 proportion.
 	\item From 60 to 69 mm the amplification regions, filled with drift gas, 
@@
 
-The calibration of the detector has been performed with a 
-dependence on $z$, the position along the beam line axis, due to 
+The time-to-position calibration of the detector has been performed with a 
+dependence on $z$, the position along the beamline axis, due to 
 variations in the magnetic fields. To perform this calibration we took  
 dedicated data at 1.2 GeV beam energy. In 
-this data set, we were able to select elastic events, for which the kinematic 
-of the helium recoil can be calculated from the electron kinematic and 
+this data set, we were able to select elastic events, for which the kinematics
+of the helium recoil can be calculated from the electron kinematics and 
 directly compared to the measurement in the RTPC. This comparison helped to 
@@
 the drift path of electrons. A more detailed description of the calibration process 
-is available in~\cite{Dupre:2017upj}.
-
-\section{DVCS event selection}
-
-\subsection{Particle identification}
-
-The electrons are detected with the baseline CLAS detectors, the drift chamber measures the kinematic 
+is available in Ref.~\cite{Dupre:2017upj}.
+
+\section{DVCS Event Selection}
+
+\subsection{Particle Identification}
+
+The scattered electrons were detected with the baseline CLAS detectors. The drift chamber measured the kinematics
 of the electron and the signal measured in both the Cerenkov counter and electromagnetic calorimeter
-provide the identification. A signal of good quality is also required in the 
-time-of-flight system, which serves as a time reference for all detectors. 
-Protons are detected with the baseline CLAS detectors as well, the drift chamber measures the kinematic 
-of the proton and the time-of-flight system ensure its identification.
-Several 
+provided the identification. A signal of good quality was also required in the 
+time-of-flight system, which served as a time reference for all detectors. 
+Protons were detected with the baseline CLAS detectors as well, the drift chamber measured the kinematics
+of the proton and the time-of-flight system ensured its identification. Several 
 fiducial cuts are applied to ensure that particles did not go through part of the inner calorimeter 
-or the solenoid, as well as to reject the edges of the detectors, where efficiency is rapidly 
+or the solenoid, as well as to reject the edges of the detectors, where their efficiency is rapidly 
 decreasing. Kinematic corrections are also applied to the electrons and protons to correct for energy loss
-and biases in calibration, they are at subpercent level except for protons below 500 MeV/c for which they
-go up to 10\% at the detection limit of 200 MeV/c.
+and biases in calibration, which are at the subpercent level except for protons below 500 MeV for which they
+go up to 10\% at the detection limit of 200 MeV.
 
 The photons from DVCS are mainly detected with the inner calorimeter. No specific 
-identification cuts are used in this detector as large energy deposit are dominantly 
-from electrons and photons, which cannot be separated reliably. However, the detection 
-of an electron at larger angle in CLAS highly suppresses the number of electrons 
-in the calorimeter, moreover the exclusivity cuts used later in the analysis further 
-this suppression. Left over accidentals are accounted for in the background subtraction 
+identification cuts were used in this detector as large energy deposit was dominantly 
+from electrons and photons, which could not be separated reliably. However, the detection 
+of an electron at large angle in CLAS highly suppressed the number of electrons 
+in the calorimeter; moreover, the exclusivity cuts used later in the analysis further 
+this suppression. Left-over accidentals were accounted for in the background subtraction 
 described below. The inner calorimeter was calibrated through a series of steps, 
@@
 
-The helium-4 nuclei are detected with the RTPC using a series of constraints on the quality
+The helium-4 nuclei were detected with the RTPC using a series of constraints on the quality
 of the track reconstruction. As the chamber was operated at low gain and had very low efficiency 
@@
 
-Finally, we select events that contain a single electron, a high energy photon ($E>2$ GeV) and
-either a helium or a proton. We apply a selection cut on the two charged particles 
-to ensure they originate from the same vertex inside the target, thus rejecting accidentals and
+Finally, we selected events that contain a single electron, a high energy photon ($E>2$ GeV) and
+either a helium or a proton. We applied a selection cut on the two charged particles 
+to ensure they originated from the same vertex inside the target, thus rejecting accidentals and
 events from the target windows.
-Moreover, since we are aiming to study deep processes occurring at the partonic level, we select
-$Q^2>1$ GeV$^2$. Also, the transferred momentum squared to the recoil $^{4}He$ is bound by
-   a minimum value based on basic energy momentum conservation:
+Moreover, since we are aiming to study deep processes occurring at the partonic level, we selected
+$Q^2>1$~GeV$^2$. Also, the transferred momentum squared to the recoil $^{4}He$ was bound by
+   a minimum value based on basic energy-momentum conservation:
 \begin{equation}
@@
 where $\epsilon ^{2} = \frac{4M^{2}_{^4\!He}x^{2}_{A}}{Q^{2}}$. For incoherent DVCS, 
-we use a similar cut where $x_A$ is replaced by $x$ and $M_{^4\!He}$ by $M_{p}$.
-
-\subsection{Exclusive photo-production selection}
+we used a similar cut where $x_A$ is replaced by $x$ and $M_{^4\!He}$ by $M_{p}$.
+
+\subsection{Exclusive Photo-Production Selection}
 
@@
 exclusivity of the process. However, in our experiment, where particles 
-are detected at very different energies and with very different detector 
-resolutions, this method would not be sufficient. For instance the momentum 
+were detected at very different energies and with very different detector 
+resolutions, this method was not sufficient. For instance the momentum 
 of the helium nuclei is negligible in the missing energy observable, thus
 this valuable information has no impact on a selection using this observable only.
-To circumvent this issue, we constrain the selection of our exclusive events by using seven 
+To address this issue, we constrained the selection of our exclusive events by using seven 
 variables selected to optimize the use of all the detector information available. 
-The seven variables are defined as follow for the coherent 
-DVCS (replace helium by proton for the incoherent case):
+The seven variables are defined as follows for coherent 
+DVCS case (replace helium by proton for the incoherent case):
 \begin{itemize}
 	\item Co-planarity ($\Delta \phi$) of the virtual photon, the real photon and
-		the recoil helium, defined as the angle between the helium, virtual photon
-		plane and the virtual photon, real photon plane;
-	\item Missing energy of the full system;
-	\item Missing mass of the full system;
-	\item Missing transverse momentum of the full system;
+		the recoil helium;
+	\item Missing energy of the complete final state;
+	\item Missing mass of the complete final state;
+	\item Missing transverse momentum of the complete final state;
 	\item Missing mass of the electron-helium system;
@@
 
-In the analysis, we apply selection cuts based on a fit of the exclusive peak at 3$\sigma$ around 
+In the analysis, we applied selection cuts based on a fit of the exclusive peak at 3$\sigma$ around 
 the mean value for each variable. This systematic method helps to avoid any bias 
 in the selection of the events. The selection of coherent DVCS with these variables is illustrated in 
-Fig. \ref{fig:CohExcCuts}. We note on these distributions only few minor anomalies, where the 
-distribution have some asymmetries. These are linked with the detector resolutions, that impact
-some of the kinematic variables non linearly. The selection of incoherent DVCS is presented in 
-Fig. \ref{fig:IncExcCuts}, with two main differences: larger distributions overall and more
-offset distributions. The larger distributions are mainly attributed to the effect of 
+Fig. \ref{fig:CohExcCuts}. We note on these distributions only a few minor anomalies, where the 
+distributions have some asymmetries. These are linked with the detector resolution, which impact
+some of the kinematic variables non-linearly. The selection of incoherent DVCS is presented in 
+Fig. \ref{fig:IncExcCuts}, with two main differences: wider distributions and larger
+offset from the nominal expectations. The wider distributions are mainly attributed to the effect of 
 Fermi motion, but simulations have shown that this effect is not strong enough to fully 
-reproduce the distribution widths and final state interactions must play a role as well. 
-The offsets of some distributions is caused by slight detector 
+reproduce the distribution widths and FSIs must play a role as well. 
+The offsets of some distributions are caused by slight detector 
 misalignment between CLAS sectors and are within the levels obtained with free proton 
@@
         (blue) and after (black line filled
-	in Grey) the exclusivity cuts used to select coherent DVCS represented by the 
+	in gray) the exclusivity cuts used to select coherent DVCS represented by the 
 	red dashed lines. The histograms are shown as a function of the 
 	seven variables used for the exclusivity selection described in the text, 
-	plus the missing $P_x$ and $P_y$, in order left to right and top to bottom. 
+	plus the missing $P_x$ and $P_y$ components, in order left to right and top to bottom. 
 	}
@@
    and after (black line filled
-	in Grey) the exclusivity cuts used to select coherent DVCS represented by the 
+	in gray) the exclusivity cuts used to select coherent DVCS represented by the 
 	red dashed lines. The histograms are shown as a function of the 
 	seven variables used for the exclusivity selection described in the text, 
-	plus the missing $P_x$ and $P_y$, in order left to right and top to bottom.}
+	plus the missing $P_x$ and $P_y$ components, in order left to right and top to bottom.}
 \label{fig:IncExcCuts}
@@
 
-\subsection{Background subtraction}
-
-The main contamination is expected to be 
+\subsection{Background Subtraction}
+
+The main signal contamination comes 
 from the exclusive production of a $\pi^0$, the final state of which is very similar to DVCS with 
@@
 easy to confuse this process with single photon production. In order to estimate the contribution from
-this channel in the data, we measure the exclusive $\pi^0$ production in the same way as DVCS, with 
+this channel in the data, we measured the exclusive $\pi^0$ production in the same way as DVCS, with 
 a series of exclusivity cuts, completed by a selection cut on the invariant mass of the two photons
 to match the $\pi^0$ mass. The events obtained for the coherent and incoherent
-channels are shown in Fig. \ref{fig:CohPi0Simul} and \ref{fig:InCohPi0Simul}, respectively. Using 
-this sample, we elaborated an event generator by adjusting it to the data after being processed
-in the simulation of the detectors. the result of this process is shown with the red histograms 
-of Fig. \ref{fig:CohPi0Simul} and 
-\ref{fig:InCohPi0Simul}. To correct the experimental data, we estimate the number of single photon 
+channels are shown in Figs. \ref{fig:CohPi0Simul} and \ref{fig:InCohPi0Simul}, respectively. Using 
+this sample, we developed an event generator and adjusted it to the data. The result of which 
+is shown with the red histograms of Figs. \ref{fig:CohPi0Simul} and 
+\ref{fig:InCohPi0Simul}. To correct the experimental data, we then estimated the number of single photon 
 events coming from the exclusive $\pi^0$ production as:
@@
 $N_{2\gamma,\pi^0}^{Sim}$ the number of simulated exclusive $\pi^0$ fully reconstructed and $N_{2\gamma,\pi^0}^{Exp}$
-the number of experimentally measured exclusive $\pi^0$. This number can then be subtracted from
+the number of experimentally measured exclusive $\pi^0$. This number was then subtracted from
 the experimentally measured number of DVCS events ($N_{DVCS}^{Exp}$) to get the corrected result: 
@@
 
-We show in Fig.~\ref{fig:cont_yield} the $\pi^0$ contamination for the $-t$ bins, where it varies
-the most from one bin to another. The study
-shows 2 to 4\% contamination in the coherent channel and 3 to 17\% in the incoherent
-channel. After subtracting this contamination, we make no further correction to 
+We show in Fig.~\ref{fig:cont_yield} the $\pi^0$ contamination for the $-t$ 
+bins, where it varies the most from one bin to another. The study shows 2 to 
+4\% contamination in the coherent channel and 3 to 17\% in the incoherent 
+channel. After subtracting this contamination from the denominator of the 
+asymmetry, we make no further correction to 
 the DVCS BSA, \textit{i.e}., we assume the exclusive $\pi^0$ production has no such 
@@
 contamination fraction in the DVCS events as a function of the 
-transferred momentum squared -$t$ and integrated over the kinematical 
+transferred momentum squared -$t$ and integrated over the kinematic 
 variables $Q^2$, $x_B$, and $\phi$.}
@@
 possible to have particles from different events being combined and pass all the cuts to get 
-into the data sample. To evaluate the number of such events, we invert the vertex selection 
+into the data sample. To evaluate the number of such events, we inverted the vertex selection 
 of the two charged 
-particles of the process, electron and helium (or proton in the incoherent case), and request that they
-are separate. We find 4.1\% of the coherent and 6.5\% of the incoherent samples are accidentals.
-
-\subsection{Systematic uncertainties}
-
-To evaluate the systematic error of the measurement, we performed several specialized studies. We 
+particles of the process, electron and helium (or proton in the incoherent case), and requested that they
+are separate. We found that 4.1\% of the coherent and 6.5\% of the incoherent samples were accidentals,
+they are also subtracted from the denominator of the asymmetry.
+
+\subsection{Systematic Uncertainties}
+
+To further evaluate the systematic uncertainty of the measurements, we performed several specialized studies. We 
 evaluated the impact of changing the exclusivity selection cuts by varying them from 1 to 5 $\sigma$. 
-We evaluated the impact of changing the binning in $\phi$ on the extraction of the beam-spin asymmetry
-at 90°. The precision with which we know the beam polarization is estimated based on the spread 
-of its measurements during the complete run period. We studied how different methods of
+We also evaluated the impact of changing the binning in $\phi$ on the extraction of the BSA
+at 90°. The beam polarization was measured using M\o{}ller scattering runs, the uncertainty was 
+estimated based on the known precision of the dedicated apparatus and the spread 
+of the measurements during the complete run period. We studied how different methods of
 simulating the exclusive $\pi^0$ production affected the single-photon background and
@@
 radiative corrections are expected to be small
-for this process, we did not apply them, but associated an error of their expected value.
+for this process, we did not apply them, but associated an uncertainty equal to their expected value.
 These uncertainties are summarized in Tab. \ref{Table:systematic_uncertainties}, with their respective 
-evaluated values. They are added quadratically for the total systematic error presented in the results.
+evaluated values. They are added quadratically to obtain the total systematic uncertainty presented in the results.
 
@@
 \caption{The systematic uncertainties on the measured coherent and incoherent 
-beam-spin asymmetries at $\phi = 90^{\circ}$.}
+BSAs at $\phi = 90^{\circ}$.}
 \label{Table:systematic_uncertainties}
@@
 we studied the difference between the two results by analyzing the data independently using the two 
-definitions. We found no significant difference between them, as it is 
+definitions. We found no significant difference between them, as is 
 illustrated in Fig. \ref{fig:ttpComp}. We use in the final results $t$ as it is based on the 
 rigorous definition. Since the effect of resolution appears small and is partly accounted for
-in the systematic error associated to the DVCS cuts, we decided not to associate an extra
-systematic error based on this study.
+in the systematic uncertainty associated to the DVCS cuts, we decided not to associate an extra
+systematic uncertainty based on this study.
 
@@
 observe the dominant sinusoidal component typical of the DVCS BSA, with an amplitude almost 
-double than the one measured for the free proton \cite{Jo:2015ema}. This 
-predicted feature of nuclear DVCS \cite{Guzey:2003jh} is observed here for the first time, we
-can conclude that this measurement cleanly isolates the coherent DVCS process. The absence of 
-this feature in the previous measurement by HERMES \cite{Airapetian:2009cga} and its clear observation here indicates that the recoil 
-detection is necessary to isolate the effects of the coherent DVCS process from backgrounds.
+double that measured for the free proton \cite{Jo:2015ema}. This 
+predicted feature of nuclear DVCS \cite{Guzey:2003jh} is observed here for the first time, due
+to the fact that this measurement cleanly isolates the coherent DVCS process. The absence of 
+this feature in the previous measurement by HERMES \cite{Airapetian:2009cga} and its clear 
+observation here indicates that the recoil detection is necessary to isolate the effects of 
+the coherent DVCS process from the incoherent background.
 
@@
 	function of $\phi$ and $Q^2$ 
-	(top panels), $x$ (middle panels) or $-t$ (lower panels). Error bars are  
-	statistical, Grey bands represent the systematic uncertainties. The full red lines show
+	(top panels), $x$ (middle panels) and $-t$ (lower panels). The error bars are  
+	statistical and the gray bands represent the systematic uncertainties. The full red lines show
 	the fit of the data with the form of Eq.~\ref{eq:A_LU-coh}.}
@@
 \center
-\includegraphics[width=17cm]{fig3/Coherent_ALU_phi_90.pdf}
+\includegraphics[width=16cm]{fig3/Coherent_ALU_phi_90.pdf}
 \caption{The BSA at 90° as a function of $Q^2$ (top panel), $x$ (middle panel) and $-t$ (lower panel).
 	Our results are shown with black squares, HERMES results 
-	with green circles \cite{Airapetian:2009cga}. Theoretical predictions 
-	by Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
-	with red full line and dashed blue, while the calculation by Fucini 
-	{\it et al.}~\cite{Fucini:2018gso} is shown with a magenta long dash line.}
+	with green circles~\cite{Airapetian:2009cga}. Theoretical predictions 
+	by Liuti \textit{et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
+	by the red full line and the dashed blue line, while the calculation by Fucini 
+	\textit{et al.}~\cite{Fucini:2018gso} is shown with the magenta long dashed line.}
 \label{fig:CohALU90}
@@
 
-We extract the BSA at 90° in Fig. \ref{fig:CohALU90}, the model compared to the 
-data~\cite{Liuti:2005gi} is based on the hypothesis that the main nuclear effects are 
-included by accounting for the nucleon off-shellness and kinematics in nuclei. It 
-appears that this model undershoots the results systematically. However, a new independent 
-calculation \cite{Fucini:2018gso}, using similar principles but with a non diagonal nuclear spectral 
-function \cite{Viviani:2001wu} based on the Av18 nucleon-nucleon potential \cite{Wiringa:1994wb} 
+We show the extraction of the BSA at 90° in Fig. \ref{fig:CohALU90} together with the 
+past HERMES Collaboration results~\cite{Airapetian:2009cga}. Two models are compared to the 
+data, they are both based on the hypothesis that the main nuclear effects are 
+included by accounting for the nucleon off-shellness and the kinematics of nucleons in nuclei. The 
+one by Liuti \textit{et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} 
+appears to undershoot the results systematically. However, the more recent and independent 
+calculation by Fucini \textit{et al.}~\cite{Fucini:2018gso}, using similar principles but with a non-diagonal nuclear spectral 
+function \cite{Viviani:2001wu} based on the AV18 nucleon-nucleon potential \cite{Wiringa:1994wb} 
 and the UIV three-body forces \cite{Pudliner:1995wk}, has been able to reproduce the data very 
-well. Another factor in the difference is that the recent calculation by Fucini {\it et 
-al.}~\cite{Fucini:2018gso} benefited from using the precise kinematic of each points presented 
-in appendix \ref{sec:fullresults}. Including this information appears to have a significant 
+well. A factor in the difference is that the recent calculation by Fucini {\it et 
+al.}~\cite{Fucini:2018gso} benefited from using the precise kinematics of each of the points presented 
+in Appendix \ref{sec:fullresults}. Including this information appears to have a significant 
 impact on some points, for instance the $-t$ distribution appears to have a peculiar structure 
-which is well reproduced when using this information.
-
-One of the motivation for the choice of helium-4 for the coherent DVCS measurement was
-a simplified extraction of the CFF $\mathcal{H}_A$ from
+that is well reproduced when using this information.
+
+One of the motivations for the choice of helium-4 for the coherent DVCS measurement was
+a simplified extraction of the CFF $\mathcal{H}_A$ from the
 data. To perform this step, we used the form from Eq. \ref{eq:A_LU-coh} to fit the data in Fig. 
-\ref{fig:CohALUphi}. We present in Fig. \ref{fig:CohCFF} the real and imaginary parts 
-of the single CFF of the helium-4 nucleus extracted. The results are rather encouraging, the two parts
-of the CFF are constrained by data without the need of any model assumption. This capacity to obtain a
+\ref{fig:CohALUphi}. We present in Fig. \ref{fig:CohCFF} the extracted real and imaginary parts 
+of the single CFF of the helium-4 nucleus. The results are rather encouraging. The two parts
+of the CFF are constrained by data without the need for any model assumption. This capacity to obtain a
 model independent result with such a limited data set offers a striking contrast with the
@@
 	using the VGG model as input \cite{Vanderhaeghen:1999xj,Guidal:2004nd}, and
-	the blue long dash line shows the predictions by Liuti {\it et 
+	the blue long dashed line shows the predictions by Liuti {\it et 
 	al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv}.} 
@@
 We can see that the effect of changing the input nucleon GPD model
-is of similar size or larger than the difference between nuclear 
+is of similar size or larger than the difference between the nuclear 
 models. However, at the level of precision of the present data,
@@
 photo-production on a nucleus is the first to clearly isolate the effect of 
-coherent nuclear DVCS and of nuclear GPDs. While, the statistical precision and 
+coherent nuclear DVCS and of nuclear GPDs. While the statistical precision and 
 the kinematic coverage are still behind the experimental results of
@@
 framework. Moreover, the extraction of the CFF appears to be very convenient based
-on the BSA measurement only. Together, these findings  validate the relevance of the 
+on the BSA measurement only. Together, these findings  validate the relevance of
 coherent nuclear DVCS to study the nucleus globally in terms of quarks and 
@@
 	helium-4 as a function of $\phi$ and $Q^2$ 
-	(top panels), $x$ (middle panels) or $-t$ (lower panels). Error bars are  
-	statistical, Grey bands represent the systematic uncertainties. The data is fitted with the 
+	(top panels), $x$ (middle panels) and $-t$ (lower panels). The error bars are  
+	statistical and the gray bands represent the systematic uncertainties. The data is fitted with the 
 	form $\frac{\alpha \sin(\phi)}{1+\beta \cos(\phi)}$; the results of the 
@@
 The results for the measurement of the BSA in the incoherent DVCS channel are presented in
-Fig. \ref{fig:InCohALUphi}. They display patterns rather similar to the one observed with the 
+Fig. \ref{fig:InCohALUphi}. They display patterns rather similar to those observed with the 
 free proton, with a clear domination of their sinusoidal component. To compare the data to 
@@
 The asymmetries at 90° are presented in Fig. \ref{fig:IncALU} together with the theoretical
-calculation presented previously in Fig. \ref{fig:CohALU90}. We observe an important improvement
-on the precision compared to 
-the HERMES data, which offers a strong constraint on the model presented. As in the
+calculation by the same groups as presented in Fig. \ref{fig:CohALU90}. We observe a 
+significant improvement on the precision compared to 
+the HERMES data, which offers more constraint on the models presented. As in the
 coherent case, the calculation appears to have issues reproducing the shape of the data,
@@
 effect, which allows to cancel out
-the effects from the nucleon structure and highlight nuclear effects. Such ratio is presented
+the effects from the nucleon structure and highlight nuclear effects. Such a ratio is presented
 in Fig. \ref{fig:IncRatios}.
@@
 linked to the different input model used for the free nucleon GPD rather than to differences in the 
-treatment of the nuclear effects. Also, Fucini {\it et al.} appear to reproduce the 
-shape of the $x_B$ distribution, which would indicate that it is linked to kinematic effects.
-Altogether, this result confirms that most models significantly overshoot the data and that 
-the BSA in the incoherent DVCS channel is suppressed by 20 to 30 \% compared to the free proton.
+treatment of the nuclear effects. Also, Fucini {\it et al.} appear to roughly reproduce the 
+shape of the $x_B$ distribution, which might indicate that it is linked to correlations between kinematic variables.
+In conclusion, the BSA in the incoherent DVCS channel is suppressed by 20 to 30\% compared to the free proton,
+which was not expected by most models.
 
@@
 	by Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
-	with red full line and dashed blue, while the calculation by Fucini 
-	{\it et al.}~\cite{Fucini:2019xlc} is shown with a magenta long dash line.}
+	by the red full line and the dashed blue line, while the calculation by Fucini 
+	{\it et al.}~\cite{Fucini:2019xlc} is shown with the magenta long dashed line.}
 \label{fig:IncALU}
@@
 	by Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
-	with red full line and dashed blue, a calculation adapted by Fucini 
-	{\it et al.}~\cite{Fucini:2019xlc} is shown with a magenta long dash line and the
-	the black dot-dash line is the calculation by Guzey {\it et al.}~\cite{Guzey:2008th}.}
+	by the red full line and the dashed blue line, a calculation adapted by Fucini 
+	{\it et al.}~\cite{Fucini:2019xlc} is shown with the magenta long dashed line and 
+	the black dot-dashed line is the calculation by Guzey {\it et al.}~\cite{Guzey:2008th}.}
 \label{fig:IncRatios}
@@
 made in the impulse approximation. Moreover, we showed that the CFF extraction can be 
-immediately performed using these data without any model prescription. The incoherent DVCS measurement 
+immediately performed using these data without any model assumptions. The incoherent DVCS measurement 
 however reveals relatively small asymmetries in comparison to previous free proton 
-measurements. It remains unclear what is the source of the suppression of the BSA as both 
+measurements. The source of this suppression of the BSA remains unclear as both 
 initial and final state effect contributions could lead to such outcome. We presented 
-various models for both channels, while old and recent work agree nicely with the data
-from the coherent channel, it appears more difficult to reproduce the incoherent ones.
-A future experimental program using tagging at the upgraded CLAS12 detector is 
+various models for both channels. While old and recent work agree nicely with the data
+from the coherent channel, it appears more difficult to reproduce the incoherent DVCS data.
+A future experimental program using tagging at the upgraded CLAS12 detector with 11~GeV
+electron beam is 
 planned to address this question in the coming years by using a new recoil detector 
@@
 \appendix
-\section{Expressions for the BSA of the coherent DVCS}
+\section{Expressions for the BSA of the Coherent DVCS}
 \label{sec:eq}
@@
 We present in this appendix the detailed expressions used for Eq. \ref{eq:coh_BSA} 
-and Eq. \ref{eq:alpha1} to \ref{eq:alpha4}. These are adapted from the work of 
+and Eqs. \ref{eq:alpha1} to \ref{eq:alpha4}. These are adapted from the work of 
 Kirchner and Müller \cite{Kirchner:2003wt} to match the notations and conventions used
@@
 \right\} - 4 x_A^2{(2-y)}^2 (2+\epsilon^2) \frac{t}{Q^2} \nonumber \\
-pdflatex prc-dvcshelium.tex
 & \phantom{\bigg[} & + 8 K^2 \frac{\epsilon^2 Q^2}{t} \,\,\,\,\,\,\, \bigg] F_A^2(t)  \\
@@
 \frac{\epsilon^2 Q^2}{t} \right\} F_A^2(t)  \\
-c_2^{BH} = & \phantom{\bigg[} & 8 K^2 \frac{\epsilon^2 Q^2}{t} F_A^2(t) 
+c_2^{BH} = & \phantom{\bigg[} & 8 K^2 \frac{\epsilon^2 Q^2}{t} F_A^2(t),
 \end{eqnarray} 
-where $F_A(t)$ is the electromagnetic form factor of the $^4$He. 
+where $F_A(t)$ is the electromagnetic form factor of $^4$He. 
 The coefficient for the DVCS contribution is given by: 
@@
    c_0^{DVCS}= 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + \epsilon^2} \, 
-   {\mathcal H}_A {\mathcal H}^{\star}_A 
+   {\mathcal H}_A {\mathcal H}^{\star}_A .
    \label{eq:c0DVCS}
@@
 \frac{x_At}{Q^2}-\frac{3\epsilon^{2}}{4.0} \bigg\} \nonumber \\&-& 4K \left( 
-2-2y+y^2+\frac{\epsilon^{2}}{2}y^2\right)\frac{1+\sqrt{1+\epsilon^{2}}-\epsilon^{2}}{(1+e2)^{5/2}}\bigg\{1-(1-3x_A)\frac{t}{Q^2}\nonumber\\&\,\,\,\,&\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,+\frac{1-\sqrt{1+\epsilon^{2}}+3\epsilon^{2}}{1+\sqrt{1+\epsilon^{2}}-\epsilon^{2}}
-\frac{x_A*t}{Q^2}\bigg\} \label{eq:c1I}
+2-2y+y^2+\frac{\epsilon^{2}}{2}y^2\right)\frac{1+\sqrt{1+\epsilon^{2}}-\epsilon^{2}}{(1+e2)^{5/2}}
+\bigg\{1-(1-3x_A)\frac{t}{Q^2}\nonumber\\&\,\,\,\,&\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,+
+\frac{1-\sqrt{1+\epsilon^{2}}+3\epsilon^{2}}{1+\sqrt{1+\epsilon^{2}}-\epsilon^{2}} 
+\frac{x_A t}{Q^2}\bigg\}. \label{eq:c1I}
 \end{eqnarray}
 
-\section{Tables of results with kinematic information}
+\section{Tables of Results with Kinematics Information}
 \label{sec:fullresults}

### 2021-02-02 eg6-letters/long-paper/prc-dvcshelium.tex
Update figures and author list

@@
-\documentclass{article}
-\usepackage[left=3.5cm,right=2.5cm,top=2cm,bottom=2cm,includefoot,includehead,headheight=15pt]{geometry}
+%\documentclass{article}
+%\usepackage[left=3.5cm,right=2.5cm,top=2cm,bottom=2cm,includefoot,includehead,headheight=15pt]{geometry}
 %\usepackage{lineno}
-%\documentclass[aps,prc,preprint,superscriptaddress]{revtex4}
+\documentclass[aps,prc,preprint,superscriptaddress]{revtex4}
 %\usepackage{amsmath,amssymb}             % AMS Math
@@
 
-%\input author_list.tex
+\input author_list.tex
 
 \date{\today}
-%TODO
-\maketitle
 
@@
 
-%\maketitle
+\maketitle
 
@@
 	Our results are shown with black squares, HERMES results 
-	with green circles~\cite{Airapetian:2009cga}. Theoretical predictions 
-	by Liuti \textit{et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
-	by the red full line and the dashed blue line, while the calculation by Fucini 
-	\textit{et al.}~\cite{Fucini:2018gso} is shown with the magenta long dashed line.}
+	with green circles~\cite{Airapetian:2009cga}. The theoretical prediction 
+	by Liuti \textit{et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} is shown 
+	by the full blue line, while the calculation by Fucini 
+	\textit{et al.}~\cite{Fucini:2018gso} is shown with the magenta dashed line.}
 \label{fig:CohALU90}
@@
 	$-t$ (bottom). Our measurement is represented with black squares and the HERMES 
-	measurement \cite{Airapetian:2009cga} with green circles. Theoretical predictions 
-	by Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
-	by the red full line and the dashed blue line, while the calculation by Fucini 
-	{\it et al.}~\cite{Fucini:2019xlc} is shown with the magenta long dashed line.}
+	measurement \cite{Airapetian:2009cga} with green circles. The theoretical prediction 
+	by Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} is shown 
+	by the full blue line, while the calculation by Fucini 
+	{\it et al.}~\cite{Fucini:2019xlc} is shown with the magenta dashed line.}
 \label{fig:IncALU}
@@
 	represented with black squares and the HERMES 
-	measurement \cite{Airapetian:2009cga} with green circles. Theoretical predictions 
-	by Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} are shown 
-	by the red full line and the dashed blue line, a calculation adapted by Fucini 
-	{\it et al.}~\cite{Fucini:2019xlc} is shown with the magenta long dashed line and 
+	measurement \cite{Airapetian:2009cga} with green circles. The theoretical prediction
+	by Liuti {\it et al.}~\cite{Liuti:2005gi,GonzalezHernandez:2012jv} is shown 
+	by the full blue line, the calculation by Fucini 
+	{\it et al.}~\cite{Fucini:2019xlc} is shown with the magenta dashed line, and 
 	the black dot-dashed line is the calculation by Guzey {\it et al.}~\cite{Guzey:2008th}.}

### 2021-02-02 eg6-letters/long-paper/source_files/Coh/Coherent_ALU_phi_90.C

@@ -94,7 +94,7 @@ void Coherent_ALU_phi_90()
    graphS->SetMarkerStyle(34);
    graphS->SetMarkerSize(1.5);
    graphS->SetMarkerColor(6);
-   graphS->SetLineStyle(9);
+   graphS->SetLineStyle(7);
    graphS->SetLineWidth(2);
    graphS->SetLineColor(6);
    graphS->Draw("l");
@@ -138,10 +138,14 @@ void Coherent_ALU_phi_90()
    entry->SetMarkerStyle(21);
    entry->SetMarkerSize(1.5);
    entry->SetTextFont(42);
-   TLegendEntry *entry2=leg->AddEntry("graphS","Fucini et al. [31]","L");
-   entry2->SetLineStyle(9);
-   entry2->SetLineWidth(2);
-   entry2->SetLineColor(6);
+   entry=leg->AddEntry("HERMES","HERMES [10]","P");
+   entry->SetLineColor(1);
+   entry->SetLineStyle(1);
+   entry->SetLineWidth(1);
+   entry->SetMarkerColor(8);
+   entry->SetMarkerStyle(8);
+   entry->SetMarkerSize(1.5);
+   entry->SetTextFont(42);
    leg->Draw();
    TLine *line = new TLine(0.85,0,2.6,0);
    line->SetLineStyle(7);
@@ -230,7 +234,7 @@ void Coherent_ALU_phi_90()
    graphT->SetMarkerStyle(34);
    graphT->SetMarkerSize(1.5);
    graphT->SetMarkerColor(6);
-   graphT->SetLineStyle(9);
+   graphT->SetLineStyle(7);
    graphT->SetLineWidth(2);
    graphT->SetLineColor(6);
    graphT->Draw("l");
@@ -301,55 +305,55 @@ void Coherent_ALU_phi_90()
    graph->SetLineWidth(2);
    graph->Draw("c");
    
-   Double_t Graph1_fx24[16] = {
-   0.0053,
-   0.0277,
-   0.0672,
-   0.1223,
-   0.1911,
-   0.271,
-   0.3592,
-   0.4525,
-   0.5475,
-   0.6408,
-   0.729,
-   0.8089,
-   0.8777,
-   0.9328,
-   0.9723,
-   0.9947};
-   Double_t Graph1_fy24[16] = {
-   0.312336,
-   0.327893,
-   0.316997,
-   0.287221,
-   0.245252,
-   0.194805,
-   0.134905,
[…]

### 2021-02-02 eg6-letters/long-paper/source_files/Coh/Coherent_CFF.C

@@ -755,7 +755,7 @@ void Coherent_CFF()
    entry->SetMarkerStyle(21);
    entry->SetMarkerSize(1.5);
    entry->SetTextFont(42);
-   entry=leg->AddEntry("graphCFF","Guzey et al. [17]","L");
+   entry=leg->AddEntry("graphCFF","Guzey et al. [18,38]","L");
    entry->SetLineColor(2);
    entry->SetLineStyle(1);
    entry->SetLineWidth(2);
@@ -913,12 +913,12 @@ void Coherent_CFF()
    leg->SetLineWidth(1);
    leg->SetFillColor(0);
    leg->SetFillStyle(1001);
-   entry=leg->AddEntry("Graph0","Guzey et al. [17]","L");
+   entry=leg->AddEntry("Graph0","Guzey et al. (VGG)","L");
    entry->SetLineColor(1);
    entry->SetLineStyle(7);
    entry->SetLineWidth(2);
    entry->SetTextFont(42);
-   TLegendEntry *entry2=leg->AddEntry("graph","Liuti et al. [29]","L");
+   TLegendEntry *entry2=leg->AddEntry("graph","Liuti et al. [30,31]","L");
    entry2->SetLineStyle(9);
    entry2->SetLineWidth(2);
    entry2->SetTextFont(42);

### 2021-02-02 eg6-letters/long-paper/source_files/InCoh/ALU_90_p_vs_Q2_shortscenrario.C

@@ -99,7 +99,7 @@ void ALU_90_p_vs_Q2_shortscenrario()
    0.175,
    0.134};
    TGraph *graphS = new TGraph(4,_sx1,_sy1);
-   graphS->SetLineStyle(9);
+   graphS->SetLineStyle(7);
    graphS->SetLineWidth(2);
    graphS->SetLineColor(6);
    graphS->Draw("l");
@@ -114,12 +114,12 @@ void ALU_90_p_vs_Q2_shortscenrario()
    TLegendEntry *entry;
    entry=leg->AddEntry("clas","CLAS (this work)","p");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Scope","Fucini et al. [40]","l");
-   entry->SetLineStyle(9);
+   entry=leg->AddEntry("Scope","Fucini et al. [41]","l");
+   entry->SetLineStyle(7);
    entry->SetLineWidth(2);
    entry->SetLineColor(6);
    entry->SetTextFont(42);
-   leg->Draw();
+//   leg->Draw();
    TLine *line = new TLine(0.8,0,3.8,0);
    line->SetLineStyle(7);
    line->Draw();

### 2021-02-02 eg6-letters/long-paper/source_files/InCoh/ALU_90_p_vs_t_shortscenrario.C

@@ -106,7 +106,7 @@ void ALU_90_p_vs_t_shortscenrario()
    0.173,
    0.165};
    TGraph *graphS = new TGraph(4,_sx1,_sy1);
-   graphS->SetLineStyle(9);
+   graphS->SetLineStyle(7);
    graphS->SetLineWidth(2);
    graphS->SetLineColor(6);
    graphS->Draw("l");
@@ -182,10 +182,6 @@ void ALU_90_p_vs_t_shortscenrario()
    0.1352,
    0.199169,
    0.243986,  
-  
-  
-  
-
    0.273819,
    0.29121,
    0.298917,
@@ -207,7 +203,7 @@ void ALU_90_p_vs_t_shortscenrario()
    graph->SetMarkerColor(2);
    graph->SetMarkerStyle(21);
    graph->SetMarkerSize(1.5);
-   graph->Draw("c");
+//   graph->Draw("c");
    
    Double_t Graph4_fx1009[16] = {
    0.0026,
@@ -284,7 +280,7 @@ void ALU_90_p_vs_t_shortscenrario()
    gre->SetFillStyle(1000);
    gre->SetLineColor(4);
    gre->SetLineWidth(2);
-   gre->SetLineStyle(7);
+ //  gre->SetLineStyle(7);
    gre->SetMarkerColor(4);
    gre->SetMarkerStyle(22);
    gre->SetMarkerSize(1.5);
@@ -294,7 +290,7 @@ void ALU_90_p_vs_t_shortscenrario()
    line->SetLineStyle(7);
    line->Draw();
    
-   TLegend *leg = new TLegend(0.46,0.64,0.92,0.92,NULL,"brNDC");
+   TLegend *leg = new TLegend(0.5,0.65,0.92,0.92,NULL,"brNDC");
    leg->SetBorderSize(1);
    leg->SetLineColor(1);
    leg->SetLineStyle(1);
@@ -304,10 +300,10 @@ void ALU_90_p_vs_t_shortscenrario()
    TLegendEntry *entry=leg->AddEntry("Graph0","CLAS (This work)","P");
    entry->SetTextFont(42);
    entry=leg->AddEntry("Graph1","HERMES [10]","P");
-   entry=leg->AddEntry("Graph3","Liuti et al. (low x_{B}) [29]","L");
-   entry=leg->AddEntry("Graph4","Liuti et al. (high x_{B}) [29]","L");
[…]

### 2021-02-02 eg6-letters/long-paper/source_files/InCoh/ALU_90_p_vs_x_shortscenrario.C

@@ -134,7 +134,7 @@ void ALU_90_p_vs_x_shortscenrario()
    graph->SetFillStyle(1000);
    graph->SetLineColor(2);
    graph->SetLineWidth(2);
-   graph->Draw("c");
+//   graph->Draw("c");
    
    Double_t _sx1[4] = {
    0.162,
@@ -151,7 +151,7 @@ void ALU_90_p_vs_x_shortscenrario()
    0.169,
    0.147};
    TGraph *graphS = new TGraph(4,_sx1,_sy1);
-   graphS->SetLineStyle(9);
+   graphS->SetLineStyle(7);
    graphS->SetLineWidth(2);
    graphS->SetLineColor(6);
    graphS->Draw("l");
@@ -192,7 +192,7 @@ void ALU_90_p_vs_x_shortscenrario()
    980.425};
    graph = new TGraph(16,Graph2_fx5,Graph2_fy5);
    graph->SetName("Graph2");
-   graph->SetLineStyle(7);
+//   graph->SetLineStyle(7);
    graph->SetLineColor(4);
    graph->SetLineWidth(2);
    graph->Draw("c");
@@ -201,7 +201,7 @@ void ALU_90_p_vs_x_shortscenrario()
    line->SetLineStyle(7);
    line->Draw();
    
-   TLegend *leg = new TLegend(0.5,0.7,0.92,0.92,NULL,"brNDC");
+   TLegend *leg = new TLegend(0.44,0.67,0.92,0.92,NULL,"brNDC");
    leg->SetBorderSize(1);
    leg->SetLineColor(1);
    leg->SetLineStyle(1);
@@ -210,16 +210,16 @@ void ALU_90_p_vs_x_shortscenrario()
    leg->SetFillStyle(1001);
    TLegendEntry *entry=leg->AddEntry("Graph0","CLAS (This work)","P");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Graph1","Liuti et al. (low -t) [29]","L");
+   entry=leg->AddEntry("Graph1","Liuti et al. (low -t) [30,31]","L");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Graph2","Liuti et al. (high -t) [29]","L");
+   entry=leg->AddEntry("Graph2","Liuti et al. (high -t) [30,31]","L");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("GraphS","Fucini et al. [40]","L");
[…]

### 2021-02-02 eg6-letters/long-paper/source_files/InCoh/ALU_ratioInc_Q2_shortscenrario.C

@@ -16,7 +16,7 @@ void ALU_ratioInc_Q2_shortscenrario()
    Can->SetFrameBorderMode(0);
    Can->SetFrameBorderMode(0);
    
-   TH2F *HALU_RATIO_Q2__1 = new TH2F("HALU_RATIO_Q2__1","",100,0.8,3.8,100,-0.1,1.5);
+   TH2F *HALU_RATIO_Q2__1 = new TH2F("HALU_RATIO_Q2__1","",100,0.8,3.8,100,-0.1,1.7);
    HALU_RATIO_Q2__1->SetStats(0);
 
    Int_t ci;      // for color index setting
@@ -85,7 +85,7 @@ void ALU_ratioInc_Q2_shortscenrario()
    0.9904,
    0.9759};
    TGraph *graphS = new TGraph(4,_sx1,_sy1);
-   graphS->SetLineStyle(9);
+   graphS->SetLineStyle(7);
    graphS->SetLineWidth(2);
    graphS->SetLineColor(6);
    graphS->Draw("l");
@@ -120,23 +120,34 @@ void ALU_ratioInc_Q2_shortscenrario()
    gre->SetMarkerSize(1.5);
    gre->Draw("p");
 
-   TLegend *leg = new TLegend(0.54,0.80,0.92,0.92,NULL,"brNDC");
+    TLegend *leg = new TLegend(0.19,0.72,0.88,0.92,NULL,"brNDC");
+   leg->SetNColumns(2);
    leg->SetBorderSize(1);
-   leg->SetTextSize(0.05);
-   leg->SetLineColor(1);
-   leg->SetLineStyle(1);
-   leg->SetLineWidth(1);
-   leg->SetFillColor(0);
-   leg->SetFillStyle(1001);
-   TLegendEntry *entry=leg->AddEntry("gre","CLAS (This work)","P");
+   TLegendEntry *entry=leg->AddEntry("Graph0","CLAS (This work)","P");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("graphS","Fucini et al. [40]","L");
-   entry->SetLineStyle(9);
+   entry=leg->AddEntry("Graph2","Liuti et al. [30,31]","L");
+   entry->SetLineStyle(1);
+   entry->SetLineWidth(2);
+   entry->SetLineColor(4);
+   entry->SetTextFont(42);
+   entry=leg->AddEntry("GraphH","HERMES [10]","P");
+   entry->SetMarkerColor(8);
+   entry->SetMarkerStyle(8);
[…]

### 2021-02-02 eg6-letters/long-paper/source_files/InCoh/ALU_ratioInc_t_shortscenrario.C

@@ -101,7 +101,7 @@ void ALU_ratioInc_t_shortscenrario()
    0.8344};
    TGraph *graphS = new TGraph(4,_sx1,_sy1);
    graphS->SetName("GraphS");
-   graphS->SetLineStyle(9);
+   graphS->SetLineStyle(7);
    graphS->SetLineWidth(2);
    graphS->SetLineColor(6);
    graphS->Draw("l");
@@ -161,7 +161,7 @@ void ALU_ratioInc_t_shortscenrario()
    graph->SetName("Graph2");
    graph->SetLineColor(2);
    graph->SetLineWidth(2);
-   graph->Draw("c");
+//   graph->Draw("c");
    
    Double_t Graph3_fx16[16] = {
    0.0026,
@@ -201,7 +201,7 @@ void ALU_ratioInc_t_shortscenrario()
    graph->SetName("Graph3");
    graph->SetLineColor(4);
    graph->SetLineWidth(2);
-   graph->SetLineStyle(7);
+//   graph->SetLineStyle(7);
    graph->Draw("c");
    
    Double_t Graph4_fx17[13] = {
@@ -245,18 +245,18 @@ void ALU_ratioInc_t_shortscenrario()
    entry->SetTextFont(42);
    entry=leg->AddEntry("GraphH","HERMES [10]","P");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Graph2","Liuti et al. (low -t) [29]","L");
+   entry=leg->AddEntry("Graph2","Liuti et al. (low -t) [30,31]","L");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Graph4","Guzey et al. [37]","L");
+   entry=leg->AddEntry("Graph4","Guzey et al. [38]","L");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Graph3","Liuti et al. (high -t) [29]","L");
+   entry=leg->AddEntry("Graph3","Liuti et al. (high -t) [30,31]","L");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("GraphS","Fucini et al. [40]","L");
+   entry=leg->AddEntry("GraphS","Fucini et al. [41]","L");
    entry->SetLineStyle(9);
    entry->SetLineWidth(2);
    entry->SetLineColor(6);
    entry->SetTextFont(42);
-   leg->Draw();
+//   leg->Draw();
    Can_R_t->Modified();
    Can_R_t->cd();
    Can_R_t->SetSelected(Can_R_t);

### 2021-02-02 eg6-letters/long-paper/source_files/InCoh/ALU_ratioInc_x_shortscenrario.C

@@ -101,7 +101,7 @@ void ALU_ratioInc_x_shortscenrario()
    0.9742};
    TGraph *graphS = new TGraph(4,_sx1,_sy1);
    graphS->SetName("GraphS");
-   graphS->SetLineStyle(9);
+   graphS->SetLineStyle(7);
    graphS->SetLineWidth(2);
    graphS->SetLineColor(6);
    graphS->Draw("l");
@@ -161,7 +161,7 @@ void ALU_ratioInc_x_shortscenrario()
    graph->SetName("Graph2");
    graph->SetLineColor(2);
    graph->SetLineWidth(2);
-   graph->Draw("c");
+//   graph->Draw("c");
    
    Double_t Graph2_fx4[16] = {
    0.0053,
@@ -201,7 +201,7 @@ void ALU_ratioInc_x_shortscenrario()
    graph->SetName("Graph3");
    graph->SetLineColor(4);
    graph->SetLineWidth(2);
-   graph->SetLineStyle(7);
+//   graph->SetLineStyle(7);
      graph->Draw("c");
    
    Double_t Graph4_fx6[7] = {
@@ -233,18 +233,18 @@ void ALU_ratioInc_x_shortscenrario()
    entry->SetTextFont(42);
    entry=leg->AddEntry("GraphH","HERMES [10]","P");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Graph2","Liuti et al. (low -t) [29]","L");
+   entry=leg->AddEntry("Graph2","Liuti et al. (low -t) [30,31]","L");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Graph4","Guzey et al. [37]","L");
+   entry=leg->AddEntry("Graph4","Guzey et al. [38]","L");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("Graph3","Liuti et al. (high -t) [29]","L");
+   entry=leg->AddEntry("Graph3","Liuti et al. (high -t) [30,31]","L");
    entry->SetTextFont(42);
-   entry=leg->AddEntry("GraphS","Fucini et al. [40]","L");
+   entry=leg->AddEntry("GraphS","Fucini et al. [41]","L");
    entry->SetLineStyle(9);
    entry->SetLineWidth(2);
    entry->SetLineColor(6);
    entry->SetTextFont(42);
-   leg->Draw();
+//   leg->Draw();
    Can_R_x->Modified();
    Can_R_x->cd();
    Can_R_x->SetSelected(Can_R_x);

### 2021-02-19 eg6-letters/long-paper/prc-dvcshelium.tex
Changes for PRC submission

@@
 \center
-\includegraphics[width=10.0cm]{fig1/GPD.png}
+\includegraphics[width=10.0cm]{GPD.png}
 \caption{General representation for the GPDs of a nucleon represented by the triple lines and noted $N$.
@@
 \center
-\includegraphics[width=9cm]{fig1/finalplane.png}
+\includegraphics[width=9cm]{finalplane.png}
 	\caption{Illustration of the scattering (or leptonic) and production (or hadronic) planes
@@
 \center
-\includegraphics[width=9cm]{fig3/DVCS_diagram.pdf}
+\includegraphics[width=9cm]{DVCS_diagram.pdf}
 \caption{Diagram representing the coherent nuclear DVCS, where we 
@@
 \center
-\includegraphics[width=8cm]{fig3/AlphaCoefs.png}
+\includegraphics[width=8cm]{AlphaCoefs.png}
 	\caption{Coefficients presented in Eqs. \ref{eq:alpha1} to \ref{eq:alpha4}.
@@
 \center
-\includegraphics[width=10cm]{fig3/handbag_incoherent.pdf}
+\includegraphics[width=10cm]{handbag_incoherent.pdf}
 \caption{Diagram representing the incoherent nuclear DVCS.}
@@
 \center
-	\includegraphics[width=10.5cm]{fig3/HERMES_BSA.png}
+	\includegraphics[width=10.5cm]{HERMES_BSA.png}
 	\caption{The $\sin(\phi)$ moment of the BSA as a function of $-t$ measured by HERMES
@@
 \center
-\includegraphics[width=10cm]{fig3/HERMES_BSA_2.png}
+\includegraphics[width=10cm]{HERMES_BSA_2.png}
 \caption{The $\sin(\phi)$ moment of the BSA at low and high $-t$ as a function of $A$ measured by HERMES
@@
 \center
-\includegraphics[width=8cm]{fig3/CLAS_geantview-PS.jpg}
+\includegraphics[width=8cm]{CLAS_geantview-PS.jpg}
 	\caption{View of the CLAS detector setup.}
@@
 \center
-\includegraphics[width=8cm]{fig3/IC-CLAS.png}
+\includegraphics[width=8cm]{IC-CLAS.png}
 	\caption{Representation of the inner calorimeter (IC) of CLAS. The crystals that compose the
@@
 \center
-\includegraphics[width=14cm]{fig3/solenoid.png}
+\includegraphics[width=14cm]{solenoid.png}
 \caption{Representation of the center of CLAS with the beam background in red with and without
@@
 \center
-\includegraphics[width=10cm]{fig3/RTPC_new_1.png}
+\includegraphics[width=10cm]{RTPC_new_1.png}
 \caption{Cut view of the RTPC.}
@@
 \center
-\includegraphics[trim=10 10 10 5,clip,width=16.5cm]{fig3/all_coh_exc_cuts.png}
+\includegraphics[trim=10 10 10 5,clip,width=16.5cm]{all_coh_exc_cuts.png}
         \caption{Distributions of the coherent photon production events before 
@@
 \includegraphics[trim=10 10 10 
-   5,clip,width=16.5cm]{fig3/all_incoh_exc_cuts.png}
+   5,clip,width=16.5cm]{all_incoh_exc_cuts.png}
 \caption{Distributions of the incoherent photon production events before (blue) 
@@
 \center
-\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/xB_Coh_pi0.png}
-\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/Q2_Coh_pi0.png}
-\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/t_Coh_pi0.png}
-\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/phi_h_Coh_pi0.png}
+\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{xB_Coh_pi0.png}
+\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{Q2_Coh_pi0.png}
+\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{t_Coh_pi0.png}
+\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{phi_h_Coh_pi0.png}
 	\caption{The measured (filled blue) and simulated (red) distributions of
@@
 \center
-\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/xB_InCoh_pi0.png}
-\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/Q2_InCoh_pi0.png}
-\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/t_InCoh_pi0.png}
-\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{fig3/pi0/phi_h_InCoh_pi0.png}
+\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{xB_InCoh_pi0.png}
+\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{Q2_InCoh_pi0.png}
+\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{t_InCoh_pi0.png}
+\includegraphics[trim=70 15 70 70,clip,width=6.3cm]{phi_h_InCoh_pi0.png}
 	\caption{The measured (filled blue) and simulated (red) distributions of
@@
 \begin{figure}[tbp]
-\includegraphics[width=8cm]{fig3/T_ratio_pi0_dvcs_Coh_t.pdf}
-\includegraphics[width=8cm]{fig3/T_ratio_pi0_dvcs_InCoh_t.pdf}
+\includegraphics[width=8cm]{T_ratio_pi0_dvcs_Coh_t.pdf}
+\includegraphics[width=8cm]{T_ratio_pi0_dvcs_InCoh_t.pdf}
 \caption{The estimated coherent (left) and incoherent (right) $\pi^{0}$ 
@@
 \center
-\includegraphics[width=15cm]{fig3/t_tprime_ALU_90_p_shortscenrario.pdf}
+\includegraphics[width=15cm]{t_tprime_ALU_90_p_shortscenrario.pdf}
 	\caption{The BSA at 90° ($A_{LU}^{Incoh} (90^\circ)$) as a
@@
 \center
-\includegraphics[width=12cm]{fig3/Coherent_ALU_phi.pdf}
+\includegraphics[width=12cm]{Coherent_ALU_phi.pdf}
 	\caption{The BSA in the coherent exclusive photo-production off helium-4 as a 
@@
 \center
-\includegraphics[width=16cm]{fig3/Coherent_ALU_phi_90.pdf}
+\includegraphics[width=16cm]{Coherent_ALU_phi_90.pdf}
 \caption{The BSA at 90° as a function of $Q^2$ (top panel), $x$ (middle panel) and $-t$ (lower panel).
@@
 \center
-\includegraphics[width=14cm]{fig3/Coherent_CFF.pdf}
+\includegraphics[width=14cm]{Coherent_CFF.pdf}
 	\caption{The imaginary (top panels) and real (bottom panels) parts of the helium-4
@@
 \center
-\includegraphics[width=15cm]{fig3/incoherent_ALU_phi.pdf}
+\includegraphics[width=15cm]{incoherent_ALU_phi.pdf}
 	\caption{The BSA in the incoherent exclusive photo-production off a proton bound in
@@
 \center
-\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_Q2_shortscenrario.pdf}
-\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_t_shortscenrario.pdf}
-\includegraphics[width=7.4cm]{fig3/ALU_90_p_vs_x_shortscenrario.pdf}
+\includegraphics[width=7.4cm]{ALU_90_p_vs_Q2_shortscenrario.pdf}
+\includegraphics[width=7.4cm]{ALU_90_p_vs_t_shortscenrario.pdf}
+\includegraphics[width=7.4cm]{ALU_90_p_vs_x_shortscenrario.pdf}
 	\caption{The BSA at 90° as a function of  $Q^2$ (top left), $x$ (top right) and 
@@
 \center
-\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_Q2_shortscenrario.pdf}
-\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_t_shortscenrario.pdf}
-\includegraphics[width=7.4cm]{fig3/ALU_ratioInc_x_shortscenrario.pdf}
+\includegraphics[width=7.4cm]{ALU_ratioInc_Q2_shortscenrario.pdf}
+\includegraphics[width=7.4cm]{ALU_ratioInc_t_shortscenrario.pdf}
+\includegraphics[width=7.4cm]{ALU_ratioInc_x_shortscenrario.pdf}
 	\caption{DVCS BSA ratio of the bound proton to the free proton as a function of 

### 2021-02-19 eg6-letters/long-paper/t-tprime_incoh/t_tprime_ALU_90_p_shortscenrario.C

@@ -1,673 +1,0 @@
-void t_tprime_ALU_90_p_shortscenrario()
-{
-//=========Macro generated from canvas: Cann/
-//=========  (Wed Apr 29 12:45:02 2020) by ROOT version 6.14/04
-   TCanvas *Cann = new TCanvas("Cann", "",0,0,1000,400);
-   gStyle->SetOptFit(1);
-   Cann->Range(0,0,1,1);
-   Cann->SetFillColor(0);
-   Cann->SetBorderMode(0);
-   Cann->SetBorderSize(2);
-   Cann->SetRightMargin(0.02722204);
-   Cann->SetBottomMargin(0.255814);
-   Cann->SetFrameBorderMode(0);
-  
-// ------------>Primitives in pad: Cann_1
-   TPad *Cann_1 = new TPad("Cann_1", "_1",0,0,0.3911937,0.9029345);
-   Cann_1->Draw();
-   Cann_1->cd();
-   Cann_1->Range(-1.224138,-0.30625,4.5,0.5);
-   Cann_1->SetFillColor(0);
-   Cann_1->SetBorderMode(0);
-   Cann_1->SetBorderSize(2);
-   Cann_1->SetLeftMargin(0.2012048);
-   Cann_1->SetRightMargin(0);
-   Cann_1->SetTopMargin(0);
-   Cann_1->SetBottomMargin(0.255814);
-   Cann_1->SetFrameBorderMode(0);
-   Cann_1->SetFrameBorderMode(0);
-   
-   TH2F *HALU_p_vs_Q2__1 = new TH2F("HALU_p_vs_Q2__1","",100,0.8,3.8,100,-0.05,0.35);
-   HALU_p_vs_Q2__1->SetStats(0);
-
-   Int_t ci;      // for color index setting
-   TColor *color; // for color definition with alpha
-   ci = TColor::GetColor("#000099");
-   HALU_p_vs_Q2__1->SetLineColor(ci);
-   HALU_p_vs_Q2__1->GetXaxis()->SetTitle("Q^{2} [GeV^{2}]");
-   HALU_p_vs_Q2__1->GetXaxis()->CenterTitle(true);
-   HALU_p_vs_Q2__1->GetXaxis()->SetNdivisions(605);
-   HALU_p_vs_Q2__1->GetXaxis()->SetLabelFont(22);
-   HALU_p_vs_Q2__1->GetXaxis()->SetLabelSize(0.05);
[…]

### 2021-05-01 eg6-letters/long-paper/prc-dvcshelium.tex
Edits for PRC

@@
 measurement of the nuclear DVCS is challenging experimentally and the first attempts by 
-the HERMES Collaboration \cite{Airapetian:2009cga} led to controversial conclusions. We present here
+the HERMES Collaboration \cite{Airapetian:2009cga} to unravel an $A$ dependent nuclear
+effect have been unsuccessful. We present here
 in detail the more recent measurements by the CLAS Collaboration, which has been already partially presented
@@
 reach strong conclusions about possible nuclear effects. Yet, in the coherent DVCS case a rather
-strong effect was expected, leading to a conflict between the HERMES results and theoretical
+strong effect was expected, leading to an apparent conflict between the HERMES results and theoretical
 expectations.
@@
 
-An issue with the HERMES measurement and how it is obtained from data has been raised in
-Ref. \cite{Guzey:2003jh} to explain the discrepancy with theoretical expectations.
-The main concern is that the DVCS process is not fully detected and the scattered target
+A characteristic of the HERMES measurement and how it was obtained from data can however
+explain the discrepancy with theoretical expectations~\cite{Guzey:2003jh,Airapetian:2009cga}.
+The main point being that the DVCS process is not fully detected and the scattered target
 is instead reconstructed through a missing mass measurement of the other reaction products. The 
@@
 coherent and incoherent channels properly. 
-Instead, the results are labeled "coherent enriched" and "incoherent enriched" at low and high 
+Thus, the results are labeled "coherent enriched" and "incoherent enriched" at low and high 
 $-t$, respectively. This label is based on the assumption that the very different behavior of the
@@
 
-Altogether, large error bars and the failure to properly separate the coherent and 
+Altogether, large error bars and the impossibility to properly separate the coherent and 
 incoherent channels have strongly impaired the interpretation of the measurement 
@@
 Altogether, CLAS provided a large acceptance for momenta 
-starting at 200 MeV. The nuclear DVCS experiment took place from October to December 2009
+starting at 200~MeV. The nuclear DVCS experiment took place from October to December 2009
 at an electron beam energy of 6.064 GeV, with the beam intensity varying
@@
 The recoil helium nuclei from coherent DVCS are mostly emitted between 150 
-and 200 MeV at the beam energy of 6~GeV. Therefore, a specific detector was 
+and 200~MeV at the beam energy of 6~GeV. Therefore, a specific detector was 
 needed to detect them. To design the present setup, inspiration was drawn from the 

### 2021-07-22 eg6-letters/long-paper/prc-dvcshelium.tex
Update figures for PRC

@@
 	\caption{The measured (filled blue) and simulated (red) distributions of
-	coherent exclusive $\pi^0$ production as a function of $x$, $Q^2$, $-t$ and $\phi$.}
+	coherent exclusive $\pi^0$ production as a function of $x$ (panel a), 
+        $Q^2$ (panel b), $-t$ (panel c) and $\phi$ (panel d).}
 \label{fig:CohPi0Simul}
@@
 	\caption{The measured (filled blue) and simulated (red) distributions of
-	incoherent exclusive $\pi^0$ production as a function of $x$, $Q^2$, $-t$ and $\phi$.}
+	incoherent exclusive $\pi^0$ production as a function of $x$ (panel a), 
+        $Q^2$ (panel b), $-t$ (panel c) and $\phi$ (panel d).}
 \label{fig:InCohPi0Simul}
@@
 We also evaluated the impact of changing the binning in $\phi$ on the extraction of the BSA
-at 90°. The beam polarization was measured using M\o{}ller scattering runs, the uncertainty was 
+at 90 degrees. The beam polarization was measured using M\o{}ller scattering runs, the uncertainty was 
 estimated based on the known precision of the dedicated apparatus and the spread 
@@
 \caption{The systematic uncertainties on the measured coherent and incoherent 
-BSAs at $\phi = 90^{\circ}$.}
+BSAs at $\phi = 90$~deg.}
 \label{Table:systematic_uncertainties}
@@
 \includegraphics[width=15cm]{t_tprime_ALU_90_p_shortscenrario.pdf}
-	\caption{The BSA at 90° ($A_{LU}^{Incoh} (90^\circ)$) as a
-	function of $Q^2$, $x_{B}$ and $-t$, using the photon based $t$ definition (red)
+	\caption{The BSA at 90 degrees ($A_{LU}^{Incoh} (90~\mathrm{deg})$) as a
+	function of $Q^2$ (panel a), $x_{B}$ (panel b) and $-t$ (panel c), using the photon based $t$ definition (red)
 	and the proton based $t^\prime$ definition (black).}
@@
 \includegraphics[width=16cm]{Coherent_ALU_phi_90.pdf}
-\caption{The BSA at 90° as a function of $Q^2$ (top panel), $x$ (middle panel) and $-t$ (lower panel).
+\caption{The BSA at 90 degrees as a function of $Q^2$ (panel a), $x$ (panel b) and $-t$ (panel c).
 	Our results are shown with black squares, HERMES results 
@@
 
-We show the extraction of the BSA at 90° in Fig. \ref{fig:CohALU90} together with the 
+We show the extraction of the BSA at 90 degrees in Fig. \ref{fig:CohALU90} together with the 
 past HERMES Collaboration results~\cite{Airapetian:2009cga}. Two models are compared to the 
@@
 \includegraphics[width=14cm]{Coherent_CFF.pdf}
-	\caption{The imaginary (top panels) and real (bottom panels) parts of the helium-4
-	CFF $\mathcal{H}_A$ as a function of $Q^2$ (left panels), $x$ (middle panels) and 
-	$-t$ (right panels). The red full line is the theoretical calculation by 
+	\caption{The imaginary part of the helium-4 CFF $\mathcal{H}_A$ is shown as 
+        a function of $Q^2$ (panel a), $x$ (panel b) and 
+	$-t$ (panel c). The real part of the helium-4 CFF $\mathcal{H}_A$ is shown as 
+        a function of $Q^2$ (panel d), $x$ (panel e) and 
+	$-t$ (panel f). The red full line is the theoretical calculation by 
 	Guzey {\it et al.}~\cite{Guzey:2003jh,Guzey:2008th}, the black dashed line is the same calculation 
@@
 free proton, with a clear domination of their sinusoidal component. To compare the data to 
-models, we extract the BSA at 90° with a fit of the form $\frac{\alpha \sin(\phi)}{1+\beta \cos(\phi)}$.
-
-The asymmetries at 90° are presented in Fig. \ref{fig:IncALU} together with the theoretical
+models, we extract the BSA at 90 degrees with a fit of the form $\frac{\alpha \sin(\phi)}{1+\beta \cos(\phi)}$.
+
+The asymmetries at 90 degrees are presented in Fig. \ref{fig:IncALU} together with the theoretical
 calculation by the same groups as presented in Fig. \ref{fig:CohALU90}. We observe a 
@@
 \includegraphics[width=7.4cm]{ALU_90_p_vs_x_shortscenrario.pdf}
-	\caption{The BSA at 90° as a function of  $Q^2$ (top left), $x$ (top right) and 
-	$-t$ (bottom). Our measurement is represented with black squares and the HERMES 
+	\caption{The BSA at 90 degrees as a function of $Q^2$ (panel a), $-t$ (panel b) 
+        and $x_B$ (panel c). Our measurement is represented with black squares and the HERMES 
 	measurement \cite{Airapetian:2009cga} with green circles. The theoretical prediction 
@@
 	\caption{DVCS BSA ratio of the bound proton to the free proton as a function of 
-	$Q^2$ (top left), $x$ (top right) and $-t$ (bottom). The present measurement is 
+	$Q^2$ (panel a), $-t$ (panel b) and $x_B$ (panel c). The present measurement is 
 	represented with black squares and the HERMES 
@@
          \hline
- $\langle Q^{2} \rangle$ & $\langle x_{B} \rangle$ & $\langle -t \rangle$  & $A_{LU}$(90$^{\circ}$) $\pm$ stat. $\pm$ syst.\\
+ $\langle Q^{2} \rangle$ & $\langle x_{B} \rangle$ & $\langle -t \rangle$  & $A_{LU}$(90 deg) $\pm$ stat. $\pm$ syst.\\
  (GeV$^{2}$) &           & (GeV$^{2}$) &  \\
@@
   \end{tabular}
-  \caption{Values of the coherent $A_{LU}$(90$^{\circ}$) in $Q^2$ (top block), $x_B$ (middle block), and $-t$ (bottom block) bins. }
+  \caption{Values of the coherent $A_{LU}$(90 deg) in $Q^2$ (top block), $x_B$ (middle block), and $-t$ (bottom block) bins. }
   \label{table:Coh_BSA_90}
@@
 \hline
- $\langle Q^{2} \rangle$ & $\langle x_{B} \rangle$ & $\langle -t \rangle$  & $A_{LU}$(90$^{\circ}$) $\pm$ stat. $\pm$ syst.\\
+ $\langle Q^{2} \rangle$ & $\langle x_{B} \rangle$ & $\langle -t \rangle$  & $A_{LU}$(90 deg) $\pm$ stat. $\pm$ syst.\\
  (GeV$^{2}$) &           & (GeV$^{2}$) &  \\
@@
  \end{tabular}
- \caption{Values of the incoherent $A_{LU}$(90$^{\circ}$) in $Q^2$ (top block), $x_B$ (middle block), and $-t$ (bottom block) bins.}
+ \caption{Values of the incoherent $A_{LU}$(90 deg) in $Q^2$ (top block), $x_B$ (middle block), and $-t$ (bottom block) bins.}
  \label{table:InCoh_BSA_90}
